### 2024-07-17 articolo/main.tex
prima definizione

\documentclass{article}
\usepackage{graphicx, amssymb,amsthm, amsmath, tikz-cd}

\usepackage[english]{babel}

\theoremstyle{definition}
\newtheorem{definition}{Definizione}

\theoremstyle{definition}
\newtheorem{example}{Esempio}

\newcommand{\id}[1]{id_{#1}}

\begin{document}

\section{Concetti di di base}

Questa sezione presenta i concetti di base di teoria delle cateogrie [...]

\subsection{Categorie}

	\begin{definition}[Categorie]
		Una \emph{categoria $\mathcal{C}$} è composta da:
		\begin{enumerate}
			\item una collezione di \emph{oggetti} $Ob(\mathcal{C})$;
			\item una collezione di \emph{morfismi} $Mor(\mathcal{C})$;
			\item due operazioni che assegnano ad ogni morfismo $f$ un oggetto $dom\ f$, detto \emph{dominio} e un oggetto $cod\ f$, detto \emph{codominio}, denotando con $f: A \rightarrow B$ il fatto che $dom\ f = A \text{ e } cod\ f = B$; la collezione di tutti i morfismi da un oggetto $A$ ad un oggetto $B$ in $\mathcal{C}$ è denotato con $\mathcal{C}(A, B)$;
			\item un operatore di composizione che assegna ad ogni coppia di morfismi $f$, $g$ tali che $dom\ g = cod\ f$, un morfismo \emph{composto} $g \circ f: dom\ f \rightarrow cod\ g$, tale da soddisfare
				\[
					h \circ (g \circ f) = (h \circ g) \circ f
				\]
				per ogni $f$, $g$, $h$ tali che $dom\ g = cod\ f \text{e} dom\ h = cod\ f$;
			\item per ogni oggetto $A$, un morfismo \emph{identità} $\id{A}: A \rightarrow A$ tale che:
				\[
					\id{B} \circ f = f = f \circ \id{A}
				\]
				per ogni $f: A \rightarrow B$.
		\end{enumerate}
	\end{definition}

	[puntualizzazione sull'utilizzo improprio del temine "collezione" nella definizione].

	Un primo esempio interessante è il seguente, nonché fonte di intuizioni per buona parte di questa presentazione della teoria delle categorie.

	\begin{example}
		La categoria $\textbf{Set}$ è la categoria degli insiemi e delle funzioni totali tra essi. La composizione di morfismi corrisponde alla composizione di funzioni, e i morfismi identità corrispondono alle funzioni identità.
	\end{example}

\end{document}

### 2024-07-17 articolo/main.tex
prima definizione
numerazione definizioni, esempi ecc
da diagrammi a mono, epi, iso

@@
 
-\theoremstyle{definition}
-\newtheorem{definition}{Definizione}
+\theoremstyle{plain}
+\newtheorem{theorem}{Teorema}[section]
+\newtheorem{obs}[theorem]{Osservazione}
+\newtheorem{prop}[theorem]{Proposizione}
 
 \theoremstyle{definition}
-\newtheorem{example}{Esempio}
+\newtheorem{definition}[theorem]{Definizione}
+\newtheorem{example}[theorem]{Esempio}
 
 \newcommand{\id}[1]{id_{#1}}
+
+\tikzcdset{row sep/normal=5em}
+\tikzcdset{column sep/normal=5em}
 
@@
 
-	\begin{definition}[Categorie]
+	\begin{definition}[Categorie, sottocategorie]
 		Una \emph{categoria $\mathcal{C}$} è composta da:
@@
 			\item una collezione di \emph{morfismi} $Mor(\mathcal{C})$;
-			\item due operazioni che assegnano ad ogni morfismo $f$ un oggetto $dom\ f$, detto \emph{dominio} e un oggetto $cod\ f$, detto \emph{codominio}, denotando con $f: A \rightarrow B$ il fatto che $dom\ f = A \text{ e } cod\ f = B$; la collezione di tutti i morfismi da un oggetto $A$ ad un oggetto $B$ in $\mathcal{C}$ è denotato con $\mathcal{C}(A, B)$;
-			\item un operatore di composizione che assegna ad ogni coppia di morfismi $f$, $g$ tali che $dom\ g = cod\ f$, un morfismo \emph{composto} $g \circ f: dom\ f \rightarrow cod\ g$, tale da soddisfare
+			\item due operazioni che assegnano ad ogni morfismo $f$ un 
+				oggetto $dom\ f$, detto \emph{dominio} e un oggetto $cod\ f$, detto \emph{codominio}, 
+				denotando con $f: A \rightarrow B$ il fatto che $dom\ f = A \text{ e } cod\ f = B$; 
+				la collezione di tutti i morfismi da un oggetto $A$ ad un oggetto $B$ in $\mathcal{C}$ è 
+				denotato con $\mathcal{C}(A, B)$;
+			\item un operatore di composizione che assegna ad ogni coppia di morfismi $f$, $g$ tali che 
+				$dom\ g = cod\ f$, un morfismo \emph{composto} $g \circ f: dom\ f \rightarrow cod\ g$, 
+				tale da soddisfare
 				\[
@@
 				\]
-				per ogni $f$, $g$, $h$ tali che $dom\ g = cod\ f \text{e} dom\ h = cod\ f$;
+				per ogni $f$, $g$, $h$ tali che $dom\ g = cod\ f \text{ e } dom\ h = cod\ f$;
 			\item per ogni oggetto $A$, un morfismo \emph{identità} $\id{A}: A \rightarrow A$ tale che:
@@
 				per ogni $f: A \rightarrow B$.
+		\end{enumerate}
+
+		Una categoria $\mathcal{B}$ è una \emph{sottocategoria} di $\mathcal{C}$ se
+		\begin{enumerate}
+			\item ogni oggetto di $\mathcal{B}$ è un oggetto di $\mathcal{C}$;
+			\item se $B$ e $B'$ sono oggetti di $\mathcal{B}$, $\mathcal{B}(B, B') \subseteq \mathcal{C}(B, B')$;
+			\item morfismi composti e identità di $\mathcal{B}$ sono gli stessi di $\mathcal{C}$.
 		\end{enumerate}
@@
 
+	Un modo di rappresentare una categoria $\mathcal{C}$ è mediante \emph{diagrammi}, come illustrato di seguito,
+	i cui vertici sono etichettati con oggetti di $\mathcal{C}$, e le frecce con morfismi di $f$, dove una 
+	freccia $f$ da $A$ a $B$ rappresenta il morfismo $f: A \rightarrow B$. 
+	Un diagramma è detto \emph{commutativo} se, per ogni coppia di vertici $A$, $C$, 
+	ogni percorso da $A$ a $C$ determina lo stesso morfismo:
+	\[
+		\begin{tikzcd}
+			A \arrow[r, "f"] \arrow[rd, "h" swap] & B  \arrow[d, "g"] \\
+			& C 
+		\end{tikzcd}
+	\]
+	in questo caso, la commutatività di tale diagramma esprime l'uguaglianza $f \circ g = h$.
+
+	\begin{definition}[Monomorfismi, epimorfismi, isomorfismi]
+		Un morfismo $m:B \rightarrow C$ in una categoria $\mathcal{C}$ è un \emph{monomorfismo}
+		(oppure è \emph{mono}) se, per ogni coppia di morfismi $f, g: A \rightarrow B$ in $\mathcal{C}$, 
+		l'uguaglianaza $m \circ f = m \circ g$ implica $f = g$. \-
+		Un morfismo $e: C \rightarrow D$ in $\mathcal{C}$ è un \emph{epimorfismo} (oppure è \emph{epi}) se
+		l'uguaglianza $f \circ e = g \circ e$ implica $f = g$. \-
+		Un morfismo $\phi: A \rightarrow B$ in $\mathcal{C}$ è un \emph{isomorfismo} se esiste in $\mathcal{C}$
+		un morfismo $\psi: B \rightarrow A$ tale che $\psi \circ \phi = \id{A}$ e $\phi \circ \psi = \id B$.
+
+	\end{definition}
+
+	Ancora una volta, è possibile utilizzare la categoria degli insiemi per avere un'intuizione efficace.
+
+	\begin{example}
+		In $\textbf{Set}$, un monomorfismo $m: A \rightarrow B$ è una funzione iniettiva dall'inieme $A$ all'insieme $B$,
+		un epimorfismo $e: C \rightarrow D$ è una funzione surgettiva da $C$ a $D$, mentre un isomorfismo $\phi: E \rightarrow F$
+		è una corripondenza biunivoca tra gli insiemi $E$ ed $F$
+	\end{example}
+
+	[Non andrei troppo nel dettaglio con gli esempi]
+
 \end{document}

### 2024-07-18 articolo/main.tex
aggiustamento typos

@@
 			\item ogni oggetto di $\mathcal{B}$ è un oggetto di $\mathcal{C}$;
-			\item se $B$ e $B'$ sono oggetti di $\mathcal{B}$, $\mathcal{B}(B, B') \subseteq \mathcal{C}(B, B')$;
+			\item se $A$ e $B$ sono oggetti di $\mathcal{B}$, $\mathcal{B}(A, B) \subseteq \mathcal{C}(A, B)$;
 			\item morfismi composti e identità di $\mathcal{B}$ sono gli stessi di $\mathcal{C}$.
 		\end{enumerate}
+
+		Una sottocategoria $\mathcal{B}$ di $\mathcal{C}$ si dice \emph{completa} se, per ogni coppia di oggetti $A$, $B$,si ha
+		$\mathcal{B}(A, B) = \mathcal{C}(A, B)$.
+
 	\end{definition}
@@
 
-	Un primo esempio interessante è il seguente, nonché fonte di intuizioni per buona parte di questa presentazione della teoria delle categorie.
+	Un primo esempio interessante è il seguente, nonché fonte di intuizioni per buona parte 
+	di questa presentazione della teoria delle categorie.
 
@@
 		La categoria $\textbf{Set}$ è la categoria degli insiemi e delle funzioni totali tra essi. 
-		La composizione di morfismi corrisponde alla composizione di funzioni, e i morfismi identità corrispondono alle funzioni identità.
+		La composizione di morfismi corrisponde alla composizione di funzioni, 
+		e i morfismi identità corrispondono alle funzioni identità.
 	\end{example}
@@
 	\]
-	in questo caso, la commutatività di tale diagramma esprime l'uguaglianza $f \circ g = h$.
+	in questo caso, la commutatività di tale diagramma esprime l'uguaglianza $g \circ f = h$.
 
@@
 
-	Ancora una volta, è possibile utilizzare la categoria degli insiemi per avere un'intuizione efficace.
+	Le definizioni di monomorfismo, epimorfismo e isomorfismo sono una generalizzazione di un concetto ben noto
+	in teoria degli insiemi, come illustra il seguente esempio.
 
 	\begin{example}
-		In $\textbf{Set}$, un monomorfismo $m: A \rightarrow B$ è una funzione iniettiva dall'inieme $A$ all'insieme $B$,
-		un epimorfismo $e: C \rightarrow D$ è una funzione surgettiva da $C$ a $D$, mentre un isomorfismo $\phi: E \rightarrow F$
+		In $\textbf{Set}$, un monomorfismo $m: A \rightarrow B$ è una 
+		funzione iniettiva dall'inieme $A$ all'insieme $B$,
+		un epimorfismo $e: C \rightarrow D$ è una funzione surgettiva 
+		da $C$ a $D$, mentre un isomorfismo $\phi: E \rightarrow F$
 		è una corripondenza biunivoca tra gli insiemi $E$ ed $F$

### 2024-07-18 articolo/main.tex
aggiustamento

@@
 
-		Una sottocategoria $\mathcal{B}$ di $\mathcal{C}$ si dice \emph{completa} se, per ogni coppia di oggetti $A$, $B$,si ha
+		Una sottocategoria $\mathcal{B}$ di $\mathcal{C}$ si dice \emph{completa} se, 
+		per ogni coppia di oggetti $A$, $B$,si ha
 		$\mathcal{B}(A, B) = \mathcal{C}(A, B)$.
@@
 		e i morfismi identità corrispondono alle funzioni identità.
+		La categoria $\textbf{Fin}$ i cui oggetti sono insiemi finiti e i cui morfismi sono 
+		funzioni tra insiemi finiti è una sottocategoria completa di $\textbf{Set}$.
 	\end{example}
@@
 
+	\begin{definition}[Oggetti iniziali e terminali]
+		Sia $\mathcal{C}$ una categoria. 
+		Un oggetto $0$ in $\mathcal{C}$ è detto \emph{oggetto iniziale} se, 
+		per ogni oggetto $A$, esiste esattamente un morfismo da $0$ ad $A$ in $\mathcal{C}$.
+		Un oggetto $1$ si dice \emph{oggetto terminale} se, per ogni oggetto $A$, 
+		esiste un unico morfismo da $A$ ad $1$ in $\mathcal{C}$.  
+	\end{definition}
+
 \end{document}

### 2024-07-21 articolo/main.tex
funtori, trasformazioni naturali

@@
 
+	[...]
+
+\section{Funtori, trasformazioni naturali e categorie funtore}
+
+	Date due categorie $\mathcal{C}$ e $\mathcal{D}$, 
+	un funtore $F: \mathcal{C} \rightarrow \mathcal{D}$ 
+	è una mappa tra categorie, mappando ogni oggetto $A$ di $\mathcal{C}$ in un oggetto $F(A)$ di $\mathcal{D}$
+	e ogni morfismo $f: A \rightarrow B$ di $\mathcal{C}$ in un morfismo $F(f): F(A) \rightarrow F(B)$ in $\mathcal{D}$ e tale che:
+	\begin{itemize}
+		\item $F(\id{A}) = \id{F(A)}$;
+		\item $F(g \circ f) = F(g) \circ F(f)$.
+	\end{itemize}
+
+	Dati due funtori $F \text{,} G : \mathcal{C} \rightarrow \mathcal{D}$, una \emph{trasformazione naturale}
+	$\eta: F \rightarrow G$ è una mappa tra funtori che 
+	che assegna ad ogni oggetto $A$ di $\mathcal{C}$ un morfismo $\eta_A:F(A)\rightarrow G(A)$ in $\mathcal D$ tale che
+	per ogni morfismo $f: A \rightarrow B$ in $\mathcal C$ il seguente diagramma in $\mathcal D$ commuti: 
+	\[
+		\begin{tikzcd}
+			F(A) \arrow[r, "{\eta_A}"] \arrow[d, "F(f)" swap]& G(A) \arrow[d, "G(f)"] \\
+			F(B) \arrow[r, "{\eta_B}" swap] & G(B)
+		\end{tikzcd}
+	\]
+
 \end{document}

### 2024-08-05 final_1/Tesi/main.tex
minima

\documentclass[a4paper, twoside,openright]{report}
\usepackage[T1]{fontenc} % Font encoding, T1 = it
\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
\usepackage[english]{babel} % Lingua principale italiano, con parti in inglese
\usepackage{graphicx} % Per includere immagini esterne
\usepackage{lipsum} % genera testo fittizio
\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento
\usepackage[fontsize=13pt]{scrextend} %dimensione font

\usepackage{titlesec} %indice

\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
\pagestyle{headings}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{obs}[theorem]{Observation}

% General Setting diagrams
\usepackage{tikz-cd} %diagrammi
\tikzcdset{row sep/normal=5em}
\tikzcdset{column sep/normal=5em}
\tikzcdset{every label/.append style = {font = \small}}

\begin{document}

\newcommand{\cat}[1]{\mathscr{#1}}
\newcommand{\Ob}{\mathcal{O}b}
\newcommand{\Hom}{\mathcal{H}om}
\newcommand{\Set}{\mathbf{Set}}
\newcommand{\initial}{\textbf 0}
\newcommand{\terminal}{\mathds{1}}

% input file frontespizio.tex
% \input{frontespizio}

\tableofcontents

% \chapter*{Introduction}
% [TODO]

\chapter{Background}

In this chapter will be defined the building blocks for this work, almost entirely based on categories.
The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts. This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.

\section{Basic Notions}

%The very fist concept to get familiar with is what is a category. We can see a category as a general construction that can provide any level of abstraction needed. In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something. The definition is about what a category is composed by, and how the objects in it interact between themselves.

This section is all about basic definitions and examples, to get familiar with the formalism of categories.

\subsection{Categories}

\begin{definition}[Category]\label{def:category}
    A \emph{category} $\cat{C}$ comprises:
    \begin{enumerate}
        \item A collection of \emph{objects} $\Ob(\cat{C})$;
        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$.
    \end{enumerate}
    For each morphism $f \in \Hom(\cat{C})$, there are two operators $dom$ and $cod$ which map every morphism to two objects, respectively, its \emph{domain} and its \emph{codomain}. In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$. The collection of all morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$. The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
    $$
        h \circ (g \circ f) = (h\circ g) \circ f
    $$
    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
    \[
        id_B \circ f = f = f \circ id_A 
    \]
\end{definition}

The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.

\begin{example}\label{ex:1_cat}
    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$. In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
\end{example}

To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in wich the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
    \[
    \begin{tikzcd}
        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
        W \arrow[r, "f" swap] & Y        
    \end{tikzcd}
    \]
The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
A more rigorous definition of what a diagram is will be given later (Definition~\ref{def:diagram}).

\begin{example}
    It is easy to see that taking sets as objects and total functions as arrows, we obtain a category. In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative. For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $\forall a \in A: id_A(a) = a$.
    This category is usually denoted as $\Set$.
\end{example}

\begin{remark}\label{rem:small_cats}
    It is important to note that the Definition~\ref{def:category} above does not specify what kind of collections are, for a category $\cat{C}$, $\Ob(\cat{C})$ and $\Hom(\cat{C})$.
    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox. It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
\end{remark}

\subsection{Mono, Epi and Iso}

Between all morphisms of a category, it is possible to distinguish some that have certain properties, as well as functions between sets can be surjective, injective or bijective.

\begin{definition}[Monomorphism]\label{def:mono}
    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
\end{definition}

\begin{definition}[Epimorphism]\label{def:epi}
    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
\end{definition}

\begin{definition}[Isomorphism]\label{def:iso}
    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$. Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
\end{definition}

\begin{example}
    In $\Set$, monomorphisms are injective functions, epimorphism are surjective functions and isomorphisms are bijections.
\end{example}

\subsection{Categories from other categories}

Starting from a category $\cat{C}$, it is possible to construct some other categories with interesting property.
An example is the \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
Each definition in category theory has a dual form. In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$. Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite{pierce91}.

Another important notion is that of subcategory.
\begin{definition}[Subcategory]
    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
    \begin{enumerate}
        \item each object of $\cat{D}$ is an object of $\cat{C}$;
        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
        \item composites and identities of $\cat{D}$ are the same of $\cat{C}$
    \end{enumerate}

    If the inclusion at~\ref{inc} is an equality (i.e. $\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
\end{definition}

An object of a category can raise a category itself. This is the case of slice (and coslice) categories.

\begin{definition}[Slice Category]\label{def:slice_cat}
    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ is given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
    \[
        \begin{tikzcd}
            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
            & X
        \end{tikzcd}
    \]
    -- i.e, $g \circ \phi = f$.
    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
    \[
        \begin{tikzcd}
            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
            & X & 
        \end{tikzcd}
    \]

    The dual definition is \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), obtained by taking as objects all the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ such that $g = \phi \circ f$. 
\end{definition}

Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.

\begin{definition}[Product category]
    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$. Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.

\end{definition}

\section{Functors, Natural transformations and Beyond}

A functor is a structure preserving map between categories.

\subsection{Functors}
\begin{definition}[Functor]
    Let $\cat{C}$ and $\cat{D}$ be categories. A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
    \begin{itemize}
        \item $F(id_{A}) = id_{F(A)}$;
        \item $F(g \circ f) = F(g) \circ F(f)$.
    \end{itemize}

    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
\end{definition}

\begin{example}
    A first example of functor is the \emph{identity functor}. Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself. 
\end{example}

Once defined what is a functor, we can give a more rigorous definition of diagram. Although this may seem extremely technical, it will be useful, especially in the definition of limits (Definition~\ref{def:limit}).

\begin{definition}[Diagram]\label{def:diagram}
    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
\end{definition}

\begin{example}\label{ex: span}
    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
    A span can be viewed as the generalization of relations between sets. In fact, in $\Set$, a span in a relation $R \subseteq A \times B$, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.

    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
\end{example}

Functor are often used to generalize some structural behaviour that constructions in categories have. An important example of this fact is the universal property. The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions.~\cite{Herrlich_Strecker_1979}

\begin{definition}[Universal property]\label{def:univ_prop}
    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$. A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
    \[
        \begin{tikzcd}
            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
            & F(A') & A'
        \end{tikzcd}
    \]

    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.

    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
    \[
        \begin{tikzcd}
            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
            A & G(A) \arrow[r, "u" swap] & B
        \end{tikzcd}
    \]
\end{definition}

Given two functors which share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of "changing the functor acting on that object".

\subsection{Natural transformations}

\begin{definition}[Natural transformation]
    Let $F,G : \cat {C \rightarrow D}$ be two functors. A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$ is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
    \[
        \begin{tikzcd}
            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
        \end{tikzcd}
    \]
    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.

    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$. In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.    
\end{definition}

\begin{obs}\label{obs:comp_assoc_nat_tran}
It is easy to see that, given two natural transformation $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$. This follows by the fact that the diagram
\[
        \begin{tikzcd}
            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
                & H(A) \arrow[d, "H(f)"] \\
            F(B) \arrow[r, "{\eta_B}"swap]
                & G(B) \arrow[r, "{\theta_B}" swap]
                & H(B)
        \end{tikzcd}
\]
commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is even possible to show associativity of composition of natural transformations.
\end{obs}

\subsection{Functor Category}

The Observation~\ref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects. This led us to define a particular kind of category, in which objects are functors between two fixed categories, and arrow are natural transformations.

\begin{definition}[Functor Category]\label{def:functor_category}
    Let $\cat C$ and $\cat D$ be two categories. The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
\end{definition}

A functor with a small category as domain (Remark~\ref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category. Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e. $[\cat C, \Set]$.

\begin{remark}
    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$. This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition we give above.
\end{remark}

\subsection{Comma categories}

Functor constructions allow us to generalise basic concept already seen for categories. An important example of this fact are comma categories, a more general notion of slice categories (Definition~\ref{def:slice_cat}).

% \begin{definition}[Comma category]
%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
%     \[
%         \begin{tikzcd}
%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
%             F(C) \arrow[r, "g"] & G(B)
%         \end{tikzcd}
%     \]
%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
% \end{definition}

\begin{definition}[Comma category]\label{def:comma_category}
    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
    \[
        \begin{tikzcd}
            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
        \end{tikzcd}
    \]
    Then, the \emph{slice category $(S \downarrow T)$} is the category in which: 
    \begin{itemize}
        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
        \[
            \begin{tikzcd}
            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
            T(C) \arrow[r, "g"] & T(B)
            \end{tikzcd}
        \]
        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
    \end{itemize}
\end{definition}

Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in Example~\ref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
\[
    \begin{tikzcd}
        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
    \end{tikzcd}
\]
It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.

At the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C$.

\section{Universal Constructions}

\subsection{Initial and Terminal Objects}

The next definitions are about \emph{universal constructions}. The simplest ones are the notion of initial and, dually, terminal objects.

\begin{definition}[Initial and terminal object]
    An object $A$ of a category $\cat C$ is said to be \emph{initial} if, for each other object $B$ of $\cat C$, there exists a unique morphism from $A$ to $B$.
    Dually, an object $Z$ is said to be a terminal object in a category $\cat C$ if, for any other object $X$ of $\cat C$, there exists a unique morphism from $X$ to $Z$.
    An initial object of a category is indicated by the symbol $\initial$, and a terminal object is indicated by the symbol $\terminal$.
\end{definition}

\begin{obs}\label{obs:terminal_are_isomorph}
    It makes sense to refer to an initial (and terminal) object as \emph{the} initial (\emph{the} terminal) object. Suppose indeed that $\initial$ and $\initial'$ are two distinct initial objects of a category $\cat C$. Then, there exists a unique morphism from $\initial$ to $\initial'$, say $f$. At the same way, it must exist a unique morphism from $\initial'$ to $\initial$, say $g$. Then, $g\circ f$ must be exactly $id_{\initial}$, and $f \circ g = id_{\initial'}$, and then they are isomorphic. The same argument works for the terminal object.
    The reason why this argument works is because initial and terminal objects have the \emph{universal property} (Definition~\ref{def:univ_prop}), [Integrare qui!]
\end{obs}

\begin{example}\label{ex:set_init_term}
    In $\Set$, the initial object is the empty set $\varnothing$, because, for each set $S$, there exists the empty function from $\varnothing$ to $S$. The terminal object of $\Set$ is the singleton $\{ \bullet \}$, because there is exactly one function from a set $S$ to $\{ \bullet \}$, namely, the function which sends each $s \in S$ to $\bullet$. It is possible to visualize the Observation~\ref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective.
\end{example}

We now illustrate a result on functor categories (Definition~\ref{def:functor_category}) that will be useful later.

\begin{prop}
    Let $\cat D$ be a category. If $\cat D$ has an initial object, then, for any category $\cat C$, $[\cat{C, D}]$ has an initial object. If $\cat D$ has a terminal object, then, for any category $\cat C$, $[\cat{C, D}]$ has a terminal object.
\end{prop}

\begin{proof}
    Let $\initial_{\cat{D}}$ be the initial object of $\cat D$,  and consider the constant functor $I(f) = id_{\initial_{\cat D}}$ for all $f \in \Hom(\cat C)$. Then, for any $G: \cat{C \rightarrow D}$, $\eta: I \rightarrow G$, defining $\eta_A$ as the \emph{unique morphism from $\initial_{\cat D}$ to $G(A)$} for each $A \in \Ob(\cat C)$, is a natural transformation $I \dot\rightarrow G$, as the diagram below shows:
    \[
        \begin{tikzcd}
            I(A)=\initial_{\cat D} 
                    \arrow[r, "{\eta_A}"]
                    \arrow[d, "{I(f) = id_{\initial_{\cat D}}}" swap] &
            G(A)
                    \arrow[d, "G(f)"] \\
            I(A') = \initial_{\cat D}
                    \arrow[r, "{\eta_{A'}}" swap] &
            G(A')
        \end{tikzcd}
    \]
    for each $f: A \rightarrow A'$, the square above must commute, since there is only one morphism from $\initial_{\cat D}$ to $G(A')$. For the same reason, $\eta$ is the only natural transformation from $I$ to $G$, being indeed the initial object of $[\cat{C, D}]$.

    Defining $T(f) = id_{\terminal_{\cat D}}$ for each $f \in \Hom(\cat C)$. Then, $\theta:F\rightarrow T$, for any $F: \cat{C \rightarrow D}$, defining $\theta_A$ as the \emph{unique morphism from $F(A)$ to $\terminal_{\cat{D}}$} is a natural transformation due to the commutativity of the following diagram for each $f: A \rightarrow A'$:
    \[
        \begin{tikzcd}
            F(A) \arrow[r, "{\theta_A}"] \arrow[d, "F(f)" swap] &
            T(A) = \terminal_{\cat D} \arrow[d, "{T(f) = id_{\terminal_{\cat D}}}"] \\
            F(A') \arrow[r, "{\theta_{A'}}" swap] & T(A') = \terminal_{\cat D}
        \end{tikzcd}
    \]
    Hence, $\theta$ is the unique natural transformation from $F$ to $T$, and $T$ is the terminal object of $[\cat{C, D}]$.
\end{proof}

In particular, every presheaf has an initial and a terminal object, because $\Set$ do (Example~\ref{ex:set_init_term}).

\subsection{Products and Coproducts}

More complex constructions are products (and, dually, coproducts).

\begin{definition}[Product]
    A \emph{product} of two objects $A$ an $B$ is an object $A \times B$ together with two \emph{projection arrows} $\pi_1:A\times B \rightarrow A$ and $\pi_2: A \times B \rightarrow B$ such that, for every object $C$ and pair of arrows $f: C \rightarrow A$, $g: C \rightarrow B$, there is exactly one arrow $\langle f, g \rangle : c \rightarrow A \times B$ making the diagram commutes
    \[
        \begin{tikzcd}
                    & C \arrow[dl, "f" swap] \arrow[d, dashed, "{\langle f, g \rangle}" description] \arrow[dr, "g"] & \\
                A   & A \times B  \arrow[l, "{\pi_1}"] \arrow[r, "{\pi_2}" swap]    &  B    
        \end{tikzcd}
    \]
   -- i.e., such that $\pi_1 \circ \langle f, g \rangle = f$ and $\pi_2 \circ \langle f, g \rangle  = g$.

\end{definition}

\begin{definition}[Coproduct]
    The dual of the product is the \emph{coproduct}.
    A coproduct of two objects $A$ and $B$ is an object $A + B$ together with two arrows $\iota_1:A\rightarrow A+B$, $\iota_2: B \rightarrow A + B$ such that, for every object $C$ and pair of arrows $f:A \rightarrow C$, $g:B \rightarrow C$, there is a unique arrow $[f, g] : A + B \rightarrow C$ such that the diagram commutes
    \[
        \begin{tikzcd}
            A \arrow[r, "{\iota_1}"] \arrow[dr, "f" swap] & A+B \arrow[d, dashed, "{[f,g]}" description] & B \arrow[l, "{\iota_2}" swap] \arrow[dl, "g"] \\
            & C & 
        \end{tikzcd}
    \]
    -- i.e., such that $[f, g] \circ \iota_1 = f$ and $[f, g] \circ \iota_2 = g$.
\end{definition}

\begin{example}
    $\Set$ have both products and coproduts. Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A + B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$. 
\end{example}

The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrow for each object in the product). We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.

Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction owns the universal property.

\subsection{Equalizers and Coequalzers}

The next notion is about a construction that make parallel arrows (i.e., two possibly distinct morphisms with the same domain and codomain) equal. In $\Set$, given two functions $f, g: A \rightarrow B$, such construction corresponds exactly to the restriction of the domain to the set of elements on which $f$ and $g$ are equal. Specifically, if we take the set $E = \{x \in A \mid f(x) = g(x)\}$, and we take the function $e: E \rightarrow A$ defined by $e(x) = x$, we obtain what is called an \emph{equalizer} for $f$ and $g$. In fact, $e$ is that function that make $f$ and $g$ be the same function -- i.e., $f \circ e = g \circ e$.
This concept can be generalized as follows.

\begin{definition}[Equalizer and Coequalizer]
    Let $f, g: A \rightarrow B$ be two arrows of a category $\cat C$. An \emph{equalizer} for $f$ and $g$ is pair $(E, e)$, where $E$ is an object and $e: E \rightarrow A$ is an arrow in $\cat C$ such that:
    \begin{enumerate}
        \item \label{eq_1} $ f \circ e = g \circ e$; and
        \item if $(E', e')$ is another pair that satisfies~\ref{eq_1}, then there exists a unique $h: E' \rightarrow E$ such that $e \circ h = e'$.
    \end{enumerate}
    \[
        \begin{tikzcd}
            E \arrow[r, "e"] & A \arrow[r, shift left, "f"] \arrow[r, shift right, "g" swap] & B \\
            E' \arrow[u, dashed, "k"] \arrow[ur, "e'" swap] & 
        \end{tikzcd}
    \]

    A \emph{coequalizer} of $f$ and $g$, dually, is a pair $(c, C)$, where $C$ is an object and $c: B \rightarrow C$ such that $c \circ f = c \circ g$, with the universal property.
\end{definition}

\subsection{Pullbacks and Pushouts}

Another (pair of) construction(s) one can find in a category, given two arrows, is the pullback (and the pushout).

\begin{definition}[Pullback, Pushout]
        A \emph{pullback} of two arrows $f: A \rightarrow C$ and $g: B \rightarrow C$ is a triple $(P, \pi_g, \pi_f)$ containing an object $P$ and a pair of arrows $\pi_g: P \rightarrow A$, $\pi_f: P \rightarrow B$ such that:
        \begin{enumerate}
            \item\label{pb_1} $f \circ \pi_g = g \circ \pi_f$; and
            \item if $(X, p, q)$, where $p: X \rightarrow A$ and $q: X \rightarrow B$, satisfies~\ref{pb_1}, then there is a unique $k:X \rightarrow P$ such that $p = \pi_g \circ k$ and $j = \pi_f \circ k$.
        \end{enumerate}
        \[
        \begin{tikzcd}
        X \arrow[drr, bend left=20, "q"] \arrow[ddr, bend right=20,"p" swap] \arrow[dr, dashed, "k"] & & \\
        & P  \arrow[d, "{\pi_g}" swap] \arrow[r, "{\pi_f}"] & B \arrow[d, "g"] \\
        & A  \arrow[r, "f" swap] & C
        \end{tikzcd}
    \]

    Dually, the \emph{pushout} of two arrows $f: A \rightarrow B$ and $g: A\rightarrow C$ is a triple $(\iota_g, \iota_f, I)$, where $I$ is an object and $\iota_g:B \rightarrow I$ and $\iota_f: C \rightarrow I$ are morphisms such that:
    \begin{enumerate}
        \item\label{po_1} $\iota_g \circ f = \iota_f \circ g$; and 
        \item if $(i, j, Y)$, where $i: B \rightarrow Y$ and $j: C \rightarrow Y$, satisfies~\ref{po_1}, then there is a unique $h: I \rightarrow Y$ such that $i = h \circ \iota_g$ and $j = h \circ \iota_f$.  
    \end{enumerate}
    \[\begin{tikzcd}
        A & C \\
        B & I \\
        && Y
        \arrow["g", from=1-1, to=1-2]
        \arrow["f" swap, from=1-1, to=2-1]
        \arrow["{{\iota_f}}", from=1-2, to=2-2]
        \arrow["j", bend left=20, from=1-2, to=3-3]
        \arrow["{{\iota_g}}" swap, from=2-1, to=2-2]
        \arrow["i" swap, bend right=20, from=2-1, to=3-3]
        \arrow["h", dashed, from=2-2, to=3-3]
    \end{tikzcd}\]
    {% \[
        %     \begin{tikzcd}
        %         Y & &\\
        %         & I \arrow[ul, dashed, "h"] & B \arrow[l, "{\iota_g}" swap] \arrow[ull, bend right=20, "i"swap] \\
        %         & C \arrow[u, "{\iota_f}"] \arrow[uul, bend left=20, "j"] & A \arrow[l, "g"] \arrow[u, "f" swap]
        %     \end{tikzcd}
        % \]
    }
\end{definition}

Pullbacks (and, dually pushouts) are construction slightly more general than products and equalizers. An intuition of what they represent is given by considering what is concretely a pullback in the category of sets.

\begin{example}
    In $\Set$, given two functions $f: A \rightarrow C$ and $g: B \rightarrow C$, a pullback of $f$ and $g$ exists and is exactly the set $P = \{(x, y) \in A \times B \mid f(x) = g(y)\}$, with $\pi_f : P \rightarrow B$ and $\pi_g : P \rightarrow C$ defined, respectively, by $\pi_f((x, y)) = y$ and $\pi_g((x, y)) = x$. In this way, we have then, $\forall (x, y) \in P$:
    \begin{align*}
        (f \circ \pi_g) ((x, y))
                    &= f(\pi_g((x, y)))     &&  \\
                    & = f(x)                &&  \textit{Definition of $\pi_g$} \\
                    & = g(y)                &&  (x, y) \in P \\
                    & = g(\pi_f((x, y)))    &&  \textit{Definition of $\pi_f$} \\
                    & = (g \circ \pi_f) ((x, y)) && 
    \end{align*}
    thus, $f \circ \pi_g = g \circ \pi_f$.
\end{example}

\subsection{Limits and Colimits}

We now introduce the notion that generalize all the universal constructions defined above. In fact, initial objects, products, equalizers an pullback (dually, terminal objects, coproducts, coequalizers and pushouts) can be seen as the particular case of a certain type of construction, called limit.

To define what a limit is, we first need to define cones.

\begin{definition}[Cones]
    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$. A \emph{cone} for $D$ is an object $X$ of $\cat C$, together with arrows $f_i : X \rightarrow D(i)$ indexed by $\cat I$ (i.e. one for each object $i$ of $\cat I$), such that, for each morphism $\alpha: i \rightarrow j$ of $\cat I$, the following diagram commutes:
    \[
        \begin{tikzcd}
            & X \arrow[dl, "{f_i}"swap] \arrow[dr, "{f_j}"] & \\
            D(i) \arrow[rr, "{D(\alpha)}" swap] & & D(j)
        \end{tikzcd}
    \]
    -- i.e., $D(\alpha) \circ f_i = f_j$.
    We denote such cone as $\{f_i: X \rightarrow D(i)\}$.

\end{definition}

\begin{obs}\label{obs:category_of_cones}
    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$ is defined to have cones for $D$ as objects and cone morphisms as arrows, where a con morphism $\phi: C \rightarrow C'$ from a cone $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
    \[
        \begin{tikzcd}
            X \arrow[rr, "{\phi}"] \arrow[dr, "{f_i}" swap] & & X' \arrow[dl, "{f_i'}"] \\
            & D(i) &
        \end{tikzcd}
    \]
\end{obs}

\begin{definition}[Limits]\label{def:limit}
    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$. A cone $\{f_i: X \rightarrow D(i)\}$ is a \emph{limit} provided that, for any other cone $\{f_{i}': X' \rightarrow D(i)\}$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
    \[
        \begin{tikzcd}
            X' \arrow[rr, dashed, "k"] \arrow[dr, "{f_i'}" swap] & & X \arrow[dl, "{f_i}"] \\
            & D(i) &
        \end{tikzcd}
    \]
    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$.
\end{definition}

\begin{obs}
    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in Observation~\ref{obs:category_of_cones}.
\end{obs}

The following examples show how limits are general concepts for the constructions defined above.

\begin{example}
    Let $D$ be the empty diagram in the category $\cat C$. Then, a cone for $D$ is any object of $\cat C$, while a limit is the terminal object of $\cat C$.
\end{example}

\begin{example}\label{ex:product_are_limits}
    Let $D$ be the following diagram:
    \[
        \begin{tikzcd}
            A & & B
        \end{tikzcd}
    \]
    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in Example~\ref{ex: span}):
    \[
        \begin{tikzcd}
            A & X \arrow[l, "f" swap] \arrow[r, "g"] & B
        \end{tikzcd}
    \]
    A limit for $D$ is, if it exists, the product of $A$ and $B$.
\end{example}

\begin{example}
    A pullback is the limit for the diagram below.
    \[
        \begin{tikzcd}
            & B \arrow[d, "g"] \\
            A \arrow[r, "f" swap] & C
        \end{tikzcd}
    \]
    In fact, a cone for the diagram above is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$ and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
    Thus, the following diagram is a cone:
    \[
        \begin{tikzcd}
            P \arrow[r, "{\psi}"] \arrow[d, "{\phi}" swap] & B \arrow[d, "g"] \\
            A \arrow[r, "f" swap] & C
        \end{tikzcd}
    \]
    For $(P, \phi, \psi)$ to be a pullback, it must have the universal property. In other words, it has to be a limit.

    This example show us that a pullback is a limit for a cospan (Example~\ref{ex: span}).
\end{example}

\begin{example}\label{ex:equaliz_are_limits}
    A limit for the diagram below is an equalizer for $f$ and $g$.
    \[
        \begin{tikzcd}
            A \arrow[r, shift left, "f"] \arrow[r, shift right,"g"swap] & B
        \end{tikzcd}
    \]
\end{example}

The connection between constructions as products and equalizers and limits is made clear by the following theorem. The idea behind the proof is the fact that, given a diagram $D : \cat I \rightarrow \cat C$, if each subset of objects $X = \{D(i) \mid i \in \Ob(\cat I)\} \subseteq \Ob(\cat C)$ has a product $(\prod_{i \in I} D(i), (\pi_i)_{i \in \Ob( \cat I)})$ and each pair of arrows $f, g \in \cat C (D(i), D(j))$ has an equalizer $Eq(f, g)$, then one can construct the cone taking the equalizer of the arrows that has as domain the product of the objects of the diagram, and as codomain the product of the codomains of the arrows of the diagram. This construction has the universal property because equalizers and product do.

\begin{theorem}[Limit theorem]
    Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
\end{theorem}

\begin{proof}
    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.

    The \emph{if} statement is easily satisfied as shown in Example~\ref{ex:equaliz_are_limits} and Example~\ref{ex:product_are_limits}.

    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
    \begin{enumerate}
        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
    \end{enumerate}

    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
    Let now:
    \[
        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
    \]
    defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.

    What we want now is to show that $(L, (p_i)_{i \in \Ob(\cat I)})$ is the limit of $D$, namely, show that conditions given at the beginning are valid.

    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
    \begin{align*}
        D(\alpha) \circ p_i 
            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
            &= p_j                                  && \textit{Definition of $p_j$} \\
    \end{align*}

    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated. By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$. For each arrow $\alpha: i \rightarrow j$, we have:
    \begin{align*}
            \gamma_\alpha \circ q 
                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
                &= q_j                          && \textit{Definition of $q_j$} \\
                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
    \end{align*}
    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$. Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
\end{proof}

The dual notions of cones and limits are that of cocones and colimits.

\begin{definition}(Cocones, Colimits)
    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$. A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
\end{definition}

All examples done about limits are still valid, in their dual form, for what regard colimits. In fact, initial objects, coequalizer, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples. The limit theorem is still valid, considering coequalizers and coproducts, and the proof is much the same.

\begin{example}
    Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
    \[
        \begin{tikzcd}
            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
        \end{tikzcd}
    \]
    a cocone for $S$ is any commutative square of the form
    \[
        \begin{tikzcd}
            & C & \\
            L \arrow[ur, "f"] &
            X \arrow[l, "l"swap] \arrow[r, "r"]&
            R \arrow[ul, "g" swap]
        \end{tikzcd}
    \]
    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
    A colimit for $S$ is then a pushout of $l$ and $r$.
\end{example}

\begin{remark}
    Since a diagram is nothing more than a functor form a "shape" category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
\end{remark}

\section{Adhesivity}

% ---------------- Bibliography ---------------- %
\bibliographystyle{alpha}
\bibliography{bibliography}

\end{document}

### 2024-08-05 final_1/source/mainOld.tex
minima

--- 2024-08-05 final_1/Tesi/main.tex
@@
 \begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphism are surjective functions and isomorphisms are bijections.
+    In $\Set$, monomorphisms are injective functions, epimorphism are surjective functions and ismorphisms are bijections.
 \end{example}
@@
     Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
+A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if, for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
     \[
@@
 
-The next definitions are about \emph{universal constructions}. The simplest ones are the notion of initial and, dually, terminal objects.
+The next definitions are about \emph{universal constructions}. The simplest are the notion of initial and, dually, terminal objects.
 
@@
 \begin{obs}\label{obs:terminal_are_isomorph}
-    It makes sense to refer to an initial (and terminal) object as \emph{the} initial (\emph{the} terminal) object.
+    It make sense to refer to an initial (and terminal) object as \emph{the} initial (\emph{the} terminal) object.
 Suppose indeed that $\initial$ and $\initial'$ are two distinct initial objects of a category $\cat C$.
 Then, there exists a unique morphism from $\initial$ to $\initial'$, say $f$.
-At the same way, it must exist a unique morphism from $\initial'$ to $\initial$, say $g$.
+At the same way, it must exists a unique morphism from $\initial'$ to $\initial$, say $g$.
 Then, $g\circ f$ must be exactly $id_{\initial}$, and $f \circ g = id_{\initial'}$, and then they are isomorphic.
@@
 \begin{definition}[Product]
-    A \emph{product} of two objects $A$ an $B$ is an object $A \times B$ together with two \emph{projection arrows} $\pi_1:A\times B \rightarrow A$ and $\pi_2: A \times B \rightarrow B$ such that, for every object $C$ and pair of arrows $f: C \rightarrow A$, $g: C \rightarrow B$, there is exactly one arrow $\langle f, g \rangle : c \rightarrow A \times B$ making the diagram commutes
+    A \emph{product} of two objects $A$ an $B$ is an object $A \times B$ together with two \emph{projection arrows} $\pi_1:A\times B \rightarrow A$ and $\pi_2: A \times B \rightarrow B$ such that, for every object $C$ and pair of arrows $f: C \rightarrow A$, $g: C \rightarrow B$, there is exactly one arrow $\langle f, g \rangle : c \rightarrow A \times B$ making the diagram
     \[
@@
     \]
-   -- i.e., such that $\pi_1 \circ \langle f, g \rangle = f$ and $\pi_2 \circ \langle f, g \rangle  = g$.
+
+    commute -- i.e., such that $\pi_1 \circ \langle f, g \rangle = f$ and $\pi_2 \circ \langle f, g \rangle  = g$.
 
@@
     The dual of the product is the \emph{coproduct}.
-    A coproduct of two objects $A$ and $B$ is an object $A + B$ together with two arrows $\iota_1:A\rightarrow A+B$, $\iota_2: B \rightarrow A + B$ such that, for every object $C$ and pair of arrows $f:A \rightarrow C$, $g:B \rightarrow C$, there is a unique arrow $[f, g] : A + B \rightarrow C$ such that the diagram commutes
+    A coproduct of two objects $A$ and $B$ is an object $A + B$ together with two arrows $\iota_1:A\rightarrow A+B$, $\iota_2: B \rightarrow A + B$ such that, for every object $C$ and pair of arrows $f:A \rightarrow C$, $g:B \rightarrow C$, there is a unique arrow $[f, g] : A + B \rightarrow C$ such that the diagram
     \[
@@
     \]
-    -- i.e., such that $[f, g] \circ \iota_1 = f$ and $[f, g] \circ \iota_2 = g$.
+    commutes -- i.e., such that $[f, g] \circ \iota_1 = f$ and $[f, g] \circ \iota_2 = g$.
 \end{definition}
@@
     $\Set$ have both products and coproduts.
-Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A + B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
+Given two sets $A$ and $B$, the categorical product is the set-theoretic catesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A + B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
 \end{example}
 
-The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrow for each object in the product).
+Both the notion of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrow for each object in the product).
 We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
@@
 
-The next notion is about a construction that make parallel arrows (i.e., two possibly distinct morphisms with the same domain and codomain) equal.
+The next notion is about a construction that make parallel arrows (i.e., two possibly distinct morphisms whit the same domain and codomain) equal.
 In $\Set$, given two functions $f, g: A \rightarrow B$, such construction corresponds exactly to the restriction of the domain to the set of elements on which $f$ and $g$ are equal.
@@
 In fact, $e$ is that function that make $f$ and $g$ be the same function -- i.e., $f \circ e = g \circ e$.
-This concept can be generalized as follows.
+This concept can be generalized as it follows.
 

### 2024-08-05 final_1/source/main.tex
Fixed example on spans

--- 2024-08-05 final_1/Tesi/main.tex
@@
+% !TeX root = main.tex
 \documentclass[a4paper, twoside,openright]{report}
@@
 \chapter{Background}
-
 In this chapter will be defined the building blocks for this work, almost entirely based on categories.
@@
     A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a span in a relation $R \subseteq A \times B$, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
+In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
 The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.

### 2024-08-07 Article/main.tex
Fixed typos, closure under compositions, reg monos...

--- 2024-08-05 final_1/source/main.tex
@@
-% !TeX root = main.tex
 \documentclass[a4paper, twoside,openright]{report}
@@
 \usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale italiano, con parti in inglese
+\usepackage[english]{babel} % Lingua principale inglese
 \usepackage{graphicx} % Per includere immagini esterne
-\usepackage{lipsum} % genera testo fittizio
 \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento
@@
 \newcommand{\Set}{\mathbf{Set}}
+\newcommand{\Reg}{\mathcal{R}eg}
+\newcommand{\Mono}{\mathcal{M}ono}
 \newcommand{\initial}{\textbf 0}
@@
 
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in wich the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
+To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
     \[
@@
 It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
+    Another clarification must to be done, still considering $\Set$.
+Given two sets $A$ and $B$, $\Set(A, B)$ is also a set.
+A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
 \end{remark}
@@
     An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
+The class of all monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
 \end{definition}
@@
 In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite{pierce91}.
+Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
 
@@
         \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item composites and identities of $\cat{D}$ are the same of $\cat{C}$
+        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$
     \end{enumerate}
@@
 $\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
+    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ g \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
 \end{definition}
 
-An object of a category can raise a category itself. This is the case of slice (and coslice) categories.
+An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
 
@@
 In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
+
     The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
@@
 
+\begin{prop}\label{prop:eq_are_mono}
+    Let $e: E \rightarrow A$ be the arrow that equalize $f, g : A \rightarrow B$ in a category $\cat C$. Then, $e$ is a monomorphism.
+\end{prop}
+
+\begin{proof}
+    Suppose $X$ be an object and $x, y: X \rightarrow E$ be two morphisms in $\cat C$ such that $e \circ x = e \circ y$, and let $z = e \circ x$.
+Then, since $e$ is an equalizer, $f \circ e = g \circ e$, and $f \circ z = g \circ z$.
+But, for the universal property of equalizers, there must be exactly one $u: Z \rightarrow E$ such that $z = e \circ u$.
+It follow that $x = u$ and $y = u$, hence $x = y$.
+\end{proof}
+
+Of all monomorphism, an intrersting subclass of them is the one that contains only the equalizers.
+
+\begin{definition}[Regular Monomorphism]\label{def:reg_mono}
+    A monomorphism that is an equalizer for a pair of arrows is said \emph{regular monomorphism}. The class of all regular monomorphisms of a category $\cat C$ is denoted $\Reg(\cat C)$.
+\end{definition}
+
 \subsection{Pullbacks and Pushouts}
@@
 \end{example}
+
+Given a subclass of morphisms of a category, an important property is \emph{stability} under certain type of constructions.
+In our case, we are interested in stability under pullbacks and under pushouts.
+\[
+    \begin{tikzcd}\label{diag:p_square}\tag{$\ast$}
+        A \arrow[r, "f"] \arrow[d, "m"swap] & B \arrow[d, "n"] \\
+        C \arrow[r, "g" swap] & D
+    \end{tikzcd}
+\]
+\begin{definition}[Stability under pullbacks, pushouts]
+    Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
+    $\mathcal A$ is said to be \emph{stable under pushouts} if, for every square as the one in \eqref{diag:p_square}, if $m \in \mathcal{A}$, then $n \in \mathcal{A}$.
+\end{definition}
 

### 2024-08-08 Article/main.tex
Preservation, reflection, lifting and creation of (co)limits

@@
     \]
-    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$.
+    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$
 \end{definition}
@@
 
-    What we want now is to show that $(L, (p_i)_{i \in \Ob(\cat I)})$ is the limit of $D$, namely, show that conditions given at the beginning are valid.
+    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, show that conditions given at the beginning are valid.
 
@@
 
+In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behave whit respect to the constructions defined so far.
+
+\begin{definition}
+    Let $D : \cat{I \rightarrow C}$ be a diagram, and $F: \cat{C \rightarrow D}$ a functor. We say that $F$:
+    \begin{enumerate}
+        \item \emph{preserves limits} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $D$, then $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
+        \item \emph{reflects limits} of $D$ if a cone $(L, l_i)_{i \in \cat I}$ is a limit for $D$ whenever $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
+        \item \emph{lifts limits} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $F \circ D$, there exists a limit $(L', l_i')_{i \in \cat I}$ such that $(F(L'), F(l_i'))_{i \in \cat I} = (L, l_i)_{i \in \cat I}$.
+        \item \emph{creates limits} of $D$ if $D$ has a limit and $F$ preserves and reflects limits along it.
+    \end{enumerate}
+    The dual notions are obtained in the obvious way, namely, substituting the words \textit{"limits"} and \textit{"cones"} with \textit{"colimits"} and \textit{"cocones"}.
+\end{definition}
+
 \section{Adhesivity}

### 2024-08-08 Article/main.tex
Introduction to graphs

@@
 
-\section{Basic Notions}
+\section{Basic Notions}\label{sect:basic_nots}
 
@@
 
-\subsection{Categories}
+\subsection{Categories}\label{ssect:cats}
 
@@
 
-\subsection{Mono, Epi and Iso}
+\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
 
@@
 
-\subsection{Categories from other categories}
+\subsection{Categories from other categories}\label{ssect:cats_from_cats}
 
@@
 
-\section{Functors, Natural transformations and Beyond}
+\section{Functors, Natural transformations and Beyond}\label{sect:funct_nats}
 
@@
 
-\section{Universal Constructions}
+\section{Universal Constructions}\label{sect:univ_constr}
 
@@
 
-\section{Adhesivity}
+\section{Adhesivity}\label{sect:adh}
+
+\chapter{Categories of Graphs}
+This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
+Starting from set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
+
+\section{Set-Theoretic Definition of Graphs}
+
+A first obvious definition of graph is given via sets and set-theoretic tools. The next definition recalls how a graph intuitively is.
+
+\begin{definition}[Graph]
+    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
+    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
+\end{definition}
+
+\begin{definition}[Graph Homomorphism]
+    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
+    \[
+        h_V \circ s_G = s_H \circ h_E
+    \]
+    and
+    \[
+        h_V \circ t_G = t_H \circ h_E
+    \]
+    that is, a structure preserving map.
+    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
+\end{definition}
+
+Graphs together with graph homomorphisms from a category.
+
+\begin{definition}[Category of Graphs]
+    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
+\end{definition}
+
+All the constructions defined in Section~\ref{sect:univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
+The next examples try to make this point clear.
+
+\begin{example}
+    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
+The initial object instead is the graph with exactly one node and a single edge from that node to itself.
+\end{example}
+
+\begin{example}
+    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
+\end{example}
+
+\begin{example}
+    Equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ which is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
+Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
+\end{example}
+
+\subsection{Graph with Equivalences}
+
+It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
+The ones we are interested in are \emph{equivalence relations}.
+Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
+A graph with equivalence is a graph with a relation of that kind of relation defined over its set of vertices.
+
+\begin{definition}[Graph with Equivalence]
+    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
+\end{definition}
 

### 2024-08-08 Article/main.tex
Introduction to graphs with equivalence and readme

@@
 
-A first obvious definition of graph is given via sets and set-theoretic tools. The next definition recalls how a graph intuitively is.
+First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
+
+\subsection{Simple Graphs}
 

### 2024-08-08 Article/main.tex
Updated defs on graphs with equivalence

@@
 
-At the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C$.
+In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C$.
 
@@
 The same argument works for the terminal object.
-    The reason why this argument works is because initial and terminal objects have the \emph{universal property} (Definition~\ref{def:univ_prop}), [Integrare qui!]
+    The reason why this argument works is because initial and terminal objects have the \emph{universal property} (Definition~\ref{def:univ_prop}), i.e., 
 \end{obs}
@@
 
-\begin{definition}[Category of Graphs]
+\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
     $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
@@
 
-\begin{definition}[Graph with Equivalence]
+\begin{definition}[Graph with Equivalence~\cite{concur2006}]
     A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
+An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that, if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
+Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
+\end{definition}
+
+The next consideration will be useful later.
+
+\begin{remark}
+    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
+Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
+\end{remark}
+
+\begin{obs}
+    $\mathbf{Graph}$, defined in Definition~\ref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
+\end{obs}
+
+\begin{definition}[Quotient functor]
+    The functor $Q: \mathbf{EqGrph \rightarrow Graph}$, which maps each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$ is called \emph{quotient functor}.
 \end{definition}

### 2024-08-10 Article/main.tex
minima (typo etc.)

@@
 \chapter{Background}
-In this chapter will be defined the building blocks for this work, almost entirely based on categories.
+In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
 The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
@@
     \end{enumerate}
-    For each morphism $f \in \Hom(\cat{C})$, there are two operators $dom$ and $cod$ which map every morphism to two objects, respectively, its \emph{domain} and its \emph{codomain}.
+    For each morphism $f \in \Hom(\cat{C})$, there are two operators $dom$ and $cod$ that map every morphism to two objects, respectively, its \emph{domain} and its \emph{codomain}.
 In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of all morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
+The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
     An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
@@
 For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $\forall a \in A: id_A(a) = a$.
-    This category is usually denoted as $\Set$.
+    This category is denoted as $\Set$.
 \end{example}
@@
 \begin{remark}\label{rem:small_cats}
-    It is important to note that the Definition~\ref{def:category} above does not specify what kind of collections are, for a category $\cat{C}$, $\Ob(\cat{C})$ and $\Hom(\cat{C})$.
+    It is important to note that the Definition~\ref{def:category} above does not specify what kind of collections
+    %for a category $\cat{C}$, 
+    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
     Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
 It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, $\Set(A, B)$ is also a set.
+    Another clarification must to be done, still considering $\Set$. Given two sets $A$ and $B$, $\Set(A, B)$ is also a set.
+    {\color{red}{non esattamente}}
     A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
@@
 
-Between all morphisms of a category, it is possible to distinguish some that have certain properties, as well as functions between sets can be surjective, injective or bijective.
+Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
 
@@
     An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of all monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
+The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
 \end{definition}
@@
 \begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphism are surjective functions and isomorphisms are bijections.
+    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
 \end{example}
@@
 
-Starting from a category $\cat{C}$, it is possible to construct some other categories with interesting property.
+Starting from a category $\cat{C}$, it is possible to construct other categories with interesting property.
 An example is the \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
@@
 Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
+{\color{red} la discussione sul duale temo confonda}
 
@@
 $\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ g \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
+    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
 \end{definition}
@@
 \begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ is given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
+    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
     \[
@@
 
-    The dual definition is \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), obtained by taking as objects all the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ such that $g = \phi \circ f$.
+    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
 \end{definition}
@@
 
-Once defined what is a functor, we can give a more rigorous definition of diagram.
+Once defined what a functor is, we can give a more rigorous definition of diagram.
 Although this may seem extremely technical, it will be useful, especially in the definition of limits (Definition~\ref{def:limit}).
@@
 An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions.~\cite{Herrlich_Strecker_1979}
+The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions~\cite{Herrlich_Strecker_1979}.
 
@@
 
-Given two functors which share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of "changing the functor acting on that object".
+Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
 
@@
     Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$ is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
+A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
     \[
@@
 \begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformation $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
+It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
 This follows by the fact that the diagram
@@
 \]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is even possible to show associativity of composition of natural transformations.
+commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
 \end{obs}
@@
 The Observation~\ref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This led us to define a particular kind of category, in which objects are functors between two fixed categories, and arrow are natural transformations.
+This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
 
 \begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be two categories.
+    Let $\cat C$ and $\cat D$ be categories.
 The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
@@
     What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition we give above.
+This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
 \end{remark}
@@
     Dually, an object $Z$ is said to be a terminal object in a category $\cat C$ if, for any other object $X$ of $\cat C$, there exists a unique morphism from $X$ to $Z$.
-    An initial object of a category is indicated by the symbol $\initial$, and a terminal object is indicated by the symbol $\terminal$.
+    An initial object is indicated by the symbol $\initial$, and a terminal object by the symbol $\terminal$.
 \end{definition}
@@
     It makes sense to refer to an initial (and terminal) object as \emph{the} initial (\emph{the} terminal) object.
-Suppose indeed that $\initial$ and $\initial'$ are two distinct initial objects of a category $\cat C$.
+Suppose that $\initial$ and $\initial'$ are distinct initial objects of a category $\cat C$.
 Then, there exists a unique morphism from $\initial$ to $\initial'$, say $f$.
-At the same way, it must exist a unique morphism from $\initial'$ to $\initial$, say $g$.
+Likewise, it must exist a unique morphism from $\initial'$ to $\initial$, say $g$.
 Then, $g\circ f$ must be exactly $id_{\initial}$, and $f \circ g = id_{\initial'}$, and then they are isomorphic.
 The same argument works for the terminal object.
-    The reason why this argument works is because initial and terminal objects have the \emph{universal property} (Definition~\ref{def:univ_prop}), i.e., 
+    The reason why this argument works is because initial and terminal objects have the \emph{universal property} (Definition~\ref{def:univ_prop}), i.e., {\color{red} ?????}
 \end{obs}
@@
 \begin{example}
-    $\Set$ have both products and coproduts.
+    $\Set$ has both products and coproduts.
 Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A + B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
@@
 
-The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrow for each object in the product).
+The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for each object in the product).
 We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
 
-Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction owns the universal property.
+Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction satifies the universal property.
 
@@
 \begin{prop}\label{prop:eq_are_mono}
-    Let $e: E \rightarrow A$ be the arrow that equalize $f, g : A \rightarrow B$ in a category $\cat C$. Then, $e$ is a monomorphism.
+    Let $e: E \rightarrow A$ be the arrow that equalizes $f, g : A \rightarrow B$ in a category $\cat C$. Then, $e$ is a monomorphism.
 \end{prop}
@@
 
-Of all monomorphism, an intrersting subclass of them is the one that contains only the equalizers.
+Of all monomorphism, an interesting subclass of them is the one that contains only the equalizers.
 
@@
 
-Another (pair of) construction(s) one can find in a category, given two arrows, is the pullback (and the pushout).
+Given two arrows, another pair of constructions one can find in a category is given by pullbacks and pushouts.
 
@@
 
-Pullbacks (and, dually pushouts) are construction slightly more general than products and equalizers.
+Pullbacks (and, dually, pushouts) are a construction that is slightly more general than products and equalizers.
 An intuition of what they represent is given by considering what is concretely a pullback in the category of sets.
@@
 \begin{definition}[Stability under pullbacks, pushouts]
-    Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
-    $\mathcal A$ is said to be \emph{stable under pushouts} if, for every square as the one in \eqref{diag:p_square}, if $m \in \mathcal{A}$, then $n \in \mathcal{A}$.
+    Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every pullback square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
+    $\mathcal A$ is said to be \emph{stable under pushouts} if, for every pushout square as the one in \eqref{diag:p_square}, if $m \in \mathcal{A}$, then $n \in \mathcal{A}$.
 \end{definition}
@@
 \begin{obs}\label{obs:category_of_cones}
-    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$ is defined to have cones for $D$ as objects and cone morphisms as arrows, where a con morphism $\phi: C \rightarrow C'$ from a cone $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
+    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$, is defined to have cones for $D$ as objects and cone morphisms as arrows, where a cone morphism $\phi: C \rightarrow C'$ from $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
     \[
@@
     \]
-    A limit for $D$ is, if it exists, the product of $A$ and $B$.
+    If it exists, a limit for $D$ is the product of $A$ and $B$.
 \end{example}
@@
 The idea behind the proof is the fact that, given a diagram $D : \cat I \rightarrow \cat C$, if each subset of objects $X = \{D(i) \mid i \in \Ob(\cat I)\} \subseteq \Ob(\cat C)$ has a product $(\prod_{i \in I} D(i), (\pi_i)_{i \in \Ob( \cat I)})$ and each pair of arrows $f, g \in \cat C (D(i), D(j))$ has an equalizer $Eq(f, g)$, then one can construct the cone taking the equalizer of the arrows that has as domain the product of the objects of the diagram, and as codomain the product of the codomains of the arrows of the diagram.
-This construction has the universal property because equalizers and product do.
+This construction has the universal property because equalizers and products do.
 
@@
     \]
-    defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
+    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
     Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
 
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, show that conditions given at the beginning are valid.
+    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
 
@@
 
-All examples done about limits are still valid, in their dual form, for what regard colimits.
-In fact, initial objects, coequalizer, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
+All the examples we provided about limits are still valid, in their dual form, for what regard colimits.
+In fact, initial objects, coequalizers, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
 The limit theorem is still valid, considering coequalizers and coproducts, and the proof is much the same.
@@
 \begin{remark}
-    Since a diagram is nothing more than a functor form a "shape" category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
+    Since a diagram is nothing more than a functor from a ``shape'' category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
 \end{remark}
 
-In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behave whit respect to the constructions defined so far.
+In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.
 
@@
     \end{enumerate}
-    The dual notions are obtained in the obvious way, namely, substituting the words \textit{"limits"} and \textit{"cones"} with \textit{"colimits"} and \textit{"cocones"}.
+    The dual notions are obtained in the obvious way, namely, substituting the words ``limits'' and ``cones'' with ``colimits'' and ``cocones'', respectively
 \end{definition}
@@
 This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
+Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
 
@@
 \begin{example}
-    Equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ which is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
+    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
 Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.

### 2024-09-08 Article/main.tex
Considerations on faithful functors

--- 2024-08-08 Article/main.tex
@@
 In this chapter will be defined the building blocks for this work, almost entirely based on categories.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
+The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) and reuse them in different contexts.
 This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
@@
         \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$.
+        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
     \end{enumerate}
@@
 
-Starting from a category $\cat{C}$, it is possible to construct some other categories with interesting property.
+Starting from a category $\cat{C}$, it is possible to construct some other categories with interesting properties.
 An example is the \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
@@
 
+Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
+The following definitions are about this particular type of functors.
+
+\begin{definition}[Full functor, faithful functor, fully faithful functor]
+    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
+    $$
+        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
+    $$
+    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
+\end{definition}
+
+\begin{obs}
+    Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
+This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
+\end{obs}
+
+\begin{example}
+    Let $\cat C$ be a category and $\cat D$ a subcategory.
+The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
+$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
+If $\cat D$ is a full subcategory, then $I$ is fully faithful.
+\end{example}
+
+Having such classification among functors turns out to be useful in many contexts.
+For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
+Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
+Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
+Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
+
+\begin{prop}
+    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
+\end{prop}
+
 Given two functors which share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of "changing the functor acting on that object".
@@
 
-\subsection{Functor Category}
+\subsection{Functor Categories}
 
@@
 \section{Universal Constructions}\label{sect:univ_constr}
+
+% What we are interested in are the "best" construction having a certain property, and we exprtess this fact via requiring unique factorization when another construction does.
 
@@
     $\Set$ have both products and coproduts.
-Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A + B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
+Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A \coprod B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
 \end{example}
@@
     \]
+    We can refer to this situation also saying that \emph{$\pi_g$ is a pullback of $g$ along $f$}.
 
@@
 
-\begin{example}
+\begin{example}\label{ex:pb_in_set}
     In $\Set$, given two functions $f: A \rightarrow C$ and $g: B \rightarrow C$, a pullback of $f$ and $g$ exists and is exactly the set $P = \{(x, y) \in A \times B \mid f(x) = g(y)\}$, with $\pi_f : P \rightarrow B$ and $\pi_g : P \rightarrow C$ defined, respectively, by $\pi_f((x, y)) = y$ and $\pi_g((x, y)) = x$.
@@
 
+Another important example to our aims is a concrete definition of what is a pushout in the category of sets, and why morally we can regard a pushout as \textit{the way to identify part of an object with a part of another}~\cite{Barr_Wells_1995}.
+
+\begin{example}\label{ex:po_in_set}
+    \color{red}
+    In $\Set$, given two functions $f: A \rightarrow B$ and $g: A \rightarrow C$, the pushout of them is the set $X = (B \coprod C) /_\sim$, where $\sim$ is the least equivalence relation such that $f(a) \sim g(a)$ for each $a \in A$, with $\iota_g:B \rightarrow X$ and $\iota_f : C \rightarrow X$ as arrows, sending each element of the domain in the corresponding equivalence class in $X$.
+In particular, for each $a \in A$:
+    \begin{align*}
+        (\iota_g \circ f) (a)
+                        &= \iota_g(f(a))    &&\\
+                        &= [(f(a), 0)]           && \textit{Definition of $\iota_g$} \\
+                        &= [(g(a), 1)]           && f(a) \sim g(a) \\
+                        &= \iota_f(g(a))    && \textit{Definition of $\iota_f$} \\
+                        &= (\iota_f \circ g) (a) &&
+    \end{align*}
+    % This is not sure!!
+    When both $f$ and $g$ are monos (that is, injections), then we can construct the pushout taking at the same way we have done above, with $(f(a), 0) \sim (g(a), 1)$ when such $a$ exists and $(b, 0) \sim (c, 1)$ on each $b$ and $c$ with no preimage in $A$, with $\iota_f$ and $\iota_g$ injective.
+    An easy way to see this fact is considering the following situation: let $f: A \rightarrow A \cup B$ and $g: A \rightarrow A \cup C$, with $A$ disjoint from $B$ and $C$, $f(a)= a$ and $g(a) = a$.
+Then the pushout is the object $A \cup B \cup C$, with the inclusion as arrows, that are also injective.
+    A more general case is what happens considering functions $f: A \rightarrow B$ and $g: A \rightarrow C$ injective.
+Differently from the previous example, in this case is not possible to take just the union of codomains as the pushout, but rather the disjoint union of them and then identify the elements $f(a)$ with $g(a)$, as we have done above.
+In the category of sets and functions, we have the certainty that the pullback arrows are injective.
+In fact, taking the equivalence relation $\sim$, we have that $f(a) \sim f(a')$ if and only if $a = a'$ by hypothesis, and then $x \sim x'$ if and only if $x = x'$, then the pushout morphisms sends each element in an equivalence class composed only by the element itself, thus are injective.
+    This is an interesting property that in other categories may do not hold, and will be recalled later.
+\end{example}
+
 Given a subclass of morphisms of a category, an important property is \emph{stability} under certain type of constructions.
@@
 \]
-\begin{definition}[Stability under pullbacks, pushouts]
+\begin{definition}\label{def:stab_under_po_pb}[Stability under pullbacks, pushouts]
     Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
@@
 
+\begin{example}\label{ex:lim_of_sets}
+    Limit theorem gives us an easy way to calculate limits.
+An example of this fact is how limits are computed in $\Set$.
+Given a diagram $D: \cat{I} \rightarrow \Set$, where $\cat I$ is a small category and $I = Ob(\cat I)$, its limit is the set $L$ defined as follows:
+    $$
+        L = \{ (d_i)_{i \in I} \in \prod_{i \in I}D(i) \mid \forall \phi \in \cat I(i, i'), D(\phi)(d_i) = d_{i'} \}
+    $$
+    with projections as arrows.
+\end{example}
+
 The dual notions of cones and limits are that of cocones and colimits.
@@
 The limit theorem is still valid, considering coequalizers and coproducts, and the proof is much the same.
+examples of these facts will follow.
 
@@
 
+\begin{example}\label{ex:colm_of_sets}
+    As mentioned before, the limit theorem in its dual form is still valid.
+As we have done in Example~\ref{ex:lim_of_sets} we illustrate how to construct colimits in the category of sets.
+Given a small category $\cat I$, $ I = Ob(\cat I)$, and a diagram $D: \cat I \rightarrow \Set$, consider the equivalence relation $\sim$ defined on $\coprod_{i\in I} D(i)$ such that $d_i \sim d_{i'}$ if $d_i \in D(i), d_{i'} \in D(i')$ and there exists some $\phi \in \cat I(i, i')$ such that $D(\phi)(d_i) = d_{i'}$.
+Then, a colimit for $D$ is the set
+    $$
+        C = \big ( \coprod_{i \in I} D(i) \big ) / \sim
+    $$
+    with the inclusions as arrows.
+\end{example}
+
 \begin{remark}
@@
 \section{Adhesivity}\label{sect:adh}
+
+The next section is about adhesivity.
+An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
+
+\begin{definition}(Van Kampen property)
+    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
+    % \[
+    % \begin{tikzcd}
+    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
+    %     C \arrow[r, "g" swap]                & D
+    % \end{tikzcd}
+    % \]
+    \[
+    \begin{tikzcd}[row sep = scriptsize]
+        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
+        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
+        & C \arrow[r, "g" swap]                & D                  & \\
+        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
+    \end{tikzcd}
+    \]
+    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
+    \begin{itemize}
+        \item it is a pushout;
+        \item $a, b, c, d \in \mathcal{A}$;
+        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the down squares are pullbacks.
+    \end{itemize}
+\end{definition}
+
+We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
+
+\begin{definition}
+    Let $\cat C$ be a category and $\mathcal M$ a subclass of $\Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_po_pb}).
+    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
+    \begin{enumerate}
+        \item it has pullbacks along arrows of $\mathcal M$;
+        \item it has pushouts along arrows of $\mathcal M$;
+        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
+    \end{enumerate}
+    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
+\end{definition}
 
@@
 \begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
+    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \ \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
 An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that, if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
@@
 \begin{definition}[Quotient functor]
-    The functor $Q: \mathbf{EqGrph \rightarrow Graph}$, which maps each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$ is called \emph{quotient functor}.
+    The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$.
 \end{definition}

### 2024-09-08 Article/main.tex
Reordering

--- 2024-08-10 Article/main.tex
@@
 
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
+Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
+The following definitions are about this particular type of functors.
+
+\begin{definition}[Full functor, faithful functor, fully faithful functor]
+    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
+    $$
+        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
+    $$
+    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
+\end{definition}
+
+\begin{obs}
+    Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
+This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
+\end{obs}
+
+\begin{example}
+    Let $\cat C$ be a category and $\cat D$ a subcategory.
+The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
+$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
+If $\cat D$ is a full subcategory, then $I$ is fully faithful.
+\end{example}
+
+Having such classification among functors turns out to be useful in many contexts.
+For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
+Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
+Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
+Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
+
+\begin{prop}
+    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
+\end{prop}
 
 \subsection{Natural transformations}
+
+Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
 
@@
             S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g"] & T(B)
+            T(C) \arrow[r, "g" swap] & T(B)
             \end{tikzcd}
@@
 \section{Universal Constructions}\label{sect:univ_constr}
+
+% What we are interested in are the "best" construction having a certain property, and we exprtess this fact via requiring unique factorization when another construction does
 
@@
     $\Set$ has both products and coproduts.
-Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A + B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
+Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A \coprod B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
 \end{example}
@@
 
+Another important example to our aims is a concrete definition of what is a pushout in the category of sets, and why morally we can regard a pushout as \textit{the way to identify part of an object with a part of another}~\cite{Barr_Wells_1995}.
+
+\begin{example}\label{ex:po_in_set}
+    \color{blue}
+    In $\Set$, given two functions $f: A \rightarrow B$ and $g: A \rightarrow C$, the pushout of them is the set $X = (B \coprod C) /_\sim$, where $\sim$ is the least equivalence relation such that $f(a) \sim g(a)$ for each $a \in A$, with $\iota_g:B \rightarrow X$ and $\iota_f : C \rightarrow X$ as arrows, sending each element of the domain in the corresponding equivalence class in $X$.
+In particular, for each $a \in A$:
+    \begin{align*}
+        (\iota_g \circ f) (a)
+                        &= \iota_g(f(a))    &&\\
+                        &= [(f(a), 0)]           && \textit{Definition of $\iota_g$} \\
+                        &= [(g(a), 1)]           && f(a) \sim g(a) \\
+                        &= \iota_f(g(a))    && \textit{Definition of $\iota_f$} \\
+                        &= (\iota_f \circ g) (a) &&
+    \end{align*}
+    % This is not sure!!
+    When both $f$ and $g$ are monos (that is, injections), then we can construct the pushout taking at the same way we have done above, with $(f(a), 0) \sim (g(a), 1)$ when such $a$ exists and $(b, 0) \sim (c, 1)$ on each $b$ and $c$ with no preimage in $A$, with $\iota_f$ and $\iota_g$ injective.
+    An easy way to see this fact is considering the following situation: let $f: A \rightarrow A \cup B$ and $g: A \rightarrow A \cup C$, with $A$ disjoint from $B$ and $C$, $f(a)= a$ and $g(a) = a$.
+Then the pushout is the object $A \cup B \cup C$, with the inclusion as arrows, that are also injective.
+    A more general case is what happens considering functions $f: A \rightarrow B$ and $g: A \rightarrow C$ injective.
+Differently from the previous example, in this case is not possible to take just the union of codomains as the pushout, but rather the disjoint union of them and then identify the elements $f(a)$ with $g(a)$, as we have done above.
+In the category of sets and functions, we have the certainty that the pullback arrows are injective.
+In fact, taking the equivalence relation $\sim$, we have that $f(a) \sim f(a')$ if and only if $a = a'$ by hypothesis, and then $x \sim x'$ if and only if $x = x'$, then the pushout morphisms sends each element in an equivalence class composed only by the element itself, thus are injective.
+    This is an interesting property that in other categories may do not hold, and will be recalled later.
+\end{example}
+
 Given a subclass of morphisms of a category, an important property is \emph{stability} under certain type of constructions.
@@
 \]
-\begin{definition}[Stability under pullbacks, pushouts]
+\begin{definition}\label{def:stab_under_pb_po}[Stability under pullbacks, pushouts]
     Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every pullback square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
@@
 \section{Adhesivity}\label{sect:adh}
+
+The next section is about adhesivity.
+An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
+
+\begin{definition}(Van Kampen property)
+    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
+    % \[
+    % \begin{tikzcd}
+    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
+    %     C \arrow[r, "g" swap]                & D
+    % \end{tikzcd}
+    % \]
+    \[
+    \begin{tikzcd}[row sep = scriptsize]
+        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
+        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
+        & C \arrow[r, "g" swap]                & D                  & \\
+        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
+    \end{tikzcd}
+    \]
+    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
+    \begin{itemize}
+        \item it is a pushout;
+        \item $a, b, c, d \in \mathcal{A}$;
+        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
+    \end{itemize}
+\end{definition}
+
+We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
+
+\begin{definition}
+    Let $\cat C$ be a category and $\mathcal M$ a subclass of $\Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_pb_po}).
+    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
+    \begin{enumerate}
+        \item it has pullbacks along arrows of $\mathcal M$;
+        \item it has pushouts along arrows of $\mathcal M$;
+        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
+    \end{enumerate}
+    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
+\end{definition}
 

### 2024-09-08 Article/main.tex
Pushouts in Set, Full and Faithful functors

--- 2024-09-08 Article/main.tex
@@
 \begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
+    let $F: \cat C \rightarrow \cat D$ be a functor, and consider the induced function
     $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
+        F_{X, Y} : {\cat C}(X, Y) \rightarrow {\cat D}(F(X), F(Y))
     $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
+    If, for each $X$, $Y$ objects of $\cat C$, $F_{X, Y}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
 \end{definition}
-
-\begin{obs}
-    Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-\end{obs}
 
@@
 The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
+$I$ is a faithful functor, because, given any pair of objects $X$ and $Y$ of $\cat D$, $I_{X, Y}$ is injective.
 If $\cat D$ is a full subcategory, then $I$ is fully faithful.
 \end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
 
@@
 \begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \ \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
+    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
 An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that, if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
@@
 \begin{definition}[Quotient functor]
-    The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$.
+    The functor $Q: \mathbf{EqGrph \rightarrow Graph}$, which maps each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$ is called \emph{quotient functor}.
 \end{definition}

### 2024-09-09 Article/main.tex
criterion for M-adh and some corrections, to review

--- 2024-09-08 Article/main.tex
@@
 It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$. Given two sets $A$ and $B$, $\Set(A, B)$ is also a set.
-    {\color{red}{non esattamente}}
+    Another clarification must to be done, still considering $\Set$.
+Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
+This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
+    {\color{green}{rivedere}}
     A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
@@
 The same argument works for the terminal object.
-    The reason why this argument works is because initial and terminal objects have the \emph{universal property} (Definition~\ref{def:univ_prop}), i.e., {\color{red} ?????}
 \end{obs}
@@
 
-\begin{example}
+\begin{example}\label{ex:pb_as_limit}
     A pullback is the limit for the diagram below.
@@
         \item \emph{reflects limits} of $D$ if a cone $(L, l_i)_{i \in \cat I}$ is a limit for $D$ whenever $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
-        \item \emph{lifts limits} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $F \circ D$, there exists a limit $(L', l_i')_{i \in \cat I}$ such that $(F(L'), F(l_i'))_{i \in \cat I} = (L, l_i)_{i \in \cat I}$.
+        \item \emph{lifts limits (uniquely)} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $F \circ D$, there exists a (unique) limit $(L', l_i')_{i \in \cat I}$ for $D$ such that $(F(L'), F(l_i'))_{i \in \cat I} = (L, l_i)_{i \in \cat I}$.
         \item \emph{creates limits} of $D$ if $D$ has a limit and $F$ preserves and reflects limits along it.
@@
 \end{definition}
+
+\begin{obs}\label{obs:funct_creat_lim_then_lift}[~\cite{Adámek_Herrlich_Strecker_2009}]
+    It holds that if a functor creates limits, then lifts uniquely limits.
+\end{obs}
 
@@
 
-\begin{definition}
+\begin{definition}\label{def:adh}[$\mathcal{M}$-adhesivity]
     Let $\cat C$ be a category and $\mathcal M$ a subclass of $\Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_pb_po}).
@@
     \begin{enumerate}
-        \item it has pullbacks along arrows of $\mathcal M$;
-        \item it has pushouts along arrows of $\mathcal M$;
+        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback ( such pullbacks are called $\mathcal M$-pullbacks);
+        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
         \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
@@
 \end{definition}
+
+% Verificare la M-adesività utilizzando la definizione data sopra può essere particolarmente ostico. Per questa ragione, è possibile ricorrere al seguente risultato. [A new crit for MN-adh]
+
+Verifying $\mathcal M$-adhesivity using the definition above may turn out to be vary complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
+
+\begin{theorem}
+    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
+Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
+    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pullbacks, then $\cat C$ is $\mathcal M$-adhesive.
+\end{theorem}
+
+The idea behind this theorem is to simplify calculation to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
+
+\begin{proof}
+    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in Definition~\ref{def:adh}.
+    \begin{itemize}
+        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
+Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (Example~\ref{ex:pb_as_limit}).
+Since $F$ creates pullbacks, hence lift them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
+        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
+Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
+Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
+        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
+    \end{itemize}
+
+\end{proof}
 

### 2024-09-10 Article/main.tex
Some adjustments

@@
 \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento
-\usepackage[fontsize=13pt]{scrextend} %dimensione font
+\usepackage[fontsize=12pt]{scrextend} %dimensione font
 
@@
     \]
-    Then, the \emph{slice category $(S \downarrow T)$} is the category in which: 
+    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
     \begin{itemize}
@@
 
-\begin{theorem}[Limit theorem]
+\begin{theorem}\label{th:limit}[Limit theorem]
     Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
@@
 
+\begin{obs}\label{obs:limits_in_presh}
+    So far we introduced categories of presheaves.
+In these categories, an interesting fact is that limits and colimits are computed pointwise -- i.e., the limit of a diagram in a category of presheaves is exactly the limit on each of its components.
+\end{obs}
+
 In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.
@@
 \begin{definition}\label{def:adh}[$\mathcal{M}$-adhesivity]
-    Let $\cat C$ be a category and $\mathcal M$ a subclass of $\Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_pb_po}).
+    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_pb_po}).
     Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
@@
 
+These examples show how some kind of limits are computed among graphs, but we have already said something similar about categories of presheaves (Observation~\ref{obs:limits_in_presh}).
+In fact, The category of graphs in nothing than
+
 \subsection{Graph with Equivalences}
@@
 
-\begin{definition}[Quotient functor]
-    The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$.
-\end{definition}
+% \begin{definition}[Quotient functor]
+%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps
+%     each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} 
+%     $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if 
+%     $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences 
+%     $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$.
+% \end{definition}
+
+% \begin{definition}[Quotient functor]
+%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps each $\mathcal{G} = (G, \sim)$ onto its quotient graph $G/_{\sim} = (V_G/_{\sim},E_G, s_G', t_G')$, such that, for each edge $e$:
+%     \begin{itemize}
+%         \item $s_G'([e]_{\sim}) = [v]_{\sim_G}$
+%     \end{itemize}
+% \end{definition}
+
+Some examples of limits will follow.
+
+\begin{example}
+    The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
+\end{example}
+
+\begin{example}
+    Given two graphs with equivalences $\mathcal{G} = (G, \sim_G) $ and $\mathcal{H} = (H, \sim_{H})$, one can construct the product graph $\mathcal{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\mathcal{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
+\end{example}
+
+\begin{example}
+    An equalizer in $\mathbf{EgGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$.
+The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
+\end{example}
+
+The two previous examples shows that the category $\mathbf{EgGrph}$ has both equalizer and finite products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EgGrph}$ has finite limits.
+
+\begin{example}
+    Given two parallel morphisms $f, g: \mathcal{G \rightarrow H}$ in $\mathbf{EgGrph}$, the coequalizer $(\mathcal{C}, c)$ is the graph 
+\end{example}
 

### 2024-09-10 Article/main.tex
Some adjustments

@@
 \begin{example}
-    An equalizer in $\mathbf{EgGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$.
+    An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$.
 The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
@@
 
-The two previous examples shows that the category $\mathbf{EgGrph}$ has both equalizer and finite products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EgGrph}$ has finite limits.
-
-\begin{example}
-    Given two parallel morphisms $f, g: \mathcal{G \rightarrow H}$ in $\mathbf{EgGrph}$, the coequalizer $(\mathcal{C}, c)$ is the graph 
-\end{example}
+The two previous examples shows that the category $\mathbf{EqGrph}$ has both equalizer and finite products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits.
 

### 2024-09-11 Article/main.tex
More on Graphs

@@
 
+\begin{prop}\label{prop:epi_mono_prop}
+    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
+    \begin{enumerate}
+        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
+        \item if $g \circ f$ is mono, then $f$ is mono;
+        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
+        \item if $g \circ f$ is epi, then $g$ is epi.
+    \end{enumerate}
+\end{prop}
+
 \subsection{Categories from other categories}\label{ssect:cats_from_cats}
@@
 
-\subsection{Natural transformations}
+\subsection{Natural Transformations}
 
@@
 
-\subsection{Comma categories}
+\subsection{Comma Categories}
 
@@
 These examples show how some kind of limits are computed among graphs, but we have already said something similar about categories of presheaves (Observation~\ref{obs:limits_in_presh}).
-In fact, The category of graphs in nothing than
+In fact, it is possible to show the equivalence between the category of graphs and $[\bullet \rightrightarrows \bullet , \Set]$.
+The easy way of computing depends on the fact that in a category of presheaves, limits are computed objectwise [citation needed], as we implicitly have done in the previous examples.
 
@@
 Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with a relation of that kind of relation defined over its set of vertices.
+A graph with equivalence is a graph with such a relation defined over its set of vertices.
 
@@
 \end{definition}
-
-The next consideration will be useful later.
 
@@
 
-Some examples of limits will follow.
-
-\begin{example}
+In the category of graphs with equivalences universal constructions are easy to obtain. 
 The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-\end{example}
-
-\begin{example}
 Given two graphs with equivalences $\mathcal{G} = (G, \sim_G) $ and $\mathcal{H} = (H, \sim_{H})$, one can construct the product graph $\mathcal{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\mathcal{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-\end{example}
-
-\begin{example}
 An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$.
 The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-\end{example}
-
+Coequalizers are computed in the same way. Computing 
 The two previous examples shows that the category $\mathbf{EqGrph}$ has both equalizer and finite products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits.

### 2024-09-11 Article/main.tex
Graphs as functor categories

@@
 
-\section{Set-Theoretic Definition of Graphs}
+\section{Set-Theoretic Definitions of Graphs}
 
@@
 
-\subsection{Simple Graphs}
+\subsection{Graphs}
 
@@
 
-\begin{definition}[Graph Homomorphism]
+\begin{definition}\label{def:graph_hom}[Graph Homomorphism]
     Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
@@
 
-\begin{example}
+\begin{example}\label{ex:in_term_in_graph}
     The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
@@
 \end{example}
-
-These examples show how some kind of limits are computed among graphs, but we have already said something similar about categories of presheaves (Observation~\ref{obs:limits_in_presh}).
-In fact, it is possible to show the equivalence between the category of graphs and $[\bullet \rightrightarrows \bullet , \Set]$.
-The easy way of computing depends on the fact that in a category of presheaves, limits are computed objectwise [citation needed], as we implicitly have done in the previous examples.
 
@@
 
-\begin{remark}
+\begin{remark}\label{rem:eq_as_surj}
     It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
@@
 
-In the category of graphs with equivalences universal constructions are easy to obtain. 
+%TODO: RIGUARDARE QUESTA PARTE!!!
+
+In the category of graphs with equivalences, universal constructions are easy to obtain. 
 The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
@@
 The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-Coequalizers are computed in the same way. Computing 
-The two previous examples shows that the category $\mathbf{EqGrph}$ has both equalizer and finite products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits.
+
+Previous examples show that the category $\mathbf{EqGrph}$ has both (c)equalizer and finite (co)products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
+
+%TODO: EGGS
+
+\section{Graphs as Functors}
+
+Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
+We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
+This concept is perfectly represented by categories of presheaves, where an object is nothing than a way to interpret objects of a category as sets.
+An example will make clear what we are talking about.
+
+Considering the category of graphs (as defined in Definition~\ref{def:cat_of_graph}), it is possible to show that 
+$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
+where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
+A morphisms $\eta: G \dot\rightarrow H$ is a natural trasformation, and the commutativity of the diagram below is given by definition of graph morphisms (Definition~\ref{def:graph_hom})
+$$
+    \begin{tikzcd}
+        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
+        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
+    \end{tikzcd}
+$$
+(and the same for $t$).
+
+Example~\ref{ex:in_term_in_graph} and following, in which limits and colimits are computed component-wise, are a concrete instance of Observation~\ref{obs:limits_in_presh}.
+
+More complex objects are graphs with equivalence.
+We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[V \rightrightarrows E \rightarrow Q, \Set]$, in which each object $\mathcal{G}$ is a functor mapping the arrow $q: E \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
+The component $\mathcal{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
 

### 2024-09-11 Article/main.tex
commenti

@@
 \usepackage{graphicx} % Per includere immagini esterne
+\usepackage{todonotes}
 \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento
@@
 \section{Functors, Natural transformations and Beyond}\label{sect:funct_nats}
-
+\todo{Toglierei il "beyond" DC}
 A functor is a structure preserving map between categories. 
-
+\todo{E cambierei anche l'intro a questa sezione DC}
 \subsection{Functors}
@@
 
-\begin{obs}\label{obs:funct_creat_lim_then_lift}[~\cite{Adámek_Herrlich_Strecker_2009}]
+\begin{obs}\label{obs:funct_creat_lim_then_lift}%[~\cite{Adámek_Herrlich_Strecker_2009}]
     It holds that if a functor creates limits, then lifts uniquely limits.
@@
 
+\color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
+
+Sec. 1 Categorie e funtori
+
+>def di categorie
+	-menzionare che data una categoria c'è il duale
+	-epi, mono e  iso
+
+>funtori e trasf naturali
+
+>categorie comma (con slice e coslice come sottocaso)
+
+Sec. 2: Limiti e colimiti
+Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
+
+>definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
+	-epi e mono regolari
+
+>Limiti nelle categorie di funtori e comma
+
+Sec. 3: Adesività
+Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
+\color{black}
+
 \chapter{Categories of Graphs}

### 2024-09-11 Article/main.tex
Lemma2.2.1, Theroem2.2.2, without proof

@@
 \newtheorem{prop}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{cor}[theorem]{Corollary}
 
@@
 
-\section{Functors, Natural transformations and Beyond}\label{sect:funct_nats}
-\todo{Toglierei il "beyond" DC}
+\section{Functors and Natural Transformations}\label{sect:funct_nats}
+
 A functor is a structure preserving map between categories. 
 \todo{E cambierei anche l'intro a questa sezione DC}
+
 \subsection{Functors}
@@
 
-\begin{obs}\label{obs:funct_creat_lim_then_lift}%[~\cite{Adámek_Herrlich_Strecker_2009}]
-    It holds that if a functor creates limits, then lifts uniquely limits.
+\begin{obs}\label{obs:funct_creat_lim_then_lift}
+    It holds that if a functor creates limits, then lifts uniquely limits~\cite{Adamek_Herrlich_Strecker_2009}.
 \end{obs}
@@
 
+Graphs with equivalences are alternative representation of \emph{quotient graphs} over an equivalence relation.
+The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
+
+\begin{definition}\label{def:quot_func}[Quotient Functor]
+    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
+    \begin{itemize}
+        \item on objects, given $\mathcal{G}=(G, \sim_{G})$ as $Q(\mathcal{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
+        \item on morphisms, given $h = (h_V, h_E): \mathcal{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
+    \end{itemize}
+\end{definition}
+
 In the category of graphs with equivalences, universal constructions are easy to obtain. 
@@
 
-Previous examples show that the category $\mathbf{EqGrph}$ has both (c)equalizer and finite (co)products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
+Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
+
+An important characterization in the category of graphs with equivalences is the following.
+
+\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
+    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
+That is, if $h: \mathcal{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
+\end{prop}
 
@@
 where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural trasformation, and the commutativity of the diagram below is given by definition of graph morphisms (Definition~\ref{def:graph_hom})
+A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by definition of graph morphisms (Definition~\ref{def:graph_hom})
 $$
@@
 
-Example~\ref{ex:in_term_in_graph} and following, in which limits and colimits are computed component-wise, are a concrete instance of Observation~\ref{obs:limits_in_presh}.
+Example~\ref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of Observation~\ref{obs:limits_in_presh}.
 
@@
 The component $\mathcal{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
+In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
+
+Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \mathcal{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
+
+\begin{lemma}
+    $\mathbf{EqGrph}$ is stable under $\Reg(\mathbf{EqGrph})$-pushouts and $\Reg({\mathbf{EqGrph}})$-pullbacks.
+\end{lemma}
+
+\begin{theorem}
+    $EqGrph$ is $\Reg(\mathbf{EqGrph})$-adhesive.
+\end{theorem}
 

### 2024-09-11 Article/main.tex
Lemma2.2.1, Theroem2.2.2, without proof

@@
 \usepackage{graphicx} % Per includere immagini esterne
-\usepackage{todonotes}
 \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento
@@
 
-\section{Functors and Natural Transformations}\label{sect:funct_nats}
+\section{Functors, Natural transformations and Beyond}\label{sect:funct_nats}
 
 A functor is a structure preserving map between categories.
-\todo{E cambierei anche l'intro a questa sezione DC}
 
@@
 
-\color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-Sec. 1 Categorie e funtori
-
->def di categorie
-	-menzionare che data una categoria c'è il duale
-	-epi, mono e  iso
-
->funtori e trasf naturali
-
->categorie comma (con slice e coslice come sottocaso)
-
-Sec. 2: Limiti e colimiti
-Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
->definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-	-epi e mono regolari
-
->Limiti nelle categorie di funtori e comma
-
-Sec. 3: Adesività
-Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-\color{black}
-
 \chapter{Categories of Graphs}

### 2024-09-13 Article/main.tex
Appendix and reordering

--- 2024-09-11 Article/main.tex
@@
 
+\begin{prop}\label{prop:monos_pres_by_pullback}
+    Let $f: A \rightarrow C$, $g: B \rightarrow C$ arrows in any category $\cat C$, and consider the pullback square:
+    $$
+        \begin{tikzcd}
+            P \arrow[r, "{\pi_f}"] \arrow[d, "{\pi_g}"swap] & B \arrow[d, "g"] \\
+            A \arrow[r, "f"swap] & C
+        \end{tikzcd}
+    $$
+    If $g$ is mono, then so is $\pi_g$.
+\end{prop}
+
 \subsection{Limits and Colimits}
@@
 
+The dual notions of cones and limits are that of cocones and colimits.
+
+\begin{definition}(Cocones, Colimits)
+    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$.
+A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
+    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
+\end{definition}
+
 The following examples show how limits are general concepts for the constructions defined above.
@@
     \]
+\end{example}
+
+All the examples we provided about limits are still valid, in their dual form, for what regard colimits.
+In fact, initial objects, coequalizers, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
+
+\begin{example}
+    Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
+    \[
+        \begin{tikzcd}
+            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
+        \end{tikzcd}
+    \]
+    a cocone for $S$ is any commutative square of the form
+    \[
+        \begin{tikzcd}
+            & C & \\
+            L \arrow[ur, "f"] &
+            X \arrow[l, "l"swap] \arrow[r, "r"]&
+            R \arrow[ul, "g" swap]
+        \end{tikzcd}
+    \]
+    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
+    A colimit for $S$ is then a pushout of $l$ and $r$.
 \end{example}
@@
 This construction has the universal property because equalizers and products do.
+A detailed proof is in the appendix.
 
@@
 
+\begin{remark}
+    The theorem above (and its relative proof) can be stated in its dual form leading to a theorem on existence of colimits, and a relative criterion to calculate them (taking the dual of the proof).
+\end{remark}
+
+\begin{example}\label{ex:lim_of_sets}
+    Limit theorem gives us an easy way to calculate limits.
+An example of this fact is how limits are computed in $\Set$.
+Given a diagram $D: \cat{I} \rightarrow \Set$, where $\cat I$ is a small category and $I = Ob(\cat I)$, its limit is the set $L$ defined as follows:
+    $$
+        L = \{ (d_i)_{i \in I} \in \prod_{i \in I}D(i) \mid \forall \phi \in \cat I(i, i'), D(\phi)(d_i) = d_{i'} \}
+    $$
+    with projections as arrows.
+\end{example}
+
+\begin{example}\label{ex:colm_of_sets}
+    As we have done in Example~\ref{ex:lim_of_sets} we illustrate how to construct colimits in the category of sets.
+Given a small category $\cat I$, $ I = Ob(\cat I)$, and a diagram $D: \cat I \rightarrow \Set$, consider the equivalence relation $\sim$ defined on $\coprod_{i\in I} D(i)$ such that $d_i \sim d_{i'}$ if $d_i \in D(i), d_{i'} \in D(i')$ and there exists some $\phi \in \cat I(i, i')$ such that $D(\phi)(d_i) = d_{i'}$.
+Then, a colimit for $D$ is the set
+    $$
+        C = \big ( \coprod_{i \in I} D(i) \big ) / \sim
+    $$
+    with the inclusions as arrows.
+\end{example}
+
+\begin{remark}
+    Since a diagram is nothing more than a functor from a ``shape'' category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
+\end{remark}
+
+\begin{obs}\label{obs:limits_in_presh}
+    So far we introduced categories of presheaves.
+In these categories, an interesting fact is that limits and colimits are computed pointwise -- i.e., the limit of a diagram in a category of presheaves is exactly the limit on each of its components.
+\end{obs}
+
+In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.
+
+\begin{definition}
+    Let $D : \cat{I \rightarrow C}$ be a diagram, and $F: \cat{C \rightarrow D}$ a functor. We say that $F$:
+    \begin{enumerate}
+        \item \emph{preserves limits} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $D$, then $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
+        \item \emph{reflects limits} of $D$ if a cone $(L, l_i)_{i \in \cat I}$ is a limit for $D$ whenever $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
+        \item \emph{lifts limits (uniquely)} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $F \circ D$, there exists a (unique) limit $(L', l_i')_{i \in \cat I}$ for $D$ such that $(F(L'), F(l_i'))_{i \in \cat I} = (L, l_i)_{i \in \cat I}$.
+        \item \emph{creates limits} of $D$ if $D$ has a limit and $F$ preserves and reflects limits along it.
+    \end{enumerate}
+    The dual notions are obtained in the obvious way, namely, substituting the words ``limits'' and ``cones'' with ``colimits'' and ``cocones'', respectively
+\end{definition}
+
+\begin{obs}\label{obs:funct_creat_lim_then_lift}
+    It holds that if a functor creates limits, then lifts uniquely limits~\cite{Adamek_Herrlich_Strecker_2009}.
+\end{obs}
+
+\section{Adhesivity}\label{sect:adh}
+
+The next section is about adhesivity.
+An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
+
+\begin{definition}(Van Kampen property)
+    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
+    % \[
+    % \begin{tikzcd}
+    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
+    %     C \arrow[r, "g" swap]                & D
+    % \end{tikzcd}
+    % \]
+    \[
+    \begin{tikzcd}[row sep = scriptsize]
+        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
+        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
+        & C \arrow[r, "g" swap]                & D                  & \\
+        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
+    \end{tikzcd}
+    \]
+    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
+    \begin{itemize}
+        \item it is a pushout;
+        \item $a, b, c, d \in \mathcal{A}$;
+        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
+    \end{itemize}
+\end{definition}
+
+We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
+
+\begin{definition}\label{def:adh}[$\mathcal{M}$-adhesivity]
+    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_pb_po}).
+    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
+    \begin{enumerate}
+        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback ( such pullbacks are called $\mathcal M$-pullbacks);
+        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
+        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
+    \end{enumerate}
+    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
+\end{definition}
+
+% Verificare la M-adesività utilizzando la definizione data sopra può essere particolarmente ostico. Per questa ragione, è possibile ricorrere al seguente risultato. [A new crit for MN-adh]
+
+Verifying $\mathcal M$-adhesivity using the definition above may turn out to be vary complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
+
+\begin{theorem}\label{th:crit_for_adh}
+    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
+Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
+    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pullbacks, then $\cat C$ is $\mathcal M$-adhesive.
+\end{theorem}
+
+The idea behind this theorem is to simplify calculation to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
+
+\begin{proof}
+    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in Definition~\ref{def:adh}.
+    \begin{itemize}
+        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
+Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (Example~\ref{ex:pb_as_limit}).
+Since $F$ creates pullbacks, hence lift them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
+        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
+Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
+Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
+        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
+    \end{itemize}
+
+\end{proof}
+
+\color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
+
+Sec. 1 Categorie e funtori
+
+>def di categorie
+	-menzionare che data una categoria c'è il duale
+	-epi, mono e  iso
+
+>funtori e trasf naturali
+
+>categorie comma (con slice e coslice come sottocaso)
+
+Sec. 2: Limiti e colimiti
+Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
+
+>definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
+	-epi e mono regolari
+
+>Limiti nelle categorie di funtori e comma
+
+Sec. 3: Adesività
+Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
+\color{black}
+
+\chapter{Categories of Graphs}
+This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
+Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
+
+\section{Set-Theoretic Definitions of Graphs}
+
+First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
+
+\subsection{Graphs}
+
+\begin{definition}[Graph]
+    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
+    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
+\end{definition}
+
+\begin{definition}\label{def:graph_hom}[Graph Homomorphism]
+    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
+    \[
+        h_V \circ s_G = s_H \circ h_E
+    \]
+    and
+    \[
+        h_V \circ t_G = t_H \circ h_E
+    \]
+    that is, a structure preserving map.
+    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
+\end{definition}
+
+Graphs together with graph homomorphisms from a category.
+
+\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
+    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
+\end{definition}
+
+All the constructions defined in Section~\ref{sect:univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
+The next examples try to make this point clear.
+
+\begin{example}\label{ex:in_term_in_graph}
+    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
+The initial object instead is the graph with exactly one node and a single edge from that node to itself.
+\end{example}
+
+\begin{example}
+    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
+\end{example}
+
+\begin{example}
+    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
+Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
+\end{example}
+
+\subsection{Graph with Equivalences}
+
+It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
+The ones we are interested in are \emph{equivalence relations}.
+Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
+A graph with equivalence is a graph with such a relation defined over its set of vertices.
+
+\begin{definition}[Graph with Equivalence~\cite{concur2006}]
+    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
+An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that, if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
+Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
+\end{definition}
+
+\begin{remark}\label{rem:eq_as_surj}
+    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
+Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
+\end{remark}
+
+\begin{obs}
+    $\mathbf{Graph}$, defined in Definition~\ref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
+\end{obs}
+
+% \begin{definition}[Quotient functor]
+%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps
+%     each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} 
+%     $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if 
+%     $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences 
+%     $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$.
+% \end{definition}
+
+% \begin{definition}[Quotient functor]
+%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps each $\mathcal{G} = (G, \sim)$ onto its quotient graph $G/_{\sim} = (V_G/_{\sim},E_G, s_G', t_G')$, such that, for each edge $e$:
+%     \begin{itemize}
+%         \item $s_G'([e]_{\sim}) = [v]_{\sim_G}$
+%     \end{itemize}
+% \end{definition}
+
+%TODO: RIGUARDARE QUESTA PARTE!!!
+
+Graphs with equivalences are alternative representation of \emph{quotient graphs} over an equivalence relation.
+The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
+
+\begin{definition}\label{def:quot_func}[Quotient Functor]
+    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
+    \begin{itemize}
+        \item on objects, given $\mathcal{G}=(G, \sim_{G})$ as $Q(\mathcal{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
+        \item on morphisms, given $h = (h_V, h_E): \mathcal{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
+    \end{itemize}
+\end{definition}
+
+In the category of graphs with equivalences, universal constructions are easy to obtain. 
+The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
+Given two graphs with equivalences $\mathcal{G} = (G, \sim_G) $ and $\mathcal{H} = (H, \sim_{H})$, one can construct the product graph $\mathcal{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\mathcal{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
+An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$.
+The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
+
+Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
+
+An important characterization in the category of graphs with equivalences is the following.
+
+\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
+    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
+That is, if $h: \mathcal{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
+\end{prop}
+
+%TODO: EGGS
+\subsection{E-Graphs}
+
+E-Graphs are a particular type of graphs with equivalences, in which holds that
+$$
+    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
+$$
+for each pair of edges $e$, $e'$ of $\mathcal{G} = (G, \sim)$.
+
+\section{Graphs as Functors}
+
+Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
+We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
+This concept is perfectly represented by categories of presheaves, where an object is nothing than a way to interpret objects of a category as sets.
+An example will make clear what we are talking about.
+
+Considering the category of graphs (as defined in Definition~\ref{def:cat_of_graph}), it is possible to show that 
+$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
+where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
+A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by definition of graph morphisms (Definition~\ref{def:graph_hom})
+$$
+    \begin{tikzcd}
+        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
+        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
+    \end{tikzcd}
+$$
+(and the same for $t$).
+
+Example~\ref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of Observation~\ref{obs:limits_in_presh}.
+
+More complex objects are graphs with equivalence.
+We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[V \rightrightarrows E \rightarrow Q, \Set]$, in which each object $\mathcal{G}$ is a functor mapping the arrow $q: E \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
+The component $\mathcal{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
+In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
+
+Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \mathcal{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
+Since limits are computed pointwise, pullbacks preserve regular monomorphisms (Proposition~\ref{prop:monos_pres_by_pullback}).
+Regular monos are preserved also by pushouts.
+Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
+
+\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
+    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of Definition~\ref{def:stab_under_pb_po}).
+\end{lemma}
+
+\begin{theorem}
+    $\mathbf{EqGrph}$ is quasiadhesive.
+\end{theorem}
+
+\begin{proof}
+    In order to apply Theorem~\ref{th:crit_for_adh}, we can consider the quotient functor defined in Definition~\ref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
+We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mappend onto monos in $\mathbf{Graph}$.
+In addition to Lemma~\ref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
+    \todo{Generalizzare il fatto che i limiti in $\mathbf{EqGrph}$ rimangono limiti in $\mathbf{Graph}$} 
+\end{proof}
+
+% ----------------- Appendix ------------------ %
+**\appendix
+
+\chapter{Omitted Proofs}
+
+\paragraph{Theorem~\ref{th:limit}.}
+ Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
 \begin{proof}
@@
 
-\begin{example}\label{ex:lim_of_sets}
-    Limit theorem gives us an easy way to calculate limits.
-An example of this fact is how limits are computed in $\Set$.
-Given a diagram $D: \cat{I} \rightarrow \Set$, where $\cat I$ is a small category and $I = Ob(\cat I)$, its limit is the set $L$ defined as follows:
-    $$
-        L = \{ (d_i)_{i \in I} \in \prod_{i \in I}D(i) \mid \forall \phi \in \cat I(i, i'), D(\phi)(d_i) = d_{i'} \}
-    $$
-    with projections as arrows.
-\end{example}
-
-The dual notions of cones and limits are that of cocones and colimits.
-
-\begin{definition}(Cocones, Colimits)
-    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$.
-A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
-    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
-\end{definition}
-
-All the examples we provided about limits are still valid, in their dual form, for what regard colimits.
-In fact, initial objects, coequalizers, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
-The limit theorem is still valid, considering coequalizers and coproducts, and the proof is much the same.
-
-\begin{example}
-    Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
-    \[
-        \begin{tikzcd}
-            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
-        \end{tikzcd}
-    \]
-    a cocone for $S$ is any commutative square of the form
-    \[
-        \begin{tikzcd}
-            & C & \\
-            L \arrow[ur, "f"] &
-            X \arrow[l, "l"swap] \arrow[r, "r"]&
-            R \arrow[ul, "g" swap]
-        \end{tikzcd}
-    \]
-    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
-    A colimit for $S$ is then a pushout of $l$ and $r$.
-\end{example}
-
-\begin{example}\label{ex:colm_of_sets}
-    As mentioned before, the limit theorem in its dual form is still valid.
-As we have done in Example~\ref{ex:lim_of_sets} we illustrate how to construct colimits in the category of sets.
-Given a small category $\cat I$, $ I = Ob(\cat I)$, and a diagram $D: \cat I \rightarrow \Set$, consider the equivalence relation $\sim$ defined on $\coprod_{i\in I} D(i)$ such that $d_i \sim d_{i'}$ if $d_i \in D(i), d_{i'} \in D(i')$ and there exists some $\phi \in \cat I(i, i')$ such that $D(\phi)(d_i) = d_{i'}$.
-Then, a colimit for $D$ is the set
-    $$
-        C = \big ( \coprod_{i \in I} D(i) \big ) / \sim
-    $$
-    with the inclusions as arrows.
-\end{example}
-
-\begin{remark}
-    Since a diagram is nothing more than a functor from a ``shape'' category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
-\end{remark}
-
-\begin{obs}\label{obs:limits_in_presh}
-    So far we introduced categories of presheaves.
-In these categories, an interesting fact is that limits and colimits are computed pointwise -- i.e., the limit of a diagram in a category of presheaves is exactly the limit on each of its components.
-\end{obs}
-
-In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.
-
-\begin{definition}
-    Let $D : \cat{I \rightarrow C}$ be a diagram, and $F: \cat{C \rightarrow D}$ a functor. We say that $F$:
-    \begin{enumerate}
-        \item \emph{preserves limits} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $D$, then $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
-        \item \emph{reflects limits} of $D$ if a cone $(L, l_i)_{i \in \cat I}$ is a limit for $D$ whenever $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
-        \item \emph{lifts limits (uniquely)} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $F \circ D$, there exists a (unique) limit $(L', l_i')_{i \in \cat I}$ for $D$ such that $(F(L'), F(l_i'))_{i \in \cat I} = (L, l_i)_{i \in \cat I}$.
-        \item \emph{creates limits} of $D$ if $D$ has a limit and $F$ preserves and reflects limits along it.
-    \end{enumerate}
-    The dual notions are obtained in the obvious way, namely, substituting the words ``limits'' and ``cones'' with ``colimits'' and ``cocones'', respectively
-\end{definition}
-
-\begin{obs}\label{obs:funct_creat_lim_then_lift}
-    It holds that if a functor creates limits, then lifts uniquely limits~\cite{Adamek_Herrlich_Strecker_2009}.
-\end{obs}
-
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}\label{def:adh}[$\mathcal{M}$-adhesivity]
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback ( such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-% Verificare la M-adesività utilizzando la definizione data sopra può essere particolarmente ostico. Per questa ragione, è possibile ricorrere al seguente risultato. [A new crit for MN-adh]
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be vary complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pullbacks, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculation to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in Definition~\ref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (Example~\ref{ex:pb_as_limit}).
-Since $F$ creates pullbacks, hence lift them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-\color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-Sec. 1 Categorie e funtori
-
->def di categorie
-	-menzionare che data una categoria c'è il duale
-	-epi, mono e  iso
-
->funtori e trasf naturali
-
->categorie comma (con slice e coslice come sottocaso)
-
-Sec. 2: Limiti e colimiti
-Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
->definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-	-epi e mono regolari
-
->Limiti nelle categorie di funtori e comma
-
-Sec. 3: Adesività
-Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-\color{black}
-
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}\label{def:graph_hom}[Graph Homomorphism]
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in Section~\ref{sect:univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with such a relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that, if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in Definition~\ref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-% \begin{definition}[Quotient functor]
-%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps
-%     each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} 
-%     $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if 
-%     $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences 
-%     $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$.
-% \end{definition}
-
-% \begin{definition}[Quotient functor]
-%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps each $\mathcal{G} = (G, \sim)$ onto its quotient graph $G/_{\sim} = (V_G/_{\sim},E_G, s_G', t_G')$, such that, for each edge $e$:
-%     \begin{itemize}
-%         \item $s_G'([e]_{\sim}) = [v]_{\sim_G}$
-%     \end{itemize}
-% \end{definition}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-Graphs with equivalences are alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-
-\begin{definition}\label{def:quot_func}[Quotient Functor]
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\mathcal{G}=(G, \sim_{G})$ as $Q(\mathcal{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \mathcal{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\mathcal{G} = (G, \sim_G) $ and $\mathcal{H} = (H, \sim_{H})$, one can construct the product graph $\mathcal{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\mathcal{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following.
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \mathcal{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-%TODO: EGGS
-
-\section{Graphs as Functors}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in Definition~\ref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by definition of graph morphisms (Definition~\ref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-Example~\ref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of Observation~\ref{obs:limits_in_presh}.
-
-More complex objects are graphs with equivalence.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[V \rightrightarrows E \rightarrow Q, \Set]$, in which each object $\mathcal{G}$ is a functor mapping the arrow $q: E \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\mathcal{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \mathcal{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
-
-\begin{lemma}
-    $\mathbf{EqGrph}$ is stable under $\Reg(\mathbf{EqGrph})$-pushouts and $\Reg({\mathbf{EqGrph}})$-pullbacks.
-\end{lemma}
-
-\begin{theorem}
-    $EqGrph$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{theorem}
-
 % ---------------- Bibliography ---------------- %

### 2024-09-20 Article/main.tex
minima

@@
 
-Functor constructions allow us to generalise basic concept already seen for categories.
+Functor constructions allow us to generalise basic concepts already seen for categories.
 An important example of this fact are comma categories, a more general notion of slice categories (Definition~\ref{def:slice_cat}).
@@
 
-In particular, every presheaf has an initial and a terminal object, because $\Set$ do (Example~\ref{ex:set_init_term}).
+In particular, every presheaf has an initial and a terminal object, because $\Set$ does (Example~\ref{ex:set_init_term}).
 
@@
 
-The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for each object in the product).
-We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
+The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for
+each object in the product).
+We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as
+$\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
 
@@
 \begin{prop}\label{prop:eq_are_mono}
-    Let $e: E \rightarrow A$ be the arrow that equalizes $f, g : A \rightarrow B$ in a category $\cat C$. Then, $e$ is a monomorphism.
+    Let $e: E \rightarrow A$ be the arrow that equalizes $f, g : A \rightarrow B$ in a category $\cat C$. Then $e$ is a monomorphism.
 \end{prop}
@@
     Suppose $X$ be an object and $x, y: X \rightarrow E$ be two morphisms in $\cat C$ such that $e \circ x = e \circ y$, and let $z = e \circ x$.
-Then, since $e$ is an equalizer, $f \circ e = g \circ e$, and $f \circ z = g \circ z$.
+Then, since $e$ is an equalizer, $f \circ e = g \circ e$ and $f \circ z = g \circ z$.
 But, for the universal property of equalizers, there must be exactly one $u: Z \rightarrow E$ such that $z = e \circ u$.
@@
 
-Of all monomorphism, an interesting subclass of them is the one that contains only the equalizers.
+Of all monomorphisms, an interesting subclass of them is the one that contains only the equalizers.
 
@@
     % This is not sure!!
-    When both $f$ and $g$ are monos (that is, injections), then we can construct the pushout taking at the same way we have done above, with $(f(a), 0) \sim (g(a), 1)$ when such $a$ exists and $(b, 0) \sim (c, 1)$ on each $b$ and $c$ with no preimage in $A$, with $\iota_f$ and $\iota_g$ injective.
+    When both $f$ and $g$ are monos (that is, injections), then we can construct the pushout in the same way we have done above, with $(f(a), 0) \sim (g(a), 1)$ when such $a$ exists and $(b, 0) \sim (c, 1)$ on each $b$ and $c$ with no preimage in $A$, with $\iota_f$ and $\iota_g$ injective.
     An easy way to see this fact is considering the following situation: let $f: A \rightarrow A \cup B$ and $g: A \rightarrow A \cup C$, with $A$ disjoint from $B$ and $C$, $f(a)= a$ and $g(a) = a$.
-Then the pushout is the object $A \cup B \cup C$, with the inclusion as arrows, that are also injective.
+Then the pushout is the object $A \cup B \cup C$, with the inclusions as arrows, that are also injective.
     A more general case is what happens considering functions $f: A \rightarrow B$ and $g: A \rightarrow C$ injective.
@@
 We now introduce the notion that generalize all the universal constructions defined above.
-In fact, initial objects, products, equalizers an pullback (dually, terminal objects, coproducts, coequalizers and pushouts) can be seen as the particular case of a certain type of construction, called limit.
+In fact, initial objects, products, equalizers and pullbacks (dually, terminal objects, coproducts, coequalizers and pushouts) can be seen as the particular case of a certain type of construction, called limit.
 
@@
     \]
-    In fact, a cone for the diagram above is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$ and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
+    In fact, a cone for the diagram above is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$, and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
     Thus, the following diagram is a cone:
@@
 
-All the examples we provided about limits are still valid, in their dual form, for what regard colimits.
+All the examples we provided about limits are still valid, in their dual form, for colimits.
 In fact, initial objects, coequalizers, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
@@
 \begin{example}\label{ex:colm_of_sets}
-    As we have done in Example~\ref{ex:lim_of_sets} we illustrate how to construct colimits in the category of sets.
+    As we have done in Example~\ref{ex:lim_of_sets}, we illustrate how to construct colimits in the category of sets.
 Given a small category $\cat I$, $ I = Ob(\cat I)$, and a diagram $D: \cat I \rightarrow \Set$, consider the equivalence relation $\sim$ defined on $\coprod_{i\in I} D(i)$ such that $d_i \sim d_{i'}$ if $d_i \in D(i), d_{i'} \in D(i')$ and there exists some $\phi \in \cat I(i, i')$ such that $D(\phi)(d_i) = d_{i'}$.
@@
     \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback ( such pullbacks are called $\mathcal M$-pullbacks);
+        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
         \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
@@
 
-The idea behind this theorem is to simplify calculation to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
+The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
 
@@
 Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (Example~\ref{ex:pb_as_limit}).
-Since $F$ creates pullbacks, hence lift them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
+Since $F$ creates pullbacks, hence lifts them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exists a pullback $(P, p_B, p_D)$ in $\cat C$.
         \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.

### 2024-09-20 Article/main.tex
minima

@@
     A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that, if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
+An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
 Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
@@
 
-Graphs with equivalences are alternative representation of \emph{quotient graphs} over an equivalence relation.
+Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
 The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
@@
     In order to apply Theorem~\ref{th:crit_for_adh}, we can consider the quotient functor defined in Definition~\ref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mappend onto monos in $\mathbf{Graph}$.
+We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
 In addition to Lemma~\ref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.

### 2024-09-21 Article/main.tex
minima

@@
 
-\subsection{Equalizers and Coequalzers}
+\subsection{Equalizers and Coequalizers}
 
@@
 We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing than a way to interpret objects of a category as sets.
+This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
 An example will make clear what we are talking about.
@@
 where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by definition of graph morphisms (Definition~\ref{def:graph_hom})
+A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (Definition~\ref{def:graph_hom})
 $$
@@
 
-More complex objects are graphs with equivalence.
+Graphs with equivalence are more complex objects.
 We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[V \rightrightarrows E \rightarrow Q, \Set]$, in which each object $\mathcal{G}$ is a functor mapping the arrow $q: E \rightarrow Q$ onto an epimorphism (i.e., a surjective function).

### 2024-09-22 Article/main.tex
fixed typos and some changes

@@
 
+\begin{definition}\label{def:dual_cat}[Dual Category]
+    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
+    \begin{itemize}
+        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
+        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
+    \end{itemize}
+    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
+    Such category is called \emph{dual category} or \emph{opposite category}.
+\end{definition}
+
+Duality is a concept that we will encounter most of the time.
+Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
+There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
+
+%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
+% Each definition in category theory has a dual form.
+In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
+Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
+{\color{red} la discussione sul duale temo confonda}
+
 To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
@@
 In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $\forall a \in A: id_A(a) = a$.
+For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
     This category is denoted as $\Set$.
@@
 
+\begin{remark}
+    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
+    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
+\end{remark}
+
 \begin{prop}\label{prop:epi_mono_prop}
@@
 
-Starting from a category $\cat{C}$, it is possible to construct other categories with interesting property.
-An example is the \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-Another important notion is that of subcategory.
+Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
+
+The first notion to introduce is the one of subcategory.
+
 \begin{definition}[Subcategory]
@@
         \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$
+        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
     \end{enumerate}
@@
 
+\todo{E cambierei anche l'intro a questa sezione DC}
+
+\subsection{Functors}
+
 A functor is a structure preserving map between categories. 
-\todo{E cambierei anche l'intro a questa sezione DC}
-
-\subsection{Functors}
 \begin{definition}[Functor]
@@
     $\Set$ has both products and coproduts.
-Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A \coprod B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
-\end{example}
-
-The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for
-each object in the product).
-We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as
-$\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
-
-Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction satifies the universal property.
+Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjoint sum $A \coprod B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
+\end{example}
+
+The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for each object in the product).
+We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
+
+Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction satisfies the universal property.
 
@@
 \begin{prop}\label{prop:eq_are_mono}
-    Let $e: E \rightarrow A$ be the arrow that equalizes $f, g : A \rightarrow B$ in a category $\cat C$. Then $e$ is a monomorphism.
+    Let $e: E \rightarrow A$ be the arrow that equalizes $f, g : A \rightarrow B$ in a category $\cat C$. Then, $e$ is a monomorphism.
 \end{prop}
@@
     Suppose $X$ be an object and $x, y: X \rightarrow E$ be two morphisms in $\cat C$ such that $e \circ x = e \circ y$, and let $z = e \circ x$.
-Then, since $e$ is an equalizer, $f \circ e = g \circ e$ and $f \circ z = g \circ z$.
+Then, since $e$ is an equalizer, $f \circ e = g \circ e$, and $f \circ z = g \circ z$.
 But, for the universal property of equalizers, there must be exactly one $u: Z \rightarrow E$ such that $z = e \circ u$.
@@
 
-% Verificare la M-adesività utilizzando la definizione data sopra può essere particolarmente ostico. Per questa ragione, è possibile ricorrere al seguente risultato. [A new crit for MN-adh]
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be vary complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
+\begin{obs}
+    $\Set$ is adhesive.
+    % It is easy to check the first two points of the definition~\ref{def:adh} while for the Van Kampen property of pushouts along monos [...]
+\end{obs}
+
+Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
 
@@
 Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pullbacks, then $\cat C$ is $\mathcal M$-adhesive.
+    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
 \end{theorem}
@@
 Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (Example~\ref{ex:pb_as_limit}).
-Since $F$ creates pullbacks, hence lifts them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exists a pullback $(P, p_B, p_D)$ in $\cat C$.
+Since $F$ creates pullbacks, hence lifts them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
         \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
@@
 
-Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
+% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
 The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
+Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
+Such functor is defined as follow.
 
@@
 
+\begin{obs}
+    Quotient functor preserves limits. 
+\end{obs}
+
 Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \mathcal{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
@@
 Regular monos are preserved also by pushouts.
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
+Again, since (co)limits are computed pointwise \color{red}{(?)}\color{black}, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
 
@@
 % ----------------- Appendix ------------------ %
-**\appendix
+\appendix
 

### 2024-09-22 Article/main.tex
Reg closed under comosition

@@
 
+\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
+
 % General Setting diagrams
@@
 \newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\textbf 0}
+\newcommand{\initial}{\mymathbb{0}}
 \newcommand{\terminal}{\mathds{1}}
@@
 An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions~\cite{Herrlich_Strecker_1979}.
+The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
 
@@
 
+\color{red}{
     \begin{obs}
@@
     \end{obs}
+}\color{black}
 
@@
 The terminal object of $\Set$ is the singleton $\{ \bullet \}$, because there is exactly one function from a set $S$ to $\{ \bullet \}$, namely, the function which sends each $s \in S$ to $\bullet$.
-It is possible to visualize the Observation~\ref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective.
+It is possible to visualize the Observation~\ref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective, while there exists a unique initial object.
 \end{example}
@@
     $\Set$ has both products and coproduts.
-Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjoint sum $A \coprod B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
+Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjoint sum $A \amalg B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
 \end{example}
@@
 \end{definition}
+
+\begin{obs}
+    Given two composable regular monos $m$ and $n$, suppose that $n$ equalizes two arrows $f$ and $g$. Then, we have
+    \begin{align*}
+        g \circ (n \circ m) &= (g \circ n) \circ m &&\\
+                            &= (f \circ n) \circ m  && \textit{$n$ equalizer} \\
+                            &= f \circ (n \circ m)
+    \end{align*}
+    Since $n \circ m$ is mono (Proposition~\ref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
+\end{obs}
 
@@
     \color{blue}
-    In $\Set$, given two functions $f: A \rightarrow B$ and $g: A \rightarrow C$, the pushout of them is the set $X = (B \coprod C) /_\sim$, where $\sim$ is the least equivalence relation such that $f(a) \sim g(a)$ for each $a \in A$, with $\iota_g:B \rightarrow X$ and $\iota_f : C \rightarrow X$ as arrows, sending each element of the domain in the corresponding equivalence class in $X$.
+    In $\Set$, given two functions $f: A \rightarrow B$ and $g: A \rightarrow C$, the pushout of them is the set $X = (B \amalg C) /_\sim$, where $\sim$ is the least equivalence relation such that $f(a) \sim g(a)$ for each $a \in A$, with $\iota_g:B \rightarrow X$ and $\iota_f : C \rightarrow X$ as arrows, sending each element of the domain in the corresponding equivalence class in $X$.
 In particular, for each $a \in A$:

### 2024-09-24 Article/main.tex
Adjoints, Q preserves (co)limits

@@
 
-\section{Functors and Natural Transformations}\label{sect:funct_nats}
+\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
 
@@
 
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C$.
+In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
+
+\subsection{Adjoints}
+
+\begin{definition}\label{def:adjoint}[Adjoint Functor]
+    Let $\cat C$ and $\cat D$ be categories, and let $F:\cat{C \rightarrow D}$ and $G : \cat{D \rightarrow C}$ be functors.
+$G$ is called \emph{left adjoint} of $F$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (G \circ F)$ such that, for each object $A$ and each arrow $f: A \rightarrow G(B)$ of $\cat C$, there exists a unique arrow $g: F(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
+    \[
+        \begin{tikzcd}
+            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & G(F(A)) \arrow[d, dashed, "G(g)"] \\
+            & G(B)
+        \end{tikzcd}
+    \] -- i.e., if $G(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
+
+    Analogously, $F$ is called \emph{right adjoint} of $G$ provided that there exists a natural transformation $\epsilon : (F \circ G) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: F(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow G(B)$ of $\cat C$ such that the following diagram commutes:
+    \[
+        \begin{tikzcd}
+            F(G(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
+            F(A) \arrow[u, dashed, "F(f)"] \arrow[ur, "g"swap] 
+        \end{tikzcd}
+    \] -- i.e., $\epsilon_{B} \circ F(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
+\end{definition}
+
+% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
+In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
 
@@
 \]
+
 \begin{definition}\label{def:stab_under_pb_po}[Stability under pullbacks, pushouts]
@@
 \begin{prop}\label{prop:monos_pres_by_pullback}
-    Let $f: A \rightarrow C$, $g: B \rightarrow C$ arrows in any category $\cat C$, and consider the pullback square:
-    $$
+    Let $f: A \rightarrow C$, $g: B \rightarrow C$ be arrows in any category $\cat C$, and consider the following pullback square:
+    \[
         \begin{tikzcd}
@@
         \end{tikzcd}
-    $$
+    \]
     If $g$ is mono, then so is $\pi_g$.
@@
 \end{obs}
+
+The next theorem is about a particular property that adjoint functors have.
+
+\begin{theorem}\label{th:adjoints_preserves_lim}
+    Let $F: \cat{C \rightarrow D}$ be a functor, and $G: \cat{D \rightarrow C}$ its right adjoint. Then, $G$ preserves limits.
+\end{theorem}
+
+\begin{remark}
+    The dual of the theorem above states that, if $G$ is a functor and $F$ is a left adjoint, then $F$ preserves colimits.
+\end{remark}
 
@@
 Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[V \rightrightarrows E \rightarrow Q, \Set]$, in which each object $\mathcal{G}$ is a functor mapping the arrow $q: E \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
+We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\mathcal{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
 The component $\mathcal{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
@@
 
-\begin{obs}
-    Quotient functor preserves limits. 
-\end{obs}
+We now give some considerations on quotient functor.
+
+\begin{prop}
+    Quotient functor has a left adjoint and a right adjoint.
+\end{prop}
+
+\begin{proof}
+    To prove the statement we just have to find the adjoints. 
+    A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\mathcal{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
+To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
+The unit of the adjunction $\eta: Q \dot\rightarrow I$ is the one mapping $\mathcal{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \mathcal{G} \rightarrow I(\mathcal{H})$ in $\mathbf{EqGrph}$ -- that is, a morphism from a graph with equivalence onto a graph with all non-equivalent nodes, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
+    In particular, $I(\mathcal{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\mathcal{G}$ to $\mathcal{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
+Then, the arrow $I(h): I(Q(\mathcal{G})) \rightarrow I(\mathcal{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
+
+    A similar argument shows that the functor mapping each graph onto another wit all equivalent nodes is a right adjoint of $Q$.
+\end{proof}
+
+The following result lies on Theorem~\ref{th:adjoints_preserves_lim} and its dual.
+
+\begin{cor}\label{cor:quot_preserves_co_lim}
+    Quotient functor preserves limits and colimits. 
+\end{cor}
 

### 2024-09-24 Article/main.tex
minima on proof for prop 2.2.1

@@
 To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Q \dot\rightarrow I$ is the one mapping $\mathcal{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \mathcal{G} \rightarrow I(\mathcal{H})$ in $\mathbf{EqGrph}$ -- that is, a morphism from a graph with equivalence onto a graph with all non-equivalent nodes, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
+The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\mathcal{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \mathcal{G} \rightarrow I(\mathcal{H})$ in $\mathbf{EqGrph}$ -- that is, a morphism from a graph with equivalence onto a graph with all non-equivalent nodes, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
     In particular, $I(\mathcal{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\mathcal{G}$ to $\mathcal{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
@@
 In addition to Lemma~\ref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-    \todo{Generalizzare il fatto che i limiti in $\mathbf{EqGrph}$ rimangono limiti in $\mathbf{Graph}$} 
 \end{proof}

### 2024-09-26 Article/main.tex
minima on proof for prop 2.2.1

@@
 \newcommand{\terminal}{\mathds{1}}
+\newcommand{\eqgraph}[1]{\mathbb{#1}}
 
@@
 \begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\mathcal{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\mathcal{G} = (G, \sim_G)\rightarrow \mathcal{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
+    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
+An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
 Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
@@
 
-% \begin{definition}[Quotient functor]
-%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps
-%     each graph with equivalence $\mathcal{G} = (G, \sim_G)$ to its \emph{quotient graph} 
-%     $G/_{\sim_G} = (V_G/_{\sim_G}, E_G, s_G', t_G')$, with $s_G'([e]_{\sim_G}) = [v]_{\sim_G}$ if 
-%     $s_G(e) = v$ and the same for $t_G'$, and each homomorphism between graphs with equivalences 
-%     $h: \mathcal{G \rightarrow H}$ to $Q(h)$ defined by $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$.
-% \end{definition}
-
-% \begin{definition}[Quotient functor]
-%     The \emph{quotient functor} $Q: \mathbf{EqGrph \rightarrow Graph}$ is the functor that maps each $\mathcal{G} = (G, \sim)$ onto its quotient graph $G/_{\sim} = (V_G/_{\sim},E_G, s_G', t_G')$, such that, for each edge $e$:
-%     \begin{itemize}
-%         \item $s_G'([e]_{\sim}) = [v]_{\sim_G}$
-%     \end{itemize}
-% \end{definition}
-
 %TODO: RIGUARDARE QUESTA PARTE!!!
@@
 % Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\mathcal{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
+The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
 Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
@@
     \begin{itemize}
-        \item on objects, given $\mathcal{G}=(G, \sim_{G})$ as $Q(\mathcal{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \mathcal{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
+        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
+        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
     \end{itemize}
@@
 The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\mathcal{G} = (G, \sim_G) $ and $\mathcal{H} = (H, \sim_{H})$, one can construct the product graph $\mathcal{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\mathcal{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \mathcal{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\mathcal{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\mathcal{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \mathcal{E \rightarrow G}$.
+Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
+An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
 The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
@@
     In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \mathcal{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
+That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
 \end{prop}
-
-%TODO: EGGS
-\subsection{E-Graphs}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\mathcal{G} = (G, \sim)$.
 
@@
 Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\mathcal{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\mathcal{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
+We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
+The component $\eqgraph{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
 In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
@@
     To prove the statement we just have to find the adjoints. 
-    A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\mathcal{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
+    A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
 To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\mathcal{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \mathcal{G} \rightarrow I(\mathcal{H})$ in $\mathbf{EqGrph}$ -- that is, a morphism from a graph with equivalence onto a graph with all non-equivalent nodes, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    In particular, $I(\mathcal{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\mathcal{G}$ to $\mathcal{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\mathcal{G})) \rightarrow I(\mathcal{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
+The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$ -- that is, a morphism from a graph with equivalence onto a graph with all non-equivalent nodes, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
+    In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
+Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
 
@@
 
-Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \mathcal{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
+Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
 Since limits are computed pointwise, pullbacks preserve regular monomorphisms (Proposition~\ref{prop:monos_pres_by_pullback}).
 Regular monos are preserved also by pushouts.
-Again, since (co)limits are computed pointwise \color{red}{(?)}\color{black}, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
+Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
 
@@
 \end{proof}
+
+%TODO: EGGS
+\section{E-Graphs}\label{sect:eggs}
+
+E-Graphs are a particular type of graphs with equivalences, in which holds that
+$$
+    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
+$$
+for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
+In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
+\[
+    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
+\] for each $e$, $e' \in \eqgraph{G}(E)$.
+But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
+But $S$ (and the projection arrows) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ is the pullback of $(q \circ t, q \circ t)$.
+Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that {\color{red}{there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$}}.
+
+\begin{definition}\label{def:cat_of_eggs}[Category of E-Graphs]
+    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
+\end{definition}
 

### 2024-09-27 Article/main.tex
quasi-adh of EGG

@@
 \newcommand{\eqgraph}[1]{\mathbb{#1}}
+\newcommand{\Egg}{\mathbf{EGG}}
 
@@
 
-\begin{example}
+\begin{example}\label{ex:full_subc_inc_fully_faith}
     Let $\cat C$ be a category and $\cat D$ a subcategory.
@@
 
+\begin{prop}\label{prop:inc_funct_reflects_so_limits}
+    A fully faithful functor reflects all limits and colimits.
+\end{prop}
+
 The next theorem is about a particular property that adjoint functors have.
@@
     \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
+        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
+Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
 Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (Example~\ref{ex:pb_as_limit}).
@@
 
-    A similar argument shows that the functor mapping each graph onto another wit all equivalent nodes is a right adjoint of $Q$.
+    A similar argument shows that the functor mapping each graph onto another with all equivalent nodes is a right adjoint of $Q$.
 \end{proof}
@@
 
-%TODO: EGGS
 \section{E-Graphs}\label{sect:eggs}
@@
 \end{definition}
+
+Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
+Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (Example~\ref{ex:full_subc_inc_fully_faith}), it reflects all limits (Propositon~\ref{prop:inc_funct_reflects_so_limits}).
+But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
+Then, we can conclude as follows.
+
+\begin{lemma}
+    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
+\end{lemma}
+
+Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
+Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
+
+\begin{prop}
+    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
+\end{prop}
+
+At this point, by direct application of Theorem~\ref{th:crit_for_adh}, it is possible to state what follows.
+
+\begin{cor}
+    $\mathbf{EGG}$ is quasiadhesive.
+\end{cor}
 

### 2024-09-27 Article/main.tex
quasi-adh of EGG

@@
 \usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
+\usepackage{cleveref}
 \raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
@@
 The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (Definition~\ref{def:diagram}).
+A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
 
@@
 \begin{remark}\label{rem:small_cats}
-    It is important to note that the Definition~\ref{def:category} above does not specify what kind of collections
+    It is important to note that the \Cref{def:category} above does not specify what kind of collections
     %for a category $\cat{C}$, 
@@
 Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (Definition~\ref{def:limit}).
+Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
 
@@
 
-The Observation~\ref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
+The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
 This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
@@
 
-A functor with a small category as domain (Remark~\ref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
+A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
 Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
@@
 Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (Definition~\ref{def:slice_cat}).
+An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
 
@@
 
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in Example~\ref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
+Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
 \[
@@
 \end{definition}
+\todo{sistemare la definizione}
 
@@
 The terminal object of $\Set$ is the singleton $\{ \bullet \}$, because there is exactly one function from a set $S$ to $\{ \bullet \}$, namely, the function which sends each $s \in S$ to $\bullet$.
-It is possible to visualize the Observation~\ref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective, while there exists a unique initial object.
-\end{example}
-
-We now illustrate a result on functor categories (Definition~\ref{def:functor_category}) that will be useful later.
+It is possible to visualize the \Cref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective, while there exists a unique initial object.
+\end{example}
+
+We now illustrate a result on functor categories (\Cref{def:functor_category}) that will be useful later.
 
@@
 
-In particular, every presheaf has an initial and a terminal object, because $\Set$ does (Example~\ref{ex:set_init_term}).
+In particular, every presheaf has an initial and a terminal object, because $\Set$ does (\Cref{ex:set_init_term}).
 
@@
     \end{align*}
-    Since $n \circ m$ is mono (Proposition~\ref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
+    Since $n \circ m$ is mono (\Cref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
 \end{obs}
@@
 \begin{obs}
-    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in Observation~\ref{obs:category_of_cones}.
+    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in \Cref{obs:category_of_cones}.
 \end{obs}
@@
     \]
-    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in Example~\ref{ex: span}):
+    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in \Cref{ex: span}):
     \[
@@
 
-    This example show us that a pullback is a limit for a cospan (Example~\ref{ex: span}).
+    This example show us that a pullback is a limit for a cospan (\Cref{ex: span}).
 \end{example}
@@
 \begin{example}\label{ex:colm_of_sets}
-    As we have done in Example~\ref{ex:lim_of_sets}, we illustrate how to construct colimits in the category of sets.
+    As we have done in \Cref{ex:lim_of_sets}, we illustrate how to construct colimits in the category of sets.
 Given a small category $\cat I$, $ I = Ob(\cat I)$, and a diagram $D: \cat I \rightarrow \Set$, consider the equivalence relation $\sim$ defined on $\coprod_{i\in I} D(i)$ such that $d_i \sim d_{i'}$ if $d_i \in D(i), d_{i'} \in D(i')$ and there exists some $\phi \in \cat I(i, i')$ such that $D(\phi)(d_i) = d_{i'}$.
@@
 \begin{definition}\label{def:adh}[$\mathcal{M}$-adhesivity]
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (Definition~\ref{def:stab_under_pb_po}).
+    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
     Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
@@
     $\Set$ is adhesive.
-    % It is easy to check the first two points of the definition~\ref{def:adh} while for the Van Kampen property of pushouts along monos [...]
+    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
 \end{obs}
@@
 \begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in Definition~\ref{def:adh}.
+    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
     \begin{itemize}
@@
 Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (Example~\ref{ex:pb_as_limit}).
-Since $F$ creates pullbacks, hence lifts them (Observation~\ref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
+Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{ex:pb_as_limit}).
+Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
         \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
@@
 
-\color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-Sec. 1 Categorie e funtori
-
->def di categorie
-	-menzionare che data una categoria c'è il duale
-	-epi, mono e  iso
-
->funtori e trasf naturali
-
->categorie comma (con slice e coslice come sottocaso)
-
-Sec. 2: Limiti e colimiti
-Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
->definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-	-epi e mono regolari
-
->Limiti nelle categorie di funtori e comma
-
-Sec. 3: Adesività
-Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-\color{black}
+{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
+
+% Sec. 1 Categorie e funtori
+
+% >def di categorie
+% 	-menzionare che data una categoria c'è il duale
+% 	-epi, mono e  iso
+
+% >funtori e trasf naturali
+
+% >categorie comma (con slice e coslice come sottocaso)
+
+% Sec. 2: Limiti e colimiti
+% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
+
+% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
+% 	-epi e mono regolari
+
+% >Limiti nelle categorie di funtori e comma
+
+% Sec. 3: Adesività
+% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
+% \color{black}
+}
 
@@
 
-All the constructions defined in Section~\ref{sect:univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
+All the constructions defined in \Cref{sect:univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
 The next examples try to make this point clear.
@@
 \begin{obs}
-    $\mathbf{Graph}$, defined in Definition~\ref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
+    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
 \end{obs}
@@
 
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by Theorem~\ref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
+Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
 
@@
 
-Considering the category of graphs (as defined in Definition~\ref{def:cat_of_graph}), it is possible to show that 
+Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
 $$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
 where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (Definition~\ref{def:graph_hom})
+A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
 $$
@@
 
-Example~\ref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of Observation~\ref{obs:limits_in_presh}.
+\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
 
@@
 We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in Remark~\ref{rem:eq_as_surj}.
+The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
 In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
@@
 
-The following result lies on Theorem~\ref{th:adjoints_preserves_lim} and its dual.
+The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
 
@@
 
-Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Since limits are computed pointwise, pullbacks preserve regular monomorphisms (Proposition~\ref{prop:monos_pres_by_pullback}).
+Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
+Since limits are computed pointwise, pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
 Regular monos are preserved also by pushouts.
@@
 \begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of Definition~\ref{def:stab_under_pb_po}).
+    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
 \end{lemma}
@@
 \begin{proof}
-    In order to apply Theorem~\ref{th:crit_for_adh}, we can consider the quotient functor defined in Definition~\ref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
+    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
 We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to Lemma~\ref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
+In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
 \end{proof}
@@
 Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (Example~\ref{ex:full_subc_inc_fully_faith}), it reflects all limits (Propositon~\ref{prop:inc_funct_reflects_so_limits}).
+Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
 But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
@@
 Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (Proposition~\ref{prop:reg_mono_in_EG_are_mono_in_graph}).
+Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
 
@@
 
-At this point, by direct application of Theorem~\ref{th:crit_for_adh}, it is possible to state what follows.
+At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
 
@@
 
-\paragraph{Theorem~\ref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
+\paragraph{\Cref{th:limit}.}
+ Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
 \begin{proof}
@@
 
-    The \emph{if} statement is easily satisfied as shown in Example~\ref{ex:equaliz_are_limits} and Example~\ref{ex:product_are_limits}.
+    The \emph{if} statement is easily satisfied as shown in \Cref{ex:equaliz_are_limits} and \Cref{ex:product_are_limits}.
 

### 2024-10-01 Article/main.tex
minima
def EGraph

@@
 \usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{cleveref}
+\usepackage{hyperref, cleveref}
 \raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
@@
 
+Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
+
 \begin{definition}\label{def:dual_cat}[Dual Category]
@@
 
+For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
+This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
+
+\begin{definition}[Subobjects]
+    Let $C$ be an object in a category $\cat C$.
+Then, if $m: A \rightarrow C$ is mono, $(A, m)$ is said to be a \emph{subobject} of $C$.
+Factorization of morphisms induces a preorder on subobjects of an object.
+$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
+    \[
+        \begin{tikzcd}[row sep=9]
+            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
+            & B \\
+            C \arrow[ur, "n"swap] &
+        \end{tikzcd}
+    \]
+    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subibjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$.
+\end{definition}
+
+An useful fact about subobjects is how factorization behaves.
+In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
+Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
+Suppose $k$ is another morphism such that $m = n \circ k$.
+We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
+This is to say what follows.
+
+\begin{prop}\label{prop:fact_of_subobjects_is_unique}
+    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
+\end{prop}
+
 \begin{definition}[Epimorphism]\label{def:epi}
@@
 
-\begin{definition}\label{def:adjoint}[Adjoint Functor]
+\begin{definition}[Adjoint Functor]\label{def:adjoint}
     Let $\cat C$ and $\cat D$ be categories, and let $F:\cat{C \rightarrow D}$ and $G : \cat{D \rightarrow C}$ be functors.
@@
 
-\begin{definition}\label{def:stab_under_pb_po}[Stability under pullbacks, pushouts]
+\begin{definition}[Stability under pullbacks, pushouts]\label{def:stab_under_pb_po}
     Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every pullback square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
@@
 
-\begin{theorem}\label{th:limit}[Limit theorem]
+\begin{theorem}[Limit theorem]\label{th:limit}
     Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
@@
 
-\begin{definition}\label{def:adh}[$\mathcal{M}$-adhesivity]
+\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
     Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
@@
 
-\begin{definition}\label{def:graph_hom}[Graph Homomorphism]
+\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
     Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
@@
 
-\begin{definition}\label{def:quot_func}[Quotient Functor]
+\begin{definition}[Quotient Functor]\label{def:quot_func}
     The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
@@
 But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (and the projection arrows) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that {\color{red}{there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$}}.
-
-\begin{definition}\label{def:cat_of_eggs}[Category of E-Graphs]
+But $S$ (with the projection arrows$p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
+Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
+To find a structure to express this fact, we have to consider a more general case.
+
+Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
+\[
+    \begin{tikzcd}
+        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
+        X \arrow[r, "f"swap] & Y
+    \end{tikzcd}
+\]
+Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
+\todo{capire quanto andare nello specifico qui}
+
+Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
+Specifically, we want, in the following situation, $i$ to be mono and unique.
+\[
+    \begin{tikzcd}
+        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
+        & \eqgraph{G}(E) \times \eqgraph{G}(E)
+    \end{tikzcd}
+\]
+We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
+From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
+The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
+If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
+
+\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
     The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.

### 2024-10-04 Article/main.tex
minima

@@
 But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows$p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
+But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
 Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
@@
 Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
+The following result follows by the fact that a fully and faithful functor preserves limits, and then preserves equalizers.
 

### 2024-10-08 Article/main.tex
minima

@@
 
-\begin{definition}[Adjoint Functor]\label{def:adjoint}
-    Let $\cat C$ and $\cat D$ be categories, and let $F:\cat{C \rightarrow D}$ and $G : \cat{D \rightarrow C}$ be functors.
-$G$ is called \emph{left adjoint} of $F$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (G \circ F)$ such that, for each object $A$ and each arrow $f: A \rightarrow G(B)$ of $\cat C$, there exists a unique arrow $g: F(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & G(F(A)) \arrow[d, dashed, "G(g)"] \\
-            & G(B)
-        \end{tikzcd}
-    \] -- i.e., if $G(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-    Analogously, $F$ is called \emph{right adjoint} of $G$ provided that there exists a natural transformation $\epsilon : (F \circ G) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: F(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow G(B)$ of $\cat C$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(G(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-            F(A) \arrow[u, dashed, "F(f)"] \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \] -- i.e., $\epsilon_{B} \circ F(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-\end{definition}
-\todo{sistemare la definizione}
+% \begin{definition}[Adjoint Functor]\label{def:adjoint}
+%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
+$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
+%     \[
+%         \begin{tikzcd}
+%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
+%             & L(B)
+%         \end{tikzcd}
+%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
+
+%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
+%     \[
+%         \begin{tikzcd}
+%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
+%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
+%         \end{tikzcd}
+%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
+% \end{definition}
+%\todo{sistemare la definizione}
+
+\begin{definition}[Right Adjoint]\label{def:right_adjoint}
+    Let $R: \cat{C \rightarrow D}$ be a functor.
+$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
+    \[
+        \begin{tikzcd}
+            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
+            & R(B)
+        \end{tikzcd}
+    \]
+    --i.e., $R(g) \circ \eta_A = f$.
+\end{definition}
+
+\begin{prop}\label{prop:ext_left_to_funct}
+    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
+\end{prop}
+
+\begin{proof}
+    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}. It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$ such that: $R(L(f)) \circ \eta_X = \eta_Y \circ f$.
+\end{proof}
+
+\begin{definition}[Left Adjoint]\label{def:left_adjoint}
+    Let $L: \cat{D \rightarrow C}$ be a functor.
+$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
+    \[
+        \begin{tikzcd}
+            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
+            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
+        \end{tikzcd}
+    \]
+    -- i.e., $\epsilon_B \circ L(f) = g$.
+\end{definition}
+
+As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
+
+The connection between left and right adjoints is expressed in the following proposition.
+
+\begin{prop}
+    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
+\end{prop}
+
+\begin{proof}
+
+\end{proof}
 
@@
 To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$ -- that is, a morphism from a graph with equivalence onto a graph with all non-equivalent nodes, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
+The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
+    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
 Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
 
-    A similar argument shows that the functor mapping each graph onto another with all equivalent nodes is a right adjoint of $Q$.
+    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$ such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
+We have then the following situation:
+    \[
+        \begin{tikzcd}
+            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
+            & T(\mathcal{H}) = \eqgraph{H}
+        \end{tikzcd}
+    \]
+    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
+Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
+Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ G)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
 \end{proof}
@@
 
+\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
+    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
+\end{prop}
+
+\begin{proof}
+    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
+Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
+The argument lies on the consideration that limits in presheaves categories are computed pointwise.
+In fact, we can
+\end{proof}
+
 Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
@@
 
+\begin{proof}
+    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
+    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
+(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
+\end{proof}
+
 Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
 Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves limits, and then preserves equalizers.
+The following result follows by the fact that a fully and faithful functor preserves equalizers.
+{\color{red}{????
+Da dimostrare}}
 

### 2024-10-09 Article/main.tex
Proof prop 2.2.1

@@
     To prove the statement we just have to find the adjoints. 
-    A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
+    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
 To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
@@
 Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
+
+    Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
+    Consider the following situation:
+    \[
+        \begin{tikzcd}
+            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
+            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
+            & \mathcal{G} \\
+            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
+            \arrow[u, dashed, "I(f)"] 
+            \arrow[ur, "g"swap] 
+        \end{tikzcd}
+    \]
+    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
+Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
 

### 2024-10-10 Article/main.tex
osservazioni

@@
     \end{enumerate}
-    For each morphism $f \in \Hom(\cat{C})$, there are two operators $dom$ and $cod$ that map every morphism to two objects, respectively, its \emph{domain} and its \emph{codomain}.
+   \todo{Non sono d'accordo con quello che è scritto qui.
+Non è vero che per ogni morfismo esistono due operatori dom e cod.
+Semmai esistono due operatori che ad ogni morfismo associano un dominio ed un codominio} For each morphism $f \in \Hom(\cat{C})$, there are two operators $dom$ and $cod$ that map every morphism to two objects, respectively, its \emph{domain} and its \emph{codomain}.
 In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
@@
 \begin{example}
-    It is easy to see that taking sets as objects and total functions as arrows, we obtain a category.
+    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
 In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
@@
     Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono, $(A, m)$ is said to be a \emph{subobject} of $C$.
+Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
+Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
 Factorization of morphisms induces a preorder on subobjects of an object.
@@
     \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subibjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$.
+    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
 \end{definition}
@@
 \end{prop}
+\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
 
@@
 \todo{E cambierei anche l'intro a questa sezione DC}
+\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
 

### 2024-10-10 Article/main.tex
minori

@@
 \end{prop}
-
+\todo{Devi mostrare che eta risulta naturale (viene in automatico ma conviene scriverlo per la dimostrazione successiva).}
 \begin{proof}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}. It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$ such that: $R(L(f)) \circ \eta_X = \eta_Y \circ f$.
+    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
+It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
 \end{proof}
@@
 \begin{proof}
-
+	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
+	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
+	    \[
+	\begin{tikzcd}
+		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
+		& R(B)
+	\end{tikzcd}
+	\]
+
+	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
+	\begin{align*}
+		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
+	\end{align*}
+	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
  \end{proof}
@@
 \section{Universal Constructions}\label{sect:univ_constr}
-
+\todo{Questa è da riscriviere e ridurre}
 % What we are interested in are the "best" construction having a certain property, and we exprtess this fact via requiring unique factorization when another construction does

### 2024-10-10 Article/main.tex
lemma 2.2.3

@@
 
+Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
+
+\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
+    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
+\end{prop}
+
 Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
@@
 
+\color{red}{
+
+\begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
+    Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
+\end{lemma}
+
+\begin{proof}
+    Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
+    \[
+        \begin{tikzcd}
+            G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
+            G_2 \arrow[r, "j" swap] & P
+        \end{tikzcd}
+    \]
+    In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise,\color{green}{commentato}\color{black}
+
+    %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
+Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
+\end{proof}
+
+}\color{black}
 Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Since limits are computed pointwise, pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts.
+Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
+Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
 Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
@@
 \end{lemma}
+
+% Q crea pullback, Q crea pushout sui reg mono.
 

### 2024-10-13 Article/main.tex
osservazioni

@@
     In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
+Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
 \end{prop}
-\todo{Devi mostrare che eta risulta naturale (viene in automatico ma conviene scriverlo per la dimostrazione successiva).}
 \begin{proof}
     Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
+Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unqiue arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
+    \[
+    \begin{tikzcd}
+    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
+    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
+    \end{tikzcd}
+    \]
+
+    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
+    \[
+    \begin{tikzcd}
+    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
+    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
+    \end{tikzcd}
+    \]    \[
+    \begin{tikzcd}
+    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
+    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
+    \end{tikzcd}
+    \]
+
+    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
 \end{proof}
@@
 % Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
+The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph\todo{sposta questo discorso dopo il calcolo dei limiti, così che sia appena prima della dimostrazione sugli aggiunti} $G/_{\sim_G}$.
 Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
@@
 In the category of graphs with equivalences, universal constructions are easy to obtain.
+\begin{prop}COME SI CALCOLANO I LIMITI IN $\mathbf{EqGrph}$
+\end{prop}
+\begin{proof}
+	TO DO
+\end{proof}
+
+ \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
 The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
@@
 
-An important characterization in the category of graphs with equivalences is the following.
+An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
 
@@
 \section{Graphs as Functors}
-
+\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
+ senso come remark separato e la restante parte della sezione si salda a quella precedente}
 Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
@@
 
-    Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
+    Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
+Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
     Consider the following situation:
@@
 
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$ such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
+    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$ \todo{stesso problema di prima.
+Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.}such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
 We have then the following situation:
@@
 }\color{black}
+
+COSE DA FARE
+
+>Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente )
+
+>Quoziente crea certi pushout (questo va fatto ex novo)
+
 Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
@@
 \section{E-Graphs}\label{sect:eggs}
+
+COSE DA FARE:
+Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
+
+>Definizione
+>Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
+> cor del calcolo dei limiti: caratterizzare mono regolari
+>I crea limiti e i giusti pushout
+> e-graph sono quasiadesivi
 

### 2024-10-13 Article/main.tex
lemmi vari

@@
 \end{prop}
+\todo{Devi mostrare che eta risulta naturale (viene in automatico ma conviene scriverlo per la dimostrazione successiva).}
 \begin{proof}
+    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
+It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
     Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
@@
 In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}COME SI CALCOLANO I LIMITI IN $\mathbf{EqGrph}$
+\begin{prop}
+    COME SI CALCOLANO I LIMITI IN $\mathbf{EqGrph}$
 \end{prop}
@@
 \end{proof}
-
  \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
@@
 \section{Graphs as Functors}
+
 \todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
  senso come remark separato e la restante parte della sezione si salda a quella precedente}
+
 Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
@@
     A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$ \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.}such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
+Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.} such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
 We have then the following situation:
@@
     \]
-    In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise,\color{green}{commentato}\color{black}
+    In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
+    \[
+        \begin{tikzcd}
+            G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
+            G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
+        \end{tikzcd}
+    \]
+    From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
 
@@
 \end{proof}
-
 }\color{black}
-
+\todo[color=green!40]{
 COSE DA FARE
-
 >Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
-
 >Quoziente crea certi pushout (questo va fatto ex novo)
-
-Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
+}
+% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
 Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
@@
 % Q crea pullback, Q crea pushout sui reg mono.
+
+\begin{lemma}
+    The quotient functor creates pullbacks.
+\end{lemma}
+
+\begin{proof}
+    We will show now that $Q$ reflects pullbacks.
+    Consider the following diagram in $\mathbf{Graph}$
+    \[
+        \begin{tikzcd}
+            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
+            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
+        \end{tikzcd}
+    \]
+    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
+We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
+\color{green}{continuare}\color{black}
+    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
+\end{proof}
+
+\begin{lemma}
+    The quotient functor creates pullbacks along regular monomorphism.
+\end{lemma}
 
@@
 
+\todo[color=green!40]{
     COSE DA FARE:
 Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
-
 >Definizione
@@
 > e-graph sono quasiadesivi
+}
 

### 2024-10-14 Article/main.tex
tolto un todo
minima

@@
 \usepackage{graphicx} % Per includere immagini esterne
-\usepackage{todonotes}
-\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento
+\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
+% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
 \usepackage[fontsize=12pt]{scrextend} %dimensione font
@@
 \end{prop}
-\todo{Devi mostrare che eta risulta naturale (viene in automatico ma conviene scriverlo per la dimostrazione successiva).}
 \begin{proof}
@@
 
+\begin{remark}
+    The family above mentioned is called \emph{unit} of the adjunction.
+\end{remark}
+
 \begin{definition}[Left Adjoint]\label{def:left_adjoint}
@@
 As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
+The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
 
@@
 In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}
+\begin{prop}\label{prop:limits_in_EqGrph}
     COME SI CALCOLANO I LIMITI IN $\mathbf{EqGrph}$
+    % GUESS: limiti calcolati componente per componente su E e V, e restrizioni su Q (?) come in Graph (Dipende da prefasci).
 \end{prop}
@@
 
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$ \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.} such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
+    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
+    \todo{stesso problema di prima. Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.}
+    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
 We have then the following situation:
@@
 Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ G)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
+Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
 \end{proof}
@@
 We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-\color{green}{continuare}\color{black}
+    \color{green}{
+        Since limits are computed pointwise in $\mathbf{EqGrph}$ on $E$ and $V$ components, we have that 
+        % IDEA: come si calcola un pullback in EgGrph?
+--> componente per componente, e poi su Q la least equiv relation such that ..., quindi applicando il funtore quoziente ottengo esattamente il pullback dei quozienti.
+    }\color{black}
     Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
@@
 \begin{lemma}
-    The quotient functor creates pullbacks along regular monomorphism.
+    The quotient functor creates pushouts along regular monomorphism.
 \end{lemma}
+
+\begin{proof}
+    1) --> Q preserva pushout along reg monos ()
+\end{proof}
 

### 2024-10-16 Article/main.tex
prove

@@
 
+In the category of graphs with equivalences, universal constructions are easy to obtain. 
+\begin{prop}\label{prop:limits_in_EqGrph}
+    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
+Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
+    \begin{itemize}
+        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
+        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
+    \end{itemize}
+    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
+(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
+\end{prop}
+
+\begin{proof}
+
+    \color{red}{
+    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
+Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
+Our claim is $D(\alpha) \circ l^i = l^j$.
+Hence,
+    \begin{align*}
+        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
+                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
+                            &= (l^j_V, l^j_E)                       \\
+                            &= l^j                              
+    \end{align*}
+    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
+But such equivalence relation exists in every case, considering the identity.
+This led us to the second point of the proof, that is, the universal property.
+    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
+    For the cone described above to be a limit must be valid the universal property.
+Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
+Suppose the following situation:
+    \[
+        \begin{tikzcd}
+            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
+            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
+            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
+        \end{tikzcd}
+    \]
+    The universal property the follows from the definition of least equivalence relation.
+    } \color{black}
+\end{proof}
+
+ \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
+The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
+Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
+An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
+The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
+
+Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
+
+An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
+
+\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
+    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
+That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
+\end{prop}
+
+\section{Graphs as Functors}
+
+\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
+ senso come remark separato e la restante parte della sezione si salda a quella precedente}
+
+Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
+We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
+This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
+An example will make clear what we are talking about.
+
+Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
+$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
+where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
+A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
+$$
+    \begin{tikzcd}
+        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
+        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
+    \end{tikzcd}
+$$
+(and the same for $t$).
+
+\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
+
+Graphs with equivalence are more complex objects.
+We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
+The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
+In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
+
 % Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
@@
 \end{definition}
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    COME SI CALCOLANO I LIMITI IN $\mathbf{EqGrph}$
-    % GUESS: limiti calcolati componente per componente su E e V, e restrizioni su Q (?) come in Graph (Dipende da prefasci).
-\end{prop}
-\begin{proof}
-    TO DO
-\end{proof}
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
 
@@
 \end{proof}
+
+\begin{cor}\label{cor:quot_pres_reg_mono_pushouts}
+    Quotient functor preserves pushouts along regular monomorphisms.
+\end{cor}
+
 }\color{black}
@@
     \color{green}{
-        Since limits are computed pointwise in $\mathbf{EqGrph}$ on $E$ and $V$ components, we have that 
+        from \Cref{prop:limits_in_EqGrph}, we note that a limit in $\mathbf{EqGrph}$ is nothing more than the limit graph embedded with an equivalence relation.
         % IDEA: come si calcola un pullback in EgGrph?
@@
 
-\begin{proof}
-    1) --> Q preserva pushout along reg monos ()
-\end{proof}
+% \begin{proof}
+%     Consider the following situation
+% \end{proof}
 

### 2024-10-18 Article/main.tex
quoteint creates pullbacks

@@
     \end{enumerate}
-   \todo{Non sono d'accordo con quello che è scritto qui.
-Non è vero che per ogni morfismo esistono due operatori dom e cod.
-Semmai esistono due operatori che ad ogni morfismo associano un dominio ed un codominio} For each morphism $f \in \Hom(\cat{C})$, there are two operators $dom$ and $cod$ that map every morphism to two objects, respectively, its \emph{domain} and its \emph{codomain}.
+    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
 In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
@@
 This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    {\color{green}{rivedere}}
     A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
@@
 % Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph\todo{sposta questo discorso dopo il calcolo dei limiti, così che sia appena prima della dimostrazione sugli aggiunti} $G/_{\sim_G}$.
+The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
 Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
@@
     A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima. Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.}
+    \todo{stesso problema di prima.
+Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
+UPDATE: probabilmente questo non è nu funtore aggiunto}
     such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
@@
 
-\begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-    Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
+% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
+%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
+% \end{lemma}
+
+% \begin{proof}
+%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
+%     \[
+%         \begin{tikzcd}
+%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
+%             G_2 \arrow[r, "j" swap] & P
+%         \end{tikzcd}
+%     \]
+%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
+%     \[
+%         \begin{tikzcd}
+%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
+%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
+%         \end{tikzcd}
+%     \]
+%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
+
+%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
+Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
+% \end{proof}
+
+\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
+    Quotient functor preserves pushouts along regular monomorphisms.
 \end{lemma}
-
-\begin{proof}
-    Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-    \[
-        \begin{tikzcd}
-            G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-            G_2 \arrow[r, "j" swap] & P
-        \end{tikzcd}
-    \]
-    In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-    \[
-        \begin{tikzcd}
-            G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-            G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-        \end{tikzcd}
-    \]
-    From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-    %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-\end{proof}
-
-\begin{cor}\label{cor:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{cor}
+\todo{Capire qui!}
 
@@
 We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-    \color{green}{
-        from \Cref{prop:limits_in_EqGrph}, we note that a limit in $\mathbf{EqGrph}$ is nothing more than the limit graph embedded with an equivalence relation.
-        % IDEA: come si calcola un pullback in EgGrph?
---> componente per componente, e poi su Q la least equiv relation such that ..., quindi applicando il funtore quoziente ottengo esattamente il pullback dei quozienti.
-    }\color{black}
+But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
     Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.

### 2024-10-20 Article/main.tex
reordering of section on limits

@@
 
+\begin{example}\label{ex:0_cat}
+    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
+\end{example}
+
 \begin{example}\label{ex:1_cat}
@@
     Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unqiue arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
+Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
     \[
@@
 In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-
-\section{Universal Constructions}\label{sect:univ_constr}
-\todo{Questa è da riscriviere e ridurre}
-% What we are interested in are the "best" construction having a certain property, and we exprtess this fact via requiring unique factorization when another construction does
-
-\subsection{Initial and Terminal Objects}
-
-The next definitions are about \emph{universal constructions}. The simplest ones are the notion of initial and, dually, terminal objects.
-
-\begin{definition}[Initial and terminal object]
-    An object $A$ of a category $\cat C$ is said to be \emph{initial} if, for each other object $B$ of $\cat C$, there exists a unique morphism from $A$ to $B$.
-    Dually, an object $Z$ is said to be a terminal object in a category $\cat C$ if, for any other object $X$ of $\cat C$, there exists a unique morphism from $X$ to $Z$.
-    An initial object is indicated by the symbol $\initial$, and a terminal object by the symbol $\terminal$.
-\end{definition}
-
-\begin{obs}\label{obs:terminal_are_isomorph}
-    It makes sense to refer to an initial (and terminal) object as \emph{the} initial (\emph{the} terminal) object.
-Suppose that $\initial$ and $\initial'$ are distinct initial objects of a category $\cat C$.
-Then, there exists a unique morphism from $\initial$ to $\initial'$, say $f$.
-Likewise, it must exist a unique morphism from $\initial'$ to $\initial$, say $g$.
-Then, $g\circ f$ must be exactly $id_{\initial}$, and $f \circ g = id_{\initial'}$, and then they are isomorphic.
-The same argument works for the terminal object.
-\end{obs}
-
-\begin{example}\label{ex:set_init_term}
-    In $\Set$, the initial object is the empty set $\varnothing$, because, for each set $S$, there exists the empty function from $\varnothing$ to $S$.
-The terminal object of $\Set$ is the singleton $\{ \bullet \}$, because there is exactly one function from a set $S$ to $\{ \bullet \}$, namely, the function which sends each $s \in S$ to $\bullet$.
-It is possible to visualize the \Cref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective, while there exists a unique initial object.
-\end{example}
-
-We now illustrate a result on functor categories (\Cref{def:functor_category}) that will be useful later.
-
-\begin{prop}
-    Let $\cat D$ be a category.
-If $\cat D$ has an initial object, then, for any category $\cat C$, $[\cat{C, D}]$ has an initial object.
-If $\cat D$ has a terminal object, then, for any category $\cat C$, $[\cat{C, D}]$ has a terminal object.
-\end{prop}
-
-\begin{proof}
-    Let $\initial_{\cat{D}}$ be the initial object of $\cat D$,  and consider the constant functor $I(f) = id_{\initial_{\cat D}}$ for all $f \in \Hom(\cat C)$.
-Then, for any $G: \cat{C \rightarrow D}$, $\eta: I \rightarrow G$, defining $\eta_A$ as the \emph{unique morphism from $\initial_{\cat D}$ to $G(A)$} for each $A \in \Ob(\cat C)$, is a natural transformation $I \dot\rightarrow G$, as the diagram below shows:
-    \[
-        \begin{tikzcd}
-            I(A)=\initial_{\cat D} 
-                    \arrow[r, "{\eta_A}"]
-                    \arrow[d, "{I(f) = id_{\initial_{\cat D}}}" swap] &
-            G(A)
-                    \arrow[d, "G(f)"] \\
-            I(A') = \initial_{\cat D}
-                    \arrow[r, "{\eta_{A'}}" swap] &
-            G(A')
-        \end{tikzcd}
-    \]
-    for each $f: A \rightarrow A'$, the square above must commute, since there is only one morphism from $\initial_{\cat D}$ to $G(A')$.
-For the same reason, $\eta$ is the only natural transformation from $I$ to $G$, being indeed the initial object of $[\cat{C, D}]$.
-
-    Defining $T(f) = id_{\terminal_{\cat D}}$ for each $f \in \Hom(\cat C)$.
-Then, $\theta:F\rightarrow T$, for any $F: \cat{C \rightarrow D}$, defining $\theta_A$ as the \emph{unique morphism from $F(A)$ to $\terminal_{\cat{D}}$} is a natural transformation due to the commutativity of the following diagram for each $f: A \rightarrow A'$:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[r, "{\theta_A}"] \arrow[d, "F(f)" swap] &
-            T(A) = \terminal_{\cat D} \arrow[d, "{T(f) = id_{\terminal_{\cat D}}}"] \\
-            F(A') \arrow[r, "{\theta_{A'}}" swap] & T(A') = \terminal_{\cat D}
-        \end{tikzcd}
-    \]
-    Hence, $\theta$ is the unique natural transformation from $F$ to $T$, and $T$ is the terminal object of $[\cat{C, D}]$.
-\end{proof}
-
-In particular, every presheaf has an initial and a terminal object, because $\Set$ does (\Cref{ex:set_init_term}).
-
-\subsection{Products and Coproducts}
-
-More complex constructions are products (and, dually, coproducts).
-
-\begin{definition}[Product]
-    A \emph{product} of two objects $A$ an $B$ is an object $A \times B$ together with two \emph{projection arrows} $\pi_1:A\times B \rightarrow A$ and $\pi_2: A \times B \rightarrow B$ such that, for every object $C$ and pair of arrows $f: C \rightarrow A$, $g: C \rightarrow B$, there is exactly one arrow $\langle f, g \rangle : c \rightarrow A \times B$ making the diagram commutes
-    \[
-        \begin{tikzcd}
-                    & C \arrow[dl, "f" swap] \arrow[d, dashed, "{\langle f, g \rangle}" description] \arrow[dr, "g"] & \\
-                A   & A \times B  \arrow[l, "{\pi_1}"] \arrow[r, "{\pi_2}" swap]    &  B    
-        \end{tikzcd}
-    \]
-   -- i.e., such that $\pi_1 \circ \langle f, g \rangle = f$ and $\pi_2 \circ \langle f, g \rangle  = g$.
-
-\end{definition}
-
-\begin{definition}[Coproduct]
-    The dual of the product is the \emph{coproduct}.
-    A coproduct of two objects $A$ and $B$ is an object $A + B$ together with two arrows $\iota_1:A\rightarrow A+B$, $\iota_2: B \rightarrow A + B$ such that, for every object $C$ and pair of arrows $f:A \rightarrow C$, $g:B \rightarrow C$, there is a unique arrow $[f, g] : A + B \rightarrow C$ such that the diagram commutes
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\iota_1}"] \arrow[dr, "f" swap] & A+B \arrow[d, dashed, "{[f,g]}" description] & B \arrow[l, "{\iota_2}" swap] \arrow[dl, "g"] \\
-            & C & 
-        \end{tikzcd}
-    \]
-    -- i.e., such that $[f, g] \circ \iota_1 = f$ and $[f, g] \circ \iota_2 = g$.
-\end{definition}
-
-\begin{example}
-    $\Set$ has both products and coproduts.
-Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjoint sum $A \amalg B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
-\end{example}
-
-The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for each object in the product).
-We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
-
-Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction satisfies the universal property.
-
-\subsection{Equalizers and Coequalizers}
-
-The next notion is about a construction that make parallel arrows (i.e., two possibly distinct morphisms with the same domain and codomain) equal.
-In $\Set$, given two functions $f, g: A \rightarrow B$, such construction corresponds exactly to the restriction of the domain to the set of elements on which $f$ and $g$ are equal.
-Specifically, if we take the set $E = \{x \in A \mid f(x) = g(x)\}$, and we take the function $e: E \rightarrow A$ defined by $e(x) = x$, we obtain what is called an \emph{equalizer} for $f$ and $g$.
-In fact, $e$ is that function that make $f$ and $g$ be the same function -- i.e., $f \circ e = g \circ e$.
-This concept can be generalized as follows.
-
-\begin{definition}[Equalizer and Coequalizer]
-    Let $f, g: A \rightarrow B$ be two arrows of a category $\cat C$.
-An \emph{equalizer} for $f$ and $g$ is pair $(E, e)$, where $E$ is an object and $e: E \rightarrow A$ is an arrow in $\cat C$ such that:
-    \begin{enumerate}
-        \item \label{eq_1} $ f \circ e = g \circ e$; and
-        \item if $(E', e')$ is another pair that satisfies~\ref{eq_1}, then there exists a unique $h: E' \rightarrow E$ such that $e \circ h = e'$.
-    \end{enumerate}
-    \[
-        \begin{tikzcd}
-            E \arrow[r, "e"] & A \arrow[r, shift left, "f"] \arrow[r, shift right, "g" swap] & B \\
-            E' \arrow[u, dashed, "k"] \arrow[ur, "e'" swap] & 
-        \end{tikzcd}
-    \]
-
-    A \emph{coequalizer} of $f$ and $g$, dually, is a pair $(c, C)$, where $C$ is an object and $c: B \rightarrow C$ such that $c \circ f = c \circ g$, with the universal property.
-\end{definition}
-
-\begin{prop}\label{prop:eq_are_mono}
-    Let $e: E \rightarrow A$ be the arrow that equalizes $f, g : A \rightarrow B$ in a category $\cat C$. Then, $e$ is a monomorphism.
-\end{prop}
-
-\begin{proof}
-    Suppose $X$ be an object and $x, y: X \rightarrow E$ be two morphisms in $\cat C$ such that $e \circ x = e \circ y$, and let $z = e \circ x$.
-Then, since $e$ is an equalizer, $f \circ e = g \circ e$, and $f \circ z = g \circ z$.
-But, for the universal property of equalizers, there must be exactly one $u: Z \rightarrow E$ such that $z = e \circ u$.
-It follow that $x = u$ and $y = u$, hence $x = y$.
-\end{proof}
-
-Of all monomorphisms, an interesting subclass of them is the one that contains only the equalizers.
-
-\begin{definition}[Regular Monomorphism]\label{def:reg_mono}
-    A monomorphism that is an equalizer for a pair of arrows is said \emph{regular monomorphism}. The class of all regular monomorphisms of a category $\cat C$ is denoted $\Reg(\cat C)$.
-\end{definition}
-
-\begin{obs}
-    Given two composable regular monos $m$ and $n$, suppose that $n$ equalizes two arrows $f$ and $g$. Then, we have
-    \begin{align*}
-        g \circ (n \circ m) &= (g \circ n) \circ m &&\\
-                            &= (f \circ n) \circ m  && \textit{$n$ equalizer} \\
-                            &= f \circ (n \circ m)
-    \end{align*}
-    Since $n \circ m$ is mono (\Cref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
-\end{obs}
-
-\subsection{Pullbacks and Pushouts}
-
-Given two arrows, another pair of constructions one can find in a category is given by pullbacks and pushouts.
-
-\begin{definition}[Pullback, Pushout]
-        A \emph{pullback} of two arrows $f: A \rightarrow C$ and $g: B \rightarrow C$ is a triple $(P, \pi_g, \pi_f)$ containing an object $P$ and a pair of arrows $\pi_g: P \rightarrow A$, $\pi_f: P \rightarrow B$ such that:
-        \begin{enumerate}
-            \item\label{pb_1} $f \circ \pi_g = g \circ \pi_f$; and
-            \item if $(X, p, q)$, where $p: X \rightarrow A$ and $q: X \rightarrow B$, satisfies~\ref{pb_1}, then there is a unique $k:X \rightarrow P$ such that $p = \pi_g \circ k$ and $j = \pi_f \circ k$.
-        \end{enumerate}
-        \[
-        \begin{tikzcd}
-        X \arrow[drr, bend left=20, "q"] \arrow[ddr, bend right=20,"p" swap] \arrow[dr, dashed, "k"] & & \\
-        & P  \arrow[d, "{\pi_g}" swap] \arrow[r, "{\pi_f}"] & B \arrow[d, "g"] \\
-        & A  \arrow[r, "f" swap] & C
-        \end{tikzcd}
-    \]
-
-    Dually, the \emph{pushout} of two arrows $f: A \rightarrow B$ and $g: A\rightarrow C$ is a triple $(\iota_g, \iota_f, I)$, where $I$ is an object and $\iota_g:B \rightarrow I$ and $\iota_f: C \rightarrow I$ are morphisms such that:
-    \begin{enumerate}
-        \item\label{po_1} $\iota_g \circ f = \iota_f \circ g$; and 
-        \item if $(i, j, Y)$, where $i: B \rightarrow Y$ and $j: C \rightarrow Y$, satisfies~\ref{po_1}, then there is a unique $h: I \rightarrow Y$ such that $i = h \circ \iota_g$ and $j = h \circ \iota_f$.
-    \end{enumerate}
-    \[\begin{tikzcd}
-        A & C \\
-        B & I \\
-        && Y
-        \arrow["g", from=1-1, to=1-2]
-        \arrow["f" swap, from=1-1, to=2-1]
-        \arrow["{{\iota_f}}", from=1-2, to=2-2]
-        \arrow["j", bend left=20, from=1-2, to=3-3]
-        \arrow["{{\iota_g}}" swap, from=2-1, to=2-2]
-        \arrow["i" swap, bend right=20, from=2-1, to=3-3]
-        \arrow["h", dashed, from=2-2, to=3-3]
-    \end{tikzcd}\]
-    {% \[
-        %     \begin{tikzcd}
-        %         Y & &\\
-        %         & I \arrow[ul, dashed, "h"] & B \arrow[l, "{\iota_g}" swap] \arrow[ull, bend right=20, "i"swap] \\
-        %         & C \arrow[u, "{\iota_f}"] \arrow[uul, bend left=20, "j"] & A \arrow[l, "g"] \arrow[u, "f" swap]
-        %     \end{tikzcd}
-        % \]
-    }
-\end{definition}
-
-Pullbacks (and, dually, pushouts) are a construction that is slightly more general than products and equalizers.
-An intuition of what they represent is given by considering what is concretely a pullback in the category of sets.
-
-\begin{example}
-    In $\Set$, given two functions $f: A \rightarrow C$ and $g: B \rightarrow C$, a pullback of $f$ and $g$ exists and is exactly the set $P = \{(x, y) \in A \times B \mid f(x) = g(y)\}$, with $\pi_f : P \rightarrow B$ and $\pi_g : P \rightarrow C$ defined, respectively, by $\pi_f((x, y)) = y$ and $\pi_g((x, y)) = x$.
-In this way, we have then, $\forall (x, y) \in P$:
-    \begin{align*}
-        (f \circ \pi_g) ((x, y))
-                    &= f(\pi_g((x, y)))     &&  \\
-                    & = f(x)                &&  \textit{Definition of $\pi_g$} \\
-                    & = g(y)                &&  (x, y) \in P \\
-                    & = g(\pi_f((x, y)))    &&  \textit{Definition of $\pi_f$} \\
-                    & = (g \circ \pi_f) ((x, y)) && 
-    \end{align*}
-    thus, $f \circ \pi_g = g \circ \pi_f$.
-\end{example}
-
-Another important example to our aims is a concrete definition of what is a pushout in the category of sets, and why morally we can regard a pushout as \textit{the way to identify part of an object with a part of another}~\cite{Barr_Wells_1995}.
-
-\begin{example}\label{ex:po_in_set}
-    \color{blue}
-    In $\Set$, given two functions $f: A \rightarrow B$ and $g: A \rightarrow C$, the pushout of them is the set $X = (B \amalg C) /_\sim$, where $\sim$ is the least equivalence relation such that $f(a) \sim g(a)$ for each $a \in A$, with $\iota_g:B \rightarrow X$ and $\iota_f : C \rightarrow X$ as arrows, sending each element of the domain in the corresponding equivalence class in $X$.
-In particular, for each $a \in A$:
-    \begin{align*}
-        (\iota_g \circ f) (a)
-                        &= \iota_g(f(a))    &&\\
-                        &= [(f(a), 0)]           && \textit{Definition of $\iota_g$} \\
-                        &= [(g(a), 1)]           && f(a) \sim g(a) \\
-                        &= \iota_f(g(a))    && \textit{Definition of $\iota_f$} \\
-                        &= (\iota_f \circ g) (a) &&
-    \end{align*}
-    % This is not sure!!
-    When both $f$ and $g$ are monos (that is, injections), then we can construct the pushout in the same way we have done above, with $(f(a), 0) \sim (g(a), 1)$ when such $a$ exists and $(b, 0) \sim (c, 1)$ on each $b$ and $c$ with no preimage in $A$, with $\iota_f$ and $\iota_g$ injective.
-    An easy way to see this fact is considering the following situation: let $f: A \rightarrow A \cup B$ and $g: A \rightarrow A \cup C$, with $A$ disjoint from $B$ and $C$, $f(a)= a$ and $g(a) = a$.
-Then the pushout is the object $A \cup B \cup C$, with the inclusions as arrows, that are also injective.
-    A more general case is what happens considering functions $f: A \rightarrow B$ and $g: A \rightarrow C$ injective.
-Differently from the previous example, in this case is not possible to take just the union of codomains as the pushout, but rather the disjoint union of them and then identify the elements $f(a)$ with $g(a)$, as we have done above.
-In the category of sets and functions, we have the certainty that the pullback arrows are injective.
-In fact, taking the equivalence relation $\sim$, we have that $f(a) \sim f(a')$ if and only if $a = a'$ by hypothesis, and then $x \sim x'$ if and only if $x = x'$, then the pushout morphisms sends each element in an equivalence class composed only by the element itself, thus are injective.
-    This is an interesting property that in other categories may do not hold, and will be recalled later.
-\end{example}
-
-Given a subclass of morphisms of a category, an important property is \emph{stability} under certain type of constructions.
-In our case, we are interested in stability under pullbacks and under pushouts.
-\[
-    \begin{tikzcd}\label{diag:p_square}\tag{$\ast$}
-        A \arrow[r, "f"] \arrow[d, "m"swap] & B \arrow[d, "n"] \\
-        C \arrow[r, "g" swap] & D
-    \end{tikzcd}
-\]
-
-\begin{definition}[Stability under pullbacks, pushouts]\label{def:stab_under_pb_po}
-    Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every pullback square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
-    $\mathcal A$ is said to be \emph{stable under pushouts} if, for every pushout square as the one in \eqref{diag:p_square}, if $m \in \mathcal{A}$, then $n \in \mathcal{A}$.
-\end{definition}
-
-\begin{prop}\label{prop:monos_pres_by_pullback}
-    Let $f: A \rightarrow C$, $g: B \rightarrow C$ be arrows in any category $\cat C$, and consider the following pullback square:
-    \[
-        \begin{tikzcd}
-            P \arrow[r, "{\pi_f}"] \arrow[d, "{\pi_g}"swap] & B \arrow[d, "g"] \\
-            A \arrow[r, "f"swap] & C
-        \end{tikzcd}
-    \]
-    If $g$ is mono, then so is $\pi_g$.
-\end{prop}
-
-\subsection{Limits and Colimits}
-
-We now introduce the notion that generalize all the universal constructions defined above.
-In fact, initial objects, products, equalizers and pullbacks (dually, terminal objects, coproducts, coequalizers and pushouts) can be seen as the particular case of a certain type of construction, called limit.
-
-To define what a limit is, we first need to define cones.
-
-\begin{definition}[Cones]
-    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
-A \emph{cone} for $D$ is an object $X$ of $\cat C$, together with arrows $f_i : X \rightarrow D(i)$ indexed by $\cat I$ (i.e.
-one for each object $i$ of $\cat I$), such that, for each morphism $\alpha: i \rightarrow j$ of $\cat I$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            & X \arrow[dl, "{f_i}"swap] \arrow[dr, "{f_j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}" swap] & & D(j)
-        \end{tikzcd}
-    \]
-    -- i.e., $D(\alpha) \circ f_i = f_j$.
-    We denote such cone as $\{f_i: X \rightarrow D(i)\}$.
-
-\end{definition}
-
-\begin{obs}\label{obs:category_of_cones}
-    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$, is defined to have cones for $D$ as objects and cone morphisms as arrows, where a cone morphism $\phi: C \rightarrow C'$ from $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
-    \[
-        \begin{tikzcd}
-            X \arrow[rr, "{\phi}"] \arrow[dr, "{f_i}" swap] & & X' \arrow[dl, "{f_i'}"] \\
-            & D(i) &
-        \end{tikzcd}
-    \]
-\end{obs}
-
-\begin{definition}[Limits]\label{def:limit}
-    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
-A cone $\{f_i: X \rightarrow D(i)\}$ is a \emph{limit} provided that, for any other cone $\{f_{i}': X' \rightarrow D(i)\}$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
-    \[
-        \begin{tikzcd}
-            X' \arrow[rr, dashed, "k"] \arrow[dr, "{f_i'}" swap] & & X \arrow[dl, "{f_i}"] \\
-            & D(i) &
-        \end{tikzcd}
-    \]
-    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$
-\end{definition}
-
-\begin{obs}
-    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in \Cref{obs:category_of_cones}.
-\end{obs}
-
-The dual notions of cones and limits are that of cocones and colimits.
-
-\begin{definition}(Cocones, Colimits)
-    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$.
-A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
-    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
-\end{definition}
-
-The following examples show how limits are general concepts for the constructions defined above.
-
-\begin{example}
-    Let $D$ be the empty diagram in the category $\cat C$. Then, a cone for $D$ is any object of $\cat C$, while a limit is the terminal object of $\cat C$.
-\end{example}
-
-\begin{example}\label{ex:product_are_limits}
-    Let $D$ be the following diagram:
-    \[
-        \begin{tikzcd}
-            A & & B
-        \end{tikzcd}
-    \]
-    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in \Cref{ex: span}):
-    \[
-        \begin{tikzcd}
-            A & X \arrow[l, "f" swap] \arrow[r, "g"] & B
-        \end{tikzcd}
-    \]
-    If it exists, a limit for $D$ is the product of $A$ and $B$.
-\end{example}
-
-\begin{example}\label{ex:pb_as_limit}
-    A pullback is the limit for the diagram below.
-    \[
-        \begin{tikzcd}
-            & B \arrow[d, "g"] \\
-            A \arrow[r, "f" swap] & C
-        \end{tikzcd}
-    \]
-    In fact, a cone for the diagram above is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$, and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
-    Thus, the following diagram is a cone:
-    \[
-        \begin{tikzcd}
-            P \arrow[r, "{\psi}"] \arrow[d, "{\phi}" swap] & B \arrow[d, "g"] \\
-            A \arrow[r, "f" swap] & C
-        \end{tikzcd}
-    \]
-    For $(P, \phi, \psi)$ to be a pullback, it must have the universal property. In other words, it has to be a limit.
-
-    This example show us that a pullback is a limit for a cospan (\Cref{ex: span}).
-\end{example}
-
-\begin{example}\label{ex:equaliz_are_limits}
-    A limit for the diagram below is an equalizer for $f$ and $g$.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, shift left, "f"] \arrow[r, shift right,"g"swap] & B
-        \end{tikzcd}
-    \]
-\end{example}
-
-All the examples we provided about limits are still valid, in their dual form, for colimits.
-In fact, initial objects, coequalizers, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
-
-\begin{example}
-    Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
-    \[
-        \begin{tikzcd}
-            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
-        \end{tikzcd}
-    \]
-    a cocone for $S$ is any commutative square of the form
-    \[
-        \begin{tikzcd}
-            & C & \\
-            L \arrow[ur, "f"] &
-            X \arrow[l, "l"swap] \arrow[r, "r"]&
-            R \arrow[ul, "g" swap]
-        \end{tikzcd}
-    \]
-    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
-    A colimit for $S$ is then a pushout of $l$ and $r$.
-\end{example}
-
-The connection between constructions as products and equalizers and limits is made clear by the following theorem.
-The idea behind the proof is the fact that, given a diagram $D : \cat I \rightarrow \cat C$, if each subset of objects $X = \{D(i) \mid i \in \Ob(\cat I)\} \subseteq \Ob(\cat C)$ has a product $(\prod_{i \in I} D(i), (\pi_i)_{i \in \Ob( \cat I)})$ and each pair of arrows $f, g \in \cat C (D(i), D(j))$ has an equalizer $Eq(f, g)$, then one can construct the cone taking the equalizer of the arrows that has as domain the product of the objects of the diagram, and as codomain the product of the codomains of the arrows of the diagram.
-This construction has the universal property because equalizers and products do.
-A detailed proof is in the appendix.
-
-\begin{theorem}[Limit theorem]\label{th:limit}
-    Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
-\end{theorem}
-
-\begin{remark}
-    The theorem above (and its relative proof) can be stated in its dual form leading to a theorem on existence of colimits, and a relative criterion to calculate them (taking the dual of the proof).
-\end{remark}
-
-\begin{example}\label{ex:lim_of_sets}
-    Limit theorem gives us an easy way to calculate limits.
-An example of this fact is how limits are computed in $\Set$.
-Given a diagram $D: \cat{I} \rightarrow \Set$, where $\cat I$ is a small category and $I = Ob(\cat I)$, its limit is the set $L$ defined as follows:
-    $$
-        L = \{ (d_i)_{i \in I} \in \prod_{i \in I}D(i) \mid \forall \phi \in \cat I(i, i'), D(\phi)(d_i) = d_{i'} \}
-    $$
-    with projections as arrows.
-\end{example}
-
-\begin{example}\label{ex:colm_of_sets}
-    As we have done in \Cref{ex:lim_of_sets}, we illustrate how to construct colimits in the category of sets.
-Given a small category $\cat I$, $ I = Ob(\cat I)$, and a diagram $D: \cat I \rightarrow \Set$, consider the equivalence relation $\sim$ defined on $\coprod_{i\in I} D(i)$ such that $d_i \sim d_{i'}$ if $d_i \in D(i), d_{i'} \in D(i')$ and there exists some $\phi \in \cat I(i, i')$ such that $D(\phi)(d_i) = d_{i'}$.
-Then, a colimit for $D$ is the set
-    $$
-        C = \big ( \coprod_{i \in I} D(i) \big ) / \sim
-    $$
-    with the inclusions as arrows.
-\end{example}
-
-\begin{remark}
-    Since a diagram is nothing more than a functor from a ``shape'' category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
-\end{remark}
-
-\begin{obs}\label{obs:limits_in_presh}
-    So far we introduced categories of presheaves.
-In these categories, an interesting fact is that limits and colimits are computed pointwise -- i.e., the limit of a diagram in a category of presheaves is exactly the limit on each of its components.
-\end{obs}
-
-In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.
-
-\begin{definition}
-    Let $D : \cat{I \rightarrow C}$ be a diagram, and $F: \cat{C \rightarrow D}$ a functor. We say that $F$:
-    \begin{enumerate}
-        \item \emph{preserves limits} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $D$, then $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
-        \item \emph{reflects limits} of $D$ if a cone $(L, l_i)_{i \in \cat I}$ is a limit for $D$ whenever $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
-        \item \emph{lifts limits (uniquely)} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $F \circ D$, there exists a (unique) limit $(L', l_i')_{i \in \cat I}$ for $D$ such that $(F(L'), F(l_i'))_{i \in \cat I} = (L, l_i)_{i \in \cat I}$.
-        \item \emph{creates limits} of $D$ if $D$ has a limit and $F$ preserves and reflects limits along it.
-    \end{enumerate}
-    The dual notions are obtained in the obvious way, namely, substituting the words ``limits'' and ``cones'' with ``colimits'' and ``cocones'', respectively
-\end{definition}
-
-\begin{obs}\label{obs:funct_creat_lim_then_lift}
-    It holds that if a functor creates limits, then lifts uniquely limits~\cite{Adamek_Herrlich_Strecker_2009}.
-\end{obs}
-
-\begin{prop}\label{prop:inc_funct_reflects_so_limits}
-    A fully faithful functor reflects all limits and colimits.
-\end{prop}
-
-The next theorem is about a particular property that adjoint functors have.
-
-\begin{theorem}\label{th:adjoints_preserves_lim}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and $G: \cat{D \rightarrow C}$ its right adjoint. Then, $G$ preserves limits.
-\end{theorem}
-
-\begin{remark}
-    The dual of the theorem above states that, if $G$ is a functor and $F$ is a left adjoint, then $F$ preserves colimits.
-\end{remark}
-
+\input{Limit}
 \section{Adhesivity}\label{sect:adh}
@@
 Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{ex:pb_as_limit}).
+Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
 Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
@@
 
-All the constructions defined in \Cref{sect:univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
+All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
 The next examples try to make this point clear.
@@
 The ones we are interested in are \emph{equivalence relations}.
-Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with such a relation defined over its set of vertices.
+%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
+A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
 
@@
 
-    The \emph{if} statement is easily satisfied as shown in \Cref{ex:equaliz_are_limits} and \Cref{ex:product_are_limits}.
+    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
 

### 2024-10-20 Article/Appendix/Omitted_Proofs.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/main.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
-\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{hyperref, cleveref}
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\Reg}{\mathcal{R}eg}
-\newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\mymathbb{0}}
-\newcommand{\terminal}{\mathds{1}}
-\newcommand{\eqgraph}[1]{\mathbb{#1}}
-\newcommand{\Egg}{\mathbf{EGG}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
-
-\section{Basic Notions}\label{sect:basic_nots}
-
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
-
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
-
-\subsection{Categories}\label{ssect:cats}
-
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
-    \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
-
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:0_cat}
-    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
-\end{example}
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
-
-\begin{definition}\label{def:dual_cat}[Dual Category]
-    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
-    \begin{itemize}
-        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
-        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
-    \end{itemize}
-    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
-    Such category is called \emph{dual category} or \emph{opposite category}.
-\end{definition}
-
-Duality is a concept that we will encounter most of the time.
-Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
-There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
-
-%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-% Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
-    This category is denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the \Cref{def:category} above does not specify what kind of collections
-    %for a category $\cat{C}$, 
-    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
-This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
-
-Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
-\end{definition}
-
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
-
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
-Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
-Factorization of morphisms induces a preorder on subobjects of an object.
-$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
-
-An useful fact about subobjects is how factorization behaves.
-In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
-Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
-Suppose $k$ is another morphism such that $m = n \circ k$.
-We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
-This is to say what follows.
-
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
-\end{example}
-
-\begin{remark}
-    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
-    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
-\end{remark}
-
-\begin{prop}\label{prop:epi_mono_prop}
-    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
-    \begin{enumerate}
-        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
-        \item if $g \circ f$ is mono, then $f$ is mono;
-        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
-        \item if $g \circ f$ is epi, then $g$ is epi.
-    \end{enumerate}
-\end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
-
-\subsection{Categories from other categories}\label{ssect:cats_from_cats}
-
-Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
-
-The first notion to introduce is the one of subcategory.
-
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
-\end{definition}
-
-An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
-\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
-
-\todo{E cambierei anche l'intro a questa sezione DC}
-\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
-
-\subsection{Functors}
-
-A functor is a structure preserving map between categories. 
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
-The following definitions are about this particular type of functors.
-
-\begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
-    $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
-    $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
-\end{definition}
-
-\color{red}{
-    \begin{obs}
-        Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-    \end{obs}
-}\color{black}
-
-\begin{example}\label{ex:full_subc_inc_fully_faith}
-    Let $\cat C$ be a category and $\cat D$ a subcategory.
-The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
-If $\cat D$ is a full subcategory, then $I$ is fully faithful.
-\end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
-
-\subsection{Natural Transformations}
-
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Categories}
-
-The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
-\end{remark}
-
-\subsection{Comma Categories}
-
-Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g" swap] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
-
-\subsection{Adjoints}
-
-% \begin{definition}[Adjoint Functor]\label{def:adjoint}
-%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
-$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-%     \[
-%         \begin{tikzcd}
-%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
-%             & L(B)
-%         \end{tikzcd}
-%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
-%     \[
-%         \begin{tikzcd}
-%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
-%         \end{tikzcd}
-%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-% \end{definition}
-%\todo{sistemare la definizione}
-
-\begin{definition}[Right Adjoint]\label{def:right_adjoint}
-    Let $R: \cat{C \rightarrow D}$ be a functor.
-$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
-            & R(B)
-        \end{tikzcd}
-    \]
-    --i.e., $R(g) \circ \eta_A = f$.
-\end{definition}
-
-\begin{prop}\label{prop:ext_left_to_funct}
-    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
-Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
-\end{prop}
-\begin{proof}
-    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
-    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
-    \end{tikzcd}
-    \]
-
-    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
-    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
-    \end{tikzcd}
-    \]    \[
-    \begin{tikzcd}
-    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
-    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
-    \end{tikzcd}
-    \]
-
-    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
-\end{proof}
-
-\begin{remark}
-    The family above mentioned is called \emph{unit} of the adjunction.
-\end{remark}
-
-\begin{definition}[Left Adjoint]\label{def:left_adjoint}
-    Let $L: \cat{D \rightarrow C}$ be a functor.
-$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
-            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
-        \end{tikzcd}
-    \]
-    -- i.e., $\epsilon_B \circ L(f) = g$.
-\end{definition}
-
-As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
-The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
-
-The connection between left and right adjoints is expressed in the following proposition.
-
-\begin{prop}
-    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
-\end{prop}
-
-\begin{proof}
-	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
-	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
-	    \[
-	\begin{tikzcd}
-		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
-		& R(B)
-	\end{tikzcd}
-	\]
-
-	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
-	\begin{align*}
-		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
-	\end{align*}
-	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
- \end{proof}
-
-% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
-In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-\begin{obs}
-    $\Set$ is adhesive.
-    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
-\end{obs}
-
-Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
-
-\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
-    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\end{prop}
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}\label{th:crit_for_adh}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
-Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
-Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-% Sec. 1 Categorie e funtori
-
-% >def di categorie
-% 	-menzionare che data una categoria c'è il duale
-% 	-epi, mono e  iso
-
-% >funtori e trasf naturali
-
-% >categorie comma (con slice e coslice come sottocaso)
-
-% Sec. 2: Limiti e colimiti
-% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
-% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-% 	-epi e mono regolari
-
-% >Limiti nelle categorie di funtori e comma
-
-% Sec. 3: Adesività
-% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
-}
-
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
-Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
-    \begin{itemize}
-        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
-        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
-    \end{itemize}
-    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
-\end{prop}
-
-\begin{proof}
-
-    \color{red}{
-    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
-Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
-Our claim is $D(\alpha) \circ l^i = l^j$.
-Hence,
-    \begin{align*}
-        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
-                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
-                            &= (l^j_V, l^j_E)                       \\
-                            &= l^j                              
-    \end{align*}
-    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
-But such equivalence relation exists in every case, considering the identity.
-This led us to the second point of the proof, that is, the universal property.
-    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
-    For the cone described above to be a limit must be valid the universal property.
-Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-Suppose the following situation:
-    \[
-        \begin{tikzcd}
-            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
-            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
-        \end{tikzcd}
-    \]
-    The universal property the follows from the definition of least equivalence relation.
-    } \color{black}
-\end{proof}
-
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
-
-\begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-We now give some considerations on quotient functor.
-
-\begin{prop}
-    Quotient functor has a left adjoint and a right adjoint.
-\end{prop}
-
-\begin{proof}
-    To prove the statement we just have to find the adjoints. 
-    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
-To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
-
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
-    Consider the following situation:
-    \[
-        \begin{tikzcd}
-            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
-            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
-            & \mathcal{G} \\
-            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
-            \arrow[u, dashed, "I(f)"] 
-            \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \]
-    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
-Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
-
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
-UPDATE: probabilmente questo non è nu funtore aggiunto}
-    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
-We have then the following situation:
-    \[
-        \begin{tikzcd}
-            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
-            & T(\mathcal{H}) = \eqgraph{H}
-        \end{tikzcd}
-    \]
-    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
-Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
-\end{proof}
-
-The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
-
-\begin{cor}\label{cor:quot_preserves_co_lim}
-    Quotient functor preserves limits and colimits. 
-\end{cor}
-
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
-\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{lemma}
-\todo{Capire qui!}
-
-}\color{black}
-\todo[color=green!40]{
-COSE DA FARE
->Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
->Quoziente crea certi pushout (questo va fatto ex novo)
-}
-% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
-
-\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
-\end{lemma}
-
-% Q crea pullback, Q crea pushout sui reg mono.
-
-\begin{lemma}
-    The quotient functor creates pullbacks.
-\end{lemma}
-
-\begin{proof}
-    We will show now that $Q$ reflects pullbacks.
-    Consider the following diagram in $\mathbf{Graph}$
-    \[
-        \begin{tikzcd}
-            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
-            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
-        \end{tikzcd}
-    \]
-    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
-We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
-    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
-\end{proof}
-
-\begin{lemma}
-    The quotient functor creates pushouts along regular monomorphism.
-\end{lemma}
-
-% \begin{proof}
-%     Consider the following situation
-% \end{proof}
-
-\begin{theorem}
-    $\mathbf{EqGrph}$ is quasiadhesive.
-\end{theorem}
-
-\begin{proof}
-    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{proof}
-
-\section{E-Graphs}\label{sect:eggs}
-
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
-In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
-\[
-    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
-\] for each $e$, $e' \in \eqgraph{G}(E)$.
-But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
-To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
-
-Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
-Specifically, we want, in the following situation, $i$ to be mono and unique.
-\[
-    \begin{tikzcd}
-        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
-        & \eqgraph{G}(E) \times \eqgraph{G}(E)
-    \end{tikzcd}
-\]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
-From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
-The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
-If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
-
-\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
-\end{definition}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
 \chapter{Omitted Proofs}
@@
 \end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}

### 2024-10-20 Article/Background.tex
reordering + redefn of graphs eqgrph

--- 2024-08-05 final_1/source/mainOld.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale italiano, con parti in inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage{lipsum} % genera testo fittizio
-\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento
-\usepackage[fontsize=13pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\initial}{\textbf 0}
-\newcommand{\terminal}{\mathds{1}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
 \chapter{Background}
 
-In this chapter will be defined the building blocks for this work, almost entirely based on categories.
+In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
 The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
@@
 
-\section{Basic Notions}
-
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
-
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
-
-\subsection{Categories}
-
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$.
-    \end{enumerate}
-    For each morphism $f \in \Hom(\cat{C})$, there are two operators $dom$ and $cod$ which map every morphism to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of all morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
-
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in wich the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (Definition~\ref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $\forall a \in A: id_A(a) = a$.
-    This category is usually denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the Definition~\ref{def:category} above does not specify what kind of collections are, for a category $\cat{C}$, $\Ob(\cat{C})$ and $\Hom(\cat{C})$.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}
-
-Between all morphisms of a category, it is possible to distinguish some that have certain properties, as well as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphism are surjective functions and ismorphisms are bijections.
-\end{example}
-
-\subsection{Categories from other categories}
-
-Starting from a category $\cat{C}$, it is possible to construct some other categories with interesting property.
-An example is the \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite{pierce91}.
-
-Another important notion is that of subcategory.
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item composites and identities of $\cat{D}$ are the same of $\cat{C}$
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-\end{definition}
-
-An object of a category can raise a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ is given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition is \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), obtained by taking as objects all the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ such that $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
-\section{Functors, Natural transformations and Beyond}
-
-A functor is a structure preserving map between categories.
-
-\subsection{Functors}
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what is a functor, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (Definition~\ref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a span in a relation $R \subseteq A \times B$, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions.~\cite{Herrlich_Strecker_1979}
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if, for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Given two functors which share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of "changing the functor acting on that object".
-
-\subsection{Natural transformations}
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$ is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformation $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is even possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Category}
-
-The Observation~\ref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This led us to define a particular kind of category, in which objects are functors between two fixed categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be two categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (Remark~\ref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition we give above.
-\end{remark}
-
-\subsection{Comma categories}
-
-Functor constructions allow us to generalise basic concept already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (Definition~\ref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{slice category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g"] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in Example~\ref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-At the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C$.
-
-\section{Universal Constructions}
-
-\subsection{Initial and Terminal Objects}
-
-The next definitions are about \emph{universal constructions}. The simplest are the notion of initial and, dually, terminal objects.
-
-\begin{definition}[Initial and terminal object]
-    An object $A$ of a category $\cat C$ is said to be \emph{initial} if, for each other object $B$ of $\cat C$, there exists a unique morphism from $A$ to $B$.
-    Dually, an object $Z$ is said to be a terminal object in a category $\cat C$ if, for any other object $X$ of $\cat C$, there exists a unique morphism from $X$ to $Z$.
-    An initial object of a category is indicated by the symbol $\initial$, and a terminal object is indicated by the symbol $\terminal$.
-\end{definition}
-
-\begin{obs}\label{obs:terminal_are_isomorph}
-    It make sense to refer to an initial (and terminal) object as \emph{the} initial (\emph{the} terminal) object.
-Suppose indeed that $\initial$ and $\initial'$ are two distinct initial objects of a category $\cat C$.
-Then, there exists a unique morphism from $\initial$ to $\initial'$, say $f$.
-At the same way, it must exists a unique morphism from $\initial'$ to $\initial$, say $g$.
-Then, $g\circ f$ must be exactly $id_{\initial}$, and $f \circ g = id_{\initial'}$, and then they are isomorphic.
-The same argument works for the terminal object.
-    The reason why this argument works is because initial and terminal objects have the \emph{universal property} (Definition~\ref{def:univ_prop}), [Integrare qui!]
-\end{obs}
-
-\begin{example}\label{ex:set_init_term}
-    In $\Set$, the initial object is the empty set $\varnothing$, because, for each set $S$, there exists the empty function from $\varnothing$ to $S$.
-The terminal object of $\Set$ is the singleton $\{ \bullet \}$, because there is exactly one function from a set $S$ to $\{ \bullet \}$, namely, the function which sends each $s \in S$ to $\bullet$.
-It is possible to visualize the Observation~\ref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective.
-\end{example}
-
-We now illustrate a result on functor categories (Definition~\ref{def:functor_category}) that will be useful later.
-
-\begin{prop}
-    Let $\cat D$ be a category.
-If $\cat D$ has an initial object, then, for any category $\cat C$, $[\cat{C, D}]$ has an initial object.
-If $\cat D$ has a terminal object, then, for any category $\cat C$, $[\cat{C, D}]$ has a terminal object.
-\end{prop}
-
-\begin{proof}
-    Let $\initial_{\cat{D}}$ be the initial object of $\cat D$,  and consider the constant functor $I(f) = id_{\initial_{\cat D}}$ for all $f \in \Hom(\cat C)$.
-Then, for any $G: \cat{C \rightarrow D}$, $\eta: I \rightarrow G$, defining $\eta_A$ as the \emph{unique morphism from $\initial_{\cat D}$ to $G(A)$} for each $A \in \Ob(\cat C)$, is a natural transformation $I \dot\rightarrow G$, as the diagram below shows:
-    \[
-        \begin{tikzcd}
-            I(A)=\initial_{\cat D} 
-                    \arrow[r, "{\eta_A}"]
-                    \arrow[d, "{I(f) = id_{\initial_{\cat D}}}" swap] &
-            G(A)
-                    \arrow[d, "G(f)"] \\
-            I(A') = \initial_{\cat D}
-                    \arrow[r, "{\eta_{A'}}" swap] &
-            G(A')
-        \end{tikzcd}
-    \]
-    for each $f: A \rightarrow A'$, the square above must commute, since there is only one morphism from $\initial_{\cat D}$ to $G(A')$.
-For the same reason, $\eta$ is the only natural transformation from $I$ to $G$, being indeed the initial object of $[\cat{C, D}]$.
-
-    Defining $T(f) = id_{\terminal_{\cat D}}$ for each $f \in \Hom(\cat C)$.
-Then, $\theta:F\rightarrow T$, for any $F: \cat{C \rightarrow D}$, defining $\theta_A$ as the \emph{unique morphism from $F(A)$ to $\terminal_{\cat{D}}$} is a natural transformation due to the commutativity of the following diagram for each $f: A \rightarrow A'$:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[r, "{\theta_A}"] \arrow[d, "F(f)" swap] &
-            T(A) = \terminal_{\cat D} \arrow[d, "{T(f) = id_{\terminal_{\cat D}}}"] \\
-            F(A') \arrow[r, "{\theta_{A'}}" swap] & T(A') = \terminal_{\cat D}
-        \end{tikzcd}
-    \]
-    Hence, $\theta$ is the unique natural transformation from $F$ to $T$, and $T$ is the terminal object of $[\cat{C, D}]$.
-\end{proof}
-
-In particular, every presheaf has an initial and a terminal object, because $\Set$ do (Example~\ref{ex:set_init_term}).
-
-\subsection{Products and Coproducts}
-
-More complex constructions are products (and, dually, coproducts).
-
-\begin{definition}[Product]
-    A \emph{product} of two objects $A$ an $B$ is an object $A \times B$ together with two \emph{projection arrows} $\pi_1:A\times B \rightarrow A$ and $\pi_2: A \times B \rightarrow B$ such that, for every object $C$ and pair of arrows $f: C \rightarrow A$, $g: C \rightarrow B$, there is exactly one arrow $\langle f, g \rangle : c \rightarrow A \times B$ making the diagram
-    \[
-        \begin{tikzcd}
-                    & C \arrow[dl, "f" swap] \arrow[d, dashed, "{\langle f, g \rangle}" description] \arrow[dr, "g"] & \\
-                A   & A \times B  \arrow[l, "{\pi_1}"] \arrow[r, "{\pi_2}" swap]    &  B    
-        \end{tikzcd}
-    \]
-
-    commute -- i.e., such that $\pi_1 \circ \langle f, g \rangle = f$ and $\pi_2 \circ \langle f, g \rangle  = g$.
-
-\end{definition}
-
-\begin{definition}[Coproduct]
-    The dual of the product is the \emph{coproduct}.
-    A coproduct of two objects $A$ and $B$ is an object $A + B$ together with two arrows $\iota_1:A\rightarrow A+B$, $\iota_2: B \rightarrow A + B$ such that, for every object $C$ and pair of arrows $f:A \rightarrow C$, $g:B \rightarrow C$, there is a unique arrow $[f, g] : A + B \rightarrow C$ such that the diagram
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\iota_1}"] \arrow[dr, "f" swap] & A+B \arrow[d, dashed, "{[f,g]}" description] & B \arrow[l, "{\iota_2}" swap] \arrow[dl, "g"] \\
-            & C & 
-        \end{tikzcd}
-    \]
-    commutes -- i.e., such that $[f, g] \circ \iota_1 = f$ and $[f, g] \circ \iota_2 = g$.
-\end{definition}
-
-\begin{example}
-    $\Set$ have both products and coproduts.
-Given two sets $A$ and $B$, the categorical product is the set-theoretic catesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjount sum $A + B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$.
-\end{example}
-
-Both the notion of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrow for each object in the product).
-We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
-
-Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction owns the universal property.
-
-\subsection{Equalizers and Coequalzers}
-
-The next notion is about a construction that make parallel arrows (i.e., two possibly distinct morphisms whit the same domain and codomain) equal.
-In $\Set$, given two functions $f, g: A \rightarrow B$, such construction corresponds exactly to the restriction of the domain to the set of elements on which $f$ and $g$ are equal.
-Specifically, if we take the set $E = \{x \in A \mid f(x) = g(x)\}$, and we take the function $e: E \rightarrow A$ defined by $e(x) = x$, we obtain what is called an \emph{equalizer} for $f$ and $g$.
-In fact, $e$ is that function that make $f$ and $g$ be the same function -- i.e., $f \circ e = g \circ e$.
-This concept can be generalized as it follows.
-
-\begin{definition}[Equalizer and Coequalizer]
-    Let $f, g: A \rightarrow B$ be two arrows of a category $\cat C$.
-An \emph{equalizer} for $f$ and $g$ is pair $(E, e)$, where $E$ is an object and $e: E \rightarrow A$ is an arrow in $\cat C$ such that:
-    \begin{enumerate}
-        \item \label{eq_1} $ f \circ e = g \circ e$; and
-        \item if $(E', e')$ is another pair that satisfies~\ref{eq_1}, then there exists a unique $h: E' \rightarrow E$ such that $e \circ h = e'$.
-    \end{enumerate}
-    \[
-        \begin{tikzcd}
-            E \arrow[r, "e"] & A \arrow[r, shift left, "f"] \arrow[r, shift right, "g" swap] & B \\
-            E' \arrow[u, dashed, "k"] \arrow[ur, "e'" swap] & 
-        \end{tikzcd}
-    \]
-
-    A \emph{coequalizer} of $f$ and $g$, dually, is a pair $(c, C)$, where $C$ is an object and $c: B \rightarrow C$ such that $c \circ f = c \circ g$, with the universal property.
-\end{definition}
-
-\subsection{Pullbacks and Pushouts}
-
-Another (pair of) construction(s) one can find in a category, given two arrows, is the pullback (and the pushout).
-
-\begin{definition}[Pullback, Pushout]
-        A \emph{pullback} of two arrows $f: A \rightarrow C$ and $g: B \rightarrow C$ is a triple $(P, \pi_g, \pi_f)$ containing an object $P$ and a pair of arrows $\pi_g: P \rightarrow A$, $\pi_f: P \rightarrow B$ such that:
-        \begin{enumerate}
-            \item\label{pb_1} $f \circ \pi_g = g \circ \pi_f$; and
-            \item if $(X, p, q)$, where $p: X \rightarrow A$ and $q: X \rightarrow B$, satisfies~\ref{pb_1}, then there is a unique $k:X \rightarrow P$ such that $p = \pi_g \circ k$ and $j = \pi_f \circ k$.
-        \end{enumerate}
-        \[
-        \begin{tikzcd}
-        X \arrow[drr, bend left=20, "q"] \arrow[ddr, bend right=20,"p" swap] \arrow[dr, dashed, "k"] & & \\
-        & P  \arrow[d, "{\pi_g}" swap] \arrow[r, "{\pi_f}"] & B \arrow[d, "g"] \\
-        & A  \arrow[r, "f" swap] & C
-        \end{tikzcd}
-    \]
-
-    Dually, the \emph{pushout} of two arrows $f: A \rightarrow B$ and $g: A\rightarrow C$ is a triple $(\iota_g, \iota_f, I)$, where $I$ is an object and $\iota_g:B \rightarrow I$ and $\iota_f: C \rightarrow I$ are morphisms such that:
-    \begin{enumerate}
-        \item\label{po_1} $\iota_g \circ f = \iota_f \circ g$; and 
-        \item if $(i, j, Y)$, where $i: B \rightarrow Y$ and $j: C \rightarrow Y$, satisfies~\ref{po_1}, then there is a unique $h: I \rightarrow Y$ such that $i = h \circ \iota_g$ and $j = h \circ \iota_f$.
-    \end{enumerate}
-    \[\begin{tikzcd}
-        A & C \\
-        B & I \\
-        && Y
-        \arrow["g", from=1-1, to=1-2]
-        \arrow["f" swap, from=1-1, to=2-1]
-        \arrow["{{\iota_f}}", from=1-2, to=2-2]
-        \arrow["j", bend left=20, from=1-2, to=3-3]
-        \arrow["{{\iota_g}}" swap, from=2-1, to=2-2]
-        \arrow["i" swap, bend right=20, from=2-1, to=3-3]
-        \arrow["h", dashed, from=2-2, to=3-3]
-    \end{tikzcd}\]
-    {% \[
-        %     \begin{tikzcd}
-        %         Y & &\\
-        %         & I \arrow[ul, dashed, "h"] & B \arrow[l, "{\iota_g}" swap] \arrow[ull, bend right=20, "i"swap] \\
-        %         & C \arrow[u, "{\iota_f}"] \arrow[uul, bend left=20, "j"] & A \arrow[l, "g"] \arrow[u, "f" swap]
-        %     \end{tikzcd}
-        % \]
-    }
-\end{definition}
-
-Pullbacks (and, dually pushouts) are construction slightly more general than products and equalizers.
-An intuition of what they represent is given by considering what is concretely a pullback in the category of sets.
-
-\begin{example}
-    In $\Set$, given two functions $f: A \rightarrow C$ and $g: B \rightarrow C$, a pullback of $f$ and $g$ exists and is exactly the set $P = \{(x, y) \in A \times B \mid f(x) = g(y)\}$, with $\pi_f : P \rightarrow B$ and $\pi_g : P \rightarrow C$ defined, respectively, by $\pi_f((x, y)) = y$ and $\pi_g((x, y)) = x$.
-In this way, we have then, $\forall (x, y) \in P$:
-    \begin{align*}
-        (f \circ \pi_g) ((x, y))
-                    &= f(\pi_g((x, y)))     &&  \\
-                    & = f(x)                &&  \textit{Definition of $\pi_g$} \\
-                    & = g(y)                &&  (x, y) \in P \\
-                    & = g(\pi_f((x, y)))    &&  \textit{Definition of $\pi_f$} \\
-                    & = (g \circ \pi_f) ((x, y)) && 
-    \end{align*}
-    thus, $f \circ \pi_g = g \circ \pi_f$.
-\end{example}
-
-\subsection{Limits and Colimits}
-
-We now introduce the notion that generalize all the universal constructions defined above.
-In fact, initial objects, products, equalizers an pullback (dually, terminal objects, coproducts, coequalizers and pushouts) can be seen as the particular case of a certain type of construction, called limit.
-
-To define what a limit is, we first need to define cones.
-
-\begin{definition}[Cones]
-    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
-A \emph{cone} for $D$ is an object $X$ of $\cat C$, together with arrows $f_i : X \rightarrow D(i)$ indexed by $\cat I$ (i.e.
-one for each object $i$ of $\cat I$), such that, for each morphism $\alpha: i \rightarrow j$ of $\cat I$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            & X \arrow[dl, "{f_i}"swap] \arrow[dr, "{f_j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}" swap] & & D(j)
-        \end{tikzcd}
-    \]
-    -- i.e., $D(\alpha) \circ f_i = f_j$.
-    We denote such cone as $\{f_i: X \rightarrow D(i)\}$.
-
-\end{definition}
-
-\begin{obs}\label{obs:category_of_cones}
-    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$ is defined to have cones for $D$ as objects and cone morphisms as arrows, where a con morphism $\phi: C \rightarrow C'$ from a cone $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
-    \[
-        \begin{tikzcd}
-            X \arrow[rr, "{\phi}"] \arrow[dr, "{f_i}" swap] & & X' \arrow[dl, "{f_i'}"] \\
-            & D(i) &
-        \end{tikzcd}
-    \]
-\end{obs}
-
-\begin{definition}[Limits]\label{def:limit}
-    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
-A cone $\{f_i: X \rightarrow D(i)\}$ is a \emph{limit} provided that, for any other cone $\{f_{i}': X' \rightarrow D(i)\}$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
-    \[
-        \begin{tikzcd}
-            X' \arrow[rr, dashed, "k"] \arrow[dr, "{f_i'}" swap] & & X \arrow[dl, "{f_i}"] \\
-            & D(i) &
-        \end{tikzcd}
-    \]
-    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$.
-\end{definition}
-
-\begin{obs}
-    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in Observation~\ref{obs:category_of_cones}.
-\end{obs}
-
-The following examples show how limits are general concepts for the constructions defined above.
-
-\begin{example}
-    Let $D$ be the empty diagram in the category $\cat C$. Then, a cone for $D$ is any object of $\cat C$, while a limit is the terminal object of $\cat C$.
-\end{example}
-
-\begin{example}\label{ex:product_are_limits}
-    Let $D$ be the following diagram:
-    \[
-        \begin{tikzcd}
-            A & & B
-        \end{tikzcd}
-    \]
-    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in Example~\ref{ex: span}):
-    \[
-        \begin{tikzcd}
-            A & X \arrow[l, "f" swap] \arrow[r, "g"] & B
-        \end{tikzcd}
-    \]
-    A limit for $D$ is, if it exists, the product of $A$ and $B$.
-\end{example}
-
-\begin{example}
-    A pullback is the limit for the diagram below.
-    \[
-        \begin{tikzcd}
-            & B \arrow[d, "g"] \\
-            A \arrow[r, "f" swap] & C
-        \end{tikzcd}
-    \]
-    In fact, a cone for the diagram above is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$ and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
-    Thus, the following diagram is a cone:
-    \[
-        \begin{tikzcd}
-            P \arrow[r, "{\psi}"] \arrow[d, "{\phi}" swap] & B \arrow[d, "g"] \\
-            A \arrow[r, "f" swap] & C
-        \end{tikzcd}
-    \]
-    For $(P, \phi, \psi)$ to be a pullback, it must have the universal property. In other words, it has to be a limit.
-
-    This example show us that a pullback is a limit for a cospan (Example~\ref{ex: span}).
-\end{example}
-
-\begin{example}\label{ex:equaliz_are_limits}
-    A limit for the diagram below is an equalizer for $f$ and $g$.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, shift left, "f"] \arrow[r, shift right,"g"swap] & B
-        \end{tikzcd}
-    \]
-\end{example}
-
-The connection between constructions as products and equalizers and limits is made clear by the following theorem.
-The idea behind the proof is the fact that, given a diagram $D : \cat I \rightarrow \cat C$, if each subset of objects $X = \{D(i) \mid i \in \Ob(\cat I)\} \subseteq \Ob(\cat C)$ has a product $(\prod_{i \in I} D(i), (\pi_i)_{i \in \Ob( \cat I)})$ and each pair of arrows $f, g \in \cat C (D(i), D(j))$ has an equalizer $Eq(f, g)$, then one can construct the cone taking the equalizer of the arrows that has as domain the product of the objects of the diagram, and as codomain the product of the codomains of the arrows of the diagram.
-This construction has the universal property because equalizers and product do.
-
-\begin{theorem}[Limit theorem]
-    Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
-\end{theorem}
-
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement is easily satisfied as shown in Example~\ref{ex:equaliz_are_limits} and Example~\ref{ex:product_are_limits}.
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i)_{i \in \Ob(\cat I)})$ is the limit of $D$, namely, show that conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-The dual notions of cones and limits are that of cocones and colimits.
-
-\begin{definition}(Cocones, Colimits)
-    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$.
-A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
-    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
-\end{definition}
-
-All examples done about limits are still valid, in their dual form, for what regard colimits.
-In fact, initial objects, coequalizer, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
-The limit theorem is still valid, considering coequalizers and coproducts, and the proof is much the same.
-
-\begin{example}
-    Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
-    \[
-        \begin{tikzcd}
-            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
-        \end{tikzcd}
-    \]
-    a cocone for $S$ is any commutative square of the form
-    \[
-        \begin{tikzcd}
-            & C & \\
-            L \arrow[ur, "f"] &
-            X \arrow[l, "l"swap] \arrow[r, "r"]&
-            R \arrow[ul, "g" swap]
-        \end{tikzcd}
-    \]
-    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
-    A colimit for $S$ is then a pushout of $l$ and $r$.
-\end{example}
-
-\begin{remark}
-    Since a diagram is nothing more than a functor form a "shape" category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
-\end{remark}
-
-\section{Adhesivity}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}
+\input{Background_sections/Basic_Notions}
+\input{Background_sections/Functors_NatTrans_Adjs}
+\input{Background_sections/Limit}
+\input{Background_sections/Adhesivity}

### 2024-10-20 Article/Background_sections/Adhesivity.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/main.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
-\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{hyperref, cleveref}
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\Reg}{\mathcal{R}eg}
-\newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\mymathbb{0}}
-\newcommand{\terminal}{\mathds{1}}
-\newcommand{\eqgraph}[1]{\mathbb{#1}}
-\newcommand{\Egg}{\mathbf{EGG}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
-
-\section{Basic Notions}\label{sect:basic_nots}
-
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
-
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
-
-\subsection{Categories}\label{ssect:cats}
-
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
-    \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
-
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:0_cat}
-    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
-\end{example}
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
-
-\begin{definition}\label{def:dual_cat}[Dual Category]
-    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
-    \begin{itemize}
-        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
-        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
-    \end{itemize}
-    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
-    Such category is called \emph{dual category} or \emph{opposite category}.
-\end{definition}
-
-Duality is a concept that we will encounter most of the time.
-Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
-There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
-
-%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-% Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
-    This category is denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the \Cref{def:category} above does not specify what kind of collections
-    %for a category $\cat{C}$, 
-    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
-This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
-
-Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
-\end{definition}
-
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
-
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
-Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
-Factorization of morphisms induces a preorder on subobjects of an object.
-$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
-
-An useful fact about subobjects is how factorization behaves.
-In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
-Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
-Suppose $k$ is another morphism such that $m = n \circ k$.
-We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
-This is to say what follows.
-
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
-\end{example}
-
-\begin{remark}
-    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
-    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
-\end{remark}
-
-\begin{prop}\label{prop:epi_mono_prop}
-    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
-    \begin{enumerate}
-        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
-        \item if $g \circ f$ is mono, then $f$ is mono;
-        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
-        \item if $g \circ f$ is epi, then $g$ is epi.
-    \end{enumerate}
-\end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
-
-\subsection{Categories from other categories}\label{ssect:cats_from_cats}
-
-Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
-
-The first notion to introduce is the one of subcategory.
-
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
-\end{definition}
-
-An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
-\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
-
-\todo{E cambierei anche l'intro a questa sezione DC}
-\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
-
-\subsection{Functors}
-
-A functor is a structure preserving map between categories. 
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
-The following definitions are about this particular type of functors.
-
-\begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
-    $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
-    $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
-\end{definition}
-
-\color{red}{
-    \begin{obs}
-        Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-    \end{obs}
-}\color{black}
-
-\begin{example}\label{ex:full_subc_inc_fully_faith}
-    Let $\cat C$ be a category and $\cat D$ a subcategory.
-The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
-If $\cat D$ is a full subcategory, then $I$ is fully faithful.
-\end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
-
-\subsection{Natural Transformations}
-
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Categories}
-
-The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
-\end{remark}
-
-\subsection{Comma Categories}
-
-Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g" swap] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
-
-\subsection{Adjoints}
-
-% \begin{definition}[Adjoint Functor]\label{def:adjoint}
-%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
-$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-%     \[
-%         \begin{tikzcd}
-%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
-%             & L(B)
-%         \end{tikzcd}
-%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
-%     \[
-%         \begin{tikzcd}
-%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
-%         \end{tikzcd}
-%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-% \end{definition}
-%\todo{sistemare la definizione}
-
-\begin{definition}[Right Adjoint]\label{def:right_adjoint}
-    Let $R: \cat{C \rightarrow D}$ be a functor.
-$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
-            & R(B)
-        \end{tikzcd}
-    \]
-    --i.e., $R(g) \circ \eta_A = f$.
-\end{definition}
-
-\begin{prop}\label{prop:ext_left_to_funct}
-    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
-Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
-\end{prop}
-\begin{proof}
-    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
-    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
-    \end{tikzcd}
-    \]
-
-    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
-    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
-    \end{tikzcd}
-    \]    \[
-    \begin{tikzcd}
-    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
-    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
-    \end{tikzcd}
-    \]
-
-    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
-\end{proof}
-
-\begin{remark}
-    The family above mentioned is called \emph{unit} of the adjunction.
-\end{remark}
-
-\begin{definition}[Left Adjoint]\label{def:left_adjoint}
-    Let $L: \cat{D \rightarrow C}$ be a functor.
-$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
-            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
-        \end{tikzcd}
-    \]
-    -- i.e., $\epsilon_B \circ L(f) = g$.
-\end{definition}
-
-As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
-The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
-
-The connection between left and right adjoints is expressed in the following proposition.
-
-\begin{prop}
-    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
-\end{prop}
-
-\begin{proof}
-	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
-	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
-	    \[
-	\begin{tikzcd}
-		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
-		& R(B)
-	\end{tikzcd}
-	\]
-
-	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
-	\begin{align*}
-		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
-	\end{align*}
-	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
- \end{proof}
-
-% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
-In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
 \section{Adhesivity}\label{sect:adh}
@@
 \end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-% Sec. 1 Categorie e funtori
-
-% >def di categorie
-% 	-menzionare che data una categoria c'è il duale
-% 	-epi, mono e  iso
-
-% >funtori e trasf naturali
-
-% >categorie comma (con slice e coslice come sottocaso)
-
-% Sec. 2: Limiti e colimiti
-% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
-% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-% 	-epi e mono regolari
-
-% >Limiti nelle categorie di funtori e comma
-
-% Sec. 3: Adesività
-% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
-}
-
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
-Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
-    \begin{itemize}
-        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
-        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
-    \end{itemize}
-    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
-\end{prop}
-
-\begin{proof}
-
-    \color{red}{
-    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
-Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
-Our claim is $D(\alpha) \circ l^i = l^j$.
-Hence,
-    \begin{align*}
-        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
-                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
-                            &= (l^j_V, l^j_E)                       \\
-                            &= l^j                              
-    \end{align*}
-    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
-But such equivalence relation exists in every case, considering the identity.
-This led us to the second point of the proof, that is, the universal property.
-    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
-    For the cone described above to be a limit must be valid the universal property.
-Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-Suppose the following situation:
-    \[
-        \begin{tikzcd}
-            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
-            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
-        \end{tikzcd}
-    \]
-    The universal property the follows from the definition of least equivalence relation.
-    } \color{black}
-\end{proof}
-
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
-
-\begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-We now give some considerations on quotient functor.
-
-\begin{prop}
-    Quotient functor has a left adjoint and a right adjoint.
-\end{prop}
-
-\begin{proof}
-    To prove the statement we just have to find the adjoints. 
-    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
-To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
-
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
-    Consider the following situation:
-    \[
-        \begin{tikzcd}
-            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
-            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
-            & \mathcal{G} \\
-            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
-            \arrow[u, dashed, "I(f)"] 
-            \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \]
-    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
-Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
-
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
-UPDATE: probabilmente questo non è nu funtore aggiunto}
-    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
-We have then the following situation:
-    \[
-        \begin{tikzcd}
-            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
-            & T(\mathcal{H}) = \eqgraph{H}
-        \end{tikzcd}
-    \]
-    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
-Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
-\end{proof}
-
-The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
-
-\begin{cor}\label{cor:quot_preserves_co_lim}
-    Quotient functor preserves limits and colimits. 
-\end{cor}
-
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
-\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{lemma}
-\todo{Capire qui!}
-
-}\color{black}
-\todo[color=green!40]{
-COSE DA FARE
->Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
->Quoziente crea certi pushout (questo va fatto ex novo)
-}
-% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
-
-\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
-\end{lemma}
-
-% Q crea pullback, Q crea pushout sui reg mono.
-
-\begin{lemma}
-    The quotient functor creates pullbacks.
-\end{lemma}
-
-\begin{proof}
-    We will show now that $Q$ reflects pullbacks.
-    Consider the following diagram in $\mathbf{Graph}$
-    \[
-        \begin{tikzcd}
-            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
-            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
-        \end{tikzcd}
-    \]
-    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
-We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
-    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
-\end{proof}
-
-\begin{lemma}
-    The quotient functor creates pushouts along regular monomorphism.
-\end{lemma}
-
-% \begin{proof}
-%     Consider the following situation
-% \end{proof}
-
-\begin{theorem}
-    $\mathbf{EqGrph}$ is quasiadhesive.
-\end{theorem}
-
-\begin{proof}
-    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{proof}
-
-\section{E-Graphs}\label{sect:eggs}
-
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
-In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
-\[
-    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
-\] for each $e$, $e' \in \eqgraph{G}(E)$.
-But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
-To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
-
-Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
-Specifically, we want, in the following situation, $i$ to be mono and unique.
-\[
-    \begin{tikzcd}
-        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
-        & \eqgraph{G}(E) \times \eqgraph{G}(E)
-    \end{tikzcd}
-\]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
-From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
-The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
-If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
-
-\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
-\end{definition}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
-\chapter{Omitted Proofs}
-
-\paragraph{\Cref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}

### 2024-10-20 Article/Background_sections/Basic_Notions.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/main.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
-\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{hyperref, cleveref}
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\Reg}{\mathcal{R}eg}
-\newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\mymathbb{0}}
-\newcommand{\terminal}{\mathds{1}}
-\newcommand{\eqgraph}[1]{\mathbb{#1}}
-\newcommand{\Egg}{\mathbf{EGG}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
-
 \section{Basic Notions}\label{sect:basic_nots}
@@
 \begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
+    It is easy to see that taking sets as objects and (total) functions as arrows, we obtain a category.
 In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
@@
 \end{definition}
-
-\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
-
-\todo{E cambierei anche l'intro a questa sezione DC}
-\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
-
-\subsection{Functors}
-
-A functor is a structure preserving map between categories. 
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
-The following definitions are about this particular type of functors.
-
-\begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
-    $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
-    $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
-\end{definition}
-
-\color{red}{
-    \begin{obs}
-        Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-    \end{obs}
-}\color{black}
-
-\begin{example}\label{ex:full_subc_inc_fully_faith}
-    Let $\cat C$ be a category and $\cat D$ a subcategory.
-The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
-If $\cat D$ is a full subcategory, then $I$ is fully faithful.
-\end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
-
-\subsection{Natural Transformations}
-
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Categories}
-
-The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
-\end{remark}
-
-\subsection{Comma Categories}
-
-Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g" swap] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
-
-\subsection{Adjoints}
-
-% \begin{definition}[Adjoint Functor]\label{def:adjoint}
-%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
-$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-%     \[
-%         \begin{tikzcd}
-%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
-%             & L(B)
-%         \end{tikzcd}
-%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
-%     \[
-%         \begin{tikzcd}
-%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
-%         \end{tikzcd}
-%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-% \end{definition}
-%\todo{sistemare la definizione}
-
-\begin{definition}[Right Adjoint]\label{def:right_adjoint}
-    Let $R: \cat{C \rightarrow D}$ be a functor.
-$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
-            & R(B)
-        \end{tikzcd}
-    \]
-    --i.e., $R(g) \circ \eta_A = f$.
-\end{definition}
-
-\begin{prop}\label{prop:ext_left_to_funct}
-    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
-Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
-\end{prop}
-\begin{proof}
-    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
-    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
-    \end{tikzcd}
-    \]
-
-    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
-    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
-    \end{tikzcd}
-    \]    \[
-    \begin{tikzcd}
-    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
-    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
-    \end{tikzcd}
-    \]
-
-    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
-\end{proof}
-
-\begin{remark}
-    The family above mentioned is called \emph{unit} of the adjunction.
-\end{remark}
-
-\begin{definition}[Left Adjoint]\label{def:left_adjoint}
-    Let $L: \cat{D \rightarrow C}$ be a functor.
-$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
-            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
-        \end{tikzcd}
-    \]
-    -- i.e., $\epsilon_B \circ L(f) = g$.
-\end{definition}
-
-As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
-The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
-
-The connection between left and right adjoints is expressed in the following proposition.
-
-\begin{prop}
-    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
-\end{prop}
-
-\begin{proof}
-	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
-	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
-	    \[
-	\begin{tikzcd}
-		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
-		& R(B)
-	\end{tikzcd}
-	\]
-
-	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
-	\begin{align*}
-		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
-	\end{align*}
-	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
- \end{proof}
-
-% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
-In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-\begin{obs}
-    $\Set$ is adhesive.
-    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
-\end{obs}
-
-Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
-
-\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
-    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\end{prop}
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}\label{th:crit_for_adh}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
-Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
-Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-% Sec. 1 Categorie e funtori
-
-% >def di categorie
-% 	-menzionare che data una categoria c'è il duale
-% 	-epi, mono e  iso
-
-% >funtori e trasf naturali
-
-% >categorie comma (con slice e coslice come sottocaso)
-
-% Sec. 2: Limiti e colimiti
-% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
-% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-% 	-epi e mono regolari
-
-% >Limiti nelle categorie di funtori e comma
-
-% Sec. 3: Adesività
-% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
-}
-
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
-Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
-    \begin{itemize}
-        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
-        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
-    \end{itemize}
-    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
-\end{prop}
-
-\begin{proof}
-
-    \color{red}{
-    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
-Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
-Our claim is $D(\alpha) \circ l^i = l^j$.
-Hence,
-    \begin{align*}
-        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
-                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
-                            &= (l^j_V, l^j_E)                       \\
-                            &= l^j                              
-    \end{align*}
-    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
-But such equivalence relation exists in every case, considering the identity.
-This led us to the second point of the proof, that is, the universal property.
-    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
-    For the cone described above to be a limit must be valid the universal property.
-Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-Suppose the following situation:
-    \[
-        \begin{tikzcd}
-            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
-            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
-        \end{tikzcd}
-    \]
-    The universal property the follows from the definition of least equivalence relation.
-    } \color{black}
-\end{proof}
-
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
-
-\begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-We now give some considerations on quotient functor.
-
-\begin{prop}
-    Quotient functor has a left adjoint and a right adjoint.
-\end{prop}
-
-\begin{proof}
-    To prove the statement we just have to find the adjoints. 
-    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
-To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
-
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
-    Consider the following situation:
-    \[
-        \begin{tikzcd}
-            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
-            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
-            & \mathcal{G} \\
-            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
-            \arrow[u, dashed, "I(f)"] 
-            \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \]
-    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
-Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
-
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
-UPDATE: probabilmente questo non è nu funtore aggiunto}
-    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
-We have then the following situation:
-    \[
-        \begin{tikzcd}
-            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
-            & T(\mathcal{H}) = \eqgraph{H}
-        \end{tikzcd}
-    \]
-    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
-Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
-\end{proof}
-
-The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
-
-\begin{cor}\label{cor:quot_preserves_co_lim}
-    Quotient functor preserves limits and colimits. 
-\end{cor}
-
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
-\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{lemma}
-\todo{Capire qui!}
-
-}\color{black}
-\todo[color=green!40]{
-COSE DA FARE
->Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
->Quoziente crea certi pushout (questo va fatto ex novo)
-}
-% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
-
-\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
-\end{lemma}
-
-% Q crea pullback, Q crea pushout sui reg mono.
-
-\begin{lemma}
-    The quotient functor creates pullbacks.
-\end{lemma}
-
-\begin{proof}
-    We will show now that $Q$ reflects pullbacks.
-    Consider the following diagram in $\mathbf{Graph}$
-    \[
-        \begin{tikzcd}
-            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
-            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
-        \end{tikzcd}
-    \]
-    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
-We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
-    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
-\end{proof}
-
-\begin{lemma}
-    The quotient functor creates pushouts along regular monomorphism.
-\end{lemma}
-
-% \begin{proof}
-%     Consider the following situation
-% \end{proof}
-
-\begin{theorem}
-    $\mathbf{EqGrph}$ is quasiadhesive.
-\end{theorem}
-
-\begin{proof}
-    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{proof}
-
-\section{E-Graphs}\label{sect:eggs}
-
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
-In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
-\[
-    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
-\] for each $e$, $e' \in \eqgraph{G}(E)$.
-But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
-To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
-
-Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
-Specifically, we want, in the following situation, $i$ to be mono and unique.
-\[
-    \begin{tikzcd}
-        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
-        & \eqgraph{G}(E) \times \eqgraph{G}(E)
-    \end{tikzcd}
-\]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
-From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
-The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
-If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
-
-\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
-\end{definition}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
-\chapter{Omitted Proofs}
-
-\paragraph{\Cref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}

### 2024-10-20 Article/Background_sections/Functors_NatTrans_Adjs.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/main.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
-\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{hyperref, cleveref}
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\Reg}{\mathcal{R}eg}
-\newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\mymathbb{0}}
-\newcommand{\terminal}{\mathds{1}}
-\newcommand{\eqgraph}[1]{\mathbb{#1}}
-\newcommand{\Egg}{\mathbf{EGG}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
-
-\section{Basic Notions}\label{sect:basic_nots}
-
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
-
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
-
-\subsection{Categories}\label{ssect:cats}
-
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
-    \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
-
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:0_cat}
-    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
-\end{example}
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
-
-\begin{definition}\label{def:dual_cat}[Dual Category]
-    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
-    \begin{itemize}
-        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
-        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
-    \end{itemize}
-    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
-    Such category is called \emph{dual category} or \emph{opposite category}.
-\end{definition}
-
-Duality is a concept that we will encounter most of the time.
-Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
-There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
-
-%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-% Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
-    This category is denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the \Cref{def:category} above does not specify what kind of collections
-    %for a category $\cat{C}$, 
-    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
-This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
-
-Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
-\end{definition}
-
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
-
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
-Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
-Factorization of morphisms induces a preorder on subobjects of an object.
-$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
-
-An useful fact about subobjects is how factorization behaves.
-In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
-Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
-Suppose $k$ is another morphism such that $m = n \circ k$.
-We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
-This is to say what follows.
-
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
-\end{example}
-
-\begin{remark}
-    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
-    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
-\end{remark}
-
-\begin{prop}\label{prop:epi_mono_prop}
-    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
-    \begin{enumerate}
-        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
-        \item if $g \circ f$ is mono, then $f$ is mono;
-        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
-        \item if $g \circ f$ is epi, then $g$ is epi.
-    \end{enumerate}
-\end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
-
-\subsection{Categories from other categories}\label{ssect:cats_from_cats}
-
-Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
-
-The first notion to introduce is the one of subcategory.
-
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
-\end{definition}
-
-An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
 \section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
@@
 In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-\begin{obs}
-    $\Set$ is adhesive.
-    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
-\end{obs}
-
-Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
-
-\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
-    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\end{prop}
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}\label{th:crit_for_adh}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
-Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
-Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-% Sec. 1 Categorie e funtori
-
-% >def di categorie
-% 	-menzionare che data una categoria c'è il duale
-% 	-epi, mono e  iso
-
-% >funtori e trasf naturali
-
-% >categorie comma (con slice e coslice come sottocaso)
-
-% Sec. 2: Limiti e colimiti
-% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
-% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-% 	-epi e mono regolari
-
-% >Limiti nelle categorie di funtori e comma
-
-% Sec. 3: Adesività
-% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
-}
-
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
-Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
-    \begin{itemize}
-        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
-        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
-    \end{itemize}
-    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
-\end{prop}
-
-\begin{proof}
-
-    \color{red}{
-    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
-Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
-Our claim is $D(\alpha) \circ l^i = l^j$.
-Hence,
-    \begin{align*}
-        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
-                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
-                            &= (l^j_V, l^j_E)                       \\
-                            &= l^j                              
-    \end{align*}
-    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
-But such equivalence relation exists in every case, considering the identity.
-This led us to the second point of the proof, that is, the universal property.
-    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
-    For the cone described above to be a limit must be valid the universal property.
-Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-Suppose the following situation:
-    \[
-        \begin{tikzcd}
-            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
-            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
-        \end{tikzcd}
-    \]
-    The universal property the follows from the definition of least equivalence relation.
-    } \color{black}
-\end{proof}
-
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
-
-\begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-We now give some considerations on quotient functor.
-
-\begin{prop}
-    Quotient functor has a left adjoint and a right adjoint.
-\end{prop}
-
-\begin{proof}
-    To prove the statement we just have to find the adjoints. 
-    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
-To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
-
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
-    Consider the following situation:
-    \[
-        \begin{tikzcd}
-            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
-            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
-            & \mathcal{G} \\
-            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
-            \arrow[u, dashed, "I(f)"] 
-            \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \]
-    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
-Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
-
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
-UPDATE: probabilmente questo non è nu funtore aggiunto}
-    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
-We have then the following situation:
-    \[
-        \begin{tikzcd}
-            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
-            & T(\mathcal{H}) = \eqgraph{H}
-        \end{tikzcd}
-    \]
-    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
-Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
-\end{proof}
-
-The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
-
-\begin{cor}\label{cor:quot_preserves_co_lim}
-    Quotient functor preserves limits and colimits. 
-\end{cor}
-
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
-\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{lemma}
-\todo{Capire qui!}
-
-}\color{black}
-\todo[color=green!40]{
-COSE DA FARE
->Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
->Quoziente crea certi pushout (questo va fatto ex novo)
-}
-% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
-
-\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
-\end{lemma}
-
-% Q crea pullback, Q crea pushout sui reg mono.
-
-\begin{lemma}
-    The quotient functor creates pullbacks.
-\end{lemma}
-
-\begin{proof}
-    We will show now that $Q$ reflects pullbacks.
-    Consider the following diagram in $\mathbf{Graph}$
-    \[
-        \begin{tikzcd}
-            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
-            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
-        \end{tikzcd}
-    \]
-    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
-We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
-    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
-\end{proof}
-
-\begin{lemma}
-    The quotient functor creates pushouts along regular monomorphism.
-\end{lemma}
-
-% \begin{proof}
-%     Consider the following situation
-% \end{proof}
-
-\begin{theorem}
-    $\mathbf{EqGrph}$ is quasiadhesive.
-\end{theorem}
-
-\begin{proof}
-    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{proof}
-
-\section{E-Graphs}\label{sect:eggs}
-
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
-In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
-\[
-    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
-\] for each $e$, $e' \in \eqgraph{G}(E)$.
-But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
-To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
-
-Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
-Specifically, we want, in the following situation, $i$ to be mono and unique.
-\[
-    \begin{tikzcd}
-        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
-        & \eqgraph{G}(E) \times \eqgraph{G}(E)
-    \end{tikzcd}
-\]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
-From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
-The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
-If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
-
-\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
-\end{definition}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
-\chapter{Omitted Proofs}
-
-\paragraph{\Cref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}

### 2024-10-20 Article/Background_sections/Limit.tex
reordering + redefn of graphs eqgrph

\section{Limits and Universal Constructions}\label{sect:limits_univ_constr}

\todo{aggiungere i diagrammi e sistemare per l'indice}

\subsection{Limits and Colimits}

% ---- Coni, Limiti ----

\begin{definition}[Cones]
    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$. A \emph{cone} for $D$ is an object $X$ of $\cat C$, together with arrows $f_i : X \rightarrow D(i)$ indexed by $\cat I$ (i.e. one for each object $i$ of $\cat I$), such that, for each morphism $\alpha: i \rightarrow j$ of $\cat I$, the following diagram commutes:
    \[
        \begin{tikzcd}
            & X \arrow[dl, "{f_i}"swap] \arrow[dr, "{f_j}"] & \\
            D(i) \arrow[rr, "{D(\alpha)}" swap] & & D(j)
        \end{tikzcd}
    \]
    -- i.e., $D(\alpha) \circ f_i = f_j$.
    We denote such cone as $\{f_i: X \rightarrow D(i)\}$.

\end{definition}

\begin{obs}\label{obs:category_of_cones}
    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$, is defined to have cones for $D$ as objects and cone morphisms as arrows, where a cone morphism $\phi: C \rightarrow C'$ from $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
    \[
        \begin{tikzcd}
            X \arrow[rr, "{\phi}"] \arrow[dr, "{f_i}" swap] & & X' \arrow[dl, "{f_i'}"] \\
            & D(i) &
        \end{tikzcd}
    \]
\end{obs}

\begin{definition}[Limits]\label{def:limit}
    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$. A cone $\{f_i: X \rightarrow D(i)\}$ is a \emph{limit} provided that, for any other cone $\{f_{i}': X' \rightarrow D(i)\}$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
    \[
        \begin{tikzcd}
            X' \arrow[rr, dashed, "k"] \arrow[dr, "{f_i'}" swap] & & X \arrow[dl, "{f_i}"] \\
            & D(i) &
        \end{tikzcd}
    \]
    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$
\end{definition}

\begin{obs}
    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in \Cref{obs:category_of_cones}.
\end{obs}

The dual notions of cones and limits are that of cocones and colimits.

\begin{definition}(Cocones, Colimits)
    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$. A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
\end{definition}

\begin{remark}
    It makes sense to refer to a (co)limit as \emph{the} (co)limit. Suppose $(P, p_i)_{i\in \cat I}$ and $(Q, q_i)_{i \in \cat I}$ be limits for a diagram $D: \cat{I \rightarrow C}$. Then, there exists a unique morphism $h: Q \rightarrow P$ such that $p_i \circ k = q_i$ for each $i$. At the same way, there exists a unique morphisms $k: P \rightarrow Q$ such that $q_i \circ k = p_i$ for each $i$. From the existence of the identity, must be $k \circ h = id_{Q}$ and $h \circ k = id_P$, that is, $P$ and $Q$ are isomorphic.
\end{remark}

Notion such limits and colimits are generalization of more particular cases that will be now introduced, that we will often call \emph{universal constructions}.

% ---- Oggetti Iniziali & Terminali ----

\begin{definition}[Initial Object, Terminal Object]
    Consider the empty diagram (i.e., a diagram $D: \textbf{0} \rightarrow \cat C$ where $\textbf{0}$ is the empty category \Cref{ex:0_cat}). Then, the limit of $D$ is called \emph{terminal object} and the colimit of $D$ is called \emph{initial object}, denoted, respectively, $\terminal_\cat{C}$ and $\initial_{\cat C}$. (Subscripts are omitted when they are clear from the context).
\end{definition}

\begin{example}\label{ex:set_init_term}
    In $\Set$, the initial object is the empty set $\varnothing$, because, for each set $S$, there exists the empty function from $\varnothing$ to $S$. The terminal object of $\Set$ is the singleton $\{ \bullet \}$, because there is exactly one function from a set $S$ to $\{ \bullet \}$, namely, the function which sends each $s \in S$ to $\bullet$.
    % It is possible to visualize the \Cref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective, while there exists a unique initial object.
\end{example}

We now illustrate a result on functor categories (\Cref{def:functor_category}) that will be useful later.

\begin{prop}
    Let $\cat D$ be a category. If $\cat D$ has an initial object, then, for any category $\cat C$, $[\cat{C, D}]$ has an initial object. If $\cat D$ has a terminal object, then, for any category $\cat C$, $[\cat{C, D}]$ has a terminal object.
\end{prop}

\begin{proof}
    Let $\initial_{\cat{D}}$ be the initial object of $\cat D$,  and consider the constant functor $I(f) = id_{\initial_{\cat D}}$ for all $f \in \Hom(\cat C)$. Then, for any $G: \cat{C \rightarrow D}$, $\eta: I \rightarrow G$, defining $\eta_A$ as the \emph{unique morphism from $\initial_{\cat D}$ to $G(A)$} for each $A \in \Ob(\cat C)$, is a natural transformation $I \dot\rightarrow G$, as the diagram below shows:
    \[
        \begin{tikzcd}
            I(A)=\initial_{\cat D} 
                    \arrow[r, "{\eta_A}"]
                    \arrow[d, "{I(f) = id_{\initial_{\cat D}}}" swap] &
            G(A)
                    \arrow[d, "G(f)"] \\
            I(A') = \initial_{\cat D}
                    \arrow[r, "{\eta_{A'}}" swap] &
            G(A')
        \end{tikzcd}
    \]
    for each $f: A \rightarrow A'$, the square above must commute, since there is only one morphism from $\initial_{\cat D}$ to $G(A')$. For the same reason, $\eta$ is the only natural transformation from $I$ to $G$, being indeed the initial object of $[\cat{C, D}]$.

    Defining $T(f) = id_{\terminal_{\cat D}}$ for each $f \in \Hom(\cat C)$. Then, $\theta:F\rightarrow T$, for any $F: \cat{C \rightarrow D}$, defining $\theta_A$ as the \emph{unique morphism from $F(A)$ to $\terminal_{\cat{D}}$} is a natural transformation due to the commutativity of the following diagram for each $f: A \rightarrow A'$:
    \[
        \begin{tikzcd}
            F(A) \arrow[r, "{\theta_A}"] \arrow[d, "F(f)" swap] &
            T(A) = \terminal_{\cat D} \arrow[d, "{T(f) = id_{\terminal_{\cat D}}}"] \\
            F(A') \arrow[r, "{\theta_{A'}}" swap] & T(A') = \terminal_{\cat D}
        \end{tikzcd}
    \]
    Hence, $\theta$ is the unique natural transformation from $F$ to $T$, and $T$ is the terminal object of $[\cat{C, D}]$.
\end{proof}

In particular, every presheaf has an initial and a terminal object, because $\Set$ does (\Cref{ex:set_init_term}).

% ----- Prodotti, Coprodotti ----

\begin{definition}[Product, Coproduct]
        Let $D$ be the following diagram:
    \[
        \begin{tikzcd}
            A & & B
        \end{tikzcd}
    \]
    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in \Cref{ex: span}):
    \[
        \begin{tikzcd}
            A & X \arrow[l, "f" swap] \arrow[r, "g"] & B
        \end{tikzcd}
    \]
    If it exists, a limit for $D$ is called \emph{product} of $A$ and $B$, usually denoted as $(A\times B, \pi_A, \pi_B)$, while whose arrows are called \emph{projections}.
    The colimit of $D$ is called \emph{coproduct} of $A$ and $B$, usually denoted as $(\iota_A, \iota_B, A + B)$.
\end{definition}

\begin{example}
    $\Set$ has both products and coproduts. Given two sets $A$ and $B$, the categorical product is the set-theoretic cartesian product $A \times B$, together with the two projections $\pi_A$ and $\pi_B$, while the coproduct is the disjoint sum $A \amalg B = \{ (x, 0) \mid x \in A\} \cup \{(y, 1) \mid y \in B \}$, together with the two canonical injections $\iota_A$ and $\iota B$, where $\iota_A(a) = (a, 0)$ and $\iota_B(b) = (b, 1)$. 
\end{example}

The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for each object in the product). We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as \- $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.

% ---- Equalizzatori, Coequalizzatori ----

\begin{definition}[Equalizer, Coequalizer]\label{def:equalizer_coequalizer}
    Let $D$ be the diagram below.
    \[
        \begin{tikzcd}
            A \arrow[r, shift left, "f"] \arrow[r, shift right,"g"swap] & B
        \end{tikzcd}
    \]
    The limit of $D$ is called \emph{equalizer}, and its colimit is called \emph{coequalizer}.
\end{definition}

\begin{prop}\label{prop:eq_are_mono}
    Let $e: E \rightarrow A$ be the arrow that equalizes $f, g : A \rightarrow B$ in a category $\cat C$. Then, $e$ is a monomorphism.
\end{prop}

\begin{proof}
    Suppose $X$ be an object and $x, y: X \rightarrow E$ be two morphisms in $\cat C$ such that $e \circ x = e \circ y$, and let $z = e \circ x$. Then, since $e$ is an equalizer, $f \circ e = g \circ e$, and $f \circ z = g \circ z$. But, for the universal property of limits, there must be exactly one $u: Z \rightarrow E$ such that $z = e \circ u$. It follow that $x = u$ and $y = u$, hence $x = y$.
\end{proof}

Of all monomorphisms, an interesting subclass of them is the one that contains only the equalizers.

\begin{definition}[Regular Monomorphism]\label{def:reg_mono}
    A monomorphism that is an equalizer for a pair of arrows is said \emph{regular monomorphism}. The class of all regular monomorphisms of a category $\cat C$ is denoted $\Reg(\cat C)$.
\end{definition}

\begin{obs}
    Given two composable regular monos $m$ and $n$, suppose that $n$ equalizes two arrows $f$ and $g$. Then, we have
    \begin{align*}
        g \circ (n \circ m) &= (g \circ n) \circ m &&\\
                            &= (f \circ n) \circ m  && \textit{$n$ equalizer} \\
                            &= f \circ (n \circ m)
    \end{align*}
    Since $n \circ m$ is mono (\Cref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
\end{obs}

% ---- Pullback, Pushout -----

\begin{definition}[Pullback, Pushout]\label{def:pullback_pushout}
    Let $D$ be the cospan $(f, C, g) : A \rightharpoondown B$. % $$(A \xrightarrow{f} C \xleftarrow{g} B)$.
     A cone for $D$ is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$, and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
    Thus, the following diagram is a cone:
    \[
        \begin{tikzcd}
            P \arrow[r, "{\psi}"] \arrow[d, "{\phi}" swap] & B \arrow[d, "g"] \\
            A \arrow[r, "f" swap] & C
        \end{tikzcd}
    \]
     Then, the limit of $D$ is called \emph{pullback} of $f$ and $g$.
     Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
    \[
        \begin{tikzcd}
            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
        \end{tikzcd}
    \]
    a cocone for $S$ is any commutative square of the form
    \[
        \begin{tikzcd}
            & C & \\
            L \arrow[ur, "f"] &
            X \arrow[l, "l"swap] \arrow[r, "r"]&
            R \arrow[ul, "g" swap]
        \end{tikzcd}
    \]
    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
    The colimit for $S$ is called \emph{pushout} of $l$ and $r$.
\end{definition}

\begin{example}
    In $\Set$, given two functions $f: A \rightarrow C$ and $g: B \rightarrow C$, a pullback of $f$ and $g$ exists and is exactly the set $P = \{(x, y) \in A \times B \mid f(x) = g(y)\}$, with $\pi_f : P \rightarrow B$ and $\pi_g : P \rightarrow C$ defined, respectively, by $\pi_f((x, y)) = y$ and $\pi_g((x, y)) = x$. In this way, we have then, $\forall (x, y) \in P$:
    \begin{align*}
        (f \circ \pi_g) ((x, y))
                    &= f(\pi_g((x, y)))     &&  \\
                    & = f(x)                &&  \textit{Definition of $\pi_g$} \\
                    & = g(y)                &&  (x, y) \in P \\
                    & = g(\pi_f((x, y)))    &&  \textit{Definition of $\pi_f$} \\
                    & = (g \circ \pi_f) ((x, y)) && 
    \end{align*}
    thus, $f \circ \pi_g = g \circ \pi_f$.
\end{example}

Another important example to our aims is a concrete definition of what is a pushout in the category of sets, and why morally we can regard a pushout as \textit{the way to identify part of an object with a part of another}~\cite{Barr_Wells_1995}.

\begin{example}\label{ex:po_in_set}
    \color{blue}
    In $\Set$, given two functions $f: A \rightarrow B$ and $g: A \rightarrow C$, the pushout of them is the set $X = (B \amalg C) /_\sim$, where $\sim$ is the least equivalence relation such that $f(a) \sim g(a)$ for each $a \in A$, with $\iota_g:B \rightarrow X$ and $\iota_f : C \rightarrow X$ as arrows, sending each element of the domain in the corresponding equivalence class in $X$. In particular, for each $a \in A$:
    \begin{align*}
        (\iota_g \circ f) (a)
                        &= \iota_g(f(a))    &&\\
                        &= [(f(a), 0)]           && \textit{Definition of $\iota_g$} \\
                        &= [(g(a), 1)]           && f(a) \sim g(a) \\
                        &= \iota_f(g(a))    && \textit{Definition of $\iota_f$} \\
                        &= (\iota_f \circ g) (a) &&
    \end{align*}
    % This is not sure!!
    When both $f$ and $g$ are monos (that is, injections), then we can construct the pushout in the same way we have done above, with $(f(a), 0) \sim (g(a), 1)$ when such $a$ exists and $(b, 0) \sim (c, 1)$ on each $b$ and $c$ with no preimage in $A$, with $\iota_f$ and $\iota_g$ injective.
    An easy way to see this fact is considering the following situation: let $f: A \rightarrow A \cup B$ and $g: A \rightarrow A \cup C$, with $A$ disjoint from $B$ and $C$, $f(a)= a$ and $g(a) = a$. Then the pushout is the object $A \cup B \cup C$, with the inclusions as arrows, that are also injective.
    A more general case is what happens considering functions $f: A \rightarrow B$ and $g: A \rightarrow C$ injective. Differently from the previous example, in this case is not possible to take just the union of codomains as the pushout, but rather the disjoint union of them and then identify the elements $f(a)$ with $g(a)$, as we have done above. In the category of sets and functions, we have the certainty that the pullback arrows are injective. In fact, taking the equivalence relation $\sim$, we have that $f(a) \sim f(a')$ if and only if $a = a'$ by hypothesis, and then $x \sim x'$ if and only if $x = x'$, then the pushout morphisms sends each element in an equivalence class composed only by the element itself, thus are injective.
    This is an interesting property that in other categories may do not hold, and will be recalled later.
\end{example}

Given a subclass of morphisms of a category, an important property is \emph{stability} under certain type of constructions. In our case, we are interested in stability under pullbacks and under pushouts.
\[
    \begin{tikzcd}\label{diag:p_square}\tag{$\ast$}
        A \arrow[r, "f"] \arrow[d, "m"swap] & B \arrow[d, "n"] \\
        C \arrow[r, "g" swap] & D
    \end{tikzcd}
\]

\begin{definition}[Stability under pullbacks, pushouts]\label{def:stab_under_pb_po}
    Given a category $\cat C$, a subclass $\mathcal{A} \subseteq \Hom(\cat C)$ is said to be \emph{stable under pullbacks} if, for every pullback square as the one in \eqref{diag:p_square}, if $n \in \mathcal{A}$, then $m \in \mathcal{A}$.
    $\mathcal A$ is said to be \emph{stable under pushouts} if, for every pushout square as the one in \eqref{diag:p_square}, if $m \in \mathcal{A}$, then $n \in \mathcal{A}$.
\end{definition}

\begin{prop}\label{prop:monos_pres_by_pullback}
    Let $f: A \rightarrow C$, $g: B \rightarrow C$ be arrows in any category $\cat C$, and consider the following pullback square:
    \[
        \begin{tikzcd}
            P \arrow[r, "{\pi_f}"] \arrow[d, "{\pi_g}"swap] & B \arrow[d, "g"] \\
            A \arrow[r, "f"swap] & C
        \end{tikzcd}
    \]
    If $g$ is mono, then so is $\pi_g$.
\end{prop}

The proposition above can be dualised stating that pushouts preserves epimorphisms.

The connection between constructions as products and equalizers and limits is made clear by the following theorem. The idea behind the proof is the fact that, given a diagram $D : \cat I \rightarrow \cat C$, if each subset of objects $X = \{D(i) \mid i \in \Ob(\cat I)\} \subseteq \Ob(\cat C)$ has a product $(\prod_{i \in I} D(i), (\pi_i)_{i \in \Ob( \cat I)})$ and each pair of arrows $f, g \in \cat C (D(i), D(j))$ has an equalizer $Eq(f, g)$, then one can construct the cone taking the equalizer of the arrows that has as domain the product of the objects of the diagram, and as codomain the product of the codomains of the arrows of the diagram. This construction has the universal property because equalizers and products do. A detailed proof is in the appendix.

\begin{theorem}[Limit theorem]\label{th:limit}
    Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all finite equalizers.
\end{theorem}

\begin{remark}
    The theorem above (and its relative proof) can be stated in its dual form leading to a theorem on existence of colimits, and a relative criterion to calculate them (taking the dual of the proof).
\end{remark}

\begin{example}\label{ex:lim_of_sets}
    Limit theorem gives us an easy way to calculate limits. An example of this fact is how limits are computed in $\Set$. Given a diagram $D: \cat{I} \rightarrow \Set$, where $\cat I$ is a small category and $I = Ob(\cat I)$, its limit is the set $L$ defined as follows:
    $$
        L = \{ (d_i)_{i \in I} \in \prod_{i \in I}D(i) \mid \forall \phi \in \cat I(i, i'), D(\phi)(d_i) = d_{i'} \}
    $$
    with projections as arrows.
\end{example}

\begin{example}\label{ex:colm_of_sets}
    As we have done in \Cref{ex:lim_of_sets}, we illustrate how to construct colimits in the category of sets. Given a small category $\cat I$, $ I = Ob(\cat I)$, and a diagram $D: \cat I \rightarrow \Set$, consider the equivalence relation $\sim$ defined on $\coprod_{i\in I} D(i)$ such that $d_i \sim d_{i'}$ if $d_i \in D(i), d_{i'} \in D(i')$ and there exists some $\phi \in \cat I(i, i')$ such that $D(\phi)(d_i) = d_{i'}$. Then, a colimit for $D$ is the set
    $$
        C = \big ( \coprod_{i \in I} D(i) \big ) / \sim
    $$
    with the inclusions as arrows.
\end{example}

\begin{remark}
    Since a diagram is nothing more than a functor from a ``shape'' category to another, it makes sense to talk about limits of functors in general, even when they are not intended to be diagrams.
\end{remark}

\begin{obs}\label{obs:limits_in_presh}
    So far we introduced categories of presheaves. In these categories, an interesting fact is that limits and colimits are computed pointwise -- i.e., the limit of a diagram in a category of presheaves is exactly the limit on each of its components.
\end{obs}

In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.

\begin{definition}
    Let $D : \cat{I \rightarrow C}$ be a diagram, and $F: \cat{C \rightarrow D}$ a functor. We say that $F$:
    \begin{enumerate}
        \item \emph{preserves limits} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $D$, then $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
        \item \emph{reflects limits} of $D$ if a cone $(L, l_i)_{i \in \cat I}$ is a limit for $D$ whenever $(F(L), F(l_i))_{i \in \cat I}$ is a limit for $F \circ D$.
        \item \emph{lifts limits (uniquely)} of $D$ if, given a limit $(L, l_i)_{i \in \cat I}$ for $F \circ D$, there exists a (unique) limit $(L', l_i')_{i \in \cat I}$ for $D$ such that $(F(L'), F(l_i'))_{i \in \cat I} = (L, l_i)_{i \in \cat I}$.
        \item \emph{creates limits} of $D$ if $D$ has a limit and $F$ preserves and reflects limits along it.
    \end{enumerate}
    The dual notions are obtained in the obvious way, namely, substituting the words ``limits'' and ``cones'' with ``colimits'' and ``cocones'', respectively
\end{definition}

\begin{obs}\label{obs:funct_creat_lim_then_lift}
    It holds that if a functor creates limits, then lifts uniquely limits~\cite{Adamek_Herrlich_Strecker_2009}.
\end{obs}

\begin{prop}\label{prop:inc_funct_reflects_so_limits}
    A fully faithful functor reflects all limits and colimits.
\end{prop}

The next theorem is about a particular property that adjoint functors have.

\begin{theorem}\label{th:adjoints_preserves_lim}
    Let $F: \cat{C \rightarrow D}$ be a functor, and $G: \cat{D \rightarrow C}$ its right adjoint. Then, $G$ preserves limits.
\end{theorem}

\begin{remark}
    The dual of the theorem above states that, if $G$ is a functor and $F$ is a left adjoint, then $F$ preserves colimits.
\end{remark}

### 2024-10-20 Article/Cat_of_Graphs.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/main.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
-\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{hyperref, cleveref}
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\Reg}{\mathcal{R}eg}
-\newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\mymathbb{0}}
-\newcommand{\terminal}{\mathds{1}}
-\newcommand{\eqgraph}[1]{\mathbb{#1}}
-\newcommand{\Egg}{\mathbf{EGG}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
-
-\section{Basic Notions}\label{sect:basic_nots}
-
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
-
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
-
-\subsection{Categories}\label{ssect:cats}
-
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
-    \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
-
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:0_cat}
-    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
-\end{example}
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
-
-\begin{definition}\label{def:dual_cat}[Dual Category]
-    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
-    \begin{itemize}
-        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
-        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
-    \end{itemize}
-    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
-    Such category is called \emph{dual category} or \emph{opposite category}.
-\end{definition}
-
-Duality is a concept that we will encounter most of the time.
-Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
-There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
-
-%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-% Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
-    This category is denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the \Cref{def:category} above does not specify what kind of collections
-    %for a category $\cat{C}$, 
-    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
-This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
-
-Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
-\end{definition}
-
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
-
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
-Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
-Factorization of morphisms induces a preorder on subobjects of an object.
-$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
-
-An useful fact about subobjects is how factorization behaves.
-In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
-Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
-Suppose $k$ is another morphism such that $m = n \circ k$.
-We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
-This is to say what follows.
-
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
-\end{example}
-
-\begin{remark}
-    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
-    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
-\end{remark}
-
-\begin{prop}\label{prop:epi_mono_prop}
-    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
-    \begin{enumerate}
-        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
-        \item if $g \circ f$ is mono, then $f$ is mono;
-        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
-        \item if $g \circ f$ is epi, then $g$ is epi.
-    \end{enumerate}
-\end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
-
-\subsection{Categories from other categories}\label{ssect:cats_from_cats}
-
-Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
-
-The first notion to introduce is the one of subcategory.
-
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
-\end{definition}
-
-An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
-\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
-
-\todo{E cambierei anche l'intro a questa sezione DC}
-\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
-
-\subsection{Functors}
-
-A functor is a structure preserving map between categories. 
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
-The following definitions are about this particular type of functors.
-
-\begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
-    $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
-    $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
-\end{definition}
-
-\color{red}{
-    \begin{obs}
-        Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-    \end{obs}
-}\color{black}
-
-\begin{example}\label{ex:full_subc_inc_fully_faith}
-    Let $\cat C$ be a category and $\cat D$ a subcategory.
-The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
-If $\cat D$ is a full subcategory, then $I$ is fully faithful.
-\end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
-
-\subsection{Natural Transformations}
-
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Categories}
-
-The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
-\end{remark}
-
-\subsection{Comma Categories}
-
-Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g" swap] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
-
-\subsection{Adjoints}
-
-% \begin{definition}[Adjoint Functor]\label{def:adjoint}
-%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
-$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-%     \[
-%         \begin{tikzcd}
-%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
-%             & L(B)
-%         \end{tikzcd}
-%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
-%     \[
-%         \begin{tikzcd}
-%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
-%         \end{tikzcd}
-%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-% \end{definition}
-%\todo{sistemare la definizione}
-
-\begin{definition}[Right Adjoint]\label{def:right_adjoint}
-    Let $R: \cat{C \rightarrow D}$ be a functor.
-$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
-            & R(B)
-        \end{tikzcd}
-    \]
-    --i.e., $R(g) \circ \eta_A = f$.
-\end{definition}
-
-\begin{prop}\label{prop:ext_left_to_funct}
-    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
-Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
-\end{prop}
-\begin{proof}
-    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
-    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
-    \end{tikzcd}
-    \]
-
-    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
-    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
-    \end{tikzcd}
-    \]    \[
-    \begin{tikzcd}
-    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
-    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
-    \end{tikzcd}
-    \]
-
-    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
-\end{proof}
-
-\begin{remark}
-    The family above mentioned is called \emph{unit} of the adjunction.
-\end{remark}
-
-\begin{definition}[Left Adjoint]\label{def:left_adjoint}
-    Let $L: \cat{D \rightarrow C}$ be a functor.
-$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
-            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
-        \end{tikzcd}
-    \]
-    -- i.e., $\epsilon_B \circ L(f) = g$.
-\end{definition}
-
-As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
-The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
-
-The connection between left and right adjoints is expressed in the following proposition.
-
-\begin{prop}
-    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
-\end{prop}
-
-\begin{proof}
-	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
-	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
-	    \[
-	\begin{tikzcd}
-		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
-		& R(B)
-	\end{tikzcd}
-	\]
-
-	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
-	\begin{align*}
-		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
-	\end{align*}
-	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
- \end{proof}
-
-% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
-In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-\begin{obs}
-    $\Set$ is adhesive.
-    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
-\end{obs}
-
-Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
-
-\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
-    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\end{prop}
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}\label{th:crit_for_adh}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
-Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
-Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-% Sec. 1 Categorie e funtori
-
-% >def di categorie
-% 	-menzionare che data una categoria c'è il duale
-% 	-epi, mono e  iso
-
-% >funtori e trasf naturali
-
-% >categorie comma (con slice e coslice come sottocaso)
-
-% Sec. 2: Limiti e colimiti
-% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
-% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-% 	-epi e mono regolari
-
-% >Limiti nelle categorie di funtori e comma
-
-% Sec. 3: Adesività
-% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
-}
+\newcommand{\graph}[1]{\mathcal{#1}}
+\newcommand{\Graph}{\mathbf{Graph}}
+\newcommand{\EqGrph}{\mathbf{EqGrph}}
+\newcommand{\Q}{Q} % Quotient functor
 
@@
 
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
-Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
-    \begin{itemize}
-        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
-        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
-    \end{itemize}
-    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
-\end{prop}
-
-\begin{proof}
-
-    \color{red}{
-    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
-Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
-Our claim is $D(\alpha) \circ l^i = l^j$.
-Hence,
-    \begin{align*}
-        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
-                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
-                            &= (l^j_V, l^j_E)                       \\
-                            &= l^j                              
-    \end{align*}
-    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
-But such equivalence relation exists in every case, considering the identity.
-This led us to the second point of the proof, that is, the universal property.
-    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
-    For the cone described above to be a limit must be valid the universal property.
-Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-Suppose the following situation:
-    \[
-        \begin{tikzcd}
-            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
-            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
-        \end{tikzcd}
-    \]
-    The universal property the follows from the definition of least equivalence relation.
-    } \color{black}
-\end{proof}
-
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
-
-\begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-We now give some considerations on quotient functor.
-
-\begin{prop}
-    Quotient functor has a left adjoint and a right adjoint.
-\end{prop}
-
-\begin{proof}
-    To prove the statement we just have to find the adjoints. 
-    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
-To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
-
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
-    Consider the following situation:
-    \[
-        \begin{tikzcd}
-            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
-            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
-            & \mathcal{G} \\
-            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
-            \arrow[u, dashed, "I(f)"] 
-            \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \]
-    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
-Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
-
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
-UPDATE: probabilmente questo non è nu funtore aggiunto}
-    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
-We have then the following situation:
-    \[
-        \begin{tikzcd}
-            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
-            & T(\mathcal{H}) = \eqgraph{H}
-        \end{tikzcd}
-    \]
-    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
-Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
-\end{proof}
-
-The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
-
-\begin{cor}\label{cor:quot_preserves_co_lim}
-    Quotient functor preserves limits and colimits. 
-\end{cor}
-
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
-\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{lemma}
-\todo{Capire qui!}
-
-}\color{black}
-\todo[color=green!40]{
-COSE DA FARE
->Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
->Quoziente crea certi pushout (questo va fatto ex novo)
-}
-% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
-
-\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
-\end{lemma}
-
-% Q crea pullback, Q crea pushout sui reg mono.
-
-\begin{lemma}
-    The quotient functor creates pullbacks.
-\end{lemma}
-
-\begin{proof}
-    We will show now that $Q$ reflects pullbacks.
-    Consider the following diagram in $\mathbf{Graph}$
-    \[
-        \begin{tikzcd}
-            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
-            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
-        \end{tikzcd}
-    \]
-    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
-We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
-    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
-\end{proof}
-
-\begin{lemma}
-    The quotient functor creates pushouts along regular monomorphism.
-\end{lemma}
-
-% \begin{proof}
-%     Consider the following situation
-% \end{proof}
-
-\begin{theorem}
-    $\mathbf{EqGrph}$ is quasiadhesive.
-\end{theorem}
-
-\begin{proof}
-    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{proof}
-
-\section{E-Graphs}\label{sect:eggs}
-
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
-In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
-\[
-    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
-\] for each $e$, $e' \in \eqgraph{G}(E)$.
-But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
-To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
-
-Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
-Specifically, we want, in the following situation, $i$ to be mono and unique.
-\[
-    \begin{tikzcd}
-        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
-        & \eqgraph{G}(E) \times \eqgraph{G}(E)
-    \end{tikzcd}
-\]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
-From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
-The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
-If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
-
-\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
-\end{definition}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
-\chapter{Omitted Proofs}
-
-\paragraph{\Cref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}
+\input{Graph_sections/Graphs}
+\input{Graph_sections/Eq_Graphs}
+\input{Graph_sections/EGGs}

### 2024-10-20 Article/Categories_of_Graphs_old.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/main.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
-\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{hyperref, cleveref}
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\Reg}{\mathcal{R}eg}
-\newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\mymathbb{0}}
-\newcommand{\terminal}{\mathds{1}}
-\newcommand{\eqgraph}[1]{\mathbb{#1}}
-\newcommand{\Egg}{\mathbf{EGG}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
-
-\section{Basic Notions}\label{sect:basic_nots}
-
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
-
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
-
-\subsection{Categories}\label{ssect:cats}
-
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
-    \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
-
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:0_cat}
-    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
-\end{example}
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
-
-\begin{definition}\label{def:dual_cat}[Dual Category]
-    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
-    \begin{itemize}
-        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
-        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
-    \end{itemize}
-    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
-    Such category is called \emph{dual category} or \emph{opposite category}.
-\end{definition}
-
-Duality is a concept that we will encounter most of the time.
-Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
-There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
-
-%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-% Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
-    This category is denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the \Cref{def:category} above does not specify what kind of collections
-    %for a category $\cat{C}$, 
-    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
-This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
-
-Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
-\end{definition}
-
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
-
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
-Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
-Factorization of morphisms induces a preorder on subobjects of an object.
-$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
-
-An useful fact about subobjects is how factorization behaves.
-In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
-Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
-Suppose $k$ is another morphism such that $m = n \circ k$.
-We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
-This is to say what follows.
-
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
-\end{example}
-
-\begin{remark}
-    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
-    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
-\end{remark}
-
-\begin{prop}\label{prop:epi_mono_prop}
-    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
-    \begin{enumerate}
-        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
-        \item if $g \circ f$ is mono, then $f$ is mono;
-        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
-        \item if $g \circ f$ is epi, then $g$ is epi.
-    \end{enumerate}
-\end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
-
-\subsection{Categories from other categories}\label{ssect:cats_from_cats}
-
-Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
-
-The first notion to introduce is the one of subcategory.
-
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
-\end{definition}
-
-An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
-\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
-
-\todo{E cambierei anche l'intro a questa sezione DC}
-\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
-
-\subsection{Functors}
-
-A functor is a structure preserving map between categories. 
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
-The following definitions are about this particular type of functors.
-
-\begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
-    $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
-    $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
-\end{definition}
-
-\color{red}{
-    \begin{obs}
-        Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-    \end{obs}
-}\color{black}
-
-\begin{example}\label{ex:full_subc_inc_fully_faith}
-    Let $\cat C$ be a category and $\cat D$ a subcategory.
-The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
-If $\cat D$ is a full subcategory, then $I$ is fully faithful.
-\end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
-
-\subsection{Natural Transformations}
-
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Categories}
-
-The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
-\end{remark}
-
-\subsection{Comma Categories}
-
-Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g" swap] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
-
-\subsection{Adjoints}
-
-% \begin{definition}[Adjoint Functor]\label{def:adjoint}
-%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
-$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-%     \[
-%         \begin{tikzcd}
-%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
-%             & L(B)
-%         \end{tikzcd}
-%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
-%     \[
-%         \begin{tikzcd}
-%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
-%         \end{tikzcd}
-%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-% \end{definition}
-%\todo{sistemare la definizione}
-
-\begin{definition}[Right Adjoint]\label{def:right_adjoint}
-    Let $R: \cat{C \rightarrow D}$ be a functor.
-$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
-            & R(B)
-        \end{tikzcd}
-    \]
-    --i.e., $R(g) \circ \eta_A = f$.
-\end{definition}
-
-\begin{prop}\label{prop:ext_left_to_funct}
-    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
-Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
-\end{prop}
-\begin{proof}
-    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
-    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
-    \end{tikzcd}
-    \]
-
-    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
-    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
-    \end{tikzcd}
-    \]    \[
-    \begin{tikzcd}
-    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
-    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
-    \end{tikzcd}
-    \]
-
-    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
-\end{proof}
-
-\begin{remark}
-    The family above mentioned is called \emph{unit} of the adjunction.
-\end{remark}
-
-\begin{definition}[Left Adjoint]\label{def:left_adjoint}
-    Let $L: \cat{D \rightarrow C}$ be a functor.
-$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
-            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
-        \end{tikzcd}
-    \]
-    -- i.e., $\epsilon_B \circ L(f) = g$.
-\end{definition}
-
-As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
-The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
-
-The connection between left and right adjoints is expressed in the following proposition.
-
-\begin{prop}
-    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
-\end{prop}
-
-\begin{proof}
-	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
-	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
-	    \[
-	\begin{tikzcd}
-		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
-		& R(B)
-	\end{tikzcd}
-	\]
-
-	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
-	\begin{align*}
-		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
-	\end{align*}
-	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
- \end{proof}
-
-% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
-In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-\begin{obs}
-    $\Set$ is adhesive.
-    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
-\end{obs}
-
-Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
-
-\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
-    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\end{prop}
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}\label{th:crit_for_adh}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
-Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
-Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-% Sec. 1 Categorie e funtori
-
-% >def di categorie
-% 	-menzionare che data una categoria c'è il duale
-% 	-epi, mono e  iso
-
-% >funtori e trasf naturali
-
-% >categorie comma (con slice e coslice come sottocaso)
-
-% Sec. 2: Limiti e colimiti
-% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
-% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-% 	-epi e mono regolari
-
-% >Limiti nelle categorie di funtori e comma
-
-% Sec. 3: Adesività
-% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
-}
-
 \chapter{Categories of Graphs}
@@
 \end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
-\chapter{Omitted Proofs}
-
-\paragraph{\Cref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}

### 2024-10-20 Article/Graph_sections/EGGs.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/Categories_of_Graphs_old.tex
@@
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
-Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
-    \begin{itemize}
-        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
-        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
-    \end{itemize}
-    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
-\end{prop}
-
-\begin{proof}
-
-    \color{red}{
-    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
-Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
-Our claim is $D(\alpha) \circ l^i = l^j$.
-Hence,
-    \begin{align*}
-        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
-                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
-                            &= (l^j_V, l^j_E)                       \\
-                            &= l^j                              
-    \end{align*}
-    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
-But such equivalence relation exists in every case, considering the identity.
-This led us to the second point of the proof, that is, the universal property.
-    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
-    For the cone described above to be a limit must be valid the universal property.
-Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-Suppose the following situation:
-    \[
-        \begin{tikzcd}
-            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
-            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
-        \end{tikzcd}
-    \]
-    The universal property the follows from the definition of least equivalence relation.
-    } \color{black}
-\end{proof}
-
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
-
-\begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-We now give some considerations on quotient functor.
-
-\begin{prop}
-    Quotient functor has a left adjoint and a right adjoint.
-\end{prop}
-
-\begin{proof}
-    To prove the statement we just have to find the adjoints. 
-    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
-To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
-
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
-    Consider the following situation:
-    \[
-        \begin{tikzcd}
-            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
-            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
-            & \mathcal{G} \\
-            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
-            \arrow[u, dashed, "I(f)"] 
-            \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \]
-    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
-Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
-
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
-UPDATE: probabilmente questo non è nu funtore aggiunto}
-    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
-We have then the following situation:
-    \[
-        \begin{tikzcd}
-            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
-            & T(\mathcal{H}) = \eqgraph{H}
-        \end{tikzcd}
-    \]
-    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
-Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
-\end{proof}
-
-The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
-
-\begin{cor}\label{cor:quot_preserves_co_lim}
-    Quotient functor preserves limits and colimits. 
-\end{cor}
-
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
-\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{lemma}
-\todo{Capire qui!}
-
-}\color{black}
-\todo[color=green!40]{
-COSE DA FARE
->Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
->Quoziente crea certi pushout (questo va fatto ex novo)
-}
-% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
-
-\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
-\end{lemma}
-
-% Q crea pullback, Q crea pushout sui reg mono.
-
-\begin{lemma}
-    The quotient functor creates pullbacks.
-\end{lemma}
-
-\begin{proof}
-    We will show now that $Q$ reflects pullbacks.
-    Consider the following diagram in $\mathbf{Graph}$
-    \[
-        \begin{tikzcd}
-            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
-            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
-        \end{tikzcd}
-    \]
-    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
-We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
-    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
-\end{proof}
-
-\begin{lemma}
-    The quotient functor creates pushouts along regular monomorphism.
-\end{lemma}
-
-% \begin{proof}
-%     Consider the following situation
-% \end{proof}
-
-\begin{theorem}
-    $\mathbf{EqGrph}$ is quasiadhesive.
-\end{theorem}
-
-\begin{proof}
-    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{proof}
-
 \section{E-Graphs}\label{sect:eggs}
@@
 Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
+The following result follows by the fact that a full and faithful functor preserves equalizers.
 {\color{red}{????

### 2024-10-20 Article/Graph_sections/Eq_Graphs.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/main.tex
@@
-\documentclass[a4paper, twoside,openright]{report}
-\usepackage[T1]{fontenc} % Font encoding, T1 = it
-\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
-\usepackage{graphicx} % Per includere immagini esterne
-\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-% \usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
-\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
-\usepackage{titlesec} %indice
-
-\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
-\usepackage{hyperref, cleveref}
-\raggedbottom % Se la pagina non è completa, lascia lo spazio alla fine
-\pagestyle{headings}
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
-
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-
-% General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
-
-\begin{document}
-
-\newcommand{\cat}[1]{\mathscr{#1}}
-\newcommand{\Ob}{\mathcal{O}b}
-\newcommand{\Hom}{\mathcal{H}om}
-\newcommand{\Set}{\mathbf{Set}}
-\newcommand{\Reg}{\mathcal{R}eg}
-\newcommand{\Mono}{\mathcal{M}ono}
-\newcommand{\initial}{\mymathbb{0}}
-\newcommand{\terminal}{\mathds{1}}
-\newcommand{\eqgraph}[1]{\mathbb{#1}}
-\newcommand{\Egg}{\mathbf{EGG}}
-
-% input file frontespizio.tex
-% \input{frontespizio}
-
-\tableofcontents
-
-% \chapter*{Introduction}
-% [TODO]
-
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
-
-\section{Basic Notions}\label{sect:basic_nots}
-
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
-
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
-
-\subsection{Categories}\label{ssect:cats}
-
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
-    \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
-
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:0_cat}
-    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
-\end{example}
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
-
-\begin{definition}\label{def:dual_cat}[Dual Category]
-    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
-    \begin{itemize}
-        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
-        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
-    \end{itemize}
-    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
-    Such category is called \emph{dual category} or \emph{opposite category}.
-\end{definition}
-
-Duality is a concept that we will encounter most of the time.
-Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
-There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
-
-%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-% Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
-    This category is denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the \Cref{def:category} above does not specify what kind of collections
-    %for a category $\cat{C}$, 
-    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
-This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
-
-Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
-\end{definition}
-
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
-
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
-Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
-Factorization of morphisms induces a preorder on subobjects of an object.
-$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
-
-An useful fact about subobjects is how factorization behaves.
-In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
-Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
-Suppose $k$ is another morphism such that $m = n \circ k$.
-We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
-This is to say what follows.
-
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
-\end{example}
-
-\begin{remark}
-    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
-    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
-\end{remark}
-
-\begin{prop}\label{prop:epi_mono_prop}
-    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
-    \begin{enumerate}
-        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
-        \item if $g \circ f$ is mono, then $f$ is mono;
-        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
-        \item if $g \circ f$ is epi, then $g$ is epi.
-    \end{enumerate}
-\end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
-
-\subsection{Categories from other categories}\label{ssect:cats_from_cats}
-
-Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
-
-The first notion to introduce is the one of subcategory.
-
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
-\end{definition}
-
-An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
-\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
-
-\todo{E cambierei anche l'intro a questa sezione DC}
-\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
-
-\subsection{Functors}
-
-A functor is a structure preserving map between categories. 
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
-The following definitions are about this particular type of functors.
-
-\begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
-    $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
-    $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
-\end{definition}
-
-\color{red}{
-    \begin{obs}
-        Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-    \end{obs}
-}\color{black}
-
-\begin{example}\label{ex:full_subc_inc_fully_faith}
-    Let $\cat C$ be a category and $\cat D$ a subcategory.
-The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
-If $\cat D$ is a full subcategory, then $I$ is fully faithful.
-\end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
-
-\subsection{Natural Transformations}
-
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Categories}
-
-The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
-\end{remark}
-
-\subsection{Comma Categories}
-
-Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g" swap] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
-
-\subsection{Adjoints}
-
-% \begin{definition}[Adjoint Functor]\label{def:adjoint}
-%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
-$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-%     \[
-%         \begin{tikzcd}
-%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
-%             & L(B)
-%         \end{tikzcd}
-%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
-%     \[
-%         \begin{tikzcd}
-%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
-%         \end{tikzcd}
-%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-% \end{definition}
-%\todo{sistemare la definizione}
-
-\begin{definition}[Right Adjoint]\label{def:right_adjoint}
-    Let $R: \cat{C \rightarrow D}$ be a functor.
-$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
-            & R(B)
-        \end{tikzcd}
-    \]
-    --i.e., $R(g) \circ \eta_A = f$.
-\end{definition}
-
-\begin{prop}\label{prop:ext_left_to_funct}
-    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
-Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
-\end{prop}
-\begin{proof}
-    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
-    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
-    \end{tikzcd}
-    \]
-
-    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
-    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
-    \end{tikzcd}
-    \]    \[
-    \begin{tikzcd}
-    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
-    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
-    \end{tikzcd}
-    \]
-
-    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
-\end{proof}
-
-\begin{remark}
-    The family above mentioned is called \emph{unit} of the adjunction.
-\end{remark}
-
-\begin{definition}[Left Adjoint]\label{def:left_adjoint}
-    Let $L: \cat{D \rightarrow C}$ be a functor.
-$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
-            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
-        \end{tikzcd}
-    \]
-    -- i.e., $\epsilon_B \circ L(f) = g$.
-\end{definition}
-
-As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
-The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
-
-The connection between left and right adjoints is expressed in the following proposition.
-
-\begin{prop}
-    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
-\end{prop}
-
-\begin{proof}
-	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
-	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
-	    \[
-	\begin{tikzcd}
-		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
-		& R(B)
-	\end{tikzcd}
-	\]
-
-	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
-	\begin{align*}
-		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
-	\end{align*}
-	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
- \end{proof}
-
-% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
-In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-\begin{obs}
-    $\Set$ is adhesive.
-    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
-\end{obs}
-
-Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
-
-\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
-    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\end{prop}
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}\label{th:crit_for_adh}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
-Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
-Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
-
-% Sec. 1 Categorie e funtori
-
-% >def di categorie
-% 	-menzionare che data una categoria c'è il duale
-% 	-epi, mono e  iso
-
-% >funtori e trasf naturali
-
-% >categorie comma (con slice e coslice come sottocaso)
-
-% Sec. 2: Limiti e colimiti
-% Io sinceramente questa la riscriverei completamente. La definizione di (co)limite deve venire prima e solo dopo deve venire l'elenco degli esempi. Struttura che propongo:
-
-% >definizione, esempi e se avanza tempo come si calcolano (co)limiti generali a partire da quelli "base" (tipo prodotti da pb e equalizzatori) 
-% 	-epi e mono regolari
-
-% >Limiti nelle categorie di funtori e comma
-
-% Sec. 3: Adesività
-% Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
-}
-
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
+\section{Graphs with Equivalences}
 
@@
 
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
+Formally,  A \emph{graph with equivalence} is a pair $\eqgraph{G} = (\graph G, \sim_\graph{G})$ where $\graph{G}$ is a graph and $\sim_\graph{G} \subseteq V_\graph{G}\times V_\graph{G}$ is an equivalence relation over its set of nodes.
+An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (\graph{G}, \sim_\graph{G})\rightarrow \eqgraph{H} = (\graph{H}, \sim_\graph{H})$ is a graph homomorphism $h = (h_V, h_E):\graph{G} \rightarrow \graph{H}$ such that if $v_1 \sim_\graph{G} v_2$ then $h_V(v_1) \sim_\graph{H} h_V(v_2)$.
+
+\todo{Remark su categorie in cui si può passare dalle relazioni di equivalenza al quoziente (Categorie Regolari (?)) per giustificare la def. di eq-grafo}.
+
+As we have done in \Cref{sect:graphs}, we can think to a graph with equivalence as a presheaf, this time from a category $E \rightrightarrows V \rightarrow C$, where the image of $C$ along the presheaf is the set of the equivalence classes, requiring that the morphism $V\rightarrow C$ is an epimorphism (that is, a surjective function).
+
+\begin{definition}[Category of Graphs with Equivalences]
+    The category $\EqGrph$ is the subcategory of $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V \xrightarrow{q} C, \Set]$$ such that, for each $\eqgraph{G} \in \Ob(\EqGrph)$, $\eqgraph{G}(q)$ is an epimorphism.
 \end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
 
@@
 \end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
 
@@
     } \color{black}
-\end{proof}
+\end{proof} \todo{Rivedere completamente questa proposizione e riadattarla alla definizione come prefasci.}
 
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
+\todo{Esempi, da copiare praticamente dalla versione precedente}
 
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
+From \Cref{prop:limits_in_EqGrph} it is possible to derive a string characterisation of regular monomorphisms in $\EqGrph$.
+Intuitively, a regular mono among graphs with equivalence is a morphism that not only preserves equivalences but reflects them too, that is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_\graph{H} h_V(v_2)$ implies $v_1 \sim_\graph{G} v_2$, then $h$ is regular mono.
 
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
+\begin{prop}\label{prop:reg_monos_in_EqGrph}
+    In $\EqGrph$, a monomorphims is regular if it is mono on all the components.
 \end{prop}
 
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
+\todo{prova}
 
 % Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
+The graph with equivalence $(\graph{G}, \sim_\graph{G})$ is another representation of the graph $\graph{G}/_{\sim_\graph{G}}$.
+Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence, which is defined below.
+The idea is to identify the graph with equivalence  above with $\graph{G}/_{\sim_\graph{G}} = (V/_{\sim_\graph G}, E, s', t')$, where $s'(e) = [v]_{\sim_\graph G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_\graph G}$ if $t(e) = v$, and, consequently, having coherent action on homomorphisms.
+
+% \begin{definition}[Quotient Functor]\label{def:quot_func}
+%     The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
+%     \begin{itemize}
+%         \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
+%         \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
+%     \end{itemize}
+% \end{definition}
 
 \begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
+    The \emph{quotient functor} is the functor $\Q: \EqGrph \rightarrow \Graph$ such that, for each $\eqgraph{G, H}$ and for each morphism $\phi = (\phi_E, \phi_V, \phi_C) : \eqgraph{G \dot\to H}$:
     \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
+        \item $\Q(\eqgraph{G})(E) = \eqgraph{G}(E)$, $\Q(\eqgraph{G})(V) = \eqgraph{G}(C)$;
+        \item $\Q(\eqgraph{G})(s) = \eqgraph{G}(q \circ s)$, $\Q(\eqgraph{G})(t) = \eqgraph{G}(q \circ t)$;
+        \item $\Q(\phi_E) = \phi_E$, $\Q(\phi_V) \circ \eqgraph{G}(q) = \phi_C \circ \eqgraph{H}(q) $.
     \end{itemize}
@@
 
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
+     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor
+     \todo{il punto è che NON sai che I è un funtore. Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore}
+     that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
     Consider the following situation:
@@
 
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
 \begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
@@
 
-}\color{black}
 \todo[color=green!40]{
@@
 \end{proof}
-
-\section{E-Graphs}\label{sect:eggs}
-
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
-In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
-\[
-    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
-\] for each $e$, $e' \in \eqgraph{G}(E)$.
-But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
-To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
-
-Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
-Specifically, we want, in the following situation, $i$ to be mono and unique.
-\[
-    \begin{tikzcd}
-        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
-        & \eqgraph{G}(E) \times \eqgraph{G}(E)
-    \end{tikzcd}
-\]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
-From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
-The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
-If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
-
-\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
-\end{definition}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
-\chapter{Omitted Proofs}
-
-\paragraph{\Cref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}

### 2024-10-20 Article/Graph_sections/Graphs.tex
reordering + redefn of graphs eqgrph

\section{Graphs}\label{sect:graphs}

A (directed graph) $\graph{G}$ is a mathematical structure consisting of a set of edge, a set of nodes and two functions, one assigning a \emph{source} node and one assigning a \emph{target} node to an edge. Formally, $\graph{G}$ is a quadruple $(V_\graph{G}, E_\graph{G}, s_\graph{G}, t_\graph{G})$, where $V_\graph{G}$ is the set of nodes, $E_\graph{G}$ is the set of edges, and $s_\graph{G}, t_\graph{G}: E_\graph{G} \rightarrow V_\graph{G}$ are the source and the target functions.

A \emph{graph homomorphism} $h: \graph{G \rightarrow H}$ is then a pair of functions $h = (h_V: V_\graph{G} \rightarrow V_\graph{H}, h_E: E_\graph{G} \rightarrow E_\graph{H})$ such that
    \[
        h_V \circ s_\graph{G} = s_\graph{H} \circ h_E
    \]
    and
    \[
        h_V \circ t_\graph{G} = t_\graph{H} \circ h_E
    \]
that is, a structure preserving map.

We can then generalize such notion to something more abstract, considering a graph nothing more than a presheaf from the category $(E \rightrightarrows V)$ to the category of sets.
Having two of such presheaves, a natural transformation from one to another encapsulates the behavior of a graph morphism due to naturality. We can now define the category of graphs.

\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
    We denote as $\Graph$ the category $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
\end{definition}

\todo{Dimostrare come si calcolano i limiti nelle categorie di prefasci (conponente per componente) e poi dare qualche esempio, porendendolo dalla versione precedente. Dimostrare anche come sono fatti i mono (mono sulle componenti).}
\begin{remark}
    TODO: Si può generalizzare a tutte le categorie regolari per evitare di perdere le proprietà che usiamo (da eq.rel. a quot.).
\end{remark}

### 2024-10-20 Article/UniversalConstructions.tex
reordering + redefn of graphs eqgrph

--- 2024-10-20 Article/Background_sections/Limit.tex
@@
-\section{Limits and Universal Constructions}\label{sect:limits_univ_constr}
+\section{Universal Constructions}\label{sect:univ_constr}
+\todo{Questa è da riscriviere e ridurre}
+% What we are interested in are the "best" construction having a certain property, and we exprtess this fact via requiring unique factorization when another construction does
 
-\todo{aggiungere i diagrammi e sistemare per l'indice}
+\subsection{Initial and Terminal Objects}
 
-\subsection{Limits and Colimits}
+The next definitions are about \emph{universal constructions}. The simplest ones are the notion of initial and, dually, terminal objects.
 
-% ---- Coni, Limiti ----
-
-\begin{definition}[Cones]
-    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
-A \emph{cone} for $D$ is an object $X$ of $\cat C$, together with arrows $f_i : X \rightarrow D(i)$ indexed by $\cat I$ (i.e.
-one for each object $i$ of $\cat I$), such that, for each morphism $\alpha: i \rightarrow j$ of $\cat I$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            & X \arrow[dl, "{f_i}"swap] \arrow[dr, "{f_j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}" swap] & & D(j)
-        \end{tikzcd}
-    \]
-    -- i.e., $D(\alpha) \circ f_i = f_j$.
-    We denote such cone as $\{f_i: X \rightarrow D(i)\}$.
-
+\begin{definition}[Initial and terminal object]
+    An object $A$ of a category $\cat C$ is said to be \emph{initial} if, for each other object $B$ of $\cat C$, there exists a unique morphism from $A$ to $B$.
+    Dually, an object $Z$ is said to be a terminal object in a category $\cat C$ if, for any other object $X$ of $\cat C$, there exists a unique morphism from $X$ to $Z$.
+    An initial object is indicated by the symbol $\initial$, and a terminal object by the symbol $\terminal$.
 \end{definition}
 
-\begin{obs}\label{obs:category_of_cones}
-    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$, is defined to have cones for $D$ as objects and cone morphisms as arrows, where a cone morphism $\phi: C \rightarrow C'$ from $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
-    \[
-        \begin{tikzcd}
-            X \arrow[rr, "{\phi}"] \arrow[dr, "{f_i}" swap] & & X' \arrow[dl, "{f_i'}"] \\
-            & D(i) &
-        \end{tikzcd}
-    \]
+\begin{obs}\label{obs:terminal_are_isomorph}
+    It makes sense to refer to an initial (and terminal) object as \emph{the} initial (\emph{the} terminal) object.
+Suppose that $\initial$ and $\initial'$ are distinct initial objects of a category $\cat C$.
+Then, there exists a unique morphism from $\initial$ to $\initial'$, say $f$.
+Likewise, it must exist a unique morphism from $\initial'$ to $\initial$, say $g$.
+Then, $g\circ f$ must be exactly $id_{\initial}$, and $f \circ g = id_{\initial'}$, and then they are isomorphic.
+The same argument works for the terminal object.
 \end{obs}
-
-\begin{definition}[Limits]\label{def:limit}
-    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
-A cone $\{f_i: X \rightarrow D(i)\}$ is a \emph{limit} provided that, for any other cone $\{f_{i}': X' \rightarrow D(i)\}$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
-    \[
-        \begin{tikzcd}
-            X' \arrow[rr, dashed, "k"] \arrow[dr, "{f_i'}" swap] & & X \arrow[dl, "{f_i}"] \\
-            & D(i) &
-        \end{tikzcd}
-    \]
-    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$
-\end{definition}
-
-\begin{obs}
-    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in \Cref{obs:category_of_cones}.
-\end{obs}
-
-The dual notions of cones and limits are that of cocones and colimits.
-
-\begin{definition}(Cocones, Colimits)
-    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$.
-A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
-    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
-\end{definition}
-
-\begin{remark}
-    It makes sense to refer to a (co)limit as \emph{the} (co)limit.
-Suppose $(P, p_i)_{i\in \cat I}$ and $(Q, q_i)_{i \in \cat I}$ be limits for a diagram $D: \cat{I \rightarrow C}$.
-Then, there exists a unique morphism $h: Q \rightarrow P$ such that $p_i \circ k = q_i$ for each $i$.
-At the same way, there exists a unique morphisms $k: P \rightarrow Q$ such that $q_i \circ k = p_i$ for each $i$.
-From the existence of the identity, must be $k \circ h = id_{Q}$ and $h \circ k = id_P$, that is, $P$ and $Q$ are isomorphic.
-\end{remark}
-
-Notion such limits and colimits are generalization of more particular cases that will be now introduced, that we will often call \emph{universal constructions}.
-
-% ---- Oggetti Iniziali & Terminali ----
-
-\begin{definition}[Initial Object, Terminal Object]
-    Consider the empty diagram (i.e., a diagram $D: \textbf{0} \rightarrow \cat C$ where $\textbf{0}$ is the empty category \Cref{ex:0_cat}).
-Then, the limit of $D$ is called \emph{terminal object} and the colimit of $D$ is called \emph{initial object}, denoted, respectively, $\terminal_\cat{C}$ and $\initial_{\cat C}$.
-(Subscripts are omitted when they are clear from the context).
-\end{definition}
 
@@
 The terminal object of $\Set$ is the singleton $\{ \bullet \}$, because there is exactly one function from a set $S$ to $\{ \bullet \}$, namely, the function which sends each $s \in S$ to $\bullet$.
-    % It is possible to visualize the \Cref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective, while there exists a unique initial object.
+It is possible to visualize the \Cref{obs:terminal_are_isomorph}: given two singletons $\{ \bullet \}$ and $\{ \star \}$, the function between them is bijective, while there exists a unique initial object.
 \end{example}
@@
 
-% ----- Prodotti, Coprodotti ----
+\subsection{Products and Coproducts}
 
-\begin{definition}[Product, Coproduct]
-        Let $D$ be the following diagram:
+More complex constructions are products (and, dually, coproducts).
+
+\begin{definition}[Product]
+    A \emph{product} of two objects $A$ an $B$ is an object $A \times B$ together with two \emph{projection arrows} $\pi_1:A\times B \rightarrow A$ and $\pi_2: A \times B \rightarrow B$ such that, for every object $C$ and pair of arrows $f: C \rightarrow A$, $g: C \rightarrow B$, there is exactly one arrow $\langle f, g \rangle : c \rightarrow A \times B$ making the diagram commutes
     \[
         \begin{tikzcd}
-            A & & B
+                    & C \arrow[dl, "f" swap] \arrow[d, dashed, "{\langle f, g \rangle}" description] \arrow[dr, "g"] & \\
+                A   & A \times B  \arrow[l, "{\pi_1}"] \arrow[r, "{\pi_2}" swap]    &  B    
         \end{tikzcd}
     \]
-    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in \Cref{ex: span}):
+   -- i.e., such that $\pi_1 \circ \langle f, g \rangle = f$ and $\pi_2 \circ \langle f, g \rangle  = g$.
+
+\end{definition}
+
+\begin{definition}[Coproduct]
+    The dual of the product is the \emph{coproduct}.
+    A coproduct of two objects $A$ and $B$ is an object $A + B$ together with two arrows $\iota_1:A\rightarrow A+B$, $\iota_2: B \rightarrow A + B$ such that, for every object $C$ and pair of arrows $f:A \rightarrow C$, $g:B \rightarrow C$, there is a unique arrow $[f, g] : A + B \rightarrow C$ such that the diagram commutes
     \[
         \begin{tikzcd}
-            A & X \arrow[l, "f" swap] \arrow[r, "g"] & B
+            A \arrow[r, "{\iota_1}"] \arrow[dr, "f" swap] & A+B \arrow[d, dashed, "{[f,g]}" description] & B \arrow[l, "{\iota_2}" swap] \arrow[dl, "g"] \\
+            & C & 
         \end{tikzcd}
     \]
-    If it exists, a limit for $D$ is called \emph{product} of $A$ and $B$, usually denoted as $(A\times B, \pi_A, \pi_B)$, while whose arrows are called \emph{projections}.
-    The colimit of $D$ is called \emph{coproduct} of $A$ and $B$, usually denoted as $(\iota_A, \iota_B, A + B)$.
+    -- i.e., such that $[f, g] \circ \iota_1 = f$ and $[f, g] \circ \iota_2 = g$.
 \end{definition}
@@
 The notions of product and coproduct can be easily generalized, extending the definition to the product (and coproduct) of a family of objects, together with appropriate arrows (e.g., the projection arrows for each object in the product).
-We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as \- $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
+We will denote the product of a collection of objects indexed by a (finite) category $\cat I$ as $\big(\prod_{i \in \Ob(\cat I)} X_i, (\pi_i)_{i \in \Ob(\cat I)}\big)$, and the coproduct as $\big((\iota_i)_{i \in \Ob(\cat I)}, \coprod_{i \in \Ob(\cat I)} X_i\big)$.
 
-% ---- Equalizzatori, Coequalizzatori ----
+Again, the definition of these constructions is divided into two parts: one stating what the construction is, and another stating that the construction satisfies the universal property.
 
-\begin{definition}[Equalizer, Coequalizer]\label{def:equalizer_coequalizer}
-    Let $D$ be the diagram below.
+\subsection{Equalizers and Coequalizers}
+
+The next notion is about a construction that make parallel arrows (i.e., two possibly distinct morphisms with the same domain and codomain) equal.
+In $\Set$, given two functions $f, g: A \rightarrow B$, such construction corresponds exactly to the restriction of the domain to the set of elements on which $f$ and $g$ are equal.
+Specifically, if we take the set $E = \{x \in A \mid f(x) = g(x)\}$, and we take the function $e: E \rightarrow A$ defined by $e(x) = x$, we obtain what is called an \emph{equalizer} for $f$ and $g$.
+In fact, $e$ is that function that make $f$ and $g$ be the same function -- i.e., $f \circ e = g \circ e$.
+This concept can be generalized as follows.
+
+\begin{definition}[Equalizer and Coequalizer]
+    Let $f, g: A \rightarrow B$ be two arrows of a category $\cat C$.
+An \emph{equalizer} for $f$ and $g$ is pair $(E, e)$, where $E$ is an object and $e: E \rightarrow A$ is an arrow in $\cat C$ such that:
+    \begin{enumerate}
+        \item \label{eq_1} $ f \circ e = g \circ e$; and
+        \item if $(E', e')$ is another pair that satisfies~\ref{eq_1}, then there exists a unique $h: E' \rightarrow E$ such that $e \circ h = e'$.
+    \end{enumerate}
     \[
         \begin{tikzcd}
-            A \arrow[r, shift left, "f"] \arrow[r, shift right,"g"swap] & B
+            E \arrow[r, "e"] & A \arrow[r, shift left, "f"] \arrow[r, shift right, "g" swap] & B \\
+            E' \arrow[u, dashed, "k"] \arrow[ur, "e'" swap] & 
         \end{tikzcd}
     \]
-    The limit of $D$ is called \emph{equalizer}, and its colimit is called \emph{coequalizer}.
+
+    A \emph{coequalizer} of $f$ and $g$, dually, is a pair $(c, C)$, where $C$ is an object and $c: B \rightarrow C$ such that $c \circ f = c \circ g$, with the universal property.
 \end{definition}
@@
 Then, since $e$ is an equalizer, $f \circ e = g \circ e$, and $f \circ z = g \circ z$.
-But, for the universal property of limits, there must be exactly one $u: Z \rightarrow E$ such that $z = e \circ u$.
+But, for the universal property of equalizers, there must be exactly one $u: Z \rightarrow E$ such that $z = e \circ u$.
 It follow that $x = u$ and $y = u$, hence $x = y$.
@@
 
-% ---- Pullback, Pushout -----
+\subsection{Pullbacks and Pushouts}
 
-\begin{definition}[Pullback, Pushout]\label{def:pullback_pushout}
-    Let $D$ be the cospan $(f, C, g) : A \rightharpoondown B$. % $$(A \xrightarrow{f} C \xleftarrow{g} B)$.
-     A cone for $D$ is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$, and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
-    Thus, the following diagram is a cone:
+Given two arrows, another pair of constructions one can find in a category is given by pullbacks and pushouts.
+
+\begin{definition}[Pullback, Pushout]
+        A \emph{pullback} of two arrows $f: A \rightarrow C$ and $g: B \rightarrow C$ is a triple $(P, \pi_g, \pi_f)$ containing an object $P$ and a pair of arrows $\pi_g: P \rightarrow A$, $\pi_f: P \rightarrow B$ such that:
+        \begin{enumerate}
+            \item\label{pb_1} $f \circ \pi_g = g \circ \pi_f$; and
+            \item if $(X, p, q)$, where $p: X \rightarrow A$ and $q: X \rightarrow B$, satisfies~\ref{pb_1}, then there is a unique $k:X \rightarrow P$ such that $p = \pi_g \circ k$ and $j = \pi_f \circ k$.
+        \end{enumerate}
         \[
         \begin{tikzcd}
-            P \arrow[r, "{\psi}"] \arrow[d, "{\phi}" swap] & B \arrow[d, "g"] \\
-            A \arrow[r, "f" swap] & C
+        X \arrow[drr, bend left=20, "q"] \arrow[ddr, bend right=20,"p" swap] \arrow[dr, dashed, "k"] & & \\
+        & P  \arrow[d, "{\pi_g}" swap] \arrow[r, "{\pi_f}"] & B \arrow[d, "g"] \\
+        & A  \arrow[r, "f" swap] & C
         \end{tikzcd}
     \]
-     Then, the limit of $D$ is called \emph{pullback} of $f$ and $g$.
-     Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
-    \[
-        \begin{tikzcd}
-            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
-        \end{tikzcd}
-    \]
-    a cocone for $S$ is any commutative square of the form
-    \[
-        \begin{tikzcd}
-            & C & \\
-            L \arrow[ur, "f"] &
-            X \arrow[l, "l"swap] \arrow[r, "r"]&
-            R \arrow[ul, "g" swap]
-        \end{tikzcd}
-    \]
-    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
-    The colimit for $S$ is called \emph{pushout} of $l$ and $r$.
+
+    Dually, the \emph{pushout} of two arrows $f: A \rightarrow B$ and $g: A\rightarrow C$ is a triple $(\iota_g, \iota_f, I)$, where $I$ is an object and $\iota_g:B \rightarrow I$ and $\iota_f: C \rightarrow I$ are morphisms such that:
+    \begin{enumerate}
+        \item\label{po_1} $\iota_g \circ f = \iota_f \circ g$; and 
+        \item if $(i, j, Y)$, where $i: B \rightarrow Y$ and $j: C \rightarrow Y$, satisfies~\ref{po_1}, then there is a unique $h: I \rightarrow Y$ such that $i = h \circ \iota_g$ and $j = h \circ \iota_f$.
+    \end{enumerate}
+    \[\begin{tikzcd}
+        A & C \\
+        B & I \\
+        && Y
+        \arrow["g", from=1-1, to=1-2]
+        \arrow["f" swap, from=1-1, to=2-1]
+        \arrow["{{\iota_f}}", from=1-2, to=2-2]
+        \arrow["j", bend left=20, from=1-2, to=3-3]
+        \arrow["{{\iota_g}}" swap, from=2-1, to=2-2]
+        \arrow["i" swap, bend right=20, from=2-1, to=3-3]
+        \arrow["h", dashed, from=2-2, to=3-3]
+    \end{tikzcd}\]
+    {% \[
+        %     \begin{tikzcd}
+        %         Y & &\\
+        %         & I \arrow[ul, dashed, "h"] & B \arrow[l, "{\iota_g}" swap] \arrow[ull, bend right=20, "i"swap] \\
+        %         & C \arrow[u, "{\iota_f}"] \arrow[uul, bend left=20, "j"] & A \arrow[l, "g"] \arrow[u, "f" swap]
+        %     \end{tikzcd}
+        % \]
+    }
 \end{definition}
+
+Pullbacks (and, dually, pushouts) are a construction that is slightly more general than products and equalizers.
+An intuition of what they represent is given by considering what is concretely a pullback in the category of sets.
 
@@
 
-The proposition above can be dualised stating that pushouts preserves epimorphisms.
+\subsection{Limits and Colimits}
+
+We now introduce the notion that generalize all the universal constructions defined above.
+In fact, initial objects, products, equalizers and pullbacks (dually, terminal objects, coproducts, coequalizers and pushouts) can be seen as the particular case of a certain type of construction, called limit.
+
+To define what a limit is, we first need to define cones.
+
+\begin{definition}[Cones]
+    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
+A \emph{cone} for $D$ is an object $X$ of $\cat C$, together with arrows $f_i : X \rightarrow D(i)$ indexed by $\cat I$ (i.e.
+one for each object $i$ of $\cat I$), such that, for each morphism $\alpha: i \rightarrow j$ of $\cat I$, the following diagram commutes:
+    \[
+        \begin{tikzcd}
+            & X \arrow[dl, "{f_i}"swap] \arrow[dr, "{f_j}"] & \\
+            D(i) \arrow[rr, "{D(\alpha)}" swap] & & D(j)
+        \end{tikzcd}
+    \]
+    -- i.e., $D(\alpha) \circ f_i = f_j$.
+    We denote such cone as $\{f_i: X \rightarrow D(i)\}$.
+
+\end{definition}
+
+\begin{obs}\label{obs:category_of_cones}
+    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$, is defined to have cones for $D$ as objects and cone morphisms as arrows, where a cone morphism $\phi: C \rightarrow C'$ from $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
+    \[
+        \begin{tikzcd}
+            X \arrow[rr, "{\phi}"] \arrow[dr, "{f_i}" swap] & & X' \arrow[dl, "{f_i'}"] \\
+            & D(i) &
+        \end{tikzcd}
+    \]
+\end{obs}
+
+\begin{definition}[Limits]\label{def:limit}
+    Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
+A cone $\{f_i: X \rightarrow D(i)\}$ is a \emph{limit} provided that, for any other cone $\{f_{i}': X' \rightarrow D(i)\}$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
+    \[
+        \begin{tikzcd}
+            X' \arrow[rr, dashed, "k"] \arrow[dr, "{f_i'}" swap] & & X \arrow[dl, "{f_i}"] \\
+            & D(i) &
+        \end{tikzcd}
+    \]
+    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$
+\end{definition}
+
+\begin{obs}
+    Given a diagram $D$, a limit for $D$ is exactly the terminal object of the category $\textbf{Cone}(D)$, defined in \Cref{obs:category_of_cones}.
+\end{obs}
+
+The dual notions of cones and limits are that of cocones and colimits.
+
+\begin{definition}(Cocones, Colimits)
+    A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$.
+A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
+    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
+\end{definition}
+
+The following examples show how limits are general concepts for the constructions defined above.
+
+\begin{example}
+    Let $D$ be the empty diagram in the category $\cat C$. Then, a cone for $D$ is any object of $\cat C$, while a limit is the terminal object of $\cat C$.
+\end{example}
+
+\begin{example}\label{ex:product_are_limits}
+    Let $D$ be the following diagram:
+    \[
+        \begin{tikzcd}
+            A & & B
+        \end{tikzcd}
+    \]
+    Then, a cone for $D$ is an object $X$ and two arrows $f: X \rightarrow A$, $g: X \rightarrow B$ (i.e., a span, defined in \Cref{ex: span}):
+    \[
+        \begin{tikzcd}
+            A & X \arrow[l, "f" swap] \arrow[r, "g"] & B
+        \end{tikzcd}
+    \]
+    If it exists, a limit for $D$ is the product of $A$ and $B$.
+\end{example}
+
+\begin{example}\label{ex:pb_as_limit}
+    A pullback is the limit for the diagram below.
+    \[
+        \begin{tikzcd}
+            & B \arrow[d, "g"] \\
+            A \arrow[r, "f" swap] & C
+        \end{tikzcd}
+    \]
+    In fact, a cone for the diagram above is an object $P$ and three arrows $\phi:P \rightarrow A$, $\psi: P \rightarrow B$, and $h: P \rightarrow C$, but the latter is uniquely determined by the other ones ($f \circ \phi = h = g \circ \psi$).
+    Thus, the following diagram is a cone:
+    \[
+        \begin{tikzcd}
+            P \arrow[r, "{\psi}"] \arrow[d, "{\phi}" swap] & B \arrow[d, "g"] \\
+            A \arrow[r, "f" swap] & C
+        \end{tikzcd}
+    \]
+    For $(P, \phi, \psi)$ to be a pullback, it must have the universal property. In other words, it has to be a limit.
+
+    This example show us that a pullback is a limit for a cospan (\Cref{ex: span}).
+\end{example}
+
+\begin{example}\label{ex:equaliz_are_limits}
+    A limit for the diagram below is an equalizer for $f$ and $g$.
+    \[
+        \begin{tikzcd}
+            A \arrow[r, shift left, "f"] \arrow[r, shift right,"g"swap] & B
+        \end{tikzcd}
+    \]
+\end{example}
+
+All the examples we provided about limits are still valid, in their dual form, for colimits.
+In fact, initial objects, coequalizers, coproducts and pullbacks are particular cases of limits, and the way to see this fact is the same seen in previous examples.
+
+\begin{example}
+    Given a span $S = (l, X, r): L \rightharpoonup R$, shown in the diagram below,
+    \[
+        \begin{tikzcd}
+            L & X \arrow[l, "l"swap] \arrow[r, "r"]& R
+        \end{tikzcd}
+    \]
+    a cocone for $S$ is any commutative square of the form
+    \[
+        \begin{tikzcd}
+            & C & \\
+            L \arrow[ur, "f"] &
+            X \arrow[l, "l"swap] \arrow[r, "r"]&
+            R \arrow[ul, "g" swap]
+        \end{tikzcd}
+    \]
+    (the morphism $X \rightarrow C$ is uniquely determined by the relation $f \circ l = g \circ r$).
+    A colimit for $S$ is then a pushout of $l$ and $r$.
+\end{example}
 

### 2024-10-20 Article/main.tex
reordering + redefn of graphs eqgrph

@@
 
-\chapter{Background}
-In this chapter the building blocks for this work, almost entirely based on categories, will be defined.
-The aim of what follows is not only to introduce concepts that will be used later, but also to understand how category theory is general enough to give the abstraction of known notions (mainly from set theory) to reuse them in different contexts.
-This is not a complete tutorial on categories, but instead a sufficient compendium of definitions to make clear what will be done in the next chapters.
+\input{Background}
+\input{Cat_of_Graphs}
 
-\section{Basic Notions}\label{sect:basic_nots}
+% ----------------- Appendix ------------------ %
+\input{Appendix}
 
-%The very fist concept to get familiar with is what is a category.
-We can see a category as a general construction that can provide any level of abstraction needed.
-In fact, the definition is not about what the category represents, but instead a more general scheme that \emph{may} represent something.
-The definition is about what a category is composed by, and how the objects in it interact between themselves.
+% ---------------- Bibliography ---------------- %
+\bibliographystyle{alpha}
 
-This section is all about basic definitions and examples, to get familiar with the formalism of categories.
+\bibliography{bibliography}
 
-\subsection{Categories}\label{ssect:cats}
+\end{document}
 
-\begin{definition}[Category]\label{def:category}
-    A \emph{category} $\cat{C}$ comprises:
-    \begin{enumerate}
-        \item A collection of \emph{objects} $\Ob(\cat{C})$;
-        \item A collection of \emph{arrows} (or \emph{morphisms}) $\Hom(\cat{C})$, often called \emph{homset}.
-    \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
-In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
-The collection of morphisms from an object $A$ to an object $B$ is denoted as $\cat{C}(A, B)$.
-    An operator $\circ$ of \emph{composition} maps every couple of morphisms $f$, $g$ with $cod\ f = dom \ g$ (in this case $f$ and $g$ are said to be composable) to a morphism $g \circ f : dom\ f \rightarrow cod \ g$.
-The composition operator is associative, i.e., for each composable arrows $f$, $g$ and $h$, it holds that
-    $$
-        h \circ (g \circ f) = (h\circ g) \circ f
-    $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
-    \[
-        id_B \circ f = f = f \circ id_A 
-    \]
-\end{definition}
+% --------------- Commenti ------------------- %
 
-The most important thing here is not the structure of the objects, but instead how this structure is preserved by the morphisms.
-
-\begin{example}\label{ex:0_cat}
-    A trivial example of category is the one with no objects, and hence no morphisms. Such category is denoted by $\textbf 0$ and is called \emph{empty category}.
-\end{example}
-
-\begin{example}\label{ex:1_cat}
-    The category with just one object and just one arrow, the identity arrow on that object, is denoted $\textbf 1$.
-In particular, the only object of this category is $\bullet$, and the only arrow is $id_{\bullet}$.
-\end{example}
-
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
-
-\begin{definition}\label{def:dual_cat}[Dual Category]
-    Given a category $\cat C$, there exist a category $\cat C^{op}$ such that:
-    \begin{itemize}
-        \item $Ob(\cat C^{op}) = Ob(\cat C)$;
-        \item if $f: A \rightarrow B$ is a morphism in $\cat C$, then $f: B\rightarrow A$ is a morphism in $\cat C ^ {op}$.
-    \end{itemize}
-    Hence, given $f : A \rightarrow B$ and $g: B \rightarrow C$ arrows in $\cat C$, as $g \circ f: A \rightarrow C$ is an arrow in $\cat C$, then $f \circ g: C \rightarrow A$ is an arrow in $\cat C ^{op}$.
-    Such category is called \emph{dual category} or \emph{opposite category}.
-\end{definition}
-
-Duality is a concept that we will encounter most of the time.
-Given a property $P$ valid for a category $\cat C$, we will refer to the same property in the opposite category $\cat C^{op}$ as the \emph{dual} of $P$, without explicitly constructing $\cat C^{op}$.
-There exist some properties that coincide exactly with their dual, and such properties are said to be \emph{self dual} properties.
-
-%  \emph{dual category} of a category $\cat{C}$, denoted $\cat{C}^{op}$, in which the objects are the same of $\cat{C}$, and the arrows are the opposite of the arrows in $\cat{C}$, i.e., if $f: A \rightarrow B$ is an arrow of $\cat{C}$, then $f: B \rightarrow A$ is an arrow of $\cat{C}^{op}$.
-% Each definition in category theory has a dual form.
-In general, if a statement $S$ is true in a category $\cat{C}$, then the opposite of the statement, $S^{op}$, obtained switching the words "domain" and "codomain" and replacing each composite $g \circ f$ into $f \circ g$, is still true in the category $\cat{C}^{op}$.
-Moreover, since every category is the opposite of its opposite, if a statement $S$ is true for every category, then $S^{op}$ is also true for every category ~\cite[pp8-9]{pierce91}.
-{\color{red} la discussione sul duale temo confonda}
-
-To represent morphisms of a category $\cat{C}$ it is possible to use \emph{diagrams}, as the one below, in which the vertices are objects of $\cat{C}$, and the edges are morphisms of $\cat{C}$.
-    \[
-    \begin{tikzcd}
-        X \arrow[d, "g'" swap] \arrow[r, "f'"] & Z \arrow[d, "g"] \\
-        W \arrow[r, "f" swap] & Y        
-    \end{tikzcd}
-    \]
-The diagram is said to commute whenever  $f \circ g' = g \circ f'$. Unique morphisms are represented with dashed arrows.
-A more rigorous definition of what a diagram is will be given later (\Cref{def:diagram}).
-
-\begin{example}
-    It is easy to see that taking sets as objects and total \todo{Ha senso mettere totale qui?}functions as arrows, we obtain a category.
-In fact, given two functions $f: A \rightarrow B$ and $g: B \rightarrow C$, it is possible to compose them obtaining an arrow $g \circ f : A \rightarrow C$, and the composition is associative.
-For each set $A$ there exists an identity function $id_A: A \rightarrow A$ such that $id_A(a) = a$ for each $a\in A$.
-    This category is denoted as $\Set$.
-\end{example}
-
-\begin{remark}\label{rem:small_cats}
-    It is important to note that the \Cref{def:category} above does not specify what kind of collections
-    %for a category $\cat{C}$, 
-    $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are.
-    Taking $\Set$ as example, the collection $\Ob(\Set)$ cannot be a set itself, due to Russel's paradox.
-It would be more appropriate referring to a category $\cat{C}$ which $\Ob(\cat{C})$ and $\Hom(\cat{C})$ are both sets as a \emph{small category}, but it is assumed in this work, except where it is made explicit, for a category to be small.
-    Another clarification must to be done, still considering $\Set$.
-Given two sets $A$ and $B$, it is possible to construct the set $B^A$ of all functions from $A$ to $B$.
-This is isomorphic to $\Set(A, B)$, for each pair of sets $A$ and $B$.
-    A category $\cat C$ where, for each pair of objects $A$ and $B$, $\cat C (A, B)$ is a set is said to be \emph{locally small}.
-\end{remark}
-
-\subsection{Mono, Epi and Iso}\label{ssect:Mono_epi_iso}
-
-Between the morphisms of a category, it is possible to distinguish some that have certain properties, as functions between sets can be surjective, injective or bijective.
-
-\begin{definition}[Monomorphism]\label{def:mono}
-    An arrow $f:B\rightarrow C$ in a category $\cat{C}$ is a \emph{monomorphism} if, for any pair of arrows of $\cat{C}$ $g:A \rightarrow B$, $h: A \rightarrow B$, the equality $f \circ g = f \circ h$ implies $g = h$.
-The class of monomorphisms of $\cat C$ is denoted $\Mono(\cat C)$.
-\end{definition}
-
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
-
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
-Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
-Lo standard, per quanto ne so, è usare sottoggetto per una classe di equivalenza di mono o, al massimo, per i mono}, $(A, m)$ is said to be a \emph{subobject} of $C$.
-Factorization of morphisms induces a preorder on subobjects of an object.
-$(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
-
-An useful fact about subobjects is how factorization behaves.
-In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
-Then, if $(A, m)\leq (B, n)$, we have $m = n \circ h$ for some $h$.
-Suppose $k$ is another morphism such that $m = n \circ k$.
-We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
-This is to say what follows.
-
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
-
-\begin{definition}[Epimorphism]\label{def:epi}
-    An arrow $f: A\rightarrow B$ in a category $\cat{C}$ is an \emph{epimorphism} if, for any pair of arrows of $\cat{C}$ $g : B \rightarrow C$, $h: B \rightarrow C$, the equality $g \circ f = h \circ f$ implies $g = h$.
-\end{definition}
-
-\begin{definition}[Isomorphism]\label{def:iso}
-    An arrow $f:A \rightarrow B$ is an \emph{isomorphism} if there is an arrow $f^{-1}:B \rightarrow A$, called the \emph{inverse} of $f$, such that $f^{-1}\circ f = id_{A}$ and $f \circ f^{-1} = id_{B}$.
-Two objects are said to be \emph{isomorphic} if there is an isomorphism between them.
-\end{definition}
-
-\begin{example}
-    In $\Set$, monomorphisms are injective functions, epimorphisms are surjective functions and isomorphisms are bijections.
-\end{example}
-
-\begin{remark}
-    Mono and epi are dual concepts. This fact is easily shown by considering how a monomorphism $m$ in a category $\cat C$ behaves in the dual category $\cat C^{op}$.
-    In $\cat C$ we have that $m \circ f = m \circ g$ implies $f = g$. In $\cat C^{op}$, the we can state that $f \circ m = g \circ m$ implies $f = g$, obtaining the definition of epi. 
-\end{remark}
-
-\begin{prop}\label{prop:epi_mono_prop}
-    The following statements hold for every pair of composable arrows $f$ and $g$ for any category $\cat C$:
-    \begin{enumerate}
-        \item if both $f$ and $g$ are mono, then $g \circ f$ is mono;
-        \item if $g \circ f$ is mono, then $f$ is mono;
-        \item if both $f$ and $g$ are epi, then $g \circ f$ is epi;
-        \item if $g \circ f$ is epi, then $g$ is epi.
-    \end{enumerate}
-\end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
-
-\subsection{Categories from other categories}\label{ssect:cats_from_cats}
-
-Starting from a category, it is possible to construct other categories with some interesting properties, as the following examples show.
-
-The first notion to introduce is the one of subcategory.
-
-\begin{definition}[Subcategory]
-    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
-    \begin{enumerate}
-        \item each object of $\cat{D}$ is an object of $\cat{C}$;
-        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
-        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
-    \end{enumerate}
-
-    If the inclusion at~\ref{inc} is an equality (i.e.
-$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
-    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
-\end{definition}
-
-An object of a category marks out a category itself. This is the case of slice (and coslice) categories.
-
-\begin{definition}[Slice Category]\label{def:slice_cat}
-    Given a category $\cat{C}$ and an object $X \in \Ob(\cat{C})$, the \emph{slice category} $\cat{C}/X$ is the category that has pairs $(A, f)$ as objects, where $A$ is an object of $C$ and $f: A \rightarrow X$ is an arrow in $\cat{C}$, and arrows $\phi: (A, f) \rightarrow (B, g)$ are given by a morphism $\phi: A \rightarrow B$ of $\cat{C}$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[d, "g"] \\
-            & X
-        \end{tikzcd}
-    \]
-    -- i.e, $g \circ \phi = f$.
-    Composition between two arrows in $\cat{C}/X$ $\phi: (A, f) \rightarrow (B, g)$ and $\psi: (B, g) \rightarrow (C, h)$ is the arrow $\psi \circ \phi : (A, f) \rightarrow (C, h)$ obtained in the obvious way:
-    \[
-        \begin{tikzcd}
-            A \arrow[bend left=30]{rr}{\psi \circ \phi}  \arrow[r, "{\phi}"] \arrow[dr, "f" swap] & B \arrow[r, "{\psi}"] \arrow[d, "g"] & C \arrow[dl, "h"] \\
-            & X & 
-        \end{tikzcd}
-    \]
-
-    The dual definition of \emph{coslice category}, noted $X/\cat{C}$ (where $X \in \Ob(\cat{C})$), is obtained by taking as objects the morhisms of $\cat{C}$ with domain $X$ and as arrows the morphisms $\phi: (A, f) \rightarrow (B, g)$ such that $f:X\rightarrow A, g:B \rightarrow X \text{ of }\cat{C}$ and $g = \phi \circ f$.
-\end{definition}
-
-Furthermore, it is possible to raise a new category from two old ones by taking their product, as the following definition shows.
-
-\begin{definition}[Product category]
-    Given two categories $\cat C, \cat D$, the \emph{product category} $\cat{C\times D}$ has as objects pairs of objects $(A, B)$, where $A \in \Ob(\cat C), B \in \Ob(\cat D)$, and as arrows pairs of morphisms $(f, g)$, where $f$ is an arrow in $\cat C$ and $g$ is an arrow in $\cat D$.
-Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
-\end{definition}
-
-\section{Functors, Natural Transformations, Adjoints}\label{sect:funct_nats}
-
-\todo{E cambierei anche l'intro a questa sezione DC}
-\todo{la 1.1 è un po' povera come sezione, se sposti questa sezione sui funtori prima, poi puoi arricchire la 1.1 con la sottosezione sulle comma}
-
-\subsection{Functors}
-
-A functor is a structure preserving map between categories. 
-\begin{definition}[Functor]
-    Let $\cat{C}$ and $\cat{D}$ be categories.
-A \emph{functor} $F:\cat{C \rightarrow D}$ is a map taking each object of $A \in \Ob(\cat{C})$ to an object $F(A) \in \Ob(\cat{D})$ and each arrow $f:A\rightarrow B$ of $\cat C$ to a arrow $F(f): F(A) \rightarrow F(B)$ of $\cat D$, such that, for all objects $A \in \Ob(\cat C)$ and composable arrows $f$ and $g$ of $\cat C$:
-    \begin{itemize}
-        \item $F(id_{A}) = id_{F(A)}$;
-        \item $F(g \circ f) = F(g) \circ F(f)$.
-    \end{itemize}
-
-    In this case, $\cat C$ is called \emph{domain} and $\cat D$ is called \emph{codomain} of the functor $F$.
-\end{definition}
-
-\begin{example}
-    A first example of functor is the \emph{identity functor}.
-Given a category $\cat C$, the identity functor $Id_\cat C :\cat{C \rightarrow C}$ is the functor that maps each object on itself and each arrow onto itself.
-\end{example}
-
-Once defined what a functor is, we can give a more rigorous definition of diagram.
-Although this may seem extremely technical, it will be useful, especially in the definition of limits (\Cref{def:limit}).
-
-\begin{definition}[Diagram]\label{def:diagram}
-    A \emph{diagram in a category $\cat C$ of shape $\cat I$} is a functor $D: \cat{I \rightarrow C}$.
-    The category $\cat I$ can be considered as the category indexing the objects and the morphisms of $\cat C$ shaped in $\cat I$.
-\end{definition}
-
-\begin{example}\label{ex: span}
-    A diagram of shape $\Lambda = (L \xleftarrow{l} X \xrightarrow{r} R)$ is said to be a \emph{span}, and is denoted by $(l, X, r): L \rightharpoonup R$.
-    A span can be viewed as the generalization of relations between sets.
-In fact, in $\Set$, a relation $R \subseteq A \times B$ is a span, with the projections $\pi_A : R \rightarrow A$ and $\pi_B : R \rightarrow B$ as arrows.
-
-    The dual notion of span is a \emph{cospan}, namely, a diagram of shape $\Lambda^{op} = (L \xrightarrow{l} X \xleftarrow{r} R)$, and is denoted by $(l, X, r): L \rightharpoondown R$.
-\end{example}
-
-Functor are often used to generalize some structural behaviour that constructions in categories have.
-An important example of this fact is the universal property.
-The definition is not straightforward, but it gives the abstraction of a property that will be useful in further definitions%~\cite{Herrlich_Strecker_1979}.
-
-\begin{definition}[Universal property]\label{def:univ_prop}
-    Let $F: \cat{C \rightarrow D}$ be a functor, and let $B \in \Ob(\cat D)$.
-A pair $(u, A)$, with $A \in \Ob(\cat C)$ and $u: B \rightarrow F(A)$ is said to be an \emph{universal map for $B$ with respect to $F$} if for each $A' \in \Ob(\cat C)$ and each $f: B \rightarrow F(A')$ there exists a unique morphism $h \in \cat C(A, A')$ such that the following triangle commute:
-    \[
-        \begin{tikzcd}
-            B \arrow[r, "u"] \arrow[dr, "f" swap] & F(A) \arrow[d, dashed, "F(h)"] & A \arrow[d, dashed, "h"]\\
-            & F(A') & A'
-        \end{tikzcd}
-    \]
-
-    -- i.e. there exists a unique $h$ such that $F(h) \circ u = f$. In this case, $(u, A)$ is said to have the \emph{universal property}.
-
-    Dually, if $G: \cat C \rightarrow \cat D$ is a functor and $B \in \Ob(\cat D)$, then a pair $(A, u)$ is a \emph{co-universal map for $B$ with respect to $G$} if $u:G(A) \rightarrow B$ and for each $A' \in \Ob(\cat C)$ and each $f: G(A') \rightarrow B$ there exists a unique morphism $h \in \cat{C}(A', A)$ such that the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            A' \arrow[d, dashed, "h" swap] & G(A') \arrow[d, dashed, "G(h)" swap] \arrow[dr, "f"] \\
-            A & G(A) \arrow[r, "u" swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-Some interesting properties of certain functors depend strictly on how they behave on the homsets of the domain and the codomain categories.
-The following definitions are about this particular type of functors.
-
-\begin{definition}[Full functor, faithful functor, fully faithful functor]
-    Let $F: \cat C \rightarrow \cat D$ be a functor, and consider the inducted function
-    $$
-        F_{A, B} : {\cat C}(A, B) \rightarrow {\cat D}(F(A), F(B))
-    $$
-    If, for each $A$, $B$ objects of $\cat C$, $F_{A, B}$ is surjective, then $F$ is said to be \emph{full}, if it is injective, $F$ is said to be \emph{faithful}, if it is both injective and surjective, $F$ is said to be \emph{fully faithful}.
-\end{definition}
-
-\color{red}{
-    \begin{obs}
-        Properties such as fullness and faithfulness are so called \emph{self-dual}, because the dual notion coincide with the same notion.
-This fact can be advantageous because if for example the faithfulness implies the preservation of some property, then the dual property is implied at the same way.
-    \end{obs}
-}\color{black}
-
-\begin{example}\label{ex:full_subc_inc_fully_faith}
-    Let $\cat C$ be a category and $\cat D$ a subcategory.
-The inclusion functor $I: \cat{D \rightarrow C}$, mapping each object and each arrow onto itself.
-$I$ is a faithful functor, because, given any pair of objects $A$ and $B$ of $\cat D$, $I_{A, B}$ is injective.
-If $\cat D$ is a full subcategory, then $I$ is fully faithful.
-\end{example}
-
-Having such classification among functors turns out to be useful in many contexts.
-For example, consider $F(m): F(B) \rightarrow F(C)$ be a monomorphism in a category $\cat D$, where $F: \cat C \rightarrow \cat D$ is a faithful functor.
-Then, if $f, g: A \rightarrow B$ are two morphisms in $\cat C$ such that $m \circ f = m \circ g$, then $F(m \circ f) = F(m) \circ F(f) = F(m) \circ F(g) = F(m\circ g)$.
-Since $F(m)$ is mono, then $F(f) = F(g)$, and, since $F_{A, B}$ is injective, $f = g$.
-Together with the fact that faithfulness is a self-dual concept, we have a proof for what follows~\cite{Herrlich_Strecker_1979}.
-
-\begin{prop}
-    Let $F: \cat{C \rightarrow D}$ be a faithful functor. Then $F$ reflects monomorphisms and epimorphisms.
-\end{prop}
-
-\subsection{Natural Transformations}
-
-Given two functors that share domain and codomain categories, it is possible to define a transformation between them, taking each object of the domain of the functors to an arrow in the codomain of the functors that represent the action of ``changing the functor acting on that object''.
-
-\begin{definition}[Natural transformation]
-    Let $F,G : \cat {C \rightarrow D}$ be two functors.
-A \emph{natural transformation} $\eta$ between them, denoted $\eta: F \dot\rightarrow G$, is a function $\eta: \Ob(\cat C) \rightarrow \Hom(\cat D)$ taking each $A \in \Ob(\cat C)$ to a morphism $\eta_A:F(A) \rightarrow G(A)$ in $\cat{D}$, such that, for each morphism $f: A \rightarrow B$ of $\cat C$, the following diagram commutes:
-    \[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
-        \end{tikzcd}
-    \]
-    -- i.e., such that $G(f) \circ \eta_A = \eta_B \circ F(f)$.
-
-    We say that $\eta: F \dot\rightarrow G$ is a \emph{natural isomorphism} if, for each $A \in \Ob(\cat C) \text{, } \eta_A$ is an isomorphism in $\cat D$.
-In this case, $F$ and $G$ are said to be \emph{naturally isomorphic}, and is denoted $F \cong G$.
-\end{definition}
-
-\begin{obs}\label{obs:comp_assoc_nat_tran}
-It is easy to see that, given two natural transformations $\eta:F\dot\rightarrow G$, $\theta: G \dot\rightarrow H$, it is possible to compose them obtaining a new natural transformation $\xi = \theta \circ \eta : F \dot \rightarrow H$.
-This follows by the fact that the diagram
-\[
-        \begin{tikzcd}
-            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] 
-                & G(A) \arrow[d, "G(f)"] \arrow[r, "{\theta_A}"]
-                & H(A) \arrow[d, "H(f)"] \\
-            F(B) \arrow[r, "{\eta_B}"swap]
-                & G(B) \arrow[r, "{\theta_B}" swap]
-                & H(B)
-        \end{tikzcd}
-\]
-commutes because the two inner squares do. Sticking another diagram on the right of the one above, it is possible to show associativity of composition of natural transformations.
-\end{obs}
-
-\subsection{Functor Categories}
-
-The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
-
-\begin{definition}[Functor Category]\label{def:functor_category}
-    Let $\cat C$ and $\cat D$ be categories.
-The category whose objects are functors between $\cat C$ and $\cat D$ and whose arrows are natural transformations between them is said to be a \emph{functor category}, and it is denoted by $[\cat{C, D}]$.
-\end{definition}
-
-A functor with a small category as domain (\Cref{rem:small_cats}) and $\Set$ as codomain is said to be a \emph{presheaf} on that category.
-Given a category $\cat C$, it is possible to construct the functor category of the presheaves on $\cat C$, i.e.
-$[\cat C, \Set]$.
-
-\begin{remark}
-    What we are calling here a presheaf is not totally accurate, because technically a presheaf on a small category $\cat C$ is a functor $F: \cat C ^{op} \rightarrow \Set$.
-This technicality would bring more complexity, and it is beyond the scope of this work, so we will continue adopting the definition given above.
-\end{remark}
-
-\subsection{Comma Categories}
-
-Functor constructions allow us to generalise basic concepts already seen for categories.
-An important example of this fact are comma categories, a more general notion of slice categories (\Cref{def:slice_cat}).
-
-% \begin{definition}[Comma category]
-%     Given two functors $F: \cat{C} \rightarrow \cat{E}$, $G: \cat{D} \rightarrow \cat{E}$, the \emph{comma category $(F \downarrow G)$} is the category whose objects are triples $(A, f, B)$, with $A \in \Ob(\cat C)$, $B \in \Ob(\cat D)$ and $f \in \cat{E}(F(A), G(B))$, and whose morphisms are the pairs $(a, b) : (A, f, B) \rightarrow (C, g, D)$ where $a : A \rightarrow C$, $b: B \rightarrow D$ and such that
-%     \[
-%         \begin{tikzcd}
-%             F(A) \arrow[r, "f"] \arrow[d, "F(a)" swap] & G(B) \arrow[d, "G(b)"] \\
-%             F(C) \arrow[r, "g"] & G(B)
-%         \end{tikzcd}
-%     \]
-%     commutes; composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-% \end{definition}
-
-\begin{definition}[Comma category]\label{def:comma_category}
-    Let $\cat{C \text{, } D \text{ and } E}$ be categories, and let $S: \cat{C \rightarrow E}$, $T:\cat{D \rightarrow E}$ be functors (source and target):
-    \[
-        \begin{tikzcd}
-            \cat{C} \arrow[r, "S"] & \cat{E} & \cat{D} \arrow[l, "T" swap]
-        \end{tikzcd}
-    \]
-    Then, the \emph{comma category $(S \downarrow T)$} is the category in which: 
-    \begin{itemize}
-        \item the objects are triples $(A, f, B)$, where $A \in \Ob(\cat{C})$, $B \in \Ob(\cat D)$ and $f: S(A) \rightarrow T(B)$ is an arrow of $\cat E$;
-        \item the arrows are pairs $(c, d): (A, f, B) \rightarrow (C, g, D)$, where $c \in \Hom(\cat C)$ and $d \in \Hom(\cat D)$, such that the square below commutes;
-        \[
-            \begin{tikzcd}
-            S(A) \arrow[r, "f"] \arrow[d, "S(c)" swap] & G(B) \arrow[d, "T(d)"] \\
-            T(C) \arrow[r, "g" swap] & T(B)
-            \end{tikzcd}
-        \]
-        \item composition of morphisms is obtained via pairwise composition, i.e., $(a, b) \circ (c, d) = (a \circ c, b \circ d)$.
-    \end{itemize}
-\end{definition}
-
-Thus, the slice category $\cat C / X$ is the comma category given by the two functors $Id_{\cat C}$ (the identity functor), and the functor $!_X: \textbf{1} \rightarrow \cat C$, where $\textbf 1$ is the one-object category defined in \Cref{ex:1_cat}, and $!_X$ sends the only object of $\textbf{1}$ to $X$ (then the only morphism of $\textbf{1}$ to $id_X$ of $\cat C$):
-\[
-    \begin{tikzcd}
-        \cat C \arrow[r, "{Id_\cat C}"] & \cat C & \textbf{1} \arrow[l, "{!_X}"swap]
-    \end{tikzcd}
-\]
-It is easy to see that $(Id_\cat C \downarrow !_X)$ is exactly the same of $\cat C / X$.
-
-In the same way, it is possible to define coslice categories in terms of comma categories: the category $(!_X \downarrow Id_\cat C)$ is exactly the coslice $X / \cat C $.
-
-\subsection{Adjoints}
-
-% \begin{definition}[Adjoint Functor]\label{def:adjoint}
-%     Let $\cat C$ and $\cat D$ be categories, and let $R:\cat{C \rightarrow D}$ and $L : \cat{D \rightarrow C}$ be functors.
-$L$ is called \emph{left adjoint} of $R$ if there exists a natural transformation $\eta: Id_{\cat C} \dot\rightarrow (L \circ R)$ such that, for each object $A$ and each arrow $f: A \rightarrow L(B)$ of $\cat C$, there exists a unique arrow $g: R(A) \rightarrow B$ of $\cat D$ such that the following diagrams commutes:
-%     \[
-%         \begin{tikzcd}
-%             A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & L(R(A)) \arrow[d, dashed, "L(g)"] \\
-%             & L(B)
-%         \end{tikzcd}
-%     \] -- i.e., if $L(g) \circ \eta_{A} = f$. In this case $\eta$ is called the \emph{unit} of the adjoint.
-
-%     Analogously, $R$ is called \emph{right adjoint} of $L$ provided that there exists a natural transformation $\epsilon : (R \circ L) \dot\rightarrow Id_{\cat D}$ such that, for each arrow $g: R(A) \rightarrow B$ of $\cat D$ there exists a unique arrow $f: A \rightarrow L(B)$ of $\cat C$ such that the following diagram commutes:
-%     \[
-%         \begin{tikzcd}
-%             R(L(B)) \arrow[r, "{\epsilon_{B}}"] & B \\
-%             R(A) \arrow[u, dashed, "R(f)"] \arrow[ur, "g"swap] 
-%         \end{tikzcd}
-%     \] -- i.e., $\epsilon_{B} \circ R(f) = g$. In this case, $\epsilon$ is called \emph{co-unit} of the adjoint.
-% \end{definition}
-%\todo{sistemare la definizione}
-
-\begin{definition}[Right Adjoint]\label{def:right_adjoint}
-    Let $R: \cat{C \rightarrow D}$ be a functor.
-$R$ is said \emph{right adjoint} if, for each object $A$ of $\cat D$, there exists an object $L(A)$ and an arrow $\eta_A:A \rightarrow R(L(A))$ in $\cat C$ such that, for each arrow $f: A \rightarrow R(B)$ of $\cat D$, there is a unique arrow $g:L(A) \rightarrow B$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            A \arrow[r, "{\eta_A}"] \arrow[dr, "f" swap] & R(L(A)) \arrow[d, dashed, "R(g)"] \\
-            & R(B)
-        \end{tikzcd}
-    \]
-    --i.e., $R(g) \circ \eta_A = f$.
-\end{definition}
-
-\begin{prop}\label{prop:ext_left_to_funct}
-    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
-Moreover, there exists a natural transformation $id_{\cat{D}}\to R\circ L$.
-\end{prop}
-\begin{proof}
-    % Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
-    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}.
-Given $f\colon X \rightarrow Y$, we can define $L(f)$ as the unique arrow  $L(X) \rightarrow L(Y)$ whose image through $R$ fits in the diagram below.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "f" swap] & R(L(X)) \arrow[d, dashed, "R(L(f))"] \\
-    	Y\arrow[r, "\eta_Y" swap]& R(L(Y))
-    \end{tikzcd}
-    \]
-
-    To see that in this way we get a functor it is now enough to notice the commutativity of the following diagrams.
-    \[
-    \begin{tikzcd}
-    	X \arrow[r, "{\eta_X}"] \arrow[d, "{id_X}" swap] & R(L(X)) \arrow[d, "{R(id_{L(X)})}"]   \\
-    	Y\arrow[r, "{\eta_Y}" swap] & R(L(Y))
-    \end{tikzcd}
-    \]    \[
-    \begin{tikzcd}
-    	   X \arrow[d, "{\eta_X}" swap]  \arrow[r, "{f}"]& Y \arrow[d, "{\eta_Y}" swap] \arrow[r, "{g}"]& Z\arrow[d, "{\eta_Z}"]\\
-    	R(L(X))  \arrow[r, "{R(L(f))}" swap] & R(L(Y)) \arrow[r, "{R(L(g))}" swap] & R(L(Z))
-    \end{tikzcd}
-    \]
-
-    Finally, by construction the family given by all the $\eta_A\colon A\to R(L(A))$ is natural and we can conclude. 
-\end{proof}
-
-\begin{remark}
-    The family above mentioned is called \emph{unit} of the adjunction.
-\end{remark}
-
-\begin{definition}[Left Adjoint]\label{def:left_adjoint}
-    Let $L: \cat{D \rightarrow C}$ be a functor.
-$L$ is a \emph{left adjoint} if, for each object $B$ of $\cat C$, there exists an object $R(B)$ and an arrow $\epsilon_B : L(R(B)) \rightarrow B$ in $\cat D$ such that, for each arrow $g: L(A) \rightarrow B$ of $\cat C$, there exists a unique arrow $f:A \rightarrow R(B)$ such that the following diagram commutes.
-    \[
-        \begin{tikzcd}
-            L(R(B)) \arrow[r, "{\epsilon_B}"] & B \\
-            L(A) \arrow[u, dashed, "L(f)"] \arrow[ur, "g"swap]
-        \end{tikzcd}
-    \]
-    -- i.e., $\epsilon_B \circ L(f) = g$.
-\end{definition}
-
-As we have shown before, it is possible to extend the mapping $A \rightarrow R(B)$ to a functor $R$, whose functoriality follows placing $\epsilon_X \circ L(R(f)) = f \circ \epsilon_Y$ for each $f: X \rightarrow Y$.
-The family $\epsilon_B : L(R(B)) \rightarrow B$ is natural and it is called \emph{counit} of the adjunction.
-
-The connection between left and right adjoints is expressed in the following proposition.
-
-\begin{prop}
-    Let $L$ be the functor of \Cref{prop:ext_left_to_funct}. Then, $L$ is a left adjoint.
-\end{prop}
-
-\begin{proof}
-	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
-	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
-	    \[
-	\begin{tikzcd}
-		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
-		& R(B)
-	\end{tikzcd}
-	\]
-
-	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
-	\begin{align*}
-		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
-	\end{align*}
-	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
- \end{proof}
-
-% Il concetto di functore aggiunto è molto più complesso di come viene presentato qui.
-In questo lavoro, avere una definizione di funtore aggiunto serve soltanto per una certa proprietà che verrà presentata nel capitolo sui limiti.
-\input{Limit}
-\section{Adhesivity}\label{sect:adh}
-
-The next section is about adhesivity.
-An adhesive category is intuitively a category in which pushouts of (some) monomorphisms exist and they behave more or less as they do among sets.
-
-\begin{definition}(Van Kampen property)
-    Let $\mathcal A$ be a subclass of $\Hom(\cat C)$, and consider the diagram below:
-    % \[
-    % \begin{tikzcd}
-    %     A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"] \\
-    %     C \arrow[r, "g" swap]                & D
-    % \end{tikzcd}
-    % \]
-    \[
-    \begin{tikzcd}[row sep = scriptsize]
-        A' \arrow[ddd, "m'"swap] \arrow[rrr, "f'"] \arrow[dr, "a"swap] & & & B \arrow[ddd, "n'"] \arrow[dl, "b"] \\
-        & A \arrow[r, "f"] \arrow[d, "m" swap] & B \arrow[d, "n"]   & \\
-        & C \arrow[r, "g" swap]                & D                  & \\
-        C' \arrow[rrr, "g'"swap] \arrow[ur, "c"] & & & D' \arrow[ul, "d" swap] 
-    \end{tikzcd}
-    \]
-    we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
-    \begin{itemize}
-        \item it is a pushout;
-        \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
-    \end{itemize}
-\end{definition}
-
-We are now ready to give the notion of $\mathcal M$-adhesivity. % CITE: https://web3.arxiv.org/pdf/2407.06181
-
-\begin{definition}[$\mathcal{M}$-adhesivity]\label{def:adh}
-    Let $\cat C$ be a category and $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts (\Cref{def:stab_under_pb_po}).
-    Then $\cat C$ is \emph{$\mathcal M$-adhesive} if
-    \begin{enumerate}
-        \item every cospan $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ can be completed to a pullback (such pullbacks are called $\mathcal M$-pullbacks);
-        \item every span $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ can be completed to a pushout (such pushouts are called $\mathcal M$-pushouts);
-        \item pushouts along $\mathcal M$-arrows are $\mathcal M$-Van Kampen squares.
-    \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\end{definition}
-
-\begin{obs}
-    $\Set$ is adhesive.
-    % It is easy to check the first two points of the \Cref{def:adh} while for the Van Kampen property of pushouts along monos [...]
-\end{obs}
-
-Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.
-
-\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
-    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\end{prop}
-
-Verifying $\mathcal M$-adhesivity using the definition above may turn out to be very complex, so we can make use of the following result~\cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
-
-\begin{theorem}\label{th:crit_for_adh}
-    Let $\cat C$ be a category, $\mathcal M \subseteq \Mono(\cat C)$ containing all isomorphisms, closed under composition and stable under pullbacks and pushouts.
-Let now $F: \cat{C \rightarrow D}$ be a functor with $\cat D$ $\mathcal{N}$-adhesive for some $\mathcal{N} \subseteq \Mono(\cat D)$.
-    If $F$ is such that $F(\mathcal{M}) \subseteq \mathcal N$ and creates pullbacks and $\mathcal{M}$-pushout, then $\cat C$ is $\mathcal M$-adhesive.
-\end{theorem}
-
-The idea behind this theorem is to simplify calculations to show that a certain category is adhesive for some subclass of monomorphisms, considering a functor from the category of which we want to prove adhesivity to a category we know it is adhesive, requiring that such functor has some properties.
-
-\begin{proof}
-    In order to prove $\mathcal M$-adhesivity of $\cat C$, we have to verify the condition in \Cref{def:adh}.
-    \begin{itemize}
-        \item Let $C \xrightarrow[]{g} D \xleftarrow[]{m} B$ with $m \in \mathcal M$ be a cospan in $\cat C$.
-Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
-Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.
-        \item Let $C \xleftarrow{m} A \xrightarrow{f} B$ with $ m \in \mathcal M$ be a cospan in $\cat C$.
-Analogously to the previous point, applying the functor $F$ we obtain $F(C) \xleftarrow{F(m)} F(A) \xrightarrow{F(f)} F(B)$ with $ F(m) \in \mathcal N$, and there exists a $\mathcal N$-pushout $(q_{F(C)}, q_{F(B)}, F(Q))$ in $\cat D$.
-Since $F$ reflects pushouts, $(q_C, q_B, Q)$ is a $\mathcal{M}$-pushout in $\cat C$.
-        \item the Van Kampen property of $\mathcal M$-pullbacks follows from the closure under pullbacks and pushouts of $\mathcal M$ and from the fact that $F$ reflects pullbacks.
-    \end{itemize}
-
-\end{proof}
-
-{% \color{red}{ [DC]Alcuni commenti su questo capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
+{% \color{red}{ [DC]Alcuni commenti su PRIMO capitolo. Non sono soddisfatto dall'ordine della presentazione. Io  personalmente proporrei il seguente indice:
 
@@
 % Unica osservazione che ho per ora è che terrei il cubo invece del diagramma che hai fatto}
-% \color{black}
 }
-
-\chapter{Categories of Graphs}
-This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
-
-\section{Set-Theoretic Definitions of Graphs}
-
-First obvious definitions of graph are given via sets and set-theoretic tools, remarking what intuitively graphs are. We present in this section a few classes of graphs.
-
-\subsection{Graphs}
-
-\begin{definition}[Graph]
-    A \emph{graph} $G$ is a tuple $(V, E, s, t)$, where $V$ and $E$ are sets (respectively, the set of vertices, or nodes, and the set of edges, or arcs), and $s, t: E \rightarrow V$ are two functions (respectively, the source and the target of an edge).
-    In general, given a graph $G$, we write $V(G)$ to denote the set of vertices and $E(G)$ the set of edges of $G$.
-\end{definition}
-
-\begin{definition}[Graph Homomorphism]\label{def:graph_hom}
-    Given two graphs $G=(V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, a \emph{graph homomorphism} $h: G \rightarrow H$ is a pair of functions $h = (h_V: V_G \rightarrow V_H, h_E: E_G \rightarrow E_H)$ such that
-    \[
-        h_V \circ s_G = s_H \circ h_E
-    \]
-    and
-    \[
-        h_V \circ t_G = t_H \circ h_E
-    \]
-    that is, a structure preserving map.
-    Given two graph homomorphisms $h = (h_V, h_E): G \rightarrow H$, $k = (k_V, k_E): H \rightarrow I$, the homomorphism $ k \circ h = (k_V \circ h_V, k_E \circ h_E): G \rightarrow I$ is the \emph{composite} of $h$ and $k$.
-\end{definition}
-
-Graphs together with graph homomorphisms from a category.
-
-\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
-    $\mathbf{Graph}$ is the category in which objects are graphs and arrows are graph homomorphisms.
-\end{definition}
-
-All the constructions defined in \Cref{sect:limits_univ_constr} exists in $\mathbf{Graph}$, and they are very similar to construction in $\Set$, intuitively because of the set-theoretic nature of graphs.
-The next examples try to make this point clear.
-
-\begin{example}\label{ex:in_term_in_graph}
-    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
-The initial object instead is the graph with exactly one node and a single edge from that node to itself.
-\end{example}
-
-\begin{example}
-    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
-\end{example}
-
-\begin{example}
-    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
-Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
-\end{example}
-
-\subsection{Graph with Equivalences}
-
-It is possible to endow the set of vertices of a graph with any sort of relation, requiring that such relation is preserved by homomorphisms.
-The ones we are interested in are \emph{equivalence relations}.
-%Recall that an equivalence relation $R$ over a set $A$, $R \subseteq A\times A$, is a relation that is \emph{reflexive} ($\forall a \in A, aRa$), \emph{transitive} ($\forall a, b, c \in A, aRb \text{ and } bRc \Rightarrow aRc$) and \emph{symmetric} ($\forall a, b \in A, aRb \Rightarrow bRa$).
-A graph with equivalence is a graph with an equivalence relation defined over its set of vertices.
-
-\begin{definition}[Graph with Equivalence~\cite{concur2006}]
-    A \emph{graph with equivalence} is a pair $\eqgraph{G} = (G, \sim_G)$ where $G$ is a graph and $\sim_G \subseteq V(G)\times V(G)$ is an equivalence relation over its set of nodes.
-An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (G, \sim_G)\rightarrow \eqgraph{H} = (H, \sim_H)$ is a graph homomorphism $h = (h_V, h_E):G \rightarrow H$ such that if $v_1 \sim_G v_2$ then $h_V(v_1) \sim_H h_V(v_2)$.
-Graphs with equivalences together with their homomorphism from a category, denoted $\mathbf{EqGrph}$.
-\end{definition}
-
-\begin{remark}\label{rem:eq_as_surj}
-    It is possible to define an equivalence relation $\sim \ \subseteq S\times S$ as a surjective function mapping each $s \in S$ to a partition of $S$ in which each element is equivalent according to $\sim$, that is, its \emph{equivalence class}.
-Formally, an equivalence relation $\sim \ \subseteq S\times S$ is fully described by a function $f_\sim : S \rightarrow \{[s]_\sim \mid s \in S \}$, where $[s]_\sim = \{t \in S \mid t \sim s\}$, defined by $f_{\sim}(s) = [s]_\sim$.
-\end{remark}
-
-\begin{obs}
-    $\mathbf{Graph}$, defined in \Cref{def:cat_of_graph} is equivalent to the full subcategory of $\mathbf{EqGrph}$ where objects are graphs $(G, =)$, i.e., in which each node is equivalent only to itself.
-\end{obs}
-
-%TODO: RIGUARDARE QUESTA PARTE!!!
-
-In the category of graphs with equivalences, universal constructions are easy to obtain. 
-\begin{prop}\label{prop:limits_in_EqGrph}
-    Let $D: \cat I \rightarrow \mathbf{EqGrph}$ be a diagram.
-Then, a limit for $D$ is $(\eqgraph{L}, l^i)_{i\in \Ob(\cat I)}$ with in which $\eqgraph{L} = (\mathcal{L}, \sim_{\mathcal{L}})$ is a graph in which (in $\Set$):
-    \begin{itemize}
-        \item $(V_{\mathcal{L}}, l^i_{V})$ is the limit of all the $V_{D(i)}$;
-        \item $(E_{\mathcal{L}}, l^i_{E})$ is the limit of all the $E_{D(i)}$.
-    \end{itemize}
-    And the equivalence relation on nodes is the least equivalence relation $\sim_{\mathcal{L}}$ such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$m then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-(Here $\sim_i$ denotes the equivalence relation of $D(i)$).
-\end{prop}
-
-\begin{proof}
-
-    \color{red}{
-    Firstly, we show that $(\eqgraph{L}, l^i)_{\cat I}$ is a cone.
-Let $D(\alpha) : D(i) \rightarrow D(j)$, with $\alpha: i \rightarrow j$ morphism in $\cat I$.
-Our claim is $D(\alpha) \circ l^i = l^j$.
-Hence,
-    \begin{align*}
-        D(\alpha) \circ l^i &= (h_V, h_E) \circ (l^i_V, l^i_E)      \\
-                            &= (h_V \circ l^i_V, h_E \circ l^i_E)   \\
-                            &= (l^j_V, l^j_E)                       \\
-                            &= l^j                              
-    \end{align*}
-    For $(\eqgraph{L}, l^i)_{\cat I}$ to be a cone, the only constraint on the equivalence relation $\sim_{\mathcal{L}}$ is to be such that graph homomorphisms above can preserve it.
-But such equivalence relation exists in every case, considering the identity.
-This led us to the second point of the proof, that is, the universal property.
-    % L'idea qui è di prendere la relazione di equivalenza tale che il grafo limite abbia la proprietà universale.
-    For the cone described above to be a limit must be valid the universal property.
-Such condition is is satisfied taking the least equivalence relation such that, given two vertices $v$ and $w$ of $\eqgraph{L}$, if $v\sim_{\mathcal{L}}w$ then $l^i_V(v) \sim_i l^i_V(w)$ for each $i\in \Ob(\cat I)$.
-Suppose the following situation:
-    \[
-        \begin{tikzcd}
-            & \eqgraph{L}'  \arrow[d, "h"] \arrow[ddl, bend right=30, "{q^i}"swap] \arrow[ddr, bend left=30, "{q^j}"] & \\
-            & \eqgraph{L} \arrow[dl, "{l^i}"swap] \arrow[dr, "{l^j}"] & \\
-            D(i) \arrow[rr, "{D(\alpha)}"]& &  D(j)
-        \end{tikzcd}
-    \]
-    The universal property the follows from the definition of least equivalence relation.
-    } \color{black}
-\end{proof}
-
- \todo{riscrivere questa parte come esempi che derivano dalla proposizione precedente}
-The terminal object in $\mathbf{EqGrph}$ is the graph with only one node, only one edge and with the single node equivalent only to itself, while the initial object is the graph with no nodes and no edges.
-Given two graphs with equivalences $\eqgraph{G} = (G, \sim_G) $ and $\eqgraph{H} = (H, \sim_{H})$, one can construct the product graph $\eqgraph{G \times H} = (G \times H, \sim_{G \times H})$, together with the two projections $\pi_G$ and $\pi_H$,  where $\sim_{G \times H}$ is the least equivalence relation on $G \times H$ such that, if $w_1$ and $w_2$ are nodes of $\eqgraph{G \times H}$, we have $w_1 \sim_{G \times H} w_2$ if $\pi_G(w_1) \sim_G \pi_G(w_2)$ and $\pi_H(w_1) \sim_H \pi_H(w_2)$.
-An equalizer in $\mathbf{EqGrph}$ for a pair of morphisms $f, g: \eqgraph{G \rightarrow H}$ is exactly the same as in $\mathbf{Graph}$, namely, $(\eqgraph{E} = (E, \sim_E), e)$, where $E$ is the greatest subgraph of the underlying graph of $\eqgraph{G}$ on which $f$ and $g$ are equal, together with the inclusion $e: \eqgraph{E \rightarrow G}$.
-The equivalence relation is preserved ($\sim_E$ is $\sim_G$ restricted to the set of vertices of $E$).
-
-Previous examples show that the category $\mathbf{EqGrph}$ has both (co)equalizers and finite (co)products, so, by \Cref{th:limit}, we can conclude that $\mathbf{EqGrph}$ has finite limits and colimits.
-
-An important characterization in the category of graphs with equivalences is the following. \todo{questo deriva da 2.1.11}
-
-\begin{prop}\label{prop:reg_mono_in_EG_are_mono_in_graph}
-    In $\mathbf{EqGrph}$, a monomorphism is regular if it reflects equivalences.
-That is, if $h: \eqgraph{G \rightarrow H}$ is mono and such that $h_V (v_1) \sim_H h_V(v_2) \Rightarrow v_1 \sim_G v_2$, then $h$ is regular mono.
-\end{prop}
-
-\section{Graphs as Functors}
-
-\todo{non ha senso avere questa parte come sezione: "graph as functors"  ha
- senso come remark separato e la restante parte della sezione si salda a quella precedente}
-
-Set-theoretical definitions of graphs are straightforward, but a further level of abstraction allows us to highlight some interesting properties of these objects.
-We can indeed consider a graph as a functor from a category of ``primitive objects'' (e.g., the object representing edges and the object representing vertices) onto a category which provides a representation of them.
-This concept is perfectly represented by categories of presheaves, where an object is nothing more than a way to interpret objects of a category as sets.
-An example will make clear what we are talking about.
-
-Considering the category of graphs (as defined in \Cref{def:cat_of_graph}), it is possible to show that 
-$$\mathbf{Graph} \cong [E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
-where an object $G$ is a functor, having $G(V)$ as the set of vertices, $G(E)$ as the set of edges, $G(s)$ and $G(t)$ as the source and target functions.
-A morphisms $\eta: G \dot\rightarrow H$ is a natural transformation, and the commutativity of the diagram below is given by the definition of graph morphisms (\Cref{def:graph_hom})
-$$
-    \begin{tikzcd}
-        G(E) \arrow[r, "{\eta_E}"] \arrow[d, "G(s)"swap] & H(E) \arrow[d, "H(s)"] \\
-        G(V) \arrow[r, "{\eta_V}"swap] & H(V)
-    \end{tikzcd}
-$$
-(and the same for $t$).
-
-\Cref{ex:in_term_in_graph} and following, in which limits and colimits are computed pointwise, are a concrete instance of \Cref{obs:limits_in_presh}.
-
-Graphs with equivalence are more complex objects.
-We can think of $\mathbf{EqGrph}$ as a subcategory of the category $[E \rightrightarrows V \rightarrow Q, \Set]$, in which each object $\eqgraph{G}$ is a functor mapping the arrow $q: V \rightarrow Q$ onto an epimorphism (i.e., a surjective function).
-The component $\eqgraph{G}(q)$ here is intended to be the function discussed in \Cref{rem:eq_as_surj}.
-In the following, we will refer with $\mathbf{Graph}$ and $\mathbf{EqGrph}$ to the category of presheaves we have just introduced.
-
-% Graphs with equivalences are an alternative representation of \emph{quotient graphs} over an equivalence relation.
-The graph with equivalence $\eqgraph{G} = (G, \sim_G)$ is another representation of the graph $G/_{\sim_G}$.
-Such graph is called \emph{quotient graph}, and it can be expressed by the action of a functor over a graph with equivalence.
-Such functor is defined as follow.
-
-\begin{definition}[Quotient Functor]\label{def:quot_func}
-    The \emph{quotient functor} $Q: \mathbf{EqGrph} \rightarrow \mathbf{Graph}$ is defined as follows:
-    \begin{itemize}
-        \item on objects, given $\eqgraph{G}=(G, \sim_{G})$ as $Q(\eqgraph{G}) = G/_{\sim_G} = (V/_{\sim_G}, E, s', t')$, where $s'(e) = [v]_{\sim_G}$ if $s(e) = v$, and $t'(e) = [v]_{\sim_G}$ if $t(e) = v$;
-        \item on morphisms, given $h = (h_V, h_E): \eqgraph{G \rightarrow H}$, as $Q(h_V)([v]_{\sim_G}) = [h_V(v)]_{\sim_H}$, and $Q(h_E) = h_E$.
-    \end{itemize}
-\end{definition}
-
-We now give some considerations on quotient functor.
-
-\begin{prop}
-    Quotient functor has a left adjoint and a right adjoint.
-\end{prop}
-
-\begin{proof}
-    To prove the statement we just have to find the adjoints. 
-    %A good candidate to be the left adjoint is the functor $I: \mathbf{Graph \rightarrow EqGrph}$, which sends each graph $G$ to $\eqgraph{G} = (G, =_G)$ (the graph in which each node is equivalent only to itself).
-To see that this functor is the adjoint we were looking for, we can apply the definition of left adjoint.
-The unit of the adjunction $\eta: Id_{\mathbf{EqGrph}} \dot\rightarrow I \circ Q$ is the one mapping $\eqgraph{G} = (G, \sim_G)$ onto $(G/_{\sim_G}, =)$,  and, given a morphism $f: \eqgraph{G} \rightarrow I(\eqgraph{H})$ in $\mathbf{EqGrph}$, we can find only one arrow $h$ in $\mathbf{Graph}$ such that $I(h) \circ \eta_{G} = f$.
-    % In particular, $I(\eqgraph{H})$ is a graph with equivalence which maps the morphism $q:V\rightarrow Q$ onto the identity $id_V: V \rightarrow V$, hence a morphism from $\eqgraph{G}$ to $\eqgraph{H}$ is a natural transformation $f = (f_E, f_V, f_Q = f_V)$.
-Then, the arrow $I(h): I(Q(\eqgraph{G})) \rightarrow I(\eqgraph{H})$ is given by $I(h_V, h_E) = (f_V, f_E, f_V)$.
-
-     Let $I: \mathbf{Graph \rightarrow EqGrph}$ be the functor \todo{il punto è che NON sai che I è un funtore.
-Quello che devi fare è mostrare che epsilon ha la proprietà di una counità, DOPO deduci che I è un funtore} that sends each graph $\mathcal{G}$ onto the graph with equivalence $(\mathcal{G}, =_{\mathcal{G}})$, where $=_{\mathcal G}$ is the identity relation.
-    Consider the following situation:
-    \[
-        \begin{tikzcd}
-            (Q \circ I)(\mathcal{G}) = \mathcal{G}/_{=_{\mathcal{G}}}
-            \arrow[r, "{\epsilon_{\mathcal{G}}}"] 
-            & \mathcal{G} \\
-            {I(\mathcal{H}) = (\mathcal{H}, =_{\mathcal{H}})}
-            \arrow[u, dashed, "I(f)"] 
-            \arrow[ur, "g"swap] 
-        \end{tikzcd}
-    \]
-    The graph $\mathcal G/_{=_{\mathcal{G}}}$ is exactly the graph $\mathcal G$, hence the arrow $\epsilon_\mathcal{G}$ is the identity arrow $id_\mathcal{G}$, so the arrow $I(f)$ is uniquely determined by $g$, having $\epsilon_{\mathcal{G}} \circ I(f) = I(f) = g$.
-Therefore, $\epsilon: (Q \circ I) \rightarrow Id_{\mathbf{Graph}}$ is the counit of the adjunction, and $I$ is a left adjoint.
-
-    A right adjoint of $Q$ is the functor $T: \mathbf{Graph \rightarrow EqGrph}$
-    \todo{stesso problema di prima.
-Io riscriverei anche questa metà perché non si capisce la notazione e ad un certo punto occorre usare le proprietà dei quozienti in Set, cosa che non è evidente.
-UPDATE: probabilmente questo non è nu funtore aggiunto}
-    such that, for each graph $\mathcal{G}$ of $\mathbf{Graph}$, $T(\mathcal{G}) = (\mathcal{G}, \approx_{\mathcal{G}})$, where $\approx_{\mathcal{G}}$ is the total relation among vertices of $\mathcal{G}$.
-We have then the following situation:
-    \[
-        \begin{tikzcd}
-            \eqgraph{G} = (\mathcal{G}, \sim_{\mathcal{G}}) \arrow[r, "{\eta_{\eqgraph{G}}}"] \arrow[dr, "f"swap] & (T \circ Q)(\eqgraph{G}) = (\mathcal{G}/_{\sim_{\mathcal{G}}}, \approx_{\mathcal{G}/_{\sim_{\mathcal{G}}}}) \arrow[d, dashed, "h"] \\
-            & T(\mathcal{H}) = \eqgraph{H}
-        \end{tikzcd}
-    \]
-    Since $\eqgraph{H}$ is in the image of $T$, it is a graph with all equivalent nodes.
-Then, the morphism $f$ is a graph morphism that in addition sends each equivalence class of vertices onto the unique class in the graph $\eqgraph{H}$.
-Then, $f$ factors uniquely as $h \circ \eta_\eqgraph{G}$, and $h$ is a graph morphism extended to a morphism in $\mathbf{EqGrph}$ by sending the unique equivalence class on $(T \circ Q)(\eqgraph{G})$ onto the unique equivalence class in $\eqgraph{H}$, and $\eta: Id_{\mathbf{EqGrph}} \rightarrow (T \circ Q)$ is the unit of the adjunction.
-\end{proof}
-
-The following result lies on \Cref{th:adjoints_preserves_lim} and its dual.
-
-\begin{cor}\label{cor:quot_preserves_co_lim}
-    Quotient functor preserves limits and colimits. 
-\end{cor}
-
-\color{red}{
-
-% \begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
-%     Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
-% \end{lemma}
-
-% \begin{proof}
-%     Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
-%     \[
-%         \begin{tikzcd}
-%             G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
-%             G_2 \arrow[r, "j" swap] & P
-%         \end{tikzcd}
-%     \]
-%     In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise, we have the following situation in the codomain category of the presheaves:
-%     \[
-%         \begin{tikzcd}
-%             G(Q) \arrow[r, "{m_Q}"] \arrow[d, "n_{Q}" swap] & G_1(Q) \arrow[d, "i_{Q}"] \\
-%             G_2(Q) \arrow[r, "j_{Q}" swap] & P(Q)
-%         \end{tikzcd}
-%     \]
-%     From \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, the fact that $m$ is regular mono (i.e., $m=(m_E, m_V, m_Q)$ is mono on each component) implies that $j = (j_E, j_V, j_Q)$ is mono on each component, hence a regular mono in $\mathbf{EqGrph}$.
-
-%     %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q).
-Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
-% \end{proof}
-
-\begin{lemma}\label{lemma:quot_pres_reg_mono_pushouts}
-    Quotient functor preserves pushouts along regular monomorphisms.
-\end{lemma}
-\todo{Capire qui!}
-
-}\color{black}
-\todo[color=green!40]{
-COSE DA FARE
->Quoziente crea i limiti (questo dovrebbe derivare direttamente dalla sezione precedente ) 
->Quoziente crea certi pushout (questo va fatto ex novo)
-}
-% Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}).
-Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}).
-Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.
-
-\begin{lemma}\label{lemma:eqgrph_stab_po_pb}
-    In $\mathbf{EqGrph}$,  $\Reg(\mathbf{EqGrph})$ is stable under pushouts and pullbacks (in the sense of \Cref{def:stab_under_pb_po}).
-\end{lemma}
-
-% Q crea pullback, Q crea pushout sui reg mono.
-
-\begin{lemma}
-    The quotient functor creates pullbacks.
-\end{lemma}
-
-\begin{proof}
-    We will show now that $Q$ reflects pullbacks.
-    Consider the following diagram in $\mathbf{Graph}$
-    \[
-        \begin{tikzcd}
-            & Q(\eqgraph{G}) \arrow[d, "Q(f)"] \\
-            Q(\eqgraph{H}) \arrow[r, "Q(g)"swap] & Q(\eqgraph{K})
-        \end{tikzcd}
-    \]
-    and let $(\mathcal P, p_{Q(f)}, p_{Q(g)})$ be the pullback.
-We want to show that, if  $(\eqgraph{P}, p_f, p_g)$ is the pullback of the arrows $f$ and $g$ in $\mathbf{EqGrph}$, then $Q(\eqgraph{P}) = \mathcal{P}$, $Q(p_f) = p_{Q(f)}$ and $Q(p_g) = p_{Q(g)}$.
-But, since $Q$ preserves limits, $Q(\eqgraph{P}) = \mathcal{P}$ (and so the arrows).
-    Hence, from \Cref{cor:quot_preserves_co_lim}, we can conclude that $Q$ creates pullbacks.
-\end{proof}
-
-\begin{lemma}
-    The quotient functor creates pushouts along regular monomorphism.
-\end{lemma}
-
-% \begin{proof}
-%     Consider the following situation
-% \end{proof}
-
-\begin{theorem}
-    $\mathbf{EqGrph}$ is quasiadhesive.
-\end{theorem}
-
-\begin{proof}
-    In order to apply \Cref{th:crit_for_adh}, we can consider the quotient functor defined in \Cref{def:quot_func} $Q: \mathbf{EqGrph \rightarrow Graph}$.
-We note that $Q$ creates limits, and that regular monos in $\mathbf{EqGrph}$ are mapped onto monos in $\mathbf{Graph}$.
-In addition to \Cref{lemma:eqgrph_stab_po_pb}, we can conclude that $\mathbf{EqGrph}$ is $\Reg(\mathbf{EqGrph})$-adhesive.
-\end{proof}
-
-\section{E-Graphs}\label{sect:eggs}
-
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
-
-E-Graphs are a particular type of graphs with equivalences, in which holds that
-$$
-    \frac{s(e) \sim s(e')}{t(e) \sim t(e')}
-$$
-for each pair of edges $e$, $e'$ of $\eqgraph{G} = (G, \sim)$.
-In a more general case, considering a graph with equivalence as a functor $\eqgraph{G} : (E \rightrightarrows V \rightarrow Q) \rightarrow \Set$, the inference rule above rewrites as
-\[
-    \frac{\eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e')}{\eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e')}
-\] for each $e$, $e' \in \eqgraph{G}(E)$.
-But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
-Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
-To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
-
-Since both $S$ and $T$ are subobjects of $\eqgraph{G}(E) \times \eqgraph{G}(E)$, we can make use of the \Cref{prop:fact_of_subobjects_is_unique}.
-Specifically, we want, in the following situation, $i$ to be mono and unique.
-\[
-    \begin{tikzcd}
-        S \arrow[rr, "i"] \arrow[dr, "{\langle p_1, p_2 \rangle}"swap] & & T \arrow[dl, "{\langle q_1, q_2\rangle}"] \\
-        & \eqgraph{G}(E) \times \eqgraph{G}(E)
-    \end{tikzcd}
-\]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
-From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
-The uniqueness follows from \Cref{prop:fact_of_subobjects_is_unique}.
-If such $i$ exists, then $\eqgraph{G}$ is an e-graph.
-
-\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
-\end{definition}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a fully and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}
-
-% ----------------- Appendix ------------------ %
-\appendix
-
-\chapter{Omitted Proofs}
-
-\paragraph{\Cref{th:limit}.}
- Let $\cat C$ be a category. Then $\cat C$ has all finite limits if and only if $\cat C$ has all finite products and all equalizers.
-\begin{proof}
-    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
-
-    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
-
-    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
-    \begin{enumerate}
-        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
-        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
-    \end{enumerate}
-
-    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
-    Let now:
-    \[
-        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
-    \]
-    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
-    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
-
-    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
-
-    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
-    \begin{align*}
-        D(\alpha) \circ p_i 
-            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
-            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
-            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
-            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
-            &= p_j                                  && \textit{Definition of $p_j$} \\
-    \end{align*}
-
-    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
-By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
-For each arrow $\alpha: i \rightarrow j$, we have:
-    \begin{align*}
-            \gamma_\alpha \circ q 
-                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
-                &= q_j                          && \textit{Definition of $q_j$} \\
-                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
-                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
-                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
-    \end{align*}
-    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
-Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
-\end{proof}
-
-% ---------------- Bibliography ---------------- %
-\bibliographystyle{alpha}
-\bibliography{bibliography}
-
-\end{document}

### 2024-10-21 Article/Graph_sections/Eq_Graphs.tex
hints

@@
+\color{blue}
+
+\section{Graphs with equivalences - notes and results}
+\begin{definition}
+	A \emph{graph with equivalence} is a 6-uple $(A, B, C, s, t, q)$ where $A, B$ and $C$ are set, $s,t\colon A\rightrightarrows B$ are functions and $q\colon B\to C$ is another surjective function.
+
+	A morphism  $(A, B, C, s, t, q)\to (A', B', C', s', t', q')$ is a triple $(h_1, h_2, h_3)$ of functions $h_1\colon A\to A'$, $h_2\colon B\to B'$ and $h_3\colon C\to C'$ making the following diagrams commute.
+
+	\[\xymatrix{A \ar[r]^{s} \ar[d]_{h_1} & B \ar[d]^{h_2} & A \ar[r]^{s} \ar[d]_{h_1}& B \ar[d]^{h_2} & B \ar[d]_{h_2} \ar[r]^{q} & C \ar[d]^{h_3}\\A' \ar[r]_{s'} & B' & A ' \ar[r]_{t'}& B' & B' \ar[r]_{q'} & C'}\]
+
+	In this way we get a category $\EqGrph$.
+\end{definition}
+
+\begin{remark}\label{rem:fedele}
+	There is a faithful functor $U\colon \EqGrph\to \Graph$, forgetting the quotient part. \todo{Questo è per te da dimostrare.}
+\end{remark}
+
+\begin{prop}\label{prop:limits}
+	$\EqGrph$ is complete, cocomplete and $U$ preserves limits and colimits.
+\end{prop}
+
+\begin{proof}
+	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$ we define\todo{WARNING: \emph{non} è immediatamente ovvio come si fa a  generalizzare questo passaggio ad altre categorie diverse da quella degli insiemi - serve almeno completezza e presenza dei coequalizzatori.} an equivalence relation on $B$ putting
+	\[b\sim b' \iff q_i(p_{2, i}(b))=q_i(p_{2, i}(b')) \text{ for every $i\in \cat{I}$}\]
+
+	Let $q\colon B\to Q$ be the resulting quotient map.
+By definition, for every $i\in \cat{I}$, if $b\sim b'$ we have	 $q_i\circ p_{2,i}(b)=q_i\circ p_{2,i}(b')$, yielding a unique $p_{3,i}\colon Q\to Q_i$ fitting in the square below.
+
+\[\xymatrix{ B \ar[d]_{p_{2,i}} \ar[r]^{q} & Q \ar@{.>}[d]^{p_{3,i}}\\ B_i \ar[r]_{q_i} & Q_i}\]
+
+	We have to show that in this way we get a cone over the diagram $D$. Let $f\colon i\to j$ be an arrow of $\cat{I}$, then we have:
+	\begin{align*}
+	U(D(f)\circ (p_{1,i}, p_{2, i}, p_{3,i}))&=U(D(f))\circ(p_{1,i}, p_{2, i})\\&=(p_{1,j}, p_{2, j})\\&= U(D(f)\circ (p_{1,j}, p_{2, j}, p_{3,j}))
+	\end{align*}
+	 And faithfulness of $U$ yields the thesis.
+
+	 To see that this cone is terminal, let $(E, F, G, a, b, c)$ be another graph with the vertex of a cone with sides $(t_{1,i},t_{2, i}, t_{3,i})$.
+By construction, we have an arrow $(t_1, t_2)\colon (E, F, a, b)\to (A, B, s, t)$ such that
+	 \[\xymatrix{&E \ar@{.>}[dl]_{t_1} \ar[dr]^{t_{1,i}}&&&F \ar@{.>}[dl]_{t_2} \ar[dr]^{t_{2,i}}\\ A \ar[rr]_{p_{1,i}} & & A_i & B \ar[rr]_{p_{2,i}}&& B_i }\]
+
+	Let now $g$ and $g'$ be two elements of $F$ such that $c(g)=c(g')$, then for every $i\in \cat{I}$
+	\begin{align*}
+		q_i(p_{2,i}(t_2(g)))&=q_i(t_{2,i}(g))\\&=t_{3, i}(c(g))\\&=t_{3, i}(c'(g))\\&=q_i(t_{2,i}(g'))\\&=	q_i(p_{2,i}(t_2(g')))
+	\end{align*}
+
+	Thus $t_2(g)\sim t_2(g')$, so that we have a, unique, dotted arrow $t_3\colon G\to Q$ as below
+
+	\[\xymatrix{ F \ar[d]_{t_{2}} \ar[r]^{c} & G \ar@{.>}[d]^{t_{3}}\\ B \ar[r]_{q} & Q}\]
+
+	Faithfulness \todo{esercizio per te: scrivere la dimostrazione di queste ultime due righe}of $U$ now guarantees that $(t_1, t_2, t_3)$ is the unique arrow such that $(p_{1,i}, p_{2,i}, p_{3,i})\circ(t_1, t_2, t_3)=(t_{1,i},t_{2, i}, t_{3,i})$.
+
+	\todo{esercizio per te: fare i colimiti.
+Hint: la dimostrazione è diversa ma più semplice.
+Se $(A, B, s,t)$ è il colimite di $U\circ D$ puoi considerare il colimite $Q$ dei vari $Q_i$.
+Per la proprietà del colimite hai una freccia $B\to Q$ (come la definisci?).
+Ora devi mostrare che è epi.}
+\end{proof}
+
+\begin{cor}
+	An arrow $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ in $\EqGrph$ is mono if and only if $h_1$ and $h_2$ are mono in $\Set$.
+\end{cor}
+\begin{proof}
+	\todo{esercizio per te, usa fedeltà e continuità}
+\end{proof}
+
+Let us turn to another functor $\EqGrph\to \Graph$.
+
+\begin{definition}
+The \emph{quotient functor} $Q\EqGrph\to \Graph $ sends $(A, B, C, s,t, q)$ to $(A, C, q\circ s, q\circ t)$ and an arrow $(h_1, h_2, h_3) \colon (A, B, C, s,t, q)\to (E, F, G, a,b, c)$ to $(h_1, h_3)$.
+\end{definition}
+
+\todo{Verifica che questa cosa funziona $(h_1, h_3)$ è un morfismo di grafi?}
+
+\begin{lemma}
+	$Q$ is both a left and right adjoint.
+\end{lemma}
+\begin{proof} Let us start proving that $Q$ is a left adjoint.
+Let $R(A,B, s, t)$ be $(A, B, B, s,t, id_{B})$ , so that $Q(R(A,B,s,t))=(A,B,s,t)$.
+Now, suppose that an arrow $(h_1, h_2)\colon Q(E,F,G, a,b,c)\to (A,B, s,t)$ is given.
+Consider the triple $(h_1, h_2, h_2\circ c)$.
+Notice that
+	\[h_2\circ c\circ a= s\circ h_1 \qquad  h_2\circ c\circ b= t\circ h_1\]
+
+	 then we have three squares:
+
+\[\xymatrix{E \ar[r]^{a} \ar[d]_{h_1} & F \ar[d]^{h_2\circ c} & E \ar[r]^{b} \ar[d]_{h_1}& F \ar[d]_{h_2\circ C} & B \ar[d]_{h_2\circ c} \ar[r]^{c} & C \ar[d]^{h_2}\\A \ar[r]_{s} & B & A  \ar[r]_{t}& B & B \ar[r]_{id_B} & B}\]
+
+	 We have therefore found a morphism whose image through $Q$ fits in the diagram below.
+	\[\xymatrix{(A, B, s,t)\ar[r]^{(id_A, id_B)} &(A, B, s,t)\\ (E, G, q\circ s, q\circ t) \ar[ur]_{(h_1, h_2)} \ar[u]^{Q(h_1, h_2\circ q, h_2)}}\]
+
+Uniqueness of
+
+We can now turn to the second half of the thesis. To see that $Q$ is a right adjoint,
+
+\end{proof}
+
+\begin{cor}Let $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ be a morphism of $\EqGrph$, then the following are equivalent:
+	\begin{enumerate}
+		\item $(h_1, h_2, h_3)$ is a regular mono;
+		\item $h_1$, $h_2$, $h_3$ are all monos;
+		\item $h_1$ and $h_2$ are mono and for every $f, f'\in F$, $c(h_2(f))=c(h_2(f'))$ if and only if $q(f)=q(f')$.
+	\end{enumerate}
+\end{cor}
+\begin{proof}
+	$1\Rightarrow 2.$ \todo{Esercizio}
+
+	\smallskip \noindent
+	$2\Rightarrow 3.$ \todo{Esercizio}
+
+	$3\Rightarrow 1.$
+\end{proof}
+
+\begin{prop}
+	$Q$ creates limits and colimits.
+\end{prop}
+\begin{proof}
+	\todo{esercizio per te (devi verificare solo la riflessione: ma dato un diagramma in grafi fatto di quozienti, come costruisci un insieme di vertici per il (co)limite?)}
+\end{proof}
+
+\color{black}
 \section{Graphs with Equivalences}
@@
 As we have done in \Cref{sect:graphs}, we can think to a graph with equivalence as a presheaf, this time from a category $E \rightrightarrows V \rightarrow C$, where the image of $C$ along the presheaf is the set of the equivalence classes, requiring that the morphism $V\rightarrow C$ is an epimorphism (that is, a surjective function).
+
+\todo{Io sinceramente qua propongo una struttura "intermedia" da usare come definizione.
+Un grafo con equivalenza è una sestupla (A, B, C, s, t, q) tale che blah blah.
+Segue remark che questo equivale a dare:
+
+>un funtore da un opportuna categoria che manda certe frecce in epi
+>un grafo con una relazione di equivalenza sui vertici}
 

### 2024-10-22 Article/Graph_sections/Eq_Graphs.tex
stabilità

@@
 \section{Graphs with equivalences - notes and results}
+
+\subsection{Some results on kernel pair and regular epis}
+\todo{Questi risultati vanno completati e distribuiti lungo la tesi: quello sui kernel pair nella parte sui pullback, quello sugli epi regolari nella parte sui coequalizzatori, quelli che riguardano l'adesività nella relativa sezione}
+
+\todo{Sicuramente devi anche mettere dei riferimenti ai risultati della sez. sull'adesività (tipo alla proposizione che gli M-pushout sono pullback)}
+
+\begin{lemma}\label{lem:pb1}
+	Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
+	\[\xymatrix{X\ar[r]^{f} \ar[d]_{t} & Y \ar[d]^{k}\ar[r]^{g} &Z \ar[d]^{h}\\A \ar[r]_{a}& B \ar[r]_{b} & C}\]
+\end{lemma}
+\begin{proof}
+	\todo{Esercizio per te}
+\end{proof}
+
+\begin{definition}A \emph{kernel pair} $(K_f, p_{f, 1}, p_{f,2})$ for an arrow $f\colon X\to Y$ is an object $K_f$ with two arrows $p_{f,1}, p_{f, 2}\colon K_f\to X$ making the following square a pullback.
+	\[\xymatrix{K_f \ar[r]^{p_{f,1}} \ar[d]_{p_{f,2}}& X \ar[d]^{f}\\ X \ar[r]_{f} & Y}\]
+\end{definition}
+
+\begin{remark}
+	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
+\end{remark}
+
+\begin{lemma}\label{lem:salvavita1}
+Suppose that the following square is given and that $f\colon X\to Y$ and $g\colon Z\to W$ have kernel pairs.
+\[\xymatrix{X \ar[d]_{f}\ar[r]^{h}& Z \ar[d]^{g} \\ Y \ar[r]_{t}& W}\]
+
+Then there exists a unique arrow $k_h\colon K_f\to K_g$ making the squares below commutes.
+
+\[\xymatrix{K_f \ar[d]_{p_{f, 1}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,1}} & K_f \ar[d]_{p_{f,2}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,2}} \\ X \ar[r]_{h}& Z & X \ar[r]_{h}& Z}\]
+
+Moreover, if the beginning square is a pullback, then also the preceding ones are so.
+\end{lemma}
+\begin{proof}
+	Computing we have
+	\begin{align*}
+		g\circ h\circ p_{f,1}&=t\circ f\circ p_{f,1}\\&=t\circ f\circ p_{f,2}\\&=g\circ h\circ p_{f,2}
+	\end{align*}
+	So that the wanted $k_h$ exists, and it is unique, by the universal property of $K_g$ as the pullback of $g$ along itself.
+
+	To prove the second half of the thesis, let us consider the  two rectangles below, which, by \Cref{lem:pb1} are pullbacks.
+\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{h} \ar[d]^{f} & Z \ar[d]^{g} & K_f \ar[r]^{p_{f,2}}  \ar[d]_{p_{f,1}} & X \ar[d]^{f} \ar[r]^{h}& Z \ar[d]^{g}\\
+	X \ar[r]_{f}& Y \ar[r]_{t}& W&  X \ar[r]_f & Y\ar[r]_{t} & W}\]
+
+	But then the following ones are pullbacks too.
+ 	\[\xymatrix{K_f \ar@/^.4cm/[rr]^{h\circ p_{f,2}} \ar[r]_{k_h} \ar[d]_{p_{f,1}}& K_g  \ar[r]_{p_{g,2}} \ar[d]_{p_{g,1}} & Z \ar[d]^{g} & K_f \ar@/^.4cm/[rr]^{h\circ p_{f,1}} \ar[r]_{k_h} \ar[d]_{p_{f,2}}& K_g \ar[r]_{p_{g,1}} \ar[d]_{p_{g,2}} & Z \ar[d]^{g}\\X \ar@/_.4cm/[rr]_{t\circ f}\ar[r]^{h}& Z \ar[r]^{g} & W & X \ar@/_.4cm/[rr]_{t\circ f} \ar[r]^{h}& Z \ar[r]^{g}& W}\]
+
+ 	The thesis now follows again by \Cref{lem:pb1}.
+\end{proof}
+
+\begin{lemma}\label{lem:salvavita2}
+Let $\cat{C}$ be an $\mathcal{M}$-adhesive category and suppose that the cube below is given, in which every face is a pullback and the bottom one is an $\mathcal{M}$-pushout.
+
+ 	\[\xymatrix@C=10pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D}\]
+Then the square below is a pushout.
+\[\xymatrix{K_{a} \ar[r]^{k_{f'}}  \ar[d]_{k_{m'}}& K_b \ar[d]^{k_{n'}}\\ K_c \ar[r]_{k_{g'}} & K_d}\]
+\end{lemma}
+\begin{proof} By \Cref{lem:salvavita2} in the following cube the vertical faces are all pullbacks. 
+		\[\xymatrix@C=10pt@R=10pt{&K_a\ar[dd]|\hole_(.65){p_{a,1}}\ar[rr]^{k_{f'}} \ar[dl]_{k_{m'}} && K_b \ar[dd]^{p_{b,1}} \ar[dl]_{k_{n'}} \\ K_c  \ar[dd]_{p_{c,1}}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){p_{d,1}}\\&A'\ar[rr]|\hole^(.65){f'} \ar[dl]^{m'} && B' \ar[dl]^{n'} \\C' \ar[rr]_{g'} & & D'}\]
+	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
+\end{proof}
+
+\begin{lemma}[Slanting square Lemma]\label{label:lem:salvavita3}
+Let $\cat{C}$ be an $\mathcal{M}$-adhesive category and suppose that the following diagram is given, in which the whole vertical faces are pullbacks, $a$, $b$, $c$ and $d$ are regular epi and the bottom face is a pushout.
+\todo{Sistema il diagramma per renderlo leggibile}
+\[\xymatrix@C=15pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dddd]_(.3){d}\\&A \ar[dd]_{z}\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dd]_{y} \ar[dddl]^{n} \\C \ar[dd]_{x}\ar[ddrr]^(.35){g} & &\\&E\ar[rr]|\hole^(.35){e} \ar[dl]^{t} && F \ar[dl]^{u} \\G \ar[rr]_{v} & & H}\]
+Then the square below is a pushout
+\[\xymatrix{A \ar[r]^{f}\ar[d]_{m}& B \ar[d]^{n}\\ C \ar[r]_{g} & H}\]
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{prop}\label{prop:regepi}
+	Let $e\colon X\to Y$ be a regular epi in a category $\cat{C}$ with a kernel pair $p_1, p_2\colon P\rightrightarrows X$, then $e$ is the coequalizer of $p_1$ and $p_2$.
+\end{prop}
+\begin{proof}
+	By hypothesis there exists a pair $f, g\colon Z\rightrightarrows X$ of which $e$ is the coequalizer, since $e\circ f=e\circ g$ we have a diagram
+	\[\xymatrix{	Z \ar@/^.5cm/[drr]^{f} \ar@/_.5cm/[ddr]_{g} \ar@{.>}[dr]^{k}& &	\\ &P\ar[r]^{p_1} \ar[d]_{p_2} & X \ar[d]^{e} \\& X \ar[r]_{e}  & Y}\]
+	and thus there exists  the dotted $k\colon Z\to P$. Let $h\colon Z\to V$ be an arrow such that $h\circ p_1=h\circ p_2$, then
+	\begin{align*}h\circ f &= h \circ p_1\circ k \\&= h \circ p_2\circ k \\&=h\circ g
+	\end{align*}
+	and thus there exists a unique $l\colon Y\to V$ such that $l\circ e=h$.
+\end{proof}
+
+\begin{cor}\label{cor:regepi1}
+Let $\cat{C}$ be a category with pullbacks and $\phi\colon D\to D'$ be a natural transformation between two functor $D, D'\colon \cat{I}\to \cat{C}$.
+If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
+\end{cor}
+\begin{proof}
+	Let $K_i$ be the kernel pair of $\phi_i$, with projections $p_{1,i}, p_{2,i}\colon K_i\rightrightarrows D(i)$. Given an arrow $f\colon i\to j$ in $\cat{I}$, we have 
+	\begin{align*}
+		\phi_j\circ D(f)\circ p_{1,i}&=D'(f)\circ \phi_i\circ p_{1,i}\\&=D'(f)\circ \phi_i\circ p_{2,i}\\&=\phi_j\circ D(f)\circ p_{2,i}
+	\end{align*}
+
+	Thus the outer boundary of the diagram below commutes, yielding the dotted arrows $K(f)$.
+	\[\xymatrix{K_i \ar@{.>}[dr]^{K(f)}\ar[r]^{p_{1,i}} \ar[d]_{p_{2,i}}& D(i) \ar[dr]^{D(f)}\\D(i) \ar[dr]_{D(f)}&K_j \ar[r]^{p_{1,j}} \ar[d]_{p_{2,j}} & D(j) \ar[d]^{\phi_j}\\ &D(j) \ar[r]_{\phi_j} & D'(j)}\]
+
+	In this way \todo{esercizio per te}.
+We get a functor $E\colon \cat{I}\to \cat{C}$ with two natural transformations $p_{1}, p_2\colon E\rightrightarrows D$.
+By \Cref{prop:regepi} every component  $\phi_i$ of $\phi$ is the coequalizer of $p_{1,i}, p_{2,i}\colon E\rightrightarrows D$ and so $\phi$ is the coequalizer of $p_1$ and $p_2$.
+\end{proof}
+
+\begin{lemma}\label{lem:regepi}
+	Let $D, D'\colon \cat{I}\rightrightarrows  \cat{C}$ be two diagrams diagram with colimiting cocone $(C, \{c_i\}_{i\in \cat{I}})$ and   $(Q, \{q_i\}_{i\in \cat{I}})$.
+If $\phi\colon D\to D'$ is a natural transformation in which all components are regular epis, then the canonical arrow\todo{definisci questa freccia esplicitamente}  $c\colon C\to Q$ is a regular epi to.
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
 \begin{definition}
@@
 
-\begin{proof}
-	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$ we define\todo{WARNING: \emph{non} è immediatamente ovvio come si fa a  generalizzare questo passaggio ad altre categorie diverse da quella degli insiemi - serve almeno completezza e presenza dei coequalizzatori.} an equivalence relation on $B$ putting
-	\[b\sim b' \iff q_i(p_{2, i}(b))=q_i(p_{2, i}(b')) \text{ for every $i\in \cat{I}$}\]
+\begin{remark}\label{rem:ima}\todo{Dimostrala}In $\Set$ we have the following property: for every square as the one below, if $e\colon X\to Y$ is epi and $m\colon M\to Z$ is mono, then there exists a unique dotted arrow $Y\to M$ making the diagram below commutative.
+	\[\xymatrix{X \ar[r]^{f} \ar[d]_{e}& M \ar[d]^{m}\\ Y \ar[r]_{g} & Z}\] 
+\end{remark}
 
-	Let $q\colon B\to Q$ be the resulting quotient map.
-By definition, for every $i\in \cat{I}$, if $b\sim b'$ we have	 $q_i\circ p_{2,i}(b)=q_i\circ p_{2,i}(b')$, yielding a unique $p_{3,i}\colon Q\to Q_i$ fitting in the square below.
+\begin{proof}\todo{Per generalizzare ad altre categorie: serve poter fattorizzare con un epi regolare.} 
+	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$.
+Let $(L, \{l_i\}_{i\in \cat{I}})$ be a limiting cocone of the diagram given by the $Q_i$ \todo{Metti un remark prima dicendo che hai sempre un funtore (tre in realtà) verso $\Set$},
 
-\[\xymatrix{ B \ar[d]_{p_{2,i}} \ar[r]^{q} & Q \ar@{.>}[d]^{p_{3,i}}\\ B_i \ar[r]_{q_i} & Q_i}\]
+	Now, notice that $(B, \{q_i\circ p_{2,i}\}_{i\in \cat{I}})$ is a cone over the diagram given by the $Q_i$ \todo{Dimostralo}, so that we have an arrow $l\colon B\to L$.
+This arrow is not epi in general, let $Q$ be its image and $q\colon B\to Q$ be the resulting epi and $m\colon Q\to L$ the corresponding mono.
+	By definition the external square in the diagram below commutes, so for every $i\in \cat{I}$, \Cref{rem:ima} yields the dotted arrow $p_{3,i}$.
+	\[\xymatrix{B \ar[r]^{p_{2,i}} \ar[d]_{q}& B_i \ar[r]^{q_i} & Q_i \ar[d]^{id_{Q_i}}\\ Q \ar[r]_{m} \ar@{.>}[urr]_{p_{3,i}}& L \ar[r]_{l_i} & Q_i}\]
 
@@
 Se $(A, B, s,t)$ è il colimite di $U\circ D$ puoi considerare il colimite $Q$ dei vari $Q_i$.
-Per la proprietà del colimite hai una freccia $B\to Q$ (come la definisci?).
-Ora devi mostrare che è epi.}
+Per la proprietà del colimite hai una freccia $B\to Q$, mostra che è epi (segue in una riga dai risultati che abbiamo).}
 \end{proof}
@@
 	\todo{esercizio per te, usa fedeltà e continuità}
-\end{proof}
-
-Let us turn to another functor $\EqGrph\to \Graph$.
-
-\begin{definition}
-The \emph{quotient functor} $Q\EqGrph\to \Graph $ sends $(A, B, C, s,t, q)$ to $(A, C, q\circ s, q\circ t)$ and an arrow $(h_1, h_2, h_3) \colon (A, B, C, s,t, q)\to (E, F, G, a,b, c)$ to $(h_1, h_3)$.
-\end{definition}
-
-\todo{Verifica che questa cosa funziona $(h_1, h_3)$ è un morfismo di grafi?}
-
-\begin{lemma}
-	$Q$ is both a left and right adjoint.
-\end{lemma}
-\begin{proof} Let us start proving that $Q$ is a left adjoint.
-Let $R(A,B, s, t)$ be $(A, B, B, s,t, id_{B})$ , so that $Q(R(A,B,s,t))=(A,B,s,t)$.
-Now, suppose that an arrow $(h_1, h_2)\colon Q(E,F,G, a,b,c)\to (A,B, s,t)$ is given.
-Consider the triple $(h_1, h_2, h_2\circ c)$.
-Notice that
-	\[h_2\circ c\circ a= s\circ h_1 \qquad  h_2\circ c\circ b= t\circ h_1\]
-
-	 then we have three squares:
-
-\[\xymatrix{E \ar[r]^{a} \ar[d]_{h_1} & F \ar[d]^{h_2\circ c} & E \ar[r]^{b} \ar[d]_{h_1}& F \ar[d]_{h_2\circ C} & B \ar[d]_{h_2\circ c} \ar[r]^{c} & C \ar[d]^{h_2}\\A \ar[r]_{s} & B & A  \ar[r]_{t}& B & B \ar[r]_{id_B} & B}\]
-
-	 We have therefore found a morphism whose image through $Q$ fits in the diagram below.
-	\[\xymatrix{(A, B, s,t)\ar[r]^{(id_A, id_B)} &(A, B, s,t)\\ (E, G, q\circ s, q\circ t) \ar[ur]_{(h_1, h_2)} \ar[u]^{Q(h_1, h_2\circ q, h_2)}}\]
-
-Uniqueness of
-
-We can now turn to the second half of the thesis. To see that $Q$ is a right adjoint,
-
 \end{proof}
@@
 
-	$3\Rightarrow 1.$
+	\smallskip \noindent 
+	$3\Rightarrow 1.$\todo{Esercizio}
+\end{proof}
+
+Let us turn to another functor $\EqGrph\to \Graph$.
+
+\begin{definition}
+The \emph{quotient functor} $Q:\EqGrph\to \Graph $ sends $(A, B, C, s,t, q)$ to $(A, C, q\circ s, q\circ t)$ and an arrow $(h_1, h_2, h_3) \colon (A, B, C, s,t, q)\to (E, F, G, a,b, c)$ to $(h_1, h_3)$.
+\end{definition}
+
+\todo{Verifica che questa cosa funziona $(h_1, h_3)$ è un morfismo di grafi?}
+
+\begin{lemma}
+	$Q$ is a left  adjoint.
+\end{lemma}
+\begin{proof} Let us start proving that $Q$ is a left adjoint.
+Let $R(A,B, s, t)$ be $(A, B, B, s,t, id_{B})$ , so that $Q(R(A,B,s,t))=(A,B,s,t)$.
+Now, suppose that an arrow $(h_1, h_2)\colon Q(E,F,G, a,b,c)\to (A,B, s,t)$ is given.
+Consider the triple $(h_1, h_2, h_2\circ c)$.
+Notice that, since $(h_1, h_2)$ is an arrow in $\Graph$:
+	\[h_2\circ c\circ a= s\circ h_1 \qquad  h_2\circ c\circ b= t\circ h_1\]
+
+	 Then we have three squares:
+
+\[\xymatrix{E \ar[r]^{a} \ar[d]_{h_1} & F \ar[d]^{h_2\circ c} & E \ar[r]^{b} \ar[d]_{h_1}& F \ar[d]_{h_2\circ c} & B \ar[d]_{h_2\circ c} \ar[r]^{c} & C \ar[d]^{h_2}\\A \ar[r]_{s} & B & A  \ar[r]_{t}& B & B \ar[r]_{id_B} & B}\]
+
+	 We have therefore found a morphism $(E,F,G, a,b,c)\to R(A,B,s,t)$ whose image through $Q$ fits in the diagram below.
+	\[\xymatrix{(A, B, s,t)\ar[r]^{(id_A, id_B)} &(A, B, s,t)\\ (E, G, q\circ s, q\circ t) \ar[ur]_{(h_1, h_2)} \ar[u]^{Q(h_1, h_2\circ q, h_2)}}\]
+
+\todo{Esercizio: prova unicità (è facile)}
 \end{proof}
@@
 \begin{prop}
-	$Q$ creates limits and colimits.
+	$Q$ creates colimits.
 \end{prop}
 \begin{proof}
-	\todo{esercizio per te (devi verificare solo la riflessione: ma dato un diagramma in grafi fatto di quozienti, come costruisci un insieme di vertici per il (co)limite?)}
+	\todo{esercizio per te (devi verificare solo la riflessione: ma dato un diagramma in grafi fatto di quozienti, come costruisci un insieme di vertici per il colimite?)}
 \end{proof}
+
+\subsection{Adhesivity of $\EqGrph$}
+
+\begin{lemma}\label{lem:stab}
+In $\EqGrph$ pushouts along regular monos are stable.
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{lemma}\label{lem:vk}
+In $\EqGrph$ pushouts along regular monos are Van Kampen.
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+From \Cref{prop:limits} and \Cref{lem:stab,lem:vk} we deduce at once the following.
+
+\begin{cor}\label{cor:equi}
+	$\EqGrph$ is quasiadhesive.
+\end{cor}
 

### 2024-10-23 Article/Graph_sections/Eq_Graphs.tex
stabilità

@@
 
+\begin{cor}\label{cor:cube} Let $\cat{C}$ be a category and suppose that  the solid part of the following cube is given
+	\[\xymatrix@C=13pt@R=13pt{&Y'\ar[dd]|\hole_(.65){y}\ar[rr]^{g'} \ar@{.>}[dl]_{q'} && Z' \ar[dd]^{z} \ar[dl]_{r'} \\ B'  \ar[dd]_{b}\ar[rr]^(.65){k'} & & C' \ar[dd]_(.3){c}\\&Y\ar[rr]|\hole^(.65){g} \ar[dl]^{q} && Z \ar[dl]^{r} \\B \ar[rr]_{k} & & C}\]
+	If the front face is a pullback then there is a unique $q'\colon Y'\to B'$ filling the diagram.
+If, moreover, the other two vertical faces are also pullbacks, then the following square is a pullback too.
+	\[\xymatrix{Y' \ar[r]^{q'} \ar[d]_{y}& B'\ar[d]^{b}\\ Y \ar[r]_{q} & B}\]
+\end{cor}
+\begin{proof}
+	Let us compute:
+	\begin{align*}
+		c\circ r'\circ g'&=r\circ z \circ g'\\&=r\circ g \circ y\\&=k\circ q \circ y
+	\end{align*}
+	Since the front face is a pullback, this guarantees the existence of $q'$.  The second half of the thesis follows applying \cref{lem:pb1} to the following rectangle.
+	\[\xymatrix{Y'\ar@/^.4cm/[rr]^{r'\circ g'} \ar[r]_{q'} \ar[d]_{y}& B'\ar[d]_{b}\ar[r]_{k'}& C'\ar[d]^{c}\\ Y\ar@/_.4cm/[rr]_{r\circ g} \ar[r]^{q} & B \ar[r]^{k}& C}\]
+\end{proof}
+
+In an $\mathcal{M}$-adhesive category, pullbacks also enjoy a kind of left cancellation property.
+
+\begin{lemma}\label{lem:pb2}
+	Let $\cat{C}$ be a category with pullbacks, given the following diagrams:
+	\[
+	\xymatrix{Y\ar[r]^{f_2} \ar[d]_{f_1} & X_2 \ar[d]^{r_2} & Z_1 \ar[d]_{x_1}\ar[r]^{z_1} & W \ar[r]^{w} \ar[d]_{r} & Q'\ar[d]^{q} & Z_2 \ar[d]_{x_2} \ar[r]^{z_2}  & W  \ar[r]^{w} \ar[d]_{r}  & Q' \ar[d]^{q}\\ X_1 \ar[r]_{r_1} &R  & X_1 \ar[r]_{r_1} & R \ar[r]_{s}  & Q& X_2 \ar[r]_{r_2} & R \ar[r]_{s} & Q}\]
+	if the first square is a stable pushout and the whole rectangles and their left halves are pullbacks, then their common right half is a pullback too.
+\end{lemma}
+\begin{proof}Pulling back  $q$ along $s$ we get a square 
+	\[\xymatrix{U \ar[r]^{u} \ar[d]_{h}& Q' \ar[d]^{q}\\ R \ar[r]_s & S}\]
+	Notice that
+	\[
+	q\circ w\circ z_1=s\circ r_1\circ x_1 \qquad 
+	q\circ w\circ z_2=s\circ r_2\circ x_2 \]
+	Thus we get $u_1\colon Z_1\to U$ and $u_2\colon Z_2\to U$ fitting in the rectangles
+	\[\xymatrix{  Z_1  \ar@/^.4cm/[rr]^{w\circ z_1}\ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q}&  Z_2 \ar@/^.4cm/[rr]^{w\circ z_2} \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\  X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
+	which, by hypothesis and  \cref{lem:pb1} have left halves which are pullbacks. Now,
+	\[s\circ r_1\circ f_1 =s\circ r_2\circ f_2\]
+	Pulling back $q$ along this arrow we get another square
+	\[\xymatrix@C=40pt{Z'_0 \ar[r]^{t} \ar[d]_{y}& Q' \ar[d]^{q}\\ R \ar[r]_{s\circ r_1\circ f_1} & S}\]
+	In particular, we obtain the dotted $b_1\colon Z'_0\to Z_1$ and $b_2\colon Z'_0\to Z_2$ in
+	\[\xymatrix@C=30pt{ Z'_0 \ar@/^.4cm/[rrr]^{t}\ar[d]_{y} \ar@{.>}[r]_{b_1} & Z_1  \ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q} &Z'_0 \ar@/^.4cm/[rrr]^{t} \ar[d]_{y}\ar@{.>}[r]_{b_2}  & Z_2  \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
+	in which, using again \cref{lem:pb1}, all of the squares on the bottom rows are pullbacks.
+
+	We are going to construct another row above these two rectangles. By hypothesis 
+	\[q\circ w = s\circ r\]
+	Thus there exists a unique $g\colon W\to U$ such that
+	\[r=h\circ g \qquad w=u\circ g\]
+	Moreover, we also have that
+	\[\begin{split}h\circ g \circ z_1&=r \circ z_1\\&= r_1\circ x_1 \\&=h\circ u_1
+	\end{split}\qquad\begin{split}h\circ g \circ z_2&=r \circ z_2\\&= r_2\circ x_2 \\&=h\circ u_2
+	\end{split}\]
+	and 
+	\[\begin{split}u\circ g \circ z_1&=w \circ z_1\\&= u\circ u_1 
+	\end{split} \qquad \begin{split}u\circ g \circ z_1&=w \circ z_2\\&= u\circ u_2
+	\end{split}\]
+	which together show that
+	\[g\circ z_1=u_1 \qquad g\circ z_2=u_2\]
+
+	Summing up, we can depict all the arrows we have constucted so far in the following diagrams
+	\[\xymatrix{Z'_0 \ar[r]^{b_1} \ar[d]_{id_{Z'}}& Z_1 \ar[r]^{z_1} \ar[d]_{id_{Z_1}} &  W \ar[d]_g \ar[r]^{w} & Q' \ar[d]^{id_{Q'}}&& Z'_0 \ar[r]^{b_2}  \ar[d]_{id_{Z'}}& Z_2 \ar[d]_{id_{Z_2}} \ar[r]^{z_2}&  W \ar[d]_g\ar[r]^{w}& Q' \ar[d]^{id_{Q'}}\\ Z'_0 \ar[d]_{y} \ar[r]^{b_1} & Z_1  \ar[r]^{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]^{u} & Q'  \ar[d]^{q}& &Z'_0  \ar[d]_{y}\ar[r]^{b_2}  & Z_2  \ar[r]^{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]^{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & &Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
+	If we show that $g$ is an isomorphism we are done. Consider the cubes
+	\[\xymatrix@C=13pt@R=13pt{&Z_0'\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{z_2}  &&Z'_0\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{F_j(b)} \ar[dl]_{u_2}\\Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){z_1} & & W \ar[dd]_(.3){r}&& Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){u_1} & &U \ar[dd]_(.3){h}\\&Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2} && Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2}\\X_1 \ar[rr]_{r_1} & & R && X_1 \ar[rr]_{r_1} & & R}\]
+	in which the vertical faces are pullbacks. Since the bottom face is a stable pushout we can deduce that
+	\[\xymatrix{Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{z_2} & Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{u_2}\\ Z_1 \ar[r]_{z_1}& W & Z_1 \ar[r]_{u_1}& U }\]
+	are pushout squares too. The arrow $g$ fits in the following  diagram
+	\[\xymatrix{Z'_0\ar[r]^{b_2} \ar[d] _{b_1}& Z_2 \ar@/^.3cm/[ddr]^{u_2}\ar[d]^{z_2} \\ Z_1 \ar[r]_{z_1}  \ar@/_.3cm/[drr]_{u_1}& W \ar[dr]^{g} \\ &&U}\]
+	and thus it is an isomorphism.
+\end{proof}
+
 \begin{definition}A \emph{kernel pair} $(K_f, p_{f, 1}, p_{f,2})$ for an arrow $f\colon X\to Y$ is an object $K_f$ with two arrows $p_{f,1}, p_{f, 2}\colon K_f\to X$ making the following square a pullback.
@@
 \end{remark}
+
+\begin{prop}\label{prop:kermono}
+	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
+\end{prop}
+\begin{proof}\todo{esercizio}
+\end{proof}
+
+\begin{cor}\label{cor:kermono}
+	Let $(K_f, p_{f,1}, p_{f,2})$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, p_{f,1}, p_{f,2})$ is a kernel pair also for $m\circ f$.
+\end{cor}
+\begin{proof}
+	It is enough to see that, by \Cref{lem:pb1,prop:kermono} the outer boundary of the following square is a pullback.
+	\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{id_X} \ar[d]_{f}&X\ar[d]^{f} \\X \ar[d]_{id_X} \ar[r]_{f} & Y \ar[d]_{id_Y} \ar[r]_{id_Y}& Y \ar[d]^{m}\\X \ar[r]_{f} & Y \ar[r]_{m} & Z}\]
+
+\end{proof}
 
@@
 \begin{lemma}\label{lem:salvavita2}
-Let $\cat{C}$ be an $\mathcal{M}$-adhesive category and suppose that the cube below is given, in which every face is a pullback and the bottom one is an $\mathcal{M}$-pushout.
+Let $\cat{C}$ be an $\mathcal{M}$-adhesive category with all pullbacks and suppose that the cube below is given, in which every face is a pullback and the bottom one is an $\mathcal{M}$-pushout.
 
@@
 	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
-\end{proof}
-
-\begin{lemma}[Slanting square Lemma]\label{label:lem:salvavita3}
-Let $\cat{C}$ be an $\mathcal{M}$-adhesive category and suppose that the following diagram is given, in which the whole vertical faces are pullbacks, $a$, $b$, $c$ and $d$ are regular epi and the bottom face is a pushout.
-\todo{Sistema il diagramma per renderlo leggibile}
-\[\xymatrix@C=15pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dddd]_(.3){d}\\&A \ar[dd]_{z}\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dd]_{y} \ar[dddl]^{n} \\C \ar[dd]_{x}\ar[ddrr]^(.35){g} & &\\&E\ar[rr]|\hole^(.35){e} \ar[dl]^{t} && F \ar[dl]^{u} \\G \ar[rr]_{v} & & H}\]
-Then the square below is a pushout
-\[\xymatrix{A \ar[r]^{f}\ar[d]_{m}& B \ar[d]^{n}\\ C \ar[r]_{g} & H}\]
-\end{lemma}
-\begin{proof}
-	contenuto...
 \end{proof}
@@
 
-	In this way \todo{esercizio per te}.
-We get a functor $E\colon \cat{I}\to \cat{C}$ with two natural transformations $p_{1}, p_2\colon E\rightrightarrows D$.
+	In this way \todo{esercizio per te}we get a functor $E\colon \cat{I}\to \cat{C}$ with two natural transformations $p_{1}, p_2\colon E\rightrightarrows D$.
 By \Cref{prop:regepi} every component  $\phi_i$ of $\phi$ is the coequalizer of $p_{1,i}, p_{2,i}\colon E\rightrightarrows D$ and so $\phi$ is the coequalizer of $p_1$ and $p_2$.
@@
 
+\todo{COSE DA FARE: nel capitolo 1 metti una proposizione in cui mostri che da ogni trasf naturale $D\to D'$ puoi ricavare una freccia tra i colimiti, così in questa e nelle altre proposizioni puoi citarla.}
+
 \begin{lemma}\label{lem:regepi}
 	Let $D, D'\colon \cat{I}\rightrightarrows  \cat{C}$ be two diagrams diagram with colimiting cocone $(C, \{c_i\}_{i\in \cat{I}})$ and   $(Q, \{q_i\}_{i\in \cat{I}})$.
-If $\phi\colon D\to D'$ is a natural transformation in which all components are regular epis, then the canonical arrow\todo{definisci questa freccia esplicitamente}  $c\colon C\to Q$ is a regular epi to.
+If $\cat{C}$ has all colimits for diagrams of shape $\cat{I}$ and $\phi\colon D\to D'$ is a natural transformation in which all components are regular epis, then the canonical arrow\todo{richiama prop precedente}  $c\colon C\to Q$ is a regular epi to.
 \end{lemma}
 \begin{proof}
-	contenuto...
+	By \Cref{cor:regepi1} we know that $\phi\colon D\to D'$ is a regular epi, so that there is a functor $E\colon \cat{I}\to \cat{C}$ and $\alpha, \beta\colon E\rightrightarrows D$ such that $\phi$ is a coequalizer for $\alpha$ and $\beta$.
+Let $(P, \{p_i\}_{i\in \cat{I}})$ be the colimit of $E$, by ???\todo{richiama prop sulla freccia tra i colimiti} we have arrows $a, b\colon P\rightrightarrows  C$ fitting in the diagram belows:
+	\[\xymatrix{E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i}& P \ar@{.>}[d]^{a} & E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i} & P \ar@{.>}[d]^{b}\\ D(i) \ar[r]_{c_i} & C & D(i) \ar[r]_{c_i} & C}\]
+
+	We want to show that $c$ coequalizes $a$ and $b$. Let thus $t\colon C\to T$ be an arrow such that $t\circ a=t\circ b$. Then for every $i\in I$ we have 
+	\begin{align*}
+		t\circ c_i\circ \alpha_i&=t\circ a\circ p_i\\&=t\circ b\circ p_i\\&=t\circ c_i\circ \beta_i
+	\end{align*}
+
+	Thus there is $t_i\colon D'(i)\to T$ such that $t\circ c_i=t_i\circ \phi_i$.
+It is now easy to see that $(T, \{t_i\}_{i\in \cat{I}})$ is a cocone on $D'$ \todo{Verificalo!}.
+Thus we have an arrow $k\colon Q\to T$ such that $k\circ q_i=t_i$.
+But then we have
+	\begin{align*}
+		k\circ c\circ c_i&=k\circ q_i\circ \phi_i\\&=t_i\circ \phi\\&=t\circ c_i
+	\end{align*}
+	Showing that $k\circ c=t$.
+
+	For uniqueness, let $k'$ be another arrow $Q\to T$ such that $k'\circ c=t$, then we have
+	\begin{align*}
+		k'\circ q_i\circ \phi_i&=k'\circ c\circ c_i\\&=t\circ c_i\\&=t_i\circ \phi_i
+	\end{align*}
+	Since $\phi_i$ is a regular epi, by ???\todo{mettere nel capitolo 1 una proposizione che mostra che epi regolari sono epi} this entails $k'\circ q_i=t_i$.
+By construction $k\circ q_i=t_i$ and  so $k=k'$ since $(Q, \{q_i\}_{i\in \cat{I}})$ is a colimiting cocone.
 \end{proof}
@@
 
-	In this way we get a category $\EqGrph$.
+	In this way, defining the composition componentwise, we get a category $\EqGrph$.
 \end{definition}
@@
 \begin{remark}\label{rem:fedele}
-	There is a faithful functor $U\colon \EqGrph\to \Graph$, forgetting the quotient part. \todo{Questo è per te da dimostrare.}
+	There is a faithful functor $U\colon \EqGrph\to \Graph$, forgetting the quotient part. \todo{Questo è per te da dimostrare (forse meglio come proposizione che come remark).}
+\end{remark}
+
+\begin{remark}
+There is another functor $V\colon \EqGrph\to \Set$ sending $(A, B,C, s,t, q)$ to $C$ and a morphism to its last component.	
 \end{remark}
@@
 \begin{remark}\label{rem:ima}\todo{Dimostrala}In $\Set$ we have the following property: for every square as the one below, if $e\colon X\to Y$ is epi and $m\colon M\to Z$ is mono, then there exists a unique dotted arrow $Y\to M$ making the diagram below commutative.
-	\[\xymatrix{X \ar[r]^{f} \ar[d]_{e}& M \ar[d]^{m}\\ Y \ar[r]_{g} & Z}\] 
+	\[\xymatrix{X \ar[r]^{f} \ar[d]_{e}& M \ar[d]^{m}\\ Y \ar[r]_{g} \ar@{.>}[ur]^{h}& Z}\] 
 \end{remark}
@@
 	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$.
-Let $(L, \{l_i\}_{i\in \cat{I}})$ be a limiting cocone of the diagram given by the $Q_i$ \todo{Metti un remark prima dicendo che hai sempre un funtore (tre in realtà) verso $\Set$},
+Let $(L, \{l_i\}_{i\in \cat{I}})$ be a limiting cone for $V\circ D$.
 
-	Now, notice that $(B, \{q_i\circ p_{2,i}\}_{i\in \cat{I}})$ is a cone over the diagram given by the $Q_i$ \todo{Dimostralo}, so that we have an arrow $l\colon B\to L$.
+	Now, notice that $(B, \{q_i\circ p_{2,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Dimostralo}, so that we have an arrow $l\colon B\to L$.
 This arrow is not epi in general, let $Q$ be its image and $q\colon B\to Q$ be the resulting epi and $m\colon Q\to L$ the corresponding mono.
@@
 
-	Let now $g$ and $g'$ be two elements of $F$ such that $c(g)=c(g')$, then for every $i\in \cat{I}$
+	Moreover $(G, \{t_{3,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Verificalo}, thus there exists an arrow $t\colon G\to L$ such that $l_i\circ t =t_{3,i}$. Now, precomposing with $c$ we get
 	\begin{align*}
-		q_i(p_{2,i}(t_2(g)))&=q_i(t_{2,i}(g))\\&=t_{3, i}(c(g))\\&=t_{3, i}(c'(g))\\&=q_i(t_{2,i}(g'))\\&=	q_i(p_{2,i}(t_2(g')))
+		l_i\circ t\circ c&=t_{3,i}\circ c\\&=q_i\circ t_{2,i}\\&=q_i\circ p_{2,i}\circ t_2\\&=l_i\circ l\circ t_2
 	\end{align*}
 
-	Thus $t_2(g)\sim t_2(g')$, so that we have a, unique, dotted arrow $t_3\colon G\to Q$ as below
+	Therefore the solid part of the diagram below commutes and \Cref{rem:ima} yields the dotted arrow $t_3\colon G\to Q$.
 
-	\[\xymatrix{ F \ar[d]_{t_{2}} \ar[r]^{c} & G \ar@{.>}[d]^{t_{3}}\\ B \ar[r]_{q} & Q}\]
+	\[\xymatrix{F \ar[r]^{t_2} \ar[d]_{c}& B \ar[r]^{q} & Q \ar[d]^{m}\\G \ar[rr]_{t} \ar@{.>}[urr]^{t_3}&& L}\]
 
-	Faithfulness \todo{esercizio per te: scrivere la dimostrazione di queste ultime due righe}of $U$ now guarantees that $(t_1, t_2, t_3)$ is the unique arrow such that $(p_{1,i}, p_{2,i}, p_{3,i})\circ(t_1, t_2, t_3)=(t_{1,i},t_{2, i}, t_{3,i})$.
-
-	\todo{esercizio per te: fare i colimiti.
+	Faithfulness \todo{esercizio per te: scrivere la dimostrazione di queste ultime due righe}of $U$ now guarantees that $(t_1, t_2, t_3)$ is the unique arrow such that $(p_{1,i}, p_{2,i}, p_{3,i})\circ(t_1, t_2, t_3)=(t_{1,i},t_{2, i}, t_{3,i})$.	\todo{esercizio per te: fare i colimiti.
 Hint: la dimostrazione è diversa ma più semplice.
@@
 
-\begin{cor}Let $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ be a morphism of $\EqGrph$, then the following are equivalent:
+\begin{cor}\label{cor:regmono}Let $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ be a morphism of $\EqGrph$, then the following are equivalent:
 	\begin{enumerate}
@@
 
-\begin{prop}
+\begin{prop}\label{prop:colimit}
 	$Q$ creates colimits.
@@
 \end{proof}
+
+\begin{example}
+	\todo{Q non preserva i limiti}
+\end{example}
 
@@
 \begin{proof}
-	contenuto...
+	Suppose that the cube below is given, in which all the vertical faces are pullbacks and the bottom face is a pushout, with $(h_1, h_2, h_3)\colon (A_1,B_1,C_1, s_1,t_1,q_1)\to (A_2,B_2,C_2, s_2,t_2,q_2)$ a regular mono\todo{Questo diagramma va sistemato per farlo stare nella pagina (val la pena magari dire "sia $\mathcal{G}_1$ il grafo....")}.
+
+		\[\xymatrix@C=20pt@R=20pt{&(A'_1,B'_1,C'_1, s'_1,t'_1,q'_1)\ar[dd]|\hole_(.65){(a_1, a_2, a_3)}\ar[rr]^{(h'_1, h'_2, h'_3)} \ar[dl]_{(k'_1, k'_2, k'_3)} && (A'_2,B'_2,C'_2, s'_2,t'_2,q'_2) \ar[dd]^{(b_1, b_2, b_3)} \ar[dl]_{(t'_1, t'_2, t'_3)} \\ (A'_3,B'_3,C'_3, s'_3,t'_3,q'_3) \ar[dd]_{(c_1, c_2, c_3)}\ar[rr]^(.65){(p'_1,p'_2,p'_3)} & & (A'_4,B'_4,C'_4, s'_4,t'_4,q'_4) \ar[dd]_(.3){(d_1, d_2, d_3)}\\&(A_1,B_1,C_1, s_1,t_1,q_1)\ar[rr]|\hole^(.65){(h_1, h_2, h_3)} \ar[dl]^{(k_1, k_2, k_3)} && (A_2,B_2,C_2, s_2,t_2,q_2) \ar[dl]^{(t_1, t_2, t_3)} \\(A_3,B_3,C_3, s_3,t_3,q_3) \ar[rr]_{(p_1, p_2, p_3)} & & (A_4,B_4,C_4, s_4,t_4,q_4)}\]
+
+By \Cref{prop:limits,cor:regmono} the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as vertical faces, thus their top faces are $\mathcal{M}$-pushouts.
+
+\[\xymatrix@C=10pt@R=10pt{&A'_1\ar[dd]|\hole_(.65){a_1}\ar[rr]^{h'_1} \ar[dl]_{k'_1} && A'_2 \ar[dd]^{b_1} \ar[dl]_{t'_1} && B'_1\ar[dd]|\hole_(.65){a_2}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[dd]^{b_2} \ar[dl]_{t'_2}\\ A'_3  \ar[dd]_{c_1}\ar[rr]^(.7){p'_1} & & A'_4 \ar[dd]_(.3){d_1} &&B'_3  \ar[dd]_{c_2}\ar[rr]^(.7){p'_2} & & B'_4 \ar[dd]_(.3){d_2}\\&A_1\ar[rr]|\hole^(.65){h_1} \ar[dl]^{k_1} && A_2 \ar[dl]^{t_1} && B_1\ar[rr]|\hole^(.65){h_2} \ar[dl]^{k_2} && B_2 \ar[dl]^{t_2} \\A_3 \ar[rr]_{p_1} & & A_4&&B_3 \ar[rr]_{p_2} & & B_4}\]
+
+Now,  using \Cref{cor:cube}, we can consider a third cube, which, by \Cref{prop:colimit}, has a bottom face an $\mathcal{M}$-pushout and pullbacks as vertical faces, so that its top face is an $\mathcal{M}$-pushout too.
+
+\[\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C'_4 \ar[dd]_(.3){d_3}\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]
+
+Moreover, by the proof of \Cref{prop:limits} we know that there are monos $m_2\colon C'_2\to U $ and $m_3\colon C'_3\to Y$ fitting in the diagrams
+\[\xymatrix{B'_3\ar[r]^{p'_2} \ar[d]^{q'_3} \ar@/_.4cm/[dd]_{c_2}& B'_4\ar@/^.2cm/[dr]^{q'_4} && B'_2 \ar@/_.4cm/[dd]_{b_2} \ar[r]^{t'_2} \ar[d]^{q'_2}& B'_4 \ar@/^.2cm/[dr]^{q'_4} \\C'_3  \ar[r]^{m_3}& Y \ar[r]^{y_1} \ar[d]_{y_2} & C'_4 \ar[d]^{d_3} &C'_2 \ar[r]^{m_2}& U\ar[r]^{u_1} \ar[d]_{u_2} & C'_4 \ar[d]^{d_3}\\  B_3  \ar[r]_{q_2}& C_3 \ar[r]_{p_3}& C_4 &B_2 \ar[r]_{q_2}&  C_2 \ar[r]_{t_3}& C_4}\]
+
+For $C'_1$, the we can make a similar argument, let $S$ be the pullback of $m_2$ along $x_1$, using \Cref{lem:pb1} and, again, the proof of \Cref{prop:limits} we know that $q'_1$ arise as the factorization of the arrow $B'_1\to S$ induced by $q'_2\circ h'_2$ and $a_2$ so that we have a diagram.
+	\[\xymatrix{ B'_1 \ar@/_.4cm/[dd]_{a_2} \ar[r]^{h'_2} \ar[d]^{q'_2}& B'_2 \ar@/^.2cm/[dr]^{q'_2} \\C'_1 \ar[r]^{m_1}& S\ar[r]^{s_1} \ar[d]_{s_2}&C'_2 \ar[d]^{m_2}\\  B_2 \ar@/_.2cm/[dr]_{q_2}&  T \ar[r]^{x_1} \ar[d]_{x_2}& U \ar[d]_{u_2} \\ & C_1 \ar[r]_{h_3}&  C_2}\]
+
+%Notice that $s_2\colon S\to T$, being the pullback of a mono is mono by ????\todo{metti questo lemma da qualche parte: il pullback di un mono è mono}
+Moreover, notice that \todo{Esercizio (basta comporre prima e dopo con gli opportuni epi e mono)}
+
+\[s_1\circ m_1 = h'_3 \quad w\circ s_2\circ m_1=  m_3\circ k'_3 \quad t'_3=u_1\circ m_2 \quad p_3=y_1\circ m_3\]
+
+Let now $(z_1, z_2, z_3)\colon (A'_2, B'_2, C'_2)\to (E, F, G, e, f, g)$ and $(w_1, w_2, w_3)\colon (A'_3, B'_3, C'_3)\to (E, F, G, e, f, g)$ be two morphisms such that 
+\[(z_1, z_2, z_3)\circ (h'_1, h'_2, h'_3)=(w_1, w_2, w_3)\circ (k'_1, k'_2, k'_3)\] 
+Let $z\colon B'_4\to F$ be the arrow induced by $z_2$ and $w_2$, we want to construct the dotted arrow $w\colon C'_4 \to G$ in the diagram below
+
+ \todo{Finisci il diagramma}
+\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[rr]^{p'_2} && B'_4  \ar[rr]^{z}&& F \ar[ddddd]^{g}\\& C'_1 \ar[d]_{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \\ C'_3 \ar[dd]_{m_3}\\&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C'_4 \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]
+
+Now by \Cref{prop:regepi} $d_3$ is the coequalizer of its kernel pair. On the other hand, by \Cref{lem:salvavita2}  we know that the top face of the cube below is a pushout.
+\[\xymatrix@C=15pt@R=15pt{&K_{s_2\circ m_1\circ q'_1}\ar[dd]|\hole_(.65){p_{s_2\circ m_1\circ q'_1,1}}\ar[rr]^{k_{h'_2}} \ar[dl]_{k_{k'_2}} && K_{m_2\circ q'_2} \ar[dd]^{p_{m_2\circ q'_2,1}} \ar[dl]_{k_{t'_2}} \\ K_{m_3\circ q'_3}  \ar[dd]_{p_{m_3\circ q'_3,1}}\ar[rr]^(.7){k_{p'_2}} & & K_{q'_4} \ar[dd]_(.3){p_{q'_4,1}}\\&B'_1\ar[rr]|\hole^(.65){h'_2} \ar[dl]^{k'_2} && B'_2 \ar[dl]^{t'_2} \\B'_3 \ar[rr]_{p'_2} & & C_4}\]
+Moreover, since $m_3$ and $m_2$ are monos, or by \Cref{cor:kermono} we also know that
+\[q'_3\circ p_{m_3\circ q'_3, 1}  = q'_3\circ p_{m_3\circ q'_3,2} \qquad q'_2\circ p_{m_2\circ q'_2, 1}  = q'_2\circ p_{m_2\circ q'_2,2}\]
+
+Now, we have
+\[
+\begin{split}
+	g\circ z\circ p_{q'_4,1} \circ k_{p'_2}&=g\circ z\circ p'_2\circ p_{m_3\circ q'_3, 1}\\&=g\circ w_2\circ \circ  p_{m_3\circ q'_3, 1}\\&=w_3\circ q'_3\circ p_{m_3\circ q'_3, 1}\\&=w_3\circ q'_3\circ p_{m_3\circ q'_3, 2}\\&=g\circ w_2\circ \circ  p_{m_3\circ q'_3, 2}\\&=g\circ z\circ p'_2\circ p_{m_3\circ q'_3, 2}\\&=g\circ z\circ p_{q'_4,2} \circ k_{p'_2}
+\end{split} \qquad 
+\begin{split}
+g\circ z\circ p_{q'_4,1} \circ k_{t'_2}&=g\circ z\circ t'_2\circ p_{m_2\circ q'_2, 1}\\&=g\circ z_2\circ \circ  p_{m_2\circ q'_2, 1}\\&=z_3\circ q'_2\circ p_{m_2\circ q'_2, 1}\\&=z_3\circ q'_2\circ p_{m_2\circ q'_2, 2}\\&=g\circ z_2\circ \circ  p_{m_2\circ q'_2, 2}\\&=g\circ z\circ t'_2\circ p_{m_2\circ q'_2, 2}\\&=g\circ z\circ p_{q'_4,2} \circ k_{t'_2}
+\end{split}
+\]
+
+The thesis now follows \todo{Scrivi perché}
+
+\todo{Esercizio: prova unicità}
+
 \end{proof}

### 2024-10-23 Article/Graph_sections/Eq_Graphs.tex
minori

@@
 
+\iffalse 
 In an $\mathcal{M}$-adhesive category, pullbacks also enjoy a kind of left cancellation property.
@@
 \end{proof} 
+\fi
 
@@
 \[(z_1, z_2, z_3)\circ (h'_1, h'_2, h'_3)=(w_1, w_2, w_3)\circ (k'_1, k'_2, k'_3)\] 
-Let $z\colon B'_4\to F$ be the arrow induced by $z_2$ and $w_2$, we want to construct the dotted arrow $w\colon C'_4 \to G$ in the diagram below
+Let $z\colon B'_4\to F$ be the arrow induced by $z_2$ and $w_2$, we want to construct the dotted arrow $v\colon C'_4 \to G$ in the diagram below
 
- \todo{Finisci il diagramma}
-\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[rr]^{p'_2} && B'_4  \ar[rr]^{z}&& F \ar[ddddd]^{g}\\& C'_1 \ar[d]_{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \\ C'_3 \ar[dd]_{m_3}\\&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C'_4 \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]
+ \todo{Sistema il diagramma mettendo gli opportuni buchi}
+\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[dd]|(.5)\hole_(.62){q'_1}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[ddd]|(.33)\hole^{q'_2} \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[ddd]_{q'_3} \ar[rr]^(.65){p'_2} && B'_4  \ar[rr]^(.65){z}&& F \ar[ddddd]^{g}\\& C'_1 \ar@/^.2cm/[drr]^{h'_3} \ar@/_.2cm/[ddl]_{k'_3} \ar[d]^{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \ar@/^.2cm/[dddr]^{z_3} \ar[lddd]_{t'_3}\\ C'_3 \ar@/_.5cm/[ddrr]^(.65){p'_3} \ar[ddrrrr]_{w_3} \ar[dd]_{m_3}\\&T\ar[dd]|(.25)\hole|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]|(.25)\hole_{w} && U \ar[dd]^(.3){u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]_(.65){y_1} & & C'_4 \ar@{.>}[rr]_(.65){v} \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]
 

### 2024-10-24 Article/Appendix/Omitted_Proofs.tex
Reordered files + new version EqGrph

@@
 \chapter{Omitted Proofs}
+
+\paragraph{\Cref{lemma:pullback_lemma}.}
+    Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
+    \[
+        \begin{tikzcd}
+            X \arrow[r, "f"] \arrow[d, "t"swap] & Y \arrow[r, "g"] \arrow[d, "k"] & Z \arrow[d, "h"] \\
+            A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+\begin{proof}
+    For the ``only if'' part, suppose the left square to be a pullback. To verify the outer rectangle is a pullback, consider the following situation:
+    \[
+        \begin{tikzcd}
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} & & \\
+            & & & Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    But the right square is a pullback implies that there exists a unique $u$ such that
+    \[
+        \begin{tikzcd}
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15, dashed]{drr}{u}& & \\
+            & &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    And, since the left square is a pullback, there exists a unique $v$ such that
+    \[
+        \begin{tikzcd}
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15]{drr}{u} \arrow[dr, "v", dashed]& & \\
+            & X \arrow[r, "f"] \arrow[d, "t"swap] &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    Hence, the whole rectangle is a pullback.
+
+    For the ``if'' part, consider the following situation.
+    \[
+        \begin{tikzcd}
+            P \arrow[bend left=30]{rrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} & \\
+            & & Y \arrow[d, "k"] \\
+            & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    We have now to show that the unique arrow $v: P \to X$ (of the outer rectangle) is such that $f \circ v = p_1$, but this follows from the fact that the right square is a pullback, having the following situation.
+    \[
+        \begin{tikzcd}
+            P \arrow[bend left=30]{rrrd}{g \circ p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15, dashed]{drr}{u}& & \\
+            & &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    \todo{Rivedere questa dimostrazione}
+\end{proof}
 

### 2024-10-24 Article/Background_sections/Limit.tex
Reordered files + new version EqGrph

@@
 
-\begin{obs}
-    Given two composable regular monos $m$ and $n$, suppose that $n$ equalizes two arrows $f$ and $g$. Then, we have
-    \begin{align*}
-        g \circ (n \circ m) &= (g \circ n) \circ m &&\\
-                            &= (f \circ n) \circ m  && \textit{$n$ equalizer} \\
-                            &= f \circ (n \circ m)
-    \end{align*}
-    Since $n \circ m$ is mono (\Cref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
-\end{obs}
+% -- NON SEMPRE E' VERO !!! ---
+% \begin{obs}
+%     Given two composable regular monos $m$ and $n$, suppose that $n$ equalizes two arrows $f$ and $g$. Then, we have
+%     \begin{align*}
+%         g \circ (n \circ m) &= (g \circ n) \circ m &&\\
+%                             &= (f \circ n) \circ m  && \textit{$n$ equalizer} \\
+%                             &= f \circ (n \circ m)
+%     \end{align*}
+%     Since $n \circ m$ is mono (\Cref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
+% \end{obs}
 
@@
 
+The following lemma is a classical result, its proof is in the appendix.
+
+\begin{lemma}[Pullback Lemma]\label{lemma:pullback_lemma}
+        Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
+        \[
+            \begin{tikzcd}
+                X \arrow[r, "f"] \arrow[d, "t"swap] & Y \arrow[r, "g"] \arrow[d, "k"] & Z \arrow[d, "h"] \\
+                A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+            \end{tikzcd}
+        \]
+\end{lemma}
+
 The connection between constructions as products and equalizers and limits is made clear by the following theorem.

### 2024-10-24 Article/Graph_sections/Eq_Graphs.tex
Reordered files + new version EqGrph

--- 2024-10-22 Article/Graph_sections/Eq_Graphs.tex
@@
-\color{blue}
-
-\section{Graphs with equivalences - notes and results}
-
-\subsection{Some results on kernel pair and regular epis}
-\todo{Questi risultati vanno completati e distribuiti lungo la tesi: quello sui kernel pair nella parte sui pullback, quello sugli epi regolari nella parte sui coequalizzatori, quelli che riguardano l'adesività nella relativa sezione}
-
-\todo{Sicuramente devi anche mettere dei riferimenti ai risultati della sez. sull'adesività (tipo alla proposizione che gli M-pushout sono pullback)}
-
-\begin{lemma}\label{lem:pb1}
-	Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
-	\[\xymatrix{X\ar[r]^{f} \ar[d]_{t} & Y \ar[d]^{k}\ar[r]^{g} &Z \ar[d]^{h}\\A \ar[r]_{a}& B \ar[r]_{b} & C}\]
-\end{lemma}
-\begin{proof}
-	\todo{Esercizio per te}
-\end{proof}
-
-\begin{definition}A \emph{kernel pair} $(K_f, p_{f, 1}, p_{f,2})$ for an arrow $f\colon X\to Y$ is an object $K_f$ with two arrows $p_{f,1}, p_{f, 2}\colon K_f\to X$ making the following square a pullback.
-	\[\xymatrix{K_f \ar[r]^{p_{f,1}} \ar[d]_{p_{f,2}}& X \ar[d]^{f}\\ X \ar[r]_{f} & Y}\]
-\end{definition}
-
-\begin{remark}
-	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
-\end{remark}
-
-\begin{lemma}\label{lem:salvavita1}
-Suppose that the following square is given and that $f\colon X\to Y$ and $g\colon Z\to W$ have kernel pairs.
-\[\xymatrix{X \ar[d]_{f}\ar[r]^{h}& Z \ar[d]^{g} \\ Y \ar[r]_{t}& W}\]
-
-Then there exists a unique arrow $k_h\colon K_f\to K_g$ making the squares below commutes.
-
-\[\xymatrix{K_f \ar[d]_{p_{f, 1}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,1}} & K_f \ar[d]_{p_{f,2}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,2}} \\ X \ar[r]_{h}& Z & X \ar[r]_{h}& Z}\]
-
-Moreover, if the beginning square is a pullback, then also the preceding ones are so.
-\end{lemma}
-\begin{proof}
-	Computing we have
-	\begin{align*}
-		g\circ h\circ p_{f,1}&=t\circ f\circ p_{f,1}\\&=t\circ f\circ p_{f,2}\\&=g\circ h\circ p_{f,2}
-	\end{align*}
-	So that the wanted $k_h$ exists, and it is unique, by the universal property of $K_g$ as the pullback of $g$ along itself.
-
-	To prove the second half of the thesis, let us consider the  two rectangles below, which, by \Cref{lem:pb1} are pullbacks.
-\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{h} \ar[d]^{f} & Z \ar[d]^{g} & K_f \ar[r]^{p_{f,2}}  \ar[d]_{p_{f,1}} & X \ar[d]^{f} \ar[r]^{h}& Z \ar[d]^{g}\\
-	X \ar[r]_{f}& Y \ar[r]_{t}& W&  X \ar[r]_f & Y\ar[r]_{t} & W}\]
-
-	But then the following ones are pullbacks too.
- 	\[\xymatrix{K_f \ar@/^.4cm/[rr]^{h\circ p_{f,2}} \ar[r]_{k_h} \ar[d]_{p_{f,1}}& K_g  \ar[r]_{p_{g,2}} \ar[d]_{p_{g,1}} & Z \ar[d]^{g} & K_f \ar@/^.4cm/[rr]^{h\circ p_{f,1}} \ar[r]_{k_h} \ar[d]_{p_{f,2}}& K_g \ar[r]_{p_{g,1}} \ar[d]_{p_{g,2}} & Z \ar[d]^{g}\\X \ar@/_.4cm/[rr]_{t\circ f}\ar[r]^{h}& Z \ar[r]^{g} & W & X \ar@/_.4cm/[rr]_{t\circ f} \ar[r]^{h}& Z \ar[r]^{g}& W}\]
-
- 	The thesis now follows again by \Cref{lem:pb1}.
-\end{proof}
-
-\begin{lemma}\label{lem:salvavita2}
-Let $\cat{C}$ be an $\mathcal{M}$-adhesive category and suppose that the cube below is given, in which every face is a pullback and the bottom one is an $\mathcal{M}$-pushout.
-
- 	\[\xymatrix@C=10pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D}\]
-Then the square below is a pushout.
-\[\xymatrix{K_{a} \ar[r]^{k_{f'}}  \ar[d]_{k_{m'}}& K_b \ar[d]^{k_{n'}}\\ K_c \ar[r]_{k_{g'}} & K_d}\]
-\end{lemma}
-\begin{proof} By \Cref{lem:salvavita2} in the following cube the vertical faces are all pullbacks. 
-		\[\xymatrix@C=10pt@R=10pt{&K_a\ar[dd]|\hole_(.65){p_{a,1}}\ar[rr]^{k_{f'}} \ar[dl]_{k_{m'}} && K_b \ar[dd]^{p_{b,1}} \ar[dl]_{k_{n'}} \\ K_c  \ar[dd]_{p_{c,1}}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){p_{d,1}}\\&A'\ar[rr]|\hole^(.65){f'} \ar[dl]^{m'} && B' \ar[dl]^{n'} \\C' \ar[rr]_{g'} & & D'}\]
-	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
-\end{proof}
-
-\begin{lemma}[Slanting square Lemma]\label{label:lem:salvavita3}
-Let $\cat{C}$ be an $\mathcal{M}$-adhesive category and suppose that the following diagram is given, in which the whole vertical faces are pullbacks, $a$, $b$, $c$ and $d$ are regular epi and the bottom face is a pushout.
-\todo{Sistema il diagramma per renderlo leggibile}
-\[\xymatrix@C=15pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dddd]_(.3){d}\\&A \ar[dd]_{z}\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dd]_{y} \ar[dddl]^{n} \\C \ar[dd]_{x}\ar[ddrr]^(.35){g} & &\\&E\ar[rr]|\hole^(.35){e} \ar[dl]^{t} && F \ar[dl]^{u} \\G \ar[rr]_{v} & & H}\]
-Then the square below is a pushout
-\[\xymatrix{A \ar[r]^{f}\ar[d]_{m}& B \ar[d]^{n}\\ C \ar[r]_{g} & H}\]
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{prop}\label{prop:regepi}
-	Let $e\colon X\to Y$ be a regular epi in a category $\cat{C}$ with a kernel pair $p_1, p_2\colon P\rightrightarrows X$, then $e$ is the coequalizer of $p_1$ and $p_2$.
-\end{prop}
-\begin{proof}
-	By hypothesis there exists a pair $f, g\colon Z\rightrightarrows X$ of which $e$ is the coequalizer, since $e\circ f=e\circ g$ we have a diagram
-	\[\xymatrix{	Z \ar@/^.5cm/[drr]^{f} \ar@/_.5cm/[ddr]_{g} \ar@{.>}[dr]^{k}& &	\\ &P\ar[r]^{p_1} \ar[d]_{p_2} & X \ar[d]^{e} \\& X \ar[r]_{e}  & Y}\]
-	and thus there exists  the dotted $k\colon Z\to P$. Let $h\colon Z\to V$ be an arrow such that $h\circ p_1=h\circ p_2$, then
-	\begin{align*}h\circ f &= h \circ p_1\circ k \\&= h \circ p_2\circ k \\&=h\circ g
-	\end{align*}
-	and thus there exists a unique $l\colon Y\to V$ such that $l\circ e=h$.
-\end{proof}
-
-\begin{cor}\label{cor:regepi1}
-Let $\cat{C}$ be a category with pullbacks and $\phi\colon D\to D'$ be a natural transformation between two functor $D, D'\colon \cat{I}\to \cat{C}$.
-If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
-\end{cor}
-\begin{proof}
-	Let $K_i$ be the kernel pair of $\phi_i$, with projections $p_{1,i}, p_{2,i}\colon K_i\rightrightarrows D(i)$. Given an arrow $f\colon i\to j$ in $\cat{I}$, we have 
-	\begin{align*}
-		\phi_j\circ D(f)\circ p_{1,i}&=D'(f)\circ \phi_i\circ p_{1,i}\\&=D'(f)\circ \phi_i\circ p_{2,i}\\&=\phi_j\circ D(f)\circ p_{2,i}
-	\end{align*}
-
-	Thus the outer boundary of the diagram below commutes, yielding the dotted arrows $K(f)$.
-	\[\xymatrix{K_i \ar@{.>}[dr]^{K(f)}\ar[r]^{p_{1,i}} \ar[d]_{p_{2,i}}& D(i) \ar[dr]^{D(f)}\\D(i) \ar[dr]_{D(f)}&K_j \ar[r]^{p_{1,j}} \ar[d]_{p_{2,j}} & D(j) \ar[d]^{\phi_j}\\ &D(j) \ar[r]_{\phi_j} & D'(j)}\]
-
-	In this way \todo{esercizio per te}.
-We get a functor $E\colon \cat{I}\to \cat{C}$ with two natural transformations $p_{1}, p_2\colon E\rightrightarrows D$.
-By \Cref{prop:regepi} every component  $\phi_i$ of $\phi$ is the coequalizer of $p_{1,i}, p_{2,i}\colon E\rightrightarrows D$ and so $\phi$ is the coequalizer of $p_1$ and $p_2$.
-\end{proof}
-
-\begin{lemma}\label{lem:regepi}
-	Let $D, D'\colon \cat{I}\rightrightarrows  \cat{C}$ be two diagrams diagram with colimiting cocone $(C, \{c_i\}_{i\in \cat{I}})$ and   $(Q, \{q_i\}_{i\in \cat{I}})$.
-If $\phi\colon D\to D'$ is a natural transformation in which all components are regular epis, then the canonical arrow\todo{definisci questa freccia esplicitamente}  $c\colon C\to Q$ is a regular epi to.
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{definition}
-	A \emph{graph with equivalence} is a 6-uple $(A, B, C, s, t, q)$ where $A, B$ and $C$ are set, $s,t\colon A\rightrightarrows B$ are functions and $q\colon B\to C$ is another surjective function.
-
-	A morphism  $(A, B, C, s, t, q)\to (A', B', C', s', t', q')$ is a triple $(h_1, h_2, h_3)$ of functions $h_1\colon A\to A'$, $h_2\colon B\to B'$ and $h_3\colon C\to C'$ making the following diagrams commute.
-
-	\[\xymatrix{A \ar[r]^{s} \ar[d]_{h_1} & B \ar[d]^{h_2} & A \ar[r]^{s} \ar[d]_{h_1}& B \ar[d]^{h_2} & B \ar[d]_{h_2} \ar[r]^{q} & C \ar[d]^{h_3}\\A' \ar[r]_{s'} & B' & A ' \ar[r]_{t'}& B' & B' \ar[r]_{q'} & C'}\]
-
-	In this way we get a category $\EqGrph$.
-\end{definition}
-
-\begin{remark}\label{rem:fedele}
-	There is a faithful functor $U\colon \EqGrph\to \Graph$, forgetting the quotient part. \todo{Questo è per te da dimostrare.}
-\end{remark}
-
-\begin{prop}\label{prop:limits}
-	$\EqGrph$ is complete, cocomplete and $U$ preserves limits and colimits.
-\end{prop}
-
-\begin{remark}\label{rem:ima}\todo{Dimostrala}In $\Set$ we have the following property: for every square as the one below, if $e\colon X\to Y$ is epi and $m\colon M\to Z$ is mono, then there exists a unique dotted arrow $Y\to M$ making the diagram below commutative.
-	\[\xymatrix{X \ar[r]^{f} \ar[d]_{e}& M \ar[d]^{m}\\ Y \ar[r]_{g} & Z}\] 
-\end{remark}
-
-\begin{proof}\todo{Per generalizzare ad altre categorie: serve poter fattorizzare con un epi regolare.} 
-	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$.
-Let $(L, \{l_i\}_{i\in \cat{I}})$ be a limiting cocone of the diagram given by the $Q_i$ \todo{Metti un remark prima dicendo che hai sempre un funtore (tre in realtà) verso $\Set$},
-
-	Now, notice that $(B, \{q_i\circ p_{2,i}\}_{i\in \cat{I}})$ is a cone over the diagram given by the $Q_i$ \todo{Dimostralo}, so that we have an arrow $l\colon B\to L$.
-This arrow is not epi in general, let $Q$ be its image and $q\colon B\to Q$ be the resulting epi and $m\colon Q\to L$ the corresponding mono.
-	By definition the external square in the diagram below commutes, so for every $i\in \cat{I}$, \Cref{rem:ima} yields the dotted arrow $p_{3,i}$.
-	\[\xymatrix{B \ar[r]^{p_{2,i}} \ar[d]_{q}& B_i \ar[r]^{q_i} & Q_i \ar[d]^{id_{Q_i}}\\ Q \ar[r]_{m} \ar@{.>}[urr]_{p_{3,i}}& L \ar[r]_{l_i} & Q_i}\]
-
-	We have to show that in this way we get a cone over the diagram $D$. Let $f\colon i\to j$ be an arrow of $\cat{I}$, then we have:
-	\begin{align*}
-	U(D(f)\circ (p_{1,i}, p_{2, i}, p_{3,i}))&=U(D(f))\circ(p_{1,i}, p_{2, i})\\&=(p_{1,j}, p_{2, j})\\&= U(D(f)\circ (p_{1,j}, p_{2, j}, p_{3,j}))
-	\end{align*}
-	 And faithfulness of $U$ yields the thesis.
-
-	 To see that this cone is terminal, let $(E, F, G, a, b, c)$ be another graph with the vertex of a cone with sides $(t_{1,i},t_{2, i}, t_{3,i})$.
-By construction, we have an arrow $(t_1, t_2)\colon (E, F, a, b)\to (A, B, s, t)$ such that
-	 \[\xymatrix{&E \ar@{.>}[dl]_{t_1} \ar[dr]^{t_{1,i}}&&&F \ar@{.>}[dl]_{t_2} \ar[dr]^{t_{2,i}}\\ A \ar[rr]_{p_{1,i}} & & A_i & B \ar[rr]_{p_{2,i}}&& B_i }\]
-
-	Let now $g$ and $g'$ be two elements of $F$ such that $c(g)=c(g')$, then for every $i\in \cat{I}$
-	\begin{align*}
-		q_i(p_{2,i}(t_2(g)))&=q_i(t_{2,i}(g))\\&=t_{3, i}(c(g))\\&=t_{3, i}(c'(g))\\&=q_i(t_{2,i}(g'))\\&=	q_i(p_{2,i}(t_2(g')))
-	\end{align*}
-
-	Thus $t_2(g)\sim t_2(g')$, so that we have a, unique, dotted arrow $t_3\colon G\to Q$ as below
-
-	\[\xymatrix{ F \ar[d]_{t_{2}} \ar[r]^{c} & G \ar@{.>}[d]^{t_{3}}\\ B \ar[r]_{q} & Q}\]
-
-	Faithfulness \todo{esercizio per te: scrivere la dimostrazione di queste ultime due righe}of $U$ now guarantees that $(t_1, t_2, t_3)$ is the unique arrow such that $(p_{1,i}, p_{2,i}, p_{3,i})\circ(t_1, t_2, t_3)=(t_{1,i},t_{2, i}, t_{3,i})$.
-
-	\todo{esercizio per te: fare i colimiti.
-Hint: la dimostrazione è diversa ma più semplice.
-Se $(A, B, s,t)$ è il colimite di $U\circ D$ puoi considerare il colimite $Q$ dei vari $Q_i$.
-Per la proprietà del colimite hai una freccia $B\to Q$, mostra che è epi (segue in una riga dai risultati che abbiamo).}
-\end{proof}
-
-\begin{cor}
-	An arrow $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ in $\EqGrph$ is mono if and only if $h_1$ and $h_2$ are mono in $\Set$.
-\end{cor}
-\begin{proof}
-	\todo{esercizio per te, usa fedeltà e continuità}
-\end{proof}
-
-\begin{cor}Let $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ be a morphism of $\EqGrph$, then the following are equivalent:
-	\begin{enumerate}
-		\item $(h_1, h_2, h_3)$ is a regular mono;
-		\item $h_1$, $h_2$, $h_3$ are all monos;
-		\item $h_1$ and $h_2$ are mono and for every $f, f'\in F$, $c(h_2(f))=c(h_2(f'))$ if and only if $q(f)=q(f')$.
-	\end{enumerate}
-\end{cor}
-\begin{proof}
-	$1\Rightarrow 2.$ \todo{Esercizio}
-
-	\smallskip \noindent
-	$2\Rightarrow 3.$ \todo{Esercizio}
-
-	\smallskip \noindent 
-	$3\Rightarrow 1.$\todo{Esercizio}
-\end{proof}
-
-Let us turn to another functor $\EqGrph\to \Graph$.
-
-\begin{definition}
-The \emph{quotient functor} $Q:\EqGrph\to \Graph $ sends $(A, B, C, s,t, q)$ to $(A, C, q\circ s, q\circ t)$ and an arrow $(h_1, h_2, h_3) \colon (A, B, C, s,t, q)\to (E, F, G, a,b, c)$ to $(h_1, h_3)$.
-\end{definition}
-
-\todo{Verifica che questa cosa funziona $(h_1, h_3)$ è un morfismo di grafi?}
-
-\begin{lemma}
-	$Q$ is a left  adjoint.
-\end{lemma}
-\begin{proof} Let us start proving that $Q$ is a left adjoint.
-Let $R(A,B, s, t)$ be $(A, B, B, s,t, id_{B})$ , so that $Q(R(A,B,s,t))=(A,B,s,t)$.
-Now, suppose that an arrow $(h_1, h_2)\colon Q(E,F,G, a,b,c)\to (A,B, s,t)$ is given.
-Consider the triple $(h_1, h_2, h_2\circ c)$.
-Notice that, since $(h_1, h_2)$ is an arrow in $\Graph$:
-	\[h_2\circ c\circ a= s\circ h_1 \qquad  h_2\circ c\circ b= t\circ h_1\]
-
-	 Then we have three squares:
-
-\[\xymatrix{E \ar[r]^{a} \ar[d]_{h_1} & F \ar[d]^{h_2\circ c} & E \ar[r]^{b} \ar[d]_{h_1}& F \ar[d]_{h_2\circ c} & B \ar[d]_{h_2\circ c} \ar[r]^{c} & C \ar[d]^{h_2}\\A \ar[r]_{s} & B & A  \ar[r]_{t}& B & B \ar[r]_{id_B} & B}\]
-
-	 We have therefore found a morphism $(E,F,G, a,b,c)\to R(A,B,s,t)$ whose image through $Q$ fits in the diagram below.
-	\[\xymatrix{(A, B, s,t)\ar[r]^{(id_A, id_B)} &(A, B, s,t)\\ (E, G, q\circ s, q\circ t) \ar[ur]_{(h_1, h_2)} \ar[u]^{Q(h_1, h_2\circ q, h_2)}}\]
-
-\todo{Esercizio: prova unicità (è facile)}
-\end{proof}
-
-\begin{prop}
-	$Q$ creates colimits.
-\end{prop}
-\begin{proof}
-	\todo{esercizio per te (devi verificare solo la riflessione: ma dato un diagramma in grafi fatto di quozienti, come costruisci un insieme di vertici per il colimite?)}
-\end{proof}
-
-\subsection{Adhesivity of $\EqGrph$}
-
-\begin{lemma}\label{lem:stab}
-In $\EqGrph$ pushouts along regular monos are stable.
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}\label{lem:vk}
-In $\EqGrph$ pushouts along regular monos are Van Kampen.
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-From \Cref{prop:limits} and \Cref{lem:stab,lem:vk} we deduce at once the following.
-
-\begin{cor}\label{cor:equi}
-	$\EqGrph$ is quasiadhesive.
-\end{cor}
-
-\color{black}
 \section{Graphs with Equivalences}

### 2024-10-24 Article/Graph_sections/Graphs.tex
Reordered files + new version EqGrph

@@
 
-We can then generalize such notion to something more abstract, considering a graph nothing more than a presheaf from the category $(E \rightrightarrows V)$ to the category of sets.
+We can then generalize such notion to something more abstract, considering a graph to be nothing more than a presheaf from the category $(E \rightrightarrows V)$ to the category of sets.
 Having two of such presheaves, a natural transformation from one to another encapsulates the behavior of a graph morphism due to naturality. We can now define the category of graphs.

### 2024-10-26 Article/Background_sections/Adhesivity.tex
section on kernel pairs + some proofs

@@
 \end{proof}
+
+\begin{cor}\label{cor:adhesivity_functor_categories}
+    Let $\cat A$ be a $\mathcal M$-adhesive category for some $\mathcal M \subseteq \Hom(\cat A)$.
+Then, for every other category $\cat C$, the functor category $[\cat C, \cat A]$ is $\mathcal M^{\cat C}$-adhesive, where
+    \[
+        \mathcal{M}^\cat C = \{\eta \in \Hom([\cat C, \cat A]) \mid \eta_C \in \mathcal M \textit{ for each object $C$ of $\cat C$ }\}
+    \]
+\end{cor}
+
+Since $\Set$ is adhesive, we can conclude what follows.
+
+\begin{cor}\label{cor:presh_adhesive}
+    Every category of presheaves is adhesive.
+\end{cor}

### 2024-10-26 Article/Background_sections/Basic_Notions.tex
section on kernel pairs + some proofs

@@
 
+The next proposition will be useful later.
+
+\begin{prop}\label{prop:prop_epi_mono_Set}
+    In $\Set$, for every commutative square as the one below, if $e: X \to Y$ is epi and $m: M \to Z$ is mono, then there exists a unique morphism $h: Y \to M$ making the whole diagram below commutative.
+    \[
+        \begin{tikzcd}
+            X \ar[r, "f"] \ar[d, "e"swap] & M \ar[d, "m"] \\
+            Y \ar[ur, dashed, "h"] \ar[r, "g"swap] & Z
+        \end{tikzcd}
+    \]
+\end{prop}
+
+\begin{proof}
+    Before we start proving the statement, we have to note that, given a function $t: A \to B$, it is possible to decompose it as a composition of a injective function and a surjective function, considering the function $A \to t(A)$ sending each element onto its image along $t$, and then applying the inclusion $t(A) \to B$, and such functions are unique.
+Another way to factorize $t$ is via a composition of a surjective function and an injective function.
+Consider the equivalence relation $\sim$ defined on $A$, where $a \sim a'$ whenever $t(a) = t(a')$.
+This equivalence relation induces a map $A \to A/_\sim$, which is surjective.
+The function $A/_\sim \to B$, mapping each equivalence class onto its image along $t$ is then injective, and this factorization in unique too.
+
+    Let now be $f = f_i \circ f_s$ be the decomposition of $f$ with $f_s$ surjective (i.e., epi in $\Set$) and $f_i$ injective (i.e., mono in $\Set$), and $g = g_i \circ g_s$ be the decomposition of $g$ with $g_i$ injective and $g_s$ surjective, having the following situation.
+    \[
+        \begin{tikzcd}
+            X \ar[r, "{f_s}"] \ar[d, "e"] & f(X) \ar[r, "{f_i}"] & M \ar[d, "m"] \\
+            Y \ar[r, "{g_i}"swap] \ar[urr, "h"]& Y/_\sim \ar[r, "{g_s}"swap] & Z
+        \end{tikzcd}
+    \]
+    For the diagram above to commute, must be $f_i \circ f_s = h \circ e$ and $g_s \circ g_i = m \circ h$\todo{completare!!!}
+\end{proof}
+
 \subsection{Categories from other categories}\label{ssect:cats_from_cats}
@@
 Composition and identities are defined pairwise: $(f, g) \circ (h, k) = (f \circ h, g \circ k)$, and $id_{(A, B)} = (id_A, id_B)$.
-
 \end{definition}

### 2024-10-26 Article/Background_sections/Limit.tex
section on kernel pairs + some proofs

@@
 
+The dual of the proposition above states that a coequalizer is an epimmorphism.
+
 Of all monomorphisms, an interesting subclass of them is the one that contains only the equalizers.
 
-\begin{definition}[Regular Monomorphism]\label{def:reg_mono}
-    A monomorphism that is an equalizer for a pair of arrows is said \emph{regular monomorphism}. The class of all regular monomorphisms of a category $\cat C$ is denoted $\Reg(\cat C)$.
+\begin{definition}[Regular Monomorphism, Regular Epimorphism]\label{def:reg_mono}
+    A monomorphism that is an equalizer for a pair of arrows is said \emph{regular monomorphism}.
+The class of all regular monomorphisms of a category $\cat C$ is denoted $\Reg(\cat C)$.
+An epimorphism that is a coequalizer for a pair of arrows is said \emph{regular epimorphism}.
 \end{definition}
@@
 
+\begin{cor}\label{cor:cube} 
+    Let $\cat{C}$ be a category and suppose that  the solid part of the following cube is given
+	\[\begin{tikzcd}[row sep=13 pt, column sep=13 pt]
+    	& {Y'} && {Z'} \\
+    	{B'} && {C'} \\
+    	& Y && Z \\
+    	B && C
+    	\arrow["{g'}", from=1-2, to=1-4]
+    	\arrow["{q'}"', dashed, from=1-2, to=2-1]
+    	\arrow["y"'{pos=0.8}, from=1-2, to=3-2]
+    	\arrow["{r'}", from=1-4, to=2-3]
+    	\arrow["z", from=1-4, to=3-4]
+    	\arrow["{k'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+    	\arrow["b"', from=2-1, to=4-1]
+    	\arrow["c"{pos=0.7}, from=2-3, to=4-3]
+    	\arrow["g"{pos=0.3}, from=3-2, to=3-4]
+    	\arrow["q"'{pos=0.2}, from=3-2, to=4-1]
+    	\arrow["r", from=3-4, to=4-3]
+    	\arrow["k"', from=4-1, to=4-3]
+        \end{tikzcd}\]
+	If the front face is a pullback then there is a unique $q'\colon Y'\to B'$ filling the diagram.
+If, moreover, the other two vertical faces are also pullbacks, then the following square is a pullback too.
+	\[\begin{tikzcd}
+	    Y' \ar[r, "{q'}"] \ar[d, "y"swap] & B' \ar[d,"b"] \\
+            Y \ar[r, "q"swap] & B
+	\end{tikzcd}\]
+\end{cor}
+\begin{proof}
+	Let us compute:
+	\begin{align*}
+            c\circ r'\circ g'   &=  r\circ z \circ g'   \\
+                                &=  r\circ g \circ y    \\
+                                &=k\circ q \circ y
+	\end{align*}
+	Since the front face is a pullback, this guarantees the existence of $q'$.  The second half of the thesis follows applying \Cref{lemma:pullback_lemma} to the following rectangle.
+	\[\begin{tikzcd}[row sep=15 pt, column sep=15 pt]
+	{Y'} && {B'} && {C'} \\
+	\\
+	Y && B && C
+	\arrow["{q'}"', from=1-1, to=1-3]
+	\arrow["{r' \circ g'}", bend left = 30, from=1-1, to=1-5]
+	\arrow["y"', from=1-1, to=3-1]
+	\arrow["{k'}"', from=1-3, to=1-5]
+	\arrow["b", from=1-3, to=3-3]
+	\arrow["c", from=1-5, to=3-5]
+	\arrow["q", from=3-1, to=3-3]
+	\arrow["{r \circ g}"', bend right=30, from=3-1, to=3-5]
+	\arrow["k", from=3-3, to=3-5]
+\end{tikzcd}\]
+\end{proof}
+
 The connection between constructions as products and equalizers and limits is made clear by the following theorem.
@@
 \end{remark}
+
+\subsection{Kernel pairs}
+
+\begin{definition}[Kernel Pair]
+    A \emph{kernel pair} for an arrow $f: A \to B$ is an object $K_f$ together with two arrows $\pi_1^f, \pi_2^f : K_f \to A$, denoted as $(K_f, \pi_1^f, \pi_2^f)$, such that the following square is a pullback.
+    \[
+        \begin{tikzcd}
+            K_f \ar[r, "{\pi_1^f}"] \ar[d, "{\pi_2^f}" swap] & A \arrow[d, "f"] \\
+            A \ar[r, "f"swap] & B
+        \end{tikzcd}
+    \]
+\end{definition}
+
+\begin{remark}
+	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
+\end{remark}
+
+\begin{prop}\label{prop:kermono}
+	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
+\end{prop}
+
+\begin{proof}
+    To prove the ``if'' part of the statement, let $f, g: A \to M$ be such that $m\circ f = m\circ g$, and consider the following situation.
+    \[
+        \begin{tikzcd}
+        A \arrow[drr, bend left=20, "f"] \arrow[ddr, bend right=20,"g" swap] \arrow[dr, dashed, "u"] & & \\
+        & M  \arrow[d, "{id_M}" swap] \arrow[r, "{id_M}"] & M \arrow[d, "m"] \\
+        & M  \arrow[r, "m" swap] & X
+        \end{tikzcd}
+    \]
+    For the universal property of pullbacks, we have that $$f  =  id_M \circ u =  g$$
+    Hence, $m$ is mono.
+
+    Conversely, if $m$ is mono, then, we have that
+    \begin{align*}
+        m \circ f = m \circ g   &\Rightarrow    f = g \\
+                                &\Rightarrow    f \circ id_M = g\circ id_M
+    \end{align*}
+    Hence, $f$ is the unique arrow that makes the commutative square illustrated above a pushout.
+\end{proof}
+
+\begin{cor}\label{cor:kermono}
+	Let $(K_f, \pi^f_i), \pi^f_2)$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, \pi^f_1, \pi^f_2)$ is a kernel pair also for $m\circ f$.
+\end{cor}
+\begin{proof}
+    It is enough to see that, by \Cref{lemma:pullback_lemma} and \Cref{prop:kermono} the outer boundary of the following square is a pullback.
+        \[\begin{tikzcd}[row sep=13 pt, column sep=13 pt]
+    	{K_f} && X && X \\
+    	\\
+    	X && Y && Y \\
+    	\\
+    	X && Y && Z
+    	\arrow["{\pi_f^2}", from=1-1, to=1-3]
+    	\arrow["{\pi_f^2}"', from=1-1, to=3-1]
+    	\arrow["{id_X}", from=1-3, to=1-5]
+    	\arrow["f", from=1-3, to=3-3]
+    	\arrow["f", from=1-5, to=3-5]
+    	\arrow["f", from=3-1, to=3-3]
+    	\arrow["{id_X}"', from=3-1, to=5-1]
+    	\arrow["{id_Y}", from=3-3, to=3-5]
+    	\arrow["{id_Y}", from=3-3, to=5-3]
+    	\arrow["m", from=3-5, to=5-5]
+    	\arrow["f"', from=5-1, to=5-3]
+    	\arrow["m"', from=5-3, to=5-5]
+    \end{tikzcd}\]
+\end{proof}
+
+\begin{lemma}
+    Suppose the following situation, and that $f: X \to Y$ and $g: Z \to W$ have kernel pairs.
+    \[
+        \begin{tikzcd}
+            X \ar[r, "h"] \ar[d, "f"swap] & Z \ar[d, "g"] \\
+            Y \ar[r, "t"swap] & W
+        \end{tikzcd}
+    \]
+
+    Then, there exists a unique arrow $k_h: K_f \to K_g$ making the squares below commute.
+    \[
+        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
+            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^1}"swap] & K_g \ar[d, "{\pi_g^1}"] \\
+            X \ar[r, "h"swap] & Z 
+        \end{tikzcd}
+        \qquad
+        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
+            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^2}"swap] & K_g \ar[d, "{\pi_g^2}"] \\
+            X \ar[r, "h"swap] & Z 
+        \end{tikzcd}
+    \]
+
+    Moreover, if the beginning square is a pullback, then also the preceding ones are so.
+\end{lemma}
+
+\begin{proof}
+    Computing, we have
+    \begin{align*}
+        g \circ h \circ \pi_f^1 &=  t \circ f \circ \pi_f^1     \\
+                                &=  t \circ f \circ \pi_f^2     \\
+                                &=  g \circ h \circ \pi_f^2
+    \end{align*}
+    By the universal property of $K_g$ as the pullback of $g$ along itself, such $k_h$ exists and it is unique.
+
+    To prove the second half of the thesis, let us consider the two rectangles below, which, by \Cref{lemma:pullback_lemma} are pullbacks.
+    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
+	{K_f} & X & Z \\
+	X & Y & W
+	\arrow["{\pi_f^1}", from=1-1, to=1-2]
+	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
+	\arrow["h", from=1-2, to=1-3]
+	\arrow["f", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["f"', from=2-1, to=2-2]
+	\arrow["t"', from=2-2, to=2-3]
+    \end{tikzcd}
+    \qquad
+    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
+	{K_f} & X & Z \\
+	X & Y & W
+	\arrow["{\pi_f^2}", from=1-1, to=1-2]
+	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
+	\arrow["h", from=1-2, to=1-3]
+	\arrow["f", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["f"', from=2-1, to=2-2]
+	\arrow["t"', from=2-2, to=2-3]
+    \end{tikzcd}
+    \]
+    But then the following ones are pullbacks too.
+    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
+	{K_f} & {K_g} & Z \\
+	X & Y & W
+	\arrow["{k_h}"', from=1-1, to=1-2]
+	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
+	\arrow["{\pi_g^2}"', from=1-2, to=1-3]
+	\arrow["{\pi_g^1}", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["h", from=2-1, to=2-2]
+	\arrow["g", from=2-2, to=2-3]
+        \arrow["{h\circ \pi_f^2}", from=1-1, to=1-3, bend left = 30]
+        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
+    \end{tikzcd}
+    \qquad
+    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
+	{K_f} & {K_g} & Z \\
+	X & Y & W
+	\arrow["{k_h}"', from=1-1, to=1-2]
+	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
+	\arrow["{\pi_g^1}"', from=1-2, to=1-3]
+	\arrow["{\pi_g^2}", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["h", from=2-1, to=2-2]
+	\arrow["g", from=2-2, to=2-3]
+        \arrow["{h\circ \pi_f^1}", from=1-1, to=1-3, bend left = 30]
+        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
+    \end{tikzcd}
+    \]
+
+    The thesis follows again by \Cref{lemma:pullback_lemma}.
+\end{proof}
+
+\begin{cor}
+    Let $\cat C$ be a category with pullbacks and $\phi : D \to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
+If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
+\end{cor}
+
+\begin{proof}
+    TODO
+\end{proof}

### 2024-10-26 Article/Graph_sections/Eq_Graphs_Notes_Results.tex
section on kernel pairs + some proofs

\color{blue}

\section{Graphs with equivalences - notes and results}

\subsection{Some results on kernel pair and regular epis}
\todo{Questi risultati vanno completati e distribuiti lungo la tesi: quello sui kernel pair nella parte sui pullback, quello sugli epi regolari nella parte sui coequalizzatori, quelli che riguardano l'adesività nella relativa sezione}

\todo{Sicuramente devi anche mettere dei riferimenti ai risultati della sez. sull'adesività (tipo alla proposizione che gli M-pushout sono pullback)}

\begin{lemma}\label{lem:pb1}
	Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
	\[\xymatrix{X\ar[r]^{f} \ar[d]_{t} & Y \ar[d]^{k}\ar[r]^{g} &Z \ar[d]^{h}\\A \ar[r]_{a}& B \ar[r]_{b} & C}\]
\end{lemma}
\begin{proof}
	\todo{Esercizio per te}
\end{proof}

\begin{cor}\label{cor:cube} Let $\cat{C}$ be a category and suppose that  the solid part of the following cube is given
	\[\xymatrix@C=13pt@R=13pt{&Y'\ar[dd]|\hole_(.65){y}\ar[rr]^{g'} \ar@{.>}[dl]_{q'} && Z' \ar[dd]^{z} \ar[dl]_{r'} \\ B'  \ar[dd]_{b}\ar[rr]^(.65){k'} & & C' \ar[dd]_(.3){c}\\&Y\ar[rr]|\hole^(.65){g} \ar[dl]^{q} && Z \ar[dl]^{r} \\B \ar[rr]_{k} & & C}\]
	If the front face is a pullback then there is a unique $q'\colon Y'\to B'$ filling the diagram. If, moreover, the other two vertical faces are also pullbacks, then the following square is a pullback too.
	\[\xymatrix{Y' \ar[r]^{q'} \ar[d]_{y}& B'\ar[d]^{b}\\ Y \ar[r]_{q} & B}\]
\end{cor}
\begin{proof}
	Let us compute:
	\begin{align*}
		c\circ r'\circ g'&=r\circ z \circ g'\\&=r\circ g \circ y\\&=k\circ q \circ y
	\end{align*}
	Since the front face is a pullback, this guarantees the existence of $q'$.  The second half of the thesis follows applying \cref{lem:pb1} to the following rectangle.
	\[\xymatrix{Y'\ar@/^.4cm/[rr]^{r'\circ g'} \ar[r]_{q'} \ar[d]_{y}& B'\ar[d]_{b}\ar[r]_{k'}& C'\ar[d]^{c}\\ Y\ar@/_.4cm/[rr]_{r\circ g} \ar[r]^{q} & B \ar[r]^{k}& C}\]
\end{proof}

\iffalse 
In an $\mathcal{M}$-adhesive category, pullbacks also enjoy a kind of left cancellation property.

\begin{lemma}\label{lem:pb2}
	Let $\cat{C}$ be a category with pullbacks, given the following diagrams:
	\[
	\xymatrix{Y\ar[r]^{f_2} \ar[d]_{f_1} & X_2 \ar[d]^{r_2} & Z_1 \ar[d]_{x_1}\ar[r]^{z_1} & W \ar[r]^{w} \ar[d]_{r} & Q'\ar[d]^{q} & Z_2 \ar[d]_{x_2} \ar[r]^{z_2}  & W  \ar[r]^{w} \ar[d]_{r}  & Q' \ar[d]^{q}\\ X_1 \ar[r]_{r_1} &R  & X_1 \ar[r]_{r_1} & R \ar[r]_{s}  & Q& X_2 \ar[r]_{r_2} & R \ar[r]_{s} & Q}\]
	if the first square is a stable pushout and the whole rectangles and their left halves are pullbacks, then their common right half is a pullback too.
\end{lemma}
\begin{proof}Pulling back  $q$ along $s$ we get a square 
	\[\xymatrix{U \ar[r]^{u} \ar[d]_{h}& Q' \ar[d]^{q}\\ R \ar[r]_s & S}\]
	Notice that
	\[
	q\circ w\circ z_1=s\circ r_1\circ x_1 \qquad 
	q\circ w\circ z_2=s\circ r_2\circ x_2 \]
	Thus we get $u_1\colon Z_1\to U$ and $u_2\colon Z_2\to U$ fitting in the rectangles
	\[\xymatrix{  Z_1  \ar@/^.4cm/[rr]^{w\circ z_1}\ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q}&  Z_2 \ar@/^.4cm/[rr]^{w\circ z_2} \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\  X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	which, by hypothesis and  \cref{lem:pb1} have left halves which are pullbacks. Now,
	\[s\circ r_1\circ f_1 =s\circ r_2\circ f_2\]
	Pulling back $q$ along this arrow we get another square
	\[\xymatrix@C=40pt{Z'_0 \ar[r]^{t} \ar[d]_{y}& Q' \ar[d]^{q}\\ R \ar[r]_{s\circ r_1\circ f_1} & S}\]
	In particular, we obtain the dotted $b_1\colon Z'_0\to Z_1$ and $b_2\colon Z'_0\to Z_2$ in
	\[\xymatrix@C=30pt{ Z'_0 \ar@/^.4cm/[rrr]^{t}\ar[d]_{y} \ar@{.>}[r]_{b_1} & Z_1  \ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q} &Z'_0 \ar@/^.4cm/[rrr]^{t} \ar[d]_{y}\ar@{.>}[r]_{b_2}  & Z_2  \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	in which, using again \cref{lem:pb1}, all of the squares on the bottom rows are pullbacks.

	We are going to construct another row above these two rectangles. By hypothesis 
	\[q\circ w = s\circ r\]
	Thus there exists a unique $g\colon W\to U$ such that
	\[r=h\circ g \qquad w=u\circ g\]
	Moreover, we also have that
	\[\begin{split}h\circ g \circ z_1&=r \circ z_1\\&= r_1\circ x_1 \\&=h\circ u_1
	\end{split}\qquad\begin{split}h\circ g \circ z_2&=r \circ z_2\\&= r_2\circ x_2 \\&=h\circ u_2
	\end{split}\]
	and 
	\[\begin{split}u\circ g \circ z_1&=w \circ z_1\\&= u\circ u_1 
	\end{split} \qquad \begin{split}u\circ g \circ z_1&=w \circ z_2\\&= u\circ u_2
	\end{split}\]
	which together show that
	\[g\circ z_1=u_1 \qquad g\circ z_2=u_2\]

	Summing up, we can depict all the arrows we have constucted so far in the following diagrams
	\[\xymatrix{Z'_0 \ar[r]^{b_1} \ar[d]_{id_{Z'}}& Z_1 \ar[r]^{z_1} \ar[d]_{id_{Z_1}} &  W \ar[d]_g \ar[r]^{w} & Q' \ar[d]^{id_{Q'}}&& Z'_0 \ar[r]^{b_2}  \ar[d]_{id_{Z'}}& Z_2 \ar[d]_{id_{Z_2}} \ar[r]^{z_2}&  W \ar[d]_g\ar[r]^{w}& Q' \ar[d]^{id_{Q'}}\\ Z'_0 \ar[d]_{y} \ar[r]^{b_1} & Z_1  \ar[r]^{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]^{u} & Q'  \ar[d]^{q}& &Z'_0  \ar[d]_{y}\ar[r]^{b_2}  & Z_2  \ar[r]^{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]^{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & &Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	If we show that $g$ is an isomorphism we are done. Consider the cubes
	\[\xymatrix@C=13pt@R=13pt{&Z_0'\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{z_2}  &&Z'_0\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{F_j(b)} \ar[dl]_{u_2}\\Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){z_1} & & W \ar[dd]_(.3){r}&& Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){u_1} & &U \ar[dd]_(.3){h}\\&Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2} && Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2}\\X_1 \ar[rr]_{r_1} & & R && X_1 \ar[rr]_{r_1} & & R}\]
	in which the vertical faces are pullbacks. Since the bottom face is a stable pushout we can deduce that
	\[\xymatrix{Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{z_2} & Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{u_2}\\ Z_1 \ar[r]_{z_1}& W & Z_1 \ar[r]_{u_1}& U }\]
	are pushout squares too. The arrow $g$ fits in the following  diagram
	\[\xymatrix{Z'_0\ar[r]^{b_2} \ar[d] _{b_1}& Z_2 \ar@/^.3cm/[ddr]^{u_2}\ar[d]^{z_2} \\ Z_1 \ar[r]_{z_1}  \ar@/_.3cm/[drr]_{u_1}& W \ar[dr]^{g} \\ &&U}\]
	and thus it is an isomorphism.
\end{proof} 
\fi

\begin{definition}A \emph{kernel pair} $(K_f, p_{f, 1}, p_{f,2})$ for an arrow $f\colon X\to Y$ is an object $K_f$ with two arrows $p_{f,1}, p_{f, 2}\colon K_f\to X$ making the following square a pullback.
	\[\xymatrix{K_f \ar[r]^{p_{f,1}} \ar[d]_{p_{f,2}}& X \ar[d]^{f}\\ X \ar[r]_{f} & Y}\]
\end{definition}

\begin{remark}
	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
\end{remark}

\begin{prop}\label{prop:kermono}
	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
\end{prop}
\begin{proof}\todo{esercizio}
\end{proof}

\begin{cor}\label{cor:kermono}
	Let $(K_f, p_{f,1}, p_{f,2})$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, p_{f,1}, p_{f,2})$ is a kernel pair also for $m\circ f$.
\end{cor}
\begin{proof}
	It is enough to see that, by \Cref{lem:pb1,prop:kermono} the outer boundary of the following square is a pullback.
	\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{id_X} \ar[d]_{f}&X\ar[d]^{f} \\X \ar[d]_{id_X} \ar[r]_{f} & Y \ar[d]_{id_Y} \ar[r]_{id_Y}& Y \ar[d]^{m}\\X \ar[r]_{f} & Y \ar[r]_{m} & Z}\]

\end{proof}

\begin{lemma}\label{lem:salvavita1}
Suppose that the following square is given and that $f\colon X\to Y$ and $g\colon Z\to W$ have kernel pairs.
\[\xymatrix{X \ar[d]_{f}\ar[r]^{h}& Z \ar[d]^{g} \\ Y \ar[r]_{t}& W}\]

Then there exists a unique arrow $k_h\colon K_f\to K_g$ making the squares below commutes.

\[\xymatrix{K_f \ar[d]_{p_{f, 1}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,1}} & K_f \ar[d]_{p_{f,2}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,2}} \\ X \ar[r]_{h}& Z & X \ar[r]_{h}& Z}\]

Moreover, if the beginning square is a pullback, then also the preceding ones are so.
\end{lemma}
\begin{proof}
	Computing we have
	\begin{align*}
		g\circ h\circ p_{f,1}&=t\circ f\circ p_{f,1}\\&=t\circ f\circ p_{f,2}\\&=g\circ h\circ p_{f,2}
	\end{align*}
	So that the wanted $k_h$ exists, and it is unique, by the universal property of $K_g$ as the pullback of $g$ along itself.

	To prove the second half of the thesis, let us consider the  two rectangles below, which, by \Cref{lem:pb1} are pullbacks.
\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{h} \ar[d]^{f} & Z \ar[d]^{g} & K_f \ar[r]^{p_{f,2}}  \ar[d]_{p_{f,1}} & X \ar[d]^{f} \ar[r]^{h}& Z \ar[d]^{g}\\
	X \ar[r]_{f}& Y \ar[r]_{t}& W&  X \ar[r]_f & Y\ar[r]_{t} & W}\]

	But then the following ones are pullbacks too.
 	\[\xymatrix{K_f \ar@/^.4cm/[rr]^{h\circ p_{f,2}} \ar[r]_{k_h} \ar[d]_{p_{f,1}}& K_g  \ar[r]_{p_{g,2}} \ar[d]_{p_{g,1}} & Z \ar[d]^{g} & K_f \ar@/^.4cm/[rr]^{h\circ p_{f,1}} \ar[r]_{k_h} \ar[d]_{p_{f,2}}& K_g \ar[r]_{p_{g,1}} \ar[d]_{p_{g,2}} & Z \ar[d]^{g}\\X \ar@/_.4cm/[rr]_{t\circ f}\ar[r]^{h}& Z \ar[r]^{g} & W & X \ar@/_.4cm/[rr]_{t\circ f} \ar[r]^{h}& Z \ar[r]^{g}& W}\]

 	The thesis now follows again by \Cref{lem:pb1}.
\end{proof}

\begin{lemma}\label{lem:salvavita2}
Let $\cat{C}$ be an $\mathcal{M}$-adhesive category with all pullbacks and suppose that the cube below is given, in which every face is a pullback and the bottom one is an $\mathcal{M}$-pushout.

 	\[\xymatrix@C=10pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D}\]
Then the square below is a pushout.
\[\xymatrix{K_{a} \ar[r]^{k_{f'}}  \ar[d]_{k_{m'}}& K_b \ar[d]^{k_{n'}}\\ K_c \ar[r]_{k_{g'}} & K_d}\]
\end{lemma}
\begin{proof} By \Cref{lem:salvavita1} in the following cube the vertical faces are all pullbacks. 
		\[\xymatrix@C=10pt@R=10pt{&K_a\ar[dd]|\hole_(.65){p_{a,1}}\ar[rr]^{k_{f'}} \ar[dl]_{k_{m'}} && K_b \ar[dd]^{p_{b,1}} \ar[dl]_{k_{n'}} \\ K_c  \ar[dd]_{p_{c,1}}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){p_{d,1}}\\&A'\ar[rr]|\hole^(.65){f'} \ar[dl]^{m'} && B' \ar[dl]^{n'} \\C' \ar[rr]_{g'} & & D'}\]
	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
\end{proof}

\begin{prop}\label{prop:regepi}
	Let $e\colon X\to Y$ be a regular epi in a category $\cat{C}$ with a kernel pair $p_1, p_2\colon P\rightrightarrows X$, then $e$ is the coequalizer of $p_1$ and $p_2$.
\end{prop}
\begin{proof}
	By hypothesis there exists a pair $f, g\colon Z\rightrightarrows X$ of which $e$ is the coequalizer, since $e\circ f=e\circ g$ we have a diagram
	\[\xymatrix{	Z \ar@/^.5cm/[drr]^{f} \ar@/_.5cm/[ddr]_{g} \ar@{.>}[dr]^{k}& &	\\ &P\ar[r]^{p_1} \ar[d]_{p_2} & X \ar[d]^{e} \\& X \ar[r]_{e}  & Y}\]
	and thus there exists  the dotted $k\colon Z\to P$. Let $h\colon Z\to V$ be an arrow such that $h\circ p_1=h\circ p_2$, then
	\begin{align*}h\circ f &= h \circ p_1\circ k \\&= h \circ p_2\circ k \\&=h\circ g
	\end{align*}
	and thus there exists a unique $l\colon Y\to V$ such that $l\circ e=h$.
\end{proof}

\begin{cor}\label{cor:regepi1}
Let $\cat{C}$ be a category with pullbacks and $\phi\colon D\to D'$ be a natural transformation between two functor $D, D'\colon \cat{I}\to \cat{C}$. If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
\end{cor}
\begin{proof}
	Let $K_i$ be the kernel pair of $\phi_i$, with projections $p_{1,i}, p_{2,i}\colon K_i\rightrightarrows D(i)$. Given an arrow $f\colon i\to j$ in $\cat{I}$, we have 
	\begin{align*}
		\phi_j\circ D(f)\circ p_{1,i}&=D'(f)\circ \phi_i\circ p_{1,i}\\&=D'(f)\circ \phi_i\circ p_{2,i}\\&=\phi_j\circ D(f)\circ p_{2,i}
	\end{align*}

	Thus the outer boundary of the diagram below commutes, yielding the dotted arrows $K(f)$.
	\[\xymatrix{K_i \ar@{.>}[dr]^{K(f)}\ar[r]^{p_{1,i}} \ar[d]_{p_{2,i}}& D(i) \ar[dr]^{D(f)}\\D(i) \ar[dr]_{D(f)}&K_j \ar[r]^{p_{1,j}} \ar[d]_{p_{2,j}} & D(j) \ar[d]^{\phi_j}\\ &D(j) \ar[r]_{\phi_j} & D'(j)}\]

	In this way \todo{esercizio per te}we get a functor $E\colon \cat{I}\to \cat{C}$ with two natural transformations $p_{1}, p_2\colon E\rightrightarrows D$. By \Cref{prop:regepi} every component  $\phi_i$ of $\phi$ is the coequalizer of $p_{1,i}, p_{2,i}\colon E\rightrightarrows D$ and so $\phi$ is the coequalizer of $p_1$ and $p_2$.
\end{proof}

\todo{COSE DA FARE: nel capitolo 1 metti una proposizione in cui mostri che da ogni trasf naturale $D\to D'$ puoi ricavare una freccia tra i colimiti, così in questa e nelle altre proposizioni puoi citarla.}

\begin{lemma}\label{lem:regepi}
	Let $D, D'\colon \cat{I}\rightrightarrows  \cat{C}$ be two diagrams diagram with colimiting cocone $(C, \{c_i\}_{i\in \cat{I}})$ and   $(Q, \{q_i\}_{i\in \cat{I}})$. If $\cat{C}$ has all colimits for diagrams of shape $\cat{I}$ and $\phi\colon D\to D'$ is a natural transformation in which all components are regular epis, then the canonical arrow\todo{richiama prop precedente}  $c\colon C\to Q$ is a regular epi to.
\end{lemma}
\begin{proof}
	By \Cref{cor:regepi1} we know that $\phi\colon D\to D'$ is a regular epi, so that there is a functor $E\colon \cat{I}\to \cat{C}$ and $\alpha, \beta\colon E\rightrightarrows D$ such that $\phi$ is a coequalizer for $\alpha$ and $\beta$. Let $(P, \{p_i\}_{i\in \cat{I}})$ be the colimit of $E$, by ???\todo{richiama prop sulla freccia tra i colimiti} we have arrows $a, b\colon P\rightrightarrows  C$ fitting in the diagram belows:
	\[\xymatrix{E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i}& P \ar@{.>}[d]^{a} & E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i} & P \ar@{.>}[d]^{b}\\ D(i) \ar[r]_{c_i} & C & D(i) \ar[r]_{c_i} & C}\]

	We want to show that $c$ coequalizes $a$ and $b$. Let thus $t\colon C\to T$ be an arrow such that $t\circ a=t\circ b$. Then for every $i\in I$ we have 
	\begin{align*}
		t\circ c_i\circ \alpha_i&=t\circ a\circ p_i\\&=t\circ b\circ p_i\\&=t\circ c_i\circ \beta_i
	\end{align*}

	Thus there is $t_i\colon D'(i)\to T$ such that $t\circ c_i=t_i\circ \phi_i$. It is now easy to see that $(T, \{t_i\}_{i\in \cat{I}})$ is a cocone on $D'$ \todo{Verificalo!}.  Thus we have an arrow $k\colon Q\to T$ such that $k\circ q_i=t_i$. But then we have
	\begin{align*}
		k\circ c\circ c_i&=k\circ q_i\circ \phi_i\\&=t_i\circ \phi\\&=t\circ c_i
	\end{align*}
	Showing that $k\circ c=t$.

	For uniqueness, let $k'$ be another arrow $Q\to T$ such that $k'\circ c=t$, then we have
	\begin{align*}
		k'\circ q_i\circ \phi_i&=k'\circ c\circ c_i\\&=t\circ c_i\\&=t_i\circ \phi_i
	\end{align*}
	Since $\phi_i$ is a regular epi, by ???\todo{mettere nel capitolo 1 una proposizione che mostra che epi regolari sono epi} this entails $k'\circ q_i=t_i$. By construction $k\circ q_i=t_i$ and  so $k=k'$ since $(Q, \{q_i\}_{i\in \cat{I}})$ is a colimiting cocone.
\end{proof}

\begin{definition}
	A \emph{graph with equivalence} is a 6-uple $(A, B, C, s, t, q)$ where $A, B$ and $C$ are set, $s,t\colon A\rightrightarrows B$ are functions and $q\colon B\to C$ is another surjective function.

	A morphism  $(A, B, C, s, t, q)\to (A', B', C', s', t', q')$ is a triple $(h_1, h_2, h_3)$ of functions $h_1\colon A\to A'$, $h_2\colon B\to B'$ and $h_3\colon C\to C'$ making the following diagrams commute.

	\[\xymatrix{A \ar[r]^{s} \ar[d]_{h_1} & B \ar[d]^{h_2} & A \ar[r]^{s} \ar[d]_{h_1}& B \ar[d]^{h_2} & B \ar[d]_{h_2} \ar[r]^{q} & C \ar[d]^{h_3}\\A' \ar[r]_{s'} & B' & A ' \ar[r]_{t'}& B' & B' \ar[r]_{q'} & C'}\]

	In this way, defining the composition componentwise, we get a category $\EqGrph$.
\end{definition}

\begin{remark}\label{rem:fedele}
	There is a faithful functor $U\colon \EqGrph\to \Graph$, forgetting the quotient part. \todo{Questo è per te da dimostrare (forse meglio come proposizione che come remark).}
\end{remark}

\begin{remark}
There is another functor $V\colon \EqGrph\to \Set$ sending $(A, B,C, s,t, q)$ to $C$ and a morphism to its last component.	
\end{remark}

\begin{prop}\label{prop:limits}
	$\EqGrph$ is complete, cocomplete and $U$ preserves limits and colimits.
\end{prop}

\begin{remark}\label{rem:ima}\todo{Dimostrala}In $\Set$ we have the following property: for every square as the one below, if $e\colon X\to Y$ is epi and $m\colon M\to Z$ is mono, then there exists a unique dotted arrow $Y\to M$ making the diagram below commutative.
	\[\xymatrix{X \ar[r]^{f} \ar[d]_{e}& M \ar[d]^{m}\\ Y \ar[r]_{g} \ar@{.>}[ur]^{h}& Z}\] 
\end{remark}

\begin{proof}\todo{Per generalizzare ad altre categorie: serve poter fattorizzare con un epi regolare.} 
	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$. Let $(L, \{l_i\}_{i\in \cat{I}})$ be a limiting cone for $V\circ D$.

	Now, notice that $(B, \{q_i\circ p_{2,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Dimostralo}, so that we have an arrow $l\colon B\to L$. This arrow is not epi in general, let $Q$ be its image and $q\colon B\to Q$ be the resulting epi and $m\colon Q\to L$ the corresponding mono.
	By definition the external square in the diagram below commutes, so for every $i\in \cat{I}$, \Cref{rem:ima} yields the dotted arrow $p_{3,i}$.
	\[\xymatrix{B \ar[r]^{p_{2,i}} \ar[d]_{q}& B_i \ar[r]^{q_i} & Q_i \ar[d]^{id_{Q_i}}\\ Q \ar[r]_{m} \ar@{.>}[urr]_{p_{3,i}}& L \ar[r]_{l_i} & Q_i}\]

	We have to show that in this way we get a cone over the diagram $D$. Let $f\colon i\to j$ be an arrow of $\cat{I}$, then we have:
	\begin{align*}
	U(D(f)\circ (p_{1,i}, p_{2, i}, p_{3,i}))  &=  U(D(f))\circ(p_{1,i}, p_{2, i})\\
                                                   &=  (p_{1,j}, p_{2, j})\\
                                                   &=  U(D(f)\circ (p_{1,j}, p_{2, j}, p_{3,j}))
	\end{align*}
	 And faithfulness of $U$ yields the thesis.

	 To see that this cone is terminal, let $(E, F, G, a, b, c)$ be another graph with the vertex of a cone with sides $(t_{1,i},t_{2, i}, t_{3,i})$. By construction, we have an arrow $(t_1, t_2)\colon (E, F, a, b)\to (A, B, s, t)$ such that
	 \[\xymatrix{&E \ar@{.>}[dl]_{t_1} \ar[dr]^{t_{1,i}}&&&F \ar@{.>}[dl]_{t_2} \ar[dr]^{t_{2,i}}\\ A \ar[rr]_{p_{1,i}} & & A_i & B \ar[rr]_{p_{2,i}}&& B_i }\]

        Moreover $(G, \{t_{3,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Verificalo}, thus there exists an arrow $t\colon G\to L$ such that $l_i\circ t =t_{3,i}$. Now, precomposing with $c$ we get
	\begin{align*}
		l_i\circ t\circ c&=t_{3,i}\circ c\\&=q_i\circ t_{2,i}\\&=q_i\circ p_{2,i}\circ t_2\\&=l_i\circ l\circ t_2
	\end{align*}

	Therefore the solid part of the diagram below commutes and \Cref{rem:ima} yields the dotted arrow $t_3\colon G\to Q$.

	\[\xymatrix{F \ar[r]^{t_2} \ar[d]_{c}& B \ar[r]^{q} & Q \ar[d]^{m}\\G \ar[rr]_{t} \ar@{.>}[urr]^{t_3}&& L}\]

	Faithfulness \todo{esercizio per te: scrivere la dimostrazione di queste ultime due righe}of $U$ now guarantees that $(t_1, t_2, t_3)$ is the unique arrow such that $(p_{1,i}, p_{2,i}, p_{3,i})\circ(t_1, t_2, t_3)=(t_{1,i},t_{2, i}, t_{3,i})$.	\todo{esercizio per te: fare i colimiti. Hint: la dimostrazione è diversa ma più semplice. Se $(A, B, s,t)$ è il colimite di $U\circ D$ puoi considerare il colimite $Q$ dei vari $Q_i$. Per la proprietà del colimite hai una freccia $B\to Q$, mostra che è epi (segue in una riga dai risultati che abbiamo).}
\end{proof}

\begin{cor}
	An arrow $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ in $\EqGrph$ is mono if and only if $h_1$ and $h_2$ are mono in $\Set$.
\end{cor}
\begin{proof}
	\todo{esercizio per te, usa fedeltà e continuità}
\end{proof}

\begin{cor}\label{cor:regmono}Let $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ be a morphism of $\EqGrph$, then the following are equivalent:
	\begin{enumerate}
		\item $(h_1, h_2, h_3)$ is a regular mono;
		\item $h_1$, $h_2$, $h_3$ are all monos;
		\item $h_1$ and $h_2$ are mono and for every $f, f'\in F$, $c(h_2(f))=c(h_2(f'))$ if and only if $q(f)=q(f')$.
	\end{enumerate}
\end{cor}
\begin{proof}
	$1\Rightarrow 2.$ \todo{Esercizio}

	\smallskip \noindent
	$2\Rightarrow 3.$ \todo{Esercizio}

	\smallskip \noindent 
	$3\Rightarrow 1.$\todo{Esercizio}
\end{proof}

Let us turn to another functor $\EqGrph\to \Graph$.

\begin{definition}
The \emph{quotient functor} $Q:\EqGrph\to \Graph $ sends $(A, B, C, s,t, q)$ to $(A, C, q\circ s, q\circ t)$ and an arrow $(h_1, h_2, h_3) \colon (A, B, C, s,t, q)\to (E, F, G, a,b, c)$ to $(h_1, h_3)$.
\end{definition}

\todo{Verifica che questa cosa funziona $(h_1, h_3)$ è un morfismo di grafi?}

\begin{lemma}
	$Q$ is a left  adjoint.
\end{lemma}
\begin{proof} Let us start proving that $Q$ is a left adjoint. Let $R(A,B, s, t)$ be $(A, B, B, s,t, id_{B})$ , so that $Q(R(A,B,s,t))=(A,B,s,t)$. Now, suppose that an arrow $(h_1, h_2)\colon Q(E,F,G, a,b,c)\to (A,B, s,t)$ is given. Consider the triple $(h_1, h_2, h_2\circ c)$. Notice that, since $(h_1, h_2)$ is an arrow in $\Graph$:
	\[h_2\circ c\circ a= s\circ h_1 \qquad  h_2\circ c\circ b= t\circ h_1\]

	 Then we have three squares:

\[\xymatrix{E \ar[r]^{a} \ar[d]_{h_1} & F \ar[d]^{h_2\circ c} & E \ar[r]^{b} \ar[d]_{h_1}& F \ar[d]_{h_2\circ c} & B \ar[d]_{h_2\circ c} \ar[r]^{c} & C \ar[d]^{h_2}\\A \ar[r]_{s} & B & A  \ar[r]_{t}& B & B \ar[r]_{id_B} & B}\]

	 We have therefore found a morphism $(E,F,G, a,b,c)\to R(A,B,s,t)$ whose image through $Q$ fits in the diagram below.
	\[\xymatrix{(A, B, s,t)\ar[r]^{(id_A, id_B)} &(A, B, s,t)\\ (E, G, q\circ s, q\circ t) \ar[ur]_{(h_1, h_2)} \ar[u]^{Q(h_1, h_2\circ q, h_2)}}\]

\todo{Esercizio: prova unicità (è facile)}
\end{proof}

\begin{prop}\label{prop:colimit}
	$Q$ creates colimits.
\end{prop}
\begin{proof}
	\todo{esercizio per te (devi verificare solo la riflessione: ma dato un diagramma in grafi fatto di quozienti, come costruisci un insieme di vertici per il colimite?)}
\end{proof}

\begin{example}
	\todo{Q non preserva i limiti}
\end{example}

\subsection{Adhesivity of $\EqGrph$}

\begin{lemma}\label{lem:stab}
In $\EqGrph$ pushouts along regular monos are stable.
\end{lemma}
\begin{proof}
	Suppose that the cube below is given, in which all the vertical faces are pullbacks and the bottom face is a pushout, with $(h_1, h_2, h_3)\colon (A_1,B_1,C_1, s_1,t_1,q_1)\to (A_2,B_2,C_2, s_2,t_2,q_2)$ a regular mono\todo{Questo diagramma va sistemato per farlo stare nella pagina (val la pena magari dire "sia $\mathcal{G}_1$ il grafo....")}.

		\[\xymatrix@C=20pt@R=20pt{&(A'_1,B'_1,C'_1, s'_1,t'_1,q'_1)\ar[dd]|\hole_(.65){(a_1, a_2, a_3)}\ar[rr]^{(h'_1, h'_2, h'_3)} \ar[dl]_{(k'_1, k'_2, k'_3)} && (A'_2,B'_2,C'_2, s'_2,t'_2,q'_2) \ar[dd]^{(b_1, b_2, b_3)} \ar[dl]_{(t'_1, t'_2, t'_3)} \\ (A'_3,B'_3,C'_3, s'_3,t'_3,q'_3) \ar[dd]_{(c_1, c_2, c_3)}\ar[rr]^(.65){(p'_1,p'_2,p'_3)} & & (A'_4,B'_4,C'_4, s'_4,t'_4,q'_4) \ar[dd]_(.3){(d_1, d_2, d_3)}\\&(A_1,B_1,C_1, s_1,t_1,q_1)\ar[rr]|\hole^(.65){(h_1, h_2, h_3)} \ar[dl]^{(k_1, k_2, k_3)} && (A_2,B_2,C_2, s_2,t_2,q_2) \ar[dl]^{(t_1, t_2, t_3)} \\(A_3,B_3,C_3, s_3,t_3,q_3) \ar[rr]_{(p_1, p_2, p_3)} & & (A_4,B_4,C_4, s_4,t_4,q_4)}\]

By \Cref{prop:limits,cor:regmono} the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as vertical faces, thus their top faces are $\mathcal{M}$-pushouts.

\[\xymatrix@C=10pt@R=10pt{&A'_1\ar[dd]|\hole_(.65){a_1}\ar[rr]^{h'_1} \ar[dl]_{k'_1} && A'_2 \ar[dd]^{b_1} \ar[dl]_{t'_1} && B'_1\ar[dd]|\hole_(.65){a_2}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[dd]^{b_2} \ar[dl]_{t'_2}\\ A'_3  \ar[dd]_{c_1}\ar[rr]^(.7){p'_1} & & A'_4 \ar[dd]_(.3){d_1} &&B'_3  \ar[dd]_{c_2}\ar[rr]^(.7){p'_2} & & B'_4 \ar[dd]_(.3){d_2}\\&A_1\ar[rr]|\hole^(.65){h_1} \ar[dl]^{k_1} && A_2 \ar[dl]^{t_1} && B_1\ar[rr]|\hole^(.65){h_2} \ar[dl]^{k_2} && B_2 \ar[dl]^{t_2} \\A_3 \ar[rr]_{p_1} & & A_4&&B_3 \ar[rr]_{p_2} & & B_4}\]

Now,  using \Cref{cor:cube}, we can consider a third cube, which, by \Cref{prop:colimit}, has a bottom face an $\mathcal{M}$-pushout and pullbacks as vertical faces, so that its top face is an $\mathcal{M}$-pushout too.

\[\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C'_4 \ar[dd]_(.3){d_3}\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]

Moreover, by the proof of \Cref{prop:limits} we know that there are monos $m_2\colon C'_2\to U $ and $m_3\colon C'_3\to Y$ fitting in the diagrams
\[\xymatrix{B'_3\ar[r]^{p'_2} \ar[d]^{q'_3} \ar@/_.4cm/[dd]_{c_2}& B'_4\ar@/^.2cm/[dr]^{q'_4} && B'_2 \ar@/_.4cm/[dd]_{b_2} \ar[r]^{t'_2} \ar[d]^{q'_2}& B'_4 \ar@/^.2cm/[dr]^{q'_4} \\C'_3  \ar[r]^{m_3}& Y \ar[r]^{y_1} \ar[d]_{y_2} & C'_4 \ar[d]^{d_3} &C'_2 \ar[r]^{m_2}& U\ar[r]^{u_1} \ar[d]_{u_2} & C'_4 \ar[d]^{d_3}\\  B_3  \ar[r]_{q_2}& C_3 \ar[r]_{p_3}& C_4 &B_2 \ar[r]_{q_2}&  C_2 \ar[r]_{t_3}& C_4}\]

For $C'_1$, the we can make a similar argument, let $S$ be the pullback of $m_2$ along $x_1$, using \Cref{lem:pb1} and, again, the proof of \Cref{prop:limits} we know that $q'_1$ arise as the factorization of the arrow $B'_1\to S$ induced by $q'_2\circ h'_2$ and $a_2$ so that we have a diagram.
	\[\xymatrix{ B'_1 \ar@/_.4cm/[dd]_{a_2} \ar[r]^{h'_2} \ar[d]^{q'_2}& B'_2 \ar@/^.2cm/[dr]^{q'_2} \\C'_1 \ar[r]^{m_1}& S\ar[r]^{s_1} \ar[d]_{s_2}&C'_2 \ar[d]^{m_2}\\  B_2 \ar@/_.2cm/[dr]_{q_2}&  T \ar[r]^{x_1} \ar[d]_{x_2}& U \ar[d]_{u_2} \\ & C_1 \ar[r]_{h_3}&  C_2}\]

%Notice that $s_2\colon S\to T$, being the pullback of a mono is mono by ????\todo{metti questo lemma da qualche parte: il pullback di un mono è mono}
Moreover, notice that \todo{Esercizio (basta comporre prima e dopo con gli opportuni epi e mono)}

\[s_1\circ m_1 = h'_3 \quad w\circ s_2\circ m_1=  m_3\circ k'_3 \quad t'_3=u_1\circ m_2 \quad p_3=y_1\circ m_3\]

Let now $(z_1, z_2, z_3)\colon (A'_2, B'_2, C'_2)\to (E, F, G, e, f, g)$ and $(w_1, w_2, w_3)\colon (A'_3, B'_3, C'_3)\to (E, F, G, e, f, g)$ be two morphisms such that 
\[(z_1, z_2, z_3)\circ (h'_1, h'_2, h'_3)=(w_1, w_2, w_3)\circ (k'_1, k'_2, k'_3)\] 
Let $z\colon B'_4\to F$ be the arrow induced by $z_2$ and $w_2$, we want to construct the dotted arrow $v\colon C'_4 \to G$ in the diagram below

 \todo{Sistema il diagramma mettendo gli opportuni buchi}
\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[dd]|(.5)\hole_(.62){q'_1}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[ddd]|(.33)\hole^{q'_2} \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[ddd]_{q'_3} \ar[rr]^(.65){p'_2} && B'_4  \ar[rr]^(.65){z}&& F \ar[ddddd]^{g}\\& C'_1 \ar@/^.2cm/[drr]^{h'_3} \ar@/_.2cm/[ddl]_{k'_3} \ar[d]^{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \ar@/^.2cm/[dddr]^{z_3} \ar[lddd]_{t'_3}\\ C'_3 \ar@/_.5cm/[ddrr]^(.65){p'_3} \ar[ddrrrr]_{w_3} \ar[dd]_{m_3}\\&T\ar[dd]|(.25)\hole|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]|(.25)\hole_{w} && U \ar[dd]^(.3){u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]_(.65){y_1} & & C'_4 \ar@{.>}[rr]_(.65){v} \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]

Now by \Cref{prop:regepi} $d_3$ is the coequalizer of its kernel pair. On the other hand, by \Cref{lem:salvavita2}  we know that the top face of the cube below is a pushout.
\[\xymatrix@C=15pt@R=15pt{&K_{s_2\circ m_1\circ q'_1}\ar[dd]|\hole_(.65){p_{s_2\circ m_1\circ q'_1,1}}\ar[rr]^{k_{h'_2}} \ar[dl]_{k_{k'_2}} && K_{m_2\circ q'_2} \ar[dd]^{p_{m_2\circ q'_2,1}} \ar[dl]_{k_{t'_2}} \\ K_{m_3\circ q'_3}  \ar[dd]_{p_{m_3\circ q'_3,1}}\ar[rr]^(.7){k_{p'_2}} & & K_{q'_4} \ar[dd]_(.3){p_{q'_4,1}}\\&B'_1\ar[rr]|\hole^(.65){h'_2} \ar[dl]^{k'_2} && B'_2 \ar[dl]^{t'_2} \\B'_3 \ar[rr]_{p'_2} & & C_4}\]
Moreover, since $m_3$ and $m_2$ are monos, or by \Cref{cor:kermono} we also know that
\[q'_3\circ p_{m_3\circ q'_3, 1}  = q'_3\circ p_{m_3\circ q'_3,2} \qquad q'_2\circ p_{m_2\circ q'_2, 1}  = q'_2\circ p_{m_2\circ q'_2,2}\]

Now, we have
\[
\begin{split}
	g\circ z\circ p_{q'_4,1} \circ k_{p'_2}&=g\circ z\circ p'_2\circ p_{m_3\circ q'_3, 1}\\&=g\circ w_2\circ \circ  p_{m_3\circ q'_3, 1}\\&=w_3\circ q'_3\circ p_{m_3\circ q'_3, 1}\\&=w_3\circ q'_3\circ p_{m_3\circ q'_3, 2}\\&=g\circ w_2\circ \circ  p_{m_3\circ q'_3, 2}\\&=g\circ z\circ p'_2\circ p_{m_3\circ q'_3, 2}\\&=g\circ z\circ p_{q'_4,2} \circ k_{p'_2}
\end{split} \qquad 
\begin{split}
g\circ z\circ p_{q'_4,1} \circ k_{t'_2}&=g\circ z\circ t'_2\circ p_{m_2\circ q'_2, 1}\\&=g\circ z_2\circ \circ  p_{m_2\circ q'_2, 1}\\&=z_3\circ q'_2\circ p_{m_2\circ q'_2, 1}\\&=z_3\circ q'_2\circ p_{m_2\circ q'_2, 2}\\&=g\circ z_2\circ \circ  p_{m_2\circ q'_2, 2}\\&=g\circ z\circ t'_2\circ p_{m_2\circ q'_2, 2}\\&=g\circ z\circ p_{q'_4,2} \circ k_{t'_2}
\end{split}
\]

The thesis now follows \todo{Scrivi perché}

\todo{Esercizio: prova unicità}

\end{proof}

\begin{lemma}\label{lem:vk}
In $\EqGrph$ pushouts along regular monos are Van Kampen.
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}

From \Cref{prop:limits} and \Cref{lem:stab,lem:vk} we deduce at once the following.

\begin{cor}\label{cor:equi}
	$\EqGrph$ is quasiadhesive.
\end{cor}

\color{black}

### 2024-10-26 Article/Graph_sections/Eq_Graphs_integration.tex
section on kernel pairs + some proofs

\section{Graphs with Equivalences}\label{sect:eq_graphs}
A graph with equivalence is a 6-tuple $\eqgraph{G} =  (E, V, C, s, t, q)$, where $E$ and $V$ are, respectively, the edges and the vertices sets, and $C$ is the set of the equivalence classes among vertices, $s,t : E \to V$ are the source and target functions and $q: V \to C$ is the \emph{quotient} function, that is, the map from a vertex to its equivalence class. For this definition to make sense, $q$ needs to be surjective. A morphisms $h$ from a graph with equivalence $\eqgraph{G} =  (E, V, C, s, t, q)$ to another $\eqgraph{H} = (E', V', C', s', t',  q')$ is a triple $h = (h_E, h_V, h_C)$ of functions $h_V : V \to V'$, $h_E : E \to E'$ and $h_C : C \to C'$ such that:
\begin{itemize}
    \item $h_E \circ s = s' \circ h_V$;
    \item $h_E \circ t = t' \circ h_V$;
    \item $h_C \circ q = q' \circ h_C$.
\end{itemize}

\begin{remark}
     A graph with equivalence can be viewed as a graph endowed with an equivalence relation over its set of vertices, $(\graph G, \sim_\graph{G})$. An homomorphism between two graphs with equivalences $h :\eqgraph{G} = (\graph{G}, \sim_\graph{G})\rightarrow \eqgraph{H} = (\graph{H}, \sim_\graph{H})$ is a graph homomorphism $h = (h_V, h_E):\graph{G} \rightarrow \graph{H}$ such that if $v_1 \sim_\graph{G} v_2$ then $h_V(v_1) \sim_\graph{H} h_V(v_2)$. In $\Set$, it is possible to formalize an equivalence relation $\sim$ over $X$ as a surjective function sending each element $x$ on its equivalence class $[x]_{\sim}$, and this justify our formalization via surjective functions (i.e., epimorphisms).
\end{remark}

As we have done in \Cref{sect:graphs}, we can think to a graph with equivalence as a presheaf, this time from a category $E \rightrightarrows V \rightarrow C$, where the image of $C$ along the presheaf is the set of the equivalence classes, requiring that the morphism $V\rightarrow C$ is an epimorphism (that is, a surjective function).

\begin{definition}[Category of Graphs with Equivalences]\label{def:eq_grphs}
    The category $\EqGrph$ is the subcategory of $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V \xrightarrow{q} C, \Set]$$ such that, for each $\eqgraph{G} \in \Ob(\EqGrph)$, $\eqgraph{G}(q)$ is an epimorphism. 
\end{definition}

\begin{obs}\label{obs:eq_grph_morph_det_by_first_two_comp}
    Morphisms of graphs with equivalence are uniquely determined by the first two component. That is, if $h_1 = (h_E, h_V, \phi)$ and $h_2 = (h_E, h_V, \psi)$, then $\phi = \psi$.
\end{obs}

\begin{proof}
    Let $h_1, h_2 : \eqgraph{G \to H}$, where $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$. Then, we have the following situation
    \[
        \begin{tikzcd}
            V_G \arrow[r, "{h_V}"] \arrow[d, "{q_G}"swap] & V_H \arrow[d, "{q_H}"] & V_G \arrow[l, "{h_V}"swap] \arrow[d, "{q_G}"] \\
            C_G \arrow[r, "{\phi}"swap] & C_H & \arrow[l, "{\psi}"] C_G
        \end{tikzcd}
     \]
     Then, we have:
     \begin{align*}
         \psi \circ q_G &= q_H \circ h_V \\
                        &= \phi \circ q_G
     \end{align*}
     From the fact that $q_G$ is epi, we can conclude $\phi = \psi$.
\end{proof}

A graph with equivalence is then a graph with an extra structure, the quotient map. Hence, it is possible to get the underlying graph by forgetting it. Such action is described by the \emph{forgetful functor} $U : \EqGrph \to \Graph$, that maps each graph with equivalence $\eqgraph{G} =  (E, V, C, s, t, q)$ onto $U(\eqgraph{G}) = (E, V, s, t)$, and each morphisms $h = (h_E, h_V, h_C)$ onto $U(h) = (h_E, h_V)$. $U$ is effectively a functor, since, on identities, $U((id_E, id_V, id_C)) = (id_E, id_V)$, and on compositions $U(h \circ k) = U((h_E \circ k_E, h_V 1circ k_V, h_C \circ k_C)) = (h_E \circ k_E, h_V \circ k_V) = (h_E, h_V) \circ (k_E \circ k_V) = U(h) \circ U(k)$.

\begin{prop}\label{prop:U_is_faithf}
    The forgetful functor $U: \EqGrph \to \Graph$ is faithful.
\end{prop}

\begin{proof}
    Let $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$  be two graphs with equivalences, and let $h, k : \eqgraph{G \to H}$.
    If $U(h) = U(k)$ (i.e., the first two component of $h$ and $k$ are the same), from \Cref{obs:eq_grph_morph_det_by_first_two_comp}, we can conclude that $h = k$. Then, the restriction $U_{\eqgraph{G, H}} : \EqGrph(\eqgraph{G, H}) \to \Graph(U(\eqgraph{G}), U(\eqgraph{H}))$, therefore $U$ is faithful.
\end{proof}

Another functor that will be useful later is $V: \EqGrph \to \Set$, that sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.

\begin{prop}
    $\EqGrph$ has all limits, colimits and $U$ preserves limits and colimits.
\end{prop}

\begin{proof}
    Let $D : \cat I \to \EqGrph$ be a diagram. In the following, we will denote the graph with equivalence $D(i)$ as $(E_i, V_i, C_i, s_i, t_i, q_i)$.
    Let now be the graph $(A, B, s, t)$ the limit of $U \circ D$, with projections $(\pi_E^i, \pi_V^i):(A, B, s, t) \to (E_i, V_i, s_i, t_i)$. Notice now that $(B, (q_i\circ \pi_V^i)_{i \in \cat I})$ is a cone for $V \circ D$. To see this, let $\alpha : i \to j$ be an arrow of $\cat I$, $D(\alpha) = (h_E, h_V, h_C)$, $U \circ D (\alpha) = (h_E, h_V)$. From the definition of cone, we have that $U \circ D (\alpha) \circ (\pi_E^i, \pi_V^i) = (\pi_E^j, \pi_V^j)$, hence $h_V \circ \pi_V^i = \pi_V^j$. 
    Consider now the following diagram in $\Set$
    \[
        \begin{tikzcd}[row sep=25 pt, column sep = 25 pt]
            & B \arrow[dl, "{\pi_V^i}"swap] \arrow[dr, "{\pi_V^j}"] & \\
            V_i \arrow[rr, "{h_V}"] \arrow[d, "{q_i}" swap] & & V_j \arrow[d, "{q_j}"] \\
            C_i \arrow[rr, "{h_C}" swap] & & C_j 
        \end{tikzcd}
    \]
    So we have $q_j \circ h_V \circ \pi_V^i = q_j \circ \pi_V^j$, by definition of graph with equivalence, $h_C \circ q_i \circ \pi_V^i = q_j$, and, by definition of $V$, $V \circ D (\alpha) \circ q_i \circ \pi_V^i = q_j \circ \pi_V^j$.
    Suppose now $(L, (l_i)_{i \in \cat I})$ be a limit for $V \circ D$, so that we have an arrow $l: B \to L$. This arrow is not epi in general, so let $Q$ be its image, $q: Q \to B$ be the resulting epi and $m: Q \to L$ the corresponding mono, as the diagram below shows. By definition, the external rectangle commutes, so, for each $i$ object of $\cat I$, 
    REMARK\todo{epi-mono factorization in Set (or Regular Cats in general)}
    yields the dotted arrow $\pi_C^i$.
    \[
        \begin{tikzcd}
            B \arrow[r, "{\pi_V^i}"] \arrow[d, "q" swap] & B_i \arrow[r, "{q_i}"] & Q_i \arrow[d, "{id_{Q_i}}"] \\
            Q \arrow[urr, dashed, "\pi_C^i"] \arrow[r, "m" swap] &L \arrow[r, "{l_i}"swap] & Q_i
        \end{tikzcd}
    \]
    We have to show that in this way we get a cone over the diagram $D$. Let $\alpha : i\to j$ be an arrow of $\cat{I}$, then we have:
    \begin{align*}
    U(D(\alpha)\circ (\pi_E^i, \pi_V^i, \pi_C^i))  &=  U(D(\alpha))\circ(\pi_E^i, \pi_V^i)\\
                                                   &=  (\pi_E^j, \pi_V^j)\\
                                                   &=  U(D(\alpha)\circ (\pi_E^j, \pi_V^j, \pi_C^j))
    \end{align*}
    And faithfulness of $U$ yields the thesis.

    To see that this cone is terminal, let $((E, F, G, a, b, c), \tau_i = (\tau_E^i, \tau_V^i, \tau_C^i)_{i \in \cat I})$ be another cone. By construction, we have an arrow $(\tau_E, \tau_V):(E, F, a, b) \to (A, B, s, t)$ such that
    \[
        \begin{tikzcd}
            & E \arrow[dl, dashed, "{\tau_E}" swap] \arrow[dr, "{\tau_E^i}"] & \\
            A \arrow[rr, "{\pi_E^i}" swap] & & A_i 
        \end{tikzcd}
        %
        \qquad
        %
        \begin{tikzcd}
            & F \arrow[dl, dashed, "{\tau_V}" swap] \arrow[dr, "{\tau_V^i}"] & \\
            B \arrow[rr, "{\pi_V^i}" swap] & & B_i 
        \end{tikzcd}
    \]

    For the same reason as before, $(G, (\tau_C^i)_{i\in \cat I})$ is a cone over $V \circ D$, thus there exists an arrow $\tau : G \to L$ such that $l_i \circ \tau = \tau_C^i$. At this point, we get
    \begin{align*}
        l_i\circ \tau \circ c 
                        &= \tau_C^i\circ c              && \\
                        &=q_i\circ \tau_V^i             && \textit{$\tau_i$ is a morphism in $\EqGrph$}\\
                        &=q_i\circ \pi_V^i\circ \tau_V  && \textit{Diagram above} \\
                        &=l_i\circ l\circ \tau_V        && \textit{$(B, (q_i\circ \pi_V^i)_{i \in \cat I})$ cone} 
    \end{align*}

    Therefore, the outer part of the rectangle below commutes, and by REMARK \todo{epi-reg fact in SET} there exists a unique $\tau_C: G \to Q$
    \[
        \begin{tikzcd}
            F \arrow[r, "{\tau_V}"] \arrow[d, "c"swap] & B \arrow[r, "q"] & Q \arrow[d, "m"] \\
            G \arrow[urr, dashed, "{\tau_C}"] \arrow[rr, "{\tau}"swap] & & L
        \end{tikzcd}
    \]
     Faithfulness of $U$ guarantees that $(\tau_E, \tau_V, \tau_C)$ is the unique arrow such that $(\pi_E^i, \pi_V^i, \pi_C^i) \circ (\tau_E, \tau_V, \tau_C) = (\tau_E^i, \tau_V^i, \tau_C^i)$.
     \todo{Dimostrazione dello statement di sopra, e colimiti}
\end{proof}

\begin{cor}\label{cor:mono_in_EqGrph}
    An arrow $h = (h_E, h_V, h_C): \eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G) \to \eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ in $\EqGrph$ is mono if and only if $h_E$ and $h_V$ are mono in $\Set$.
\end{cor}

\begin{proof}
    The ``if'' part is given by the fact that $U$ is faithful, and hence reflects monomorphisms. Since a morphism ain a category of presheaves is mono if and only if it is injective on each component \todo{commentato il link, dimostrare questa cosa}
    % https://ncatlab.org/nlab/show/category+of+presheaves#properties
    we have that, if  $U(h)$ is mono, that is, $h_E$ and $h_V$ are injective in $\Set$, then $h$ is mono.
    For the ``only if'' part, suppose $f = (f_E, f_V, f_C)$, $g=(g_E, g_V, g_C)$, $f, g : \eqgraph{H \to K}$ be such that $h \circ f = h \circ g$. Then, we have
    \begin{align*}
        h \circ f   &= (h_E \circ f_E, h_V \circ f_V, h_C \circ f_C) \\
                    &= (h_E \circ f_E, h_V \circ f_V, h_V \circ f_V \circ \eqgraph{K}(q)) \\
                    &= (h_E \circ g_E, h_V \circ g_V, h_V \circ g_V \circ \eqgraph{K}(q))
    \end{align*}    
    Since $\eqgraph{K}(q)$ is epi, we have, on the third component, that $h_V \circ f_V \circ \eqgraph{K}(q) = h_V \circ g_V \circ \eqgraph{K}(q))$ implies $f_C = g_C$, and hence $f = g$    
\end{proof}

\begin{cor}\label{cor:regmono}Let $ h = (h_E, h_V, h_C): \eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G) \to \eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ be a morphism of $\EqGrph$, then the following are equivalent:
	\begin{enumerate}
		\item $h$ is a regular mono;
		\item $h_E$, $h_V$, $h_C$ are all monos;
		\item $h_E$ and $h_V$ are mono and for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$.
	\end{enumerate}
\end{cor}
\begin{proof}
	$1\Rightarrow 2.$ If $h$ is mono, from \Cref{cor:mono_in_EqGrph} we have that $h_E$ and $h_V$ are monos. To derive $h_C$ mono, suppose $f, g :  \eqgraph{H \to K}$ to be the arrows equalized by $h$. Then we have
    \begin{align*}
        f_C \circ h_C \circ \eqgraph{G}(q)  &=  f_C \circ \eqgraph{H}(q) \circ h_V \\
                                            &=  \eqgraph{K}(q) \circ f_V \circ h_V \\
                                            &=  \eqgraph{K}(q) \circ g_V \circ h_V \\
                                            &=  g_C \circ h_C \circ \eqgraph{G}(q)
    \end{align*}
    since $\eqgraph{G}(q)$ is epi, we have that $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, thus a monomorphism.

	\smallskip \noindent
	$2\Rightarrow 3.$ The leftward side of the statement is satisfied by the definition of morphism of graphs with equivalences. For the remaining part, we have
    \begin{align*}
        (\eqgraph{H}(q) \circ h_V) (v)  &=  (\eqgraph{H}(q) \circ h_V)(v') \\
        (h_C \circ \eqgraph{G}(q))(v)   &=  (h_C \circ \eqgraph{G}(q))(v')  
    \end{align*}
        since $h_C$ is mono, we can conclude $\eqgraph{G}(q)(v)= \eqgraph{G}(q)(v')$.

	\smallskip \noindent 
	$3\Rightarrow 1.$\todo{Esercizio} \color{green}{idea: force the comm. of the diagram on the last two components to obtain the two arrows that are equalized, and show that the condition in 3 is sufficient to conclude reg. mono} \color{black}
\end{proof}

Let us turn to another functor $\EqGrph\to \Graph$.

\begin{definition}
The \emph{quotient functor} $Q:\EqGrph\to \Graph $ sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $(E_G, C_G, q_G\circ s_G, q_G\circ t_G)$ and an arrow $(h_E, h_V, h_C) \colon (E_G, V_G, C_G, s_G, t_G, q_G)\to (E_H, V_H, C_H, s_H, t_H, q_H)$ to $(h_E, h_C)$.
\end{definition}

\begin{remark}
    The action of the functor on a morphism of graphs with equivalences gives a morphism of graphs, in fact $q_H \circ s_H \circ h_E = q_H \circ h_V \circ s_G = h_C \circ q_G \circ s_G$. The same is valid for $t_H$ and $t_G$. 
\end{remark}

\begin{lemma}
    $Q$ is a left adjoint.
\end{lemma}

\begin{proof}
    Let $R((A, B, s, t))$ be $(A, B, B, s, t, id_B)$, so that $Q(R((A, B, s, t))) = (A, B, s, t)$. Now, suppose that $h = (h_E, h_V): Q((E, V, C, s', t', q)) \to (A, B, s, t)$  is an arrow in $\Graph$, and consider the triple $(h_E, h_V, h_V \circ q)$. Since $h$ is a morphism of $\Graph$, 
    \[h_V\circ q\circ s'= s\circ h_E \qquad  h_V\circ q\circ t' = t\circ h_E\]
    Then we have the following squares:
    \[
        \begin{tikzcd}
            E \arrow[r, "{h_E}"] \arrow[d, "{s_G}"swap] & A \arrow[d, "s"] \\
            V \arrow[r, "{h_V \circ q}"swap] & B
        \end{tikzcd}
        \qquad
        \begin{tikzcd}
            E \arrow[r, "{h_E}"] \arrow[d, "{t_G}"swap] & A \arrow[d, "t"] \\
            V \arrow[r, "{h_V \circ q}"swap] & B
        \end{tikzcd}
        \qquad
        \begin{tikzcd}
            V \arrow[r, "{h_V\circ q}"] \arrow[d, "q" swap] & B \arrow[d, "{id_B}"] \\
            C \arrow[r, "{h_V}"swap] & B
        \end{tikzcd}
    \]

    We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below.
    \[
        \begin{tikzcd}
            (A, B, s, t) \arrow[r, "{id_A, id_B}"] & (A, B, s, t)\\
            (E, C, q\circ s', q\circ t') \arrow[u, "{Q((h_E, h_V \circ q, h_V))}"] \arrow[ur, "{(h_E, h_V)}" swap] 
        \end{tikzcd}
    \]
    Such arrow is unique. Suppose $f = (f_E, f_V, f_C)$ to be another arrow wit such property. Then, it must be $(id_A, id_B) \circ Q(f) = (f_E, f_C) = (h_E, h_C)$. Finally, $f_C = f_V \circ q = h_V \circ q$. 
\end{proof}

\begin{prop}
    $Q$ creates colimits.
\end{prop}

\begin{proof}
    Preserve from \Cref{th:adjoints_preserves_lim}. Remain to see Reflect.
\end{proof}

### 2024-10-28 Article/Background_sections/Adhesivity.tex
Some proofs, reordering of material

@@
     \]
+    \[\begin{tikzcd}[row sep=25, column sep=25]
+	& {A'} && {B'} \\
+	{C'} && {D'} \\
+	& A && B \\
+	C && D
+	\arrow["{f'}", from=1-2, to=1-4]
+	\arrow["{m'}"', from=1-2, to=2-1]
+	\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{n'}"', from=1-4, to=2-3]
+	\arrow["b", from=1-4, to=3-4]
+	\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
+	\arrow["c"', from=2-1, to=4-1]
+	\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
+	\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
+	\arrow["m", from=3-2, to=4-1]
+	\arrow["n", from=3-4, to=4-3]
+	\arrow["g"', from=4-1, to=4-3]
+    \end{tikzcd}\]
     we say that the inner square is an \emph{$\mathcal A$-Van Kampen} square if:
@@
 \end{cor}
+
+\begin{lemma}
+    Let $\cat C$ be an $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
+        \[\begin{tikzcd}[row sep=25, column sep=25]
+	& {A'} && {B'} \\
+	{C'} && {D'} \\
+	& A && B \\
+	C && D
+	\arrow["{f'}", from=1-2, to=1-4]
+	\arrow["{m'}"', from=1-2, to=2-1]
+	\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{n'}"', from=1-4, to=2-3]
+	\arrow["b", from=1-4, to=3-4]
+	\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
+	\arrow["c"', from=2-1, to=4-1]
+	\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
+	\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
+	\arrow["m", from=3-2, to=4-1]
+	\arrow["n", from=3-4, to=4-3]
+	\arrow["g"', from=4-1, to=4-3]
+    \end{tikzcd}\]
+
+    Then, the square below is a pushout.
+    \[
+        \begin{tikzcd}%[row sep=25, column sep=25]
+            {K_a} \ar[r, "{k_{f'}}"] \ar[d, "{k_{m'}}"'] & {K_b} \ar[d, "{k_{n'}}"] \\
+            {K_c} \ar[r, "{k_{g'}}"'] & {K_d}
+        \end{tikzcd}
+    \]
+\end{lemma}
+
+\begin{proof}
+    By \Cref{lemma:kern_pairs_pres_pullbacks}, in the following cube the vertical faces are pullbacks.
+    \[\begin{tikzcd}[row sep = 20, column sep = 20]
+        & {K_a} && {K_b} \\
+        {K_c} && {K_d} \\
+        & {A'} && {B'} \\
+        {C'} && {D'}
+        \arrow["{k_{f'}}", from=1-2, to=1-4]
+        \arrow["{k_{m'}}"', from=1-2, to=2-1]
+        \arrow["{\pi_a^1}"{pos=0.7}, from=1-2, to=3-2]
+        \arrow["{k_{n'}}", from=1-4, to=2-3]
+        \arrow["{\pi_b^1}", from=1-4, to=3-4]
+        \arrow["{k_{g'}}"{pos=0.7}, from=2-1, to=2-3, crossing over]
+        \arrow["{\pi_c^1}"', from=2-1, to=4-1]
+        \arrow["{f'}"'{pos=0.3}, from=3-2, to=3-4]
+        \arrow["{\pi_d^1}"{pos=0.7}, from=2-3, to=4-3, crossing over]
+        \arrow["{m'}", from=3-2, to=4-1]
+        \arrow["{n'}", from=3-4, to=4-3]
+        \arrow["{g'}"', from=4-1, to=4-3]
+    \end{tikzcd}\]
+
+    {\color{red} Non ho capito la dimostrazione!!}
+\end{proof}

### 2024-10-28 Article/Background_sections/Limit.tex
Some proofs, reordering of material

@@
 
-The dual of the proposition above states that a coequalizer is an epimmorphism.
+The dual of the proposition above states that a coequalizer is an epimorphism.
 
@@
 
-\subsection{Kernel pairs}
+\begin{prop}\label{prop:nat_tran_induces_unique_arrow_between_colimits}
+    Let $D, D': \cat{I \to C}$ be two functors, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
+Then, a natural transformation $\phi: D \dot\to D'$ induces a unique arrow $c: C \to C'$.
+\end{prop}
+
+\begin{proof}
+    Consider the following situation.
+    \[\begin{tikzcd}[row sep=26 pt, column sep= 13 pt]
+        & C & \\
+        D(i) \ar[ur, "{c_i}"] \ar[d, "{\phi_i}"swap] \ar[rr, "{D(\alpha)}"]&& D(j) \ar[ul, "{c_j}"swap] \ar[d, "{\phi_j}"] \\
+        D'(i) \ar[dr, "{c_i'}" swap] \ar[rr, "{D'(\alpha)}" swap] && D'(j) \ar[dl, "{c_j'}"] \\
+        & C' &
+    \end{tikzcd}\]
+
+    To prove the statement, we note that $((c_i' \circ \phi_i)_{i \in \cat I}, C')$ is a cocone for $D$. Computing, we have, for each $i$, $j$ and $\alpha: i \to j$
+    \begin{align*}
+        c_j' \circ \phi_j \circ D(\alpha)   
+                        &=  c_j' \circ D'(\alpha) \circ \phi_i  &&\textit{Naturality of $\phi$}\\
+                        &=  c_i' \circ \phi_i                   &&\textit{$((c_i')_{i\in \cat I}, C')$ is a colimit for $D'$}
+    \end{align*}
+
+    Since $((c_i')_{i \in \cat I}, C)$ is a limit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
+\end{proof}
+
+\subsection{Kernel Pairs an Regular Epimorphisms}
 
 \begin{definition}[Kernel Pair]
-    A \emph{kernel pair} for an arrow $f: A \to B$ is an object $K_f$ together with two arrows $\pi_1^f, \pi_2^f : K_f \to A$, denoted as $(K_f, \pi_1^f, \pi_2^f)$, such that the following square is a pullback.
+    A \emph{kernel pair} for an arrow $f: A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f : K_f \to A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the following square is a pullback.
     \[
         \begin{tikzcd}
-            K_f \ar[r, "{\pi_1^f}"] \ar[d, "{\pi_2^f}" swap] & A \arrow[d, "f"] \\
+            K_f \ar[r, "{\pi^1_f}"] \ar[d, "{\pi^2_f}" swap] & A \arrow[d, "f"] \\
             A \ar[r, "f"swap] & B
@@
     \[
-        \begin{tikzcd}
-        A \arrow[drr, bend left=20, "f"] \arrow[ddr, bend right=20,"g" swap] \arrow[dr, dashed, "u"] & & \\
-        & M  \arrow[d, "{id_M}" swap] \arrow[r, "{id_M}"] & M \arrow[d, "m"] \\
+        \begin{tikzcd}[row sep=26, column sep = 26]
+        A \arrow[drr, bend left=30, "f"] \arrow[ddr, bend right=30,"g" swap] \arrow[dr, dashed, "u"] & & \\
+        & M  \arrow[d, "{id_M}"] \arrow[r, "{id_M}"] & M \arrow[d, "m"] \\
         & M  \arrow[r, "m" swap] & X
@@
 \begin{cor}\label{cor:kermono}
-	Let $(K_f, \pi^f_i), \pi^f_2)$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, \pi^f_1, \pi^f_2)$ is a kernel pair also for $m\circ f$.
+	Let $(K_f, \pi_f^1, \pi_f^2)$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
 \end{cor}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:kern_pairs_pres_pullbacks}
     Suppose the following situation, and that $f: X \to Y$ and $g: Z \to W$ have kernel pairs.
@@
 
-\begin{cor}
-    Let $\cat C$ be a category with pullbacks and $\phi : D \to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
+\begin{prop}\label{prop:reg_epi_coeq}
+    Let $e: X \to Y$ be a regular epimorphism in a category $\cat C$ with a kernel pair $(K, \pi_1, \pi_2)$. Then, $e$ is the coequalizer of $\pi_1$ and $\pi_2$.
+\end{prop}
+
+\begin{proof}
+    By hypothesis, there exists a pair $f, g: Z \to X$ of which $e$ is the coequalizer. Since $e \circ f = e \circ g$, we have
+    \[
+        \begin{tikzcd}[row sep= 20, column sep = 13]
+            Z \ar[drr, "f", bend left=30] \ar[ddr, "g"swap, bend right=30] \ar[dr, dashed, "k"] & & \\
+            & K \ar[r, "{\pi_1}"] \ar[d, "{\pi_2}" swap] & X \ar[d, "e"] \\
+            & X \ar[r, "e"swap] & Y
+        \end{tikzcd}
+    \]
+    thus there exists the unique $k: Z \to K$. Let now $h: Z \to V$ be an arrow such that $h \circ \pi_1 = h \circ \pi_2$, then
+    \begin{align*}
+        h \circ f &= h \circ \pi_1 \circ k \\
+                  &= h \circ \pi_2 \circ k \\
+                  &= h \circ g
+    \end{align*}
+    and thus there exists a unique $l: Y \to V$ such that $l \circ e = h$.
+\end{proof}
+
+\begin{cor}\label{cor:reg_epi_components_reg_epi_nat_trans}
+    Let $\cat C$ be a category with pullbacks and $\phi : D \dot\to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
 If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
@@
 \begin{proof}
-    TODO
+    Let $(K_i, \pi_i^1, \pi_i^2)$ be the kernel pair of $\phi_i$ for each $i$. Given an arrow $\alpha: i \to j$ of $\cat I$, we have
+    \begin{align*}
+        \phi_j \circ D(\alpha) \circ \pi_i^1 &= D'(\alpha) \circ \phi_i \circ \pi_i^1 \\
+                                             &= D'(\alpha) \circ \phi_i \circ \pi_i^2 \\
+                                             &= \phi_j \circ D(\alpha) \circ \pi_i^2
+    \end{align*}
+    Thus, the outer boundary of the diagram below commutes, yielding the arrow $K(\alpha)$
+    \[
+        \begin{tikzcd}[row sep=26, column sep=26]
+            {K_i} \ar[r, "{\pi_i^1}"] \ar[d, "{\pi_i^2}"swap] \ar[dr, dashed, "{K(\alpha)}"] & D(i) \ar[dr, "{D(\alpha)}"] \\
+            D(i) \ar[dr, "{D(\alpha)}"swap] & K_j \ar[r, "{\pi_j^1}"] \ar[d, "{\pi_j^2}"swap] & D(j) \ar[d, "{\phi_j}"] \\
+            & D(j) \ar[r, "{\phi_j}"swap] & D'(j)
+        \end{tikzcd}
+    \]
+
+    In this way, we get a functor $E: \cat{I \to C}$, 
+    {
+        \color{blue} which maps each $i$ onto $K_i$ and each arrow $\alpha$ onto $K(\alpha)$
+        We have in fact $E(id_i) = K(id_i) : K_i \to K_i$ is the arrow such that
+        \[
+            \begin{split}
+                D(id_i) \circ \pi_i^1 &= \pi_i^1 \circ K(id_i) \\
+                \pi_i^1 &= \pi_i^1 \circ K(id_i)
+            \end{split}
+                \qquad
+            \begin{split}
+                D(id_i) \circ \pi_i^2 &= \pi_i^2 \circ K(id_i) \\
+                \pi_i^2 &= \pi_i^2 \circ K(id_i)
+            \end{split}
+        \]
+        Thus, for the universal property of pullbacks, $K(id_i) = id_{K_i}$.
+
+        Suppose now $\alpha : i \to j$ and $\beta: j \to k$. Computing, we have
+        \[
+            \begin{split}
+                \pi_k^1 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^1 \\
+                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^1 \\
+                                                    &= D(\beta) \circ \pi_j^1 \circ K(\alpha) \\
+                                                    &= \pi_k^1 \circ K(\beta) \circ K(\alpha)
+            \end{split} \qquad
+            \begin{split}
+                \pi_k^2 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^2 \\
+                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^2 \\
+                                                    &= D(\beta) \circ \pi_j^2 \circ K(\alpha) \\
+                                                    &= \pi_k^2 \circ K(\beta) \circ K(\alpha)
+            \end{split}
+        \]
+        Again, for universal property of pullbacks, necessarily we have $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving functoriality of $E$.
+    }
+
+     Hence, we have two natural transformations $\pi^1, \pi^2 : E \dot\to D$.
+By \Cref{prop:reg_epi_coeq}, every component $\phi_i$ is the coequalizer of $\pi_i^1, \pi_i^2: E \to D$, and so $\phi$ is the coequalizer of $\pi^1$ and $\pi^2$.
 \end{proof}
+
+\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
+    Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
+If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
+\end{lemma}
+
+\begin{proof}
+    By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi: D \dot\to D'$ is a regular epimorphism, so that there is a functor $E: \cat{I \to C}$ and $\eta, \theta: E \dot\to D$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
+Let now $((p_i)_{i \in \cat I}, P)$ be the colimit of $E$, by \Cref{prop:nat_tran_induces_unique_arrow_between_colimits}, we have $a, b: P \to C$ fitting in the diagram below.
+    \[
+        \begin{tikzcd}[row sep = 26, column sep = 26]
+            E(i) \ar[r, "{p_i}"] \ar[d, "{\eta_i}"swap] & P \ar[d, dashed, "a"] \\
+            D(i) \ar[r, "{c_i}"swap] & C
+        \end{tikzcd}
+        \qquad
+        \begin{tikzcd}[row sep = 26, column sep = 26]
+            E(i) \ar[r, "{p_i}"] \ar[d, "{\theta_i}"swap] & P \ar[d, dashed, "b"] \\
+            D(i) \ar[r, "{c_i}"swap] & C
+        \end{tikzcd}
+    \]
+
+    We want to show that $c$ coequalizes $\eta$ and $\theta$. Let thus $t: C \to T$ be an arrow such that $t \circ a = t \circ b$. Then, for every $i$, we have
+    \begin{align*}
+        t \circ c_i \circ \eta_i &= t \circ a \circ p_i \\
+                                 &= t \circ b \circ p_i \\
+                                 &= t \circ c_i \circ \theta_i
+    \end{align*}
+
+    Thus, there is $t_i: D(i) \to T$ such that $t\circ c_i = t_i \circ \phi_i$.
+It is now easy to see that $((t_i)_{i \in \cat I}, T)$ is a cocone of $D'$: suppose $\alpha: i \to j$ be an arrow of $\cat I$, obtaining
+    \begin{align*}
+        t_i \circ \phi_i &= t \circ c_i \\
+                         &= t \circ c_j \circ D(\alpha) \\
+                         &= t_j \circ \phi_j \circ D(\alpha) \\
+                         &= t_j \circ D'(\alpha) \circ \phi_i
+    \end{align*}
+    By the hypothesis that $\phi_i$ is regular epi for each $i$, therefore epi (by the dual of \Cref{prop:eq_are_mono}), we can conclude $t_i = t_j \circ D'(\alpha)$.
+
+    Hence, we have an arrow $k: C' \to T$ such that $k \circ c_i' = t_i$. But then
+    \begin{align*}
+        c \circ c \circ c_i &= k \circ c_i' \circ \phi_i \\
+                            &= t_i \circ \phi \\
+                            &= t \circ c_i
+    \end{align*}
+    Showing that $k \circ c = t$.
+
+    For the uniqueness, let $k': C' \to T$ be another arrow such that $k' \circ c = t$. Then we have
+    \begin{align*}
+        k' \circ c_i' \circ \phi_i &= k' \circ c \circ c_i \\
+                                   &= t \circ c_i \\
+                                   &= t_i \circ \phi_i
+    \end{align*}    
+    Since $\phi_i$ is a regular epimorphism, we have $k' \circ c_i' = t_i$, and, because $k \circ c_i' = t_i$ by construction, we can conclude that $k'=k$ since $((c_i')_{i \in \cat I}, C')$ is a colimit.
+\end{proof}

### 2024-10-28 Article/Graph_sections/Eq_Graphs_Notes_Results.tex
Some proofs, reordering of material

@@
 
-\subsection{Some results on kernel pair and regular epis}
-\todo{Questi risultati vanno completati e distribuiti lungo la tesi: quello sui kernel pair nella parte sui pullback, quello sugli epi regolari nella parte sui coequalizzatori, quelli che riguardano l'adesività nella relativa sezione}
+{% \subsection{Some results on kernel pair and regular epis}
+% \todo{Questi risultati vanno completati e distribuiti lungo la tesi: quello sui kernel pair nella parte sui pullback, quello sugli epi regolari nella parte sui coequalizzatori, quelli che riguardano l'adesività nella relativa sezione}
 
-\todo{Sicuramente devi anche mettere dei riferimenti ai risultati della sez. sull'adesività (tipo alla proposizione che gli M-pushout sono pullback)}
+% \todo{Sicuramente devi anche mettere dei riferimenti ai risultati della sez. sull'adesività (tipo alla proposizione che gli M-pushout sono pullback)}
 
-\begin{lemma}\label{lem:pb1}
-	Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
-	\[\xymatrix{X\ar[r]^{f} \ar[d]_{t} & Y \ar[d]^{k}\ar[r]^{g} &Z \ar[d]^{h}\\A \ar[r]_{a}& B \ar[r]_{b} & C}\]
-\end{lemma}
-\begin{proof}
-	\todo{Esercizio per te}
-\end{proof}
+% \begin{lemma}\label{lem:pb1}
+% 	Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
+% 	\[\xymatrix{X\ar[r]^{f} \ar[d]_{t} & Y \ar[d]^{k}\ar[r]^{g} &Z \ar[d]^{h}\\A \ar[r]_{a}& B \ar[r]_{b} & C}\]
+% \end{lemma}
+% \begin{proof}
+% 	\todo{Esercizio per te}
+% \end{proof}
 
-\begin{cor}\label{cor:cube} Let $\cat{C}$ be a category and suppose that  the solid part of the following cube is given
-	\[\xymatrix@C=13pt@R=13pt{&Y'\ar[dd]|\hole_(.65){y}\ar[rr]^{g'} \ar@{.>}[dl]_{q'} && Z' \ar[dd]^{z} \ar[dl]_{r'} \\ B'  \ar[dd]_{b}\ar[rr]^(.65){k'} & & C' \ar[dd]_(.3){c}\\&Y\ar[rr]|\hole^(.65){g} \ar[dl]^{q} && Z \ar[dl]^{r} \\B \ar[rr]_{k} & & C}\]
-	If the front face is a pullback then there is a unique $q'\colon Y'\to B'$ filling the diagram.
+% \begin{cor}\label{cor:cube} Let $\cat{C}$ be a category and suppose that  the solid part of the following cube is given
+% 	\[\xymatrix@C=13pt@R=13pt{&Y'\ar[dd]|\hole_(.65){y}\ar[rr]^{g'} \ar@{.>}[dl]_{q'} && Z' \ar[dd]^{z} \ar[dl]_{r'} \\ B'  \ar[dd]_{b}\ar[rr]^(.65){k'} & & C' \ar[dd]_(.3){c}\\&Y\ar[rr]|\hole^(.65){g} \ar[dl]^{q} && Z \ar[dl]^{r} \\B \ar[rr]_{k} & & C}\]
+% 	If the front face is a pullback then there is a unique $q'\colon Y'\to B'$ filling the diagram.
 If, moreover, the other two vertical faces are also pullbacks, then the following square is a pullback too.
-	\[\xymatrix{Y' \ar[r]^{q'} \ar[d]_{y}& B'\ar[d]^{b}\\ Y \ar[r]_{q} & B}\]
-\end{cor}
-\begin{proof}
-	Let us compute:
-	\begin{align*}
-		c\circ r'\circ g'&=r\circ z \circ g'\\&=r\circ g \circ y\\&=k\circ q \circ y
-	\end{align*}
-	Since the front face is a pullback, this guarantees the existence of $q'$.  The second half of the thesis follows applying \cref{lem:pb1} to the following rectangle.
-	\[\xymatrix{Y'\ar@/^.4cm/[rr]^{r'\circ g'} \ar[r]_{q'} \ar[d]_{y}& B'\ar[d]_{b}\ar[r]_{k'}& C'\ar[d]^{c}\\ Y\ar@/_.4cm/[rr]_{r\circ g} \ar[r]^{q} & B \ar[r]^{k}& C}\]
-\end{proof}
+% 	\[\xymatrix{Y' \ar[r]^{q'} \ar[d]_{y}& B'\ar[d]^{b}\\ Y \ar[r]_{q} & B}\]
+% \end{cor}
+% \begin{proof}
+% 	Let us compute:
+% 	\begin{align*}
+% 		c\circ r'\circ g'&=r\circ z \circ g'\\&=r\circ g \circ y\\&=k\circ q \circ y
+% 	\end{align*}
+% 	Since the front face is a pullback, this guarantees the existence of $q'$.  The second half of the thesis follows applying \cref{lem:pb1} to the following rectangle.
+% 	\[\xymatrix{Y'\ar@/^.4cm/[rr]^{r'\circ g'} \ar[r]_{q'} \ar[d]_{y}& B'\ar[d]_{b}\ar[r]_{k'}& C'\ar[d]^{c}\\ Y\ar@/_.4cm/[rr]_{r\circ g} \ar[r]^{q} & B \ar[r]^{k}& C}\]
+% \end{proof}
 
-\iffalse 
-In an $\mathcal{M}$-adhesive category, pullbacks also enjoy a kind of left cancellation property.
+% \iffalse 
+% In an $\mathcal{M}$-adhesive category, pullbacks also enjoy a kind of left cancellation property.
 
-\begin{lemma}\label{lem:pb2}
-	Let $\cat{C}$ be a category with pullbacks, given the following diagrams:
-	\[
-	\xymatrix{Y\ar[r]^{f_2} \ar[d]_{f_1} & X_2 \ar[d]^{r_2} & Z_1 \ar[d]_{x_1}\ar[r]^{z_1} & W \ar[r]^{w} \ar[d]_{r} & Q'\ar[d]^{q} & Z_2 \ar[d]_{x_2} \ar[r]^{z_2}  & W  \ar[r]^{w} \ar[d]_{r}  & Q' \ar[d]^{q}\\ X_1 \ar[r]_{r_1} &R  & X_1 \ar[r]_{r_1} & R \ar[r]_{s}  & Q& X_2 \ar[r]_{r_2} & R \ar[r]_{s} & Q}\]
-	if the first square is a stable pushout and the whole rectangles and their left halves are pullbacks, then their common right half is a pullback too.
-\end{lemma}
-\begin{proof}Pulling back  $q$ along $s$ we get a square 
-	\[\xymatrix{U \ar[r]^{u} \ar[d]_{h}& Q' \ar[d]^{q}\\ R \ar[r]_s & S}\]
-	Notice that
-	\[
-	q\circ w\circ z_1=s\circ r_1\circ x_1 \qquad 
-	q\circ w\circ z_2=s\circ r_2\circ x_2 \]
-	Thus we get $u_1\colon Z_1\to U$ and $u_2\colon Z_2\to U$ fitting in the rectangles
-	\[\xymatrix{  Z_1  \ar@/^.4cm/[rr]^{w\circ z_1}\ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q}&  Z_2 \ar@/^.4cm/[rr]^{w\circ z_2} \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\  X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
-	which, by hypothesis and  \cref{lem:pb1} have left halves which are pullbacks. Now,
-	\[s\circ r_1\circ f_1 =s\circ r_2\circ f_2\]
-	Pulling back $q$ along this arrow we get another square
-	\[\xymatrix@C=40pt{Z'_0 \ar[r]^{t} \ar[d]_{y}& Q' \ar[d]^{q}\\ R \ar[r]_{s\circ r_1\circ f_1} & S}\]
-	In particular, we obtain the dotted $b_1\colon Z'_0\to Z_1$ and $b_2\colon Z'_0\to Z_2$ in
-	\[\xymatrix@C=30pt{ Z'_0 \ar@/^.4cm/[rrr]^{t}\ar[d]_{y} \ar@{.>}[r]_{b_1} & Z_1  \ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q} &Z'_0 \ar@/^.4cm/[rrr]^{t} \ar[d]_{y}\ar@{.>}[r]_{b_2}  & Z_2  \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
-	in which, using again \cref{lem:pb1}, all of the squares on the bottom rows are pullbacks.
+% \begin{lemma}\label{lem:pb2}
+% 	Let $\cat{C}$ be a category with pullbacks, given the following diagrams:
+% 	\[
+% 	\xymatrix{Y\ar[r]^{f_2} \ar[d]_{f_1} & X_2 \ar[d]^{r_2} & Z_1 \ar[d]_{x_1}\ar[r]^{z_1} & W \ar[r]^{w} \ar[d]_{r} & Q'\ar[d]^{q} & Z_2 \ar[d]_{x_2} \ar[r]^{z_2}  & W  \ar[r]^{w} \ar[d]_{r}  & Q' \ar[d]^{q}\\ X_1 \ar[r]_{r_1} &R  & X_1 \ar[r]_{r_1} & R \ar[r]_{s}  & Q& X_2 \ar[r]_{r_2} & R \ar[r]_{s} & Q}\]
+% 	if the first square is a stable pushout and the whole rectangles and their left halves are pullbacks, then their common right half is a pullback too.
+% \end{lemma}
+% \begin{proof}Pulling back  $q$ along $s$ we get a square 
+% 	\[\xymatrix{U \ar[r]^{u} \ar[d]_{h}& Q' \ar[d]^{q}\\ R \ar[r]_s & S}\]
+% 	Notice that
+% 	\[
+% 	q\circ w\circ z_1=s\circ r_1\circ x_1 \qquad 
+% 	q\circ w\circ z_2=s\circ r_2\circ x_2 \]
+% 	Thus we get $u_1\colon Z_1\to U$ and $u_2\colon Z_2\to U$ fitting in the rectangles
+% 	\[\xymatrix{  Z_1  \ar@/^.4cm/[rr]^{w\circ z_1}\ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q}&  Z_2 \ar@/^.4cm/[rr]^{w\circ z_2} \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\  X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
+% 	which, by hypothesis and  \cref{lem:pb1} have left halves which are pullbacks. Now,
+% 	\[s\circ r_1\circ f_1 =s\circ r_2\circ f_2\]
+% 	Pulling back $q$ along this arrow we get another square
+% 	\[\xymatrix@C=40pt{Z'_0 \ar[r]^{t} \ar[d]_{y}& Q' \ar[d]^{q}\\ R \ar[r]_{s\circ r_1\circ f_1} & S}\]
+% 	In particular, we obtain the dotted $b_1\colon Z'_0\to Z_1$ and $b_2\colon Z'_0\to Z_2$ in
+% 	\[\xymatrix@C=30pt{ Z'_0 \ar@/^.4cm/[rrr]^{t}\ar[d]_{y} \ar@{.>}[r]_{b_1} & Z_1  \ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q} &Z'_0 \ar@/^.4cm/[rrr]^{t} \ar[d]_{y}\ar@{.>}[r]_{b_2}  & Z_2  \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
+% 	in which, using again \cref{lem:pb1}, all of the squares on the bottom rows are pullbacks.
 
-	We are going to construct another row above these two rectangles. By hypothesis 
-	\[q\circ w = s\circ r\]
-	Thus there exists a unique $g\colon W\to U$ such that
-	\[r=h\circ g \qquad w=u\circ g\]
-	Moreover, we also have that
-	\[\begin{split}h\circ g \circ z_1&=r \circ z_1\\&= r_1\circ x_1 \\&=h\circ u_1
-	\end{split}\qquad\begin{split}h\circ g \circ z_2&=r \circ z_2\\&= r_2\circ x_2 \\&=h\circ u_2
-	\end{split}\]
-	and 
-	\[\begin{split}u\circ g \circ z_1&=w \circ z_1\\&= u\circ u_1 
-	\end{split} \qquad \begin{split}u\circ g \circ z_1&=w \circ z_2\\&= u\circ u_2
-	\end{split}\]
-	which together show that
-	\[g\circ z_1=u_1 \qquad g\circ z_2=u_2\]
+% 	We are going to construct another row above these two rectangles. By hypothesis 
+% 	\[q\circ w = s\circ r\]
+% 	Thus there exists a unique $g\colon W\to U$ such that
+% 	\[r=h\circ g \qquad w=u\circ g\]
+% 	Moreover, we also have that
+% 	\[\begin{split}h\circ g \circ z_1&=r \circ z_1\\&= r_1\circ x_1 \\&=h\circ u_1
+% 	\end{split}\qquad\begin{split}h\circ g \circ z_2&=r \circ z_2\\&= r_2\circ x_2 \\&=h\circ u_2
+% 	\end{split}\]
+% 	and 
+% 	\[\begin{split}u\circ g \circ z_1&=w \circ z_1\\&= u\circ u_1 
+% 	\end{split} \qquad \begin{split}u\circ g \circ z_1&=w \circ z_2\\&= u\circ u_2
+% 	\end{split}\]
+% 	which together show that
+% 	\[g\circ z_1=u_1 \qquad g\circ z_2=u_2\]
 
-	Summing up, we can depict all the arrows we have constucted so far in the following diagrams
-	\[\xymatrix{Z'_0 \ar[r]^{b_1} \ar[d]_{id_{Z'}}& Z_1 \ar[r]^{z_1} \ar[d]_{id_{Z_1}} &  W \ar[d]_g \ar[r]^{w} & Q' \ar[d]^{id_{Q'}}&& Z'_0 \ar[r]^{b_2}  \ar[d]_{id_{Z'}}& Z_2 \ar[d]_{id_{Z_2}} \ar[r]^{z_2}&  W \ar[d]_g\ar[r]^{w}& Q' \ar[d]^{id_{Q'}}\\ Z'_0 \ar[d]_{y} \ar[r]^{b_1} & Z_1  \ar[r]^{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]^{u} & Q'  \ar[d]^{q}& &Z'_0  \ar[d]_{y}\ar[r]^{b_2}  & Z_2  \ar[r]^{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]^{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & &Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
-	If we show that $g$ is an isomorphism we are done. Consider the cubes
-	\[\xymatrix@C=13pt@R=13pt{&Z_0'\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{z_2}  &&Z'_0\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{F_j(b)} \ar[dl]_{u_2}\\Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){z_1} & & W \ar[dd]_(.3){r}&& Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){u_1} & &U \ar[dd]_(.3){h}\\&Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2} && Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2}\\X_1 \ar[rr]_{r_1} & & R && X_1 \ar[rr]_{r_1} & & R}\]
-	in which the vertical faces are pullbacks. Since the bottom face is a stable pushout we can deduce that
-	\[\xymatrix{Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{z_2} & Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{u_2}\\ Z_1 \ar[r]_{z_1}& W & Z_1 \ar[r]_{u_1}& U }\]
-	are pushout squares too. The arrow $g$ fits in the following  diagram
-	\[\xymatrix{Z'_0\ar[r]^{b_2} \ar[d] _{b_1}& Z_2 \ar@/^.3cm/[ddr]^{u_2}\ar[d]^{z_2} \\ Z_1 \ar[r]_{z_1}  \ar@/_.3cm/[drr]_{u_1}& W \ar[dr]^{g} \\ &&U}\]
-	and thus it is an isomorphism.
-\end{proof} 
-\fi
+% 	Summing up, we can depict all the arrows we have constucted so far in the following diagrams
+% 	\[\xymatrix{Z'_0 \ar[r]^{b_1} \ar[d]_{id_{Z'}}& Z_1 \ar[r]^{z_1} \ar[d]_{id_{Z_1}} &  W \ar[d]_g \ar[r]^{w} & Q' \ar[d]^{id_{Q'}}&& Z'_0 \ar[r]^{b_2}  \ar[d]_{id_{Z'}}& Z_2 \ar[d]_{id_{Z_2}} \ar[r]^{z_2}&  W \ar[d]_g\ar[r]^{w}& Q' \ar[d]^{id_{Q'}}\\ Z'_0 \ar[d]_{y} \ar[r]^{b_1} & Z_1  \ar[r]^{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]^{u} & Q'  \ar[d]^{q}& &Z'_0  \ar[d]_{y}\ar[r]^{b_2}  & Z_2  \ar[r]^{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]^{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & &Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
+% 	If we show that $g$ is an isomorphism we are done. Consider the cubes
+% 	\[\xymatrix@C=13pt@R=13pt{&Z_0'\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{z_2}  &&Z'_0\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{F_j(b)} \ar[dl]_{u_2}\\Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){z_1} & & W \ar[dd]_(.3){r}&& Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){u_1} & &U \ar[dd]_(.3){h}\\&Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2} && Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2}\\X_1 \ar[rr]_{r_1} & & R && X_1 \ar[rr]_{r_1} & & R}\]
+% 	in which the vertical faces are pullbacks. Since the bottom face is a stable pushout we can deduce that
+% 	\[\xymatrix{Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{z_2} & Z'_0 \ar[d]_{b_1} \ar[r]^{b_2}&  Z_2 \ar[d]^{u_2}\\ Z_1 \ar[r]_{z_1}& W & Z_1 \ar[r]_{u_1}& U }\]
+% 	are pushout squares too. The arrow $g$ fits in the following  diagram
+% 	\[\xymatrix{Z'_0\ar[r]^{b_2} \ar[d] _{b_1}& Z_2 \ar@/^.3cm/[ddr]^{u_2}\ar[d]^{z_2} \\ Z_1 \ar[r]_{z_1}  \ar@/_.3cm/[drr]_{u_1}& W \ar[dr]^{g} \\ &&U}\]
+% 	and thus it is an isomorphism.
+% \end{proof} 
+% \fi
 
-\begin{definition}A \emph{kernel pair} $(K_f, p_{f, 1}, p_{f,2})$ for an arrow $f\colon X\to Y$ is an object $K_f$ with two arrows $p_{f,1}, p_{f, 2}\colon K_f\to X$ making the following square a pullback.
-	\[\xymatrix{K_f \ar[r]^{p_{f,1}} \ar[d]_{p_{f,2}}& X \ar[d]^{f}\\ X \ar[r]_{f} & Y}\]
-\end{definition}
+% \begin{definition}A \emph{kernel pair} $(K_f, p_{f, 1}, p_{f,2})$ for an arrow $f\colon X\to Y$ is an object $K_f$ with two arrows $p_{f,1}, p_{f, 2}\colon K_f\to X$ making the following square a pullback.
+% 	\[\xymatrix{K_f \ar[r]^{p_{f,1}} \ar[d]_{p_{f,2}}& X \ar[d]^{f}\\ X \ar[r]_{f} & Y}\]
+% \end{definition}
 
-\begin{remark}
-	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
-\end{remark}
+% \begin{remark}
+% 	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
+% \end{remark}
 
-\begin{prop}\label{prop:kermono}
-	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
-\end{prop}
-\begin{proof}\todo{esercizio}
-\end{proof}
+% \begin{prop}\label{prop:kermono}
+% 	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
+% \end{prop}
+% \begin{proof}\todo{esercizio}
+% \end{proof}
 
-\begin{cor}\label{cor:kermono}
-	Let $(K_f, p_{f,1}, p_{f,2})$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, p_{f,1}, p_{f,2})$ is a kernel pair also for $m\circ f$.
-\end{cor}
-\begin{proof}
-	It is enough to see that, by \Cref{lem:pb1,prop:kermono} the outer boundary of the following square is a pullback.
-	\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{id_X} \ar[d]_{f}&X\ar[d]^{f} \\X \ar[d]_{id_X} \ar[r]_{f} & Y \ar[d]_{id_Y} \ar[r]_{id_Y}& Y \ar[d]^{m}\\X \ar[r]_{f} & Y \ar[r]_{m} & Z}\]
+% \begin{cor}\label{cor:kermono}
+% 	Let $(K_f, p_{f,1}, p_{f,2})$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, p_{f,1}, p_{f,2})$ is a kernel pair also for $m\circ f$.
+% \end{cor}
+% \begin{proof}
+% 	It is enough to see that, by \Cref{lem:pb1,prop:kermono} the outer boundary of the following square is a pullback.
+% 	\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{id_X} \ar[d]_{f}&X\ar[d]^{f} \\X \ar[d]_{id_X} \ar[r]_{f} & Y \ar[d]_{id_Y} \ar[r]_{id_Y}& Y \ar[d]^{m}\\X \ar[r]_{f} & Y \ar[r]_{m} & Z}\]
 
-\end{proof}
+% \end{proof}
 
-\begin{lemma}\label{lem:salvavita1}
-Suppose that the following square is given and that $f\colon X\to Y$ and $g\colon Z\to W$ have kernel pairs.
-\[\xymatrix{X \ar[d]_{f}\ar[r]^{h}& Z \ar[d]^{g} \\ Y \ar[r]_{t}& W}\]
+% \begin{lemma}\label{lem:salvavita1}
+% Suppose that the following square is given and that $f\colon X\to Y$ and $g\colon Z\to W$ have kernel pairs.
+% \[\xymatrix{X \ar[d]_{f}\ar[r]^{h}& Z \ar[d]^{g} \\ Y \ar[r]_{t}& W}\]
 
-Then there exists a unique arrow $k_h\colon K_f\to K_g$ making the squares below commutes.
+% Then there exists a unique arrow $k_h\colon K_f\to K_g$ making the squares below commutes.
 
-\[\xymatrix{K_f \ar[d]_{p_{f, 1}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,1}} & K_f \ar[d]_{p_{f,2}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,2}} \\ X \ar[r]_{h}& Z & X \ar[r]_{h}& Z}\]
+% \[\xymatrix{K_f \ar[d]_{p_{f, 1}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,1}} & K_f \ar[d]_{p_{f,2}}\ar@{.>}[r]^{k_h}& K_g \ar[d]^{p_{g,2}} \\ X \ar[r]_{h}& Z & X \ar[r]_{h}& Z}\]
 
-Moreover, if the beginning square is a pullback, then also the preceding ones are so.
-\end{lemma}
-\begin{proof}
-	Computing we have
-	\begin{align*}
-		g\circ h\circ p_{f,1}&=t\circ f\circ p_{f,1}\\&=t\circ f\circ p_{f,2}\\&=g\circ h\circ p_{f,2}
-	\end{align*}
-	So that the wanted $k_h$ exists, and it is unique, by the universal property of $K_g$ as the pullback of $g$ along itself.
+% Moreover, if the beginning square is a pullback, then also the preceding ones are so.
+% \end{lemma}
+% \begin{proof}
+% 	Computing we have
+% 	\begin{align*}
+% 		g\circ h\circ p_{f,1}&=t\circ f\circ p_{f,1}\\&=t\circ f\circ p_{f,2}\\&=g\circ h\circ p_{f,2}
+% 	\end{align*}
+% 	So that the wanted $k_h$ exists, and it is unique, by the universal property of $K_g$ as the pullback of $g$ along itself.
 
-	To prove the second half of the thesis, let us consider the  two rectangles below, which, by \Cref{lem:pb1} are pullbacks.
-\[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{h} \ar[d]^{f} & Z \ar[d]^{g} & K_f \ar[r]^{p_{f,2}}  \ar[d]_{p_{f,1}} & X \ar[d]^{f} \ar[r]^{h}& Z \ar[d]^{g}\\
-	X \ar[r]_{f}& Y \ar[r]_{t}& W&  X \ar[r]_f & Y\ar[r]_{t} & W}\]
+% 	To prove the second half of the thesis, let us consider the  two rectangles below, which, by \Cref{lem:pb1} are pullbacks.
+% \[\xymatrix{K_f\ar[r]^{p_{f,1}}  \ar[d]_{p_{f,2}}& X \ar[r]^{h} \ar[d]^{f} & Z \ar[d]^{g} & K_f \ar[r]^{p_{f,2}}  \ar[d]_{p_{f,1}} & X \ar[d]^{f} \ar[r]^{h}& Z \ar[d]^{g}\\
+% 	X \ar[r]_{f}& Y \ar[r]_{t}& W&  X \ar[r]_f & Y\ar[r]_{t} & W}\]
 
-	But then the following ones are pullbacks too.
- 	\[\xymatrix{K_f \ar@/^.4cm/[rr]^{h\circ p_{f,2}} \ar[r]_{k_h} \ar[d]_{p_{f,1}}& K_g  \ar[r]_{p_{g,2}} \ar[d]_{p_{g,1}} & Z \ar[d]^{g} & K_f \ar@/^.4cm/[rr]^{h\circ p_{f,1}} \ar[r]_{k_h} \ar[d]_{p_{f,2}}& K_g \ar[r]_{p_{g,1}} \ar[d]_{p_{g,2}} & Z \ar[d]^{g}\\X \ar@/_.4cm/[rr]_{t\circ f}\ar[r]^{h}& Z \ar[r]^{g} & W & X \ar@/_.4cm/[rr]_{t\circ f} \ar[r]^{h}& Z \ar[r]^{g}& W}\]
+% 	But then the following ones are pullbacks too.
+%  	\[\xymatrix{K_f \ar@/^.4cm/[rr]^{h\circ p_{f,2}} \ar[r]_{k_h} \ar[d]_{p_{f,1}}& K_g  \ar[r]_{p_{g,2}} \ar[d]_{p_{g,1}} & Z \ar[d]^{g} & K_f \ar@/^.4cm/[rr]^{h\circ p_{f,1}} \ar[r]_{k_h} \ar[d]_{p_{f,2}}& K_g \ar[r]_{p_{g,1}} \ar[d]_{p_{g,2}} & Z \ar[d]^{g}\\X \ar@/_.4cm/[rr]_{t\circ f}\ar[r]^{h}& Z \ar[r]^{g} & W & X \ar@/_.4cm/[rr]_{t\circ f} \ar[r]^{h}& Z \ar[r]^{g}& W}\]
 
- 	The thesis now follows again by \Cref{lem:pb1}.
-\end{proof}
+%  	The thesis now follows again by \Cref{lem:pb1}.
+% \end{proof}
 
-\begin{lemma}\label{lem:salvavita2}
-Let $\cat{C}$ be an $\mathcal{M}$-adhesive category with all pullbacks and suppose that the cube below is given, in which every face is a pullback and the bottom one is an $\mathcal{M}$-pushout.
+% \begin{lemma}\label{lem:salvavita2}
+% Let $\cat{C}$ be an $\mathcal{M}$-adhesive category with all pullbacks and suppose that the cube below is given, in which every face is a pullback and the bottom one is an $\mathcal{M}$-pushout.
 
- 	\[\xymatrix@C=10pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D}\]
-Then the square below is a pushout.
-\[\xymatrix{K_{a} \ar[r]^{k_{f'}}  \ar[d]_{k_{m'}}& K_b \ar[d]^{k_{n'}}\\ K_c \ar[r]_{k_{g'}} & K_d}\]
-\end{lemma}
-\begin{proof} By \Cref{lem:salvavita1} in the following cube the vertical faces are all pullbacks. 
-		\[\xymatrix@C=10pt@R=10pt{&K_a\ar[dd]|\hole_(.65){p_{a,1}}\ar[rr]^{k_{f'}} \ar[dl]_{k_{m'}} && K_b \ar[dd]^{p_{b,1}} \ar[dl]_{k_{n'}} \\ K_c  \ar[dd]_{p_{c,1}}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){p_{d,1}}\\&A'\ar[rr]|\hole^(.65){f'} \ar[dl]^{m'} && B' \ar[dl]^{n'} \\C' \ar[rr]_{g'} & & D'}\]
-	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
-\end{proof}
+%  	\[\xymatrix@C=10pt@R=10pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D}\]
+% Then the square below is a pushout.
+% \[\xymatrix{K_{a} \ar[r]^{k_{f'}}  \ar[d]_{k_{m'}}& K_b \ar[d]^{k_{n'}}\\ K_c \ar[r]_{k_{g'}} & K_d}\]
+% \end{lemma}
+% \begin{proof} By \Cref{lem:salvavita1} in the following cube the vertical faces are all pullbacks. 
+% 		\[\xymatrix@C=10pt@R=10pt{&K_a\ar[dd]|\hole_(.65){p_{a,1}}\ar[rr]^{k_{f'}} \ar[dl]_{k_{m'}} && K_b \ar[dd]^{p_{b,1}} \ar[dl]_{k_{n'}} \\ K_c  \ar[dd]_{p_{c,1}}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){p_{d,1}}\\&A'\ar[rr]|\hole^(.65){f'} \ar[dl]^{m'} && B' \ar[dl]^{n'} \\C' \ar[rr]_{g'} & & D'}\]
+% 	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
+% \end{proof}
 
-\begin{prop}\label{prop:regepi}
-	Let $e\colon X\to Y$ be a regular epi in a category $\cat{C}$ with a kernel pair $p_1, p_2\colon P\rightrightarrows X$, then $e$ is the coequalizer of $p_1$ and $p_2$.
-\end{prop}
-\begin{proof}
-	By hypothesis there exists a pair $f, g\colon Z\rightrightarrows X$ of which $e$ is the coequalizer, since $e\circ f=e\circ g$ we have a diagram
-	\[\xymatrix{	Z \ar@/^.5cm/[drr]^{f} \ar@/_.5cm/[ddr]_{g} \ar@{.>}[dr]^{k}& &	\\ &P\ar[r]^{p_1} \ar[d]_{p_2} & X \ar[d]^{e} \\& X \ar[r]_{e}  & Y}\]
-	and thus there exists  the dotted $k\colon Z\to P$. Let $h\colon Z\to V$ be an arrow such that $h\circ p_1=h\circ p_2$, then
-	\begin{align*}h\circ f &= h \circ p_1\circ k \\&= h \circ p_2\circ k \\&=h\circ g
-	\end{align*}
-	and thus there exists a unique $l\colon Y\to V$ such that $l\circ e=h$.
-\end{proof}
+% \begin{prop}\label{prop:regepi}
+% 	Let $e\colon X\to Y$ be a regular epi in a category $\cat{C}$ with a kernel pair $p_1, p_2\colon P\rightrightarrows X$, then $e$ is the coequalizer of $p_1$ and $p_2$.
+% \end{prop}
+% \begin{proof}
+% 	By hypothesis there exists a pair $f, g\colon Z\rightrightarrows X$ of which $e$ is the coequalizer, since $e\circ f=e\circ g$ we have a diagram
+% 	\[\xymatrix{	Z \ar@/^.5cm/[drr]^{f} \ar@/_.5cm/[ddr]_{g} \ar@{.>}[dr]^{k}& &	\\ &P\ar[r]^{p_1} \ar[d]_{p_2} & X \ar[d]^{e} \\& X \ar[r]_{e}  & Y}\]
+% 	and thus there exists  the dotted $k\colon Z\to P$. Let $h\colon Z\to V$ be an arrow such that $h\circ p_1=h\circ p_2$, then
+% 	\begin{align*}h\circ f &= h \circ p_1\circ k \\&= h \circ p_2\circ k \\&=h\circ g
+% 	\end{align*}
+% 	and thus there exists a unique $l\colon Y\to V$ such that $l\circ e=h$.
+% \end{proof}
 
-\begin{cor}\label{cor:regepi1}
-Let $\cat{C}$ be a category with pullbacks and $\phi\colon D\to D'$ be a natural transformation between two functor $D, D'\colon \cat{I}\to \cat{C}$.
+% \begin{cor}\label{cor:regepi1}
+% Let $\cat{C}$ be a category with pullbacks and $\phi\colon D\to D'$ be a natural transformation between two functor $D, D'\colon \cat{I}\to \cat{C}$.
 If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
-\end{cor}
-\begin{proof}
-	Let $K_i$ be the kernel pair of $\phi_i$, with projections $p_{1,i}, p_{2,i}\colon K_i\rightrightarrows D(i)$. Given an arrow $f\colon i\to j$ in $\cat{I}$, we have 
-	\begin{align*}
-		\phi_j\circ D(f)\circ p_{1,i}&=D'(f)\circ \phi_i\circ p_{1,i}\\&=D'(f)\circ \phi_i\circ p_{2,i}\\&=\phi_j\circ D(f)\circ p_{2,i}
-	\end{align*}
+% \end{cor}
+% \begin{proof}
+% 	Let $K_i$ be the kernel pair of $\phi_i$, with projections $p_{1,i}, p_{2,i}\colon K_i\rightrightarrows D(i)$. Given an arrow $f\colon i\to j$ in $\cat{I}$, we have 
+% 	\begin{align*}
+% 		\phi_j\circ D(f)\circ p_{1,i}&=D'(f)\circ \phi_i\circ p_{1,i}\\&=D'(f)\circ \phi_i\circ p_{2,i}\\&=\phi_j\circ D(f)\circ p_{2,i}
+% 	\end{align*}
 
-	Thus the outer boundary of the diagram below commutes, yielding the dotted arrows $K(f)$.
-	\[\xymatrix{K_i \ar@{.>}[dr]^{K(f)}\ar[r]^{p_{1,i}} \ar[d]_{p_{2,i}}& D(i) \ar[dr]^{D(f)}\\D(i) \ar[dr]_{D(f)}&K_j \ar[r]^{p_{1,j}} \ar[d]_{p_{2,j}} & D(j) \ar[d]^{\phi_j}\\ &D(j) \ar[r]_{\phi_j} & D'(j)}\]
+% 	Thus the outer boundary of the diagram below commutes, yielding the dotted arrows $K(f)$.
+% 	\[\xymatrix{K_i \ar@{.>}[dr]^{K(f)}\ar[r]^{p_{1,i}} \ar[d]_{p_{2,i}}& D(i) \ar[dr]^{D(f)}\\D(i) \ar[dr]_{D(f)}&K_j \ar[r]^{p_{1,j}} \ar[d]_{p_{2,j}} & D(j) \ar[d]^{\phi_j}\\ &D(j) \ar[r]_{\phi_j} & D'(j)}\]
 
-	In this way \todo{esercizio per te}we get a functor $E\colon \cat{I}\to \cat{C}$ with two natural transformations $p_{1}, p_2\colon E\rightrightarrows D$.
+% 	In this way \todo{esercizio per te}we get a functor $E\colon \cat{I}\to \cat{C}$ with two natural transformations $p_{1}, p_2\colon E\rightrightarrows D$.
 By \Cref{prop:regepi} every component  $\phi_i$ of $\phi$ is the coequalizer of $p_{1,i}, p_{2,i}\colon E\rightrightarrows D$ and so $\phi$ is the coequalizer of $p_1$ and $p_2$.
-\end{proof}
+% \end{proof}
 
-\todo{COSE DA FARE: nel capitolo 1 metti una proposizione in cui mostri che da ogni trasf naturale $D\to D'$ puoi ricavare una freccia tra i colimiti, così in questa e nelle altre proposizioni puoi citarla.}
+% \todo{COSE DA FARE: nel capitolo 1 metti una proposizione in cui mostri che da ogni trasf naturale $D\to D'$ puoi ricavare una freccia tra i colimiti, così in questa e nelle altre proposizioni puoi citarla.}
 
-\begin{lemma}\label{lem:regepi}
-	Let $D, D'\colon \cat{I}\rightrightarrows  \cat{C}$ be two diagrams diagram with colimiting cocone $(C, \{c_i\}_{i\in \cat{I}})$ and   $(Q, \{q_i\}_{i\in \cat{I}})$.
+% \begin{lemma}\label{lem:regepi}
+% 	Let $D, D'\colon \cat{I}\rightrightarrows  \cat{C}$ be two diagrams diagram with colimiting cocone $(C, \{c_i\}_{i\in \cat{I}})$ and   $(Q, \{q_i\}_{i\in \cat{I}})$.
 If $\cat{C}$ has all colimits for diagrams of shape $\cat{I}$ and $\phi\colon D\to D'$ is a natural transformation in which all components are regular epis, then the canonical arrow\todo{richiama prop precedente}  $c\colon C\to Q$ is a regular epi to.
-\end{lemma}
-\begin{proof}
-	By \Cref{cor:regepi1} we know that $\phi\colon D\to D'$ is a regular epi, so that there is a functor $E\colon \cat{I}\to \cat{C}$ and $\alpha, \beta\colon E\rightrightarrows D$ such that $\phi$ is a coequalizer for $\alpha$ and $\beta$.
+% \end{lemma}
+% \begin{proof}
+% 	By \Cref{cor:regepi1} we know that $\phi\colon D\to D'$ is a regular epi, so that there is a functor $E\colon \cat{I}\to \cat{C}$ and $\alpha, \beta\colon E\rightrightarrows D$ such that $\phi$ is a coequalizer for $\alpha$ and $\beta$.
 Let $(P, \{p_i\}_{i\in \cat{I}})$ be the colimit of $E$, by ???\todo{richiama prop sulla freccia tra i colimiti} we have arrows $a, b\colon P\rightrightarrows  C$ fitting in the diagram belows:
-	\[\xymatrix{E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i}& P \ar@{.>}[d]^{a} & E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i} & P \ar@{.>}[d]^{b}\\ D(i) \ar[r]_{c_i} & C & D(i) \ar[r]_{c_i} & C}\]
+% 	\[\xymatrix{E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i}& P \ar@{.>}[d]^{a} & E(i) \ar[r]^{p_i} \ar[d]_{\alpha_i} & P \ar@{.>}[d]^{b}\\ D(i) \ar[r]_{c_i} & C & D(i) \ar[r]_{c_i} & C}\]
 
-	We want to show that $c$ coequalizes $a$ and $b$. Let thus $t\colon C\to T$ be an arrow such that $t\circ a=t\circ b$. Then for every $i\in I$ we have 
-	\begin{align*}
-		t\circ c_i\circ \alpha_i&=t\circ a\circ p_i\\&=t\circ b\circ p_i\\&=t\circ c_i\circ \beta_i
-	\end{align*}
+% 	We want to show that $c$ coequalizes $a$ and $b$. Let thus $t\colon C\to T$ be an arrow such that $t\circ a=t\circ b$. Then for every $i\in I$ we have 
+% 	\begin{align*}
+% 		t\circ c_i\circ \alpha_i&=t\circ a\circ p_i\\&=t\circ b\circ p_i\\&=t\circ c_i\circ \beta_i
+% 	\end{align*}
 
-	Thus there is $t_i\colon D'(i)\to T$ such that $t\circ c_i=t_i\circ \phi_i$.
+% 	Thus there is $t_i\colon D'(i)\to T$ such that $t\circ c_i=t_i\circ \phi_i$.
 It is now easy to see that $(T, \{t_i\}_{i\in \cat{I}})$ is a cocone on $D'$ \todo{Verificalo!}.
@@
 But then we have
-	\begin{align*}
-		k\circ c\circ c_i&=k\circ q_i\circ \phi_i\\&=t_i\circ \phi\\&=t\circ c_i
-	\end{align*}
-	Showing that $k\circ c=t$.
+% 	\begin{align*}
+% 		k\circ c\circ c_i&=k\circ q_i\circ \phi_i\\&=t_i\circ \phi\\&=t\circ c_i
+% 	\end{align*}
+% 	Showing that $k\circ c=t$.
 
-	For uniqueness, let $k'$ be another arrow $Q\to T$ such that $k'\circ c=t$, then we have
-	\begin{align*}
-		k'\circ q_i\circ \phi_i&=k'\circ c\circ c_i\\&=t\circ c_i\\&=t_i\circ \phi_i
-	\end{align*}
-	Since $\phi_i$ is a regular epi, by ???\todo{mettere nel capitolo 1 una proposizione che mostra che epi regolari sono epi} this entails $k'\circ q_i=t_i$.
+% 	For uniqueness, let $k'$ be another arrow $Q\to T$ such that $k'\circ c=t$, then we have
+% 	\begin{align*}
+% 		k'\circ q_i\circ \phi_i&=k'\circ c\circ c_i\\&=t\circ c_i\\&=t_i\circ \phi_i
+% 	\end{align*}
+% 	Since $\phi_i$ is a regular epi, by ???\todo{mettere nel capitolo 1 una proposizione che mostra che epi regolari sono epi} this entails $k'\circ q_i=t_i$.
 By construction $k\circ q_i=t_i$ and  so $k=k'$ since $(Q, \{q_i\}_{i\in \cat{I}})$ is a colimiting cocone.
-\end{proof}
+% \end{proof}
 
-\begin{definition}
-	A \emph{graph with equivalence} is a 6-uple $(A, B, C, s, t, q)$ where $A, B$ and $C$ are set, $s,t\colon A\rightrightarrows B$ are functions and $q\colon B\to C$ is another surjective function.
+% \begin{definition}
+% 	A \emph{graph with equivalence} is a 6-uple $(A, B, C, s, t, q)$ where $A, B$ and $C$ are set, $s,t\colon A\rightrightarrows B$ are functions and $q\colon B\to C$ is another surjective function.
 
-	A morphism  $(A, B, C, s, t, q)\to (A', B', C', s', t', q')$ is a triple $(h_1, h_2, h_3)$ of functions $h_1\colon A\to A'$, $h_2\colon B\to B'$ and $h_3\colon C\to C'$ making the following diagrams commute.
+% 	A morphism  $(A, B, C, s, t, q)\to (A', B', C', s', t', q')$ is a triple $(h_1, h_2, h_3)$ of functions $h_1\colon A\to A'$, $h_2\colon B\to B'$ and $h_3\colon C\to C'$ making the following diagrams commute.
 
-	\[\xymatrix{A \ar[r]^{s} \ar[d]_{h_1} & B \ar[d]^{h_2} & A \ar[r]^{s} \ar[d]_{h_1}& B \ar[d]^{h_2} & B \ar[d]_{h_2} \ar[r]^{q} & C \ar[d]^{h_3}\\A' \ar[r]_{s'} & B' & A ' \ar[r]_{t'}& B' & B' \ar[r]_{q'} & C'}\]
+% 	\[\xymatrix{A \ar[r]^{s} \ar[d]_{h_1} & B \ar[d]^{h_2} & A \ar[r]^{s} \ar[d]_{h_1}& B \ar[d]^{h_2} & B \ar[d]_{h_2} \ar[r]^{q} & C \ar[d]^{h_3}\\A' \ar[r]_{s'} & B' & A ' \ar[r]_{t'}& B' & B' \ar[r]_{q'} & C'}\]
 
-	In this way, defining the composition componentwise, we get a category $\EqGrph$.
-\end{definition}
+% 	In this way, defining the composition componentwise, we get a category $\EqGrph$.
+% \end{definition}
 
-\begin{remark}\label{rem:fedele}
-	There is a faithful functor $U\colon \EqGrph\to \Graph$, forgetting the quotient part. \todo{Questo è per te da dimostrare (forse meglio come proposizione che come remark).}
-\end{remark}
+% \begin{remark}\label{rem:fedele}
+% 	There is a faithful functor $U\colon \EqGrph\to \Graph$, forgetting the quotient part. \todo{Questo è per te da dimostrare (forse meglio come proposizione che come remark).}
+% \end{remark}
 
-\begin{remark}
-There is another functor $V\colon \EqGrph\to \Set$ sending $(A, B,C, s,t, q)$ to $C$ and a morphism to its last component.	
-\end{remark}
+% \begin{remark}
+% There is another functor $V\colon \EqGrph\to \Set$ sending $(A, B,C, s,t, q)$ to $C$ and a morphism to its last component.	
+% \end{remark}
 
-\begin{prop}\label{prop:limits}
-	$\EqGrph$ is complete, cocomplete and $U$ preserves limits and colimits.
-\end{prop}
+% \begin{prop}\label{prop:limits}
+% 	$\EqGrph$ is complete, cocomplete and $U$ preserves limits and colimits.
+% \end{prop}
 
-\begin{remark}\label{rem:ima}\todo{Dimostrala}In $\Set$ we have the following property: for every square as the one below, if $e\colon X\to Y$ is epi and $m\colon M\to Z$ is mono, then there exists a unique dotted arrow $Y\to M$ making the diagram below commutative.
-	\[\xymatrix{X \ar[r]^{f} \ar[d]_{e}& M \ar[d]^{m}\\ Y \ar[r]_{g} \ar@{.>}[ur]^{h}& Z}\] 
-\end{remark}
+% \begin{remark}\label{rem:ima}\todo{Dimostrala}In $\Set$ we have the following property: for every square as the one below, if $e\colon X\to Y$ is epi and $m\colon M\to Z$ is mono, then there exists a unique dotted arrow $Y\to M$ making the diagram below commutative.
+% 	\[\xymatrix{X \ar[r]^{f} \ar[d]_{e}& M \ar[d]^{m}\\ Y \ar[r]_{g} \ar@{.>}[ur]^{h}& Z}\] 
+% \end{remark}
 
-\begin{proof}\todo{Per generalizzare ad altre categorie: serve poter fattorizzare con un epi regolare.} 
-	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$.
+% \begin{proof}\todo{Per generalizzare ad altre categorie: serve poter fattorizzare con un epi regolare.} 
+% 	NOTATION: $D(i)$ is $(A_i, B_i, Q_i, s_i, t_i, q_i)$.	Let $(A, B, s, t)$ be the limit of $U\circ D$, with projections $(p_{1,i}, p_{2,i})\colon (A,B, s,t)\to (A_i, B_i, s_i, t_i)$.
 Let $(L, \{l_i\}_{i\in \cat{I}})$ be a limiting cone for $V\circ D$.
 
-	Now, notice that $(B, \{q_i\circ p_{2,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Dimostralo}, so that we have an arrow $l\colon B\to L$.
+% 	Now, notice that $(B, \{q_i\circ p_{2,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Dimostralo}, so that we have an arrow $l\colon B\to L$.
 This arrow is not epi in general, let $Q$ be its image and $q\colon B\to Q$ be the resulting epi and $m\colon Q\to L$ the corresponding mono.
-	By definition the external square in the diagram below commutes, so for every $i\in \cat{I}$, \Cref{rem:ima} yields the dotted arrow $p_{3,i}$.
-	\[\xymatrix{B \ar[r]^{p_{2,i}} \ar[d]_{q}& B_i \ar[r]^{q_i} & Q_i \ar[d]^{id_{Q_i}}\\ Q \ar[r]_{m} \ar@{.>}[urr]_{p_{3,i}}& L \ar[r]_{l_i} & Q_i}\]
+% 	By definition the external square in the diagram below commutes, so for every $i\in \cat{I}$, \Cref{rem:ima} yields the dotted arrow $p_{3,i}$.
+% 	\[\xymatrix{B \ar[r]^{p_{2,i}} \ar[d]_{q}& B_i \ar[r]^{q_i} & Q_i \ar[d]^{id_{Q_i}}\\ Q \ar[r]_{m} \ar@{.>}[urr]_{p_{3,i}}& L \ar[r]_{l_i} & Q_i}\]
 
-	We have to show that in this way we get a cone over the diagram $D$. Let $f\colon i\to j$ be an arrow of $\cat{I}$, then we have:
-	\begin{align*}
-	U(D(f)\circ (p_{1,i}, p_{2, i}, p_{3,i}))  &=  U(D(f))\circ(p_{1,i}, p_{2, i})\\
-                                                   &=  (p_{1,j}, p_{2, j})\\
-                                                   &=  U(D(f)\circ (p_{1,j}, p_{2, j}, p_{3,j}))
-	\end{align*}
-	 And faithfulness of $U$ yields the thesis.
+% 	We have to show that in this way we get a cone over the diagram $D$. Let $f\colon i\to j$ be an arrow of $\cat{I}$, then we have:
+% 	\begin{align*}
+% 	U(D(f)\circ (p_{1,i}, p_{2, i}, p_{3,i}))  &=  U(D(f))\circ(p_{1,i}, p_{2, i})\\
+%                                                    &=  (p_{1,j}, p_{2, j})\\
+%                                                    &=  U(D(f)\circ (p_{1,j}, p_{2, j}, p_{3,j}))
+% 	\end{align*}
+% 	 And faithfulness of $U$ yields the thesis.
 
-	 To see that this cone is terminal, let $(E, F, G, a, b, c)$ be another graph with the vertex of a cone with sides $(t_{1,i},t_{2, i}, t_{3,i})$.
+% 	 To see that this cone is terminal, let $(E, F, G, a, b, c)$ be another graph with the vertex of a cone with sides $(t_{1,i},t_{2, i}, t_{3,i})$.
 By construction, we have an arrow $(t_1, t_2)\colon (E, F, a, b)\to (A, B, s, t)$ such that
-	 \[\xymatrix{&E \ar@{.>}[dl]_{t_1} \ar[dr]^{t_{1,i}}&&&F \ar@{.>}[dl]_{t_2} \ar[dr]^{t_{2,i}}\\ A \ar[rr]_{p_{1,i}} & & A_i & B \ar[rr]_{p_{2,i}}&& B_i }\]
+% 	 \[\xymatrix{&E \ar@{.>}[dl]_{t_1} \ar[dr]^{t_{1,i}}&&&F \ar@{.>}[dl]_{t_2} \ar[dr]^{t_{2,i}}\\ A \ar[rr]_{p_{1,i}} & & A_i & B \ar[rr]_{p_{2,i}}&& B_i }\]
 
-        Moreover $(G, \{t_{3,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Verificalo}, thus there exists an arrow $t\colon G\to L$ such that $l_i\circ t =t_{3,i}$.
+%         Moreover $(G, \{t_{3,i}\}_{i\in \cat{I}})$ is a cone over $V\circ D$, \todo{Verificalo}, thus there exists an arrow $t\colon G\to L$ such that $l_i\circ t =t_{3,i}$.
 Now, precomposing with $c$ we get
-	\begin{align*}
-		l_i\circ t\circ c&=t_{3,i}\circ c\\&=q_i\circ t_{2,i}\\&=q_i\circ p_{2,i}\circ t_2\\&=l_i\circ l\circ t_2
-	\end{align*}
+% 	\begin{align*}
+% 		l_i\circ t\circ c&=t_{3,i}\circ c\\&=q_i\circ t_{2,i}\\&=q_i\circ p_{2,i}\circ t_2\\&=l_i\circ l\circ t_2
+% 	\end{align*}
 
-	Therefore the solid part of the diagram below commutes and \Cref{rem:ima} yields the dotted arrow $t_3\colon G\to Q$.
+% 	Therefore the solid part of the diagram below commutes and \Cref{rem:ima} yields the dotted arrow $t_3\colon G\to Q$.
 
-	\[\xymatrix{F \ar[r]^{t_2} \ar[d]_{c}& B \ar[r]^{q} & Q \ar[d]^{m}\\G \ar[rr]_{t} \ar@{.>}[urr]^{t_3}&& L}\]
+% 	\[\xymatrix{F \ar[r]^{t_2} \ar[d]_{c}& B \ar[r]^{q} & Q \ar[d]^{m}\\G \ar[rr]_{t} \ar@{.>}[urr]^{t_3}&& L}\]
 
-	Faithfulness \todo{esercizio per te: scrivere la dimostrazione di queste ultime due righe}of $U$ now guarantees that $(t_1, t_2, t_3)$ is the unique arrow such that $(p_{1,i}, p_{2,i}, p_{3,i})\circ(t_1, t_2, t_3)=(t_{1,i},t_{2, i}, t_{3,i})$.	\todo{esercizio per te: fare i colimiti.
+% 	Faithfulness \todo{esercizio per te: scrivere la dimostrazione di queste ultime due righe}of $U$ now guarantees that $(t_1, t_2, t_3)$ is the unique arrow such that $(p_{1,i}, p_{2,i}, p_{3,i})\circ(t_1, t_2, t_3)=(t_{1,i},t_{2, i}, t_{3,i})$.	\todo{esercizio per te: fare i colimiti.
 Hint: la dimostrazione è diversa ma più semplice.
@@
 Per la proprietà del colimite hai una freccia $B\to Q$, mostra che è epi (segue in una riga dai risultati che abbiamo).}
-\end{proof}
+% \end{proof}
 
-\begin{cor}
-	An arrow $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ in $\EqGrph$ is mono if and only if $h_1$ and $h_2$ are mono in $\Set$.
-\end{cor}
-\begin{proof}
-	\todo{esercizio per te, usa fedeltà e continuità}
-\end{proof}
+% \begin{cor}
+% 	An arrow $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ in $\EqGrph$ is mono if and only if $h_1$ and $h_2$ are mono in $\Set$.
+% \end{cor}
+% \begin{proof}
+% 	\todo{esercizio per te, usa fedeltà e continuità}
+% \end{proof}
 
-\begin{cor}\label{cor:regmono}Let $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ be a morphism of $\EqGrph$, then the following are equivalent:
-	\begin{enumerate}
-		\item $(h_1, h_2, h_3)$ is a regular mono;
-		\item $h_1$, $h_2$, $h_3$ are all monos;
-		\item $h_1$ and $h_2$ are mono and for every $f, f'\in F$, $c(h_2(f))=c(h_2(f'))$ if and only if $q(f)=q(f')$.
-	\end{enumerate}
-\end{cor}
-\begin{proof}
-	$1\Rightarrow 2.$ \todo{Esercizio}
+% \begin{cor}\label{cor:regmono}Let $(h_1, h_2, h_3)\colon (A, B, C, s,t, q)\to (E, F, G, a,b,c)$ be a morphism of $\EqGrph$, then the following are equivalent:
+% 	\begin{enumerate}
+% 		\item $(h_1, h_2, h_3)$ is a regular mono;
+% 		\item $h_1$, $h_2$, $h_3$ are all monos;
+% 		\item $h_1$ and $h_2$ are mono and for every $f, f'\in F$, $c(h_2(f))=c(h_2(f'))$ if and only if $q(f)=q(f')$.
+% 	\end{enumerate}
+% \end{cor}
+% \begin{proof}
+% 	$1\Rightarrow 2.$ \todo{Esercizio}
 
-	\smallskip \noindent
-	$2\Rightarrow 3.$ \todo{Esercizio}
+% 	\smallskip \noindent
+% 	$2\Rightarrow 3.$ \todo{Esercizio}
 
-	\smallskip \noindent 
-	$3\Rightarrow 1.$\todo{Esercizio}
-\end{proof}
+% 	\smallskip \noindent 
+% 	$3\Rightarrow 1.$\todo{Esercizio}
+% \end{proof}
 
-Let us turn to another functor $\EqGrph\to \Graph$.
+% Let us turn to another functor $\EqGrph\to \Graph$.
 
-\begin{definition}
-The \emph{quotient functor} $Q:\EqGrph\to \Graph $ sends $(A, B, C, s,t, q)$ to $(A, C, q\circ s, q\circ t)$ and an arrow $(h_1, h_2, h_3) \colon (A, B, C, s,t, q)\to (E, F, G, a,b, c)$ to $(h_1, h_3)$.
-\end{definition}
+% \begin{definition}
+% The \emph{quotient functor} $Q:\EqGrph\to \Graph $ sends $(A, B, C, s,t, q)$ to $(A, C, q\circ s, q\circ t)$ and an arrow $(h_1, h_2, h_3) \colon (A, B, C, s,t, q)\to (E, F, G, a,b, c)$ to $(h_1, h_3)$.
+% \end{definition}
 
-\todo{Verifica che questa cosa funziona $(h_1, h_3)$ è un morfismo di grafi?}
+% \todo{Verifica che questa cosa funziona $(h_1, h_3)$ è un morfismo di grafi?}
 
-\begin{lemma}
-	$Q$ is a left  adjoint.
-\end{lemma}
-\begin{proof} Let us start proving that $Q$ is a left adjoint.
+% \begin{lemma}
+% 	$Q$ is a left  adjoint.
+% \end{lemma}
+% \begin{proof} Let us start proving that $Q$ is a left adjoint.
 Let $R(A,B, s, t)$ be $(A, B, B, s,t, id_{B})$ , so that $Q(R(A,B,s,t))=(A,B,s,t)$.
@@
 Notice that, since $(h_1, h_2)$ is an arrow in $\Graph$:
-	\[h_2\circ c\circ a= s\circ h_1 \qquad  h_2\circ c\circ b= t\circ h_1\]
+% 	\[h_2\circ c\circ a= s\circ h_1 \qquad  h_2\circ c\circ b= t\circ h_1\]
 
-	 Then we have three squares:
+% 	 Then we have three squares:
 
-\[\xymatrix{E \ar[r]^{a} \ar[d]_{h_1} & F \ar[d]^{h_2\circ c} & E \ar[r]^{b} \ar[d]_{h_1}& F \ar[d]_{h_2\circ c} & B \ar[d]_{h_2\circ c} \ar[r]^{c} & C \ar[d]^{h_2}\\A \ar[r]_{s} & B & A  \ar[r]_{t}& B & B \ar[r]_{id_B} & B}\]
+% \[\xymatrix{E \ar[r]^{a} \ar[d]_{h_1} & F \ar[d]^{h_2\circ c} & E \ar[r]^{b} \ar[d]_{h_1}& F \ar[d]_{h_2\circ c} & B \ar[d]_{h_2\circ c} \ar[r]^{c} & C \ar[d]^{h_2}\\A \ar[r]_{s} & B & A  \ar[r]_{t}& B & B \ar[r]_{id_B} & B}\]
 
-	 We have therefore found a morphism $(E,F,G, a,b,c)\to R(A,B,s,t)$ whose image through $Q$ fits in the diagram below.
-	\[\xymatrix{(A, B, s,t)\ar[r]^{(id_A, id_B)} &(A, B, s,t)\\ (E, G, q\circ s, q\circ t) \ar[ur]_{(h_1, h_2)} \ar[u]^{Q(h_1, h_2\circ q, h_2)}}\]
+% 	 We have therefore found a morphism $(E,F,G, a,b,c)\to R(A,B,s,t)$ whose image through $Q$ fits in the diagram below.
+% 	\[\xymatrix{(A, B, s,t)\ar[r]^{(id_A, id_B)} &(A, B, s,t)\\ (E, G, q\circ s, q\circ t) \ar[ur]_{(h_1, h_2)} \ar[u]^{Q(h_1, h_2\circ q, h_2)}}\]
 
-\todo{Esercizio: prova unicità (è facile)}
-\end{proof}
+% \todo{Esercizio: prova unicità (è facile)}
+% \end{proof}
+}
+\subsection{Rimanenze da integrare}
 

### 2024-10-28 Article/Background_sections/Limit.tex
Restating Cor. 2.2.7

@@
 
-\begin{remark}
+\begin{remark}\label{rem:limits_are_unique_up_to_isomorphisms}
     It makes sense to refer to a (co)limit as \emph{the} (co)limit.
@@
 
+\begin{remark}
+    Since a kernel pair is nothing more that a pullback, that is, a limit, by \Cref{rem:limits_are_unique_up_to_isomorphisms}, it make sense to refer to it as \emph{the} kernel pair for a morphism $f$.
+\end{remark}
+
+\begin{example}\label{ex:kernel_pairs_in_Set}
+    In $\Set$, a kernel pair for a function $f: A\to B$ is the set
+    \[
+        K_f=\{(x, y) \in A \times A \mid f(x) = f(y)\}
+    \]
+    together with the canonical projection on the first and the second component of the pairs.
+\end{example}
+
 \begin{prop}\label{prop:kermono}
@@
 \begin{cor}\label{cor:kermono}
-	Let $(K_f, \pi_f^1, \pi_f^2)$ be a kernel pair for $f\colon X\to Y$. Then for every mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
+	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$ if and only if, for each mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
 \end{cor}
@@
     \end{tikzcd}\]
+    The leftward part of the statement follows by definition of monomorphism an \Cref{lemma:pullback_lemma}.
 \end{proof}

### 2024-10-28 Article/Graph_sections/Eq_Graphs_integration.tex
Restating Cor. 2.2.7

@@
 		\item $h_E$, $h_V$, $h_C$ are all monos;
-		\item $h_E$ and $h_V$ are mono and for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$.
+%		\item $h_E$ and $h_V$ are mono and for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$.
+            \item $h_E$ and $h_V$ are mono and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_H \circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_G$.
 	\end{enumerate}
@@
 	\smallskip \noindent
-	$2\Rightarrow 3.$ The leftward side of the statement is satisfied by the definition of morphism of graphs with equivalences. For the remaining part, we have
-    \begin{align*}
-        (\eqgraph{H}(q) \circ h_V) (v)  &=  (\eqgraph{H}(q) \circ h_V)(v') \\
-        (h_C \circ \eqgraph{G}(q))(v)   &=  (h_C \circ \eqgraph{G}(q))(v')  
-    \end{align*}
-        since $h_C$ is mono, we can conclude $\eqgraph{G}(q)(v)= \eqgraph{G}(q)(v')$.
+	% $2\Rightarrow 3.$ The leftward side of the statement is satisfied by the definition of morphism of graphs with equivalences. For the remaining part, we have
+ %    \begin{align*}
+ %        (\eqgraph{H}(q) \circ h_V) (v)  &=  (\eqgraph{H}(q) \circ h_V)(v') \\
+ %        (h_C \circ \eqgraph{G}(q))(v)   &=  (h_C \circ \eqgraph{G}(q))(v')  
+ %    \end{align*}
+ %        since $h_C$ is mono, we can conclude $\eqgraph{G}(q)(v)= \eqgraph{G}(q)(v')$.
+        \smallskip \noindent
+	$2\Rightarrow 3.$ We note that, by \Cref{cor:kermono}, $(K, \pi_1, \pi_2)$ is the kernel pair of $q_G$ if and only if it is the kernel pair also of $h_C \circ q_G$, since $h_C$ is mono by hypothesis.
+The thesis follows from $h_C \circ q_G = q_H \circ h_V$, and from the hypothesis of $h_E$ mono.
 
@@
 \end{proof}
+
+\begin{remark}
+    It is possible to restate the third point of the \Cref{cor:regmono}, by \Cref{ex:kernel_pairs_in_Set}, as 
+    \begin{displayquote}
+    \textit{$h_E$ and $h_V$ are mono and, for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$}
+    \end{displayquote}
+    That is, a regular monomorphism in $\EqGrph$ is a morphism that reflects equivalences besides preserving them.
+\end{remark}
 

### 2024-10-29 Article/Background_sections/Basic_Notions.tex
Def of subobjects, lemma 1.2.13, 1.2.15

@@
 
-For a morphism, from an algebraic point of view, being mono means being \emph{left cancellable}.
-This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
+\begin{remark}\label{rem:fact_of_subobject_is_unique}
+    For a morphism, from an algebraic point of view, being mono means being \emph{left cancelable}.
+    %This fact can led us to define a particular kind of class of morphisms, which will reveal useful further.
+    Let $A$ be an object in a category $\cat C$.
+Given two monomorphism $m: X \to A$ and $n: Y \to A$, then if  $h: X \to Y$ is a morphism such that $m = n \circ h$, then is the unique one: suppose $k$ is another morphism such that $m = n \circ k$.
+We can conclude $h = k$ observing that $n \circ h = n \circ k$ implies $h = k$ when $n$ is mono, which is by hypothesis.
+\end{remark}
 
-\begin{definition}[Subobjects]
-    Let $C$ be an object in a category $\cat C$.
+\begin{definition}[Subobject]\label{def:subobj}
+    Starting from this consideration, we can define a preorder on monomorphisms, placing $m \leq n$ if $m = n \circ h$ for some $h$.
+Such preorder induces an equivalence relation $\equiv$ on monomorphisms with codomain $A$, where $m \equiv n$ whenever $m \leq n$ and $n \leq m$, and the corresponding equivalence class is called \emph{subobject} of $A$.
+\end{definition}
+
+% \begin{definition}[Subobjects]
+%     Let $C$ be an object in a category $\cat C$.
 Then, if $m: A \rightarrow C$ is mono\todo{sinceramente non trovo molto sensata la scelta di chiamare sottoggetto la coppia $(A, m)$.
@@
 $(A, m) \leq (B, n)$ whenever there exists a morphism $f : A\rightarrow B$ such that $m = n \circ f$.
-    \[
-        \begin{tikzcd}[row sep=9]
-            A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
-            & B \\
-            C \arrow[ur, "n"swap] &
-        \end{tikzcd}
-    \]
-    Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
-\end{definition}
+%     \[
+%         \begin{tikzcd}[row sep=9]
+%             A \arrow[dr, "m"] \arrow[dd, dashed, "f"swap] & \\
+%             & B \\
+%             C \arrow[ur, "n"swap] &
+%         \end{tikzcd}
+%     \]
+%     Two subobject $(A, m)$ and $(B, n)$ can are said to be \emph{equivalent subobjects}, written $(A, m) \approx (B, n)$ if $(A, m)\leq (B, n)$ and $(B, n) \leq (A, m)$. 
+% \end{definition}
 
-An useful fact about subobjects is how factorization behaves.
+% An useful fact about subobjects is how factorization behaves.
 In particular $(A, m)$ and $(B, n)$ are subobjects of $C$.
@@
 
-\begin{prop}\label{prop:fact_of_subobjects_is_unique}
-    Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
-\end{prop}
+% \begin{prop}\label{prop:fact_of_subobjects_is_unique}
+%     Let $(A, m)$ and $(B, n)$ be subobjects of $C$ in a category $\cat C$, with $(A, m)\leq (B, n)$. Then, the factorization of $m$ through $n$ is unique.
+% \end{prop}
 

### 2024-10-29 Article/Background_sections/Functors_NatTrans_Adjs.tex
Def of subobjects, lemma 1.2.13, 1.2.15

@@
 The \Cref{obs:comp_assoc_nat_tran} shows that natural transformations recreate on the functors the same structure that morphisms in a category have on objects.
-This leds us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
+This leads us to define a particular kind of category, in which objects are functors between two categories, and arrow are natural transformations.
 
@@
 \end{definition}
+
+\begin{lemma}\label{lemma:canonical_equiv}
+    Let $\cat{C, D, I}$ be categories. Then, it holds that
+    \[
+        \cat{[I, [C, D]] \cong [I \times C, D]}
+    \]
+\end{lemma}
 
@@
 \end{remark}
+
+\begin{lemma}\label{lemma:limits_of_presheaves}
+    Let $\cat C$ be a category, and let $[\cat C, \Set]$ be the category of presheaves on $\cat C$.
+Let $D: \cat I \to [\cat C, \Set]$ be a diagram of shape $\cat I$ on the presheaves category early mentioned.
+Then,
+    \begin{enumerate}
+        \item The limit of $D$ exists, and it is the presheaf $L: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $L(A)$ is the limit in $\Set$ of the values of the presheaves $D(i)(A)$ for each $i$.
+        \item The colimit of $D$ exists, and it is the presheaf $C: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $C(A)$ is the colimit in $\Set$ of the values of the presheaves $D(i)(A)$, for each $i$.
+    \end{enumerate}
+\end{lemma}
 

### 2024-10-29 Article/Background_sections/Limit.tex
Def of subobjects, lemma 1.2.13, 1.2.15

@@
     \]
-    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$
+    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$. Sometimes we will refer to the unique arrow $k$ as the \emph{mediating arrow}.
 \end{definition}
@@
 
-\begin{obs}\label{obs:limits_in_presh}
-    So far we introduced categories of presheaves.
-In these categories, an interesting fact is that limits and colimits are computed pointwise -- i.e., the limit of a diagram in a category of presheaves is exactly the limit on each of its components.
-\end{obs}
-
 In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.
@@
 
+\begin{prop}\label{prop:pairng_of_kernel_pairs_mono}
+    Let $(K, p_1, p_2)$ be the kernel pair of $f: X \to Y$, and let $(X\times X, \pi_1, \pi_2)$ be the product of $X$ with itself.
+Then, the mediating arrow $\langle p_1, p_2\rangle : K \to X \times X$ is mono.
+\end{prop}
+
 \begin{prop}\label{prop:kermono}
@@
 \end{proof}
+
+\begin{remark}\label{rem:monos_in_presh_cats}
+    From characterization of monos via pullbacks in \Cref{prop:kermono} and \Cref{lemma:limits_of_presheaves}, we have that a mono in a category of presheaves is a natural transformation of which each component is mono.
+\end{remark}
 

### 2024-10-29 Article/Graph_sections/EGGs.tex
Def of subobjects, lemma 1.2.13, 1.2.15

@@
 \begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The full subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
+    The subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
 \end{definition}

### 2024-10-29 Article/Graph_sections/Graphs.tex
Some proofs, reordering of material
Def of subobjects, lemma 1.2.13, 1.2.15

@@
 
-\todo{Dimostrare come si calcolano i limiti nelle categorie di prefasci (conponente per componente) e poi dare qualche esempio, porendendolo dalla versione precedente.
-Dimostrare anche come sono fatti i mono (mono sulle componenti).}
+Since $\Graph$ is a category of presheaves, \Cref{lemma:limits_of_presheaves} guarantees the existence of limits and colimits, and gives us an easy way to compute them.
+
+\begin{cor}\label{cor:graph_has_co_limits}
+    $\Graph$ has all limits and colimits.
+\end{cor}
+
+\begin{example}\label{ex:in_term_in_graph}
+    The initial object in $\mathbf{Graph}$ is the empty graph, i.e., the graph with an empty set of vertices and an empty set of edges.
+The initial object instead is the graph with exactly one node and a single edge from that node to itself.
+\end{example}
+
+\begin{example}
+    Given two graphs $G = (V_G, E_G, s_G, t_G)$ and $H=(V_H, E_H, s_H, t_H)$, the graph $G \times H = (V_G\times V_H, E_G \times E_H, (s_G, s_H), (t_G, t_H))$, where $(s_G, s_H), (t_G, t_H):V_G\times V_H \rightarrow E_G \times E_H$ are the pairwise sources and targets, is the categorical product in $\mathbf{Graph}$, together with the two projections $\pi_G: G \times H \rightarrow G$, $\pi_H : G \times H \rightarrow H$ defined in the obvious way.
+\end{example}
+
+\begin{example}
+    The equalizer of two morphisms $h, k: G \rightarrow H$ in $\mathbf{Graph}$ is defined as in $\Set$, that is,  a graph $Q$ together with a graph morphism $q$ that is the restriction of $G$ to all the vertices and all the arcs that are mapped on the same vertices and edges both from $h$ and $k$.
+Formally, $(Q, q)$ is an equalizer for $h, k: G \rightarrow H$, $h = (h_V, h_E), k = (k_V, k_E)$ where $V(Q) = \{ n \in V(G) \mid h_V(n) = k_V(n)\}$, $E(Q) = \{ e \in E(G) \mid h_E(e) = k_E(e)\}$, $s_Q = s_G \mid_{V(Q)}$, $t_E = t_G \mid_{V(Q)}$.
+\end{example}
+
+%\todo{Dimostrare come si calcolano i limiti nelle categorie di prefasci (conponente per componente) e poi dare qualche esempio, porendendolo dalla versione precedente.
+Dimostrare anche come sono fatti i mono (mono sulle componenti) (Nei prefasci dipende dalla caratterizzqazione dei mono via pullback (Vedi roba kernel pairs)).}
 \begin{remark}

### 2024-10-30 Article/Background_sections/Basic_Notions.tex
Def of subobjects, lemma 1.2.13, 1.2.15

@@
     \end{enumerate}
-    Two operators, $dom$ and $cod$, that map every morphism $f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
+    Two operators, $dom$ and $cod$, that map every morphism \-$f \in \Hom(\cat{C})$ to two objects, respectively, its \emph{domain} and its \emph{codomain}.
 In case $dom\ f = A$ and $cod\ f = B$, we will write $f: A \rightarrow B$.
@@
 \end{prop}
-\todo{val la pena osservare la relazione di equivalenza tra sottoggetti corrisponde ad avere un isomorfismo tra i domini}
+
+\begin{obs}\label{obs:equiv_subobj_implies_isom_of_domains}
+    Consider two monomorphisms $m: X \to A$ and $n: Y \to A$, and suppose $m \equiv n$ (in the sense of \Cref{def:subobj}).
+This corresponds to having a isomorphism between $X$ and $Y$.
+in fact, since $m \leq n$, there exists s unique $h: Y \to X$ such that $m = n \circ h$, and, since $n \leq m$, there exists a unique $k: X \to Y$ such that $n = m \circ k$.
+But then
+    \[
+        \begin{split}
+            m &= n \circ h \\
+              &= m \circ h \circ k
+        \end{split}
+        \qquad
+        \begin{split}
+            n &= m \circ k \\
+              &= n \circ h \circ k
+        \end{split}
+    \]
+    Since $m$ is mono, we obtain $id_X = h \circ k$, and, since $n$ is mono, $id_Y = k\circ h$, thus, an isomorphism. 
+\end{obs}
 
@@
 
-\begin{proof}
+{\color{red}\begin{proof}
     Before we start proving the statement, we have to note that, given a function $t: A \to B$, it is possible to decompose it as a composition of a injective function and a surjective function, considering the function $A \to t(A)$ sending each element onto its image along $t$, and then applying the inclusion $t(A) \to B$, and such functions are unique.
@@
     For the diagram above to commute, must be $f_i \circ f_s = h \circ e$ and $g_s \circ g_i = m \circ h$\todo{completare!!!}
-\end{proof}
+\end{proof}}
 

### 2024-10-30 Article/Graph_sections/Eq_Graphs_integration.tex
Def of subobjects, lemma 1.2.13, 1.2.15

@@
     \[
-        \begin{tikzcd}
+        \begin{tikzcd}[row sep = 26, column sep = 26]
             & E \arrow[dl, dashed, "{\tau_E}" swap] \arrow[dr, "{\tau_E^i}"] & \\
@@
         %
-        \begin{tikzcd}
+        \begin{tikzcd}[row sep = 26, column sep = 26]
             & F \arrow[dl, dashed, "{\tau_V}" swap] \arrow[dr, "{\tau_V^i}"] & \\

### 2024-11-04 Article/Background_sections/Basic_Notions.tex
some proofs

@@
 
-{\color{red}\begin{proof}
-    Before we start proving the statement, we have to note that, given a function $t: A \to B$, it is possible to decompose it as a composition of a injective function and a surjective function, considering the function $A \to t(A)$ sending each element onto its image along $t$, and then applying the inclusion $t(A) \to B$, and such functions are unique.
+%{\color{red}\begin{proof}
+%    Before we start proving the statement, we have to note that, given a function $t: A \to B$, it is possible to decompose it as a composition of a injective function and a surjective function, considering the function $A \to t(A)$ sending each element onto its image along $t$, and then applying the inclusion $t(A) \to B$, and such functions are unique.
 Another way to factorize $t$ is via a composition of a surjective function and an injective function.
@@
 
-    Let now be $f = f_i \circ f_s$ be the decomposition of $f$ with $f_s$ surjective (i.e., epi in $\Set$) and $f_i$ injective (i.e., mono in $\Set$), and $g = g_i \circ g_s$ be the decomposition of $g$ with $g_i$ injective and $g_s$ surjective, having the following situation.
-    \[
-        \begin{tikzcd}
-            X \ar[r, "{f_s}"] \ar[d, "e"] & f(X) \ar[r, "{f_i}"] & M \ar[d, "m"] \\
-            Y \ar[r, "{g_i}"swap] \ar[urr, "h"]& Y/_\sim \ar[r, "{g_s}"swap] & Z
-        \end{tikzcd}
-    \]
-    For the diagram above to commute, must be $f_i \circ f_s = h \circ e$ and $g_s \circ g_i = m \circ h$\todo{completare!!!}
-\end{proof}}
+%    Let now be $f = f_i \circ f_s$ be the decomposition of $f$ with $f_s$ surjective (i.e., epi in $\Set$) and $f_i$ injective (i.e., mono in $\Set$), and $g = g_i \circ g_s$ be the decomposition of $g$ with $g_i$ injective and $g_s$ surjective, having the following situation.
+%    \[
+%        \begin{tikzcd}
+%            X \ar[r, "{f_s}"] \ar[d, "e"] & f(X) \ar[r, "{f_i}"] & M \ar[d, "m"] \\
+%            Y \ar[r, "{g_i}"swap] \ar[urr, "h"]& Y/_\sim \ar[r, "{g_s}"swap] & Z
+%        \end{tikzcd}
+%   \]
+%    For the diagram above to commute, must be $f_i \circ f_s = h \circ e$ and $g_s \circ g_i = m \circ h$\todo{completare!!!}
+%\end{proof}}
+\begin{proof}
+	Let $y \in Y$.
+Since $e$ is epi (i.e., surjective), there exists $x \in X$ such that $e(x) = y$.
+Then, we put $h(y) = f(x)$.
+$h$ is well defined, in fact, let $x' \in X$ be such that $e(x') = y$.
+In this case, we have $h(x) = f(x')$, and so
+	\begin{align*}
+		(m \circ f) (x')  &= (g \circ e) (x') \\
+				&= g(y)		\\
+				&= (g \circ e) (x)	\\
+				&= (m \circ f) (x)
+	\end{align*}
+	since $m$ is mono by hypothesis, $f(x) = f(x')$.
+\end{proof}
 

### 2024-11-04 Article/Background_sections/Limit.tex
Def of subobjects, lemma 1.2.13, 1.2.15
some proofs

@@
 
-\subsection{Kernel Pairs an Regular Epimorphisms}
+\subsection{Kernel Pairs and Regular Epimorphisms}
 
@@
 \end{prop}
+
+\begin{proof}
+	Suppose $\langle p_1, p_2 \rangle \circ f = \langle p_1, p_2 \rangle \circ g$ for $f, g: Z \to K$. Then, we have
+	\[
+		\begin{split}
+			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
+			\pi_1 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_1 \circ \langle p_1, p_2 \rangle \circ g \\
+			p_1 \circ f &= p_1 \circ g
+		\end{split}
+		\qquad
+		\begin{split}
+			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
+			\pi_2 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_2 \circ \langle p_1, p_2 \rangle \circ g \\
+			p_2 \circ f &= p_2 \circ g
+		\end{split}
+	\]
+	Thus, from the universal property of the pullback, $f = g$.
+\end{proof}
 
@@
 
-    In this way, we get a functor $E: \cat{I \to C}$, 
-    {
-        \color{blue} which maps each $i$ onto $K_i$ and each arrow $\alpha$ onto $K(\alpha)$
-        We have in fact $E(id_i) = K(id_i) : K_i \to K_i$ is the arrow such that
+    In this way, we get a functor $K: \cat{I \to C}$, 
+    which maps each $i$ onto $K_i$ and each arrow $\alpha$ onto $K(\alpha)$. 
+	We have in fact $K(id_i) : K_i \to K_i$ is the arrow such that
         \[
@@
         \]
-        Again, for universal property of pullbacks, necessarily we have $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving functoriality of $E$.
-    }
+        Again, for universal property of pullbacks, necessarily we have $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving functoriality of $K$.
 

### 2024-11-04 Article/Graph_sections/EGGs.tex
some proofs

@@
 But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
+But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the kernel pair of $q \circ s$, and $T$ (together with the projections $q_1, q_2$) is the kernel pair of $q \circ t$ (\Cref{ex:kernel_pairs_in_Set}).
 Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
@@
 
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
+% Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
+% \[
+%     \begin{tikzcd}
+%         K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
+%         X \arrow[r, "f"swap] & Y
+%     \end{tikzcd}
+% \]
+% Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
+% \todo{capire quanto andare nello specifico qui}
+
+TODO: usare kernel pairs e sottoggetti per definire gli EGGs, usando \Cref{prop:pairing_of_kernel_pairs_mono} e \Cref{rem:fact_of_subobject_is_unique}
 

### 2024-11-04 Article/Graph_sections/Eq_Graphs_Notes_Results.tex
minima
finita dimostrazione

--- 2024-10-26 Article/Graph_sections/Eq_Graphs_Notes_Results.tex
@@
 
+{
 \subsection{Some results on kernel pair and regular epis}
@@
 \end{proof}
+}
+\subsection{Rimanenze da integrare}
 
@@
  \todo{Sistema il diagramma mettendo gli opportuni buchi}
-\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[dd]|(.5)\hole_(.62){q'_1}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[ddd]|(.33)\hole^{q'_2} \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[ddd]_{q'_3} \ar[rr]^(.65){p'_2} && B'_4  \ar[rr]^(.65){z}&& F \ar[ddddd]^{g}\\& C'_1 \ar@/^.2cm/[drr]^{h'_3} \ar@/_.2cm/[ddl]_{k'_3} \ar[d]^{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \ar@/^.2cm/[dddr]^{z_3} \ar[lddd]_{t'_3}\\ C'_3 \ar@/_.5cm/[ddrr]^(.65){p'_3} \ar[ddrrrr]_{w_3} \ar[dd]_{m_3}\\&T\ar[dd]|(.25)\hole|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]|(.25)\hole_{w} && U \ar[dd]^(.3){u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]_(.65){y_1} & & C'_4 \ar@{.>}[rr]_(.65){v} \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]
+\[\xymatrix@C=35pt@R=15pt{& B'_1 \ar[dd]|(.5)\hole_(.62){q'_1}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[ddd]|(.33)\hole^{q'_2} \ar[dl]_{t'_2} \ar@/^.2cm/[dr]^{z_2}\\B'_3 \ar[ddd]_{q'_3} \ar[rr]^(.65){p'_2} && B'_4  \ar[rr]^(.65){z} \ar[ddddd]_{q'_4}&& F \ar[ddddd]^{g}\\& C'_1 \ar@/^.2cm/[drr]^{h'_3} \ar@/_.2cm/[ddl]_{k'_3} \ar[d]^{m_1}\\& S \ar[rr]^{s_1} \ar[dd]_{s_2} && C'_2 \ar[dd]^{m_2} \ar@/^.2cm/[dddr]^{z_3} \ar[lddd]_{t'_3}\\ C'_3 \ar@/_.5cm/[ddrr]^(.65){p'_3} \ar[ddrrrr]_{w_3} \ar[dd]_{m_3}\\&T\ar[dd]|(.25)\hole|\hole_(.65){x_2}\ar[rr]^{x_1} \ar[dl]|(.25)\hole_{w} && U \ar[dd]^(.3){u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]_(.65){y_1} & & C'_4 \ar@{.>}[rr]_(.65){v} \ar[dd]_(.3){d_3} && G\\&C_1\ar[rr]|\hole^(.65){h_3} \ar[dl]^{k_3} && C_2 \ar[dl]^{t_3} \\C_3 \ar[rr]_{p_3} & & C_4}\]
 
@@
 \begin{lemma}\label{lem:vk}
-In $\EqGrph$ pushouts along regular monos are Van Kampen.
+In $\EqGrph$ pushouts along regular monos are Reg-Van Kampen.
 \end{lemma}
 \begin{proof}
-	contenuto...
+In lieu of \Cref{lem:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $(h_1, h_2, h_3)\colon (A_1,B_1,C_1, s_1,t_1,q_1)\to (A_2,B_2,C_2, s_2,t_2,q_2)$ is a regular mono, the front faces are pullbacks too.
+\todo{Questo diagramma va sistemato per farlo stare nella pagina (val la pena magari dire "sia $\mathcal{G}_1$ il grafo....")}.
+
+\[\xymatrix@C=20pt@R=20pt{&(A'_1,B'_1,C'_1, s'_1,t'_1,q'_1)\ar[dd]|\hole_(.65){(a_1, a_2, a_3)}\ar[rr]^{(h'_1, h'_2, h'_3)} \ar[dl]_{(k'_1, k'_2, k'_3)} && (A'_2,B'_2,C'_2, s'_2,t'_2,q'_2) \ar[dd]^{(b_1, b_2, b_3)} \ar[dl]_{(t'_1, t'_2, t'_3)} \\ (A'_3,B'_3,C'_3, s'_3,t'_3,q'_3) \ar[dd]_{(c_1, c_2, c_3)}\ar[rr]^(.65){(p'_1,p'_2,p'_3)} & & (A'_4,B'_4,C'_4, s'_4,t'_4,q'_4) \ar[dd]_(.3){(d_1, d_2, d_3)}\\&(A_1,B_1,C_1, s_1,t_1,q_1)\ar[rr]|\hole^(.65){(h_1, h_2, h_3)} \ar[dl]^{(k_1, k_2, k_3)} && (A_2,B_2,C_2, s_2,t_2,q_2) \ar[dl]^{(t_1, t_2, t_3)} \\(A_3,B_3,C_3, s_3,t_3,q_3) \ar[rr]_{(p_1, p_2, p_3)} & & (A_4,B_4,C_4, s_4,t_4,q_4)}\]
+
+By \Cref{prop:limits,cor:regmono} the following two cubes have $\mathcal{M}$-pushouts as bottom and top faces and pullbacks as back faces, thus their front faces are pullbacks too.
+
+\[\xymatrix@C=10pt@R=10pt{&A'_1\ar[dd]|\hole_(.65){a_1}\ar[rr]^{h'_1} \ar[dl]_{k'_1} && A'_2 \ar[dd]^{b_1} \ar[dl]_{t'_1} && B'_1\ar[dd]|\hole_(.65){a_2}\ar[rr]^{h'_2} \ar[dl]_{k'_2} && B'_2 \ar[dd]^{b_2} \ar[dl]_{t'_2}\\ A'_3  \ar[dd]_{c_1}\ar[rr]^(.7){p'_1} & & A'_4 \ar[dd]_(.3){d_1} &&B'_3  \ar[dd]_{c_2}\ar[rr]^(.7){p'_2} & & B'_4 \ar[dd]_(.3){d_2}\\&A_1\ar[rr]|\hole^(.65){h_1} \ar[dl]^{k_1} && A_2 \ar[dl]^{t_1} && B_1\ar[rr]|\hole^(.65){h_2} \ar[dl]^{k_2} && B_2 \ar[dl]^{t_2} \\A_3 \ar[rr]_{p_1} & & A_4&&B_3 \ar[rr]_{p_2} & & B_4}\]
+
+On the other hand we can consider the diagrams below, in which the inner squares are pullbacks.
+Since the outer diagrams commute, by definition of porphism of $\EqGrph$, then we have the existence of the dotted $m_2\colon C'_2\to U$, $m_3\colon C'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
+
+\[\xymatrix{C'_3 \ar@{.>}[dr]^{m_3} \ar@/^.3cm/[drr]^{p'_3} \ar@/_.3cm/[ddr]_{d_3} &&& C'_2 \ar@{.>}[dr]^{m_2} \ar@/^.3cm/[drr]^{t'_3} \ar@/_.3cm/[ddr]_{d_2}\\&Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
+
+\[\xymatrix{B'_3 \ar@{.>}[dr]^{a_3} \ar[r]^{p'_2} \ar[d]_{q'_3} &B'_4\ar[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{t'_2} \ar[d]_{q'_2} &B'_4\ar[dr]^{q'_4}\\C'_3 \ar[dr]_{d_3} &Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&C_2' \ar[dr]_{d_2}& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
+
+Now, notice that  $m_3$ and $m_2$ are monos because $d_3$ and $d_2$ are regular monos. By the proof of \Cref{prop:limits}, to conclude it is enough to show that
+\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
+
+Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $a_3$ and $a_2$ and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:limits}.
+
+No if we compute we have:
+\[\begin{split}
+	y_1\circ a_3&= q'_4\circ p'_2\\&=p'_3 \circ q'_3\\&=y_1\circ m_3\circ q'_3  
+\end{split}\qquad \begin{split}
+	u_1\circ a_2&= q'_4\circ t'_2\\&=t'_3 \circ q'_3\\&=u_1\circ m_2\circ q'_2  
+\end{split}\]
+\[\begin{split}
+y_2\circ a_3&= d_3\circ q_3'\\&=y_2\circ m_3\circ q'_3
+\end{split}\qquad \begin{split}
+u_2\circ a_2&= d_2\circ q_2'\\&=u_2\circ m_2\circ q'_2
+\end{split}\]
+And we have done.
 \end{proof}
 
+\todo{Una cosa che manca nei due lemmi precedenti è la seguente: bisognerebbe contollare che lse mappe source e target che appaiano tra i vari  A e B sono esattamente quelle che mi danno la struttura di pushout.
+Questo si può fare a mano, ma sarebbe meglio inserire un lemma da qualche parte che dice: i due funtori Graph -> Set jointly creano tutto (questo segue immediatamente dal fatto che Graph è una categoria di prefasci) Però va scritto e citato nelle prove di entrambi.}
 From \Cref{prop:limits} and \Cref{lem:stab,lem:vk} we deduce at once the following.
@@
 \begin{cor}\label{cor:equi}
-	$\EqGrph$ is quasiadhesive.
+	$\EqGrph$ is Reg-adhesive.
 \end{cor}

### 2024-11-04 Article/Graph_sections/EGGs.tex
advances on EGGs

--- 2024-10-29 Article/Graph_sections/EGGs.tex
@@
 \section{E-Graphs}\label{sect:eggs}
+
+\newcommand{\EGG}{\mathbf{EGG}}
 
@@
 But this is to say that, given the two set $S = \{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ s)(e) = \eqgraph{G}(q \circ s)(e') \}$ and $T =\{ (e, e') \in \eqgraph{G}(E) \times \eqgraph{G}(E) \mid \eqgraph{G}(q \circ t)(e) = \eqgraph{G}(q \circ t)(e') \} $, $S \subseteq T$.
-But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the pullback of $(q \circ s, q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the pullback of $(q \circ t, q \circ t)$.
+But $S$ (with the projection arrows $p_1$ and $p_2$) is exactly the kernel pair of $\eqgraph{G}(q \circ s)$, and $T$ (together with the projections $q_1, q_2$) is the kernel pair of $\eqgraph{G}(q \circ t)$ (\Cref{ex:kernel_pairs_in_Set}).
 Then, a more general way to express that $\eqgraph{G}$ is an e-graph is by saying that $\eqgraph{G}$ is such that there exists a monomorphism, which is the canonical inclusion, in $\Set$ from $S$ to $T$.
 To find a structure to express this fact, we have to consider a more general case.
-
-Consider an arrow $f: X \rightarrow Y$, and let $(K, \pi_1, \pi_2)$ be the pullback of $(f, f)$.
-\[
-    \begin{tikzcd}
-        K \arrow[r, "{\pi_1}"] \arrow[d, "{\pi_2}"swap] & X \arrow[d, "f"] \\
-        X \arrow[r, "f"swap] & Y
-    \end{tikzcd}
-\]
-Such pullback induces an arrow $\langle \pi_1, \pi_2 \rangle : K \rightarrow X\times X$. Such arrow is mono and unique, because of the universal property of the pullback, indeed a subobject.
-\todo{capire quanto andare nello specifico qui}
 
@@
 \]
-We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
+% We have then that $\langle p_1, p_2 \rangle$ is mono, then so is $\langle q_1, q_2 \rangle \circ i$.
 From \Cref{prop:epi_mono_prop}, we can conclude that $i$ is mono too.
@@
 \begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-    The subcategory of $\mathbf{EqGrph}$ whose objects are this particular kind of graphs is denoted as $\mathbf{EGG}$.
+    $\EGG$ is the subcategory of $\EqGrph$ such that
+	\begin{itemize}
+		\item $\eqgraph{G} \in \EGG$ if, being $(S, p_1, p_2)$ and $(T, q_1, q_2)$, respectively, the kernel pair of $\eqgraph{G}(q \circ s)$ and the kernel pair of $\eqgraph{G}(q \circ t)$, it holds that $\langle p_1, p_2 \rangle \leq \langle q_1, q_2 \rangle$ (in the sense of \Cref{def:subobj});
+		\item given two e-graphs $\eqgraph{G, H}$, $\EGG(\eqgraph{G, H}) =\EqGrph(\eqgraph{G, H})$ (i.e., a full subcategory).
+	\end{itemize}
 \end{definition}
+
+Since $\EGG$ is a full subcategory of $\EqGrph$, there exists a fully faithful functor $I: \EGG \to \EqGrph$ (\Cref{ex:full_subc_inc_fully_faith}).
+
+\begin{lemma}
+	$\EGG$ has all limits and colimits, and $I$ preserves them.
+\end{lemma}
+
+\begin{proof}
+	Let $D: \cat I \to \EGG$ be a diagram, and suppose $(\eqgraph{L}, (l_i)_{i \in \cat{I}})$ be a limit for $I \circ D$, where $l_i = (l_E^i, l_V^i, l_C^i)$.
+Then, it is sufficient to show that $(\eqgraph{L}, (l_i)_{i \in \cat I})$ is a limit for $D$ (i.e., $\eqgraph{L}$ is an e-graph).
+To see this, consider $e, e' \in \eqgraph{L}(E)$, and suppose $\eqgraph{L}(q \circ s)(e) = \eqgraph{L}(q \circ s)(e')$.
+Then, we have $(l_C^i \circ \eqgraph{L}(q \circ s))(e) = (l_C^i \circ \eqgraph{L}(q \circ s))(e')$, but, since
+	\[\begin{split}
+		l_C^i \circ \eqgraph{L}(q \circ s) &= l_C^i \circ \eqgraph{L}(q) \circ \eqgraph{L}(s) \\
+						   &= D(i)(q) \circ l_V^i \circ \eqgraph{L}(s)	\\
+						   &= D(i)(q \circ s)\circ l_E^i
+	\end{split}\]
+	the equation above rewrites as
+	\[(D(i)(q \circ s))(l_E^i (e)) = (D(i)(q \circ s))(l_E^i (e')) \]
+	Since $D(i)$ is an e-graph, we have then
+	\[(D(i)(q \circ t))(l_E^i (e)) = (D(i)(q \circ t))(l_E^i (e')) \]
+	and, retracing the previous steps, \[ (l_C^i \circ \eqgraph{L}(q \circ t))(e) = (l_C^i \circ \eqgraph{L}(q \circ t))(e')\]
+\end{proof}
 

### 2024-11-05 Article/Graph_sections/EGGs.tex
compiling
minima

@@
 	and, retracing the previous steps, \[ (l_C^i \circ \eqgraph{L}(q \circ t))(e) = (l_C^i \circ \eqgraph{L}(q \circ t))(e')\]
+	\todo{finire qui. Credo che si possa dimostrare che se $h: \eqgraph{G \to H}$ è un morfismo in $\EqGrph$ con $\eqgraph H$ EGG allora anche $\eqgraph{G}$ è un EGG.}
 \end{proof}
-
-\begin{prop}\label{prop:prod_of_EGGs_is_EGG}
-    The product of two e-graphs in $\mathbf{EqGrph}$ is an e-graph.
-\end{prop}
-
-\begin{proof}
-    Let $\eqgraph{G}$, $\eqgraph{H}$ be two e-graphs in $\mathbf{EqGrph}$.
-Then, we want to to show that $\eqgraph{G \times H}$ is an e-graph too.
-The argument lies on the consideration that limits in presheaves categories are computed pointwise.
-In fact, we can
-\end{proof}
-
-Consider now the inclusion functor $I: \mathbf{EGG} \rightarrow \mathbf{EqGrph}$.
-Since $\mathbf{EGG}$ is a full subcategory of $\mathbf{EqGrph}$, $I$ is full and faithful (\Cref{ex:full_subc_inc_fully_faith}), it reflects all limits (\Cref{prop:inc_funct_reflects_so_limits}).
-But limits are also preserved, since the limit in $\mathbf{EqGrph}$ in which objects are e-graphs is an e-graph together with morphisms that are also morphisms of $\mathbf{EGG}$ since it is a full subcategory.
-Then, we can conclude as follows.
-
-\begin{lemma}
-    The inclusion functor $I: \mathbf{EGG \rightarrow EqGrph}$ creates limits.
-\end{lemma}
-
-\begin{proof}
-    To prove that $I$ creates limits, we have to show that both preserves and reflects limits.
-    To see that $I$ preserves limits, it is sufficient to note that a limit of e-graphs in $\mathbf{EqGrph}$ is again an e-graph, together with morphisms.
-(Note that, since $\Egg$ is a full subcategory of $\mathbf{EqGrph}$, these morphisms in $\mathbf{EqGrph}$ are morphisms of $\Egg$ too).
-\end{proof}
-
-Since $I$ is faithful, monomorphisms in $\mathbf{EqGrph}$ between graphs that are e-graphs too are monomorphisms in $\Egg$ too.
-Regular monomorphisms in $\Egg$ are, as in $\mathbf{EqGrph}$, monomorphisms which reflect equivalences, hence natural transformations with all the three components mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}).
-The following result follows by the fact that a full and faithful functor preserves equalizers.
-{\color{red}{????
-Da dimostrare}}
-
-\begin{prop}
-    Let $I$ be the inclusion functor from $\Egg$ to $\mathbf{EqGrph}$. Then, $I(\Reg(\Egg)) \subseteq \Reg(\mathbf{EqGrph})$.
-\end{prop}
-
-At this point, by direct application of \Cref{th:crit_for_adh}, it is possible to state what follows.
-
-\begin{cor}
-    $\mathbf{EGG}$ is quasiadhesive.
-\end{cor}

### 2024-11-06 Article/Graph_sections/Eq_Graphs_integration.tex

@@
     \item $h_E \circ t = t' \circ h_V$;
-    \item $h_C \circ q = q' \circ h_C$.
+    \item $h_C \circ q = q' \circ h_V$.
 \end{itemize}
@@
     If $U(h) = U(k)$ (i.e., the first two component of $h$ and $k$ are the same), from \Cref{obs:eq_grph_morph_det_by_first_two_comp}, we can conclude that $h = k$.
-Then, the restriction $U_{\eqgraph{G, H}} : \EqGrph(\eqgraph{G, H}) \to \Graph(U(\eqgraph{G}), U(\eqgraph{H}))$, therefore $U$ is faithful.
+Then, the restriction $U_{\eqgraph{G, H}} : \EqGrph(\eqgraph{G, H}) \to \Graph(U(\eqgraph{G}), U(\eqgraph{H}))$ is injective, therefore $U$ is faithful.
 \end{proof}
@@
         \begin{tikzcd}
-            B \arrow[r, "{\pi_V^i}"] \arrow[d, "q" swap] & B_i \arrow[r, "{q_i}"] & Q_i \arrow[d, "{id_{Q_i}}"] \\
+            B \arrow[r, "{\pi_V^i}"] \arrow[d, "q" swap] & B_ i \arrow[r, "{q_i}"] & Q_i \arrow[d, "{id_{Q_i}}"] \\
             Q \arrow[urr, dashed, "\pi_C^i"] \arrow[r, "m" swap] &L \arrow[r, "{l_i}"swap] & Q_i
@@
     The ``if'' part is given by the fact that $U$ is faithful, and hence reflects monomorphisms.
-Since a morphism ain a category of presheaves is mono if and only if it is injective on each component \todo{commentato il link, dimostrare questa cosa}
-    % https://ncatlab.org/nlab/show/category+of+presheaves#properties
-    we have that, if  $U(h)$ is mono, that is, $h_E$ and $h_V$ are injective in $\Set$, then $h$ is mono.
+Since a morphism in a category of presheaves is mono if and only if it is injective on each component, we have that, if  $U(h)$ is mono, that is, $h_E$ and $h_V$ are injective in $\Set$, then $h$ is mono.
     For the ``only if'' part, suppose $f = (f_E, f_V, f_C)$, $g=(g_E, g_V, g_C)$, $f, g : \eqgraph{H \to K}$ be such that $h \circ f = h \circ g$. Then, we have

### 2024-11-06 Article/Graph_sections/Eq_Graphs_integration.tex
minima

@@
 This arrow is not epi in general, so let $Q$ be its image, $q: Q \to B$ be the resulting epi and $m: Q \to L$ the corresponding mono, as the diagram below shows.
-By definition, the external rectangle commutes, so, for each $i$ object of $\cat I$,
-    REMARK\todo{epi-mono factorization in Set (or Regular Cats in general)}
-    yields the dotted arrow $\pi_C^i$.
+By definition, the external rectangle commutes, so, for each $i$ object of $\cat I$, \Cref{prop:prop_epi_mono_Set} yields the dotted arrow $\pi_C^i$.
     \[
@@
 
-    To see that this cone is terminal, let $((E, F, G, a, b, c), \tau_i = (\tau_E^i, \tau_V^i, \tau_C^i)_{i \in \cat I})$ be another cone.
+	To see that this cone is terminal, let $((E, F, G, a, b, c), (\tau_i)_{i \in \cat I})$, where $\tau_i = (\tau_E^i, \tau_V^i, \tau_C^i)$, be another cone.
 By construction, we have an arrow $(\tau_E, \tau_V):(E, F, a, b) \to (A, B, s, t)$ such that
@@
 
-    Therefore, the outer part of the rectangle below commutes, and by REMARK \todo{epi-reg fact in SET} there exists a unique $\tau_C: G \to Q$
+	Therefore, the outer part of the rectangle below commutes, and by \Cref{prop:prop_epi_mono_Set} there exists a unique $\tau_C: G \to Q$
     \[
@@
      \todo{Dimostrazione dello statement di sopra, e colimiti}
+
+     For colimits, let $(A, B, s, t)$ be the colimit of $U \circ D$, together with morphisms $(\kappa_i)_{i \in \cat I} = (\kappa_E^i, \kappa_V^i)_{i \in \cat I}$, and suppose $((c_i)_{i \in \cat I}, C)$ be the colimit of $V \circ D$.
+Then, we have the following situation
+     \[
+	     \begin{tikzcd}[row sep = 25, column sep=25]
+			& B & \\
+			B_i \ar[rr, "{h_V}"] \ar[ur, "{\kappa_V^i}"] \ar[d, "{q_i}"swap] & & B_j \ar[ul, "{\kappa_V^j}"swap] \ar[d, "q_j"] \\
+			C_i \ar[rr, "{h_C}" swap] \ar[dr, "{c_i}"swap] & & C_j \ar[dl, "{c_j}"] \\
+			& C &
+		\end{tikzcd}
+     \]
+     Then, $((c_i \circ q_i)_{i \in \cat I}, C)$ is a cocone for all $B_i$, and, since $((\kappa_i)_{i \in \cat I}, B)$ is the colimit of all $B_i$ (\Cref{lemma:limits_of_presheaves}), there exists a unique arrow $q: B \to C$ such that, for each $i$, $q \circ \kappa_V^i = c_i \circ q_i$.
+Such $q$ is epi {\color{red}{dimostrare}}, and thus $(A, B, C, s, t, q)$ is the colimit of $D$.
+{\color{red}{rifinire, dimostrare unicità}}.
+
 \end{proof}

### 2024-11-07 Article/Graph_sections/EGGs.tex
minima
dimostrazione

@@
 
+APPUNTI
+Chiamiamo $(A_i, B_i, Q_i, s_i, t_i, q_i)$ le componenti del diagramma.
+Chiamiamo $(U_i, u_{1, i} , u_{2,i})$ il kernel pair di $q_i\circ s_i$.
+Sia $(A, B, Q, s,t,q )$ il limite in $\EqGrph$ e $(U, u_1, u_2)$ il kernel pair di $q\circ s$.
+Vogliamo far vedere che $q\circ t \circ u_1= q\circ t\circ u_2$.
+Sia anche $(L, l_i)$ il limite del diagramma dato dai $Q_i$.
+In particolare abbiamo $m\colon Q\to L$ mono.
+
+Osserviamo che 
+\begin{align*}
+q_i\circ s_i\circ \pi^i_E\circ u_1 &= q_i\circ \pi^i_V\circ s\circ u_1\\&= \pi^i\circ q\circ s\circ u_1\\&=\pi^i\circ q\circ s\circ u_2=\dots (percorso al contrario)
+\end{align*}
+
+Dunque per ogni $i$ esiste una freccia $a_i\colon U\to U_{i}$ tale che il diagramma sotto commuta
+\[
+\xymatrix{U \ar@{.>}[dr]^{a_i}\ar[r]^{u_1} \ar[d]_{u_2}& A \ar[drr]^{\pi^i_E}\\A \ar[ddr]_{\pi^i_E}&U_i \ar[dd]_{u_{2,i}} \ar[rr]^{u_{1,i}}& & A_i \ar[d]^{s_i}\\
+& & &B_i \ar[d]^{q_i}\\&A_i \ar[r]_{s_i} & B_i \ar[r]_{s_i} & Q_i}
+\]
+
+\begin{align*}
+	l_i\circ m\circ q\circ t \circ u_1 &= q_i \circ \pi^{i}_V\circ t\circ u_1 \\&=q_i\circ t_i\circ \pi^i_E\circ u_1\\&=q_i\circ t_i\circ u_{1,i}\circ a_i\\&=q_i\circ t_i\circ u_{2,i}\circ a_i\\=\dots (uguaglianze al contrario)
+\end{align*}
+
+Dunque le frecce $m\circ q\circ t \circ u_1, m\circ q\circ t \circ u_2\colon U\rightrightarrows L$ sono uguali. Ma $m$ è mono per costruzione e allora $q\circ t \circ u_1=q\circ t \circ u_2$.
+
+FINE APPUNTI
+
 \begin{proof}
@@
 	and, retracing the previous steps, \[ (l_C^i \circ \eqgraph{L}(q \circ t))(e) = (l_C^i \circ \eqgraph{L}(q \circ t))(e')\]
-	\todo{finire qui. Credo che si possa dimostrare che se $h: \eqgraph{G \to H}$ è un morfismo in $\EqGrph$ con $\eqgraph H$ EGG allora anche $\eqgraph{G}$ è un EGG.}
+	\todo{finire qui.}
 \end{proof}

### 2024-11-07 Article/Graph_sections/EGGs.tex
dimostrazione

@@
 \begin{lemma}
-	$\EGG$ has all limits and colimits, and $I$ preserves them.
+	$\EGG$ has all limits and $I$ preserves them.
 \end{lemma}
+
+\begin{proof}
+	Let $D: \cat{I} \to \EGG$ be a diagram, with $D(i) = (A_i, B_i, C_i, s_i, t_i, q_i)$, let $(U, u_1^i, u_2^i)$ be the kernel pair of $q_i\circ s_i$.
+Let now be $(A, B, C, s, t, q)$, togehter with projections $(\pi_E^i, \pi_V^i, \pi_C^i)_{i \in \cat I}$ the limit of $I \circ D$, let $(U, u_1, u_2)$ be the kernel pair of $q\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $V\circ I\circ D$.
+	By construction (proof of \Cref{???}\todo{citazione}), there exists a monomorphism $m: Q \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
+	\begin{align*}
+		q_i\circ s_i\circ \pi^i_E\circ u_1 	&= q_i\circ \pi^i_V\circ s\circ u_1\\
+							&= \pi_C^i\circ q\circ s\circ u_1\\
+							&=\pi_C^i\circ q\circ s\circ u_2\\
+							&= q_i \circ s_i \circ \pi_E^i \circ u_2
+	\end{align*}
+	Then, for each $i$, there exists an arrow $a_i:U\to U_i$ making the following diagram to commute
+	\[
+		\begin{tikzcd}[row sep = 25, column sep = 25]
+			U \ar[r, "{u_1}"] \ar[d, "{u_2}"swap font=\small] \ar[dr, dashed, "{a_i}"] & A \ar[drr, "{\pi_E^i}"] && \\
+			A \ar[ddr, "{\pi_E^i}"swap] & U_i \ar[rr, "{u_1^i}"] \ar[dd, "{u_2^i}"swap]&& A_i \ar[d, "{s_i}"] \\
+			& & & B_i \ar[d, "{q_i}"]\\
+			& A_i \ar[r, "{s_i}"swap] & B_i \ar[r, "{q_i}"swap] & C_i
+		\end{tikzcd}
+	\]
+	We have then
+	\begin{align*}
+		l_i\circ m \circ q \circ t \circ u_1	&= q_i \circ \pi_V^i \circ t \circ u_1 \\
+							&= q_i \circ t_i \circ \pi_E^i \circ u_1 \\
+							&= q_i \circ t_i \circ u_1^i \circ a_i \\
+							&= q_i \circ t_i \circ u_2^i \circ a_i \\
+							&= q_i \circ t_i \circ \pi_E^i \circ u_2 \\
+							&= q_i \circ \pi_V^i \circ t \circ u_2 \\
+							&= l_i \circ m \circ q \circ t \circ u_2
+	\end{align*}
+	By universal property of limits, we have that $m\circ q \circ t \circ u_1 = m \circ q \circ t \circ u_2$, and, since $m$ is mono, $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis.
+\end{proof}
 

### 2024-11-07 Article/Graph_sections/EGGs.tex
minima

@@
 		\begin{tikzcd}[row sep = 25, column sep = 25]
-			U \ar[r, "{u_1}"] \ar[d, "{u_2}"swap font=\small] \ar[dr, dashed, "{a_i}"] & A \ar[drr, "{\pi_E^i}"] && \\
+			U \ar[r, "{u_1}"] \ar[d, "{u_2}"swap] \ar[dr, dashed, "{a_i}"] & A \ar[drr, "{\pi_E^i}"] && \\
 			A \ar[ddr, "{\pi_E^i}"swap] & U_i \ar[rr, "{u_1^i}"] \ar[dd, "{u_2^i}"swap]&& A_i \ar[d, "{s_i}"] \\
@@
 	\end{align*}
-	By universal property of limits, we have that $m\circ q \circ t \circ u_1 = m \circ q \circ t \circ u_2$, and, since $m$ is mono, $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis.
+	By universal property of limits, we have that \- $m\circ q \circ t \circ u_1 = m \circ q \circ t \circ u_2$, and, since $m$ is mono, $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis.
+\end{proof}
+
+\begin{cor}\label{cor:I_creates_limits}
+	$I$ creates limits.
+\end{cor}
+
+\begin{cor}\label{cor:reg_mono_EGG}
+	$h: \eqgraph{G \to H}$ is a regular mono in $EGG$ if and only if it is a regular mono in $\EqGrph$.
+\end{cor}
+
+\begin{lemma}\label{lem:I_pres_pushouts_of_monos}
+	$I$ preserves pushouts along regular monomorphisms.	
+\end{lemma}
+
+\begin{proof}
+	TODO	
 \end{proof}

### 2024-11-07 Article/Graph_sections/EGGs.tex
minima

@@
 
-APPUNTI
-Chiamiamo $(A_i, B_i, Q_i, s_i, t_i, q_i)$ le componenti del diagramma.
+% APPUNTI
+%Chiamiamo $(A_i, B_i, Q_i, s_i, t_i, q_i)$ le componenti del diagramma.
 Chiamiamo $(U_i, u_{1, i} , u_{2,i})$ il kernel pair di $q_i\circ s_i$.
@@
 
-Osserviamo che 
-\begin{align*}
-q_i\circ s_i\circ \pi^i_E\circ u_1 &= q_i\circ \pi^i_V\circ s\circ u_1\\&= \pi^i\circ q\circ s\circ u_1\\&=\pi^i\circ q\circ s\circ u_2=\dots (percorso al contrario)
-\end{align*}
+%Osserviamo che 
+%\begin{align*}
+%q_i\circ s_i\circ \pi^i_E\circ u_1 &= q_i\circ \pi^i_V\circ s\circ u_1\\&= \pi^i\circ q\circ s\circ u_1\\&=\pi^i\circ q\circ s\circ u_2=\dots (percorso al contrario)
+%\end{align*}
 
-Dunque per ogni $i$ esiste una freccia $a_i\colon U\to U_{i}$ tale che il diagramma sotto commuta
-\[
-\xymatrix{U \ar@{.>}[dr]^{a_i}\ar[r]^{u_1} \ar[d]_{u_2}& A \ar[drr]^{\pi^i_E}\\A \ar[ddr]_{\pi^i_E}&U_i \ar[dd]_{u_{2,i}} \ar[rr]^{u_{1,i}}& & A_i \ar[d]^{s_i}\\
-& & &B_i \ar[d]^{q_i}\\&A_i \ar[r]_{s_i} & B_i \ar[r]_{s_i} & Q_i}
-\]
+%Dunque per ogni $i$ esiste una freccia $a_i\colon U\to U_{i}$ tale che il diagramma sotto commuta
+%\[
+%\xymatrix{U \ar@{.>}[dr]^{a_i}\ar[r]^{u_1} \ar[d]_{u_2}& A \ar[drr]^{\pi^i_E}\\A \ar[ddr]_{\pi^i_E}&U_i \ar[dd]_{u_{2,i}} \ar[rr]^{u_{1,i}}& & A_i \ar[d]^{s_i}\\
+%& & &B_i \ar[d]^{q_i}\\&A_i \ar[r]_{s_i} & B_i \ar[r]_{s_i} & Q_i}
+%\]
 
-\begin{align*}
-	l_i\circ m\circ q\circ t \circ u_1 &= q_i \circ \pi^{i}_V\circ t\circ u_1 \\&=q_i\circ t_i\circ \pi^i_E\circ u_1\\&=q_i\circ t_i\circ u_{1,i}\circ a_i\\&=q_i\circ t_i\circ u_{2,i}\circ a_i\\=\dots (uguaglianze al contrario)
-\end{align*}
+%\begin{align*}
+%	l_i\circ m\circ q\circ t \circ u_1 &= q_i \circ \pi^{i}_V\circ t\circ u_1 \\&=q_i\circ t_i\circ \pi^i_E\circ u_1\\&=q_i\circ t_i\circ u_{1,i}\circ a_i\\&=q_i\circ t_i\circ u_{2,i}\circ a_i\\=\dots (uguaglianze al contrario)
+%\end{align*}
 
-Dunque le frecce $m\circ q\circ t \circ u_1, m\circ q\circ t \circ u_2\colon U\rightrightarrows L$ sono uguali. Ma $m$ è mono per costruzione e allora $q\circ t \circ u_1=q\circ t \circ u_2$.
+%Dunque le frecce $m\circ q\circ t \circ u_1, m\circ q\circ t \circ u_2\colon U\rightrightarrows L$ sono uguali. Ma $m$ è mono per costruzione e allora $q\circ t \circ u_1=q\circ t \circ u_2$.
 
-FINE APPUNTI
-
-\begin{proof}
-	Let $D: \cat I \to \EGG$ be a diagram, and suppose $(\eqgraph{L}, (l_i)_{i \in \cat{I}})$ be a limit for $I \circ D$, where $l_i = (l_E^i, l_V^i, l_C^i)$.
-Then, it is sufficient to show that $(\eqgraph{L}, (l_i)_{i \in \cat I})$ is a limit for $D$ (i.e., $\eqgraph{L}$ is an e-graph).
-To see this, consider $e, e' \in \eqgraph{L}(E)$, and suppose $\eqgraph{L}(q \circ s)(e) = \eqgraph{L}(q \circ s)(e')$.
-Then, we have $(l_C^i \circ \eqgraph{L}(q \circ s))(e) = (l_C^i \circ \eqgraph{L}(q \circ s))(e')$, but, since
-	\[\begin{split}
-		l_C^i \circ \eqgraph{L}(q \circ s) &= l_C^i \circ \eqgraph{L}(q) \circ \eqgraph{L}(s) \\
-						   &= D(i)(q) \circ l_V^i \circ \eqgraph{L}(s)	\\
-						   &= D(i)(q \circ s)\circ l_E^i
-	\end{split}\]
-	the equation above rewrites as
-	\[(D(i)(q \circ s))(l_E^i (e)) = (D(i)(q \circ s))(l_E^i (e')) \]
-	Since $D(i)$ is an e-graph, we have then
-	\[(D(i)(q \circ t))(l_E^i (e)) = (D(i)(q \circ t))(l_E^i (e')) \]
-	and, retracing the previous steps, \[ (l_C^i \circ \eqgraph{L}(q \circ t))(e) = (l_C^i \circ \eqgraph{L}(q \circ t))(e')\]
-	\todo{finire qui.}
-\end{proof}
+%FINE APPUNTI

### 2024-11-08 Article/Background_sections/Adhesivity.tex
some proofs
last proofs

@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:pushouts_kernel_pairs}
     Let $\cat C$ be an $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
@@
 
-    {\color{red} Non ho capito la dimostrazione!!}
+	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
+
 \end{proof}

### 2024-11-08 Article/Graph_sections/EGGs.tex
last proofs

@@
 }
+
+\iffalse
 
@@
 	\end{itemize}
+\end{definition}
+
+\fi
+
+E-Graphs are a particular type of graphs with equivalences.
+
+\begin{definition}[E-Graph]\label{def:e_graph}
+	Given a graph with equivalence $\eqgraph{G} = (E, V, C, s, t, q)$, let $(S, p_1, p_2)$ be the kernel pair of $q \circ s$. Then, $\eqgraph G$ is an \emph{e-graph} if it holds that
+	\[
+		q \circ t \circ p_1 = q \circ t \circ p_2
+	\]
+\end{definition}
+
+\begin{remark}
+	From a set-theoretic point of view, $\eqgraph{G} = (\graph{G}, \sim)$ is a graph with equivalence, where $\graph{G} = (E, V, s, t)$ in which holds that, for each pair of edges $e$, $e'$,
+	\[
+		\frac{s(e)\sim s(e')}{t(e)\sim t(e')}
+	\]
+	As we have considered in the section on graphs with equivalences, we can formalize the equivalence relation with a surjective function $q: V \to V/_\sim = C$, rewriting the inference rule above as an inclusion.
+	Let $S = \{(e, e') \in E\times E \mid q(s(e)) = q(s(e'))\}$ and $T = \{(e, e') \in E \times E \mid q(t(e)) = q(t(e'))\}$.
+Then, $\eqgraph{G}$ is an e-graph if $S \subseteq T$.
+As we noted in \Cref{ex:kernel_pairs_in_Set}, $S$ is the kernel pair of $q \circ s$ and $T$ is the kernel pair of $q \circ t$, if endowed with canonical projections.
+Moreover, we notice that the pairing of such projections yields a subobject of the product $E \times E$ \Cref{prop:pairng_of_kernel_pairs_mono}.
+Hence, by \Cref{rem:fact_of_subobject_is_unique}, the \Cref{def:e_graph} express this fact using categorial constructions.
+\end{remark}
+
+\begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
+	$\EGG$ is the subcategory of $\EqGrph$ in which objects are e-graphs, and, given two e-graphs $\eqgraph{G, H}$, $\EGG(\eqgraph{G, H}) = \EqGrph(\eqgraph{G, H})$.
 \end{definition}
@@
 \begin{proof}
-	TODO	
+	Let $\eqgraph{G}_1 = (A_1, B_1, C_1, s_1, t_1, q_1)$, $\eqgraph{G}_2 = (A_2, B_2, C_2, s_2, t_2, q_2)$ and $\eqgraph{G}_3 = (A_3, B_3, C_3, s_3, t_3, q_3)$ be e-graphs,  $h: \eqgraph{G}_1 \to \eqgraph{G}_2$ and $m: \eqgraph{G}_1 \to \eqgraph{G}_3$ be two morphisms with $m$ mono.
+Let now $\eqgraph{P} = (A, B, C, s, t, q)$, together with $k: \eqgraph{G}_3 \to \eqgraph{P}$ and $n: \eqgraph{G}_2 \to \eqgraph{P}$, the pushout of $h$ and $m$.
+	Let $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i\circ s_i$, for $i = 1, 2, 3$, and let $(U, u_1, u_2)$ be the kernel pair of $q \circ s$.
+	Consider the following cube in $\Set$
+	\[\begin{tikzcd}[row sep=25, column sep = 25]
+	& {A_1} && {A_2} \\
+	{A_3} && A \\
+	& {C_1} && {C_2} \\
+	{C_3} && C
+	\arrow["{h_E}", from=1-2, to=1-4]
+	\arrow["{m_E}"', from=1-2, to=2-1]
+	\arrow["{q_1\circ s_1}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{n_E}", from=1-4, to=2-3]
+	\arrow["{q_2\circ s_2}", from=1-4, to=3-4]
+	\arrow["{k_E}"{pos=0.7}, from=2-1, to=2-3, crossing over]
+	\arrow["{q_3\circ s_3}"', from=2-1, to=4-1]
+	\arrow["{h_C}"{pos=0.8}, from=3-2, to=3-4]
+	\arrow["{m_C}"', from=3-2, to=4-1]
+	\arrow["{n_C}", from=3-4, to=4-3]
+	\arrow["{k_C}"', from=4-1, to=4-3]
+	\arrow["{q\circ s}"'{pos=0.2}, from=2-3, to=4-3, crossing over]
+	\end{tikzcd}\]
+	By adhesivity of $\Set$, and since $m$ is regular mono, the cube above is Van Kampen, and, by \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, all the faces are pullbacks.
+Then, applying \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout
+	\[\begin{tikzcd}[row sep=27, column sep = 27]
+		K_1 \ar[r, "{f_h}"] \ar[d, "{f_m}"swap] & K_2 \ar[d, "{f_n}"] \\
+		K_3 \ar[r, "{f_k}"swap] & U
+	\end{tikzcd}\]
+
+	Hence, we end up with the following situation
+	\[
+		\begin{tikzcd}[row sep = 20, column sep = 20]
+	& {K_1} && {K_2} \\
+	{K_3} && U \\
+	& {A_1} && {A_2} \\
+	{A_3} && A \\
+	& {C_1} && {C_2} \\
+	{C_3} && C
+	\arrow["{f_h}", from=1-2, to=1-4]
+	\arrow["{f_m}"', from=1-2, to=2-1]
+	\arrow["{\pi_1^1}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{f_n}", from=1-4, to=2-3]
+	\arrow["{\pi^1_2}", from=1-4, to=3-4]
+	\arrow["{f_k}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["{\pi_3^1}"', from=2-1, to=4-1]
+	\arrow["{u_1}"'{pos=0.3}, from=2-3, to=4-3, crossing over]
+	\arrow["{h_E}"{pos=0.8}, from=3-2, to=3-4]
+	\arrow["{m_E}"', from=3-2, to=4-1]
+	\arrow["{q_1\circ s_1}"'{pos=0.7}, from=3-2, to=5-2]
+	\arrow["{n_E}", from=3-4, to=4-3]
+	\arrow["{q_2\circ s_2}", from=3-4, to=5-4]
+	\arrow["{k_E}"{pos=0.7}, from=4-1, to=4-3, crossing over]
+	\arrow["{q_3\circ s_3}"', from=4-1, to=6-1]
+	\arrow["{h_C}"{pos=0.8}, from=5-2, to=5-4]
+	\arrow["{q\circ s}"'{pos=0.2}, from=4-3, to=6-3, crossing over]
+	\arrow["{m_C}"', from=5-2, to=6-1]
+	\arrow["{n_C}", from=5-4, to=6-3]
+	\arrow["{k_C}"', from=6-1, to=6-3]
+	\end{tikzcd}
+		\qquad
+		\begin{tikzcd}[row sep = 20, column sep = 20]
+	& {K_1} && {K_2} \\
+	{K_3} && U \\
+	& {A_1} && {A_2} \\
+	{A_3} && A \\
+	& {C_1} && {C_2} \\
+	{C_3} && C
+	\arrow["{f_h}", from=1-2, to=1-4]
+	\arrow["{f_m}"', from=1-2, to=2-1]
+	\arrow["{\pi_1^2}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{f_n}", from=1-4, to=2-3]
+	\arrow["{\pi^2_2}", from=1-4, to=3-4]
+	\arrow["{f_k}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["{\pi_3^2}"', from=2-1, to=4-1]
+	\arrow["{u_2}"'{pos=0.3}, from=2-3, to=4-3, crossing over]
+	\arrow["{h_E}"{pos=0.8}, from=3-2, to=3-4]
+	\arrow["{m_E}"', from=3-2, to=4-1]
+	\arrow["{q_1\circ s_1}"'{pos=0.7}, from=3-2, to=5-2]
+	\arrow["{n_E}", from=3-4, to=4-3]
+	\arrow["{q_2\circ s_2}", from=3-4, to=5-4]
+	\arrow["{k_E}"{pos=0.7}, from=4-1, to=4-3, crossing over]
+	\arrow["{q_3\circ s_3}"', from=4-1, to=6-1]
+	\arrow["{h_C}"{pos=0.8}, from=5-2, to=5-4]
+	\arrow["{q\circ s}"'{pos=0.2}, from=4-3, to=6-3, crossing over]
+	\arrow["{m_C}"', from=5-2, to=6-1]
+	\arrow["{n_C}", from=5-4, to=6-3]
+	\arrow["{k_C}"', from=6-1, to=6-3]
+		\end{tikzcd}\]
+
+	Computing, we have
+	\[
+		\begin{split}
+			q \circ t \circ u_1 \circ f_n &= q \circ t \circ n_E \circ \pi_2^1 \\ &= n_C \circ q_2 \circ s_2 \circ \pi_2^1 \\&= n_C \circ q_2 \circ s_2 \circ \pi_2^2 \\&=q \circ t \circ u_2 \circ f_n 
+			\end{split}
+			\qquad
+			\begin{split} q \circ t \circ u_1 \circ f_k &= q \circ t \circ k_E \circ \pi_3^1 \\ &= k_C \circ q_3 \circ s_3 \circ \pi_3^1 \\&= k_C \circ q_3 \circ s_3 \circ \pi_3^2 \\&=q \circ t \circ u_2 \circ f_k
+			\end{split}
+	\]
+	By universal property of pushouts, we can conclude $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis.
 \end{proof}
+
+\begin{cor}
+	$I$ creates pushouts along regular monos.
+\end{cor}
+
+By direct application of \Cref{th:crit_for_adh}, we can conclude what follows.{rem:fact_of_subobject_is_unique}
+
+\begin{cor}
+	$\EGG$ is $\Reg(\EGG)-adhesive$.
+\end{cor}
 

### 2024-11-10 Article/Graph_sections/EGGs.tex
eqgrph pushouts reg mono stable

@@
 
-\todo[color=green!40]{
-    COSE DA FARE:
-Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
->Definizione
->Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
-> cor del calcolo dei limiti: caratterizzare mono regolari
->I crea limiti e i giusti pushout
-> e-graph sono quasiadesivi
-}
+%\todo[color=green!40]{
+%    COSE DA FARE:
+%Questa sezione ha più o meno gli stessi problemi della precedente. L'ordine da rispettare imho è il seguente:
+%>Definizione
+%>Calcolo dei limiti e certi colimiti (si fanno come in EqGrph)
+%> cor del calcolo dei limiti: caratterizzare mono regolari
+%>I crea limiti e i giusti pushout
+%> e-graph sono quasiadesivi
+%}
 
@@
 
-By direct application of \Cref{th:crit_for_adh}, we can conclude what follows.{rem:fact_of_subobject_is_unique}
+By direct application of \Cref{th:crit_for_adh}, we can conclude what follows.
 

### 2024-11-10 Article/Graph_sections/Eq_Graphs_integration.tex
eqgrph pushouts reg mono stable

@@
 
-\begin{prop}
+\begin{prop}\label{prop:eqgrph_complete}
     $\EqGrph$ has all limits, colimits and $U$ preserves limits and colimits.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:quot_funct_left_adj}
     $Q$ is a left adjoint.
@@
 
-\begin{prop}
+\begin{prop}\label{prop:quot_creat_colims}
     $Q$ creates colimits.
@@
 \end{proof}
+
+\begin{example}
+	TODO: Q does not preserves limits.
+\end{example}
+
+\subsection{Adhesivity of $\EqGrph$}
+
+\begin{lemma}\label{lemma:reg_push_stable}
+	In $\EqGrph$, pushouts along regular monos are stable.
+\end{lemma}
+
+\begin{proof}
+	Let $\graph{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\graph{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$, and, in the diagram above, suppose all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is regular mono.
+	\[\begin{tikzcd}[row sep=23, column sep =23]
+	& {\mathcal{G}_1'} && {\mathcal{G}_2'} \\
+	{\mathcal{G}_3'} && {\mathcal{G}_4'} \\
+	& {\mathcal{G}_1} && {\mathcal{G}_2} \\
+	{\mathcal{G}_3} && {\mathcal{G}_4}
+	\arrow["{h'}", from=1-2, to=1-4]
+	\arrow["{k'}"', from=1-2, to=2-1]
+	\arrow["b"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{t'}", from=1-4, to=2-3]
+	\arrow["c", from=1-4, to=3-4]
+	\arrow["{p'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["a"', from=2-1, to=4-1]
+	\arrow["h"{pos=0.7}, from=3-2, to=3-4]
+	\arrow["d"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\arrow["k"', from=3-2, to=4-1]
+	\arrow["t", from=3-4, to=4-3]
+	\arrow["p"', from=4-1, to=4-3]
+	\end{tikzcd}\]
+	By \Cref{prop:eqgrph_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as vertical faces, thus their top faces are $\mathcal{M}$-pushouts.
+	\[\begin{tikzcd}[row sep=20, column sep = 20]
+	& {A_1'} && {A_2'} \\
+	{A_3'} && {A_4'} \\
+	& {A_1} && {A_2} \\
+	{A_3} && {A_4}
+	\arrow["{h'_V}", from=1-2, to=1-4]
+	\arrow["{k'_V}"', from=1-2, to=2-1]
+	\arrow["{b_V}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{t'_V}", from=1-4, to=2-3]
+	\arrow["{c_V}", from=1-4, to=3-4]
+	\arrow["{p'_V}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["{a_V}"', from=2-1, to=4-1]
+	\arrow["{h_V}"{pos=0.7}, from=3-2, to=3-4]
+	\arrow["{d_V}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\arrow["{k_V}"', from=3-2, to=4-1]
+	\arrow["{t_V}", from=3-4, to=4-3]
+	\arrow["{p_V}"', from=4-1, to=4-3]
+	\end{tikzcd}\qquad
+	\begin{tikzcd}[row sep=20, column sep = 20]
+	& {B_1'} && {B_2'} \\
+	{B_3'} && {B_4'} \\
+	& {B_1} && {B_2} \\
+	{B_3} && {B_4}
+	\arrow["{h'_E}", from=1-2, to=1-4]
+	\arrow["{k'_E}"', from=1-2, to=2-1]
+	\arrow["{b_E}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{t'_E}", from=1-4, to=2-3]
+	\arrow["{c_E}"', from=1-4, to=3-4]
+	\arrow["{p'_E}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["{a_E}"', from=2-1, to=4-1]
+	\arrow["{h_E}"{pos=0.7}, from=3-2, to=3-4]
+	\arrow["{d_E}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\arrow["{k_E}"', from=3-2, to=4-1]
+	\arrow["{t_E}", from=3-4, to=4-3]
+	\arrow["{p_E}"', from=4-1, to=4-3]
+	\end{tikzcd}
+	\]
+	Now, using \Cref{cor:cube}, we can consider a third cube, which, by \Cref{prop:quot_creat_colims}, has a $\mathcal{M}$-pushout as bottom face and pullbacks as vertical faces, so that its top face is a $\mathcal M$-pushout too.
+	\[\begin{tikzcd}[row sep=20, column sep = 20]
+	& {T} && {U} \\
+	{Y} && {C_4'} \\
+	& {C_1} && {C_2} \\
+	{C_3} && {C_4}
+	\arrow["{x_1}", from=1-2, to=1-4]
+	\arrow["{w}"', from=1-2, to=2-1]
+	\arrow["{x_2}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{u_1}", from=1-4, to=2-3]
+	\arrow["{u_2}", from=1-4, to=3-4]
+	\arrow["{y_1}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["{y_2}"', from=2-1, to=4-1]
+	\arrow["{h_C}"{pos=0.7}, from=3-2, to=3-4]
+	\arrow["{d_C}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\arrow["{k_C}"', from=3-2, to=4-1]
+	\arrow["{t_C}", from=3-4, to=4-3]
+	\arrow["{p_C}"', from=4-1, to=4-3]
+	\end{tikzcd}\]
+
+	Moreover, by the proof of \Cref{prop:eqgrph_complete}, we know that there are monos $m_2:C_2'\to U$ and $m_3:C_3'\to Y$ fitting in the diagrams
+	\[\begin{tikzcd}[row sep=18, column sep = 18]
+	{B'_3} && {B'_4} \\
+	\\
+	{C'_3} && Y && {C'_4} \\
+	\\
+	{B_3} && {C_3} && {C_4}
+	\arrow["{p'_V}", from=1-1, to=1-3]
+	\arrow["{q'_3}", from=1-1, to=3-1]
+	\arrow["{q'_4}", from=1-3, to=3-5, bend left = 20]
+	\arrow["{m_3}", from=3-1, to=3-3]
+	\arrow["{y_1}", from=3-3, to=3-5]
+	\arrow["{y_2}"', from=3-3, to=5-3]
+	\arrow["{d_C}", from=3-5, to=5-5]
+	\arrow["{q_3}"', from=5-1, to=5-3]
+	\arrow["{p_C}"', from=5-3, to=5-5]
+        \arrow["{c_V}"', from=1-1, to=5-1, bend right = 20, shift right=1]
+	\end{tikzcd}\qquad\begin{tikzcd}[row sep=18, column sep = 18]
+	{B'_2} && {B'_4} \\
+	\\
+	{C'_2} && U && {C'_4} \\
+	\\
+	{B_2} && {C_2} && {C_4}
+	\arrow["{t'_V}", from=1-1, to=1-3]
+	\arrow["{q'_2}", from=1-1, to=3-1]
+	\arrow["{q'_4}", from=1-3, to=3-5, bend left = 20]
+	\arrow["{m_2}", from=3-1, to=3-3]
+	\arrow["{u_1}", from=3-3, to=3-5]
+	\arrow["{u_2}"', from=3-3, to=5-3]
+	\arrow["{d_C}", from=3-5, to=5-5]
+	\arrow["{q_2}"', from=5-1, to=5-3]
+	\arrow["{t_C}"', from=5-3, to=5-5]
+        \arrow["{b_V}"', from=1-1, to=5-1, bend right = 20, shift right = 1]
+	\end{tikzcd}\]
+
+	For $C'_1$, we can make a similar argument, let $S$ be the pullback of $m_2$ along $x_1$, using \Cref{lemma:pullback_lemma} and, again, the proof of \Cref{prop:eqgrph_complete} we know that $q'_1$ arise as the factorization of the arrow $B'_1\to S$ induced by $q'_2\circ h'_2$ and $a_2$ so that we have a diagram.
+	\[\begin{tikzcd}[row sep = 20, column sep =20]
+	{B'_1} && {B'_2} \\
+	\\
+	{C'_3} && S && {C'_2} \\
+	\\
+	{B_1} && T && U \\
+	\\
+	&& {C_1} && {C_2}
+	\arrow["{h'_V}", from=1-1, to=1-3]
+	\arrow["{q'_1}", from=1-1, to=3-1]
+	\arrow["{q'_2}", from=1-3, to=3-5, bend left = 20]
+	\arrow["{m_1}", from=3-1, to=3-3]
+	\arrow["{s_1}", from=3-3, to=3-5]
+	\arrow["{s_2}"', from=3-3, to=5-3]
+	\arrow["{m_2}", from=3-5, to=5-5]
+	\arrow["{q_1}"', from=5-1, to=7-3, bend right = 20, shift right = 1]
+	\arrow["{x_1}", from=5-3, to=5-5]
+	\arrow["{x_2}"', from=5-3, to=7-3]
+	\arrow["{u_2}", from=5-5, to=7-5]
+	\arrow["{h_C}"', from=7-3, to=7-5]
+        \arrow["{a_V}"', from=1-1, to=5-1, bend right = 20, shift right = 1]
+	\end{tikzcd}\]
+
+	Moreover, we have that
+	\[
+		\begin{split}
+			s_1 \circ m_1 \circ q_1 &= q'2 \circ h'_V \\ &= h'_C \circ q'_1
+		\end{split}\qquad\begin{split}
+			q'_4 \circ t'_V &= t'_C \circ q'_2\\ &= u_1\circ m_2 \circ q'_2
+		\end{split}\quad\begin{split}
+			y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
+		\end{split}\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'
+		\end{split}
+	\]
+	Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p_C = y_1 \circ m_3$.
+	Let now $z: \graph{G}'_2 \to \graph H = (E, V, Q, s, t, q)$, $w: \graph G_3^1 \to \graph H$ be two morphisms such that $z \circ h' = w \circ k'$, and let $\phi:B'_4 \to V$ be the arrow induced by $z_V$ and $w_V$.
+We want to construct the arrow $v: C'_4 \to Q$ in the diagram below.
+	\[\begin{tikzcd}[row sep = 25, column sep = 25]
+	& {B_1'} && {B_2'} \\
+	{B_3'} && {B_4'} && V \\
+	& T && U \\
+	Y && {C_4'} && Q \\
+	& {C_1} && {C_2} \\
+	{C_3} && {C_4}
+	\arrow["{h_V'}", from=1-2, to=1-4]
+	\arrow["{k_V'}"', from=1-2, to=2-1]
+	\arrow["{s_2\circ m_1 \circ q_1'}"{description, pos=0.7}, from=1-2, to=3-2]
+	\arrow["{t_V'}", from=1-4, to=2-3]
+	\arrow["{z_V}", from=1-4, to=2-5]
+	\arrow["{m_2\circ q'_2}"{pos=0.7}, from=1-4, to=3-4]
+	\arrow["{m_3 \circ q'_3}"', from=2-1, to=4-1]
+	\arrow["q", from=2-5, to=4-5]
+	\arrow["{x_1}"{pos=0.8}, from=3-2, to=3-4]
+	\arrow["w"', from=3-2, to=4-1]
+	\arrow["{x_2}"'{pos=0.7}, from=3-2, to=5-2]
+	\arrow["{u_1}", from=3-4, to=4-3]
+	\arrow["{u_2}"{pos=0.7}, from=3-4, to=5-4]
+	\arrow["{y_2}"', from=4-1, to=6-1]
+	\arrow["{h_C}"{pos=0.8}, from=5-2, to=5-4]
+	\arrow["{k_C}", from=5-2, to=6-1]
+	\arrow["{t_C}", from=5-4, to=6-3]
+	\arrow["{p_C}"', from=6-1, to=6-3]
+	\arrow["{p_V'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["\phi"{pos=0.8}, from=2-3, to=2-5, crossing over]
+	\arrow["{q'_4}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\arrow["{y_1}"{pos=0.7}, from=4-1, to=4-3, crossing over]
+	\arrow["{d_C}"'{pos=0.7}, from=4-3, to=6-3, crossing over]
+	\arrow["v"{pos=0.8}, dashed, from=4-3, to=4-5, crossing over]
+	\end{tikzcd}\]
+
+	By \Cref{prop:reg_epi_coeq}, $d_C$ is the coequalizer of its kernel pair. On the other hand, by \Cref{lemma:pushouts_kernel_pairs}, we know that the top face of the cube below is a pushout.
+	\[\begin{tikzcd}[row sep=20, column sep = 20]
+	& {K_{s_2\circ m_1 \circ q_1'}} && {K_{m_2\circ q_2'}} \\
+	{K_{m_3 \circ q_3'}} && {K_{q_4'}} \\
+	& {B'_1} && {B'_2} \\
+	{B'_3} && {B'_4}
+	\arrow["{k_{h'_V}}", from=1-2, to=1-4]
+	\arrow["{k_{k_V'}}"', from=1-2, to=2-1]
+	\arrow["{\pi_{s_2\circ m_1 \circ q_1'}^1}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{k_{t_V'}}", from=1-4, to=2-3]
+	\arrow["{\pi_{m_2\circ q_2'}^1}", from=1-4, to=3-4]
+	\arrow["{k_{p_V'}}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+	\arrow["{\pi_{m_3 \circ q_3'}^1}"', from=2-1, to=4-1]
+	\arrow["{h_V'}"{pos=0.7}, from=3-2, to=3-4]
+	\arrow["{\pi_{q_4'}^1}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\arrow["{k_V'}"', from=3-2, to=4-1]
+	\arrow["{t_V'}", from=3-4, to=4-3]
+	\arrow["{p_V'}"', from=4-1, to=4-3]
+	\end{tikzcd}\]
+	And, since $m_3$ and $m_2$ are monos,
+	\[\begin{split}
+		q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
+	\end{split}\qquad\begin{split}
+		q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
+	\end{split}\]
+
+	Computing, we obtain
+	\[\begin{split}
+		q \circ \phi \circ \pi_{q'_4}^1 \circ k_{p_V'} &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'} \\ &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{p'_V}
+	\end{split}\qquad\begin{split}
+		q \circ \phi \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'} \\ &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{t'_V}
+	\end{split}\]
+
+	Since the previous cube has a pushout as top face, by universal property, we have
+	\[
+		q \circ \phi \circ \pi_{q'4}^1 = q \circ \phi \circ \pi_{q'_4}^2
+	\]
+	hence
+	\[
+		v \circ q'_4 \circ \pi_{q'_4}^1 = v \circ q'_4 \circ \pi_{q'_4}^2
+	\]
+
+	\todo{rimane unicità}
+\end{proof}

### 2024-11-11 Article/Background_sections/Limit.tex
eqgrph pushouts reg mono van kampen

@@
 
+\begin{lemma}\label{lemma:limits_of_presheaves}
+    Let $\cat C$ be a category, and let $[\cat C, \Set]$ be the category of presheaves on $\cat C$.
+Let $D: \cat I \to [\cat C, \Set]$ be a diagram of shape $\cat I$ on the presheaves category early mentioned.
+Then,
+    \begin{enumerate}
+        \item The limit of $D$ exists, and it is the presheaf $L: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $L(A)$ is the limit in $\Set$ of the values of the presheaves $D(i)(A)$ for each $i$.
+        \item The colimit of $D$ exists, and it is the presheaf $C: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $C(A)$ is the colimit in $\Set$ of the values of the presheaves $D(i)(A)$, for each $i$.
+    \end{enumerate}
+\end{lemma}
+
 In the next sections, we will work on a special kind of diagrams with certain properties. In particular, we are interested in how a functor behaves with respect to the constructions defined so far.

### 2024-11-11 Article/Graph_sections/Eq_Graphs_integration.tex
eqgrph pushouts reg mono van kampen

@@
 \begin{example}
-	TODO: Q does not preserves limits.
+	TODO: Q does not preserve limits.
 \end{example}
@@
 
-\begin{lemma}\label{lemma:reg_push_stable}
+\begin{lemma}\label{lemma:stab}
 	In $\EqGrph$, pushouts along regular monos are stable.
@@
 \end{proof}
+
+\begin{lemma}\label{lemma:van_kampen}
+	In $\EqGrph$, pushouts along regular monos are $\Reg(\EqGrph)$-Van Kampen.
+\end{lemma}
+
+\begin{proof}
+	In lieu of \Cref{lem:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono, the front faces are pullbacks too, where $\graph{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\graph{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
+        \[\begin{tikzcd}[row sep=23, column sep =23]
+        & {\mathcal{G}_1'} && {\mathcal{G}_2'} \\
+        {\mathcal{G}_3'} && {\mathcal{G}_4'} \\
+        & {\mathcal{G}_1} && {\mathcal{G}_2} \\
+        {\mathcal{G}_3} && {\mathcal{G}_4}
+        \arrow["{h'}", from=1-2, to=1-4]
+        \arrow["{k'}"', from=1-2, to=2-1]
+        \arrow["b"'{pos=0.7}, from=1-2, to=3-2]
+        \arrow["{t'}", from=1-4, to=2-3]
+        \arrow["c", from=1-4, to=3-4]
+        \arrow["{p'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+        \arrow["a"', from=2-1, to=4-1]
+        \arrow["h"{pos=0.7}, from=3-2, to=3-4]
+        \arrow["d"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+        \arrow["k"', from=3-2, to=4-1]
+        \arrow["t", from=3-4, to=4-3]
+        \arrow["p"', from=4-1, to=4-3]
+        \end{tikzcd}\]
+        By \Cref{prop:eqgrph_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as back faces, thus their front faces are pullbacks too.
+        \[\begin{tikzcd}[row sep=20, column sep = 20]
+        & {A_1'} && {A_2'} \\
+        {A_3'} && {A_4'} \\
+        & {A_1} && {A_2} \\
+        {A_3} && {A_4}
+        \arrow["{h'_V}", from=1-2, to=1-4]
+        \arrow["{k'_V}"', from=1-2, to=2-1]
+        \arrow["{b_V}"'{pos=0.7}, from=1-2, to=3-2]
+        \arrow["{t'_V}", from=1-4, to=2-3]
+        \arrow["{c_V}", from=1-4, to=3-4]
+        \arrow["{p'_V}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+        \arrow["{a_V}"', from=2-1, to=4-1]
+        \arrow["{h_V}"{pos=0.7}, from=3-2, to=3-4]
+        \arrow["{d_V}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+        \arrow["{k_V}"', from=3-2, to=4-1]
+        \arrow["{t_V}", from=3-4, to=4-3]
+        \arrow["{p_V}"', from=4-1, to=4-3]
+        \end{tikzcd}\qquad
+        \begin{tikzcd}[row sep=20, column sep = 20]
+        & {B_1'} && {B_2'} \\
+        {B_3'} && {B_4'} \\
+        & {B_1} && {B_2} \\
+        {B_3} && {B_4}
+        \arrow["{h'_E}", from=1-2, to=1-4]
+        \arrow["{k'_E}"', from=1-2, to=2-1]
+        \arrow["{b_E}"'{pos=0.7}, from=1-2, to=3-2]
+        \arrow["{t'_E}", from=1-4, to=2-3]
+        \arrow["{c_E}"', from=1-4, to=3-4]
+        \arrow["{p'_E}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+        \arrow["{a_E}"', from=2-1, to=4-1]
+        \arrow["{h_E}"{pos=0.7}, from=3-2, to=3-4]
+        \arrow["{d_E}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+        \arrow["{k_E}"', from=3-2, to=4-1]
+        \arrow["{t_E}", from=3-4, to=4-3]
+        \arrow["{p_E}"', from=4-1, to=4-3]
+        \end{tikzcd}
+        \]
+
+	On the other hand we can consider the diagrams below, in which the inner squares are pullbacks.
+Since the outer diagrams commute, by definition of porphism of $\EqGrph$, then we have the existence of $m_2\colon C'_2\to U$, $m_3\colon C'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
+
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+	{C'_3} &&& {C_2'} \\
+	& Y & {C'_4} & {} & U & {C_4'} \\
+	& {C_3} & {C_4} && {C_2} & {C_4}
+	\arrow["{m_3}", dashed, from=1-1, to=2-2]
+	\arrow["{p'_C}", from=1-1, to=2-3, bend left = 20]
+	\arrow["{c_C}"', from=1-1, to=3-2, bend right = 20]
+	\arrow["{m_2}", dashed, from=1-4, to=2-5]
+	\arrow["{t'_C}", from=1-4, to=2-6, bend left = 20]
+	\arrow["{b_C}"', from=1-4, to=3-5, bend right = 20]
+	\arrow["{y_1}", from=2-2, to=2-3]
+	\arrow["{y_2}"', from=2-2, to=3-2]
+	\arrow["{d_C}", from=2-3, to=3-3]
+	\arrow["{u_1}", from=2-5, to=2-6]
+	\arrow["{u_2}"', from=2-5, to=3-5]
+	\arrow["{d_C}", from=2-6, to=3-6]
+	\arrow["{p_C}"', from=3-2, to=3-3]
+	\arrow["{t_C}"', from=3-5, to=3-6]
+	\end{tikzcd}\]
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+	{B_3'} & {B'_4} && {B'_2} & {B'_4} \\
+	{C'_3} & Y & {C'_4} & {C_2'} & U & {C_4'} \\
+	& {C_3} & {C_4} && {C_2} & {C_4}
+	\arrow["{p'_V}", from=1-1, to=1-2]
+	\arrow["{q'_3}"', from=1-1, to=2-1]
+	\arrow["f", dashed, from=1-1, to=2-2]
+	\arrow["{q'_4}", from=1-2, to=2-3]
+	\arrow["{t'_V}", from=1-4, to=1-5]
+	\arrow["{q'_2}"', from=1-4, to=2-4]
+	\arrow["g", dashed, from=1-4, to=2-5]
+	\arrow["{q'_4}", from=1-5, to=2-6]
+	\arrow["{c_C}"', from=2-1, to=3-2]
+	\arrow["{y_1}", from=2-2, to=2-3]
+	\arrow["{y_2}"', from=2-2, to=3-2]
+	\arrow["{d_C}", from=2-3, to=3-3]
+	\arrow["{b_C}"', from=2-4, to=3-5]
+	\arrow["{u_1}", from=2-5, to=2-6]
+	\arrow["{u_2}"', from=2-5, to=3-5]
+	\arrow["{d_C}", from=2-6, to=3-6]
+	\arrow["{p_C}"', from=3-2, to=3-3]
+	\arrow["{t_C}"', from=3-5, to=3-6]
+\end{tikzcd}\]
+
+	Now, notice that $m_3$ and $m_2$ are monos because $c_C$ and $b_C$ are monos (\Cref{cor:regmono}). By the proof of \Cref{prop:eqgrph_complete}, to conclude it is enough to show that
+	\[\begin{split}
+		m_3 \circ q'_3 = f
+	\end{split}
+	\qquad
+	\begin{split}
+		m_2\circ q'_2 = g
+	\end{split}\]
+	Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $f$ and $g$, and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:eqgrph_complete}.
+
+	Now, if we compute, we obtain:
+	\[\begin{split}
+		y_1 \circ f &= q'_4 \circ p'_V \\ &= p'_C \circ q'_3 \\ &= y_1 \circ m_3 \circ q'_3
+	\end{split}
+	\qquad
+	\begin{split}
+		u_1 \circ g &= q'_4 \circ t'_V \\ &= t'_C \circ q'_3 \\ &= u_1 \circ m_2 \circ q'_2
+	\end{split}\]
+	\[\begin{split}
+		y_2 \circ f &= d_C \circ q'_3 \\ &= y_2 \circ m_3 \circ q'_3
+	\end{split}
+	\qquad
+	\begin{split}
+		u_2 \circ g &= d_V \circ q'_2 \\ &= u_2 \circ m_2 \circ q'_2
+	\end{split}\]
+	Concluding the proof.
+\end{proof}
+
+From \Cref{prop:eqgrph_complete} and \Cref{lemma:stab,lemma:van_kampen}, by \Cref{th:crit_for_adh}, we can deduce at once the following.
+
+\begin{cor}\label{cor:eqgrph_reg_adh}
+	$\EqGrph$ is $\Reg(\EqGrph)$-adhesive.
+\end{cor}

### 2024-11-11 Article/Graph_sections/Eq_Graphs_integration.tex
first complete

@@
 
+{\color{red}
 \begin{prop}\label{prop:quot_creat_colims}
@@
 \end{prop}
+}
 
@@
 
+{\color{blue}
 \begin{example}
-	TODO: Q does not preserve limits.
+	$Q$ does not preserve limits.
+Indeed, let $\eqgraph{G}_1 = (E_1, A, A, s_1, t_1, id_A)$, $\eqgraph{G}_2 = (E_2, B, B, s_2, t_2, id_B)$ and $\eqgraph{G}_3 = (E_3, A + B, \terminal, s_3, t_3, !_{A + B})$, and let $h = (h_E, \iota_A, !_A): \eqgraph{G}_1 \to \eqgraph{G}_3$, $k = (k_E, \iota_B, !_B): \eqgraph{G}_2 \to \eqgraph{G}_3$, where $(\iota_A, \iota_B, A + B)$ is the coproduct of $A$ and $B$, $\terminal$ is the intial object (in $\Set$, the singleton set as shown in \Cref{ex:set_init_term}), and $!_X$ the unique arrow $X \to \terminal$.
+	The following two diagrams show the pullback of $h$ and $k$ and the pullback of $Q(h)$ and $Q(k)$, on the second component (the vertices of the graphs)
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+		\initial \ar[r, "{p_1}"] \ar[d, "{p_2}" swap] & A \ar[d, "{\iota_A}"] \\
+		B \ar[r, "{\iota_B}"swap] & A+B
+	\end{tikzcd}\
+	\qquad
+	\begin{tikzcd}[row sep = 20, column sep = 20]
+		{A \times B} \ar[r, "{\pi_A}"] \ar[d, "{\pi_B}"swap] & A \ar[d, "{!_A}"] \\
+		B \ar[r, "{!_B}"swap] & \terminal
+	\end{tikzcd}\]
+
+	But the arrow $\initial \to A\times B$ is not epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
 \end{example}
+}
 

### 2024-11-11 Article/Graph_sections/Eq_Graphs_integration.tex
first complete

@@
 Such action is described by the \emph{forgetful functor} $U : \EqGrph \to \Graph$, that maps each graph with equivalence $\eqgraph{G} =  (E, V, C, s, t, q)$ onto $U(\eqgraph{G}) = (E, V, s, t)$, and each morphisms $h = (h_E, h_V, h_C)$ onto $U(h) = (h_E, h_V)$.
-$U$ is effectively a functor, since, on identities, $U((id_E, id_V, id_C)) = (id_E, id_V)$, and on compositions $U(h \circ k) = U((h_E \circ k_E, h_V 1circ k_V, h_C \circ k_C)) = (h_E \circ k_E, h_V \circ k_V) = (h_E, h_V) \circ (k_E \circ k_V) = U(h) \circ U(k)$.
+$U$ is effectively a functor, since, on identities, $U((id_E, id_V, id_C)) = (id_E, id_V)$, and on compositions
+\[\begin{split}
+	U(h \circ k) &= U((h_E \circ k_E, h_V \circ k_V, h_C \circ k_C))\\ &= (h_E \circ k_E, h_V \circ k_V) \\&= (h_E, h_V) \circ (k_E \circ k_V) \\&= U(h) \circ U(k)
+\end{split}\]
 

### 2024-11-12 Article/Background_sections/Limit.tex
introduction

@@
 
-    Since $((c_i')_{i \in \cat I}, C)$ is a limit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
+    Since $((c_i')_{i \in \cat I}, C)$ is a colimit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
 \end{proof}
@@
     Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
-If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
+If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $\phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
 \end{lemma}

### 2024-11-12 Article/Graph_sections/Eq_Graphs_integration.tex
introduction

@@
 \begin{obs}\label{obs:eq_grph_morph_det_by_first_two_comp}
-    Morphisms of graphs with equivalence are uniquely determined by the first two component. That is, if $h_1 = (h_E, h_V, \phi)$ and $h_2 = (h_E, h_V, \psi)$, then $\phi = \psi$.
+    Morphisms of graphs with equivalences are uniquely determined by the first two component. That is, if $h_1 = (h_E, h_V, \phi)$ and $h_2 = (h_E, h_V, \psi)$, then $\phi = \psi$.
 \end{obs}
@@
     \]
-     Faithfulness of $U$ guarantees that $(\tau_E, \tau_V, \tau_C)$ is the unique arrow such that $(\pi_E^i, \pi_V^i, \pi_C^i) \circ (\tau_E, \tau_V, \tau_C) = (\tau_E^i, \tau_V^i, \tau_C^i)$.
-     \todo{Dimostrazione dello statement di sopra, e colimiti}
+     Faithfulness of $U$ and \Cref{obs:eq_grph_morph_det_by_first_two_comp} guarantees that $(\tau_E, \tau_V, \tau_C)$ is the unique arrow such that $(\pi_E^i, \pi_V^i, \pi_C^i) \circ (\tau_E, \tau_V, \tau_C) = (\tau_E^i, \tau_V^i, \tau_C^i)$.
 
@@
      Then, $((c_i \circ q_i)_{i \in \cat I}, C)$ is a cocone for all $B_i$, and, since $((\kappa_i)_{i \in \cat I}, B)$ is the colimit of all $B_i$ (\Cref{lemma:limits_of_presheaves}), there exists a unique arrow $q: B \to C$ such that, for each $i$, $q \circ \kappa_V^i = c_i \circ q_i$.
-Such $q$ is epi {\color{red}{dimostrare}}, and thus $(A, B, C, s, t, q)$ is the colimit of $D$.
-{\color{red}{rifinire, dimostrare unicità}}.
+Such $q$ is epi, by application of \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}, and thus $(A, B, C, s, t, q)$, together with arrows $(\kappa_E^i, \kappa_V^i, c_i)_{i \in \cat I}$ is the colimit of $D$.
 
@@
 \begin{proof}
-	In lieu of \Cref{lem:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono, the front faces are pullbacks too, where $\graph{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\graph{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
+	In lieu of \Cref{lemma:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono, the front faces are pullbacks too, where $\graph{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\graph{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
         \[\begin{tikzcd}[row sep=23, column sep =23]

### 2024-11-13 Article/Graph_sections/EGGs.tex
eqgrph pushouts reg mono van kampen
minori

@@
 Let now be $(A, B, C, s, t, q)$, togehter with projections $(\pi_E^i, \pi_V^i, \pi_C^i)_{i \in \cat I}$ the limit of $I \circ D$, let $(U, u_1, u_2)$ be the kernel pair of $q\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $V\circ I\circ D$.
-	By construction (proof of \Cref{???}\todo{citazione}), there exists a monomorphism $m: Q \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
+	By construction (proof of \Cref{prop:eqgrph_complete}), there exists a monomorphism $m: Q \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
 	\begin{align*}
@@
 	\end{tikzcd}\]
-	By adhesivity of $\Set$, and since $m$ is regular mono, the cube above is Van Kampen, and, by \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, all the faces are pullbacks.
-Then, applying \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout
+	By adhesivity of $\Set$, and since $m$ is regular mono, the cube above is Van Kampen \todo{Non esisono i cubi di Van Kampen, a essere Van Kampen sono certi quadrati},
+
+	\color{blue}
+
+	Since $m$ is a regular mono then $m_C$ is mono by ???.
+Then, by adhesivity of $\Set$, the bottom face of the cube above is a Van Kampen square and thus a pullback.
+Therefore by \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout.
+	\color{black}
+
+	 and, by \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, all the \todo{vertical} faces are pullbacks. Then, applying \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout
 	\[\begin{tikzcd}[row sep=27, column sep = 27]
@@
 	\]
-	By universal property of pushouts, we can conclude $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis.
+	By universal property of pushouts, we can conclude $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis. \todo{Qua estendi un pochino: da questo si deduce che esiste una freccia blah blah}
 \end{proof}

### 2024-11-13 Article/Background_sections/Adhesivity.tex
minori

@@
     We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
+\todo{NO, questo è sbagliato: bisogna introdurre la nozione di adesività forte (cioè VK vale per tutti i cubi)}
 \end{definition}
@@
     In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
+\todo{almeno la seconda parte devi provarla o citarla per le M-adesive}
 \end{prop}
@@
     Let $\cat A$ be a $\mathcal M$-adhesive category for some $\mathcal M \subseteq \Hom(\cat A)$.
-Then, for every other category $\cat C$, the functor category $[\cat C, \cat A]$ is $\mathcal M^{\cat C}$-adhesive, where
+Then, for every other category $\cat C$, the functor category $[\cat C, \cat A]$ is $\mathcal M^{\cat C}$-adhesive, where \todo{Devi chiedere che C abbia tutti i pullback}
     \[
@@
 
+\color{blue}\todo{Ti inserisco una versione un po' più generale del lemma sotto}
+
 \begin{lemma}\label{lemma:pushouts_kernel_pairs}
-    Let $\cat C$ be an $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
+	Let $\cat C$ be an \todo{Qua serve adesività forte} $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube below the top face is an $\mathcal{M}$-pushout.
+	\[\begin{tikzcd}[row sep=25, column sep=25]
+		& {A'} && {B'} \\
+		{C'} && {D'} \\
+		& A && B \\
+		C && D
+		\arrow["{f'}", from=1-2, to=1-4]
+		\arrow["{m'}"', from=1-2, to=2-1]
+		\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
+		\arrow["{n'}"', from=1-4, to=2-3]
+		\arrow["b", from=1-4, to=3-4]
+		\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
+		\arrow["c"', from=2-1, to=4-1]
+		\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
+		\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
+		\arrow["m", from=3-2, to=4-1]
+		\arrow["n", from=3-4, to=4-3]
+		\arrow["g"', from=4-1, to=4-3]
+	\end{tikzcd}\]
+
+	Then, the square below is a pushout.
+	\[
+	\begin{tikzcd}%[row sep=25, column sep=25]
+		{K_a} \ar[r, "{k_{f'}}"] \ar[d, "{k_{m'}}"'] & {K_b} \ar[d, "{k_{n'}}"] \\
+		{K_c} \ar[r, "{k_{g'}}"'] & {K_d}
+	\end{tikzcd}
+	\]
+\end{lemma}
+
+\begin{proof}
+	Since $f'$, being the pullback of $f$, is in $\mathcal{M}$ then by  \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats} the bottom face of the cube is a pullback.
+Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks \todo{Nota che le frecce verticali NON sono mono in generale: qua serve adesività forte}.
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+		& {K_a} && {K_b} \\
+		{K_c} && {K_d} \\
+		& {A'} && {B'} \\
+		{C'} && {D'}
+		\arrow["{k_{f'}}", from=1-2, to=1-4]
+		\arrow["{k_{m'}}"', from=1-2, to=2-1]
+		\arrow["{\pi_a^1}"{pos=0.7}, from=1-2, to=3-2]
+		\arrow["{k_{n'}}", from=1-4, to=2-3]
+		\arrow["{\pi_b^1}", from=1-4, to=3-4]
+		\arrow["{k_{g'}}"{pos=0.7}, from=2-1, to=2-3, crossing over]
+		\arrow["{\pi_c^1}"', from=2-1, to=4-1]
+		\arrow["{f'}"'{pos=0.3}, from=3-2, to=3-4]
+		\arrow["{\pi_d^1}"{pos=0.7}, from=2-3, to=4-3, crossing over]
+		\arrow["{m'}", from=3-2, to=4-1]
+		\arrow["{n'}", from=3-4, to=4-3]
+		\arrow["{g'}"', from=4-1, to=4-3]
+	\end{tikzcd}\]
+
+Now the thesis follows from strong $\mathcal{M}$-adhesivity.
+\end{proof}
+
+\color{black}
+
+\begin{lemma}\label{lemma:pushouts_kernel_pairs}
+    Let $\cat C$ be an \todo{Qua serve adesività forte} $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
         \[\begin{tikzcd}[row sep=25, column sep=25]

### 2024-11-14 Article/Background_sections/Adhesivity.tex
minima

@@
 \end{prop}
+
+\begin{proof}
+	Let the following square be a pushout, with $m$ mono.
+	\[\begin{tikzcd}[row sep = 26, column sep = 26]
+		A \ar[r, "f"] \ar[d, "m"swap] & B \ar[d, "n"] \\
+		C \ar[r, "g"swap] & D
+	\end{tikzcd}\]
+	Consider now the following cube.
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+	& A && B \\
+	A && B \\
+	& A && B \\
+	C && D \\
+	& {}
+	\arrow["f", from=1-2, to=1-4]
+	\arrow["{id_A}"', from=1-2, to=2-1]
+	\arrow["{id_A}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{id_B}"', from=1-4, to=2-3]
+	\arrow["{id_B}", from=1-4, to=3-4]
+	\arrow["m"', from=2-1, to=4-1]
+	\arrow["f"{pos=0.7}, from=3-2, to=3-4]
+	\arrow["m"', from=3-2, to=4-1]
+	\arrow["n", from=3-4, to=4-3]
+	\arrow["g"', from=4-1, to=4-3]
+	\arrow["f"{pos=0.7}, from=2-1, to=2-3, crossing over]
+	\arrow["n"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\end{tikzcd}\]
+
+	We have then that the top face is a pullback, and by \Cref{prop:kermono}, the left face is a pullback.
+Since the bottom face is a pushout by hypothesis, we have that the front face and the right one are pullbacks (by adhesivity).
+Hence, we can conclude that the starting square (which is the front and the bottom face of the cube) is a pushout, and by \Cref{prop:kermono}, since the left face is a pullback, $n$ is mono.
+\end{proof}
 

### 2024-11-14 Article/Cat_of_Graphs.tex
minori
Some proofs, reordering of material
Def of subobjects, lemma 1.2.13, 1.2.15
some proofs
eqgrph pushouts reg mono van kampen
first complete
minima

@@
-\newcommand{\graph}[1]{\mathcal{#1}}
+\renewcommand{\graph}[1]{\mathcal{#1}}
 \newcommand{\Graph}{\mathbf{Graph}}
@@
 This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a category to another.
+Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between categories.
 
 \input{Graph_sections/Graphs}
-\input{Graph_sections/Eq_Graphs}
+%\input{Graph_sections/Eq_Graphs_Notes_Results}
+\input{Graph_sections/Eq_Graphs_integration}
 \input{Graph_sections/EGGs}

### 2024-11-14 Article/Graph_sections/Eq_Graphs_integration.tex
minima

@@
 
-Another functor that will be useful later is $V: \EqGrph \to \Set$, that sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.
+Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$ and $h = (h_E, h_V, h_C)$ to $h_C$.
 
@@
 	\\
-	{C'_3} && S && {C'_2} \\
+	{C'_1} && S && {C'_2} \\
 	\\
@@
 		\begin{split}
-			s_1 \circ m_1 \circ q_1 &= q'2 \circ h'_V \\ &= h'_C \circ q'_1
+			s_1 \circ m_1 \circ q_1 &= q'_2 \circ h'_V \\ &= h'_C \circ q'_1
 		\end{split}\qquad\begin{split}
 			q'_4 \circ t'_V &= t'_C \circ q'_2\\ &= u_1\circ m_2 \circ q'_2
-		\end{split}\quad\begin{split}
+		\end{split}
+	\]\[
+		\begin{split}
 			y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
@@
 	\]
-	Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p_C = y_1 \circ m_3$.
+	Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.
 	Let now $z: \graph{G}'_2 \to \graph H = (E, V, Q, s, t, q)$, $w: \graph G_3^1 \to \graph H$ be two morphisms such that $z \circ h' = w \circ k'$, and let $\phi:B'_4 \to V$ be the arrow induced by $z_V$ and $w_V$.

### 2024-11-14 Article/Graph_sections/Graphs.tex
minima

@@
 
-A (directed graph) $\graph{G}$ is a mathematical structure consisting of a set of edge, a set of nodes and two functions, one assigning a \emph{source} node and one assigning a \emph{target} node to an edge.
+A (directed graph) $\graph{G}$ is a structure consisting of a set of edge, a set of nodes and two functions, one assigning a \emph{source} node and one assigning a \emph{target} node to an edge.
 Formally, $\graph{G}$ is a quadruple $(V_\graph{G}, E_\graph{G}, s_\graph{G}, t_\graph{G})$, where $V_\graph{G}$ is the set of nodes, $E_\graph{G}$ is the set of edges, and $s_\graph{G}, t_\graph{G}: E_\graph{G} \rightarrow V_\graph{G}$ are the source and the target functions.

### 2024-11-14 Article/Graph_sections/Eq_Graphs_integration.tex
proof of 2.2.12

@@
 
-Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$ and $h = (h_E, h_V, h_C)$ to $h_C$.
+Another functor that will be useful later is $V: \EqGrph \to \Set$, that sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.
 
@@
 \end{prop}
-}
 
@@
     Preserve from \Cref{th:adjoints_preserves_lim}. Remain to see Reflect.
+	Let $D: \cat I \to \EqGrph$ be a diagram, and let $((c_i)_{i\in \cat I}, \eqgraph{C})$ be the colimit of $Q \circ D$, where $\eqgraph{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
+	Let now $T: \EqGrph \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.
+	Let then $((b_i)_{i\in \cat I}, B)$ be the colimit of $T \circ D$.
+	Consider the following situation.
+	\[\begin{tikzcd}[row sep = 24, column sep = 24]
+		& B & \\
+		B_i \ar[ur, "{b_i}"] \ar[rr, "h_V"] \ar[d, "{q_i}"] & & B_j \ar[ul, "{b_j}"swap] \ar[d, "{q_j}" swap] \\
+		C_i \ar[dr, "{c_C^i}" swap] \ar[rr, "{h_C}"swap] & & C_j \ar[dl, "{c_C^j}"] \\
+		& C &
+	\end{tikzcd}\]
+
+	Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $T \circ D$, there exists a unique $q: B \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
+	Consider now the functor $W: \EqGrph \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component.
+By \Cref{prop:eqgrph_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, A)$ is the colimit of $W \circ D$.
+	Notice that $((b_i \circ s_i)_{i \in \cat{I}}, B)$ and $((b_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
+It remains now to show that $(A, B, C, s, t, q)$, together with $(c_E^i, b_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
 \end{proof}
+
+}
 

### 2024-11-15 Article/Cat_of_Graphs.tex
proof of 2.2.12

@@
 This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
-Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between categories.
+Starting from the set-theoretical definition of graphs, we will give an abstraction via functor categories, in which a graph is nothing but a functor between a categories.
 

### 2024-11-15 Article/Graph_sections/Eq_Graphs_integration.tex
proof of 2.2.12

@@
 
-Another functor that will be useful later is $V: \EqGrph \to \Set$, that sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.
+Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.
 

### 2024-11-16 Article/Background_sections/Adhesivity.tex

@@
     Let $\cat A$ be a $\mathcal M$-adhesive category for some $\mathcal M \subseteq \Hom(\cat A)$.
-Then, for every other category $\cat C$, the functor category $[\cat C, \cat A]$ is $\mathcal M^{\cat C}$-adhesive, where \todo{Devi chiedere che C abbia tutti i pullback}
+Then, if $\cat C$ is a category whith all the pullbacks, the functor category $[\cat C, \cat A]$ is $\mathcal M^{\cat C}$-adhesive, where
     \[

### 2024-11-16 Article/Background_sections/Basic_Notions.tex
minori
eqgrph pushouts reg mono van kampen

@@
 \end{proof}
+{\color{red}
+\begin{cor}\label{cor:unique}
+	% La fattorizzazione di un morfismo è unica a meno di isomorfismo \todo{Scrivilo bene (l'isomorfismo dovrà rispettare certe coerenze) e dimostralo}
+	In $\Set$, let $f:A \to B$ be a morphism, and let $f=m \circ e$, $f=m'\circ e'$ be two factorizations of $f$, with $e: A \to X$ and $e': A \to Y$ epis and $m: X \to B$, $m': Y \to B$ monos.
+	Then, there exists an isomorphism $\phi: X \to Y$.
+\end{cor}
 
+\begin{proof}
+	Representing the hypothesis in diagrams, we have the following situation
+	\[\begin{tikzcd}
+		A \ar[r, "e"] \ar[d, "e'"swap] & X \ar[d, "m"] & A \ar[r, "e'"] \ar[d, "e"swap] & Y \ar[d, "m'"] \\
+		Y \ar[r, "m'"swap] \ar[ur, dashed, "h"] & B    & X \ar[r, "m"swap] \ar[ur, dashed, "k"] & B 
+	\end{tikzcd}\]
+	where the dashed arrows are yielded by \Cref{prop:prop_epi_mono_Set}. Hence, we have that
+	\[\begin{split}
+		id_X \circ e &= h \circ e' \\ &= h \circ k \circ e
+	\end{split}\qquad\begin{split}
+		id_Y \circ e' &= k \circ e \\ &= k \circ h \circ e'
+	\end{split}\]
+	Hence, $h \circ k = id_X$, $k \circ h = id_Y$, obtaining the isomorphism.
+\end{proof}
+}
 \subsection{Categories from other categories}\label{ssect:cats_from_cats}

### 2024-11-16 Article/Graph_sections/Eq_Graphs_integration.tex
proof of 2.2.12

@@
 
-Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.
+Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$ and $h = (h_E, h_V, h_C)$ to $h_C$.
 
@@
 	For $C'_1$, we can make a similar argument, let $S$ be the pullback of $m_2$ along $x_1$, using \Cref{lemma:pullback_lemma} and, again, the proof of \Cref{prop:eqgrph_complete} we know that $q'_1$ arise as the factorization of the arrow $B'_1\to S$ induced by $q'_2\circ h'_2$ and $a_2$ so that we have a diagram.
-	\[\begin{tikzcd}[row sep = 20, column sep =20]
+	\[\begin{tikzcd}[row sep = 16, column sep =16]
 	{B'_1} && {B'_2} \\
@@
 We want to construct the arrow $v: C'_4 \to Q$ in the diagram below.
-	\[\begin{tikzcd}[row sep = 25, column sep = 25]
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
 	& {B_1'} && {B_2'} \\

### 2024-11-18 Article/introduction.tex
minima

\chapter*{Introduction}

This work discusses the adhesivity of e-graphs, a data structure introduced in \cite{???}\todo{citations}, giving them a structure of category and then working on its algebraic properties.

The first chapter is about basic concepts of category theory, such as categories, limits, constructions and adhesivity, that will be used to model the categories on which in the second chapter we will work on.
The second chapter is entirely focused on graphs, starting from a general notion of graphs, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, 
source and target, which assign to each edge a source vertex and a target one. The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization of them but also makes in evidence particular properties proper of graphs. Then, we endow graphs with an equivalence relation among verices, to end up with an adhesivity result. The last part is about e-graphs, that are nothing but graphs with a certain type of equivalence relation, inheriting then almost all the properties of the category of graphs with equivalences.

### 2024-11-18 Article/Background_sections/Adhesivity.tex
minima

@@
     % \]
+	\iffalse
     \[
@@
     \]
+	\fi
     \[\begin{tikzcd}[row sep=25, column sep=25]
@@
         \item $a, b, c, d \in \mathcal{A}$;
-        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
+%        \item whenever the top and the left squares are pullbacks then the outer square is a pushout if and only of the right and the bottom squares are pullbacks.
+	\item whenever the back and the left squares of the cube are pullbacks, then the top square is a pullback if and only if the front and the right squares are pullbacks.
     \end{itemize}
@@
 Applying $F$, we obtain $F(C) \xrightarrow[]{F(g)} F(D) \xleftarrow[]{F(m)} B$, with $F(m) \in \mathcal{N}$ by hypothesis.
-Then, there exists a pullback $(P_F, p_{F(B)}, p_{(F(D))})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
+Then, there exists a pullback $(P_F, p_{F(B)}, p_{F(D)})$ in $\cat D$, which is an $\mathcal N$-pullback (\Cref{def:pullback_pushout}).
 Since $F$ creates pullbacks, hence lifts them (\Cref{obs:funct_creat_lim_then_lift}), there exist a pullback $(P, p_B, p_D)$ in $\cat C$.

### 2024-11-19 Article/Background_sections/Adhesivity.tex
minima

@@
     \end{itemize}
+	when in the last requirement holds only the \textit{if} part, we say that the category is $\mathcal{A}$-stable.
+Moreover, $\Hom(\cat C)$-Van Kampen squares are said to be \emph{Van Kampen}, and $\Hom(\cat C)$-stable squares are called \emph{stable}.
 \end{definition}
@@
     \end{enumerate}
-    We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
-\todo{NO, questo è sbagliato: bisogna introdurre la nozione di adesività forte (cioè VK vale per tutti i cubi)}
+	$\cat C$ is said to be \emph{strictly $\mathcal{M}$-adhesive} if $\mathcal{M}$-pushouts are Van Kampen sqaures.
+	We also say that $\cat C$ is \emph{adhesive} when it is strictly $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is strictly $\Reg(\cat C)$-adhesive.% \todo{NO, questo è sbagliato: bisogna introdurre la nozione di adesività forte (cioè VK vale per tutti i cubi)}
 \end{definition}
 
+    %We also say that $\cat C$ is \emph{adhesive} when it is $\Mono(\cat C)$-adhesive, and \emph{quasiadhesive} when it is $\Reg(\cat C)$-adhesive.
+\todo{NO, questo è sbagliato: bisogna introdurre la nozione di adesività forte (cioè VK vale per tutti i cubi)}
 \begin{obs}
@@
     In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
-\todo{almeno la seconda parte devi provarla o citarla per le M-adesive}
+%\todo{almeno la seconda parte devi provarla o citarla per le M-adesive}
+	In $\mathcal{M}$-adhesive categories, $\mathcal{M}$-pushouts are pullbacks.
 \end{prop}
@@
 Hence, we can conclude that the starting square (which is the front and the bottom face of the cube) is a pushout, and by \Cref{prop:kermono}, since the left face is a pullback, $n$ is mono.
+
+	Suppose now that $\cat C$ is $\mathcal{M}$-adhesive, and let the following square be a $\mathcal{M}$-pushout, so $m, n \in \mathcal{M}$.
+	\[\begin{tikzcd}[row sep = 26, column sep = 26]
+		A \ar[r, "f"] \ar[d, "m"swap] & B \ar[d, "n"] \\
+		C \ar[r, "g"swap] & D
+	\end{tikzcd}\]
+	Consider now the following cube.
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+	& A && B \\
+	A && B \\
+	& A && B \\
+	C && D \\
+	& {}
+	\arrow["f", from=1-2, to=1-4]
+	\arrow["{id_A}"', from=1-2, to=2-1]
+	\arrow["{id_A}"'{pos=0.7}, from=1-2, to=3-2]
+	\arrow["{id_B}"', from=1-4, to=2-3]
+	\arrow["{id_B}", from=1-4, to=3-4]
+	\arrow["m"', from=2-1, to=4-1]
+	\arrow["f"{pos=0.7}, from=3-2, to=3-4]
+	\arrow["m"', from=3-2, to=4-1]
+	\arrow["n", from=3-4, to=4-3]
+	\arrow["g"', from=4-1, to=4-3]
+	\arrow["f"{pos=0.7}, from=2-1, to=2-3, crossing over]
+	\arrow["n"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+	\end{tikzcd}\]
+	By the same argument as before, we can conclude that the starting square is a pullback.
 \end{proof}
@@
 
-\color{blue}\todo{Ti inserisco una versione un po' più generale del lemma sotto}
-
 \begin{lemma}\label{lemma:pushouts_kernel_pairs}
-	Let $\cat C$ be an \todo{Qua serve adesività forte} $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube below the top face is an $\mathcal{M}$-pushout.
+	Let $\cat C$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube below the top face is an $\mathcal{M}$-pushout.
 	\[\begin{tikzcd}[row sep=25, column sep=25]
@@
 	Since $f'$, being the pullback of $f$, is in $\mathcal{M}$ then by  \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats} the bottom face of the cube is a pullback.
-Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks \todo{Nota che le frecce verticali NON sono mono in generale: qua serve adesività forte}.
+Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks.
 	\[\begin{tikzcd}[row sep = 20, column sep = 20]
@@
 
-\color{black}
-
 \begin{lemma}\label{lemma:pushouts_kernel_pairs}
-    Let $\cat C$ be an \todo{Qua serve adesività forte} $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
+    Let $\cat C$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
         \[\begin{tikzcd}[row sep=25, column sep=25]

### 2024-11-19 Article/Graph_sections/EGGs.tex
minima

@@
 	\end{tikzcd}\]
-	By adhesivity of $\Set$, and since $m$ is regular mono, the cube above is Van Kampen \todo{Non esisono i cubi di Van Kampen, a essere Van Kampen sono certi quadrati},
 
-	\color{blue}
-
-	Since $m$ is a regular mono then $m_C$ is mono by ???.
+	Since $m$ is a regular mono then $m_C$ is mono by \Cref{cor:reg_mono_EGG} and \Cref{cor:regmono}.
 Then, by adhesivity of $\Set$, the bottom face of the cube above is a Van Kampen square and thus a pullback.
 Therefore by \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout.
-	\color{black}
 
-	 and, by \Cref{prop:monos_are_preserved_by_pullbacks_in_adh_cats}, all the \todo{vertical} faces are pullbacks. Then, applying \Cref{lemma:pushouts_kernel_pairs}, the square below is a pushout
 	\[\begin{tikzcd}[row sep=27, column sep = 27]
@@
 	\]
-	By universal property of pushouts, we can conclude $q \circ t \circ u_1 = q \circ t \circ u_2$, hence the thesis. \todo{Qua estendi un pochino: da questo si deduce che esiste una freccia blah blah}
+	By universal property of pushouts, there must exists a unque arrow $v: U \to C$ such that 
+	\[\begin{split}v \circ f_n &= q \circ t \circ u_1 \circ f_n\\v\circ f_n  &= q \circ t \circ u_2 \circ f_n \end{split}\qquad\begin{split}v \circ f_k &= q \circ t \circ u_1 \circ f_k\\v \circ f_k &= q \circ t \circ u_2 \circ f_k\end{split}\]
+		 hence, we deduce $q \circ t \circ u_1 = q \circ t \circ u_2$, and the thesis follows.
 \end{proof}

### 2024-11-19 Article/Graph_sections/Eq_Graphs_integration.tex
minima

@@
 
-Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$ and $h = (h_E, h_V, h_C)$ to $h_C$.
+Another functor that will be useful later is $V: \EqGrph \to \Set$, sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $C_G$, and $h = (h_E, h_V, h_C)$ to $h_C$.
 
@@
 
-{\color{blue}
 \begin{example}
@@
 \end{example}
-}
 
@@
 			y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
-		\end{split}\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'
-		\end{split}
+		\end{split}%\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'\end{split}
 	\]
@@
 	\[\begin{split}
-		q \circ \phi \circ \pi_{q'_4}^1 \circ k_{p_V'} &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'} \\ &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{p'_V}
+		q \circ \phi \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'} \\ &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{p'_V}
 	\end{split}\qquad\begin{split}
@@
 	\[
-		q \circ \phi \circ \pi_{q'4}^1 = q \circ \phi \circ \pi_{q'_4}^2
+		q \circ \phi \circ \pi_{q'_4}^1 = q \circ \phi \circ \pi_{q'_4}^2
 	\]
-	hence
+	hence, $v$ is the mediating arrow.
 	\[
@@
 	\]
-
-	\todo{rimane unicità}
 \end{proof}

### 2024-11-20 Article/Background_sections/Basic_Notions.tex

@@
 
-Given an arrow $f A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
+Given an arrow $f: A \rightarrow B$ in a category $\cat C$, we say that $f$ \emph{factors through} $g: C \rightarrow B$ if there exists an arrow $h: A \rightarrow C$ such that $f = h \circ g$.
 

### 2024-11-20 Article/Background_sections/Limit.tex

@@
 \section{Limits and Universal Constructions}\label{sect:limits_univ_constr}
-
-\todo{aggiungere i diagrammi e sistemare per l'indice}
 
@@
     -- i.e., $D(\alpha) \circ f_i = f_j$.
-    We denote such cone as $\{f_i: X \rightarrow D(i)\}$.
+	We denote such cone as $(X, (f_i)_{i\in\cat I})$.% $\{f_i: X \rightarrow D(i)\}$.
 
@@
 \begin{obs}\label{obs:category_of_cones}
-    Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$, is defined to have cones for $D$ as objects and cone morphisms as arrows, where a cone morphism $\phi: C \rightarrow C'$ from $C = \{f_i: X \rightarrow D(i)\}$ to $C' = \{f_i':X' \rightarrow D(i)\}$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
+	Given a diagram $D$, the category of the cones for $D$, denoted $\textbf{Cone}(D)$, is defined to have cones for $D$ as objects and cone morphisms as arrows, where a cone morphism $\phi: C \rightarrow C'$ from $C =(X, (f_i)_{i\in\cat I})$ to $C' = (X', (f_i')_{i \in \cat I})$ is a morphism $\phi: X \rightarrow X'$ such that the following diagram commutes for each $i$:
     \[
@@
 	Let $D:\cat {I \rightarrow C}$ be a diagram in $\cat C$ of shape $\cat I$.
-A cone $\{f_i: X \rightarrow D(i)\}$ is a \emph{limit} provided that, for any other cone $\{f_{i}': X' \rightarrow D(i)\}$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
+A cone $(X, (f_i)_{i \in \cat I})$ is a \emph{limit} provided that, for any other cone $(X', (f_i')_{i \in \cat I})$ for $D$, then there exists a unique morphism $k: X' \rightarrow X$ such that the following diagram commutes for each object $i$ of $\cat I$:
     \[
@@
     \]
-    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$. Sometimes we will refer to the unique arrow $k$ as the \emph{mediating arrow}.
+    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Sometimes we will refer to the unique arrow $k$ as the \emph{mediating arrow}.
 \end{definition}
@@
 	A \emph{cocone} for a diagram $D: \cat{I \rightarrow C}$ is an object $Y$ of $\cat C$ together with arrows $f_i : D(i) \rightarrow Y$ such that, for each $g: D(i) \rightarrow D(j)$ of $\cat C$, $f_j \circ g = f_i$.
-A cocone is denoted $\{f_i: D(i) \rightarrow Y \}$.
-    A \emph{colimit} for $D$ is a cocone $C = \{f_i: D(i) \rightarrow Y \}$ with the universal property -- i.e., if $C' = \{ f_i' : D(i) \rightarrow Y'\}$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
+A cocone is denoted $((f_i)_{i\in\cat I}, Y)$.
+	A \emph{colimit} for $D$ is a cocone $((f_i)_{i \in \cat I}, Y)$ with the universal property -- i.e., if $((f_i')_{i \in \cat I}, Y')$ is another cone for $D$, then there exists a unique arrow $h:Y \rightarrow Y'$ such that, for each $i$, $h \circ f_i = f_i'$.
 \end{definition}
@@
 \begin{example}\label{ex:po_in_set}
-    \color{blue}
     In $\Set$, given two functions $f: A \rightarrow B$ and $g: A \rightarrow C$, the pushout of them is the set $X = (B \amalg C) /_\sim$, where $\sim$ is the least equivalence relation such that $f(a) \sim g(a)$ for each $a \in A$, with $\iota_g:B \rightarrow X$ and $\iota_f : C \rightarrow X$ as arrows, sending each element of the domain in the corresponding equivalence class in $X$.
@@
 In fact, taking the equivalence relation $\sim$, we have that $f(a) \sim f(a')$ if and only if $a = a'$ by hypothesis, and then $x \sim x'$ if and only if $x = x'$, then the pushout morphisms sends each element in an equivalence class composed only by the element itself, thus are injective.
-    This is an interesting property that in other categories may do not hold, and will be recalled later.
 \end{example}
@@
 The connection between constructions as products and equalizers and limits is made clear by the following theorem.
-The idea behind the proof is the fact that, given a diagram $D : \cat I \rightarrow \cat C$, if each subset of objects $X = \{D(i) \mid i \in \Ob(\cat I)\} \subseteq \Ob(\cat C)$ has a product $(\prod_{i \in I} D(i), (\pi_i)_{i \in \Ob( \cat I)})$ and each pair of arrows $f, g \in \cat C (D(i), D(j))$ has an equalizer $Eq(f, g)$, then one can construct the cone taking the equalizer of the arrows that has as domain the product of the objects of the diagram, and as codomain the product of the codomains of the arrows of the diagram.
+The idea behind the proof is the fact that, given a diagram $D : \cat I \rightarrow \cat C$, if each subset of objects $X = \{D(i) \mid i \in \Ob(\cat I)\} \subseteq \Ob(\cat C)$ has a product $(\prod_{i \in I} D(i), (\pi_i)_{i \in \Ob( \cat I)})$ and each pair of arrows $f, g \in \cat C (D(i), D(j))$ has an equalizer, then one can construct the cone taking the equalizer of the arrows that has as domain the product of the objects of the diagram, and as codomain the product of the codomains of the arrows of the diagram.
 This construction has the universal property because equalizers and products do.

### 2024-11-20 Article/Limit.tex

--- 2024-11-11 Article/Background_sections/Limit.tex
@@
 \section{Limits and Universal Constructions}\label{sect:limits_univ_constr}
-
-\todo{aggiungere i diagrammi e sistemare per l'indice}
-
 \subsection{Limits and Colimits}
@@
     \]
-    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$. Sometimes we will refer to the unique arrow $k$ as the \emph{mediating arrow}.
+    -- i.e., $f_i \circ k = f_i'$ for each object $i$ of $\cat I$. Such limit is denoted as $(X, f_i)_{i \in \cat I}$
 \end{definition}
@@
 
-\begin{remark}\label{rem:limits_are_unique_up_to_isomorphisms}
+\begin{remark}
     It makes sense to refer to a (co)limit as \emph{the} (co)limit.
@@
 
-The dual of the proposition above states that a coequalizer is an epimorphism.
-
 Of all monomorphisms, an interesting subclass of them is the one that contains only the equalizers.
 
-\begin{definition}[Regular Monomorphism, Regular Epimorphism]\label{def:reg_mono}
-    A monomorphism that is an equalizer for a pair of arrows is said \emph{regular monomorphism}.
-The class of all regular monomorphisms of a category $\cat C$ is denoted $\Reg(\cat C)$.
-An epimorphism that is a coequalizer for a pair of arrows is said \emph{regular epimorphism}.
+\begin{definition}[Regular Monomorphism]\label{def:reg_mono}
+    A monomorphism that is an equalizer for a pair of arrows is said \emph{regular monomorphism}. The class of all regular monomorphisms of a category $\cat C$ is denoted $\Reg(\cat C)$.
 \end{definition}
 
-% -- NON SEMPRE E' VERO !!! ---
-% \begin{obs}
-%     Given two composable regular monos $m$ and $n$, suppose that $n$ equalizes two arrows $f$ and $g$. Then, we have
-%     \begin{align*}
-%         g \circ (n \circ m) &= (g \circ n) \circ m &&\\
-%                             &= (f \circ n) \circ m  && \textit{$n$ equalizer} \\
-%                             &= f \circ (n \circ m)
-%     \end{align*}
-%     Since $n \circ m$ is mono (\Cref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
-% \end{obs}
+\begin{obs}
+    Given two composable regular monos $m$ and $n$, suppose that $n$ equalizes two arrows $f$ and $g$. Then, we have
+    \begin{align*}
+        g \circ (n \circ m) &= (g \circ n) \circ m &&\\
+                            &= (f \circ n) \circ m  && \textit{$n$ equalizer} \\
+                            &= f \circ (n \circ m)
+    \end{align*}
+    Since $n \circ m$ is mono (\Cref{prop:epi_mono_prop}), we have shown that, given a category $\cat C$, $\Reg(\cat C)$ is closed under composition. 
+\end{obs}
 
@@
 
-The following lemma is a classical result, its proof is in the appendix.
-
-\begin{lemma}[Pullback Lemma]\label{lemma:pullback_lemma}
-        Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
-        \[
-            \begin{tikzcd}
-                X \arrow[r, "f"] \arrow[d, "t"swap] & Y \arrow[r, "g"] \arrow[d, "k"] & Z \arrow[d, "h"] \\
-                A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
-            \end{tikzcd}
-        \]
-\end{lemma}
-
-\begin{cor}\label{cor:cube} 
-    Let $\cat{C}$ be a category and suppose that  the solid part of the following cube is given
-	\[\begin{tikzcd}[row sep=13 pt, column sep=13 pt]
-    	& {Y'} && {Z'} \\
-    	{B'} && {C'} \\
-    	& Y && Z \\
-    	B && C
-    	\arrow["{g'}", from=1-2, to=1-4]
-    	\arrow["{q'}"', dashed, from=1-2, to=2-1]
-    	\arrow["y"'{pos=0.8}, from=1-2, to=3-2]
-    	\arrow["{r'}", from=1-4, to=2-3]
-    	\arrow["z", from=1-4, to=3-4]
-    	\arrow["{k'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
-    	\arrow["b"', from=2-1, to=4-1]
-    	\arrow["c"{pos=0.7}, from=2-3, to=4-3]
-    	\arrow["g"{pos=0.3}, from=3-2, to=3-4]
-    	\arrow["q"'{pos=0.2}, from=3-2, to=4-1]
-    	\arrow["r", from=3-4, to=4-3]
-    	\arrow["k"', from=4-1, to=4-3]
-        \end{tikzcd}\]
-	If the front face is a pullback then there is a unique $q'\colon Y'\to B'$ filling the diagram.
-If, moreover, the other two vertical faces are also pullbacks, then the following square is a pullback too.
-	\[\begin{tikzcd}
-	    Y' \ar[r, "{q'}"] \ar[d, "y"swap] & B' \ar[d,"b"] \\
-            Y \ar[r, "q"swap] & B
-	\end{tikzcd}\]
-\end{cor}
-\begin{proof}
-	Let us compute:
-	\begin{align*}
-            c\circ r'\circ g'   &=  r\circ z \circ g'   \\
-                                &=  r\circ g \circ y    \\
-                                &=k\circ q \circ y
-	\end{align*}
-	Since the front face is a pullback, this guarantees the existence of $q'$.  The second half of the thesis follows applying \Cref{lemma:pullback_lemma} to the following rectangle.
-	\[\begin{tikzcd}[row sep=15 pt, column sep=15 pt]
-	{Y'} && {B'} && {C'} \\
-	\\
-	Y && B && C
-	\arrow["{q'}"', from=1-1, to=1-3]
-	\arrow["{r' \circ g'}", bend left = 30, from=1-1, to=1-5]
-	\arrow["y"', from=1-1, to=3-1]
-	\arrow["{k'}"', from=1-3, to=1-5]
-	\arrow["b", from=1-3, to=3-3]
-	\arrow["c", from=1-5, to=3-5]
-	\arrow["q", from=3-1, to=3-3]
-	\arrow["{r \circ g}"', bend right=30, from=3-1, to=3-5]
-	\arrow["k", from=3-3, to=3-5]
-\end{tikzcd}\]
-\end{proof}
-
 The connection between constructions as products and equalizers and limits is made clear by the following theorem.
@@
 
-\begin{lemma}\label{lemma:limits_of_presheaves}
-    Let $\cat C$ be a category, and let $[\cat C, \Set]$ be the category of presheaves on $\cat C$.
-Let $D: \cat I \to [\cat C, \Set]$ be a diagram of shape $\cat I$ on the presheaves category early mentioned.
-Then,
-    \begin{enumerate}
-        \item The limit of $D$ exists, and it is the presheaf $L: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $L(A)$ is the limit in $\Set$ of the values of the presheaves $D(i)(A)$ for each $i$.
-        \item The colimit of $D$ exists, and it is the presheaf $C: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $C(A)$ is the colimit in $\Set$ of the values of the presheaves $D(i)(A)$, for each $i$.
-    \end{enumerate}
-\end{lemma}
+\begin{obs}\label{obs:limits_in_presh}
+    So far we introduced categories of presheaves.
+In these categories, an interesting fact is that limits and colimits are computed pointwise -- i.e., the limit of a diagram in a category of presheaves is exactly the limit on each of its components.
+\end{obs}
 
@@
 \end{remark}
-
-\begin{prop}\label{prop:nat_tran_induces_unique_arrow_between_colimits}
-    Let $D, D': \cat{I \to C}$ be two functors, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
-Then, a natural transformation $\phi: D \dot\to D'$ induces a unique arrow $c: C \to C'$.
-\end{prop}
-
-\begin{proof}
-    Consider the following situation.
-    \[\begin{tikzcd}[row sep=26 pt, column sep= 13 pt]
-        & C & \\
-        D(i) \ar[ur, "{c_i}"] \ar[d, "{\phi_i}"swap] \ar[rr, "{D(\alpha)}"]&& D(j) \ar[ul, "{c_j}"swap] \ar[d, "{\phi_j}"] \\
-        D'(i) \ar[dr, "{c_i'}" swap] \ar[rr, "{D'(\alpha)}" swap] && D'(j) \ar[dl, "{c_j'}"] \\
-        & C' &
-    \end{tikzcd}\]
-
-    To prove the statement, we note that $((c_i' \circ \phi_i)_{i \in \cat I}, C')$ is a cocone for $D$. Computing, we have, for each $i$, $j$ and $\alpha: i \to j$
-    \begin{align*}
-        c_j' \circ \phi_j \circ D(\alpha)   
-                        &=  c_j' \circ D'(\alpha) \circ \phi_i  &&\textit{Naturality of $\phi$}\\
-                        &=  c_i' \circ \phi_i                   &&\textit{$((c_i')_{i\in \cat I}, C')$ is a colimit for $D'$}
-    \end{align*}
-
-    Since $((c_i')_{i \in \cat I}, C)$ is a limit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
-\end{proof}
-
-\subsection{Kernel Pairs and Regular Epimorphisms}
-
-\begin{definition}[Kernel Pair]
-    A \emph{kernel pair} for an arrow $f: A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f : K_f \to A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the following square is a pullback.
-    \[
-        \begin{tikzcd}
-            K_f \ar[r, "{\pi^1_f}"] \ar[d, "{\pi^2_f}" swap] & A \arrow[d, "f"] \\
-            A \ar[r, "f"swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-\begin{remark}
-	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
-\end{remark}
-
-\begin{remark}
-    Since a kernel pair is nothing more that a pullback, that is, a limit, by \Cref{rem:limits_are_unique_up_to_isomorphisms}, it make sense to refer to it as \emph{the} kernel pair for a morphism $f$.
-\end{remark}
-
-\begin{example}\label{ex:kernel_pairs_in_Set}
-    In $\Set$, a kernel pair for a function $f: A\to B$ is the set
-    \[
-        K_f=\{(x, y) \in A \times A \mid f(x) = f(y)\}
-    \]
-    together with the canonical projection on the first and the second component of the pairs.
-\end{example}
-
-\begin{prop}\label{prop:pairng_of_kernel_pairs_mono}
-    Let $(K, p_1, p_2)$ be the kernel pair of $f: X \to Y$, and let $(X\times X, \pi_1, \pi_2)$ be the product of $X$ with itself.
-Then, the mediating arrow $\langle p_1, p_2\rangle : K \to X \times X$ is mono.
-\end{prop}
-
-\begin{proof}
-	Suppose $\langle p_1, p_2 \rangle \circ f = \langle p_1, p_2 \rangle \circ g$ for $f, g: Z \to K$. Then, we have
-	\[
-		\begin{split}
-			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
-			\pi_1 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_1 \circ \langle p_1, p_2 \rangle \circ g \\
-			p_1 \circ f &= p_1 \circ g
-		\end{split}
-		\qquad
-		\begin{split}
-			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
-			\pi_2 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_2 \circ \langle p_1, p_2 \rangle \circ g \\
-			p_2 \circ f &= p_2 \circ g
-		\end{split}
-	\]
-	Thus, from the universal property of the pullback, $f = g$.
-\end{proof}
-
-\begin{prop}\label{prop:kermono}
-	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
-\end{prop}
-
-\begin{proof}
-    To prove the ``if'' part of the statement, let $f, g: A \to M$ be such that $m\circ f = m\circ g$, and consider the following situation.
-    \[
-        \begin{tikzcd}[row sep=26, column sep = 26]
-        A \arrow[drr, bend left=30, "f"] \arrow[ddr, bend right=30,"g" swap] \arrow[dr, dashed, "u"] & & \\
-        & M  \arrow[d, "{id_M}"] \arrow[r, "{id_M}"] & M \arrow[d, "m"] \\
-        & M  \arrow[r, "m" swap] & X
-        \end{tikzcd}
-    \]
-    For the universal property of pullbacks, we have that $$f  =  id_M \circ u =  g$$
-    Hence, $m$ is mono.
-
-    Conversely, if $m$ is mono, then, we have that
-    \begin{align*}
-        m \circ f = m \circ g   &\Rightarrow    f = g \\
-                                &\Rightarrow    f \circ id_M = g\circ id_M
-    \end{align*}
-    Hence, $f$ is the unique arrow that makes the commutative square illustrated above a pushout.
-\end{proof}
-
-\begin{remark}\label{rem:monos_in_presh_cats}
-    From characterization of monos via pullbacks in \Cref{prop:kermono} and \Cref{lemma:limits_of_presheaves}, we have that a mono in a category of presheaves is a natural transformation of which each component is mono.
-\end{remark}
-
-\begin{cor}\label{cor:kermono}
-	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$ if and only if, for each mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
-\end{cor}
-\begin{proof}
-    It is enough to see that, by \Cref{lemma:pullback_lemma} and \Cref{prop:kermono} the outer boundary of the following square is a pullback.
-        \[\begin{tikzcd}[row sep=13 pt, column sep=13 pt]
-    	{K_f} && X && X \\
-    	\\
-    	X && Y && Y \\
-    	\\
-    	X && Y && Z
-    	\arrow["{\pi_f^2}", from=1-1, to=1-3]
-    	\arrow["{\pi_f^2}"', from=1-1, to=3-1]
-    	\arrow["{id_X}", from=1-3, to=1-5]
-    	\arrow["f", from=1-3, to=3-3]
-    	\arrow["f", from=1-5, to=3-5]
-    	\arrow["f", from=3-1, to=3-3]
-    	\arrow["{id_X}"', from=3-1, to=5-1]
-    	\arrow["{id_Y}", from=3-3, to=3-5]
-    	\arrow["{id_Y}", from=3-3, to=5-3]
-    	\arrow["m", from=3-5, to=5-5]
-    	\arrow["f"', from=5-1, to=5-3]
-    	\arrow["m"', from=5-3, to=5-5]
-    \end{tikzcd}\]
-    The leftward part of the statement follows by definition of monomorphism an \Cref{lemma:pullback_lemma}.
-\end{proof}
-
-\begin{lemma}\label{lemma:kern_pairs_pres_pullbacks}
-    Suppose the following situation, and that $f: X \to Y$ and $g: Z \to W$ have kernel pairs.
-    \[
-        \begin{tikzcd}
-            X \ar[r, "h"] \ar[d, "f"swap] & Z \ar[d, "g"] \\
-            Y \ar[r, "t"swap] & W
-        \end{tikzcd}
-    \]
-
-    Then, there exists a unique arrow $k_h: K_f \to K_g$ making the squares below commute.
-    \[
-        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
-            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^1}"swap] & K_g \ar[d, "{\pi_g^1}"] \\
-            X \ar[r, "h"swap] & Z 
-        \end{tikzcd}
-        \qquad
-        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
-            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^2}"swap] & K_g \ar[d, "{\pi_g^2}"] \\
-            X \ar[r, "h"swap] & Z 
-        \end{tikzcd}
-    \]
-
-    Moreover, if the beginning square is a pullback, then also the preceding ones are so.
-\end{lemma}
-
-\begin{proof}
-    Computing, we have
-    \begin{align*}
-        g \circ h \circ \pi_f^1 &=  t \circ f \circ \pi_f^1     \\
-                                &=  t \circ f \circ \pi_f^2     \\
-                                &=  g \circ h \circ \pi_f^2
-    \end{align*}
-    By the universal property of $K_g$ as the pullback of $g$ along itself, such $k_h$ exists and it is unique.
-
-    To prove the second half of the thesis, let us consider the two rectangles below, which, by \Cref{lemma:pullback_lemma} are pullbacks.
-    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
-	{K_f} & X & Z \\
-	X & Y & W
-	\arrow["{\pi_f^1}", from=1-1, to=1-2]
-	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
-	\arrow["h", from=1-2, to=1-3]
-	\arrow["f", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["f"', from=2-1, to=2-2]
-	\arrow["t"', from=2-2, to=2-3]
-    \end{tikzcd}
-    \qquad
-    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
-	{K_f} & X & Z \\
-	X & Y & W
-	\arrow["{\pi_f^2}", from=1-1, to=1-2]
-	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
-	\arrow["h", from=1-2, to=1-3]
-	\arrow["f", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["f"', from=2-1, to=2-2]
-	\arrow["t"', from=2-2, to=2-3]
-    \end{tikzcd}
-    \]
-    But then the following ones are pullbacks too.
-    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
-	{K_f} & {K_g} & Z \\
-	X & Y & W
-	\arrow["{k_h}"', from=1-1, to=1-2]
-	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
-	\arrow["{\pi_g^2}"', from=1-2, to=1-3]
-	\arrow["{\pi_g^1}", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["h", from=2-1, to=2-2]
-	\arrow["g", from=2-2, to=2-3]
-        \arrow["{h\circ \pi_f^2}", from=1-1, to=1-3, bend left = 30]
-        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
-    \end{tikzcd}
-    \qquad
-    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
-	{K_f} & {K_g} & Z \\
-	X & Y & W
-	\arrow["{k_h}"', from=1-1, to=1-2]
-	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
-	\arrow["{\pi_g^1}"', from=1-2, to=1-3]
-	\arrow["{\pi_g^2}", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["h", from=2-1, to=2-2]
-	\arrow["g", from=2-2, to=2-3]
-        \arrow["{h\circ \pi_f^1}", from=1-1, to=1-3, bend left = 30]
-        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
-    \end{tikzcd}
-    \]
-
-    The thesis follows again by \Cref{lemma:pullback_lemma}.
-\end{proof}
-
-\begin{prop}\label{prop:reg_epi_coeq}
-    Let $e: X \to Y$ be a regular epimorphism in a category $\cat C$ with a kernel pair $(K, \pi_1, \pi_2)$. Then, $e$ is the coequalizer of $\pi_1$ and $\pi_2$.
-\end{prop}
-
-\begin{proof}
-    By hypothesis, there exists a pair $f, g: Z \to X$ of which $e$ is the coequalizer. Since $e \circ f = e \circ g$, we have
-    \[
-        \begin{tikzcd}[row sep= 20, column sep = 13]
-            Z \ar[drr, "f", bend left=30] \ar[ddr, "g"swap, bend right=30] \ar[dr, dashed, "k"] & & \\
-            & K \ar[r, "{\pi_1}"] \ar[d, "{\pi_2}" swap] & X \ar[d, "e"] \\
-            & X \ar[r, "e"swap] & Y
-        \end{tikzcd}
-    \]
-    thus there exists the unique $k: Z \to K$. Let now $h: Z \to V$ be an arrow such that $h \circ \pi_1 = h \circ \pi_2$, then
-    \begin{align*}
-        h \circ f &= h \circ \pi_1 \circ k \\
-                  &= h \circ \pi_2 \circ k \\
-                  &= h \circ g
-    \end{align*}
-    and thus there exists a unique $l: Y \to V$ such that $l \circ e = h$.
-\end{proof}
-
-\begin{cor}\label{cor:reg_epi_components_reg_epi_nat_trans}
-    Let $\cat C$ be a category with pullbacks and $\phi : D \dot\to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
-If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
-\end{cor}
-
-\begin{proof}
-    Let $(K_i, \pi_i^1, \pi_i^2)$ be the kernel pair of $\phi_i$ for each $i$. Given an arrow $\alpha: i \to j$ of $\cat I$, we have
-    \begin{align*}
-        \phi_j \circ D(\alpha) \circ \pi_i^1 &= D'(\alpha) \circ \phi_i \circ \pi_i^1 \\
-                                             &= D'(\alpha) \circ \phi_i \circ \pi_i^2 \\
-                                             &= \phi_j \circ D(\alpha) \circ \pi_i^2
-    \end{align*}
-    Thus, the outer boundary of the diagram below commutes, yielding the arrow $K(\alpha)$
-    \[
-        \begin{tikzcd}[row sep=26, column sep=26]
-            {K_i} \ar[r, "{\pi_i^1}"] \ar[d, "{\pi_i^2}"swap] \ar[dr, dashed, "{K(\alpha)}"] & D(i) \ar[dr, "{D(\alpha)}"] \\
-            D(i) \ar[dr, "{D(\alpha)}"swap] & K_j \ar[r, "{\pi_j^1}"] \ar[d, "{\pi_j^2}"swap] & D(j) \ar[d, "{\phi_j}"] \\
-            & D(j) \ar[r, "{\phi_j}"swap] & D'(j)
-        \end{tikzcd}
-    \]
-
-    In this way, we get a functor $K: \cat{I \to C}$, 
-    which maps each $i$ onto $K_i$ and each arrow $\alpha$ onto $K(\alpha)$. 
-	We have in fact $K(id_i) : K_i \to K_i$ is the arrow such that
-        \[
-            \begin{split}
-                D(id_i) \circ \pi_i^1 &= \pi_i^1 \circ K(id_i) \\
-                \pi_i^1 &= \pi_i^1 \circ K(id_i)
-            \end{split}
-                \qquad
-            \begin{split}
-                D(id_i) \circ \pi_i^2 &= \pi_i^2 \circ K(id_i) \\
-                \pi_i^2 &= \pi_i^2 \circ K(id_i)
-            \end{split}
-        \]
-	Thus, for the universal property of pullbacks, $K(id_i) = id_{K_i}$.
-
-        Suppose now $\alpha : i \to j$ and $\beta: j \to k$. Computing, we have
-        \[
-            \begin{split}
-                \pi_k^1 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^1 \\
-                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^1 \\
-                                                    &= D(\beta) \circ \pi_j^1 \circ K(\alpha) \\
-                                                    &= \pi_k^1 \circ K(\beta) \circ K(\alpha)
-            \end{split} \qquad
-            \begin{split}
-                \pi_k^2 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^2 \\
-                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^2 \\
-                                                    &= D(\beta) \circ \pi_j^2 \circ K(\alpha) \\
-                                                    &= \pi_k^2 \circ K(\beta) \circ K(\alpha)
-            \end{split}
-        \]
-        Again, for universal property of pullbacks, necessarily we have $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving functoriality of $K$.
-
-     Hence, we have two natural transformations $\pi^1, \pi^2 : E \dot\to D$.
-By \Cref{prop:reg_epi_coeq}, every component $\phi_i$ is the coequalizer of $\pi_i^1, \pi_i^2: E \to D$, and so $\phi$ is the coequalizer of $\pi^1$ and $\pi^2$.
-\end{proof}
-
-\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
-    Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
-If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
-\end{lemma}
-
-\begin{proof}
-    By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi: D \dot\to D'$ is a regular epimorphism, so that there is a functor $E: \cat{I \to C}$ and $\eta, \theta: E \dot\to D$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
-Let now $((p_i)_{i \in \cat I}, P)$ be the colimit of $E$, by \Cref{prop:nat_tran_induces_unique_arrow_between_colimits}, we have $a, b: P \to C$ fitting in the diagram below.
-    \[
-        \begin{tikzcd}[row sep = 26, column sep = 26]
-            E(i) \ar[r, "{p_i}"] \ar[d, "{\eta_i}"swap] & P \ar[d, dashed, "a"] \\
-            D(i) \ar[r, "{c_i}"swap] & C
-        \end{tikzcd}
-        \qquad
-        \begin{tikzcd}[row sep = 26, column sep = 26]
-            E(i) \ar[r, "{p_i}"] \ar[d, "{\theta_i}"swap] & P \ar[d, dashed, "b"] \\
-            D(i) \ar[r, "{c_i}"swap] & C
-        \end{tikzcd}
-    \]
-
-    We want to show that $c$ coequalizes $\eta$ and $\theta$. Let thus $t: C \to T$ be an arrow such that $t \circ a = t \circ b$. Then, for every $i$, we have
-    \begin{align*}
-        t \circ c_i \circ \eta_i &= t \circ a \circ p_i \\
-                                 &= t \circ b \circ p_i \\
-                                 &= t \circ c_i \circ \theta_i
-    \end{align*}
-
-    Thus, there is $t_i: D(i) \to T$ such that $t\circ c_i = t_i \circ \phi_i$.
-It is now easy to see that $((t_i)_{i \in \cat I}, T)$ is a cocone of $D'$: suppose $\alpha: i \to j$ be an arrow of $\cat I$, obtaining
-    \begin{align*}
-        t_i \circ \phi_i &= t \circ c_i \\
-                         &= t \circ c_j \circ D(\alpha) \\
-                         &= t_j \circ \phi_j \circ D(\alpha) \\
-                         &= t_j \circ D'(\alpha) \circ \phi_i
-    \end{align*}
-    By the hypothesis that $\phi_i$ is regular epi for each $i$, therefore epi (by the dual of \Cref{prop:eq_are_mono}), we can conclude $t_i = t_j \circ D'(\alpha)$.
-
-    Hence, we have an arrow $k: C' \to T$ such that $k \circ c_i' = t_i$. But then
-    \begin{align*}
-        c \circ c \circ c_i &= k \circ c_i' \circ \phi_i \\
-                            &= t_i \circ \phi \\
-                            &= t \circ c_i
-    \end{align*}
-    Showing that $k \circ c = t$.
-
-    For the uniqueness, let $k': C' \to T$ be another arrow such that $k' \circ c = t$. Then we have
-    \begin{align*}
-        k' \circ c_i' \circ \phi_i &= k' \circ c \circ c_i \\
-                                   &= t \circ c_i \\
-                                   &= t_i \circ \phi_i
-    \end{align*}    
-    Since $\phi_i$ is a regular epimorphism, we have $k' \circ c_i' = t_i$, and, because $k \circ c_i' = t_i$ by construction, we can conclude that $k'=k$ since $((c_i')_{i \in \cat I}, C')$ is a colimit.
-\end{proof}

### 2024-11-20 Article/Appendix/Omitted_Proofs.tex
minima

--- 2024-10-20 Article/Appendix/Omitted_Proofs.tex
@@
 \chapter{Omitted Proofs}
+
+\paragraph{\Cref{lemma:pullback_lemma}.}
+    Suppose that the following diagram is given and its right half is a pullback. Then the whole rectangle is a pullback if and only if its left half is a pullback.
+    \[
+	    \begin{tikzcd}[row sep = 20, column sep = 20]
+            X \arrow[r, "f"] \arrow[d, "t"swap] & Y \arrow[r, "g"] \arrow[d, "k"] & Z \arrow[d, "h"] \\
+            A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+\begin{proof}
+    For the ``only if'' part, suppose the left square to be a pullback. To verify the outer rectangle is a pullback, consider the following situation:
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} & & \\
+            & & & Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    But the right square is a pullback implies that there exists a unique $u$ such that
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15, dashed]{drr}{u}& & \\
+            & &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    And, since the left square is a pullback, there exists a unique $v$ such that
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15]{drr}{u} \arrow[dr, "v", dashed]& & \\
+            & X \arrow[r, "f"] \arrow[d, "t"swap] &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    Hence, the whole rectangle is a pullback.
+
+    For the ``if'' part, consider the following situation.
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} & \\
+            & & Y \arrow[d, "k"] \\
+            & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    We have now to show that the unique arrow $v: P \to X$ (of the outer rectangle) is such that $f \circ v = p_1$, but this follows from the fact that the right square is a pullback, having the following situation.
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{g \circ p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15, dashed]{drr}{u}& & \\
+            & &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+\end{proof}
 

### 2024-11-20 Article/Background_sections/Basic_Notions.tex
minima

@@
     $$
-    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ (or, when it is clear from the context, just denoted $A$)  such that, for each $f: A \rightarrow B$:
+    For each object $A$, an \emph{identity} morphism $id_A : A \rightarrow A$ such that, for each $f: A \rightarrow B$
     \[
@@
 \end{remark}
+
+\begin{definition}[Subcategory]
+    A category $\cat{D}$ is a \emph{subcategory} of a category $\cat{C}$ if:
+    \begin{enumerate}
+        \item each object of $\cat{D}$ is an object of $\cat{C}$;
+        \item \label{inc} each morphism between two objects of $\cat{D}$ is a morphism of $\cat{C}$; and
+        \item \label{comp} composites and identities of $\cat{D}$ are the same of $\cat{C}$.
+    \end{enumerate}
+
+    If the inclusion at~\ref{inc} is an equality (i.e.
+$\cat{D}(A, B) = \cat{C}(A, B)$ for each couple of objects $A$, $B$ of $\cat{D}$), then $\cat{D}$ is said to be a \emph{full subcategory} of $\cat{C}$.
+    Another way to express that composites are the same (point~\ref{comp}) is to say that if $f, g \in \Hom(\cat D)$ are composable, then $g \circ f \in \Hom(\cat D)$, i.e., $\Hom(\cat D)$ is \emph{closed under composition}.
+\end{definition}
 
@@
 \end{proof}
-{\color{red}
+
 \begin{cor}\label{cor:unique}
@@
 	\end{split}\]
-	Hence, $h \circ k = id_X$, $k \circ h = id_Y$, obtaining the isomorphism.
+	Hence, iìsince $e$ and $e'$ are epimorphisms,  $h \circ k = id_X$, $k \circ h = id_Y$, obtaining the isomorphism.
 \end{proof}
-}
+
+\iffalse
+
 \subsection{Categories from other categories}\label{ssect:cats_from_cats}
@@
 \end{definition}
+\fi

### 2024-11-20 Article/Graph_sections/Eq_Graphs_integration.tex
minima

--- 2024-11-19 Article/Graph_sections/Eq_Graphs_integration.tex
@@
 \section{Graphs with Equivalences}\label{sect:eq_graphs}
+
+A (directed graph) $\graph{G}$ is a structure consisting of a set of edge, a set of nodes and two functions, one assigning a \emph{source} node and one assigning a \emph{target} node to an edge.
+Formally, $\graph{G}$ is a quadruple $(V_\graph{G}, E_\graph{G}, s_\graph{G}, t_\graph{G})$, where $V_\graph{G}$ is the set of nodes, $E_\graph{G}$ is the set of edges, and $s_\graph{G}, t_\graph{G}: E_\graph{G} \rightarrow V_\graph{G}$ are the source and the target functions.
+
+A \emph{graph homomorphism} $h: \graph{G \rightarrow H}$ is then a pair of functions $h = (h_V: V_\graph{G} \rightarrow V_\graph{H}, h_E: E_\graph{G} \rightarrow E_\graph{H})$ such that
+    \[
+        h_V \circ s_\graph{G} = s_\graph{H} \circ h_E
+    \]
+    and
+    \[
+        h_V \circ t_\graph{G} = t_\graph{H} \circ h_E
+    \]
+that is, a structure preserving map.
+
+We can then generalize such notion to something more abstract, considering a graph to be nothing more than a presheaf from the category $(E \rightrightarrows V)$ to the category of sets.
+Having two of such presheaves, a natural transformation from one to another encapsulates the behavior of a graph morphism due to naturality. We can now define the category of graphs.
+
+\begin{definition}[Category of Graphs]\label{def:cat_of_graph}
+    We denote as $\Graph$ the category $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
+\end{definition}
+
+Since $\Graph$ is a category of presheaves, \Cref{lemma:limits_of_presheaves} guarantees the existence of limits and colimits, and gives us an easy way to compute them.
+
+\begin{cor}\label{cor:graph_has_co_limits}
+    $\Graph$ has all limits and colimits.
+\end{cor}
+
 A graph with equivalence is a 6-tuple $\eqgraph{G} =  (E, V, C, s, t, q)$, where $E$ and $V$ are, respectively, the edges and the vertices sets, and $C$ is the set of the equivalence classes among vertices, $s,t : E \to V$ are the source and target functions and $q: V \to C$ is the \emph{quotient} function, that is, the map from a vertex to its equivalence class.
 For this definition to make sense, $q$ needs to be surjective.
-A morphisms $h$ from a graph with equivalence $\eqgraph{G} =  (E, V, C, s, t, q)$ to another $\eqgraph{H} = (E', V', C', s', t',  q')$ is a triple $h = (h_E, h_V, h_C)$ of functions $h_V : V \to V'$, $h_E : E \to E'$ and $h_C : C \to C'$ such that:
-\begin{itemize}
-    \item $h_E \circ s = s' \circ h_V$;
-    \item $h_E \circ t = t' \circ h_V$;
-    \item $h_C \circ q = q' \circ h_V$.
-\end{itemize}
+A morphisms $h$ from a graph with equivalence $\eqgraph{G} =  (E, V, C, s, t, q)$ to another $\eqgraph{H} = (E', V', C', s', t',  q')$ is a triple $h = (h_E, h_V, h_C)$ of functions $h_V : V \to V'$, $h_E : E \to E'$ and $h_C : C \to C'$ such that
+\[
+    h_E \circ s = s' \circ h_V \qquad h_E \circ t = t' \circ h_V'\qquad h_C \circ q = q' \circ h_V
+\]
 
@@
 
-As we have done in \Cref{sect:graphs}, we can think to a graph with equivalence as a presheaf, this time from a category $E \rightrightarrows V \rightarrow C$, where the image of $C$ along the presheaf is the set of the equivalence classes, requiring that the morphism $V\rightarrow C$ is an epimorphism (that is, a surjective function).
+As we have done for graphs, we can think to a graph with equivalence as a presheaf, this time from a category $E \rightrightarrows V \rightarrow C$, where the image of $C$ along the presheaf is the set of the equivalence classes, requiring that the morphism $V\rightarrow C$ is an epimorphism (that is, a surjective function).
 
@@
 \begin{obs}\label{obs:eq_grph_morph_det_by_first_two_comp}
-    Morphisms of graphs with equivalences are uniquely determined by the first two component. That is, if $h_1 = (h_E, h_V, \phi)$ and $h_2 = (h_E, h_V, \psi)$, then $\phi = \psi$.
-\end{obs}
-
-\begin{proof}
-    Let $h_1, h_2 : \eqgraph{G \to H}$, where $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$. Then, we have the following situation
+    Morphisms of graphs with equivalences are uniquely determined by the first two components.
+That is, if $h_1 = (h_E, h_V, \phi)$ and $h_2 = (h_E, h_V, \psi)$, then $\phi = \psi$.
+Indeed, consider two arrows $h_1, h_2 : \eqgraph{G \to H}$, where $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$.
+Then, we have the following situation
     \[
@@
      From the fact that $q_G$ is epi, we can conclude $\phi = \psi$.
-\end{proof}
+\end{obs}
 
@@
 \begin{cor}\label{cor:mono_in_EqGrph}
-    An arrow $h = (h_E, h_V, h_C): \eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G) \to \eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ in $\EqGrph$ is mono if and only if $h_E$ and $h_V$ are mono in $\Set$.
+    Let $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ be two graphs with equivalences.
+Then, an arrow $h = (h_E, h_V, h_C): \eqgraph{G} \to \eqgraph{H}$ in $\EqGrph$ is mono if and only if $h_E$ and $h_V$ are mono in $\Set$.
 \end{cor}
@@
 Since a morphism in a category of presheaves is mono if and only if it is injective on each component, we have that, if  $U(h)$ is mono, that is, $h_E$ and $h_V$ are injective in $\Set$, then $h$ is mono.
-    For the ``only if'' part, suppose $f = (f_E, f_V, f_C)$, $g=(g_E, g_V, g_C)$, $f, g : \eqgraph{H \to K}$ be such that $h \circ f = h \circ g$. Then, we have
+	For the ``only if'' part, suppose $f = (f_E, f_V, f_C)$, $g=(g_E, g_V, g_C)$, $f, g : \eqgraph{H \to K}$, where $\eqgraph{K} = (E_K, V_K, C_K, s_K, t_K, q_K)$, be such that $h \circ f = h \circ g$.
+Then, we have
     \begin{align*}
         h \circ f   &= (h_E \circ f_E, h_V \circ f_V, h_C \circ f_C) \\
-                    &= (h_E \circ f_E, h_V \circ f_V, h_V \circ f_V \circ \eqgraph{K}(q)) \\
-                    &= (h_E \circ g_E, h_V \circ g_V, h_V \circ g_V \circ \eqgraph{K}(q))
+                    &= (h_E \circ f_E, h_V \circ f_V, h_V \circ f_V \circ q_K) \\
+                    &= (h_E \circ g_E, h_V \circ g_V, h_V \circ g_V \circ q_K)
     \end{align*}    
-    Since $\eqgraph{K}(q)$ is epi, we have, on the third component, that $h_V \circ f_V \circ \eqgraph{K}(q) = h_V \circ g_V \circ \eqgraph{K}(q))$ implies $f_C = g_C$, and hence $f = g$    
+    Since $q_K$ is epi, we have, on the third component, that $h_V \circ f_V \circ q_K = h_V \circ g_V \circ q_K$ implies $f_C = g_C$, and hence $f = g$    
 \end{proof}
 
-\begin{cor}\label{cor:regmono}Let $ h = (h_E, h_V, h_C): \eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G) \to \eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ be a morphism of $\EqGrph$, then the following are equivalent:
+\begin{cor}\label{cor:regmono}Let $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ be two graphs with equivalences, and let $ h = (h_E, h_V, h_C): \eqgraph{G}\to \eqgraph{H} $ be a morphism of $\EqGrph$, then the following are equivalent:
 	\begin{enumerate}
@@
 	$1\Rightarrow 2.$ If $h$ is mono, from \Cref{cor:mono_in_EqGrph} we have that $h_E$ and $h_V$ are monos.
-To derive $h_C$ mono, suppose $f, g :  \eqgraph{H \to K}$ to be the arrows equalized by $h$.
+To derive $h_C$ mono, suppose $f, g :  \eqgraph{H \to K}$, where $\eqgraph{K} = (E_K, V_K, C_K, s_K, t_K, q_K)$to be the arrows equalized by $h$.
 Then we have
     \begin{align*}
-        f_C \circ h_C \circ \eqgraph{G}(q)  &=  f_C \circ \eqgraph{H}(q) \circ h_V \\
-                                            &=  \eqgraph{K}(q) \circ f_V \circ h_V \\
-                                            &=  \eqgraph{K}(q) \circ g_V \circ h_V \\
-                                            &=  g_C \circ h_C \circ \eqgraph{G}(q)
+        f_C \circ h_C \circ q_G  &=  f_C \circ q_H \circ h_V \\
+                                            &=  q_K \circ f_V \circ h_V \\
+                                            &=  q_K \circ g_V \circ h_V \\
+                                            &=  g_C \circ h_C \circ q_G
     \end{align*}
-    since $\eqgraph{G}(q)$ is epi, we have that $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, thus a monomorphism.
+    since $q_G$ is epi, we have that $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, thus a monomorphism.
 
@@
 \begin{definition}
-The \emph{quotient functor} $Q:\EqGrph\to \Graph $ sends $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $(E_G, C_G, q_G\circ s_G, q_G\circ t_G)$ and an arrow $(h_E, h_V, h_C) \colon (E_G, V_G, C_G, s_G, t_G, q_G)\to (E_H, V_H, C_H, s_H, t_H, q_H)$ to $(h_E, h_C)$.
+The \emph{quotient functor} $Q:\EqGrph\to \Graph $ is defined as the one sending $(E_G, V_G, C_G, s_G, t_G, q_G)$ to $(E_G, C_G, q_G\circ s_G, q_G\circ t_G)$ and an arrow $(h_E, h_V, h_C) \colon (E_G, V_G, C_G, s_G, t_G, q_G)\to (E_H, V_H, C_H, s_H, t_H, q_H)$ to $(h_E, h_C)$.
 \end{definition}
@@
 
-{\color{red}
 \begin{prop}\label{prop:quot_creat_colims}
@@
 \end{proof}
-
-}
 

### 2024-11-21 Article/Background_sections/Adhesivity.tex

@@
 
-	We have then that the top face is a pullback, and by \Cref{prop:kermono}, the left face is a pullback.
+	We have then that the top face is a pushout, and by \Cref{prop:kermono}, the left face is a pullback.
 Since the bottom face is a pushout by hypothesis, we have that the front face and the right one are pullbacks (by adhesivity).
-Hence, we can conclude that the starting square (which is the front and the bottom face of the cube) is a pushout, and by \Cref{prop:kermono}, since the left face is a pullback, $n$ is mono.
-
+Hence, if $\cat C$ is adhesive, we can conclude that the starting square (which is the front and the bottom face of the cube) is a pushout, and by \Cref{prop:kermono}, since the left face is a pullback, $n$ is mono.
+If $\cat C$ is $\mathcal M$-adhesive, with $m \in \mathcal{M}$ (that is, the square is a $\mathcal{M}$-pushout), $n \in \mathcal M$, and the vertical arrows then in $\mathcal{M}$.
+Hence, the front face is a pullback.
+\iffalse
 	Suppose now that $\cat C$ is $\mathcal{M}$-adhesive, and let the following square be a $\mathcal{M}$-pushout, so $m, n \in \mathcal{M}$.
@@
 	\end{tikzcd}\]
-	By the same argument as before, we can conclude that the starting square is a pullback.
+	By the same argument as before, we can conclude that the starting square is a pullback.\fi
 \end{proof}
@@
     Let $\cat A$ be a $\mathcal M$-adhesive category for some $\mathcal M \subseteq \Hom(\cat A)$.
-Then, if $\cat C$ is a category whith all the pullbacks, the functor category $[\cat C, \cat A]$ is $\mathcal M^{\cat C}$-adhesive, where
+Then, if $\cat A$ is a category whith all the pullbacks, the functor category $[\cat C, \cat A]$ is $\mathcal M^{\cat C}$-adhesive, where
     \[
@@
 \end{proof}
-
-\begin{lemma}\label{lemma:pushouts_kernel_pairs}
-    Let $\cat C$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that the cube below is given, in which every face is a pullback and the bottom one is a $\mathcal{M}$-pushout.
-        \[\begin{tikzcd}[row sep=25, column sep=25]
-	& {A'} && {B'} \\
-	{C'} && {D'} \\
-	& A && B \\
-	C && D
-	\arrow["{f'}", from=1-2, to=1-4]
-	\arrow["{m'}"', from=1-2, to=2-1]
-	\arrow["a"'{pos=0.7}, from=1-2, to=3-2]
-	\arrow["{n'}"', from=1-4, to=2-3]
-	\arrow["b", from=1-4, to=3-4]
-	\arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
-	\arrow["c"', from=2-1, to=4-1]
-	\arrow["f"'{pos=0.3}, from=3-2, to=3-4]
-	\arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
-	\arrow["m", from=3-2, to=4-1]
-	\arrow["n", from=3-4, to=4-3]
-	\arrow["g"', from=4-1, to=4-3]
-    \end{tikzcd}\]
-
-    Then, the square below is a pushout.
-    \[
-        \begin{tikzcd}%[row sep=25, column sep=25]
-            {K_a} \ar[r, "{k_{f'}}"] \ar[d, "{k_{m'}}"'] & {K_b} \ar[d, "{k_{n'}}"] \\
-            {K_c} \ar[r, "{k_{g'}}"'] & {K_d}
-        \end{tikzcd}
-    \]
-\end{lemma}
-
-\begin{proof}
-    By \Cref{lemma:kern_pairs_pres_pullbacks}, in the following cube the vertical faces are pullbacks.
-    \[\begin{tikzcd}[row sep = 20, column sep = 20]
-        & {K_a} && {K_b} \\
-        {K_c} && {K_d} \\
-        & {A'} && {B'} \\
-        {C'} && {D'}
-        \arrow["{k_{f'}}", from=1-2, to=1-4]
-        \arrow["{k_{m'}}"', from=1-2, to=2-1]
-        \arrow["{\pi_a^1}"{pos=0.7}, from=1-2, to=3-2]
-        \arrow["{k_{n'}}", from=1-4, to=2-3]
-        \arrow["{\pi_b^1}", from=1-4, to=3-4]
-        \arrow["{k_{g'}}"{pos=0.7}, from=2-1, to=2-3, crossing over]
-        \arrow["{\pi_c^1}"', from=2-1, to=4-1]
-        \arrow["{f'}"'{pos=0.3}, from=3-2, to=3-4]
-        \arrow["{\pi_d^1}"{pos=0.7}, from=2-3, to=4-3, crossing over]
-        \arrow["{m'}", from=3-2, to=4-1]
-        \arrow["{n'}", from=3-4, to=4-3]
-        \arrow["{g'}"', from=4-1, to=4-3]
-    \end{tikzcd}\]
-
-	$f'$ is in $\mathcal{M}$ as it is the pullback of $\mathcal{M}$, thus the bottom face of the cube is a Van Kampen pushout and the thesis follows.
-
-\end{proof}

### 2024-11-21 Article/Background_sections/Limit.tex

@@
 
+\begin{prop}\label{prop:nat_tran_induces_unique_arrow_between_colimits}
+    Let $D, D': \cat{I \to C}$ be two functors, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
+Then, a natural transformation $\phi: D \dot\to D'$ induces a unique arrow $c: C \to C'$.
+\end{prop}
+
+\begin{proof}
+    Consider the following situation.
+    \[\begin{tikzcd}[row sep=26 pt, column sep= 13 pt]
+        & C & \\
+        D(i) \ar[ur, "{c_i}"] \ar[d, "{\phi_i}"swap] \ar[rr, "{D(\alpha)}"]&& D(j) \ar[ul, "{c_j}"swap] \ar[d, "{\phi_j}"] \\
+        D'(i) \ar[dr, "{c_i'}" swap] \ar[rr, "{D'(\alpha)}" swap] && D'(j) \ar[dl, "{c_j'}"] \\
+        & C' &
+    \end{tikzcd}\]
+
+    To prove the statement, we note that $((c_i' \circ \phi_i)_{i \in \cat I}, C')$ is a cocone for $D$. Computing, we have, for each $i$, $j$ and $\alpha: i \to j$
+    \begin{align*}
+        c_j' \circ \phi_j \circ D(\alpha)   
+                        &=  c_j' \circ D'(\alpha) \circ \phi_i  &&\textit{Naturality of $\phi$}\\
+                        &=  c_i' \circ \phi_i                   &&\textit{$((c_i')_{i\in \cat I}, C')$ is a colimit for $D'$}
+    \end{align*}
+
+    Since $((c_i')_{i \in \cat I}, C)$ is a colimit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
+\end{proof}
 Notion such limits and colimits are generalization of more particular cases that will be now introduced, that we will often call \emph{universal constructions}.
@@
 
-\begin{prop}
+\iffalse\begin{prop}
     Let $\cat D$ be a category.
@@
     Hence, $\theta$ is the unique natural transformation from $F$ to $T$, and $T$ is the terminal object of $[\cat{C, D}]$.
-\end{proof}
+\end{proof}\fi
 
@@
 \begin{lemma}\label{lemma:limits_of_presheaves}
-    Let $\cat C$ be a category, and let $[\cat C, \Set]$ be the category of presheaves on $\cat C$.
-Let $D: \cat I \to [\cat C, \Set]$ be a diagram of shape $\cat I$ on the presheaves category early mentioned.
+    Let $\cat C, \cat D$ be a categories, and let $[\cat C, \cat D]$ be the category of functors from $\cat C$ to $\cat D$.
+Let $D: \cat I \to [\cat C, \cat D]$ be a diagram of shape $\cat I$ on the functor category early mentioned.
 Then,
     \begin{enumerate}
-        \item The limit of $D$ exists, and it is the presheaf $L: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $L(A)$ is the limit in $\Set$ of the values of the presheaves $D(i)(A)$ for each $i$.
-        \item The colimit of $D$ exists, and it is the presheaf $C: \cat C \to \Set$ such that, for each object $A$ of $\cat C$, $C(A)$ is the colimit in $\Set$ of the values of the presheaves $D(i)(A)$, for each $i$.
+        \item The limit of $D$ exists, and it is the functor $L: \cat C \to \cat D$ such that, for each object $A$ of $\cat C$, $L(A)$ is the limit in $\cat D$ of the values of the functors $D(i)(A)$ for each $i$.
+        \item The colimit of $D$ exists, and it is the functor $C: \cat C \to \cat D$ such that, for each object $A$ of $\cat C$, $C(A)$ is the colimit in $\cat D$ of the values of the functors $D(i)(A)$, for each $i$.
     \end{enumerate}
@@
 
+\begin{prop}\label{prop:inc_creat}
+	Let $\cat D$ be a full subcategory of a category $\cat C$, $D: \cat{I \to D}$ be a diagram and $I: \cat{D \to C}$ be the inclusion functor.
+Then, if $(L, (l_i)_{i \in \cat I})$ is the limit of $I \circ D$, and $L$ is an object of $\cat D$ for each diagram $D$, then the inclusion functor creates limits.
+\end{prop}
+
 The next theorem is about a particular property that adjoint functors have.
@@
 \end{remark}
-
-\begin{prop}\label{prop:nat_tran_induces_unique_arrow_between_colimits}
-    Let $D, D': \cat{I \to C}$ be two functors, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
-Then, a natural transformation $\phi: D \dot\to D'$ induces a unique arrow $c: C \to C'$.
-\end{prop}
-
-\begin{proof}
-    Consider the following situation.
-    \[\begin{tikzcd}[row sep=26 pt, column sep= 13 pt]
-        & C & \\
-        D(i) \ar[ur, "{c_i}"] \ar[d, "{\phi_i}"swap] \ar[rr, "{D(\alpha)}"]&& D(j) \ar[ul, "{c_j}"swap] \ar[d, "{\phi_j}"] \\
-        D'(i) \ar[dr, "{c_i'}" swap] \ar[rr, "{D'(\alpha)}" swap] && D'(j) \ar[dl, "{c_j'}"] \\
-        & C' &
-    \end{tikzcd}\]
-
-    To prove the statement, we note that $((c_i' \circ \phi_i)_{i \in \cat I}, C')$ is a cocone for $D$. Computing, we have, for each $i$, $j$ and $\alpha: i \to j$
-    \begin{align*}
-        c_j' \circ \phi_j \circ D(\alpha)   
-                        &=  c_j' \circ D'(\alpha) \circ \phi_i  &&\textit{Naturality of $\phi$}\\
-                        &=  c_i' \circ \phi_i                   &&\textit{$((c_i')_{i\in \cat I}, C')$ is a colimit for $D'$}
-    \end{align*}
-
-    Since $((c_i')_{i \in \cat I}, C)$ is a colimit by hypothesis, then must exists a unique arrow $c:C \to C'$ such that $c \circ c_i = \phi_i \circ c_i'$, having the thesis.
-\end{proof}
 

### 2024-11-21 Article/Graph_sections/EGGs.tex

@@
 \begin{definition}[Category of E-Graphs]\label{def:cat_of_eggs}
-	$\EGG$ is the subcategory of $\EqGrph$ in which objects are e-graphs, and, given two e-graphs $\eqgraph{G, H}$, $\EGG(\eqgraph{G, H}) = \EqGrph(\eqgraph{G, H})$.
+	$\EGG$ is the full subcategory of $\EqGrph$ in which objects are e-graphs. %and, given two e-graphs $\eqgraph{G, H}$, $\EGG(\eqgraph{G, H}) = \EqGrph(\eqgraph{G, H})$.
 \end{definition}
@@
 
+By the previous results, we can deduce what follows from \Cref{prop:inc_creat}.
+
 \begin{cor}\label{cor:I_creates_limits}
@@
 \begin{cor}\label{cor:reg_mono_EGG}
-	$h: \eqgraph{G \to H}$ is a regular mono in $EGG$ if and only if it is a regular mono in $\EqGrph$.
+	$h: \eqgraph{G \to H}$ is a regular mono in $\EGG$ if and only if it is a regular mono in $\EqGrph$.
 \end{cor}
@@
 \begin{lemma}\label{lem:I_pres_pushouts_of_monos}
-	$I$ preserves pushouts along regular monomorphisms.	
+	Let $\eqgraph{G}_1 = (A_1, B_1, C_1, s_1, t_1, q_1)$, $\eqgraph{G}_2 = (A_2, B_2, C_2, s_2, t_2, q_2)$ and $\eqgraph{G}_3 = (A_3, B_3, C_3, s_3, t_3, q_3)$ be e-graphs,  $h: \eqgraph{G}_1 \to \eqgraph{G}_2$ and $m: \eqgraph{G}_1 \to \eqgraph{G}_3$ be two morphisms with $m$ mono.
+Then, the pushout of $h$ and $m$ is again an e-graph.
 \end{lemma}
@@
 \begin{proof}
-	Let $\eqgraph{G}_1 = (A_1, B_1, C_1, s_1, t_1, q_1)$, $\eqgraph{G}_2 = (A_2, B_2, C_2, s_2, t_2, q_2)$ and $\eqgraph{G}_3 = (A_3, B_3, C_3, s_3, t_3, q_3)$ be e-graphs,  $h: \eqgraph{G}_1 \to \eqgraph{G}_2$ and $m: \eqgraph{G}_1 \to \eqgraph{G}_3$ be two morphisms with $m$ mono.
-Let now $\eqgraph{P} = (A, B, C, s, t, q)$, together with $k: \eqgraph{G}_3 \to \eqgraph{P}$ and $n: \eqgraph{G}_2 \to \eqgraph{P}$, the pushout of $h$ and $m$.
+	Let $\eqgraph{P} = (A, B, C, s, t, q)$, together with $k: \eqgraph{G}_3 \to \eqgraph{P}$ and $n: \eqgraph{G}_2 \to \eqgraph{P}$, the pushout of $h$ and $m$.
 	Let $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i\circ s_i$, for $i = 1, 2, 3$, and let $(U, u_1, u_2)$ be the kernel pair of $q \circ s$.
@@
 	\]
-	By universal property of pushouts, there must exists a unque arrow $v: U \to C$ such that 
-	\[\begin{split}v \circ f_n &= q \circ t \circ u_1 \circ f_n\\v\circ f_n  &= q \circ t \circ u_2 \circ f_n \end{split}\qquad\begin{split}v \circ f_k &= q \circ t \circ u_1 \circ f_k\\v \circ f_k &= q \circ t \circ u_2 \circ f_k\end{split}\]
-		 hence, we deduce $q \circ t \circ u_1 = q \circ t \circ u_2$, and the thesis follows.
+	By universal property of pushouts, we deduce $q \circ t \circ u_1 = q \circ t \circ u_2$, and the thesis follows.
 \end{proof}

### 2024-11-21 Article/Conclusions.tex
Intro, Conc

\chapter*{Conclusions}
\addcontentsline{toc}{chapter}{Conclusions}

The result we ended up with is then $\Reg(\EGG))$-adhesivity, where $\EGG$ is a category of functors which have $\Set$ as codomain category.
The main question is now, is it strictly necessary to have $\Set$ as codomain of this functors? The entire work is developed in a more general perspective, using the least possible concept directly connected with set theory, using instead categorial constructions. The property of $\Set$ we have made large use of is the equivalence between quotient and product subobjects, which holds in exact categories.
Hence, this work can be viewed as a starting point to a more general study on e-graphs, in which edges, nodes and equivalence classes can be not only sets but objects of any exact category.

### 2024-11-21 Article/introduction.tex

@@
 \chapter*{Introduction}
+\addcontentsline{toc}{chapter}{Introduction}
+
+\iffalse
 
@@
 The last part is about e-graphs, that are nothing but graphs with a certain type of equivalence relation, inheriting then almost all the properties of the category of graphs with equivalences.
+
+Graphs arise almost everywhere in computer science, due to their capability of abstraction of real world situations and their simplicity.
+In concurrency theory, for example, system states are represented in a strightformward way using such structures, allowing representation of states and transitions, (e.g., Petri Nets), but also providing methods to model parallelism.
+...
+Examples of this can be foud in {\color{red} Concur2006, Left-Linear rules in Adh cats}.
+
+A formal definition of e-graphs, using category theory, allows us to analize certain adhesivity properties of this structure, in order to integrate it in a more general reseach line regarding concurrent rewriting systems.
+The main standard for rewriting systems, nowadays, is the DPO approach,
+
+\fi
+
+The developlment of equality graphs (e-graphs) is to be brought back to the eighties, in the context of automatic theorem provers (ATPs).
+E-Graphs are then an extension of prior structures, in order to represemt in a more compact way equivalence classes of expressions mantaining closure-under-congruence invariant.
+One of the aims of this work is to present a more theoretic representation of e-graphs than the one at the state of the art presented in \cite{egg}, using category theory formalism, in order to integrate the existence of such structure in a research line concerning concurrency of rewrinig-based formalisms.
+Indeed, graph-like structures turned out to be very advantageous for distributed system respresentation.
+An example of this fact could be a graph as the abstraction a set of entities and relations between them within a state, while rewriting steps model computation steps that, modifying the graph result in changes of the state of the system.
+A standard approach for this is the DPO (double pushout) approach, due to its flexibility and locality properties.
+A presentation of e-graphs as the one in this work allows to move beyond the operational representation via data structures, in favour of a formalization that model the changes of the structure too.
+In this setup, adhesivity results permit to make use of all the advantages on DPO rewriting, because of the generality of such framework.
+The elegance of such formalism lies on the definition itself of adhesive categories, namely categories where is reqired of the existence of pullbacks and pushouts along (some) monomorphisms, which are additionally required to be Van Kampen (that is, stability of pushouts under pullbacks and stability of pullbacks under combined pushouts and pullbacks \cite{Ehrig_Golas}).
+The only downside of such formalism is the difficulty of proofs using the definition.
+For cerain calasses of caeogries, there exists a charaterization of such property, presented in \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
+
+%Category theory provides uniform proofs and constructions across a wide range
+%of models. The usual approach is to find a natural class of categories with the right
+%structure to support the range of constructions particular to the application area.
+
+In order to work with e-graphs, some considreration on graphs with equivalences are in order to be done.
+A graph with equivalence is nothing but a graph endowed with an equivalence relation among its nodes.
+The main result on this kind of graphs is a weak adhesivity property that holds for particular monomorphisms.
+Then, such result is inherited by e-graphs, which are graphs with equivalence with additional requirements that can be intuitively summarized as \textit{the property of edges to have equivalent sources whenever targets are equivalent}.
+
+Then, the structure of this work is the following.
+The first chapter is about basic concepts of category theory, such as categories, limits, constructions and adhesivity, that will be used to model the categories on which in the second chapter we will work on.
+The prinicpal aim is to build up the categorial toolbox to work with.
+Category theory provides a general and uniform formalism, hence almost all definitions may seem very abstract, hence some concrete examples will be done.
+The second chapter is entirely focused on graphs, starting from a general notion of graphs, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, source and target, which assign to each edge a source vertex and a target one.
+The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization of them but also makes in evidence particular properties proper of graphs.
+Then, we endow graphs with an equivalence relation among verices, to end up with an adhesivity result.
+The last part is about e-graphs, and in particular their formalization and how they inherit certain properties from graphs with equivalences.

### 2024-11-22 Article/introduction.tex
minima

@@
 In this setup, adhesivity results permit to make use of all the advantages on DPO rewriting, because of the generality of such framework.
-The elegance of such formalism lies on the definition itself of adhesive categories, namely categories where is reqired of the existence of pullbacks and pushouts along (some) monomorphisms, which are additionally required to be Van Kampen (that is, stability of pushouts under pullbacks and stability of pullbacks under combined pushouts and pullbacks \cite{Ehrig_Golas}).
+The elegance of such formalism lies on the definition itself of adhesive categories, namely categories where it is guaranteed the existence of pullbacks and pushouts along (some) monomorphisms, which are additionally required to be Van Kampen (that is, stability of pushouts under pullbacks and stability of pullbacks under combined pushouts and pullbacks \cite{Ehrig_Golas}).
 The only downside of such formalism is the difficulty of proofs using the definition.

### 2024-11-22 Article/introduction.tex
scaletta intro

--- 2024-11-21 Article/introduction.tex
@@
 \fi
+
+I contenuti dell'introduzione vanno bene, ma li riaggiusterei leggermente, in modo da dare anche un po' di contesto.
+
+\begin{itemize}
+\item i formalismi visuali hanno una lunga tradizione e stanno avendo una rinascita di interesse, data anche la complessita dei sistemi software e hardware attuali
+\item la manipolazione di grafi ha un fine fra le altre cose quello di ottimizzare i sistemi o di permetterne l'upgrade di componenti
+\item servono basi formali solide, per poter parlare ad esempio di parallelismo e concorrenza
+\item le categorie adesive e il DPO sono diventate il formalismo d'eccezione per questo tipo di considerazioni
+\item fra i vari formalismi grafici, gli e-graph, utilizzati per xxx, stanno riscuotendo successo grazie alle implementazioni efficienti, ma manca ancora un theoretical underpinning
+\item qualche fa la tesi e' mostrare come anche gli e-graphs ricadano nel paradigma adesive+DPO
+\end{itemize}
 

### 2024-11-22 Article/Conclusions.tex
scaletta conclusioni

@@
 \addcontentsline{toc}{chapter}{Conclusions}
+
+In questo caso, una introduzione meno brusca, ricapitolando un po' la struttura e soprattutto il fine della tesi
+
+\begin{itemize}
+\item la tesi ha investigato le proprieta' di adesivita' di egss, ottenendo che ...
+\item questo e' interessante perche' permette di sfruttare il formalismo. Ad esempio, per parlare di update concorrenti, al momento non considerati per eggs
+\item i conti sono stati fatti su Set, ma senza sfruttare l;e proprieta' della categoria. Questo permettera' strutture piu' generali come term graphs, grafi gerarchici etc
+\item altri modelli fromali di9 eggs non nen conosciamo, ma alemno con quello di Gjuica faremo un confronto, anche se e' molto piu' copmplesso del nostro.
+\end{itemize}
 

### 2024-11-22 Article/Conclusions.tex
minima

@@
 
+\iffalse
 In questo caso, una introduzione meno brusca, ricapitolando un po' la struttura e soprattutto il fine della tesi
@@
 Hence, this work can be viewed as a starting point to a more general study on e-graphs, in which edges, nodes and equivalence classes can be not only sets but objects of any exact category.
+\fi
+
+Retracing the work, we have defined graphs with equivalence and e-graphs in a more abstract way, untied from potential implementations, in order to analyze formal properties of this kind of structures.
+
+Then, based upon this framework, we proved adhesive properties of graphs with equivalences and e-graphs, obtaining an interesting result of adhesivity
+(both of theses structure are adhesive with respect to the class of their regular monomorphisms)
+useful for a potential exploiting in state-of-the-art techniques, such as the DPO approach for concurrent updates to the structure, currently not explored yet.
+
+Both graphs with equivalence and e-graphs are considered in this work as functors with $\Set$ as codomain category.
+One may ask then, is it strictly necessary to have $\Set$ as codomain of this functors?
+The entire work is developed in a more general perspective, using the least possible concept directly connected with set theory, using instead categorial construction, and requiring only $\mathcal{M}$-adhesivity and exactness (this last concept is quite implicit in $\Set$, hence is not explicitly mentioned, but is, intuitively, the one that permitted the equivalence noted in \Cref{rem:eqgrph_set_eq}).
+Hence, a future work will be a more general presentation of this structures, substituting $\Set$ with any category with this properties.

### 2024-11-22 Article/Graph_sections/Eq_Graphs_integration.tex
minima

@@
 
-\begin{remark}
+\begin{remark}\label{rem:eqgrph_set_eq}
      A graph with equivalence can be viewed as a graph endowed with an equivalence relation over its set of vertices, $(\graph G, \sim_\graph{G})$.
@@
 
-\begin{cor}\label{cor:regmono}Let $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ be two graphs with equivalences, and let $ h = (h_E, h_V, h_C): \eqgraph{G}\to \eqgraph{H} $ be a morphism of $\EqGrph$, then the following are equivalent:
-	\begin{enumerate}
-		\item $h$ is a regular mono;
-		\item $h_E$, $h_V$, $h_C$ are all monos;
-%		\item $h_E$ and $h_V$ are mono and for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$.
-            \item $h_E$ and $h_V$ are mono and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_H \circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_G$.
-	\end{enumerate}
+\begin{cor}\label{cor:regmono}
+	Let $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ be two graphs with equivalences,
+	and let $ h = (h_E, h_V, h_C): \eqgraph{G}\to \eqgraph{H} $ be a regular monomorphism of $\EqGrph$, then $h_E$, $h_V$, $h_C$ are all monos.
 \end{cor}
 \begin{proof}
-	$1\Rightarrow 2.$ If $h$ is mono, from \Cref{cor:mono_in_EqGrph} we have that $h_E$ and $h_V$ are monos.
+	If $h$ is mono, from \Cref{cor:mono_in_EqGrph} we have that $h_E$ and $h_V$ are monos.
 To derive $h_C$ mono, suppose $f, g :  \eqgraph{H \to K}$, where $\eqgraph{K} = (E_K, V_K, C_K, s_K, t_K, q_K)$to be the arrows equalized by $h$.
@@
     since $q_G$ is epi, we have that $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, thus a monomorphism.
+	\iffalse
 
@@
 mono} \color{black}
+	\fi
+\end{proof}
+
+\begin{prop}
+	Let $\eqgraph{G} = (E_G, V_G, C_G, s_G, t_G, q_G)$ and $\eqgraph{H} = (E_H, V_H, C_H, s_H, t_H, q_H)$ be two graphs with equivalences,
+	and let $ h = (h_E, h_V, h_C): \eqgraph{G}\to \eqgraph{H} $ be a regular monomorphism of $\EqGrph$.
+Then, $h_E$ and $h_V$ are mono and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_H \circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_G$.
+\end{prop}
+
+\begin{proof}
+	By \Cref{cor:regmono}, we have that $h_E$, $h_V$ and $h_E$ are all monos.
+Hence, by \Cref{cor:kermono}, $(K, \pi_1, \pi_2)$ is the kernel pair of $q_G$ if and only if it is the kernel pair also of $h_C \circ q_G$, since $h_C$ is mono by hypothesis.
+The thesis follows from $h_C \circ q_G = q_H \circ h_V$, and from the hypothesis of $h_E$ mono.
+
 \end{proof}
@@
 \begin{remark}
-    It is possible to restate the third point of the \Cref{cor:regmono}, by \Cref{ex:kernel_pairs_in_Set}, as 
+    It is possible to restate the last proposition, by \Cref{ex:kernel_pairs_in_Set}, as 
     \begin{displayquote}

### 2024-11-22 Article/introduction.tex
minima

@@
 
-\fi
+%\fi
 
@@
 
-The developlment of equality graphs (e-graphs) is to be brought back to the eighties, in the context of automatic theorem provers (ATPs).
-E-Graphs are then an extension of prior structures, in order to represemt in a more compact way equivalence classes of expressions mantaining closure-under-congruence invariant.
-One of the aims of this work is to present a more theoretic representation of e-graphs than the one at the state of the art presented in \cite{egg}, using category theory formalism, in order to integrate the existence of such structure in a research line concerning concurrency of rewrinig-based formalisms.
-Indeed, graph-like structures turned out to be very advantageous for distributed system respresentation.
+\fi
+
+The developlment of visual formalisms such as equality graphs (e-graphs) is to be brought back to the eighties, in the context of automatic theorem provers (ATPs).
+E-Graphs are then an extension of prior structures, in order to represent in a more compact way equivalence classes of expressions mantaining closure-under-congruence invariant.
+Graph manipulation turns out to be very useful in practical fields such as systems optimization or even components upgrades, hence the development of formal frameworks is necessary, especially for what concernes parallelism and concurrency, as the research line in which this work wants to be integrated.
+
+In recent years, indeed, graph-like structures found a wide diffusion as models to rewriting-based formalisms and dependency analisys.
 An example of this fact could be a graph as the abstraction a set of entities and relations between them within a state, while rewriting steps model computation steps that, modifying the graph result in changes of the state of the system.
-A standard approach for this is the DPO (double pushout) approach, due to its flexibility and locality properties.
+
+Due to its flexibility and locality properties, DPO (double pushout) approach and adhesive categrìories have become a standard model for this kind of considerations. 
 A presentation of e-graphs as the one in this work allows to move beyond the operational representation via data structures, in favour of a formalization that model the changes of the structure too.
@@
 
-%Category theory provides uniform proofs and constructions across a wide range
-%of models. The usual approach is to find a natural class of categories with the right
-%structure to support the range of constructions particular to the application area.
+Among all graphic frameworks, e-graphs, widely used in modern SMT (satisfiability modulo theories) solvers, such as Z3, are having success, due efficiency of their implementations, but is still missing a solid theoretical underpinning, since almost all the progress remains implementation-based.
+Thus, one of the aims of this work is to present a more theoretic representation of e-graphs than the one at the state of the art presented in \cite{egg}, using categorial tools to be formalized.
+Then, the main result is to show that e-graphs relapse in the current adhesive paradigm.
 

### 2024-11-22 Article/introduction.tex
updated intro

--- 2024-11-22 Article/introduction.tex
@@
 
-The developlment of equality graphs (e-graphs) is to be brought back to the eighties, in the context of automatic theorem provers (ATPs).
-E-Graphs are then an extension of prior structures, in order to represemt in a more compact way equivalence classes of expressions mantaining closure-under-congruence invariant.
-One of the aims of this work is to present a more theoretic representation of e-graphs than the one at the state of the art presented in \cite{egg}, using category theory formalism, in order to integrate the existence of such structure in a research line concerning concurrency of rewrinig-based formalisms.
-Indeed, graph-like structures turned out to be very advantageous for distributed system respresentation.
-An example of this fact could be a graph as the abstraction a set of entities and relations between them within a state, while rewriting steps model computation steps that, modifying the graph result in changes of the state of the system.
-A standard approach for this is the DPO (double pushout) approach, due to its flexibility and locality properties.
-A presentation of e-graphs as the one in this work allows to move beyond the operational representation via data structures, in favour of a formalization that model the changes of the structure too.
-In this setup, adhesivity results permit to make use of all the advantages on DPO rewriting, because of the generality of such framework.
-The elegance of such formalism lies on the definition itself of adhesive categories, namely categories where is reqired of the existence of pullbacks and pushouts along (some) monomorphisms, which are additionally required to be Van Kampen (that is, stability of pushouts under pullbacks and stability of pullbacks under combined pushouts and pullbacks \cite{Ehrig_Golas}).
-The only downside of such formalism is the difficulty of proofs using the definition.
+\fi
+
+The developlment of visual formalisms such as equality graphs (e-graphs) has to be brought back to the eighties, in the context of automatic theorem provers (ATPs).
+E-Graphs are an extension of prior structures, in order to represent in a more compact way equivalence classes of expressions, mantaining closure-under-congruence invariant.
+Graph manipulation turns out to be useful in practical fields such as systems optimization or components upgrades.
+The development of formal frameworks is therefore necessary, especially for what concernes parallelism and concurrency, as the research line in which this work wants to be integrated.
+
+In recent years, graph-like structures found a wide diffusion as models to rewriting-based formalisms and dependency analisys.
+As an example, a graph can model a set of entities and relations between them within a state, while rewriting steps can model computation steps that, modifying the graph, result in changes of the state of the system.
+
+Dependency and concurrency harden the process of program optimization, because application order of rewrites can significantly improve the quality of the overall rewitten program.
+Such problem is known as \textit{phase-ordering problem}, and a recent approach, known as equality saturation, was developed in \cite{Tate_2011}.
+This technique provides an alternative to heuristic methods, consisting of keeping track of a set of candidate equivalent optimized programs, 
+computed by repeatedly inferring equivalences between program fragments.
+E-Graphs provide a compact representation of this set, making operation feasible in concrete applications.
+
+Due to its flexibility and locality properties, DPO (double pushout) approach and adhesive categories have become a standard model for rewriting-based formalisms. 
+A presentation of e-graphs as the one in this work allows to move beyond the operational representation via data structures, in favour of a formalization that models the changes of the structure as well.
+In this setup, adhesivity results allow to make use of all the advantages of DPO rewriting, because of the generality of such framework.
+The elegance of such formalism lies on the definition of adhesive categories, i.e., categories where it is guaranteed the existence of pullbacks and pushouts along (some) monomorphisms, which are additionally required to be Van Kampen (stability of pushouts under pullbacks and stability of pullbacks under combined pushouts and pullbacks \cite{Ehrig_Golas}).
+The only downside of such formalism is the difficulty of proving statements using the definition. 
 For cerain calasses of caeogries, there exists a charaterization of such property, presented in \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}.
 
-%Category theory provides uniform proofs and constructions across a wide range
-%of models. The usual approach is to find a natural class of categories with the right
-%structure to support the range of constructions particular to the application area.
+Among all graphic frameworks, e-graphs, widely used in modern SMT (satisfiability modulo theories) solvers, such as Z3, are gaining success, due to the efficiency of their implementations, but is still missing a solid theoretical underpinning, since almost all the progresses remain implementation-based.
+Thus, one of the aims of this work is to present a more theoretic representation of e-graphs than the one at the state of the art presented in \cite{egg}, using categorial tools to be formalized.
+The main result is, therefore, to show that e-graphs relapse in the current adhesive paradigm.
 
-In order to work with e-graphs, some considreration on graphs with equivalences are in order to be done.
+In order to work with e-graphs, some considreration on graphs with equivalences are to be done. 
 A graph with equivalence is nothing but a graph endowed with an equivalence relation among its nodes. 
 The main result on this kind of graphs is a weak adhesivity property that holds for particular monomorphisms. 
-Then, such result is inherited by e-graphs, which are graphs with equivalence with additional requirements that can be intuitively summarized as \textit{the property of edges to have equivalent sources whenever targets are equivalent}.
+Such result is, then, inherited by e-graphs, which are graphs with equivalence which satisfies additional requirements that can be intuitively summarized as \textit{the property of edges to have equivalent sources whenever targets are equivalent}.
 

### 2024-11-23 Article/introduction.tex
updated intro

@@
 
-Then, the structure of this work is the following.
+The work is structured as follows.
 The first chapter is about basic concepts of category theory, such as categories, limits, constructions and adhesivity, that will be used to model the categories on which in the second chapter we will work on.
-The prinicpal aim is to build up the categorial toolbox to work with.
-Category theory provides a general and uniform formalism, hence almost all definitions may seem very abstract, hence some concrete examples will be done.
-The second chapter is entirely focused on graphs, starting from a general notion of graphs, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, source and target, which assign to each edge a source vertex and a target one.
+The main aim is to build up the categorial toolbox to work with. 
+Category theory provides a general and uniform formalism, hence almost all definitions may seem very abstract, however some concrete examples will be done.
+The second chapter is entirely focused on graphs, starting from a general notion of graph, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, source and target, which assign to each edge a source vertex and a target one.
 The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization of them but also makes in evidence particular properties proper of graphs.
-Then, we endow graphs with an equivalence relation among verices, to end up with an adhesivity result.
+Then, we endow graphs with an equivalence relation among vertices, to end up with an adhesivity result.
 The last part is about e-graphs, and in particular their formalization and how they inherit certain properties from graphs with equivalences.

### 2024-11-23 Article/introduction.tex
intro

--- 2024-11-22 Article/introduction.tex
@@
+% !TeX root = ./main.tex
+
 \chapter*{Introduction}
@@
 
+The use of graph-like structures as flexible and powerful models in rewriting-based formalisms and dependency analysis has a long tradition in computer science and related fields.
+These structures offer an intuitive and expressive framework for capturing the behavior and evolution of complex systems.
+
+Graphs, for instance, can represent a set of entities as nodes and the relationships between them as edges, providing a clear depiction of the system's state at any given moment.
+Rewriting steps then model computational processes, simulating changes in the system’s state.
+These transformations might involve the addition, removal, or reconfiguration of nodes and edges, enabling the representation of diverse phenomena such as changes in a software system's architecture, the evolution of a biological network, or updates within a dependency graph.
+
+Among the various rewriting methodologies, the Double Pushout (DPO) approach \cite{Ehrig_Golas,ehrig2006fundamentals}has emerged as one of the leading paradigms.
+This rewriting paradigm, paired with the framework of $\mathcal{M}$-adhesive  categories \cite{lack2005adhesive,azzi2019essence,behr2022fundamentals}, provides a robust mathematical foundation for defining and applying rewriting rules.
+
 The developlment of visual formalisms such as equality graphs (e-graphs) has to be brought back to the eighties, in the context of automatic theorem provers (ATPs).
@@
 
-In recent years, graph-like structures found a wide diffusion as models to rewriting-based formalisms and dependency analisys.
-As an example, a graph can model a set of entities and relations between them within a state, while rewriting steps can model computation steps that, modifying the graph, result in changes of the state of the system.
+The development of visual formalisms, such as \emph{equality graphs} (e-graphs), can be traced back to the 1980s, originating in the context of automatic theorem provers (ATPs)\todo{mettere referenza}.
+E-graphs provide a compact and efficient way to represent equivalence classes of expressions while maintaining the crucial property of closure under congruence.
+This ensures that equivalences are preserved across all contexts in which an expression might appear, making e-graphs a robust tools for reasoning about equivalence of algebraic expressions\todo{Non sicuro dell'ultima riga}.
+
+The utility of e-graphs extends beyond theoretical applications, finding practical relevance in fields such as systems optimization and component upgrades.\todo{Qua servirebbero degli esempi di uso di cui non ho idea}
+
+The more this approach is used, the greater the need for formal frameworks to guide the development and application of e-graphs.
+In particular, addressing issues of parallelism and concurrency is critical for developing a mathematically sound understanding of these structures.
+
+ By integrating the theory of e-graphs manipulation into the broader subject of DPO rewriting, this work aims to put on more mathematically firm ground the status of e-graphs.
+Moreover, it allows to apply to this new context the well known results about concurrency and parallelism already known provided by the abstract theory of DPO rewriting systems \cite{baldan1999concurrent,ehrig1999handbook}.
+
+ On the technical level, to reach our aim we need to prove some adhesivity property of e-graphs. 
+ In order to do so, some considreration on graphs with equivalences are in order. 
+ A graph with equivalence is nothing but a graph endowed with an equivalence relation among its nodes. 
+ The main result on this kind of graphs is a weak adhesivity property that holds for regular monomorphisms. 
+ Such result is, then, inherited by e-graphs \todo{Da qualche parte mettere riferimento a \cite{egg}}, which are graphs with equivalence which satisfies additional requirements that can be intuitively summarized as the property of edges to have equivalent sources whenever targets are equivalent.
+
+On the technical level, to reach our objective we need to prove that the category of e-graphs exhibits a specific adhesivity property.
+To this end, it is necessary to first examine \emph{graphs with equivalence}, as they form the foundational structure underlying e-graphs.
+
+A graph with equivalence is simply a graph where an equivalence relation is defined on its nodes.
+The primary result concerning graphs with equivalences is an adhesivity property with respect to regular monomorphisms.
+
+This adhesivity result, in turn, extends naturally, via the results of \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}, to e-graphs \todo{Add reference to \cite{egg} da qualche parte}, which are a specialized class of graphs with equivalences that satisfy additional structural constraints.
+Specifically, e-graphs enforce a condition that edges must respect equivalence relations: if two edges have equivalent target nodes, then their source nodes must also be equivalent.
 
@@
 computed by repeatedly inferring equivalences between program fragments.
-E-Graphs provide a compact representation of this set, making operation feasible in concrete applications.
+E-Graphs provide a compact representation of this set, making operation feasible in concrete applications.\todo{Non ho capito questo paragrafo}
 
-Due to its flexibility and locality properties, DPO (double pushout) approach and adhesive categories have become a standard model for rewriting-based formalisms. 
+\iffalse 
 A presentation of e-graphs as the one in this work allows to move beyond the operational representation via data structures, in favour of a formalization that models the changes of the structure as well.
@@
 
-Among all graphic frameworks, e-graphs, widely used in modern SMT (satisfiability modulo theories) solvers, such as Z3, are gaining success, due to the efficiency of their implementations, but is still missing a solid theoretical underpinning, since almost all the progresses remain implementation-based.
-Thus, one of the aims of this work is to present a more theoretic representation of e-graphs than the one at the state of the art presented in \cite{egg}, using categorial tools to be formalized.
-The main result is, therefore, to show that e-graphs relapse in the current adhesive paradigm.
-
 In order to work with e-graphs, some considreration on graphs with equivalences are to be done. 
@@
 The main result on this kind of graphs is a weak adhesivity property that holds for particular monomorphisms. 
-Such result is, then, inherited by e-graphs, which are graphs with equivalence which satisfies additional requirements that can be intuitively summarized as \textit{the property of edges to have equivalent sources whenever targets are equivalent}.
+Such result is, then, inherited by e-graphs \todo{Da qualche parte mettere riferimento a \cite{egg}}, which are graphs with equivalence which satisfies additional requirements that can be intuitively summarized as \textit{the property of edges to have equivalent sources whenever targets are equivalent}.
+\fi
 
-Then, the structure of this work is the following.
-The first chapter is about basic concepts of category theory, such as categories, limits, constructions and adhesivity, that will be used to model the categories on which in the second chapter we will work on.
-The prinicpal aim is to build up the categorial toolbox to work with.
-Category theory provides a general and uniform formalism, hence almost all definitions may seem very abstract, hence some concrete examples will be done.
-The second chapter is entirely focused on graphs, starting from a general notion of graphs, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, source and target, which assign to each edge a source vertex and a target one.
-The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization of them but also makes in evidence particular properties proper of graphs.
-Then, we endow graphs with an equivalence relation among verices, to end up with an adhesivity result.
-The last part is about e-graphs, and in particular their formalization and how they inherit certain properties from graphs with equivalences.
+\smallskip \emph{Synopsis.} \Cref{chap:one} introduces the basic concepts of category theory that will be used throughout this thesis.
+The main goal of this chapter is to build the categorical toolbox necessary for the remainder of the work.
+Category theory provides a general and uniform formalism, which has the side effect of making many definitions seem quite abstract.
+To address this, we will provide concrete examples to help clarify and illustrate the concepts.
+\Cref{chap:two} is focused on graphs.
+The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization, putting in evidence the categorical properties proper of graphs which we will need.
+We will then endow graphs with an equivalence relation among vertices, and proof that the resulting category satisfies an adhesivity property.
+Finally, in the last part we will examin e-graphs, showing that they inherit the above adhesivity property from graphs with equivalences.

### 2024-11-23 Article/Cat_of_Graphs.tex
minima
minori

--- 2024-11-14 Article/Cat_of_Graphs.tex
@@
 
-\chapter{Categories of Graphs}
+\chapter{Categories of Graphs}\label{chap:two}
 This chapter is about graphs, and how it is possible to formalize them using categories in order to point out their properties from an abstract point of view.
@@
 
-\input{Graph_sections/Graphs}
+%\input{Graph_sections/Graphs}
 %\input{Graph_sections/Eq_Graphs_Notes_Results}

### 2024-11-23 Article/introduction.tex
minimo reshuffling intro

--- 2024-11-22 Article/introduction.tex
@@
 
-The developlment of visual formalisms such as equality graphs (e-graphs) has to be brought back to the eighties, in the context of automatic theorem provers (ATPs).
-E-Graphs are an extension of prior structures, in order to represent in a more compact way equivalence classes of expressions, mantaining closure-under-congruence invariant.
-Graph manipulation turns out to be useful in practical fields such as systems optimization or components upgrades.
-The development of formal frameworks is therefore necessary, especially for what concernes parallelism and concurrency, as the research line in which this work wants to be integrated.
+The use of graph-like structures as specification tools, as well as formal models, in rewriting-based formalisms and dependency analysis has a long tradition in computer science.
+% and related fields. 
+These structures offer an intuitive, flexible, and expressive framework for describing the behaviour and the evolution of complex systems.
 
-In recent years, graph-like structures found a wide diffusion as models to rewriting-based formalisms and dependency analisys.
-As an example, a graph can model a set of entities and relations between them within a state, while rewriting steps can model computation steps that, modifying the graph, result in changes of the state of the system.
+For instance, graphs can represent a set of entities as nodes and the relationships between them as edges, providing a clear depiction of the state of a system at any given moment.
+Rewriting steps then model computational processes, simulating changes in the system.
+These transformations might involve the addition, removal, or reconfiguration of nodes and edges, enabling the representation of diverse phenomena such as modifications in the architecture of a software system, evolution steps of a biological network, or updates within a dependency graph.
 
-Dependency and concurrency harden the process of program optimization, because application order of rewrites can significantly improve the quality of the overall rewitten program.
+%The development of visual formalisms such as equality graphs (e-graphs) has to be brought back to the 1980s, in the context of automatic theorem provers (ATPs).
+%^E-Graphs are an extension of prior structures, in order to represent in a more compact way equivalence classes of expressions, maintaining closure-under-congruence invariant.
+%Graph manipulation turns out to be useful in practical fields such as systems optimisation or components upgrades.
+%The development of formal frameworks is therefore necessary, especially for what concerns parallelism and concurrency, as the research line in which this work wants to be integrated.
+
+The development of the visual formalism of \emph{equality graphs} (e-graphs) can be traced back to the 1980s, originating in the context of automatic theorem provers (ATPs)\todo{mettere referenza}.
+E-graphs provide a compact and efficient way to represent equivalence classes of expressions while maintaining the crucial property of closure under congruence.
+This ensures that equivalences are preserved across all contexts in which an expression might appear, making e-graphs a robust tools for reasoning about equivalence of algebraic expressions.
+%\todo{Non sicuro dell'ultima riga}.
+
+Dependency and concurrency harden the process of program optimisation, because application order of rewrites can significantly improve the quality of the overall program.
 Such problem is known as \textit{phase-ordering problem}, and a recent approach, known as equality saturation, was developed in \cite{Tate_2011}.
@@
 E-Graphs provide a compact representation of this set, making operation feasible in concrete applications.
+%\todo{Non ho capito questo paragrafo}
 
-Due to its flexibility and locality properties, DPO (double pushout) approach and adhesive categories have become a standard model for rewriting-based formalisms. 
+The utility of e-graphs thus extends beyond theoretical applications, finding practical relevance in fields such as system optimisation and component upgrading.
+%\todo{Qua servirebbero degli esempi di uso}
+%
+However, the more a formalism is used, the greater is the need for formal frameworks to guide its development and application.
+In particular, addressing issues of parallelism and concurrency is critical for
+a mathematically 
+sound understanding of these structures.
+
+Among the rewriting paradigms for graph-like structures, one of the leading proposal is the Double Pushout (DPO) approach \cite{Ehrig_Golas,ehrig2006fundamentals}, since it provides, paired with the framework of $\mathcal{M}$-adhesive  categories \cite{lack2005adhesive,azzi2019essence,behr2022fundamentals}, a robust mathematical foundation for the definition and the application of rules.
+%
+Integrating the theory of e-graphs manipulation into the broader subject of DPO rewriting would put on firmer ground the status of e-graphs.
+Moreover, it would allow to apply to this new context the well known results about concurrency and parallelism already known provided by the abstract theory of DPO rewriting systems \cite{baldan1999concurrent,ehrig1999handbook}.
+
+Such an integration is the main aim of the thesis.
+ On the technical level, to reach our aim we need to prove some adhesivity property of e-graphs. 
+ In order to do so, some consideration on graphs with equivalences are in order. 
+ A graph with equivalence is nothing but a graph endowed with an equivalence relation among its nodes. 
+ The main result on this kind of graphs is a weak adhesivity property that holds for regular monomorphisms. 
+% Such result is, then, inherited by e-graphs \todo{Da qualche parte mettere riferimento a \cite{egg}}, which are graphs with equivalence which satisfies additional requirements that can be intuitively summarized as the property of edges to have equivalent sources whenever targets are equivalent.
+%
+%%On the technical level, to reach our objective we need to prove that the category of e-graphs exhibits a specific adhesivity property.
+To this end, it is necessary to first examine \emph{graphs with equivalence}, as they form the foundational structure underlying e-graphs.
+%
+%A graph with equivalence is simply a graph where an equivalence relation is defined on its nodes.
+The primary result concerning graphs with equivalences is an adhesivity property with respect to regular monomorphisms.
+%
+This adhesivity result, in turn, extends naturally, via the results of \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}, to e-graphs \todo{Add reference to \cite{egg} da qualche parte}, which in fact can be interpreted as a specialised class of graphs with equivalences that satisfy additional structural constraints.
+Specifically, e-graphs enforce a condition that edges must respect equivalence relations: if two edges have equivalent target nodes, then their source nodes must also be equivalent.
+
+\iffalse 
 A presentation of e-graphs as the one in this work allows to move beyond the operational representation via data structures, in favour of a formalization that models the changes of the structure as well.
@@
 The main result on this kind of graphs is a weak adhesivity property that holds for particular monomorphisms. 
-Such result is, then, inherited by e-graphs, which are graphs with equivalence which satisfies additional requirements that can be intuitively summarized as \textit{the property of edges to have equivalent sources whenever targets are equivalent}.
+Such result is, then, inherited by e-graphs \todo{Da qualche parte mettere riferimento a \cite{egg}}, 
+which are graphs with equivalence which satisfies additional requirements that can be intuitively summarised 
+as \textit{the property of edges to have equivalent sources whenever targets are equivalent}.
+\fi
 
-Then, the structure of this work is the following.
-The first chapter is about basic concepts of category theory, such as categories, limits, constructions and adhesivity, that will be used to model the categories on which in the second chapter we will work on.
-The prinicpal aim is to build up the categorial toolbox to work with.
-Category theory provides a general and uniform formalism, hence almost all definitions may seem very abstract, hence some concrete examples will be done.
-The second chapter is entirely focused on graphs, starting from a general notion of graphs, that is, a two sorted algebra consisting of a set of edges and a set of vertices and two operators, source and target, which assign to each edge a source vertex and a target one.
-The structure we will use to model graphs are presheaves, which not only provides a straightforward formalization of them but also makes in evidence particular properties proper of graphs.
-Then, we endow graphs with an equivalence relation among verices, to end up with an adhesivity result.
-The last part is about e-graphs, and in particular their formalization and how they inherit certain properties from graphs with equivalences.
+\smallskip \emph{Synopsis.} \Cref{chap:one} introduces the basic concepts of category theory that will be used throughout this thesis.
+The main goal of this chapter is to build the categorical toolbox necessary for the remainder of the work.
+Category theory provides a general and uniform formalism, which has the side effect of making many definitions seem quite abstract.
+To address this, we will provide concrete examples to help clarify and illustrate the concepts.
+\Cref{chap:two} focuses on graphs.
+The structure we will use to model graphs are presheaves, which not only provides a straightforward formalisation, putting in evidence the categorical properties of graphs that we will need.
+We will then endow graphs with an equivalence relation among vertices, and proof that the resulting category satisfies an adhesivity property.
+Finally, in the last part we will examine
+ e-graphs, showing that they inherit the above adhesivity property from graphs with equivalences.

### 2024-11-23 Article/Conclusions.tex
updated intro
minori

--- 2024-11-22 Article/Conclusions.tex
@@
 Hence, this work can be viewed as a starting point to a more general study on e-graphs, in which edges, nodes and equivalence classes can be not only sets but objects of any exact category.
+\fi
+
+In this work, we have defined graphs with equivalences and e-graphs in a more abstract manner than \cite{egg}, independent of specific implementations.
+This allowe us  to analyze the categorical properties of these structures.
+Building upon this framework, we have property, in particular, the adhesivivty of graphs with equivalences and e-graphs with respect to the class of regular monomorphisms.
+This result is potentially useful for advancing state-of-the-art techniques, such as the DPO approach for concurrent updates to the structure, which has not yet been explored.
+
+Both graphs with equivalences and e-graphs can be realized as functors with values in $\Set$.
+One might ask whether it is strictly necessary to use $\Set$ as the codomain of these functors.
+Our framework is developed from a more general perspective, using minimal set-theoretic concepts and instead relying on categorical constructions.
+It only requires $\mathcal{M}$-adhesivity and exactness  \cite{barrexact}.
+This propert certainly hold in $\Set$ (and more generally every elementary topos \cite{maclane2012sheaves}).
+Roughly speaking, this is  the property that enabled the equivalence noted in \Cref{rem:eqgrph_set_eq}.
+Therefore, a potential direction for future work will be to provide a more general presentation of these structures, replacing $\Set$ with any adhesive and exact category.

### 2024-11-23 Article/Conclusions.tex
minima

@@
 
-In this work, we have defined graphs with equivalences and e-graphs in a more abstract manner than \cite{egg}, independent of specific implementations.
-This allowe us  to analyze the categorical properties of these structures.
-Building upon this framework, we have property, in particular, the adhesivivty of graphs with equivalences and e-graphs with respect to the class of regular monomorphisms.
+In this work, we have defined graphs with equivalences and e-graphs in an abstract manner, making it independent of specific implementations such as in \cite{egg}.
+This allows  to analyse the categorical properties of these structures.
+Building upon this framework, we have proved, in particular, the adhesivity of graphs with equivalences and e-graphs with respect to the class of regular monomorphisms.
 This result is potentially useful for advancing state-of-the-art techniques, such as the DPO approach for concurrent updates to the structure, which has not yet been explored.
@@
 It only requires $\mathcal{M}$-adhesivity and exactness  \cite{barrexact}.
-This propert certainly hold in $\Set$ (and more generally every elementary topos \cite{maclane2012sheaves}).
+These properties certainly holdy in $\Set$ and more generally in every elementary topos \cite{maclane2012sheaves}.
 Roughly speaking, this is  the property that enabled the equivalence noted in \Cref{rem:eqgrph_set_eq}.

### 2024-11-23 Article/introduction.tex
minima

@@
 
-The utility of e-graphs thus extends beyond theoretical applications, finding practical relevance in fields such as system optimisation and component upgrading.
+The utility of e-graphs thus extends beyond theoretical applications, finding practical relevance in fields such as system optimisation and upgrading.
 %\todo{Qua servirebbero degli esempi di uso}
@@
 Integrating the theory of e-graphs manipulation into the broader subject of DPO rewriting would put on firmer ground the status of e-graphs.
-Moreover, it would allow to apply to this new context the well known results about concurrency and parallelism already known provided by the abstract theory of DPO rewriting systems \cite{baldan1999concurrent,ehrig1999handbook}.
+Moreover, it would allow to apply to this new context well-known results about concurrency and parallelism already provided by the theory of DPO rewriting systems \cite{baldan1999concurrent,ehrig1999handbook}.
 
@@
  On the technical level, to reach our aim we need to prove some adhesivity property of e-graphs. 
- In order to do so, some consideration on graphs with equivalences are in order. 
+ In order to do so, some considerations on graphs with equivalences are in order. 
  A graph with equivalence is nothing but a graph endowed with an equivalence relation among its nodes. 
@@
 
-\smallskip \emph{Synopsis.} \Cref{chap:one} introduces the basic concepts of category theory that will be used throughout this thesis.
-The main goal of this chapter is to build the categorical toolbox necessary for the remainder of the work.
-Category theory provides a general and uniform formalism, which has the side effect of making many definitions seem quite abstract.
-To address this, we will provide concrete examples to help clarify and illustrate the concepts.
+\smallskip \emph{Synopsis.} \Cref{chap:one} introduces the basic concepts of category theory used throughout this thesis.
+The main goal of this chapter is to build the toolbox necessary for the remainder of the work.
+Category theory provides a general and uniform formalism, which sometimes can make definitions seem quite abstract.
+To address this, we provide concrete examples to help clarify and illustrate the concepts.
 \Cref{chap:two} focuses on graphs.
-The structure we will use to model graphs are presheaves, which not only provides a straightforward formalisation, putting in evidence the categorical properties of graphs that we will need.
-We will then endow graphs with an equivalence relation among vertices, and proof that the resulting category satisfies an adhesivity property.
-Finally, in the last part we will examine
+The structure we  use to model graphs are presheaves, which not only provides a straightforward formalisation, putting in evidence the categorical properties of graphs that we  need.
+We then endow graphs with an equivalence relation among vertices, and proof that the resulting category satisfies an adhesivity property.
+Finally, in the last part we examine
  e-graphs, showing that they inherit the above adhesivity property from graphs with equivalences.

### 2024-11-23 Article/introduction.tex
minima

@@
 
-Among the rewriting paradigms for graph-like structures, one of the leading proposal is the Double Pushout (DPO) approach \cite{Ehrig_Golas,ehrig2006fundamentals}, since it provides, paired with the framework of $\mathcal{M}$-adhesive  categories \cite{lack2005adhesive,azzi2019essence,behr2022fundamentals}, a robust mathematical foundation for the definition and the application of rules.
+Among the rewriting paradigms for graph-like structures, one of the leading proposal is the Double Pushout (DPO) approach \cite{Ehrig_Golas,ehrig2006fundamentals}, since it provides, paired with the framework of $\mathcal{M}$-adhesive  categories \cite{lack2005adhesive,azzi2019essence,behr2022fundamentals}, a robust mathematical foundation for the definition and the application of rules,
+that us the identification of a subgraph to be removed and the insertion of a new subgraph.
 %

### 2024-11-23 Article/Background_sections/Limit.tex
final

@@
 
-The following lemma is a classical result, its proof is in the appendix.
+The following lemma is a classical result.
 
@@
 \end{lemma}
+
+\begin{proof}
+    For the ``only if'' part, suppose the left square to be a pullback. To verify the outer rectangle is a pullback, consider the following situation:
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} & & \\
+            & & & Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    But the right square is a pullback implies that there exists a unique $u$ such that
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15, dashed]{drr}{u}& & \\
+            & &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    And, since the left square is a pullback, there exists a unique $v$ such that
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15]{drr}{u} \arrow[dr, "v", dashed]& & \\
+            & X \arrow[r, "f"] \arrow[d, "t"swap] &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    Hence, the whole rectangle is a pullback.
+
+    For the ``if'' part, consider the following situation.
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrd}{p_1} \arrow[bend right=30, swap]{ddr}{p_2} & \\
+            & & Y \arrow[d, "k"] \\
+            & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+    We have now to show that the unique arrow $v: P \to X$ (of the outer rectangle) is such that $f \circ v = p_1$, but this follows from the fact that the right square is a pullback, having the following situation.
+    \[
+        \begin{tikzcd}[row sep = 20, column sep = 20]
+            P \arrow[bend left=30]{rrrd}{g \circ p_1} \arrow[bend right=30, swap]{ddr}{p_2} \arrow[bend left=15, dashed]{drr}{u}& & \\
+            & &  Y \arrow[r, "g"] \arrow[d, "k"]& Z \arrow[d, "h"] \\
+            & A \arrow[r, "a"swap] & B \arrow[r, "b"swap] & C
+        \end{tikzcd}
+    \]
+\end{proof}
 
@@
 This construction has the universal property because equalizers and products do.
-A detailed proof is in the appendix.
 
@@
 \end{theorem}
+
+\begin{proof}
+    Let $D: \cat{I \rightarrow C}$ a diagram, with $\cat I$ finite.
+
+    The \emph{if} statement follows from definitions of products and equalizers (\Cref{def:pullback_pushout}, \Cref{def:equalizer_coequalizer})
+
+    To satisfy the \emph{only if} statement, we want an object $L$ together with morphisms $p_i : L \rightarrow D(j)$ such that:
+    \begin{enumerate}
+        \item\label{item:cone} $\{p_i: L \rightarrow D(i)\}$ is a cone -- i.e., for each morphism of $\cat I$ $\alpha : i \rightarrow j$, $D(\alpha) \circ p_i = p_j$; and
+        \item\label{item:univ_prop} for each $E$ and $q_i : E \rightarrow D(j)$ in $\cat C$, with $D(\alpha) \circ q_i = q_j$ for each $\alpha : i \rightarrow j$ of $\cat I$, there exists a unique $f: E \rightarrow L$ such that $q_i = p_i \circ f$ for each $i \in \Ob(\cat I)$.
+    \end{enumerate}
+
+    Consider the two products (which exist by hypothesis) $\prod_{j \in \Ob(\cat I)} D(j)$, the product of the objects of the diagram, and $\prod_{\alpha \in \Hom(\cat I)}D(cod \ \alpha)$, the product of the codomains of the morphisms in $D$, where $\pi_x$ is the $x$-th projection of the product.
+    Let now:
+    \[
+        \gamma, \varepsilon : \prod_{j \in \Ob(\cat I)}D(j) \ \longrightarrow \prod_{\alpha \in \Hom(\cat I)} D(cod \ \alpha)
+    \]
+    be defined by $\gamma_\alpha = \pi_{D(cod\ \alpha)}$ (the projection on the codomain of $\alpha$) and $\varepsilon_\alpha = D(\alpha) \circ \pi_{D(dom \ \alpha)}$.
+    Let now $e: L \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$ the equalizer of $\gamma$ and $\varepsilon$ (which exists by hypothesis), and, for each $j \in \Ob(\cat I)$, $p_j: L \rightarrow D(j)$, defined by $p_j = \pi_{D(j)} \circ e$.
+
+    What we want now is to show that $(L, (p_i))_{i \in \cat I}$ is the limit of $D$, namely, to prove that the conditions given at the beginning are valid.
+
+    For condition~\ref{item:cone}, we have to show that, for each $\alpha : i \rightarrow j$ of $\cat I$, we have $D(\alpha) \circ p_i = p_j$:
+    \begin{align*}
+        D(\alpha) \circ p_i 
+            &= D(\alpha) \circ \pi_{D(i)} \circ e   && \textit{Definition of $p_j$} \\
+            &= \varepsilon_{\alpha} \circ e         && \textit{Definition of $\varepsilon$}\\
+            &= \gamma_\alpha \circ e                && \textit{$e$ is an equalizer of $\pi, \varepsilon$}\\
+            &= \pi_{D(j)} \circ e                   && \textit{Definition of $\pi$} \\
+            &= p_j                                  && \textit{Definition of $p_j$} \\
+    \end{align*}
+
+    For condition~\ref{item:univ_prop}, suppose that $(E, (q_i)_{i \in \Ob(\cat I)})$ has the properties stated.
+By definition of product, there exists a (unique) arrow $q: E \rightarrow \prod_{j \in \Ob(\cat I)}D(j)$.
+For each arrow $\alpha: i \rightarrow j$, we have:
+    \begin{align*}
+            \gamma_\alpha \circ q 
+                &= \pi_{D(j)} \circ q           && \textit{Definition of $\pi$} \\
+                &= q_j                          && \textit{Definition of $q_j$} \\
+                &= D(\alpha) \circ q_i          && \textit{Assumption on $q_j$} \\
+                &= D(\alpha) \circ \pi_{D(j)} \circ q   &&\textit{Definition of $q_i$} \\
+                &= \varepsilon_{\alpha} \circ q && \textit{Definition of $\varepsilon$} \\
+    \end{align*}
+    Since $e$ equalizes $\pi$ and $\varepsilon$, there exists a unique $f: E \rightarrow L$ in $\cat C$ such that $q = e \circ f$.
+Then, for each $j \in \Ob(\cat I)$, we have $\pi_{D(j)} \circ q = \pi_{D(j)} \circ e \circ f$, hence, $q_i = p_i \circ f$.
+\end{proof}
 

### 2024-11-23 Article/introduction.tex
final

--- 2024-11-23 Article/introduction.tex
@@
 \addcontentsline{toc}{chapter}{Introduction}
-
+\markboth{INTRODUCTION}{}
 \iffalse
@@
 %^E-Graphs are an extension of prior structures, in order to represent in a more compact way equivalence classes of expressions, maintaining closure-under-congruence invariant.
-%Graph manipulation turns out to be useful in practical fields such as systems optimisation or components upgrades.
+%Graph manipulation turns out to be useful in practical fields such as systems optimization or components upgrades.
 %The development of formal frameworks is therefore necessary, especially for what concerns parallelism and concurrency, as the research line in which this work wants to be integrated.
 
-The development of the visual formalism of \emph{equality graphs} (e-graphs) can be traced back to the 1980s, originating in the context of automatic theorem provers (ATPs)\todo{mettere referenza}.
+The development of the visual formalism of \emph{equality graphs} (e-graphs) can be traced back to the 1980s, originating in the context of automatic theorem provers (ATPs) \cite{Nelson1980}. 
 E-graphs provide a compact and efficient way to represent equivalence classes of expressions while maintaining the crucial property of closure under congruence. 
@@
 
-Dependency and concurrency harden the process of program optimisation, because application order of rewrites can significantly improve the quality of the overall program.
+Dependency and concurrency harden the process of program optimization, because application order of rewrites can significantly improve the quality of the overall program.
 Such problem is known as \textit{phase-ordering problem}, and a recent approach, known as equality saturation, was developed in \cite{Tate_2011}.
@@
 
-The utility of e-graphs thus extends beyond theoretical applications, finding practical relevance in fields such as system optimisation and component upgrading.
+The utility of e-graphs thus extends beyond theoretical applications, finding practical relevance in fields such as system optimization and component upgrading.
+Example of uses can be found in \cite{Cheli2021}.
 %\todo{Qua servirebbero degli esempi di uso}
@@
 
-Among the rewriting paradigms for graph-like structures, one of the leading proposal is the Double Pushout (DPO) approach \cite{Ehrig_Golas,ehrig2006fundamentals}, since it provides, paired with the framework of $\mathcal{M}$-adhesive  categories \cite{lack2005adhesive,azzi2019essence,behr2022fundamentals}, a robust mathematical foundation for the definition and the application of rules.
+%Among the rewriting paradigms for graph-like structures, one of the leading proposal is the Double Pushout (DPO) approach \cite{Ehrig_Golas,ehrig2006fundamentals}, since it provides, paired with the framework of $\mathcal{M}$-adhesive  categories \cite{lack2005adhesive,azzi2019essence,behr2022fundamentals}, a robust mathematical foundation for the definition and the application of rules.
+Among the rewriting paradigms for graph-like structures, one of the leading proposal is the Double Pushout (DPO) approach \cite{Ehrig_Golas,ehrig2006fundamentals}, since it provides, paired with the framework of $\mathcal{M}$-adhesive  categories \cite{lack2005adhesive,azzi2019essence,behr2022fundamentals}, a robust mathematical foundation for the definition and the application of rules,
+that us the identification of a subgraph to be removed and the insertion of a new subgraph.
 %
@@
 %
-This adhesivity result, in turn, extends naturally, via the results of \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}, to e-graphs \todo{Add reference to \cite{egg} da qualche parte}, which in fact can be interpreted as a specialised class of graphs with equivalences that satisfy additional structural constraints.
+ This adhesivity result, in turn, extends naturally, via the results of \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity}, to e-graphs, which in fact can be interpreted as a specialised class of graphs with equivalences that satisfy additional structural constraints.
+ An operational presentation of such structures can be found in \cite{egg}. 
  Specifically, e-graphs enforce a condition that edges must respect equivalence relations: if two edges have equivalent target nodes, then their source nodes must also be equivalent.

### 2024-11-27 Beamer/main.tex
Presentazione

\documentclass[8pt]{beamer}

\usefonttheme{serif}
\usetheme{CambridgeUS}

\usepackage[utf8]{inputenc} %utf8
%\usepackage[italian]{babel}
\usepackage[T1]{fontenc}
\author{Roberto Biondo}
\institute{\small Dipartimento di Informatica\\Università di Pisa}
\title{\textbf{On Adhesivity of EGGs}}
\usepackage{datetime}
\newdate{date}{29}{11}{2024}
\date{\displaydate{date}}

\usepackage{wrapfig}
\usepackage[T1]{fontenc} % Font encoding, T1 = it
%\usepackage[size=a4]{breamerposter}
\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
%\usepackage[english]{babel} % Lingua principale inglese
\usepackage{graphicx} % Per includere immagini esterne
%\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
%\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry} %impaginazione e margini documento -- DA POROBLEMI!!!
%\usepackage[fontsize=12pt]{scrextend} %dimensione font

%\usepackage{titlesec} %indice

\usepackage{csquotes}

%\usepackage[all,cmtip]{xy}

\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
\usepackage{subcaption}

\usepackage{multicol}

\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}

% General Setting diagrams
\usepackage{tikz-cd} %diagrammi
\usetikzlibrary{svg.path}
\tikzcdset{row sep/normal=5em}
\tikzcdset{column sep/normal=5em}
\tikzcdset{every label/.append style = {font = \small}}

\begin{document}

\newcommand{\cat}[1]{\mathscr{#1}}
\newcommand{\Ob}{\mathcal{O}b}
\newcommand{\Hom}{\mathcal{H}om}
\newcommand{\Set}{\mathbf{Set}}
\newcommand{\Reg}{\mathcal{R}eg}
\newcommand{\Mono}{\mathcal{M}ono}
\newcommand{\initial}{\mymathbb{0}}
\newcommand{\terminal}{\mathds{1}}
\newcommand{\eqgraph}[1]{\mathbb{#1}}
\newcommand{\EqGrph}{\mathbf{EqGrph}}
\newcommand{\Egg}{\mathbf{EGG}}

\begin{frame}
        \titlepage
        %\maketitle
\end{frame}

\begin{frame}\frametitle{Contenuti}
        \tableofcontents
\end{frame}

\section{Overview}

\begin{frame}\frametitle{Formalismi Grafici}
	Formalismi grafici:
	\begin{itemize}
		\item Analisi delle dipendenze
		\item Bioinformatica
		\item Sistemi di riscrittura
		\item Ottimizzazione
		\item Ingegneria del software
	\end{itemize}

\end{frame}

\section{Background}
\begin{frame}[fragile]\frametitle{Categorie} %, Funtori}
	Modello \emph{categoriale}.

	\smallskip

        Una categoria $\cat C$ è composta da:
	\begin{itemize}\item\emph{oggetti}\item\emph{morfismi} (o \emph{frecce})\end{itemize}
        \[
                \begin{tikzcd} A \arrow[loop left, "{id_A}"] \arrow[r, "f"] & B \arrow[loop right, "{id_B}"] \end{tikzcd}
        \]

        \smallskip

        La categoria i cui oggetti sono gli insiemi e i cui morfismi sono le funzioni tra essi è denominata $\Set$.

        \smallskip

        $f: A \to B$ può essere:
        \begin{itemize}
                \item un \emph{monomorfismo} : $f \circ g = f \circ h \Rightarrow g = h$;
                \item un \emph{epimorfismo} : $g \circ f = h \circ f \Rightarrow g = h$;
                \item un \emph{isomorfimso} : esiste $k$ tale che $f \circ k = id_B$ e $k \circ f = id_A$.
        \end{itemize}

\end{frame}

\begin{frame}[fragile]\frametitle{Funtori, Trasformazioni Naturali}
	Un \emph{funtore} $F: \cat{C \to D}$:
        \[\begin{tikzcd} F(A) \arrow[loop left, "{F(id_A) = id_{F(A)}}"] \arrow[r, "F(f)"] 
        \arrow[rr, bend left=30, "{F(g \circ f) = F(g) \circ F(f)}"] & F(B) \arrow[r, "F(g)"] & F(C) 
        \arrow[loop right, "{F(id_C) = id_{F(C)}}"] \end{tikzcd}\]

        Una \emph{trasformazione naturale} $\eta:F \dot\to G$: % è una mappa tra due funtori $F, G: \cat{C \to D}$, che assegna ad ogni oggetto $A$ di $\cat C$ un morfismo $\eta_A$ di $\cat D$. 
    \[
        \begin{tikzcd}[row sep = 20, column sep = 20]
            F(A) \arrow[d, "F(f)" swap] \arrow[r, "{\eta_A}"] & G(A) \arrow[d, "G(f)"] \\
            F(B) \arrow[r, "{\eta_B}"swap] & G(B)
        \end{tikzcd}
    \]

    \emph{Categoria di funtori} $[\cat{C, D}]$:
    \begin{itemize}
	    \item Oggetti: funtori (con dominio $\cat C$ e codominio $\cat D$)
	    \item Morfismi: trasformazioni naturali
	\end{itemize}
        \smallskip

    Le categorie di funtori il cui codominio è $\Set$ sono dette \emph{categorie di prefasci}.
\end{frame}

\begin{frame}[fragile]\frametitle{Categorie di Grafi}

	\begin{wrapfigure}{R}{0.4\textwidth}
		\begin{tikzpicture}
		[scale=.8,auto=left, every node/.style={circle,fill=blue!20}]
		\node (s1) at (1, 4) {$s_1$};
		\node (s2) at (1, 2)  {$s_2$};
		\node (t1) at (4, 4)  {$t_1$};
		\node (t2) at (4, 2) {$t_2$};

		\path (s1) edge [->](t1);
		\path (s2) edge [->](t2);

		\draw[dashed]  (0,1) -- (2, 1) -- (2, 5) -- (0, 5) -- (0, 1);
		\draw[dashed]  (3,1) -- (5, 1) -- (5, 5) -- (3, 5) -- (3, 1);

		\end{tikzpicture}
	\end{wrapfigure}

	Un grafo $G$ è costituito da:
	\begin{itemize}
		\item Un insieme di nodi $V$
		\item Un insieme di archi $E$
		\item $s: E \to V$ funzione sorgente
		\item $t: E \to V$ funzione destinazione
	\end{itemize}
	In altre parole, un grafo è un elemento di $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$.

	Un \emph{grafo con eqiuvalenza} $(G, \sim)$ è costituito da:
	\begin{itemize}
		\item Un grafo $G$
		\item Una relazione di quivalenza $\sim$ definita sui vertici
	\end{itemize}
	Ossia, un elemento di $[E \rightrightarrows V \to Q, \Set]$, tale che la freccia $q: V \to Q$ sia surgettiva (epi).

	Un E-Grafo $(G, \sim)$ è un grafo con equivalenza tale che
	\[
		\frac{s_G(e)\sim s_G(e')}{t_G(e) \sim t_G(e')}
	\]
\end{frame}

\begin{frame}[fragile]\frametitle{Pullback, Pushout, Equalizzatori}
	\begin{figure}[h]
		\begin{subfigure}{0.25\textwidth}
			\[\begin{tikzcd}[row sep = 20, column sep = 20]
				P' \arrow[dr, dashed, "v"] \arrow[drr, "{p_1'}", bend left=20] \arrow[ddr, "{p_2'}"swap, bend right=20] & & \\
 									& P \arrow[r, "{p_1}"] \arrow[d, "{p_2}"swap] 			& A \arrow[d, "f"] \\
									& B \arrow[r, "g"swap] 						& C
			\end{tikzcd}\]
			\caption{Pullback}
			\label{fig:pg}
		\end{subfigure}
		\qquad
		\begin{subfigure}{0.25\textwidth}
			\[\begin{tikzcd}[row sep = 20, column sep = 20]
				A \arrow[r, "f"] \arrow[d, "g"swap] 	& B \arrow[d, "{q_1}"] 	\arrow[ddr, "{q_1'}", bend left=20]	& \\
				C \arrow[r, "{q_2}"swap]  \arrow[drr, "{q_2'}"swap, bend right=20] & Q \arrow[dr, dashed, "u"] 	& \\
							& 				& Q'
			\end{tikzcd}\]
			\caption{Pushout}
			\label{po}
		\end{subfigure}
		\qquad
		\begin{subfigure}{0.25\textwidth}
			\[\begin{tikzcd}[row sep = 20, column sep = 20]
				E \arrow[r, "e"] & A \arrow[r, "f", shift left=1] \arrow[r,"g"swap, shift right = 1] & B \\
				E' \arrow[u, dashed, "h"] \arrow[ur, "{e'}"swap] &
			\end{tikzcd}\]
			\caption{Equalizzatore}
			\label{eq}
		\end{subfigure}
	\end{figure}

	In $\Set$:
	\begin{itemize}
		\item Pullback di $f$ e $g$: $ P = \{(x, y) \in A \times B \mid f(x) = g (y)\}$
		\item Pushout di $f$ e $g$:  $Q = (A \coprod B)/\sim$
		\item Equalizzatore di $f$ e $g$: $E=\{x \in A \mid f(x) = g(x)\}$
	\end{itemize}
\end{frame}

\begin{frame}[fragile]\frametitle{Adesività}

	\begin{wrapfigure}{ur}{0.4\textwidth}
                \[
                \begin{tikzcd}[row sep=11, column sep=11]
                        & {A'} && {B'} \\
                        {C'} && {D'} \\
                        & A && B \\
                        C && D
                        \arrow["{f'}", from=1-2, to=1-4]
                        \arrow["{m'}"', from=1-2, to=2-1]
                        \arrow["a"'{pos=0.7}, from=1-2, to=3-2]
                        \arrow["{n'}"', from=1-4, to=2-3]
                        \arrow["b", from=1-4, to=3-4]
                        \arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
                        \arrow["c"', from=2-1, to=4-1]
                        \arrow["f"'{pos=0.3}, from=3-2, to=3-4]
                        \arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
                        \arrow["m", from=3-2, to=4-1]
                        \arrow["n", from=3-4, to=4-3]
                        \arrow["g"', from=4-1, to=4-3]
                    \end{tikzcd}
            \]
        \end{wrapfigure}
	Una categoria $\cat C$ è adesiva se:
	\begin{itemize}
		\item ha tutti i pushout di monomorfismi
		\item ha tutti i pullback
		\item i pushout di monomorfismi sono \emph{Van Kampen}
	\end{itemize}
\end{frame}

\begin{frame}[fragile]\frametitle{Approccio DPO su Categorie Adesive}
	Sia $\cat C$ una categoria adesiva.
	\begin{figure}[h]
		\begin{subfigure}{0.25\textwidth}
			\[\begin{tikzcd}[row sep = 20, column sep = 20] L & K \arrow[r, "r"] \arrow[l, "l"swap] & L \end{tikzcd}\]
		\label{fig:rule}
		\caption{Regola}
		\end{subfigure}
		\qquad
		\begin{subfigure}{0.25\textwidth}
			\[\begin{tikzcd}[row sep = 20, column sep = 20]
			L \arrow[d, "{m_L}"swap] & K\arrow[d, "{m_K}"] \arrow[r, "r"] \arrow[l, "l"swap] & R \arrow[d, "{m_R}"] \\
				G & D \arrow[l, "{l*}"] \arrow[r, "{r*}"swap] & H
		\end{tikzcd}\]
		\caption{Passo di derivazione}
		\label{fig:step}
		\end{subfigure}
	\end{figure}
	$l$ e $r$ sono due morfismi, possibilmente mono, di $\cat C$, 
	mentre i due quadrati sono pushout.

	\begin{figure}
		\includegraphics[width=0.4\linewidth]{imgs/fancyDPO}
	\end{figure}
\end{frame}

\end{document}

### 2024-11-27 Beamer/main.tex
Presentazione

@@
 
+\begin{frame}\frametitle{EGGs}
+
+%	\begin{image}
+
+%	\end{image}
+
+	La categoria degli E-Grafi è detta $\Egg$, dal nome della libreria che li implementa in Rust.
+
+	\smallskip
+
+	La definizione attuale è troppo operativa per ottenere dei risultati teorici.
+
+	\smallskip
+
+	Tuttavia gli utilizzi sono molteplici, dalla \emph{equality saturation} all'ottimizzazione in fase di compilazione.
+\end{frame}
+
 \begin{frame}[fragile]\frametitle{Pullback, Pushout, Equalizzatori}
@@
 
+\section{Conclusioni}
+\begin{frame}\frametitle{Conclusioni}
+	\begin{itemize}
+		\item Formalizzazione degli E-Grafi mediante categorie
+		\item Adesività rispetto ad alcuni morfismi
+	\end{itemize}
+
+	LAvori futuri: sostituire la categoria $\Set$ con una qualsiasi categoria esatta e adesiva.
+\end{frame}
+
 \end{document}

### 2024-11-28 Beamer/main.tex
Presentazione

@@
 \usefonttheme{serif}
-\usetheme{CambridgeUS}
+\usetheme{Singapore}
 
@@
 
-\begin{frame}[fragile]\frametitle{Categorie di Grafi}
+\section{Grafi}
 
+\begin{frame}[fragile]\frametitle{Definizione dei Grafi}
+
+	Un grafo $G$ è costituito da:
+	\begin{itemize}
+		\item Un insieme di nodi $V$
+		\item Un insieme di archi $E$
+		\item $s: E \to V$ funzione sorgente
+		\item $t: E \to V$ funzione destinazione
+	\end{itemize}
+	In altre parole, un grafo è un elemento di $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$.
+\end{frame}
+
+\begin{frame}\frametitle{Grafi ed Equivalenze}
 	\begin{wrapfigure}{R}{0.4\textwidth}
@@
 	\end{wrapfigure}
-
-	Un grafo $G$ è costituito da:
-	\begin{itemize}
-		\item Un insieme di nodi $V$
-		\item Un insieme di archi $E$
-		\item $s: E \to V$ funzione sorgente
-		\item $t: E \to V$ funzione destinazione
-	\end{itemize}
-	In altre parole, un grafo è un elemento di $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$.
 
@@
 \end{frame}
+
+\section{Adesività}
 
@@
 		\item Pullback di $f$ e $g$: $ P = \{(x, y) \in A \times B \mid f(x) = g (y)\}$
-		\item Pushout di $f$ e $g$:  $Q = (A \coprod B)/\sim$
+		\item Pushout di $f$ e $g$:  $Q = (A \coprod B)/_\sim$
 		\item Equalizzatore di $f$ e $g$: $E=\{x \in A \mid f(x) = g(x)\}$
@@
 
-\begin{frame}[fragile]\frametitle{Adesività}
-
-	\begin{wrapfigure}{ur}{0.4\textwidth}
-                \[
-                \begin{tikzcd}[row sep=11, column sep=11]
-                        & {A'} && {B'} \\
-                        {C'} && {D'} \\
-                        & A && B \\
-                        C && D
-                        \arrow["{f'}", from=1-2, to=1-4]
-                        \arrow["{m'}"', from=1-2, to=2-1]
-                        \arrow["a"'{pos=0.7}, from=1-2, to=3-2]
-                        \arrow["{n'}"', from=1-4, to=2-3]
-                        \arrow["b", from=1-4, to=3-4]
-                        \arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
-                        \arrow["c"', from=2-1, to=4-1]
-                        \arrow["f"'{pos=0.3}, from=3-2, to=3-4]
-                        \arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
-                        \arrow["m", from=3-2, to=4-1]
-                        \arrow["n", from=3-4, to=4-3]
-                        \arrow["g"', from=4-1, to=4-3]
-                    \end{tikzcd}
-            \]
-        \end{wrapfigure}
-	Una categoria $\cat C$ è adesiva se:
-	\begin{itemize}
-		\item ha tutti i pushout di monomorfismi
-		\item ha tutti i pullback
-		\item i pushout di monomorfismi sono \emph{Van Kampen}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]\frametitle{Approccio DPO su Categorie Adesive}
-	Sia $\cat C$ una categoria adesiva.
+\begin{frame}[fragile]\frametitle{Approccio DPO}
+	Sia $\cat C$ una categoria.
 	\begin{figure}[h]
@@
 \end{frame}
+\begin{frame}[fragile]\frametitle{Adesività}
+
+	\iffalse
+	\begin{wrapfigure}{l}{0.4\textwidth}
+                \[
+                \begin{tikzcd}[row sep=11, column sep=11]
+                        & {A'} && {B'} \\
+                        {C'} && {D'} \\
+                        & A && B \\
+                        C && D
+                        \arrow["{f'}", from=1-2, to=1-4]
+                        \arrow["{m'}"', from=1-2, to=2-1]
+                        \arrow["a"'{pos=0.7}, from=1-2, to=3-2]
+                        \arrow["{n'}"', from=1-4, to=2-3]
+                        \arrow["b", from=1-4, to=3-4]
+                        \arrow["{g'}"{pos=0.7}, from=2-1, to=2-3, crossing over]
+                        \arrow["c"', from=2-1, to=4-1]
+                        \arrow["f"'{pos=0.3}, from=3-2, to=3-4]
+                        \arrow["d"{pos=0.3}, from=2-3, to=4-3, crossing over]
+                        \arrow["m", from=3-2, to=4-1]
+                        \arrow["n", from=3-4, to=4-3]
+                        \arrow["g"', from=4-1, to=4-3]
+                    \end{tikzcd}
+            \]
+        \end{wrapfigure}
+	\fi
+
+	Una categoria $\cat C$ è adesiva se:
+	\begin{itemize}
+		\item ha tutti i pushout di monomorfismi
+		\item ha tutti i pullback
+		\item i pushout di monomorfismi sono \emph{Van Kampen} - ossia che tali pushout sono stabili stoot pullback e i pubblack sono stabili sotto pushout combinati con pullback
+	\end{itemize}
+
+	\smallskip
+
+	L'adesività permette di estendere l'approccio DPO a categorie più complesse come quelle dei grafi.
+
+	\smallskip
+
+	\smallskip
+\begin{figure}%
+    \centering
+    \subfloat[\centering DPO su grafi]{{\includegraphics[width=5cm]{imgs/DPOgraphs} }}%
+    \qquad
+    \subfloat[\centering DPO per reazione di Dies-Alder]{{\includegraphics[width=5cm]{imgs/reaction} }}%
+    \label{fig:example}%
+\end{figure}
+
+\end{frame}
 
@@
 
-	LAvori futuri: sostituire la categoria $\Set$ con una qualsiasi categoria esatta e adesiva.
+	Lavori futuri: sostituire la categoria $\Set$ con una qualsiasi categoria esatta e adesiva.
 \end{frame}

### 2024-11-28 Beamer/main.tex
Minima

@@
 \usepackage[utf8]{inputenc} %utf8
-%\usepackage[italian]{babel}
 \usepackage[T1]{fontenc}
@@
 \usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-%\usepackage[english]{babel} % Lingua principale inglese
+%\usepackage[italian]{babel} % Lingua principale inglese
 \usepackage{graphicx} % Per includere immagini esterne
+
 %\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
@@
 %\usepackage[fontsize=12pt]{scrextend} %dimensione font
-
+%\usepackage{}
 %\usepackage{titlesec} %indice
@@
 
+\end{frame}
+
+\section{Grafi}
+
+\begin{frame}[fragile]\frametitle{Definizione dei Grafi}
+
 	\emph{Categoria di funtori} $[\cat{C, D}]$:
@@
 	\end{itemize}
+
 	\smallskip
@@
 	    Le categorie di funtori il cui codominio è $\Set$ sono dette \emph{categorie di prefasci}.
-\end{frame}
 
-\section{Grafi}
-
-\begin{frame}[fragile]\frametitle{Definizione dei Grafi}
+	    \smallskip
 
@@
 
-%	\begin{image}
-
-%	\end{image}
+	\begin{figure}
+		\includegraphics[width=\linewidth]{imgs/eggs}
+	\end{figure}
 
@@
 		\end{subfigure}
-		\qquad
-		\begin{subfigure}{0.25\textwidth}
-			\[\begin{tikzcd}[row sep = 20, column sep = 20]
-				E \arrow[r, "e"] & A \arrow[r, "f", shift left=1] \arrow[r,"g"swap, shift right = 1] & B \\
-				E' \arrow[u, dashed, "h"] \arrow[ur, "{e'}"swap] &
-			\end{tikzcd}\]
-			\caption{Equalizzatore}
-			\label{eq}
-		\end{subfigure}
 	\end{figure}
@@
 		\item Pushout di $f$ e $g$:  $Q = (A \coprod B)/_\sim$
-		\item Equalizzatore di $f$ e $g$: $E=\{x \in A \mid f(x) = g(x)\}$
 	\end{itemize}
@@
 \begin{frame}[fragile]\frametitle{Approccio DPO}
-	Sia $\cat C$ una categoria.
 	\begin{figure}[h]
@@
 
-	\begin{figure}
-		\includegraphics[width=0.4\linewidth]{imgs/fancyDPO}
-	\end{figure}
+	\begin{wrapfigure}{ri}{0.5\textwidth}
+		\includegraphics[width=0.7\linewidth]{imgs/fancyDPO}
+	\end{wrapfigure}
+
+	Risultati:
+	\begin{itemize}
+		\item Confluenza
+		\item Terminazione
+		\item Parallelismo e concorrenza
+	\end{itemize}
 \end{frame}
+
 \begin{frame}[fragile]\frametitle{Adesività}
@@
 		\item ha tutti i pullback
-		\item i pushout di monomorfismi sono \emph{Van Kampen} - ossia che tali pushout sono stabili stoot pullback e i pubblack sono stabili sotto pushout combinati con pullback
+		\item i pushout di monomorfismi sono \emph{Van Kampen}
+			\begin{itemize}
+				\item ossia che tali pushout sono stabili sotto pullback e i pullback sono stabili sotto pushout combinati con pullback
+			\end{itemize}
 	\end{itemize}
@@
 
-	Lavori futuri: sostituire la categoria $\Set$ con una qualsiasi categoria esatta e adesiva.
+	Lavori futuri: \begin{itemize}
+		\item Sostituire la categoria $\Set$ con una qualsiasi categoria adesiva
+		\item Generalizzare il risultato ad alti tipi di grafi, e.g., ipergrafi
+	\end{itemize}
 \end{frame}

### 2024-12-09 icgt/main.tex
iniziale

\documentclass[runningheads,envcountsect]{llncs}

\usepackage{stmaryrd}
\usepackage{bbding}
%\Envelope
\usepackage{amsmath,amsfonts,amssymb}
\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
\usepackage[all]{xy}

\usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
\usepackage[english]{babel} % Lingua principale inglese
\usepackage{graphicx} % Per includere immagini esterne
\usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}

\usepackage{csquotes}

%\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
\usepackage{hyperref, cleveref}

\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}

\newcommand{\Ob}{\mathcal{O}b}
\newcommand{\Hom}{\mathcal{H}om}
\newcommand{\Set}{\mathbf{Set}}
\newcommand{\Reg}{\mathcal{Reg}}
\newcommand{\Mono}{\mathcal{Mono}}
\newcommand{\initial}{\mymathbb{0}}
\newcommand{\terminal}{\mathds{1}}
\newcommand{\eg}[1]{\mathbf{EqGraph}_{\textbf {\textup{#1}}}}
\newcommand{\egg}[1]{\mathbf{EGG}_{\textbf {\textup{#1}}}}

\makeatletter
\def\@citecolor{blue}%
\def\@urlcolor{blue}%
\def\@linkcolor{blue}%
\def\UrlFont{\rmfamily}
\def\orcidID#1{\smash{\href{http://orcid.org/#1}{\protect\raisebox{-1.25pt}{\protect\includegraphics{orcid_color.eps}}}}}
\makeatother

\def\R{\mathsf{R}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\def\E{\textbf {\textup{E}}}

\bibliographystyle{abbrv}

\title{On the adhesivity properties of equivalence graphs\thanks{???????}}

\titlerunning{????} %TODO optional, please use if title is longer than one line

%% Author with single affiliation.
\author{Roberto Biondo \inst{1}{\small\Envelope}\and Davide Castelnovo\inst{1}\orcidID{0000-0002-5926-5615}
	\and \\Fabio Gadducci\inst{1}\orcidID{0000-0003-0690-3051}
}
\institute{Dept.~of Computer Science, University of Pisa, Italy. 
	\email{r.biondo@studenti.unipi.it},
	\email{castelnovod@gmail.com},
	 \email{fabio.gadducci@unipi.it}
}

%frecce
\newcommand{\mor}{\mathsf{Mor}}
\newcommand{\mon}{\mathsf{Mono}}
\newcommand{\reg}{\mathsf{Reg}}
\newcommand{\mto}{\rightarrowtail}
\newcommand{\eto}{\twoheadrightarrow}

\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}

\begin{document}

	\maketitle \todo{Scegliere un titolo vero e mettere i ringraziamenti}
	\begin{abstract}
\todo{a very nice abstract}
	\end{abstract}

\section{Introduction}
\todo{A very nice introduction}
\section{$\mathcal{M}$-adhesive categories}

This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}. Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects, so
``$X\in \X$'' means that $X$ is an object of $\X$. We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.  Given an integer $n\in \mathbb{Z}$, $[0,n]$ denotes the set of natural numbers less than or equal to $n$; in particular, $[0,n]=\emptyset$ if $n<0$.

\subsection{$\mathcal{M}$-adhesivity}\label{subsec:ade}
The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}. In order to define it we need to introduce some terminology.  Let  $\X$ be a category. A subclass $\mathcal{A}$ of
$\mor(\X)$ is called
\begin{itemize}
	\parbox{11cm}{\item
		\emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one on the right, 	if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
		\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable.{\tiny }}\hfill
	\parbox{2cm}{$\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}$}
	\parbox{11cm}{}\hfill
\end{itemize}

\begin{definition}[Van Kampen property]
	Let $\X$ be a category and consider the diagram\\
	\parbox{10cm}{
		aside.
		Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the bottom square
		is an \emph{$\mathcal{A}$-Van Kampen square} if
		\begin{enumerate}
			\item it is a pushout square;
			\item 	whenever the cube above has pullbacks as back and left faces and the vertical arrows belong to $\mathcal{A}$, then its top face is a pushout 
			if and only if the front and right faces are pullbacks.
	\end{enumerate}}
	\parbox{2cm}{$\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }$ }\\
	Pushout squares that enjoy only the ``if'' half of item (2) above are called \emph{$\mathcal{A}$-stable}.

	A $\mor(\X)$-Van Kampen square is called  \emph{Van
		Kampen} and a $\mor(\X)$-stable square  \emph{stable}.
\end{definition}

We can now define $\mathcal{M}$-adhesive categories.

\begin{definition}[$\mathcal{M}$-adhesive category]
	Let $\X$ be a category and $\mathcal{M}$ a subclass of
	$\mon(\X)$  including  all isomorphisms, closed under composition,  and stable under pullbacks and pushouts.  The category  $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
	\begin{enumerate}
		\item it has \emph{$\mathcal{M}$-pullbacks}, i.e.~pullbacks along arrows of $\mathcal{M}$;
		\item it has \emph{$\mathcal{M}$-pushouts}, i.e.~pushouts along arrows of $\mathcal{M}$;
		\item  $\mathcal{M}$-pushouts are $\mathcal{M}$-Van Kampen squares.
	\end{enumerate}

	A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
	if $\mathcal{M}$-pushouts are Van Kampen squares.
\end{definition}

We write $m\colon X\rightarrowtail Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.

\begin{remark}
	\label{rem:salva}
	\emph{Adhesivity} and \emph{quasiadhesivity} 
	\cite{lack2005adhesive,garner2012axioms} coincide with strict
	$\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity,
	respectively.
\end{remark}

$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of slice and functor categories \cite{mac2013categories}, as shown by the following theorems~\cite{ehrig2006fundamentals,lack2005adhesive}.

\begin{theorem}\todo{controllare meglio}
	\label{thm:slice-functors}
	Let $\X$ be an $\mathcal{M}$-adhesive category. Given an object $X$
	the category $\X/X$ is $\mathcal{M}/X$-adhesive with
	$\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
	\mathcal{M}\}$. Similarly, $X/\X$ is $X/\mathcal{M}$-adhesive with
	$X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}$.

	Moreover for every small category $\Y$, the category $\X^\Y$ of
	functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
	$\mathcal{M}^{\Y}:=\{\eta \in \mor(\X^\Y) \mid \eta_Y \in
	\mathcal{M} \text{ for every } Y\in \Y\}$.
\end{theorem}

We can list various examples of $\mathcal{M}$-adhesive categories (see
\cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).

\begin{example}
	\label{ex:adhesive}
	$\cat{Set}$ is adhesive, and, more generally, every topos is
	adhesive~\cite{lack2006toposes}. By the closure properties above, every presheaf $[\cat{X},\cat{Set}]$ is adhesive, thus the category
	$\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is adhesive
	where $E \rightrightarrows {V}$ is the two objects category with two
	morphisms $s,t \colon{E} \to {V}$. Similarly, various
	categories of hypergraphs can be shown to be adhesive, such as term
	graphs and hierarchical graphs~\cite{CastelnovoGM24}. Note that the category $\cat{sGraphs}$ of simple graphs, 
	i.e.~graphs without parallel edges, is
	$\reg{(\cat{sGraphs})}$-adhesive~\cite{BehrHK23} but not
	quasiadhesive.
\end{example}

\subsection{Kernel pairs}
\todo{Inserire parte della tesi su kp}
\subsection{Factorization systems}
\todo{Inserire qualche cosa su sist. di fattorizazzione e M-adesività - devo pensare a come mettere la questione senza prendere troppo spazio}

\section{Graphs with equivalences}

\subsection{Graph signatures}
\todo{Inserire def di graph signature}

\todo{Grafi su una segnatura sono adesivi (grafi)}

\todo{Inserire equivalenze (stesso discorso della tesi)}

\subsection{E-graphs}

\todo{Copincollare dalla tesi senza grandi modifiche}

\section{Conclusions and further works}
\todo{Some very nice conclusions}
\bibliography{biblio}

\appendix
\section{Comparison with Ghica}
\todo{Lo vogliamo fare?}

\end{document}

### 2024-12-09 Beamer/main.tex

@@
 
-        Una categoria $\cat C$ è composta da:
+        Una categoria $\cat C$ \`e composta da:
 	\begin{itemize}\item\emph{oggetti}\item\emph{morfismi} (o \emph{frecce})\end{itemize}
@@
 
-        La categoria i cui oggetti sono gli insiemi e i cui morfismi sono le funzioni tra essi è denominata $\Set$.
+        La categoria i cui oggetti sono gli insiemi e i cui morfismi sono le funzioni tra essi \`e denominata $\Set$.
 
@@
 
-        $f: A \to B$ può essere:
+        $f: A \to B$ pu\`o essere:
         \begin{itemize}
@@
                 \item un \emph{epimorfismo} : $g \circ f = h \circ f \Rightarrow g = h$;
-                \item un \emph{isomorfimso} : esiste $k$ tale che $f \circ k = id_B$ e $k \circ f = id_A$.
+                \item un \emph{isomorfismo} : esiste $k$ tale che $f \circ k = id_B$ e $k \circ f = id_A$.
         \end{itemize}
@@
 
-        Una \emph{trasformazione naturale} $\eta:F \dot\to G$: % è una mappa tra due funtori $F, G: \cat{C \to D}$, che assegna ad ogni oggetto $A$ di $\cat C$ un morfismo $\eta_A$ di $\cat D$. 
+        Una \emph{trasformazione naturale} $\eta:F \dot\to G$: %  una mappa tra due funtori $F, G: \cat{C \to D}$, che assegna ad ogni oggetto $A$ di $\cat C$ un morfismo $\eta_A$ di $\cat D$. 
     \[
@@
 
-	    Le categorie di funtori il cui codominio è $\Set$ sono dette \emph{categorie di prefasci}.
+	    Le categorie di funtori il cui codominio \`e $\Set$ sono dette \emph{categorie di prefasci}.
 
@@
 
-	Un grafo $G$ è costituito da:
+	Un grafo $G$ \`e costituito da:
 	\begin{itemize}
@@
 	\end{itemize}
-	In altre parole, un grafo è un elemento di $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$.
+	Un morfismo fra grafi \`e una coppia $f_V: V_1 \to V_2$, $f_E: E_1 \to E_2$ che rispetta sorgente e destinazione.
+
+	    \smallskip
+
+	In altre parole, un grafo \`e un oggetto della categoria $$[E \mathrel{\mathop{\rightrightarrows}^{s}_{t}} V , \Set]$$
 \end{frame}
@@
 
-	Un \emph{grafo con eqiuvalenza} $(G, \sim)$ è costituito da:
+	Un \emph{grafo con equivalenza} $(G, \sim)$ \`e dato da:
 	\begin{itemize}
 		\item Un grafo $G$
-		\item Una relazione di quivalenza $\sim$ definita sui vertici
+		\item Una relazione di equivalenza $\sim$ definita sui vertici
 	\end{itemize}
+
 	Ossia, un elemento di $[E \rightrightarrows V \to Q, \Set]$, tale che la freccia $q: V \to Q$ sia surgettiva (epi).
 
-	Un E-Grafo $(G, \sim)$ è un grafo con equivalenza tale che
+	Un E-Grafo $(G, \sim)$ \`e un grafo con equivalenza tale che
 	\[
@@
 
-	La categoria degli E-Grafi è detta $\Egg$, dal nome della libreria che li implementa in Rust.
+	La categoria degli E-Grafi \`e detta $\Egg$, dal nome della libreria che li implementa in Rust.
 
@@
 
-	La definizione attuale è troppo operativa per ottenere dei risultati teorici.
+	La definizione attuale \`e esplicitamente operativa, e risulta difficile per ottenere dei risultati teorici.
 
@@
 
-\section{Adesività}
+\section{Adesivit\`a}
 
@@
 		\item Pullback di $f$ e $g$: $ P = \{(x, y) \in A \times B \mid f(x) = g (y)\}$
-		\item Pushout di $f$ e $g$:  $Q = (A \coprod B)/_\sim$
+		\item Pushout di $f$ e $g$:  $Q = (A + B)/_\sim$
 	\end{itemize}
@@
 	\end{figure}
-	$l$ e $r$ sono due morfismi, possibilmente mono, di $\cat C$, 
-	mentre i due quadrati sono pushout.
+	$l$ e $r$ sono morfismi, il primo dei quali mono, di $\cat C$, 
+	mentre i quadrati sono pushout.
 
@@
 
-	Risultati:
+\smallskip
+
+	Tecniche per parlare di:
 	\begin{itemize}
@@
 
-\begin{frame}[fragile]\frametitle{Adesività}
+\begin{frame}[fragile]\frametitle{Adesivit\`a}
 
@@
 
-	Una categoria $\cat C$ è adesiva se:
+	Una categoria $\cat C$ \`e adesiva se:
 	\begin{itemize}
@@
 			\begin{itemize}
-				\item ossia che tali pushout sono stabili sotto pullback e i pullback sono stabili sotto pushout combinati con pullback
+				\item ossia tali pushout sono stabili sotto pullback e i pullback sono stabili sotto pushout combinati con pullback
 			\end{itemize}
@@
 
-	L'adesività permette di estendere l'approccio DPO a categorie più complesse come quelle dei grafi.
+	L'adesivit\`a permette di estendere l'approccio DPO a categorie di grafi pi\`u complesse.
 
@@
 \begin{frame}\frametitle{Conclusioni}
+	Nel lavoro di tesi abbiamo
 	\begin{itemize}
-		\item Formalizzazione degli E-Grafi mediante categorie
-		\item Adesività rispetto ad alcuni morfismi
+		\item Formalizzato gli E-Grafi mediante categorie di prefasci
+		\item Provato l'adesivit\`a rispetto a una sottoclasse di monomorfismi
 	\end{itemize}
 
-	Lavori futuri: \begin{itemize}
-		\item Sostituire la categoria $\Set$ con una qualsiasi categoria adesiva
-		\item Generalizzare il risultato ad alti tipi di grafi, e.g., ipergrafi
+	Come lavori futuri vogliamo \begin{itemize}
+		\item Sostituire la categoria $\Set$ con una generica categoria adesiva
+		\item Generalizzare il risultato ad altri tipi di grafi, e.g., ipergrafi e term graph
 	\end{itemize}

### 2025-01-28 icgt/main.tex
Kernel pairs

@@
 %\Envelope
-\usepackage{amsmath,amsfonts,amssymb}
 \newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
+\usepackage{amsmath,amsthm,amssymb,mathrsfs, dsfont} %simboli matematici
 \usepackage[all]{xy}
@@
 
-%\usepackage{amssymb,amsthm, amsmath, mathrsfs, dsfont} %simboli matematici
 \usepackage{hyperref, cleveref}
+
+% General Setting diagrams
+\usepackage{tikz-cd} %diagrammi
+\tikzcdset{row sep/normal=5em}
+\tikzcdset{column sep/normal=5em}
+\tikzcdset{every label/.append style = {font = \small}}
+
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{prop}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{cor}[theorem]{Corollary}
+
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{obs}[theorem]{Observation}
 
@@
 \todo{Inserire parte della tesi su kp}
+
+\subsection{Kernel Pairs and Regular Epimorphisms}
+
+\begin{definition}[Kernel Pair]
+    A \emph{kernel pair} for an arrow $f: A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f : K_f \to A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the following square is a pullback.
+    \[
+        \begin{tikzcd}
+            K_f \ar[r, "{\pi^1_f}"] \ar[d, "{\pi^2_f}" swap] & A \arrow[d, "f"] \\
+            A \ar[r, "f"swap] & B
+        \end{tikzcd}
+    \]
+\end{definition}
+
+\begin{remark}
+	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
+\end{remark}
+
+\begin{remark}
+    Since a kernel pair is nothing more that a pullback, that is, a limit, by \Cref{rem:limits_are_unique_up_to_isomorphisms}, it make sense to refer to it as \emph{the} kernel pair for a morphism $f$.
+\end{remark}
+
+\begin{example}\label{ex:kernel_pairs_in_Set}
+    In $\Set$, a kernel pair for a function $f: A\to B$ is the set
+    \[
+        K_f=\{(x, y) \in A \times A \mid f(x) = f(y)\}
+    \]
+    together with the canonical projection on the first and the second component of the pairs.
+\end{example}
+
+\begin{prop}\label{prop:pairng_of_kernel_pairs_mono}
+    Let $(K, p_1, p_2)$ be the kernel pair of $f: X \to Y$, and let $(X\times X, \pi_1, \pi_2)$ be the product of $X$ with itself.
+Then, the mediating arrow $\langle p_1, p_2\rangle : K \to X \times X$ is mono.
+\end{prop}
+
+\begin{proof}
+	Suppose $\langle p_1, p_2 \rangle \circ f = \langle p_1, p_2 \rangle \circ g$ for $f, g: Z \to K$. Then, we have
+	\[
+		\begin{split}
+			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
+			\pi_1 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_1 \circ \langle p_1, p_2 \rangle \circ g \\
+			p_1 \circ f &= p_1 \circ g
+		\end{split}
+		\qquad
+		\begin{split}
+			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
+			\pi_2 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_2 \circ \langle p_1, p_2 \rangle \circ g \\
+			p_2 \circ f &= p_2 \circ g
+		\end{split}
+	\]
+	Thus, from the universal property of the pullback, $f = g$.
+\end{proof}
+
+\begin{prop}\label{prop:kermono}
+	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
+\end{prop}
+
+\begin{proof}
+    To prove the ``if'' part of the statement, let $f, g: A \to M$ be such that $m\circ f = m\circ g$, and consider the following situation.
+    \[
+        \begin{tikzcd}[row sep=26, column sep = 26]
+        A \arrow[drr, bend left=30, "f"] \arrow[ddr, bend right=30,"g" swap] \arrow[dr, dashed, "u"] & & \\
+        & M  \arrow[d, "{id_M}"] \arrow[r, "{id_M}"] & M \arrow[d, "m"] \\
+        & M  \arrow[r, "m" swap] & X
+        \end{tikzcd}
+    \]
+    For the universal property of pullbacks, we have that $$f  =  id_M \circ u =  g$$
+    Hence, $m$ is mono.
+
+    Conversely, if $m$ is mono, then, we have that
+    \begin{align*}
+        m \circ f = m \circ g   &\Rightarrow    f = g \\
+                                &\Rightarrow    f \circ id_M = g\circ id_M
+    \end{align*}
+    Hence, $f$ is the unique arrow that makes the commutative square illustrated above a pushout.
+\end{proof}
+
+\begin{remark}\label{rem:monos_in_presh_cats}
+    From characterization of monos via pullbacks in \Cref{prop:kermono} and \Cref{lemma:limits_of_presheaves}, we have that a mono in a category of presheaves is a natural transformation of which each component is mono.
+\end{remark}
+
+\begin{cor}\label{cor:kermono}
+	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$ if and only if, for each mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
+\end{cor}
+\begin{proof}
+    It is enough to see that, by \Cref{lemma:pullback_lemma} and \Cref{prop:kermono} the outer boundary of the following square is a pullback.
+        \[\begin{tikzcd}[row sep=13 pt, column sep=13 pt]
+    	{K_f} && X && X \\
+    	\\
+    	X && Y && Y \\
+    	\\
+    	X && Y && Z
+    	\arrow["{\pi_f^2}", from=1-1, to=1-3]
+    	\arrow["{\pi_f^2}"', from=1-1, to=3-1]
+    	\arrow["{id_X}", from=1-3, to=1-5]
+    	\arrow["f", from=1-3, to=3-3]
+    	\arrow["f", from=1-5, to=3-5]
+    	\arrow["f", from=3-1, to=3-3]
+    	\arrow["{id_X}"', from=3-1, to=5-1]
+    	\arrow["{id_Y}", from=3-3, to=3-5]
+    	\arrow["{id_Y}", from=3-3, to=5-3]
+    	\arrow["m", from=3-5, to=5-5]
+    	\arrow["f"', from=5-1, to=5-3]
+    	\arrow["m"', from=5-3, to=5-5]
+    \end{tikzcd}\]
+    The leftward part of the statement follows by definition of monomorphism an \Cref{lemma:pullback_lemma}.
+\end{proof}
+
+\begin{lemma}\label{lemma:kern_pairs_pres_pullbacks}
+    Suppose the following situation, and that $f: X \to Y$ and $g: Z \to W$ have kernel pairs.
+    \[
+        \begin{tikzcd}
+            X \ar[r, "h"] \ar[d, "f"swap] & Z \ar[d, "g"] \\
+            Y \ar[r, "t"swap] & W
+        \end{tikzcd}
+    \]
+
+    Then, there exists a unique arrow $k_h: K_f \to K_g$ making the squares below commute.
+    \[
+        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
+            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^1}"swap] & K_g \ar[d, "{\pi_g^1}"] \\
+            X \ar[r, "h"swap] & Z 
+        \end{tikzcd}
+        \qquad
+        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
+            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^2}"swap] & K_g \ar[d, "{\pi_g^2}"] \\
+            X \ar[r, "h"swap] & Z 
+        \end{tikzcd}
+    \]
+
+    Moreover, if the beginning square is a pullback, then also the preceding ones are so.
+\end{lemma}
+
+\begin{proof}
+    Computing, we have
+    \begin{align*}
+        g \circ h \circ \pi_f^1 &=  t \circ f \circ \pi_f^1     \\
+                                &=  t \circ f \circ \pi_f^2     \\
+                                &=  g \circ h \circ \pi_f^2
+    \end{align*}
+    By the universal property of $K_g$ as the pullback of $g$ along itself, such $k_h$ exists and it is unique.
+
+    To prove the second half of the thesis, let us consider the two rectangles below, which, by \Cref{lemma:pullback_lemma} are pullbacks.
+    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
+	{K_f} & X & Z \\
+	X & Y & W
+	\arrow["{\pi_f^1}", from=1-1, to=1-2]
+	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
+	\arrow["h", from=1-2, to=1-3]
+	\arrow["f", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["f"', from=2-1, to=2-2]
+	\arrow["t"', from=2-2, to=2-3]
+    \end{tikzcd}
+    \qquad
+    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
+	{K_f} & X & Z \\
+	X & Y & W
+	\arrow["{\pi_f^2}", from=1-1, to=1-2]
+	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
+	\arrow["h", from=1-2, to=1-3]
+	\arrow["f", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["f"', from=2-1, to=2-2]
+	\arrow["t"', from=2-2, to=2-3]
+    \end{tikzcd}
+    \]
+    But then the following ones are pullbacks too.
+    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
+	{K_f} & {K_g} & Z \\
+	X & Y & W
+	\arrow["{k_h}"', from=1-1, to=1-2]
+	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
+	\arrow["{\pi_g^2}"', from=1-2, to=1-3]
+	\arrow["{\pi_g^1}", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["h", from=2-1, to=2-2]
+	\arrow["g", from=2-2, to=2-3]
+        \arrow["{h\circ \pi_f^2}", from=1-1, to=1-3, bend left = 30]
+        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
+    \end{tikzcd}
+    \qquad
+    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
+	{K_f} & {K_g} & Z \\
+	X & Y & W
+	\arrow["{k_h}"', from=1-1, to=1-2]
+	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
+	\arrow["{\pi_g^1}"', from=1-2, to=1-3]
+	\arrow["{\pi_g^2}", from=1-2, to=2-2]
+	\arrow["g", from=1-3, to=2-3]
+	\arrow["h", from=2-1, to=2-2]
+	\arrow["g", from=2-2, to=2-3]
+        \arrow["{h\circ \pi_f^1}", from=1-1, to=1-3, bend left = 30]
+        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
+    \end{tikzcd}
+    \]
+
+    The thesis follows again by \Cref{lemma:pullback_lemma}.
+\end{proof}
+
+\begin{prop}\label{prop:reg_epi_coeq}
+    Let $e: X \to Y$ be a regular epimorphism in a category $\cat C$ with a kernel pair $(K, \pi_1, \pi_2)$. Then, $e$ is the coequalizer of $\pi_1$ and $\pi_2$.
+\end{prop}
+
+\begin{proof}
+    By hypothesis, there exists a pair $f, g: Z \to X$ of which $e$ is the coequalizer. Since $e \circ f = e \circ g$, we have
+    \[
+        \begin{tikzcd}[row sep= 20, column sep = 13]
+            Z \ar[drr, "f", bend left=30] \ar[ddr, "g"swap, bend right=30] \ar[dr, dashed, "k"] & & \\
+            & K \ar[r, "{\pi_1}"] \ar[d, "{\pi_2}" swap] & X \ar[d, "e"] \\
+            & X \ar[r, "e"swap] & Y
+        \end{tikzcd}
+    \]
+    thus there exists the unique $k: Z \to K$. Let now $h: Z \to V$ be an arrow such that $h \circ \pi_1 = h \circ \pi_2$, then
+    \begin{align*}
+        h \circ f &= h \circ \pi_1 \circ k \\
+                  &= h \circ \pi_2 \circ k \\
+                  &= h \circ g
+    \end{align*}
+    and thus there exists a unique $l: Y \to V$ such that $l \circ e = h$.
+\end{proof}
+
+\begin{cor}\label{cor:reg_epi_components_reg_epi_nat_trans}
+    Let $\cat C$ be a category with pullbacks and $\phi : D \dot\to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
+If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
+\end{cor}
+
+\begin{proof}
+    Let $(K_i, \pi_i^1, \pi_i^2)$ be the kernel pair of $\phi_i$ for each $i$. Given an arrow $\alpha: i \to j$ of $\cat I$, we have
+    \begin{align*}
+        \phi_j \circ D(\alpha) \circ \pi_i^1 &= D'(\alpha) \circ \phi_i \circ \pi_i^1 \\
+                                             &= D'(\alpha) \circ \phi_i \circ \pi_i^2 \\
+                                             &= \phi_j \circ D(\alpha) \circ \pi_i^2
+    \end{align*}
+    Thus, the outer boundary of the diagram below commutes, yielding the arrow $K(\alpha)$
+    \[
+        \begin{tikzcd}[row sep=26, column sep=26]
+            {K_i} \ar[r, "{\pi_i^1}"] \ar[d, "{\pi_i^2}"swap] \ar[dr, dashed, "{K(\alpha)}"] & D(i) \ar[dr, "{D(\alpha)}"] \\
+            D(i) \ar[dr, "{D(\alpha)}"swap] & K_j \ar[r, "{\pi_j^1}"] \ar[d, "{\pi_j^2}"swap] & D(j) \ar[d, "{\phi_j}"] \\
+            & D(j) \ar[r, "{\phi_j}"swap] & D'(j)
+        \end{tikzcd}
+    \]
+
+    In this way, we get a functor $K: \cat{I \to C}$, 
+    which maps each $i$ onto $K_i$ and each arrow $\alpha$ onto $K(\alpha)$. 
+	We have in fact $K(id_i) : K_i \to K_i$ is the arrow such that
+        \[
+            \begin{split}
+                D(id_i) \circ \pi_i^1 &= \pi_i^1 \circ K(id_i) \\
+                \pi_i^1 &= \pi_i^1 \circ K(id_i)
+            \end{split}
+                \qquad
+            \begin{split}
+                D(id_i) \circ \pi_i^2 &= \pi_i^2 \circ K(id_i) \\
+                \pi_i^2 &= \pi_i^2 \circ K(id_i)
+            \end{split}
+        \]
+	Thus, for the universal property of pullbacks, $K(id_i) = id_{K_i}$.
+
+        Suppose now $\alpha : i \to j$ and $\beta: j \to k$. Computing, we have
+        \[
+            \begin{split}
+                \pi_k^1 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^1 \\
+                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^1 \\
+                                                    &= D(\beta) \circ \pi_j^1 \circ K(\alpha) \\
+                                                    &= \pi_k^1 \circ K(\beta) \circ K(\alpha)
+            \end{split} \qquad
+            \begin{split}
+                \pi_k^2 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^2 \\
+                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^2 \\
+                                                    &= D(\beta) \circ \pi_j^2 \circ K(\alpha) \\
+                                                    &= \pi_k^2 \circ K(\beta) \circ K(\alpha)
+            \end{split}
+        \]
+        Again, for universal property of pullbacks, necessarily we have $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving functoriality of $K$.
+
+     Hence, we have two natural transformations $\pi^1, \pi^2 : E \dot\to D$.
+By \Cref{prop:reg_epi_coeq}, every component $\phi_i$ is the coequalizer of $\pi_i^1, \pi_i^2: E \to D$, and so $\phi$ is the coequalizer of $\pi^1$ and $\pi^2$.
+\end{proof}
+
+\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
+    Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
+If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $\phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
+\end{lemma}
+
+\begin{proof}
+    By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi: D \dot\to D'$ is a regular epimorphism, so that there is a functor $E: \cat{I \to C}$ and $\eta, \theta: E \dot\to D$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
+Let now $((p_i)_{i \in \cat I}, P)$ be the colimit of $E$, by \Cref{prop:nat_tran_induces_unique_arrow_between_colimits}, we have $a, b: P \to C$ fitting in the diagram below.
+    \[
+        \begin{tikzcd}[row sep = 26, column sep = 26]
+            E(i) \ar[r, "{p_i}"] \ar[d, "{\eta_i}"swap] & P \ar[d, dashed, "a"] \\
+            D(i) \ar[r, "{c_i}"swap] & C
+        \end{tikzcd}
+        \qquad
+        \begin{tikzcd}[row sep = 26, column sep = 26]
+            E(i) \ar[r, "{p_i}"] \ar[d, "{\theta_i}"swap] & P \ar[d, dashed, "b"] \\
+            D(i) \ar[r, "{c_i}"swap] & C
+        \end{tikzcd}
+    \]
+
+    We want to show that $c$ coequalizes $\eta$ and $\theta$. Let thus $t: C \to T$ be an arrow such that $t \circ a = t \circ b$. Then, for every $i$, we have
+    \begin{align*}
+        t \circ c_i \circ \eta_i &= t \circ a \circ p_i \\
+                                 &= t \circ b \circ p_i \\
+                                 &= t \circ c_i \circ \theta_i
+    \end{align*}
+
+    Thus, there is $t_i: D(i) \to T$ such that $t\circ c_i = t_i \circ \phi_i$.
+It is now easy to see that $((t_i)_{i \in \cat I}, T)$ is a cocone of $D'$: suppose $\alpha: i \to j$ be an arrow of $\cat I$, obtaining
+    \begin{align*}
+        t_i \circ \phi_i &= t \circ c_i \\
+                         &= t \circ c_j \circ D(\alpha) \\
+                         &= t_j \circ \phi_j \circ D(\alpha) \\
+                         &= t_j \circ D'(\alpha) \circ \phi_i
+    \end{align*}
+    By the hypothesis that $\phi_i$ is regular epi for each $i$, therefore epi (by the dual of \Cref{prop:eq_are_mono}), we can conclude $t_i = t_j \circ D'(\alpha)$.
+
+    Hence, we have an arrow $k: C' \to T$ such that $k \circ c_i' = t_i$. But then
+    \begin{align*}
+        c \circ c \circ c_i &= k \circ c_i' \circ \phi_i \\
+                            &= t_i \circ \phi \\
+                            &= t \circ c_i
+    \end{align*}
+    Showing that $k \circ c = t$.
+
+    For the uniqueness, let $k': C' \to T$ be another arrow such that $k' \circ c = t$. Then we have
+    \begin{align*}
+        k' \circ c_i' \circ \phi_i &= k' \circ c \circ c_i \\
+                                   &= t \circ c_i \\
+                                   &= t_i \circ \phi_i
+    \end{align*}    
+    Since $\phi_i$ is a regular epimorphism, we have $k' \circ c_i' = t_i$, and, because $k \circ c_i' = t_i$ by construction, we can conclude that $k'=k$ since $((c_i')_{i \in \cat I}, C')$ is a colimit.
+\end{proof}
+
 \subsection{Factorization systems}

### 2025-01-28 icgt/main.tex
Kernel pairs
minori
ipergrafi

@@
 \newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
-\usepackage{amsmath,amsthm,amssymb,mathrsfs, dsfont} %simboli matematici
-\usepackage[all]{xy}
+\usepackage{amsmath,amssymb,mathrsfs, dsfont} %simboli matematici
+\usepackage[all, cmtip]{xy}
 
@@
 \usepackage[tickmarkheight=.5em,textwidth=\marginparwidth,textsize=small]{todonotes}
-
+\usepackage{mathtools}
 \usepackage{csquotes}
@@
 \usepackage{hyperref, cleveref}
+\usepackage{tikz}
+\usetikzlibrary{decorations.markings}
 
 % General Setting diagrams
-\usepackage{tikz-cd} %diagrammi
-\tikzcdset{row sep/normal=5em}
-\tikzcdset{column sep/normal=5em}
-\tikzcdset{every label/.append style = {font = \small}}
+%\usepackage{tikz-cd} %diagrammi
+%\tikzcdset{row sep/normal=5em}
+%\tikzcdset{column sep/normal=5em}
+%\tikzcdset{every label/.append style = {font = \small}}
 
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{cor}[theorem]{Corollary}
+\spnewtheorem*{notation}{Notation}{\bfseries}{}
 
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{obs}[theorem]{Observation}
+%funtori
+\usepackage[usestackEOL]{stackengine}
+\newcommand\functorop[1][l]{\csname#1functor\endcsname}
+\newcommand\lfunctorop[3]{%
+	\setbox0=\hbox{$#2$}%
+	\kern\wd0%
+	\ensurestackMath{\Centerstack[c]{#1\\ \mathllap{#2\;\,}\mathclap{\DownArrow}\\#3}}%
+}		
+\newcommand\rfunctorop[3]{%
+	\setbox0=\hbox{$#2$}%
+	\ensurestackMath{\Centerstack[c]{#1\\\mathclap{\UpArrow}\mathrlap{\,\;#2}\\#3}}%
+	\kern\wd0%
+}
+\newcommand\functoropmapsto{\mathrel{\ensurestackMath{\Centerstack[c]{\longmapsto\\ \\\longmapsto}}}}
+\setstackgap{L}{1.3\normalbaselineskip}
+\newcommand\UpArrow{\rotatebox[origin=c]{90}{$\longrightarrow$\,}}
+\newcommand\DownArrow{\rotatebox[origin=c]{-90}{$\longrightarrow$\,}}
+\newcommand\functor[1][l]{\csname#1functor\endcsname}
+\newcommand\lfunctor[3]{%
+	\setbox0=\hbox{$#2$}%
+	\kern\wd0%
+	\ensurestackMath{\Centerstack[c]{#1\\ \mathllap{#2\;\,}\mathclap{\DownArrow}\\#3}}%
+}
+\newcommand\rfunctor[3]{%
+	\setbox0=\hbox{$#2$}%
+	\ensurestackMath{\Centerstack[c]{#1\\\mathclap{\DownArrow}\mathrlap{\,\;#2}\\#3}}%
+	\kern\wd0%
+}
+\newcommand\functormapsto{\mathrel{\ensurestackMath{\Centerstack[c]{\longmapsto\\ \\\longmapsto}}}}
+\setstackgap{L}{1.3\normalbaselineskip}
 
@@
 
+%categorie varie
+\newcommand{\catname}[1]{\textbf{\textup{#1}}}
+\newcommand{\lab}{\catname{LHyp}}
+\newcommand{\hyp}{\catname{Hyp}}
+\newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
+\newcommand{\gr}{\textbf{\textup{Graph}}}
+\newcommand{\dgr}{\catname{SGraph}}
+\newcommand{\dg}{\catname{DAG}}
+\newcommand{\rt}{\mathsf{dcl_s}}
+\newcommand{\rta}{\mathsf{dcl}}
+\newcommand{\rtd}{\mathsf{dcl_{d}}}
+\newcommand{\slice}[2]{(\catname{#1}\downarrow{#2})}
+\newcommand{\tg}[0]{\catname{TG}_{\Sigma}}
+\newcommand{\teg}[0]{\catname{TeGr}_{\Sigma}}
+\newcommand{\sv}[0]{\mathsf{Sieves}}
+\newcommand{\mono}[1]{\mathcal{M}({#1})}
+\newcommand{\pro}{\mathsf{prod}}
+\newcommand{\spro}{\mathsf{ps}}
+\newcommand{\prol}{\mathsf{lprod}}
+\newcommand{\pred}[1]{{\downarrow}#1}
+\newcommand{\colim}[0]{\mathrm{colim}}
+\newcommand{\cod}{\mathsf{cod}}
+\renewcommand{\sp}{\mathsf{sp}}
+\renewcommand{\sup}{\mathsf{sup}}
+\newcommand{\cow}[1]{\mathsf{cwd}({#1})}
+\renewcommand{\inf}{\mathsf{inf}}
+\newcommand{\dom}{\mathsf{dom}}
+\newcommand{\dwnarrow}{\downarrow \hspace{-2pt}}
+\newcommand{\Dwnarrow}{\Downarrow \hspace{-2pt}}
+
+\newcommand{\ari}{\mathsf{ar}}
+\newcommand{\abs}[1]{\lvert #1\rvert}
+
+\newcommand{\upstr}[1] { {#1}^{\uparrow }}
+\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}#2}
+\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}
+
 \bibliographystyle{abbrv}
+
+%frecce
+\newcommand{\mor}{\mathsf{Mor}}
+\newcommand{\mon}{\mathsf{Mono}}
+\newcommand{\reg}{\mathsf{Reg}}
+\newcommand{\mto}{\rightarrowtail}
+\newcommand{\eto}{\twoheadrightarrow}
+\newcommand{\id}[1]{\mathsf{id}_{#1}}
 
@@
 
-%frecce
-\newcommand{\mor}{\mathsf{Mor}}
-\newcommand{\mon}{\mathsf{Mono}}
-\newcommand{\reg}{\mathsf{Reg}}
-\newcommand{\mto}{\rightarrowtail}
-\newcommand{\eto}{\twoheadrightarrow}
-
 \authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
@@
 
+\tikzset{->-/.style={decoration={
+			markings,
+			mark=at position #1 with {\arrow{>}}},postaction={decorate}}}
 	\maketitle \todo{Scegliere un titolo vero e mettere i ringraziamenti}
@@
 
+\todo{Va riscritta tutta con xy}
+
 This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.
+
+\begin{notation}
+	contenuto...
+\end{notation}
 Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects, so
@@
 
-\subsection{Kernel pairs}
 \todo{Inserire parte della tesi su kp}
-
+\iffalse 
 \subsection{Kernel Pairs and Regular Epimorphisms}
@@
 
-\begin{prop}\label{prop:pairng_of_kernel_pairs_mono}
+\begin{proposition}\label{prop:pairng_of_kernel_pairs_mono}
     Let $(K, p_1, p_2)$ be the kernel pair of $f: X \to Y$, and let $(X\times X, \pi_1, \pi_2)$ be the product of $X$ with itself.
 Then, the mediating arrow $\langle p_1, p_2\rangle : K \to X \times X$ is mono.
-\end{prop}
+\end{proposition}
 
@@
 
-\begin{prop}\label{prop:kermono}
+\begin{proposition}\label{prop:kermono}
 	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
-\end{prop}
+\end{proposition}
 
@@
 
-\begin{cor}\label{cor:kermono}
+\begin{corollary}\label{cor:kermono}
 	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$ if and only if, for each mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
-\end{cor}
+\end{corollary}
 \begin{proof}
@@
 
-\begin{prop}\label{prop:reg_epi_coeq}
+\begin{proposition}\label{prop:reg_epi_coeq}
     Let $e: X \to Y$ be a regular epimorphism in a category $\cat C$ with a kernel pair $(K, \pi_1, \pi_2)$. Then, $e$ is the coequalizer of $\pi_1$ and $\pi_2$.
-\end{prop}
+\end{proposition}
 
@@
 
-\begin{cor}\label{cor:reg_epi_components_reg_epi_nat_trans}
+\begin{corollary}\label{cor:reg_epi_components_reg_epi_nat_trans}
     Let $\cat C$ be a category with pullbacks and $\phi : D \dot\to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
 If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
-\end{cor}
+\end{corollary}
 
@@
 \todo{Inserire qualche cosa su sist. di fattorizazzione e M-adesività - devo pensare a come mettere la questione senza prendere troppo spazio}
+\fi
 
-\section{Graphs with equivalences}
+\section{Hypergraphical structures}
+\todo{A very nice introduction}
 
-\subsection{Graph signatures}
-\todo{Inserire def di graph signature}
+\subsection{The category of hypergraphs}
 
-\todo{Grafi su una segnatura sono adesivi (grafi)}
+We will start this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
 
-\todo{Inserire equivalenze (stesso discorso della tesi)}
+A pivotal role will be played by the Kleene star $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{...}.
+In particular, given a set $X$, $X^\star$ is the set of functions with a natural number as domain.
+Then the neutral element is $?_X\colon \emptyset \to X$ and the composition of $f\colon n\to X$ with $g\colon m\to X$ is simply the arrow $n+m\to X$ induced by them.
+If $h\colon X\to Y$ is an arrow in $\Set$, then $h^\star \colon \X^\star\to Y^\star$ is the composition with $h$.
 
-\subsection{E-graphs}
+\begin{definition}A \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, whose elements are called respectively \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} functions  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
+A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute.
 
-\todo{Copincollare dalla tesi senza grandi modifiche}
+	\[\xymatrix{ E_{\mathcal{G}} \ar[d]_{h} \ar[r]^{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}& E_{\mathcal{G}} \ar[r]^{t_{\mathcal{G}}} \ar[d]_{h} & V^\star_{\mathcal{G}} \ar[d]^{k^\star}  \\ E_{\mathcal{G}} \ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} & E_{\mathcal{G}} \ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} }\]
+	We define $\hyp$ to be the resulting category.
+\end{definition}
+
+Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$, then we can present $\hyp$ as a comma category.
+\begin{proposition}\label{prop:com}
+	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
+\end{proposition}
+\begin{proof}
+	 Define two functors $F\colon  \hyp \to \comma{\id{\Set}}{\pro^\star} $
+	and $G\colon \comma{\id{\Set}}{\pro^\star}\to \hyp$	 as follows 
+	\begin{align*}
+		\functor[l]{(E_\mathcal{{G}}, V_\mathcal{{G}}, s_\mathcal{{G}}, t_\mathcal{{G}})}{(f,g)}{\left(E_\mathcal{{H}}, V_\mathcal{{H}}, s_\mathcal{{H}}, t_\mathcal{{H}}\right)}
+		\functormapsto
+		\rfunctor{\left(E_\mathcal{{G}}, V_\mathcal{{G}}, 	\left(s_\mathcal{{G}}, t_\mathcal{{G}}\right)\right)}{(f, g) }{\left(E_\mathcal{{H}}, V_\mathcal{{H}}, \left(s_\mathcal{{H}}, t_\mathcal{{H}}\right)\right)}
+	\end{align*}
+	 \begin{align*}
+		\functor[l]{(E_\mathcal{{G}}, V_\mathcal{{G}}, p_{\mathcal{G}})}{(f,g)}{(E_\mathcal{{H}}, V_\mathcal{{H}}, p_{\mathcal{H}})}
+		\functormapsto
+		\rfunctor{(E_\mathcal{{G}}, V_\mathcal{{G}}, 	\pi_1\circ  p_{\mathcal{G}}, \pi_2\circ  p_{\mathcal{G}})}{(f, g) }{(E_\mathcal{{H}}, V_\mathcal{{H}}, 	\pi_1\circ  p_{\mathcal{H}}, \pi_2\circ  p_{\mathcal{H}})}
+	\end{align*} 
+	Now it is immediate to notice that they are one the inverse of the other.
+\end{proof}
+
+We can show that the  Kleene star preserves pullbacks (see also \cite[Sec.
+3]{carboni1995connected}  and \cite[Ch.4]{leinster2004higher} for details and a deeper and more conceptual approach).\index{Kleene star}
+
+\begin{proposition}\label{prop:pb}
+	The functor $(-)^\star$ preserves pullbacks.
+\end{proposition}
+\begin{proof}
+	Suppose that a pullbacks square as the one below is given.
+	\[\xymatrix{P \ar[r]^{p_1} \ar[d]_{p_2}& X \ar[d]^{f}\\ Y \ar[r]_{g} & Z}\]
+	and consider the solid part of the following diagram.
+	\[\xymatrix{Z\ar@{.>}[dr]^{t} \ar@/^.3cm/[drr]^{t_1} \ar@/_.3cm/[ddr]_{t_2}\\&P^\star \ar[r]^{p^\star_1} \ar[d]_{p^\star_2}& X^\star \ar[d]^{f^\star}\\ &Y^\star \ar[r]_{g^\star} & Z^\star}\]
+	For every $z\in Z$ we have $t_1(z)\colon n\to X$ and $t_2(z)\colon m\to Y$ such that
+	\[f^\star(t_1(x))=g^\star(t_2(z))\]
+	In particular this entails that $n=m$ and that there is $t(z)\colon n\to P$ as in the diagram below 
+	\[\xymatrix{n\ar[dr]^{t(z)} \ar@/^.3cm/[drr]^{t_1(z)} \ar@/_.3cm/[ddr]_{t_2(z)}\\&P \ar[r]^{p_1} \ar[d]_{p_2}& X \ar[d]^{f}\\ &Y \ar[r]_{g} & Z}\]
+	But this is equivalent to say that the dotted $t\colon Z\to P$ exists, while its uniqueness follows at once from the universal property of the pullback with which we started.
+\end{proof}
+
+\begin{remark}\label{rem:mono}
+	Preservation of pullbacks implies that $(-)^\star$ sends monos to monos.
+\end{remark}
+
+\begin{corollary}\label{prop:hypadh}
+	$\hyp$ is an adhesive category.
+\end{corollary}
+\begin{proof}
+	$(-)^\star$ preserves pullbacks by \Cref{prop:pb}, while $\pro$ is continuous by definition, thus the thesis follows from This follows from \Cref{comma,prop:com}.
+\end{proof}
+
+\Cref{prop:left,prop:com} allows us to deduce immediately the following.
+
+\begin{proposition}\label{cor:left}
+	The forgetful functor $U_{\catname{Hyp}}\colon \hyp \to \catname{Set}$ which sends an hypergraph $\mathcal{G}$ to its set of nodes has a left adjoint $\Delta_{\hyp}$.
+\end{proposition}
+
+\begin{remark}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\hyp}(X)$ is the hypergraph which has $X$ as set of nodes and $\emptyset$ as set of hyperedges and $?_X$ as both source and target function.
+\end{remark}
+
+Hypergraphs,  can be represented graphically.
+We will use dots to denote nodes and squares to denote hyperedges, the name of a node or of an hyperedge will be put near the corresponding dot or square.
+Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge will have an arrowhead in the middle pointing towards the hyperedge, while the lines to the targets will have arrowheads pointing to the target nodes.
+We will decorate the arrow corresponding to the $i^{th}$ letter (i.e.~its value at $i-1$) of a target or a source with a label $i$.
+
+\begin{example}Take $V_{\mathcal{G}}$ to be be $\{v_1, v_2, v_3, v_4, v_5\}$ and $E_{\mathcal{G}}$ to be $\{h_1, h_2, h_3\}$. Sources and targets are given by:
+	\[\begin{matrix}
+		s_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}}  & \begin{matrix}
+			0 \mapsto v_1\\
+			1\mapsto v_2
+		\end{matrix} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+			0 \mapsto v_3\\
+			1\mapsto v_4 
+		\end{matrix} && s_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 
+		0 \mapsto v_5\\
+		t_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+			0 \mapsto v_3\\
+			1\mapsto v_4
+		\end{matrix} && t_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & 0\mapsto v_5 && t_{\mathcal{G}}(h_3)\colon 0\to V_{\mathcal{G}} &  t_{\mathcal{G}}(h_3)=?_{ V_{\mathcal{G}}} 
+	\end{matrix}\]
+
+	We can draw the resulting $\mathcal{G}$ as follows:
+	\begin{center}\begin{tikzpicture}
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-1.5) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_5$}] (E) at (6,-0.75) {};
+			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
+			\draw[->-=.5](4.75,-0.75)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](E)--(7,-0.75)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (4.25, -1) rectangle (4.75, -0.5) {};
+			\node at (4.5, -0.3){$h_2$};
+			\node at (1.5, -0.3){$h_1$};
+			\node at (7.25, -0.3){$h_3$};
+			\draw[rounded corners] (7, -1) rectangle (7.5, -0.5) {};
+			\draw(A)[->-=.5]..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw(B)[->-=.5]..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\draw(C)[->-=.5]..controls(3.5,0)and(4.2,-0.25)..(4.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw(D)[->-=.5]..controls(3.5,-1.5)and(4.2,-1.3)..(4.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\draw[->-=.5](1.75,-0.9)..controls(1.8,-1.3)and(2.5,-1.5)..(D)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+			\draw[->-=.5] (1.75,-0.6)..controls(1.8,-0.25)and(2.5,0)..(C) node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+		\end{tikzpicture}
+	\end{center}
+\end{example}
+\begin{example}\label{exa_2} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
+	\[\begin{matrix}
+		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+			0 \mapsto v_1\\
+			1\mapsto v_2
+		\end{matrix}&& s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
+			0 \mapsto v_1\\
+			1\mapsto v_4	
+		\end{matrix}\\
+		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
+		0 \mapsto v_1 && 		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&   t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5
+	\end{matrix}\]
+
+	Now we can depict $\mathcal{G}$ as
+	\begin{center}\begin{tikzpicture}
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,-0.75) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-2.25) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=right:{$v_5$}] (E) at (6,-1.5) {};
+			\draw[->-=.5] (1.75,-0.75)--(C)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
+			\draw[->-=.5] (4.75,-1.5)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (-1.5,0)--(A)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (4.25, -1.75) rectangle (4.75, -1.25) {};
+			\node at (4.5, -1.05){$h_3$};
+			\node at (1.5, -0.3){$h_2$};
+			\node at (-1.75, 0.45){$h_1$};
+			\draw[rounded corners] (-2, -0.25) rectangle (-1.5, 0.25) {};
+			\draw[->-=.5] (A)..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (B)..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\draw[->-=.5] (C)..controls(3.5,-0.75)and(4.2,-0.95)..(4.25,-1.35)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (D)..controls(3.5,-2.25)and(4.2,-2.05)..(4.25,-1.65)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+		\end{tikzpicture}
+	\end{center}
+\end{example}
+
+\begin{example}\label{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature, we can construct the hypergraph $\mathcal{G}^\Sigma$ taking $V_{\mathcal{G}^\Sigma}$ and $E_{\mathcal{G}^\Sigma}$ to be respectively the singleton $\{\heartsuit\}$ and the set $O_\Sigma$.
+We put
+	\[\begin{matrix}
+		s_{\mathcal{G}^\Sigma}\colon O_\Sigma\to \{\heartsuit\}^\star & o\mapsto \delta_\heartsuit^{\ari_\Sigma(o)}
+		&&
+		t_{\mathcal{G}^\Sigma}\colon O_\Sigma\to \{\heartsuit\}^\star & o\mapsto \delta_\heartsuit
+	\end{matrix}\]
+	For instance let $\Sigma_G$ be the signature of groups of \Cref{ex:g}, then $\mathcal{G}^{\Sigma_G}$ is depicted as:
+	\begin{center}
+		\begin{tikzpicture}
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v$}] (V) at (0,0) {};
+			\node(E)at(-2, 0.4){$e$};
+			\node(M)at(0, 2.15){$\cdot$};
+			\node(I)at(2, 0.5){$(-)^{-1}$};
+			\draw[->-=.5](-1.75,0)--(V)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](V)..controls(-0.5,0.5)and(-0.8,1)..(-0.25,1.6)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$2$};
+			\draw[->-=.5](V)..controls(-1,0.6)and(-1,1.1)..(-0.25,1.9)node[pos=0.5, left,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](0.25,1.75)..controls(0.8,0.8)and(0.5,0.5)..(V)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](V)--(1.75,0)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](2.25,0)..controls(3.5,0)and(2.5,-2)..(V)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+			\draw[rounded corners] (-2.25, -0.25) rectangle (-1.75, 0.25) {};
+			\draw[rounded corners] (-0.25, 1.5) rectangle (0.25, 2) {};
+			\draw[rounded corners] (2.25, -0.25) rectangle (1.75, 0.25) {};
+		\end{tikzpicture}
+	\end{center}
+\end{example}
+
+\subsubsection{$\hyp$ as a topos of presheaves}
+
+By \Cref{lim} we already know that $\hyp$ has all pullbacks and by \Cref{prop:hypadh} we know that it is adhesive.
+Actually more can be proved about it: we can realize $\hyp$ as a topos of presheaves \cite{bonchi2022string}.
+
+\begin{definition}Let $\catname{H}$ be the category in which:
+	\begin{itemize}
+		\item the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$
+		\item arrows are given by the identities $\id{k,l}$ and $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$;
+		\item composition is defined simply putting, for every $f_i\colon (k,l)\rightarrow \bullet$:
+		\begin{equation*}
+			f_i=f_i\circ \id{k,l} \qquad f_i = \id{\bullet}\circ f_i 
+		\end{equation*}
+	\end{itemize}
+\end{definition}
+
+Now, given $F\colon \catname{H}\to \catname{Set}$ we can define
+\[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
+For every element $x$ of $F(k,l)$ we can put
+\begin{align*}
+	s^F_{k,l}(x)\colon k\to F(\bullet) \quad i \mapsto F(f_i)(x)\qquad 
+	t^F_{k,l}(x)\colon l\to F(\bullet) \quad i \mapsto F(f_{i+k})(x)
+\end{align*}
+obtaining
+$s_F, t_F\colon E_F\rightrightarrows \mathcal{F}(\bullet)^{\star}$.
+Let $\mathcal{G}_F$ be the resulting hypergraph.
+Now, every $\eta\colon F\rightarrow H$ in $\catname{Set}^{\catname{H}}$ has components $\eta_{k,l}\colon F(k,l)\to H(k,l)$, $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$, thus it induces a function $\hat{\eta}\colon E_F\rightarrow E_H$ such that the following squares commute
+\[\xymatrix{ E_F \ar[r]^{s_F} \ar[d]_{\hat{\eta}}& F(\bullet)^\star \ar[d]^{\eta^\star_\bullet} & E_F \ar[r]^{t_F} \ar[d]_{\hat{\eta}} & F(\bullet)^\star \ar[d]^{\eta^\star_\bullet}\\ E_H \ar[r]_{s_H} & H(\bullet)^\star & E_H \ar[r]_{t_H}& H(\bullet)^\star}\]
+
+This is equivalent to say that $\eta$ induces a morphism $(\hat{\eta}, \eta_{\bullet})\colon \mathcal{G}_F\to \mathcal{G}_H$.
+It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \catname{Set}^{\catname{H}}\to \hyp$.
+
+\begin{proposition}
+	$\hyp$ is equivalent to the category $\catname{Set}^{\catname{H}}$.
+\end{proposition}
+\begin{proof}
+	Let $X$ be a set, for every $n\in \mathbb{N}$ define
+	\[X_{n}:= \left\{w\in X^{\star} \mid \dom(w)=n\right\}\]
+	In particular, if $F\colon \catname{H}\to \catname{Set}$ then the image of the coprojection $\iota^{F}_{k,l}\colon F(k,l)\to E_F$ is the intersection
+	\[s^{-1}_F\left(F(\bullet)_{k}\right)\cap t^{-1}_F\left(F(\bullet)_{l}\right) \]
+
+	We are now ready to that $\mathcal{G}_{-}$ is full and essentially surjective.
+	\begin{itemize}
+		\item For fullness, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of hypergraphs and define $f_{k,l}$ to be $f\circ \iota^F_{k,l}$, the composition of $h$ with Now, if $x\in F(k,l)$ then
+		\[\begin{split}
+			s_H (f_{k,l} (x))&=s_H \left(f \left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt}\left(s_{F} \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)
+		\end{split}\qquad \begin{split}
+			t_H (f_{k,l} (x))&=s_t\hspace{-1pt} \left(f \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt} \left(t_{F}\hspace{-1pt} \left(\iota^F_{k,l} (x)\right)\right)
+		\end{split}\]
+		Therefore there exists $\eta_{k,l}\colon F(k,l)\to H(k,l)$ fitting in the diagram below
+		\[\xymatrix{F(k,l) \ar[r]^-{\iota^{F}_{k,l}} \ar@{.>}[d]_{\eta_{k,l}}& E_F \ar[d]^{f_{k,l}}\\ H(k,l) \ar[r]_-{\iota^{H}_{k,l}}& E_H}\]
+		Define $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ simply as $g^\star$, then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
+Indeed, if $f_i\colon (k,l)\to \bullet$ we have:
+		\[\xymatrix{F(k,l) \ar@/^.4cm/[rr]^{s^F_{k,l}} \ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{s_F}& F(\bullet)^\star \ar[d]^{g^\star}&F(k,l) \ar@/^.4cm/[rr]^{t^F_{k,l}}\ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{t_F}& F(\bullet)^\star \ar[d]^{g^\star}\\ H(k,l) \ar@/_.4cm/[rr]_{s^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{s_H}& H(\bullet)^\star& H(k,l) \ar@/_.4cm/[rr]_{t^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{t_H}& H(\bullet)^\star}\]
+		Thus if $i<k$ then
+		\begin{align*}
+			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(s^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(s^F_{k,l}(x)\right)(i)\\&=s^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
+		\end{align*}
+		while, if $k\leq i < k+l-1$
+		\begin{align*}
+			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(t^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(t^F_{k,l}(x)\right)(i)\\&=t^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
+		\end{align*}
+		Finally, by contruction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$. 
+		\item Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define 
+		\[F_{\mathcal{G}}(k,l):=s_\mathcal{G}^{-1}(V_k)\cap t_\mathcal{G}^{-1}(V_l) \qquad F_{\mathcal{G}}(\bullet):=V_\mathcal{G}\]
+		Given $f_i\colon (k,l)\to \bullet$ we put
+		\[F_{\mathcal{G}}(f_i)\colon F_{\mathcal{G}}(k,l)\to F_{\mathcal{G}}(\bullet) \qquad x\mapsto \begin{cases}
+			s_\mathcal{G}(x)(i) & i<k\\
+			t_\mathcal{G}(x) (i-k) &i\leq k < k+l-1
+		\end{cases}  \]
+
+		$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$ and for every $h\in E_\mathcal{G}$ there exists a unique pair $(k,l)$ such that $h\in F_{\mathcal{G}}(k,l) $, namely the pair $(\dom(s_\mathcal{G})(h), \dom(t_\mathcal{G})(h))$thus
+		\[\sum_{k,l\in \mathbb{N}}F_{\mathcal{G}}(k,l)\simeq E\]
+		Moreover, by construction $s_{F_{\mathcal{G}}}=s$ and $t_{F_{\mathcal{G}}}=t$, from which the thesis follows. 
+	\end{itemize}
+\end{proof}
+As a corollary we get immediately the following.
+\begin{corollary}
+	$\hyp$ is a complete category.
+\end{corollary}
+
+\subsection{Labelling hypergraph with an algebraic signature}\index{signature!algebraic -}
+Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature, we are going to use the hypergraph $\mathcal{G}^{\Sigma}$ of \Cref{exa_3} in order to label hyperedges with operations.
+\begin{definition}Let $\Sigma=(O, \ari)$ be an algebraic signature, the category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.\index{hypergraph!algebraically labelled -}
+\end{definition}
+\Cref{cor:mono} and \Cref{cor:slice} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterization of monomorphisms in it.
+\begin{proposition}\label{prop:mono}
+	For every algebraic signature $\Sigma$, $\hyps$ is an adhesive category.
+Moreover a morphism $(h,k)$ between two object of $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions.
+\end{proposition}
+
+\begin{remark}\label{rem:label}	
+	Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, since  $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the singleton an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  such that, for every $e\in E_{\mathcal{H}}$
+	\[\ari_\Sigma(h(e))=s_\mathcal{H}(e)\]
+
+	On the other hand, if $\mathcal{H}$ has an hyperedge $e$ such that $t_{\mathcal{H}}(e)$ has a length different from $1$, then there is no morphism $\mathcal{H}\to \mathcal{G}^{\Sigma}$.
+Indeed, if such a morphism $(h,!_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^\Sigma$ exists, then, for every $e\in E_{\mathcal{H}}$ we have
+	\begin{align*}
+		f^{\star}(t_{\mathcal{H}}(h))&=t_{\mathcal{G}^{\Sigma}}(f(h))\\&=\delta_\heartsuit
+	\end{align*}
+	and so $\dom(t_{\mathcal{H}}(h))=1$.  
+\end{remark}
+
+$\hyp_{\Sigma}$, as any slice category, has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \catname{Set}$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\hyp}(\mathcal{H}$).
+Now, $U_{\hyp}(\mathcal{G}^{\Sigma})=\{v\}$ thus, for every set $X$, there is only one arrow $X\to U_{\hyp}(\mathcal{G}^{\Sigma})$.
+Define $\Delta_{\Sigma}(X)\colon \Delta_{\hyp}(X)\to \mathcal{G}^{\Sigma}$ to be the transpose of this arrow.
+
+\begin{proposition} $U_\Sigma$
+	has a left adjoint $\Delta_\Sigma$.
+\end{proposition}
+\begin{proof}Let $(h, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be an object of $\hyp_{\Sigma}$, and suppose that there exists $f\colon X\to U_{\Sigma}(\mathcal{H})$.
+Since $U_{\Sigma}(\mathcal{H})=U_{\hyp}(\mathcal{H})$ and $\id{\catname{Set}}$ is the unit of $\Delta_\hyp \dashv U_{\hyp}$, there exists a unique morphism $(k,f)\colon \Delta_{\hyp}(X)\to \mathcal{H}$ of $\hyp$.
+Since the set of hyperedges of $\Delta_{\hyp}(X)$ is empty, $k$ must be $?_{E_\mathcal{H}}$ and the commutativity of each of the two triangles below is equivalent to that of the other
+	\[\xymatrix{\Delta_\hyp(X) \ar[rr]^{(?_{E_\mathcal{H}}, f)} \ar[dr]_{\Delta_\Sigma(X)} && \mathcal{H} \ar[dl]^{(h, !_{V_\mathcal{H}})} & U_\hyp(\Delta_\hyp(X)) \ar[rr]^{f} \ar[dr]_{U_\hyp(\Delta_\Sigma(X))\hspace{10pt}} && U_\hyp(X) \ar[dl]^{!_{V_\mathcal{H}}}\\& \mathcal{G}^\Sigma &&&U_\hyp\hspace{-1.5pt}\left(\mathcal{G}^\Sigma\right)}\]
+	But the triangle on the right commutes because $U_{\hyp}(\mathcal{G}^{\Sigma})$ is terminal.
+\end{proof}
+
+We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
+\begin{example}\label{lab_1}
+	The simplest example is given by the identity $\id{\mathcal{G}^\Sigma}\colon \mathcal{G}^\Sigma\rightarrow \mathcal{G}^{\Sigma}$. If $\Sigma$ is the signature of groups $\Sigma_G$we get 
+	\begin{center}
+		\begin{tikzpicture}
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$\heartsuit$}] (V) at (0,0) {};
+			\node(E)at(-2, 0.4){$e$};
+			\node(M)at(0, 2.15){$\cdot$};
+			\node(I)at(2, 0.75){$(-)^{-1}$};
+
+			\node(E')at(-2, 0){$e$};
+			\node(M')at(0, 1.75){$\cdot$};
+			\node(I')at(2, 0){$(-)^{-1}$};
+			\draw[->-=.5](-1.75,0)--(V)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](V)..controls(-0.5,0.5)and(-0.8,1)..(-0.25,1.6)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$2$};
+			\draw[->-=.5](V)..controls(-1,0.6)and(-1,1.1)..(-0.25,1.9)node[pos=0.5, left,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](0.25,1.75)..controls(0.8,0.8)and(0.5,0.5)..(V)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](V)--(1.5,0)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](2.5,0)..controls(4,0)and(2.5,-2)..(V)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+			\draw[rounded corners] (-2.25, -0.25) rectangle (-1.75, 0.25) {};
+			\draw[rounded corners] (-0.25, 1.5) rectangle (0.25, 2) {};
+			\draw[rounded corners] (2.5, -0.5) rectangle (1.5, 0.5) {};
+		\end{tikzpicture}
+	\end{center}
+\end{example}
+
+\begin{example}\label{lab_2}
+	Take again $\Sigma_G$ the signature of groups, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
+	\begin{align*}
+		e=f(h_1) \quad \cdot=f(h_2)\quad \cdot=f(h_3)
+	\end{align*}
+	In this case we get the following picture
+
+	\begin{center}\begin{tikzpicture}
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,-0.75) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-2.25) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=right:{$v_5$}] (E) at (6,-1.5) {};
+			\draw[->-=.5] (1.75,-0.75)--(C)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
+			\draw[->-=.5] (4.75,-1.5)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (-1.5,0)--(A)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (4.25, -1.75) rectangle (4.75, -1.25) {};
+			\node at (4.5, -1.05){$h_3$};
+			\node at (1.5, -0.3){$h_2$};
+			\node at (-1.75, 0.45){$h_1$};
+			\draw[rounded corners] (-2, -0.25) rectangle (-1.5, 0.25) {};
+			\draw[->-=.5] (A)..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (B)..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\draw[->-=.5] (C)..controls(3.5,-0.75)and(4.2,-0.95)..(4.25,-1.35)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (D)..controls(3.5,-2.25)and(4.2,-2.05)..(4.25,-1.65)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\node at (-1.75,0) {$e$};
+			\node at (1.5,-0.75) {$\cdot$};
+			\node at (4.5,-1.5) {$\cdot$};
+		\end{tikzpicture}
+	\end{center}
+\end{example}
+
+\subsection{Term Graphs}
+
+\section{Hypergraphs with equivalences}
+
+\subsection{title}
+
+\section{title}
+
+\section{EGGS}
 

### 2025-01-29 icgt/fact_sys.tex
Fact_Sys

\subsection{Factorization systems}

\begin{definition}[Factorization System]\label{def:fact_sys}
	Let $\X$ be a category, and let $\E$, $\M$ be two classes of arrows.
	Then, $(\E, \M)$ is a \emph{factorization system} if:
	\begin{enumerate}
		\item $\E$ and $\M$ are closed under composition with isomorphisms: if $f: X \to Y$ belongs to $\E$ (to $\M$), and $h: Y\to Z$ is an isomorphism, then $h \circ f$ belongs to $\E$ (to $\M$);
		\item every arrow $f: X \to Y$ of $\X$ admits an \emph{$(\E, \M)$-factorization}, that is, there are arrows $e \in \E$ and $m \in \M$ such that $f = m\circ e$;
		\item every $e \in \E$ has the \emph{left lifting property} with respect to every $m \in \M$: for every commutative square as the one below, with $e \in \E$ and $m \in \M$,
			there exists a unique $k: Y \to Z$ whitch fits in it.
			\[\xymatrix{
					X\ar[r]^{g} \ar[d]_e & Z \ar[d]^m \\ Y \ar@{.>}[ur]^k \ar[r]_f & V
			}\]
	\end{enumerate}
	A factorization system $(\E, \M)$ is \emph{proper} if every $e \in \E$ is epi and every $m \in \M$ is mono, while it is \emph{stable} is $\E$ is stable under pullbacks.
\end{definition}

\begin{remark}\label{rem:dual_fact_sys}
	It is immediate to notice that, given a factorization system $(\E, \M)$ on a category $\X$, then $(\M, \E)$ is a factorization system on $\X^{op}$, which is proper if $(\E, \M)$ is so, and it is stable if
	$\M$ is stable under pushouts in $\X$.
\end{remark}

\begin{remark}
	If $(\E, \M)$ is a factorization system for a category $\X$, then $\E$ is the class of all the arrows with the left lifting property with respect to every $m\in \M$.
	Indeed, if $f:X \to Y$ is an arrow with such a property with respect to every element of $\M$, it is possible to factorize it as $f = m \circ e$, with $m: M \to Y$ in $\M$ and 
	$e: X \to M$ in $\E$, obtaining the above situation by definition.
	\[\xymatrix{X \ar[r]^e\ar[d]_f & M \ar[d]^m \\ Y \ar[r]_{\id{Y}} \ar@{.>}[ur]^k & Y}\]
	From this, it is possible to prove that $k$ and $m$ are mutually inverses, hence $f = m\circ e$ belongs to $\E$ due to closure under isomorphisms.
\end{remark}

\begin{proposition}
	Let $(\E, \M)$ be a factorization system on $\X$. Then $\E$ contains every isomorphism, and it is closed under composition.
\end{proposition}

By \Cref{rem:dual_fact_sys}, we have also that $\M$ is closed under composition, and contains every isomorphism.

\begin{lemma}
	Let $(\E, \M)$ be a factorization system on $\X$. If $e:Y \to E$, $e': Y\to E'$ and $m: E \to X$, $m':E'\to X$ are arrows, respectively, in $\E$ and in $\M$ such that $e'\circ m' = e \circ m$,
	then there exists a unique isomorphism $\phi: E \to E'$ such that the diagram below commutes.
	\[\xymatrix{Y\ar[r]^{e'}\ar[d]_{e}&E'\ar[d]^{m'}\\E\ar[r]_{m}\ar@{.>}[ur]^{\phi}\ar[r]_{m}&X}\]
\end{lemma}

\begin{proof}
	Suppose the following situation.
	\[\xymatrix{X \ar[r]^e\ar[d]_{e'}&E\ar[d]^{m}&&X\ar[r]^{e'}\ar[d]_{e}&{E'}\ar[d]^{m'}\\{E'}\ar[r]_{m'}\ar@{.>}[ur]^{\phi}&Y&&E\ar[r]_{m}\ar@{.>}[ur]^{\psi}&Y}\]
	From the commutativity of the diagrams below, we obtain at once $\phi\circ\psi=\id{E'}$ and $\psi\circ\phi=\id{E}$.
	\[\xymatrix{
			X\ar[rr]^{e}\ar[dd]_{e}\ar[dr]_{e'}&&E\ar[r]^{m}\ar[dl]^{\psi}&Y\ar[dd]^{\id{Y}} &&& X\ar[rr]^{e'}\ar[dd]_{e'}\ar[dr]_{e}&&{E'}\ar[r]^{m}\ar[dl]^{\phi}&Y\ar[dd]^{\id{Y}}\\
							     & {E'}\ar[dl]_{\phi}\ar[drr]^{m'}& & &&&  & {E'}\ar[dl]_{\psi}\ar[drr]^{m'}& & \\
			E\ar[rrr]_{m} &&& Y &&& {E'} \ar[rrr]_{m'} &&& Y
	}\]
\end{proof}

The previous lemma allows us to deduce other useful properties of factorization systems.

\begin{proposition}
	Given a factorization system $(\E, \M)$ on a category $\X$, it holds that:
	\begin{enumerate}
		\item an arrow $f:X\to Y$ that factors as $m \circ e$ belongs to $\M$ if and only if $e$ is an isomorphism;
		\item $f\in \E$ and $f\in\M$ if and only if $f$ is an isomorphism;
		\item $\M$ is stable under pullbacks;
		\item if $(\E, \M)$ is proper, then $g\circ f \in \M$ implies $f \in \M$.
	\end{enumerate}
\end{proposition}

\todo{proof?}

### 2025-01-29 icgt/main.tex
Fact_Sys
monoid

@@
 \usepackage{hyperref, cleveref}
+\usepackage{tikz-cd}
 \usepackage{tikz}
@@
 \def\E{\textbf {\textup{E}}}
+\def\T{\textbf {\textup{1}}}
+\def\A{\textbf {\textup{A}}}
 
@@
 \newcommand{\sv}[0]{\mathsf{Sieves}}
-\newcommand{\mono}[1]{\mathcal{M}({#1})}
+\newcommand{\mono}[1]{\mathsf{Mon}(\catname{#1})}
+\newcommand{\mo}[1]{{#1}_\mathsf{Mon}}
 \newcommand{\pro}{\mathsf{prod}}
@@
 
+%sommatoria e prodotto per xy
+
+\usepackage{relsize}
+\newcommand{\Sum}{\mathlarger{\sum}}
+\newcommand{\Prod}{\mathlarger{\prod}}
+
 \bibliographystyle{abbrv}
@@
 \begin{notation}
-	contenuto...
-\end{notation}
 Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects, so
@@
 We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.
-Given an integer $n\in \mathbb{Z}$, $[0,n]$ denotes the set of natural numbers less than or equal to $n$; in particular, $[0,n]=\emptyset$ if $n<0$.
+Given an object $X$, we will denote by $?_X$ the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one.
+\end{notation}
 
@@
 The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.
-In order to define it we need to introduce some terminology.
-Let  $\X$ be a category.
-A subclass $\mathcal{A}$ of
-$\mor(\X)$ is called
+
+In order to define it we need to introduce some terminology.  Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is called
 \begin{itemize}
-	\parbox{11cm}{\item
-		\emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one on the right, 	if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
-		\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable.{\tiny }}\hfill
-	\parbox{2cm}{$\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}$}
-	\parbox{11cm}{}\hfill
+	\item		\emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one  below, if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
+	\[\xymatrix{A \ar[r]^{f} \ar[d]_{m}& B \ar[d]^{n} \\ C \ar[r]_{g} & D}\]
+		\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable.
 \end{itemize}
 
-\begin{definition}[Van Kampen property]
-	Let $\X$ be a category and consider the diagram\\
-	\parbox{10cm}{
-		aside.
-		Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the bottom square
-		is an \emph{$\mathcal{A}$-Van Kampen square} if
+\begin{definition}
+	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the following diagram.
+
+		\[
+	\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }\]
+
+	We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
 		\begin{enumerate}
@@
 			if and only if the front and right faces are pullbacks.
-	\end{enumerate}}
-	\parbox{2cm}{$\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }$ }\\
-	Pushout squares that enjoy only the ``if'' half of item (2) above are called \emph{$\mathcal{A}$-stable}.
-
-	A $\mor(\X)$-Van Kampen square is called  \emph{Van
+	\end{enumerate}
+
+	Pushout squares that enjoy only the ``if'' half of item (2) above are called \emph{$\mathcal{A}$-stable}. A $\mor(\X)$-Van Kampen square is called  \emph{Van
 		Kampen} and a $\mor(\X)$-stable square  \emph{stable}.
@@
 
-\begin{definition}[$\mathcal{M}$-adhesive category]
+\begin{definition}
 	Let $\X$ be a category and $\mathcal{M}$ a subclass of
@@
 	A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
-	if $\mathcal{M}$-pushouts are Van Kampen squares.
+	if $\mathcal{M}$-pushouts are Van Kampen. We write $m\colon X \mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
 \end{definition}
-
-We write $m\colon X\rightarrowtail Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
 
@@
 \todo{Inserire parte della tesi su kp}
-\iffalse 
+
 \subsection{Kernel Pairs and Regular Epimorphisms}
@@
 \todo{Inserire qualche cosa su sist. di fattorizazzione e M-adesività - devo pensare a come mettere la questione senza prendere troppo spazio}
-\fi
-
-\section{Hypergraphical structures}
-\todo{A very nice introduction}
-
-\subsection{The category of hypergraphs}
-
-We will start this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
+\todo{Di questo possiamo sbattercene perché tanto siamo su $\Set$}
+
+\section{Hypergraphical structures}\label{sec:hyper}
 
@@
 Then the neutral element is $?_X\colon \emptyset \to X$ and the composition of $f\colon n\to X$ with $g\colon m\to X$ is simply the arrow $n+m\to X$ induced by them.
-If $h\colon X\to Y$ is an arrow in $\Set$, then $h^\star \colon \X^\star\to Y^\star$ is the composition with $h$.
+If $h\colon X\to Y$ is an arrow in $\Set$, then $h^\star \colon X^\star\to Y^\star$ is the composition with $h$.
+
+\subsection{The category of hypergraphs}
+
+We will start this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
 
@@
 \appendix
+\section{Some properties of comma categories}
+In this section we will briefly recall the definition of the comma category associated to two functors and some of its properties.
+\begin{definition}\index{category!comma -}
+	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comma{L}{R}$ is the category in which
+	\begin{itemize}
+		\item objects are triples $(A, B, f)$ with $A\in \A$, $B\in \B$, and $f\colon L(A)\rightarrow R(B)$; 
+		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the following diagram commutes
+		\[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}\]
+	\end{itemize}
+\end{definition} 
+We have two forgetful functors 	$U_L\colon \comma{L}{R}\to \A$ and $U_R\colon \comma{L}{R} \to \B$ given, respectively by
+\[
+\begin{split}
+	\functor[l]{(A,B, f)}{(h,k)}{(A', B', g)}
+	& \functormapsto
+	\rfunctor{A}{h}{A'}
+\end{split}\quad 
+\begin{split}
+	\functor[l]{(A,B, f)}{(h,k)}{(A', B', g)}
+	& \functormapsto
+	\rfunctor{B}{k}{B'}
+\end{split}
+\]
+
+Given $L\colon \A\to \X$ and $R\colon \B\to \X$, we can also consider their duals $L^{op}\colon \A^{op}\to \X^{op}$ and $R^{op}\colon \B^{op}\to \X^{op}$.
+An arrow $f\colon L(A)\to R(B)$ in $\X$ is the same ting as an arrow $f\colon R^{op}(B)\to L^{op}(A)$ in $\X^{op}$, thus $\left(\comma{L}{R}\right)$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
+Moreover, the commutativity in  $\X$ of the square
+\[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}\]
+is tantamount to the commutativity in $\X^{op}$ of the square 
+\[\xymatrix@C=25pt{ R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ L(A') \ar[r]_{L(h)}  & L(A) }\]
+Summing up we have just proved the following fact.
+\begin{proposition}\label{prop:dual}
+	$(\comma{L}{R})^{op}$ is equal to	$\comma{R^{op}}{L^{op}}$, moreover $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
+\end{proposition}
+
+We can notice another useful fact,  showing that in some cases we can guarantee  the existence of a left adjoint to $U_R$.
+
+\begin{proposition}\label{prop:left}
+	If $\A$ has initial objects and $L$ preserves them then the forgetful functor $U_R\colon \comma{L}{R}\to \B$ has a left adjoint $\Delta$.
+\end{proposition}
+\begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{B})$, where $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
+Consider $\id{B}\colon B\to U_R(\Delta(B))$ be the identity, and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given.
+By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, since $L$ preserves initial objects, the following square commutes.
+	\[\xymatrix@C=30pt{L(0) \ar[r]^{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B')}\]
+	Thus $(h,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$	such that $U_R(h,k)=k$.
+\end{proof}
+Dualizing we get immediately the following.
+\begin{corollary}If $\B$ has terminal objects preserved by $R$ then $U_L\colon \comma{L}{R}\to \A$ has a right adjoint.
+\end{corollary}
+
+\subsection{Slice categories}
+
+This section is devoted to recall some basic facts about the so called \emph{slice categories}.
+\begin{definition}\index{category!slice -}
+	Let $X$ be an object of a category $\X$, we will define the following two categories.
+
+	\begin{itemize}
+		\item The \emph{ slice category over $X$} is the category $\X/X$ which has as objects arrows $f\colon Y\to X$ and  in which an arrow $h\colon f\to g$ is $h\colon Y\to Y'$ in $\X$ such that the following triangle commutes.
+		\[\xymatrix@C=15pt{Y \ar[dr]_{f} \ar[rr]^{h}&& Y' \ar[dl]^{g}\\ & X}\] 
+		\item  	 Dually, the \emph{ slice category under $X$} is the category $X/\X$ in which objects are arrows $f\colon X\to Y$  with domain $X$ and a morphism $h\colon  f\to g$ is an arrow of $\X$ fitting in a triangle as the one below.
+		\[\xymatrix@C=15pt{&X \ar[dr]^{g}\ar[dl]_{f}\\ Y  \ar[rr]_{h}&& Y'}\] 
+	\end{itemize}
+\end{definition}
+
+\begin{remark} For every $X\in\ X$ we have forgetful functors
+	\[\begin{split}
+		\dom_X&\colon \X/X\to \X\\
+		\functor[l]{f}{h}{g}
+		&\functormapsto
+		\rfunctor{\dom(f) }{h}{\dom(g)}
+	\end{split}\qquad \begin{split}
+		\cod_X&\colon X/\X\to \X\\
+		\functor[l]{f}{h}{g}
+		&\functormapsto
+		\rfunctor{\cod(f) }{h}{\cod(g)}
+	\end{split}\]
+\end{remark}
+
+We can realize the slice over and under an object $X\in \X$ as comma categories.
+
+\begin{proposition}\label{prop:commaapp}
+	For every object $X$ in a category $\X$, if $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object $*$, then $\X/X$ and $X/\X$ are isomorphic to, respectively,  $\comma{\id{X}}{\delta_X}$ and $\comma{\delta_X}{\id{X}}$ .
+\end{proposition}
+\begin{proof} Define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows
+	\[	\begin{split}
+		\functor[l]{(Y, *,  f)}{(h, \id{*} )}{( Y', *,  g)}
+		\functormapsto
+		\rfunctor{f }{h}{g}
+	\end{split} \qquad \begin{split}
+		\functor[l]{f }{h}{g}
+		\functormapsto
+		\rfunctor{(\dom(f), *, f)}{(h, \id{*} )}{(\dom(g), *, g)}
+	\end{split}\]
+	Similarly, we have $F_2\colon \comma{\delta_X}{\id{X}}\to X/\X$ and $G_2\colon X/\X\to \comma{\delta_X}{\id{X}}$
+	\[	\begin{split}
+		\functor[l]{(*, Y, f)}{(\id{*},h )}{(*, Y', g)}
+		\functormapsto
+		\rfunctor{f }{h}{g}
+	\end{split} \qquad \begin{split}
+		\functor[l]{f }{h}{g}
+		\functormapsto
+		\rfunctor{(*, \cod(f), f)}{(\id{*}, h )}{(*, \cod(g), g)}
+	\end{split}\]
+	It is now obvious to see that $F_1,G_1$ and $F_2, G_2$ are pairs of inverses.
+\end{proof}
+
+A straightforward application of \cref{lim} now yields the following.
+\begin{corollary}\label{cor:pbapp}
+	If $\X$ has pullbacks, then for every object $X$, the slice $\X/X$ has pullbacks too.
+\end{corollary}
+
+\section{Some notes on free monoids}
+
+In this appendix we will provide a brief exposition to the problem of constructing the \emph{free internal monoid} in a monoidal category $(\X, \otimes, I )$.
+This  construction is needed in \Cref{sec:hyper} to provide a concrete representation to hypergraphs.
+The standard references on the subject are \cite{dubuc1974free,kelly1980unified,lack2010note}
+
+\begin{definition}
+	Let $(\X, \otimes, I)$ be a monoidal category.
+An \emph{monoid} is a triple $(X, m, e)$ made by an object $X$ equipped with arrows $m\colon X\otimes X\to X$ and $e\colon I\to X$ making the following diagram commute.
+
+	\[\]
+
+	A \emph{morphism of monoids} between $(X, m, e)$ and $(X', m', e')$ is an arrow $f\colon X\to X'$ fitting in the diagram below.
+
+	\[\]
+Monoids with their morphisms form a category $\mono{X}$, such category has an obvious forgetful functor $\mo{U}\colon\mono{X}\to X$ sending $(X, m, e)$ to $X$ and a morphism to itself.
+\end{definition}
+
+We are interested in provide sufficient conditions to guarantee the existence of a left adjoint to $\mo{U}$.
+The idea is to mimic the construction of the \emph{kleene star} functor $\Set\to \Set$ \cite{bibid}, i.e.~ the functor sending $X$ to the set of finite words over it.
+
+\begin{definition}
+	Let $(\X, \otimes, I )$ be  a monoidal category with countable coproduct.
+We say that $(\X, \otimes.
+I)$ is \emph{countably distributive} if, given a countable family $\{X_i\}_{i}$ and an object $Y$, the unique dotted morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms.
+	\[\xymatrix{&Y\otimes X_i \ar[dl]_{j_i} \ar[dr]^{\id{Y}\otimes h_i} \\ \Sum_{i\in I} Y\otimes X_i \ar@{.>}[rr]_{\phi}&& Y\otimes (\Sum_{i\in I}X_i) }\]
+	\[\xymatrix{&X_i \otimes Y \ar[dl]_{k_i} \ar[dr]^{ h_i \otimes \id{Y}} \\ \Sum_{i\in I}  X_i \otimes Y \ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \otimes Y}\]
+\end{definition}
+
+We cite the following, fundamental, result proved in \cite{lack2010note}.
+
+\begin{theorem}
+	Let $(\X, \otimes, I )$ be a countably distributive monoidal category. Then $\mo{U}$ has a left adjoint sending $\mo{F}$ to $\sum_{n\in \mathbb{N}} X^{\otimes n}$.
+\end{theorem}
+
+As a concluding step, we ask for a compatibility property between countable coproducts and pullbacks, to assure that $\mo{F}$ preserves pullbacks.
+
+\begin{definition}
+	Let $\X$ be a category and suppose that $(X, \{j_i\}_{i\in I})$ is a coproduct.
+We say that $(X, \{j_i\}_{i\in I})$ is \emph{stable under pullbacks} if, given an arrow $f\colon Y\to X$ such that for every $i\in I$ the pullback square below exists,  the cocone $(Y, \{k_i\}_{i\in I})$ is a coproduct.
+	\[\xymatrix{Y_i \ar[r]^{k_i} \ar[d]_{p_i} & Y \ar[d]^{f}\\ X_i\ar[r]_{j_i} & X}\]
+
+\end{definition}
+
+We are now ready to provide the claimed continuity property of $\mo{F}$.
+
+\begin{proposition}
+	Let $(\X, \otimes, I)$ be a countably distributive monoidal category and suppose that countable  coproducts in $\X$ are stable under pullbacks.
+Then the functor $\mo{F}\colon \X\to \mono{X}$ preserves pullbacks.
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
 \section{Comparison with Ghica}

### 2025-01-31 icgt/main.tex

@@
 
+\newcommand{\lgh}{\mathsf{lg}}
+
 \DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
@@
 \def\A{\textbf {\textup{A}}}
-
+\def\M{\mathcal{M}}
 %categorie varie
@@
 
-\todo{Va riscritta tutta con xy}
-
 This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.
@@
 
-\begin{theorem}\todo{controllare meglio}
+\begin{theorem}
 	\label{thm:slice-functors}
-	Let $\X$ be an $\mathcal{M}$-adhesive category. Given an object $X$
-	the category $\X/X$ is $\mathcal{M}/X$-adhesive with
-	$\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
-	\mathcal{M}\}$. Similarly, $X/\X$ is $X/\mathcal{M}$-adhesive with
-	$X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}$.
-
-	Moreover for every small category $\Y$, the category $\X^\Y$ of
+	Let $\X$ be an $\mathcal{M}$-adhesive category, then the following hold true:
+	\begin{enumerate}
+		\item if $L\colon \X\to $
+		\item for every object $X$
+		the categories $\X/X$  and $X/X$ are, respectively, $\mathcal{M}/X$-adhesive and $X/\mathcal{M}$-adhesive, where
+		\[\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
+		\mathcal{M}\} \qquad X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}\]
+		\item for every small category $\Y$, the category $\X^\Y$ of
 		functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
 		$\mathcal{M}^{\Y}:=\{\eta \in \mor(\X^\Y) \mid \eta_Y \in
-	\mathcal{M} \text{ for every } Y\in \Y\}$.
+		\mathcal{M} \text{ for every } Y\in \Y\}$;
+		\item given a  full and faithful $I\colon \Y\to \X$ and a class $\mathcal{M}'$ of arrows in $\Y$ stable under pullbacks, containing all isomorphism
+	\end{enumerate} 
 \end{theorem}
 
-We can list various examples of $\mathcal{M}$-adhesive categories (see
-\cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).
+We will briefly list som examples of $\mathcal{M}$-adhesive categories.
 
@@
 \begin{proposition}\label{prop:kermono}
-	An arrow $m\colon M\to X$ is mono if and only if $(M, id_M, id_M)$ is a kernel pair for it.
+	An arrow $m\colon M\to X$ is mono if and only if $(M, MM, \id{M})$ is a kernel pair for it.
 \end{proposition}
@@
         A \arrow[drr, bend left=30, "f"] \arrow[ddr, bend right=30,"g" swap] \arrow[dr, dashed, "u"] & & \\
-        & M  \arrow[d, "{id_M}"] \arrow[r, "{id_M}"] & M \arrow[d, "m"] \\
+        & M  \arrow[d, "{\id{M}}"] \arrow[r, "{\id{M}}"] & M \arrow[d, "m"] \\
         & M  \arrow[r, "m" swap] & X
@@
     \]
-    For the universal property of pullbacks, we have that $$f  =  id_M \circ u =  g$$
+    For the universal property of pullbacks, we have that $$f  =  \id{M} \circ u =  g$$
     Hence, $m$ is mono.
@@
         m \circ f = m \circ g   &\Rightarrow    f = g \\
-                                &\Rightarrow    f \circ id_M = g\circ id_M
+                                &\Rightarrow    f \circ \id{M} = g\circ \id{M}
     \end{align*}
@@
     	\arrow["{\pi_f^2}"', from=1-1, to=3-1]
-    	\arrow["{id_X}", from=1-3, to=1-5]
+    	\arrow["{id{X}}", from=1-3, to=1-5]
     	\arrow["f", from=1-3, to=3-3]
@@
 
-\subsection{Factorization systems}
-\todo{Inserire qualche cosa su sist. di fattorizazzione e M-adesività - devo pensare a come mettere la questione senza prendere troppo spazio}
-\todo{Di questo possiamo sbattercene perché tanto siamo su $\Set$}
+\input{./fact_sys}
 
@@
 \section{Some properties of comma categories}
-In this section we will briefly recall the definition of the comma category associated to two functors and some of its properties.
+In this section we will briefly recall the definition of the comma category \cite{mac2013categories} associated to two functors and some of its properties.
 \begin{definition}\index{category!comma -}
@@
 
-We can notice another useful fact,  showing that in some cases we can guarantee  the existence of a left adjoint to $U_R$.
+\begin{lemma}\label{colim}
+	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
+Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite{castelnovo2023thesis,castelnovo2022newcriterionmathcalmmathcalnadhesivity}).
+\end{lemma}
+\begin{proof}
+	Suppose that $U_L\circ F$ and $U_R\circ F$ have colimiting cocones  $\left(A, \{a_D\}_{D\in \D}\right)$ and $\left(B, \{b_D\}_{D\in \D}\right)$ respectively.
+By hypothesis $\left(L(A), \{L\left(a_D\right)\}_{D\in \D}\right)$ is colimiting for $L\circ U_L\circ F$.
+Now, if we define
+	\[F(D):=(A_D, B_D, f_D)\]
+	then we have arrows $R(a_i)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comma{L}{R}$ and so
+	\begin{align*}
+		R\left(b_{D'}\right)\circ f_{D'}\circ L(U_L(F(d)))&=R\left(b_{D'}\right)\circ R\left(U_R\left(F(d)\right)\right)\circ f_D\\&=R\left(b_{D'}\circ U_R\left(F(d)\right)\right)\circ f_D\\&=R\left(b_D\right)\circ f_D
+	\end{align*}
+	Thus there exists $f\colon L(A)\rightarrow R(B)$ such that
+	\[\xymatrix@C=35pt{ L(A_D) \ar[r]^{L(a_D)} \ar[d]_{f_D}& L(A) \ar[d]^{f}\\ R(B_D) \ar[r]_{R(b_D)} &R(B)}\]
+	Notice that $f$ is the unique arrow in $\X$ wich makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comma{L}{R}$.
+If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.
+
+	First of all, let us show that it is a cocone. Given $d\colon D\to D'$ in $\D$ we have:
+	\begin{align*}
+		\left(a_{D'}, b_{D'}\right)\circ F(d)&=	\left(a_{D'}, b_{D'}\right)\circ \left(U_L(F(d)), U_R(F(d))\right)\\&=\left( a_{D'}\circ U_L(F(d)),  b_{D'}\circ U_R(F(d)) \right)\\&=\left(a_D, b_D\right)
+	\end{align*}
+	For the colimiting property, let $\left((X, Y, g), \left\{\left(x_D, y_D\right)\right\}_{D\in \D}\right)$ be another cocone on $F$.
+In particular $\left(X, \left\{x_D\right\}_{D\in \D}\right)$ and $\left(Y, \left\{y_D\right\}_{D\in \D}\right)$ are cocones on $U_L\circ F$ and $U_R\circ F$ respectively, so we have uniquely determined arrows $x\colon A\rightarrow X$ and $y\colon B\rightarrow Y$ such that
+	\[x\circ a_D= x_D \qquad y\circ b_D= y_D\]
+	Let us show that $(x,y)$ is an arrow of $\comma{L}{R}$. Given $D\in \D$ we have
+	\begin{align*}
+		R(y)\circ f\circ L(a_D)&=R(y)\circ R\left(b_D\right)\circ f_D\\&=R\left(y\circ b_D\right)\circ f_D\\&=R\left(y_D\right)\circ f_D\\&= g\circ L\left(x_D\right)\\&=g\circ L\left(x\circ a_D\right)\\&=g\circ L(x)\circ L\left(a_D\right)
+	\end{align*}
+	from which it follows  that the following diagram commutes.
+	\[\xymatrix@C=35pt{L(A)\ar[d]_{f} \ar[r]^{L(x)} & X \ar[d]^{g}\\ R(B) \ar[r]_{R(y)}& Y}\]
+	This shows that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ and the thesis follows.
+\end{proof}
+
+\Cref{prop:dual} and \Cref{colim} now yields the following.
+\begin{corollary}\label{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ I$.
+\end{corollary}
+
+We can use \cref{lim} to characterize monos in comma categories. 
+\begin{corollary}\label{cor:mono}
+	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comma{L}{R}$ is mono if and only if both $h$ and $k$ are monomorphisms.
+\end{corollary}
+\begin{proof}
+	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the following square is a pullback in $\comma{L}{R}$
+	\[\xymatrix@C=50pt{(A, B, f)  \ar[r]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}& (A, B, f)  \ar[d]^{(h,k)} \\ (A, B, f)  \ar[r]_{(h,k)}& (A', B', g) }\]
+	Using \cref{lim} we deduce that the following two squares are pullbacks in $\A$ and $\B$.
+	\[\xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
+	From which it follows that $h$ and $k$ are monos.
+
+	\smallskip\noindent 
+	$(\Leftarrow)$ Since $h$ and $k$ are monos then we have two pullback squares 	
+	\[\xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
+	By \cref{lim} this implies that 
+	\[\xymatrix@C=50pt{(A, B, f)  \ar[r]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}& (A, B, f)  \ar[d]^{(h,k)} \\ (A, B, f)  \ar[r]_{(h,k)}& (A', B', g) }\]
+	is a pullback in $\comma{L}{R}$ and we are done.
+\end{proof}
+
+We end this section pointing out another useful fact,  showing that in some cases we can guarantee  the existence of a left adjoint to $U_R$.
 
@@
 
-A straightforward application of \cref{lim} now yields the following.
+A straightforward application of \Cref{lim} now yields the following.
 \begin{corollary}\label{cor:pbapp}
@@
 	Let $(\X, \otimes, I)$ be a monoidal category.
-An \emph{monoid} is a triple $(X, m, e)$ made by an object $X$ equipped with arrows $m\colon X\otimes X\to X$ and $e\colon I\to X$ making the following diagram commute.
-
-	\[\]
-
-	A \emph{morphism of monoids} between $(X, m, e)$ and $(X', m', e')$ is an arrow $f\colon X\to X'$ fitting in the diagram below.
-
-	\[\]
+An \emph{monoid} is a triple $(X, m, e)$ made by an object $X$ equipped with arrows $m\colon X\otimes X\to X$ and $e\colon I\to X$ making the following diagrams commute, where $\alpha$ is the associator and $\lambda$ and $\rho$ the two unitors.
+
+	\[\xymatrix@C=35pt{(X\otimes X) \ar[r]^{\alpha_{X, X, X}} \ar[dd]_{m\otimes \id{X}}\otimes X & X\otimes (X\otimes X) \ar[d]^{\id{X}\otimes m} & X \ar[r]^{\rho^{-1}_X}  \ar[d]_{\lambda^{-1}_X} \ar[ddr]_{\id{X}}& X\otimes I \ar[d]^{\id{X}\otimes e}\\& X\otimes X \ar[d]^{m}  & I\otimes X \ar[d]_{e\otimes \id{X}} & X\otimes X \ar[d]^{m} \\X\otimes X  \ar[r]_{m}& X & X\otimes X \ar[r]_{m} & X}\]
+
+	A \emph{morphism of monoids} between $(X, m, e)$ and $(X', m', e')$ is an arrow $f\colon X\to X'$ fitting in the diagrams below.
+
+	\[\xymatrix{X\otimes X \ar[r]^{f\otimes f} \ar[d]_{m}& Y\otimes Y \ar[d]^{m'} && I\ar[dr]^{e'} \ar[dl]_{e}\\ X\ar[r]_{f} & Y & X \ar[rr]_{f} && Y }\]
 Monoids with their morphisms form a category $\mono{X}$, such category has an obvious forgetful functor $\mo{U}\colon\mono{X}\to X$ sending $(X, m, e)$ to $X$ and a morphism to itself.
+
+If the functor $\mo{U}$ has a left adjoint $\mo{F}\colon \X\to \mono{\X}$, we will define the \emph{Kleene star} functor $(-)^\star\colon \X \to \X$ as $\mo{U}\circ \mo{F}$.
 \end{definition}
@@
 We are interested in provide sufficient conditions to guarantee the existence of a left adjoint to $\mo{U}$.
-The idea is to mimic the construction of the \emph{kleene star} functor $\Set\to \Set$ \cite{bibid}, i.e.~ the functor sending $X$ to the set of finite words over it.
+The idea is to mimic the construction of the usual functor $\Set\to \Set$ \cite{sakarovitch2009elements} sending $X$ to the set of finite words over it.
 
@@
 \begin{theorem}
-	Let $(\X, \otimes, I )$ be a countably distributive monoidal category. Then $\mo{U}$ has a left adjoint sending $\mo{F}$ to $\sum_{n\in \mathbb{N}} X^{\otimes n}$.
+	Let $(\X, \otimes, I )$ be a countably distributive monoidal category. Then $\mo{U}\colon \mono{X}\to \X$ has a left adjoint  $\mo{F}\colon \X\to \mono{X}$ defined as
+\[	\functor[l]{X}{f}{Y}
+\functormapsto
+\rfunctor{\sum_{i\in \mathbb{N}} X^{\otimes n}}{\sum_{i\in \mathbb{N}} f^{\otimes n}}{\sum_{i\in \mathbb{N}} Y^{\otimes n}}\]
 \end{theorem}
 
-As a concluding step, we ask for a compatibility property between countable coproducts and pullbacks, to assure that $\mo{F}$ preserves pullbacks.
+\begin{remark}\label{rem:lg} Let $\X$ be a category with finite limits and suppose that $(\X, \times, 1)$ is countably distributive.
+Then for every object $X$ in $\X$ we have a \emph{length homomorphism} $\lgh_X\colon \mo{F}(X)\to \mo{F}(1)$.
+The underlying morphism $X^\star \to 1^\star$ in $\X$ is simply $\sum_{n\in \mathbb{N}} (!_X)^{\otimes n}$.
+Notice, moreover, that for every $f\colon X\to Y$ we have a commutative triangle as the one below.
+	\[\xymatrix{X^\star \ar[rr]^{f^\star} \ar[dr]_{\lgh_X}&& Y^\star  \ar[dl]^{\lgh_Y}\\ & 1^\star }\]
+\end{remark}
+
+As a concluding step, we ask for a compatibility property between countable coproducts and pullbacks, to assure that $\mo{F}$ preserves pullbacks \cite{bibid}.
 
 \begin{definition}
-	Let $\X$ be a category and suppose that $(X, \{j_i\}_{i\in I})$ is a coproduct.
-We say that $(X, \{j_i\}_{i\in I})$ is \emph{stable under pullbacks} if, given an arrow $f\colon Y\to X$ such that for every $i\in I$ the pullback square below exists,  the cocone $(Y, \{k_i\}_{i\in I})$ is a coproduct.
-	\[\xymatrix{Y_i \ar[r]^{k_i} \ar[d]_{p_i} & Y \ar[d]^{f}\\ X_i\ar[r]_{j_i} & X}\]
-
+	Let $\X$ be a category, we say that $\X$ is \emph{countably extensive} if:
+	\begin{enumerate}
+		\item  for every coprojections $j_i \colon X_i\to \sum_{i\in I}^{X_i} $ in a countaple coproduct and arrow $f\colon Y\to \sum_{i\in I} X_i$, a pullback of $j_i$ along $f$ exists; 
+		\item given a countable set $I$, a coproduct $(X, \{j_i\}_{i\in I})$, an arrow $f\colon Z\to X$ and a family of squares
+		\[\xymatrix{Z_i \ar[r]^{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar[r]_{j_i} & X}\]
+		then the above squares are all pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.
+	\end{enumerate} 
 \end{definition}
 
+\begin{remark}\label{rem:pb}
+Suppose that  $(\X, \times, 1)$ is a countably distributive monoidal category, with $\X$ countably extensive. Then the following squares are pullbacks for every $n\in \mathbb{N}$ and object $X$.
+\[\xymatrix{X^{n} \ar[r]^-{j_n} \ar[d]_{!_{X^n}}& X^\star \ar[d]^{\lgh_X} & Y^{n} \ar[r]^-{k_n} \ar[d]_{!_{Y^n}}& Y^\star \ar[d]^{\lgh_Y}\\ 1 \ar[r]_{a_n}&  1^\star & 1 \ar[r]_{a_n}&  1^\star}\]
+\end{remark}
+
+An elementary, but quite important property of countably extensive category is the following.
+
+\begin{proposition}\label{prop:inj}
+Let $\X$ be a countably extensive category, then countable coproducts are disjoints and have monos as coprojections. 
+\end{proposition}
+\begin{proof}
+Let $(X, \{j_i\}_{i\in I})$ be a coproduct for some countable set $I$. For every $i\in I$, consider the family ${k_{i, h}}_{h\in I}$ defined as
+\[k_{i, h}:=\begin{cases}
+	?_{X_{i}} & h\neq i\\
+	\id{X_i} &h=i
+\end{cases}\]
+It is immediate to notice that $(X_{i}, \{k_{i,h}\}_{h\in I})$ is a countable coproduct. Thus the squares below, where $h\neq i$, are all pullbacks.
+	\[\xymatrix{0 \ar[r]^{?_{X_h}} \ar[d]_{?_{X_h}}& X_h \ar[d]^{j_h} & X_i \ar[r]^{\id{X_i}} \ar[d]_{\id{X_i}}& X_i \ar[d]^{j_i}\\ X_i \ar[r]_{j_i} & X & X_i \ar[r]_{j_i} & X}\]
+	The thesis now follows at once.
+\end{proof}
+
 We are now ready to provide the claimed continuity property of $\mo{F}$.
@@
 \begin{proposition}
-	Let $(\X, \otimes, I)$ be a countably distributive monoidal category and suppose that countable  coproducts in $\X$ are stable under pullbacks.
-Then the functor $\mo{F}\colon \X\to \mono{X}$ preserves pullbacks.
+	Let $\X$ be a category with finite limits such that the cartesian structure $(\X, \times, 1)$ is countably distributive.
+Suppose, moreover, that countable  coproducts in $\X$ are stable under pullbacks.
+Then the Kleene star $(-)^\star \colon \X\to \X$ preserves pullbacks.
 \end{proposition}
 \begin{proof}
-	contenuto...
+ Suppose that the solid part of the diagram below is given, where  the inner square is the image of a pullback through $(-)^\star$.
+
+ \[\xymatrix{T \ar@/^.4cm/[drr]^{t_1} \ar@/_.4cm/[ddr]_{t_2} \ar@{.>}[dr]^t\\ & P^\star  \ar[d]_{q^\star}\ar[r]^{p^\star}& X^\star \ar[d]^{f^\star} \\ & Y^\star\ar[r]_{g^\star} & Z^\star}\]
+
+	For every $n\in \mathbb{N}$, consider the coprojection $k_n\circ Z^n\to Z^\star$ and let $T_n$ be the pullback below.
+	\[\xymatrix{T_n \ar[r]^{p_n} \ar[d]_{q_n} & T  \ar[d]^{f^\star \circ t_1}\\
+	Z^n \ar[r]_{k_n}& Z^\star}\]
+
+	Notice that, by \Cref{rem:lg} and since $f^\star \circ t_1$ is equal to $g^\star \circ t_2$, we have
+	\[
+	\begin{split}
+		\lgh_X\circ t_1 \circ p_n&=\lgh_Z\circ f^\star \circ t_1\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=a_n\circ !_{Z^n}\circ q_n\\&=a_n\circ !_{T_n}
+	\end{split}\qquad \begin{split}
+		\lgh_Y\circ t_2 \circ p_n&=\lgh_Z\circ g^\star \circ t_2\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=a_n\circ !_{Z^n}\circ q_n\\&=a_n\circ !_{T_n}
+	\end{split}\]
+
+	Thus in the diagram below the solid part commutes, yielding the dotted $x_n\colon T_n\to X^n$ and $y_n\colon T_n\to Y^n$.
+
+	\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{x_n} \ar[r]^{p_n} & T \ar[dr]^{t_1}&& T_n \ar@/_.3cm/[ddr]_{!_{T_n}} \ar[r]^{p_n} \ar@{.>}[dr]^{y_n}& T \ar[dr]^{t_2}\\ &X^n   \ar[d]_{!_{X^n}}\ar[r]^{j_n}& X^\star \ar[d]^{\lgh_X}& & Y^n \ar[d]_{!_{Y^n}}  \ar[r]^{h_n}& Y^\star \ar[d]^{\lgh_Y}\\ & 1 \ar[r]_{a_n}& 1^\star && 1  \ar[r]_{a_n}& 1^\star}\]
+
+	Now, limits commutes with limits, and, moreover, we have
+	\begin{align*}	
+	k_n\circ f^n\circ x_n & =f^\star \circ j_n\circ x^n\\&=f^\star \circ t_1\circ p_n\\&=g^\star \circ t_2\circ p_n\\&=g^\star \circ h_n\circ y_n\\&=k_n \circ g^n\circ y_n 
+	\end{align*}
+	so, by \Cref{prop:inj}, the solid part of the diagram below commutes an the inner square is a pullback, therefore we obtain the dotted arrow $b_n\colon T_n\to P^n $.
+	\[\xymatrix{T_n \ar@{.>}[dr]^{b_n}  \ar@/^.4cm/[drr]^{x_n} \ar@/_.4cm/[ddr]_{y_n} \\ & P^n \ar[d]_{q^n} \ar[r]^{p^n}& X^n \ar[d]^{f^n}\\ &  Y^n  \ar[r]_{g^n}& Z^n}\]
+
+	Since $\X$ is countably extensive, then $(T, \{p_n\}_{n\in \mathbb{N}})$ is a coproduct for the family $\{T_n\}_{n\in \mathbb{N}}$ and so we can define the arrow $t\colon T\to P^\star$ as $\sum_{n\in \mathbb{N}} b_n$
+
+	Let $v_n\colon P^n\to P^\star$ be te coprojection, to see that $t$ fits in the initial diagram it is now enough to compute.
+	\[\begin{split}
+		p^\star \circ t \circ p_n&= \sum_{i\in \mathbb{N}} p^i \circ \sum_{i\in \mathbb{N}} b_i\circ p_n\\&
+		=\sum_{i\in I}p_i\circ v_n\circ b_n\\&= j_n\circ p_n\circ v_n\\&=j_n\circ x_n\\&=t_1\circ p_n
+ 	\end{split} \qquad \begin{split}
+ 	q^\star \circ t \circ p_n&= \sum_{i\in \mathbb{N}} q^i \circ \sum_{i\in \mathbb{N}} b_i\circ p_n\\&
+ 	=\sum_{i\in I}q_i\circ v_n\circ b_n\\&= h_n\circ p_n\circ v_n\\&=j_n\circ x_n\\&=t_2\circ p_n
+ 	\end{split}\]
+ 	so that $p^\star \circ t = t_1$ and $q^\star\circ t = t_2$.
+
+We are left with uniqueness. Let $t'\colon T\to P^\star$ be another arrow such that $p^\star \circ t' = t_1$ and $q^\star\circ t' = t_2$, then
+\begin{align*}
+\lgh_P\circ t' \circ p_n&=\lgh_X\circ p^\star \circ t'\circ p_n\\&=\lgh_X\circ t_1\circ p_n\\&=a_n\circ !_{T_n}
+\end{align*}
+
+So that, for every natural $n$, there exists an arrow $u_n\colon T_n \to X^n$ fitting in the diagram below.
+\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{u_n} \ar[r]^{p_n} & T \ar[dr]^{t'}\\ &P^n   \ar[d]_{!_{P^n}}\ar[r]^{v_n}& P^\star \ar[d]^{\lgh_P}\\ & 1 \ar[r]_{a_n}& 1^\star }\]
+Moreover, we have
+\[\begin{split}
+j_n\circ	p^n\circ u_n&=p^\star \circ  v_n\circ u_n\\&=p^\star \circ t'\circ p_n\\&=t_1\circ p_n\\&=j_n\circ x_n\\&=j_n\circ p^n\circ b_n
+\end{split}\qquad \begin{split}
+h_n\circ	q^n\circ u_n&=q^\star \circ  v_n\circ u_n\\&=q^\star \circ t'\circ p_n\\&=t_2\circ p_n\\&=h_n\circ y_n\\&=h_n\circ q^n\circ b_n
+\end{split}\]
+
+By \Cref{prop:inj} the previous equalities entails
+\[p^n\circ u_n=p^n\circ b_n \qquad q^n\circ u_n=q^n\circ b_n\]
+so that $u_n=b_n$ and we can conclude.
 \end{proof}

### 2025-02-01 icgt/main.tex
minori

@@
 	\begin{enumerate}
-		\item if $L\colon \X\to $
+		\item if $\Y$ is an $\mathcal{N}$-adhesive category $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to A$ one preserving pullbacks, then $\comma{L}{R}$ is $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
+		\[\comma{\mathcal{N}}{\mathcal{M}}:=\{(h,k) \in \mor(\comma{L}{R}) \mid h\in \mathcal{N}, k\in \mathcal{M}\}\]
 		\item for every object $X$
@@
 		\[\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
-		\mathcal{M}\} \qquad X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}\]
+		\mathcal{M}\} \hspace{5pt} X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}\]
 		\item for every small category $\Y$, the category $\X^\Y$ of
@@
 		\mathcal{M} \text{ for every } Y\in \Y\}$;
-		\item given a  full and faithful $I\colon \Y\to \X$ and a class $\mathcal{M}'$ of arrows in $\Y$ stable under pullbacks, containing all isomorphism
+		\item given a  full and faithful $I\colon \Y\to \X$ and a class $\mathcal{M}'$ of arrows in $\Y$ stable under pullbacks, pushout, containing all isomorphism and closed under composition an decomposition, if image of $\mathcal{M}'$ under $I$ is contained in $\mathcal{M}$ and $a$
 	\end{enumerate} 
@@
 
-We will briefly list som examples of $\mathcal{M}$-adhesive categories.
+We will briefly list some examples of $\mathcal{M}$-adhesive categories.
 
@@
 \end{example}
-
-\todo{Inserire parte della tesi su kp}
 

### 2025-02-03 icgt/main.tex
cose

@@
 \spnewtheorem*{notation}{Notation}{\bfseries}{}
+\spnewtheorem*{convention}{Convention}{\bfseries}{}
 
@@
 	\label{thm:slice-functors}
-	Let $\X$ be an $\mathcal{M}$-adhesive category, then the following hold true:
+	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category, then the following hold true:
 	\begin{enumerate}
-		\item if $\Y$ is an $\mathcal{N}$-adhesive category $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to A$ one preserving pullbacks, then $\comma{L}{R}$ is $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
+		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to A$ one preserving pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
 		\[\comma{\mathcal{N}}{\mathcal{M}}:=\{(h,k) \in \mor(\comma{L}{R}) \mid h\in \mathcal{N}, k\in \mathcal{M}\}\]
 		\item for every object $X$
-		the categories $\X/X$  and $X/X$ are, respectively, $\mathcal{M}/X$-adhesive and $X/\mathcal{M}$-adhesive, where
+		the categories $\X/X$  and $X/X$ are, respectively, (strictly) $\mathcal{M}/X$-adhesive and (strictly) $X/\mathcal{M}$-adhesive, where
 		\[\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
@@
 		\item for every small category $\Y$, the category $\X^\Y$ of
-		functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
+		functors $\Y\to \X$ is (strictly) $\mathcal{M}^{\Y}$-adhesive, where
 		$\mathcal{M}^{\Y}:=\{\eta \in \mor(\X^\Y) \mid \eta_Y \in
 		\mathcal{M} \text{ for every } Y\in \Y\}$;
-		\item given a  full and faithful $I\colon \Y\to \X$ and a class $\mathcal{M}'$ of arrows in $\Y$ stable under pullbacks, pushout, containing all isomorphism and closed under composition an decomposition, if image of $\mathcal{M}'$ under $I$ is contained in $\mathcal{M}$ and $a$
+		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ and  stable under pullbacks, pushout, containing all isomorphism and closed under composition and decomposition.
 	\end{enumerate} 
@@
 
-A pivotal role will be played by the Kleene star $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{...}.
-In particular, given a set $X$, $X^\star$ is the set of functions with a natural number as domain.
-Then the neutral element is $?_X\colon \emptyset \to X$ and the composition of $f\colon n\to X$ with $g\colon m\to X$ is simply the arrow $n+m\to X$ induced by them.
-If $h\colon X\to Y$ is an arrow in $\Set$, then $h^\star \colon X^\star\to Y^\star$ is the composition with $h$.
-
-\subsection{The category of hypergraphs}
-
-We will start this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
-
-\begin{definition}A \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, whose elements are called respectively \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} functions  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
-A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute.
+In this section we introduce the notion of \emph{$\X$-hypergraph}.
+In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usua \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,wadler1995monads}.
+In\Cref{app:mon} the interested reader can find a brief review of the construction of such a monad.
+
+\begin{convention}
+	In this section we will operate inside a countably distributive and extensive cartesian category $(\X, \times, I)$ with finite limits.
+As shown in \Cref{app:mon}, then $\mo{U}\colon \mono{\X}\to \X$ has a left adjoint $\mo{F}$ and $\mo{F}\circ \mo{U}$ preserves pullbacks.
+Denoting by $(-)^\star$ such composition, we can assume that $X^\star$ is the coproduct $\sum_{n\in \mathbb{N}}X^n$.
+\end{convention}
+
+\begin{remark}\label{rem:mono}
+	Preservation of pullbacks implies that $(-)^\star$ sends monos to monos.
+\end{remark}
+
+\subsection{The category of $\X$-hypergraphs}
+
+We will start this section with the definition of $\X$-hypergraphs and we will see how to label them with an algebraic signature.
+
+\begin{definition}An \emph{$\X$-hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two objects $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the object of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
+A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of morphisms $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute.
 
 	\[\xymatrix{ E_{\mathcal{G}} \ar[d]_{h} \ar[r]^{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}& E_{\mathcal{G}} \ar[r]^{t_{\mathcal{G}}} \ar[d]_{h} & V^\star_{\mathcal{G}} \ar[d]^{k^\star}  \\ E_{\mathcal{G}} \ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} & E_{\mathcal{G}} \ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} }\]
-	We define $\hyp$ to be the resulting category.
+	We define $\hyp_\X$ to be the resulting category.
 \end{definition}
 
-Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$, then we can present $\hyp$ as a comma category.
+Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$, then we can present $\hyp_\X$ as a comma category.
 \begin{proposition}\label{prop:com}
-	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
+	$\hyp_\X$ is isomorphic to $\comma{\id{\X}}{\pro^\star}$
 \end{proposition}
@@
 
-We can show that the  Kleene star preserves pullbacks (see also \cite[Sec.
-3]{carboni1995connected}  and \cite[Ch.4]{leinster2004higher} for details and a deeper and more conceptual approach).\index{Kleene star}
-
-\begin{proposition}\label{prop:pb}
-	The functor $(-)^\star$ preserves pullbacks.
-\end{proposition}
-\begin{proof}
-	Suppose that a pullbacks square as the one below is given.
-	\[\xymatrix{P \ar[r]^{p_1} \ar[d]_{p_2}& X \ar[d]^{f}\\ Y \ar[r]_{g} & Z}\]
-	and consider the solid part of the following diagram.
-	\[\xymatrix{Z\ar@{.>}[dr]^{t} \ar@/^.3cm/[drr]^{t_1} \ar@/_.3cm/[ddr]_{t_2}\\&P^\star \ar[r]^{p^\star_1} \ar[d]_{p^\star_2}& X^\star \ar[d]^{f^\star}\\ &Y^\star \ar[r]_{g^\star} & Z^\star}\]
-	For every $z\in Z$ we have $t_1(z)\colon n\to X$ and $t_2(z)\colon m\to Y$ such that
-	\[f^\star(t_1(x))=g^\star(t_2(z))\]
-	In particular this entails that $n=m$ and that there is $t(z)\colon n\to P$ as in the diagram below 
-	\[\xymatrix{n\ar[dr]^{t(z)} \ar@/^.3cm/[drr]^{t_1(z)} \ar@/_.3cm/[ddr]_{t_2(z)}\\&P \ar[r]^{p_1} \ar[d]_{p_2}& X \ar[d]^{f}\\ &Y \ar[r]_{g} & Z}\]
-	But this is equivalent to say that the dotted $t\colon Z\to P$ exists, while its uniqueness follows at once from the universal property of the pullback with which we started.
-\end{proof}
-
-\begin{remark}\label{rem:mono}
-	Preservation of pullbacks implies that $(-)^\star$ sends monos to monos.
-\end{remark}
-
 \begin{corollary}\label{prop:hypadh}
-	$\hyp$ is an adhesive category.
+If $\X$ is (strictly) $\mathcal{M}$-adhesive	then $\hyp$ is an (strict) $\comma{\mathcal{M}}{\mathcal{M}}$-adhesive category.
 \end{corollary}
 \begin{proof}
-	$(-)^\star$ preserves pullbacks by \Cref{prop:pb}, while $\pro$ is continuous by definition, thus the thesis follows from This follows from \Cref{comma,prop:com}.
+	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.
 \end{proof}
@@
 
-\begin{proposition}\label{cor:left}
-	The forgetful functor $U_{\catname{Hyp}}\colon \hyp \to \catname{Set}$ which sends an hypergraph $\mathcal{G}$ to its set of nodes has a left adjoint $\Delta_{\hyp}$.
+\begin{proposition}\label{cor:left} If $\X$ has an initial object, then the forgetful functor $U_{\X}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\X}$.
 \end{proposition}
 
-\begin{remark}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\hyp}(X)$ is the hypergraph which has $X$ as set of nodes and $\emptyset$ as set of hyperedges and $?_X$ as both source and target function.
-\end{remark}
-
-Hypergraphs,  can be represented graphically.
+\begin{example}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\Set}(X)$ is the hypergraph which has $X$ as set of nodes and $\emptyset$ as set of hyperedges and $?_X$ as both source and target function.
+\end{example}
+
+\todo{forse possiamo anche cancellare tutti gli esempi sotto}
+
+$\Set$-hypergraphs,  can be represented graphically.
 We will use dots to denote nodes and squares to denote hyperedges, the name of a node or of an hyperedge will be put near the corresponding dot or square.
@@
 
-\subsubsection{$\hyp$ as a topos of presheaves}
-
-By \Cref{lim} we already know that $\hyp$ has all pullbacks and by \Cref{prop:hypadh} we know that it is adhesive.
-Actually more can be proved about it: we can realize $\hyp$ as a topos of presheaves \cite{bonchi2022string}.
+\subsubsection{$\hyp_\X$ as a category of functors}
+
+Following \cite{bonchi2022string}, we can present $\hyp_\X$ as a category of functor over a suitable category.
 
@@
 
-Now, given $F\colon \catname{H}\to \catname{Set}$ we can define
+Given $F\colon \catname{H}\to \catname{Set}$, since $\X$ has countable coproducts we can define
 \[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
-For every element $x$ of $F(k,l)$ we can put
-\begin{align*}
-	s^F_{k,l}(x)\colon k\to F(\bullet) \quad i \mapsto F(f_i)(x)\qquad 
-	t^F_{k,l}(x)\colon l\to F(\bullet) \quad i \mapsto F(f_{i+k})(x)
-\end{align*}
-obtaining
-$s_F, t_F\colon E_F\rightrightarrows \mathcal{F}(\bullet)^{\star}$.
+
+Now, for every $k$, $l$, $i$ and $j$ in $\mathbb{N}$ with $i< k$ and $j< l$ we can define $s^F_{k,l}\colon F(k,l)\to F(\bullet)^k$,  $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ as the unique ones fitting in the diagrams below, where the vertical arrows are the projections.
+\[\xymatrix{F(k,l)  \ar@{.>}[r]^{s^F_{k,l}} \ar[dr]_{F(f_i)}& F(\bullet)^{k} \ar[d]^{\pi^F_{i}} & F(k,l) \ar@{.>}[r]^{t^F_{k,l}} \ar[dr]_{F(f_{k+j})} & F(\bullet)^{l} \ar[d]^{\pi^F_{j}} \\ & F(\bullet) && F(\bullet)}\]
+
+In turn, these arrows allow us to consider
+$s_F, t_F\colon E_F\rightrightarrows F(\bullet)^{\star}$ as the unique arrows fitting in the diagrams below, where the vertical arrows are coprojections.
+\[\xymatrix{F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{s^{F}_{k,l}}& F(\bullet)^{k} \ar[d]^{b^F_{k}} & F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{t^{F}_{k,l}}& F(\bullet)^{l} \ar[d]^{b^F_{l}}\\ E_F \ar@{.>}[r]_-{s_F}& F(\bullet)^\star & E_F \ar@{.>}[r]_-{t_F}& F(\bullet)^\star}\]
+
 Let $\mathcal{G}_F$ be the resulting hypergraph.
-Now, every $\eta\colon F\rightarrow H$ in $\catname{Set}^{\catname{H}}$ has components $\eta_{k,l}\colon F(k,l)\to H(k,l)$, $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$, thus it induces a function $\hat{\eta}\colon E_F\rightarrow E_H$ such that the following squares commute
-\[\xymatrix{ E_F \ar[r]^{s_F} \ar[d]_{\hat{\eta}}& F(\bullet)^\star \ar[d]^{\eta^\star_\bullet} & E_F \ar[r]^{t_F} \ar[d]_{\hat{\eta}} & F(\bullet)^\star \ar[d]^{\eta^\star_\bullet}\\ E_H \ar[r]_{s_H} & H(\bullet)^\star & E_H \ar[r]_{t_H}& H(\bullet)^\star}\]
-
-This is equivalent to say that $\eta$ induces a morphism $(\hat{\eta}, \eta_{\bullet})\colon \mathcal{G}_F\to \mathcal{G}_H$.
-It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \catname{Set}^{\catname{H}}\to \hyp$.
+Now, every $\eta\colon F\rightarrow H$ in $\catname{Set}^{\catname{H}}$ has components $\eta_{k,l}\colon F(k,l)\to H(k,l)$, $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$.
+In particular we can define $\hat{\eta}\colon E_F\rightarrow E_H$ as $\sum_{k,l\in \mathbb{N}}\eta_{k,l}$.
+Now, on the one hand, we have
+\[\begin{split}
+	\pi^H_i\circ \eta^k_\bullet \circ  s^F_{k,l}&=\eta_\bullet \circ \pi^F_i \circ s^F_{k,l}\\&=\eta_\bullet \circ F(f_i)\\&=H(f_i)\circ \eta_{k,l}\\&=\pi^H_i\circ s^{H}_{k,l}\circ \eta_{k,l}
+\end{split} \qquad \begin{split}
+\pi^H_j\circ \eta^k_\bullet \circ  t^F_{k,l}&=\eta_\bullet \circ \pi^F_j \circ t^F_{k,l}\\&=\eta_\bullet \circ F(f_{k+j})\\&=H(f_{k+j})\circ \eta_{k,l}\\&=\pi^H_j\circ t^{H}_{k,l}\circ \eta_{k,l}
+\end{split} \]
+so that $\eta^k_\bullet \circ  s^F_{k,l}=s^{H}_{k,l}\circ \eta_{k,l}$ and $eta^k_\bullet \circ  t^F_{k,l}= t^{H}_{k,l}\circ \eta_{k,l}$. On the other hand, these equalities give us the following:
+\[\begin{split}
+	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ s^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ s^{F}_{k,l} \\&=b^H_{k}\circ s^H_{k,l}\circ \eta_{k,l}\\&=s_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	s_H\circ \hat{\eta}\circ a^F_{k,l}
+\end{split} \qquad \begin{split}
+	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ t^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ t^{F}_{k,l} \\&=b^H_{k}\circ t^H_{k,l}\circ \eta_{k,l}\\&=t_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	t_H\circ \hat{\eta}\circ a^F_{k,l}
+\end{split}\]
+which, in turn, entail that  that the following squares commute
+\[\xymatrix{E_F \ar[r]^{s_F} \ar@{.>}[d]_{\hat{\eta}}& F(\bullet)^\star \ar[d]^{\eta^\star_\bullet} & E_F \ar[r]^{t_F} \ar[d]_{\hat{\eta}} & F(\bullet)^\star \ar[d]^{\eta^\star_\bullet}\\ E_H \ar[r]_{s_H} & H(\bullet)^\star & E_H \ar[r]_{t_H}& H(\bullet)^\star}\]
+
+This is the same as saying that $\eta$ induces a morphism $(\hat{\eta}, \eta_{\bullet})\colon \mathcal{G}_F\to \mathcal{G}_H$.
+It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \catname{\X}^{\catname{H}}\to \hyp_\X$.
+
+\begin{remark}\label{rem:utile}
+For every $k\in \mathbb{N}$ consider the following pullback diagram	
+	\[\xymatrix{F(\bullet)_k  \ar[r]^{q_1} \ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ 1 \ar[r]_{o_k} & 1^\star}\]
+	Now, notice that 
+	\[\begin{split}
+		\lgh_{F(\bullet)}\circ b^{F}_k\circ s^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ s^F_{k,l}\\&=o_k\circ !_{F(k,l)}
+	\end{split} \qquad \begin{split}
+	\lgh_{F(\bullet)}\circ b^{F}_k\circ t^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ t^F_{k,l}\\&=o_k\circ !_{F(k,l)}
+	\end{split}\]
+so that we have two diagrams:
+	\[\xymatrix{F(k,l)\ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^1_{k,l}}  \ar@/_.5cm/[ddr]_{!_{F(k,l)}}&F(\bullet)^k \ar[dr]^{b^F_k}&& F(k,l) \ar@/_.5cm/[ddr]_{!_{F(k,l)}} \ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^2_{k,l}} &F(\bullet)^k \ar[dr]^{b^F_k}\\ & F(\bullet)_k  \ar[r]^{q_{k}} \ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} && F(\bullet)_k  \ar[r]^{q_{k} }\ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ &  1 \ar[r]_{o_k} & 1^\star && 1 \ar[r]_{o_k} & 1^\star}\]
+
+	Moreover we have
+	\[\begin{split}
+		s_F\circ a^F_{k,l}&=b^F_k\circ s^{F}_{k,l}\\&=
+		q_{k}\circ u^1_{k,l}	\end{split} \qquad \begin{split}
+		t_F\circ a^F_{k,l}&=b^F_k\circ t^{F}_{k,l}\\&=
+		q_{k}\circ u^2_{k,l}	\end{split}  \]
+
+	Therefore these two arrows, in turn, yield the dotted $v^1_{k,l}\colon F(k,l)\to F(\bullet)_k $ and $v^2_{k,l}\colon F(k,l)\to F(\bullet)_l$ as in the diagram below, where the right and bottom squares are pullbacks.
+	\[\xymatrix@C=45pt{F(k,l)  \ar[dr]^{a^F_{k,l}} \ar@{.>}[r]^{v^2_{k,l}} \ar@{.>}[d]^{v^1_{k,l}} \ar@/^.8cm/[rr]^{u^2_{k,l}} \ar@/_.5cm/[dd]_{u^1_{k,l}}& P_{l} \ar[r]_{p_{l,1}} \ar[d]_{p_{l,2}}& F(\bullet)_{l} \ar[d]^{q_{l}}\\ P_k \ar[r]^{p_{k,2}} \ar[d]^{p_{k,1}}& E_F \ar[r]_{s_F}  \ar[d]^{t_F}& F(\bullet)^\star \\ F(\bullet)_k  \ar[r]_{q_{k}}& F(\bullet)^\star}\]
+
+ By hypothesis, $\X$ is countably extensive, thus for every $k, l\in \mathbb{N}$, the following diagrams are pullbacks.
+ \[\xymatrix{F(k,l) \ar[r]^{a^F_{k,l}} & E_F \ar[d]^{}\\ 
+ F(\bullet)^k& F(\bullet)^\star}\]
+
+ Let now $d_1\colon Z\to P_l$ and $d_2\colon Z\to P_k $ be two arrows such that
+ \[p_{k,2}\circ d_2=p_{t,2}\circ d_1\]
+
+ Then we have
+ \begin{align*}
+ t_{F}\circ 	p_{t_2}\circ d_1&= \end{align*}
+
+ Showing, finally, that 
+\end{remark}
 
 \begin{proposition}
-	$\hyp$ is equivalent to the category $\catname{Set}^{\catname{H}}$.
+	$\hyp_\X$ is equivalent to the category $\catname{\X}^{\catname{H}}$.
 \end{proposition}
 \begin{proof}
-	Let $X$ be a set, for every $n\in \mathbb{N}$ define
-	\[X_{n}:= \left\{w\in X^{\star} \mid \dom(w)=n\right\}\]
+
+	For every object $X$ of $\X$ and $n\in \mathbb{N}$, we can define $X_n$ as the following pullback (cfr.~\Cref{app:mon})
+	\[\]
 	In particular, if $F\colon \catname{H}\to \catname{Set}$ then the image of the coprojection $\iota^{F}_{k,l}\colon F(k,l)\to E_F$ is the intersection
@@
 
-	We are now ready to that $\mathcal{G}_{-}$ is full and essentially surjective.
+We already know that $\mathcal{G}_{-}$ is faithful, we still have to show that it is full and essentially surjective.
 	\begin{itemize}
-		\item For fullness, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of hypergraphs and define $f_{k,l}$ to be $f\circ \iota^F_{k,l}$, the composition of $h$ with Now, if $x\in F(k,l)$ then
+		\item For fullness, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of $\X$-hypergraphs.
+Define $f_{k,l}\colon F(k,l)\to $ to be $f\circ a^F_{k,l}$, the composition of $h$ with Now, if $x\in F(k,l)$ then
 		\[\begin{split}
@@
 \end{proof}
-As a corollary we get immediately the following.
-\begin{corollary}
-	$\hyp$ is a complete category.
-\end{corollary}
 
@@
 
-\section{Some notes on free monoids}
+\section{Some notes on free monoids}\label{app:mon}
 
@@
 
-As a concluding step, we ask for a compatibility property between countable coproducts and pullbacks, to assure that $\mo{F}$ preserves pullbacks \cite{bibid}.
+As a concluding step, we ask for a compatibility property between countable coproducts and pullbacks, to assure that $\mo{F}$ preserves pullbacks (see also \cite[Sec.
+3]{carboni1995connected}  and \cite[Ch.4]{leinster2004higher} for details and a deeper and more conceptual approach in the case of $\Set$).
 
@@
 Suppose that  $(\X, \times, 1)$ is a countably distributive monoidal category, with $\X$ countably extensive. Then the following squares are pullbacks for every $n\in \mathbb{N}$ and object $X$.
-\[\xymatrix{X^{n} \ar[r]^-{j_n} \ar[d]_{!_{X^n}}& X^\star \ar[d]^{\lgh_X} & Y^{n} \ar[r]^-{k_n} \ar[d]_{!_{Y^n}}& Y^\star \ar[d]^{\lgh_Y}\\ 1 \ar[r]_{a_n}&  1^\star & 1 \ar[r]_{a_n}&  1^\star}\]
+\[\xymatrix{X^{n} \ar[r]^-{j_n} \ar[d]_{!_{X^n}}& X^\star \ar[d]^{\lgh_X} & Y^{n} \ar[r]^-{k_n} \ar[d]_{!_{Y^n}}& Y^\star \ar[d]^{\lgh_Y}\\ 1 \ar[r]_{o_n}&  1^\star & 1 \ar[r]_{o_n}&  1^\star}\]
 \end{remark}
@@
 	\begin{split}
-		\lgh_X\circ t_1 \circ p_n&=\lgh_Z\circ f^\star \circ t_1\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=a_n\circ !_{Z^n}\circ q_n\\&=a_n\circ !_{T_n}
+		\lgh_X\circ t_1 \circ p_n&=\lgh_Z\circ f^\star \circ t_1\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=o_n\circ !_{Z^n}\circ q_n\\&=o_n\circ !_{T_n}
 	\end{split}\qquad \begin{split}
-		\lgh_Y\circ t_2 \circ p_n&=\lgh_Z\circ g^\star \circ t_2\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=a_n\circ !_{Z^n}\circ q_n\\&=a_n\circ !_{T_n}
+		\lgh_Y\circ t_2 \circ p_n&=\lgh_Z\circ g^\star \circ t_2\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=o_n\circ !_{Z^n}\circ q_n\\&=o_n\circ !_{T_n}
 	\end{split}\]
@@
 
-	\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{x_n} \ar[r]^{p_n} & T \ar[dr]^{t_1}&& T_n \ar@/_.3cm/[ddr]_{!_{T_n}} \ar[r]^{p_n} \ar@{.>}[dr]^{y_n}& T \ar[dr]^{t_2}\\ &X^n   \ar[d]_{!_{X^n}}\ar[r]^{j_n}& X^\star \ar[d]^{\lgh_X}& & Y^n \ar[d]_{!_{Y^n}}  \ar[r]^{h_n}& Y^\star \ar[d]^{\lgh_Y}\\ & 1 \ar[r]_{a_n}& 1^\star && 1  \ar[r]_{a_n}& 1^\star}\]
+	\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{x_n} \ar[r]^{p_n} & T \ar[dr]^{t_1}&& T_n \ar@/_.3cm/[ddr]_{!_{T_n}} \ar[r]^{p_n} \ar@{.>}[dr]^{y_n}& T \ar[dr]^{t_2}\\ &X^n   \ar[d]_{!_{X^n}}\ar[r]^{j_n}& X^\star \ar[d]^{\lgh_X}& & Y^n \ar[d]_{!_{Y^n}}  \ar[r]^{h_n}& Y^\star \ar[d]^{\lgh_Y}\\ & 1 \ar[r]_{o_n}& 1^\star && 1  \ar[r]_{o_n}& 1^\star}\]
 
@@
 \begin{align*}
-\lgh_P\circ t' \circ p_n&=\lgh_X\circ p^\star \circ t'\circ p_n\\&=\lgh_X\circ t_1\circ p_n\\&=a_n\circ !_{T_n}
+\lgh_P\circ t' \circ p_n&=\lgh_X\circ p^\star \circ t'\circ p_n\\&=\lgh_X\circ t_1\circ p_n\\&=o_n\circ !_{T_n}
 \end{align*}
@@
 So that, for every natural $n$, there exists an arrow $u_n\colon T_n \to X^n$ fitting in the diagram below.
-\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{u_n} \ar[r]^{p_n} & T \ar[dr]^{t'}\\ &P^n   \ar[d]_{!_{P^n}}\ar[r]^{v_n}& P^\star \ar[d]^{\lgh_P}\\ & 1 \ar[r]_{a_n}& 1^\star }\]
+\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{u_n} \ar[r]^{p_n} & T \ar[dr]^{t'}\\ &P^n   \ar[d]_{!_{P^n}}\ar[r]^{v_n}& P^\star \ar[d]^{\lgh_P}\\ & 1 \ar[r]_{o_n}& 1^\star }\]
 Moreover, we have

### 2025-02-04 icgt/Hypergraphs_with_equivalences.tex
Hyp w/equiv

\section{Hypergraphs with equivalences}

\begin{definition}
	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is the object of \emph{equivalence classes} and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is an epimorphism called \emph{quotient map}. A morphism $h:\mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute.
	\[\xymatrix{
		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} \\
		{E_\mathcal{H}}\ar[r]^{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	 			& {E_\mathcal{H}}\ar[r]^{t_\mathcal{H}} & {V_{\mathcal{H}^\star}} \\
						      & {V_\mathcal{G}}\ar[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {C_{\mathcal{G}}} \ar[d]^{h_C} \\
						      & {V_\mathcal{H}}\ar[r]^{q_\mathcal{H}} & {C_\mathcal{H}}
	}\]
	The category of hypergraphs with equivalences and their morphisms is denoted $\EqHyp$.

\end{definition}

\begin{remark}\label{rem:eqhyp_morphs}
	Morphisms of hypergraphs with equivalences are uniquely determined by the first two components. That is, if $h_1 = (h_E, h_V, f)$ and $h_2 = (h_E, h_V, g)$ are two morphisms $\mathcal{G \to H}$, then we have
	\[\xymatrix{
			{V_\mathcal{G}} \ar[r]^{h_V}\ar[d]_{q_\mathcal{G}} & V_\mathcal{H} \ar[d]^{q_\mathcal{H}} & V_\mathcal{G}\ar[l]_{h_V}\ar[d]^{q_\mathcal{G}}\\
			C_{\mathcal{G}}\ar[r]_{f} & C_{\mathcal{H}} & C_{\mathcal{G}}\ar[l]^{g}
	}\]
	Hence,
	\begin{align*}
		f \circ q_\mathcal{G} &= q_\mathcal{H}\circ h_V \\ &=g\circ q_\mathcal{G}
	\end{align*}
	Since $q_\mathcal{G}$ is epi, we obtain $f = g$.
\end{remark}

$\EqHyp$ has a forgetful functor $U_{\EqHyp}:\EqHyp \to \Set$, which sends each $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ into $V_\mathcal{G}$, and each $h = (h_E, h_V, h_C)$ onto $h_V$.

\begin{proposition}
	$U_\EqHyp$ has a left adjoint $\Delta_{\EqHyp}: \Set \to \EqHyp$.
\end{proposition}

\begin{proof}
	For each set $X$, define $\Delta_\EqHyp(X):= (\emptyset, X, \{\bullet\}, ?_X, ?_X, !_X)$. Consider now $h: \Delta_{\EqHyp}(X) \to \mathcal{H}$.
	\[\xymatrix@C=2.3cm{
			\Delta_{\EqHyp}(X) \ar@{.>}[d]_{\Delta_\EqHyp(f)} \ar[dr]^{h} & \\
			\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) \ar[r]_{\epsilon_{\mathcal{H}}} & \mathcal{H}
	}\]
	Where $\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) = (\emptyset, V_\mathcal{H}, \{\bullet\}, ?_{V_\mathcal{H}}, ?_{V_\mathcal{H}}, !_{V_\mathcal{H}})$ and $\epsilon_{\mathcal{H}} = (?_{E_\mathcal{H}}, id_{V_\mathcal{H}}, g)$.
	Note that, since $\Delta_{\EqHyp}(X)$ has the empty set as object of edges, $h_E = ?_{E_\mathcal{H}}$, then, the unique arrow that fits in the diagram is $\Delta_{\EqHyp}(f) = (?_{E_\mathcal{H}}, h_V, id_{\{\bullet\}})$.

\end{proof}

### 2025-02-04 icgt/Hypergraphs_with_equivalences.tex
Hyp w/equiv

@@
 	}\]
-	Where $\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) = (\emptyset, V_\mathcal{H}, \{\bullet\}, ?_{V_\mathcal{H}}, ?_{V_\mathcal{H}}, !_{V_\mathcal{H}})$ and $\epsilon_{\mathcal{H}} = (?_{E_\mathcal{H}}, id_{V_\mathcal{H}}, g)$.
-	Note that, since $\Delta_{\EqHyp}(X)$ has the empty set as object of edges, $h_E = ?_{E_\mathcal{H}}$, then, the unique arrow that fits in the diagram is $\Delta_{\EqHyp}(f) = (?_{E_\mathcal{H}}, h_V, id_{\{\bullet\}})$.
+	Where $\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) = (\emptyset, V_\mathcal{H}, \{\bullet\}, ?_{V_\mathcal{H}}, ?_{V_\mathcal{H}}, !_{V_\mathcal{H}})$ and $\epsilon_{\mathcal{H}} = (?_{E_\mathcal{H}}, \id{V_\mathcal{H}}, g)$.
+	Note that, since $\Delta_{\EqHyp}(X)$ has the empty set as object of edges, $h_E = ?_{E_\mathcal{H}}$, then, the unique arrow that fits in the diagram is $\Delta_{\EqHyp}(f) = (?_{E_\mathcal{H}}, h_V, \id{\{\bullet\}})$.
 
 \end{proof}
+
+We now define another functor $T: \EqHyp \to \hyp$, which ``forgets'' the quotient part, mapping each hypergraph with equivalence $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ onto $T(\mathcal{G})=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
+Then, we have the following result.
+
+\begin{proposition}
+	$T$ has a left adjoint $L: \hyp \to \EqHyp$.
+\end{proposition}
+
+\begin{proof}
+	Let $\mathcal{G}$ be a hypergraph, and define $L(\mathcal{G}) := \mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, \{\bullet\}, s_\mathcal{G}, t_\mathcal{G}, !_{V_\mathcal{G}})$.
+Let now $h: L(\mathcal{G})\to \mathcal{H}$ be a morphism in $\EqHyp$, and consider the following situation.
+	\[\xymatrix@C=2.3cm{
+		L(\mathcal{G}) \ar@{.>}[d]_{L(f)} \ar[dr]^{h}\\ L(T(\mathcal{H})) \ar[r]_{\epsilon_{\mathcal{H}}} & \mathcal{H}
+	}\]
+	Where $L(T(\mathcal{H}))=(E_\mathcal{H}, V_{\mathcal{H}}, \{\bullet\}, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$.
+Then, $\epsilon_\mathcal{H} = (\id{E_\mathcal{H}}, \id{V_\mathcal{H}}, h_C)$ (recall that by \Cref{rem:eqhyp_morphs}, the last component is uniquely determined by the first two), and $L(f)$ must be $(h_E, h_V, \id{\{\bullet\}})$.
+\end{proof}

### 2025-02-04 icgt/main.tex
Hyp w/equiv
minori

@@
 In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usua \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,wadler1995monads}.
-In\Cref{app:mon} the interested reader can find a brief review of the construction of such a monad.
+In \Cref{app:mon} the interested reader can find a brief review of the construction of such a monad.
 
@@
 \end{split} \]
-so that $\eta^k_\bullet \circ  s^F_{k,l}=s^{H}_{k,l}\circ \eta_{k,l}$ and $eta^k_\bullet \circ  t^F_{k,l}= t^{H}_{k,l}\circ \eta_{k,l}$. On the other hand, these equalities give us the following:
+so that $\eta^k_\bullet \circ  s^F_{k,l}=s^{H}_{k,l}\circ \eta_{k,l}$ and $\eta^k_\bullet \circ  t^F_{k,l}= t^{H}_{k,l}\circ \eta_{k,l}$. On the other hand, these equalities give us the following:
 \[\begin{split}
@@
 \begin{remark}\label{rem:utile}
-For every $k\in \mathbb{N}$ consider the following pullback diagram	
-	\[\xymatrix{F(\bullet)_k  \ar[r]^{q_1} \ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ 1 \ar[r]_{o_k} & 1^\star}\]
+	By \Cref{rem:salv} we know that countably distributivity entails that, for every $k,l\in \mathbb{N}$, the arrow $b^F_k\times b^F_l$ is a coprojection, thus extensivity entails that the square is a pullback
+	\[\xymatrix@C=30pt{F(k,l) \ar[d]_{(s^F_{k,l}, t^F_{k,l})}  \ar[r]^{a^F_{k,l}}& E_F \ar[d]^{(s_F, t_F)} \\ F(\bullet)^k\times F(\bullet)^l \ar[r]_{b^F_k\times b^F_l} & F(\bullet)^\star\times F(\bullet)^\star}\]
+
+	\iffalse 
+	As in \Cref{rem:pb}, countably extensivity of $X$ guarantees that, for every $k\in \mathbb{N}$ following square is a pullback.	
+	\[\xymatrix{F(\bullet)^k  \ar[r]^{b^F_k} \ar[d]_{!_{F(\bullet)^k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ 1 \ar[r]_{o_k} & 1^\star}\]
+
 	Now, notice that 
@@
  Showing, finally, that
+ \fi  
 \end{remark}
@@
 \begin{proof}	
-
-	For every object $X$ of $\X$ and $n\in \mathbb{N}$, we can define $X_n$ as the following pullback (cfr.~\Cref{app:mon})
-	\[\]
-	In particular, if $F\colon \catname{H}\to \catname{Set}$ then the image of the coprojection $\iota^{F}_{k,l}\colon F(k,l)\to E_F$ is the intersection
-	\[s^{-1}_F\left(F(\bullet)_{k}\right)\cap t^{-1}_F\left(F(\bullet)_{l}\right) \]
-
 We already know that $\mathcal{G}_{-}$ is faithful, we still have to show that it is full and essentially surjective.
@@
 		\item For fullness, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of $\X$-hypergraphs.
-Define $f_{k,l}\colon F(k,l)\to $ to be $f\circ a^F_{k,l}$, the composition of $h$ with Now, if $x\in F(k,l)$ then
+By \Cref{rem:utile}, for every $k,l\in \mathbb{N}$, the front square in diagram below is a pullback, yielding the dotted arrow $\eta_{k,l}\colon F(k,l)\to H(k,l)$.
+		\[\xymatrix@C=10pt{F(k,l)   \ar[dd]_{(s^F_{k,l}, t^F_{k,l})}\ar[rr]^-{a^F_{k,l}} \ar@{.>}[dr]_{\eta_{k,l }}&& E_F \ar[dd]|\hole^(.7){(s_F, t_F)}  \ar[dr]^{f}\\ & H(k,l) \ar[dd]_(.3){(s^H_{k,l}, t^H_{k,l})}\ar[rr]^(.4){a^H_{k,l}} &&  E_H \ar[dd]^{(s_H, t_H)}\\F(\bullet)^k\times F(\bullet)^l \ar[dr]_{g^k\times g^l} \ar[rr]|\hole^(.65){b^F_{k,l}\times b^F_{k,l}}& &F(\bullet)^\star \times F(\bullet)^\star  \ar[dr]^{g^\star\times g^\star}\\&H(\bullet)^k\times H(\bullet)^l \ar[rr]_{b^H_k\times b^H_l} && H(\bullet)^\star \times H(\bullet)^\star  }\]
+
+		As $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ we can simply take  $g$.
+Then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
+Indeed, given an arrow $f_i\colon(k,l)\to \bullet$ then we have :
+		\begin{align*}
+			\eta_\bullet \circ F(f_i)&=g\circ F(f_i)
+			\\&= \begin{cases}
+			g\circ \pi^F_i\circ s^F_{k,l} & i <k\\
+			g\circ \pi^F_i\circ t^F_{k,l} & \text{otherwise}
+			\end{cases}
+			\\&=
+			\begin{cases}
+		\pi^H_i\circ g^k\circ s^F_{k,l} & i <k\\
+		\pi^H_i\circ g^k\circ t^F_{k,l} 	& \text{otherwise}
+			\end{cases}\\&=
+		\begin{cases}
+	\pi^H_i\circ s^H_{k,l} \circ \eta_{k,l}& i <k\\
+	\pi^H_i\circ t^H_{k,l} \circ \eta_{k,l}	& \text{otherwise}
+	\end{cases}\\&=H(i)\circ \eta_{k,l}
+		\end{align*}
+		Finally, by construction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$.
+
+		\item  Let us turn to essential surjectivity.
+Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define $F_{\mathcal{G}}(\bullet):=V_{\mathcal{G}}$ and $F_{\mathcal{G}}(k,l)$ by the following pullback.
+Notice that, by \Cref{rem:salv} and countably extensivity, $(E_{\mathcal{{G}}}, \{a_{k,l}\}_{k,l\in \mathbb{N}})$ is a coproduct.
+		\[\xymatrix@C=30pt{F_\mathcal{G}(k,l) \ar[d]_{p_{k,l}}  \ar[r]^{a_{k,l}}& E_{\mathcal{G}} \ar[d]^{(s_F, t_F)} \\ V_{\mathcal{G}}^k\times V_{\mathcal{G}}^l \ar[r]_{b_k\times b_l} & V_{\mathcal{G}}^\star\times V_{\mathcal{G}}^\star}\]
+
+		Let $q_{i;k,l}\colon V_\mathcal{G}^k\times V_{\mathcal{G}}^l\to V_\mathcal{G} $ be the $i^{\text{th}}$ projection, then for every morphism $f_i\colon (k,l)\to \bullet$ in $\catname{H}$ we can define $F_{\mathcal{G}}(f_i)$ as $q_{i; k,l}\circ p_{k,l}$.
+$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$.
+
+		Now, we know that there is an isomorphism $\phi \colon E_{\mathcal{G}} to \sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)$ making the diagram below commutative.
+		\[\xymatrix{\\& F_{\mathcal{G}}(k,l) \\E_{\mathcal{G}} & & \sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)}\]
+
+		 moreover, by construction we have
 		\[\begin{split}
-			s_H (f_{k,l} (x))&=s_H \left(f \left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt}\left(s_{F} \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)
-		\end{split}\qquad \begin{split}
-			t_H (f_{k,l} (x))&=s_t\hspace{-1pt} \left(f \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt} \left(t_{F}\hspace{-1pt} \left(\iota^F_{k,l} (x)\right)\right)
+		s_{F_{\mathcal{G}}}\circ a^{F_{\mathcal{G}}}_{k,l}&=b^{F_{\mathcal{G}}}\circ s^{F_{\mathcal{G}}}_{k,l}
 		\end{split}\]
-		Therefore there exists $\eta_{k,l}\colon F(k,l)\to H(k,l)$ fitting in the diagram below
-		\[\xymatrix{F(k,l) \ar[r]^-{\iota^{F}_{k,l}} \ar@{.>}[d]_{\eta_{k,l}}& E_F \ar[d]^{f_{k,l}}\\ H(k,l) \ar[r]_-{\iota^{H}_{k,l}}& E_H}\]
-		Define $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ simply as $g^\star$, then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
-Indeed, if $f_i\colon (k,l)\to \bullet$ we have:
-		\[\xymatrix{F(k,l) \ar@/^.4cm/[rr]^{s^F_{k,l}} \ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{s_F}& F(\bullet)^\star \ar[d]^{g^\star}&F(k,l) \ar@/^.4cm/[rr]^{t^F_{k,l}}\ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{t_F}& F(\bullet)^\star \ar[d]^{g^\star}\\ H(k,l) \ar@/_.4cm/[rr]_{s^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{s_H}& H(\bullet)^\star& H(k,l) \ar@/_.4cm/[rr]_{t^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{t_H}& H(\bullet)^\star}\]
-		Thus if $i<k$ then
-		\begin{align*}
-			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(s^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(s^F_{k,l}(x)\right)(i)\\&=s^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
-		\end{align*}
-		while, if $k\leq i < k+l-1$
-		\begin{align*}
-			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(t^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(t^F_{k,l}(x)\right)(i)\\&=t^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
-		\end{align*}
-		Finally, by contruction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$. 
-		\item Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define 
-		\[F_{\mathcal{G}}(k,l):=s_\mathcal{G}^{-1}(V_k)\cap t_\mathcal{G}^{-1}(V_l) \qquad F_{\mathcal{G}}(\bullet):=V_\mathcal{G}\]
-		Given $f_i\colon (k,l)\to \bullet$ we put
-		\[F_{\mathcal{G}}(f_i)\colon F_{\mathcal{G}}(k,l)\to F_{\mathcal{G}}(\bullet) \qquad x\mapsto \begin{cases}
-			s_\mathcal{G}(x)(i) & i<k\\
-			t_\mathcal{G}(x) (i-k) &i\leq k < k+l-1
-		\end{cases}  \]
-
-		$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$ and for every $h\in E_\mathcal{G}$ there exists a unique pair $(k,l)$ such that $h\in F_{\mathcal{G}}(k,l) $, namely the pair $(\dom(s_\mathcal{G})(h), \dom(t_\mathcal{G})(h))$thus
-		\[\sum_{k,l\in \mathbb{N}}F_{\mathcal{G}}(k,l)\simeq E\]
-		Moreover, by construction $s_{F_{\mathcal{G}}}=s$ and $t_{F_{\mathcal{G}}}=t$, from which the thesis follows. 
+
+		$s_{F_{\mathcal{G}}}=s_{\mathcal{G}}$ and $t_{F_{\mathcal{G}}}=t_{\mathcal{G}}$, from which the thesis follows. 
 	\end{itemize}
@@
 
-\section{Hypergraphs with equivalences}
+\section{Hypergraphs  and term graphs with equivalences}
 
 \subsection{title}
-
-\section{title}
 
@@
 
+\begin{remark}\label{rem:salv}
+	There is a property of countably distributive categories which is worth to be pointed out.
+Let $\{X_i\}_{i\in I}$ and $\{Y_j\}_{j\in J}$ be two countable family of objects, then for every $i\in I$ there is an isomorphism $\phi_{i}\colon \sum_{j\in J}X_i\times Y_j\to X_i\times \sum_{j\in J} Y_j$ fitting in the following triangle, where $\alpha^j_j$ and $y_j$ are coprojections.
+	\[\xymatrix{& X_i\otimes Y_j \ar[dl]_{\alpha^i_j} \ar[dr]^{\id{X_i}\otimes y_j} \\ \Sum_{j\in J} X_i\otimes Y_j \ar[rr]_{\phi_i}&& X_i\otimes (\Sum_{j\in J}Y_j) }\]
+
+	Moreover, we also have an isomorphism $\psi\colon \sum_{i\in I}(X_i\otimes \sum_{j\in J}Y_j)\to (\sum_{i\in I}X_i) \otimes (\sum_{j\in J} Y_j)$ as in the triangle below, where, again, $\beta_i$ and $x_i$ are coprojections.
+	\[\xymatrix{&X_i \otimes \Sum_{j\in J}Y_j \ar[dl]_{\beta_i} \ar[dr]^{ x_i \otimes \sum_{j\in J} \id{Y_j}} \\ \Sum_{i\in I} ( X_i \otimes \Sum_{j\in J}Y_j) \ar[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \otimes (\Sum_{j\in J}Y_j)}\]
+
+		Now, since coproducts commute with coproducts, in every category there is a third isomorphism $\theta \colon \sum_{(i,j)\times I\times J}(X_i\otimes Y_j) \to \sum_{i\in I}\sum_{j\in J}(X_i\otimes Y_j)$ making the following diagram commutative, in which all arrows besides $\theta$ are coprojections.
+		\[\xymatrix{\Sum_{(i,j)\times I\times J}(X_i\otimes Y_j)  \ar[r]^-{\theta}& \Sum_{i\in I}\Sum_{j\in J}(X_i\otimes Y_j) \\ X_i\otimes Y_j  \ar[r]_{\alpha^i_j} \ar[u]^-{\delta_{i,j}}& \Sum_{j\in J}(X_i\otimes J) \ar[u]_-{\gamma_i}}\]
+
+		Putting all these morphisms together, we get the following diagram.
+	\[\xymatrix@C=38pt{\Sum_{(i,j)\in I\times J} (X_i\otimes Y_j) \ar[d]_{\theta}\\ \Sum_{i\in I} \Sum_{j\in J} (X_i\otimes Y_j) \ar[r]^-{\sum_{i\in I}\phi_i}& \Sum_{i\in I}(X_i\otimes \Sum_{j\in J} Y_j) \ar[dr]^-{\psi} \\ \Sum_{j\in J}  (X_i\otimes Y_j) \ar[r]^{\phi_i} \ar[u]^-{\gamma_{i}} & X_i\otimes \Sum_{j\in J} Y_j \ar[u]^-{\beta_i}\ar[r]^-{x_i\otimes \sum_{j\in J}\id{Y_j}}&  (\Sum_{i\in I}X_i) \otimes (\Sum_{j\in J}Y_j)\\X_i\otimes Y_j \ar@/^1.7cm/[uuu]^-{\delta_{i,j}} \ar[u]^{\alpha^i_j} \ar[ur]_{\hspace{3pt}\id{X_i}\otimes y_j} \ar@/_1cm/[urr]_{x_i\otimes y_j}}\]
+
+Summing up, we have just proved that $((\sum_{i\in I}X_i) \otimes (\sum_{j\in J} Y_j), \{x_{i}\otimes y_j\}_{I\times J})$
+ is a coproduct for the family $\{x_i\otimes y_j\}_{(i,j)\in I\times J}$.
+\end{remark}
+
 We cite the following, fundamental, result proved in \cite{lack2010note}.

### 2025-02-04 icgt/Hypergraphs_with_equivalences.tex

@@
 	\[\xymatrix{
-		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} \\
-		{E_\mathcal{H}}\ar[r]^{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	 			& {E_\mathcal{H}}\ar[r]^{t_\mathcal{H}} & {V_{\mathcal{H}^\star}} \\
-						      & {V_\mathcal{G}}\ar[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {C_{\mathcal{G}}} \ar[d]^{h_C} \\
-						      & {V_\mathcal{H}}\ar[r]^{q_\mathcal{H}} & {C_\mathcal{H}}
+		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {C_{\mathcal{G}}} \ar[d]^{h_C} \\
+		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}^\star}}& {V_\mathcal{H}}\ar[r]_{q_\mathcal{H}} & {C_\mathcal{H}}
 	}\]

### 2025-02-04 icgt/Hypergraphs_with_equivalences.tex
Hyp w/equiv

@@
 \begin{proof}
-	Let $\mathcal{G}$ be a hypergraph, and define $L(\mathcal{G}) := \mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, \{\bullet\}, s_\mathcal{G}, t_\mathcal{G}, !_{V_\mathcal{G}})$.
+	Let $\mathcal{G}$ be a hypergraph, and define $L(\mathcal{G}) := (E_\mathcal{G}, V_{\mathcal{G}}, \{\bullet\}, s_\mathcal{G}, t_\mathcal{G}, !_{V_\mathcal{G}})$.
 Let now $h: L(\mathcal{G})\to \mathcal{H}$ be a morphism in $\EqHyp$, and consider the following situation.
@@
 \end{proof}
+
+\begin{remark}
+	$T$ is faithful. Indeed, consider two morphisms $h = (h_E, h_V, h_C)$ and $k = (k_E, k_V, k_C)$, and suppose $T(h) = T(k)$, that is, $(h_E, h_V) = (k_E, k_V)$.
+	By \Cref{rem:eqhyp_morphs}, we can conclude also $h_C = k_C$, and hence the faithfulness of $T$.
+\end{remark}

### 2025-02-06 icgt/main.tex
cose

@@
 \newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
+\newcommand{\EqHyp}{\catname{EqHyp}} %equivalence hypergraphs
 \newcommand{\gr}{\textbf{\textup{Graph}}}
@@
 \end{example}
+
+\begin{remark}\label{rem:deco}
+	We can point out an important property of strict $\mathcal{M}$-adhesive categories with pullbacks and consider the $\mathcal{M}$-pushout square below.
+	\[\xymatrix{A \ar[r]^{f} \ar@{>->}[d]_{m}& B \ar@{>->}[d]^{n}\\ C \ar[r]_{g} & D}\]
+
+	Given an arrow $d\colon X\to D$, we can present the object $X$ has a pushout: indeed, consider the following cube, in which all the three vertical squares are pullbacks.
+	\[
+	\xymatrix@C=15pt@R=9pt{&V\ar[dd]|\hole_(.65){a}\ar[rr]^{v} \ar@{>.>}[dl]_{u} && Y \ar[dd]^{b} \ar@{>->}[dl]_{y} \\ Z  \ar[dd]_{c}\ar[rr]^(.7){z} & & X \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{g} & & D }\]
+
+Now, notice that, since the front square is a pullback, then the dotted arrow $u\colon V\to Z$ exists.
+Moreover, the usual composition and decomposition property of pullbacks \cite{mac2013categories} entails that the left face of the cube so obtained is a pullback too, proving that $u$ is in $\mathcal{M}$ and that the top square is a pushout.
+
+	Clearly if the arrow $p\colon X\to D$ is in $\mathcal{M}$, we can omit the assumptions of strictness and the existence of all pullbacks.
+\end{remark}
+
+Finally, another  useful properties of $\mathcal{M}$-adhesive category are the following.
+\begin{proposition}\label{prop:regmono}
+	If $\X$ is $\mathcal{M}$-adhesive then the following are true:
+	\begin{enumerate}
+		\item every $\mathcal{M}$-pushout square is also a pullback;
+		\item every arrow in $\mathcal{M}$ is a regular mono.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}
+	\begin{enumerate}
+		\item  Consider the following cube in which the bottom face is an $\mathcal{M}$-pushout.
+		\[\xymatrix@C=15pt@R=9pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_(.6){\id{B}} \\ A  \ar@{>->}[dd]_{m}\ar[rr]^(.65){g} & & B \ar@{>->}[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{f} & & D}\]
+		By construction the top face of the cube is a pushout and the back one a pullback.
+The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the thesis follows.
+		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback.
+		\[\xymatrix{X \ar@{>->}[r]^{m} \ar@{>->}[d]_{m}& Y \ar@{>->}[d]^{h}\\ Y \ar@{>->}[r]^{k} & Z}\]
+		It is now immediate to see that $m$ is the equalizer of $h$ and $k$. \qed
+	\end{enumerate}
+\end{proof}
 
@@
 In this section we introduce the notion of \emph{$\X$-hypergraph}.
-In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usua \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,wadler1995monads}.
+In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usual \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,wadler1995monads}.
 In \Cref{app:mon} the interested reader can find a brief review of the construction of such a monad.
@@
 \begin{convention}
-	In this section we will operate inside a countably distributive and extensive cartesian category $(\X, \times, I)$ with finite limits.
+	In this section and in the following one we will operate inside a countably distributive and extensive cartesian category $(\X, \times, I)$ with finite limits.
 As shown in \Cref{app:mon}, then $\mo{U}\colon \mono{\X}\to \X$ has a left adjoint $\mo{F}$ and $\mo{F}\circ \mo{U}$ preserves pullbacks.
 Denoting by $(-)^\star$ such composition, we can assume that $X^\star$ is the coproduct $\sum_{n\in \mathbb{N}}X^n$.
+We will also assume that $(-)^\star$ preserves equalizers.
+\todo{Non c'è nessuna ragione categoriale carina come l'estensività che garantisce la preservazione degli equalizzatori.
+In $\Set$ è vero per un risultato di Carboni e Johnstone che non credo si generalizzi}
 \end{convention}
@@
 \begin{corollary}\label{prop:hypadh}
-If $\X$ is (strictly) $\mathcal{M}$-adhesive	then $\hyp$ is an (strict) $\comma{\mathcal{M}}{\mathcal{M}}$-adhesive category.
+If $\X$ is (strictly) $\mathcal{N}$-adhesive	then $\hyp$ is an (strict) $\mathcal{M}$-adhesive category, where $\mathcal{M}$ is the class of all morphism $(h,k)$ with both $h$ and $k$ in $\mathcal{N}$.
+
+In particular, if $\X$ is (quasi)adhesive then so is $\hyp$.
 \end{corollary}
@@
 \end{proof}
+
+Another useful corollary of \Cref{prop:com} is the following one.
+
+\begin{corollary}\label{cor:monhyper}
+A morphism $(h,k)$ is a mono in $\hyp_\X$ if and only if both its components are mono in $\X$.
+\end{corollary}
 
@@
 
-\begin{example}\label{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature, we can construct the hypergraph $\mathcal{G}^\Sigma$ taking $V_{\mathcal{G}^\Sigma}$ and $E_{\mathcal{G}^\Sigma}$ to be respectively the singleton $\{\heartsuit\}$ and the set $O_\Sigma$.
-We put
-	\[\begin{matrix}
-		s_{\mathcal{G}^\Sigma}\colon O_\Sigma\to \{\heartsuit\}^\star & o\mapsto \delta_\heartsuit^{\ari_\Sigma(o)}
-		&&
-		t_{\mathcal{G}^\Sigma}\colon O_\Sigma\to \{\heartsuit\}^\star & o\mapsto \delta_\heartsuit
-	\end{matrix}\]
-	For instance let $\Sigma_G$ be the signature of groups of \Cref{ex:g}, then $\mathcal{G}^{\Sigma_G}$ is depicted as:
+\todo{Anche 'sta sezione possiamo anche buttarla via}
+\subsubsection{$\hyp_\X$ as a category of functors}
+
+Following \cite{bonchi2022string}, we can present $\hyp_\X$ as a category of functor over a suitable category.
+
+\begin{definition}Let $\catname{H}$ be the category in which:
+	\begin{itemize}
+		\item the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$
+		\item arrows are given by the identities $\id{k,l}$ and $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$;
+		\item composition is defined simply putting, for every $f_i\colon (k,l)\rightarrow \bullet$:
+		\begin{equation*}
+			f_i=f_i\circ \id{k,l} \qquad f_i = \id{\bullet}\circ f_i 
+		\end{equation*}
+	\end{itemize}
+\end{definition}
+
+Given $F\colon \catname{H}\to \catname{Set}$, since $\X$ has countable coproducts we can define
+\[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
+
+Now, for every $k$, $l$, $i$ and $j$ in $\mathbb{N}$ with $i< k$ and $j< l$ we can define $s^F_{k,l}\colon F(k,l)\to F(\bullet)^k$,  $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ as the unique ones fitting in the diagrams below, where the vertical arrows are the projections.
+\[\xymatrix{F(k,l)  \ar@{.>}[r]^{s^F_{k,l}} \ar[dr]_{F(f_i)}& F(\bullet)^{k} \ar[d]^{\pi^F_{k,i}} & F(k,l) \ar@{.>}[r]^{t^F_{k,l}} \ar[dr]_{F(f_{k+j})} & F(\bullet)^{l} \ar[d]^{\pi^F_{l,j}} \\ & F(\bullet) && F(\bullet)}\]
+
+In turn, these arrows allow us to consider
+$s_F, t_F\colon E_F\rightrightarrows F(\bullet)^{\star}$ as the unique arrows fitting in the diagrams below, where the vertical arrows are coprojections.
+\[\xymatrix{F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{s^{F}_{k,l}}& F(\bullet)^{k} \ar[d]^{b^F_{k}} & F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{t^{F}_{k,l}}& F(\bullet)^{l} \ar[d]^{b^F_{l}}\\ E_F \ar@{.>}[r]_-{s_F}& F(\bullet)^\star & E_F \ar@{.>}[r]_-{t_F}& F(\bullet)^\star}\]
+
+Let $\mathcal{G}_F$ be the resulting hypergraph.
+Now, every $\eta\colon F\rightarrow H$ in $\catname{Set}^{\catname{H}}$ has components $\eta_{k,l}\colon F(k,l)\to H(k,l)$, $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$.
+In particular we can define $\hat{\eta}\colon E_F\rightarrow E_H$ as $\sum_{k,l\in \mathbb{N}}\eta_{k,l}$.
+Now, on the one hand, we have
+\[\begin{split}
+	\pi^H_i\circ \eta^k_\bullet \circ  s^F_{k,l}&=\eta_\bullet \circ \pi^F_i \circ s^F_{k,l}\\&=\eta_\bullet \circ F(f_i)\\&=H(f_i)\circ \eta_{k,l}\\&=\pi^H_{k,i}\circ s^{H}_{k,l}\circ \eta_{k,l}
+\end{split} \qquad \begin{split}
+\pi^H_j\circ \eta^k_\bullet \circ  t^F_{k,l}&=\eta_\bullet \circ \pi^F_j \circ t^F_{k,l}\\&=\eta_\bullet \circ F(f_{k+j})\\&=H(f_{k+j})\circ \eta_{k,l}\\&=\pi^H_{l,j}\circ t^{H}_{k,l}\circ \eta_{k,l}
+\end{split} \]
+so that $\eta^k_\bullet \circ  s^F_{k,l}=s^{H}_{k,l}\circ \eta_{k,l}$ and $\eta^k_\bullet \circ  t^F_{k,l}= t^{H}_{k,l}\circ \eta_{k,l}$. On the other hand, these equalities give us the following:
+\[\begin{split}
+	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ s^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ s^{F}_{k,l} \\&=b^H_{k}\circ s^H_{k,l}\circ \eta_{k,l}\\&=s_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	s_H\circ \hat{\eta}\circ a^F_{k,l}
+\end{split} \qquad \begin{split}
+	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ t^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ t^{F}_{k,l} \\&=b^H_{k}\circ t^H_{k,l}\circ \eta_{k,l}\\&=t_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	t_H\circ \hat{\eta}\circ a^F_{k,l}
+\end{split}\]
+which, in turn, entail that  that the following squares commute
+\[\xymatrix{E_F \ar[r]^{s_F} \ar@{.>}[d]_{\hat{\eta}}& F(\bullet)^\star \ar[d]^{\eta^\star_\bullet} & E_F \ar[r]^{t_F} \ar[d]_{\hat{\eta}} & F(\bullet)^\star \ar[d]^{\eta^\star_\bullet}\\ E_H \ar[r]_{s_H} & H(\bullet)^\star & E_H \ar[r]_{t_H}& H(\bullet)^\star}\]
+
+This is the same as saying that $\eta$ induces a morphism $(\hat{\eta}, \eta_{\bullet})\colon \mathcal{G}_F\to \mathcal{G}_H$.
+It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \catname{\X}^{\catname{H}}\to \hyp_\X$.
+
+\begin{remark}\label{rem:utile}
+	By \Cref{rem:salv} we know that countably distributivity entails that, for every $k,l\in \mathbb{N}$, the arrow $b^F_k\times b^F_l$ is a coprojection, thus extensivity entails that the square is a pullback
+	\[\xymatrix@C=30pt{F(k,l) \ar[d]_{(s^F_{k,l}, t^F_{k,l})}  \ar[r]^{a^F_{k,l}}& E_F \ar[d]^{(s_F, t_F)} \\ F(\bullet)^k\times F(\bullet)^l \ar[r]_{b^F_k\times b^F_l} & F(\bullet)^\star\times F(\bullet)^\star}\]
+
+	\iffalse 
+	As in \Cref{rem:pb}, countably extensivity of $X$ guarantees that, for every $k\in \mathbb{N}$ following square is a pullback.	
+	\[\xymatrix{F(\bullet)^k  \ar[r]^{b^F_k} \ar[d]_{!_{F(\bullet)^k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ 1 \ar[r]_{o_k} & 1^\star}\]
+
+	Now, notice that 
+	\[\begin{split}
+		\lgh_{F(\bullet)}\circ b^{F}_k\circ s^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ s^F_{k,l}\\&=o_k\circ !_{F(k,l)}
+	\end{split} \qquad \begin{split}
+	\lgh_{F(\bullet)}\circ b^{F}_k\circ t^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ t^F_{k,l}\\&=o_k\circ !_{F(k,l)}
+	\end{split}\]
+so that we have two diagrams:
+	\[\xymatrix{F(k,l)\ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^1_{k,l}}  \ar@/_.5cm/[ddr]_{!_{F(k,l)}}&F(\bullet)^k \ar[dr]^{b^F_k}&& F(k,l) \ar@/_.5cm/[ddr]_{!_{F(k,l)}} \ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^2_{k,l}} &F(\bullet)^k \ar[dr]^{b^F_k}\\ & F(\bullet)_k  \ar[r]^{q_{k}} \ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} && F(\bullet)_k  \ar[r]^{q_{k} }\ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ &  1 \ar[r]_{o_k} & 1^\star && 1 \ar[r]_{o_k} & 1^\star}\]
+
+	Moreover we have
+	\[\begin{split}
+		s_F\circ a^F_{k,l}&=b^F_k\circ s^{F}_{k,l}\\&=
+		q_{k}\circ u^1_{k,l}	\end{split} \qquad \begin{split}
+		t_F\circ a^F_{k,l}&=b^F_k\circ t^{F}_{k,l}\\&=
+		q_{k}\circ u^2_{k,l}	\end{split}  \]
+
+	Therefore these two arrows, in turn, yield the dotted $v^1_{k,l}\colon F(k,l)\to F(\bullet)_k $ and $v^2_{k,l}\colon F(k,l)\to F(\bullet)_l$ as in the diagram below, where the right and bottom squares are pullbacks.
+	\[\xymatrix@C=45pt{F(k,l)  \ar[dr]^{a^F_{k,l}} \ar@{.>}[r]^{v^2_{k,l}} \ar@{.>}[d]^{v^1_{k,l}} \ar@/^.8cm/[rr]^{u^2_{k,l}} \ar@/_.5cm/[dd]_{u^1_{k,l}}& P_{l} \ar[r]_{p_{l,1}} \ar[d]_{p_{l,2}}& F(\bullet)_{l} \ar[d]^{q_{l}}\\ P_k \ar[r]^{p_{k,2}} \ar[d]^{p_{k,1}}& E_F \ar[r]_{s_F}  \ar[d]^{t_F}& F(\bullet)^\star \\ F(\bullet)_k  \ar[r]_{q_{k}}& F(\bullet)^\star}\]
+
+ By hypothesis, $\X$ is countably extensive, thus for every $k, l\in \mathbb{N}$, the following diagrams are pullbacks.
+ \[\xymatrix{F(k,l) \ar[r]^{a^F_{k,l}} & E_F \ar[d]^{}\\ 
+ F(\bullet)^k& F(\bullet)^\star}\]
+
+ Let now $d_1\colon Z\to P_l$ and $d_2\colon Z\to P_k $ be two arrows such that
+ \[p_{k,2}\circ d_2=p_{t,2}\circ d_1\]
+
+ Then we have
+ \begin{align*}
+ t_{F}\circ 	p_{t_2}\circ d_1&= \end{align*}
+
+ Showing, finally, that
+ \fi  
+\end{remark}
+
+\begin{proposition}
+	$\hyp_\X$ is equivalent to the category $\catname{\X}^{\catname{H}}$.
+\end{proposition}
+\begin{proof}	
+We already know that $\mathcal{G}_{-}$ is faithful, we still have to show that it is full and essentially surjective.
+	\begin{itemize}
+		\item For fullness, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of $\X$-hypergraphs.
+By \Cref{rem:utile}, for every $k,l\in \mathbb{N}$, the front square in diagram below is a pullback, yielding the dotted arrow $\eta_{k,l}\colon F(k,l)\to H(k,l)$.
+		\[\xymatrix@C=10pt{F(k,l)   \ar[dd]_{(s^F_{k,l}, t^F_{k,l})}\ar[rr]^-{a^F_{k,l}} \ar@{.>}[dr]_{\eta_{k,l }}&& E_F \ar[dd]|\hole^(.7){(s_F, t_F)}  \ar[dr]^{f}\\ & H(k,l) \ar[dd]_(.3){(s^H_{k,l}, t^H_{k,l})}\ar[rr]^(.4){a^H_{k,l}} &&  E_H \ar[dd]^{(s_H, t_H)}\\F(\bullet)^k\times F(\bullet)^l \ar[dr]_{g^k\times g^l} \ar[rr]|\hole^(.65){b^F_{k,l}\times b^F_{k,l}}& &F(\bullet)^\star \times F(\bullet)^\star  \ar[dr]^{g^\star\times g^\star}\\&H(\bullet)^k\times H(\bullet)^l \ar[rr]_{b^H_k\times b^H_l} && H(\bullet)^\star \times H(\bullet)^\star  }\]
+
+		As $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ we can simply take  $g$.
+Then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
+Indeed, given an arrow $f_i\colon(k,l)\to \bullet$ then we have :
+		\begin{align*}
+			\eta_\bullet \circ F(f_i)&=g\circ F(f_i)
+			\\&= \begin{cases}
+			g\circ \pi^F_i\circ s^F_{k,l} & i <k\\
+			g\circ \pi^F_i\circ t^F_{k,l} & \text{otherwise}
+			\end{cases}
+			\\&=
+			\begin{cases}
+		\pi^H_i\circ g^k\circ s^F_{k,l} & i <k\\
+		\pi^H_i\circ g^k\circ t^F_{k,l} 	& \text{otherwise}
+			\end{cases}\\&=
+		\begin{cases}
+	\pi^H_i\circ s^H_{k,l} \circ \eta_{k,l}& i <k\\
+	\pi^H_i\circ t^H_{k,l} \circ \eta_{k,l}	& \text{otherwise}
+	\end{cases}\\&=H(i)\circ \eta_{k,l}
+		\end{align*}
+		Finally, by construction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$.
+
+		\item  Let us turn to essential surjectivity.
+Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define $F_{\mathcal{G}}(\bullet):=V_{\mathcal{G}}$ and $F_{\mathcal{G}}(k,l)$ by the following pullback.
+Notice that, by \Cref{rem:salv} and countably extensivity, $(E_{\mathcal{{G}}}, \{a_{k,l}\}_{k,l\in \mathbb{N}})$ is a coproduct.
+		\[\xymatrix@C=30pt{F_\mathcal{G}(k,l) \ar[d]_{p_{k,l}}  \ar[r]^{a_{k,l}}& E_{\mathcal{G}} \ar[d]^{(s_F, t_F)} \\ V_{\mathcal{G}}^k\times V_{\mathcal{G}}^l \ar[r]_{b_k\times b_l} & V_{\mathcal{G}}^\star\times V_{\mathcal{G}}^\star}\]
+
+		Let $q_{i;k,l}\colon V_\mathcal{G}^k\times V_{\mathcal{G}}^l\to V_\mathcal{G} $ be the $i^{\text{th}}$ projection, then for every morphism $f_i\colon (k,l)\to \bullet$ in $\catname{H}$ we can define $F_{\mathcal{G}}(f_i)$ as $q_{i; k,l}\circ p_{k,l}$.
+$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$.
+
+		Notice that $p_{k,l}=(s^{F_{\mathcal{G}}}_{k,l}, t^{F_{\mathcal{G}}}_{k,l})$. To see this, it is enough to compose with the projections:
+		\begin{align*}
+			q_{i;k,l}\circ p_{k,l}&=F_{\mathcal{G}}(f_i)\\&=\begin{cases}
+				\pi^{F_{\mathcal{G}}}_{k, i} \circ F_{\mathcal{G}}(f_i) & i<k\\
+				\pi^{F_{\mathcal{G}}}_{l, i} \circ F_{\mathcal{G}}(f_i) &\text{otherwise}
+			\end{cases}\\&=\begin{cases}
+		s^{F_{\mathcal{G}}}_{k,l} & i<k\\
+		t^{F_{\mathcal{G}}}_{k,l} &\text{otherwise}
+			\end{cases}\\&=q_{i;k,l}\circ (s^{F_{\mathcal{G}}}_{k,l}, t^{F_{\mathcal{G}}}_{k,l})
+		\end{align*}
+		In particular, this entails that 
+		\[\begin{split}
+	s^{F_{\mathcal{G}}}\circ a^{F_{\mathcal{G}}}_{k,l}&=b^{F_{\mathcal{G}}}_k \circ s^{F_{\mathcal{G}}}_{k,l}\\&= b_k \circ s^{F_{\mathcal{G}}}_{k,l}\\&=s_F\circ a_{k,l}
+		\end{split} \qquad \begin{split}
+	t^{F_{\mathcal{G}}}\circ a^{F_{\mathcal{G}}}_{k,l}&=b^{F_{\mathcal{G}}}_l \circ t^{F_{\mathcal{G}}}_{k,l}\\&= b_l \circ s^{F_{\mathcal{G}}}_{k,l}\\&=t_F\circ a_{k,l}
+		\end{split}\]
+
+		Now, we know that there is an isomorphism $\phi \colon E_{\mathcal{G}} \to \sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)$ making the diagram below commutative.
+	\[\xymatrix{& F_{\mathcal{G}}(k,l) \ar[dr]^{a^{F_\mathcal{{G}}}_{k,l}} \ar[dl]_{a_{k,l}} \\E_{\mathcal{G}} \ar[rr]_-{\phi} & & \Sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)}\]
+
+	Therefore we have
+	\[\begin{split}
+	s_{F_{\mathcal{G}}} \circ \phi \circ a_{k,l}&=	s_{F_{\mathcal{G}}}  \circ a^{F_{\mathcal{G}}}_{k,l}	\\&= s_F\circ a_{k,l} \end{split} \qquad \begin{split}
+	t_{F_{\mathcal{G}}} \circ \phi \circ a_{k,l}&=	t_{F_{\mathcal{G}}}  \circ a^{F_{\mathcal{G}}}_{k,l}	\\&= t_F\circ a_{k,l} \end{split}\]
+
+	This allows us to conclude that $(\phi, \id{V_{\mathcal{G}}})$ is an isomorphism in $\hyp_\X$, from which the thesis now follows. \qed
+	\end{itemize}
+\end{proof}
+
+\subsection{Labelling hypergraph with an algebraic signature}
+
+\begin{definition}
+An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by an object $O_\Sigma$ and an arrow $\ari_\Sigma\colon O_\Sigma \to 1^\star$.
+
+We define the \emph{$\X$-hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} as $(0_\Sigma, 1, \ari_\Sigma, o_1\circ !_{O_\Sigma})$.
+,The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
+\end{definition}
+
+\begin{example}\label{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature in $\Set$.
+This simply amount to a set of \emph{operations} with an associated natural number, called \emph{arity}.
+	For instance let $\Sigma_G$ be the signature of groups, then $\mathcal{G}^{\Sigma_G}$ can be depicted as:
 	\begin{center}
@@
 
-\subsubsection{$\hyp_\X$ as a category of functors}
-
-Following \cite{bonchi2022string}, we can present $\hyp_\X$ as a category of functor over a suitable category.
-
-\begin{definition}Let $\catname{H}$ be the category in which:
-	\begin{itemize}
-		\item the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$
-		\item arrows are given by the identities $\id{k,l}$ and $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$;
-		\item composition is defined simply putting, for every $f_i\colon (k,l)\rightarrow \bullet$:
-		\begin{equation*}
-			f_i=f_i\circ \id{k,l} \qquad f_i = \id{\bullet}\circ f_i 
-		\end{equation*}
-	\end{itemize}
-\end{definition}
-
-Given $F\colon \catname{H}\to \catname{Set}$, since $\X$ has countable coproducts we can define
-\[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
-
-Now, for every $k$, $l$, $i$ and $j$ in $\mathbb{N}$ with $i< k$ and $j< l$ we can define $s^F_{k,l}\colon F(k,l)\to F(\bullet)^k$,  $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ as the unique ones fitting in the diagrams below, where the vertical arrows are the projections.
-\[\xymatrix{F(k,l)  \ar@{.>}[r]^{s^F_{k,l}} \ar[dr]_{F(f_i)}& F(\bullet)^{k} \ar[d]^{\pi^F_{i}} & F(k,l) \ar@{.>}[r]^{t^F_{k,l}} \ar[dr]_{F(f_{k+j})} & F(\bullet)^{l} \ar[d]^{\pi^F_{j}} \\ & F(\bullet) && F(\bullet)}\]
-
-In turn, these arrows allow us to consider
-$s_F, t_F\colon E_F\rightrightarrows F(\bullet)^{\star}$ as the unique arrows fitting in the diagrams below, where the vertical arrows are coprojections.
-\[\xymatrix{F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{s^{F}_{k,l}}& F(\bullet)^{k} \ar[d]^{b^F_{k}} & F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{t^{F}_{k,l}}& F(\bullet)^{l} \ar[d]^{b^F_{l}}\\ E_F \ar@{.>}[r]_-{s_F}& F(\bullet)^\star & E_F \ar@{.>}[r]_-{t_F}& F(\bullet)^\star}\]
-
-Let $\mathcal{G}_F$ be the resulting hypergraph.
-Now, every $\eta\colon F\rightarrow H$ in $\catname{Set}^{\catname{H}}$ has components $\eta_{k,l}\colon F(k,l)\to H(k,l)$, $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$.
-In particular we can define $\hat{\eta}\colon E_F\rightarrow E_H$ as $\sum_{k,l\in \mathbb{N}}\eta_{k,l}$.
-Now, on the one hand, we have
-\[\begin{split}
-	\pi^H_i\circ \eta^k_\bullet \circ  s^F_{k,l}&=\eta_\bullet \circ \pi^F_i \circ s^F_{k,l}\\&=\eta_\bullet \circ F(f_i)\\&=H(f_i)\circ \eta_{k,l}\\&=\pi^H_i\circ s^{H}_{k,l}\circ \eta_{k,l}
-\end{split} \qquad \begin{split}
-\pi^H_j\circ \eta^k_\bullet \circ  t^F_{k,l}&=\eta_\bullet \circ \pi^F_j \circ t^F_{k,l}\\&=\eta_\bullet \circ F(f_{k+j})\\&=H(f_{k+j})\circ \eta_{k,l}\\&=\pi^H_j\circ t^{H}_{k,l}\circ \eta_{k,l}
-\end{split} \]
-so that $\eta^k_\bullet \circ  s^F_{k,l}=s^{H}_{k,l}\circ \eta_{k,l}$ and $\eta^k_\bullet \circ  t^F_{k,l}= t^{H}_{k,l}\circ \eta_{k,l}$. On the other hand, these equalities give us the following:
-\[\begin{split}
-	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ s^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ s^{F}_{k,l} \\&=b^H_{k}\circ s^H_{k,l}\circ \eta_{k,l}\\&=s_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	s_H\circ \hat{\eta}\circ a^F_{k,l}
-\end{split} \qquad \begin{split}
-	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ t^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ t^{F}_{k,l} \\&=b^H_{k}\circ t^H_{k,l}\circ \eta_{k,l}\\&=t_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	t_H\circ \hat{\eta}\circ a^F_{k,l}
-\end{split}\]
-which, in turn, entail that  that the following squares commute
-\[\xymatrix{E_F \ar[r]^{s_F} \ar@{.>}[d]_{\hat{\eta}}& F(\bullet)^\star \ar[d]^{\eta^\star_\bullet} & E_F \ar[r]^{t_F} \ar[d]_{\hat{\eta}} & F(\bullet)^\star \ar[d]^{\eta^\star_\bullet}\\ E_H \ar[r]_{s_H} & H(\bullet)^\star & E_H \ar[r]_{t_H}& H(\bullet)^\star}\]
-
-This is the same as saying that $\eta$ induces a morphism $(\hat{\eta}, \eta_{\bullet})\colon \mathcal{G}_F\to \mathcal{G}_H$.
-It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \catname{\X}^{\catname{H}}\to \hyp_\X$.
-
-\begin{remark}\label{rem:utile}
-	By \Cref{rem:salv} we know that countably distributivity entails that, for every $k,l\in \mathbb{N}$, the arrow $b^F_k\times b^F_l$ is a coprojection, thus extensivity entails that the square is a pullback
-	\[\xymatrix@C=30pt{F(k,l) \ar[d]_{(s^F_{k,l}, t^F_{k,l})}  \ar[r]^{a^F_{k,l}}& E_F \ar[d]^{(s_F, t_F)} \\ F(\bullet)^k\times F(\bullet)^l \ar[r]_{b^F_k\times b^F_l} & F(\bullet)^\star\times F(\bullet)^\star}\]
-
-	\iffalse 
-	As in \Cref{rem:pb}, countably extensivity of $X$ guarantees that, for every $k\in \mathbb{N}$ following square is a pullback.	
-	\[\xymatrix{F(\bullet)^k  \ar[r]^{b^F_k} \ar[d]_{!_{F(\bullet)^k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ 1 \ar[r]_{o_k} & 1^\star}\]
-
-	Now, notice that 
-	\[\begin{split}
-		\lgh_{F(\bullet)}\circ b^{F}_k\circ s^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ s^F_{k,l}\\&=o_k\circ !_{F(k,l)}
-	\end{split} \qquad \begin{split}
-	\lgh_{F(\bullet)}\circ b^{F}_k\circ t^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ t^F_{k,l}\\&=o_k\circ !_{F(k,l)}
-	\end{split}\]
-so that we have two diagrams:
-	\[\xymatrix{F(k,l)\ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^1_{k,l}}  \ar@/_.5cm/[ddr]_{!_{F(k,l)}}&F(\bullet)^k \ar[dr]^{b^F_k}&& F(k,l) \ar@/_.5cm/[ddr]_{!_{F(k,l)}} \ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^2_{k,l}} &F(\bullet)^k \ar[dr]^{b^F_k}\\ & F(\bullet)_k  \ar[r]^{q_{k}} \ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} && F(\bullet)_k  \ar[r]^{q_{k} }\ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ &  1 \ar[r]_{o_k} & 1^\star && 1 \ar[r]_{o_k} & 1^\star}\]
-
-	Moreover we have
-	\[\begin{split}
-		s_F\circ a^F_{k,l}&=b^F_k\circ s^{F}_{k,l}\\&=
-		q_{k}\circ u^1_{k,l}	\end{split} \qquad \begin{split}
-		t_F\circ a^F_{k,l}&=b^F_k\circ t^{F}_{k,l}\\&=
-		q_{k}\circ u^2_{k,l}	\end{split}  \]
-
-	Therefore these two arrows, in turn, yield the dotted $v^1_{k,l}\colon F(k,l)\to F(\bullet)_k $ and $v^2_{k,l}\colon F(k,l)\to F(\bullet)_l$ as in the diagram below, where the right and bottom squares are pullbacks.
-	\[\xymatrix@C=45pt{F(k,l)  \ar[dr]^{a^F_{k,l}} \ar@{.>}[r]^{v^2_{k,l}} \ar@{.>}[d]^{v^1_{k,l}} \ar@/^.8cm/[rr]^{u^2_{k,l}} \ar@/_.5cm/[dd]_{u^1_{k,l}}& P_{l} \ar[r]_{p_{l,1}} \ar[d]_{p_{l,2}}& F(\bullet)_{l} \ar[d]^{q_{l}}\\ P_k \ar[r]^{p_{k,2}} \ar[d]^{p_{k,1}}& E_F \ar[r]_{s_F}  \ar[d]^{t_F}& F(\bullet)^\star \\ F(\bullet)_k  \ar[r]_{q_{k}}& F(\bullet)^\star}\]
-
- By hypothesis, $\X$ is countably extensive, thus for every $k, l\in \mathbb{N}$, the following diagrams are pullbacks.
- \[\xymatrix{F(k,l) \ar[r]^{a^F_{k,l}} & E_F \ar[d]^{}\\ 
- F(\bullet)^k& F(\bullet)^\star}\]
-
- Let now $d_1\colon Z\to P_l$ and $d_2\colon Z\to P_k $ be two arrows such that
- \[p_{k,2}\circ d_2=p_{t,2}\circ d_1\]
-
- Then we have
- \begin{align*}
- t_{F}\circ 	p_{t_2}\circ d_1&= \end{align*}
-
- Showing, finally, that
- \fi  
+Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature, we are going to use the hypergraph $\mathcal{G}^{\Sigma}$ of \Cref{exa_3} in order to label hyperedges with operations.
+ì
+\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterization of monomorphisms in it.
+\begin{proposition}\label{prop:mono} Let $\X$ be a (strict) $\mathcal{N}$-adhesive category, then the following hold true:
+	\begin{enumerate}
+		\item a morphism $(h,k)$ between two object of $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions;
+		\item every algebraic signature $\Sigma$, $\hyps$ is an (strict) $\mathcal{M}$-adhesive category, where a morphism $(h,k)$ in $\hyps$ belongs to $\mathcal{M}$ if and only if both $h$ and $k$ are in $\mathcal{N}$.
+	\end{enumerate}
+\end{proposition}
+
+\begin{remark}\label{rem:label}	
+	Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a morphism $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares below commute.
+	\[\xymatrix{E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{s_{\mathcal{H}}}& O_\Sigma \ar[d]^{\ari_\Sigma}& E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{t_{\mathcal{H}}} & O_\Sigma \ar[d]^{o_1\circ !_{O_\Sigma}}\\ V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}}& 1^\star & V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}} & 1^\star}\]
+
+	Let $v_n\colon V^n_\mathcal{H}\colon  V^\star_{\mathcal{H}}$ be a coprojection.
+The second diagram above entails that $t_{\mathcal{H}}$ factors through $v_1\colon V_{\mathcal{H}}\to V^{\star}$.
+Indeed, in the diagram below, the inner square is a pullback by extensivity and its outer boundaries yields the second square above, so that we get the dotted $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
+	\[\xymatrix{E_{\mathcal{H}} \ar@{.>}[dr]^{\tau}\ar@/^.4cm/[drr]^{t_{\mathcal{H}}} \ar[d]_{h} \\	O_\Sigma \ar@/_.2cm/[dr]_{!_{O_\Sigma}}&V_{\mathcal{H}} \ar[r]^{v_1}\ar[d]^{!_{V_\mathcal{H}}}& V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}}\\ & 1 \ar[r]_{o_1}& 1^\star}\]
 \end{remark}
 
-\begin{proposition}
-	$\hyp_\X$ is equivalent to the category $\catname{\X}^{\catname{H}}$.
-\end{proposition}
-\begin{proof}	
-We already know that $\mathcal{G}_{-}$ is faithful, we still have to show that it is full and essentially surjective.
-	\begin{itemize}
-		\item For fullness, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of $\X$-hypergraphs.
-By \Cref{rem:utile}, for every $k,l\in \mathbb{N}$, the front square in diagram below is a pullback, yielding the dotted arrow $\eta_{k,l}\colon F(k,l)\to H(k,l)$.
-		\[\xymatrix@C=10pt{F(k,l)   \ar[dd]_{(s^F_{k,l}, t^F_{k,l})}\ar[rr]^-{a^F_{k,l}} \ar@{.>}[dr]_{\eta_{k,l }}&& E_F \ar[dd]|\hole^(.7){(s_F, t_F)}  \ar[dr]^{f}\\ & H(k,l) \ar[dd]_(.3){(s^H_{k,l}, t^H_{k,l})}\ar[rr]^(.4){a^H_{k,l}} &&  E_H \ar[dd]^{(s_H, t_H)}\\F(\bullet)^k\times F(\bullet)^l \ar[dr]_{g^k\times g^l} \ar[rr]|\hole^(.65){b^F_{k,l}\times b^F_{k,l}}& &F(\bullet)^\star \times F(\bullet)^\star  \ar[dr]^{g^\star\times g^\star}\\&H(\bullet)^k\times H(\bullet)^l \ar[rr]_{b^H_k\times b^H_l} && H(\bullet)^\star \times H(\bullet)^\star  }\]
-
-		As $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ we can simply take  $g$.
-Then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
-Indeed, given an arrow $f_i\colon(k,l)\to \bullet$ then we have :
-		\begin{align*}
-			\eta_\bullet \circ F(f_i)&=g\circ F(f_i)
-			\\&= \begin{cases}
-			g\circ \pi^F_i\circ s^F_{k,l} & i <k\\
-			g\circ \pi^F_i\circ t^F_{k,l} & \text{otherwise}
-			\end{cases}
-			\\&=
-			\begin{cases}
-		\pi^H_i\circ g^k\circ s^F_{k,l} & i <k\\
-		\pi^H_i\circ g^k\circ t^F_{k,l} 	& \text{otherwise}
-			\end{cases}\\&=
-		\begin{cases}
-	\pi^H_i\circ s^H_{k,l} \circ \eta_{k,l}& i <k\\
-	\pi^H_i\circ t^H_{k,l} \circ \eta_{k,l}	& \text{otherwise}
-	\end{cases}\\&=H(i)\circ \eta_{k,l}
-		\end{align*}
-		Finally, by construction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$.
-
-		\item  Let us turn to essential surjectivity.
-Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define $F_{\mathcal{G}}(\bullet):=V_{\mathcal{G}}$ and $F_{\mathcal{G}}(k,l)$ by the following pullback.
-Notice that, by \Cref{rem:salv} and countably extensivity, $(E_{\mathcal{{G}}}, \{a_{k,l}\}_{k,l\in \mathbb{N}})$ is a coproduct.
-		\[\xymatrix@C=30pt{F_\mathcal{G}(k,l) \ar[d]_{p_{k,l}}  \ar[r]^{a_{k,l}}& E_{\mathcal{G}} \ar[d]^{(s_F, t_F)} \\ V_{\mathcal{G}}^k\times V_{\mathcal{G}}^l \ar[r]_{b_k\times b_l} & V_{\mathcal{G}}^\star\times V_{\mathcal{G}}^\star}\]
-
-		Let $q_{i;k,l}\colon V_\mathcal{G}^k\times V_{\mathcal{G}}^l\to V_\mathcal{G} $ be the $i^{\text{th}}$ projection, then for every morphism $f_i\colon (k,l)\to \bullet$ in $\catname{H}$ we can define $F_{\mathcal{G}}(f_i)$ as $q_{i; k,l}\circ p_{k,l}$.
-$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$.
-
-		Now, we know that there is an isomorphism $\phi \colon E_{\mathcal{G}} to \sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)$ making the diagram below commutative.
-		\[\xymatrix{\\& F_{\mathcal{G}}(k,l) \\E_{\mathcal{G}} & & \sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)}\]
-
-		 moreover, by construction we have
-		\[\begin{split}
-		s_{F_{\mathcal{G}}}\circ a^{F_{\mathcal{G}}}_{k,l}&=b^{F_{\mathcal{G}}}\circ s^{F_{\mathcal{G}}}_{k,l}
-		\end{split}\]
-
-		$s_{F_{\mathcal{G}}}=s_{\mathcal{G}}$ and $t_{F_{\mathcal{G}}}=t_{\mathcal{G}}$, from which the thesis follows. 
-	\end{itemize}
-\end{proof}
-
-\subsection{Labelling hypergraph with an algebraic signature}\index{signature!algebraic -}
-Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature, we are going to use the hypergraph $\mathcal{G}^{\Sigma}$ of \Cref{exa_3} in order to label hyperedges with operations.
-\begin{definition}Let $\Sigma=(O, \ari)$ be an algebraic signature, the category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.\index{hypergraph!algebraically labelled -}
-\end{definition}
-\Cref{cor:mono} and \Cref{cor:slice} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterization of monomorphisms in it.
-\begin{proposition}\label{prop:mono}
-	For every algebraic signature $\Sigma$, $\hyps$ is an adhesive category.
-Moreover a morphism $(h,k)$ between two object of $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions.
-\end{proposition}
-
-\begin{remark}\label{rem:label}	
-	Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, since  $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the singleton an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  such that, for every $e\in E_{\mathcal{H}}$
-	\[\ari_\Sigma(h(e))=s_\mathcal{H}(e)\]
-
-	On the other hand, if $\mathcal{H}$ has an hyperedge $e$ such that $t_{\mathcal{H}}(e)$ has a length different from $1$, then there is no morphism $\mathcal{H}\to \mathcal{G}^{\Sigma}$.
-Indeed, if such a morphism $(h,!_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^\Sigma$ exists, then, for every $e\in E_{\mathcal{H}}$ we have
-	\begin{align*}
-		f^{\star}(t_{\mathcal{H}}(h))&=t_{\mathcal{G}^{\Sigma}}(f(h))\\&=\delta_\heartsuit
-	\end{align*}
-	and so $\dom(t_{\mathcal{H}}(h))=1$.  
-\end{remark}
-
-$\hyp_{\Sigma}$, as any slice category, has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \catname{Set}$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\hyp}(\mathcal{H}$).
-Now, $U_{\hyp}(\mathcal{G}^{\Sigma})=\{v\}$ thus, for every set $X$, there is only one arrow $X\to U_{\hyp}(\mathcal{G}^{\Sigma})$.
-Define $\Delta_{\Sigma}(X)\colon \Delta_{\hyp}(X)\to \mathcal{G}^{\Sigma}$ to be the transpose of this arrow.
+$\hyp_{\Sigma}$, has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \X$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\X}(\mathcal{H}$).
+Now, $U_{\X}(\mathcal{G}^{\Sigma})=1$ thus, for every object $X$, there is only one arrow $X\to U_{\X}(\mathcal{G}^{\Sigma})$.
+Define $\Delta_{\Sigma}(X)\colon \Delta_{\X}(X)\to \mathcal{G}^{\Sigma}$ as the transpose of this arrow.
+Explicitly, $\Delta_{\X}(X)=(0, X, ?_{X^\star}, ?_{X^\star})$ and $\Delta_\Sigma(X)$ is simply $(?_{O_\Sigma}, !_{X})$.
 
@@
 \begin{proof}Let $(h, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be an object of $\hyp_{\Sigma}$, and suppose that there exists $f\colon X\to U_{\Sigma}(\mathcal{H})$.
-Since $U_{\Sigma}(\mathcal{H})=U_{\hyp}(\mathcal{H})$ and $\id{\catname{Set}}$ is the unit of $\Delta_\hyp \dashv U_{\hyp}$, there exists a unique morphism $(k,f)\colon \Delta_{\hyp}(X)\to \mathcal{H}$ of $\hyp$.
-Since the set of hyperedges of $\Delta_{\hyp}(X)$ is empty, $k$ must be $?_{E_\mathcal{H}}$ and the commutativity of each of the two triangles below is equivalent to that of the other
-	\[\xymatrix{\Delta_\hyp(X) \ar[rr]^{(?_{E_\mathcal{H}}, f)} \ar[dr]_{\Delta_\Sigma(X)} && \mathcal{H} \ar[dl]^{(h, !_{V_\mathcal{H}})} & U_\hyp(\Delta_\hyp(X)) \ar[rr]^{f} \ar[dr]_{U_\hyp(\Delta_\Sigma(X))\hspace{10pt}} && U_\hyp(X) \ar[dl]^{!_{V_\mathcal{H}}}\\& \mathcal{G}^\Sigma &&&U_\hyp\hspace{-1.5pt}\left(\mathcal{G}^\Sigma\right)}\]
-	But the triangle on the right commutes because $U_{\hyp}(\mathcal{G}^{\Sigma})$ is terminal.
-\end{proof}
-
+Since, $U_{\Sigma}(\mathcal{H})=U_{\X}(\mathcal{H})$ and $\id{\X}$ is the unit of $\Delta_\X \dashv U_{\X}$, we get a morphism $(?_{E_{\mathcal{H}}},f)\colon \Delta_{\X}(X)\to \mathcal{H}$ of $\hyp_\X$.
+But then we have
+	\begin{align*}
+		(h, !_{V_{\mathcal{{H}}}})\circ (?_{E_{\mathcal{H}}}, f)&=(h\circ ?_{E_{\mathcal{H}}}, !_{V_{\mathcal{{H}}}}\circ f)\\&=(?_{0_{\Sigma}}, !_{X})\\&=\Delta_{\X}(X)
+	\end{align*}
+and the thesis follow.
+\end{proof}
+
+\todo{anche questo forse val la pena toglierlo}
 We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
@@
 \subsection{Term Graphs}
-
-\section{Hypergraphs  and term graphs with equivalences}
+\todo{a very nice introduction}
+
+Let us start using labelled hypergraphs to define term graphs.
+
+\begin{definition}\label{def:tg}\index{term graph}
+	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is mono.
+We define $\tg$ to be the full subcategory of $\hyp_{\Sigma}$ and denote by $I_\Sigma$ the inclusion.
+Restricting $U_\Sigma\colon \hyp_{\Sigma}\to \catname{Set}$ we get a forgetful functor $U_{\tg}\colon \tg\to \catname{Set}$.
+\end{definition}
+
+\begin{remark}\label{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
+Notice, moreover that since $t_{\mathcal{G}}$is mono then $\tau_{\mathcal{G}}$ is mono too.
+\end{remark}
+
+We are now going back to examine the properties of $\tg$, with the purpose of studying its adhesivity properties.
+
+\begin{proposition}\label{term:left}The forgetful functor $U_{\tg}$ has a left adjoint $\Delta_{\tg}$.
+\end{proposition}
+\begin{proof}
+	This follows noticing that, for every object $X$, $\Delta_{\Sigma}(X)$ is a term graph.
+\end{proof}
+
+Take now a mono $(i,j)\colon \mathcal{H}\to \mathcal{G}$ between  $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\hyp_\Sigma$.
+In particular we have a commutative square
+
+\[\xymatrix{E_{\mathcal{G}} \ar[r]^{t_{\mathcal{G}}} \ar[d]_{i}& V^\star_{\mathcal{G}} \ar[d]^{j} \\ E_{\mathcal{H}} \ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}}}\]
+
+By  \Cref{prop:mono} $i$ and $j$ are monos, thus if $t_{\mathcal{H}}$ is mono then $t_{\mathcal{G}}$  is mono too.
+This show that if $(l', !_{V_\mathcal{H}})$ is a term graph then $(l, !_{V_\mathcal{G}})$ belongs to $\tg$ too.
+Since $\X$ is assumed to have finite limits, applying this argument when $(i,j)$ is the equalizer in $\hyp_\Sigma$ of two parallel arrows between term graphs we get the following.
+
+\begin{proposition}\label{prop:equ}$\tg$ has equalizers and $I_{\Sigma}$ creates them.
+\end{proposition}
+
+We have a similar result also for binary products.
+
+\begin{proposition} $\tg$ has binary products and $I_\Sigma$ creates them.
+\end{proposition}
+\begin{proof}
+	Let $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be two term graphs, their product in $\hyp_{\Sigma}$ is given by $(p, !_{V_\mathcal{P}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$, where the square below  is a pullback in $\hyp$ and $(p, !_{V_\mathcal{P}})$ is the diagonal filling it.
+	\[\xymatrix@C=35pt{\mathcal{P} \ar[r]^{(p_E, p_V)} \ar[d]_{(q_E, e_V)} & \mathcal{G} \ar[d]^{(l, !_{V_\mathcal{G}})}\\ \mathcal{H} \ar[r]_{(l', !_{V_{\mathcal{H}}})}& \mathcal{G}^\Sigma}\]
+	By \Cref{prop:com} we have two pullback square in $\X$:
+	\[\xymatrix{E_\mathcal{P} \ar[r]^{p_E} \ar[d]_{q_E} & E_\mathcal{G} \ar[d]^{l} &V_{\mathcal{P}} \ar[r]^{p_V} \ar[d]_{q_V}&V_{\mathcal{G}}\ar[d]^{!_{V_\mathcal{G}}} \\ E_\mathcal{H} \ar[r]_{l'}& O_\Sigma & V_\mathcal{H}\ar[r]_{!_{V_\mathcal{H}}} & 1}\]
+	Moreover $t_{\mathcal{P}}$ fits in the following diagram.
+	\[\xymatrix{V^\star_{\mathcal{P}} \ar[rrr]^{p^\star_V} \ar[ddd]_{q^\star_V}& & &V_{\mathcal{G}}^\star \ar[ddd]^{!^\star_{V_\mathcal{G}}}\\&E_\mathcal{P} \ar[ul]^{t_{\mathcal{P}}}\ar[r]^{p_E} \ar[d]_{q_E} & E_\mathcal{G} \ar[ur]_{t_{\mathcal{G}}} \ar[d]^{l}  \\ &E_\mathcal{H} \ar[dl]_{t_{\mathcal{H}}} \ar[r]_{l'}& O_\Sigma \ar[dr]_{o_1\circ !_{O_\Sigma}} \\V^\star_{\mathcal{H}} \ar[rrr]_{!^\star_{V_\mathcal{H}}}& & &1^\star}\]
+	If we show that $\mathcal{P}$ is a term graph we are done. Take two arrows $h_1, h_{2}\colon Z\rightrightarrows  E_{\mathcal{P}}$ such that 
+	\[t_{\mathcal{P}}\circ h_1= t_{\mathcal{P}}\circ h_2 \]
+
+	We have the following chains of equalities 
+	\[\begin{split}
+		t_{\mathcal{G}}\circ p_E \circ h_1&=p^\star_V\circ t_{\mathcal{P}} \circ h_1 \\&=p^\star_V\circ t_{\mathcal{P}}\circ h_2\\&=t_{\mathcal{G}}\circ p_E\circ h_2
+	\end{split} \qquad \begin{split}
+		t_{\mathcal{H}}\circ q_E\circ h_1&=q^\star_V\circ t_{\mathcal{P}} \circ h_1\\&=q^\star_V\circ t_{\mathcal{P}}\circ h_2\\&=t_{\mathcal{H}} \circ q_E\circ h_2
+	\end{split}\]
+	Since $t_{\mathcal{G}}$ and $t_{\mathcal{H}}$ are monomorphisms we get
+	\[p_E \circ h_1=p_E\circ h_2 \qquad q_E\circ h_1=q_E \circ h_2\]
+	which, in turn, imply  $h_1=h_2$.	
+\end{proof}
+Since pullbacks can be computed from products and equalizers we also get the following.
+
+\begin{corollary}\label{cor:pb}$\tg$ has pullbacks and they are created by $I_\Sigma$.
+\end{corollary}
+\begin{remark}
+	$\tg$ in general does not have terminal objects.
+Consider an algebraic signature in $\Set$.
+Since $U_{\tg}$ preserves limits, if a terminal object exists it must have the singleton as set of nodes, therefore the set of hyperedges must be empty or a singleton $\{h\}$.
+Now take as signature the one given by two operations $a$ and $b$, both of arity $0$; we have three term graphs with only one node $v$: $\Delta_{\tg{\Sigma}}(\{v\})$, $(l_a, !_{V_{\mathcal{G}}})\colon \mathcal{G}_a\to \mathcal{G}^{\Sigma}$ and $(l_b, !_{V_{\mathcal{G}}})\colon \mathcal{G}_b\to \mathcal{G}^{\Sigma}$.
+	\begin{center}\begin{tikzpicture}
+
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=left:{$v$}] (V) at (5,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=left:{$v$}] (U) at (3,0) {};
+			\node at(5,1.25){$a$};	
+			\node at(5,1.7){$h$};
+
+			\draw[->-=.5](5,1)--(V)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$1$};
+
+			\draw[rounded corners] (4.75, 1) rectangle (5.25, 1.5) {};
+
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=left:{$v$}] (V) at (7,0) {};
+
+			\node at(7,1.25){$b$};	
+			\node at(7,1.7){$h$};
+
+			\draw[->-=.5](7,1)--(V)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$1$};
+
+			\draw[rounded corners] (6.75, 1) rectangle (7.25, 1.5) {};
+
+		\end{tikzpicture}
+	\end{center}
+	There are no morphisms in $\tg$ between the last two and from the last two to the first one, therefore none of them can be terminal.
+\end{remark}
+
+\begin{remark}
+	$\tg$, even when $\Sigma$ is an algebraic signature in $\Set$ is not an adhesive category.
+In particular it does not have pushouts along all monomorphisms.
+For instance, if we take the three term graphs of the previous remark, then have two arrows
+	$(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_a, !_{V_{\mathcal{G}_a}})$ and $(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_b, !_{V_{\mathcal{G}_a}})$ which cannot be completed to a square.
+Indeed if $(q, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^\Sigma$ is another term graph with $(g_E, g_V)\colon (l_a, !_{V_{\mathcal{G}}})\to (q, !_{V_\mathcal{H}})$ and $(k_E, k_V)\colon (l_a, !_{V_{\mathcal{G}}})\to (q, !_{V_\mathcal{H}})$  such that
+	\[(g_E, g_V)\circ (?_{\{h\}}, \id{\{v\}}) = (k_E, k_V)\circ (?_{\{h\}}, \id{\{v\}})\]
+	then $g_V=k_V$ and
+	\begin{align*}t_{\mathcal{H}}(g_E(h))&=g^\star_V(t_{\mathcal{G}}(h))\\&=g_V^\star(\delta_v)\\&=k^\star_V(\delta_V)\\&=k^\star_V(t_{\mathcal{G}}(h))\\&=t_{\mathcal{H}}(k_E(h))
+	\end{align*}
+	so that we also have $g_E=k_E$, but then
+	\begin{align*}
+		a&=l_a(h)\\&=q(g_E(h))\\&=q(k_E(h))\\&=l_b(h)\\&=b
+	\end{align*}
+\end{remark}
+
+\begin{definition}
+	Let $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l, !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be two term graph and $(f,g)$ a morphism $\mathcal{G}\to \mathcal{H}$.
+As in \Cref{rem:label}, let also $t_{\mathcal{G}}$ and $t_{\mathcal{H}}$ be $o_{1}\circ \tau_\mathcal{G}$ and $o_1\circ \tau_{\mathcal{H}}$.
+Consider the diagram below, in which the right square is a pullback, we say that $(f,g)$ \emph{preserves inputs} if the dotted arrow  $t_g\colon I_{\mathcal{{H}}, f}\to E_{\mathcal{{G}}}$ exists.
+	\[\xymatrix{E_{\mathcal{G}} \ar[dr]_{\tau_{\mathcal{G}}}&I_{\mathcal{H}, g} \ar@{.>}[l]_{t_g} \ar[r]^{w^{\mathcal{G}}_1} \ar[d]_{w^{\mathcal{G}}_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{H}}}\\ & V_{\mathcal{G}} \ar[r]_{g}  & V_{\mathcal{{H}}}}\]
+
+\end{definition}
+
+\begin{remark}\label{prop:image}
+	Notice that we have
+	\begin{align*}
+		t_{\mathcal{H}}\circ w^{\mathcal{G}}_1&=o_{\mathcal{H},1}\circ \tau_{\mathcal{H}}\circ w^{\mathcal{G}}_1\\&=o_{\mathcal{H},1}\circ g\circ w^{\mathcal{G}}_2\\&=g^\star\circ o_{\mathcal{G},1}\circ w^{\mathcal{G}}_2\\&=g^\star \circ o_{\mathcal{G},1}\circ \tau_{\mathcal{G}}\circ t_g\\&=g^\star \circ t_{\mathcal{G}}\circ t_g\\&=t_{\mathcal{H}}\circ f\circ t_g
+	\end{align*}
+	and thus, since $t_{\mathcal{H}}$ is mono, we get $w^{\mathcal{G}}_1=f\circ t_g$.
+\end{remark}
+We are now ready to show that regular monos are preserves inputs.
+
+\begin{lemma}\label{lem:reg} If a mono $(i,j)$ between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ then it preserves inputs.
+\end{lemma}
+
+\begin{proof}
+	Let $(i,j)$ be the equalizer of $(f_1, g_1)$ and $(f_2, g_2)$ are arrows from $(l', !_{V_\mathcal{H}})$ to $(k, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^\Sigma$.
+Suppose that the domain of $(i,j)$ is  $(e, !_{V_{\mathcal{E}}})\colon \mathcal{E}\to \mathcal{{G}}^\Sigma$.
+	By \Cref{prop:equ} such morphism is a regular mon also in $\hyp_\Sigma$.
+Since we have assumed that $(-)^\star$ preserves equalizer, by \Cref{lim} the  horizontal rows in the diagrams below are equalizers in $\X$.
+
+	\[\xymatrix{I_{\mathcal{H}, j} \ar@/^.4cm/[drr]^{w^{\mathcal{G}}_1}  \ar@/_.4cm/[ddr]_{w^{\mathcal{G}}_2} \ar@{.>}[dr]^{t_j}\\&E_{\mathcal{E}} \ar@{.>}[d]_{t_{\mathcal{E}}} \ar[r]^{i}& E_{\mathcal{H}} \ar[d]_{t_{\mathcal{H}}}  \ar@<.5ex>[r]^{f_1} \ar@<-.5ex>[r]_{f_2} & E_{\mathcal{K}}  \\ &V_{\mathcal{E}} \ar[r]_{j}& V_{\mathcal{H}}  \ar@<.5ex>[r]^{g_1} \ar@<-.5ex>[r]_{g_2}& V_{\mathcal{K}}}\]
+
+	Now, we have
+	\begin{align*}
+		\tau_{\mathcal{K}}\circ f_1\circ w^{\mathcal{G}}_1&=g_1\circ \tau_\mathcal{H}\circ w^{\mathcal{G}}_1\\&=g_1\circ j\circ w^{\mathcal{G}}_2\\&=g_2\circ j\circ w^{\mathcal{G}}_2\\&=g_2\circ \tau_{\mathcal{H}}\circ w^{\mathcal{G}}_1\\&=\tau_{\mathcal{K}}\circ f_2\circ w^{\mathcal{G}}_1
+	\end{align*}
+
+	By \Cref{rem:mono2}, $\tau_{\mathcal{K}}$ is a mono and so we can conclude.
+\end{proof}
+
+\begin{lemma}\label{prop:push}Let $\X$ be a strict $\mathcal{M}$-adhesive category and consider two term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$.
+Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ preserves inputs and both $f_1$ and $g_1$ are in $\mathcal{M}$,  then their pushout $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ is a term graph too.
+\end{lemma}
+
+\begin{proof} To fix the notations, let $(V^\star_{\mathcal{G}}, \{j_{\mathcal{{G}}, n} \}_{n\in \mathbb{N} })$, $(V^\star_{\mathcal{H}}, \{j_{\mathcal{{H}}, n} \}_{n\in \mathbb{N} })$, $(V^\star_{\mathcal{K}}, \{j_{\mathcal{{K}}, n} \}_{n\in \mathbb{N} })$, and $(V^\star_{\mathcal{P}}, \{j_{\mathcal{{P}}, n} \}_{n\in \mathbb{N} })$ be the coproducts defining $V^\star_{\mathcal{G}}$, $V^\star_{\mathcal{H}}$, $V^\star_{\mathcal{K}}$ and $V^\star_{\mathcal{P}}$.
+In $\hyps$ pushouts are computed componentwise, so that in the following diagrams the squares are all pushouts in $\X$.
+
+	\[\xymatrix{E_{\mathcal{G}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}} \ar@{>->}[d]^{k_E} & V_{\mathcal{G}}  \ar[r]^{g_2} \ar@{>->}[d]_{g_1}& V_{\mathcal{K}} \ar@{>->}[d]^{k_V}\\ E_{\mathcal{H}} \ar[r]_{h_E} & E_{\mathcal{P}} & V_{\mathcal{H}}  \ar[r]_{h_V}& V_{\mathcal{K}}}\]
+
+Moreover, we also know that $s_\mathcal{P}, t_{\mathcal{P}}\colon E_{\mathcal{P}}\to V_{\mathcal{P}}$  fit in the two squares below.
+
+	\[\xymatrix@C=20pt@R=20pt{V^\star_{\mathcal{G}} \ar[ddd]_{g^\star_1}\ar[rrr]^{g^\star_2} &&&V^\star_{\mathcal{K}} \ar[ddd]^{k^\star_V} & V^\star_{\mathcal{G}} \ar[ddd]_{g^\star_1} \ar[rrr]^{g^\star_2}&&& V^\star_{\mathcal{K}}\ar[ddd]^{k^\star_V} \\ & E_{\mathcal{G}} \ar[ul]^{s_{\mathcal{G}}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}} \ar[ur]_{s_{\mathcal{K}}} \ar@{>->}[d]^{k_E}&&& E_{\mathcal{G}} \ar[ul]^{t_{\mathcal{G}}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}}\ar[ur]_{t_{\mathcal{K}}}\ar@{>->}[d]^{k_E} \\ & E_{\mathcal{H}} \ar[dl]_{s_{\mathcal{H}}} \ar[r]_{h_E} & E_{\mathcal{P}} \ar[dr]^{s_{\mathcal{P}}}&&& E_{\mathcal{H}} \ar[dl]_{t_{\mathcal{H}}}\ar[r]_{h_E} & E_{\mathcal{P}} \ar[dr]^{t_{\mathcal{P}}} \\V^\star_{\mathcal{H}} \ar[rrr]_{h^\star_V} &&&V^\star_{\mathcal{P}} & V^\star_{\mathcal{H}}\ar[rrr]_{h^\star_V} &&& V^\star_{\mathcal{P}}}\]
+
+We have to show that $t_{\mathcal{P}}$ is mono, let thus $h_1, h_2\colon X\rightrightarrows E_{\mathcal{P}}$ be two arrows such that $t_\mathcal{P}\circ h_1=t_{\mathcal{P}}\circ h_2$.
+We can apply three times \Cref{rem:deco} to get the following three cubes, in which all the vertical faces are pullbacks and the top one is a pushout.
+
+\[
+\xymatrix@C=9pt@R=6pt{&I_1\ar[dd]|\hole_(.65){a_1}\ar[rr]^{v_1} \ar@{>->}[dl]_{v_2} && X_1 \ar[dd]^{b_1} \ar@{>->}[dl]_{x_1}  && I_2\ar[dd]|\hole_(.65){a_2}\ar[rr]^{s_1} \ar@{>->}[dl]_{s_2} && U_1 \ar[dd]^{c_1} \ar@{>->}[dl]_{u_1}  && I_3\ar[dd]|\hole_(.65){a_3}\ar[rr]^{r_1} \ar@{>->}[dl]_{r_2} && W_1 \ar[dd]^{d_1} \ar@{>->}[dl]_{w_1} \\ X_2  \ar[dd]_{b_2}\ar[rr]^(.7){x_2} & & X \ar[dd]_(.3){h_1} &&  U_2  \ar[dd]_{c_2}\ar[rr]^(.7){u_2} & & X_1 \ar[dd]_(.3){h_2\circ x_1} &  &W_2  \ar[dd]_{d_2}\ar[rr]^(.7){w_2} & & X_2 \ar[dd]_(.3){h_2\circ x_2 }\\&E_{\mathcal{G}}\ar[rr]|\hole^(.65){f_2} \ar@{>->}[dl]_{f_1} && E_{\mathcal{K}} \ar@{>->}[dl]^{k_E}  & & E_{\mathcal{G}}\ar[rr]|\hole^(.65){f_2} \ar@{>->}[dl]_{f_1} && E_{\mathcal{K}} \ar@{>->}[dl]^{k_E} && E_{\mathcal{G}}\ar[rr]|\hole^(.65){f_2} \ar@{>->}[dl]_{f_1} && E_{\mathcal{K}} \ar@{>->}[dl]^{k_E} \\E_{\mathcal{H}} \ar[rr]_{h_E} & & E_{\mathcal{P}} & &E_{\mathcal{H}} \ar[rr]_{h_E} & & E_{\mathcal{P}}  && E_{\mathcal{H}} \ar[rr]_{h_E} & & E_{\mathcal{P}} }\]
+
+Now it is enough to embark in a long series of tedious but straightforward computations. Let us settle some preliminary matters. If we compute we get
+\tiny
+\[	\begin{split}
+	j_{\mathcal{P},1}\circ k_V\circ \tau_{\mathcal{K}}\circ b_1\circ u_2&=k^\star_V \circ j_{\mathcal{K},1}\circ \tau_{\mathcal{K}}	\circ b_1\circ u_2\\&=k^\star_V\circ t_\mathcal{K}\circ b_1\circ u_2\\&=t_{\mathcal{P}}\circ k_E\circ b_1\circ u_2\\&=t_{\mathcal{P}}\circ h_1\circ x_1\circ u_2\\&=t_{\mathcal{P}}\circ h_2\circ x_1\circ u_2\\&=t_{\mathcal{P}}\circ h_E\circ c_2\\&=h^{\star}_V\circ t_{\mathcal{H}}\circ c_2\\&=h^\star_{V}\circ j_{\mathcal{{H}}, 1}\circ \tau_{\mathcal{H}}\circ c_2\\&=j_{\mathcal{P},1}\circ h_V\circ \tau_\mathcal{{H}}\circ c_2
+\end{split} \quad 	\begin{split}
+		j_{\mathcal{P},1}\circ h_V\circ \tau_{\mathcal{H}}\circ b_2\circ w_1&=h^\star_V \circ j_{\mathcal{H},1}\circ \tau_{\mathcal{H}}	\circ b_2\circ w_1\\&=h^\star_V\circ t_\mathcal{H}\circ b_2\circ w_1\\&=t_{\mathcal{P}}\circ h_E\circ b_2\circ w_1\\&=t_{\mathcal{P}}\circ h_1\circ x_2\circ w_1\\&=t_{\mathcal{P}}\circ h_2\circ x_2\circ w_1\\&=t_{\mathcal{P}}\circ k_E\circ d_1\\&=k^{\star}_V\circ t_{\mathcal{K}}\circ d_1\\&=k^\star_{V}\circ j_{\mathcal{{K}}, 1}\circ \tau_{\mathcal{K}}\circ d_1\\&=j_{\mathcal{P},1}\circ k_V\circ \tau_\mathcal{{K}}\circ d_1
+\end{split} \]
+
+\normalsize
+
+By \Cref{prop:inj} we know that $j_{\mathcal{P},1}$ is mono so the two diagram below commutes.
+This, in turn, by \Cref{prop:regmono}, yields the dotted arrows $e\colon U_2\to V_{\mathcal{{G}}}$ and $\hat{e}\colon W_1\to V_{\mathcal{{G}}}$ fitting in the diagram below.
+\[\xymatrix{U_2  \ar[d]_{c_2}\ar@{.>}[dr]^{e}\ar[r]^{u_2} & X_1 \ar[r]^{b_1} & E_{\mathcal{K}} \ar[d]^{\tau_{\mathcal{{K}}}} & W_1  \ar[d]_{d_1}\ar@{.>}[dr]^{\hat{e}}\ar[r]^{w_1} & X_2 \ar[r]^{b_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{{H}}}}  \\E_{\mathcal{H}} \ar[dr]_{\tau_{\mathcal{{H}}}}&V_{\mathcal{G}}  \ar[r]^{g_2} \ar@{>->}[d]_{g_1}& V_{\mathcal{K}} \ar@{>->}[d]^{k_V} & E_{\mathcal{K}} \ar[dr]_{\tau_{\mathcal{{K}}}}&V_{\mathcal{G}}  \ar@{>->}[r]^{g_1} \ar[d]_{g_2}& V_{\mathcal{H}} \ar[d]^{h_V}\\ & V_{\mathcal{{H}}} \ar[r]_{h_V} & V_{\mathcal{P}} & & V_{\mathcal{{K}}} \ar@{>->}[r]_{k_V} & V_{\mathcal{P}}}\]
+
+Since $(f_1, g_1)$ preserves inputs, we can construct the solid part of the following diagrams, proving the existence of $p\colon U_2\to I_{\mathcal{H}, g_1}$ and $\hat{p}\colon W_1\to E_{\mathcal{H}}$.
+\[\xymatrix{&U_2 \ar@{.>}[d]_{p} \ar@/_.7cm/[dd]_(.4){e}|(.69)\hole \ar@/^.3cm/[dr]^{c_2} & &&W_1 \ar@{.>}[d]_{\hat{p}} \ar@/_.7cm/[dd]_(.4){\hat{e}}|(.69)\hole \ar[r]^{w_1} & X_2 \ar[d]^{b_2}\\ &I_{\mathcal{H}, g_1} \ar@{>}[dl]_{t_{g_1}} \ar[r]^{w^{\mathcal{G}}_1} \ar[d]^{w^{\mathcal{G}}_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{H}}} & &I_{\mathcal{H}, g_1} \ar@{>}[dl]_{t_{g_1}} \ar[r]^{w^{\mathcal{G}}_1} \ar[d]^{w^{\mathcal{G}}_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{H}}}\\ E_{\mathcal{{G}}} \ar[r]_{\tau_{\mathcal{G}}}& V_{\mathcal{G}} \ar@{>->}[r]_{g_1}  & V_{\mathcal{{H}}} & E_{\mathcal{{G}}} \ar[r]_{\tau_{\mathcal{G}}}& V_{\mathcal{G}} \ar@{>->}[r]_{g_1}  & V_{\mathcal{{H}}}}\]
+
+Now, by a further computation and using \Cref{prop:image} we get:
+\[
+\begin{split}
+	t_{\mathcal{K}}\circ f_2\circ t_{g_1}\circ p&=g^\star_2\circ t_{\mathcal{G}}\circ t_{g_1}\circ p\\&=g^{\star}_2\circ j_{\mathcal{G}, 1}\circ \tau_{\mathcal{G}} \circ t_{g_1}\circ p\\&=g^{\star}_2\circ j_{\mathcal{G}, 1}\circ w^{\mathcal{G}}_2\circ p\\&=g^{\star}_2\circ j_{\mathcal{G}, 1}\circ e\\&=j_{\mathcal{H},1}\circ g_2\circ e\\&=j_{\mathcal{H},1}\circ \tau_{\mathcal{K}}\circ b_1\circ u_2\\&=t_{\mathcal{K}}\circ b_1\circ u_2
+\end{split} \quad \begin{split}
+	t_{\mathcal{H}}\circ f_1\circ t_{g_1}\circ \hat{p}&=g^\star_1\circ t_{\mathcal{G}}\circ t_{g_1}\circ \hat{p}\\&=g^{\star}_1\circ j_{\mathcal{G}, 1}\circ \tau_{\mathcal{G}} \circ t_{g_1}\circ \hat{p}\\&=g^{\star}_1\circ j_{\mathcal{G}, 1}\circ w^{\mathcal{G}}_2\circ \hat{p}\\&=g^{\star}_1\circ j_{\mathcal{G}, 1}\circ \hat{e}\\&=j_{\mathcal{H},1}\circ g_1\circ \hat{e}\\&=j_{\mathcal{H},1}\circ \tau_{\mathcal{H}}\circ b_2\circ w_1\\&=t_{\mathcal{H}}\circ b_2\circ w_1
+\end{split}\]
+
+Since $t_{\mathcal{K}}$ and $t_\mathcal{H}$ are mono we get the two dotted arrow $s\colon U_2\to I_1$ and $\hat{s}\colon W_1\to I_1$ depicted below.
+\[\xymatrix{U_2 \ar@/^.4cm/[drr]^{u_2}  \ar[d]_{p}\ar@{.>}[dr]_{s} & &&W_1 \ar@/^.4cm/[drr]^{w_1}  \ar[d]_{\hat{p}}\ar@{.>}[dr]_{\hat{s}}\\ I_{\mathcal{H}, g_1} \ar[dr]_{t_{g_1}}& I_1 \ar[r]^{v_1} \ar[d]_{a_1} & X_1 \ar[d]^{b_1} & I_{\mathcal{H}, g_1} \ar[dr]_{t_{g_1}}& I_1 \ar@{>->}[r]^{v_2} \ar[d]_{a_1} & X_2 \ar[d]^{b_2}\\ & E_{\mathcal{G}} \ar[r]_{f_2} & E_{\mathcal{K}}& & E_{\mathcal{G}} \ar@{>->}[r]_{f_1} & E_{\mathcal{H}}}\]
+
+ We can now split the remainder of proof in four steps.
+
+\smallskip \noindent 
+$	h_2\circ x_1\circ u_1=h_1\circ x_1\circ u_1$. Let us begin noticing that
+	\begin{align*}
+		k^\star_{V} \circ t_{\mathcal{K}} \circ b_1 \circ u_1& = t_{\mathcal{P}}\circ k_E \circ b_1 \circ u_1\\&=t_{\mathcal{P}}\circ h_1\circ x_1 \circ u_1\\&=t_{\mathcal{P}}\circ h_2\circ x_1 \circ u_1\\&=t_{\mathcal{P}}\circ k_E\circ c_1\\&=k^\star_V\circ t_{\mathcal{K}} \circ c_1
+	\end{align*}
+	Thus, since $k^\star_{V}\circ t_{\mathcal{{K}}}$ is mono we have that $b_1\circ u_1 = c_1$, but then we have
+	\begin{align*}
+		h_2\circ x_1\circ u_1&=k_E\circ c_1\\&= k_E\circ b_1\circ u_1\\&=h_1\circ x_1\circ u_1
+	\end{align*}
+
+\smallskip \noindent  $	h_2\circ x_1\circ u_2=h_1\circ x_1\circ u_2$. We are going to use again \Cref{prop:image} to get.
+	\begin{align*}
+		h_2\circ x_1\circ u_2&=h_E\circ c_2\\&=h_E\circ w^{\mathcal{G}}_1\circ p\\&=h_E\circ f_1\circ t_{g_1}\circ p\\&=h_E\circ f_1\circ a_1\circ s\\&=h_E\circ b_2\circ v_2\circ s\\&=h_1\circ x_2\circ v_2\circ s\\&=h_1\circ x_1\circ v_1\circ s\\&=	h_1\circ x_1\circ u_2
+	\end{align*}
+
+	\medskip Summing up the previous two points, we get that $h_1\circ x_1=h_2\circ x_1$. Let us prove that $h_1\circ x_2=h_2\circ x_2$ too.
+
+	\smallskip \noindent $h_1\circ x_2\circ w_1=h_2\circ x_2\circ w_1$. Since we already know that $h_1\circ x_1=h_2\circ x_1$, it is now enough to do the following computation.
+	\begin{align*}
+		h_2\circ x_2\circ w_1&=h_2\circ x_2\circ v_2\circ \hat{s}\\&=h_2\circ x_1\circ v_1\circ \hat{s}\\&=h_1\circ x_1\circ v_1\circ \hat{s}\\&=h_1\circ x_2\circ v_2\\&=h_E\circ b_2\circ v_2\\&=h_E\circ f_1\circ a_1\\&=h_E\circ f_1\circ t_{g,1}\circ \hat{p}\\&=h_E\circ w^{\mathcal{{G}}}_1\circ \hat{p}\\&=h_E\circ b_2\circ w_1\\&=h_1\circ x_2\circ w_1
+	\end{align*}
+
+	\smallskip \noindent $h_1\circ x_2\circ w_2=h_2\circ x_2\circ w_2$.
+
+	$h_1=h_E(h'_1)$ and $h_2=h_E(h'_2)$ for some $h'_1$ and $h'_2\in E_{\mathcal{H}}$. Let $x_1$ and $x_2$ be the unique elements of $V_{\mathcal{H}}$ such that
+	\[\delta_{x_1}=t_{\mathcal{H}}(h'_1) \qquad \delta_{x_2}=t_{\mathcal{H}}(h'_2)\]
+	Then it must be that
+	\begin{align*}\delta_{h_V(x_1)}&=h_V\circ \delta_{x_1}\\&=h^\star_V(\delta_{x_1})\\&=h^\star_V(t_{\mathcal{H}}(h'_1))\\&=t_{\mathcal{P}}(h_1)\\&=t_{\mathcal{P}}(h_2)\\&=h^\star_V(t_{\mathcal{H}}(h'_2))\\&=h^\star_V(\delta_{x_2})\\&=h_V\circ \delta_{x_2}\\&=\delta_{h_V(x_2)}
+	\end{align*}
+	showing that $h_V(x_1)=h_V(x_2)$.
+By the second point of \Cref{lem:push2}  we know that at least one between $x_1$ or $x_2$ must belong to $g_1(V_{\mathcal{G}})$.
+Without loss of generality we can suppose that it is $x_1$ (otherwise just swap it with $x_2$).
+Using \Cref{prop:image,lem:reg} we know that $h'_1$ is in the image of $f_1$, i.e.~that there exists $e\in E_\mathcal{\mathcal{G}}$ such that $h'_1=f_1(e)$, but then
+	\begin{align*}
+		k_E(f_2(e))&=h_E(f_1(e))\\&=h_E(h'_1)\\&=h_1
+	\end{align*} 
+	so we fall back to the third case and we can conclude.
+
+This concludes the proof.
+\end{proof}
+
+\Cref{cor:varie3,lem:reg,prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{corradini2005term}.
+\begin{corollary}
+	The category $\tg$ is quasiadhesive.
+\end{corollary}
+
+\input{Hypergraphs_with_equivalences}
 
@@
 
-We can use \cref{lim} to characterize monos in comma categories. 
+We can use \Cref{lim} to characterize monos in comma categories. 
 \begin{corollary}\label{cor:mono}
@@
 	\[\xymatrix@C=50pt{(A, B, f)  \ar[r]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}& (A, B, f)  \ar[d]^{(h,k)} \\ (A, B, f)  \ar[r]_{(h,k)}& (A', B', g) }\]
-	Using \cref{lim} we deduce that the following two squares are pullbacks in $\A$ and $\B$.
+	Using \Cref{lim} we deduce that the following two squares are pullbacks in $\A$ and $\B$.
 	\[\xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
@@
 	\[\xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
-	By \cref{lim} this implies that 
+	By \Cref{lim} this implies that 
 	\[\xymatrix@C=50pt{(A, B, f)  \ar[r]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}& (A, B, f)  \ar[d]^{(h,k)} \\ (A, B, f)  \ar[r]_{(h,k)}& (A', B', g) }\]

### 2025-02-06 icgt/Hypergraphs_with_equivalences.tex
cose

--- 2025-02-04 icgt/Hypergraphs_with_equivalences.tex
@@
-\section{Hypergraphs with equivalences}
+\section{Hypergraphs and term graphs with equivalences}
 
 \begin{definition}
-	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is the object of \emph{equivalence classes} and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is an epimorphism called \emph{quotient map}.
+	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is an object and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is a regular epimorphism called \emph{quotient map}.
+
 	A morphism $h:\mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute.

### 2025-02-07 icgt/Hypergraphs_with_equivalences.tex
T is continuous

@@
 \end{remark}
+
+Let now $K: \EqHyp \to \Set$ be the functor which sends each hypergraph with equivalence $\mathcal{G} = (E, V, C, s, t, q)$ onto $K(\mathcal{G}) = C$, and each morphsism $(h_E, h_V, h_C)$ to $h_C$.
+
+\begin{proposition}
+	\EqHyp is complete and cocomplete, and $T$ preserves limits and colimits.
+\end{proposition}
+
+\begin{proof}
+	Let $D: \cat{I}\to \EqHyp$ be a diagram, and, for each $i \in \cat{I}$, $D(i) = (E_i, V_i, C_i, s_i, t_i, q_i)$.
+	Suppose now $(E, V, s, t)$, together with morphisms $(\pi_i^E, \pi_i^V)$, be the limit of $T \circ D$.
+	Then, $V$, together with $(q_i\circ \pi_V^i)_{i\in \cat I}$, is a cone for $K \circ D$. Indeed, let $\alpha: i \to j$ be an arrow of $\cat I$, $D(\alpha) = (h_E,h_V, h_C)$.
+	By definition of $T$, $(T \circ D)(\alpha) = (h_E, h_V)$, hence we have the following situation.
+	\[\xymatrix{
+		& V \ar[dl]_{\pi_V^i} \ar[dr]^{\pi_V^j} & \\V_i\ar[rr]^{h_V}\ar[d]_{q_i}&&V_j\ar[d]^{q_j}\\C_i\ar[rr]_{h_C}&&C_j
+	}\]
+	Suppose now that $L$, with morphisms $(l_i)_{i\in \cat I}$ be the limit of $K\circ D$. Hence, we have an arrow $l:V \to L$, which is not epi in general.
+	Let then $l = m \circ q$ be the epi-mono factorization of it.
+Consider the following situation, where the outer rectangle commutes by definition, and the dotted arrow is yielded by ({\color{red}cite left lifting prop}).
+	\[\xymatrix{
+			V\ar[r]^{\pi_V^i}\ar[d]_{q}&V_i\ar[r]^{q_i}&C_i\ar[d]^{\id{C_i}}\\C\ar[r]_{m}\ar@{.>}[urr]^{\pi_C^i}&L\ar[r]_{l_i}&{C_i}
+	}\]
+	Thus, $(E, V, C, s, t, q)$, together with $(\pi_E^i, \pi_V^i, \pi_C^i)$ is a cone over $D$. {\color{red} remain to show that this cone is terminal}
+
+	Suppose now $(E', V', s', t')$, together with $(\kappa_E^i, \kappa_V^i)_{i \in \cat I}$, be the colimit of $T \circ D$, and $C'$, with $(c_i)_{i \in \cat I}$ be the colimit of $K \circ D$.
+	Then, we have the folliwing situation.
+	\[\xymatrix{
+								  &  {V'} &                             \\
+		V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
+		C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
+								  &  {C'} &
+	}\]
+	Then, $C'$ with morphisms $(c_i \circ q_i)_{i\in \cat I}$ is a conone for $U \circ D$. Then, there exists a unique morphism $q': V' \to C'$ such that $q'\circ \kappa_V^i = c_i\circ q_i$.
+	Such morphism is epi ({\color{red}cite Lemma 1.3.45 of the thesis}), and thus $(E', V', C', s', t', q')$, together with $(\kappa_E^i, \kappa_V^i, c_i)_{i\in \cat I}$ is the colimit of $D$.
+
+\end{proof}

### 2025-02-07 icgt/Hypergraphs_with_equivalences.tex
Regmonos

@@
 \end{proof}
+
+\begin{corollary}\label{cor:mono1}
+	An arrow $h = (h_E, h_V, h_C): \mathcal{G \to H}$ is mono if and only if $T(h)$ is mono.
+\end{corollary}
+
+\begin{proof}
+	The ``if'' part is given by the faithfulness of $T$.
+	The ``only if'' part is given by \Cref{rem:eqhyp_morphs}.
+\end{proof}
+
+\begin{corollary}\label{cor:mono2}
+	If $h = (h_E, h_V, h_C): \mathcal{G\to H}$ is a regular mono in $\EqHyp$, then $h_E, h_V$ and $h_C$ are all monos.
+\end{corollary}
+
+\begin{proof}
+	If $h$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos. Suppose now $f, g: \mathcal{H\rightrightarrows K}$ be the arrows equalized by $h$. Then, we have:
+	\begin{align*} f_C \circ h_C \circ q_\mathcal{G} &= f_C\circ q_\mathcal{H} \circ h_V\\&=q_\mathcal{K}\circ g_V \circ h_V\\&=q_\mathcal{K}\circ f_V \circ h_V\\&=g_C \circ h_C \circ q_\mathcal{G} \end{align*}
+	Since $q_\mathcal{G}$ is epi, we have $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, and thus a monomorphism.
+\end{proof}
+
+\begin{proposition}
+	Let $h = (h_E, h_V, h_C): \mathcal{G \to H}$ be a regular monomorphism in $\EqHyp$.
+	Then, $h_E$ and $h_V$ are monos and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{H}\circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$.
+\end{proposition}
+
+\begin{proof}
+	By \Cref{cor:mono2}, we have that $h_E, h_V$ and $h_C$ are all monos.
+	Hence, by \Cref{cor:kermono}, $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$ if and only if it is the kernel pair also of $h_C \circ q_\mathcal{G}$, since $h_C$ is mono by hypothesis.
+	The thesis follows from $h_C \circ q_\mathcal{G} = q_H \circ h_V$, and from the hypothesis of $h_E$ mono.
+\end{proof}
+
+\begin{remark}
+    It is possible to restate the last proposition, by \Cref{ex:kernel_pairs_in_Set}, as 
+    \begin{displayquote}
+    \textit{$h_E$ and $h_V$ are mono and, for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$}
+    \end{displayquote}
+    That is, a regular monomorphism in $\EqHyp$ is a morphism that reflects equivalences besides preserving them.
+\end{remark}

### 2025-02-10 calco/main.tex
cose

--- 2025-02-06 icgt/main.tex
@@
-\documentclass[runningheads,envcountsect]{llncs}
+\documentclass[runningheads,envcountsect]{lipics-v2021}
 
@@
 \newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
-\usepackage{amsmath,amssymb,mathrsfs, dsfont} %simboli matematici
+\usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont} %simboli matematici
 \usepackage[all, cmtip]{xy}
@@
 \usepackage[utf8]{inputenc} % Input encoding - per caratteri particolari
-\usepackage[english]{babel} % Lingua principale inglese
+%\usepackage[english]{babel} % Lingua principale inglese
 \usepackage{graphicx} % Per includere immagini esterne
@@
 
-\spnewtheorem*{notation}{Notation}{\bfseries}{}
-\spnewtheorem*{convention}{Convention}{\bfseries}{}
+%\spnewtheorem*{notation}{Notation}{\bfseries}{}
+%\spnewtheorem*{convention}{Convention}{\bfseries}{}
 
@@
 
-\titlerunning{????} %TODO optional, please use if title is longer than one line
+%\titlerunning{????} %TODO optional, please use if title is longer than one line
 
 %% Author with single affiliation.
-\author{Roberto Biondo \inst{1}{\small\Envelope}\and Davide Castelnovo\inst{1}\orcidID{0000-0002-5926-5615}
-	\and \\Fabio Gadducci\inst{1}\orcidID{0000-0003-0690-3051}
-}
-\institute{Dept.~of Computer Science, University of Pisa, Italy. 
-	\email{r.biondo@studenti.unipi.it},
-	\email{castelnovod@gmail.com},
-	 \email{fabio.gadducci@unipi.it}
-}
+%\author{Roberto Biondo \inst{1}{\small\Envelope}\and Davide Castelnovo\inst{1}\orcidID{0000-0002-5926-5615}
+	%\and \\Fabio Gadducci\inst{1}\orcidID{0000-0003-0690-3051}
+%}
+%\institute{Dept.~of Computer Science, University of Pisa, Italy. 
+	%\email{r.biondo@studenti.unipi.it},
+	%\email{castelnovod@gmail.com},
+	% \email{fabio.gadducci@unipi.it}
+%}
 
@@
 
-\begin{notation}
+%\begin{notation}
 Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects, so
@@
 Given an object $X$, we will denote by $?_X$ the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one.
-\end{notation}
+%\end{notation}
 
@@
 		\[\xymatrix{X \ar@{>->}[r]^{m} \ar@{>->}[d]_{m}& Y \ar@{>->}[d]^{h}\\ Y \ar@{>->}[r]^{k} & Z}\]
-		It is now immediate to see that $m$ is the equalizer of $h$ and $k$. \qed
+		It is now immediate to see that $m$ is the equalizer of $h$ and $k$.  
 	\end{enumerate}
@@
 
-In this section we introduce the notion of \emph{$\X$-hypergraph}.
+In this section we briegly recall the notion \emph{$\X$-hypergraph}.
 In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usual \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,wadler1995monads}.
-In \Cref{app:mon} the interested reader can find a brief review of the construction of such a monad.
-
-\begin{convention}
-	In this section and in the following one we will operate inside a countably distributive and extensive cartesian category $(\X, \times, I)$ with finite limits.
-As shown in \Cref{app:mon}, then $\mo{U}\colon \mono{\X}\to \X$ has a left adjoint $\mo{F}$ and $\mo{F}\circ \mo{U}$ preserves pullbacks.
-Denoting by $(-)^\star$ such composition, we can assume that $X^\star$ is the coproduct $\sum_{n\in \mathbb{N}}X^n$.
-We will also assume that $(-)^\star$ preserves equalizers.
-\todo{Non c'è nessuna ragione categoriale carina come l'estensività che garantisce la preservazione degli equalizzatori.
-In $\Set$ è vero per un risultato di Carboni e Johnstone che non credo si generalizzi}
-\end{convention}
+We will recall some of its proprieties.
+
+\begin{proposition}
+	The following facts are true:
+	\begin{enumerate}
+		\item for every set $X$ and $n\in \mathbb{N}$ there are arrows $v_{n}\colon X^n\to X^\star $ such that $(X^\star, \{v_{n}\}_{n\in \mathbb{N}})$ is a coproduct;
+		\item for every arrow $f\colon X\to Y$, $f^\star$ is the coproduct of the family $\{f^n\}_{n\in \mathbb{N}}$;
+		\item $(-)^\star$ preserves all \emph{connected limits} \cite{carboni1995connected}, in particular it preserves all pullbacks and equalizers.
+	\end{enumerate}
+\end{proposition}
 
@@
 
-\subsection{The category of $\X$-hypergraphs}
-
-We will start this section with the definition of $\X$-hypergraphs and we will see how to label them with an algebraic signature.
-
-\begin{definition}An \emph{$\X$-hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two objects $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the object of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
-A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of morphisms $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute.
+\subsection{The category of hypergraphs}
+
+We will start this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
+
+\begin{definition}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the set of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
+A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute.
 
 	\[\xymatrix{ E_{\mathcal{G}} \ar[d]_{h} \ar[r]^{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}& E_{\mathcal{G}} \ar[r]^{t_{\mathcal{G}}} \ar[d]_{h} & V^\star_{\mathcal{G}} \ar[d]^{k^\star}  \\ E_{\mathcal{G}} \ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} & E_{\mathcal{G}} \ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} }\]
-	We define $\hyp_\X$ to be the resulting category.
+	We define $\hyp$ to be the resulting category.
 \end{definition}
 
-Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$, then we can present $\hyp_\X$ as a comma category.
+Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$, then we can present $\hyp$ as a comma category.
 \begin{proposition}\label{prop:com}
-	$\hyp_\X$ is isomorphic to $\comma{\id{\X}}{\pro^\star}$
+	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
 \end{proposition}
@@
 \begin{corollary}\label{prop:hypadh}
-If $\X$ is (strictly) $\mathcal{N}$-adhesive	then $\hyp$ is an (strict) $\mathcal{M}$-adhesive category, where $\mathcal{M}$ is the class of all morphism $(h,k)$ with both $h$ and $k$ in $\mathcal{N}$.
-
-In particular, if $\X$ is (quasi)adhesive then so is $\hyp$.
+	 $\hyp$ is an adhesive category.
 \end{corollary}
@@
 \begin{corollary}\label{cor:monhyper}
-A morphism $(h,k)$ is a mono in $\hyp_\X$ if and only if both its components are mono in $\X$.
+A morphism $(h,k)$ is a mono in $\hyp$ if and only if both its components are injective functions.
 \end{corollary}
@@
 
-\begin{proposition}\label{cor:left} If $\X$ has an initial object, then the forgetful functor $U_{\X}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\X}$.
+\begin{proposition}\label{cor:left}  The forgetful functor $U_{\X}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\X}$.
 \end{proposition}
@@
 
-$\Set$-hypergraphs,  can be represented graphically.
+We can represent hypergraphs graphically.
 We will use dots to denote nodes and squares to denote hyperedges, the name of a node or of an hyperedge will be put near the corresponding dot or square.
 Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge will have an arrowhead in the middle pointing towards the hyperedge, while the lines to the targets will have arrowheads pointing to the target nodes.
-We will decorate the arrow corresponding to the $i^{th}$ letter (i.e.~its value at $i-1$) of a target or a source with a label $i$.
+We will decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
 
@@
 
-\todo{Anche 'sta sezione possiamo anche buttarla via}
-\subsubsection{$\hyp_\X$ as a category of functors}
+\subsubsection{$\hyp$ as a category of functors}
 
@@
 
-Given $F\colon \catname{H}\to \catname{Set}$, since $\X$ has countable coproducts we can define
+Given $F\colon \catname{H}\to \catname{Set}$ we can define
 \[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
@@
 This is the same as saying that $\eta$ induces a morphism $(\hat{\eta}, \eta_{\bullet})\colon \mathcal{G}_F\to \mathcal{G}_H$.
-It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \catname{\X}^{\catname{H}}\to \hyp_\X$.
-
+It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \Set^{\catname{H}}\to \hyp$.
+
+It is now a a straightforward exercise to see that this functor it is actually an equivalence (see \cite{castelnovo2023thesis} for details), yielding the following result.
+
+	\iffalse 
 \begin{remark}\label{rem:utile}
-	By \Cref{rem:salv} we know that countably distributivity entails that, for every $k,l\in \mathbb{N}$, the arrow $b^F_k\times b^F_l$ is a coprojection, thus extensivity entails that the square is a pullback
+Now, notice that in $\Set$ countable coproducts distributes over pullbacks, \Cref{rem:salv} we know that countably distributivity entails that, for every $k,l\in \mathbb{N}$, the arrow $b^F_k\times b^F_l$ is a coprojection, thus extensivity entails that the square is a pullback
 	\[\xymatrix@C=30pt{F(k,l) \ar[d]_{(s^F_{k,l}, t^F_{k,l})}  \ar[r]^{a^F_{k,l}}& E_F \ar[d]^{(s_F, t_F)} \\ F(\bullet)^k\times F(\bullet)^l \ar[r]_{b^F_k\times b^F_l} & F(\bullet)^\star\times F(\bullet)^\star}\]
 
-	\iffalse 
 	As in \Cref{rem:pb}, countably extensivity of $X$ guarantees that, for every $k\in \mathbb{N}$ following square is a pullback.	
@@
  Showing, finally, that
+
+\end{remark}
 \fi
-\end{remark}
 
@@
 \end{proposition}
+
+\iffalse 
 \begin{proof}	
@@
 
-	This allows us to conclude that $(\phi, \id{V_{\mathcal{G}}})$ is an isomorphism in $\hyp_\X$, from which the thesis now follows. \qed
+	This allows us to conclude that $(\phi, \id{V_{\mathcal{G}}})$ is an isomorphism in $\hyp_\X$, from which the thesis now follows. 
 	\end{itemize}
 \end{proof}
-
-\subsection{Labelling hypergraph with an algebraic signature}
+\fi
+
+\subsubsection{Labelling hypergraph with an algebraic signature}
 
 \begin{definition}
-An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by an object $O_\Sigma$ and an arrow $\ari_\Sigma\colon O_\Sigma \to 1^\star$.
-
-We define the \emph{$\X$-hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} as $(0_\Sigma, 1, \ari_\Sigma, o_1\circ !_{O_\Sigma})$.
-,The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
+An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ and an \emph{arity function} $\ari_\Sigma\colon O_\Sigma \to \mathbb{N}$.
+
+We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as setof nodes, so that $1^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, where $\delta_1$ picks the element $1$.
+The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
 \end{definition}
@@
 
-Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature, we are going to use the hypergraph $\mathcal{G}^{\Sigma}$ of \Cref{exa_3} in order to label hyperedges with operations.
-ì
 \Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterization of monomorphisms in it.
+
 \begin{proposition}\label{prop:mono} Let $\X$ be a (strict) $\mathcal{N}$-adhesive category, then the following hold true:
@@
 
-\begin{proof} To fix the notations, let $(V^\star_{\mathcal{G}}, \{j_{\mathcal{{G}}, n} \}_{n\in \mathbb{N} })$, $(V^\star_{\mathcal{H}}, \{j_{\mathcal{{H}}, n} \}_{n\in \mathbb{N} })$, $(V^\star_{\mathcal{K}}, \{j_{\mathcal{{K}}, n} \}_{n\in \mathbb{N} })$, and $(V^\star_{\mathcal{P}}, \{j_{\mathcal{{P}}, n} \}_{n\in \mathbb{N} })$ be the coproducts defining $V^\star_{\mathcal{G}}$, $V^\star_{\mathcal{H}}$, $V^\star_{\mathcal{K}}$ and $V^\star_{\mathcal{P}}$.
-In $\hyps$ pushouts are computed componentwise, so that in the following diagrams the squares are all pushouts in $\X$.
-
-	\[\xymatrix{E_{\mathcal{G}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}} \ar@{>->}[d]^{k_E} & V_{\mathcal{G}}  \ar[r]^{g_2} \ar@{>->}[d]_{g_1}& V_{\mathcal{K}} \ar@{>->}[d]^{k_V}\\ E_{\mathcal{H}} \ar[r]_{h_E} & E_{\mathcal{P}} & V_{\mathcal{H}}  \ar[r]_{h_V}& V_{\mathcal{K}}}\]
-
-Moreover, we also know that $s_\mathcal{P}, t_{\mathcal{P}}\colon E_{\mathcal{P}}\to V_{\mathcal{P}}$  fit in the two squares below.
-
-	\[\xymatrix@C=20pt@R=20pt{V^\star_{\mathcal{G}} \ar[ddd]_{g^\star_1}\ar[rrr]^{g^\star_2} &&&V^\star_{\mathcal{K}} \ar[ddd]^{k^\star_V} & V^\star_{\mathcal{G}} \ar[ddd]_{g^\star_1} \ar[rrr]^{g^\star_2}&&& V^\star_{\mathcal{K}}\ar[ddd]^{k^\star_V} \\ & E_{\mathcal{G}} \ar[ul]^{s_{\mathcal{G}}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}} \ar[ur]_{s_{\mathcal{K}}} \ar@{>->}[d]^{k_E}&&& E_{\mathcal{G}} \ar[ul]^{t_{\mathcal{G}}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}}\ar[ur]_{t_{\mathcal{K}}}\ar@{>->}[d]^{k_E} \\ & E_{\mathcal{H}} \ar[dl]_{s_{\mathcal{H}}} \ar[r]_{h_E} & E_{\mathcal{P}} \ar[dr]^{s_{\mathcal{P}}}&&& E_{\mathcal{H}} \ar[dl]_{t_{\mathcal{H}}}\ar[r]_{h_E} & E_{\mathcal{P}} \ar[dr]^{t_{\mathcal{P}}} \\V^\star_{\mathcal{H}} \ar[rrr]_{h^\star_V} &&&V^\star_{\mathcal{P}} & V^\star_{\mathcal{H}}\ar[rrr]_{h^\star_V} &&& V^\star_{\mathcal{P}}}\]
-
-We have to show that $t_{\mathcal{P}}$ is mono, let thus $h_1, h_2\colon X\rightrightarrows E_{\mathcal{P}}$ be two arrows such that $t_\mathcal{P}\circ h_1=t_{\mathcal{P}}\circ h_2$.
-We can apply three times \Cref{rem:deco} to get the following three cubes, in which all the vertical faces are pullbacks and the top one is a pushout.
-
-\[
-\xymatrix@C=9pt@R=6pt{&I_1\ar[dd]|\hole_(.65){a_1}\ar[rr]^{v_1} \ar@{>->}[dl]_{v_2} && X_1 \ar[dd]^{b_1} \ar@{>->}[dl]_{x_1}  && I_2\ar[dd]|\hole_(.65){a_2}\ar[rr]^{s_1} \ar@{>->}[dl]_{s_2} && U_1 \ar[dd]^{c_1} \ar@{>->}[dl]_{u_1}  && I_3\ar[dd]|\hole_(.65){a_3}\ar[rr]^{r_1} \ar@{>->}[dl]_{r_2} && W_1 \ar[dd]^{d_1} \ar@{>->}[dl]_{w_1} \\ X_2  \ar[dd]_{b_2}\ar[rr]^(.7){x_2} & & X \ar[dd]_(.3){h_1} &&  U_2  \ar[dd]_{c_2}\ar[rr]^(.7){u_2} & & X_1 \ar[dd]_(.3){h_2\circ x_1} &  &W_2  \ar[dd]_{d_2}\ar[rr]^(.7){w_2} & & X_2 \ar[dd]_(.3){h_2\circ x_2 }\\&E_{\mathcal{G}}\ar[rr]|\hole^(.65){f_2} \ar@{>->}[dl]_{f_1} && E_{\mathcal{K}} \ar@{>->}[dl]^{k_E}  & & E_{\mathcal{G}}\ar[rr]|\hole^(.65){f_2} \ar@{>->}[dl]_{f_1} && E_{\mathcal{K}} \ar@{>->}[dl]^{k_E} && E_{\mathcal{G}}\ar[rr]|\hole^(.65){f_2} \ar@{>->}[dl]_{f_1} && E_{\mathcal{K}} \ar@{>->}[dl]^{k_E} \\E_{\mathcal{H}} \ar[rr]_{h_E} & & E_{\mathcal{P}} & &E_{\mathcal{H}} \ar[rr]_{h_E} & & E_{\mathcal{P}}  && E_{\mathcal{H}} \ar[rr]_{h_E} & & E_{\mathcal{P}} }\]
-
-Now it is enough to embark in a long series of tedious but straightforward computations. Let us settle some preliminary matters. If we compute we get
-\tiny
-\[	\begin{split}
-	j_{\mathcal{P},1}\circ k_V\circ \tau_{\mathcal{K}}\circ b_1\circ u_2&=k^\star_V \circ j_{\mathcal{K},1}\circ \tau_{\mathcal{K}}	\circ b_1\circ u_2\\&=k^\star_V\circ t_\mathcal{K}\circ b_1\circ u_2\\&=t_{\mathcal{P}}\circ k_E\circ b_1\circ u_2\\&=t_{\mathcal{P}}\circ h_1\circ x_1\circ u_2\\&=t_{\mathcal{P}}\circ h_2\circ x_1\circ u_2\\&=t_{\mathcal{P}}\circ h_E\circ c_2\\&=h^{\star}_V\circ t_{\mathcal{H}}\circ c_2\\&=h^\star_{V}\circ j_{\mathcal{{H}}, 1}\circ \tau_{\mathcal{H}}\circ c_2\\&=j_{\mathcal{P},1}\circ h_V\circ \tau_\mathcal{{H}}\circ c_2
-\end{split} \quad 	\begin{split}
-		j_{\mathcal{P},1}\circ h_V\circ \tau_{\mathcal{H}}\circ b_2\circ w_1&=h^\star_V \circ j_{\mathcal{H},1}\circ \tau_{\mathcal{H}}	\circ b_2\circ w_1\\&=h^\star_V\circ t_\mathcal{H}\circ b_2\circ w_1\\&=t_{\mathcal{P}}\circ h_E\circ b_2\circ w_1\\&=t_{\mathcal{P}}\circ h_1\circ x_2\circ w_1\\&=t_{\mathcal{P}}\circ h_2\circ x_2\circ w_1\\&=t_{\mathcal{P}}\circ k_E\circ d_1\\&=k^{\star}_V\circ t_{\mathcal{K}}\circ d_1\\&=k^\star_{V}\circ j_{\mathcal{{K}}, 1}\circ \tau_{\mathcal{K}}\circ d_1\\&=j_{\mathcal{P},1}\circ k_V\circ \tau_\mathcal{{K}}\circ d_1
-\end{split} \]
-
-\normalsize
-
-By \Cref{prop:inj} we know that $j_{\mathcal{P},1}$ is mono so the two diagram below commutes.
-This, in turn, by \Cref{prop:regmono}, yields the dotted arrows $e\colon U_2\to V_{\mathcal{{G}}}$ and $\hat{e}\colon W_1\to V_{\mathcal{{G}}}$ fitting in the diagram below.
-\[\xymatrix{U_2  \ar[d]_{c_2}\ar@{.>}[dr]^{e}\ar[r]^{u_2} & X_1 \ar[r]^{b_1} & E_{\mathcal{K}} \ar[d]^{\tau_{\mathcal{{K}}}} & W_1  \ar[d]_{d_1}\ar@{.>}[dr]^{\hat{e}}\ar[r]^{w_1} & X_2 \ar[r]^{b_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{{H}}}}  \\E_{\mathcal{H}} \ar[dr]_{\tau_{\mathcal{{H}}}}&V_{\mathcal{G}}  \ar[r]^{g_2} \ar@{>->}[d]_{g_1}& V_{\mathcal{K}} \ar@{>->}[d]^{k_V} & E_{\mathcal{K}} \ar[dr]_{\tau_{\mathcal{{K}}}}&V_{\mathcal{G}}  \ar@{>->}[r]^{g_1} \ar[d]_{g_2}& V_{\mathcal{H}} \ar[d]^{h_V}\\ & V_{\mathcal{{H}}} \ar[r]_{h_V} & V_{\mathcal{P}} & & V_{\mathcal{{K}}} \ar@{>->}[r]_{k_V} & V_{\mathcal{P}}}\]
-
-Since $(f_1, g_1)$ preserves inputs, we can construct the solid part of the following diagrams, proving the existence of $p\colon U_2\to I_{\mathcal{H}, g_1}$ and $\hat{p}\colon W_1\to E_{\mathcal{H}}$.
-\[\xymatrix{&U_2 \ar@{.>}[d]_{p} \ar@/_.7cm/[dd]_(.4){e}|(.69)\hole \ar@/^.3cm/[dr]^{c_2} & &&W_1 \ar@{.>}[d]_{\hat{p}} \ar@/_.7cm/[dd]_(.4){\hat{e}}|(.69)\hole \ar[r]^{w_1} & X_2 \ar[d]^{b_2}\\ &I_{\mathcal{H}, g_1} \ar@{>}[dl]_{t_{g_1}} \ar[r]^{w^{\mathcal{G}}_1} \ar[d]^{w^{\mathcal{G}}_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{H}}} & &I_{\mathcal{H}, g_1} \ar@{>}[dl]_{t_{g_1}} \ar[r]^{w^{\mathcal{G}}_1} \ar[d]^{w^{\mathcal{G}}_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{H}}}\\ E_{\mathcal{{G}}} \ar[r]_{\tau_{\mathcal{G}}}& V_{\mathcal{G}} \ar@{>->}[r]_{g_1}  & V_{\mathcal{{H}}} & E_{\mathcal{{G}}} \ar[r]_{\tau_{\mathcal{G}}}& V_{\mathcal{G}} \ar@{>->}[r]_{g_1}  & V_{\mathcal{{H}}}}\]
-
-Now, by a further computation and using \Cref{prop:image} we get:
-\[
-\begin{split}
-	t_{\mathcal{K}}\circ f_2\circ t_{g_1}\circ p&=g^\star_2\circ t_{\mathcal{G}}\circ t_{g_1}\circ p\\&=g^{\star}_2\circ j_{\mathcal{G}, 1}\circ \tau_{\mathcal{G}} \circ t_{g_1}\circ p\\&=g^{\star}_2\circ j_{\mathcal{G}, 1}\circ w^{\mathcal{G}}_2\circ p\\&=g^{\star}_2\circ j_{\mathcal{G}, 1}\circ e\\&=j_{\mathcal{H},1}\circ g_2\circ e\\&=j_{\mathcal{H},1}\circ \tau_{\mathcal{K}}\circ b_1\circ u_2\\&=t_{\mathcal{K}}\circ b_1\circ u_2
-\end{split} \quad \begin{split}
-	t_{\mathcal{H}}\circ f_1\circ t_{g_1}\circ \hat{p}&=g^\star_1\circ t_{\mathcal{G}}\circ t_{g_1}\circ \hat{p}\\&=g^{\star}_1\circ j_{\mathcal{G}, 1}\circ \tau_{\mathcal{G}} \circ t_{g_1}\circ \hat{p}\\&=g^{\star}_1\circ j_{\mathcal{G}, 1}\circ w^{\mathcal{G}}_2\circ \hat{p}\\&=g^{\star}_1\circ j_{\mathcal{G}, 1}\circ \hat{e}\\&=j_{\mathcal{H},1}\circ g_1\circ \hat{e}\\&=j_{\mathcal{H},1}\circ \tau_{\mathcal{H}}\circ b_2\circ w_1\\&=t_{\mathcal{H}}\circ b_2\circ w_1
-\end{split}\]
-
-Since $t_{\mathcal{K}}$ and $t_\mathcal{H}$ are mono we get the two dotted arrow $s\colon U_2\to I_1$ and $\hat{s}\colon W_1\to I_1$ depicted below.
-\[\xymatrix{U_2 \ar@/^.4cm/[drr]^{u_2}  \ar[d]_{p}\ar@{.>}[dr]_{s} & &&W_1 \ar@/^.4cm/[drr]^{w_1}  \ar[d]_{\hat{p}}\ar@{.>}[dr]_{\hat{s}}\\ I_{\mathcal{H}, g_1} \ar[dr]_{t_{g_1}}& I_1 \ar[r]^{v_1} \ar[d]_{a_1} & X_1 \ar[d]^{b_1} & I_{\mathcal{H}, g_1} \ar[dr]_{t_{g_1}}& I_1 \ar@{>->}[r]^{v_2} \ar[d]_{a_1} & X_2 \ar[d]^{b_2}\\ & E_{\mathcal{G}} \ar[r]_{f_2} & E_{\mathcal{K}}& & E_{\mathcal{G}} \ar@{>->}[r]_{f_1} & E_{\mathcal{H}}}\]
-
- We can now split the remainder of proof in four steps.
-
-\smallskip \noindent 
-$	h_2\circ x_1\circ u_1=h_1\circ x_1\circ u_1$. Let us begin noticing that
-	\begin{align*}
-		k^\star_{V} \circ t_{\mathcal{K}} \circ b_1 \circ u_1& = t_{\mathcal{P}}\circ k_E \circ b_1 \circ u_1\\&=t_{\mathcal{P}}\circ h_1\circ x_1 \circ u_1\\&=t_{\mathcal{P}}\circ h_2\circ x_1 \circ u_1\\&=t_{\mathcal{P}}\circ k_E\circ c_1\\&=k^\star_V\circ t_{\mathcal{K}} \circ c_1
-	\end{align*}
-	Thus, since $k^\star_{V}\circ t_{\mathcal{{K}}}$ is mono we have that $b_1\circ u_1 = c_1$, but then we have
-	\begin{align*}
-		h_2\circ x_1\circ u_1&=k_E\circ c_1\\&= k_E\circ b_1\circ u_1\\&=h_1\circ x_1\circ u_1
-	\end{align*}
-
-\smallskip \noindent  $	h_2\circ x_1\circ u_2=h_1\circ x_1\circ u_2$. We are going to use again \Cref{prop:image} to get.
-	\begin{align*}
-		h_2\circ x_1\circ u_2&=h_E\circ c_2\\&=h_E\circ w^{\mathcal{G}}_1\circ p\\&=h_E\circ f_1\circ t_{g_1}\circ p\\&=h_E\circ f_1\circ a_1\circ s\\&=h_E\circ b_2\circ v_2\circ s\\&=h_1\circ x_2\circ v_2\circ s\\&=h_1\circ x_1\circ v_1\circ s\\&=	h_1\circ x_1\circ u_2
-	\end{align*}
-
-	\medskip Summing up the previous two points, we get that $h_1\circ x_1=h_2\circ x_1$. Let us prove that $h_1\circ x_2=h_2\circ x_2$ too.
-
-	\smallskip \noindent $h_1\circ x_2\circ w_1=h_2\circ x_2\circ w_1$. Since we already know that $h_1\circ x_1=h_2\circ x_1$, it is now enough to do the following computation.
-	\begin{align*}
-		h_2\circ x_2\circ w_1&=h_2\circ x_2\circ v_2\circ \hat{s}\\&=h_2\circ x_1\circ v_1\circ \hat{s}\\&=h_1\circ x_1\circ v_1\circ \hat{s}\\&=h_1\circ x_2\circ v_2\\&=h_E\circ b_2\circ v_2\\&=h_E\circ f_1\circ a_1\\&=h_E\circ f_1\circ t_{g,1}\circ \hat{p}\\&=h_E\circ w^{\mathcal{{G}}}_1\circ \hat{p}\\&=h_E\circ b_2\circ w_1\\&=h_1\circ x_2\circ w_1
-	\end{align*}
-
-	\smallskip \noindent $h_1\circ x_2\circ w_2=h_2\circ x_2\circ w_2$.
-
-	$h_1=h_E(h'_1)$ and $h_2=h_E(h'_2)$ for some $h'_1$ and $h'_2\in E_{\mathcal{H}}$. Let $x_1$ and $x_2$ be the unique elements of $V_{\mathcal{H}}$ such that
-	\[\delta_{x_1}=t_{\mathcal{H}}(h'_1) \qquad \delta_{x_2}=t_{\mathcal{H}}(h'_2)\]
-	Then it must be that
-	\begin{align*}\delta_{h_V(x_1)}&=h_V\circ \delta_{x_1}\\&=h^\star_V(\delta_{x_1})\\&=h^\star_V(t_{\mathcal{H}}(h'_1))\\&=t_{\mathcal{P}}(h_1)\\&=t_{\mathcal{P}}(h_2)\\&=h^\star_V(t_{\mathcal{H}}(h'_2))\\&=h^\star_V(\delta_{x_2})\\&=h_V\circ \delta_{x_2}\\&=\delta_{h_V(x_2)}
-	\end{align*}
-	showing that $h_V(x_1)=h_V(x_2)$.
-By the second point of \Cref{lem:push2}  we know that at least one between $x_1$ or $x_2$ must belong to $g_1(V_{\mathcal{G}})$.
-Without loss of generality we can suppose that it is $x_1$ (otherwise just swap it with $x_2$).
-Using \Cref{prop:image,lem:reg} we know that $h'_1$ is in the image of $f_1$, i.e.~that there exists $e\in E_\mathcal{\mathcal{G}}$ such that $h'_1=f_1(e)$, but then
-	\begin{align*}
-		k_E(f_2(e))&=h_E(f_1(e))\\&=h_E(h'_1)\\&=h_1
-	\end{align*} 
-	so we fall back to the third case and we can conclude.
-
-This concludes the proof.
-\end{proof}
-
 \Cref{cor:varie3,lem:reg,prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{corradini2005term}.
@@
 \end{corollary}
+
+\subsection{Hierarchical hypergraphs}
+
+\todo{da fare? lasciare per una versione estesa?}
 
@@
 
-\section{Some notes on free monoids}\label{app:mon}
-
-In this appendix we will provide a brief exposition to the problem of constructing the \emph{free internal monoid} in a monoidal category $(\X, \otimes, I )$.
-This  construction is needed in \Cref{sec:hyper} to provide a concrete representation to hypergraphs.
-The standard references on the subject are \cite{dubuc1974free,kelly1980unified,lack2010note}
-
-\begin{definition}
-	Let $(\X, \otimes, I)$ be a monoidal category.
-An \emph{monoid} is a triple $(X, m, e)$ made by an object $X$ equipped with arrows $m\colon X\otimes X\to X$ and $e\colon I\to X$ making the following diagrams commute, where $\alpha$ is the associator and $\lambda$ and $\rho$ the two unitors.
-
-	\[\xymatrix@C=35pt{(X\otimes X) \ar[r]^{\alpha_{X, X, X}} \ar[dd]_{m\otimes \id{X}}\otimes X & X\otimes (X\otimes X) \ar[d]^{\id{X}\otimes m} & X \ar[r]^{\rho^{-1}_X}  \ar[d]_{\lambda^{-1}_X} \ar[ddr]_{\id{X}}& X\otimes I \ar[d]^{\id{X}\otimes e}\\& X\otimes X \ar[d]^{m}  & I\otimes X \ar[d]_{e\otimes \id{X}} & X\otimes X \ar[d]^{m} \\X\otimes X  \ar[r]_{m}& X & X\otimes X \ar[r]_{m} & X}\]
-
-	A \emph{morphism of monoids} between $(X, m, e)$ and $(X', m', e')$ is an arrow $f\colon X\to X'$ fitting in the diagrams below.
-
-	\[\xymatrix{X\otimes X \ar[r]^{f\otimes f} \ar[d]_{m}& Y\otimes Y \ar[d]^{m'} && I\ar[dr]^{e'} \ar[dl]_{e}\\ X\ar[r]_{f} & Y & X \ar[rr]_{f} && Y }\]
-Monoids with their morphisms form a category $\mono{X}$, such category has an obvious forgetful functor $\mo{U}\colon\mono{X}\to X$ sending $(X, m, e)$ to $X$ and a morphism to itself.
-
-If the functor $\mo{U}$ has a left adjoint $\mo{F}\colon \X\to \mono{\X}$, we will define the \emph{Kleene star} functor $(-)^\star\colon \X \to \X$ as $\mo{U}\circ \mo{F}$.
-\end{definition}
-
-We are interested in provide sufficient conditions to guarantee the existence of a left adjoint to $\mo{U}$.
-The idea is to mimic the construction of the usual functor $\Set\to \Set$ \cite{sakarovitch2009elements} sending $X$ to the set of finite words over it.
-
-\begin{definition}
-	Let $(\X, \otimes, I )$ be  a monoidal category with countable coproduct.
-We say that $(\X, \otimes.
-I)$ is \emph{countably distributive} if, given a countable family $\{X_i\}_{i}$ and an object $Y$, the unique dotted morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms.
-	\[\xymatrix{&Y\otimes X_i \ar[dl]_{j_i} \ar[dr]^{\id{Y}\otimes h_i} \\ \Sum_{i\in I} Y\otimes X_i \ar@{.>}[rr]_{\phi}&& Y\otimes (\Sum_{i\in I}X_i) }\]
-	\[\xymatrix{&X_i \otimes Y \ar[dl]_{k_i} \ar[dr]^{ h_i \otimes \id{Y}} \\ \Sum_{i\in I}  X_i \otimes Y \ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \otimes Y}\]
-\end{definition}
-
-\begin{remark}\label{rem:salv}
-	There is a property of countably distributive categories which is worth to be pointed out.
-Let $\{X_i\}_{i\in I}$ and $\{Y_j\}_{j\in J}$ be two countable family of objects, then for every $i\in I$ there is an isomorphism $\phi_{i}\colon \sum_{j\in J}X_i\times Y_j\to X_i\times \sum_{j\in J} Y_j$ fitting in the following triangle, where $\alpha^j_j$ and $y_j$ are coprojections.
-	\[\xymatrix{& X_i\otimes Y_j \ar[dl]_{\alpha^i_j} \ar[dr]^{\id{X_i}\otimes y_j} \\ \Sum_{j\in J} X_i\otimes Y_j \ar[rr]_{\phi_i}&& X_i\otimes (\Sum_{j\in J}Y_j) }\]
-
-	Moreover, we also have an isomorphism $\psi\colon \sum_{i\in I}(X_i\otimes \sum_{j\in J}Y_j)\to (\sum_{i\in I}X_i) \otimes (\sum_{j\in J} Y_j)$ as in the triangle below, where, again, $\beta_i$ and $x_i$ are coprojections.
-	\[\xymatrix{&X_i \otimes \Sum_{j\in J}Y_j \ar[dl]_{\beta_i} \ar[dr]^{ x_i \otimes \sum_{j\in J} \id{Y_j}} \\ \Sum_{i\in I} ( X_i \otimes \Sum_{j\in J}Y_j) \ar[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \otimes (\Sum_{j\in J}Y_j)}\]
-
-		Now, since coproducts commute with coproducts, in every category there is a third isomorphism $\theta \colon \sum_{(i,j)\times I\times J}(X_i\otimes Y_j) \to \sum_{i\in I}\sum_{j\in J}(X_i\otimes Y_j)$ making the following diagram commutative, in which all arrows besides $\theta$ are coprojections.
-		\[\xymatrix{\Sum_{(i,j)\times I\times J}(X_i\otimes Y_j)  \ar[r]^-{\theta}& \Sum_{i\in I}\Sum_{j\in J}(X_i\otimes Y_j) \\ X_i\otimes Y_j  \ar[r]_{\alpha^i_j} \ar[u]^-{\delta_{i,j}}& \Sum_{j\in J}(X_i\otimes J) \ar[u]_-{\gamma_i}}\]
-
-		Putting all these morphisms together, we get the following diagram.
-	\[\xymatrix@C=38pt{\Sum_{(i,j)\in I\times J} (X_i\otimes Y_j) \ar[d]_{\theta}\\ \Sum_{i\in I} \Sum_{j\in J} (X_i\otimes Y_j) \ar[r]^-{\sum_{i\in I}\phi_i}& \Sum_{i\in I}(X_i\otimes \Sum_{j\in J} Y_j) \ar[dr]^-{\psi} \\ \Sum_{j\in J}  (X_i\otimes Y_j) \ar[r]^{\phi_i} \ar[u]^-{\gamma_{i}} & X_i\otimes \Sum_{j\in J} Y_j \ar[u]^-{\beta_i}\ar[r]^-{x_i\otimes \sum_{j\in J}\id{Y_j}}&  (\Sum_{i\in I}X_i) \otimes (\Sum_{j\in J}Y_j)\\X_i\otimes Y_j \ar@/^1.7cm/[uuu]^-{\delta_{i,j}} \ar[u]^{\alpha^i_j} \ar[ur]_{\hspace{3pt}\id{X_i}\otimes y_j} \ar@/_1cm/[urr]_{x_i\otimes y_j}}\]
-
-Summing up, we have just proved that $((\sum_{i\in I}X_i) \otimes (\sum_{j\in J} Y_j), \{x_{i}\otimes y_j\}_{I\times J})$
- is a coproduct for the family $\{x_i\otimes y_j\}_{(i,j)\in I\times J}$.
-\end{remark}
-
-We cite the following, fundamental, result proved in \cite{lack2010note}.
-
-\begin{theorem}
-	Let $(\X, \otimes, I )$ be a countably distributive monoidal category. Then $\mo{U}\colon \mono{X}\to \X$ has a left adjoint  $\mo{F}\colon \X\to \mono{X}$ defined as
-\[	\functor[l]{X}{f}{Y}
-\functormapsto
-\rfunctor{\sum_{i\in \mathbb{N}} X^{\otimes n}}{\sum_{i\in \mathbb{N}} f^{\otimes n}}{\sum_{i\in \mathbb{N}} Y^{\otimes n}}\]
-\end{theorem}
-
-\begin{remark}\label{rem:lg} Let $\X$ be a category with finite limits and suppose that $(\X, \times, 1)$ is countably distributive.
-Then for every object $X$ in $\X$ we have a \emph{length homomorphism} $\lgh_X\colon \mo{F}(X)\to \mo{F}(1)$.
-The underlying morphism $X^\star \to 1^\star$ in $\X$ is simply $\sum_{n\in \mathbb{N}} (!_X)^{\otimes n}$.
-Notice, moreover, that for every $f\colon X\to Y$ we have a commutative triangle as the one below.
-	\[\xymatrix{X^\star \ar[rr]^{f^\star} \ar[dr]_{\lgh_X}&& Y^\star  \ar[dl]^{\lgh_Y}\\ & 1^\star }\]
-\end{remark}
-
-As a concluding step, we ask for a compatibility property between countable coproducts and pullbacks, to assure that $\mo{F}$ preserves pullbacks (see also \cite[Sec.
-3]{carboni1995connected}  and \cite[Ch.4]{leinster2004higher} for details and a deeper and more conceptual approach in the case of $\Set$).
-
-\begin{definition}
-	Let $\X$ be a category, we say that $\X$ is \emph{countably extensive} if:
-	\begin{enumerate}
-		\item  for every coprojections $j_i \colon X_i\to \sum_{i\in I}^{X_i} $ in a countaple coproduct and arrow $f\colon Y\to \sum_{i\in I} X_i$, a pullback of $j_i$ along $f$ exists; 
-		\item given a countable set $I$, a coproduct $(X, \{j_i\}_{i\in I})$, an arrow $f\colon Z\to X$ and a family of squares
-		\[\xymatrix{Z_i \ar[r]^{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar[r]_{j_i} & X}\]
-		then the above squares are all pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.
-	\end{enumerate} 
-\end{definition}
-
-\begin{remark}\label{rem:pb}
-Suppose that  $(\X, \times, 1)$ is a countably distributive monoidal category, with $\X$ countably extensive. Then the following squares are pullbacks for every $n\in \mathbb{N}$ and object $X$.
-\[\xymatrix{X^{n} \ar[r]^-{j_n} \ar[d]_{!_{X^n}}& X^\star \ar[d]^{\lgh_X} & Y^{n} \ar[r]^-{k_n} \ar[d]_{!_{Y^n}}& Y^\star \ar[d]^{\lgh_Y}\\ 1 \ar[r]_{o_n}&  1^\star & 1 \ar[r]_{o_n}&  1^\star}\]
-\end{remark}
-
-An elementary, but quite important property of countably extensive category is the following.
-
-\begin{proposition}\label{prop:inj}
-Let $\X$ be a countably extensive category, then countable coproducts are disjoints and have monos as coprojections. 
-\end{proposition}
-\begin{proof}
-Let $(X, \{j_i\}_{i\in I})$ be a coproduct for some countable set $I$. For every $i\in I$, consider the family ${k_{i, h}}_{h\in I}$ defined as
-\[k_{i, h}:=\begin{cases}
-	?_{X_{i}} & h\neq i\\
-	\id{X_i} &h=i
-\end{cases}\]
-It is immediate to notice that $(X_{i}, \{k_{i,h}\}_{h\in I})$ is a countable coproduct. Thus the squares below, where $h\neq i$, are all pullbacks.
-	\[\xymatrix{0 \ar[r]^{?_{X_h}} \ar[d]_{?_{X_h}}& X_h \ar[d]^{j_h} & X_i \ar[r]^{\id{X_i}} \ar[d]_{\id{X_i}}& X_i \ar[d]^{j_i}\\ X_i \ar[r]_{j_i} & X & X_i \ar[r]_{j_i} & X}\]
-	The thesis now follows at once.
-\end{proof}
-
-We are now ready to provide the claimed continuity property of $\mo{F}$.
-
-\begin{proposition}
-	Let $\X$ be a category with finite limits such that the cartesian structure $(\X, \times, 1)$ is countably distributive.
-Suppose, moreover, that countable  coproducts in $\X$ are stable under pullbacks.
-Then the Kleene star $(-)^\star \colon \X\to \X$ preserves pullbacks.
-\end{proposition}
-\begin{proof}
- Suppose that the solid part of the diagram below is given, where  the inner square is the image of a pullback through $(-)^\star$.
-
- \[\xymatrix{T \ar@/^.4cm/[drr]^{t_1} \ar@/_.4cm/[ddr]_{t_2} \ar@{.>}[dr]^t\\ & P^\star  \ar[d]_{q^\star}\ar[r]^{p^\star}& X^\star \ar[d]^{f^\star} \\ & Y^\star\ar[r]_{g^\star} & Z^\star}\]
-
-	For every $n\in \mathbb{N}$, consider the coprojection $k_n\circ Z^n\to Z^\star$ and let $T_n$ be the pullback below.
-	\[\xymatrix{T_n \ar[r]^{p_n} \ar[d]_{q_n} & T  \ar[d]^{f^\star \circ t_1}\\
-	Z^n \ar[r]_{k_n}& Z^\star}\]
-
-	Notice that, by \Cref{rem:lg} and since $f^\star \circ t_1$ is equal to $g^\star \circ t_2$, we have
-	\[
-	\begin{split}
-		\lgh_X\circ t_1 \circ p_n&=\lgh_Z\circ f^\star \circ t_1\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=o_n\circ !_{Z^n}\circ q_n\\&=o_n\circ !_{T_n}
-	\end{split}\qquad \begin{split}
-		\lgh_Y\circ t_2 \circ p_n&=\lgh_Z\circ g^\star \circ t_2\circ p_n\\&=\lgh_Z\circ k_n\circ q_n\\&=o_n\circ !_{Z^n}\circ q_n\\&=o_n\circ !_{T_n}
-	\end{split}\]
-
-	Thus in the diagram below the solid part commutes, yielding the dotted $x_n\colon T_n\to X^n$ and $y_n\colon T_n\to Y^n$.
-
-	\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{x_n} \ar[r]^{p_n} & T \ar[dr]^{t_1}&& T_n \ar@/_.3cm/[ddr]_{!_{T_n}} \ar[r]^{p_n} \ar@{.>}[dr]^{y_n}& T \ar[dr]^{t_2}\\ &X^n   \ar[d]_{!_{X^n}}\ar[r]^{j_n}& X^\star \ar[d]^{\lgh_X}& & Y^n \ar[d]_{!_{Y^n}}  \ar[r]^{h_n}& Y^\star \ar[d]^{\lgh_Y}\\ & 1 \ar[r]_{o_n}& 1^\star && 1  \ar[r]_{o_n}& 1^\star}\]
-
-	Now, limits commutes with limits, and, moreover, we have
-	\begin{align*}	
-	k_n\circ f^n\circ x_n & =f^\star \circ j_n\circ x^n\\&=f^\star \circ t_1\circ p_n\\&=g^\star \circ t_2\circ p_n\\&=g^\star \circ h_n\circ y_n\\&=k_n \circ g^n\circ y_n 
-	\end{align*}
-	so, by \Cref{prop:inj}, the solid part of the diagram below commutes an the inner square is a pullback, therefore we obtain the dotted arrow $b_n\colon T_n\to P^n $.
-	\[\xymatrix{T_n \ar@{.>}[dr]^{b_n}  \ar@/^.4cm/[drr]^{x_n} \ar@/_.4cm/[ddr]_{y_n} \\ & P^n \ar[d]_{q^n} \ar[r]^{p^n}& X^n \ar[d]^{f^n}\\ &  Y^n  \ar[r]_{g^n}& Z^n}\]
-
-	Since $\X$ is countably extensive, then $(T, \{p_n\}_{n\in \mathbb{N}})$ is a coproduct for the family $\{T_n\}_{n\in \mathbb{N}}$ and so we can define the arrow $t\colon T\to P^\star$ as $\sum_{n\in \mathbb{N}} b_n$
-
-	Let $v_n\colon P^n\to P^\star$ be te coprojection, to see that $t$ fits in the initial diagram it is now enough to compute.
-	\[\begin{split}
-		p^\star \circ t \circ p_n&= \sum_{i\in \mathbb{N}} p^i \circ \sum_{i\in \mathbb{N}} b_i\circ p_n\\&
-		=\sum_{i\in I}p_i\circ v_n\circ b_n\\&= j_n\circ p_n\circ v_n\\&=j_n\circ x_n\\&=t_1\circ p_n
- 	\end{split} \qquad \begin{split}
- 	q^\star \circ t \circ p_n&= \sum_{i\in \mathbb{N}} q^i \circ \sum_{i\in \mathbb{N}} b_i\circ p_n\\&
- 	=\sum_{i\in I}q_i\circ v_n\circ b_n\\&= h_n\circ p_n\circ v_n\\&=j_n\circ x_n\\&=t_2\circ p_n
- 	\end{split}\]
- 	so that $p^\star \circ t = t_1$ and $q^\star\circ t = t_2$.
-
-We are left with uniqueness. Let $t'\colon T\to P^\star$ be another arrow such that $p^\star \circ t' = t_1$ and $q^\star\circ t' = t_2$, then
-\begin{align*}
-\lgh_P\circ t' \circ p_n&=\lgh_X\circ p^\star \circ t'\circ p_n\\&=\lgh_X\circ t_1\circ p_n\\&=o_n\circ !_{T_n}
-\end{align*}
-
-So that, for every natural $n$, there exists an arrow $u_n\colon T_n \to X^n$ fitting in the diagram below.
-\[\xymatrix{T_n  \ar@/_.3cm/[ddr]_{!_{T_n}}\ar@{.>}[dr]^{u_n} \ar[r]^{p_n} & T \ar[dr]^{t'}\\ &P^n   \ar[d]_{!_{P^n}}\ar[r]^{v_n}& P^\star \ar[d]^{\lgh_P}\\ & 1 \ar[r]_{o_n}& 1^\star }\]
-Moreover, we have
-\[\begin{split}
-j_n\circ	p^n\circ u_n&=p^\star \circ  v_n\circ u_n\\&=p^\star \circ t'\circ p_n\\&=t_1\circ p_n\\&=j_n\circ x_n\\&=j_n\circ p^n\circ b_n
-\end{split}\qquad \begin{split}
-h_n\circ	q^n\circ u_n&=q^\star \circ  v_n\circ u_n\\&=q^\star \circ t'\circ p_n\\&=t_2\circ p_n\\&=h_n\circ y_n\\&=h_n\circ q^n\circ b_n
-\end{split}\]
-
-By \Cref{prop:inj} the previous equalities entails
-\[p^n\circ u_n=p^n\circ b_n \qquad q^n\circ u_n=q^n\circ b_n\]
-so that $u_n=b_n$ and we can conclude.
-\end{proof}
-
 \section{Comparison with Ghica}

### 2025-02-10 calco/main.tex
cose

@@
 \newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
-\usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont} %simboli matematici
+\usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
+\usepackage{hyperref, cleveref} %simboli matematici
 \usepackage[all, cmtip]{xy}
@@
 
-\usepackage{hyperref, cleveref}
 \usepackage{tikz-cd}
@@
 Finally, another  useful properties of $\mathcal{M}$-adhesive category are the following.
-\begin{proposition}\label{prop:regmono}
+\begin{proposition}\label[proposition]{prop:regmono}
 	If $\X$ is $\mathcal{M}$-adhesive then the following are true:
@@
 
-\begin{example}\label{ex:kernel_pairs_in_Set}
+\begin{example}\label[example]{ex:kernel_pairs_in_Set}
     In $\Set$, a kernel pair for a function $f: A\to B$ is the set
@@
 
-\begin{proposition}\label{prop:pairng_of_kernel_pairs_mono}
+\begin{proposition}\label[proposition]{prop:pairng_of_kernel_pairs_mono}
     Let $(K, p_1, p_2)$ be the kernel pair of $f: X \to Y$, and let $(X\times X, \pi_1, \pi_2)$ be the product of $X$ with itself.
@@
 
-\begin{proposition}\label{prop:kermono}
+\begin{proposition}\label[proposition]{prop:kermono}
 	An arrow $m\colon M\to X$ is mono if and only if $(M, MM, \id{M})$ is a kernel pair for it.
@@
 
-\begin{corollary}\label{cor:kermono}
+\begin{corollary}\label[corollary]{cor:kermono}
 	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$ if and only if, for each mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
@@
 
-\begin{lemma}\label{lemma:kern_pairs_pres_pullbacks}
+\begin{lemma}\label[lemma]{lemma:kern_pairs_pres_pullbacks}
     Suppose the following situation, and that $f: X \to Y$ and $g: Z \to W$ have kernel pairs.
@@
 
-\begin{proposition}\label{prop:reg_epi_coeq}
+\begin{proposition}\label[proposition]{prop:reg_epi_coeq}
     Let $e: X \to Y$ be a regular epimorphism in a category $\cat C$ with a kernel pair $(K, \pi_1, \pi_2)$. Then, $e$ is the coequalizer of $\pi_1$ and $\pi_2$.
@@
 
-\begin{corollary}\label{cor:reg_epi_components_reg_epi_nat_trans}
+\begin{corollary}\label[corollary]{cor:reg_epi_components_reg_epi_nat_trans}
     Let $\cat C$ be a category with pullbacks and $\phi : D \dot\to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
@@
 
-\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
+\begin{lemma}\label[lemma]{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
     Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
@@
 
+\begin{remark}\label[remark]{rem:length}Notice that, $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$, the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $!^\star_X\colon X^\star \to \mathbb{N}$ which simply sends a word length.
+\end{remark}
+
 \subsection{The category of hypergraphs}
@@
 Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$, then we can present $\hyp$ as a comma category.
-\begin{proposition}\label{prop:com}
+\begin{proposition}\label[proposition]{prop:com}
 	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
 \end{proposition}
-\begin{proof}
-	 Define two functors $F\colon  \hyp \to \comma{\id{\Set}}{\pro^\star} $
-	and $G\colon \comma{\id{\Set}}{\pro^\star}\to \hyp$	 as follows 
-	\begin{align*}
-		\functor[l]{(E_\mathcal{{G}}, V_\mathcal{{G}}, s_\mathcal{{G}}, t_\mathcal{{G}})}{(f,g)}{\left(E_\mathcal{{H}}, V_\mathcal{{H}}, s_\mathcal{{H}}, t_\mathcal{{H}}\right)}
-		\functormapsto
-		\rfunctor{\left(E_\mathcal{{G}}, V_\mathcal{{G}}, 	\left(s_\mathcal{{G}}, t_\mathcal{{G}}\right)\right)}{(f, g) }{\left(E_\mathcal{{H}}, V_\mathcal{{H}}, \left(s_\mathcal{{H}}, t_\mathcal{{H}}\right)\right)}
-	\end{align*}
-	 \begin{align*}
-		\functor[l]{(E_\mathcal{{G}}, V_\mathcal{{G}}, p_{\mathcal{G}})}{(f,g)}{(E_\mathcal{{H}}, V_\mathcal{{H}}, p_{\mathcal{H}})}
-		\functormapsto
-		\rfunctor{(E_\mathcal{{G}}, V_\mathcal{{G}}, 	\pi_1\circ  p_{\mathcal{G}}, \pi_2\circ  p_{\mathcal{G}})}{(f, g) }{(E_\mathcal{{H}}, V_\mathcal{{H}}, 	\pi_1\circ  p_{\mathcal{H}}, \pi_2\circ  p_{\mathcal{H}})}
-	\end{align*} 
-	Now it is immediate to notice that they are one the inverse of the other.   
-\end{proof}
-
-\begin{corollary}\label{prop:hypadh}
+
+\begin{corollary}\label[corollary]{prop:hypadh}
 	 $\hyp$ is an adhesive category.
@@
 
-\begin{corollary}\label{cor:monhyper}
+\begin{corollary}\label[corollary]{cor:monhyper}
 A morphism $(h,k)$ is a mono in $\hyp$ if and only if both its components are injective functions.
@@
 
-\begin{proposition}\label{cor:left}  The forgetful functor $U_{\X}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\X}$.
+\begin{proposition}\label[proposition]{cor:left}  The forgetful functor $U_{\hyp}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\hyp}$.
 \end{proposition}
@@
 \end{example}
-\begin{example}\label{exa_2} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
+\begin{example}\label[example]{exa_2} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
 	\[\begin{matrix}
@@
 
-Following \cite{bonchi2022string}, we can present $\hyp_\X$ as a category of functor over a suitable category.
+Following \cite{bonchi2022string}, we can present $\hyp$ as a category of functor over a suitable category.
 
@@
 
-Given $F\colon \catname{H}\to \catname{Set}$ we can define
+The idea now is that for every functor $F\colon \catname{H}\to \catname{Set}$ we can define
 \[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
@@
 Let $\mathcal{G}_F$ be the resulting hypergraph.
-Now, every $\eta\colon F\rightarrow H$ in $\catname{Set}^{\catname{H}}$ has components $\eta_{k,l}\colon F(k,l)\to H(k,l)$, $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$.
-In particular we can define $\hat{\eta}\colon E_F\rightarrow E_H$ as $\sum_{k,l\in \mathbb{N}}\eta_{k,l}$.
-Now, on the one hand, we have
-\[\begin{split}
-	\pi^H_i\circ \eta^k_\bullet \circ  s^F_{k,l}&=\eta_\bullet \circ \pi^F_i \circ s^F_{k,l}\\&=\eta_\bullet \circ F(f_i)\\&=H(f_i)\circ \eta_{k,l}\\&=\pi^H_{k,i}\circ s^{H}_{k,l}\circ \eta_{k,l}
-\end{split} \qquad \begin{split}
-\pi^H_j\circ \eta^k_\bullet \circ  t^F_{k,l}&=\eta_\bullet \circ \pi^F_j \circ t^F_{k,l}\\&=\eta_\bullet \circ F(f_{k+j})\\&=H(f_{k+j})\circ \eta_{k,l}\\&=\pi^H_{l,j}\circ t^{H}_{k,l}\circ \eta_{k,l}
-\end{split} \]
-so that $\eta^k_\bullet \circ  s^F_{k,l}=s^{H}_{k,l}\circ \eta_{k,l}$ and $\eta^k_\bullet \circ  t^F_{k,l}= t^{H}_{k,l}\circ \eta_{k,l}$. On the other hand, these equalities give us the following:
-\[\begin{split}
-	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ s^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ s^{F}_{k,l} \\&=b^H_{k}\circ s^H_{k,l}\circ \eta_{k,l}\\&=s_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	s_H\circ \hat{\eta}\circ a^F_{k,l}
-\end{split} \qquad \begin{split}
-	\eta_{\bullet}^\star \circ s_{F}\circ a^F_{k,l}&=\eta_{\bullet}^\star \circ b^F_k\circ t^F_{k,l}\\&=b^H_k\circ \eta^k_{\bullet}\circ t^{F}_{k,l} \\&=b^H_{k}\circ t^H_{k,l}\circ \eta_{k,l}\\&=t_H\circ a^H_{k,l}\circ \eta_{k,l}\\&=	t_H\circ \hat{\eta}\circ a^F_{k,l}
-\end{split}\]
-which, in turn, entail that  that the following squares commute
-\[\xymatrix{E_F \ar[r]^{s_F} \ar@{.>}[d]_{\hat{\eta}}& F(\bullet)^\star \ar[d]^{\eta^\star_\bullet} & E_F \ar[r]^{t_F} \ar[d]_{\hat{\eta}} & F(\bullet)^\star \ar[d]^{\eta^\star_\bullet}\\ E_H \ar[r]_{s_H} & H(\bullet)^\star & E_H \ar[r]_{t_H}& H(\bullet)^\star}\]
-
-This is the same as saying that $\eta$ induces a morphism $(\hat{\eta}, \eta_{\bullet})\colon \mathcal{G}_F\to \mathcal{G}_H$.
-It is now clear that sending $F$ to $\mathcal{G}_F$ and $\eta$ to $(\hat{\eta}, \eta_{\bullet})$ defines a faithful functor $\mathcal{G}_{-}\colon \Set^{\catname{H}}\to \hyp$.
-
-It is now a a straightforward exercise to see that this functor it is actually an equivalence (see \cite{castelnovo2023thesis} for details), yielding the following result.
-
-	\iffalse 
-\begin{remark}\label{rem:utile}
-Now, notice that in $\Set$ countable coproducts distributes over pullbacks, \Cref{rem:salv} we know that countably distributivity entails that, for every $k,l\in \mathbb{N}$, the arrow $b^F_k\times b^F_l$ is a coprojection, thus extensivity entails that the square is a pullback
-	\[\xymatrix@C=30pt{F(k,l) \ar[d]_{(s^F_{k,l}, t^F_{k,l})}  \ar[r]^{a^F_{k,l}}& E_F \ar[d]^{(s_F, t_F)} \\ F(\bullet)^k\times F(\bullet)^l \ar[r]_{b^F_k\times b^F_l} & F(\bullet)^\star\times F(\bullet)^\star}\]
-
-	As in \Cref{rem:pb}, countably extensivity of $X$ guarantees that, for every $k\in \mathbb{N}$ following square is a pullback.	
-	\[\xymatrix{F(\bullet)^k  \ar[r]^{b^F_k} \ar[d]_{!_{F(\bullet)^k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ 1 \ar[r]_{o_k} & 1^\star}\]
-
-	Now, notice that 
-	\[\begin{split}
-		\lgh_{F(\bullet)}\circ b^{F}_k\circ s^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ s^F_{k,l}\\&=o_k\circ !_{F(k,l)}
-	\end{split} \qquad \begin{split}
-	\lgh_{F(\bullet)}\circ b^{F}_k\circ t^{F}_{k,l}&=o_{k}\circ !_{F(\bullet)^k}\circ t^F_{k,l}\\&=o_k\circ !_{F(k,l)}
-	\end{split}\]
-so that we have two diagrams:
-	\[\xymatrix{F(k,l)\ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^1_{k,l}}  \ar@/_.5cm/[ddr]_{!_{F(k,l)}}&F(\bullet)^k \ar[dr]^{b^F_k}&& F(k,l) \ar@/_.5cm/[ddr]_{!_{F(k,l)}} \ar[r]^{s^F_{k,l}} \ar@{.>}[dr]^{u^2_{k,l}} &F(\bullet)^k \ar[dr]^{b^F_k}\\ & F(\bullet)_k  \ar[r]^{q_{k}} \ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} && F(\bullet)_k  \ar[r]^{q_{k} }\ar[d]_{!_{F(\bullet)_k}}& F(\bullet)^\star \ar[d]^{\lgh_{F(\bullet)}} \\ &  1 \ar[r]_{o_k} & 1^\star && 1 \ar[r]_{o_k} & 1^\star}\]
-
-	Moreover we have
-	\[\begin{split}
-		s_F\circ a^F_{k,l}&=b^F_k\circ s^{F}_{k,l}\\&=
-		q_{k}\circ u^1_{k,l}	\end{split} \qquad \begin{split}
-		t_F\circ a^F_{k,l}&=b^F_k\circ t^{F}_{k,l}\\&=
-		q_{k}\circ u^2_{k,l}	\end{split}  \]
-
-	Therefore these two arrows, in turn, yield the dotted $v^1_{k,l}\colon F(k,l)\to F(\bullet)_k $ and $v^2_{k,l}\colon F(k,l)\to F(\bullet)_l$ as in the diagram below, where the right and bottom squares are pullbacks.
-	\[\xymatrix@C=45pt{F(k,l)  \ar[dr]^{a^F_{k,l}} \ar@{.>}[r]^{v^2_{k,l}} \ar@{.>}[d]^{v^1_{k,l}} \ar@/^.8cm/[rr]^{u^2_{k,l}} \ar@/_.5cm/[dd]_{u^1_{k,l}}& P_{l} \ar[r]_{p_{l,1}} \ar[d]_{p_{l,2}}& F(\bullet)_{l} \ar[d]^{q_{l}}\\ P_k \ar[r]^{p_{k,2}} \ar[d]^{p_{k,1}}& E_F \ar[r]_{s_F}  \ar[d]^{t_F}& F(\bullet)^\star \\ F(\bullet)_k  \ar[r]_{q_{k}}& F(\bullet)^\star}\]
-
- By hypothesis, $\X$ is countably extensive, thus for every $k, l\in \mathbb{N}$, the following diagrams are pullbacks.
- \[\xymatrix{F(k,l) \ar[r]^{a^F_{k,l}} & E_F \ar[d]^{}\\ 
- F(\bullet)^k& F(\bullet)^\star}\]
-
- Let now $d_1\colon Z\to P_l$ and $d_2\colon Z\to P_k $ be two arrows such that
- \[p_{k,2}\circ d_2=p_{t,2}\circ d_1\]
-
- Then we have
- \begin{align*}
- t_{F}\circ 	p_{t_2}\circ d_1&= \end{align*}
-
- Showing, finally, that
-
-\end{remark}
-\fi
+One can now show that  sending $F$ to $\mathcal{G}_F$ can be extended to an equivalence $\mathcal{G}_{-}\colon \Set^{\catname{H}}\to \hyp$ (see \cite{castelnovo2023thesis, castelnovo2022newcriterionmathcalmmathcalnadhesivity} for details).
 
 \begin{proposition}
-	$\hyp_\X$ is equivalent to the category $\catname{\X}^{\catname{H}}$.
-\end{proposition}
-
-\iffalse 
-\begin{proof}	
-We already know that $\mathcal{G}_{-}$ is faithful, we still have to show that it is full and essentially surjective.
-	\begin{itemize}
-		\item For fullness, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of $\X$-hypergraphs.
-By \Cref{rem:utile}, for every $k,l\in \mathbb{N}$, the front square in diagram below is a pullback, yielding the dotted arrow $\eta_{k,l}\colon F(k,l)\to H(k,l)$.
-		\[\xymatrix@C=10pt{F(k,l)   \ar[dd]_{(s^F_{k,l}, t^F_{k,l})}\ar[rr]^-{a^F_{k,l}} \ar@{.>}[dr]_{\eta_{k,l }}&& E_F \ar[dd]|\hole^(.7){(s_F, t_F)}  \ar[dr]^{f}\\ & H(k,l) \ar[dd]_(.3){(s^H_{k,l}, t^H_{k,l})}\ar[rr]^(.4){a^H_{k,l}} &&  E_H \ar[dd]^{(s_H, t_H)}\\F(\bullet)^k\times F(\bullet)^l \ar[dr]_{g^k\times g^l} \ar[rr]|\hole^(.65){b^F_{k,l}\times b^F_{k,l}}& &F(\bullet)^\star \times F(\bullet)^\star  \ar[dr]^{g^\star\times g^\star}\\&H(\bullet)^k\times H(\bullet)^l \ar[rr]_{b^H_k\times b^H_l} && H(\bullet)^\star \times H(\bullet)^\star  }\]
-
-		As $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ we can simply take  $g$.
-Then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
-Indeed, given an arrow $f_i\colon(k,l)\to \bullet$ then we have :
-		\begin{align*}
-			\eta_\bullet \circ F(f_i)&=g\circ F(f_i)
-			\\&= \begin{cases}
-			g\circ \pi^F_i\circ s^F_{k,l} & i <k\\
-			g\circ \pi^F_i\circ t^F_{k,l} & \text{otherwise}
-			\end{cases}
-			\\&=
-			\begin{cases}
-		\pi^H_i\circ g^k\circ s^F_{k,l} & i <k\\
-		\pi^H_i\circ g^k\circ t^F_{k,l} 	& \text{otherwise}
-			\end{cases}\\&=
-		\begin{cases}
-	\pi^H_i\circ s^H_{k,l} \circ \eta_{k,l}& i <k\\
-	\pi^H_i\circ t^H_{k,l} \circ \eta_{k,l}	& \text{otherwise}
-	\end{cases}\\&=H(i)\circ \eta_{k,l}
-		\end{align*}
-		Finally, by construction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$.
-
-		\item  Let us turn to essential surjectivity.
-Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define $F_{\mathcal{G}}(\bullet):=V_{\mathcal{G}}$ and $F_{\mathcal{G}}(k,l)$ by the following pullback.
-Notice that, by \Cref{rem:salv} and countably extensivity, $(E_{\mathcal{{G}}}, \{a_{k,l}\}_{k,l\in \mathbb{N}})$ is a coproduct.
-		\[\xymatrix@C=30pt{F_\mathcal{G}(k,l) \ar[d]_{p_{k,l}}  \ar[r]^{a_{k,l}}& E_{\mathcal{G}} \ar[d]^{(s_F, t_F)} \\ V_{\mathcal{G}}^k\times V_{\mathcal{G}}^l \ar[r]_{b_k\times b_l} & V_{\mathcal{G}}^\star\times V_{\mathcal{G}}^\star}\]
-
-		Let $q_{i;k,l}\colon V_\mathcal{G}^k\times V_{\mathcal{G}}^l\to V_\mathcal{G} $ be the $i^{\text{th}}$ projection, then for every morphism $f_i\colon (k,l)\to \bullet$ in $\catname{H}$ we can define $F_{\mathcal{G}}(f_i)$ as $q_{i; k,l}\circ p_{k,l}$.
-$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$.
-
-		Notice that $p_{k,l}=(s^{F_{\mathcal{G}}}_{k,l}, t^{F_{\mathcal{G}}}_{k,l})$. To see this, it is enough to compose with the projections:
-		\begin{align*}
-			q_{i;k,l}\circ p_{k,l}&=F_{\mathcal{G}}(f_i)\\&=\begin{cases}
-				\pi^{F_{\mathcal{G}}}_{k, i} \circ F_{\mathcal{G}}(f_i) & i<k\\
-				\pi^{F_{\mathcal{G}}}_{l, i} \circ F_{\mathcal{G}}(f_i) &\text{otherwise}
-			\end{cases}\\&=\begin{cases}
-		s^{F_{\mathcal{G}}}_{k,l} & i<k\\
-		t^{F_{\mathcal{G}}}_{k,l} &\text{otherwise}
-			\end{cases}\\&=q_{i;k,l}\circ (s^{F_{\mathcal{G}}}_{k,l}, t^{F_{\mathcal{G}}}_{k,l})
-		\end{align*}
-		In particular, this entails that 
-		\[\begin{split}
-	s^{F_{\mathcal{G}}}\circ a^{F_{\mathcal{G}}}_{k,l}&=b^{F_{\mathcal{G}}}_k \circ s^{F_{\mathcal{G}}}_{k,l}\\&= b_k \circ s^{F_{\mathcal{G}}}_{k,l}\\&=s_F\circ a_{k,l}
-		\end{split} \qquad \begin{split}
-	t^{F_{\mathcal{G}}}\circ a^{F_{\mathcal{G}}}_{k,l}&=b^{F_{\mathcal{G}}}_l \circ t^{F_{\mathcal{G}}}_{k,l}\\&= b_l \circ s^{F_{\mathcal{G}}}_{k,l}\\&=t_F\circ a_{k,l}
-		\end{split}\]
-
-		Now, we know that there is an isomorphism $\phi \colon E_{\mathcal{G}} \to \sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)$ making the diagram below commutative.
-	\[\xymatrix{& F_{\mathcal{G}}(k,l) \ar[dr]^{a^{F_\mathcal{{G}}}_{k,l}} \ar[dl]_{a_{k,l}} \\E_{\mathcal{G}} \ar[rr]_-{\phi} & & \Sum_{k,l\in \mathbb{N}} F_{\mathcal{G}}(k,l)}\]
-
-	Therefore we have
-	\[\begin{split}
-	s_{F_{\mathcal{G}}} \circ \phi \circ a_{k,l}&=	s_{F_{\mathcal{G}}}  \circ a^{F_{\mathcal{G}}}_{k,l}	\\&= s_F\circ a_{k,l} \end{split} \qquad \begin{split}
-	t_{F_{\mathcal{G}}} \circ \phi \circ a_{k,l}&=	t_{F_{\mathcal{G}}}  \circ a^{F_{\mathcal{G}}}_{k,l}	\\&= t_F\circ a_{k,l} \end{split}\]
-
-	This allows us to conclude that $(\phi, \id{V_{\mathcal{G}}})$ is an isomorphism in $\hyp_\X$, from which the thesis now follows. 
-	\end{itemize}
-\end{proof}
-\fi
+	$\hyp$ is equivalent to the category $\Set^{\catname{H}}$.
+\end{proposition}
 
 \subsubsection{Labelling hypergraph with an algebraic signature}
+
+Our interest intohypergraph stems fromm their use as a graphical representation of algebraic terms. We thus need a way to label hyperedges with symbols taken from a given algebraic signature.
 
@@
 
-\begin{example}\label{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature in $\Set$.
+\begin{example}\label[example]{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature in $\Set$.
 This simply amount to a set of \emph{operations} with an associated natural number, called \emph{arity}.
@@
 
-\begin{proposition}\label{prop:mono} Let $\X$ be a (strict) $\mathcal{N}$-adhesive category, then the following hold true:
+\begin{proposition}\label[proposition]{prop:mono} For every algebraic signature $\Sigma$, the following are true:
 	\begin{enumerate}
 		\item a morphism $(h,k)$ between two object of $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions;
-		\item every algebraic signature $\Sigma$, $\hyps$ is an (strict) $\mathcal{M}$-adhesive category, where a morphism $(h,k)$ in $\hyps$ belongs to $\mathcal{M}$ if and only if both $h$ and $k$ are in $\mathcal{N}$.
+		\item $\hyp_{\Sigma}$ is an adhesive category. 
 	\end{enumerate}
@@
 
-\begin{remark}\label{rem:label}	
-	Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a morphism $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares below commute.
-	\[\xymatrix{E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{s_{\mathcal{H}}}& O_\Sigma \ar[d]^{\ari_\Sigma}& E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{t_{\mathcal{H}}} & O_\Sigma \ar[d]^{o_1\circ !_{O_\Sigma}}\\ V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}}& 1^\star & V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}} & 1^\star}\]
-
-	Let $v_n\colon V^n_\mathcal{H}\colon  V^\star_{\mathcal{H}}$ be a coprojection.
-The second diagram above entails that $t_{\mathcal{H}}$ factors through $v_1\colon V_{\mathcal{H}}\to V^{\star}$.
-Indeed, in the diagram below, the inner square is a pullback by extensivity and its outer boundaries yields the second square above, so that we get the dotted $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
-	\[\xymatrix{E_{\mathcal{H}} \ar@{.>}[dr]^{\tau}\ar@/^.4cm/[drr]^{t_{\mathcal{H}}} \ar[d]_{h} \\	O_\Sigma \ar@/_.2cm/[dr]_{!_{O_\Sigma}}&V_{\mathcal{H}} \ar[r]^{v_1}\ar[d]^{!_{V_\mathcal{H}}}& V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}}\\ & 1 \ar[r]_{o_1}& 1^\star}\]
+\begin{remark}\label[remark]{rem:label}	
+	Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a morphism $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares below commute (cfr.~ \Cref{rem:length}).
+	\[\xymatrix{E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{s_{\mathcal{H}}}& O_\Sigma \ar[d]^{\ari_\Sigma}& E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{t_{\mathcal{H}}} & O_\Sigma \ar[d]^{\delta_1}\\ V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}}& \mathbb{N} & V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}\]
+
+	Let $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$ be a coprojection.
+The second diagram in particular above entails that $t_{\mathcal{H}}$ factors through the inclusion $v_1\colon V_{\mathcal{H}}\to V^{\star}$ of words of length $1$, i.e.
+that $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to \tau_{\mathcal{H}}$.
 \end{remark}
@@
 \begin{proof}Let $(h, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be an object of $\hyp_{\Sigma}$, and suppose that there exists $f\colon X\to U_{\Sigma}(\mathcal{H})$.
-Since, $U_{\Sigma}(\mathcal{H})=U_{\X}(\mathcal{H})$ and $\id{\X}$ is the unit of $\Delta_\X \dashv U_{\X}$, we get a morphism $(?_{E_{\mathcal{H}}},f)\colon \Delta_{\X}(X)\to \mathcal{H}$ of $\hyp_\X$.
+Since, $U_{\Sigma}(\mathcal{H})=U_{\X}(\mathcal{H})$ and the identity is the unit of $\Delta_\hyp \dashv U_{\hyp}$, we get a morphism $(?_{E_{\mathcal{H}}},f)\colon \Delta_{\X}(X)\to \mathcal{H}$ of $\hyp$.
 But then we have
-	\begin{align*}
-		(h, !_{V_{\mathcal{{H}}}})\circ (?_{E_{\mathcal{H}}}, f)&=(h\circ ?_{E_{\mathcal{H}}}, !_{V_{\mathcal{{H}}}}\circ f)\\&=(?_{0_{\Sigma}}, !_{X})\\&=\Delta_{\X}(X)
-	\end{align*}
+	\[
+	(h, !_{V_{\mathcal{{H}}}})\circ (?_{E_{\mathcal{H}}}, f)=(h\circ ?_{E_{\mathcal{H}}}, !_{V_{\mathcal{{H}}}}\circ f)=(?_{0_{\Sigma}}, !_{X})=\Delta_{\hyp}(X)\]
 and the thesis follow.   
@@
 We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
-\begin{example}\label{lab_1}
+\begin{example}\label[example]{lab_1}
 	The simplest example is given by the identity $\id{\mathcal{G}^\Sigma}\colon \mathcal{G}^\Sigma\rightarrow \mathcal{G}^{\Sigma}$. If $\Sigma$ is the signature of groups $\Sigma_G$we get 
@@
 
-\begin{example}\label{lab_2}
+\begin{example}\label[example]{lab_2}
 	Take again $\Sigma_G$ the signature of groups, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
@@
 
-\begin{definition}\label{def:tg}\index{term graph}
+\begin{definition}\label[definition]{def:tg}\index{term graph}
 	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is mono.
@@
 
-\begin{remark}\label{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
-Notice, moreover that since $t_{\mathcal{G}}$is mono then $\tau_{\mathcal{G}}$ is mono too.
+\begin{remark}\label[remark]{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
+Notice, moreover that since $t_{\mathcal{G}}$ is mono then $\tau_{\mathcal{G}}$ is mono too.
 \end{remark}
@@
 
-\begin{proposition}\label{term:left}The forgetful functor $U_{\tg}$ has a left adjoint $\Delta_{\tg}$.
+\begin{proposition}\label[proposition]{term:left}The forgetful functor $U_{\tg}$ has a left adjoint $\Delta_{\tg}$.
 \end{proposition}
@@
 
-Take now a mono $(i,j)\colon \mathcal{H}\to \mathcal{G}$ between  $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\hyp_\Sigma$.
-In particular we have a commutative square
-
-\[\xymatrix{E_{\mathcal{G}} \ar[r]^{t_{\mathcal{G}}} \ar[d]_{i}& V^\star_{\mathcal{G}} \ar[d]^{j} \\ E_{\mathcal{H}} \ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}}}\]
-
-By  \Cref{prop:mono} $i$ and $j$ are monos, thus if $t_{\mathcal{H}}$ is mono then $t_{\mathcal{G}}$  is mono too.
-This show that if $(l', !_{V_\mathcal{H}})$ is a term graph then $(l, !_{V_\mathcal{G}})$ belongs to $\tg$ too.
-Since $\X$ is assumed to have finite limits, applying this argument when $(i,j)$ is the equalizer in $\hyp_\Sigma$ of two parallel arrows between term graphs we get the following.
-
-\begin{proposition}\label{prop:equ}$\tg$ has equalizers and $I_{\Sigma}$ creates them.
-\end{proposition}
-
-We have a similar result also for binary products.
-
-\begin{proposition} $\tg$ has binary products and $I_\Sigma$ creates them.
-\end{proposition}
-\begin{proof}
-	Let $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be two term graphs, their product in $\hyp_{\Sigma}$ is given by $(p, !_{V_\mathcal{P}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$, where the square below  is a pullback in $\hyp$ and $(p, !_{V_\mathcal{P}})$ is the diagonal filling it.
-	\[\xymatrix@C=35pt{\mathcal{P} \ar[r]^{(p_E, p_V)} \ar[d]_{(q_E, e_V)} & \mathcal{G} \ar[d]^{(l, !_{V_\mathcal{G}})}\\ \mathcal{H} \ar[r]_{(l', !_{V_{\mathcal{H}}})}& \mathcal{G}^\Sigma}\]
-	By \Cref{prop:com} we have two pullback square in $\X$:
-	\[\xymatrix{E_\mathcal{P} \ar[r]^{p_E} \ar[d]_{q_E} & E_\mathcal{G} \ar[d]^{l} &V_{\mathcal{P}} \ar[r]^{p_V} \ar[d]_{q_V}&V_{\mathcal{G}}\ar[d]^{!_{V_\mathcal{G}}} \\ E_\mathcal{H} \ar[r]_{l'}& O_\Sigma & V_\mathcal{H}\ar[r]_{!_{V_\mathcal{H}}} & 1}\]
-	Moreover $t_{\mathcal{P}}$ fits in the following diagram.
-	\[\xymatrix{V^\star_{\mathcal{P}} \ar[rrr]^{p^\star_V} \ar[ddd]_{q^\star_V}& & &V_{\mathcal{G}}^\star \ar[ddd]^{!^\star_{V_\mathcal{G}}}\\&E_\mathcal{P} \ar[ul]^{t_{\mathcal{P}}}\ar[r]^{p_E} \ar[d]_{q_E} & E_\mathcal{G} \ar[ur]_{t_{\mathcal{G}}} \ar[d]^{l}  \\ &E_\mathcal{H} \ar[dl]_{t_{\mathcal{H}}} \ar[r]_{l'}& O_\Sigma \ar[dr]_{o_1\circ !_{O_\Sigma}} \\V^\star_{\mathcal{H}} \ar[rrr]_{!^\star_{V_\mathcal{H}}}& & &1^\star}\]
-	If we show that $\mathcal{P}$ is a term graph we are done. Take two arrows $h_1, h_{2}\colon Z\rightrightarrows  E_{\mathcal{P}}$ such that 
-	\[t_{\mathcal{P}}\circ h_1= t_{\mathcal{P}}\circ h_2 \]
-
-	We have the following chains of equalities 
-	\[\begin{split}
-		t_{\mathcal{G}}\circ p_E \circ h_1&=p^\star_V\circ t_{\mathcal{P}} \circ h_1 \\&=p^\star_V\circ t_{\mathcal{P}}\circ h_2\\&=t_{\mathcal{G}}\circ p_E\circ h_2
-	\end{split} \qquad \begin{split}
-		t_{\mathcal{H}}\circ q_E\circ h_1&=q^\star_V\circ t_{\mathcal{P}} \circ h_1\\&=q^\star_V\circ t_{\mathcal{P}}\circ h_2\\&=t_{\mathcal{H}} \circ q_E\circ h_2
-	\end{split}\]
-	Since $t_{\mathcal{G}}$ and $t_{\mathcal{H}}$ are monomorphisms we get
-	\[p_E \circ h_1=p_E\circ h_2 \qquad q_E\circ h_1=q_E \circ h_2\]
-	which, in turn, imply  $h_1=h_2$.	  
-\end{proof}
-Since pullbacks can be computed from products and equalizers we also get the following.
-
-\begin{corollary}\label{cor:pb}$\tg$ has pullbacks and they are created by $I_\Sigma$.
-\end{corollary}
+We canlist some categorical properties of $\tg$
+
+\begin{proposition}
+For every algebraic signatur $\Sigma$, the following are true:
+\begin{enumerate}
+	\item if  $(i,j)\colon \mathcal{H}\to \mathcal{G}$ is a mono between  $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\hyp_\Sigma$ and the latter is a term graph, then also the former is in $\tg$
+	\item $\tg$ has equalizers, binary products and pullbacks and they are created by $I_\Sigma$.
+\end{enumerate}
+\end{proposition}
+
 \begin{remark}
@@
 \begin{remark}
-	$\tg$, even when $\Sigma$ is an algebraic signature in $\Set$ is not an adhesive category.
-In particular it does not have pushouts along all monomorphisms.
-For instance, if we take the three term graphs of the previous remark, then have two arrows
+	$\tg$ is not an adhesive category. In particular it does not have pushouts along all monomorphisms. For instance, if we take the three term graphs of the previous remark, then have two arrows
 	$(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_a, !_{V_{\mathcal{G}_a}})$ and $(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_b, !_{V_{\mathcal{G}_a}})$ which cannot be completed to a square.
@@
 	then $g_V=k_V$ and
-	\begin{align*}t_{\mathcal{H}}(g_E(h))&=g^\star_V(t_{\mathcal{G}}(h))\\&=g_V^\star(\delta_v)\\&=k^\star_V(\delta_V)\\&=k^\star_V(t_{\mathcal{G}}(h))\\&=t_{\mathcal{H}}(k_E(h))
-	\end{align*}
+	\[t_{\mathcal{H}}(g_E(h))=g^\star_V(t_{\mathcal{G}}(h))=g_V^\star(\delta_v)=k^\star_V(\delta_V)=k^\star_V(t_{\mathcal{G}}(h))=t_{\mathcal{H}}(k_E(h))\]
 	so that we also have $g_E=k_E$, but then
-	\begin{align*}
-		a&=l_a(h)\\&=q(g_E(h))\\&=q(k_E(h))\\&=l_b(h)\\&=b
-	\end{align*}
+	\[
+	a=l_a(h)=q(g_E(h))=q(k_E(h))=l_b(h)=b\]
 \end{remark}
@@
 \begin{definition}
-	Let $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l, !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be two term graph and $(f,g)$ a morphism $\mathcal{G}\to \mathcal{H}$.
-As in \Cref{rem:label}, let also $t_{\mathcal{G}}$ and $t_{\mathcal{H}}$ be $o_{1}\circ \tau_\mathcal{G}$ and $o_1\circ \tau_{\mathcal{H}}$.
-Consider the diagram below, in which the right square is a pullback, we say that $(f,g)$ \emph{preserves inputs} if the dotted arrow  $t_g\colon I_{\mathcal{{H}}, f}\to E_{\mathcal{{G}}}$ exists.
-	\[\xymatrix{E_{\mathcal{G}} \ar[dr]_{\tau_{\mathcal{G}}}&I_{\mathcal{H}, g} \ar@{.>}[l]_{t_g} \ar[r]^{w^{\mathcal{G}}_1} \ar[d]_{w^{\mathcal{G}}_2} & E_{\mathcal{H}} \ar[d]^{\tau_{\mathcal{H}}}\\ & V_{\mathcal{G}} \ar[r]_{g}  & V_{\mathcal{{H}}}}\]
-
+	Let $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$  be a term graph.
+A \emph{input node} is an element of $V_{\mathcal{G}}$ not in the image of $\tau_{\mathcal{H}}$.
+A morphism $(f,g)$ between
+	Let $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l, !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\tg$, is said to \emph{preserve input nodes} if $g$ sends input nodes to input nodes.
 \end{definition}
 
+\todo{Se questo remark sotto non serve nel pezzo sulle equivalenze possiamo toglierlo}
 \begin{remark}\label{prop:image}
-	Notice that we have
-	\begin{align*}
-		t_{\mathcal{H}}\circ w^{\mathcal{G}}_1&=o_{\mathcal{H},1}\circ \tau_{\mathcal{H}}\circ w^{\mathcal{G}}_1\\&=o_{\mathcal{H},1}\circ g\circ w^{\mathcal{G}}_2\\&=g^\star\circ o_{\mathcal{G},1}\circ w^{\mathcal{G}}_2\\&=g^\star \circ o_{\mathcal{G},1}\circ \tau_{\mathcal{G}}\circ t_g\\&=g^\star \circ t_{\mathcal{G}}\circ t_g\\&=t_{\mathcal{H}}\circ f\circ t_g
-	\end{align*}
-	and thus, since $t_{\mathcal{H}}$ is mono, we get $w^{\mathcal{G}}_1=f\circ t_g$.
+	Suppose that $(f,g)\colon ((l, !_{V_{\mathcal{G}}}))\to (l', !_{V_{\mathcal{H}}})$ preserves input nodes.
+Then  if $\tau_{\mathcal{H}}(h)=g(v)$ for some $v\in V_{\mathcal{G}}$ then $h$ belongs to the image of $f$.
+Indeed, by hypothesis $v$ must be in the image of $\tau_{\mathcal{G}}$ and so there exists $k$ such that $\tau_{\mathcal{G}}(k)=v$.
+But then $\tau_{\mathcal{H}}(f(k))=g(v)$ and we can conclude that $f(k)=h$.
 \end{remark}
-We are now ready to show that regular monos are preserves inputs.
-
-\begin{lemma}\label{lem:reg} If a mono $(i,j)$ between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ then it preserves inputs.
+
+Preservation of inputs, characterizes regular monos in $\tg$.
+
+\begin{proposition}\label[proposition]{lem:reg} The following are equivalent for a a mono $(i,j)$ between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$:
+	\begin{enumerate}
+		\item $(i, j)$ is a regular mono;
+		\item $(i,j)$ preserves input nodes.
+	\end{enumerate}	
+\end{proposition}
+
+This characterization, in turn, provides us with the following result \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity,castelnovo2023thesis}.
+
+\begin{lemma}\label[lemma]{prop:push} Consider three term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$.
+Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout along $(f_2, g_2)$,  then their pushout $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ is a term graph too.
 \end{lemma}
 
-\begin{proof}
-	Let $(i,j)$ be the equalizer of $(f_1, g_1)$ and $(f_2, g_2)$ are arrows from $(l', !_{V_\mathcal{H}})$ to $(k, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^\Sigma$.
-Suppose that the domain of $(i,j)$ is  $(e, !_{V_{\mathcal{E}}})\colon \mathcal{E}\to \mathcal{{G}}^\Sigma$.
-	By \Cref{prop:equ} such morphism is a regular mon also in $\hyp_\Sigma$.
-Since we have assumed that $(-)^\star$ preserves equalizer, by \Cref{lim} the  horizontal rows in the diagrams below are equalizers in $\X$.
-
-	\[\xymatrix{I_{\mathcal{H}, j} \ar@/^.4cm/[drr]^{w^{\mathcal{G}}_1}  \ar@/_.4cm/[ddr]_{w^{\mathcal{G}}_2} \ar@{.>}[dr]^{t_j}\\&E_{\mathcal{E}} \ar@{.>}[d]_{t_{\mathcal{E}}} \ar[r]^{i}& E_{\mathcal{H}} \ar[d]_{t_{\mathcal{H}}}  \ar@<.5ex>[r]^{f_1} \ar@<-.5ex>[r]_{f_2} & E_{\mathcal{K}}  \\ &V_{\mathcal{E}} \ar[r]_{j}& V_{\mathcal{H}}  \ar@<.5ex>[r]^{g_1} \ar@<-.5ex>[r]_{g_2}& V_{\mathcal{K}}}\]
-
-	Now, we have
-	\begin{align*}
-		\tau_{\mathcal{K}}\circ f_1\circ w^{\mathcal{G}}_1&=g_1\circ \tau_\mathcal{H}\circ w^{\mathcal{G}}_1\\&=g_1\circ j\circ w^{\mathcal{G}}_2\\&=g_2\circ j\circ w^{\mathcal{G}}_2\\&=g_2\circ \tau_{\mathcal{H}}\circ w^{\mathcal{G}}_1\\&=\tau_{\mathcal{K}}\circ f_2\circ w^{\mathcal{G}}_1
-	\end{align*}
-
-	By \Cref{rem:mono2}, $\tau_{\mathcal{K}}$ is a mono and so we can conclude.   
-\end{proof}
-
-\begin{lemma}\label{prop:push}Let $\X$ be a strict $\mathcal{M}$-adhesive category and consider two term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$.
-Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ preserves inputs and both $f_1$ and $g_1$ are in $\mathcal{M}$,  then their pushout $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ is a term graph too.
-\end{lemma}
-
-\Cref{cor:varie3,lem:reg,prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{corradini2005term}.
+\Cref{thm:slice-functors}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{corradini2005term}.
 \begin{corollary}
@@
 Summing up we have just proved the following fact.
-\begin{proposition}\label{prop:dual}
+\begin{proposition}\label[proposition]{prop:dual}
 	$(\comma{L}{R})^{op}$ is equal to	$\comma{R^{op}}{L^{op}}$, moreover $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
@@
 
-\begin{lemma}\label{colim}
+\begin{lemma}\label[lemma]{colim}
 	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
@@
 \Cref{prop:dual} and \Cref{colim} now yields the following.
-\begin{corollary}\label{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ I$.
+\begin{corollary}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ I$.
 \end{corollary}
@@
 We can use \Cref{lim} to characterize monos in comma categories. 
-\begin{corollary}\label{cor:mono}
+\begin{corollary}\label[corollary]{cor:mono}
 	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comma{L}{R}$ is mono if and only if both $h$ and $k$ are monomorphisms.
@@
 
-\begin{proposition}\label{prop:left}
+\begin{proposition}\label[proposition]{prop:left}
 	If $\A$ has initial objects and $L$ preserves them then the forgetful functor $U_R\colon \comma{L}{R}\to \B$ has a left adjoint $\Delta$.
@@
 
-\begin{proposition}\label{prop:commaapp}
+\begin{proposition}\label[proposition]{prop:commaapp}
 	For every object $X$ in a category $\X$, if $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object $*$, then $\X/X$ and $X/\X$ are isomorphic to, respectively,  $\comma{\id{X}}{\delta_X}$ and $\comma{\delta_X}{\id{X}}$ .
@@
 A straightforward application of \Cref{lim} now yields the following.
-\begin{corollary}\label{cor:pbapp}
+\begin{corollary}\label[corollary]{cor:pbapp}
 	If $\X$ has pullbacks, then for every object $X$, the slice $\X/X$ has pullbacks too.

### 2025-02-12 calco/Hypergraphs_with_equivalences.tex
merge
Fact_Sys

--- 2025-02-07 icgt/Hypergraphs_with_equivalences.tex
@@
+\section{Equipping hypergraphical structures with equivalences}
+
+\subsection{Hypergraphs with equivalences}
+
+\subsubsection{Hierarchical hypergraphs with equivalences}
+
+\subsection{Term graphs with equivalences}
+
+\todo{Il materiale va distribuito nelle varie sottosezioni}
+
+\begin{definition}
+	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is an object and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is a regular epimorphism called \emph{quotient map}.
+
+	A morphism $h:\mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute.
+	\[\xymatrix{
+		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {C_{\mathcal{G}}} \ar[d]^{h_C} \\
+		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}^\star}}& {V_\mathcal{H}}\ar[r]_{q_\mathcal{H}} & {C_\mathcal{H}}
+	}\]
+	The category of hypergraphs with equivalences and their morphisms is denoted $\EqHyp$.
+
+\end{definition}
+
+\begin{remark}\label{rem:eqhyp_morphs}
+	Morphisms of hypergraphs with equivalences are uniquely determined by the first two components.
+That is, if $h_1 = (h_E, h_V, f)$ and $h_2 = (h_E, h_V, g)$ are two morphisms $\mathcal{G \to H}$, then we have
+	\[\xymatrix{
+			{V_\mathcal{G}} \ar[r]^{h_V}\ar[d]_{q_\mathcal{G}} & V_\mathcal{H} \ar[d]^{q_\mathcal{H}} & V_\mathcal{G}\ar[l]_{h_V}\ar[d]^{q_\mathcal{G}}\\
+			C_{\mathcal{G}}\ar[r]_{f} & C_{\mathcal{H}} & C_{\mathcal{G}}\ar[l]^{g}
+	}\]
+	Hence,
+	\begin{align*}
+		f \circ q_\mathcal{G} &= q_\mathcal{H}\circ h_V \\ &=g\circ q_\mathcal{G}
+	\end{align*}
+	Since $q_\mathcal{G}$ is epi, we obtain $f = g$.
+\end{remark}
+
+$\EqHyp$ has a forgetful functor $U_{\EqHyp}:\EqHyp \to \Set$, which sends each $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ into $V_\mathcal{G}$, and each $h = (h_E, h_V, h_C)$ onto $h_V$.
+
+\begin{proposition}
+	$U_\EqHyp$ has a left adjoint $\Delta_{\EqHyp}: \Set \to \EqHyp$.
+\end{proposition}
+
+\begin{proof}
+	For each set $X$, define $\Delta_\EqHyp(X):= (\emptyset, X, \{\bullet\}, ?_X, ?_X, !_X)$. Consider now $h: \Delta_{\EqHyp}(X) \to \mathcal{H}$.
+	\[\xymatrix@C=2.3cm{
+			\Delta_{\EqHyp}(X) \ar@{.>}[d]_{\Delta_\EqHyp(f)} \ar[dr]^{h} & \\
+			\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) \ar[r]_{\epsilon_{\mathcal{H}}} & \mathcal{H}
+	}\]
+	Where $\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) = (\emptyset, V_\mathcal{H}, \{\bullet\}, ?_{V_\mathcal{H}}, ?_{V_\mathcal{H}}, !_{V_\mathcal{H}})$ and $\epsilon_{\mathcal{H}} = (?_{E_\mathcal{H}}, \id{V_\mathcal{H}}, g)$.
+	Note that, since $\Delta_{\EqHyp}(X)$ has the empty set as object of edges, $h_E = ?_{E_\mathcal{H}}$, then, the unique arrow that fits in the diagram is $\Delta_{\EqHyp}(f) = (?_{E_\mathcal{H}}, h_V, \id{\{\bullet\}})$.
+
+\end{proof}
+
+We now define another functor $T: \EqHyp \to \hyp$, which ``forgets'' the quotient part, mapping each hypergraph with equivalence $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ onto $T(\mathcal{G})=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
+Then, we have the following result.
+
+\begin{proposition}
+	$T$ has a left adjoint $L: \hyp \to \EqHyp$.
+\end{proposition}
+
+\begin{proof}
+	Let $\mathcal{G}$ be a hypergraph, and define $L(\mathcal{G}) := (E_\mathcal{G}, V_{\mathcal{G}}, \{\bullet\}, s_\mathcal{G}, t_\mathcal{G}, !_{V_\mathcal{G}})$.
+Let now $h: L(\mathcal{G})\to \mathcal{H}$ be a morphism in $\EqHyp$, and consider the following situation.
+	\[\xymatrix@C=2.3cm{
+		L(\mathcal{G}) \ar@{.>}[d]_{L(f)} \ar[dr]^{h}\\ L(T(\mathcal{H})) \ar[r]_{\epsilon_{\mathcal{H}}} & \mathcal{H}
+	}\]
+	Where $L(T(\mathcal{H}))=(E_\mathcal{H}, V_{\mathcal{H}}, \{\bullet\}, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$.
+Then, $\epsilon_\mathcal{H} = (\id{E_\mathcal{H}}, \id{V_\mathcal{H}}, h_C)$ (recall that by \Cref{rem:eqhyp_morphs}, the last component is uniquely determined by the first two), and $L(f)$ must be $(h_E, h_V, \id{\{\bullet\}})$.
+\end{proof}
+
+\begin{remark}
+	$T$ is faithful. Indeed, consider two morphisms $h = (h_E, h_V, h_C)$ and $k = (k_E, k_V, k_C)$, and suppose $T(h) = T(k)$, that is, $(h_E, h_V) = (k_E, k_V)$.
+	By \Cref{rem:eqhyp_morphs}, we can conclude also $h_C = k_C$, and hence the faithfulness of $T$.
+\end{remark}
+
 \section{Hypergraphs and term graphs with equivalences}
@@
 \end{remark}
+
+Let us turn to another functor $\EqHyp \to \hyp$.
+
+\begin{definition}
+The \emph{quotient functor} $Q:\EqHyp\to \hyp $ is defined as
+the one sending $(E, V, C, s, t, q)$ to $(E, C, q^{\star}\circ s, q^{\star}\circ t)$ and an arrow $(h_E, h_V, h_C)$ to $(h_E, h_C)$.
+\end{definition}
+
+\begin{remark}
+	The action of the functor on a morphism of hypergraphs with equivalences gives a morphism of hypergraphs,
+	in fact 
+	\begin{align*}
+		q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E &= q^{\star}_\mathcal{H} \circ h_V \circ s_\mathcal{G}\\ &= h_C \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}
+	\end{align*}
+	The same is valid for $t_\mathcal{H}$ and $t_\mathcal{G}$. 
+\end{remark}
+
+\begin{lemma}\label{lemma:quot_funct_left_adj}
+    $Q$ is a left adjoint.
+\end{lemma}
+
+\begin{proof}
+	Let $R((A, B, s, t))$ be $(A, B, B, s, t, \id{B})$, so that $Q(R((A, B, s, t))) = (A, B, s, t)$.
+Now, suppose that $h = (h_E, h_V): Q((E, V, C, s', t', q)) \to (A, B, s, t)$  is an arrow in $\hyp$, and consider the triple $(h_E, h_V, h_V \circ q)$.
+Since $h$ is a morphism of $\hyp$,
+    \[h_V^{\star}\circ q^{\star}\circ s'= s\circ h_E \qquad  h_V^{\star}\circ q^{\star}\circ t' = t\circ h_E\]
+    Then we have the following squares:
+    \[\xymatrix{
+		    E \ar[r]^{h_E}\ar[d]_{s'} & A \ar[d]^{s} & E \ar[r]^{h_E}\ar[d]_{t'} & A \ar[d]^{t} & V \ar[r]^{h_V \circ q} \ar[d]_{q} & B \ar[d]^{\id{B}} \\
+		    V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & C \ar[r]_{h_V} & B
+    }\]
+
+    \iffalse\[
+        \begin{tikzcd}
+            E \arrow[r, "{h_E}"] \arrow[d, "{s_G}"swap] & A \arrow[d, "s"] \\
+            V \arrow[r, "{h_V \circ q}"swap] & B
+        \end{tikzcd}
+        \qquad
+        \begin{tikzcd}
+            E \arrow[r, "{h_E}"] \arrow[d, "{t_G}"swap] & A \arrow[d, "t"] \\
+            V \arrow[r, "{h_V \circ q}"swap] & B
+        \end{tikzcd}
+        \qquad
+        \begin{tikzcd}
+            V \arrow[r, "{h_V\circ q}"] \arrow[d, "q" swap] & B \arrow[d, "{id_B}"] \\
+            C \arrow[r, "{h_V}"swap] & B
+        \end{tikzcd}
+    \]\fi
+
+    We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below.
+
+    \[\xymatrix{
+		    (A, B, s, t) \ar[r]^{(\id{A}, \id{B})} & (A, B, s, t)\\
+		    (E, C, q^\star\circ s', q^\star\circ t') \ar[u]^{Q(h_E, h_V \circ q, h_V)} \ar[ur]_{(h_E, h_V)}
+    }\]
+
+    Such arrow is unique. Suppose $f = (f_E, f_V, f_C)$ to be another arrow with such property.
+    Then, it must be $(\id A, \id B) \circ Q(f) = (f_E, f_C) = (h_E, h_C)$. Finally, $f_C = f_V \circ q = h_V \circ q$. 
+\end{proof}
+
+\begin{proposition}\label{prop:quot_creat_colims}
+    $Q$ creates colimits.
+\end{proposition}
+
+\begin{proof}
+    Preserve from \Cref{th:adjoints_preserves_lim}. Remain to see Reflect.
+	Let $D: \cat I \to \EqHyp$ be a diagram, and let $((c_i)_{i\in \cat I}, \mathcal{C})$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
+	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.
+	Let then $((b_i)_{i\in \cat I}, B)$ be the colimit of $T \circ D$.
+	Consider the following situation.
+	\[\begin{tikzcd}[row sep = 24, column sep = 24]
+		& B & \\
+		B_i \ar[ur, "{b_i}"] \ar[rr, "h_V"] \ar[d, "{q_i}"] & & B_j \ar[ul, "{b_j}"swap] \ar[d, "{q_j}" swap] \\
+		C_i \ar[dr, "{c_C^i}" swap] \ar[rr, "{h_C}"swap] & & C_j \ar[dl, "{c_C^j}"] \\
+		& C &
+	\end{tikzcd}\]
+
+	Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $T \circ D$, there exists a unique $q: B \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
+	Consider now the functor $W: \EqHyp \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component.
+By \Cref{prop:eqgrph_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, A)$ is the colimit of $W \circ D$.
+	Notice that $((b_i \circ s_i)_{i \in \cat{I}}, B)$ and $((b_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
+It remains now to show that $(A, B, C, s, t, q)$, together with $(c_E^i, b_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
+\end{proof}
+
+\begin{example}
+	$Q$ does not preserve limits.
+Indeed, let $\mathcal{G}_1 = (E_1, A, A, s_1, t_1, id_A)$, $\mathcal{G}_2 = (E_2, B, B, s_2, t_2, id_B)$ and $\mathcal{G}_3 = (E_3, A + B, \terminal, s_3, t_3, !_{A + B})$, and let $h = (h_E, \iota_A, !_A): \mathcal{G}_1 \to \mathcal{G}_3$, $k = (k_E, \iota_B, !_B): \mathcal{G}_2 \to \mathcal{G}_3$, where $(\iota_A, \iota_B, A + B)$ is the coproduct of $A$ and $B$, $\terminal$ is the intial object (in $\Set$, the singleton set as shown in \Cref{ex:set_init_term}), and $!_X$ the unique arrow $X \to \terminal$.
+	The following two diagrams show the pullback of $h$ and $k$ and the pullback of $Q(h)$ and $Q(k)$, on the second component (the vertices of the graphs)
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+		\initial \ar[r, "{p_1}"] \ar[d, "{p_2}" swap] & A \ar[d, "{\iota_A}"] \\
+		B \ar[r, "{\iota_B}"swap] & A+B
+	\end{tikzcd}\
+	\qquad
+	\begin{tikzcd}[row sep = 20, column sep = 20]
+		{A \times B} \ar[r, "{\pi_A}"] \ar[d, "{\pi_B}"swap] & A \ar[d, "{!_A}"] \\
+		B \ar[r, "{!_B}"swap] & \terminal
+	\end{tikzcd}\]
+
+	But the arrow $\initial \to A\times B$ is not epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
+\end{example}

### 2025-02-12 calco/Hypergraphs_with_equivalences.tex
Roba su funtore quoziente

@@
 \begin{proof}
-    Preserve from \Cref{th:adjoints_preserves_lim}. Remain to see Reflect.
-	Let $D: \cat I \to \EqHyp$ be a diagram, and let $((c_i)_{i\in \cat I}, \mathcal{C})$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
-	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.
-	Let then $((b_i)_{i\in \cat I}, B)$ be the colimit of $T \circ D$.
+    Since $Q$ is a left adjoint, it preserves colimits.
+	Let $D: \cat I \to \EqHyp$ be a diagram, and let $\mathcal{C}$, together with  $(c_i)_{i\in \cat I}$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
+	\iffalse
+	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.\fi
+	Let $((b_i)_{i\in \cat I}, B)$ be the colimit of $U_\EqHyp \circ D$.
 	Consider the following situation.
+	\[\xymatrix{
+
+	}\]
 	\[\begin{tikzcd}[row sep = 24, column sep = 24]

### 2025-02-12 calco/Hypergraphs_with_equivalences.tex
EqHyp stabile

@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:eqhyp_complete}
 	\EqHyp is complete and cocomplete, and $T$ preserves limits and colimits.
@@
 	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.\fi
-	Let $((b_i)_{i\in \cat I}, B)$ be the colimit of $U_\EqHyp \circ D$.
+	Let $((\kappa_i)_{i\in \cat I}, V)$ be the colimit of $U_\EqHyp \circ D$.
 	Consider the following situation.
 	\[\xymatrix{
-
+								  &  {V} &                             \\
+		V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
+		C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
+								  &  {C} &
 	}\]
-	\[\begin{tikzcd}[row sep = 24, column sep = 24]
-		& B & \\
-		B_i \ar[ur, "{b_i}"] \ar[rr, "h_V"] \ar[d, "{q_i}"] & & B_j \ar[ul, "{b_j}"swap] \ar[d, "{q_j}" swap] \\
-		C_i \ar[dr, "{c_C^i}" swap] \ar[rr, "{h_C}"swap] & & C_j \ar[dl, "{c_C^j}"] \\
-		& C &
-	\end{tikzcd}\]
-
-	Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $T \circ D$, there exists a unique $q: B \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
+	Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $U_\EqHyp \circ D$, there exists a unique $q: V \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
 	Consider now the functor $W: \EqHyp \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component.
-By \Cref{prop:eqgrph_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, A)$ is the colimit of $W \circ D$.
-	Notice that $((b_i \circ s_i)_{i \in \cat{I}}, B)$ and $((b_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
-It remains now to show that $(A, B, C, s, t, q)$, together with $(c_E^i, b_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
+	By \Cref{prop:eqhyp_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, E)$ is the colimit of $W \circ D$.
+	Notice that $((\kappa_i \circ s_i)_{i \in \cat{I}}, B)$ and $((\kappa_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
+It remains now to show that $(E, V, C, s, t, q)$, together with $(c_E^i, \kappa_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
 \end{proof}
@@
 	The following two diagrams show the pullback of $h$ and $k$ and the pullback of $Q(h)$ and $Q(k)$, on the second component (the vertices of the graphs)
-	\[\begin{tikzcd}[row sep = 20, column sep = 20]
-		\initial \ar[r, "{p_1}"] \ar[d, "{p_2}" swap] & A \ar[d, "{\iota_A}"] \\
-		B \ar[r, "{\iota_B}"swap] & A+B
-	\end{tikzcd}\
+	\[\xymatrix{
+			\initial \ar[r]^{p_1} \ar[d]_{p_2}& A \ar[d]^{\iota_A} \\
+			B \ar[r]_{\iota_B} & A+B
+	}
 	\qquad
-	\begin{tikzcd}[row sep = 20, column sep = 20]
-		{A \times B} \ar[r, "{\pi_A}"] \ar[d, "{\pi_B}"swap] & A \ar[d, "{!_A}"] \\
-		B \ar[r, "{!_B}"swap] & \terminal
-	\end{tikzcd}\]
+	\xymatrix{
+		{A \times B} \ar[r]^{\pi_A} \ar[d]_{\pi_B} & A \ar[d]^{!_A} \\
+		B \ar[r]_{!_B} & \terminal
+	}\]
 
-	But the arrow $\initial \to A\times B$ is not epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
+	But the arrow $\initial \to A \times B$ is not epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
 \end{example}
+
+\begin{proposition}
+	In $\EqHyp$, pushouts along regular monos are stable.
+\end{proposition}
+
+\begin{proof}
+	Let $\mathcal{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, C'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
+	and, in the diagram below, suppose all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is regular mono.
+                \[
+		\xymatrix@C=10pt@R=6pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{t'} \\ \mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d}\\&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{t} \\\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 }
+	\]
+	By \Cref{prop:eqgrph_complete} and \Cref{cor:mono1}, the following cubes in $\Set$ have pushouts as bottom faces and pullbacks as vertical faces, hence their top faces are pushouts.
+	\[
+        \xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && A_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ A_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & A_4' \ar[dd]_(.3){d_V}\\&A_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && A_2 \ar[dl]^{t_V} \\A_3 \ar[rr]_{p_V} & & A_4 }
+	\qquad
+        \xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && B_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ B_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & B_4' \ar[dd]_(.3){d_E}\\&B_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && B_2 \ar[dl]^{t_E} \\B_3 \ar[rr]_{p_E} & & B_4 }
+	\]
+	Consider now the following pullbacks.
+	\[\xymatrix{
+			Y \ar[d]_{y_2}\ar[r]^{y_1}&{C_4'}\ar[d]^{d_C}&U\ar[d]_{u_2}\ar[r]^{u_1}&{C_4'}\ar[d]^{d_C}&T\ar[r]^{x_1}\ar[d]_{x_2}&U\ar[d]^{u_2}\\
+			C_3\ar[r]_{p_C}&C_4&C_2\ar[r]_{t_C}&C_4&C_1\ar[r]_{h_C}&C_2
+	}\]
+	Thus, [???]\todo{inserire in sezione 1 la proposizione} yields the following situation, in which the bottom face is a pushout, and the vertical faces are pullbacks, hence the top face is a pushout too.
+        \[\xymatrix@C=10pt@R=6pt{&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar@{.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C_4' \ar[dd]_(.3){d_C}\\&C_1\ar[rr]|\hole^(.65){h_C} \ar[dl]^{k_C} && C_2 \ar[dl]^{t_C} \\C_3 \ar[rr]_{p_C} & & C_4 }\]
+	By the proof of \Cref{prop:eqhyp_complete}, we have that $m_2 \circ q'_3 : B'_3 \to Y$ and $m_3 \circ q'_2 : B_2' \to U$ are two epi-mono factorizations, with $m_2$ and $m_3$ monos.
+	At the same way, let the following square to be a pullback.
+	\[\xymatrix{S\ar[r]^{s_1}\ar[d]_{s_2}&C'_2\ar[d]^{m_3}\\T\ar[r]_{x_1}&U}\]
+	Then, there exists a mono $m_1$ such that $m_1\circ q_1' : B_1' \to S$.
+
+\end{proof}

### 2025-02-13 calco/main.tex
Update main.tex

@@
 
-\title{On the adhesivity properties of equivalence graphs\thanks{???????}}
+%\tikzset{->-/.style={decoration={
+%			markings,
+%			mark=at position #1 with {\arrow{>}}},postaction={decorate}}}
 
@@
 \authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
+\Copyright{R.~Biondo, D.~Castelnovo, F.~Gadducci}
+
+\ccsdesc[500]{Theory of Computation~Models of computation}
+\ccsdesc[500]{Theory of Computation~Semantics and reasoning}
+
+\keywords{Adhesive categories, EGGS} %TODO mandatory; please add comma-separated list of keywords
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Access}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+
+\title{On the adhesivity of EGGS}
 
 \begin{document}
-
-\tikzset{->-/.style={decoration={
-			markings,
-			mark=at position #1 with {\arrow{>}}},postaction={decorate}}}
-	\maketitle \todo{Scegliere un titolo vero e mettere i ringraziamenti}
+\maketitle
+
 \begin{abstract}
@@
 
-This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.
+This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}
+and investigate some simple results for their relationship with kernel pairs.
 
@@
 
-\subsection{$\mathcal{M}$-adhesivity}\label{subsec:ade}
+\subsection{Background on $\mathcal{M}$-adhesivity}\label{subsec:ade}
 The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.
@@
 
-\subsection{Kernel Pairs and Regular Epimorphisms}
+\subsection{Some Results on Kernel Pairs and Regular Epis}
 

### 2025-02-13 calco/main.tex
minori
Update main.tex
conclusioni

--- 2025-02-10 calco/main.tex
@@
 
-\title{On the adhesivity properties of equivalence graphs\thanks{???????}}
+\title{On the adhesivity of EGGS}
 
@@
 			mark=at position #1 with {\arrow{>}}},postaction={decorate}}}
-	\maketitle \todo{Scegliere un titolo vero e mettere i ringraziamenti}
+
+\maketitle
+
 \begin{abstract}
@@
 
-\subsection{Hierarchical hypergraphs}
-
-\todo{da fare? lasciare per una versione estesa?}
-
 \input{Hypergraphs_with_equivalences}
@@
 \section{Conclusions and further works}
-\todo{Some very nice conclusions}
+The aim of our paper was to extend the theory of adhesive categories in order to include EGGS, 
+an up-and-coming formalism for program optimisation and synthesis via a compact representation and 
+efficient implementation of equality saturation.
+%
+To do so, we revisited and generalised the notions of hyper-graph and term graph with equivalence, and
+we extended it in order to capture EGGS as term graphs satisfying a suitable closure property.
+
+Our result opens two threads of research. The first is to use the quasi-adhesivity of EGGS in order to
+model their rewriting via the double-pushout (DPO) approach. This is likely to be straightforward, since 
+the rules adopted in the literature of EGGS seems to be span of regular monos, and such rules
+perfectly fit the mold of rewriting on quasi-adhesive categories. 
+For example, the equivalence $x \div x = 1$, taken from the introductory example in~\cite{xxx}, 
+can be modelled as the rule
+\[to draw DPO rule\]
+
+It still needs to be investigated what concurrency and termination, the key properties for DPO rewriting
+on adhesive categories, 
+means in the context of EGGS. More interestingly, another venue for development is using the adhesive 
+machinery to extend the EGGS formalism. In fact, most of the results
+presented here for hyper-graphs can be generalised to hierarchical hyper-graphs, that is, 
+hypergraphs with a hierarchy (a partial order) among 
+edges that is useful for adding structural information, such as encapsulation and sandboxing~\cite{xxx}.
+
+Finally, we will delve into and draw a comparison with an alternative categorical presentation for EGGS 
+advanced in~\cite{ghica}. The proposal is quite different from our own. Simplifying, the key is to use categories 
+of tree which are equipped with a lattice on hom-sets. We can recover trees in our approach, even 
+if we opted for term graphs in order to obtain a simpler categorical presentation. Instead of going through 
+an enrichment on hom-sets, we chose to obtain closure via suitable requirements on morphisms, even if it 
+seems that the former generalises the latter, at the expenses of a more complex machinery.
+
 \bibliography{biblio}

### 2025-02-13 calco/main.tex
pass biblio

@@
 
-In this section we briegly recall the notion \emph{$\X$-hypergraph}.
-In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usual \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,wadler1995monads}.
+In this section we briefly recall the notion \emph{$\X$-hypergraph}.
+In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usual \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95}.
 We will recall some of its proprieties.
@@
 Let $\mathcal{G}_F$ be the resulting hypergraph.
-One can now show that  sending $F$ to $\mathcal{G}_F$ can be extended to an equivalence $\mathcal{G}_{-}\colon \Set^{\catname{H}}\to \hyp$ (see \cite{castelnovo2023thesis, castelnovo2022newcriterionmathcalmmathcalnadhesivity} for details).
+One can now show that  sending $F$ to $\mathcal{G}_F$ can be extended to an equivalence $\mathcal{G}_{-}\colon \Set^{\catname{H}}\to \hyp$ (see \cite{castelnovo2023thesis,CastelnovoGM24} for details).
 
@@
 
-This characterization, in turn, provides us with the following result \cite{castelnovo2022newcriterionmathcalmmathcalnadhesivity,castelnovo2023thesis}.
+This characterization, in turn, provides us with the following result \cite{CastelnovoGM24,castelnovo2023thesis}.
 
@@
 
-\Cref{thm:slice-functors}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{corradini2005term}.
+\Cref{thm:slice-functors}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{CorradiniG05}.
 \begin{corollary}
@@
 	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
-Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite{castelnovo2023thesis,castelnovo2022newcriterionmathcalmmathcalnadhesivity}).
+Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite{castelnovo2023thesis,CastelnovoGM24}).
 \end{lemma}
@@
 
-\section{Comparison with Ghica}
-\todo{Lo vogliamo fare?}
+%\section{Comparison with Ghica}
+%\todo{Lo vogliamo fare?}
 

### 2025-02-13 calco/main.tex
minima

@@
 Our result opens two threads of research. The first is to use the quasi-adhesivity of EGGS in order to
-model their rewriting via the double-pushout (DPO) approach. This is likely to be straightforward, since 
-the rules adopted in the literature of EGGS seems to be span of regular monos, and such rules
+model their rewriting via the double-pushout (DPO) approach. This seems to be straightforward, since 
+the rules adopted in the literature of EGGS appears to be span of regular monos, and such rules
 perfectly fit the mold of rewriting on quasi-adhesive categories. 
@@
 on adhesive categories, 
-means in the context of EGGS. More interestingly, another venue for development is using the adhesive 
+mean in the context of EGGS. More interestingly, another venue for development is using the adhesive 
 machinery to extend the EGGS formalism. In fact, most of the results

### 2025-02-14 calco/Hypergraphs_with_equivalences.tex
minori
EqHyp stabile/Reg-adhesive

@@
 \subsection{Hypergraphs with equivalences}
-
-\subsubsection{Hierarchical hypergraphs with equivalences}
 
@@
 
-\begin{proposition}
+\begin{lemma}\label{lemma:stab}
 	In $\EqHyp$, pushouts along regular monos are stable.
-\end{proposition}
+\end{lemma}
 
@@
 	\]
-	By \Cref{prop:eqgrph_complete} and \Cref{cor:mono1}, the following cubes in $\Set$ have pushouts as bottom faces and pullbacks as vertical faces, hence their top faces are pushouts.
+	By \Cref{prop:eqhyp_complete} and \Cref{cor:mono1}, the following cubes in $\Set$ have pushouts as bottom faces and pullbacks as vertical faces, hence their top faces are pushouts.
 	\[
-        \xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && A_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ A_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & A_4' \ar[dd]_(.3){d_V}\\&A_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && A_2 \ar[dl]^{t_V} \\A_3 \ar[rr]_{p_V} & & A_4 }
+        \xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ A_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}\\&A_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{t_E} \\A_3 \ar[rr]_{p_E} & & A_4 }
 	\qquad
-        \xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && B_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ B_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & B_4' \ar[dd]_(.3){d_E}\\&B_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && B_2 \ar[dl]^{t_E} \\B_3 \ar[rr]_{p_E} & & B_4 }
+        \xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ B_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\&B_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{t_V} \\B_3 \ar[rr]_{p_V} & & B_4 }
 	\]
@@
 	\[\xymatrix{S\ar[r]^{s_1}\ar[d]_{s_2}&C'_2\ar[d]^{m_3}\\T\ar[r]_{x_1}&U}\]
-	Then, there exists a mono $m_1$ such that $m_1\circ q_1' : B_1' \to S$.
+	Hence, in the following diagram, the outer rectangle is a pullback.
+	\[\xymatrix{
+			S\ar[r]^{s_1}\ar[d]_{s_2}&C'_2\ar[d]^{m_3}\\T\ar[r]_{x_1}\ar[d]_{x_2}&U\ar[d]^{u_2}\\C_1\ar[r]_{h_C}&C_2
+	}\]
+	By the same argument as before, there exists a mono $m_1$ such that $m_1\circ q_1' : B_1' \to S$.
+	% Uguaglianze da capire se servono davvero
 
+	We have to show that the top face of the cube ate the beginning of the proof is a pushout.
+	Suppose then that $z: \mathcal{G}_2' \to \mathcal{H}$ and $w: \mathcal{G}_3' \to \mathcal{H}$, with $\mathcal{H} = (E, V, C, s, t, q)$,
+	are two morphisms such that $z \circ h' = w \circ h'$, and let $v_V: B'_4 \to V$ the arrow induced by $z_V$ and $w_V$.
+	We want to construct the dotted arrow $v_C$ which fits in the diagram below.
+	\[
+	\xymatrix@C=10pt@R=6pt{
+		&B_1'\ar[dd]|\hole_(.65){q_1'}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]|\hole_(.65){q_2'} \ar[dl]_{t_V'}\ar[dr]^{z_V}\\
+		B_3'  \ar[dd]_{q_3'}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
+						       &C_1'\ar[rr]|\hole^(.65){h_C'} \ar[dl]_{k_C'} && C_2' \ar[dl]^{t_C'}\ar[dr]^{z_C}\\
+		C'_3 \ar[rr]_{p_C'} & & C'_4\ar@{.>}[rr]_{v_C} && C
+	}\]
+	By {\color{red}{cite: Lemma: kernel pairs pushout M-adh cats}}, we know that the top face of the cube below is a pushout.
+\[\xymatrix@C=15pt@R=15pt{&K_{s_2\circ m_1\circ q'_1}\ar[dd]|\hole_(.65){\pi_{s_2\circ m_1\circ q'_1}^{1}}\ar[rr]^{k_{h'_2}} \ar[dl]_{k_{k'_2}} && K_{m_2\circ q'_2} \ar[dd]^{\pi_{m_2\circ q'_2}^{1}} \ar[dl]_{k_{t'_2}} \\ K_{m_3\circ q'_3}  \ar[dd]_{\pi_{m_3\circ q'_3}^{1}}\ar[rr]^(.7){k_{p'_2}} & & K_{q'_4} \ar[dd]_(.3){\pi_{q'_4}^{1}}\\&B'_1\ar[rr]|\hole^(.65){h'_2} \ar[dl]^{k'_2} && B'_2 \ar[dl]^{t'_2} \\B'_3 \ar[rr]_{p'_2} & & C_4}\]
+	And, since $m_3$ and $m_2$ are monos,
+	\[\begin{split}
+		q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
+	\end{split}\qquad\begin{split}
+		q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
+	\end{split}\]
+	Computing, we obtain
+	\[\begin{split}
+		q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\
+							      &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\
+							      &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
+							      &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\
+							      &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 \\
+							      &= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\
+							      &= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}
+	\end{split}\qquad\begin{split}
+		q \circ v_V \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\
+							      &= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\
+							      &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
+							      &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\
+							      &= q \circ z_V \circ \pi_{m_2 \circ q_2'}^2 \\
+							      &= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\
+							      &= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{t'_V}
+	\end{split}\]
+	Since the previous cube has a pushout as top face, by universal property, we have
+	\[
+		q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
+	\]
+	hence, $v_C$ is the mediating arrow.
+	\[
+		v_C \circ q'_4 \circ \pi_{q'_4}^1 = v_C \circ q'_4 \circ \pi_{q'_4}^2
+	\]
 \end{proof}
+
+\begin{lemma}\label{lemma:van_kampen}
+	In $\EqHyp$, pushouts along regular monos are $\mathcal{R}eg(\EqHyp)$-Van Kampen.
+\end{lemma}
+
+\begin{proof}
+	In lieu of \Cref{lemma:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono,
+	the front faces are pullbacks too, where $\mathcal{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
+  	\[
+	\xymatrix@C=10pt@R=6pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{t'} \\ \mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d}\\&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{t} \\\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 }
+	\]
+	By \Cref{prop:eqhyp_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as back faces,
+	thus their front faces are pullbacks too.
+	\[
+        \xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ A_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}\\&A_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{t_E} \\A_3 \ar[rr]_{p_E} & & A_4 }
+	\qquad
+        \xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ B_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\&B_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{t_V} \\B_3 \ar[rr]_{p_V} & & B_4 }
+	\]
+	On the other hand we can consider the diagrams below, in which the inner squares are pullbacks.
+	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon C'_2\to U$, $m_3\colon C'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
+	\[\xymatrix{C'_3 \ar@{.>}[dr]^{m_3} \ar@/^.3cm/[drr]^{p'_3} \ar@/_.3cm/[ddr]_{d_3} &&& C'_2 \ar@{.>}[dr]^{m_2} \ar@/^.3cm/[drr]^{t'_3} \ar@/_.3cm/[ddr]_{d_2}\\&Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
+
+		\[\xymatrix{B'_3 \ar@{.>}[dr]^{a_3} \ar[r]^{p'_2} \ar[d]_{q'_3} &B'_4\ar[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{t'_2} \ar[d]_{q'_2} &B'_4\ar[dr]^{q'_4}\\C'_3 \ar[dr]_{d_3} &Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&C_2' \ar[dr]_{d_2}& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
+
+	Now, notice that  $m_3$ and $m_2$ are monos because $d_3$ and $d_2$ are regular monos. By the proof of \Cref{prop:limits}, to conclude it is enough to show that
+	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
+
+	Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $a_3$ and $a_2$ and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:limits}.
+
+	No if we compute we have:
+	\[\begin{split}
+		y_1\circ a_3&= q'_4\circ p'_2\\&=p'_3 \circ q'_3\\&=y_1\circ m_3\circ q'_3  
+	\end{split}\qquad \begin{split}
+		u_1\circ a_2&= q'_4\circ t'_2\\&=t'_3 \circ q'_3\\&=u_1\circ m_2\circ q'_2  
+	\end{split}\]
+	\[\begin{split}
+	y_2\circ a_3&= d_3\circ q_3'\\&=y_2\circ m_3\circ q'_3
+	\end{split}\qquad \begin{split}
+	u_2\circ a_2&= d_2\circ q_2'\\&=u_2\circ m_2\circ q'_2
+	\end{split}\]
+	And we have done.
+\end{proof}

### 2025-02-14 calco/Hypergraphs_with_equivalences.tex
labeled eqhyp

@@
 
-	Now, notice that  $m_3$ and $m_2$ are monos because $d_3$ and $d_2$ are regular monos. By the proof of \Cref{prop:limits}, to conclude it is enough to show that
+	Now, notice that  $m_3$ and $m_2$ are monos because $d_3$ and $d_2$ are regular monos. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
 	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
 
-	Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $a_3$ and $a_2$ and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:limits}.
+	Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $a_3$ and $a_2$ and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:eqhyp_complete}.
 

### 2025-02-18 calco/main.tex
labeled eqhyp
eggs minima
minori

@@
-\documentclass[runningheads,envcountsect]{lipics-v2021}
-
+\documentclass[a4paper,UKenglish,cleveref,pdftex,thm-restate,numberwithinsect]{lipics-v2021}
 \usepackage{stmaryrd}
@@
 \todo{A very nice introduction}
-\section{$\mathcal{M}$-adhesive categories}
+\section{$\mathcal{M}$-adhesive categories}\label{sec:ade}
 
@@
 In order to define it we need to introduce some terminology.  Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is called
-\begin{itemize}
-	\item		\emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one  below, if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
-	\[\xymatrix{A \ar[r]^{f} \ar[d]_{m}& B \ar[d]^{n} \\ C \ar[r]_{g} & D}\]
+
+\parbox{11cm}{\begin{itemize}
+	\item		\emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one aside, if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
 		\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable.
-\end{itemize}
+\end{itemize}}\hfill
+\parbox{1cm}{
+\xymatrix{A \ar[r]^{f} \ar[d]_{m}& B \ar[d]^{n} \\ C \ar[r]_{g} & D}}
 
@@
 Finally, another  useful properties of $\mathcal{M}$-adhesive category are the following.
-\begin{proposition}\label[proposition]{prop:regmono}
+\begin{restatable}{proposition}{regmono}\label[proposition]{prop:regmono}
 	If $\X$ is $\mathcal{M}$-adhesive then the following are true:
@@
 	\end{enumerate}
-\end{proposition}
-\begin{proof}
-	\begin{enumerate}
-		\item  Consider the following cube in which the bottom face is an $\mathcal{M}$-pushout.
-		\[\xymatrix@C=15pt@R=9pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_(.6){\id{B}} \\ A  \ar@{>->}[dd]_{m}\ar[rr]^(.65){g} & & B \ar@{>->}[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{f} & & D}\]
-		By construction the top face of the cube is a pushout and the back one a pullback.
-The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the thesis follows.
-		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback.
-		\[\xymatrix{X \ar@{>->}[r]^{m} \ar@{>->}[d]_{m}& Y \ar@{>->}[d]^{h}\\ Y \ar@{>->}[r]^{k} & Z}\]
-		It is now immediate to see that $m$ is the equalizer of $h$ and $k$.  
-	\end{enumerate}
-\end{proof}
+\end{restatable}
+  [Proof in \Cref{regmono-proof}]
 
@@
 
-\Cref{prop:left,prop:com} allows us to deduce immediately the following.
+\Cref{prop:left,prop:com} allow us to deduce immediately the following.
 
@@
 
-\subsubsection{Labelling hypergraph with an algebraic signature}
+\subsubsection{Labelling hypergraph with an algebraic signature}\label{sssect:hyp_alg_sign}
 
@@
 \input{Hypergraphs_with_equivalences}
+%\input{Labeled_hyp_with_eq}
 
@@
 \appendix
+
+\section{Omitted proofs}
+\subsection{Proofs for \Cref{sec:ade}}
+\regmono*
+
+\begin{proof}\label{regmono-proof}
+	\begin{enumerate}
+		\item  Consider the following cube in which the bottom face is an $\mathcal{M}$-pushout.
+		\[\xymatrix@C=15pt@R=9pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_(.6){\id{B}} \\ A  \ar@{>->}[dd]_{m}\ar[rr]^(.65){g} & & B \ar@{>->}[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{f} & & D}\]
+		By construction the top face of the cube is a pushout and the back one a pullback.
+The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the thesis follows.
+		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback.
+		\[\xymatrix{X \ar@{>->}[r]^{m} \ar@{>->}[d]_{m}& Y \ar@{>->}[d]^{h}\\ Y \ar@{>->}[r]^{k} & Z}\]
+		It is now immediate to see that $m$ is the equalizer of $h$ and $k$.   \qedhere
+	\end{enumerate}
+\end{proof}
+
 \section{Some properties of comma categories}

### 2025-02-18 calco/Labeled_hyp_with_eq.tex

\subsection{Labeled Hypergraphs with Equivalences}

As we have done in \Cref{sssect:hyp_alg_sign}, we can define the category of hypergraphs with equivqlence labeled over an algebraic signature.

\begin{definition}
	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be an algebraic signature, and let $\mathcal{G}^{\Sigma}$ the hypergraph associated to $\Sigma$.
	Then, the \emph{hypergraph with equivalence} associated to $\Sigma$ is $L(\mathcal{G}^\Sigma)$, and the category of hypergraphs with equivalence labeled over $\Sigma$ is the 
	slice category $\EqHyp_\Sigma := \EqHyp/L(\mathcal{G}^\Sigma)$.
\end{definition}

By \Cref{thm:slice_functors}, we can deduce the following.

\begin{proposition}
	$\EqHyp_\Sigma$ is $\reg (\EqHyp_\Sigma)$-adhesive.
\end{proposition}

### 2025-02-18 calco/eggs.tex

\section{EGGs}

\todo{introduction}

\begin{definition}
	Let $\mathcal{G} = (E, V, C, s, t, q)$ be a hypergraph with equivalence, and let $(S, \pi_1, \pi_2)$ be the kernel pair of $q^\star \circ s$.
	Then, $\mathcal{G}$ is an \emph{e-hypergraph} whenever $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
	$\egg$ is the full subcategory of $\EqHyp$ where objects are e-hypergraphs, and $I: \egg \to \EqHyp$ is the inclusion functor.
\end{definition}

\begin{lemma}
	$\egg$ has all limits, and $I$ preserves them.
\end{lemma}

\beign{proof}

\end{proof}

### 2025-02-18 calco/eggs.tex
labeled eqhyp

@@
 
-\beign{proof}
+\begin{proof}
+        Let $D: \cat{I} \to \egg$ be a diagram, with $D(i) = (A_i, B_i, C_i, s_i, t_i, q_i)$, let $(U_i, u_1^i, u_2^i)$ be the kernel pair of $q_i\circ s_i$.
+	Let now be $(A, B, C, s, t, q)$, togehter with projections $(\pi_E^i, \pi_V^i, \pi_C^i)_{i \in \cat I}$ the limit of $I \circ D$,
+	let $(U, u_1, u_2)$ be the kernel pair of $q\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ D$.
+        By construction (proof of \Cref{prop:eqhyp_complete}), there exists a monomorphism $m: C \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
+        \begin{align*}
+                q_i^\star \circ s_i\circ \pi^i_E\circ u_1      &= q_i^\star\circ (\pi^i_V)^\star \circ s\circ u_1\\
+                                                        &= (\pi_C^i)^\star\circ q^\star\circ s\circ u_1\\
+                                                        &=(\pi_C^i)^\star\circ q^\star\circ s\circ u_2\\
+                                                        &= q_i^\star \circ s_i \circ \pi_E^i \circ u_2
+        \end{align*}
+        Then, for each $i$, there exists an arrow $a_i:U\to U_i$ making the following diagram to commute
+	\[
+                \xymatrix{
+			U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_i} & A \ar[drr]^{\pi_E^i} && \\
+			A \ar[ddr]_{\pi_E^i} & U_i \ar[rr]_{u_1^i} \ar[dd]^{u_2^i}&& A_i \ar[d]^{s_i} \\
+					     & & & B_i \ar[d]^{q_i}\\
+					     & A_i \ar[r]_{s_i} & B_i \ar[r]_{q_i}& C_i
+                }
+        \]
+        We have then
+        \begin{align*}
+                l_i^\star\circ m^\star \circ q^\star \circ t \circ u_1    &= q_i^\star\circ (\pi_V^i)^\star \circ t \circ u_1 \\
+                                                        &= q_i^\star \circ t_i \circ \pi_E^i \circ u_1 \\
+                                                        &= q_i^\star \circ t_i \circ u_1^i \circ a_i \\
+                                                        &= q_i^\star \circ t_i \circ u_2^i \circ a_i \\
+                                                        &= q_i^\star \circ t_i \circ \pi_E^i \circ u_2 \\
+                                                        &= q_i^\star \circ (\pi_V^i)^\star \circ t \circ u_2 \\
+                                                        &= l_i^\star \circ m^\star \circ q^\star \circ t \circ u_2
+        \end{align*}
+        By universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$, and, since $m$ is mono, $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the thesis.
+\end{proof}
 
+\begin{corollary}
+	$I$ creates limits.
+\end{corollary}
+
+\begin{corollary}
+	$h: \mathcal{G \to H}$ is a regular mono in $\egg$ if and only if it is a regular mono in $\EqHyp$.
+\end{corollary}
+
+\begin{lemma}
+	Consider the following pushout square in $\EqHyp$.
+	\[\xymatrix{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{k}&\mathcal{P}}\]
+with $m$ regular mono. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is an e-hypergraph too, and $n$ is regular mono.
+\end{lemma}
+
+\begin{proof}
+	Let $\mathcal{P} = (A, B, C, s, t, q)$, $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, and let $(U, u_1, u_2)$ the kernel pair of $q^\star \circ s$ .
+	Consider then the following situation.
+	\[\xymatrix@C=10pt@R=6pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar[dl]_{k_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){k_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{C_1^\star}\ar[rr]|\hole^(.65){h_C^\star}\ar[dl]^{m_C^\star} && {C_2^\star} \ar[dl]^{n_C^\star} \\{C_3^\star} \ar[rr]_{k_C^\star} & & C}\]
+	Since $m$ is regular mono, $m_C$ is mono ({\color{red}{inserire citazione}}).
+Then, by adhesivity of $\Set$, the bottom face is a Van Kampen square, hence a pushout.
+Therefore, by ({\color{red}{citazione}}), the square below is a pushout.
+	\[\xymatrix{K_1\ar[r]^{f_k}\ar[d]_{f_m}&K_2\ar[d]^{f_n}\\K_3\ar[r]_{f_k}&U}\]
 \end{proof}

### 2025-02-18 calco/main.tex
minori

@@
 \newcommand{\eg}[1]{\mathbf{EqGraph}_{\textbf {\textup{#1}}}}
-\newcommand{\egg}[1]{\mathbf{EGG}_{\textbf {\textup{#1}}}}
+%\newcommand{\egg}[1]{\mathbf{EGG}_{\textbf {\textup{#1}}}}
 
@@
 \newcommand{\Dwnarrow}{\Downarrow \hspace{-2pt}}
+\newcommand{\egg}{\catname{EGG}}
 
@@
 	\begin{definition}
-	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the following diagram.
-
-		\[
-	\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }\]
-
-	We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
+
+	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the cube below on the right.
+
+\parbox{9.5cm}{We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
 	\begin{enumerate}
@@
 		if and only if the front and right faces are pullbacks.
-	\end{enumerate}
+	\end{enumerate}} \hfill
+	\parbox{3cm}{
+	\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }
+}
 
@@
 
+\iffalse 
 \begin{remark}\label{rem:deco}
-	We can point out an important property of strict $\mathcal{M}$-adhesive categories with pullbacks and consider the $\mathcal{M}$-pushout square below.
-	\[\xymatrix{A \ar[r]^{f} \ar@{>->}[d]_{m}& B \ar@{>->}[d]^{n}\\ C \ar[r]_{g} & D}\]
-
-	Given an arrow $d\colon X\to D$, we can present the object $X$ has a pushout: indeed, consider the following cube, in which all the three vertical squares are pullbacks.
-	\[
-	\xymatrix@C=15pt@R=9pt{&V\ar[dd]|\hole_(.65){a}\ar[rr]^{v} \ar@{>.>}[dl]_{u} && Y \ar[dd]^{b} \ar@{>->}[dl]_{y} \\ Z  \ar[dd]_{c}\ar[rr]^(.7){z} & & X \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{g} & & D }\]
+We can point out an important property of strict $\mathcal{M}$-adhesive categories with pullbacks.  Consider the solid part of the cube aside, whose bottom case is an $\mathcal{M}$-pushout.
+
+	\parbox{9.5cm}{	Given an arrow $d\colon X\to D$, we can present the object $X$ has a pushout: indeed, consider the following cube, in which all the three vertical squares are pullbacks.}
+	\parbox{3cm}{
+	\xymatrix@C=15pt@R=9pt{&V\ar[dd]|\hole_(.65){a}\ar[rr]^{v} \ar@{>.>}[dl]_{u} && Y \ar[dd]^{b} \ar@{>->}[dl]_{y} \\ Z  \ar[dd]_{c}\ar[rr]^(.7){z} & & X \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{g} & & D }}
 
@@
 \end{remark}
-
-Finally, another  useful properties of $\mathcal{M}$-adhesive category are the following.
+\fi
+
+We can state some useful properties of $\mathcal{M}$-adhesive category.
 \begin{restatable}{proposition}{regmono}\label[proposition]{prop:regmono}
@@
 
-\begin{definition}[Kernel Pair]
-    A \emph{kernel pair} for an arrow $f: A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f : K_f \to A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the following square is a pullback.
-    \[
-        \begin{tikzcd}
-            K_f \ar[r, "{\pi^1_f}"] \ar[d, "{\pi^2_f}" swap] & A \arrow[d, "f"] \\
-            A \ar[r, "f"swap] & B
-        \end{tikzcd}
-    \]
-\end{definition}
-
-\begin{remark}
-	If a category $\cat{C}$ has pullbacks then every arrow has a kernel pair.
+In this section we recall the definition and some useful properties of \emph{kernel pairs} which will be useful in the next sections.
+
+\noindent 
+\parbox{11cm}{
+\begin{definition}
+    A \emph{kernel pair} for an arrow $f\colon A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f\colon K_f \rightrightarrows A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the following square is a pullback.
+\end{definition}}\hfill 
+\parbox{2cm}{\xymatrix@R=15pt{K_f \ar[r]_{\pi^1_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}}
+
+\begin{remark}\label{prop:pairng_of_kernel_pairs_mono}
+If $(K_f, \pi^1_f, \pi^2_f)$ is a a kernel pair for $f\colon X \to Y$ and a product of $X$ with itself exists, then the canonical arrow $\langle \pi^1_f, \pi^2_f\rangle \colon K_f \to X \times X$ is a mono.
 \end{remark}
 
-\begin{remark}
-    Since a kernel pair is nothing more that a pullback, that is, a limit, by \Cref{rem:limits_are_unique_up_to_isomorphisms}, it make sense to refer to it as \emph{the} kernel pair for a morphism $f$.
+\begin{remark}\label{prop:kermono}
+An arrow $m\colon M\to X$ is a mono if and only if it admits $(M, \id{M}, \id{M})$ as a kernel pair.
 \end{remark}
 
-\begin{example}\label[example]{ex:kernel_pairs_in_Set}
-    In $\Set$, a kernel pair for a function $f: A\to B$ is the set
-    \[
-        K_f=\{(x, y) \in A \times A \mid f(x) = f(y)\}
-    \]
-    together with the canonical projection on the first and the second component of the pairs.
-\end{example}
-
-\begin{proposition}\label[proposition]{prop:pairng_of_kernel_pairs_mono}
-    Let $(K, p_1, p_2)$ be the kernel pair of $f: X \to Y$, and let $(X\times X, \pi_1, \pi_2)$ be the product of $X$ with itself.
-Then, the mediating arrow $\langle p_1, p_2\rangle : K \to X \times X$ is mono.
-\end{proposition}
-
-\begin{proof}
-	Suppose $\langle p_1, p_2 \rangle \circ f = \langle p_1, p_2 \rangle \circ g$ for $f, g: Z \to K$. Then, we have
-	\[
-		\begin{split}
-			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
-			\pi_1 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_1 \circ \langle p_1, p_2 \rangle \circ g \\
-			p_1 \circ f &= p_1 \circ g
-		\end{split}
-		\qquad
-		\begin{split}
-			\langle p_1, p_2 \rangle \circ f &=  \langle p_1, p_2 \rangle \circ g \\
-			\pi_2 \circ \langle p_1, p_2 \rangle \circ f &=  \pi_2 \circ \langle p_1, p_2 \rangle \circ g \\
-			p_2 \circ f &= p_2 \circ g
-		\end{split}
-	\]
-	Thus, from the universal property of the pullback, $f = g$.   
-\end{proof}
-
-\begin{proposition}\label[proposition]{prop:kermono}
-	An arrow $m\colon M\to X$ is mono if and only if $(M, MM, \id{M})$ is a kernel pair for it.
-\end{proposition}
-
-\begin{proof}
-    To prove the ``if'' part of the statement, let $f, g: A \to M$ be such that $m\circ f = m\circ g$, and consider the following situation.
-    \[
-        \begin{tikzcd}[row sep=26, column sep = 26]
-        A \arrow[drr, bend left=30, "f"] \arrow[ddr, bend right=30,"g" swap] \arrow[dr, dashed, "u"] & & \\
-        & M  \arrow[d, "{\id{M}}"] \arrow[r, "{\id{M}}"] & M \arrow[d, "m"] \\
-        & M  \arrow[r, "m" swap] & X
-        \end{tikzcd}
-    \]
-    For the universal property of pullbacks, we have that $$f  =  \id{M} \circ u =  g$$
-    Hence, $m$ is mono.
-
-    Conversely, if $m$ is mono, then, we have that
-    \begin{align*}
-        m \circ f = m \circ g   &\Rightarrow    f = g \\
-                                &\Rightarrow    f \circ \id{M} = g\circ \id{M}
-    \end{align*}
-    Hence, $f$ is the unique arrow that makes the commutative square illustrated above a pushout.   
-\end{proof}
-
-\begin{remark}\label{rem:monos_in_presh_cats}
-    From characterization of monos via pullbacks in \Cref{prop:kermono} and \Cref{lemma:limits_of_presheaves}, we have that a mono in a category of presheaves is a natural transformation of which each component is mono.
-\end{remark}
-
-\begin{corollary}\label[corollary]{cor:kermono}
-	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$ if and only if, for each mono $m\colon Y\to Z$, $(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair also for $m\circ f$.
-\end{corollary}
-\begin{proof}
-    It is enough to see that, by \Cref{lemma:pullback_lemma} and \Cref{prop:kermono} the outer boundary of the following square is a pullback.
-        \[\begin{tikzcd}[row sep=13 pt, column sep=13 pt]
-    	{K_f} && X && X \\
-    	\\
-    	X && Y && Y \\
-    	\\
-    	X && Y && Z
-    	\arrow["{\pi_f^2}", from=1-1, to=1-3]
-    	\arrow["{\pi_f^2}"', from=1-1, to=3-1]
-    	\arrow["{id{X}}", from=1-3, to=1-5]
-    	\arrow["f", from=1-3, to=3-3]
-    	\arrow["f", from=1-5, to=3-5]
-    	\arrow["f", from=3-1, to=3-3]
-    	\arrow["{id_X}"', from=3-1, to=5-1]
-    	\arrow["{id_Y}", from=3-3, to=3-5]
-    	\arrow["{id_Y}", from=3-3, to=5-3]
-    	\arrow["m", from=3-5, to=5-5]
-    	\arrow["f"', from=5-1, to=5-3]
-    	\arrow["m"', from=5-3, to=5-5]
-    \end{tikzcd}\]
-    The leftward part of the statement follows by definition of monomorphism an \Cref{lemma:pullback_lemma}.   
-\end{proof}
-
-\begin{lemma}\label[lemma]{lemma:kern_pairs_pres_pullbacks}
-    Suppose the following situation, and that $f: X \to Y$ and $g: Z \to W$ have kernel pairs.
-    \[
-        \begin{tikzcd}
-            X \ar[r, "h"] \ar[d, "f"swap] & Z \ar[d, "g"] \\
-            Y \ar[r, "t"swap] & W
-        \end{tikzcd}
-    \]
-
-    Then, there exists a unique arrow $k_h: K_f \to K_g$ making the squares below commute.
-    \[
-        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
-            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^1}"swap] & K_g \ar[d, "{\pi_g^1}"] \\
-            X \ar[r, "h"swap] & Z 
-        \end{tikzcd}
-        \qquad
-        \begin{tikzcd}[row sep = 25 pt, column sep= 25 pt]
-            K_f \ar[r, dashed, "{k_h}"] \ar[d, "{\pi_f^2}"swap] & K_g \ar[d, "{\pi_g^2}"] \\
-            X \ar[r, "h"swap] & Z 
-        \end{tikzcd}
-    \]
-
-    Moreover, if the beginning square is a pullback, then also the preceding ones are so.
-\end{lemma}
-
-\begin{proof}
-    Computing, we have
-    \begin{align*}
-        g \circ h \circ \pi_f^1 &=  t \circ f \circ \pi_f^1     \\
-                                &=  t \circ f \circ \pi_f^2     \\
-                                &=  g \circ h \circ \pi_f^2
-    \end{align*}
-    By the universal property of $K_g$ as the pullback of $g$ along itself, such $k_h$ exists and it is unique.
-
-    To prove the second half of the thesis, let us consider the two rectangles below, which, by \Cref{lemma:pullback_lemma} are pullbacks.
-    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
-	{K_f} & X & Z \\
-	X & Y & W
-	\arrow["{\pi_f^1}", from=1-1, to=1-2]
-	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
-	\arrow["h", from=1-2, to=1-3]
-	\arrow["f", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["f"', from=2-1, to=2-2]
-	\arrow["t"', from=2-2, to=2-3]
-    \end{tikzcd}
-    \qquad
-    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
-	{K_f} & X & Z \\
-	X & Y & W
-	\arrow["{\pi_f^2}", from=1-1, to=1-2]
-	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
-	\arrow["h", from=1-2, to=1-3]
-	\arrow["f", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["f"', from=2-1, to=2-2]
-	\arrow["t"', from=2-2, to=2-3]
-    \end{tikzcd}
-    \]
-    But then the following ones are pullbacks too.
-    \[\begin{tikzcd}[row sep= 25 pt, column sep= 25 pt]
-	{K_f} & {K_g} & Z \\
-	X & Y & W
-	\arrow["{k_h}"', from=1-1, to=1-2]
-	\arrow["{\pi_f^1}"', from=1-1, to=2-1]
-	\arrow["{\pi_g^2}"', from=1-2, to=1-3]
-	\arrow["{\pi_g^1}", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["h", from=2-1, to=2-2]
-	\arrow["g", from=2-2, to=2-3]
-        \arrow["{h\circ \pi_f^2}", from=1-1, to=1-3, bend left = 30]
-        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
-    \end{tikzcd}
-    \qquad
-    \begin{tikzcd}[row sep = 25 pt, column sep=25 pt]
-	{K_f} & {K_g} & Z \\
-	X & Y & W
-	\arrow["{k_h}"', from=1-1, to=1-2]
-	\arrow["{\pi_f^2}"', from=1-1, to=2-1]
-	\arrow["{\pi_g^1}"', from=1-2, to=1-3]
-	\arrow["{\pi_g^2}", from=1-2, to=2-2]
-	\arrow["g", from=1-3, to=2-3]
-	\arrow["h", from=2-1, to=2-2]
-	\arrow["g", from=2-2, to=2-3]
-        \arrow["{h\circ \pi_f^1}", from=1-1, to=1-3, bend left = 30]
-        \arrow["{t \circ f}"', from=2-1, to=2-3, bend right = 30]
-    \end{tikzcd}
-    \]
-
-    The thesis follows again by \Cref{lemma:pullback_lemma}.   
-\end{proof}
-
-\begin{proposition}\label[proposition]{prop:reg_epi_coeq}
-    Let $e: X \to Y$ be a regular epimorphism in a category $\cat C$ with a kernel pair $(K, \pi_1, \pi_2)$. Then, $e$ is the coequalizer of $\pi_1$ and $\pi_2$.
-\end{proposition}
-
-\begin{proof}
-    By hypothesis, there exists a pair $f, g: Z \to X$ of which $e$ is the coequalizer. Since $e \circ f = e \circ g$, we have
-    \[
-        \begin{tikzcd}[row sep= 20, column sep = 13]
-            Z \ar[drr, "f", bend left=30] \ar[ddr, "g"swap, bend right=30] \ar[dr, dashed, "k"] & & \\
-            & K \ar[r, "{\pi_1}"] \ar[d, "{\pi_2}" swap] & X \ar[d, "e"] \\
-            & X \ar[r, "e"swap] & Y
-        \end{tikzcd}
-    \]
-    thus there exists the unique $k: Z \to K$. Let now $h: Z \to V$ be an arrow such that $h \circ \pi_1 = h \circ \pi_2$, then
-    \begin{align*}
-        h \circ f &= h \circ \pi_1 \circ k \\
-                  &= h \circ \pi_2 \circ k \\
-                  &= h \circ g
-    \end{align*}
-    and thus there exists a unique $l: Y \to V$ such that $l \circ e = h$.   
-\end{proof}
-
-\begin{corollary}\label[corollary]{cor:reg_epi_components_reg_epi_nat_trans}
-    Let $\cat C$ be a category with pullbacks and $\phi : D \dot\to D'$ be a natural transformation between two functors $D, D': \cat{I \to C}$.
-If $\phi_i$ is a regular epi for every $i$, then $\phi$ is a regular epi.
-\end{corollary}
-
-\begin{proof}
-    Let $(K_i, \pi_i^1, \pi_i^2)$ be the kernel pair of $\phi_i$ for each $i$. Given an arrow $\alpha: i \to j$ of $\cat I$, we have
-    \begin{align*}
-        \phi_j \circ D(\alpha) \circ \pi_i^1 &= D'(\alpha) \circ \phi_i \circ \pi_i^1 \\
-                                             &= D'(\alpha) \circ \phi_i \circ \pi_i^2 \\
-                                             &= \phi_j \circ D(\alpha) \circ \pi_i^2
-    \end{align*}
-    Thus, the outer boundary of the diagram below commutes, yielding the arrow $K(\alpha)$
-    \[
-        \begin{tikzcd}[row sep=26, column sep=26]
-            {K_i} \ar[r, "{\pi_i^1}"] \ar[d, "{\pi_i^2}"swap] \ar[dr, dashed, "{K(\alpha)}"] & D(i) \ar[dr, "{D(\alpha)}"] \\
-            D(i) \ar[dr, "{D(\alpha)}"swap] & K_j \ar[r, "{\pi_j^1}"] \ar[d, "{\pi_j^2}"swap] & D(j) \ar[d, "{\phi_j}"] \\
-            & D(j) \ar[r, "{\phi_j}"swap] & D'(j)
-        \end{tikzcd}
-    \]
-
-    In this way, we get a functor $K: \cat{I \to C}$, 
-    which maps each $i$ onto $K_i$ and each arrow $\alpha$ onto $K(\alpha)$. 
-	We have in fact $K(id_i) : K_i \to K_i$ is the arrow such that
-        \[
-            \begin{split}
-                D(id_i) \circ \pi_i^1 &= \pi_i^1 \circ K(id_i) \\
-                \pi_i^1 &= \pi_i^1 \circ K(id_i)
-            \end{split}
-                \qquad
-            \begin{split}
-                D(id_i) \circ \pi_i^2 &= \pi_i^2 \circ K(id_i) \\
-                \pi_i^2 &= \pi_i^2 \circ K(id_i)
-            \end{split}
-        \]
-	Thus, for the universal property of pullbacks, $K(id_i) = id_{K_i}$.
-
-        Suppose now $\alpha : i \to j$ and $\beta: j \to k$. Computing, we have
-        \[
-            \begin{split}
-                \pi_k^1 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^1 \\
-                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^1 \\
-                                                    &= D(\beta) \circ \pi_j^1 \circ K(\alpha) \\
-                                                    &= \pi_k^1 \circ K(\beta) \circ K(\alpha)
-            \end{split} \qquad
-            \begin{split}
-                \pi_k^2 \circ K(\beta \circ \alpha) &= D(\beta \circ \alpha) \circ \pi_i^2 \\
-                                                    &= D(\beta) \circ D(\alpha) \circ \pi_i^2 \\
-                                                    &= D(\beta) \circ \pi_j^2 \circ K(\alpha) \\
-                                                    &= \pi_k^2 \circ K(\beta) \circ K(\alpha)
-            \end{split}
-        \]
-        Again, for universal property of pullbacks, necessarily we have $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving functoriality of $K$.
-
-     Hence, we have two natural transformations $\pi^1, \pi^2 : E \dot\to D$.
-By \Cref{prop:reg_epi_coeq}, every component $\phi_i$ is the coequalizer of $\pi_i^1, \pi_i^2: E \to D$, and so $\phi$ is the coequalizer of $\pi^1$ and $\pi^2$.
-\end{proof}
-
-\begin{lemma}\label[lemma]{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
-    Let $D, D': \cat{I \to C}$ be two diagrams, and let $((c_i)_{i \in \cat I}, C)$ and $((c_i')_{i\in \cat I}, C')$ be, respectively, the colimit of $D$ and $D'$.
-If $\cat C$ has all colimits, for diagrams of shape $\cat I$ and $\phi: D \dot\to D'$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $C$ to $C'$ (\Cref{prop:nat_tran_induces_unique_arrow_between_colimits}) is a regular epimorphism too.
-\end{lemma}
-
-\begin{proof}
-    By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi: D \dot\to D'$ is a regular epimorphism, so that there is a functor $E: \cat{I \to C}$ and $\eta, \theta: E \dot\to D$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
-Let now $((p_i)_{i \in \cat I}, P)$ be the colimit of $E$, by \Cref{prop:nat_tran_induces_unique_arrow_between_colimits}, we have $a, b: P \to C$ fitting in the diagram below.
-    \[
-        \begin{tikzcd}[row sep = 26, column sep = 26]
-            E(i) \ar[r, "{p_i}"] \ar[d, "{\eta_i}"swap] & P \ar[d, dashed, "a"] \\
-            D(i) \ar[r, "{c_i}"swap] & C
-        \end{tikzcd}
-        \qquad
-        \begin{tikzcd}[row sep = 26, column sep = 26]
-            E(i) \ar[r, "{p_i}"] \ar[d, "{\theta_i}"swap] & P \ar[d, dashed, "b"] \\
-            D(i) \ar[r, "{c_i}"swap] & C
-        \end{tikzcd}
-    \]
-
-    We want to show that $c$ coequalizes $\eta$ and $\theta$. Let thus $t: C \to T$ be an arrow such that $t \circ a = t \circ b$. Then, for every $i$, we have
-    \begin{align*}
-        t \circ c_i \circ \eta_i &= t \circ a \circ p_i \\
-                                 &= t \circ b \circ p_i \\
-                                 &= t \circ c_i \circ \theta_i
-    \end{align*}
-
-    Thus, there is $t_i: D(i) \to T$ such that $t\circ c_i = t_i \circ \phi_i$.
-It is now easy to see that $((t_i)_{i \in \cat I}, T)$ is a cocone of $D'$: suppose $\alpha: i \to j$ be an arrow of $\cat I$, obtaining
-    \begin{align*}
-        t_i \circ \phi_i &= t \circ c_i \\
-                         &= t \circ c_j \circ D(\alpha) \\
-                         &= t_j \circ \phi_j \circ D(\alpha) \\
-                         &= t_j \circ D'(\alpha) \circ \phi_i
-    \end{align*}
-    By the hypothesis that $\phi_i$ is regular epi for each $i$, therefore epi (by the dual of \Cref{prop:eq_are_mono}), we can conclude $t_i = t_j \circ D'(\alpha)$.
-
-    Hence, we have an arrow $k: C' \to T$ such that $k \circ c_i' = t_i$. But then
-    \begin{align*}
-        c \circ c \circ c_i &= k \circ c_i' \circ \phi_i \\
-                            &= t_i \circ \phi \\
-                            &= t \circ c_i
-    \end{align*}
-    Showing that $k \circ c = t$.
-
-    For the uniqueness, let $k': C' \to T$ be another arrow such that $k' \circ c = t$. Then we have
-    \begin{align*}
-        k' \circ c_i' \circ \phi_i &= k' \circ c \circ c_i \\
-                                   &= t \circ c_i \\
-                                   &= t_i \circ \phi_i
-    \end{align*}    
-    Since $\phi_i$ is a regular epimorphism, we have $k' \circ c_i' = t_i$, and, because $k \circ c_i' = t_i$ by construction, we can conclude that $k'=k$ since $((c_i')_{i \in \cat I}, C')$ is a colimit.
-\end{proof}
+Together with \Cref{lem:pb1}, the two previous remarks while elementary, allow us to prove the following result.
+
+\begin{proposition}\label{cor:kermono}
+	Let $f\colon X\to Y$ be an arrow and $m\colon Y\to Z$ be a mono. If
+	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$, then it is also a kernel pair for $m\circ f$.
+\end{proposition}
+
+We are now going to explore some further properties of kernel pairs
+
+\begin{restatable}{lemma}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
+	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given.
+Then there exists a a unique arrow $k_h: K_f \to K_g$ compliting them.
+	\[\xymatrix{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
+
+    Moreover, if the leftmost is a pullback, then also the other ones are so.
+\end{restatable}
+[Proof in \Cref{kpp-proof}]
+
+The previous result allows us to deduce the following lemma in an $\mathcal{M}$-adhesive context.
+
+\noindent
+\parbox{7cm}{
+\begin{restatable}{lemma}{mpo}\label{lem:mpo}
+	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top face is an $\mathcal{M}$-pushout. Then the right square is a pushout.
+\end{restatable}}\hfill 
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_{m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_{n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+
+[Proof in \Cref{mpo-proof}]
+
+As a final step, we explore the relationship between regular epimorphisms and kernel pairs.
+
+\begin{restatable}{proposition}{epic}\label{prop:reg_epi_coeq}
+    Let $e\colon X \to Y$ be a regular epimorphism in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then, $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
+\end{restatable}
+[Proof in \Cref{epic-proof}]
+
+\begin{restatable}{corollary}{natepi}\label{cor:reg_epi_components_reg_epi_nat_trans}
+    Let $\X$ be a category with pullbacks and $\phi\colon F \dot\to G$ be a natural transformation between two functors $F, G: \D \rightrightarrows \X$.
+If $\phi_d$ is a regular epi for every $d$ in $\D$, then $\phi$ is a regular epi.
+\end{restatable}
+[Proof in \Cref{natepi-proof}]
+
+From the previous result we can now deduce that the class of regular epis is closed under colimits, as shown by the next lemma
+\begin{restatable}{lemma}{epicol}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
+    Let $F,G'\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
+Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in \S})$ be, respectively, the colimit of $F$ and $G$.
+If $\phi\colon  F \to G$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $X$ to $Y$ is a regular epimorphism too.
+\end{restatable}
+[Proof in \Cref{epicol-proof}]
 
@@
 
-We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as setof nodes, so that $1^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, where $\delta_1$ picks the element $1$.
+We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes, so that $1^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, where $\delta_1$ picks the element $1$.
 The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
@@
 
-\section{EGGS}
+\input{eggs}
 
@@
 \section{Omitted proofs}
+
+This section contains the proofs which are omitted from the main body oof the paper. We begin stating  a well-known fact about composition and decomposition of pullbacks \cite{mac2013categories}.
+
+\noindent
+\parbox{10cm}{
+\begin{lemma}\label{lem:pb1}
+	Let $\X$ be a category, and consider the diagram aside, in which the right square is a pullback. Then the whole rectangle is a pullback if and only if the left square is one.
+\end{lemma}} 
+	\parbox{4cm}{
+	\xymatrix@R=18pt{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}}
+\begin{proof}
+	$(\Rightarrow)$ Let $q_1\colon Q\to Y$ and $q_2\colon Q\to A$ be two arrows such that $b\circ q_1=h\circ q_2$, if we compute we get
+	\[c\circ g\circ q_1  =k\circ b\circ q_1=k\circ h\circ q_2\]
+	\parbox{9cm}{Thus by the pullback property of the whole rectangle we get the dotted $l$ in the diagram on the side. 
+	All we have to prove is that $f\circ l=q_1$. By construction we know that $g\circ f\circ l= g\circ q_1$, while we also have}
+	\hfill \parbox{4cm}{\xymatrix@R=18pt{Q \ar@/_.3cm/[dr]_{q_2}\ar@/^.4cm/[rrr]^{g\circ q_1} \ar@{.>}[r]_{l} & X \ar[d]_{a} \ar[r]_{f}& \ar[r]_{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ & A \ar[r]_{h}& B \ar[r]_{k}& C}}
+	\[	b\circ f\circ l = h\circ a\circ l= h\circ q_2=b\circ q_1\]
+	and we can conclude since the right square in the original diagram is a pullback.
+
+	For uniqueness: if $l'\colon Q\to X$ is such that $f\circ l'= q_1$ and $a\circ l'=q_2$
+	then  $g\circ f \circ l' = g\circ q_1$ and we can conclude applying the pullback property of the outer rectangle.
+
+	\smallskip \noindent 
+	\parbox{9cm}{
+	$(\Leftarrow)$ Take two arrows $q_1\colon Q\to Z$ and $q_2\colon Q\to A$ such that $c\circ q_1=k\circ h \circ q_2$
+	We can apply the pullback property of the right square to get the dotted $q\colon Q\to Y$ in the following
+
+	Now, by construction we have $b\circ q =h\circ q_2$
+	and thus, since the left square is a pullback, we get also a unique $l\colon Q\to X$ such that  $f\circ l = q$ and $a \circ l = q_2$
+	but then we clearly have} \hfill 
+	\parbox{6cm}{\vspace{7pt}
+		\xymatrix@R=18pt{Q \ar@/_.3cm/[ddr]_{q_2}\ar@/^.5cm/[drrr]^{ q_1} \ar@{.>}@/^.3cm/[drr]^(.6){ q} \ar@{.>}[dr]^{l}  \\& X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]_{b}& Z \ar[d]^{c}\\ & A \ar[r]_{h}& B \ar[r]_{k}& C}}
+	\[	g\circ f \circ l = g\circ q = q_1	\]
+
+	We are left with uniqueness. Let $l'\colon Q\to X$ be another arrow such that $q_1 = g\circ f \circ l'$ and $q_2=a\circ l'$,  then we must also have
+	\[
+	b\circ f \circ l'= h\circ a \circ l' = h\circ q_2= b\circ q\]
+	which implies $f\circ l' = q$, from which $l=l'$ follows.
+\end{proof}
+
 \subsection{Proofs for \Cref{sec:ade}}
@@
 	\end{enumerate}
+\end{proof}
+
+\kpp*
+\begin{proof}\label{kpp-proof}
+Computing, we have
+\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]
+
+Therefore the existence  and uniqueness of the wanted $k_h$ follows at once from the the universal property of $K_g$ as the pullback of $g$ along itself.
+
+To prove the second half of the thesis, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
+\[\xymatrix{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
+	X \ar[r]_{f}& Y \ar[r]_{t} & W & X \ar[r]_{f} & Y  \ar[r]_{t}& W}\]
+
+But then the following ones are pullbacks too.
+\[\xymatrix{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
+	X \ar[r]_{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]_{g} & W & X \ar[r]_{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]_{g} & W}\]
+
+The thesis now follows again by \Cref{lem:pb1}.   
+\end{proof}
+
+\noindent
+\parbox{7cm}{\mpo*}\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_{m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_{n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+
+\noindent 
+\parbox{4cm}{\xymatrix@C=10pt@R=6pt{&K_a\ar[dd]|\hole_(.65){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_{k_{m'}} && K_n\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_{k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }} \hfill \parbox{9cm}{\begin{proof}\label{mpo-proof}
+	By  \Cref{prop:regmono}  we know that the the top face of the original cube is a pullback.
+Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks.
+	The thesis now follows from strict $\mathcal{M}$-adhesivity.
+	\end{proof}}
+
+\epic*
+
+\noindent 
+\parbox{10cm}{
+\begin{proof}\label{epic-proof}
+	By hypothesis, there exists a pair $f, g\colon Z \rightrightarrows X$ of which $e$ is the coequalizer.
+	 Since $e \circ f = e \circ g$ we get the dotted arrow fitting in the digram aside.
+
+	\parbox{\textwidth}{Let now $h: Z \to V$ be an arrow such that $h \circ \pi_1 = h \circ \pi_2$, then
+	\[	h \circ f = h \circ \pi_1 \circ k 
+	= h \circ \pi_2 \circ k 
+	= h \circ g\]
+	and thus there exists a unique $l: Y \to V$ such that $l \circ e = h$. \qedhere}
+\end{proof}}\hfill
+\parbox{9cm}{\vspace{-2cm}\xymatrix{Z \ar@{.>}[r]_k \ar@/_.3cm/[dr]_{g} \ar@/^.4cm/[rr]^{f} & K_e \ar[r]_{\pi^{1}_e}  \ar[d]_{\pi^2_e}& X \ar[d]^{e}\\ & X \ar[r]_{e} & Y}}
+
+\natepi*
+\begin{proof}\label{natepi-proof}
+	Let $(K_i, \pi_d^1, \pi_d^2)$ be the kernel pair of $\phi_d$ for each object $d$ in $\D$. Given an arrow $\alpha: d \to d'$ of $\D$, we have
+	\[\phi_{d'} \circ F(\alpha) \circ \pi_d^1 = G(\alpha) \circ \phi_d \circ \pi_d^1 
+	= G(\alpha) \circ \phi_d\circ \pi_d^2 
+	= \phi_{d'} \circ F(\alpha) \circ \pi_d^2
+	\]
+
+	Thus, the solid part of the diagram below commutes, yielding the dotted arrow $K(\alpha)$.
+
+	\noindent 
+\parbox{5cm}{\xymatrix{K_d \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d} \ar@{.>}[dr]^{K(\alpha)}& F(d) \ar[dr]^{F(\alpha)} \\ F(d) \ar[dr]_{F(\alpha)} & K_{d'} \ar[r]^{\pi^1_{d'}} \ar[d]_{\pi^2_{d'}}& F(d') \ar[d]^{\phi_{d'}}\\ & F(d') \ar[r]_{\phi_{d'}} & G(d')}} \hfill \parbox{9cm}{In this way, we get a functor $K\colon \D\to \X$ mapping $d$ to $K_d$ and each arrow $\alpha$ onto $K(\alpha)$.
+Indeed, notice that $K(\id{d}) \colon  K_d \to K_d$ is the arrow such that
+\begin{align*}
+\pi_d^1 \circ K(\id{d})&=F(\id{d})\circ \pi^1_d=\id{F(d)}\circ \pi^{1}_d=\pi^1_d\\
+\pi_d^2 \circ K(\id{d})&=F(\id{d})\circ \pi^2_d=\id{F(d)}\circ \pi^{2}_d=\pi^2_d
+\end{align*}
+Thus, by the universal property of pullbacks, $K(\id{d}) = \id{K_d}$.
+}
+
+	Let now $\alpha \colon a \to b$ and $\beta\colon b \to c$ be two arrows in $\D$,  computing, we have
+	\begin{align*}
+		\pi_c^1 \circ K(\beta \circ \alpha) &
+		= F(\beta) \circ F(\alpha) \circ \pi_a^1 
+		= F(\beta) \circ \pi_b^1 \circ K(\alpha) 
+		= \pi_c^1 \circ K(\beta) \circ K(\alpha)\\
+			\pi_c^2 \circ K(\beta \circ \alpha) &
+		= F(\beta) \circ F(\alpha) \circ \pi_a^2 
+		= F(\beta) \circ \pi_b^2 \circ K(\alpha) 
+		= \pi_c^2 \circ K(\beta) \circ K(\alpha)
+	\end{align*}
+	Allowing us to conclude that $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving the functoriality of $K$.
+
+	Hence,  by construction we have two natural transformations $\pi^1, \pi^2\colon  K \rightrightarrows F$.
+By \Cref{prop:reg_epi_coeq}, every component $\phi_d$ is the coequalizer of $\pi_d^1, \pi_d^2\colon K(d) \rightrightarrows F$, and so $\phi$ is the coequalizer of $\pi^1$ and $\pi^2$.
+\end{proof}
+
+\epicol*
+
+\begin{proof}\label{epicol-proof}
+	By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi\colon F \to G$ is a regular epimorphism, so that there is a functor $E\colon \D\to \X$ and $\eta, \theta\colon E \rightrightarrows F$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
+Let now $(P, \{p_d\}_{d \in \D})$ be the colimit of $E$ and consider the unique arrows $a, b\colon P \rightrightarrows X$ fitting in the squares below
+
+\noindent 
+	\parbox{4cm}{\xymatrix{E(d) \ar[r]^{p_d} \ar[d]_{\eta_d}& P \ar@{.>}[d]^{a} &E(d) \ar[d]_{\theta_d}
+		 \ar[r]^{p_d}& P \ar@{.>}[d]^{b}\\ F(d) \ar[r]_{x_d} & X & F(d) \ar[r]_{x_d} & X}} \hfill	\parbox{8cm}{
+	We want to show that $\phi$ coequalizes $a$ and $n$. Let thus $h\colon X \to Z$ be an arrow such that $h \circ a = h \circ b$. Then, for every $d$, we have
+	\[	h \circ x_d \circ \eta_d = h \circ a \circ p_d 
+	= h \circ b \circ p_d 
+	= h \circ x_d \circ \theta_d\]}
+
+	Thus, there is $h_d: G(d) \to Z$ such that $h\circ x_d = h_d \circ \phi_d$.
+It is now easy to see that $(Z, \{h_d\}_{d \in \D})$ is a cocone on $G$.
+Suppose $\alpha: d \to d'$ is an arrow of $\D$, then
+	\[h_d\circ \phi_d=h\circ y_d=h\circ y_{d'}\circ F(\alpha)=h_{d'}\circ \phi_{d'}\circ F(\alpha)=h_{d'}\circ G(\alpha)\circ \phi_d\]
+		By the hypothesis $\phi_d$ is regular epi for each $d$ and so we can conclude that $h_d = h_{d'} \circ G(\alpha)$.
+
+	Therefore, we have an arrow $k\colon Y \to Z$ such that $k \circ y_d = h_d$. But then
+	\[
+	k \circ \phi \circ x_d = k \circ y_d \circ \phi_d = h_d \circ \phi_d = h\circ x_d\]
+	Showing that $k \circ \phi = h$.
+
+	For the uniqueness, let $k': Y \to Z$ be another arrow such that $k' \circ \phi = h$. Then we have
+	\[k'\circ y_d\circ \phi_d=k'\circ \phi \circ x_d=h\circ x_d=h_d\circ \phi_d\]
+
+	Since $\phi_d$ is a regular epimorphism, we have $k' \circ y_d = h_d$ allowing us to conclude.
 \end{proof}

### 2025-02-19 calco/eggs.tex
eggs
minori
minima

@@
 Then, by adhesivity of $\Set$, the bottom face is a Van Kampen square, hence a pushout.
-Therefore, by ({\color{red}{citazione}}), the square below is a pushout.
+Therefore, by \Cref{lem:mpo} , the square below is a pushout.
 	\[\xymatrix{K_1\ar[r]^{f_k}\ar[d]_{f_m}&K_2\ar[d]^{f_n}\\K_3\ar[r]_{f_k}&U}\]
+       Computing, we have
+        \[
+                \begin{split}
+                        q^\star \circ t \circ u_1 \circ f_n &= q^\star \circ t \circ n_E \circ \pi_2^1 \\ &= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^1 \\&= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^2 \\&=q^\star \circ t \circ u_2 \circ f_n
+                        \end{split}
+                        \qquad
+                        \begin{split} q^\star \circ t \circ u_1 \circ f_k &= q^\star \circ t \circ k_E \circ \pi_3^1 \\ &= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^1 \\&= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^2 \\&=q^\star \circ t \circ u_2 \circ f_k
+                        \end{split}
+        \]
+        By universal property of pushouts, we deduce $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the thesis follows.
 \end{proof}
+
+By direct application of \Cref{thm:slice-functors}, we can conclude what follows.
+
+\begin{corollary}
+	$\egg$ is $\reg(\egg)$-adhesive.
+\end{corollary}

### 2025-02-20 calco/main.tex
minima
minori

@@
 \begin{restatable}{lemma}{epicol}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
-    Let $F,G'\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
+    Let $F,G\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
 Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in \S})$ be, respectively, the colimit of $F$ and $G$.

### 2025-02-20 calco/Hypergraphs_with_equivalences.tex

@@
 	\begin{align*}
-		q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E &= q^{\star}_\mathcal{H} \circ h_V \circ s_\mathcal{G}\\ &= h_C \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}
+		q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E &= q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G}\\ &= h_C^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}
 	\end{align*}
@@
 	}\]
-	By {\color{red}{cite: Lemma: kernel pairs pushout M-adh cats}}, we know that the top face of the cube below is a pushout.
+	By \Cref{lem:mpo}, we know that the top face of the cube below is a pushout.
 \[\xymatrix@C=15pt@R=15pt{&K_{s_2\circ m_1\circ q'_1}\ar[dd]|\hole_(.65){\pi_{s_2\circ m_1\circ q'_1}^{1}}\ar[rr]^{k_{h'_2}} \ar[dl]_{k_{k'_2}} && K_{m_2\circ q'_2} \ar[dd]^{\pi_{m_2\circ q'_2}^{1}} \ar[dl]_{k_{t'_2}} \\ K_{m_3\circ q'_3}  \ar[dd]_{\pi_{m_3\circ q'_3}^{1}}\ar[rr]^(.7){k_{p'_2}} & & K_{q'_4} \ar[dd]_(.3){\pi_{q'_4}^{1}}\\&B'_1\ar[rr]|\hole^(.65){h'_2} \ar[dl]^{k'_2} && B'_2 \ar[dl]^{t'_2} \\B'_3 \ar[rr]_{p'_2} & & C_4}\]
@@
 \begin{lemma}\label{lemma:van_kampen}
-	In $\EqHyp$, pushouts along regular monos are $\mathcal{R}eg(\EqHyp)$-Van Kampen.
+	In $\EqHyp$, pushouts along regular monos are $\reg(\EqHyp)$-Van Kampen.
 \end{lemma}

### 2025-02-20 calco/eggs.tex
minima

@@
                 \xymatrix{
-			U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_i} & A \ar[drr]^{\pi_E^i} && \\
-			A \ar[ddr]_{\pi_E^i} & U_i \ar[rr]_{u_1^i} \ar[dd]^{u_2^i}&& A_i \ar[d]^{s_i} \\
-					     & & & B_i \ar[d]^{q_i}\\
-					     & A_i \ar[r]_{s_i} & B_i \ar[r]_{q_i}& C_i
+			U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_i} & A \ar[dr]^{\pi_E^i} & \\
+			A \ar[dr]_{\pi_E^i} & U_i \ar[r]^{u_1^i} \ar[d]_{u_2^i}& A_i \ar[d]^{q_i^\star \circ s_i} \\
+					     & A_i  \ar[r]_{q_i^\star \circ s_i}& C_i^\star
                 }
@@
 	Consider then the following situation.
-	\[\xymatrix@C=10pt@R=6pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar[dl]_{k_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){k_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{C_1^\star}\ar[rr]|\hole^(.65){h_C^\star}\ar[dl]^{m_C^\star} && {C_2^\star} \ar[dl]^{n_C^\star} \\{C_3^\star} \ar[rr]_{k_C^\star} & & C}\]
-	Since $m$ is regular mono, $m_C$ is mono ({\color{red}{inserire citazione}}).
-Then, by adhesivity of $\Set$, the bottom face is a Van Kampen square, hence a pushout.
-Therefore, by \Cref{lem:mpo} , the square below is a pushout.
+	\[\xymatrix@C=10pt@R=6pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar[dl]_{k_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){k_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{C_1^\star}\ar[rr]|\hole^(.65){h_C^\star}\ar[dl]^{m_C^\star} && {C_2^\star} \ar[dl]^{n_C^\star} \\{C_3^\star} \ar[rr]_{k_C^\star} & & C^\star}\]
+	Since $m$ is regular mono, $m_E$ is mono ({\color{red}{inserire citazione}}).
+	Then, by construction, the top face is a pushout, and since $\Set$ is adhesive, by \Cref{lem:mpo} , the square below is a pushout.
 	\[\xymatrix{K_1\ar[r]^{f_k}\ar[d]_{f_m}&K_2\ar[d]^{f_n}\\K_3\ar[r]_{f_k}&U}\]

### 2025-02-22 calco/main.tex
minima

@@
 \input{Hypergraphs_with_equivalences}
-%\input{Labeled_hyp_with_eq}
+\input{Labeled_hyp_with_eq}
 
@@
 
+In a category $\cat X$ with pullbacks, each $f: X \to Y$ induces a functor $f^*: \cat X/Y \to \cat X/X$,
+which sends each morphism $a: A \to Y$ of $\cat X$ onto its pullback along $f$, $p_a$, and each morphism $h: a \to b$ onto the unique arrow from the pullback of $a$ along $f$ to the pullback of $b$ along $f$.
+
+Then, we have the following result.
+
+\begin{proposition}
+	Let $\cat X$ be a category with pullbacks, $R: \cat{Y \to X}$ be a functor and $L: \cat{X \to Y}$ be its left adjoint, and $\eta$ the unit of the adjunction.
+	Then, each object $X$ of $\cat X$ induces an adjoint pair of functors $L_X: \cat X/X \to \cat Y/L(X)$, $R_X: \cat Y/L(X) \to \cat X/X$, 
+	where $L_X$ is the obvious functor, and $R_X$ is the composite $(\eta_X)^* \circ R$.
+\end{proposition}
+
+\begin{proof}
+	Let $f: L(l) \to b$ be a morphism of $\cat Y/L(X)$, where $l: A \to X$ in $\cat X$ and $b: B \to L(X)$ in $\cat Y$, as shown below.
+	\[\xymatrix{L(A)\ar[rr]^{f}\ar[dr]_{L(l)}&&B\ar[dl]_{b}\\&L(X)}\]
+	Then, we have the following situation in $\cat X$.
+	\[\xymatrix{
+			A \ar[rr]^{\eta_A}\ar[dr]_{l} \ar@/^2.0pc/@[black][rrrr]^{g} && R(L(A)) \ar[rr]^{R(f)} \ar[dr]_{R(L(l))} && R(B) \ar[dl]^{R(b)}\\
+						      & X \ar[rr]_{\eta_X} && R(L(X))
+	}\]
+	Where $g$ is the adjunct of $f$.
+	Consider now the pullback $P$ of $R(p)$ along $\eta_X$, as shown below.
+	\[\xymatrix{
+		A \ar@/^1.0pc/[drr]^{g}\ar@/_2.0pc/[ddr]_{l} \ar@{.>}[dr]^{v}\\&P\ar[r]^{q}\ar[d]_{\eta_X^*(R(b))}&R(B)\ar[d]^{R(b)}\\&X \ar[r]_{\eta_X}&R(L(X))
+	}\]
+	By universal property of pullbacks, the two diagrams express the same morphism $g$.
+	Hence, we can rewrite the first diagram as follows.
+	\[\xymatrix{
+			L(A)\ar[r]^{L(g)}\ar[d]_{L(l)}\ar@/^2.0pc/[rr]^{f}&(L(R(B)))\ar[d]_{L(R(b))}\ar[r]^{\epsilon_B}&B\ar[d]^{b}\\
+			L(X)\ar[r]_{L(\eta_X)}\ar@/_2.0pc/[rr]_{\id{L(X)}}&L(R(L(X)))\ar[r]_{\epsilon_{L(X)}}& L(X)
+	}\]
+	where $\epsilon$ is the counit of the adjunction.
+	This descriveb the action of functors and thus the adjunction, obtained considering the isomorphism on hom-sets of the categories.
+
+\end{proof}
+
 %\section{Comparison with Ghica}

### 2025-02-23 calco/Hypergraphs_with_equivalences.tex
ritocchi minimi

@@
+\commentato{
 \section{Equipping hypergraphical structures with equivalences}
@@
 	}\]
-	Hence,
-	\begin{align*}
-		f \circ q_\mathcal{G} &= q_\mathcal{H}\circ h_V \\ &=g\circ q_\mathcal{G}
-	\end{align*}
-	Since $q_\mathcal{G}$ is epi, we obtain $f = g$.
+	Hence $f \circ q_\mathcal{G} = q_\mathcal{H}\circ h_V  =g\circ q_\mathcal{G}$, and since $q_\mathcal{G}$ is epi, we obtain $f = g$.
 \end{remark}
@@
 	}\]
-	Where $L(T(\mathcal{H}))=(E_\mathcal{H}, V_{\mathcal{H}}, \{\bullet\}, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$.
-Then, $\epsilon_\mathcal{H} = (\id{E_\mathcal{H}}, \id{V_\mathcal{H}}, h_C)$ (recall that by \Cref{rem:eqhyp_morphs}, the last component is uniquely determined by the first two), and $L(f)$ must be $(h_E, h_V, \id{\{\bullet\}})$.
+	for $L(T(\mathcal{H}))=(E_\mathcal{H}, V_{\mathcal{H}}, \{\bullet\}, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$.
+Then $\epsilon_\mathcal{H} = (\id{E_\mathcal{H}}, \id{V_\mathcal{H}}, h_C)$ (by \Cref{rem:eqhyp_morphs}, the last component is uniquely determined by the first two), and $L(f)$ must be $(h_E, h_V, \id{\{\bullet\}})$.
 \end{proof}
@@
 \end{remark}
+}
 
@@
 \begin{definition}
-	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is an object and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is a regular epimorphism called \emph{quotient map}.
-
-	A morphism $h:\mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute.
+	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is an object and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is a regular epi called \emph{quotient map}.
+	%
+	A morphism $h:\mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute
 	\[\xymatrix{
@@
 	}\]
-	Hence,
-	\begin{align*}
-		f \circ q_\mathcal{G} &= q_\mathcal{H}\circ h_V \\ &=g\circ q_\mathcal{G}
-	\end{align*}
-	Since $q_\mathcal{G}$ is epi, we obtain $f = g$.
+	Hence $f \circ q_\mathcal{G} = q_\mathcal{H}\circ h_V =g\circ q_\mathcal{G}$, and since $q_\mathcal{G}$ is epi, we obtain $f = g$.
 \end{remark}
@@
 	Note that, since $\Delta_{\EqHyp}(X)$ has the empty set as object of edges, $h_E = ?_{E_\mathcal{H}}$, then, the unique arrow that fits in the diagram is $\Delta_{\EqHyp}(f) = (?_{E_\mathcal{H}}, h_V, \id{\{\bullet\}})$.
-
 \end{proof}
@@
 	}\]
-	Where $L(T(\mathcal{H}))=(E_\mathcal{H}, V_{\mathcal{H}}, \{\bullet\}, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$.
-Then, $\epsilon_\mathcal{H} = (\id{E_\mathcal{H}}, \id{V_\mathcal{H}}, h_C)$ (recall that by \Cref{rem:eqhyp_morphs}, the last component is uniquely determined by the first two), and $L(f)$ must be $(h_E, h_V, \id{\{\bullet\}})$.
+	for $L(T(\mathcal{H}))=(E_\mathcal{H}, V_{\mathcal{H}}, \{\bullet\}, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$.
+Then, $\epsilon_\mathcal{H} = (\id{E_\mathcal{H}}, \id{V_\mathcal{H}}, h_C)$ (by \Cref{rem:eqhyp_morphs}, the last component is uniquely determined by the first two), and $L(f)$ must be $(h_E, h_V, \id{\{\bullet\}})$.
 \end{proof}
@@
 
-Let now $K: \EqHyp \to \Set$ be the functor which sends each hypergraph with equivalence $\mathcal{G} = (E, V, C, s, t, q)$ onto $K(\mathcal{G}) = C$, and each morphsism $(h_E, h_V, h_C)$ to $h_C$.
+Let now $K: \EqHyp \to \Set$ be the functor which sends each hypergraph with equivalence $\mathcal{G} = (E, V, C, s, t, q)$ onto $K(\mathcal{G}) = C$, and each morphism $(h_E, h_V, h_C)$ to $h_C$.
 
 \begin{proposition}\label{prop:eqhyp_complete}
-	\EqHyp is complete and cocomplete, and $T$ preserves limits and colimits.
+	\EqHyp \, is complete and cocomplete, and $T$ preserves limits and colimits.
 \end{proposition}
@@
 	Then, $V$, together with $(q_i\circ \pi_V^i)_{i\in \cat I}$, is a cone for $K \circ D$. Indeed, let $\alpha: i \to j$ be an arrow of $\cat I$, $D(\alpha) = (h_E,h_V, h_C)$.
-	By definition of $T$, $(T \circ D)(\alpha) = (h_E, h_V)$, hence we have the following situation.
+	By definition of $T$, $(T \circ D)(\alpha) = (h_E, h_V)$, hence we have
 	\[\xymatrix{
@@
 	\begin{align*} f_C \circ h_C \circ q_\mathcal{G} &= f_C\circ q_\mathcal{H} \circ h_V\\&=q_\mathcal{K}\circ g_V \circ h_V\\&=q_\mathcal{K}\circ f_V \circ h_V\\&=g_C \circ h_C \circ q_\mathcal{G} \end{align*}
-	Since $q_\mathcal{G}$ is epi, we have $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, and thus a monomorphism.
+	Since $q_\mathcal{G}$ is epi, we have $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, and thus a mono.
 \end{proof}
@@
 \begin{proposition}
-	Let $h = (h_E, h_V, h_C): \mathcal{G \to H}$ be a regular monomorphism in $\EqHyp$.
+	Let $h = (h_E, h_V, h_C): \mathcal{G \to H}$ be a regular mono in $\EqHyp$.
 	Then, $h_E$ and $h_V$ are monos and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{H}\circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$.
@@
     \end{displayquote}
-    That is, a regular monomorphism in $\EqHyp$ is a morphism that reflects equivalences besides preserving them.
+    That is, a regular mono in $\EqHyp$ is a morphism that both reflects and preserves equivalences.
+    % besides preserving them.
 \end{remark}
@@
 	The action of the functor on a morphism of hypergraphs with equivalences gives a morphism of hypergraphs,
-	in fact 
-	\begin{align*}
-		q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E &= q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G}\\ &= h_C^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}
-	\end{align*}
+	in fact $q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E = q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G} = h_C^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}$.
 	The same is valid for $t_\mathcal{H}$ and $t_\mathcal{G}$. 
@@
 Now, suppose that $h = (h_E, h_V): Q((E, V, C, s', t', q)) \to (A, B, s, t)$  is an arrow in $\hyp$, and consider the triple $(h_E, h_V, h_V \circ q)$.
-Since $h$ is a morphism of $\hyp$,
-    \[h_V^{\star}\circ q^{\star}\circ s'= s\circ h_E \qquad  h_V^{\star}\circ q^{\star}\circ t' = t\circ h_E\]
-    Then we have the following squares:
+Since $h$ is a morphism of $\hyp$, we have $h_V^{\star}\circ q^{\star}\circ s'= s\circ h_E$ and $h_V^{\star}\circ q^{\star}\circ t' = t\circ h_E$.
+    Then we have the following squares
     \[\xymatrix{
@@
     \]\fi
-
-    We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below.
-
+    We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below
     \[\xymatrix{
@@
     }\]   
-
     Such arrow is unique. Suppose $f = (f_E, f_V, f_C)$ to be another arrow with such property.
@@
 	Let $((\kappa_i)_{i\in \cat I}, V)$ be the colimit of $U_\EqHyp \circ D$.
-	Consider the following situation.
+	Consider the following situation
 	\[\xymatrix{

### 2025-02-23 calco/main.tex
ritocchi minimi

@@
 
+\newcommand{\commentato}[1]{ {} }
+
 %sommatoria e prodotto per xy
@@
 
-This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.
-
+This  section briefly recalls \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}. 
+%
 %\begin{notation}
-Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects, so
+Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
 ``$X\in \X$'' means that $X$ is an object of $\X$.
 We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.
-Given an object $X$, we will denote by $?_X$ the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one.
+Given an object $X$, we  denote by $?_X$ the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one.
 %\end{notation}
@@
 \subsection{$\mathcal{M}$-adhesivity}\label{subsec:ade}
-The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.
-
-In order to define it we need to introduce some terminology.  Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is called
+The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive},
+%
+and to define it we introduce some terminology.  Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is
 
@@
 		\mathcal{M} \text{ for every } Y\in \Y\}$;
-		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ and  stable under pullbacks, pushout, containing all isomorphism and closed under composition and decomposition.
+		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ and  stable under pullbacks and pushout, containing all isomorphisms and closed under composition and decomposition.
 	\end{enumerate} 
@@
 We can state some useful properties of $\mathcal{M}$-adhesive category.
-\begin{restatable}{proposition}{regmono}\label[proposition]{prop:regmono}
+
+\begin{restatable}{proposition}{regmono}\label{prop:regmono}
 	If $\X$ is $\mathcal{M}$-adhesive then the following are true:
@@
 
-In this section we recall the definition and some useful properties of \emph{kernel pairs} which will be useful in the next sections.
+In this section we recall the definition and some properties of \emph{kernel pairs}.
+%which will be useful in the next sections.
 
@@
 \begin{definition}
-    A \emph{kernel pair} for an arrow $f\colon A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f\colon K_f \rightrightarrows A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the following square is a pullback.
+    A \emph{kernel pair} for an arrow $f\colon A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f\colon K_f \rightrightarrows A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the square aside is a pullback.
 \end{definition}}\hfill 
-\parbox{2cm}{\xymatrix@R=15pt{K_f \ar[r]_{\pi^1_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}}
-
+\parbox{2cm}{\xymatrix@R=15pt{K_f \ar[r]_{\pi^2_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}}
+
+\smallskip
 \begin{remark}\label{prop:pairng_of_kernel_pairs_mono}
@@
 
-Together with \Cref{lem:pb1}, the two previous remarks while elementary, allow us to prove the following result.
+Together with \Cref{lem:pb1}, the previous remarks allow us to prove the following result.
 
 \begin{proposition}\label{cor:kermono}
-	Let $f\colon X\to Y$ be an arrow and $m\colon Y\to Z$ be a mono. If
+	Let $f\colon X\to Y$ be an arrow and $m\colon Y\to Z$ a mono. If
 	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$, then it is also a kernel pair for $m\circ f$.
@@
 	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given.
-Then there exists a a unique arrow $k_h: K_f \to K_g$ compliting them.
+Then there exists a a unique arrow $k_h: K_f \to K_g$ completing them.
 	\[\xymatrix{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
 
-    Moreover, if the leftmost is a pullback, then also the other ones are so.
+    Moreover, if the leftmost is a pullback, then also the other two are so.
 \end{restatable}
@@
 
-As a final step, we explore the relationship between regular epimorphisms and kernel pairs.
+As a final step, we explore the link between regular epis and kernel pairs.
 
 \begin{restatable}{proposition}{epic}\label{prop:reg_epi_coeq}
-    Let $e\colon X \to Y$ be a regular epimorphism in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then, $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
+    Let $e\colon X \to Y$ be a regular epi in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then, $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
 \end{restatable}
@@
 \begin{restatable}{corollary}{natepi}\label{cor:reg_epi_components_reg_epi_nat_trans}
-    Let $\X$ be a category with pullbacks and $\phi\colon F \dot\to G$ be a natural transformation between two functors $F, G: \D \rightrightarrows \X$.
+    Let $\X$ be a category with pullbacks and $\phi\colon F \dot\to G$ a natural transformation between functors $F, G: \D \rightrightarrows \X$.
 If $\phi_d$ is a regular epi for every $d$ in $\D$, then $\phi$ is a regular epi.
@@
 
-From the previous result we can now deduce that the class of regular epis is closed under colimits, as shown by the next lemma
+From the previous result we deduce that the class of regular epis is closed under colimits.
+% as shown by the next lemma
+
 \begin{restatable}{lemma}{epicol}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
     Let $F,G\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
-Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in \S})$ be, respectively, the colimit of $F$ and $G$.
-If $\phi\colon  F \to G$ is a natural transformation in which all components are regular epimorphisms, then, the arrow induced by $\phi$ from $X$ to $Y$ is a regular epimorphism too.
+Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in \S})$ be the colimits of $F$ and $G$, respectively.
+If $\phi\colon  F \to G$ is a natural transformation whose components are regular epi, then the arrow induced by $\phi$ from $X$ to $Y$ is a regular epi too.
 \end{restatable}
@@
 
-In this section we briefly recall the notion \emph{$\X$-hypergraph}.
-In order to do it is necessary to have a monad $(-)^\star$ playing a role analogous to the usual \emph{Kleene star}, also known as \emph{list monad}, $(-)^\star\colon \Set\to \Set$ sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95}.
-We will recall some of its proprieties.
+In this section we briefly recall the notion \emph{$\X$-hypergraph}. It is necessary to have a monad $(-)^\star$ playing a role analogous to the usual \emph{Kleene star}
+ $(-)^\star\colon \Set\to \Set$, also known as \emph{list monad}, sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95}. We recall some of its proprieties.
 
@@
 		\item for every arrow $f\colon X\to Y$, $f^\star$ is the coproduct of the family $\{f^n\}_{n\in \mathbb{N}}$;
-		\item $(-)^\star$ preserves all \emph{connected limits} \cite{carboni1995connected}, in particular it preserves all pullbacks and equalizers.
+		\item $(-)^\star$ preserves all \emph{connected limits} \cite{carboni1995connected}, in particular it preserves pullbacks and equalizers.
 	\end{enumerate}
@@
 
-\begin{remark}\label[remark]{rem:length}Notice that, $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$, the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $!^\star_X\colon X^\star \to \mathbb{N}$ which simply sends a word length.
+\begin{remark}\label[remark]{rem:length}Notice that $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $!^\star_X\colon X^\star \to \mathbb{N}$, which sends a word to its length.
 \end{remark}
@@
 
-We will start this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
+We open this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
 
 \begin{definition}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the set of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
-A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute.
-
+A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute
 	\[\xymatrix{ E_{\mathcal{G}} \ar[d]_{h} \ar[r]^{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}& E_{\mathcal{G}} \ar[r]^{t_{\mathcal{G}}} \ar[d]_{h} & V^\star_{\mathcal{G}} \ar[d]^{k^\star}  \\ E_{\mathcal{G}} \ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} & E_{\mathcal{G}} \ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} }\]
@@
 
-Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$, then we can present $\hyp$ as a comma category.
+Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$: we can get $\hyp$ as a comma category.
+
 \begin{proposition}\label[proposition]{prop:com}
@@
 
-\begin{example}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\Set}(X)$ is the hypergraph which has $X$ as set of nodes and $\emptyset$ as set of hyperedges and $?_X$ as both source and target function.
+\begin{example}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\Set}(X)$ is the hypergraph which has $X$ as set of nodes, $\emptyset$ as set of hyperedges, and $?_X$ as source and target function.
 \end{example}
@@
 
-\begin{definition}Let $\catname{H}$ be the category in which:
+\begin{definition}Let $\catname{H}$ be the category isuch that
 	\begin{itemize}
-		\item the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$
+		\item the set of objects is $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$;
 		\item arrows are given by the identities $\id{k,l}$ and $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$;
-		\item composition is defined simply putting, for every $f_i\colon (k,l)\rightarrow \bullet$:
-		\begin{equation*}
-			f_i=f_i\circ \id{k,l} \qquad f_i = \id{\bullet}\circ f_i 
-		\end{equation*}
+		\item composition is defined by putting
+		%\begin{equation*}
+			$f_i=f_i\circ \id{k,l}$ and $f_i = \id{\bullet}\circ f_i$
+		%\end{equation*}
+		for every $f_i\colon (k,l)\rightarrow \bullet$.
 	\end{itemize}
@@
 
-The idea now is that for every functor $F\colon \catname{H}\to \catname{Set}$ we can define
+The idea is that for every functor $F\colon \catname{H}\to \catname{Set}$ we can define
 \[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
-
-Now, for every $k$, $l$, $i$ and $j$ in $\mathbb{N}$ with $i< k$ and $j< l$ we can define $s^F_{k,l}\colon F(k,l)\to F(\bullet)^k$,  $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ as the unique ones fitting in the diagrams below, where the vertical arrows are the projections.
+%
+Now, for every $k$, $l$, $i$ and $j$ in $\mathbb{N}$ with $i< k$ and $j< l$ we define $s^F_{k,l}\colon F(k,l)\to F(\bullet)^k$ and  $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ as the unique arrows fitting in the diagrams below, where the vertical arrows are the projections
 \[\xymatrix{F(k,l)  \ar@{.>}[r]^{s^F_{k,l}} \ar[dr]_{F(f_i)}& F(\bullet)^{k} \ar[d]^{\pi^F_{k,i}} & F(k,l) \ar@{.>}[r]^{t^F_{k,l}} \ar[dr]_{F(f_{k+j})} & F(\bullet)^{l} \ar[d]^{\pi^F_{l,j}} \\ & F(\bullet) && F(\bullet)}\]
-
+%
 In turn, these arrows allow us to consider
-$s_F, t_F\colon E_F\rightrightarrows F(\bullet)^{\star}$ as the unique arrows fitting in the diagrams below, where the vertical arrows are coprojections.
+$s_F, t_F\colon E_F\rightrightarrows F(\bullet)^{\star}$ as the unique arrows fitting in the diagrams below, where the vertical arrows are coprojections
 \[\xymatrix{F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{s^{F}_{k,l}}& F(\bullet)^{k} \ar[d]^{b^F_{k}} & F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{t^{F}_{k,l}}& F(\bullet)^{l} \ar[d]^{b^F_{l}}\\ E_F \ar@{.>}[r]_-{s_F}& F(\bullet)^\star & E_F \ar@{.>}[r]_-{t_F}& F(\bullet)^\star}\]
@@
 
-Our interest intohypergraph stems fromm their use as a graphical representation of algebraic terms. We thus need a way to label hyperedges with symbols taken from a given algebraic signature.
+Our interest for hypergraphs stems from their use as a graphical representation of algebraic terms. We thus need a way to label hyperedges with symbols taken from a signature.
 
@@
 This simply amount to a set of \emph{operations} with an associated natural number, called \emph{arity}.
-	For instance let $\Sigma_G$ be the signature of groups, then $\mathcal{G}^{\Sigma_G}$ can be depicted as:
+	For instance let $\Sigma_G$ be the signature of groups, then $\mathcal{G}^{\Sigma_G}$ can be depicted as
 	\begin{center}
@@
 
-\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterization of monomorphisms in it.
+\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
 
@@
 \begin{remark}\label[remark]{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
-Notice, moreover that since $t_{\mathcal{G}}$ is mono then $\tau_{\mathcal{G}}$ is mono too.
+Notice that since $t_{\mathcal{G}}$ is mono then $\tau_{\mathcal{G}}$ is mono too.
 \end{remark}
@@
 \begin{proof}
-	This follows noticing that, for every object $X$, $\Delta_{\Sigma}(X)$ is a term graph.   
+	This follows noticing that $\Delta_{\Sigma}(X)$ is a term graph for every object $X$.
 \end{proof}
 
-We canlist some categorical properties of $\tg$
+We can list some categorical properties of $\tg$
 
@@
 \begin{remark}
-	$\tg$ is not an adhesive category. In particular it does not have pushouts along all monomorphisms. For instance, if we take the three term graphs of the previous remark, then have two arrows
+	$\tg$ is not an adhesive category. In particular it does not have pushouts along all monos. For instance, if we take the three term graphs of the previous remark, then have two arrows
 	$(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_a, !_{V_{\mathcal{G}_a}})$ and $(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_b, !_{V_{\mathcal{G}_a}})$ which cannot be completed to a square.
@@
 
-Our result opens two threads of research. The first is to use the quasi-adhesivity of EGGS in order to
-model their rewriting via the double-pushout (DPO) approach. This seems to be straightforward, since 
-the rules adopted in the literature of EGGS appears to be span of regular monos, and such rules
+Our result opens two threads of research. The first is to use the quasi-adhesivity of EGGs to
+model their rewriting via the double-pushout (DPO) approach. This seems now easy, since 
+the rules adopted in the literature of EGGs appears to be span of regular monos, and such rules
 perfectly fit the mold of rewriting on quasi-adhesive categories. 
-For example, the equivalence $x \div x = 1$, taken from the introductory example in~\cite{xxx}, 
+For example, the equivalence $x \div x = 1$, from the introductory example in~\cite{xxx}, 
 can be modelled as the rule
@@
 on adhesive categories, 
-mean in the context of EGGS. More interestingly, another venue for development is using the adhesive 
-machinery to extend the EGGS formalism. In fact, most of the results
+mean in the context of EGGs. More interestingly, another venue for development is using the adhesive 
+machinery to extend the EGGs formalism. In fact, most of the results
 presented here for hyper-graphs can be generalised to hierarchical hyper-graphs, that is, 
@@
 
-Finally, we will delve into and draw a comparison with an alternative categorical presentation for EGGS 
-advanced in~\cite{ghica}. The proposal is quite different from our own. Simplifying, the key is to use categories 
-of tree which are equipped with a lattice on hom-sets. We can recover trees in our approach, even 
-if we opted for term graphs in order to obtain a simpler categorical presentation. Instead of going through 
-an enrichment on hom-sets, we chose to obtain closure via suitable requirements on morphisms, even if it 
+Finally, we need to draw a comparison with an alternative categorical presentation for EGGs 
+advanced in~\cite{ghica}. The proposal is quite different from our own. Simplifying, the key is to equip categories 
+of trees with a lattice on hom-sets. Instead of going through 
+such an enrichment, we chose to obtain closure via suitable requirements on morphisms, even if it 
 seems that the former generalises the latter, at the expenses of a more complex machinery.
@@
 \regmono*
-
 \begin{proof}\label{regmono-proof}
@@
 \begin{proof}\label{epicol-proof}
-	By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi\colon F \to G$ is a regular epimorphism, so that there is a functor $E\colon \D\to \X$ and $\eta, \theta\colon E \rightrightarrows F$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
+	By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi\colon F \to G$ is a regular epi, so that there is a functor $E\colon \D\to \X$ and $\eta, \theta\colon E \rightrightarrows F$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
 Let now $(P, \{p_d\}_{d \in \D})$ be the colimit of $E$ and consider the unique arrows $a, b\colon P \rightrightarrows X$ fitting in the squares below
+\medskip
 
@@
 		 \ar[r]^{p_d}& P \ar@{.>}[d]^{b}\\ F(d) \ar[r]_{x_d} & X & F(d) \ar[r]_{x_d} & X}} \hfill	\parbox{8cm}{
-	We want to show that $\phi$ coequalizes $a$ and $n$. Let thus $h\colon X \to Z$ be an arrow such that $h \circ a = h \circ b$. Then, for every $d$, we have
-	\[	h \circ x_d \circ \eta_d = h \circ a \circ p_d 
+	We want to show that $\phi$ coequalizes $a$ and $n$. Let thus $h\colon X \to Z$ be an arrow such that $h \circ a = h \circ b$. Then, for every $d$, 
+	we have
+	\[h \circ x_d \circ \eta_d = h \circ a \circ p_d 
 	= h \circ b \circ p_d 
@@
 
+	\noindent
 	Thus, there is $h_d: G(d) \to Z$ such that $h\circ x_d = h_d \circ \phi_d$.
@@
 
-	Since $\phi_d$ is a regular epimorphism, we have $k' \circ y_d = h_d$ allowing us to conclude.
+	Since $\phi_d$ is a regular epi, we have $k' \circ y_d = h_d$ allowing us to conclude.
 \end{proof}
@@
 \begin{corollary}\label[corollary]{cor:mono}
-	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comma{L}{R}$ is mono if and only if both $h$ and $k$ are monomorphisms.
+	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comma{L}{R}$ is mono if and only if both $h$ and $k$ are monos.
 \end{corollary}

### 2025-02-23 calco/Equivalence_term_graphs.tex
minima

\subsubsection{Term Graphs with Equivalences}

\begin{definition}
	Let $\Sigma$ be an algebraic signature.
	A labeled hypergraph with equivalence $l: \mathcal{G} \to L(\mathcal{G}^\Sigma)$ is a \emph{term graph with equivalence} if $t_{\mathcal{G}}$ is mono.
	We define category of term graphs with equivalence over $\Sigma$, denoted $\EqTG_{\Sigma}$, as the full subcategory of $\EqHyp_\Sigma$,
	and the corresponding inclusion functor $I_{\EqTG_\Sigma}$.
\end{definition}

\begin{proposition}
	If $l: \mathcal{G \to G}^\Sigma$ is a term graph, then $L(l)$ is a term graph with equivalence.
\end{proposition}

### 2025-02-23 calco/Labeled_hyp_with_eq.tex
minima

@@
 \end{proposition}
+
+We can lift the adjunction given by $T$ and $L$ to $EqHyp_\Sigma$ and $\hyp_\Sigma$.\todo{Non capisco se è uno svarione mio o ha senso}
+
+By \Cref{cor:mono1}, we can deduce what follows.
+
+\begin{proposition}\label{prop:monos_in_eqhyps}
+	A morphism $h$ between two objects of $\EqHyps$ is mono if and only if $T(h)$ is mono.
+\end{proposition}

### 2025-02-23 calco/Hypergraphs_with_equivalences.tex
ritocchi

@@
 \section{Hypergraphs and term graphs with equivalences}
+\label{hypereq}
 
 \begin{definition}
-	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is an object and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is a regular epi called \emph{quotient map}.
+	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $C_\mathcal{G}$ is a set and $q_{\mathcal{G}}: V_{\mathcal{G}}\to C_{\mathcal{G}}$ is a regular epi called \emph{quotient map}.
 	%
@@
 	Let $\mathcal{G}$ be a hypergraph, and define $L(\mathcal{G}) := (E_\mathcal{G}, V_{\mathcal{G}}, \{\bullet\}, s_\mathcal{G}, t_\mathcal{G}, !_{V_\mathcal{G}})$.
-Let now $h: L(\mathcal{G})\to \mathcal{H}$ be a morphism in $\EqHyp$, and consider the following situation.
+Let now $h: L(\mathcal{G})\to \mathcal{H}$ be a morphism in $\EqHyp$, and consider the following situation
 	\[\xymatrix@C=2.3cm{
@@
 \begin{corollary}\label{cor:mono1}
-	An arrow $h = (h_E, h_V, h_C): \mathcal{G \to H}$ is mono if and only if $T(h)$ is mono.
+	Let $h = (h_E, h_V, h_C): \mathcal{G \to H}$ be an arrow in  $\EqHyp$. Then it is a mono if and only if $T(h)$ is a mono.
 \end{corollary}
@@
 
-	But the arrow $\initial \to A \times B$ is not epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
+	But the arrow $\initial \to A \times B$ is not an epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
 \end{example}

### 2025-02-23 calco/Labeled_hyp_with_eq.tex
ritocchi

@@
 
-As we have done in \Cref{sssect:hyp_alg_sign}, we can define the category of hypergraphs with equivqlence labeled over an algebraic signature.
+As we have done in \Cref{sssect:hyp_alg_sign}, we can define the category of hypergraphs with equivalence labeled over an algebraic signature.
 
 \begin{definition}
-	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be an algebraic signature, and let $\mathcal{G}^{\Sigma}$ the hypergraph associated to $\Sigma$.
-	Then, the \emph{hypergraph with equivalence} associated to $\Sigma$ is $L(\mathcal{G}^\Sigma)$, and the category of hypergraphs with equivalence labeled over $\Sigma$ is the 
-	slice category $\EqHyp_\Sigma := \EqHyp/L(\mathcal{G}^\Sigma)$.
+	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to $\Sigma$.
+	Then the \emph{hypergraph with equivalence} associated to $\Sigma$ is $L(\mathcal{G}^\Sigma)$ and the category of hypergraphs with 
+	equivalence labeled over $\Sigma$ is the 
+	slice category $\EqHyp_\Sigma = \EqHyp/L(\mathcal{G}^\Sigma)$.
 \end{definition}

### 2025-02-23 calco/eggs.tex
ritocchi minimi
ritocchi

@@
 \section{EGGs}
+\label{eggs}
 
@@
 \begin{definition}
-	Let $\mathcal{G} = (E, V, C, s, t, q)$ be a hypergraph with equivalence, and let $(S, \pi_1, \pi_2)$ be the kernel pair of $q^\star \circ s$.
+	Let $\mathcal{G} = (E, V, C, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair of $q^\star \circ s$.
 	Then, $\mathcal{G}$ is an \emph{e-hypergraph} whenever $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
-	$\egg$ is the full subcategory of $\EqHyp$ where objects are e-hypergraphs, and $I: \egg \to \EqHyp$ is the inclusion functor.
+	$\egg$ is the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and $I: \egg \to \EqHyp$ is the inclusion functor.
 \end{definition}
@@
 \begin{lemma}
-	$\egg$ has all limits, and $I$ preserves them.
+	$\egg$ has all limits and $I$ preserves them.
 \end{lemma}
@@
 	let $(U, u_1, u_2)$ be the kernel pair of $q\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ D$.
-        By construction (proof of \Cref{prop:eqhyp_complete}), there exists a monomorphism $m: C \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
+        By construction (proof of \Cref{prop:eqhyp_complete}), there exists a mono $m: C \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
         \begin{align*}
@@
 \begin{corollary}
-	$h: \mathcal{G \to H}$ is a regular mono in $\egg$ if and only if it is a regular mono in $\EqHyp$.
+Let $h: \mathcal{G \to H}$ be an arrow in $\egg$. Then it is a regular mono 
+%in $\egg$
+if and only if $I(h)$ is a regular mono.
+% in $\EqHyp$.
 \end{corollary}

### 2025-02-23 calco/main.tex
minima
ritocchi

@@
 \newcommand{\EqHyp}{\catname{EqHyp}} %equivalence hypergraphs
+\newcommand{\EqHyps}{\catname{EqHyp}_{\Sigma}}
+\newcommand{\EqTG}{\catname{EqTG}}
+\newcommand{\EqTGs}{\catname{EqTG}_{\Sigma}}
 \newcommand{\gr}{\textbf{\textup{Graph}}}
@@
 \todo{A very nice introduction}
+
+\emph{Synopsis}
+The paper has the following structure. 
+In Section~\ref{sec:ade} we briefly recall 
+the theory of
+\emph{$\mathcal{M}$-adhesive categories}
+and of \emph{kernel pairs}.
+In Section~\ref{sec:hyper} we present the graphical structures of our interest, 
+namely (labelled) hypergraphs and term graphs, and we provide a
+functorial characterisation, which allows for proving their adhesivity properties.
+This is further expended in Section~\ref{hypereq} for describing hypergraphs 
+and term graphs with equivalence and in Section~\ref{eggs} for capturing
+their variants where the equivalences are closed with respect to operator application,
+thus subsuming EGGs.
+%
+All the proofs have been moved to the appendix. For the sake of completeness, 
+and in order to fix the notation, we prove all the results 
+recalled in the background section, besides those that are original 
+to our work.
+
 \section{$\mathcal{M}$-adhesive categories}\label{sec:ade}
@@
 %
-and to define it we introduce some terminology.  Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is
+and for defining it we need some notions.
+%and to define it we introduce some notions.  
+Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is said to be
 
@@
 	\end{enumerate}
-
+	%
 	A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
@@
 
-\begin{theorem}
+\begin{proposition}
 	\label{thm:slice-functors}
-	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category, then the following hold true:
+	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category. Then it holds
 	\begin{enumerate}
@@
 		\mathcal{M} \text{ for every } Y\in \Y\}$;
-		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ and  stable under pullbacks and pushout, containing all isomorphisms and closed under composition and decomposition.
+		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ that is stable under pullbacks and pushouts, contains all the isomorphisms, and is closed under composition and decomposition.
 	\end{enumerate} 
-\end{theorem}
+\end{proposition}
 
@@
 \begin{restatable}{proposition}{regmono}\label{prop:regmono}
-	If $\X$ is $\mathcal{M}$-adhesive then the following are true:
+	If $\X$ is $\mathcal{M}$-adhesive then it holds
 	\begin{enumerate}
@@
 
-We are now going to explore some further properties of kernel pairs
+We are now going to explore some further properties of kernel pairs.
 
@@
 Then there exists a a unique arrow $k_h: K_f \to K_g$ completing them.
+Moreover, if the leftmost is a pullback, then also the other two are so.
+%
 	\[\xymatrix{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
 
-    Moreover, if the leftmost is a pullback, then also the other two are so.
 \end{restatable}
@@
     Let $F,G\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
-Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in \S})$ be the colimits of $F$ and $G$, respectively.
-If $\phi\colon  F \to G$ is a natural transformation whose components are regular epi, then the arrow induced by $\phi$ from $X$ to $Y$ is a regular epi too.
+Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in D})$ be the colimits of $F$ and $G$, respectively.
+If $\phi\colon  F \to G$ is a natural transformation whose components are regular epis, then the arrow induced by $\phi$ from $X$ to $Y$ is a regular epi.
 \end{restatable}
@@
 
-In this section we briefly recall the notion \emph{$\X$-hypergraph}. It is necessary to have a monad $(-)^\star$ playing a role analogous to the usual \emph{Kleene star}
- $(-)^\star\colon \Set\to \Set$, also known as \emph{list monad}, sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95}. We recall some of its proprieties.
+In this section we briefly recall the notion \emph{$\X$-hypergraph}. It is necessary to have a monad $(-)^\star\colon \Set\to \Set$, also known as \emph{list monad},
+sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95} and playing a role analogous to the usual \emph{Kleene star}.
+We recall some of its proprieties.
 
 \begin{proposition}
-	The following facts are true:
+	The following facts hold
 	\begin{enumerate}
@@
 
-\begin{definition}Let $\catname{H}$ be the category isuch that
+\begin{definition}Let $\catname{H}$ be the category such that
 	\begin{itemize}
@@
 An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ and an \emph{arity function} $\ari_\Sigma\colon O_\Sigma \to \mathbb{N}$. 
-
+%
 We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes, so that $1^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, where $\delta_1$ picks the element $1$.
@@
 
-\begin{proposition}\label[proposition]{prop:mono} For every algebraic signature $\Sigma$, the following are true:
+\begin{proposition}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then it holds
 	\begin{enumerate}
@@
 	\[\xymatrix{E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{s_{\mathcal{H}}}& O_\Sigma \ar[d]^{\ari_\Sigma}& E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{t_{\mathcal{H}}} & O_\Sigma \ar[d]^{\delta_1}\\ V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}}& \mathbb{N} & V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}\]
-
+%	
 Let $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$ be a coprojection.
-The second diagram in particular above entails that $t_{\mathcal{H}}$ factors through the inclusion $v_1\colon V_{\mathcal{H}}\to V^{\star}$ of words of length $1$, i.e.
-that $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to \tau_{\mathcal{H}}$.
+The second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V^{\star}$ of words of length $1$, i.e.
+$t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to \tau_{\mathcal{H}}$.
 \end{remark}
@@
 Since, $U_{\Sigma}(\mathcal{H})=U_{\X}(\mathcal{H})$ and the identity is the unit of $\Delta_\hyp \dashv U_{\hyp}$, we get a morphism $(?_{E_{\mathcal{H}}},f)\colon \Delta_{\X}(X)\to \mathcal{H}$ of $\hyp$.
-But then we have
+And then the thesis follows since we have
 	\[
 	(h, !_{V_{\mathcal{{H}}}})\circ (?_{E_{\mathcal{H}}}, f)=(h\circ ?_{E_{\mathcal{H}}}, !_{V_{\mathcal{{H}}}}\circ f)=(?_{0_{\Sigma}}, !_{X})=\Delta_{\hyp}(X)\]
-and the thesis follow.   
+%and the thesis follow.   
 \end{proof}
@@
 
-We are now going back to examine the properties of $\tg$, with the purpose of studying its adhesivity properties.
+We now examine some properties of $\tg$, in order to study its adhesivity properties.
 
@@
 \begin{proposition}
-For every algebraic signatur $\Sigma$, the following are true:
+Let $\Sigma$ be an algebraic signature. Then it holds
 \begin{enumerate}
@@
 
-Preservation of inputs, characterizes regular monos in $\tg$.
-
-\begin{proposition}\label[proposition]{lem:reg} The following are equivalent for a a mono $(i,j)$ between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$:
-	\begin{enumerate}
-		\item $(i, j)$ is a regular mono;
-		\item $(i,j)$ preserves input nodes.
-	\end{enumerate}	
+Preservation of inputs characterizes regular monos in $\tg$.
+
+\begin{proposition}\label[proposition]{lem:reg} Let $(i,j)$ be a mon between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$.
+Then it is a regular mono if and only if it preserves the input nodes.
 \end{proposition}
@@
 
-\subsection{title}
+\input{Equivalence_term_graphs}
 
@@
 the rules adopted in the literature of EGGs appears to be span of regular monos, and such rules
-perfectly fit the mold of rewriting on quasi-adhesive categories. 
+perfectly fit the mold of rewriting on $\mathcal{M}$-adhesive categories. 
 For example, the equivalence $x \div x = 1$, from the introductory example in~\cite{xxx}, 
@@
 
-It still needs to be investigated what concurrency and termination, the key properties for DPO rewriting
+It still needs to be investigated what parallelism and termination, the key properties for DPO rewriting
 on adhesive categories, 
@@
 advanced in~\cite{ghica}. The proposal is quite different from our own. Simplifying, the key is to equip categories 
-of trees with a lattice on hom-sets. Instead of going through 
-such an enrichment, we chose to obtain closure via suitable requirements on morphisms, even if it 
-seems that the former generalises the latter, at the expenses of a more complex machinery.
+of trees with a lattice on hom-sets. 
+It seems that such proposal generalises our own, 
+even if at the expenses of a more complex machinery.
+%Instead of going through 
+%such an enrichment, we chose to obtain closure via suitable requirements on morphisms, even if it 
+%seems that the former generalises the latter, at the expenses of a more complex machinery.
 

### 2025-02-23 calco/main.tex
qualche pezzo di intro

@@
 
+\begin{itemize}
+\item general on adhesive categories
+\item general on the use of eggs
+\end{itemize}
+
+In the original definition, e-graphs are defined as term graphs with an additional notion of equivalence on nodes. 
+Adopting the more modern presentation via string diagrams, they are tree with sharing of subtrees, and with an 
+an equivalence $\equiv$ on nodes that is closed under xxx. In plain words, if $a$ and $b$ are two constants such that
+$a \equiv b$, then $f(a) \equiv f(b)$ for any unary operator $f$.
+
+\cite[Section~4.2]{DetlefsNS05}
+\cite{WillseyNWFTP21}
+
 \emph{Synopsis}

### 2025-02-24 calco/main.tex
commentato qualche risultato

@@
 
-\section{$\mathcal{M}$-adhesive categories}\label{sec:ade}
+\section{Facts about $\mathcal{M}$-adhesive categories and kernel pairs}\label{sec:ade}
 
@@
 
+\vspace{-.25cm}
 \parbox{9.5cm}{We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
@@
 \end{restatable}
-  [Proof in \Cref{regmono-proof}]
+%  [Proof in \Cref{regmono-proof}]
 
@@
 
-We are now going to explore some further properties of kernel pairs.
-
-\begin{restatable}{lemma}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
-	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given.
-Then there exists a a unique arrow $k_h: K_f \to K_g$ completing them.
-Moreover, if the leftmost is a pullback, then also the other two are so.
-%
-	\[\xymatrix{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
-
-\end{restatable}
-[Proof in \Cref{kpp-proof}]
-
-The previous result allows us to deduce the following lemma in an $\mathcal{M}$-adhesive context.
-
-\noindent
-\parbox{7cm}{
-\begin{restatable}{lemma}{mpo}\label{lem:mpo}
-	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top face is an $\mathcal{M}$-pushout. Then the right square is a pushout.
-\end{restatable}}\hfill 
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_{m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_{n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
-
-[Proof in \Cref{mpo-proof}]
-
-As a final step, we explore the link between regular epis and kernel pairs.
+We explore the link between regular epis and kernel pairs.
 
@@
 \end{restatable}
-[Proof in \Cref{epic-proof}]
+%[Proof in \Cref{epic-proof}]
 
@@
 \end{restatable}
-[Proof in \Cref{natepi-proof}]
+%[Proof in \Cref{natepi-proof}]
 
@@
 \end{restatable}
-[Proof in \Cref{epicol-proof}]
-
-\input{./fact_sys}
+%[Proof in \Cref{epicol-proof}]
+
+We now explore some further properties of kernel pairs and their link with adhesive categories. 
+These two final results appear to be original, and we add their proofs in \Cref{kpp-proof}.
+
+\begin{restatable}{lemma}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
+	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given. 
+	%
+	If the leftmost square is commutative, then there exists a a unique arrow $k_h: K_f \to K_g$ making the other two commutative.
+	%
+	Moreover, if the leftmost is a pullback, then also the other two are so.
+%
+	\[\xymatrix{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
+
+\end{restatable}
+%[Proof in \Cref{kpp-proof}]
+
+The previous result allows us to deduce the following lemma in an $\mathcal{M}$-adhesive context.
+
+\noindent
+\parbox{7cm}{
+\begin{restatable}{proposition}{mpo}\label{lem:mpo}
+	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top face is an $\mathcal{M}$-pushout. Then the right square is a pushout.
+\end{restatable}}\hfill 
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_{m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_{n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+
+%[Proof in \Cref{mpo-proof}]
+%
+%\input{./fact_sys}
 
@@
 \todo{forse possiamo anche cancellare tutti gli esempi sotto}
+\todo{FG ne lascerei uno, ripreso magari dalla intro e presentato come string diagram}
 
@@
 \todo{anche questo forse val la pena toglierlo}
+\todo{presentarlo come string diagram e magari prendere la segnatura de un esempio egg}
+
 We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
@@
 
-This section contains the proofs which are omitted from the main body oof the paper. We begin stating  a well-known fact about composition and decomposition of pullbacks \cite{mac2013categories}.
+This section contains the proofs which are omitted from the main body of the paper. 
+%
+We begin recalling  a well-known fact about composition and decomposition of pullbacks \cite{mac2013categories}.
 
@@
 	\xymatrix@R=18pt{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}}
+\commentato{
 \begin{proof}
@@
 \end{proof}
-
+}
+%
+\commentato{
 \subsection{Proofs for \Cref{sec:ade}}
@@
 \end{proof}
+}
 
@@
 
+\commentato{
 \epic*
-
 \noindent 

### 2025-02-24 calco/main.tex
riassunti due remark

@@
 	$\tg$ in general does not have terminal objects. 
+	%Consider an algebraic signature in $\Set$. 
+	Since $U_{\tg}$ preserves limits, if a terminal object exists it must have the singleton as set of nodes, therefore the set of hyperedges must be empty or a singleton. 
+	Hence, for a counterexample, it suffices to take as signature the one given by two operations $a$ and $b$, both of arity $0$.
+	$\tg$ is not an adhesive category, either. 
+	In particular, as noted in e.g.~\cite{CastelnovoGM24}, 
+	 it does not have pushouts along all monos. 
+\end{remark}
+
+\commentato{
+\begin{remark}
+	$\tg$ in general does not have terminal objects.
 Consider an algebraic signature in $\Set$.
 Since $U_{\tg}$ preserves limits, if a terminal object exists it must have the singleton as set of nodes, therefore the set of hyperedges must be empty or a singleton $\{h\}$.
-Now take as signature the one given by two operations $a$ and $b$, both of arity $0$; we have three term graphs with only one node $v$: $\Delta_{\tg{\Sigma}}(\{v\})$, $(l_a, !_{V_{\mathcal{G}}})\colon \mathcal{G}_a\to \mathcal{G}^{\Sigma}$ and $(l_b, !_{V_{\mathcal{G}}})\colon \mathcal{G}_b\to \mathcal{G}^{\Sigma}$.
+Hence, for a counterexaqmple it suffices to take as signature the one given by two operations $a$ and $b$, both of arity $0$; we have three term graphs with only one node $v$: $\Delta_{\tg{\Sigma}}(\{v\})$, $(l_a, !_{V_{\mathcal{G}}})\colon \mathcal{G}_a\to \mathcal{G}^{\Sigma}$ and $(l_b, !_{V_{\mathcal{G}}})\colon \mathcal{G}_b\to \mathcal{G}^{\Sigma}$.
 	\begin{center}\begin{tikzpicture}

### 2025-02-24 calco/main.tex
minima

@@
 In Section~\ref{sec:hyper} we present the graphical structures of our interest, 
-namely (labelled) hypergraphs and term graphs, and we provide a
+ (labelled, acyclic) hypergraphs and term graphs, and we provide a
 functorial characterisation, which allows for proving their adhesivity properties.
-This is further expended in Section~\ref{hypereq} for describing hypergraphs 
+This is expended in Section~\ref{hypereq} for describing hypergraphs 
 and term graphs with equivalence and in Section~\ref{eggs} for capturing
@@
 %
-All the proofs have been moved to the appendix. For the sake of completeness, 
-and in order to fix the notation, we prove all the results 
-recalled in the background section, besides those that are original 
-to our work.
+All the proofs have been moved to the appendices. 
+%For the sake of completeness, 
+%and in order to fix the notation, we prove all the results 
+%recalled in the background section, besides those that are original 
+%to our work.
 

### 2025-02-24 calco/main.tex
minima

@@
 
-We now explore some further properties of kernel pairs and their link with adhesive categories. 
-These two final results appear to be original, and we add their proofs in \Cref{kpp-proof}.
+We now explore some properties of kernel pairs and their link with adhesive categories. 
+The results below appear to be original, and we give their proofs in \Cref{kpp-proof}.
 
@@
 
-We open this section with the definition of hypergraphs and we will see how to label them with an algebraic signature.
+We open this section with the definition of hypergraphs and we show how to label them with an algebraic signature.
 

### 2025-02-26 calco/main.tex
minima
correzioni

@@
 Given an object $X$, we  denote by $?_X$ the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one.
+We will also use the notation $e\colon X\eto Y$ to denote that an arrow $e\colon X\to Y$ is a regular epi.
 %\end{notation}
@@
 
-We will briefly list some examples of $\mathcal{M}$-adhesive categories.
+We briefly list some examples of $\mathcal{M}$-adhesive categories.
 
@@
 \begin{restatable}{proposition}{epic}\label{prop:reg_epi_coeq}
-    Let $e\colon X \to Y$ be a regular epi in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then, $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
+    Let $e\colon X \eto Y$ be a regular epi in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then, $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
 \end{restatable}
@@
 \begin{restatable}{corollary}{natepi}\label{cor:reg_epi_components_reg_epi_nat_trans}
-    Let $\X$ be a category with pullbacks and $\phi\colon F \dot\to G$ a natural transformation between functors $F, G: \D \rightrightarrows \X$.
-If $\phi_d$ is a regular epi for every $d$ in $\D$, then $\phi$ is a regular epi.
+    Let $\X$ be a category with pullbacks and $\phi\colon F \to G$ a natural transformation between functors $F, G: \D \rightrightarrows \X$.
+If $\phi_d$ is a regular epi for every $d$, then $\phi$ is a regular epi.
 \end{restatable}
@@
 
-In this section we briefly recall the notion \emph{$\X$-hypergraph}. It is necessary to have a monad $(-)^\star\colon \Set\to \Set$, also known as \emph{list monad},
-sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95} and playing a role analogous to the usual \emph{Kleene star}.
+In this section we briefly recall the notion of \emph{hypergraph}.
+In order to so, a pivotal role is played by the \emph{Kleen star} monad $(-)^\star\colon \Set\to \Set$, also known as \emph{list monad},
+sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95}.
 We recall some of its proprieties.
@@
 
-\begin{remark}\label[remark]{rem:length}Notice that $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $!^\star_X\colon X^\star \to \mathbb{N}$, which sends a word to its length.
+\begin{remark}\label[remark]{rem:length}Notice that $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length.
 \end{remark}
@@
 
-\todo{forse possiamo anche cancellare tutti gli esempi sotto}
 \todo{FG ne lascerei uno, ripreso magari dalla intro e presentato come string diagram}
@@
 We will decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
-
+\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
+\iffalse 
 \begin{example}Take $V_{\mathcal{G}}$ to be be $\{v_1, v_2, v_3, v_4, v_5\}$ and $E_{\mathcal{G}}$ to be $\{h_1, h_2, h_3\}$. Sources and targets are given by:
@@
 \end{example}
+\fi
+
 \begin{example}\label[example]{exa_2} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
@@
 
+\begin{remark}\label{rem:functor}
+	It is worth to point out, as first noted in \cite{bonchi2022string}, that $\hyp$ is actually equivalent to a category of functors.
+
+	Indeed, consider the category $\catname{H}$ in which the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$ and arrows are given by the identities $\id{k,l}$, $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$.
+
+	It is quite straightforward to see that functors $\catname{H}\to \Set$ corresponds exactly to hypergaphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
+\end{remark}
+
+In particular, \Cref{rem:functor} entails the following result.
+
+\begin{proposition}\label{prop:cocomp}
+	$\hyp$ has all limits and colimits.
+\end{proposition}
+
+\iffalse
 \subsubsection{$\hyp$ as a category of functors}
@@
 \end{proposition}
+\fi
 
@@
 \end{definition}
+
+\todo{Decidere se tenere questo esempio}
 
@@
 The second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V^{\star}$ of words of length $1$, i.e.
-$t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to \tau_{\mathcal{H}}$.
+$t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
 \end{remark}
@@
 $\hyp_{\Sigma}$, has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \X$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\X}(\mathcal{H}$).
-Now, $U_{\X}(\mathcal{G}^{\Sigma})=1$ thus, for every object $X$, there is only one arrow $X\to U_{\X}(\mathcal{G}^{\Sigma})$.
-Define $\Delta_{\Sigma}(X)\colon \Delta_{\X}(X)\to \mathcal{G}^{\Sigma}$ as the transpose of this arrow.
-Explicitly, $\Delta_{\X}(X)=(0, X, ?_{X^\star}, ?_{X^\star})$ and $\Delta_\Sigma(X)$ is simply $(?_{O_\Sigma}, !_{X})$.
+Now, $U_{\hyp}(\mathcal{G}^{\Sigma})=1$ thus, for every set $X$ we can define $\Delta_{\Sigma}(X)\colon \Delta_{\X}(X)\to \mathcal{G}^{\Sigma}$  as $(?_{O_\Sigma}, !_{X})$.
+It is straightforward to see that in this way we get a left adjoint to $U_\Sigma$.
 
@@
 \end{proposition}
+\iffalse 
 \begin{proof}Let $(h, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be an object of $\hyp_{\Sigma}$, and suppose that there exists $f\colon X\to U_{\Sigma}(\mathcal{H})$.
@@
 \end{proof}
+\fi
 
@@
 \begin{example}\label[example]{lab_1}
-	The simplest example is given by the identity $\id{\mathcal{G}^\Sigma}\colon \mathcal{G}^\Sigma\rightarrow \mathcal{G}^{\Sigma}$. If $\Sigma$ is the signature of groups $\Sigma_G$we get 
+	The simplest example is given by the identity $\id{\mathcal{G}^\Sigma}\colon \mathcal{G}^\Sigma\rightarrow \mathcal{G}^{\Sigma}$. If $\Sigma$ is the signature of groups $\Sigma_G$ we get 
 	\begin{center}
@@
 
+\todo{Decidere se tenere questo esempio (io direi di no)}
 \begin{example}\label[example]{lab_2}
@@
 
-\input{Hypergraphs_with_equivalences}
+\section{Adding equivalences to hypergraphical structures}
+\label{hypereq}
+\todo{A very nice instroduction}
+
+\subsection{Hypergraphs with equivalence}
+
+Let us start with the case of general hypergraphs.
+
+\begin{definition}
+	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, Q_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $Q_\mathcal{G}$ is a set and $q_{\mathcal{G}}: V_{\mathcal{G}}\eto Q_{\mathcal{G}}$ is a surjection called \emph{quotient map}.
+	%
+	A morphism $h\colon \mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute
+	\[\xymatrix{
+		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_C} \\
+		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}^\star}}& {V_\mathcal{H}}\ar@{>>}[r]_{q_\mathcal{H}} & {Q_\mathcal{H}}
+	}\]
+	The category of hypergraphs with equivalences and their morphisms is denoted $\EqHyp$.
+
+\end{definition}
+
+\begin{remark}
+	Notice that in $\Set$ the classes of surjections, epis and regular epis coincide.
+\end{remark}
+
+\begin{remark}\label{rem:eqhyp_morphs}
+	Morphisms of hypergraphs with equivalences are uniquely determined by the first two components.
+That is, if $h_1 = (h_E, h_V, f)$ and $h_2 = (h_E, h_V, g)$ are two morphisms $\mathcal{G} \rightrightarrows \mathcal{H}$, then we have
+	\[f \circ q_\mathcal{G} = q_\mathcal{H}\circ h_V =g\circ q_\mathcal{G}\]
+
+	Since $q_\mathcal{G}$ is epi, we obtain $f = g$.
+\end{remark}
+
+Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ which sends an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
+We can now explore some of its properties to deduce some information on the structure of $\EqHyp$.
+
+\begin{restatable}{proposition}{fhyp}  The following are true:
+	\begin{enumerate}
+		\item$T$ is faithful;
+		\item $T$ has a left adjoint;
+		\item $T$ has a right adjoint.
+	\end{enumerate}
+\end{restatable}
+A proof is provided in \Cref{prop:forghyp}.
+
+\begin{corollary}\label{cor:limcolim}
+	The functor $T$ preserves limits and colimits.
+\end{corollary}
+
+Combining together the previous corollary with \Cref{rem:eqhyp_morphs} we get the following characterization of monos in $\EqHyp$.
+
+\begin{corollary}\label{cor:mono1}
+	An arrow $h = (h_E, h_V, h_C): \mathcal{G \to H}$ in $\EqHyp$ is mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
+\end{corollary}
+
+\commentato{
+	\todo{questo non serve a nulla e in più è pure scritto sbagliato}
+$\EqHyp$ has a forgetful functor $U_{\EqHyp}:\EqHyp \to \Set$, which sends each $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ into $V_\mathcal{G}$, and each $h = (h_E, h_V, h_C)$ onto $h_V$.
+
+\begin{corollary}\label{cor:ladj}
+	$U_\EqHyp$ has a left adjoint $\Delta_{\EqHyp}: \Set \to \EqHyp$.
+\end{corollary}
+
+\begin{proof}
+	For each set $X$, define $\Delta_\EqHyp(X):= (\emptyset, X, \{\bullet\}, ?_X, ?_X, !_X)$. Consider now $h: \Delta_{\EqHyp}(X) \to \mathcal{H}$.
+	\[\xymatrix@C=2.3cm{
+		\Delta_{\EqHyp}(X) \ar@{.>}[d]_{\Delta_\EqHyp(f)} \ar[dr]^{h} & \\
+		\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) \ar[r]_{\epsilon_{\mathcal{H}}} & \mathcal{H}
+	}\]
+	Where $\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) = (\emptyset, V_\mathcal{H}, \{\bullet\}, ?_{V_\mathcal{H}}, ?_{V_\mathcal{H}}, !_{V_\mathcal{H}})$ and $\epsilon_{\mathcal{H}} = (?_{E_\mathcal{H}}, \id{V_\mathcal{H}}, g)$.
+	Note that, since $\Delta_{\EqHyp}(X)$ has the empty set as object of edges, $h_E = ?_{E_\mathcal{H}}$, then, the unique arrow that fits in the diagram is $\Delta_{\EqHyp}(f) = (?_{E_\mathcal{H}}, h_V, \id{\{\bullet\}})$.
+\end{proof}}
+
+Let us notice that there $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
+We are now going to exploit it to compute limits and colimits in $\EqHyp$.
+In order to do so.
+A full proof of the following lemma can be found in \Cref{proof:comp}.
+
+\noindent
+\parbox{11cm}{
+\begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
+Let $F\colon \D \to \EqHyp$ be a diagram, and let $(\mathcal{E}_d, V_d, Q_d, s_d, t_d, q_d)$ be the image of an object $d$. Then the following hold true:
+\begin{enumerate}
+		\item $F$ has a colimit which is preserved by $K$;
+	\item let $(L, \{l_d\}_{d\in \D})$ be a limiting cocone for $K \circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$, where $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ is limiting for $T\circ F$.
+\end{enumerate}
+\end{restatable}}\hfill 
+\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>->}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
+
+\begin{corollary}\label{cor:mono2}
+	If $h = (h_E, h_V, h_C): \mathcal{G\to H}$ is a regular mono in $\EqHyp$, then $h_E, h_V$ and $h_C$ are all monos.
+\end{corollary}
+\todo{Questa è da rifare completamente}
+\begin{proof}
+	If $h$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos. Suppose now $f, g: \mathcal{H\rightrightarrows K}$ be the arrows equalized by $h$. Then, we have:
+	\begin{align*} f_C \circ h_C \circ q_\mathcal{G} &= f_C\circ q_\mathcal{H} \circ h_V\\&=q_\mathcal{K}\circ g_V \circ h_V\\&=q_\mathcal{K}\circ f_V \circ h_V\\&=g_C \circ h_C \circ q_\mathcal{G} \end{align*}
+	Since $q_\mathcal{G}$ is epi, we have $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, and thus a mono.
+\end{proof}
+
+\iffalse 
+\begin{proposition}
+	Let $h = (h_E, h_V, h_C): \mathcal{G \to H}$ be a regular mono in $\EqHyp$.
+	Then, $h_E$ and $h_V$ are monos and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{H}\circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$.
+\end{proposition}
+
+\begin{proof}
+	By \Cref{cor:mono2}, we have that $h_E, h_V$ and $h_C$ are all monos.
+	Hence, by \Cref{cor:kermono}, $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$ if and only if it is the kernel pair also of $h_C \circ q_\mathcal{G}$, since $h_C$ is mono by hypothesis.
+	The thesis follows from $h_C \circ q_\mathcal{G} = q_H \circ h_V$, and from the hypothesis of $h_E$ mono.
+\end{proof}
+
+\begin{remark}
+	It is possible to restate the last proposition, by \Cref{ex:kernel_pairs_in_Set}, as 
+	\begin{displayquote}
+		\textit{$h_E$ and $h_V$ are mono and, for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$}
+	\end{displayquote}
+	That is, a regular mono in $\EqHyp$ is a morphism that both reflects and preserves equivalences.
+	% besides preserving them.
+\end{remark}
+\fi
+
+Let us turn to another functor $\EqHyp \to \hyp$.
+
+\begin{definition}
+	The \emph{quotient functor} $Q:\EqHyp\to \hyp $ is defined as
+	the one sending $(E, V, C, s, t, q)$ to $(E, C, q^{\star}\circ s, q^{\star}\circ t)$ and an arrow $(h_E, h_V, h_C)$ to $(h_E, h_C)$.
+\end{definition}
+
+\begin{remark}
+	The action of the functor on a morphism of hypergraphs with equivalences gives a morphism of hypergraphs,
+	in fact $q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E = q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G} = h_C^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}$.
+	The same is valid for $t_\mathcal{H}$ and $t_\mathcal{G}$. 
+\end{remark}
+
+\begin{lemma}\label{lemma:quot_funct_left_adj}
+	$Q$ is a left adjoint.
+\end{lemma}
+
+\begin{proof}
+	Let $R((A, B, s, t))$ be $(A, B, B, s, t, \id{B})$, so that $Q(R((A, B, s, t))) = (A, B, s, t)$.
+Now, suppose that $h = (h_E, h_V): Q((E, V, C, s', t', q)) \to (A, B, s, t)$  is an arrow in $\hyp$, and consider the triple $(h_E, h_V, h_V \circ q)$.
+Since $h$ is a morphism of $\hyp$, we have $h_V^{\star}\circ q^{\star}\circ s'= s\circ h_E$ and $h_V^{\star}\circ q^{\star}\circ t' = t\circ h_E$.
+	Then we have the following squares
+	\[\xymatrix{
+		E \ar[r]^{h_E}\ar[d]_{s'} & A \ar[d]^{s} & E \ar[r]^{h_E}\ar[d]_{t'} & A \ar[d]^{t} & V \ar[r]^{h_V \circ q} \ar[d]_{q} & B \ar[d]^{\id{B}} \\
+		V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & C \ar[r]_{h_V} & B
+	}\]
+
+	\iffalse\[
+	\begin{tikzcd}
+		E \arrow[r, "{h_E}"] \arrow[d, "{s_G}"swap] & A \arrow[d, "s"] \\
+		V \arrow[r, "{h_V \circ q}"swap] & B
+	\end{tikzcd}
+	\qquad
+	\begin{tikzcd}
+		E \arrow[r, "{h_E}"] \arrow[d, "{t_G}"swap] & A \arrow[d, "t"] \\
+		V \arrow[r, "{h_V \circ q}"swap] & B
+	\end{tikzcd}
+	\qquad
+	\begin{tikzcd}
+		V \arrow[r, "{h_V\circ q}"] \arrow[d, "q" swap] & B \arrow[d, "{id_B}"] \\
+		C \arrow[r, "{h_V}"swap] & B
+	\end{tikzcd}
+	\]\fi
+	We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below
+	\[\xymatrix{
+		(A, B, s, t) \ar[r]^{(\id{A}, \id{B})} & (A, B, s, t)\\
+		(E, C, q^\star\circ s', q^\star\circ t') \ar[u]^{Q(h_E, h_V \circ q, h_V)} \ar[ur]_{(h_E, h_V)}
+	}\]   
+	Such arrow is unique. Suppose $f = (f_E, f_V, f_C)$ to be another arrow with such property.
+	Then, it must be $(\id A, \id B) \circ Q(f) = (f_E, f_C) = (h_E, h_C)$. Finally, $f_C = f_V \circ q = h_V \circ q$. 
+\end{proof}
+
+\begin{proposition}\label{prop:quot_creat_colims}
+	$Q$ creates colimits.
+\end{proposition}
+
+\begin{proof}
+	Since $Q$ is a left adjoint, it preserves colimits.
+	Let $D: \cat I \to \EqHyp$ be a diagram, and let $\mathcal{C}$, together with  $(c_i)_{i\in \cat I}$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
+	\iffalse
+	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.\fi
+	Let $((\kappa_i)_{i\in \cat I}, V)$ be the colimit of $U_\EqHyp \circ D$.
+	Consider the following situation
+	\[\xymatrix{
+		&  {V} &                             \\
+		V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
+		C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
+		&  {C} &
+	}\]
+	Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $U_\EqHyp \circ D$, there exists a unique $q: V \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
+	Consider now the functor $W: \EqHyp \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component.
+	By \Cref{prop:eqhyp_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, E)$ is the colimit of $W \circ D$.
+	Notice that $((\kappa_i \circ s_i)_{i \in \cat{I}}, B)$ and $((\kappa_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
+It remains now to show that $(E, V, C, s, t, q)$, together with $(c_E^i, \kappa_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
+\end{proof}
+
+\begin{example}
+	$Q$ does not preserve limits.
+Indeed, let $\mathcal{G}_1 = (E_1, A, A, s_1, t_1, id_A)$, $\mathcal{G}_2 = (E_2, B, B, s_2, t_2, id_B)$ and $\mathcal{G}_3 = (E_3, A + B, \terminal, s_3, t_3, !_{A + B})$, and let $h = (h_E, \iota_A, !_A): \mathcal{G}_1 \to \mathcal{G}_3$, $k = (k_E, \iota_B, !_B): \mathcal{G}_2 \to \mathcal{G}_3$, where $(\iota_A, \iota_B, A + B)$ is the coproduct of $A$ and $B$, $\terminal$ is the intial object (in $\Set$, the singleton set as shown in \Cref{ex:set_init_term}), and $!_X$ the unique arrow $X \to \terminal$.
+	The following two diagrams show the pullback of $h$ and $k$ and the pullback of $Q(h)$ and $Q(k)$, on the second component (the vertices of the graphs)
+	\[\xymatrix{
+		\initial \ar[r]^{p_1} \ar[d]_{p_2}& A \ar[d]^{\iota_A} \\
+		B \ar[r]_{\iota_B} & A+B
+	}
+	\qquad
+	\xymatrix{
+		{A \times B} \ar[r]^{\pi_A} \ar[d]_{\pi_B} & A \ar[d]^{!_A} \\
+		B \ar[r]_{!_B} & \terminal
+	}\]
+
+	But the arrow $\initial \to A \times B$ is not an epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
+\end{example}
+
+We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$. In particular, we are now going to show that $\EqHyp$ is $\reg(\EqHyp)$-adhesive.
+
+\begin{lemma}\label{lemma:stab}
+	In $\EqHyp$, pushouts along regular monos are stable.
+\end{lemma}
+
+\begin{proof}
+	Let $\mathcal{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, C'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
+	and, in the diagram below, suppose all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is regular mono.
+	\[
+	\xymatrix@C=10pt@R=6pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{t'} \\ \mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d}\\&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{t} \\\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 }
+	\]
+	By \Cref{prop:eqhyp_complete} and \Cref{cor:mono1}, the following cubes in $\Set$ have pushouts as bottom faces and pullbacks as vertical faces, hence their top faces are pushouts.
+	\[
+	\xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ A_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}\\&A_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{t_E} \\A_3 \ar[rr]_{p_E} & & A_4 }
+	\qquad
+	\xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ B_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\&B_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{t_V} \\B_3 \ar[rr]_{p_V} & & B_4 }
+	\]
+	Consider now the following pullbacks.
+	\[\xymatrix{
+		Y \ar[d]_{y_2}\ar[r]^{y_1}&{C_4'}\ar[d]^{d_C}&U\ar[d]_{u_2}\ar[r]^{u_1}&{C_4'}\ar[d]^{d_C}&T\ar[r]^{x_1}\ar[d]_{x_2}&U\ar[d]^{u_2}\\
+		C_3\ar[r]_{p_C}&C_4&C_2\ar[r]_{t_C}&C_4&C_1\ar[r]_{h_C}&C_2
+	}\]
+	Thus, [???]\todo{inserire in sezione 1 la proposizione} yields the following situation, in which the bottom face is a pushout, and the vertical faces are pullbacks, hence the top face is a pushout too.
+	\[\xymatrix@C=10pt@R=6pt{&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar@{.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C_4' \ar[dd]_(.3){d_C}\\&C_1\ar[rr]|\hole^(.65){h_C} \ar[dl]^{k_C} && C_2 \ar[dl]^{t_C} \\C_3 \ar[rr]_{p_C} & & C_4 }\]
+	By the proof of \Cref{prop:eqhyp_complete}, we have that $m_2 \circ q'_3 : B'_3 \to Y$ and $m_3 \circ q'_2 : B_2' \to U$ are two epi-mono factorizations, with $m_2$ and $m_3$ monos.
+	At the same way, let the following square to be a pullback.
+	\[\xymatrix{S\ar[r]^{s_1}\ar[d]_{s_2}&C'_2\ar[d]^{m_3}\\T\ar[r]_{x_1}&U}\]
+	Hence, in the following diagram, the outer rectangle is a pullback.
+	\[\xymatrix{
+		S\ar[r]^{s_1}\ar[d]_{s_2}&C'_2\ar[d]^{m_3}\\T\ar[r]_{x_1}\ar[d]_{x_2}&U\ar[d]^{u_2}\\C_1\ar[r]_{h_C}&C_2
+	}\]
+	By the same argument as before, there exists a mono $m_1$ such that $m_1\circ q_1' : B_1' \to S$.
+	% Uguaglianze da capire se servono davvero
+
+	We have to show that the top face of the cube ate the beginning of the proof is a pushout.
+	Suppose then that $z: \mathcal{G}_2' \to \mathcal{H}$ and $w: \mathcal{G}_3' \to \mathcal{H}$, with $\mathcal{H} = (E, V, C, s, t, q)$,
+	are two morphisms such that $z \circ h' = w \circ h'$, and let $v_V: B'_4 \to V$ the arrow induced by $z_V$ and $w_V$.
+	We want to construct the dotted arrow $v_C$ which fits in the diagram below.
+	\[
+	\xymatrix@C=10pt@R=6pt{
+		&B_1'\ar[dd]|\hole_(.65){q_1'}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]|\hole_(.65){q_2'} \ar[dl]_{t_V'}\ar[dr]^{z_V}\\
+		B_3'  \ar[dd]_{q_3'}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
+		&C_1'\ar[rr]|\hole^(.65){h_C'} \ar[dl]_{k_C'} && C_2' \ar[dl]^{t_C'}\ar[dr]^{z_C}\\
+		C'_3 \ar[rr]_{p_C'} & & C'_4\ar@{.>}[rr]_{v_C} && C
+	}\]
+	By \Cref{lem:mpo}, we know that the top face of the cube below is a pushout.
+	\[\xymatrix@C=15pt@R=15pt{&K_{s_2\circ m_1\circ q'_1}\ar[dd]|\hole_(.65){\pi_{s_2\circ m_1\circ q'_1}^{1}}\ar[rr]^{k_{h'_2}} \ar[dl]_{k_{k'_2}} && K_{m_2\circ q'_2} \ar[dd]^{\pi_{m_2\circ q'_2}^{1}} \ar[dl]_{k_{t'_2}} \\ K_{m_3\circ q'_3}  \ar[dd]_{\pi_{m_3\circ q'_3}^{1}}\ar[rr]^(.7){k_{p'_2}} & & K_{q'_4} \ar[dd]_(.3){\pi_{q'_4}^{1}}\\&B'_1\ar[rr]|\hole^(.65){h'_2} \ar[dl]^{k'_2} && B'_2 \ar[dl]^{t'_2} \\B'_3 \ar[rr]_{p'_2} & & C_4}\]
+	And, since $m_3$ and $m_2$ are monos,
+	\[\begin{split}
+		q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
+	\end{split}\qquad\begin{split}
+		q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
+	\end{split}\]
+	Computing, we obtain
+	\[\begin{split}
+		q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\
+		&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\
+		&= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
+		&= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\
+		&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 \\
+		&= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\
+		&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}
+	\end{split}\qquad\begin{split}
+		q \circ v_V \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\
+		&= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\
+		&= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
+		&= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\
+		&= q \circ z_V \circ \pi_{m_2 \circ q_2'}^2 \\
+		&= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\
+		&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{t'_V}
+	\end{split}\]
+	Since the previous cube has a pushout as top face, by universal property, we have
+	\[
+	q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
+	\]
+	hence, $v_C$ is the mediating arrow.
+	\[
+	v_C \circ q'_4 \circ \pi_{q'_4}^1 = v_C \circ q'_4 \circ \pi_{q'_4}^2
+	\]
+\end{proof}
+
+\begin{lemma}\label{lemma:van_kampen}
+	In $\EqHyp$, pushouts along regular monos are $\reg(\EqHyp)$-Van Kampen.
+\end{lemma}
+
+\begin{proof}
+	In lieu of \Cref{lemma:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono,
+	the front faces are pullbacks too, where $\mathcal{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
+	\[
+	\xymatrix@C=10pt@R=6pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{t'} \\ \mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d}\\&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{t} \\\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 }
+	\]
+	By \Cref{prop:eqhyp_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as back faces,
+	thus their front faces are pullbacks too.
+	\[
+	\xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ A_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}\\&A_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{t_E} \\A_3 \ar[rr]_{p_E} & & A_4 }
+	\qquad
+	\xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ B_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\&B_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{t_V} \\B_3 \ar[rr]_{p_V} & & B_4 }
+	\]
+	On the other hand we can consider the diagrams below, in which the inner squares are pullbacks.
+	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon C'_2\to U$, $m_3\colon C'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
+	\[\xymatrix{C'_3 \ar@{.>}[dr]^{m_3} \ar@/^.3cm/[drr]^{p'_3} \ar@/_.3cm/[ddr]_{d_3} &&& C'_2 \ar@{.>}[dr]^{m_2} \ar@/^.3cm/[drr]^{t'_3} \ar@/_.3cm/[ddr]_{d_2}\\&Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
+
+	\[\xymatrix{B'_3 \ar@{.>}[dr]^{a_3} \ar[r]^{p'_2} \ar[d]_{q'_3} &B'_4\ar[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{t'_2} \ar[d]_{q'_2} &B'_4\ar[dr]^{q'_4}\\C'_3 \ar[dr]_{d_3} &Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&C_2' \ar[dr]_{d_2}& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
+
+	Now, notice that  $m_3$ and $m_2$ are monos because $d_3$ and $d_2$ are regular monos. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
+	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
+
+	Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $a_3$ and $a_2$ and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:eqhyp_complete}.
+
+	No if we compute we have:
+	\[\begin{split}
+		y_1\circ a_3&= q'_4\circ p'_2\\&=p'_3 \circ q'_3\\&=y_1\circ m_3\circ q'_3  
+	\end{split}\qquad \begin{split}
+		u_1\circ a_2&= q'_4\circ t'_2\\&=t'_3 \circ q'_3\\&=u_1\circ m_2\circ q'_2  
+	\end{split}\]
+	\[\begin{split}
+		y_2\circ a_3&= d_3\circ q_3'\\&=y_2\circ m_3\circ q'_3
+	\end{split}\qquad \begin{split}
+		u_2\circ a_2&= d_2\circ q_2'\\&=u_2\circ m_2\circ q'_2
+	\end{split}\]
+	And we have done.
+\end{proof}
+
+%\input{Hypergraphs_with_equivalences}
 \input{Labeled_hyp_with_eq}
@@
 %
+
+\subsection{Proofs for \Cref{sec:ade}}\label{app:primo}
 \commentato{
-\subsection{Proofs for \Cref{sec:ade}}
 \regmono*
@@
 }
+
+\subsection{Proofs for \Cref{hypereq}}\label{app:due}
+\fhyp*
+
+\begin{proof}\label{prop:forghyp}
+	\begin{enumerate}
+		\item  This follows at once from \Cref{rem:eqhyp_morphs}.
+		\item  	Let $\mathcal{H}$ be a hypergraph, and define $L(\mathcal{H}) := (E_\mathcal{H}, V_{\mathcal{H}}, V_{\mathcal{H}}, s_\mathcal{H}, t_\mathcal{H}, \id{V_\mathcal{H}})$.
+By construction we have $T(L(\mathcal{H}))=\mathcal{H}$, thus we can define
+		$\eta_\mathcal{H}\colon \mathcal{H}\to T(L(\mathcal{H}))$ as the identitye $\id{\mathcal{H}}$.
+
+		To see that in this way we get a unit,  take an arrow $(h, k)\colon \mathcal{H}\to T(\mathcal{G})$ for some $\mathcal{G}$ in $\EqHyp$.
+Then $(h,k, q_{\mathcal{G}}\circ k)$ is an arrow $L(\mathcal{H})\to \mathcal{G}$ and the unique one such that $T(h,k, q_{\mathcal{G}}\circ k)\circ \eta_{\mathcal{H}}=(h,k)$
+
+		\item For every hypergraph $\mathcal{H}$ define $R(\mathcal{H})$ as $(E_\mathcal{H}, V_{\mathcal{H}}, 1, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$, so that $T(R(\mathcal{H}))$ is again $\mathcal{H}$.
+Now, let $\epsilon_{\mathcal{H}}\colon T(R(\mathcal{H}))\to \mathcal{H}$ be the identity and take an arrow $(h,k)\colon T(\mathcal{G})\to \mathcal{H}$ for some $\mathcal{G}$ in $\EqHyp$.
+Notice that $!_{Q_\mathcal{G}}\circ q_{\mathcal{G}}=!_{V_{\mathcal{H}}}\circ k$
+		so that $(h,k, !_{Q_\mathcal{G}})$ is an arrow $\mathcal{G}\to R(\mathcal{H})$ of $\EqHyp$ such that $\epsilon_{\mathcal{H}}\circ T(h,k, !_{Q_\mathcal{G}})=(h,k)$.
+
+		Uniqueness of such an arrow follows at once from the first point and the fact that $1$ is terminal. \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\begin{remark}\label{rem:fact}
+	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~ surjections) and of monos in$\Set$.
+In particular, we need the fact thatthey form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.
+This amount to ask that:
+
+	\noindent 
+	\parbox{11.5cm}{
+	\begin{enumerate} 
+		\item Every arrow $f\colon X\to Y$ can be factored as $m\circ e$, where $e\colon X\eto Q$ is a regular epi and $m\colon Q\mto Y$ is a monomorphism;
+			\item for every square as the one on the right, with $e\colon X\eto E$ a surjection and $m\colon N\mto Y$ a mono, there exists a unique $k\colon E\to N$ making it commutative.
+	\end{enumerate}}\hfill \parbox{2cm}{\xymatrix{X \ar@{>>}[d]_{e}\ar[r]^{f}& N \ar@{>->}[d]^{m} \\ E \ar[r]_{g} & Y}}
+
+	\hspace{1pt}\newline 
+	From these properties, one can deduce that if $f=m\circ e$ and $f=m'\circ e'$ are two factorizations of $f$ then there is an isomorphism $\phi$ such that $m=m'\circ \phi$ and $\phi \circ e=e'$.
+\end{remark}
+
+\noindent
+\parbox{11cm}{
+\comp*}\hfill 
+\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>->}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
+
+\begin{proof}\label{proof:comp}
+	\begin{enumerate}
+		\item Suppose now $(E', V', s', t')$, together with $(\kappa_E^i, \kappa_V^i)_{i \in \cat I}$, be the colimit of $T \circ D$, and $C'$, with $(c_i)_{i \in \cat I}$ be the colimit of $K \circ D$.
+		Then, we have the folliwing situation.
+		\[\xymatrix{
+			&  {V'} &                             \\
+			V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
+			C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
+			&  {C'} &
+		}\]
+		Then, $C'$ with morphisms $(c_i \circ q_i)_{i\in \cat I}$ is a conone for $U \circ D$. Then, there exists a unique morphism $q': V' \to C'$ such that $q'\circ \kappa_V^i = c_i\circ q_i$.
+		Such morphism is epi ({\color{red}cite Lemma 1.3.45 of the thesis}), and thus $(E', V', C', s', t', q')$, together with $(\kappa_E^i, \kappa_V^i, c_i)_{i\in \cat I}$ is the colimit of $D$.
+		\item  We know by \Cref{prop:cocomp} that $\hyp$ is complete, we can then consider a cone $((E, V, s, t), \{(\pi^i_E, \pi^d_V)\}_{d\in \D})$ limiting for of $T \circ D$.
+Now, $(V, \{q_d\circ \pi_V^d\}_{d\in \D})$, is a cone for $K \circ D$: indeed, if $\alpha: d \to d'$ is an arrow of $\D$, and $F(\alpha)=(h_1, h_2, f_3)$, then we have
+	\[h_2\circ q_d\circ \pi^d_V =q_{d'} \circ h_2\circ \pi^d_{V}=q_{d'}\circ \pi^{d'}_V\]
+
+\noindent 
+\parbox{9.5cm}{Thus there is an arrow $V\colon L$ such that $l_d\circ l=q_d\circ \pi^d_V$.
+We know that there exist $m\colon Q\mto L$ and $q\colon X\eto Q $ such that $m\circ q=l$.
+Since the identity is mono then there exists a unique arrow $\pi^d_Q$ fitting in the rectangle aside.} 	\hfill \parbox{3cm}{\xymatrix{
+	V\ar[r]^{\pi_V^d}\ar@{>>}[d]_{q}&V_d\ar@{>>}[r]^{q_d}&Q_d\ar[d]^{\id{Q_d}}\\Q\ar@{>->}[r]_{m}\ar@{.>}[urr]^{\pi_Q^d}&L\ar[r]_{l_d}&{Q_d}
+	}}
+
+	Let $\alpha$ be an arrow $d\to d'$ in $\D$, then we have:
+		\[T(F\alpha\circ (\pi^d_{E}, \pi^d_V, \pi^d_Q))=T(F(\alpha))\circ (\pi^d_E, \pi^d_V)=(\pi^{d'}_E, \pi^{d'}_V)=T(\pi^{d'}_{E}, \pi^{d'}_V, \pi^{d'}_Q)\]
+
+		Thus, $((E, V, C, s, t, q), \{(\pi_E^d, \pi_V^d, \pi_C^i)\}_{d\in \D})$ is a cone over $F$.
+To see that it is terminal, let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^d_E, h^d_V, h^d_Q)\}_{d\in \D})$ be another cone, then in particular there is an arrow $(h_E, h_V)\colon (E_\mathcal{G},V_\mathcal{G},  s_{\mathcal{G}}, t_{\mathcal{G}})\to (E, V, s, t)$ in $\hyp$ such that
+		\[\pi^d_E\circ h_E=h^d_E \qquad \pi^d_V\circ h_V=h^d_V\]
+
+		Moreover, applying $K$ we get that $(Q_{\mathcal{G}}, \{h^d_{Q}\}_{d\in \D})$ is a cone over $K\circ F$, so that there is an arrow $h\colon Q_{\mathcal{G}} \to L$ such that $l_d\circ h=h^d_{Q}$.
+Thus:
+		\[l_d\circ h\circ q_\mathcal{G}=h^d_Q\circ q_{\mathcal{G}}=q_{d}\circ h^d_V=q_d\circ \pi^d\circ h_V=l_d\circ l\circ h_V\]
+
+\noindent 
+\parbox{2cm}{\xymatrix{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[ur]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square below commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
+We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that
+\[(\pi^d_E, \pi^d_V, \pi^dQ)\circ (h_E, h_V, k_Q)=(h^d_E, h^d_V, h^d_Q)\]}
+
+Uniqueness follows at once from faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
+	\end{enumerate}
+\end{proof}
 

### 2025-02-26 calco/main.tex
minori

@@
 
+\todo{Tutta la parte qua sotto non mi è chiaro a cosa serva}
 In a category $\cat X$ with pullbacks, each $f: X \to Y$ induces a functor $f^*: \cat X/Y \to \cat X/X$,

### 2025-02-26 calco/Equivalence_term_graphs.tex
minima

@@
 	Let $\Sigma$ be an algebraic signature.
-	A labeled hypergraph with equivalence $l: \mathcal{G} \to L(\mathcal{G}^\Sigma)$ is a \emph{term graph with equivalence} if $t_{\mathcal{G}}$ is mono.
+	A labeled hypergraph with equivalence $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ is a \emph{term graph with equivalence} if $t_{\mathcal{G}}$ is mono.
 	We define category of term graphs with equivalence over $\Sigma$, denoted $\EqTG_{\Sigma}$, as the full subcategory of $\EqHyp_\Sigma$,
@@
 \begin{proposition}
-	If $l: \mathcal{G \to G}^\Sigma$ is a term graph, then $L(l)$ is a term graph with equivalence.
+	If $l: \mathcal{G \to G}^\Sigma$ is a term graph, then $R(l)$ is a term graph with equivalence.
 \end{proposition}
+
+We have a functor $T_\EqTGs : \EqTGs \to \tg$, defined to be $T_\Sigma \circ I_\EqTGs$. Since both $T_\Sigma$ and $I_\EqTGs$ are faithful, so is $T_\EqTGs$.
+
+If $h: \mathcal{H \to G}$ is a mono between $l': \mathcal{H} \to L(\mathcal{G}^\Sigma)$ and $l: \mathcal{G}\to L(\mathcal{G}^\Sigma)$, then, if $l\in\EqTGs$, $l'\in\EqTGs$ as well.
+This let us deduce what follows.
+
+\begin{proposition}
+	$\EqTGs$ has equalizers, and $I_{\EqTGs}$ creates them.
+\end{proposition}

### 2025-02-26 calco/Labeled_hyp_with_eq.tex
minima

@@
 	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to $\Sigma$.
-	Then the \emph{hypergraph with equivalence} associated to $\Sigma$ is $L(\mathcal{G}^\Sigma)$ and the category of hypergraphs with 
+	Then the \emph{hypergraph with equivalence} associated to $\Sigma$ is $R(\mathcal{G}^\Sigma)$ and the category of hypergraphs with 
 	equivalence labeled over $\Sigma$ is the 
@@
 
-We can lift the adjunction given by $T$ and $L$ to $EqHyp_\Sigma$ and $\hyp_\Sigma$.\todo{Non capisco se è uno svarione mio o ha senso}
+%We can lift the adjunction given by $T$ and $L$ to $\EqHyp_\Sigma$ and $\hyp_\Sigma$.\todo{Non capisco se è uno svarione mio o ha senso}
 
-By \Cref{cor:mono1}, we can deduce what follows.
+We can define a functor $T_\Sigma: \EqHyps \to \hyps$ which sends each labeled hypergraph $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ to $T_\Sigma(l) = T(l)$, and each morphism $h = (h_E, h_V, h_C)$ onto $T_\Sigma(h) = T(h)$.
+Such functor is faithful since so is $T$, hence we have the following property.
 

### 2025-02-26 calco/main.tex
minima

@@
 
+This  section briefly recalls \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.
+
 \begin{itemize}
@@
 
-This  section briefly recalls \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}. 
 %
 %\begin{notation}
+We open this background section by fixing some notation.
+%
 Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
@@
 	Let $\X$ be a category and $\mathcal{M}$ a subclass of
-	$\mon(\X)$  including  all isomorphisms, closed under composition,  and stable under pullbacks and pushouts.  The category  $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
+	$\mon(\X)$  including  all isos, closed under composition,  and stable under pullbacks and pushouts.  The category  $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
 	\begin{enumerate}
@@
 		\mathcal{M} \text{ for every } Y\in \Y\}$;
-		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ that is stable under pullbacks and pushouts, contains all the isomorphisms, and is closed under composition and decomposition.
+		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ that is stable under pullbacks and pushouts, contains all isos, and is closed under composition and decomposition.
 	\end{enumerate} 
@@
 
-In this section we briefly recall the notion of \emph{hypergraph}.
-In order to so, a pivotal role is played by the \emph{Kleen star} monad $(-)^\star\colon \Set\to \Set$, also known as \emph{list monad},
+In this section we briefly recall the notion of \emph{hypergraph}. In order to so, a pivotal role is played by the \emph{Kleen star monad} $(-)^\star\colon \Set\to \Set$, also known as 
+\emph{list monad},
 sending a set to the free monoid on it \cite{sakarovitch2009elements,Wadler95}.
@@
 
-\begin{definition}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the set of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
+\begin{definition}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the sets of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
 A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute
@@
 	\begin{enumerate}
-		\item a morphism $(h,k)$ between two object of $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions;
+		\item an arrow $(h,k)$ in $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions;
 		\item $\hyp_{\Sigma}$ is an adhesive category. 
@@
 	\begin{enumerate} 
-		\item Every arrow $f\colon X\to Y$ can be factored as $m\circ e$, where $e\colon X\eto Q$ is a regular epi and $m\colon Q\mto Y$ is a monomorphism;
+		\item Every arrow $f\colon X\to Y$ can be factored as $m\circ e$, where $e\colon X\eto Q$ is a regular epi and $m\colon Q\mto Y$ is a mono;
 			\item for every square as the one on the right, with $e\colon X\eto E$ a surjection and $m\colon N\mto Y$ a mono, there exists a unique $k\colon E\to N$ making it commutative.

### 2025-02-26 calco/main.tex
colimiti

--- 2025-02-26 calco/main.tex
@@
 \newcommand{\lgh}{\mathsf{lg}}
+\newcommand{\eq}{\mathsf{eq}}
 
@@
 
-\subsection{Kernel Pairs and Regular Epimorphisms}
+\subsection{Some properties of kernel pairs and regular epimorphisms}
 
@@
 
-We explore the link between regular epis and kernel pairs.
+Regular epis are particular well-behaved with respect to their kernel pairs.
 
@@
 
+\commentato{ 
 \begin{restatable}{corollary}{natepi}\label{cor:reg_epi_components_reg_epi_nat_trans}
@@
 %[Proof in \Cref{epicol-proof}]
-
-We now explore some properties of kernel pairs and their link with adhesive categories. 
+}
+We conclude this section exploring some properties of kernel pairs in an $\mathcal{M}$-adhesive category. 
 The results below appear to be original, and we give their proofs in \Cref{kpp-proof}.
@@
 \end{restatable}}\hfill 
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_{m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_{n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
 
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:fact}
 	The following facts hold
@@
 
-\begin{proposition}\label[proposition]{cor:left}  The forgetful functor $U_{\hyp}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\hyp}$.
+\begin{proposition}\label{cor:left}  The forgetful functor $U_{\hyp}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\hyp}$.
 \end{proposition}
@@
 
-\begin{restatable}{proposition}{fhyp}  The following are true:
+\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  The following are true:
 	\begin{enumerate}
@@
 \end{restatable}
-A proof is provided in \Cref{prop:forghyp}.
+A proof is provided in \Cref{proof:forghyp}.
 
@@
 
-\commentato{
-	\todo{questo non serve a nulla e in più è pure scritto sbagliato}
-$\EqHyp$ has a forgetful functor $U_{\EqHyp}:\EqHyp \to \Set$, which sends each $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ into $V_\mathcal{G}$, and each $h = (h_E, h_V, h_C)$ onto $h_V$.
+Now, we can consider the forgetful functor $U_{\eq}\colon \EqHyp\to \Set$ obtained composing $T$ and $U_{\hyp}$.  By \Cref{cor:left} and the second point of \Cref{prop:forghyp} we get the following.
 
 \begin{corollary}\label{cor:ladj}
-	$U_\EqHyp$ has a left adjoint $\Delta_{\EqHyp}: \Set \to \EqHyp$.
+	$U_{\eq}$ has a left adjoint $\Delta_{\eq}\colon \Set \to \EqHyp$.
 \end{corollary}
 
-\begin{proof}
-	For each set $X$, define $\Delta_\EqHyp(X):= (\emptyset, X, \{\bullet\}, ?_X, ?_X, !_X)$. Consider now $h: \Delta_{\EqHyp}(X) \to \mathcal{H}$.
-	\[\xymatrix@C=2.3cm{
-		\Delta_{\EqHyp}(X) \ar@{.>}[d]_{\Delta_\EqHyp(f)} \ar[dr]^{h} & \\
-		\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) \ar[r]_{\epsilon_{\mathcal{H}}} & \mathcal{H}
-	}\]
-	Where $\Delta_\EqHyp(U_{\EqHyp}(\mathcal{H})) = (\emptyset, V_\mathcal{H}, \{\bullet\}, ?_{V_\mathcal{H}}, ?_{V_\mathcal{H}}, !_{V_\mathcal{H}})$ and $\epsilon_{\mathcal{H}} = (?_{E_\mathcal{H}}, \id{V_\mathcal{H}}, g)$.
-	Note that, since $\Delta_{\EqHyp}(X)$ has the empty set as object of edges, $h_E = ?_{E_\mathcal{H}}$, then, the unique arrow that fits in the diagram is $\Delta_{\EqHyp}(f) = (?_{E_\mathcal{H}}, h_V, \id{\{\bullet\}})$.
-\end{proof}}
-
-Let us notice that there $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
+Let us notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
 We are now going to exploit it to compute limits and colimits in $\EqHyp$.
@@
 \end{restatable}}\hfill 
-\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>->}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
-
-\begin{corollary}\label{cor:mono2}
-	If $h = (h_E, h_V, h_C): \mathcal{G\to H}$ is a regular mono in $\EqHyp$, then $h_E, h_V$ and $h_C$ are all monos.
-\end{corollary}
-\todo{Questa è da rifare completamente}
-\begin{proof}
-	If $h$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos. Suppose now $f, g: \mathcal{H\rightrightarrows K}$ be the arrows equalized by $h$. Then, we have:
-	\begin{align*} f_C \circ h_C \circ q_\mathcal{G} &= f_C\circ q_\mathcal{H} \circ h_V\\&=q_\mathcal{K}\circ g_V \circ h_V\\&=q_\mathcal{K}\circ f_V \circ h_V\\&=g_C \circ h_C \circ q_\mathcal{G} \end{align*}
-	Since $q_\mathcal{G}$ is epi, we have $f_C \circ h_C = g_C \circ h_C$, hence $h_C$ is an equalizer for $f_C$ and $g_C$, and thus a mono.
-\end{proof}
+\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
+
+\begin{restatable}{corollary}{mn}\label{cor:mono2}
+	If $(h_E, h_V, h_Q): \mathcal{G\to H}$ is a regular mono in $\EqHyp$, then $h_E, h_V$ and $h_C$ are all monos.
+\end{restatable}
 
@@
 \noindent
-\parbox{7cm}{\mpo*}\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_{m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_{n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+\parbox{7cm}{\mpo*}\hfill \parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
 
 \noindent 
-\parbox{4cm}{\xymatrix@C=10pt@R=6pt{&K_a\ar[dd]|\hole_(.65){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_{k_{m'}} && K_n\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_{k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }} \hfill \parbox{9cm}{\begin{proof}\label{mpo-proof}
+\parbox{4cm}{\xymatrix@C=10pt@R=6pt{&K_a\ar[dd]|\hole_(.65){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_n\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_(.55){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }} \hfill \parbox{9cm}{\begin{proof}\label{mpo-proof}
 	By  \Cref{prop:regmono}  we know that the the top face of the original cube is a pullback.
@@
 
-\begin{proof}\label{prop:forghyp}
+\begin{proof}\label{proof:forghyp}
 	\begin{enumerate}
@@
 \begin{remark}\label{rem:fact}
-	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~ surjections) and of monos in$\Set$.
-In particular, we need the fact thatthey form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.
+	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~ surjections) and of monos in $\Set$.
+In particular, we need the fact that they form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.
 This amount to ask that:
@@
 
+We will also need the following well-known fact about regular epis.
+
+\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
+	Let $F,G\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
+Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in D})$ be the colimits of $F$ and $G$, respectively.
+If $\phi\colon  F \to G$ is a natural transformation whose components are regular epis, then the arrow induced by $\phi$ from $X$ to $Y$ is a regular epi.
+\end{lemma}
+
 \noindent
@@
 	\begin{enumerate}
-		\item Suppose now $(E', V', s', t')$, together with $(\kappa_E^i, \kappa_V^i)_{i \in \cat I}$, be the colimit of $T \circ D$, and $C'$, with $(c_i)_{i \in \cat I}$ be the colimit of $K \circ D$.
-		Then, we have the folliwing situation.
-		\[\xymatrix{
-			&  {V'} &                             \\
-			V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
-			C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
-			&  {C'} &
-		}\]
-		Then, $C'$ with morphisms $(c_i \circ q_i)_{i\in \cat I}$ is a conone for $U \circ D$. Then, there exists a unique morphism $q': V' \to C'$ such that $q'\circ \kappa_V^i = c_i\circ q_i$.
-		Such morphism is epi ({\color{red}cite Lemma 1.3.45 of the thesis}), and thus $(E', V', C', s', t', q')$, together with $(\kappa_E^i, \kappa_V^i, c_i)_{i\in \cat I}$ is the colimit of $D$.
-		\item  We know by \Cref{prop:cocomp} that $\hyp$ is complete, we can then consider a cone $((E, V, s, t), \{(\pi^i_E, \pi^d_V)\}_{d\in \D})$ limiting for of $T \circ D$.
-Now, $(V, \{q_d\circ \pi_V^d\}_{d\in \D})$, is a cone for $K \circ D$: indeed, if $\alpha: d \to d'$ is an arrow of $\D$, and $F(\alpha)=(h_1, h_2, f_3)$, then we have
-	\[h_2\circ q_d\circ \pi^d_V =q_{d'} \circ h_2\circ \pi^d_{V}=q_{d'}\circ \pi^{d'}_V\]
+		\item We know by \Cref{prop:cocomp} that $\hyp$ is cocomplete.
+Let thus $(E, V, s, t)$ together with $\{(\kappa_E^d, \kappa_V^d)\}_{d \in \D}$ be a colimit for $T \circ F$.
+By \Cref{colim} we also know that
 
 		 \noindent 
-\parbox{9.5cm}{Thus there is an arrow $V\colon L$ such that $l_d\circ l=q_d\circ \pi^d_V$.
+		 \parbox{10.5cm}{$(V, \{\kappa^d_V\}_{d\in \D})$ is a colimit for $U_\eq\circ F$.
+Moreover, since $\Set$ is cocomplete too we can also take a colimit $(C, \{c_d\}_{d\in \D})$ for $K\circ F$.
+Now,  let $\alpha$ be an arrow $d\to d'$ in $\D$, and suppose that $F(\alpha)$ is $(h_1, h_2, h_3)$.
+By definition of morphisms in $\EqHyp$, the square on the right commutes.}
+		\hfill 
+		\parbox{2cm}{\xymatrix{V_d \ar[r]^{h_2} \ar@{>>}[d]_{q_d} & V_{d'} \ar@{>>}[d]^{q_{d'}}\\ Q_{d} \ar[r]_{h_3} & Q_{d'}}}
+
+		Thus the family $\{q_d\}_{d\in \D}$ form a natural transformation $U_\eq\circ F\to K\circ F$.
+By \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}, the induced arrow $q: V \to C$ between the colimits is a surjection.
+We can then consider the object $(E, V, C, s, t, q)$ of $\EqHyp$, together with the family  $\{(\kappa_E^d, \kappa_V^d, c_d)\}_{d\in \D}$ which, by construction is a cocone on $F$.
+Let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^d_E, h^d_V, h^d_Q)\}_{d\in \D})$ be a cocone, then $((E_\mathcal{G},V_\mathcal{G},, s_{\mathcal{G}}, t_{\mathcal{G}}), \{(h^d_E, h^d_V)\}_{d\in \D})$ and $(Q_{\mathcal{G}}, \{h^d_Q\}_{d\in \D})$ are cocone on, respectively, $T\circ F$ and $K\circ D$, giving arrows $(h_E, h_V)$ in $\hyp$ and $h_Q$ in $\Set$ such that
+		\[(h_E, h_V)\circ (\kappa_E^d, \kappa_V^d)=(h^d_E, h^d_V) \qquad h_Q\circ c_D=h^d_Q\]
+		Now, to show that $(h_E, h_V, h_Q)$ is an arrow of $\EqHyp$ we can compute:
+		\[h_Q\circ q\circ \kappa^d_V=h_Q\circ c_d\circ q_d=h^d_Q\circ q_d=q_{\mathcal{G}} \circ h^d_V=q_{\mathcal{G}}\circ h_V\circ \kappa^d_V \]
+
+		Uniqueness of such arrow follows form the fact that $T$ is faithful and \Cref{rem:eqhyp_morphs}.
+
+		\item   $\hyp$ is complete, again by \Cref{prop:cocomp}, we can then consider a limiting cone $((E, V, s, t), \{(\pi^i_E, \pi^d_V)\}_{d\in \D})$ over of $T \circ F$.
+Now, $(V, \{q_d\circ \pi_V^d\}_{d\in \D})$, is a cone for $K \circ F$: indeed, if $\alpha: d \to d'$ is an arrow of $\D$, and $F(\alpha)=(h_1, h_2, h_3)$, then we have
+	\[h_3\circ q_d\circ \pi^d_V =q_{d'} \circ h_2\circ \pi^d_{V}=q_{d'}\circ \pi^{d'}_V\]
+
+\noindent 
+\parbox{9.5cm}{Thus there is an arrow $l\colon V\to L$ such that $l_d\circ l=q_d\circ \pi^d_V$.
 We know that there exist $m\colon Q\mto L$ and $q\colon X\eto Q $ such that $m\circ q=l$.
 Since the identity is mono then there exists a unique arrow $\pi^d_Q$ fitting in the rectangle aside.} 	\hfill \parbox{3cm}{\xymatrix{
-	V\ar[r]^{\pi_V^d}\ar@{>>}[d]_{q}&V_d\ar@{>>}[r]^{q_d}&Q_d\ar[d]^{\id{Q_d}}\\Q\ar@{>->}[r]_{m}\ar@{.>}[urr]^{\pi_Q^d}&L\ar[r]_{l_d}&{Q_d}
+	V\ar[r]^{\pi_V^d}\ar@{>>}[d]_{q}&V_d\ar@{>>}[r]^{q_d}&Q_d\ar[d]^{\id{Q_d}}\\Q\ar@{>->}[r]_{m}\ar@{.>}[urr]_{\pi_Q^d}&L\ar[r]_{l_d}&{Q_d}
 	}}
@@
 \noindent 
-\parbox{2cm}{\xymatrix{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[ur]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square below commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
-We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that
-\[(\pi^d_E, \pi^d_V, \pi^dQ)\circ (h_E, h_V, k_Q)=(h^d_E, h^d_V, h^d_Q)\]}
-
-Uniqueness follows at once from faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
+\parbox{2cm}{\xymatrix{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[ur]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
+We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that}
+\[(\pi^d_E, \pi^d_V, \pi^dQ)\circ (h_E, h_V, k_Q)=(h^d_E, h^d_V, h^d_Q)\]
+
+As in the point aboce, uniqueness is guaranteed by faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
 	\end{enumerate}
+\end{proof}
+
+\mn*
+
+\begin{proof}
+	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
+
+	\noindent 
+	\parbox{2cm}{\xymatrix{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
+	\hfill 	\parbox{11cm}{Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$.
+Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in $\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$.
+From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono $m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside.
+Now, notice that
+	}\hfill 
+	\[e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}\]
+	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.
 \end{proof}

### 2025-02-27 calco/main.tex
colimiti

@@
 \newcommand{\eq}{\mathsf{eq}}
+\newcommand{\quo}{\mathsf{Q}}
 
@@
 
-\title{On the adhesivity of EGGS}
+\title{On the adhesivity of EGGs}
 
@@
 \todo{A very nice introduction}
-
-This  section briefly recalls \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.
 
@@
 
-\begin{definition}
+\begin{definition}[\cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}]
 	Let $\X$ be a category and $\mathcal{M}$ a subclass of
@@
 %
-	\[\xymatrix{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
+	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
 
@@
 
-\begin{definition}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the sets of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
-A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the following diagrams commute
-	\[\xymatrix{ E_{\mathcal{G}} \ar[d]_{h} \ar[r]^{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}& E_{\mathcal{G}} \ar[r]^{t_{\mathcal{G}}} \ar[d]_{h} & V^\star_{\mathcal{G}} \ar[d]^{k^\star}  \\ E_{\mathcal{G}} \ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} & E_{\mathcal{G}} \ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} }\]
-	We define $\hyp$ to be the resulting category.
-\end{definition}
+\noindent 
+\parbox{10.8cm}{\begin{definition}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the sets of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
+
+\hspace{10pt} A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the diagrams on the right are commutative.
+
+\hspace{10pt}	We define $\hyp$ to be the resulting category.
+\end{definition}}\hfill\parbox{3cm}{\xymatrix@R=15pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{s_{\mathcal{H}}} & V^\star_{\mathcal{H}}} \hspace{1pt}\\ \xymatrix@R=15pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{t_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{t_{\mathcal{H}}} & V^\star_{\mathcal{H}}} }
 
@@
 
-\begin{remark}\label[remark]{rem:label}	
-Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a morphism $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares below commute (cfr.~ \Cref{rem:length}).
-	\[\xymatrix{E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{s_{\mathcal{H}}}& O_\Sigma \ar[d]^{\ari_\Sigma}& E_{\mathcal{H}} \ar[r]^{h} \ar[d]_{t_{\mathcal{H}}} & O_\Sigma \ar[d]^{\delta_1}\\ V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}}& \mathbb{N} & V^\star_{\mathcal{{H}}} \ar[r]_{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}\]
-%	
-Let $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$ be a coprojection.
+\noindent 
+\parbox{10.8cm}{\begin{remark}\label[remark]{rem:label}	
+Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a morphism $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
+
+\hspace{10pt}Now, consider a coprojection $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$.
 The second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V^{\star}$ of words of length $1$, i.e.
 $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
-\end{remark}
+\end{remark}} \hfill \parbox{3cm}{\xymatrix@R=15pt{E_{\mathcal{H}} \ar[r]_{h}\ar[d]_{s_{\mathcal{H}}} & O_\Sigma \ar[d]^{\ari_\Sigma} \\ V_{\mathcal{H}} \ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=15pt{E_{\mathcal{H}} \ar[r]_{h}\ar[d]_{t_{\mathcal{H}}} & O_\Sigma \ar[d]^{\ari_\Sigma}\\ V_{\mathcal{H}}\ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}}
 
@@
 	A morphism $h\colon \mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute
-	\[\xymatrix{
+	\[\xymatrix@R=15pt{
 		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_C} \\
@@
 \end{restatable}}\hfill 
-\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
+\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
 
@@
 
-Let us turn to another functor $\EqHyp \to \hyp$.
+We can now build another functor $\EqHyp \to \hyp$: the idea is that from an object of $\EqHyp$ one can build an hypergraph taking as set of nodes directly the codomain of the quotient map.
 
 \begin{definition}
-	The \emph{quotient functor} $Q:\EqHyp\to \hyp $ is defined as
-	the one sending $(E, V, C, s, t, q)$ to $(E, C, q^{\star}\circ s, q^{\star}\circ t)$ and an arrow $(h_E, h_V, h_C)$ to $(h_E, h_C)$.
+	We define the \emph{quotient functor} $\quo :\EqHyp\to \hyp $ as the one sending $(E, V, Q, s, t, q)$ to $(E, Q, q^{\star}\circ s, q^{\star}\circ t)$ and an arrow $(h_E, h_V, h_Q)$ to $(h_E, h_Q)$.
 \end{definition}
 
+\commentato{
 \begin{remark}
@@
 \end{remark}
-
-\begin{lemma}\label{lemma:quot_funct_left_adj}
-	$Q$ is a left adjoint.
-\end{lemma}
-
-\begin{proof}
-	Let $R((A, B, s, t))$ be $(A, B, B, s, t, \id{B})$, so that $Q(R((A, B, s, t))) = (A, B, s, t)$.
-Now, suppose that $h = (h_E, h_V): Q((E, V, C, s', t', q)) \to (A, B, s, t)$  is an arrow in $\hyp$, and consider the triple $(h_E, h_V, h_V \circ q)$.
-Since $h$ is a morphism of $\hyp$, we have $h_V^{\star}\circ q^{\star}\circ s'= s\circ h_E$ and $h_V^{\star}\circ q^{\star}\circ t' = t\circ h_E$.
-	Then we have the following squares
-	\[\xymatrix{
-		E \ar[r]^{h_E}\ar[d]_{s'} & A \ar[d]^{s} & E \ar[r]^{h_E}\ar[d]_{t'} & A \ar[d]^{t} & V \ar[r]^{h_V \circ q} \ar[d]_{q} & B \ar[d]^{\id{B}} \\
-		V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & C \ar[r]_{h_V} & B
-	}\]
-
-	\iffalse\[
-	\begin{tikzcd}
-		E \arrow[r, "{h_E}"] \arrow[d, "{s_G}"swap] & A \arrow[d, "s"] \\
-		V \arrow[r, "{h_V \circ q}"swap] & B
-	\end{tikzcd}
-	\qquad
-	\begin{tikzcd}
-		E \arrow[r, "{h_E}"] \arrow[d, "{t_G}"swap] & A \arrow[d, "t"] \\
-		V \arrow[r, "{h_V \circ q}"swap] & B
-	\end{tikzcd}
-	\qquad
-	\begin{tikzcd}
-		V \arrow[r, "{h_V\circ q}"] \arrow[d, "q" swap] & B \arrow[d, "{id_B}"] \\
-		C \arrow[r, "{h_V}"swap] & B
-	\end{tikzcd}
-	\]\fi
-	We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below
-	\[\xymatrix{
-		(A, B, s, t) \ar[r]^{(\id{A}, \id{B})} & (A, B, s, t)\\
-		(E, C, q^\star\circ s', q^\star\circ t') \ar[u]^{Q(h_E, h_V \circ q, h_V)} \ar[ur]_{(h_E, h_V)}
-	}\]   
-	Such arrow is unique. Suppose $f = (f_E, f_V, f_C)$ to be another arrow with such property.
-	Then, it must be $(\id A, \id B) \circ Q(f) = (f_E, f_C) = (h_E, h_C)$. Finally, $f_C = f_V \circ q = h_V \circ q$. 
-\end{proof}
-
-\begin{proposition}\label{prop:quot_creat_colims}
-	$Q$ creates colimits.
-\end{proposition}
-
-\begin{proof}
-	Since $Q$ is a left adjoint, it preserves colimits.
-	Let $D: \cat I \to \EqHyp$ be a diagram, and let $\mathcal{C}$, together with  $(c_i)_{i\in \cat I}$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
-	\iffalse
-	Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.\fi
-	Let $((\kappa_i)_{i\in \cat I}, V)$ be the colimit of $U_\EqHyp \circ D$.
-	Consider the following situation
-	\[\xymatrix{
-		&  {V} &                             \\
-		V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
-		C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
-		&  {C} &
-	}\]
-	Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $U_\EqHyp \circ D$, there exists a unique $q: V \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
-	Consider now the functor $W: \EqHyp \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component.
-	By \Cref{prop:eqhyp_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, E)$ is the colimit of $W \circ D$.
-	Notice that $((\kappa_i \circ s_i)_{i \in \cat{I}}, B)$ and $((\kappa_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
-It remains now to show that $(E, V, C, s, t, q)$, together with $(c_E^i, \kappa_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
-\end{proof}
-
-\begin{example}
-	$Q$ does not preserve limits.
-Indeed, let $\mathcal{G}_1 = (E_1, A, A, s_1, t_1, id_A)$, $\mathcal{G}_2 = (E_2, B, B, s_2, t_2, id_B)$ and $\mathcal{G}_3 = (E_3, A + B, \terminal, s_3, t_3, !_{A + B})$, and let $h = (h_E, \iota_A, !_A): \mathcal{G}_1 \to \mathcal{G}_3$, $k = (k_E, \iota_B, !_B): \mathcal{G}_2 \to \mathcal{G}_3$, where $(\iota_A, \iota_B, A + B)$ is the coproduct of $A$ and $B$, $\terminal$ is the intial object (in $\Set$, the singleton set as shown in \Cref{ex:set_init_term}), and $!_X$ the unique arrow $X \to \terminal$.
-	The following two diagrams show the pullback of $h$ and $k$ and the pullback of $Q(h)$ and $Q(k)$, on the second component (the vertices of the graphs)
-	\[\xymatrix{
-		\initial \ar[r]^{p_1} \ar[d]_{p_2}& A \ar[d]^{\iota_A} \\
-		B \ar[r]_{\iota_B} & A+B
 }
-	\qquad
-	\xymatrix{
-		{A \times B} \ar[r]^{\pi_A} \ar[d]_{\pi_B} & A \ar[d]^{!_A} \\
-		B \ar[r]_{!_B} & \terminal
-	}\]
-
-	But the arrow $\initial \to A \times B$ is not an epi in general (this is easy to see taking $\Set$ as example), hence such pullback is not preserved by $Q$.
+
+This functor enjoys some usefule propery, as shown by the following lemma, a proof of which can be found in \Cref{proof:quot}.
+
+\begin{restatable}{lemma}{quot}\label{lemma:quot} The following are true:
+	\begin{enumerate}
+		\item $Q$ is a left adjoint;
+		\item $Q$ creates colimits.
+	\end{enumerate}
+\end{restatable}
+
+\begin{example} Notice that, due to the way in which limits in $\EqHyp$ are computed (see \Cref{prop:eqhyp_complete}), $\quo$ does not preserve them.
+For instance,  let $A$ and $B$ be two non-empty sets and define
+	\begin{gather*}
+	\mathcal{G}_1:=(\emptyset, A, A, ?_{A^\star}, ?_{A^\star}, \id{A}) \qquad \mathcal{G}_2 := (\emptyset, B, B, ?_{B^\star}, ?_{B^\star}, \id{B}) \\ \mathcal{G}_3 := (\emptyset, A + B, 1, ?_{(A+B)^\star}, ?_{(A+B)^\star}, !_{A + B})	\end{gather*}
+
+Now, we have two morphisms $(\id{\emptyset}, \iota_A, !_A)\colon \mathcal{G}_1 \to \mathcal{G}_3$,  $(\id{\emptyset}, \iota_B, !_B)\colon  \mathcal{G}_2 \to \mathcal{G}_3$, where $\iota_A\colon A\mto A+B$  and $\iota_B\colon B \mto A+B$  are the coprojections.
+
+On the one hand, if we apply $\quo$ and compute the pullback of the resulting morphisms, we obtain an hypergraph with no hyperdeges and $A\times B$ as set of nodes.
+On the other hand, \Cref{prop:eqhyp_complete} we know that taking the pullback of the original two morphisms gives us the hypergraph with equivalence $(\emptyset, \emptyset, Q, ?_{\emptyset^\star}, ?_{\emptyset^\star}, q)$ where $Q$ is the image of $?_{A\times B}$, so that $Q$ is also empty.
 \end{example}
@@
 %\input{Hypergraphs_with_equivalences}
-\input{Labeled_hyp_with_eq}
-
-\input{Equivalence_term_graphs}
-
-\input{eggs}
+%\input{Labeled_hyp_with_eq}
+
+\subsection{Labeling hypergraphs with equivalence}
+
+As we have done in \Cref{sssect:hyp_alg_sign}, we can define the category of hypergraphs with equivalence labeled over an algebraic signature.
+
+\begin{definition}
+	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to $\Sigma$.
+	Then the \emph{hypergraph with equivalence} associated to $\Sigma$ is $R(\mathcal{G}^\Sigma)$ and the category of hypergraphs with 
+	equivalence labeled over $\Sigma$ is the 
+	slice category $\EqHyp_\Sigma = \EqHyp/L(\mathcal{G}^\Sigma)$.
+\end{definition}
+
+By \Cref{thm:slice_functors}, we can deduce the following.
+
+\begin{proposition}
+	$\EqHyp_\Sigma$ is $\reg (\EqHyp_\Sigma)$-adhesive.
+\end{proposition}
+
+%We can lift the adjunction given by $T$ and $L$ to $\EqHyp_\Sigma$ and $\hyp_\Sigma$.\todo{Non capisco se è uno svarione mio o ha senso}
+
+We can define a functor $T_\Sigma: \EqHyps \to \hyps$ which sends each labeled hypergraph $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ to $T_\Sigma(l) = T(l)$, and each morphism $h = (h_E, h_V, h_C)$ onto $T_\Sigma(h) = T(h)$.
+Such functor is faithful since so is $T$, hence we have the following property.
+
+\begin{proposition}\label{prop:monos_in_eqhyps}
+	A morphism $h$ between two objects of $\EqHyps$ is mono if and only if $T(h)$ is mono.
+\end{proposition}
+
+\subsubsection{Term Graphs with Equivalences}
+
+\begin{definition}
+	Let $\Sigma$ be an algebraic signature.
+	A labeled hypergraph with equivalence $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ is a \emph{term graph with equivalence} if $t_{\mathcal{G}}$ is mono.
+	We define category of term graphs with equivalence over $\Sigma$, denoted $\EqTG_{\Sigma}$, as the full subcategory of $\EqHyp_\Sigma$,
+	and the corresponding inclusion functor $I_{\EqTG_\Sigma}$.
+\end{definition}
+
+\begin{proposition}
+	If $l: \mathcal{G \to G}^\Sigma$ is a term graph, then $R(l)$ is a term graph with equivalence.
+\end{proposition}
+
+We have a functor $T_{\eq} : \EqTGs \to \tg$, defined to be $T_\Sigma \circ I_\eq$. Since both $T_\Sigma$ and $I_\eq$ are faithful, so is $T_\eq$.
+
+If $h: \mathcal{H \to G}$ is a mono between $l': \mathcal{H} \to L(\mathcal{G}^\Sigma)$ and $l: \mathcal{G}\to L(\mathcal{G}^\Sigma)$, then, if $l\in\EqTGs$, $l'\in\EqTGs$ as well.
+This let us deduce what follows.
+
+\begin{proposition}
+	$\EqTGs$ has equalizers, and $I_{\EqTGs}$ creates them.
+\end{proposition}
+
+\section{EGGs}
+\label{eggs}
+
+\todo{introduction}
+
+\begin{definition}
+	Let $\mathcal{G} = (E, V, C, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair of $q^\star \circ s$.
+	Then, $\mathcal{G}$ is an \emph{e-hypergraph} whenever $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
+	$\egg$ is the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and $I: \egg \to \EqHyp$ is the inclusion functor.
+\end{definition}
+
+\begin{lemma}
+	$\egg$ has all limits and $I$ preserves them.
+\end{lemma}
+
+\begin{proof}
+	Let $D: \cat{I} \to \egg$ be a diagram, with $D(i) = (A_i, B_i, C_i, s_i, t_i, q_i)$, let $(U_i, u_1^i, u_2^i)$ be the kernel pair of $q_i\circ s_i$.
+	Let now be $(A, B, C, s, t, q)$, togehter with projections $(\pi_E^i, \pi_V^i, \pi_C^i)_{i \in \cat I}$ the limit of $I \circ D$,
+	let $(U, u_1, u_2)$ be the kernel pair of $q\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ D$.
+	By construction (proof of \Cref{prop:eqhyp_complete}), there exists a mono $m: C \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
+	\begin{align*}
+		q_i^\star \circ s_i\circ \pi^i_E\circ u_1      &= q_i^\star\circ (\pi^i_V)^\star \circ s\circ u_1\\
+		&= (\pi_C^i)^\star\circ q^\star\circ s\circ u_1\\
+		&=(\pi_C^i)^\star\circ q^\star\circ s\circ u_2\\
+		&= q_i^\star \circ s_i \circ \pi_E^i \circ u_2
+	\end{align*}
+	Then, for each $i$, there exists an arrow $a_i:U\to U_i$ making the following diagram to commute
+	\[
+	\xymatrix{
+		U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_i} & A \ar[dr]^{\pi_E^i} & \\
+		A \ar[dr]_{\pi_E^i} & U_i \ar[r]^{u_1^i} \ar[d]_{u_2^i}& A_i \ar[d]^{q_i^\star \circ s_i} \\
+		& A_i  \ar[r]_{q_i^\star \circ s_i}& C_i^\star
+	}
+	\]
+	We have then
+	\begin{align*}
+		l_i^\star\circ m^\star \circ q^\star \circ t \circ u_1    &= q_i^\star\circ (\pi_V^i)^\star \circ t \circ u_1 \\
+		&= q_i^\star \circ t_i \circ \pi_E^i \circ u_1 \\
+		&= q_i^\star \circ t_i \circ u_1^i \circ a_i \\
+		&= q_i^\star \circ t_i \circ u_2^i \circ a_i \\
+		&= q_i^\star \circ t_i \circ \pi_E^i \circ u_2 \\
+		&= q_i^\star \circ (\pi_V^i)^\star \circ t \circ u_2 \\
+		&= l_i^\star \circ m^\star \circ q^\star \circ t \circ u_2
+	\end{align*}
+	By universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$, and, since $m$ is mono, $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the thesis.
+\end{proof}
+
+\begin{corollary}
+	$I$ creates limits.
+\end{corollary}
+
+\begin{corollary}
+	Let $h: \mathcal{G \to H}$ be an arrow in $\egg$. Then it is a regular mono 
+	%in $\egg$
+	if and only if $I(h)$ is a regular mono.
+	% in $\EqHyp$.
+\end{corollary}
+
+\begin{lemma}
+	Consider the following pushout square in $\EqHyp$.
+	\[\xymatrix{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{k}&\mathcal{P}}\]
+	with $m$ regular mono. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is an e-hypergraph too, and $n$ is regular mono.
+\end{lemma}
+
+\begin{proof}
+	Let $\mathcal{P} = (A, B, C, s, t, q)$, $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, and let $(U, u_1, u_2)$ the kernel pair of $q^\star \circ s$ .
+	Consider then the following situation.
+	\[\xymatrix@C=10pt@R=6pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar[dl]_{k_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){k_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{C_1^\star}\ar[rr]|\hole^(.65){h_C^\star}\ar[dl]^{m_C^\star} && {C_2^\star} \ar[dl]^{n_C^\star} \\{C_3^\star} \ar[rr]_{k_C^\star} & & C^\star}\]
+	Since $m$ is regular mono, $m_E$ is mono ({\color{red}{inserire citazione}}).
+	Then, by construction, the top face is a pushout, and since $\Set$ is adhesive, by \Cref{lem:mpo} , the square below is a pushout.
+	\[\xymatrix{K_1\ar[r]^{f_k}\ar[d]_{f_m}&K_2\ar[d]^{f_n}\\K_3\ar[r]_{f_k}&U}\]
+	Computing, we have
+	\[
+	\begin{split}
+		q^\star \circ t \circ u_1 \circ f_n &= q^\star \circ t \circ n_E \circ \pi_2^1 \\ &= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^1 \\&= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^2 \\&=q^\star \circ t \circ u_2 \circ f_n
+	\end{split}
+	\qquad
+	\begin{split} q^\star \circ t \circ u_1 \circ f_k &= q^\star \circ t \circ k_E \circ \pi_3^1 \\ &= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^1 \\&= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^2 \\&=q^\star \circ t \circ u_2 \circ f_k
+	\end{split}
+	\]
+	By universal property of pushouts, we deduce $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the thesis follows.
+\end{proof}
+
+By direct application of \Cref{thm:slice-functors}, we can conclude what follows.
+
+\begin{corollary}
+	$\egg$ is $\reg(\egg)$-adhesive.
+\end{corollary}
 
@@
 	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.
+\end{proof}
+
+\quot*
+\begin{proof}\label{proof:quot}
+	\begin{enumerate}
+		\item 
+		Let $R((A, B, s, t))$ be $(A, B, B, s, t, \id{B})$, so that $Q(R((A, B, s, t))) = (A, B, s, t)$.
+Now, suppose that $h = (h_E, h_V): Q((E, V, C, s', t', q)) \to (A, B, s, t)$  is an arrow in $\hyp$, and consider the triple $(h_E, h_V, h_V \circ q)$.
+Since $h$ is a morphism of $\hyp$, we have $h_V^{\star}\circ q^{\star}\circ s'= s\circ h_E$ and $h_V^{\star}\circ q^{\star}\circ t' = t\circ h_E$.
+		Then we have the following squares
+		\[\xymatrix{
+			E \ar[r]^{h_E}\ar[d]_{s'} & A \ar[d]^{s} & E \ar[r]^{h_E}\ar[d]_{t'} & A \ar[d]^{t} & V \ar[r]^{h_V \circ q} \ar[d]_{q} & B \ar[d]^{\id{B}} \\
+			V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & C \ar[r]_{h_V} & B
+		}\]
+
+		\iffalse\[
+		\begin{tikzcd}
+			E \arrow[r, "{h_E}"] \arrow[d, "{s_G}"swap] & A \arrow[d, "s"] \\
+			V \arrow[r, "{h_V \circ q}"swap] & B
+		\end{tikzcd}
+		\qquad
+		\begin{tikzcd}
+			E \arrow[r, "{h_E}"] \arrow[d, "{t_G}"swap] & A \arrow[d, "t"] \\
+			V \arrow[r, "{h_V \circ q}"swap] & B
+		\end{tikzcd}
+		\qquad
+		\begin{tikzcd}
+			V \arrow[r, "{h_V\circ q}"] \arrow[d, "q" swap] & B \arrow[d, "{id_B}"] \\
+			C \arrow[r, "{h_V}"swap] & B
+		\end{tikzcd}
+		\]\fi
+		We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below
+		\[\xymatrix{
+			(A, B, s, t) \ar[r]^{(\id{A}, \id{B})} & (A, B, s, t)\\
+			(E, C, q^\star\circ s', q^\star\circ t') \ar[u]^{Q(h_E, h_V \circ q, h_V)} \ar[ur]_{(h_E, h_V)}
+		}\]   
+		Such arrow is unique. Suppose $f = (f_E, f_V, f_C)$ to be another arrow with such property.
+		Then, it must be $(\id A, \id B) \circ Q(f) = (f_E, f_C) = (h_E, h_C)$. Finally, $f_C = f_V \circ q = h_V \circ q$.
+
+		\item 	Since $Q$ is a left adjoint, it preserves colimits.
+		Let $D: \cat I \to \EqHyp$ be a diagram, and let $\mathcal{C}$, together with  $(c_i)_{i\in \cat I}$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
+		\iffalse
+		Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.\fi
+		Let $((\kappa_i)_{i\in \cat I}, V)$ be the colimit of $U_\EqHyp \circ D$.
+		Consider the following situation
+		\[\xymatrix{
+			&  {V} &                             \\
+			V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
+			C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
+			&  {C} &
+		}\]
+		Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $U_\EqHyp \circ D$, there exists a unique $q: V \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
+		Consider now the functor $W: \EqHyp \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component.
+		By \Cref{prop:eqhyp_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, E)$ is the colimit of $W \circ D$.
+		Notice that $((\kappa_i \circ s_i)_{i \in \cat{I}}, B)$ and $((\kappa_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
+It remains now to show that $(E, V, C, s, t, q)$, together with $(c_E^i, \kappa_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
+\qedhere
+	\end{enumerate}
 \end{proof}

### 2025-02-28 calco/main.tex
boh

@@
 \noindent
-\parbox{7cm}{
+\parbox{7.5cm}{
 \begin{restatable}{proposition}{mpo}\label{lem:mpo}
-	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top face is an $\mathcal{M}$-pushout. Then the right square is a pushout.
+	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top is an $\mathcal{M}$-pushout and all the vertical faces are pullbacks.
+Then the right square is a pushout.
 \end{restatable}}\hfill 
@@
 \noindent
-\parbox{11cm}{
+\parbox{11.4cm}{
 \begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
-Let $F\colon \D \to \EqHyp$ be a diagram, and let $(\mathcal{E}_d, V_d, Q_d, s_d, t_d, q_d)$ be the image of an object $d$. Then the following hold true:
+Let $F\colon \D \to \EqHyp$ be a diagram, and let $(E_d, V_d, Q_d, s_d, t_d, q_d)$ be the image of an object $d$. Then the following hold true:
 \begin{enumerate}
@@
 
+\todo{Ripensandoci il funtore quoziente non serve: l'unico punto in cui si usa nella tesi è che il quoziente di un colimite è il colimite dei quozienti, ma questo segue dal punto $1$ di \Cref{prop:eqhyp_complete}.
+Inoltre la dimostrazione della creazione è sbagliata (e probabilmente quella è una cosa falsa), io cancellerei}
+
 We can now build another functor $\EqHyp \to \hyp$: the idea is that from an object of $\EqHyp$ one can build an hypergraph taking as set of nodes directly the codomain of the quotient map.
@@
 
-This functor enjoys some usefule propery, as shown by the following lemma, a proof of which can be found in \Cref{proof:quot}.
-
-\begin{restatable}{lemma}{quot}\label{lemma:quot} The following are true:
-	\begin{enumerate}
-		\item $Q$ is a left adjoint;
-		\item $Q$ creates colimits.
-	\end{enumerate}
+ A proof of the following result can be found in \Cref{proof:quot}.
+
+\begin{restatable}{lemma}{quot}\label{lemma:quot} The functor $\quo$ is a left adjoint.
 \end{restatable}
@@
 \begin{proof}
-	Let $\mathcal{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, C'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
-	and, in the diagram below, suppose all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is regular mono.
+	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
+	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is regular mono.
+By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are mono and so the top faces of these cubes are pushouts.
 	\[
-	\xymatrix@C=10pt@R=6pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{t'} \\ \mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d}\\&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{t} \\\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 }
+	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\
+		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
+		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
+		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
+		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
 	\]
-	By \Cref{prop:eqhyp_complete} and \Cref{cor:mono1}, the following cubes in $\Set$ have pushouts as bottom faces and pullbacks as vertical faces, hence their top faces are pushouts.
+
+	\noindent 
+\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pullback the third component to get the solid part of the cube aside.
+Notice, moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
+By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left fact is a pullback.
+By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
+
+	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below.
+
+	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} \\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4}\]
+
+	\noindent 
+	\parbox{8.5cm}{
+	For $Q'_1$, we can make a similar argument.
+Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ which makes the diagram aside commutative.}\hfill
+	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
+
+	\commentato {Now, notice that
+	\[s_1 \circ m_1 \circ q_1 = q'_2 \circ h'_V = h'_C \circ q'_1 \quad  	q'_4 \circ z'_V = z'_Q \circ q'_2= u_1\circ m_2 \circ q'_2\]
+
 	\[
-	\xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ A_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}\\&A_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{t_E} \\A_3 \ar[rr]_{p_E} & & A_4 }
-	\qquad
-	\xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ B_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\&B_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{t_V} \\B_3 \ar[rr]_{p_V} & & B_4 }
+\begin{split}
+	y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
+\end{split}%\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'\end{split}
 \]
-	Consider now the following pullbacks.
-	\[\xymatrix{
-		Y \ar[d]_{y_2}\ar[r]^{y_1}&{C_4'}\ar[d]^{d_C}&U\ar[d]_{u_2}\ar[r]^{u_1}&{C_4'}\ar[d]^{d_C}&T\ar[r]^{x_1}\ar[d]_{x_2}&U\ar[d]^{u_2}\\
-		C_3\ar[r]_{p_C}&C_4&C_2\ar[r]_{t_C}&C_4&C_1\ar[r]_{h_C}&C_2
-	}\]
-	Thus, [???]\todo{inserire in sezione 1 la proposizione} yields the following situation, in which the bottom face is a pushout, and the vertical faces are pullbacks, hence the top face is a pushout too.
-	\[\xymatrix@C=10pt@R=6pt{&T\ar[dd]|\hole_(.65){x_2}\ar[rr]^{x_1} \ar@{.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar[rr]^(.7){y_1} & & C_4' \ar[dd]_(.3){d_C}\\&C_1\ar[rr]|\hole^(.65){h_C} \ar[dl]^{k_C} && C_2 \ar[dl]^{t_C} \\C_3 \ar[rr]_{p_C} & & C_4 }\]
-	By the proof of \Cref{prop:eqhyp_complete}, we have that $m_2 \circ q'_3 : B'_3 \to Y$ and $m_3 \circ q'_2 : B_2' \to U$ are two epi-mono factorizations, with $m_2$ and $m_3$ monos.
-	At the same way, let the following square to be a pullback.
-	\[\xymatrix{S\ar[r]^{s_1}\ar[d]_{s_2}&C'_2\ar[d]^{m_3}\\T\ar[r]_{x_1}&U}\]
-	Hence, in the following diagram, the outer rectangle is a pullback.
-	\[\xymatrix{
-		S\ar[r]^{s_1}\ar[d]_{s_2}&C'_2\ar[d]^{m_3}\\T\ar[r]_{x_1}\ar[d]_{x_2}&U\ar[d]^{u_2}\\C_1\ar[r]_{h_C}&C_2
-	}\]
-	By the same argument as before, there exists a mono $m_1$ such that $m_1\circ q_1' : B_1' \to S$.
-	% Uguaglianze da capire se servono davvero
-
-	We have to show that the top face of the cube ate the beginning of the proof is a pushout.
-	Suppose then that $z: \mathcal{G}_2' \to \mathcal{H}$ and $w: \mathcal{G}_3' \to \mathcal{H}$, with $\mathcal{H} = (E, V, C, s, t, q)$,
-	are two morphisms such that $z \circ h' = w \circ h'$, and let $v_V: B'_4 \to V$ the arrow induced by $z_V$ and $w_V$.
+Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.}
+
+	We have to show that the top face of the cube with which we have began is a pushout.
+Let $\mathcal{H}$ be $(E, V, C, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
+Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
+\[v_E\circ h'_E=w_E\circ k'_E\qquad v_V\circ h'_V=w_V\circ k'_V\]
+
+	We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+
+	Now, \Cref{lem:mpo}, let us take the kernel pair
+
 	We want to construct the dotted arrow $v_C$ which fits in the diagram below.
@@
 	}\]
-	By \Cref{lem:mpo}, we know that the top face of the cube below is a pushout.
+	By , we know that the top face of the cube below is a pushout.
 	\[\xymatrix@C=15pt@R=15pt{&K_{s_2\circ m_1\circ q'_1}\ar[dd]|\hole_(.65){\pi_{s_2\circ m_1\circ q'_1}^{1}}\ar[rr]^{k_{h'_2}} \ar[dl]_{k_{k'_2}} && K_{m_2\circ q'_2} \ar[dd]^{\pi_{m_2\circ q'_2}^{1}} \ar[dl]_{k_{t'_2}} \\ K_{m_3\circ q'_3}  \ar[dd]_{\pi_{m_3\circ q'_3}^{1}}\ar[rr]^(.7){k_{p'_2}} & & K_{q'_4} \ar[dd]_(.3){\pi_{q'_4}^{1}}\\&B'_1\ar[rr]|\hole^(.65){h'_2} \ar[dl]^{k'_2} && B'_2 \ar[dl]^{t'_2} \\B'_3 \ar[rr]_{p'_2} & & C_4}\]
@@
 	\]
+
+%	Let now $z: \graph{G}'_2 \to \graph H = (E, V, Q, s, t, q)$, $w: \graph G_3^1 \to \graph H$ be two morphisms such that $z \circ h' = w \circ k'$, and let $\phi:B'_4 \to V$ be the arrow induced by $z_V$ and $w_V$.
+We want to construct the arrow $v: C'_4 \to Q$ in the diagram below.
+	\[\begin{tikzcd}[row sep = 20, column sep = 20]
+		& {B_1'} && {B_2'} \\
+		{B_3'} && {B_4'} && V \\
+		& T && U \\
+		Y && {C_4'} && Q \\
+		& {C_1} && {C_2} \\
+		{C_3} && {C_4}
+		\arrow["{h_V'}", from=1-2, to=1-4]
+		\arrow["{k_V'}"', from=1-2, to=2-1]
+		\arrow["{s_2\circ m_1 \circ q_1'}"{description, pos=0.7}, from=1-2, to=3-2]
+		\arrow["{t_V'}", from=1-4, to=2-3]
+		\arrow["{z_V}", from=1-4, to=2-5]
+		\arrow["{m_2\circ q'_2}"{pos=0.7}, from=1-4, to=3-4]
+		\arrow["{m_3 \circ q'_3}"', from=2-1, to=4-1]
+		\arrow["q", from=2-5, to=4-5]
+		\arrow["{x_1}"{pos=0.8}, from=3-2, to=3-4]
+		\arrow["w"', from=3-2, to=4-1]
+		\arrow["{x_2}"'{pos=0.7}, from=3-2, to=5-2]
+		\arrow["{u_1}", from=3-4, to=4-3]
+		\arrow["{u_2}"{pos=0.7}, from=3-4, to=5-4]
+		\arrow["{y_2}"', from=4-1, to=6-1]
+		\arrow["{h_C}"{pos=0.8}, from=5-2, to=5-4]
+		\arrow["{k_C}", from=5-2, to=6-1]
+		\arrow["{t_C}", from=5-4, to=6-3]
+		\arrow["{p_C}"', from=6-1, to=6-3]
+		\arrow["{p_V'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+		\arrow["\phi"{pos=0.8}, from=2-3, to=2-5, crossing over]
+		\arrow["{q'_4}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+		\arrow["{y_1}"{pos=0.7}, from=4-1, to=4-3, crossing over]
+		\arrow["{d_C}"'{pos=0.7}, from=4-3, to=6-3, crossing over]
+		\arrow["v"{pos=0.8}, dashed, from=4-3, to=4-5, crossing over]
+	\end{tikzcd}\]
+
+	By \Cref{prop:reg_epi_coeq}, $d_C$ is the coequalizer of its kernel pair. On the other hand, by \Cref{lemma:pushouts_kernel_pairs}, we know that the top face of the cube below is a pushout.
+	\[\begin{tikzcd}[row sep=20, column sep = 20]
+		& {K_{s_2\circ m_1 \circ q_1'}} && {K_{m_2\circ q_2'}} \\
+		{K_{m_3 \circ q_3'}} && {K_{q_4'}} \\
+		& {B'_1} && {B'_2} \\
+		{B'_3} && {B'_4}
+		\arrow["{k_{h'_V}}", from=1-2, to=1-4]
+		\arrow["{k_{k_V'}}"', from=1-2, to=2-1]
+		\arrow["{\pi_{s_2\circ m_1 \circ q_1'}^1}"'{pos=0.7}, from=1-2, to=3-2]
+		\arrow["{k_{t_V'}}", from=1-4, to=2-3]
+		\arrow["{\pi_{m_2\circ q_2'}^1}", from=1-4, to=3-4]
+		\arrow["{k_{p_V'}}"{pos=0.8}, from=2-1, to=2-3, crossing over]
+		\arrow["{\pi_{m_3 \circ q_3'}^1}"', from=2-1, to=4-1]
+		\arrow["{h_V'}"{pos=0.7}, from=3-2, to=3-4]
+		\arrow["{\pi_{q_4'}^1}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
+		\arrow["{k_V'}"', from=3-2, to=4-1]
+		\arrow["{t_V'}", from=3-4, to=4-3]
+		\arrow["{p_V'}"', from=4-1, to=4-3]
+	\end{tikzcd}\]
+	And, since $m_3$ and $m_2$ are monos,
+	\[\begin{split}
+		q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
+	\end{split}\qquad\begin{split}
+		q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
+	\end{split}\]
+
+	Computing, we obtain
+	\[\begin{split}
+		q \circ \phi \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'} \\ &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{p'_V}
+	\end{split}\qquad\begin{split}
+		q \circ \phi \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'} \\ &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{t'_V}
+	\end{split}\]
+
+	Since the previous cube has a pushout as top face, by universal property, we have
+	\[
+	q \circ \phi \circ \pi_{q'_4}^1 = q \circ \phi \circ \pi_{q'_4}^2
+	\]
+	hence, $v$ is the mediating arrow.
+	\[
+	v \circ q'_4 \circ \pi_{q'_4}^1 = v \circ q'_4 \circ \pi_{q'_4}^2
+	\]
+
 \end{proof}
@@
 \end{proposition}
-
-\subsubsection{Term Graphs with Equivalences}
 
@@
 \noindent
-\parbox{11cm}{
+\parbox{11.4cm}{
 \comp*}\hfill 
@@
 \noindent 
-\parbox{2cm}{\xymatrix{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[ur]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
+\parbox{2cm}{\xymatrix@R=15pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[ur]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
 We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that}
@@
 	\noindent 
-	\parbox{2cm}{\xymatrix{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
+	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
 	\hfill 	\parbox{11cm}{Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$.
@@
 \begin{proof}\label{proof:quot}
-	\begin{enumerate}
-		\item 
-		Let $R((A, B, s, t))$ be $(A, B, B, s, t, \id{B})$, so that $Q(R((A, B, s, t))) = (A, B, s, t)$.
-Now, suppose that $h = (h_E, h_V): Q((E, V, C, s', t', q)) \to (A, B, s, t)$  is an arrow in $\hyp$, and consider the triple $(h_E, h_V, h_V \circ q)$.
-Since $h$ is a morphism of $\hyp$, we have $h_V^{\star}\circ q^{\star}\circ s'= s\circ h_E$ and $h_V^{\star}\circ q^{\star}\circ t' = t\circ h_E$.
-		Then we have the following squares
-		\[\xymatrix{
-			E \ar[r]^{h_E}\ar[d]_{s'} & A \ar[d]^{s} & E \ar[r]^{h_E}\ar[d]_{t'} & A \ar[d]^{t} & V \ar[r]^{h_V \circ q} \ar[d]_{q} & B \ar[d]^{\id{B}} \\
-			V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & V^{\star} \ar[r]_{h_V^\star\circ q^\star} & B^{\star} & C \ar[r]_{h_V} & B
+  Given an hypergraph $\mathcal{H}:=(E, V, s, t)$, let us define $R(E, V, s, t)$ as $(E, V, V, s, t, \id{B})$.
+By construction $\quo(R(\mathcal{{H}})) =\mathcal{H}$ so that we can take the identity as $\epsilon_{\mathcal{H}}\colon \quo(R(\mathcal{H}))\to \mathcal{H} $.
+
+		Suppose that $\mathcal{G}$ is an object of $\EqHyp$ and take an arrow $(h_E, h_V): \quo(\mathcal{G}) \to \mathcal{H}$, then the three squares below commute, so that $(h_E,  h_V \circ q_{\mathcal{G}}, h_V)$ is a morphism of $\EqHyp$.
+		\[\xymatrix@R=15pt@C=30pt{
+			E_{\mathcal{G}} \ar[r]^{h_E}\ar[d]_{s_{\mathcal{G}}} & E \ar[d]^{s} & E_\mathcal{G} \ar[r]^{h_E}\ar[d]_{t_{\mathcal{G}}} & V \ar[d]^{t} & V_{\mathcal{G}} \ar[r]^{h_V \circ q_{\mathcal{G}}} \ar@{>>}[d]_{q_{\mathcal{G}}} & V \ar@{>>}[d]^{\id{V}} \\
+			V_{\mathcal{G}}^{\star} \ar[r]_-{h_V^\star\circ q_{\mathcal{G}}^\star} & V^{\star} & V_{\mathcal{G}}^{\star} \ar[r]_{h_V^\star\circ q_\mathcal{G}^\star} & V^{\star} & C \ar[r]_{h_V} & V
 		}\]
 
-		\iffalse\[
-		\begin{tikzcd}
-			E \arrow[r, "{h_E}"] \arrow[d, "{s_G}"swap] & A \arrow[d, "s"] \\
-			V \arrow[r, "{h_V \circ q}"swap] & B
-		\end{tikzcd}
-		\qquad
-		\begin{tikzcd}
-			E \arrow[r, "{h_E}"] \arrow[d, "{t_G}"swap] & A \arrow[d, "t"] \\
-			V \arrow[r, "{h_V \circ q}"swap] & B
-		\end{tikzcd}
-		\qquad
-		\begin{tikzcd}
-			V \arrow[r, "{h_V\circ q}"] \arrow[d, "q" swap] & B \arrow[d, "{id_B}"] \\
-			C \arrow[r, "{h_V}"swap] & B
-		\end{tikzcd}
-		\]\fi
-		We have therefore found a morphism $(E, V, C, s', t', q) \to R((A, B, s, t))$ whose image through $Q$ fits in the diagram below
-		\[\xymatrix{
-			(A, B, s, t) \ar[r]^{(\id{A}, \id{B})} & (A, B, s, t)\\
-			(E, C, q^\star\circ s', q^\star\circ t') \ar[u]^{Q(h_E, h_V \circ q, h_V)} \ar[ur]_{(h_E, h_V)}
-		}\]   
-		Such arrow is unique. Suppose $f = (f_E, f_V, f_C)$ to be another arrow with such property.
-		Then, it must be $(\id A, \id B) \circ Q(f) = (f_E, f_C) = (h_E, h_C)$. Finally, $f_C = f_V \circ q = h_V \circ q$.
-
-		\item 	Since $Q$ is a left adjoint, it preserves colimits.
-		Let $D: \cat I \to \EqHyp$ be a diagram, and let $\mathcal{C}$, together with  $(c_i)_{i\in \cat I}$ be the colimit of $Q \circ D$, where $\mathcal{C} = (A, C, q\circ s, q\circ t)$, and $D(i)$ is $(A_i, B_i, C_i, s_i, t_i, q_i)$.
-		\iffalse
-		Let now $T: \EqHyp \to \Set$ be the functor mapping each graph with equivalence onto its second component, $T((X, Y, Z, x, y, z)) = Y$, and each morphims onto its second component.\fi
-		Let $((\kappa_i)_{i\in \cat I}, V)$ be the colimit of $U_\EqHyp \circ D$.
-		Consider the following situation
-		\[\xymatrix{
-			&  {V} &                             \\
-			V_i \ar[ur]^{\kappa_i} \ar[rr]^{h_V} \ar[d]_{q_i} && V_j \ar[ul]_{\kappa_j} \ar[d]^{q_j}\\
-			C_i \ar[dr]_{c_i}      \ar[rr]_{h_C}              &&C_j  \ar[dl]^{c_j}                  \\
-			&  {C} &
-		}\]
-		Now, since $((c^i_C \circ q_i)_{i \in \cat I}, C)$ is a cocone for $U_\EqHyp \circ D$, there exists a unique $q: V \to C$, which is epi by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
-		Consider now the functor $W: \EqHyp \to \Set$ mapping each $(X, Y, Z, x, y, z)$ onto $X$, and each morphism on its first component.
-		By \Cref{prop:eqhyp_complete} and \Cref{lemma:limits_of_presheaves}, we have that $((c_E^i)_{i \in \cat I}, E)$ is the colimit of $W \circ D$.
-		Notice that $((\kappa_i \circ s_i)_{i \in \cat{I}}, B)$ and $((\kappa_i \circ t_i)_{i \in \cat I}, B)$ are cocones for $W \circ D$, so let $s$ and $t$ be, respectively, the mediating arrow for the first one and the mediating arrow for the second one.
-It remains now to show that $(E, V, C, s, t, q)$, together with $(c_E^i, \kappa_i, c_C^i)_{i \in \cat I}$, is a colimit for $D$, but this follows by the proof of \Cref{prop:eqgrph_complete}.
-\qedhere
-	\end{enumerate}
-\end{proof}
+		By construction $\epsilon_{\mathcal{H}}\circ\quo(h_E,  h_V\circ q, h_V)=(h_E, h_V)$.
+To see that such an arrow is unique, let $(f_E, f_V, f_Q)$ be a morphism such that $\epsilon_{\mathcal{H}}\circ\quo(f_E, f_V, f_Q)=(h_E, h_V)$, then $f_E=h_E$ and $f_Q=h_V$, moreover
+		\[f_V=\id{V}\circ f_V=f_Q\circ q_{\mathcal{G}}=h_{V}\circ q_\mathcal{G}  \]
+	allowing us to conclude.		
+\end{proof}
+\commentato{		\item 	Since $\quo$ is a left adjoint, it preserves colimits.
+		Let $F\colon \D \to \EqHyp$ be a diagram, to fix the notation, let  $\mathcal{C}$ be  $(E, V, s, t)$,  and $F(d)$ be $(E_d, V_d, Q_d, s_d, t_d, q_d)$.
+
+		By \Cref{prop:eqhyp_complete} we know that $F$ has a colimit, thus we only have to proof that $\quo$ reflects colimits.
+Let $(\mathcal{G}, \{\kappa^d_E, \kappa^d_V, \kappa^d_Q\}_{d\in \D})$ be a cocone over $F$ such that $(\quo(\mathcal{G}).
+\{\kappa^d_E, \kappa^d_Q\}_{d\in \D})$ is colimiting for $\quo\circ F$.
+
+		and let $(\mathcal{C}, \{(c^d_E, c^d_V)\}_{d\in \D})$, be a colimiting cocone for $\quo \circ F$.
+
+		Let $, )$ be a colimit of $F$, which exists by \Cref{prop:eqhyp_complete},  then by the same proposition we know that $(Q, \{\kappa^d_Q\}_{d\in \D})$ is colimiting for
+
+		Now, let $(U, \{\kappa_d\}_{d\in \D})$  be a colimit for $U_\eq\circ F$.
+We have already noticed in the proof of the first point of \Cref{prop:eqhyp_complete} that  the family $\{q_d\}_{d\in \D}$ defines a natural transformation $U_{\eq}\circ F\to K\circ F$, moreover, by \Cref{prop:com,colim}, $(V, \{c^d_V\}_{d\in \D})$ is colimiting for  $K\circ F$, yielding an arrow $q: V \to C$, which is a surjection by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
+
+Define now $W: \EqHyp \to \Set$ as the functors $(X, Y, Z, x, y, z)$ to the set of hyperedges $X$ and each morphism to its first component.
+Again by \Cref{prop:com,colim} $(E, \{c^d_E\}_{d\in \D})$ is colimiting for $W \circ F$.
+Moreover, let $\alpha\colon d\to d'$  be an arrow in $\D$ and suppose that $F(\alpha)=(h_1, h_2, h_3)$, then we have
+\begin{align*}
+	\kappa^\star_{d'}\circ s_{d'} \circ W(F(\alpha))&= \kappa^\star_{d'}\circ s_{d'} \circ h_1= \kappa^\star_{d'}\circ h_2\circ s_{d}=\kappa^\star\_{d'}circ U(F(\alpha))\circ s^d =\kappa^\star_d\circ s_d
+	\\\kappa^\star_{d'}\circ t_{d'} \circ W(F(\alpha))&= \kappa^\star_{d'}\circ t_{d'} \circ h_1= \kappa^\star_{d'}\circ h_2\circ t_{d}=\kappa^\star\_{d'}circ U(F(\alpha))\circ s^d =\kappa^\star_d\circ t_d
+\end{align*}
+So that $(U^\star, \{\kappa^\star_d\circ s_d\}_{d\in \D})$ and $(U^\star, \{\kappa^\star_d\circ t_d\}_{d\in \D})$ are cocones over $W\circ F$, yielding two arrows $s, t\colon E\rightrightarrows U^\star$.
+
+By the proof of the first point of \Cref{prop:eqhyp_complete} the . \qedhere }
 

### 2025-03-01 calco/main.tex
cose

@@
 \begin{remark}\label{rem:fact}
-	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~ surjections) and of monos in $\Set$.
+	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~surjections) and of monos in $\Set$.
 In particular, we need the fact that they form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.

### 2025-03-01 calco/main.tex
minima

@@
 \begin{restatable}{proposition}{regmono}\label{prop:regmono}
-	If $\X$ is $\mathcal{M}$-adhesive then it holds
+	Let $\X$ be an $\mathcal{M}$-adhesive categoru. Then it holds
 	\begin{enumerate}
@@
 
-In this section we briefly recall the notion of \emph{hypergraph}. In order to so, a pivotal role is played by the \emph{Kleen star monad} $(-)^\star\colon \Set\to \Set$, also known as 
+In this section we briefly recall the notion of \emph{hypergraph}. In order to do so, a pivotal role is played by the \emph{Kleen star monad} $(-)^\star\colon \Set\to \Set$, also known as 
 \emph{list monad},
@@
 \begin{proposition}\label{prop:fact}
-	The following facts hold
+	Let $X$ be a set and $n\in \mathbb{N}$. Then the following facts hold
 	\begin{enumerate}
-		\item for every set $X$ and $n\in \mathbb{N}$ there are arrows $v_{n}\colon X^n\to X^\star $ such that $(X^\star, \{v_{n}\}_{n\in \mathbb{N}})$ is a coproduct;
+		\item there are arrows $v_{n}\colon X^n\to X^\star $ such that $(X^\star, \{v_{n}\}_{n\in \mathbb{N}})$ is a coproduct;
 		\item for every arrow $f\colon X\to Y$, $f^\star$ is the coproduct of the family $\{f^n\}_{n\in \mathbb{N}}$;
@@
 We can represent hypergraphs graphically.
-We will use dots to denote nodes and squares to denote hyperedges, the name of a node or of an hyperedge will be put near the corresponding dot or square.
-Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge will have an arrowhead in the middle pointing towards the hyperedge, while the lines to the targets will have arrowheads pointing to the target nodes.
-We will decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
+We use dots to denote nodes and squares to denote hyperedges, the name of a node or of an hyperedge is put near the corresponding dot or square.
+Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge have an arrowhead in the middle pointing towards the hyperedge, while the lines to the targets have arrowheads pointing to the target nodes.
+We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
 \todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
@@
 \begin{remark}\label{rem:functor}
-	It is worth to point out, as first noted in \cite{bonchi2022string}, that $\hyp$ is actually equivalent to a category of functors.
-
+	It is worth to point out, as first noted in \cite{bonchi2022string}, that $\hyp$ is equivalent to a category of functors. 
+	%
 	Indeed, consider the category $\catname{H}$ in which the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$ and arrows are given by the identities $\id{k,l}$, $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$.
-
-	It is quite straightforward to see that functors $\catname{H}\to \Set$ corresponds exactly to hypergaphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
+	%
+	The functors $\catname{H}\to \Set$ corresponds exactly to hypergaphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
 \end{remark}
@@
 \begin{enumerate}
-	\item if  $(i,j)\colon \mathcal{H}\to \mathcal{G}$ is a mono between  $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\hyp_\Sigma$ and the latter is a term graph, then also the former is in $\tg$
+	\item if  $(i,j)\colon \mathcal{H}\to \mathcal{G}$ is a mono between  $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\hyp_\Sigma$ and the latter is in $\tg$, then also the former is in $\tg$
 	\item $\tg$ has equalizers, binary products and pullbacks and they are created by $I_\Sigma$.
@@
 \begin{remark}\label{prop:image}
-	Suppose that $(f,g)\colon ((l, !_{V_{\mathcal{G}}}))\to (l', !_{V_{\mathcal{H}}})$ preserves input nodes.
+	Suppose that $(f,g)\colon (l, !_{V_{\mathcal{G}}})\to (l', !_{V_{\mathcal{H}}})$ preserves input nodes.
 Then  if $\tau_{\mathcal{H}}(h)=g(v)$ for some $v\in V_{\mathcal{G}}$ then $h$ belongs to the image of $f$.
@@
 That is, if $h_1 = (h_E, h_V, f)$ and $h_2 = (h_E, h_V, g)$ are two morphisms $\mathcal{G} \rightrightarrows \mathcal{H}$, then we have
-	\[f \circ q_\mathcal{G} = q_\mathcal{H}\circ h_V =g\circ q_\mathcal{G}\]
-
+	$
+	f \circ q_\mathcal{G} = q_\mathcal{H}\circ h_V =g\circ q_\mathcal{G}.
+	$
 	Since $q_\mathcal{G}$ is epi, we obtain $f = g$.
@@
 \begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
-Let $F\colon \D \to \EqHyp$ be a diagram, and let $(E_d, V_d, Q_d, s_d, t_d, q_d)$ be the image of an object $d$. Then the following hold true:
+Let $F\colon \D \to \EqHyp$ be a diagram and $(E_d, V_d, Q_d, s_d, t_d, q_d)$ the image of an object $d$. Then it holds
 \begin{enumerate}
 		\item $F$ has a colimit which is preserved by $K$;
-	\item let $(L, \{l_d\}_{d\in \D})$ be a limiting cocone for $K \circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$, where $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ is limiting for $T\circ F$.
+	\item if $(L, \{l_d\}_{d\in \D})$ is a limiting cocone for $K \circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$, where $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ is limiting for $T\circ F$.
 \end{enumerate}

### 2025-03-02 calco/main.tex
pulizia

@@
 \begin{definition}\label[definition]{def:tg}\index{term graph}
-	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is mono.
+	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is a mono.
 We define $\tg$ to be the full subcategory of $\hyp_{\Sigma}$ and denote by $I_\Sigma$ the inclusion.
@@
 \begin{remark}\label[remark]{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
-Notice that since $t_{\mathcal{G}}$ is mono then $\tau_{\mathcal{G}}$ is mono too.
+Notice that since $t_{\mathcal{G}}$ is a mono then $\tau_{\mathcal{G}}$ is a mono too.
 \end{remark}
@@
 \begin{corollary}\label{cor:mono1}
-	An arrow $h = (h_E, h_V, h_C): \mathcal{G \to H}$ in $\EqHyp$ is mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
+	An arrow $h = (h_E, h_V, h_C): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
 \end{corollary}
@@
 
+\commentato{
 \todo{Ripensandoci il funtore quoziente non serve: l'unico punto in cui si usa nella tesi è che il quoziente di un colimite è il colimite dei quozienti, ma questo segue dal punto $1$ di \Cref{prop:eqhyp_complete}.
@@
 \end{example}
+}
 
@@
 	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
-	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is regular mono.
-By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are mono and so the top faces of these cubes are pushouts.
+	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is a regular mono.
+By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
 	\[
@@
 \begin{proposition}\label{prop:monos_in_eqhyps}
-	A morphism $h$ between two objects of $\EqHyps$ is mono if and only if $T(h)$ is mono.
+	A morphism $h$ between two objects of $\EqHyps$ is a mono if and only if $T(h)$ is a mono.
 \end{proposition}
@@
 
+\commentato{
 \quot*
@@
 By the proof of the first point of \Cref{prop:eqhyp_complete} the . \qedhere }
+}
 

### 2025-03-03 calco/main.tex
Update main.tex

@@
 \begin{restatable}{corollary}{mn}\label{cor:mono2}
-	If $(h_E, h_V, h_Q): \mathcal{G\to H}$ is a regular mono in $\EqHyp$, then $h_E, h_V$ and $h_C$ are all monos.
+	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if $h_E, h_V$ and $h_C$ are all monos.
 \end{restatable}

### 2025-03-03 calco/main.tex
minima titolo etc.

@@
 
-\title{On the adhesivity of EGGs}
-
-%\titlerunning{????} %TODO optional, please use if title is longer than one line
-
-%% Author with single affiliation.
-%\author{Roberto Biondo \inst{1}{\small\Envelope}\and Davide Castelnovo\inst{1}\orcidID{0000-0002-5926-5615}
-	%\and \\Fabio Gadducci\inst{1}\orcidID{0000-0003-0690-3051}
-%}
-%\institute{Dept.~of Computer Science, University of Pisa, Italy. 
-	%\email{r.biondo@studenti.unipi.it},
-	%\email{castelnovod@gmail.com},
-	% \email{fabio.gadducci@unipi.it}
-%}
-
-\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
-
-\begin{document}
-
 \tikzset{->-/.style={decoration={
 			markings,
-			mark=at position #1 with {\arrow{>}}},postaction={decorate}}}
+			mark=at position #1 with {\arrow{>}}},
+			postaction={decorate}
+			}}
+
+\title{EGGs are adhesive!}
+\titlerunning{EGGs are adhesive!} %TODO optional, please use if title is longer than one line
+
+% Author with single affiliation.
+\author{Roberto Biondo}
+{Department of Computer Science, University of Pisa, Pisa, IT}
+{r.biondo@studenti.unipi.it}{}{}
+
+\author{Davide Castelnovo}
+{Department of Computer Science, University of Pisa, Pisa, IT}
+{castelnovod@gmail.com}
+{https://orcid.org/0000-0002-5926-5615}{}
+
+\author{Fabio Gadducci}
+{Department of Computer Science, University of Pisa, Pisa, IT}
+{fabio.gadducci@unipi.it}
+{https://orcid.org/0000-0003-0690-3051}{}
+
+\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
+
+\Copyright{Roberto Biondo and Davide Castelnovo and Fabio Gadducci} 
+\ccsdesc[500]{Theory of Computation~Models of computation}
+\ccsdesc[500]{Theory of Computation~Semantics and reasoning}
+
+\keywords{Hypergraphs, terms graphs, e-graphs, adhesive categories.} %TODO mandatory; please add comma-separated list of keywords
+
+\funding{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 ``Spatio-Temporal Enhancement of Neural nets for Deeply
+Hierarchical Automatised Logic'' (STENDHAL) 
+and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information'' (FM4HD).}
+
+\begin{document}
 
@@
 
-In the original definition, e-graphs are defined as term graphs with an additional notion of equivalence on nodes. 
-Adopting the more modern presentation via string diagrams, they are tree with sharing of subtrees, and with an 
-an equivalence $\equiv$ on nodes that is closed under xxx. In plain words, if $a$ and $b$ are two constants such that
-$a \equiv b$, then $f(a) \equiv f(b)$ for any unary operator $f$.
+E-graphs can be concisely defined as (acyclic) term graphs with an additional notion of equivalence on nodes
+that is closed under the operators of the signature~\cite[Section~4.2]{DetlefsNS05}.
+In the presentation of term graphs via string diagrams~\cite{CastelnovoGM24}, e-graphs are trees equipped with 
+the possibility of
+sharing subtrees, and with an additional equivalence relation $\equiv$ on nodes that is closed under composition. 
+In plain words and with a toy example:
+if $a$ and $b$ are two constants such that $a \equiv b$, then $f(a) \equiv f(b)$ for any unary operator $f$.
 
@@
 In Section~\ref{sec:ade} we briefly recall 
-the theory of
-\emph{$\mathcal{M}$-adhesive categories}
-and of \emph{kernel pairs}.
+the theory of $\mathcal{M}$-adhesive categories
+and of kernel pairs.
 In Section~\ref{sec:hyper} we present the graphical structures of our interest, 

### 2025-03-03 calco/main.tex
primo abstract

@@
 \begin{abstract}
-\todo{a very nice abstract}
+The use of rewriting-based visual formalisms is on the rise. 
+%
+In the formal methods community, this is due also to the introduction of adhesive
+categories, where most properties of classical approaches to graph transformation, 
+such as parallelism and confluence, can be rephrased and proved in a general and 
+uniform way.
+%
+E-graphs (shortly, EGGs) are a formalism for program optimisation 
+via an efficient implementation of equality saturation. 
+In short, EGGs can be  defined as (acyclic) term graphs with an additional notion of 
+equivalence on nodes that is closed under the operators of the signature.
+Instead of replacing the components of a program, the optimisation step 
+is performed by adding new components and linking them to 
+the existing ones via an equivalence relation, until an optimal program is reached.
+%
+This work describes EGGs by means of adhesive categories. Besides 
+the benefits \emph{per se} of a formal presentation, making precise the properties of 
+the data structure, describing the addition of equivalent program components 
+via the standard tools of graph transformation offers the advantages given by the 
+adhesive framework in modelling e.g. concurrent updates.
 \end{abstract}
@@
 \todo{A very nice introduction}
-
 \begin{itemize}
 \item general on adhesive categories
-\item general on the use of eggs
+%\item general on the use of eggs
 \end{itemize}
 
-E-graphs can be concisely defined as (acyclic) term graphs with an additional notion of equivalence on nodes
+E-graphs (shortly, EGGs) are an up-and-coming formalism for program optimisation and synthesis via a compact 
+representation and efficient implementation of equality saturation. 
+%
+Albeit a classical data structure~\cite{DetlefsNS05}, EGGs received 
+new impulse after the seminal~\cite{WillseyNWFTP21} and
+developed a thriving community, as witnessed by the official website~\cite{eggs}.
+%
+The key idea of rewriting-based program optimisation is to perform the manipulation of a syntactical description 
+of a program, replacing some of its components in such a way that the semantics is preserved while improving 
+e.g. time or space costs of its actual computation. Instead of directly removing sub-programs, EGGs just add the 
+new components and link them to the older ones via the equivalence relation, until an optimal program is 
+reached and extracted.
+
+EGGs can be concisely defined as (acyclic) term graphs with an additional notion of equivalence on nodes
 that is closed under the operators of the signature~\cite[Section~4.2]{DetlefsNS05}.
-In the presentation of term graphs via string diagrams~\cite{CastelnovoGM24}, e-graphs are trees equipped with 
-the possibility of
-sharing subtrees, and with an additional equivalence relation $\equiv$ on nodes that is closed under composition. 
-In plain words and with a toy example:
+In the presentation of term graphs via string diagrams~\cite{CastelnovoGM24}, EGGs are (hyper-)trees equipped with 
+the possibility of sharing subtrees, as in terms graphs, with an additional equivalence relation $\equiv$ on nodes that 
+is closed under composition. In plain words and using a toy example:
 if $a$ and $b$ are two constants such that $a \equiv b$, then $f(a) \equiv f(b)$ for any unary operator $f$.
 
-\cite[Section~4.2]{DetlefsNS05}
-\cite{WillseyNWFTP21}
+%EGGs received a lot of attention in the implementation  side, as it is natural, since they have been introduced precisely as
+%a fast way to recover equality saturation.
+
+The aim of this work is to describe EGGs by means of adhesive categories. The advantages are two-fold. On the one side, 
+we put the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
+On the other side, describing the addition of equivalent sub-programs 
+in terms of DPO transformation offer the possibility of modelling parallel execution of optimisation steps as well as discussing
+about confluence and termination.
 
@@
 functorial characterisation, which allows for proving their adhesivity properties.
-This is expended in Section~\ref{hypereq} for describing hypergraphs 
+This is expanded in Section~\ref{hypereq} for describing hypergraphs 
 and term graphs with equivalence and in Section~\ref{eggs} for capturing
@@
 %
-All the proofs have been moved to the appendices. 
+Finally, in Section~\ref{conclusioni} we show draw our conclusions: we poi to further work
+and we show how optimisation steps can ve described via DPO transformation.
+%
+For the sake of space, all the proofs have been moved to the appendices. 
 %For the sake of completeness, 
@@
 \section{Conclusions and further works}
+\label{conclusioni}
 The aim of our paper was to extend the theory of adhesive categories in order to include EGGS, 

### 2025-03-03 calco/main.tex
mi fermo qua per oggi

--- 2025-03-03 calco/main.tex
@@
 	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given.
-	%
+
 	If the leftmost square is commutative, then there exists a a unique arrow $k_h: K_f \to K_g$ making the other two commutative.
-	%
-	Moreover, if the leftmost is a pullback, then also the other two are so.
-%
 	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
 
+		Moreover, the following hold true:
+		\begin{enumerate}
+			\item if the leftmost squareis a pullback, then also the other two are so;
+			\item if $h$ is mono then $k_h$ is mono too.
+		\end{enumerate} 
 \end{restatable}
@@
 The previous result allows us to deduce the following lemma in an $\mathcal{M}$-adhesive context.
-
+\todo{A questo punto la proposizione seguente possiamo anche buttarla via se serve recuperare spazio}
 \noindent
@@
 %\input{./fact_sys}
+
+\todo{Inserire bla bla}
+
+\noindent
+\parbox{7.5cm}{
+	\begin{restatable}{proposition}{mps}\label{prop:kerset}
+		Suppose that in $\Set$ the cube aside is given, whose top and bootom faces are pushout and such that $m\colon A\mto C$ and $m'\colon A'\mto C'4$ are injections.
+Then the right square, made by the kernel pairs of the vertical arrows is a pushout.
+\end{restatable}}\hfill 
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
 
@@
 \begin{restatable}{corollary}{mn}\label{cor:mono2}
-	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if $h_E, h_V$ and $h_C$ are all monos.
+	If $(h_E, h_V, h_Q): \mathcal{G\to H}$ is a regular mono in $\EqHyp$, then $h_E, h_V$ and $h_C$ are all monos.
 \end{restatable}
@@
 
+To prove \Cref{prop:kerset} we need some results about pushouts and coproducts in $\Set$.
+
+\begin{lemma}\label{lem:po_set}
+	The following are true:
+	\begin{enumerate}
+		\item if $(P, \{p_i\}_{i\in I})$ is a coproduct, then for every arrow $f\colon 1\to P$ there is exactly one $k\in I$ and $f_k\colon 1\to P_k$ such that $f=p_k\circ f_k$;
+
+		\parbox{11cm}{
+		\item suppose that the square on the right is a pushout and let $\iota_{m}\colon E\mto B$ be the inclusion of the complement of the image of $m$, then $(D, \{n, h\circ \iota_m \})$ is a coproduct; in particular, $h\circ \iota_f$ is mono.}\hfill \parbox{2cm}{\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	\begin{enumerate}
+		\item This is obvious.
+		\item Let $f\colon E\to Z$ and $k\colon C\to Z$ be two arrows with the same codomain.
+.
+By definition of complement and since $m$ is mono we know that $(B, \{m, \iota_m\})$ is a coproduct.
+Define $\phi\colon B\to Z$ as the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\]
+		By construction there is a unique arrow $\psi \circ D\to Z$ such that 
+		\[\psi \circ n=k \qquad \psi \circ h=\phi \]
+		But this entails that 
+		\[
+		\psi \circ h\circ \iota_m =\phi \circ \iota_m=f\]
+
+		On the other hand, if $\psi'\colon D\to Z$ is another arrow such that
+		\[\psi' \circ n=k \qquad \psi' \circ h\circ \iota_m=f \]
+		then we have
+		\[\psi'\circ h\circ m=\psi'\circ n\circ g=k\circ g=\phi \circ m =\psi \circ h\circ n \]
+		showing $\psi'=\psi$. \qedhere
+	\end{enumerate}
+\end{proof}
+
+\noindent
+\parbox{7.5cm}{
+\mps*}
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+
+\begin{proof} 
+	Let $u\colon K_b\to Z$ and $v\colon K_c\to Z$ be two arrows such that $u\circ k_{f'}=v\circ k_{m'}$. We want to construct an arrow $w\colon K_d\to Z$ such that 
+	\[w\circ k_{g'}=v \qquad w\circ k_{n'}=u\]
+
+	Now, if $E'\subseteq C'$ is the complement of the image of $m'$ and $\iota\colon E'\mto B'$ the corresponding inclusion, then by \Cref{lem:po_set} we know that $(D', \{n', g'\circ \iota\})$ is a coproduct.
+Thus if $x$ is an element of $K_d$, we have exactly four cases.
+
+	\begin{enumerate}
+		\item $\pi^1_d(x)$ and $\pi^2_d(x)$ both belong to the image of $n'$. Let $x_1$ and $x_2$ be such that $\pi^1_d(x)=n'(x_1)$ and $\pi^2_d(x)=n'(x_2)$, then 
+		\[n(b(x_1))=d(n'(x_1))=d(\pi^1_d(x))=d(\pi^1_d(x))=d(n'(x_2))=n(b(x_2)) \]
+		Since $n$ is mono we deduce that $b(x_1)=b(x_2)$ and so there exists $y\in K_{b}$ such that $\pi^1_d(y)=x_1$ and $\pi^2_d(x)=x_2$. But then we have
+		\begin{align*}
+	\pi^1_d(k_{n'}(y))&=n'(\pi^1_d(y)) =n'(x_1)=\pi^1_d(x)\\
+	\pi^2_d(k_{n'}(y))&=n'(\pi^2_d(y)) =n'(x_2)=\pi^2_d(x)
+		\end{align*}
+		Thus, by \Cref{lemma:kern_pairs_pres_pullbacks} $y$ is the unique element $k_{n'}(y)=x$. We can thus define $w(x)=u(y)$. 
+		\item $\pi^1_d(x)$ and $\pi^2_d(x)$ both belong to the image of $g'\circ \iota$. Consider $x_1$ and $x_2$ in $E'$ such that
+		\[g'(\iota(x_1))=\pi^1_d(x) \qquad  g'(\iota(x_2))=\pi^1_d(x)\]
+		Thus we have
+		\begin{align*}
+			g(c(\iota(x_1)))=d(g'(\iota(x_1)))=d(\pi^1_d(x))=d(\pi^2(x))=
+		\end{align*}
+
+		\item $\pi^1_d(x)$ belongs to the image of $n'$  and $\pi^2_d(x)$ to that of $g'\circ \iota$;
+		\item $\pi^2_d(x)$ belongs to the image of $n'$  and $\pi^1_d(x)$ to that of $g'\circ \iota$;
+	\end{enumerate}
+
+	To prove uniqueness, let we split the cases as above.
+	\begin{enumerate}
+		\item 
+		\item 
+		\item 
+		\item \qedhere
+	\end{enumerate}
+
+	Since $\Set$ is cocomplete, we can take a pushout square as the one  on the right below.
+
+	\parbox{10.5cm}{Now, notice that \begin{align*}
+		n'\circ \pi^1_{b}\circ k_{f'}&=n'\circ f'\circ \pi^1_{a}=g'\circ m'\circ \pi^1_{a}=g'\circ \pi^{1}_{c}\circ k_{m'}\\
+		n'\circ \pi^2_{b}\circ k_{f'}&=n'\circ f'\circ \pi^2_{a}=g'\circ m'\circ \pi^2_{a}=g'\circ \pi^{2}_{c}\circ k_{m'}
+		\end{align*}}\hfill \parbox{2cm}{\xymatrix@R=15pt{K_a \ar[r]_{k_{f'}} \ar[d]_{k_{m'}}& K_b  \ar[d]^{p_2}\\ K_c \ar[r]^{p_1} & P}}
+
+	In particular, this entails that there are two arrows $\pi_1, \pi_2\colon P\rightrightarrows D'$ such that 
+	\[\pi_1\circ p_1=g'\circ \pi^1_c \quad \pi_1\circ p_2=n'\circ \pi^1_b \quad \pi_2\circ p_1=g'\circ \pi^2_c \quad \pi_2\circ p_2=n'\circ \pi^2_b\]
+
+ Moreover,  we have
+ \begin{align*}
+ 	d\circ \pi_1\circ p_1&=d\circ g'\circ \pi^1_c=g\circ c\circ \circ \pi^1_c=g\circ c\circ \pi^2_c=d\circ g'\circ \pi^2_c=d\circ \pi_2 \circ p_1\\
+ 	d\circ \pi_1\circ p_2&=d\circ n'\circ \pi^1_b=n\circ b \circ \pi^1_b=n\circ b\circ \pi^2_b=d\circ n'\circ \pi^2_b=d\circ \pi_2 \circ p_2
+ \end{align*}
+	so that $d\circ \pi_1=d\circ p_2$.
+
+	We want now to show that $(P, \pi_1, \pi_2)$ is a kernel pair for $d$. Let $aa$
+
+We 
+For every $t$ in $T$
+
+\end{proof}
+
 \subsection{Proofs for \Cref{hypereq}}\label{app:due}

### 2025-03-03 calco/main.tex
roba per string diagrams
bozza sezione riscrittura

--- 2025-03-03 calco/main.tex
@@
 \newcommand{\EqTGs}{\catname{EqTG}_{\Sigma}}
+\newcommand{\GEqTGs}{\catname{GEqTG}_{\Sigma}}
+\newcommand{\GEqATGs}{\catname{GEqATG}_{\Sigma}}
 \newcommand{\gr}{\textbf{\textup{Graph}}}
@@
 \newcommand{\Dwnarrow}{\Downarrow \hspace{-2pt}}
-\newcommand{\egg}{\catname{EGG}}
+\newcommand{\egg}{\catname{GEqHyp}}
 
@@
 categories, where most properties of classical approaches to graph transformation, 
-such as parallelism and confluence, can be rephrased and proved in a general and 
+such as those on parallelism and causality, can be rephrased and proved in a general and 
 uniform way.
 %
-E-graphs (shortly, EGGs) are a formalism for program optimisation 
+E-graphs (or EGGs) are a formalism for program optimisation 
 via an efficient implementation of equality saturation. 
@@
 %
-This work describes EGGs by means of adhesive categories. Besides 
+This work describes EGGs by adhesive categories. Besides 
 the benefits \emph{per se} of a formal presentation, making precise the properties of 
@@
 
-\section{Conclusions and further works}
+\section{Pros and cons of adhesive rewriting}
+The previous sections has shown how term graphs with (possibly) closed equivalence
+can be described as a suitable $\mathcal{M},\mathcal{N}$-adhesive category. 
+The latter precisely capture EGGS, as originally
+presented in~\cite{WillseyNWFTP21}. 
+%
+Of course, being a purely graphical representation, there can be redundancy and possibly ambiguity,
+so that e.g. a term such as $f(a,a)$ admits a few different representations as a term graphs, given below
+
+\[f(a,a) \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
+
+Admittedly, the third one is illegal, i.e. it is not an object of $\EqTGs$ but not one of $\GEqTGs$: constants have no input, 
+and nodes that are targets of edges with the same label and source the empty word must be equivalent,
+and possibly be the same.
+%
+In general, note that a maximally shared representation of an EGG exists, and for our 
+toy example is the left-most above. In general terms,
+for an EGG $\mathcal{G}$, such a canonical form is the final object of the comma category 
+$\mathcal{G}  \downarrow \GEqTGs$. 
+This is a standard result in term graph rewriting, see e.g.~\cite{xxx}, and it holds also in the setting with equivalences.
+In fact, if $\mathcal{G}$ has no empty nodes, the unique arrow from $\mathcal{G}$ to the terminal object
+is injective on equivalence classes.
+%
+\todo{vedere se mettere qualcosa prima sugli aciclici}
+The restriction to the full category $\GEqATGs$ of those objects whose underlying graph is \emph{acyclic} is 
+straightforward, replicating all the considerations 
+above and in the previous sections, even if we refrain from explicitly presenting it.
+
+What about rewriting? The theory of $\mathcal{M},\mathcal{N}$-adhesivity ensures that if the rules are spans of 
+arrows in $\mathcal{M}$ and the match is an arrow in $\mathcal{N}$, then we can lift all the standard properties
+of the DPO approach to the category at hand. Luckily, this is the structure of the rules that is advanced in~\cite{DetlefsNS05},
+which is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity and the second
+component is a regular mono, simply adding the equivalences of interest.
+%
+For example, the equivalence $x \div x = 1$, from the introductory example in~\cite{xxx}, 
+can be modelled as the rule
+\[\mbox{to draw DPO rule, x in the same equivalence class} \]
+
+An immediate drawback of choosing the identity as the left-hand side is the possibilty to keep on repeating the same rewriting step.
+However, this is easily forbidden adopting rules \emph{with negative application conditions}~\cite{xxx}, i.e. the usual span 
+$L \leftarrow K \rightarrow R$ plus an additional arrow $n: L\rightarrow N$, such that a match $m: L \to G$ is admissible if it cannot
+be factorised through $n$. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side.
+
+\section{Conclusions and further and related works}
 \label{conclusioni}
 The aim of our paper was to extend the theory of adhesive categories in order to include EGGS, 
-an up-and-coming formalism for program optimisation and synthesis via a compact representation and 
+a formalism for program optimisation via a compact representation and 
 efficient implementation of equality saturation.
@@
 
-Our result opens two threads of research. The first is to use the quasi-adhesivity of EGGs to
-model their rewriting via the double-pushout (DPO) approach. This seems now easy, since 
-the rules adopted in the literature of EGGs appears to be span of regular monos, and such rules
-perfectly fit the mold of rewriting on $\mathcal{M}$-adhesive categories. 
-For example, the equivalence $x \div x = 1$, from the introductory example in~\cite{xxx}, 
-can be modelled as the rule
-\[to draw DPO rule\]
-
-It still needs to be investigated what parallelism and termination, the key properties for DPO rewriting
-on adhesive categories, 
-mean in the context of EGGs. More interestingly, another venue for development is using the adhesive 
+\emph{Future works.}
+Our result opens two threads of research. The first is to check how much of the $\mathcal{M},\mathcal{N}$-adhesivity 
+of EGGs can be used to model their rewriting via the double-pushout (DPO) approach. We have seen that 
+the rules adopted in the literature of EGGs appears to be span of regular monos, and as such they
+perfectly fit the mold of rewriting on $\mathcal{M}-\mathcal{N}$adhesive categories. The restriction on matches 
+though still need to be further investigated.
+%
+Also, it still needs to be investigated how parallelism and causality, the key features for DPO rewriting
+on adhesive categories, can be exploited in the context of EGGs implementation. 
+Another venue for development is using the adhesive 
 machinery to extend the EGGs formalism. In fact, most of the results
@@
 hypergraphs with a hierarchy (a partial order) among 
-edges that is useful for adding structural information, such as encapsulation and sandboxing~\cite{xxx}.
-
+edges that is useful for adding structural information, such as encapsulation and sandboxing~\cite{ghica, noi}.
+
+\emph{Related works.}
+\todo{espandere un poco}
 Finally, we need to draw a comparison with an alternative categorical presentation for EGGs 

### 2025-03-03 calco/main.tex

@@
 
-\usepackage{tikz-cd}
+%\usepackage{tikz-cd}
+
+%String Diagrams
 \usepackage{tikz}
+%\input{hypergraph.tikzdefs}
+%\input{hypergraphs.tikzstyles}
+
 \usetikzlibrary{decorations.markings}
@@
 
-\begin{example}\label[example]{exa_2} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
+\begin{example}\label[example]{exa_21} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
 	\[\begin{matrix}
@@
 \end{example}
+
+\iffalse
+%% Questa roba la devo aggiustare sennò non compila %%
+\begin{example}\label[example]{exa_2}
+	Let $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$, and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$. Then we define:
+	\[\begin{matrix}
+		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} &&
+		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}} &&
+		s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
+					0 \mapsto v_1\\
+					1\mapsto v_4
+				\end{matrix}&&
+		s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
+					0 \mapsto v_3 \\
+					1\mapsto v_2 
+				\end{matrix}\\
+
+		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 0 \mapsto v_1 &&
+		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&
+		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5 &&
+		t_\mathcal{G}(h_4)\colon 1 \to V_\mathcal{G} & 0 \mapsto v_4
+	\end{matrix}\]
+\end{example}
+\fi
 

### 2025-03-03 calco/main.tex
miinima

@@
 %
-E-graphs (or EGGs) are a formalism for program optimisation 
+E-graphs (EGGs) are a formalism for program optimisation 
 via an efficient implementation of equality saturation. 
@@
 %
-This work describes EGGs by adhesive categories. Besides 
-the benefits \emph{per se} of a formal presentation, making precise the properties of 
-the data structure, describing the addition of equivalent program components 
-via the standard tools of graph transformation offers the advantages given by the 
-adhesive framework in modelling e.g. concurrent updates.
+This work describes EGGs via adhesive categories. 
+Besides the benefits in itself of a formal presentation, which renders the 
+properties of the data structure precise, the description of the addition of equivalent 
+program components using standard graph transformation tools offers the advantages 
+of the adhesive framework in modelling, for example, concurrent updates.
+%
+%Besides 
+%the benefits \emph{per se} of a formal presentation, making precise the properties of 
+%the data structure, describing the addition of equivalent program components 
+%via the standard tools of graph transformation offers the advantages given by the 
+%adhesive framework in modelling e.g. concurrent updates.
 \end{abstract}
@@
 %
-Finally, in Section~\ref{conclusioni} we show draw our conclusions: we poi to further work
-and we show how optimisation steps can ve described via DPO transformation.
-%
-For the sake of space, all the proofs have been moved to the appendices. 
+In Section~\ref{rewriting} we put the former machinery at work, showing how the optimisation steps
+can be rephrased as suitable applications of term graph rewriting rules.
+%
+Finally, in Section~\ref{conclusioni} we draw our conclusions, hint at future endeavours and offer some 
+brief remarks on related works.
+%
+For the sake of space, proofs have been moved to the appendices. 
 %For the sake of completeness, 
@@
 \section{Pros and cons of adhesive rewriting}
+\label{rewriting}
 The previous sections has shown how term graphs with (possibly) closed equivalence

### 2025-03-04 calco/main.tex
minima

@@
 %
-For the sake of space, proofs have been moved to the appendices. 
+For the sake of space, the proofs appear in the appendices. 
 %For the sake of completeness, 
@@
 	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given. 
-
-	If the leftmost square is commutative, then there exists a a unique arrow $k_h: K_f \to K_g$ making the other two commutative.
+	%
+	If the leftmost square is commutative, then there is a a unique arrow $k_h: K_f \to K_g$ making the other two commutative
 	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
 
-		Moreover, the following hold true:
+		Moreover, it holds
 		\begin{enumerate}
-			\item if the leftmost squareis a pullback, then also the other two are so;
+			\item if the leftmost square is a pullback, then also the other two are so;
 			\item if $h$ is mono then $k_h$ is mono too.
@@
 
-The previous result allows us to deduce the following lemma in an $\mathcal{M}$-adhesive context.
+The previous lemma allows us to deduce the following results in an $\mathcal{M}$-adhesive context.
 \todo{A questo punto la proposizione seguente possiamo anche buttarla via se serve recuperare spazio}
@@
 	\begin{enumerate}
-		\item an arrow $(h,k)$ in $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions;
+		\item an arrow $(h,k)$ in $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective;
 		\item $\hyp_{\Sigma}$ is an adhesive category. 
@@
 
-\subsection{Labeling hypergraphs with equivalence}
+\subsection{Term graphs with equivalence}
 
@@
 
+\subsection{Hypergraph with closed equivalence}
 \begin{definition}
@@
 
+\subsection{Term graphs with closed equivalence}
+\todo{Here we must introduce $\GEqTGs$}
+
 \section{Pros and cons of adhesive rewriting}
 \label{rewriting}
-The previous sections has shown how term graphs with (possibly) closed equivalence
+The previous sections has shown how term graphs with equivalence,
+possibly closed with respect to operator composition,
 can be described as a suitable $\mathcal{M},\mathcal{N}$-adhesive category. 
@@
 %
-Of course, being a purely graphical representation, there can be redundancy and possibly ambiguity,
-so that e.g. a term such as $f(a,a)$ admits a few different representations as a term graphs, given below
-
-\[f(a,a) \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
-
-Admittedly, the third one is illegal, i.e. it is not an object of $\EqTGs$ but not one of $\GEqTGs$: constants have no input, 
+Being a purely graphical representation, EGGS allows for redundancy and possibly ambiguity,
+so that e.g. a term such as $a \div a$ admits a few different representations as a term graph, as shown below
+%
+\[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
+%
+Admittedly, the third one is illegal, i.e. it is an object of $\EqTGs$ but not one of $\GEqTGs$: constants have no input, 
 and nodes that are targets of edges with the same label and source the empty word must be equivalent,
-and possibly be the same.
+and possibly the same.
 %
@@
 straightforward, replicating all the considerations 
-above and in the previous sections, even if we refrain from explicitly presenting it.
+above and in the previous sections.
+% even if we refrain from explicitly presenting it.
 
@@
 which is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity and the second
-component is a regular mono, simply adding the equivalences of interest.
-%
-For example, the equivalence $x \div x = 1$, from the introductory example in~\cite{xxx}, 
-can be modelled as the rule
+component is a regular mono, simply adding the edges, nodes, and equivalence classes of interest.
+%
+An EGG rule such $x \div x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}, 
+can be modelled as the DPO rule below,
+which can be applied with a match that is injective on equivalence classes to the left-most and the middle EGG
+in the picture above
 \[\mbox{to draw DPO rule, x in the same equivalence class} \]
 
-An immediate drawback of choosing the identity as the left-hand side is the possibilty to keep on repeating the same rewriting step.
-However, this is easily forbidden adopting rules \emph{with negative application conditions}~\cite{xxx}, i.e. the usual span 
+An immediate drawback of choosing the identity as the left-hand side is the possibility to keep on repeating the same rewriting step.
+However, this is easily forbidden adopting rules \emph{with negative application conditions}~\cite{xxx}, which are given by the usual span 
 $L \leftarrow K \rightarrow R$ plus an additional arrow $n: L\rightarrow N$, such that a match $m: L \to G$ is admissible if it cannot
-be factorised through $n$. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side.
+be factorised through $n$. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side itself.
+%
+The theory of $\mathcal{M},\mathcal{N}$-adhesivity carries on with such enriched rules, see e.g~\cite{xxx}.
+
+Summing up, showing that EGGs are objects of $\GEqTGs$ and that optimisation steps are obtained via 
+DPO rules with negative application conditions unleash the xxx.
 
@@
 \emph{Future works.}
-Our result opens two threads of research. The first is to check how much of the $\mathcal{M},\mathcal{N}$-adhesivity 
-of EGGs can be used to model their rewriting via the double-pushout (DPO) approach. We have seen that 
-the rules adopted in the literature of EGGs appears to be span of regular monos, and as such they
-perfectly fit the mold of rewriting on $\mathcal{M}-\mathcal{N}$adhesive categories. The restriction on matches 
-though still need to be further investigated.
-%
-Also, it still needs to be investigated how parallelism and causality, the key features for DPO rewriting
+Our result on $\GEqTGs$ opens a few threads of research. The first is to check how the $\mathcal{M},\mathcal{N}$-adhesivity 
+of EGGs can be pushed to model their rewriting via the double-pushout (DPO) approach. We have seen that 
+the rules adopted in the literature of EGGs appears to be span of regular monos (possibly with negative application 
+conditions), and as such they perfectly fit the mould of rewriting on $\mathcal{M}, \mathcal{N}$-adhesive categories. 
+The consequences for usability on the restriction of the matches to arrows that are injective on equivalence classes
+though need to be further investigated.
+%
+Also, it still needs to be exploited how parallelism and causality, the key features for DPO rewriting
 on adhesive categories, can be exploited in the context of EGGs implementation. 
@@
 hypergraphs with a hierarchy (a partial order) among 
-edges that is useful for adding structural information, such as encapsulation and sandboxing~\cite{ghica, noi}.
+edges~\cite{ghicaZan,CastelnovoGM24}, which is useful for adding structural information, such as encapsulation and sandboxing.
 

### 2025-03-04 calco/main.tex
minima

@@
 of a program, replacing some of its components in such a way that the semantics is preserved while improving 
-e.g. time or space costs of its actual computation. Instead of directly removing sub-programs, EGGs just add the 
+the computational costs of its actual execution. Instead of directly removing sub-programs, EGGs just add the 
 new components and link them to the older ones via the equivalence relation, until an optimal program is 
@@
 
-The aim of this work is to describe EGGs by means of adhesive categories. The advantages are two-fold. On the one side, 
+The aim of this work is to prove that EGGs form an adhesive category. The advantages are two-fold. On the one side, 
 we put the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
 On the other side, describing the addition of equivalent sub-programs 
-in terms of DPO transformation offer the possibility of modelling parallel execution of optimisation steps as well as discussing
-about confluence and termination.
+in terms of DPO transformation offer the possibility of modelling parallelism and concurrency for optimisation steps 
+and discussing confluence and termination.
 
@@
 In Section~\ref{sec:hyper} we present the graphical structures of our interest, 
- (labelled, acyclic) hypergraphs and term graphs, and we provide a
+ (labelled) hypergraphs and term graphs, and we provide a
 functorial characterisation, which allows for proving their adhesivity properties.
@@
 arrows in $\mathcal{M}$ and the match is an arrow in $\mathcal{N}$, then we can lift all the standard properties
-of the DPO approach to the category at hand. Luckily, this is the structure of the rules that is advanced in~\cite{DetlefsNS05},
+of the DPO approach to the category at hand. Luckily, this is the structure of rules that is advanced in~\cite{DetlefsNS05},
 which is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity and the second
@@
 
-Summing up, showing that EGGs are objects of $\GEqTGs$ and that optimisation steps are obtained via 
-DPO rules with negative application conditions unleash the xxx.
+Summing up, showing that EGGs are objects of an $\mathcal{M},\mathcal{N}$-adhesive category $\GEqTGs$ and that optimisation 
+steps are obtained via DPO rules with negative application conditions with rules whose arrows are in $\mathcal{M}$ and via a match 
+that is in $\mathcal{N}$ allows for
 

### 2025-03-04 calco/main.tex
revised intro

@@
 categories, where most properties of classical approaches to graph transformation, 
-such as those on parallelism and causality, can be rephrased and proved in a general and 
+such as those on parallelism and confluence, can be rephrased and proved in a general and 
 uniform way.
@@
 \section{Introduction}
-\todo{A very nice introduction}
-\begin{itemize}
-\item general on adhesive categories
-%\item general on the use of eggs
-\end{itemize}
-
-E-graphs (shortly, EGGs) are an up-and-coming formalism for program optimisation and synthesis via a compact 
+The introduction of \emph{adhesive categories} marked a watershed moment for the algebraic approaches 
+to the rewriting of graph-like structures~\cite{lack2005adhesive,ehrig2006fundamentals}.
+%
+Until then, key results of the approaches on e.g. parallelism and confluence had to be proven 
+over and over again for each different formalism at hand, %let it be either xxx or xx, 
+despite the obvious similarity of the procedure.
+%
+Adhesive categories provides such a disparate set of formalisms with a common abstract framework 
+where many of these general results could be recast and uniformly proved once and for all.
+
+\vspace{.1cm}
+\noindent
+\begin{minipage}[l]{.78\linewidth }In short, following the double-pushout (DPO) approach
+to graph transformation~\cite{xxx}, a rule is given by two arrows $: K \to L$ and $r: K \rightarrow R$
+and its execution requires a match $m: L \to G$ such that the rewriting step from $G$
+to $H$ is given by the diagram aside, whose square are pushouts.
+  \end{minipage}%
+    \hfill
+  \begin{minipage}[r]{.20\linewidth }
+    \xymatrix@C=.5cm@R=.5cm{
+      L \ar[d]_{m}
+      & K \ar[r]^r \ar[l]_{l} \ar[d] & R \ar [d] \\
+      G & C \ar[r] \ar[l]                    & H
+    }
+%    \xymatrix@C=.5cm@R=.5cm{
+%      L \ar[d]_{m} \ar@{}[dr]|{(1)}
+%      & I \ar[r]^r \ar@{>->}[l]_{l} \ar[d] \ar@{}[dr]|{(2)} & R \ar [d] \\
+%      G & C \ar@{->}[r] \ar@{>->}[l]                    & H\\
+ %     & J \ar@{->}[ul] \ar@{->}[u]|{k} \ar@{->}[ur]
+ %   }
+  \end{minipage}
+\vspace{.1cm}
+
+\noindent
+Thus, $L$ and $R$ are the lift- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
+be present for the rule to be executed, yet they are not affected by the rule itself.
+%
+If a category is adhesive, and the arrows of the rules are monomorphisms, then the presence of a match ensures that the
+two pushouts exist, hence a rewriting step can be performed.
+%
+The theory of $\mathcal{M}, \mathcal{N}$-adhesivity~\cite{xxx} extend the core framework, still ensuring that if the arrow 
+of the rules are in $\mathcal{M}$ and the match is in $\mathcal{N}$, then the classical results from the theory of graph 
+transformation can still be lifted~\cite{xxx}. 
+%
+However, despite the elegance and effectiveness and the obvious advantages of proving a category 
+to be adhesive, proving that a given category satisfies the conditions 
+for being adhesive can be a daunting task. For this reason,  sufficient criteria have been provided for the core 
+framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, as well as for the extended one of
+$\mathcal{M}, \mathcal{N}$-adhesivity~\cite{CastelnovoGM24}.
+
+\emph{E-graphs} (shortly, EGGs) are an up-and-coming formalism for program optimisation and synthesis via a compact 
 representation and efficient implementation of equality saturation. 
@@
 The key idea of rewriting-based program optimisation is to perform the manipulation of a syntactical description 
-of a program, replacing some of its components in such a way that the semantics is preserved while improving 
-the computational costs of its actual execution. Instead of directly removing sub-programs, EGGs just add the 
+of a program, replacing some of its components in such a way that the semantics is preserved while 
+the computational costs of its actual execution are improved. Instead of directly removing sub-programs, EGGs just add the 
 new components and link them to the older ones via the equivalence relation, until an optimal program is 
@@
 
-The aim of this work is to prove that EGGs form an adhesive category. The advantages are two-fold. On the one side, 
+Building on the criterion developed in~\cite{CastelnovoGM24}, the aim of this work is to prove that EGGs form an 
+$\mathcal{M}, \mathcal{N}$-adhesive category for a suitable choice of $\mathcal{M}$ and $\mathcal{N}$.
+The advantages derived from this characterisation are two-fold. On the one side, 
 we put the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
-On the other side, describing the addition of equivalent sub-programs 
-in terms of DPO transformation offer the possibility of modelling parallelism and concurrency for optimisation steps 
-and discussing confluence and termination.
+On the other side, describing the optimisation steps via the DPO approach
+offers the tools for modelling their parallel and concurrent execution
+and for proving their confluence and termination.
 

### 2025-03-04 calco/main.tex
minima

@@
 In Section~\ref{rewriting} we put the former machinery at work, showing how the optimisation steps
-can be rephrased as suitable applications of term graph rewriting rules.
+can be rephrased as the application of term graph rewriting rules.
 %

### 2025-03-04 calco/main.tex
esempi aggiornati

@@
 
-%\usepackage{tikz-cd}
+\usepackage{tikz-cd}
 
@@
 \usepackage{tikz}
-%\input{hypergraph.tikzdefs}
-%\input{hypergraphs.tikzstyles}
+\usepackage[draft]{tikzit}
+\input{hypergraph.tikzdefs}
+\input{hypergraph.tikzstyles}
 
@@
 We can represent hypergraphs graphically.
-We use dots to denote nodes and squares to denote hyperedges, the name of a node or of an hyperedge is put near the corresponding dot or square.
-Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge have an arrowhead in the middle pointing towards the hyperedge, while the lines to the targets have arrowheads pointing to the target nodes.
-We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
-\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
+We use dots to denote nodes and boxex to denote hyperedges, the name of a node or of an hyperedge is put near the corresponding dot or box.
+Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge comes from the left of the box, while the lines to the targets exit from the right of the box.
+%We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
+%\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
 \iffalse 
@@
 \end{example}
-\fi
 
@@
 	\[\begin{matrix}
-		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+		A && s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
 			0 \mapsto v_1\\
@@
 		\end{matrix}\\
-		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
+			B && t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
 		0 \mapsto v_1 && 		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&   t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5
@@
 \end{example}
-
-\iffalse
-%% Questa roba la devo aggiustare sennò non compila %%
+\fi
+
 \begin{example}\label[example]{exa_2}
@@
 		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} &&
-		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}} &&
+		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}}\\
 		s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
 					0 \mapsto v_1\\
-					1\mapsto v_4
-				\end{matrix}&&
-		s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
-					0 \mapsto v_3 \\
+					1\mapsto v_2
+				\end{matrix}&& s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
+					0 \mapsto v_3\\
 					1\mapsto v_2
 				\end{matrix}\\
-
 		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 0 \mapsto v_1 &&
-		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&
-		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5 &&
+		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3\\
+		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_3 &&
 		t_\mathcal{G}(h_4)\colon 1 \to V_\mathcal{G} & 0 \mapsto v_4
 	\end{matrix}\]
+
+	Now, we can depict $\mathcal{G}$ as
+
+	\begin{center}
+        \begin{tikzpicture}
+                \begin{pgfonlayer}{nodelayer}
+                        \node[style=none] (lab1) at (-1.8, 0.8) {$h_1$};
+                        \node[style=small box] (h1) at (-1.8, 0.3) {};
+                        \node[style=small box] (2) at (-1.8, -0.5) {};
+                        \node[style=none] (lab2) at (-1.8, -1.0) {$h_2$};
+                        \node[style=none] (h1b) at (-1.8, 0.3) {};
+                        \node[style=none] (th2) at (0, 0.3) {};
+                        \node[style=none] (bh2) at (0, -0.3) {};
+                        \node[style=none] (h2b) at (0, 0) {};
+                        \node[style=none] (th3) at (1.8, 0){};
+                        \node[style=none] (bh3) at (1.8, -0.6){};
+                        \node[style=none] (h3c) at (1.8, -0.3){};
+                        \node[style=none] (2c) at (-1.8, -0.5){};
+                        \node[style=none] (lab3) at (0, 0.8) {$h_3$};
+                        \node[style=medium box] (h2) at (0, 0) {};
+                        \node[style=none] (lab4) at (1.8, 0.5) {$h_4$};
+                        \node[style=medium box] (h3) at (1.8, -0.3) {};
+                        \node[style=none](labv2) at (-0.9, -0.9) {$v_2$};
+                        \node[style=node] (v2) at (-0.9, -0.5) {};
+                        \node[style=none] (labv1) at (-0.9, 0.7) {$v_1$};
+                        \node[style=node] (v1) at (-0.9, 0.3) {};
+                        \node[style=none] (labv3) at (0.9, 0.4) {$v_3$};
+                        \node[style=node] (v3) at (0.9, 0) {};
+                        \node[style=none] (labv4) at (2.7, 0.1) {$v_4$};
+                        \node[style=node] (v4) at (2.7, -0.3) {};
+                \end{pgfonlayer}
+                \begin{pgfonlayer}{edgelayer}
+                        \draw (h1b.center) to (th2.center);
+                        \draw (2c.center) to (v2);
+                        \draw[in=180, out=30] (v2) to (bh2.center);
+                        \draw (h2b.center) to (th3.center);
+                        \draw (v4) to (h3c.center);
+                        %\draw (h3c) to (v4);
+                        \draw[in=180, out=-30](v2) to (bh3);
+                \end{pgfonlayer}
+        \end{tikzpicture}
+	\end{center}
+
 \end{example}
-\fi
 
@@
 
+\iffalse
 \todo{Decidere se tenere questo esempio}
@@
 	\end{center}
+\end{example}\fi
+
+\begin{example}\label[example]{exa_3}
+	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature where $O_\Sigma =  \{n, x, *, /\}$, where $n$ is any natural number and $x$ is any variable,
+	and $\ari_\Sigma(n)=\ari_\Sigma(x) = 0$, $\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then, $\mathcal{G}^\Sigma$ can be depicted as
+	\begin{center}
+		\begin{tikzpicture}
+			\begin{pgfonlayer}{nodelayer}
+				\node[style=node] (v) at (0, 0){};
+				\node[style=none] (vlab) at (0, -0.4){$v$};
+
+				\node[style=small box] (n) at (-1.8, 0.4) {};
+				\node[style=none] (nlab) at (-1.8, 0.9) {$n$};
+				\node[style=none] (nattach) at (-1.6, 0.4) {};
+
+				\node[style=small box] (const) at (-1.8, -0.4) {};
+				\node[style=none] (constlab) at (-1.8, -0.9){$a$};
+				\node[style=none] (constattach) at (-1.6, -0.4){};
+
+				\node[style=medium box] (times) at (0, 1.8) {};
+				\node[style=none] (timeslab) at (0, 2.6) {$*$};
+				\node[style=none] (timesin1) at (-0.2, 2.1) {};
+				\node[style=none] (timesin2) at (-0.2, 1.5) {};
+				\node[style=none] (timesout) at (0.2, 1.8){};
+
+				\node[style=medium box] (div) at (0, -1.8) {};
+				\node[style=none] (divlab) at (0, -2.6) {$/$};
+				\node[style=none] (divin1) at (-0.2, -2.1) {};
+				\node[style=none] (divin2) at (-0.2, -1.5) {};
+				\node[style=none] (divout) at (0.2, -1.8){};
+
+			\end{pgfonlayer}
+
+			\begin{pgfonlayer}{edgelayer}
+				\draw[out=180, in= 112.5] (timesin2.center) to (v); 
+				\draw[in=135, out = 180] (timesin1.center) to (v);
+				\draw[in=165, out=0] (nattach.center) to (v);
+
+				\draw[out=0, in=-165] (constattach.center) to (v);
+				\draw[out=180, in= -112.5] (divin2.center) to (v); 
+				\draw[in=-135, out = 180] (divin1.center) to (v);
+
+				\draw[in=30, out=0] (v) to (timesout.center);
+				\draw[in=-30, out=0] (v) to (divout.center);
+
+			\end{pgfonlayer}
+
+		\end{tikzpicture}
+	\end{center}
 \end{example}
@@
 \end{proof}
-\fi
 
@@
 
-We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
 \begin{example}\label[example]{lab_1}
@@
 \todo{Decidere se tenere questo esempio (io direi di no)}
+\fi
+
+We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
+
 \begin{example}\label[example]{lab_2}
-	Take again $\Sigma_G$ the signature of groups, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
-	\begin{align*}
-		e=f(h_1) \quad \cdot=f(h_2)\quad \cdot=f(h_3)
-	\end{align*}
+	Take again $\Sigma_G$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
+	\[\begin{matrix}
+		a=f(h_1) & 2=f(h_2) & *=f(h_3) & / =f(h_4)
+	\end{matrix}\]
 	In this case we get the following picture
 
+	\begin{center}
+		\begin{tikzpicture}
+			\begin{pgfonlayer}{nodelayer}
+				\node[style=none] (lab1) at (-1.8, 0.8) {$h_1$};
+				\node[style=small box] (h1) at (-1.8, 0.3) {$a$};
+				\node[style=small box] (2) at (-1.8, -0.5) {$2$};
+				\node[style=none] (lab2) at (-1.8, -1.0) {$h_2$};
+				\node[style=none] (h1b) at (-1.8, 0.3) {};
+				\node[style=none] (th2) at (0, 0.3) {};
+				\node[style=none] (bh2) at (0, -0.3) {};
+				\node[style=none] (h2b) at (0, 0) {};
+				\node[style=none] (th3) at (1.8, 0){};
+				\node[style=none] (bh3) at (1.8, -0.6){};
+				\node[style=none] (h3c) at (1.8, -0.3){};
+				\node[style=none] (2c) at (-1.8, -0.5){};
+				\node[style=none] (lab3) at (0, 0.8) {$h_3$};
+				\node[style=medium box] (h2) at (0, 0) {$*$};
+				\node[style=none] (lab4) at (1.8, 0.5) {$h_4$};
+				\node[style=medium box] (h3) at (1.8, -0.3) {$/$};
+				\node[style=none](labv2) at (-0.9, -0.9) {$v_2$};
+				\node[style=node] (v2) at (-0.9, -0.5) {};
+				\node[style=none] (labv1) at (-0.9, 0.7) {$v_1$};
+				\node[style=node] (v1) at (-0.9, 0.3) {};
+				\node[style=none] (labv3) at (0.9, 0.4) {$v_3$};
+				\node[style=node] (v3) at (0.9, 0) {};
+				\node[style=none] (labv4) at (2.7, 0.1) {$v_4$};
+				\node[style=node] (v4) at (2.7, -0.3) {};
+			\end{pgfonlayer}
+			\begin{pgfonlayer}{edgelayer}
+				\draw (h1b.center) to (th2.center);
+				\draw (2c.center) to (v2);
+				\draw[in=180, out=30] (v2) to (bh2.center);
+				\draw (h2b.center) to (th3.center);
+				\draw (v4) to (h3c.center);
+				%\draw (h3c) to (v4);
+				\draw[in=180, out=-30](v2) to (bh3);
+			\end{pgfonlayer}
+        	\end{tikzpicture}
+	\end{center}
+
+	\iffalse
 	\begin{center}\begin{tikzpicture}
@@
 		\end{tikzpicture}
-	\end{center}
+	\end{center}\fi
 \end{example}
@@
 
+\iffalse
 \todo{Tutta la parte qua sotto non mi è chiaro a cosa serva}

### 2025-03-04 calco/main.tex
roba per string diagrams

@@
 \begin{example}\label[example]{exa_3}
-	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature where $O_\Sigma =  \{n, x, *, /\}$, where $n$ is any natural number and $x$ is any variable,
+	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature with $O_\Sigma =  \{n, a, *, /\}$, where $n$ is any natural number and $a$ is any variable,
 	and $\ari_\Sigma(n)=\ari_\Sigma(x) = 0$, $\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then, $\mathcal{G}^\Sigma$ can be depicted as
@@
 \begin{example}\label[example]{lab_2}
-	Take again $\Sigma_G$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
+	Take again $\Sigma$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
 	\[\begin{matrix}

### 2025-03-04 calco/main.tex
diagrammi con frecce

@@
                         \node[style=none] (h1b) at (-1.8, 0.3) {};
-                        \node[style=none] (th2) at (0, 0.3) {};
-                        \node[style=none] (bh2) at (0, -0.3) {};
+                        \node[style=none] (th2) at (-0.3, 0.3) {};
+                        \node[style=none] (bh2) at (-0.3, -0.3) {};
                         \node[style=none] (h2b) at (0, 0) {};
-                        \node[style=none] (th3) at (1.8, 0){};
-                        \node[style=none] (bh3) at (1.8, -0.6){};
+                        \node[style=none] (th3) at (1.5, 0){};
+                        \node[style=none] (bh3) at (1.5, -0.6){};
                         \node[style=none] (h3c) at (1.8, -0.3){};
@@
                 \begin{pgfonlayer}{edgelayer}
-                        \draw (h1b.center) to (th2.center);
-                        \draw (2c.center) to (v2);
-                        \draw[in=180, out=30] (v2) to (bh2.center);
-                        \draw (h2b.center) to (th3.center);
-                        \draw (v4) to (h3c.center);
-                        %\draw (h3c) to (v4);
-                        \draw[in=180, out=-30](v2) to (bh3);
+                        \draw[style=diredge] (h1b.center) to (v1);
+                        \draw[style=diredge] (v1) to (th2.center);
+                        \draw[style=diredge] (2c.center) to (v2);
+                        \draw[style=diredge, in=180, out=30] (v2) to (bh2.center);
+                        \draw[style=diredge] (v3) to (th3.center);
+                        \draw[style=diredge] (h3c.center) to (v4);
+                        \draw[style=diredge] (h2b.center) to (v3);
+                        \draw[style=diredge,in=180, out=-30](v2) to (bh3);
                 \end{pgfonlayer}
@@
                 \node[style=none] (timeslab) at (0, 2.6) {$*$};
-				\node[style=none] (timesin1) at (-0.2, 2.1) {};
-				\node[style=none] (timesin2) at (-0.2, 1.5) {};
+                \node[style=none] (timesin1) at (-0.3, 2.1) {};
+                \node[style=none] (timesin2) at (-0.3, 1.5) {};
                 \node[style=none] (timesout) at (0.2, 1.8){};
@@
                 \node[style=none] (divlab) at (0, -2.6) {$/$};
-				\node[style=none] (divin1) at (-0.2, -2.1) {};
-				\node[style=none] (divin2) at (-0.2, -1.5) {};
+                \node[style=none] (divin1) at (-0.3, -2.1) {};
+                \node[style=none] (divin2) at (-0.3, -1.5) {};
                 \node[style=none] (divout) at (0.2, -1.8){};
@@
         \begin{pgfonlayer}{edgelayer}
-				\draw[out=180, in= 112.5] (timesin2.center) to (v); 
-				\draw[in=135, out = 180] (timesin1.center) to (v);
-				\draw[in=165, out=0] (nattach.center) to (v);
-
-				\draw[out=0, in=-165] (constattach.center) to (v);
-				\draw[out=180, in= -112.5] (divin2.center) to (v); 
-				\draw[in=-135, out = 180] (divin1.center) to (v);
-
-				\draw[in=30, out=0] (v) to (timesout.center);
-				\draw[in=-30, out=0] (v) to (divout.center);
+                \draw[style=diredge, in=180, out= 112.5] (v) to (timesin2.center); 
+                \draw[style=diredge,out=135, in= 180] (v) to (timesin1.center);
+                \draw[style=diredge,in=165, out=0] (nattach.center) to (v);
+
+                \draw[style=diredge,out=0, in=-165] (constattach.center) to (v);
+                \draw[style=diredge,in=180, out= -112.5] (v) to (divin2.center); 
+                \draw[style=diredge,out=-135, in= 180] (v) to (divin1.center);
+
+                \draw[style=diredge, in=30, out=0] (timesout.center) to (v);
+                \draw[style=diredge, in=-30, out=0] (divout.center) to (v);
 
@@
                         \node[style=none] (h1b) at (-1.8, 0.3) {};
-				\node[style=none] (th2) at (0, 0.3) {};
-				\node[style=none] (bh2) at (0, -0.3) {};
+                        \node[style=none] (th2) at (-0.3, 0.3) {};
+                        \node[style=none] (bh2) at (-0.3, -0.3) {};
                         \node[style=none] (h2b) at (0, 0) {};
-				\node[style=none] (th3) at (1.8, 0){};
-				\node[style=none] (bh3) at (1.8, -0.6){};
+                        \node[style=none] (th3) at (1.5, 0){};
+                        \node[style=none] (bh3) at (1.5, -0.6){};
                         \node[style=none] (h3c) at (1.8, -0.3){};
@@
                 \begin{pgfonlayer}{edgelayer}
-				\draw (h1b.center) to (th2.center);
-				\draw (2c.center) to (v2);
-				\draw[in=180, out=30] (v2) to (bh2.center);
-				\draw (h2b.center) to (th3.center);
-				\draw (v4) to (h3c.center);
-				%\draw (h3c) to (v4);
-				\draw[in=180, out=-30](v2) to (bh3);
+                        \draw[style=diredge] (h1b.center) to (v1);
+                        \draw[style=diredge] (v1) to (th2.center);
+                        \draw[style=diredge] (2c.center) to (v2);
+                        \draw[style=diredge, in=180, out=30] (v2) to (bh2.center);
+                        \draw[style=diredge] (v3) to (th3.center);
+                        \draw[style=diredge] (h3c.center) to (v4);
+                        \draw[style=diredge] (h2b.center) to (v3);
+                        \draw[style=diredge,in=180, out=-30](v2) to (bh3);
                 \end{pgfonlayer}

### 2025-03-04 calco/main.tex
controesempio

--- 2025-03-04 calco/main.tex
@@
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
+\usepackage{tikz-cd}
 \usepackage{hyperref, cleveref} %simboli matematici
@@
 
-\usepackage{tikz-cd}
+%\usepackage{tikz-cd}
 
@@
 \usepackage{tikz}
-\usepackage[draft]{tikzit}
-\input{hypergraph.tikzdefs}
-\input{hypergraph.tikzstyles}
+%\input{hypergraph.tikzdefs}
+%\input{hypergraphs.tikzstyles}
 
@@
 categories, where most properties of classical approaches to graph transformation, 
-such as those on parallelism and confluence, can be rephrased and proved in a general and 
+such as those on parallelism and causality, can be rephrased and proved in a general and 
 uniform way.
@@
 \section{Introduction}
-The introduction of \emph{adhesive categories} marked a watershed moment for the algebraic approaches 
-to the rewriting of graph-like structures~\cite{lack2005adhesive,ehrig2006fundamentals}.
-%
-Until then, key results of the approaches on e.g. parallelism and confluence had to be proven 
-over and over again for each different formalism at hand, %let it be either xxx or xx, 
-despite the obvious similarity of the procedure.
-%
-Adhesive categories provides such a disparate set of formalisms with a common abstract framework 
-where many of these general results could be recast and uniformly proved once and for all.
-
-\vspace{.1cm}
-\noindent
-\begin{minipage}[l]{.78\linewidth }In short, following the double-pushout (DPO) approach
-to graph transformation~\cite{xxx}, a rule is given by two arrows $: K \to L$ and $r: K \rightarrow R$
-and its execution requires a match $m: L \to G$ such that the rewriting step from $G$
-to $H$ is given by the diagram aside, whose square are pushouts.
-  \end{minipage}%
-    \hfill
-  \begin{minipage}[r]{.20\linewidth }
-    \xymatrix@C=.5cm@R=.5cm{
-      L \ar[d]_{m}
-      & K \ar[r]^r \ar[l]_{l} \ar[d] & R \ar [d] \\
-      G & C \ar[r] \ar[l]                    & H
-    }
-%    \xymatrix@C=.5cm@R=.5cm{
-%      L \ar[d]_{m} \ar@{}[dr]|{(1)}
-%      & I \ar[r]^r \ar@{>->}[l]_{l} \ar[d] \ar@{}[dr]|{(2)} & R \ar [d] \\
-%      G & C \ar@{->}[r] \ar@{>->}[l]                    & H\\
- %     & J \ar@{->}[ul] \ar@{->}[u]|{k} \ar@{->}[ur]
- %   }
-  \end{minipage}
-\vspace{.1cm}
-
-\noindent
-Thus, $L$ and $R$ are the lift- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
-be present for the rule to be executed, yet they are not affected by the rule itself.
-%
-If a category is adhesive, and the arrows of the rules are monomorphisms, then the presence of a match ensures that the
-two pushouts exist, hence a rewriting step can be performed.
-%
-The theory of $\mathcal{M}, \mathcal{N}$-adhesivity~\cite{xxx} extend the core framework, still ensuring that if the arrow 
-of the rules are in $\mathcal{M}$ and the match is in $\mathcal{N}$, then the classical results from the theory of graph 
-transformation can still be lifted~\cite{xxx}. 
-%
-However, despite the elegance and effectiveness and the obvious advantages of proving a category 
-to be adhesive, proving that a given category satisfies the conditions 
-for being adhesive can be a daunting task. For this reason,  sufficient criteria have been provided for the core 
-framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, as well as for the extended one of
-$\mathcal{M}, \mathcal{N}$-adhesivity~\cite{CastelnovoGM24}.
-
-\emph{E-graphs} (shortly, EGGs) are an up-and-coming formalism for program optimisation and synthesis via a compact 
+\todo{A very nice introduction}
+\begin{itemize}
+\item general on adhesive categories
+%\item general on the use of eggs
+\end{itemize}
+
+E-graphs (shortly, EGGs) are an up-and-coming formalism for program optimisation and synthesis via a compact 
 representation and efficient implementation of equality saturation. 
@@
 The key idea of rewriting-based program optimisation is to perform the manipulation of a syntactical description 
-of a program, replacing some of its components in such a way that the semantics is preserved while 
-the computational costs of its actual execution are improved. Instead of directly removing sub-programs, EGGs just add the 
+of a program, replacing some of its components in such a way that the semantics is preserved while improving 
+e.g. time or space costs of its actual computation. Instead of directly removing sub-programs, EGGs just add the 
 new components and link them to the older ones via the equivalence relation, until an optimal program is 
@@
 
-Building on the criterion developed in~\cite{CastelnovoGM24}, the aim of this work is to prove that EGGs form an 
-$\mathcal{M}, \mathcal{N}$-adhesive category for a suitable choice of $\mathcal{M}$ and $\mathcal{N}$.
-The advantages derived from this characterisation are two-fold. On the one side, 
+The aim of this work is to describe EGGs by means of adhesive categories. The advantages are two-fold. On the one side, 
 we put the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
-On the other side, describing the optimisation steps via the DPO approach
-offers the tools for modelling their parallel and concurrent execution
-and for proving their confluence and termination.
+On the other side, describing the addition of equivalent sub-programs 
+in terms of DPO transformation offer the possibility of modelling parallel execution of optimisation steps as well as discussing
+about confluence and termination.
 
@@
 In Section~\ref{sec:hyper} we present the graphical structures of our interest, 
- (labelled) hypergraphs and term graphs, and we provide a
+ (labelled, acyclic) hypergraphs and term graphs, and we provide a
 functorial characterisation, which allows for proving their adhesivity properties.
@@
 In Section~\ref{rewriting} we put the former machinery at work, showing how the optimisation steps
-can be rephrased as the application of term graph rewriting rules.
+can be rephrased as suitable applications of term graph rewriting rules.
 %
@@
 %
-For the sake of space, the proofs appear in the appendices. 
+For the sake of space, proofs have been moved to the appendices. 
 %For the sake of completeness, 
@@
 	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given.
-	%
-	If the leftmost square is commutative, then there is a a unique arrow $k_h: K_f \to K_g$ making the other two commutative
+
+	If the leftmost square is commutative, then there exists a a unique arrow $k_h: K_f \to K_g$ making the other two commutative.
 	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
 
-		Moreover, it holds
+		Moreover, the following hold true:
 		\begin{enumerate}
-			\item if the leftmost square is a pullback, then also the other two are so;
+			\item if the leftmost squareis a pullback, then also the other two are so;
 			\item if $h$ is mono then $k_h$ is mono too.
@@
 
-The previous lemma allows us to deduce the following results in an $\mathcal{M}$-adhesive context.
+The previous result allows us to deduce the following lemma in an $\mathcal{M}$-adhesive context.
 \todo{A questo punto la proposizione seguente possiamo anche buttarla via se serve recuperare spazio}
@@
 
+\todo{'sta cragna che segue è falsa come una moneta da 3 euro: cancellare}
 \noindent
@@
 	\begin{restatable}{proposition}{mps}\label{prop:kerset}
-		Suppose that in $\Set$ the cube aside is given, whose top and bootom faces are pushout and such that $m\colon A\mto C$ and $m'\colon A'\mto C'4$ are injections.
-Then the right square, made by the kernel pairs of the vertical arrows is a pushout.
+		Suppose that in $\Set$ the cube aside is given, whose top and bottom faces are pushout and such that $m\colon A\mto C$, $m'\colon A'\mto C'$ and $g\colon C\mto D$ are injections.
+Then the right square, made by the kernel pairs of the vertical arrows, is a pushout.
 \end{restatable}}\hfill 
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
 
@@
 We can represent hypergraphs graphically.
-We use dots to denote nodes and boxex to denote hyperedges, the name of a node or of an hyperedge is put near the corresponding dot or box.
-Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge comes from the left of the box, while the lines to the targets exit from the right of the box.
-%We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
-%\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
+We use dots to denote nodes and squares to denote hyperedges, the name of a node or of an hyperedge is put near the corresponding dot or square.
+Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge have an arrowhead in the middle pointing towards the hyperedge, while the lines to the targets have arrowheads pointing to the target nodes.
+We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
+\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
 \iffalse 
@@
 \end{example}
+\fi
 
@@
 	\[\begin{matrix}
-		A && s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
 			0 \mapsto v_1\\
@@
 		\end{matrix}\\
-			B && t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
+		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
 		0 \mapsto v_1 && 		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&   t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5
@@
 \end{example}
-\fi
-
+
+\iffalse
+%% Questa roba la devo aggiustare sennò non compila %%
 \begin{example}\label[example]{exa_2}
@@
 		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} &&
-		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}}\\
+		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}} &&
 		s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
 					0 \mapsto v_1\\
-					1\mapsto v_2
-				\end{matrix}&& s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
-					0 \mapsto v_3\\
+					1\mapsto v_4
+				\end{matrix}&&
+		s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
+					0 \mapsto v_3 \\
 					1\mapsto v_2 
 				\end{matrix}\\
+
 		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 0 \mapsto v_1 &&
-		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3\\
-		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_3 &&
+		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&
+		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5 &&
 		t_\mathcal{G}(h_4)\colon 1 \to V_\mathcal{G} & 0 \mapsto v_4
 	\end{matrix}\]
-
-	Now, we can depict $\mathcal{G}$ as
-
-	\begin{center}
-        \begin{tikzpicture}
-                \begin{pgfonlayer}{nodelayer}
-                        \node[style=none] (lab1) at (-1.8, 0.8) {$h_1$};
-                        \node[style=small box] (h1) at (-1.8, 0.3) {};
-                        \node[style=small box] (2) at (-1.8, -0.5) {};
-                        \node[style=none] (lab2) at (-1.8, -1.0) {$h_2$};
-                        \node[style=none] (h1b) at (-1.8, 0.3) {};
-                        \node[style=none] (th2) at (0, 0.3) {};
-                        \node[style=none] (bh2) at (0, -0.3) {};
-                        \node[style=none] (h2b) at (0, 0) {};
-                        \node[style=none] (th3) at (1.8, 0){};
-                        \node[style=none] (bh3) at (1.8, -0.6){};
-                        \node[style=none] (h3c) at (1.8, -0.3){};
-                        \node[style=none] (2c) at (-1.8, -0.5){};
-                        \node[style=none] (lab3) at (0, 0.8) {$h_3$};
-                        \node[style=medium box] (h2) at (0, 0) {};
-                        \node[style=none] (lab4) at (1.8, 0.5) {$h_4$};
-                        \node[style=medium box] (h3) at (1.8, -0.3) {};
-                        \node[style=none](labv2) at (-0.9, -0.9) {$v_2$};
-                        \node[style=node] (v2) at (-0.9, -0.5) {};
-                        \node[style=none] (labv1) at (-0.9, 0.7) {$v_1$};
-                        \node[style=node] (v1) at (-0.9, 0.3) {};
-                        \node[style=none] (labv3) at (0.9, 0.4) {$v_3$};
-                        \node[style=node] (v3) at (0.9, 0) {};
-                        \node[style=none] (labv4) at (2.7, 0.1) {$v_4$};
-                        \node[style=node] (v4) at (2.7, -0.3) {};
-                \end{pgfonlayer}
-                \begin{pgfonlayer}{edgelayer}
-                        \draw (h1b.center) to (th2.center);
-                        \draw (2c.center) to (v2);
-                        \draw[in=180, out=30] (v2) to (bh2.center);
-                        \draw (h2b.center) to (th3.center);
-                        \draw (v4) to (h3c.center);
-                        %\draw (h3c) to (v4);
-                        \draw[in=180, out=-30](v2) to (bh3);
-                \end{pgfonlayer}
-        \end{tikzpicture}
-	\end{center}
-
 \end{example}
+\fi
 
@@
 
-\iffalse
 \todo{Decidere se tenere questo esempio}
@@
 	\end{center}
-\end{example}\fi
-
-\begin{example}\label[example]{exa_3}
-	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature with $O_\Sigma =  \{n, a, *, /\}$, where $n$ is any natural number and $a$ is any variable,
-	and $\ari_\Sigma(n)=\ari_\Sigma(x) = 0$, $\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then, $\mathcal{G}^\Sigma$ can be depicted as
-	\begin{center}
-		\begin{tikzpicture}
-			\begin{pgfonlayer}{nodelayer}
-				\node[style=node] (v) at (0, 0){};
-				\node[style=none] (vlab) at (0, -0.4){$v$};
-
-				\node[style=small box] (n) at (-1.8, 0.4) {};
-				\node[style=none] (nlab) at (-1.8, 0.9) {$n$};
-				\node[style=none] (nattach) at (-1.6, 0.4) {};
-
-				\node[style=small box] (const) at (-1.8, -0.4) {};
-				\node[style=none] (constlab) at (-1.8, -0.9){$a$};
-				\node[style=none] (constattach) at (-1.6, -0.4){};
-
-				\node[style=medium box] (times) at (0, 1.8) {};
-				\node[style=none] (timeslab) at (0, 2.6) {$*$};
-				\node[style=none] (timesin1) at (-0.2, 2.1) {};
-				\node[style=none] (timesin2) at (-0.2, 1.5) {};
-				\node[style=none] (timesout) at (0.2, 1.8){};
-
-				\node[style=medium box] (div) at (0, -1.8) {};
-				\node[style=none] (divlab) at (0, -2.6) {$/$};
-				\node[style=none] (divin1) at (-0.2, -2.1) {};
-				\node[style=none] (divin2) at (-0.2, -1.5) {};
-				\node[style=none] (divout) at (0.2, -1.8){};
-
-			\end{pgfonlayer}
-
-			\begin{pgfonlayer}{edgelayer}
-				\draw[out=180, in= 112.5] (timesin2.center) to (v); 
-				\draw[in=135, out = 180] (timesin1.center) to (v);
-				\draw[in=165, out=0] (nattach.center) to (v);
-
-				\draw[out=0, in=-165] (constattach.center) to (v);
-				\draw[out=180, in= -112.5] (divin2.center) to (v); 
-				\draw[in=-135, out = 180] (divin1.center) to (v);
-
-				\draw[in=30, out=0] (v) to (timesout.center);
-				\draw[in=-30, out=0] (v) to (divout.center);
-
-			\end{pgfonlayer}
-
-		\end{tikzpicture}
-	\end{center}
 \end{example}
@@
 	\begin{enumerate}
-		\item an arrow $(h,k)$ in $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective;
+		\item an arrow $(h,k)$ in $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective functions;
 		\item $\hyp_{\Sigma}$ is an adhesive category. 
@@
 
+We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
 \begin{example}\label[example]{lab_1}
@@
 \todo{Decidere se tenere questo esempio (io direi di no)}
-\fi
-
-We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
-
 \begin{example}\label[example]{lab_2}
-	Take again $\Sigma$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
-	\[\begin{matrix}
-		a=f(h_1) & 2=f(h_2) & *=f(h_3) & / =f(h_4)
-	\end{matrix}\]
+	Take again $\Sigma_G$ the signature of groups, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
+	\begin{align*}
+		e=f(h_1) \quad \cdot=f(h_2)\quad \cdot=f(h_3)
+	\end{align*}
 	In this case we get the following picture
 
-	\begin{center}
-		\begin{tikzpicture}
-			\begin{pgfonlayer}{nodelayer}
-				\node[style=none] (lab1) at (-1.8, 0.8) {$h_1$};
-				\node[style=small box] (h1) at (-1.8, 0.3) {$a$};
-				\node[style=small box] (2) at (-1.8, -0.5) {$2$};
-				\node[style=none] (lab2) at (-1.8, -1.0) {$h_2$};
-				\node[style=none] (h1b) at (-1.8, 0.3) {};
-				\node[style=none] (th2) at (0, 0.3) {};
-				\node[style=none] (bh2) at (0, -0.3) {};
-				\node[style=none] (h2b) at (0, 0) {};
-				\node[style=none] (th3) at (1.8, 0){};
-				\node[style=none] (bh3) at (1.8, -0.6){};
-				\node[style=none] (h3c) at (1.8, -0.3){};
-				\node[style=none] (2c) at (-1.8, -0.5){};
-				\node[style=none] (lab3) at (0, 0.8) {$h_3$};
-				\node[style=medium box] (h2) at (0, 0) {$*$};
-				\node[style=none] (lab4) at (1.8, 0.5) {$h_4$};
-				\node[style=medium box] (h3) at (1.8, -0.3) {$/$};
-				\node[style=none](labv2) at (-0.9, -0.9) {$v_2$};
-				\node[style=node] (v2) at (-0.9, -0.5) {};
-				\node[style=none] (labv1) at (-0.9, 0.7) {$v_1$};
-				\node[style=node] (v1) at (-0.9, 0.3) {};
-				\node[style=none] (labv3) at (0.9, 0.4) {$v_3$};
-				\node[style=node] (v3) at (0.9, 0) {};
-				\node[style=none] (labv4) at (2.7, 0.1) {$v_4$};
-				\node[style=node] (v4) at (2.7, -0.3) {};
-			\end{pgfonlayer}
-			\begin{pgfonlayer}{edgelayer}
-				\draw (h1b.center) to (th2.center);
-				\draw (2c.center) to (v2);
-				\draw[in=180, out=30] (v2) to (bh2.center);
-				\draw (h2b.center) to (th3.center);
-				\draw (v4) to (h3c.center);
-				%\draw (h3c) to (v4);
-				\draw[in=180, out=-30](v2) to (bh3);
-			\end{pgfonlayer}
-        	\end{tikzpicture}
-	\end{center}
-
-	\iffalse
 	\begin{center}\begin{tikzpicture}
@@
 		\end{tikzpicture}
-	\end{center}\fi
+	\end{center}
 \end{example}
@@
 \begin{lemma}\label{lemma:stab}
-	In $\EqHyp$, pushouts along regular monos are stable.
+	In $\EqHyp$, $\reg(\EqHyp), \mathcal{N}$-pushouts are stable.
 \end{lemma}
@@
 	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
-	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout and $h$ is a regular mono.
+	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
 By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
@@
 	\noindent 
-\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pullback the third component to get the solid part of the cube aside.
+\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
 Notice, moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
-By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left fact is a pullback.
-By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
+By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
+By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
 
@@
 	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
+
+We have to show that the top face of the cube with which we have began is a pushout.
+Let $\mathcal{H}$ be $(E, V, C, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
+Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
+\[v_E\circ h'_E=w_E\circ k'_E\qquad v_V\circ h'_V=w_V\circ k'_V\]
+
+We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+
+Now, $d_V$ is a regular epi, thus
 
@@
 Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.}
-
-	We have to show that the top face of the cube with which we have began is a pushout.
-Let $\mathcal{H}$ be $(E, V, C, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
-Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
-\[v_E\circ h'_E=w_E\circ k'_E\qquad v_V\circ h'_V=w_V\circ k'_V\]
-
-	We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-
-	Now, \Cref{lem:mpo}, let us take the kernel pair
 
@@
 
-\end{proof}
+	\begin{example}
+		Un controesempio:
+		Consideriamo i grafi senza edge e con nodi dati dal seguente cubo in cui le facce verticali sono pb e le due orizzontali sono po (tutte le frecce sono inclusioni)
+		\[
+	\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_2} \ar[dl]_{?_1} && 2 \ar[dd]^{\id{2}} \ar[dl]_{i_{2,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){i_{3,4}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_2} && 2 \ar[dl]^{j} \\2 \ar@{>->}[rr]_{j'} & & 4 }
+		\]
+
+		Qui abbiamo $j'(0)=2, j'(1)=3$ e  $i_{1,3}(0)=2$
+		Come quozienti consideriamo il seguente cubo
+
+		\[
+		\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_1} \ar[dl]_{?_1} && 1 \ar[dd]^{\id{1}} \ar[dl]_{i_{1,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){\id{3}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_1} && 1 \ar[dl]^{k} \\2 \ar@{>->}[rr]_{k'} & & 3 }
+		\]
+
+	\end{example}
+
+\end{proof}
+
+\begin{example}
+	Considet the following hypergaphs with equivalence:
+	\[\mathcal{G}:=(\emptyset, 2, 2, ?_{2}, ?_2, \id{2}) \quad \mathcal{H}:=(\emptyset, 1,1, ?_{1}, ?_1, \id{1}) \quad \mathcal{G}'=(\emptyset, 2, 1, ?_{2}, ?_{2}, !_{2}) \]
+
+There is a morphism $d:=(\id{\emptyset}, !_2, \id{1})\colon \mathcal{G}'\to \mathcal{H}$. We can then construct the cube aside, where the bottom face is a pushout and the vertical ones pullbacks.
+	\[
+\xymatrix@C=30pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'}  \\ 
+	\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}' \ar[dd]^(.3){d} \\
+	&\mathcal{G}\ar[rr]|\hole^(.3){({\emptyset, !_{2}, !_2})} \ar[dl]_{\id{\mathcal{G}}} && \mathcal{H} \ar[dl]^{\id{\mathcal{H}}}  \\
+	\mathcal{G} \ar[rr]_{({\emptyset, !_{2}, !_2})} & & \mathcal{H}  }
+\]\todo{sposta di lato}
+
+\todo{finisci}
+
+\end{example}
 
@@
 
-\subsection{Term graphs with equivalence}
+\subsection{Labeling hypergraphs with equivalence}
 
@@
 
-\subsection{Hypergraph with closed equivalence}
 \begin{definition}
@@
 
-\subsection{Term graphs with closed equivalence}
-\todo{Here we must introduce $\GEqTGs$}
-
 \section{Pros and cons of adhesive rewriting}
 \label{rewriting}
-The previous sections has shown how term graphs with equivalence,
-possibly closed with respect to operator composition,
+The previous sections has shown how term graphs with (possibly) closed equivalence
 can be described as a suitable $\mathcal{M},\mathcal{N}$-adhesive category. 
@@
 %
-Being a purely graphical representation, EGGS allows for redundancy and possibly ambiguity,
-so that e.g. a term such as $a \div a$ admits a few different representations as a term graph, as shown below
-%
-\[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
-%
-Admittedly, the third one is illegal, i.e. it is an object of $\EqTGs$ but not one of $\GEqTGs$: constants have no input, 
+Of course, being a purely graphical representation, there can be redundancy and possibly ambiguity,
+so that e.g. a term such as $f(a,a)$ admits a few different representations as a term graphs, given below
+
+\[f(a,a) \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
+
+Admittedly, the third one is illegal, i.e. it is not an object of $\EqTGs$ but not one of $\GEqTGs$: constants have no input, 
 and nodes that are targets of edges with the same label and source the empty word must be equivalent,
-and possibly the same.
+and possibly be the same.
 %
@@
 straightforward, replicating all the considerations 
-above and in the previous sections.
-% even if we refrain from explicitly presenting it.
+above and in the previous sections, even if we refrain from explicitly presenting it.
 
@@
 arrows in $\mathcal{M}$ and the match is an arrow in $\mathcal{N}$, then we can lift all the standard properties
-of the DPO approach to the category at hand. Luckily, this is the structure of rules that is advanced in~\cite{DetlefsNS05},
+of the DPO approach to the category at hand. Luckily, this is the structure of the rules that is advanced in~\cite{DetlefsNS05},
 which is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity and the second
-component is a regular mono, simply adding the edges, nodes, and equivalence classes of interest.
-%
-An EGG rule such $x \div x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}, 
-can be modelled as the DPO rule below,
-which can be applied with a match that is injective on equivalence classes to the left-most and the middle EGG
-in the picture above
+component is a regular mono, simply adding the equivalences of interest.
+%
+For example, the equivalence $x \div x = 1$, from the introductory example in~\cite{xxx}, 
+can be modelled as the rule
 \[\mbox{to draw DPO rule, x in the same equivalence class} \]
 
-An immediate drawback of choosing the identity as the left-hand side is the possibility to keep on repeating the same rewriting step.
-However, this is easily forbidden adopting rules \emph{with negative application conditions}~\cite{xxx}, which are given by the usual span 
+An immediate drawback of choosing the identity as the left-hand side is the possibilty to keep on repeating the same rewriting step.
+However, this is easily forbidden adopting rules \emph{with negative application conditions}~\cite{xxx}, i.e. the usual span 
 $L \leftarrow K \rightarrow R$ plus an additional arrow $n: L\rightarrow N$, such that a match $m: L \to G$ is admissible if it cannot
-be factorised through $n$. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side itself.
-%
-The theory of $\mathcal{M},\mathcal{N}$-adhesivity carries on with such enriched rules, see e.g~\cite{xxx}.
-
-Summing up, showing that EGGs are objects of an $\mathcal{M},\mathcal{N}$-adhesive category $\GEqTGs$ and that optimisation 
-steps are obtained via DPO rules with negative application conditions with rules whose arrows are in $\mathcal{M}$ and via a match 
-that is in $\mathcal{N}$ allows for
+be factorised through $n$. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side.
 
@@
 \emph{Future works.}
-Our result on $\GEqTGs$ opens a few threads of research. The first is to check how the $\mathcal{M},\mathcal{N}$-adhesivity 
-of EGGs can be pushed to model their rewriting via the double-pushout (DPO) approach. We have seen that 
-the rules adopted in the literature of EGGs appears to be span of regular monos (possibly with negative application 
-conditions), and as such they perfectly fit the mould of rewriting on $\mathcal{M}, \mathcal{N}$-adhesive categories. 
-The consequences for usability on the restriction of the matches to arrows that are injective on equivalence classes
-though need to be further investigated.
-%
-Also, it still needs to be exploited how parallelism and causality, the key features for DPO rewriting
+Our result opens two threads of research. The first is to check how much of the $\mathcal{M},\mathcal{N}$-adhesivity 
+of EGGs can be used to model their rewriting via the double-pushout (DPO) approach. We have seen that 
+the rules adopted in the literature of EGGs appears to be span of regular monos, and as such they
+perfectly fit the mold of rewriting on $\mathcal{M}-\mathcal{N}$adhesive categories. The restriction on matches 
+though still need to be further investigated.
+%
+Also, it still needs to be investigated how parallelism and causality, the key features for DPO rewriting
 on adhesive categories, can be exploited in the context of EGGs implementation. 
@@
 hypergraphs with a hierarchy (a partial order) among 
-edges~\cite{ghicaZan,CastelnovoGM24}, which is useful for adding structural information, such as encapsulation and sandboxing.
+edges that is useful for adding structural information, such as encapsulation and sandboxing~\cite{ghica, noi}.
 
@@
 	\parbox{4cm}{
-	\xymatrix@R=18pt{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}}
+	\xymatrix@R=15pt{X \ar[d]_{a} \ar[r]_{f}& \ar[r]_{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]^{h}& B \ar[r]^{k}& C}}
 \commentato{
@@
 
+The category of $\Set$ enjoys two other remarkable and useful properties; it is \emph{distributive} and \emph{extensive}.
+Distributivity amount to the following property: for every family $\{X_i\}_{i}$ and an object $Y$, the unique morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms.
+\[\xymatrix@C=15pt@R=15pt{&Y\times X_i \ar@{>->}[dl]_{j_i} \ar@{>->}[dr]^{\id{Y}\times h_i} &&&X_i \times Y \ar@{>->}[dl]_{k_i} \ar@{>->}[dr]^{ h_i \times \id{Y}} \\ \Sum_{i\in I} Y\times X_i \ar@{.>}[rr]_{\phi}&& Y\times (\Sum_{i\in I}X_i) & \Sum_{i\in I}  X_i \times Y \ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \times Y }\]
+
+\noindent 
+\parbox{11.5cm}{\hspace{15pt} Extensivity means that given a family of objects $\{X_{i}\}_{i\in I}$ and a family of squares as the one on the right, where $j_i$ is a  coprojection, then all the squares are pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.}\hfill
+\parbox{2cm}{\xymatrix@R=15pt{Z_i \ar[r]_{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar@{>->}[r]^{j_i} & X}}
+
+These two property together yields the following fact.
+
+\begin{lemma}\label{lem:nodim}
+	Let $f,g\colon A\rightrightarrows B+C$ be two arrows with a coproduct as codomain. Then $(A, \{j_i\}_{i=0}^
+	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares.
+	\[\xymatrix@C=30pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
+		B\times B \ar@{>->}[r]_-{i_B\times i_B} & (B+C)\times (B+C) & B\times C \ar@{>->}[r]_-{i_B\times i_C} & (B+C)\times (B+C)}\]
+	\[ \xymatrix@C=30pt{A_2 \ar@{>->}[r]^{j_2}  \ar[d]_{p_2}& A   \ar[d]^{(f,g)}& A_3 \ar@{>->}[r]^{j_3}  \ar[d]_{p_3} & A \ar[d]^{(f,g)} \\
+		C\times B \ar@{>->}[r]_-{i_C\times i_B} & (B+C)\times (B+C) & C\times C \ar@{>->}[r]_-{i_C\times i_C} & (B+C)\times (B+C)}\]
+\end{lemma}
+
 \noindent
@@
 \mps*}
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
+
+\begin{proof}
+		Let $E'\subseteq C'$ be the complement of the image of $m'$ and $\iota\colon E'\mto B'$ be the corresponding inclusion.
+By \Cref{lem:po_set} we know that $(D', \{n', g'\circ \iota\})$ is a coproduct.
+Thus by \Cref{lem:nodim} we also know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
+	\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
+	\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]
+
+	Now, if we compute we get
+	\begin{align*}
+		n\circ b\circ p_0&= d\circ n'\circ p_0= d\circ \pi^1_d\circ j_0=d\circ \pi^2_d\circ j_0=d\circ n'\circ q_0=n\circ b\circ q_0\\
+g\circ c \circ  \iota \circ p_3&=d\circ g' \circ  \iota p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota \circ q_3= g \circ c\circ \iota\circ q_3
+	\end{align*}
+	Thus, since $n$ and $g$ are mono we get the dotted arrows in the diagram below.
+\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota} \\ &K_b \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d}& B' \ar[d]^{b} & E' \ar[dr]_{\iota}&K_c \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]
+
+	Now, we also know that $(C', \{m', \iota\})$ is a coproduct, thus we can apply again \Cref{lem:nodim} to $K_c$ to conclude that $(K_c, \{k_i\}_{i=0}^4)$ is a coproduct, where $k_i\colon K^i_c\to K_c$ is defined by the following pullbacks.
+
+	\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
+	\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]
+
+	Let $u\colon K_b\to Z$ and $v\colon K_c\to Z$ be two arrows such that $u\circ k_{f'}=v\circ k_{m'}$.
+We want to construct an arrow $w\colon K_d\to Z$ such that $w\circ k_{g'}=v$ and $w\circ k_{n'}=u$.
+
+\end{proof}
 
@@
 
-\iffalse
 \todo{Tutta la parte qua sotto non mi è chiaro a cosa serva}

### 2025-03-04 calco/main.tex
minima

--- 2025-03-04 calco/main.tex
@@
 
-\todo{FG ne lascerei uno, ripreso magari dalla intro e presentato come string diagram}
-
-We can represent hypergraphs graphically.
-We use dots to denote nodes and boxex to denote hyperedges, the name of a node or of an hyperedge is put near the corresponding dot or box.
-Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge comes from the left of the box, while the lines to the targets exit from the right of the box.
-%We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
-%\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
-\iffalse 
-\begin{example}Take $V_{\mathcal{G}}$ to be be $\{v_1, v_2, v_3, v_4, v_5\}$ and $E_{\mathcal{G}}$ to be $\{h_1, h_2, h_3\}$. Sources and targets are given by:
-	\[\begin{matrix}
-		s_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}}  & \begin{matrix}
-			0 \mapsto v_1\\
-			1\mapsto v_2
-		\end{matrix} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
-			0 \mapsto v_3\\
-			1\mapsto v_4 
-		\end{matrix} && s_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 
-		0 \mapsto v_5\\
-		t_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
-			0 \mapsto v_3\\
-			1\mapsto v_4
-		\end{matrix} && t_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & 0\mapsto v_5 && t_{\mathcal{G}}(h_3)\colon 0\to V_{\mathcal{G}} &  t_{\mathcal{G}}(h_3)=?_{ V_{\mathcal{G}}} 
-	\end{matrix}\]
-
-	We can draw the resulting $\mathcal{G}$ as follows:
-	\begin{center}\begin{tikzpicture}
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,0) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-1.5) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_5$}] (E) at (6,-0.75) {};
-			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
-			\draw[->-=.5](4.75,-0.75)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5](E)--(7,-0.75)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[rounded corners] (4.25, -1) rectangle (4.75, -0.5) {};
-			\node at (4.5, -0.3){$h_2$};
-			\node at (1.5, -0.3){$h_1$};
-			\node at (7.25, -0.3){$h_3$};
-			\draw[rounded corners] (7, -1) rectangle (7.5, -0.5) {};
-			\draw(A)[->-=.5]..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw(B)[->-=.5]..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-
-			\draw(C)[->-=.5]..controls(3.5,0)and(4.2,-0.25)..(4.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw(D)[->-=.5]..controls(3.5,-1.5)and(4.2,-1.3)..(4.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-
-			\draw[->-=.5](1.75,-0.9)..controls(1.8,-1.3)and(2.5,-1.5)..(D)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-			\draw[->-=.5] (1.75,-0.6)..controls(1.8,-0.25)and(2.5,0)..(C) node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-		\end{tikzpicture}
-	\end{center}
-\end{example}
-
-\begin{example}\label[example]{exa_21} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
-	\[\begin{matrix}
-		A && s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
-			0 \mapsto v_1\\
-			1\mapsto v_2
-		\end{matrix}&& s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
-			0 \mapsto v_1\\
-			1\mapsto v_4	
-		\end{matrix}\\
-			B && t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
-		0 \mapsto v_1 && 		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&   t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5
-	\end{matrix}\]
-
-	Now we can depict $\mathcal{G}$ as
-	\begin{center}\begin{tikzpicture}
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,-0.75) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-2.25) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=right:{$v_5$}] (E) at (6,-1.5) {};
-			\draw[->-=.5] (1.75,-0.75)--(C)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
-			\draw[->-=.5] (4.75,-1.5)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5] (-1.5,0)--(A)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[rounded corners] (4.25, -1.75) rectangle (4.75, -1.25) {};
-			\node at (4.5, -1.05){$h_3$};
-			\node at (1.5, -0.3){$h_2$};
-			\node at (-1.75, 0.45){$h_1$};
-			\draw[rounded corners] (-2, -0.25) rectangle (-1.5, 0.25) {};
-			\draw[->-=.5] (A)..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5] (B)..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-
-			\draw[->-=.5] (C)..controls(3.5,-0.75)and(4.2,-0.95)..(4.25,-1.35)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5] (D)..controls(3.5,-2.25)and(4.2,-2.05)..(4.25,-1.65)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-		\end{tikzpicture}
-	\end{center}
-\end{example}
-\fi
+%\todo{FG ne lascerei uno, ripreso magari dalla intro e presentato come string diagram}
 
 \begin{example}\label[example]{exa_2}
-	Let $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$, and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$. Then we define:
-	\[\begin{matrix}
-		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} &&
-		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}}\\
-		s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
-					0 \mapsto v_1\\
-					1\mapsto v_2
-				\end{matrix}&& s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
-					0 \mapsto v_3\\
-					1\mapsto v_2
-				\end{matrix}\\
-		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 0 \mapsto v_1 &&
-		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3\\
-		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_3 &&
-		t_\mathcal{G}(h_4)\colon 1 \to V_\mathcal{G} & 0 \mapsto v_4
-	\end{matrix}\]
-
-	Now, we can depict $\mathcal{G}$ as
-
+We represent hypergraphs visually: dots denote nodes and boxes hyperedges. Should we interested in their identity, we put a name near the corresponding dot or box. 
+Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge comes from the left of the box, while the lines to the targets 
+exit from the right of the box.
+Let us look at the picture below. It represent an hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
+and edges, respectively, such that  $h_1, h_2$ are constants and $h_3, h_4$ are binary operators
 	\begin{center}
@@
 	\end{center}
-
 \end{example}
+%We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
+%\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
+\iffalse 
+\begin{example}
+Take $V_{\mathcal{G}}$ to be be $\{v_1, v_2, v_3, v_4, v_5\}$ and $E_{\mathcal{G}}$ to be $\{h_1, h_2, h_3\}$. Sources and targets are given by:
+	\[\begin{matrix}
+		s_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}}  & \begin{matrix}
+			0 \mapsto v_1\\
+			1\mapsto v_2
+		\end{matrix} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+			0 \mapsto v_3\\
+			1\mapsto v_4 
+		\end{matrix} && s_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 
+		0 \mapsto v_5\\
+		t_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+			0 \mapsto v_3\\
+			1\mapsto v_4
+		\end{matrix} && t_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & 0\mapsto v_5 && t_{\mathcal{G}}(h_3)\colon 0\to V_{\mathcal{G}} &  t_{\mathcal{G}}(h_3)=?_{ V_{\mathcal{G}}} 
+	\end{matrix}\]
+
+	We can draw the resulting $\mathcal{G}$ as follows:
+	\begin{center}\begin{tikzpicture}
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-1.5) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_5$}] (E) at (6,-0.75) {};
+			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
+			\draw[->-=.5](4.75,-0.75)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5](E)--(7,-0.75)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (4.25, -1) rectangle (4.75, -0.5) {};
+			\node at (4.5, -0.3){$h_2$};
+			\node at (1.5, -0.3){$h_1$};
+			\node at (7.25, -0.3){$h_3$};
+			\draw[rounded corners] (7, -1) rectangle (7.5, -0.5) {};
+			\draw(A)[->-=.5]..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw(B)[->-=.5]..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\draw(C)[->-=.5]..controls(3.5,0)and(4.2,-0.25)..(4.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw(D)[->-=.5]..controls(3.5,-1.5)and(4.2,-1.3)..(4.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\draw[->-=.5](1.75,-0.9)..controls(1.8,-1.3)and(2.5,-1.5)..(D)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+			\draw[->-=.5] (1.75,-0.6)..controls(1.8,-0.25)and(2.5,0)..(C) node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+		\end{tikzpicture}
+	\end{center}
+\end{example}
+
+\begin{example}\label[example]{exa_21} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
+	\[\begin{matrix}
+		A && s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
+			0 \mapsto v_1\\
+			1\mapsto v_2
+		\end{matrix}&& s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
+			0 \mapsto v_1\\
+			1\mapsto v_4	
+		\end{matrix}\\
+			B && t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
+		0 \mapsto v_1 && 		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&   t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5
+	\end{matrix}\]
+
+	Now we can depict $\mathcal{G}$ as
+	\begin{center}\begin{tikzpicture}
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,-0.75) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-2.25) {};
+			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=right:{$v_5$}] (E) at (6,-1.5) {};
+			\draw[->-=.5] (1.75,-0.75)--(C)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
+			\draw[->-=.5] (4.75,-1.5)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (-1.5,0)--(A)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[rounded corners] (4.25, -1.75) rectangle (4.75, -1.25) {};
+			\node at (4.5, -1.05){$h_3$};
+			\node at (1.5, -0.3){$h_2$};
+			\node at (-1.75, 0.45){$h_1$};
+			\draw[rounded corners] (-2, -0.25) rectangle (-1.5, 0.25) {};
+			\draw[->-=.5] (A)..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (B)..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+
+			\draw[->-=.5] (C)..controls(3.5,-0.75)and(4.2,-0.95)..(4.25,-1.35)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
+			\draw[->-=.5] (D)..controls(3.5,-2.25)and(4.2,-2.05)..(4.25,-1.65)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
+		\end{tikzpicture}
+	\end{center}
+\end{example}
+\fi
+
+\commentato{
+\begin{example}\label[example]{exa_2}
+	Let $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$, and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$. Then we define:
+	\[\begin{matrix}
+		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} &&
+		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}}\\
+		s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
+					0 \mapsto v_1\\
+					1\mapsto v_2
+				\end{matrix}&& s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
+					0 \mapsto v_3\\
+					1\mapsto v_2
+				\end{matrix}\\
+		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 0 \mapsto v_1 &&
+		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3\\
+		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_3 &&
+		t_\mathcal{G}(h_4)\colon 1 \to V_\mathcal{G} & 0 \mapsto v_4
+	\end{matrix}\]
+
+	Now, we can depict $\mathcal{G}$ as
+
+	\begin{center}
+        \begin{tikzpicture}
+                \begin{pgfonlayer}{nodelayer}
+                        \node[style=none] (lab1) at (-1.8, 0.8) {$h_1$};
+                        \node[style=small box] (h1) at (-1.8, 0.3) {};
+                        \node[style=small box] (2) at (-1.8, -0.5) {};
+                        \node[style=none] (lab2) at (-1.8, -1.0) {$h_2$};
+                        \node[style=none] (h1b) at (-1.8, 0.3) {};
+                        \node[style=none] (th2) at (0, 0.3) {};
+                        \node[style=none] (bh2) at (0, -0.3) {};
+                        \node[style=none] (h2b) at (0, 0) {};
+                        \node[style=none] (th3) at (1.8, 0){};
+                        \node[style=none] (bh3) at (1.8, -0.6){};
+                        \node[style=none] (h3c) at (1.8, -0.3){};
+                        \node[style=none] (2c) at (-1.8, -0.5){};
+                        \node[style=none] (lab3) at (0, 0.8) {$h_3$};
+                        \node[style=medium box] (h2) at (0, 0) {};
+                        \node[style=none] (lab4) at (1.8, 0.5) {$h_4$};
+                        \node[style=medium box] (h3) at (1.8, -0.3) {};
+                        \node[style=none](labv2) at (-0.9, -0.9) {$v_2$};
+                        \node[style=node] (v2) at (-0.9, -0.5) {};
+                        \node[style=none] (labv1) at (-0.9, 0.7) {$v_1$};
+                        \node[style=node] (v1) at (-0.9, 0.3) {};
+                        \node[style=none] (labv3) at (0.9, 0.4) {$v_3$};
+                        \node[style=node] (v3) at (0.9, 0) {};
+                        \node[style=none] (labv4) at (2.7, 0.1) {$v_4$};
+                        \node[style=node] (v4) at (2.7, -0.3) {};
+                \end{pgfonlayer}
+                \begin{pgfonlayer}{edgelayer}
+                        \draw (h1b.center) to (th2.center);
+                        \draw (2c.center) to (v2);
+                        \draw[in=180, out=30] (v2) to (bh2.center);
+                        \draw (h2b.center) to (th3.center);
+                        \draw (v4) to (h3c.center);
+                        %\draw (h3c) to (v4);
+                        \draw[in=180, out=-30](v2) to (bh3);
+                \end{pgfonlayer}
+        \end{tikzpicture}
+	\end{center}
+
+\end{example}
+}
 
@@
 \begin{example}\label[example]{exa_3}
-	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature with $O_\Sigma =  \{n, a, *, /\}$, where $n$ is any natural number and $a$ is any variable,
-	and $\ari_\Sigma(n)=\ari_\Sigma(x) = 0$, $\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then, $\mathcal{G}^\Sigma$ can be depicted as
+	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature with $O_\Sigma =  \mathbb{N} \uplus A \uplus \{*, /\}$, 
+	let $n$ stands for any natural number and $a$ for any element in $A$, both sets interpreted as sets of constants, and
+	%so that $\ari_\Sigma(n)=\ari_\Sigma(a) = 0$, 
+	$\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then the hypergraph $\mathcal{G}^\Sigma$ can be depicted as
 	\begin{center}
@@
 \begin{example}\label[example]{lab_2}
-	Take again $\Sigma$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled defining
-	\[\begin{matrix}
-		a=f(h_1) & 2=f(h_2) & *=f(h_3) & / =f(h_4)
-	\end{matrix}\]
-	In this case we get the following picture
-
+	Consider again $\Sigma$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled by a morphism
+	$f: \mathcal{G} \to \mathcal{G}^\Sigma$ that is characterised by the image of the edges. 
+	If $f(h(1) = a$, $f(h_2) = 2$, $f(h_3) = *$, and $f(h_3) = /$, we represent it visually 
+	by putting the identifiers of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$
+	as
 		\begin{center}
@@
 This is a standard result in term graph rewriting, see e.g.~\cite{xxx}, and it holds also in the setting with equivalences.
-In fact, if $\mathcal{G}$ has no empty nodes, the unique arrow from $\mathcal{G}$ to the terminal object
-is injective on equivalence classes.
-%
-\todo{vedere se mettere qualcosa prima sugli aciclici}
-The restriction to the full category $\GEqATGs$ of those objects whose underlying graph is \emph{acyclic} is 
-straightforward, replicating all the considerations 
-above and in the previous sections.
-% even if we refrain from explicitly presenting it.
+I%
+The same construction carries on when restricting to the full category of $\GEqTGs$ of those objects whose 
+underlying term graph is \emph{acyclic}, and in this case if $\mathcal{G}$ has no empty nodes, then the unique arrow 
+from $\mathcal{G}$ to the terminal object is easily shown to be injective on equivalence classes.
 
@@
 
+Note that if the starting term graph is acyclic, so is also the arriving one.
  An immediate drawback of choosing the identity as the left-hand side is the possibility to keep on repeating the same rewriting step.
@@
 steps are obtained via DPO rules with negative application conditions with rules whose arrows are in $\mathcal{M}$ and via a match 
-that is in $\mathcal{N}$ allows for
+that is in $\mathcal{N}$ allows for exploiting all the
 
@@
 The aim of our paper was to extend the theory of adhesive categories in order to include EGGS, 
-a formalism for program optimisation via a compact representation and 
-efficient implementation of equality saturation.
+a formalism for program optimisation 
+%via a compact representation and 
+%efficient implementation of equality saturation.
 %
@@
 machinery to extend the EGGs formalism. In fact, most of the results
-presented here for hyper-graphs can be generalised to hierarchical hyper-graphs, that is, 
+presented here for hypergraphs can be generalised to hierarchical hypergraphs, that is, 
 hypergraphs with a hierarchy (a partial order) among 
@@
 \todo{espandere un poco}
-Finally, we need to draw a comparison with an alternative categorical presentation for EGGs 
-advanced in~\cite{ghica}. The proposal is quite different from our own. Simplifying, the key is to equip categories 
+Despite their wide acceptance, we are not aware of any recent attempt to provide an algebraic characterisation of EGGs,
+the only exception being in~\cite{ghica}. We leave for future works also a in-depth comparison among the two proposals,
+which appear to be related yet nevertheless quite different.
+%
+The key intuition is always to use string diagrams to represents (acyclic) term graphs or, in other words,
+props over a symmetric monoidal category. In our case we adopted a more down-to-Earth approach by equipping
+concretely the nodes of a term graph with an equivalence relation, thus extending and generalising~\cite{concur2006} 
+in the contemporary jargon of adhesive categories.
+The route chosen in~\cite{ghica} is to consider as models symmetric monoidal categories enriched over semilattices,
+so that the
+
+Simplifying, the key is to equip categories 
 of trees with a lattice on hom-sets. 

### 2025-03-04 calco/main.tex

@@
 
-The previous lemma allows us to deduce the following results in an $\mathcal{M}$-adhesive context.
-\todo{A questo punto la proposizione seguente possiamo anche buttarla via se serve recuperare spazio}
+The previous result allows us to deduce the following lemma in an $\mathcal{M}$-adhesive context.
+
+%\todo{A questo punto la proposizione seguente possiamo anche buttarla via se serve recuperare spazio}
 \noindent
@@
 
-\noindent
-\parbox{7.5cm}{
-	\begin{restatable}{proposition}{mps}\label{prop:kerset}
-		Suppose that in $\Set$ the cube aside is given, whose top and bootom faces are pushout and such that $m\colon A\mto C$ and $m'\colon A'\mto C'4$ are injections.
-Then the right square, made by the kernel pairs of the vertical arrows is a pushout.
-\end{restatable}}\hfill 
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+%\todo{'sta cragna che segue è falsa come una moneta da 3 euro: cancellare}
+%\noindent
+%\parbox{7.5cm}{
+%	\begin{restatable}{proposition}{mps}\label{prop:kerset}
+%		Suppose that in $\Set$ the cube aside is given, whose top and bottom faces are pushout and such that $m\colon A\mto C$, $m'\colon A'\mto C'$ and $g\colon C\mto D$ are injections.
+Then the right square, made by the kernel pairs of the vertical arrows, is a pushout.
+%\end{restatable}}\hfill 
+%\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
 
@@
 	\end{center}
-
+%
 	\iffalse
@@
 
+	\begin{example}
+		Un controesempio:
+		Consideriamo i grafi senza edge e con nodi dati dal seguente cubo in cui le facce verticali sono pb e le due orizzontali sono po (tutte le frecce sono inclusioni)
+		\[
+	\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_2} \ar[dl]_{?_1} && 2 \ar[dd]^{\id{2}} \ar[dl]_{i_{2,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){i_{3,4}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_2} && 2 \ar[dl]^{j} \\2 \ar@{>->}[rr]_{j'} & & 4 }
+		\]
+
+		Qui abbiamo $j'(0)=2, j'(1)=3$ e  $i_{1,3}(0)=2$
+		Come quozienti consideriamo il seguente cubo
+
+		\[
+		\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_1} \ar[dl]_{?_1} && 1 \ar[dd]^{\id{1}} \ar[dl]_{i_{1,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){\id{3}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_1} && 1 \ar[dl]^{k} \\2 \ar@{>->}[rr]_{k'} & & 3 }
+		\]
+
+	\end{example}
+
 \end{proof}
+
+\begin{example}
+	Considet the following hypergaphs with equivalence:
+	\[\mathcal{G}:=(\emptyset, 2, 2, ?_{2}, ?_2, \id{2}) \quad \mathcal{H}:=(\emptyset, 1,1, ?_{1}, ?_1, \id{1}) \quad \mathcal{G}'=(\emptyset, 2, 1, ?_{2}, ?_{2}, !_{2}) \]
+
+There is a morphism $d:=(\id{\emptyset}, !_2, \id{1})\colon \mathcal{G}'\to \mathcal{H}$. We can then construct the cube aside, where the bottom face is a pushout and the vertical ones pullbacks.
+	\[
+\xymatrix@C=30pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'}  \\ 
+	\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}' \ar[dd]^(.3){d} \\
+	&\mathcal{G}\ar[rr]|\hole^(.3){({\emptyset, !_{2}, !_2})} \ar[dl]_{\id{\mathcal{G}}} && \mathcal{H} \ar[dl]^{\id{\mathcal{H}}}  \\
+	\mathcal{G} \ar[rr]_{({\emptyset, !_{2}, !_2})} & & \mathcal{H}  }
+\]\todo{sposta di lato}
+
+\todo{finisci}
+
+\end{example}
 
@@
 
+The category of $\Set$ enjoys two other remarkable and useful properties; it is \emph{distributive} and \emph{extensive}.
+Distributivity amount to the following property: for every family $\{X_i\}_{i}$ and an object $Y$, the unique morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms.
+\[\xymatrix@C=15pt@R=15pt{&Y\times X_i \ar@{>->}[dl]_{j_i} \ar@{>->}[dr]^{\id{Y}\times h_i} &&&X_i \times Y \ar@{>->}[dl]_{k_i} \ar@{>->}[dr]^{ h_i \times \id{Y}} \\ \Sum_{i\in I} Y\times X_i \ar@{.>}[rr]_{\phi}&& Y\times (\Sum_{i\in I}X_i) & \Sum_{i\in I}  X_i \times Y \ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \times Y }\]
+
+\noindent 
+\parbox{11.5cm}{\hspace{15pt} Extensivity means that given a family of objects $\{X_{i}\}_{i\in I}$ and a family of squares as the one on the right, where $j_i$ is a  coprojection, then all the squares are pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.}\hfill
+\parbox{2cm}{\xymatrix@R=15pt{Z_i \ar[r]_{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar@{>->}[r]^{j_i} & X}}
+
+These two property together yields the following fact.
+
+\begin{lemma}\label{lem:nodim}
+	Let $f,g\colon A\rightrightarrows B+C$ be two arrows with a coproduct as codomain. Then $(A, \{j_i\}_{i=0}^
+	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares.
+	\[\xymatrix@C=30pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
+		B\times B \ar@{>->}[r]_-{i_B\times i_B} & (B+C)\times (B+C) & B\times C \ar@{>->}[r]_-{i_B\times i_C} & (B+C)\times (B+C)}\]
+	\[ \xymatrix@C=30pt{A_2 \ar@{>->}[r]^{j_2}  \ar[d]_{p_2}& A   \ar[d]^{(f,g)}& A_3 \ar@{>->}[r]^{j_3}  \ar[d]_{p_3} & A \ar[d]^{(f,g)} \\
+		C\times B \ar@{>->}[r]_-{i_C\times i_B} & (B+C)\times (B+C) & C\times C \ar@{>->}[r]_-{i_C\times i_C} & (B+C)\times (B+C)}\]
+\end{lemma}
+
+\commentato{
 \noindent
@@
 \mps*}
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
+
+\begin{proof}
+		Let $E'\subseteq C'$ be the complement of the image of $m'$ and $\iota\colon E'\mto B'$ be the corresponding inclusion.
+By \Cref{lem:po_set} we know that $(D', \{n', g'\circ \iota\})$ is a coproduct.
+Thus by \Cref{lem:nodim} we also know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
+	\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
+	\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]
+
+	Now, if we compute we get
+	\begin{align*}
+		n\circ b\circ p_0&= d\circ n'\circ p_0= d\circ \pi^1_d\circ j_0=d\circ \pi^2_d\circ j_0=d\circ n'\circ q_0=n\circ b\circ q_0\\
+g\circ c \circ  \iota \circ p_3&=d\circ g' \circ  \iota p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota \circ q_3= g \circ c\circ \iota\circ q_3
+	\end{align*}
+	Thus, since $n$ and $g$ are mono we get the dotted arrows in the diagram below.
+\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota} \\ &K_b \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d}& B' \ar[d]^{b} & E' \ar[dr]_{\iota}&K_c \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]
+
+	Now, we also know that $(C', \{m', \iota\})$ is a coproduct, thus we can apply again \Cref{lem:nodim} to $K_c$ to conclude that $(K_c, \{k_i\}_{i=0}^4)$ is a coproduct, where $k_i\colon K^i_c\to K_c$ is defined by the following pullbacks.
+
+	\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
+	\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]
+
+	Let $u\colon K_b\to Z$ and $v\colon K_c\to Z$ be two arrows such that $u\circ k_{f'}=v\circ k_{m'}$.
+We want to construct an arrow $w\colon K_d\to Z$ such that $w\circ k_{g'}=v$ and $w\circ k_{n'}=u$.
+\end{proof}
+}
 

### 2025-03-04 calco/main.tex
varia

@@
 \noindent
-\begin{minipage}[l]{.78\linewidth }In short, following the double-pushout (DPO) approach
+\begin{minipage}[l]{.78\linewidth}In short, following the double-pushout (DPO) approach
 to graph transformation~\cite{xxx}, a rule is given by two arrows $: K \to L$ and $r: K \rightarrow R$
@@
 
+\noindent
+\begin{minipage}[l]{.73\linewidth}
 \begin{definition}
@@
 %
-We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes, so that $1^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, where $\delta_1$ picks the element $1$.
+We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, which always picks the element $1$.
 The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
@@
 This simply amount to a set of \emph{operations} with an associated natural number, called \emph{arity}.
-	For instance let $\Sigma_G$ be the signature of groups, then $\mathcal{G}^{\Sigma_G}$ can be depicted as
+	For instance let $\Sigma_G$ be the signature of groups, then $\mathcal{G}^{\Sigma_G}$ can be depicted as the picture aside.
 	\begin{center}
@@
 \begin{example}\label[example]{exa_3}
-	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the algebraic signature with $O_\Sigma =  \mathbb{N} \uplus A \uplus \{*, /\}$, 
-	let $n$ stands for any natural number and $a$ for any element in $A$, both sets interpreted as sets of constants, and
+	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the signature with $O_\Sigma =  \mathbb{N} \uplus A \uplus \{*, /\}$, 
+	where $n$ stands for any natural number and $a$ for any element in $A$, both sets of constants, and
 	%so that $\ari_\Sigma(n)=\ari_\Sigma(a) = 0$, 
-	$\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then the hypergraph $\mathcal{G}^\Sigma$ can be depicted as
-	\begin{center}
+	$\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then the hypergraph $\mathcal{G}^\Sigma$ is depicted as the picture aside.
+\end{example}
+\end{minipage}
+%\begin{center}
+\hfill
+\begin{minipage}[r]{.22\linewidth}
 \begin{tikzpicture}
@@
                 \node[style=none] (divout) at (0.2, -1.8){};
-
         \end{pgfonlayer}
@@
                 \draw[style=diredge, in=-30, out=0] (divout.center) to (v);
-
         \end{pgfonlayer}
-
 \end{tikzpicture}
-\end{center}
-\end{example}
+\end{minipage}
 
@@
 	If $f(h(1) = a$, $f(h_2) = 2$, $f(h_3) = *$, and $f(h_3) = /$, we represent it visually 
-	by putting the identifiers of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$
-	as
+	by putting the identifiers of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$,
+	and removing the idetifiers on the nodes and edges of the latter, as
 		\begin{center}
@@
 			\begin{pgfonlayer}{nodelayer}
-				\node[style=none] (lab1) at (-1.8, 0.8) {$h_1$};
+				\node[style=none] (lab1) at (-1.8, 0.8) {};
 				\node[style=small box] (h1) at (-1.8, 0.3) {$a$};
 				\node[style=small box] (2) at (-1.8, -0.5) {$2$};
-				\node[style=none] (lab2) at (-1.8, -1.0) {$h_2$};
+				\node[style=none] (lab2) at (-1.8, -1.0) {};
 				\node[style=none] (h1b) at (-1.8, 0.3) {};
@@
 				\node[style=none] (2c) at (-1.8, -0.5){};
-				\node[style=none] (lab3) at (0, 0.8) {$h_3$};
+				\node[style=none] (lab3) at (0, 0.8) {};
 				\node[style=medium box] (h2) at (0, 0) {$*$};
-				\node[style=none] (lab4) at (1.8, 0.5) {$h_4$};
+				\node[style=none] (lab4) at (1.8, 0.5) {};
 				\node[style=medium box] (h3) at (1.8, -0.3) {$/$};
-				\node[style=none](labv2) at (-0.9, -0.9) {$v_2$};
+				\node[style=none](labv2) at (-0.9, -0.9) {};
 				\node[style=node] (v2) at (-0.9, -0.5) {};
-				\node[style=none] (labv1) at (-0.9, 0.7) {$v_1$};
+				\node[style=none] (labv1) at (-0.9, 0.7) {};
 				\node[style=node] (v1) at (-0.9, 0.3) {};
-				\node[style=none] (labv3) at (0.9, 0.4) {$v_3$};
+				\node[style=none] (labv3) at (0.9, 0.4) {};
 				\node[style=node] (v3) at (0.9, 0) {};
-				\node[style=none] (labv4) at (2.7, 0.1) {$v_4$};
+				\node[style=none] (labv4) at (2.7, 0.1) {};
 				\node[style=node] (v4) at (2.7, -0.3) {};
@@
 
-Let us start with the case of general hypergraphs.
+Let us start with the case of general hypergraphs. These were introduced in~\cite{concur2006}, even if no general consideration about their structure as a category was proved, and adhesivity, 
+which is the main focus here, was yet to be presented to the world.
 
@@
 This is a standard result in term graph rewriting, see e.g.~\cite{xxx}, and it holds also in the setting with equivalences.
-I%
+%
 The same construction carries on when restricting to the full category of $\GEqTGs$ of those objects whose 
@@
 %
-The theory of $\mathcal{M},\mathcal{N}$-adhesivity carries on with such enriched rules, see e.g~\cite{xxx}.
-
-Summing up, showing that EGGs are objects of an $\mathcal{M},\mathcal{N}$-adhesive category $\GEqTGs$ and that optimisation 
-steps are obtained via DPO rules with negative application conditions with rules whose arrows are in $\mathcal{M}$ and via a match 
-that is in $\mathcal{N}$ allows for exploiting all the
+The theory of $\mathcal{M},\mathcal{N}$-adhesivity carries on with such extended rules, see e.g~\cite{xxx}.
 
@@
 we extended it in order to capture EGGS as term graphs satisfying a suitable closure property.
+Summing up, we proved that EGGs are objects of an $\mathcal{M},\mathcal{N}$-adhesive category $\GEqTGs$ 
+and that optimisation steps are obtained via DPO rules (possibly with negative application conditions) whose 
+arrows are in $\mathcal{M}$ and via a match that is in $\mathcal{N}$. This fact allows for exploiting all the properties 
+of the adhesive framework when discussing about the optimisation process.
 
@@
 \emph{Related works.}
-\todo{espandere un poco}
-Despite their wide acceptance, we are not aware of any recent attempt to provide an algebraic characterisation of EGGs,
-the only exception being in~\cite{ghica}. We leave for future works also a in-depth comparison among the two proposals,
-which appear to be related yet nevertheless quite different.
-%
-The key intuition is always to use string diagrams to represents (acyclic) term graphs or, in other words,
-props over a symmetric monoidal category. In our case we adopted a more down-to-Earth approach by equipping
-concretely the nodes of a term graph with an equivalence relation, thus extending and generalising~\cite{concur2006} 
-in the contemporary jargon of adhesive categories.
-The route chosen in~\cite{ghica} is to consider as models symmetric monoidal categories enriched over semilattices,
-so that the
-
-Simplifying, the key is to equip categories 
-of trees with a lattice on hom-sets. 
-It seems that such proposal generalises our own, 
-even if at the expenses of a more complex machinery.
-%Instead of going through 
-%such an enrichment, we chose to obtain closure via suitable requirements on morphisms, even if it 
-%seems that the former generalises the latter, at the expenses of a more complex machinery.
+%\todo{espandere un poco}
+Despite the interest they have ben raising as an efficient data structure, we are not aware of any attempt to provide an 
+algebraic characterisation of EGGs, the only exception being~\cite{ghica}. We leave for future work an in-depth comparison 
+among the two proposals, which appear to be related yet quite different.
+%
+In both cases, the key intuition is  to use string diagrams to represents (acyclic) term graphs. We adopted a
+more down-to-Earth approach by equipping
+concretely the nodes of a term graph with an equivalence relation, thus directly equivalent to the original presentation~\cite{DetlefsNS05},
+at the same time extending and generalising~\cite{concur2006} in the contemporary jargon of adhesive categories.
+The route chosen in~\cite{ghica} is to consider term graphs as arrows of a symmetric monoidal category,
+and equipping them with an enrichment over semilattices, the resulting formalism being reminiscent of hierarchical hypergraphs.
+Thus, the solution in~\cite{ghica}  is  more general than ours since it can be lifted to term graphs defined over categories other than
+$\Set$.
+%
+At the same time, we both consider the DPO approach for rewriting, even if only our solution guarantees that the resulting category
+is actually adhesive, thus allowing to exploit all the features of the framework.
 

### 2025-03-05 calco/main.tex
minima

@@
 
-\begin{proposition}\label[proposition]{lem:reg} Let $(i,j)$ be a mon between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$.
+\begin{proposition}\label[proposition]{lem:reg} Let $(i,j)$ be a mono between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$.
 Then it is a regular mono if and only if it preserves the input nodes.
@@
 \begin{restatable}{corollary}{mn}\label{cor:mono2}
-	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if $h_E, h_V$ and $h_C$ are all monos.
+	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
 \end{restatable}

### 2025-03-06 calco/main.tex
revised intro e conclusions

@@
 \begin{minipage}[l]{.78\linewidth}In short, following the double-pushout (DPO) approach
-to graph transformation~\cite{xxx}, a rule is given by two arrows $: K \to L$ and $r: K \rightarrow R$
+to graph transformation~\cite{xxx}, a rule is given by two arrows $l: K \to L$ and $r: K \rightarrow R$
 and its execution requires a match $m: L \to G$ such that the rewriting step from $G$
@@
 %
-The theory of $\mathcal{M}, \mathcal{N}$-adhesivity~\cite{xxx} extend the core framework, still ensuring that if the arrow 
-of the rules are in $\mathcal{M}$ and the match is in $\mathcal{N}$, then the classical results from the theory of graph 
+The theory of $\mathcal{M}$-adhesivity~\cite{xxx} extend the core framework, still ensuring that if the arrow 
+of the rules are in $\mathcal{M}$,
+%and the match is in $\mathcal{N}$, 
+then the classical results from the theory of graph 
 transformation can still be lifted~\cite{xxx}. 
-%
-However, despite the elegance and effectiveness and the obvious advantages of proving a category 
+If only the left-hand side belongs to $\mathcal{M}$, the current theory is stil under development, as witnessed e.g.
+by~\cite{BaldanC0G24}.
+%
+However, despite the elegance and effectiveness and the immediate advantages of proving a category 
 to be adhesive, proving that a given category satisfies the conditions 
@@
 framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, as well as for the extended one of
-$\mathcal{M}, \mathcal{N}$-adhesivity~\cite{CastelnovoGM24}.
+$\mathcal{M}$-adhesivity~\cite{CastelnovoGM24}.
+%
+For some graph-like structures, such as those called \emph{hypergraph with equivalence} in~\cite{concur2006}, the question 
+of their adhesivity has not yet been settled.
 
@@
 that is closed under the operators of the signature~\cite[Section~4.2]{DetlefsNS05}.
-In the presentation of term graphs via string diagrams~\cite{CastelnovoGM24}, EGGs are (hyper-)trees equipped with 
+In the presentation of term graphs via string diagrams~\cite{CastelnovoGM24}, EGGs are (hyper)trees equipped with 
 the possibility of sharing subtrees, as in terms graphs, with an additional equivalence relation $\equiv$ on nodes that 
@@
 
-Building on the criterion developed in~\cite{CastelnovoGM24}, the aim of this work is to prove that EGGs form an 
-$\mathcal{M}, \mathcal{N}$-adhesive category for a suitable choice of $\mathcal{M}$ and $\mathcal{N}$.
-The advantages derived from this characterisation are two-fold. On the one side, 
+Building on the criterion developed in~\cite{CastelnovoGM24}, this work proves that both hypergraphs with equivalence
+and EGGs form an 
+$\mathcal{M}$-adhesive category for a suitable choice of $\mathcal{M}$.
+The advantages from this characterisation are two-fold. On the one side, 
 we put the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
@@
 functorial characterisation, which allows for proving their adhesivity properties.
-This is expanded in Section~\ref{hypereq} for describing hypergraphs 
-and term graphs with equivalence and in Section~\ref{eggs} for capturing
-their variants where the equivalences are closed with respect to operator application,
+This is expanded in Section~\ref{hypereq} for proving the $\mathcal{M}$-adhesivity
+of hypergraphs 
+and term graphs with equivalence and in Section~\ref{eggs} of
+their variants where equivalences are closed with respect to operator application,
 thus subsuming EGGs.
 %
-In Section~\ref{rewriting} we put the former machinery at work, showing how the optimisation steps
+In Section~\ref{rewriting} we put the machinery at work, showing how the optimisation steps
 can be rephrased as the application of term graph rewriting rules.
@@
 possibly closed with respect to operator composition,
-can be described as a suitable $\mathcal{M},\mathcal{N}$-adhesive category. 
+can be described as a suitable $\mathcal{M}$-adhesive category. 
 The latter precisely capture EGGS, as originally
@@
 %
-In general, note that a maximally shared representation of an EGG exists, and for our 
-toy example is the left-most above. In general terms,
-for an EGG $\mathcal{G}$, such a canonical form is the final object of the comma category 
+In general, note that both a maximally minimally and a shared representation of an EGG exist, and for our 
+toy example are the left-most and the middle one above, respectively. In general terms,
+for an EGG $\mathcal{G}$, such canonical forms are the final and the initial objects of the comma category 
 $\mathcal{G}  \downarrow \GEqTGs$. 
-This is a standard result in term graph rewriting, see e.g.~\cite{xxx}, and it holds also in the setting with equivalences.
+The former part is a standard result in term graph rewriting, see e.g.~\cite{xxx}, while the latter is specific 
+of the setting with equivalences.
 %
 The same construction carries on when restricting to the full category of $\GEqTGs$ of those objects whose 
-underlying term graph is \emph{acyclic}, and in this case if $\mathcal{G}$ has no empty nodes, then the unique arrow 
-from $\mathcal{G}$ to the terminal object is easily shown to be injective on equivalence classes.
-
-What about rewriting? The theory of $\mathcal{M},\mathcal{N}$-adhesivity ensures that if the rules are spans of 
-arrows in $\mathcal{M}$ and the match is an arrow in $\mathcal{N}$, then we can lift all the standard properties
-of the DPO approach to the category at hand. Luckily, this is the structure of rules that is advanced in~\cite{DetlefsNS05},
-which is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity and the second
-component is a regular mono, simply adding the edges, nodes, and equivalence classes of interest.
-%
-An EGG rule such $x \div x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}, 
+underlying term graph is \emph{acyclic}.
+%and in this case if $\mathcal{G}$ has no empty nodes, then the unique arrow 
+%from $\mathcal{G}$ to the terminal object is easily shown to be injective on equivalence classes.
+
+What about rewriting? The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
+arrows in $\mathcal{M}$, then we can lift all the standard properties
+of the DPO approach to the category at hand. However, the structure of rules that is advanced in~\cite{DetlefsNS05},
+is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity, hence in $\mathcal{M}$,
+while the second component does not necessarily belong to $\mathcal{M}$. 
+%
+Consider e.g. an EGG rule such $x \div x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}, 
 can be modelled as the DPO rule below,
@@
 \[\mbox{to draw DPO rule, x in the same equivalence class} \]
-
-Note that if the starting term graph is acyclic, so is also the arriving one.
- An immediate drawback of choosing the identity as the left-hand side is the possibility to keep on repeating the same rewriting step.
+The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.
+Such an asymmetry between and left- and right-hand side falls in the research about left-linear rules for 
+adhesive categories that has 
+been pursued e.g. in~\cite{BaldanC0G24},
+
+Note also that for their nature, all the rules adopted for EGGs have the identity as the left-hand side. 
+Potentially, they thus belong to any choice of $\mathcal{M}$, even if the drawback is the 
+possibility to keep on repeating the same rewriting step.
 However, this is easily forbidden adopting rules \emph{with negative application conditions}~\cite{xxx}, which are given by the usual span 
@@
 %
-The theory of $\mathcal{M},\mathcal{N}$-adhesivity carries on with such extended rules, see e.g~\cite{xxx}.
+The theory of $\mathcal{M}$-adhesivity carries on with such rules, see e.g~\cite{xxx}.
 
@@
 we extended it in order to capture EGGS as term graphs satisfying a suitable closure property.
-Summing up, we proved that EGGs are objects of an $\mathcal{M},\mathcal{N}$-adhesive category $\GEqTGs$ 
+Summing up, we proved that EGGs are objects of an $\mathcal{M}$-adhesive category $\GEqTGs$ 
 and that optimisation steps are obtained via DPO rules (possibly with negative application conditions) whose 
-arrows are in $\mathcal{M}$ and via a match that is in $\mathcal{N}$. This fact allows for exploiting all the properties 
+left-hand side is in $\mathcal{M}$, and in fact an identity. 
+%and via a match that is in $\mathcal{N}$. 
+This fact allows for exploiting the properties 
 of the adhesive framework when discussing about the optimisation process.
@@
 \emph{Future works.}
-Our result on $\GEqTGs$ opens a few threads of research. The first is to check how the $\mathcal{M},\mathcal{N}$-adhesivity 
+Our result on $\GEqTGs$ opens a few threads of research. The first is to check how the $\mathcal{M}$-adhesivity 
 of EGGs can be pushed to model their rewriting via the double-pushout (DPO) approach. We have seen that 
-the rules adopted in the literature of EGGs appears to be span of regular monos (possibly with negative application 
-conditions), and as such they perfectly fit the mould of rewriting on $\mathcal{M}, \mathcal{N}$-adhesive categories. 
-The consequences for usability on the restriction of the matches to arrows that are injective on equivalence classes
-though need to be further investigated.
+the rules adopted in the literature of EGGs appears to be spans whose left-hand side is an identity and 
+right-hand side is a regular mono (possibly with negative application 
+conditions), and as such they fit the mould of rewriting on left-linear rewriting in $\mathcal{M}$-adhesive categories. 
+%The consequences for usability on the restriction of the matches to arrows that are injective on equivalence classes
+%though need to be further investigated.
 %
@@
 The route chosen in~\cite{ghica} is to consider term graphs as arrows of a symmetric monoidal category,
-and equipping them with an enrichment over semilattices, the resulting formalism being reminiscent of hierarchical hypergraphs.
+and equipping them with an enrichment over semi-lattices, the resulting formalism being reminiscent of hierarchical hypergraphs.
 Thus, the solution in~\cite{ghica}  is  more general than ours since it can be lifted to term graphs defined over categories other than

### 2025-03-10 calco/main.tex
minima

@@
 	Consider again $\Sigma$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled by a morphism
-	$f: \mathcal{G} \to \mathcal{G}^\Sigma$ that is characterised by the image of the edges. 
-	If $f(h(1) = a$, $f(h_2) = 2$, $f(h_3) = *$, and $f(h_3) = /$, we represent it visually 
+	$(l, !_{V_\mathcal{G}}): \mathcal{G} \to \mathcal{G}^\Sigma$ that is characterised by the image of the edges. 
+	If $l(h(1) = a$, $l(h_2) = 2$, $l(h_3) = *$, and $l(h_4) = /$, we represent it visually 
 	by putting the identifiers of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$,

### 2025-03-10 calco/main.tex

@@
 	\begin{example} 
+		We can consider the following four graphs with equivalence:
+		\[\begin{split}
+		\mathcal{G}_1&=(\emptyset, \emptyset, \emptyset, \id{\emptyset^\star}, \id{\emptyset^\star}, \id{\emptyset})\\
+		\mathcal{G}_3&=(\emptyset, 2, 2, ?_{2^\star}, ?_{2^\star}, \id{2})
+		\end{split} \qquad \begin{split}
+		\mathcal{G}_2&=(\emptyset, 2, 1, ?_{2^\star}, ?_{2^\star}, !_2)\\
+		\qquad \mathcal{G}_4&=(\emptyset, 4, 3, ?_{4^\star}, ?_{4^\star}, \pi)
+		\end{split}\]
+		where $\pi\colon 4\to 3$ is defined as
+		\[0\mapsto 0 \quad 1\mapsto 0 \quad 2\mapsto 1 \quad 3\mapsto 2 \]
+
+		Now, we have morphisms $h\colon \mathcal{G}_1\to \mathcal{G}_2$, $k\colon \mathcal{G}_1\to \mathcal{G}_3$, $z\colon \mathcal{G}_2\to \mathcal{G}_4$, $p\colon \mathcal{G}_3\to \mathcal{G}_4$ defined as:
+		\[
+		h:=(\id{\emptyset}, ?_2, ?_1)\quad k:=(\id{\emptyset}, ?_2, ?_2)
+		\quad 
+		z:=(\id{\emptyset}, j, z_Q)\quad p:=(\id{\emptyset}, j', p_Q)
+		\]
+		where 
+		\[\begin{matrix}
+			j\colon 2\to 4 & \begin{matrix}
+			0\mapsto 0\\
+			1  \mapsto 1
+			\end{matrix} & z_Q\colon 1\to 3 &0\mapsto 0 & j'\colon 2\to 4 &\begin{matrix}0 \mapsto 2\\
+			1 \mapsto 3
+			\end{matrix} & p_Q\colon 2\to 3  &\begin{matrix}
+		0\mapsto 1\\
+		1\mapsto 2
+			\end{matrix}
+		\end{matrix} \]
+
+		Notice that  $\pi\circ j=z_Q$ and$\pi\circ j'=p_Q$  Thus in this way $(\mathcal{G}_4, \{z, p\})$ becomes a pushout for $h$ along $k$.
+
+		Let now $a$
+
 		Un controesempio:

### 2025-03-10 calco/main.tex
strazio di conti

@@
 \newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
+
+\newcommand{\pbc}{\mathsf{Pb}}
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
@@
 \begin{restatable}{proposition}{regmono}\label{prop:regmono}
-	Let $\X$ be an $\mathcal{M}$-adhesive categoru. Then it holds
+	Let $\X$ be an $\mathcal{M}$-adhesive category. Then it holds
 	\begin{enumerate}
@@
 
-\todo{Inserire bla bla}
-
-%\todo{'sta cragna che segue è falsa come una moneta da 3 euro: cancellare}
-%\noindent
-%\parbox{7.5cm}{
-%	\begin{restatable}{proposition}{mps}\label{prop:kerset}
-%		Suppose that in $\Set$ the cube aside is given, whose top and bottom faces are pushout and such that $m\colon A\mto C$, $m'\colon A'\mto C'$ and $g\colon C\mto D$ are injections.
-Then the right square, made by the kernel pairs of the vertical arrows, is a pushout.
-%\end{restatable}}\hfill 
-%\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
+Focusing on $\Set$, we can prove a sharper result (see \Cref{proof:kerset} for the proof).
+
+\noindent
+\parbox{7.5cm}{\begin{restatable}{lemma}{mps}\label{prop:kerset}
+	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top and bottom faces are pushout, the left face a pulllback and such that $m\colon A\mto C$ is an injection.
+Then the following are true:
+	\parbox{14cm}{\begin{enumerate}
+		\item the right face of the cube is a pullback too;
+		\item the right square, made by the kernel pairs of the vertical arrows, is a pushout.
+	\end{enumerate}}
+\end{restatable}}\hfill 
+\parbox{6cm}{\vspace{-1.1cm}\xymatrix@C=10pt@R=5pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
 
@@
 \end{proposition}
+\commentato{
 \begin{proof}
 	This follows noticing that $\Delta_{\Sigma}(X)$ is a term graph for every object $X$.
-\end{proof}
-
-We can list some categorical properties of $\tg$
+\end{proof}}
+
+We can list some other categorical properties of $\tg$.
 
@@
 	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
-\end{restatable}
-
-\iffalse 
-\begin{proposition}
-	Let $h = (h_E, h_V, h_C): \mathcal{G \to H}$ be a regular mono in $\EqHyp$.
-	Then, $h_E$ and $h_V$ are monos and $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{H}\circ h_V$ if and only if $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$.
-\end{proposition}
-
-\begin{proof}
-	By \Cref{cor:mono2}, we have that $h_E, h_V$ and $h_C$ are all monos.
-	Hence, by \Cref{cor:kermono}, $(K, \pi_1, \pi_2)$ is the kernel pair of $q_\mathcal{G}$ if and only if it is the kernel pair also of $h_C \circ q_\mathcal{G}$, since $h_C$ is mono by hypothesis.
-	The thesis follows from $h_C \circ q_\mathcal{G} = q_H \circ h_V$, and from the hypothesis of $h_E$ mono.
-\end{proof}
-
-\begin{remark}
-	It is possible to restate the last proposition, by \Cref{ex:kernel_pairs_in_Set}, as 
-	\begin{displayquote}
-		\textit{$h_E$ and $h_V$ are mono and, for every $v, v'\in V_H$, $q_H(h_V(v))=q_H(h_V(v'))$ if and only if $q_G(v)=q_G(v')$}
-	\end{displayquote}
-	That is, a regular mono in $\EqHyp$ is a morphism that both reflects and preserves equivalences.
-	% besides preserving them.
-\end{remark}
-\fi
+\end{restatable}\todo{manca ancora la dimostrazione dell'implicazione da destra a sinistra}
 
@@
 
-We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$. In particular, we are now going to show that $\EqHyp$ is $\reg(\EqHyp)$-adhesive.
+We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class $\mathcal{M}$ of monos.
+
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{restatable}{lemma}{pbm}\label{lem:pbmono}
+	The class $\pbc$ is closed under composition, decomposition and it is stable under pullbacks and pushouts
+\end{restatable}
+
+In particular, we are now going to show that $\EqHyp$ is $\reg(\EqHyp)$-adhesive.
 
@@
 
-These two property together yields the following fact.
+\noindent
+\parbox{11cm}{
+\begin{remark}\label{rem:disj}
+	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~ that the pullback between two coproduct injections is given by the initial object (with initial maps ad coprojections).
+To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and let $k$ be an element of $I$.
+Then  $(X_k, \{t_i\}_{i\in I})$ with
+	\[t_i=\begin{cases}
+		\id{X_k} & i=k\\?_{X_k} & i\neq k
+	\end{cases}\]
+	is a coproduct and so the squares on the right are pullbacks.
+\end{remark}}\hfill\parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}
+
+In particular, the previous remark yields at once the following fact.
+
+\noindent 
+\parbox{11.5cm}{\begin{proposition}\label{prop:isempty}
+	Suppose that the square on the right is a pullback.
+Let $\iota \colon E\mto Y$ be the inclusion of the complement of the image of $p_1$.
+If there exist two  arrows $t_1\colon T\to E$ and $t_2\colon T\to X$ such that \[g\circ \iota\circ t_1= f\circ t_2\] then $T$ is empty.
+\end{proposition}}\hfill \parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
+\begin{proof}
+	By the universal property of pullbacks we get an arrow $t\colon T\to P$ such that 
+	\[p_1\circ t=\iota \circ t_1 \qquad p_2\circ t=t_2\]
+	\parbox{2cm}{\xymatrix{T \ar@{.>}[r]^{s}\ar@{>>}[dr]_{\pi} \ar@/^.4cm/[rr]^{t_1} & \emptyset \ar@{>->}[r]_{?_{E}} \ar@{>->}[d]_{?_I}& E \ar@{>->}[d]^{\iota}\\ & I \ar@{>->}[r]_{i} & Y}}\hfill \parbox{10.5cm}{Let $i\colon I\mto Y$ be the inclusion of the image of $p_1$, so that we have also an epi $q\colon P\eto I$.
+By definition of complement $(Y, \{i, \iota\})$ is a coproduct, thus by  \Cref{rem:disj} the inner square in the diagram on the left is a pullback and we get a dotted arrow $s\colon T\to \emptyset$ filling the diagram.
+But a set with an arrow towards the empty set must be empty and we conclude.
+\qedhere }
+\end{proof}
+
+Extensivity and distributivity, moreover, yield the following fact.
 
@@
 
-\commentato{
-\noindent
-\parbox{7.5cm}{
-\mps*}
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
-
-\begin{proof}
-		Let $E'\subseteq C'$ be the complement of the image of $m'$ and $\iota\colon E'\mto B'$ be the corresponding inclusion.
-By \Cref{lem:po_set} we know that $(D', \{n', g'\circ \iota\})$ is a coproduct.
-Thus by \Cref{lem:nodim} we also know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
+We are now ready to exploit the previous propertis to prove \Cref{prop:kerset}, as promised.
+
+\noindent
+\parbox{7.5cm}{\mps*}\hfill
+\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{->}[rr]_{g} & & D }}
+
+\begin{proof}\label{proof:kerset}
+	We can start noticing that $m'$, being the pullback of $m$ is mono too.
+This, in turn, entails that $n$ and $n'$ are mono too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.
+
+	\noindent 
+	\parbox{11.5cm}{\hspace{15pt}
+	Let $\iota' \colon E'\mto C'$ and $\iota\colon E\to C$ be the inclusions of the complement of the images of of $m'$ and $m$ respectively .
+By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ and $(D, \{n, g\circ \iota\})$ are coproducts.
+We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]_{\iota} & C}}
+
+	\noindent
+	\parbox{10.5cm}{\hspace{15pt}To see this, let $e$ be in $E'$ and suppose that  $c(\iota'(e))=m(x)$ for some $x\in A$.
+Then we can apply the  universal property of pullbacks to build the dotted arrow in the diagram aside, where $v_0$ and $v_1$ are the arrows picking $x$ and $\iota'(e)$, respectively.
+But then $e$ must belong to the image of $m'$, which is a contradiction.}\hfill  \parbox{4cm}{\xymatrix@R=15pt{1 \ar[dr]_{v_0}  \ar@/^.3cm/[rr]^{v_1} \ar@{.>}[r]_{v}& A' \ar[d]_{a} \ar@{>->}[r]_{m'} & C' \ar[d]^{c}\\& A  \ar@{>->}[r]^{m}& C}}
+
+	\begin{enumerate}
+		\item Consider two arrows $t_1\colon T\to D' $ and $t_2\colon T\to B$ such that $d\circ t_1=n\circ t_2$. By extensivity
+
+		\noindent\parbox{9.5cm}{ of $\Set$, we already know that $(T, \{l_i\}_{i=0}^1)$ is a coproduct, where $l_i\colon T_i\mto T$ are defined by the diagram aside, whose two halves are pullbacks aside.
+}\hfill\parbox{4cm}{\xymatrix@R=15pt{T_0 \ar@{>->}[r]_{l_0} \ar[d]_{h_0} & T \ar[d]^{t_1} & T_1 \ar@{>->}[l]^{l_1} \ar[d]^{h_1}\\ E' \ar@{>->}[r]^{g'\circ \iota'} & D' & B' \ar@{>->}[l]_{n'}}}
+
+		If we compute we get
+		\[g\circ c \circ \iota' \circ h_0=d\circ g'\circ \iota' \circ h_0=d\circ t_1\circ l_0=n\circ t_2\circ l_0\]
+
+		By adhesivity of $\Set$ and \Cref{prop:regmono} the bottom face of the given cube is a pullback, therefore there exists an arrow $u\colon T_0\to A$ such that 
+		\[f\circ u=b\circ t_2\circ l_0 \qquad m\circ u=c\circ \iota'\circ h_0\]
+
+	By \Cref{prop:isempty} we conclude that $T_0$ is empty. Therefore $l_1$ is an isomorphism and we have $n'\circ h_1\circ l^{-1}_1=t_1$. On the other hand
+\[n\circ b\circ h_1\circ l^{-1}_1=d\circ n'\circ h_1\circ l^{-1}_1=d\circ t_1=n\circ t_2\]
+And we can conclude that $b\circ \circ h_1\circ l^{-1}_1=t_2$ because $n$ is a mono. The thesis now follows from the fact that  also $n'$ is mono.
+
+		\item  By \Cref{lem:nodim} we know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
 		\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
-		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
+			B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota')} & D'\times D'}\]
 		\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
-		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]
+			E'\times B' \ar@{>->}[r]_-{(g'\circ \iota') \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D'}\]
 
@@
 	n\circ b\circ p_0&= d\circ n'\circ p_0= d\circ \pi^1_d\circ j_0=d\circ \pi^2_d\circ j_0=d\circ n'\circ q_0=n\circ b\circ q_0\\
-g\circ c \circ  \iota \circ p_3&=d\circ g' \circ  \iota p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota \circ q_3= g \circ c\circ \iota\circ q_3
+	g\circ c \circ  \iota' \circ p_3&=d\circ g' \circ  \iota' p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota' \circ q_3= g \circ c\circ \iota'\circ q_3
 \end{align*}
 Thus, since $n$ and $g$ are mono we get the dotted arrows in the diagram below.
-\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota} \\ &K_b \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d}& B' \ar[d]^{b} & E' \ar[dr]_{\iota}&K_c \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]
-
-	Now, we also know that $(C', \{m', \iota\})$ is a coproduct, thus we can apply again \Cref{lem:nodim} to $K_c$ to conclude that $(K_c, \{k_i\}_{i=0}^4)$ is a coproduct, where $k_i\colon K^i_c\to K_c$ is defined by the following pullbacks.
-
-	\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
-		B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota)} & D'\times D'}\]
-	\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
-		E'\times B' \ar@{>->}[r]_-{(g'\circ \iota) \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota)\times (g'\circ \iota)} & D'\times D'}\]
-
-	Let $u\colon K_b\to Z$ and $v\colon K_c\to Z$ be two arrows such that $u\circ k_{f'}=v\circ k_{m'}$.
-We want to construct an arrow $w\colon K_d\to Z$ such that $w\circ k_{g'}=v$ and $w\circ k_{n'}=u$.
+\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\ &K_b \ar[r]^{\pi^1_b} \ar[d]_{\pi^2_b}& B' \ar[d]^{b} & E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]
+
+Notice, moreover, that 
+\[(\pi^1_d, \pi^2_d)\circ k_{g'}\circ \phi_3=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ \phi_3=(g'\times g')\circ (\iota'\circ p_3, \iota'\circ q_3)\]
+and so $k_{g'}\circ \phi_3=j_3$.
+
+Now, we also have
+\begin{align*}
+	n\circ b\circ p_1&=d\circ n'\circ p_1=d\circ \pi^1_d\circ j_1=d\circ \pi^2_d\circ j_1=d\circ g'\circ \iota'\circ q_1\\
+	n\circ b\circ q_2 &=d\circ n'\circ p_2=d\circ\pi^2_D\circ j_2
+	=d\circ \pi^1_d\circ j_2=d\circ g'\circ \iota'\circ p_2
+\end{align*}
+
+			Since the bottom face of the original cube is a pullback (again by \Cref{prop:regmono}), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
+			\[m\circ k_1=\iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=\iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]
+
+			By \Cref{prop:isempty} we conclude that $K_1$ and $K_2$
+ are both empty. In particular, we can also deduce that $(K_d, \{j_0, j_3\})$ is a coproduct.
+
+ 	\smallskip
+ \parbox{7.5cm}{We can go further. The outer part of the diagram on the right commutes, so that we have the dotted $\psi_0\circ K_b\to K_0$.
+ Now, on the one hand $\phi_0\circ \psi_0=\id{K_b}$ because if we compute we get:
+  \[(\pi^1_b, \pi^2_b)\circ \phi_0\circ \psi_0=(p_0, q_0)\circ \psi_0=(\pi^1_b, \pi^2_b)\]}\hfill \parbox{4cm}{\vspace{-.5cm}\xymatrix{K_b \ar[dr]_{(\pi^1_b, \pi^2_b)}  \ar@{>->}@/^.4cm/[rr]^{k_{n'}} \ar@{.>}[r]_{\psi_0}& K_0 \ar@{>->}[r]_{j_0}  \ar[d]^{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+ 	& B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' }
+ 	}
+
+ On the other hand, notice that 
+ \[\pi^1_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^1_b\circ \phi_0=n'\circ p_0=\pi^1_d\circ j_0 \qquad \pi^2_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^2_b\circ \phi_0=n'\circ p_0=\pi^2_d\circ j_0\]
+
+ Thus $k_{n'}\circ \phi_0=j_0$ and we have
+ \[(p_0, q_0)\circ \psi_0\circ \phi_0=(\pi^1_b, \pi^2_b)\circ \phi_0=(p_0, q_0)= \quad  j_0\circ \psi_0\circ \phi_0 = k_{n'}\circ \phi_0=j_0\]
+We can conclude that $\phi_0$ is an isomorphism and that $k_{n'}$ is a coproduct injection.
+
+ Furthermore, by definition of complement, $(C', \{\iota', m'\})$ is a coproduct. Applying again \Cref{lem:nodim} we can decompose $K_c$ in four parts, given by the pullbacks below:
+ \[\xymatrix@C=45pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
+ 	A'\times A' \ar@{>->}[r]_-{m'\times m'} & C'\times C' & A'\times E' \ar@{>->}[r]_-{m'\times  \iota'} & C'\times C'}\]
+ \[ \xymatrix@C=45pt{H_2 \ar@{>->}[r]^{x_2}  \ar[d]_{(y_2, z_2)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_3 \ar@{>->}[r]^{x_3}  \ar[d]_{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
+ 	E'\times A' \ar@{>->}[r]_-{\iota' \times m'} & C'\times C' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
+
+ Now, notice that
+ \small
+ \[\begin{split}
+(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_1&=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_1\\=&(g'\times g')\circ (m'\times \iota')\circ (y_1, z_1)\\=&((g'\circ m') \times (g'\circ \iota'))\circ (y_1, z_1)\\=&((n'\circ f') \times (g'\circ \iota'))\circ (y_1, z_1)\\=&(n'\times  (g'\circ \iota'))\circ (f'\circ y_1, z_1)
+ \end{split} \hspace{1pt} \begin{split}
+ (\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_2&=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_2\\=&(g'\times g')\circ ( \iota' \times m')\circ (y_2, z_2)\\=&((g'\circ \iota') \times (g'\circ m'))\circ (y_2, z_2)\\=&( (g'\circ \iota') \times (n'\circ f'))\circ (y_2, z_2)\\=&((g'\circ \iota') \times n')\circ (y_2, f'\circ z_2)
+ \end{split} \]
+\normalsize
+ thus we have arrows $h_1\colon H_1\to K_1$ and $h_2\colon H_2\to K_2$, showing that $H_1$ and $H_2$ are empty. On the other hand, let us consider the two diagrams below.
+
+ \[ \xymatrix@C=45pt{ H_3 \ar@{.>}[d]^{\alpha_3} \ar[r]^{x_3} \ar@/_.4cm/[dd]_{(y_3, z_3)} & K_c \ar[d]_{k_{g'}}& K_3 \ar@{.>}[d]^{\beta_3} \ar@/^.3cm$ $/[dr]^{\phi_3} \ar@/_.4cm/[dd]_{(p_3, q_3)}\\K_3 \ar@{>->}[r]^{j_3}  \ar[d]^{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} &  H_3 \ar@{>->}[r]^{x_3}  \ar[d]^{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)}  \\
+   E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
+ Their solid part commute, indeed we have:
+ \[\begin{split}
+ 	(\pi^1_d, \pi^2_d\circ k_{g'})\circ x_3&=(g'\times g')\circ (\pi^1_c, \pi^2_c) \circ x_3\\=&(g'\times g')\circ (\iota'\times \iota')\circ (y_3\times z_3)\\=&(g'\circ \iota') \times (g'\circ \iota')\circ (y_3, z_3)
+ \end{split}\qquad \begin{split}
+ (\pi^1_c, \pi^2_c)\circ \phi_3=&(\iota'\circ p_3, \iota' \circ q_3)\\=&
+(\iota'\times \iota')\circ (p_3, q_3)\\& \end{split}\]
+
+Thus we get the dotted arrows $\alpha_3$ and $\beta_3$. Now, they are one the inverse of the other. Indeed on the one hand we have:
+\begin{align*}
+j_3\circ \alpha_3\circ \beta_3&=k_{g'}\circ x_3\circ \beta_3=k_{g'} \circ \phi_3=\phi_3 \\
+(p_3, q_3)\circ \alpha_3\circ \beta_3&=(y_3, z_3)\circ \beta_3=(p_3, q_3) 
+\end{align*}
+ On the other, notice that
+ \[(\pi^1_c, \pi^2_c)\circ \phi_3\circ \alpha_3 =(\iota'\times \iota')\circ (p_3, q_3)\circ \alpha_3= (\iota'\times \iota')\circ (y_3, z_3)=(\pi^1_c, \pi^2_c)\circ x_3\]
+ Therefore $\phi_3\circ \alpha_3=x_3$ and thus $x_3\circ \beta_3\circ \alpha_3=x_3$. Moreover:
+ \[(y_3, z_3)\circ \beta_3\circ \alpha_3=(p_3, q_3\circ \alpha_3)=(y_3, z_3)\]
+
+ Summing up, we have just proved that $(K_c, \{x_0, \phi_3\})$ is a coproduct.
+
+ Let now $\gamma\colon K_b\to Z$ and $\delta\colon K_c\to Z$ be two arrows such that $\gamma\circ k_{f'}=\delta\circ k_{m'}$.
+We want to construct an arrow $\theta\colon K_d\to Z$ such that $\theta\circ k_{g'}=\delta$ and $\theta\circ k_{n'}=\gamma$.
+
+ Now, we have already proved that $(K_d, \{k'_n, j_3\})$ is a coproduct, thus there is a unique arrow $\theta\colon K_d\to Z$ such that 
+ \[\theta \circ k'_n=\gamma \qquad \theta \circ j_3=\delta \circ \phi_3 \]
+ Now, on the one hand we have
+ \begin{align*}
+ 	\theta \circ k_{g'}\circ \phi_3=\theta \circ  j_3=\delta\circ \phi_3 
+ \end{align*}
+
+ On the other hand, 
+ \[(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_0=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_0=(g'\times g')\times (m'\times m')\circ (y_0, x_0)=(n'\circ n')\ (f')\]
+
+			 \qedhere 
+	\end{enumerate}
 \end{proof}
-}
 

### 2025-03-11 calco/main.tex
lemma

@@
 	%
-	If the leftmost square is commutative, then there is a a unique arrow $k_h: K_f \to K_g$ making the other two commutative
-	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]
-
-		Moreover, it holds
+	If the leftmost square is commutative, then there is a a unique arrow $k_h\colon K_f \to K_g$ making the other three commutative.
+	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}& K_f  \ar@{.>}[r]^{k_h} \ar[d]_{(\pi^1_f,\pi^2_f)} & K_g \ar[d]^{(\pi^1_g, \pi^2_g)}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z & X\times X \ar[r]_{h\times h}& X\times Z}\]
+
+		Moreover, the following hold true:
 		\begin{enumerate}
-			\item if the leftmost square is a pullback, then also the other two are so;
-			\item if $h$ is mono then $k_h$ is mono too.
+			\item if $h$ is mono then $k_h$ is mono too;
+			\item if the leftmost square is a pullback, then also the central too are so;
+			\item if $h$ is mono and the first square is a pullback then the last one is a pullback too.
 		\end{enumerate} 
@@
 
+\end{proof}
+
 \begin{example}
-		We can consider the following four graphs with equivalence:
-		\[\begin{split}
-		\mathcal{G}_1&=(\emptyset, \emptyset, \emptyset, \id{\emptyset^\star}, \id{\emptyset^\star}, \id{\emptyset})\\
-		\mathcal{G}_3&=(\emptyset, 2, 2, ?_{2^\star}, ?_{2^\star}, \id{2})
-		\end{split} \qquad \begin{split}
-		\mathcal{G}_2&=(\emptyset, 2, 1, ?_{2^\star}, ?_{2^\star}, !_2)\\
-		\qquad \mathcal{G}_4&=(\emptyset, 4, 3, ?_{4^\star}, ?_{4^\star}, \pi)
-		\end{split}\]
-		where $\pi\colon 4\to 3$ is defined as
-		\[0\mapsto 0 \quad 1\mapsto 0 \quad 2\mapsto 1 \quad 3\mapsto 2 \]
-
-		Now, we have morphisms $h\colon \mathcal{G}_1\to \mathcal{G}_2$, $k\colon \mathcal{G}_1\to \mathcal{G}_3$, $z\colon \mathcal{G}_2\to \mathcal{G}_4$, $p\colon \mathcal{G}_3\to \mathcal{G}_4$ defined as:
-		\[
-		h:=(\id{\emptyset}, ?_2, ?_1)\quad k:=(\id{\emptyset}, ?_2, ?_2)
-		\quad 
-		z:=(\id{\emptyset}, j, z_Q)\quad p:=(\id{\emptyset}, j', p_Q)
-		\]
-		where 
-		\[\begin{matrix}
-			j\colon 2\to 4 & \begin{matrix}
-			0\mapsto 0\\
-			1  \mapsto 1
-			\end{matrix} & z_Q\colon 1\to 3 &0\mapsto 0 & j'\colon 2\to 4 &\begin{matrix}0 \mapsto 2\\
-			1 \mapsto 3
-			\end{matrix} & p_Q\colon 2\to 3  &\begin{matrix}
-		0\mapsto 1\\
-		1\mapsto 2
-			\end{matrix}
-		\end{matrix} \]
-
-		Notice that  $\pi\circ j=z_Q$ and$\pi\circ j'=p_Q$  Thus in this way $(\mathcal{G}_4, \{z, p\})$ becomes a pushout for $h$ along $k$.
-
-		Let now $a$
-
-		Un controesempio:
-		Consideriamo i grafi senza edge e con nodi dati dal seguente cubo in cui le facce verticali sono pb e le due orizzontali sono po (tutte le frecce sono inclusioni)
-		\[
-	\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_2} \ar[dl]_{?_1} && 2 \ar[dd]^{\id{2}} \ar[dl]_{i_{2,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){i_{3,4}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_2} && 2 \ar[dl]^{j} \\2 \ar@{>->}[rr]_{j'} & & 4 }
-		\]
-
-		Qui abbiamo $j'(0)=2, j'(1)=3$ e  $i_{1,3}(0)=2$
-		Come quozienti consideriamo il seguente cubo
-
-		\[
-		\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_1} \ar[dl]_{?_1} && 1 \ar[dd]^{\id{1}} \ar[dl]_{i_{1,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){\id{3}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_1} && 1 \ar[dl]^{k} \\2 \ar@{>->}[rr]_{k'} & & 3 }
-		\]
-
-	\end{example}
-
-\end{proof}
-
-\begin{example}
-	Considet the following hypergaphs with equivalence:
-	\[\mathcal{G}:=(\emptyset, 2, 2, ?_{2}, ?_2, \id{2}) \quad \mathcal{H}:=(\emptyset, 1,1, ?_{1}, ?_1, \id{1}) \quad \mathcal{G}'=(\emptyset, 2, 1, ?_{2}, ?_{2}, !_{2}) \]
-
-There is a morphism $d:=(\id{\emptyset}, !_2, \id{1})\colon \mathcal{G}'\to \mathcal{H}$. We can then construct the cube aside, where the bottom face is a pushout and the vertical ones pullbacks.
-	\[
-\xymatrix@C=30pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'}  \\ 
-	\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}' \ar[dd]^(.3){d} \\
-	&\mathcal{G}\ar[rr]|\hole^(.3){({\emptyset, !_{2}, !_2})} \ar[dl]_{\id{\mathcal{G}}} && \mathcal{H} \ar[dl]^{\id{\mathcal{H}}}  \\
-	\mathcal{G} \ar[rr]_{({\emptyset, !_{2}, !_2})} & & \mathcal{H}  }
-\]\todo{sposta di lato}
-
-\todo{finisci}
-
+
+	\todo{Qua va l'esempio di Fabio}
 \end{example}
@@
 \kpp*
-\begin{proof}\label{kpp-proof}
-Computing, we have
+\begin{proof}\label{kpp-proof}\begin{enumerate}
+		\item Let $a,b\colon T\rightrightarrows K_f$ be two arrows such that $k_h\circ a=k_h\circ b$, then we have
+\begin{align*}h\circ \pi^1_f\circ a&=\pi^1_g\circ k_h\circ a=\pi^1_g\circ k_h\circ b=h\circ \pi^1_f\circ b\\
+	h\circ \pi^2_f\circ a&=\pi^2_g\circ k_h\circ a=\pi^2_g\circ k_h\circ b=h\circ \pi^2_f\circ b
+\end{align*}
+Since $h$ is mono this entails that
+\[pi^1_f\circ a=pi^1_f\circ b \qquad pi^2_f\circ a=\pi^2_f\circ b\]
+and thus $a$ must coincide with $b$.
+
+ 		\item  We begin by computing to get:
 		\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]
-
-Therefore the existence  and uniqueness of the wanted $k_h$ follows at once from the the universal property of $K_g$ as the pullback of $g$ along itself.
+		so that  existence  and uniqueness of the wanted $k_h$ follow at once from the the universal property of $K_g$ as the pullback of $g$ along itself.
 
 		To prove the second half of the thesis, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
-\[\xymatrix{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
+		\[\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
 			X \ar[r]_{f}& Y \ar[r]_{t} & W & X \ar[r]_{f} & Y  \ar[r]_{t}& W}\]
@@
 		But then the following ones are pullbacks too.
-\[\xymatrix{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
-	X \ar[r]_{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]_{g} & W & X \ar[r]_{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]_{g} & W}\]
-
-The thesis now follows again by \Cref{lem:pb1}.   
+		\[\xymatrix@R=15pt{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
+			X \ar[r]^{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]^{g} & W & X \ar[r]^{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]^{g} & W}\]
+
+		Thus the left halves of the rectangle above are pullbacks again by \Cref{lem:pb1}.
+
+		\item 		For the last square, let $(t_1, t_2)\colon T\to X\times X$ and $s\colon T\to K_g$ be two arrows such that
+		\[(\pi^1_g, \pi^2_g)\circ s=(h\times h)\circ (t_1, t_2)\]
+
+		Thus there exist two arrows $x, y\colon T\rightrightarrows K_f$ fitting in the diagrams below.
+		\[\xymatrix@R=15pt{T\ar@{.>}[r]_-{x} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_1}& K_f \ar@{->}[r]_{k_h} \ar[d]_{\pi^1_f} & K_g \ar[d]^{\pi^1_g} & T \ar@{.>}[r]_-{y} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_2} & K_f  \ar@{->}[r]_{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ & X \ar@{>->}[r]_{h} & Y &&X \ar@{>->}[r]_{h}& Y} \]
+		By the first point $k_h$ is mono, thus we can deduce that $x=y$. By construction we have
+		\[(\pi^1_f, \pi^2_f)\circ x=(t_1, t_2) \qquad k_h\circ x=s\]
+
+		Uniqueness follows now at once again from the fact that $k_h$ is mono.
+		\qedhere
+
+	\end{enumerate}
+
 \end{proof}
@@
 
+\noindent 
+		\parbox{11.7cm}{
 \begin{lemma}\label{lem:po_set}
-	The following are true:
-	\begin{enumerate}
-		\item if $(P, \{p_i\}_{i\in I})$ is a coproduct, then for every arrow $f\colon 1\to P$ there is exactly one $k\in I$ and $f_k\colon 1\to P_k$ such that $f=p_k\circ f_k$;
-
-		\parbox{11cm}{
-		\item suppose that the square on the right is a pushout and let $\iota_{m}\colon E\mto B$ be the inclusion of the complement of the image of $m$, then $(D, \{n, h\circ \iota_m \})$ is a coproduct; in particular, $h\circ \iota_f$ is mono.}\hfill \parbox{2cm}{\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
-	\end{enumerate}
-\end{lemma}
+Suppose that the square aside is a pushout, with $m\colon A\mto B$ an injection.
+Let $\iota_{m}\colon E\mto B$ be the inclusion of the complement of the image of $m$.
+Then $(D, \{n, h\circ \iota_m \})$ is a coproduct.
+In particular, $h\circ \iota_m$ is mono.
+\end{lemma}}\hfill \parbox{2cm}{\vspace{0cm}\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
 \begin{proof}
-	\begin{enumerate}
-		\item This is obvious.
-		\item Let $f\colon E\to Z$ and $k\colon C\to Z$ be two arrows with the same codomain.
-.
+		 Let $f\colon E\to Z$ and $k\colon C\to Z$ be two arrows with the same codomain.
 By definition of complement and since $m$ is mono we know that $(B, \{m, \iota_m\})$ is a coproduct.
 Define $\phi\colon B\to Z$ as the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\]
-		By construction there is a unique arrow $\psi \circ D\to Z$ such that 
-		\[\psi \circ n=k \qquad \psi \circ h=\phi \]
-		But this entails that 
+		By construction there is a unique arrow $\psi \colon D\to Z$ such that $\psi \circ n=k$ and $\psi \circ h=\phi$, thus 
 		\[
@@
 
-		On the other hand, if $\psi'\colon D\to Z$ is another arrow such that
-		\[\psi' \circ n=k \qquad \psi' \circ h\circ \iota_m=f \]
-		then we have
-		\[\psi'\circ h\circ m=\psi'\circ n\circ g=k\circ g=\phi \circ m =\psi \circ h\circ n \]
-		showing $\psi'=\psi$. \qedhere
-	\end{enumerate}
+We are left with uniqueness. Let $\psi'\colon D\to Z$ be another arrow such that $\psi' \circ n=k$ and $\psi' \circ h\circ \iota_m=f$. Then we have
+		\[\psi'\circ h\circ m=\psi'\circ n\circ g=k\circ g=\phi \circ m =\psi \circ h\circ m \]
+		Hence $\psi'\circ h=\psi \circ h$ and so $\psi'=\psi$ because $(B, \{m, h\circ\iota_m \})$ is a coproduct. 
 \end{proof}
@@
 	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares.
-	\[\xymatrix@C=30pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
+	\[\xymatrix@C=30pt@R=15pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
 		B\times B \ar@{>->}[r]_-{i_B\times i_B} & (B+C)\times (B+C) & B\times C \ar@{>->}[r]_-{i_B\times i_C} & (B+C)\times (B+C)}\]
-	\[ \xymatrix@C=30pt{A_2 \ar@{>->}[r]^{j_2}  \ar[d]_{p_2}& A   \ar[d]^{(f,g)}& A_3 \ar@{>->}[r]^{j_3}  \ar[d]_{p_3} & A \ar[d]^{(f,g)} \\
+	\[ \xymatrix@C=30pt@R=15pt{A_2 \ar@{>->}[r]^{j_2}  \ar[d]_{p_2}& A   \ar[d]^{(f,g)}& A_3 \ar@{>->}[r]^{j_3}  \ar[d]_{p_3} & A \ar[d]^{(f,g)} \\
 		C\times B \ar@{>->}[r]_-{i_C\times i_B} & (B+C)\times (B+C) & C\times C \ar@{>->}[r]_-{i_C\times i_C} & (B+C)\times (B+C)}\]
@@
 By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ and $(D, \{n, g\circ \iota\})$ are coproducts.
-We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]_{\iota} & C}}
+We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}
 
@@
 
-		\item  By \Cref{lem:nodim} we know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
-		\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		\item 	 By \Cref{lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks.
+		\[\xymatrix@C=45pt@R=15pt{K_b \ar@{>->}[r]^{k_{n'}}  \ar[d]_{(\pi^1_b, \pi^2_b)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
 			B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota')} & D'\times D'}\]
-		\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
+		\[ \xymatrix@C=45pt@R=15pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
 			E'\times B' \ar@{>->}[r]_-{(g'\circ \iota') \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D'}\]
 
-	Now, if we compute we get
-\begin{align*}
-	n\circ b\circ p_0&= d\circ n'\circ p_0= d\circ \pi^1_d\circ j_0=d\circ \pi^2_d\circ j_0=d\circ n'\circ q_0=n\circ b\circ q_0\\
-	g\circ c \circ  \iota' \circ p_3&=d\circ g' \circ  \iota' p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota' \circ q_3= g \circ c\circ \iota'\circ q_3
-\end{align*}
-Thus, since $n$ and $g$ are mono we get the dotted arrows in the diagram below.
-\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\ &K_b \ar[r]^{\pi^1_b} \ar[d]_{\pi^2_b}& B' \ar[d]^{b} & E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]
-
-Notice, moreover, that 
-\[(\pi^1_d, \pi^2_d)\circ k_{g'}\circ \phi_3=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ \phi_3=(g'\times g')\circ (\iota'\circ p_3, \iota'\circ q_3)\]
-and so $k_{g'}\circ \phi_3=j_3$.
-
-Now, we also have
+Let us now examine $K_1$ and $K_2$. We have
 \begin{align*}
@@
 
-			Since the bottom face of the original cube is a pullback (again by \Cref{prop:regmono}), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
+Since the bottom face of the original cube is a pullback (by \Cref{prop:regmono}), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
 \[m\circ k_1=\iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=\iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]
@@
 By \Cref{prop:isempty} we conclude that $K_1$ and $K_2$
- are both empty. In particular, we can also deduce that $(K_d, \{j_0, j_3\})$ is a coproduct.
+are both empty. In particular, this implies that $(K_d, \{k_{n'}, j_3\})$ is a coproduct.
+
+We focus now on $K_3$. Computing we get
+	\begin{align*}
+	&g\circ \iota \circ w\circ p_3=g\circ c\circ \iota'\circ p_3=d\circ g'\circ \iota'\circ p_3=d\circ \pi^1_d\circ j_3\\=&d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota' \circ q_3=g\circ c\circ \iota'\circ q_3=g\circ \iota \circ w\circ q_3
+	\end{align*}
+
+\noindent 
+\parbox{3cm}{\xymatrix@R=15pt{ K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & C' \ar[r]_{c} & C }}\hfill\parbox{9.5cm}{By \Cref{lem:po_set} $g\circ \iota$ is a monomorphism, thus $w\circ p_3=w\circ q_3$ and therefore:
+\[c\circ \iota'\circ p_3=\iota\circ w\circ p_3=\iota \circ w\circ q_3=c\circ \iota'\circ q_3\]
+Thus we get the dotted $\phi_3\colon K_3\to K_c$ in the diagram aside.}
+
+Moreover, $k_{g'}\circ \phi_3=j_3$ as shown by the following computation.
+\begin{align*}
+&(\pi^1_d, \pi^2_d)\circ k_{g'}\circ \phi_3=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ \phi_3=(g'\times g')\circ (\iota'\circ p_3, \iota'\circ q_3)\\=&((g'\circ \iota') \times (g'\circ \iota'))\circ (p_3, q_3)=(\pi^1_d, \pi^2_d)\circ j_3
+\end{align*}
+
+ \commentato{
 
@@
  On the other hand, notice that 
- \[\pi^1_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^1_b\circ \phi_0=n'\circ p_0=\pi^1_d\circ j_0 \qquad \pi^2_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^2_b\circ \phi_0=n'\circ p_0=\pi^2_d\circ j_0\]
+ \begin{align*}
+ \pi^1_{d}\circ k_{n'}\circ \phi_0&=n'\circ \pi^1_b\circ \phi_0=n'\circ p_0=\pi^1_d\circ j_0 \\
+ \pi^2_{d}\circ k_{n'}\circ \phi_0&=n'\circ \pi^2_b\circ \phi_0=n'\circ p_0=\pi^2_d\circ j_0
+ \end{align*}
 
   Thus $k_{n'}\circ \phi_0=j_0$ and we have
- \[(p_0, q_0)\circ \psi_0\circ \phi_0=(\pi^1_b, \pi^2_b)\circ \phi_0=(p_0, q_0)= \quad  j_0\circ \psi_0\circ \phi_0 = k_{n'}\circ \phi_0=j_0\]
-We can conclude that $\phi_0$ is an isomorphism and that $k_{n'}$ is a coproduct injection.
-
- Furthermore, by definition of complement, $(C', \{\iota', m'\})$ is a coproduct. Applying again \Cref{lem:nodim} we can decompose $K_c$ in four parts, given by the pullbacks below:
- \[\xymatrix@C=45pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
+ \[(p_0, q_0)\circ \psi_0\circ \phi_0=(\pi^1_b, \pi^2_b)\circ \phi_0=(p_0, q_0) \qquad  j_0\circ \psi_0\circ \phi_0 = k_{n'}\circ \phi_0=j_0\]
+We can conclude that $\phi_0$ is an isomorphism, $(K_b, \{k_{n'}, (\pi^1_b, \pi^2_b)\})$ is a pullback for $(\pi^1_d, \pi^2_d)$ along $n'\times n'$ and  that$(K_d, \{k_{n'}, j_3\})$ is a coproduct.}
+
+By definition of complement, we also know that $(C', \{\iota', m'\})$ is a coproduct. We can then apply again \Cref{lem:nodim}, decomposing $K_c$ in four parts, given by the pullbacks below:
+ \[\xymatrix@C=45pt@R=15pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
  	A'\times A' \ar@{>->}[r]_-{m'\times m'} & C'\times C' & A'\times E' \ar@{>->}[r]_-{m'\times  \iota'} & C'\times C'}\]
- \[ \xymatrix@C=45pt{H_2 \ar@{>->}[r]^{x_2}  \ar[d]_{(y_2, z_2)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_3 \ar@{>->}[r]^{x_3}  \ar[d]_{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
+ \[ \xymatrix@C=45pt@R=15pt{H_2 \ar@{>->}[r]^{x_2}  \ar[d]_{(y_2, z_2)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_3 \ar@{>->}[r]^{x_3}  \ar[d]_{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
  	E'\times A' \ar@{>->}[r]_-{\iota' \times m'} & C'\times C' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
 
- Now, notice that
- \small
+ \noindent
+\parbox{7cm}{ Let us examine $H_0$. We start noticing that 
+ \begin{align*}
+ 	(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_0=&(g'\times g')\circ(\pi^1_c, \pi^2_c)\circ x_0\\=&(g'\times g')\circ (m'\times m')\circ (y_0, z_0)\\=&((g'\circ m')\times (g'\circ m'))\circ (y_0, z_0)\\=&((n'\circ f')\times (n'\circ f'))\circ (y_0, z_0)\\=&(n'\times n')\circ (f'\times f')\circ (y_0, z_0) \end{align*}}\hfill \parbox{5cm}{\xymatrix@C=30pt{H_0 \ar[rr]^{(y_0, z_0)} \ar[d]_{x_0} \ar@{.>}[dr]^{h_0}&& A'\times A' \ar[d]_{f'\times f'}\\K_c \ar[dr]_{k_{g'}}& K_b \ar[r]_-{(\pi^1_b, \pi^2_b)} \ar[d]_{k_{n'}} & B'\times B' \ar[d]_{n'\times n'}\\ &K_d \ar[r]^-{(\pi^1_d, \pi^2_d)} & D'\times D'}}
+
+ Thus we get the dotted arrow $h_0\colon H_0\to K_b$ in the diagram above. Moreover, we have
+ \[m\circ a\circ y_0=c\circ m'\circ y_0=c\circ \pi^1_c\circ x_0=c\circ pi^2_c\circ x_0=c\circ m'\circ z_0=m\circ a \circ z_0\]
+ Since $m$ is a monomorphism $a\circ y_0=a\circ z_0$ and there exists an arrow $h'_0\colon H_0\to K_a$ such that $\pi^1_a\circ h'_0=y_0$ and $\pi^2_a\circ h'_0=z_0$. Notice, that
+ \[(\pi^1_b\circ \pi^2_b)\circ h_0=(f'\times f')\circ (y_0, z_0)=(f'\times f')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(\pi^1_b, \pi^2_b)\circ k_{f'}\circ h'_0\]
+and therefore we can conclude that $k_{f'}\circ h'_0=h_0$.
+
+We can prove another property of $h'_0$. Computing we have:
+\[(\pi^1_c, \pi^2_c)\circ k'_{m'}\circ h'_0=(m'\times m')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(m'\times m')\circ (y_0, z_0)=(\pi^1_c, \pi^2_c)\circ x_0\]
+so that $k'_{m'}\circ h'_0$ must coincide with $x_0$.
+
+As a next step, let us focus on $H_1$ and $H_2$. Two computations yield: \small
  \[\begin{split}
@@
 \normalsize
- thus we have arrows $h_1\colon H_1\to K_1$ and $h_2\colon H_2\to K_2$, showing that $H_1$ and $H_2$ are empty. On the other hand, let us consider the two diagrams below.
-
- \[ \xymatrix@C=45pt{ H_3 \ar@{.>}[d]^{\alpha_3} \ar[r]^{x_3} \ar@/_.4cm/[dd]_{(y_3, z_3)} & K_c \ar[d]_{k_{g'}}& K_3 \ar@{.>}[d]^{\beta_3} \ar@/^.3cm$ $/[dr]^{\phi_3} \ar@/_.4cm/[dd]_{(p_3, q_3)}\\K_3 \ar@{>->}[r]^{j_3}  \ar[d]^{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} &  H_3 \ar@{>->}[r]^{x_3}  \ar[d]^{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)}  \\
+
+ Hence, we have arrows $h_1\colon H_1\to K_1$ and $h_2\colon H_2\to K_2$, showing that $H_1$ and $H_2$ are empty. For $H_3$, let us consider the two diagrams below.
+
+ \[ \xymatrix@C=45pt@R=15pt{ H_3 \ar@{.>}[d]^{\alpha_3} \ar[r]^{x_3} \ar@/_.4cm/[dd]_{(y_3, z_3)} & K_c \ar[d]_{k_{g'}}& K_3 \ar@{.>}[d]^{\beta_3} \ar@/^.3cm$ $/[dr]^{\phi_3} \ar@/_.4cm/[dd]_{(p_3, q_3)}\\K_3 \ar@{>->}[r]^{j_3}  \ar[d]^{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} &  H_3 \ar@{>->}[r]^{x_3}  \ar[d]^{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)}  \\
    E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
@@
 
-Thus we get the dotted arrows $\alpha_3$ and $\beta_3$. Now, they are one the inverse of the other. Indeed on the one hand we have:
+Thus we get the dotted arrows $\alpha_3$ and $\beta_3$ which are one the inverse of the other. Indeed on the one hand we have:
 \begin{align*}
-j_3\circ \alpha_3\circ \beta_3&=k_{g'}\circ x_3\circ \beta_3=k_{g'} \circ \phi_3=\phi_3 \\
-(p_3, q_3)\circ \alpha_3\circ \beta_3&=(y_3, z_3)\circ \beta_3=(p_3, q_3) 
+j_3\circ \alpha_3\circ \beta_3=k_{g'}\circ x_3\circ \beta_3=k_{g'} \circ \phi_3=\phi_3  \qquad 
+(p_3, q_3)\circ \alpha_3\circ \beta_3=(y_3, z_3)\circ \beta_3=(p_3, q_3) 
 \end{align*}
- On the other, notice that
+ On the other hand, notice that
  \[(\pi^1_c, \pi^2_c)\circ \phi_3\circ \alpha_3 =(\iota'\times \iota')\circ (p_3, q_3)\circ \alpha_3= (\iota'\times \iota')\circ (y_3, z_3)=(\pi^1_c, \pi^2_c)\circ x_3\]
@@
 
- Now, we have already proved that $(K_d, \{k'_n, j_3\})$ is a coproduct, thus there is a unique arrow $\theta\colon K_d\to Z$ such that 
- \[\theta \circ k'_n=\gamma \qquad \theta \circ j_3=\delta \circ \phi_3 \]
+ We have already proved that $(K_d, \{k'_n, j_3\})$ is a coproduct, thus there is a unique arrow $\theta\colon K_d\to Z$ such that  $\theta \circ k'_{n'}=\gamma$ and $\theta \circ j_3=\delta \circ \phi_3 $.
  Now, on the one hand we have
@@
  On the other hand, 
- \[(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_0=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_0=(g'\times g')\times (m'\times m')\circ (y_0, x_0)=(n'\circ n')\ (f')\]
-
+ \[\theta \circ k_{g'}\circ x_0=\theta \circ k_{n'}\circ h_0=\gamma \circ h_0=\gamma \circ k_{f'}\circ h'_0=\delta \circ k_{m'}\circ h'_0=\delta \circ x_0 \]
+ and we can conclude that $\theta \circ k_{g'}=\delta$ as wanted.
+
+ We are left with uniqueness. If $\theta'$ is another arrow $K_d\to Z$ such that $\theta'\circ k_{n'}=\gamma$ and $\theta'\circ k'_{g'}= \delta$. If we compute we get
+ \[\theta'\circ j_3=\theta'\circ k_{g'}\circ x_3=\delta \circ x_3=\theta \circ k_{g'}\circ x_3=\theta \circ j_3 \]
+ We already now that $\theta'\circ k_{n'}=\theta \circ k_{n'}$, so the previous identity entails that $\theta =\theta'$ as wanted.
 			 \qedhere 
 	\end{enumerate}
-\end{proof}
-
-\begin{proof} 
-	Let $u\colon K_b\to Z$ and $v\colon K_c\to Z$ be two arrows such that $u\circ k_{f'}=v\circ k_{m'}$. We want to construct an arrow $w\colon K_d\to Z$ such that 
-	\[w\circ k_{g'}=v \qquad w\circ k_{n'}=u\]
-
-	Now, if $E'\subseteq C'$ is the complement of the image of $m'$ and $\iota\colon E'\mto B'$ the corresponding inclusion, then by \Cref{lem:po_set} we know that $(D', \{n', g'\circ \iota\})$ is a coproduct.
-Thus if $x$ is an element of $K_d$, we have exactly four cases.
-
-	\begin{enumerate}
-		\item $\pi^1_d(x)$ and $\pi^2_d(x)$ both belong to the image of $n'$. Let $x_1$ and $x_2$ be such that $\pi^1_d(x)=n'(x_1)$ and $\pi^2_d(x)=n'(x_2)$, then 
-		\[n(b(x_1))=d(n'(x_1))=d(\pi^1_d(x))=d(\pi^1_d(x))=d(n'(x_2))=n(b(x_2)) \]
-		Since $n$ is mono we deduce that $b(x_1)=b(x_2)$ and so there exists $y\in K_{b}$ such that $\pi^1_d(y)=x_1$ and $\pi^2_d(x)=x_2$. But then we have
-		\begin{align*}
-	\pi^1_d(k_{n'}(y))&=n'(\pi^1_d(y)) =n'(x_1)=\pi^1_d(x)\\
-	\pi^2_d(k_{n'}(y))&=n'(\pi^2_d(y)) =n'(x_2)=\pi^2_d(x)
-		\end{align*}
-		Thus, by \Cref{lemma:kern_pairs_pres_pullbacks} $y$ is the unique element $k_{n'}(y)=x$. We can thus define $w(x)=u(y)$. 
-		\item $\pi^1_d(x)$ and $\pi^2_d(x)$ both belong to the image of $g'\circ \iota$. Consider $x_1$ and $x_2$ in $E'$ such that
-		\[g'(\iota(x_1))=\pi^1_d(x) \qquad  g'(\iota(x_2))=\pi^1_d(x)\]
-		Thus we have
-		\begin{align*}
-			g(c(\iota(x_1)))=d(g'(\iota(x_1)))=d(\pi^1_d(x))=d(\pi^2(x))=
-		\end{align*}
-
-		\item $\pi^1_d(x)$ belongs to the image of $n'$  and $\pi^2_d(x)$ to that of $g'\circ \iota$;
-		\item $\pi^2_d(x)$ belongs to the image of $n'$  and $\pi^1_d(x)$ to that of $g'\circ \iota$;
-	\end{enumerate}
-
-	To prove uniqueness, let we split the cases as above.
-	\begin{enumerate}
-		\item 
-		\item 
-		\item 
-		\item \qedhere
-	\end{enumerate}
-
-	Since $\Set$ is cocomplete, we can take a pushout square as the one  on the right below.
-
-	\parbox{10.5cm}{Now, notice that \begin{align*}
-		n'\circ \pi^1_{b}\circ k_{f'}&=n'\circ f'\circ \pi^1_{a}=g'\circ m'\circ \pi^1_{a}=g'\circ \pi^{1}_{c}\circ k_{m'}\\
-		n'\circ \pi^2_{b}\circ k_{f'}&=n'\circ f'\circ \pi^2_{a}=g'\circ m'\circ \pi^2_{a}=g'\circ \pi^{2}_{c}\circ k_{m'}
-		\end{align*}}\hfill \parbox{2cm}{\xymatrix@R=15pt{K_a \ar[r]_{k_{f'}} \ar[d]_{k_{m'}}& K_b  \ar[d]^{p_2}\\ K_c \ar[r]^{p_1} & P}}
-
-	In particular, this entails that there are two arrows $\pi_1, \pi_2\colon P\rightrightarrows D'$ such that 
-	\[\pi_1\circ p_1=g'\circ \pi^1_c \quad \pi_1\circ p_2=n'\circ \pi^1_b \quad \pi_2\circ p_1=g'\circ \pi^2_c \quad \pi_2\circ p_2=n'\circ \pi^2_b\]
-
- Moreover,  we have
- \begin{align*}
- 	d\circ \pi_1\circ p_1&=d\circ g'\circ \pi^1_c=g\circ c\circ \circ \pi^1_c=g\circ c\circ \pi^2_c=d\circ g'\circ \pi^2_c=d\circ \pi_2 \circ p_1\\
- 	d\circ \pi_1\circ p_2&=d\circ n'\circ \pi^1_b=n\circ b \circ \pi^1_b=n\circ b\circ \pi^2_b=d\circ n'\circ \pi^2_b=d\circ \pi_2 \circ p_2
- \end{align*}
-	so that $d\circ \pi_1=d\circ p_2$.
-
-	We want now to show that $(P, \pi_1, \pi_2)$ is a kernel pair for $d$. Let $aa$
-
-We 
-For every $t$ in $T$
-
 \end{proof}

### 2025-03-11 calco/main.tex
cose

@@
 
-We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class $\mathcal{M}$ of monos.
+We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.
 
 \begin{definition}
-	contenuto...
+	We define $\pbc$ as the class of all regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
 \end{definition}
@@
 \begin{restatable}{lemma}{pbm}\label{lem:pbmono}
-	The class $\pbc$ is closed under composition, decomposition and it is stable under pullbacks and pushouts
+	The class $\pbc$ is closed under composition, decomposition and it is stable under pullbacks and pushouts.
 \end{restatable}
+\begin{proof}
+	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}. We are left with stability under pullbacks.
+\end{proof}
 
@@
 \begin{lemma}\label{lemma:stab}
-	In $\EqHyp$, $\reg(\EqHyp), \mathcal{N}$-pushouts are stable.
+	In $\EqHyp$, $\pbc$-pushouts are stable.
 \end{lemma}
@@
 We have to show that the top face of the cube with which we have began is a pushout.
-Let $\mathcal{H}$ be $(E, V, C, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
-Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
-\[v_E\circ h'_E=w_E\circ k'_E\qquad v_V\circ h'_V=w_V\circ k'_V\]
-
-We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-
-Now, $d_V$ is a regular epi, thus
-
-	\commentato {Now, notice that
-	\[s_1 \circ m_1 \circ q_1 = q'_2 \circ h'_V = h'_C \circ q'_1 \quad  	q'_4 \circ z'_V = z'_Q \circ q'_2= u_1\circ m_2 \circ q'_2\]
-
-	\[
-\begin{split}
-	y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
-\end{split}%\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'\end{split}
-\]
-Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.}
-
-	We want to construct the dotted arrow $v_C$ which fits in the diagram below.
-	\[
+Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
+Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that	$v_E\circ h'_E=w_E\circ k'_E$ and $v_V\circ h'_V=w_V\circ k'_V$.
+
+\noindent 
+\parbox{9cm}{ We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
+If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+Concretely we have to construct the dotted arrow $v_C$ which fits in the diagram aside.} \hfill \parbox{3cm}{
 \xymatrix@C=10pt@R=6pt{
-		&B_1'\ar[dd]|\hole_(.65){q_1'}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]|\hole_(.65){q_2'} \ar[dl]_{t_V'}\ar[dr]^{z_V}\\
-		B_3'  \ar[dd]_{q_3'}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
-		&C_1'\ar[rr]|\hole^(.65){h_C'} \ar[dl]_{k_C'} && C_2' \ar[dl]^{t_C'}\ar[dr]^{z_C}\\
-		C'_3 \ar[rr]_{p_C'} & & C'_4\ar@{.>}[rr]_{v_C} && C
-	}\]
-	By , we know that the top face of the cube below is a pushout.
-	\[\xymatrix@C=15pt@R=15pt{&K_{s_2\circ m_1\circ q'_1}\ar[dd]|\hole_(.65){\pi_{s_2\circ m_1\circ q'_1}^{1}}\ar[rr]^{k_{h'_2}} \ar[dl]_{k_{k'_2}} && K_{m_2\circ q'_2} \ar[dd]^{\pi_{m_2\circ q'_2}^{1}} \ar[dl]_{k_{t'_2}} \\ K_{m_3\circ q'_3}  \ar[dd]_{\pi_{m_3\circ q'_3}^{1}}\ar[rr]^(.7){k_{p'_2}} & & K_{q'_4} \ar[dd]_(.3){\pi_{q'_4}^{1}}\\&B'_1\ar[rr]|\hole^(.65){h'_2} \ar[dl]^{k'_2} && B'_2 \ar[dl]^{t'_2} \\B'_3 \ar[rr]_{p'_2} & & C_4}\]
-	And, since $m_3$ and $m_2$ are monos,
+	&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
+	B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
+	&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
+	Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
+}}
+
+Now, consider the cube below, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
+We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
+\[\xymatrix@C=10pt@R=10pt{
+	&B_1'\ar@{>>}[dd]|(.53)\hole^(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rrrr]^{h_V'} \ar[dl]_(.6){k_V'} &&&& B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]^-{k_{x_1}} \ar[dd]_{k_{w}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{u_1}}\\
+	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rrrr]^(.7){p_V'} & & &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
+	&T\ar@{>->}[rrrr]|(.68)\hole_{x_1} \ar[dl]_{w} &&&& U\ar[dl]^(.4){u_1} && K_{m_3\circ q'_3} \ar@{>->}[rr]_-{k_{y_1}} && K_{q'_4} \\
+	Y \ar@{>->}[rrrr]_{y_1} & & && Q'_4}\]
+
+By construction we have that 	$m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1 = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2$ and
+
+Since $m_3$ and $m_2$ are monos we have
 \[\begin{split}
@@
 
-%	Let now $z: \graph{G}'_2 \to \graph H = (E, V, Q, s, t, q)$, $w: \graph G_3^1 \to \graph H$ be two morphisms such that $z \circ h' = w \circ k'$, and let $\phi:B'_4 \to V$ be the arrow induced by $z_V$ and $w_V$.
-We want to construct the arrow $v: C'_4 \to Q$ in the diagram below.
-	\[\begin{tikzcd}[row sep = 20, column sep = 20]
-		& {B_1'} && {B_2'} \\
-		{B_3'} && {B_4'} && V \\
-		& T && U \\
-		Y && {C_4'} && Q \\
-		& {C_1} && {C_2} \\
-		{C_3} && {C_4}
-		\arrow["{h_V'}", from=1-2, to=1-4]
-		\arrow["{k_V'}"', from=1-2, to=2-1]
-		\arrow["{s_2\circ m_1 \circ q_1'}"{description, pos=0.7}, from=1-2, to=3-2]
-		\arrow["{t_V'}", from=1-4, to=2-3]
-		\arrow["{z_V}", from=1-4, to=2-5]
-		\arrow["{m_2\circ q'_2}"{pos=0.7}, from=1-4, to=3-4]
-		\arrow["{m_3 \circ q'_3}"', from=2-1, to=4-1]
-		\arrow["q", from=2-5, to=4-5]
-		\arrow["{x_1}"{pos=0.8}, from=3-2, to=3-4]
-		\arrow["w"', from=3-2, to=4-1]
-		\arrow["{x_2}"'{pos=0.7}, from=3-2, to=5-2]
-		\arrow["{u_1}", from=3-4, to=4-3]
-		\arrow["{u_2}"{pos=0.7}, from=3-4, to=5-4]
-		\arrow["{y_2}"', from=4-1, to=6-1]
-		\arrow["{h_C}"{pos=0.8}, from=5-2, to=5-4]
-		\arrow["{k_C}", from=5-2, to=6-1]
-		\arrow["{t_C}", from=5-4, to=6-3]
-		\arrow["{p_C}"', from=6-1, to=6-3]
-		\arrow["{p_V'}"{pos=0.8}, from=2-1, to=2-3, crossing over]
-		\arrow["\phi"{pos=0.8}, from=2-3, to=2-5, crossing over]
-		\arrow["{q'_4}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
-		\arrow["{y_1}"{pos=0.7}, from=4-1, to=4-3, crossing over]
-		\arrow["{d_C}"'{pos=0.7}, from=4-3, to=6-3, crossing over]
-		\arrow["v"{pos=0.8}, dashed, from=4-3, to=4-5, crossing over]
-	\end{tikzcd}\]
+	\commentato {Now, notice that
+	\[s_1 \circ m_1 \circ q_1 = q'_2 \circ h'_V = h'_C \circ q'_1 \quad  	q'_4 \circ z'_V = z'_Q \circ q'_2= u_1\circ m_2 \circ q'_2\]
+
+	\[
+\begin{split}
+	y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
+\end{split}%\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'\end{split}
+\]
+Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.}
 
@@
  \[\theta'\circ j_3=\theta'\circ k_{g'}\circ x_3=\delta \circ x_3=\theta \circ k_{g'}\circ x_3=\theta \circ j_3 \]
- We already now that $\theta'\circ k_{n'}=\theta \circ k_{n'}$, so the previous identity entails that $\theta =\theta'$ as wanted.
+ We already know that $\theta'\circ k_{n'}=\theta \circ k_{n'}$, so the previous identity entails that $\theta =\theta'$.
 			 \qedhere 

### 2025-03-11 calco/main.tex
cose

@@
 \begin{proof}
-	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}. We are left with stability under pullbacks.
+	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}.
+We are left with stability under pullbacks.
+Consider the diagrams below, in which the first square is a pullback with $h$ in $\pbc$.
+In particular, by \Cref{prop:eqhyp_complete}, the two halves of the diagram on the right are pullbacks and so, by \Cref{lem:pb1} the whole rectangle is a pullback too.
+
+	\[\]
+
+		\[
+	\xymatrix@C=10pt@R=10pt{&& & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'}  \\\mathcal{P} & & \mathcal{G}_1 &
+	A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
+	&& V_{\mathcal{P}} && V_1 && Q_1\\
+	 &&&&A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E}  \\
+		\mathcal{G}_2 && \mathcal{G}_3 & V_3 \ar@{>->}[rr]_{p_E} & & A_4 && V_2 && V_3 && Q_3 }
+	\]
+
+	Thus, by \Cref{lem:pb1} also the right rectangle is a pullback.
 \end{proof}
@@
 Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
-Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that	$v_E\circ h'_E=w_E\circ k'_E$ and $v_V\circ h'_V=w_V\circ k'_V$.
-
-\noindent 
-\parbox{9cm}{ We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
-If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-Concretely we have to construct the dotted arrow $v_C$ which fits in the diagram aside.} \hfill \parbox{3cm}{
-\xymatrix@C=10pt@R=6pt{
+Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
+\[v_E\circ p'_E=w_E \quad v_V\circ p'_V=w_V \quad v_E\circ z'_E=o_e \quad v_V\circ z'_V=o_V\]
+
+\commentato{\xymatrix@C=10pt@R=6pt{
 		&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
@@
 
+We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+
 Now, consider the cube below, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
@@
 \[\xymatrix@C=10pt@R=10pt{
-	&B_1'\ar@{>>}[dd]|(.53)\hole^(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rrrr]^{h_V'} \ar[dl]_(.6){k_V'} &&&& B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]^-{k_{x_1}} \ar[dd]_{k_{w}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{u_1}}\\
+	&B_1'\ar@{>>}[dd]|(.53)\hole^(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rrrr]^{h_V'} \ar[dl]_(.6){k_V'} &&&& B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]^-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\
 	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rrrr]^(.7){p_V'} & & &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
-	&T\ar@{>->}[rrrr]|(.68)\hole_{x_1} \ar[dl]_{w} &&&& U\ar[dl]^(.4){u_1} && K_{m_3\circ q'_3} \ar@{>->}[rr]_-{k_{y_1}} && K_{q'_4} \\
+	&T\ar@{>->}[rrrr]|(.68)\hole_{x_1} \ar[dl]_{w} &&&& U\ar[dl]^(.4){u_1} && K_{m_3\circ q'_3} \ar@{>->}[rr]_-{k_{p'_V}} && K_{q'_4} \\
 	Y \ar@{>->}[rrrr]_{y_1} & & && Q'_4}\]
 
-By construction we have that 	$m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1 = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2$ and
-
-Since $m_3$ and $m_2$ are monos we have
-\[\begin{split}
-	q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
-\end{split}\qquad\begin{split}
-	q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
-\end{split}\]
+By construction we have that 
+\[m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1 = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad  m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 = m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2 \]
+but since $m_3$ and $m_2$ are monos this implies
+\[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]
+
 Computing, we obtain
@@
 	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\
-	&= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
-	&= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\
+	&= w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
+	&= w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\
 	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 \\
@@
 \end{split}\qquad\begin{split}
-	q \circ v_V \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\
-	&= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\
-	&= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
-	&= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\
-	&= q \circ z_V \circ \pi_{m_2 \circ q_2'}^2 \\
+	q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} &= q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 \\
+	&= q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 \\
+	&= o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
+	&= o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\
+	&= q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 \\
 	&= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\
-	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{t'_V}
+	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
 \end{split}\]
@@
 \]
-hence, $v_C$ is the mediating arrow.
-\[
-v_C \circ q'_4 \circ \pi_{q'_4}^1 = v_C \circ q'_4 \circ \pi_{q'_4}^2
-\]
-
-	\commentato {Now, notice that
-	\[s_1 \circ m_1 \circ q_1 = q'_2 \circ h'_V = h'_C \circ q'_1 \quad  	q'_4 \circ z'_V = z'_Q \circ q'_2= u_1\circ m_2 \circ q'_2\]
-
-	\[
-\begin{split}
-	y_1 \circ m_3 \circ q'_3 &= p'_V \circ q'_4\\ &= p'_C \circ q'_3
-\end{split}%\qquad\begin{split}TODO:\ w \circ s_2 \circ m_1 = m_3 \circ k_C'\end{split}
-\]
-Hence, $s_1\circ m_1 = h'_C$, $w \circ s_2 \circ m_1 = m_3 \circ k_C'$, $t'_C = u_1 \circ m_2$ and $p'_C = y_1 \circ m_3$.}
-
-	By \Cref{prop:reg_epi_coeq}, $d_C$ is the coequalizer of its kernel pair. On the other hand, by \Cref{lemma:pushouts_kernel_pairs}, we know that the top face of the cube below is a pushout.
-	\[\begin{tikzcd}[row sep=20, column sep = 20]
-		& {K_{s_2\circ m_1 \circ q_1'}} && {K_{m_2\circ q_2'}} \\
-		{K_{m_3 \circ q_3'}} && {K_{q_4'}} \\
-		& {B'_1} && {B'_2} \\
-		{B'_3} && {B'_4}
-		\arrow["{k_{h'_V}}", from=1-2, to=1-4]
-		\arrow["{k_{k_V'}}"', from=1-2, to=2-1]
-		\arrow["{\pi_{s_2\circ m_1 \circ q_1'}^1}"'{pos=0.7}, from=1-2, to=3-2]
-		\arrow["{k_{t_V'}}", from=1-4, to=2-3]
-		\arrow["{\pi_{m_2\circ q_2'}^1}", from=1-4, to=3-4]
-		\arrow["{k_{p_V'}}"{pos=0.8}, from=2-1, to=2-3, crossing over]
-		\arrow["{\pi_{m_3 \circ q_3'}^1}"', from=2-1, to=4-1]
-		\arrow["{h_V'}"{pos=0.7}, from=3-2, to=3-4]
-		\arrow["{\pi_{q_4'}^1}"'{pos=0.7}, from=2-3, to=4-3, crossing over]
-		\arrow["{k_V'}"', from=3-2, to=4-1]
-		\arrow["{t_V'}", from=3-4, to=4-3]
-		\arrow["{p_V'}"', from=4-1, to=4-3]
-	\end{tikzcd}\]
-	And, since $m_3$ and $m_2$ are monos,
-	\[\begin{split}
-		q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2
-	\end{split}\qquad\begin{split}
-		q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2
-	\end{split}\]
-
-	Computing, we obtain
-	\[\begin{split}
-		q \circ \phi \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\ &= w_C \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\ &= q \circ w_V \circ \pi_{m_3 \circ q_3'} \\ &= q \circ \phi \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{p'_V}
-	\end{split}\qquad\begin{split}
-		q \circ \phi \circ \pi_{q'_4}^1 \circ k_{t_V'} &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^1 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\ &= z_C \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\ &= q \circ z_V \circ \pi_{m_2 \circ q_2'} \\ &= q \circ \phi \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\ &= q \circ \phi \circ \pi_{q'_4}^2 \circ k_{t'_V}
-	\end{split}\]
-
-	Since the previous cube has a pushout as top face, by universal property, we have
-	\[
-	q \circ \phi \circ \pi_{q'_4}^1 = q \circ \phi \circ \pi_{q'_4}^2
-	\]
-	hence, $v$ is the mediating arrow.
-	\[
-	v \circ q'_4 \circ \pi_{q'_4}^1 = v \circ q'_4 \circ \pi_{q'_4}^2
-	\]
-
+
+Now, $q'_4$ is a regular epi and so it is the coequalizer of its kernel pair, hence there exists $v_Q\colon Q'_4\to Q$ such that $v_Q\circ q'_4=q\circ v_V$ and we can conclude.
 \end{proof}

### 2025-03-11 calco/main.tex
diagrammi
minima

--- 2025-03-11 calco/main.tex
@@
 
-As in the point aboce, uniqueness is guaranteed by faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
+As in the point above, uniqueness is guaranteed by faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
 	\end{enumerate}
@@
 \begin{proof}
-	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
-
-	\noindent 
+\emph{Only if}
+
+	\parbox{11cm}{	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos. 
+	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
+	$\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
+	is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono 
+	$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that 
+	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
+	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.}
+	\hfill
 	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
-	\hfill 	\parbox{11cm}{Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$.
-Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in $\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$.
-From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono $m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside.
-Now, notice that
-	}\hfill 
-	\[e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}\]
-	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.
+
+	\noindent
+	\emph{If}
+	Let us assume instead that $h_E$, $h_V$, and $h_Q$  are monos. XXXXX
 \end{proof}

### 2025-03-11 calco/main.tex

--- 2025-03-11 calco/main.tex
@@
 \[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
+
+\begin{center}\begin{tikzpicture}
+        \begin{pgfonlayer}{nodelayer}
+                \node[style=small box](a) at (-1.8, 0){$a$};
+                \node[style=none] (aatt) at (-1.5, 0){};
+                \node[style=node](v) at (-0.9, 0){};
+                \node[style=medium box](div) at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, -0.3){};
+                \node[style=none] (divsnd) at (-0.3, 0.3){};
+                \node[style=none] (divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{edgelayer}
+                \draw(aatt.center) to (v);
+                \draw[out=-60, in=-180] (v) to (divfst.center);
+                \draw[out=60, in=-180](v) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}
+        \begin{pgfonlayer}{nodelayer}
+                \node[style=small box](a1) at (-1.8, -0.5){$a$};
+                \node[style=none] (a1att) at (-1.5, -0.5){};
+                \node[style=node](v1) at (-0.9, -0.5){};
+                \node[style=small box](a2) at (-1.8, 0.5){$a$};
+                \node[style=none] (a2att) at (-1.5, 0.5){};
+                \node[style=node](v2) at (-0.9, 0.5){};
+                \node[style=medium box](div) at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, -0.3){};
+                \node[style=none] (divsnd) at (-0.3, 0.3){};
+                \node[style=none] (divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{edgelayer}
+                \draw(a1att.center) to (v1);
+                \draw(a2att.center) to (v2);
+                \draw[out=0, in=-120] (v1) to (divfst.center);
+                \draw[out=0, in=120](v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+                \draw[dashed, rounded corners] (-1.2, -0.8) rectangle (-0.6, 0.8);
+        \end{pgfonlayer}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}
+        \begin{pgfonlayer}{nodelayer}
+                \node[style=small box](a1) at (-1.8, -0.5){$a$};
+                \node[style=none] (a1att) at (-1.5, -0.5){};
+                \node[style=node](v1) at (-0.9, -0.5){};
+                \node[style=small box](a2) at (-1.8, 0.5){$a$};
+                \node[style=none] (a2att) at (-1.5, 0.5){};
+                \node[style=node](v2) at (-0.9, 0.5){};
+                \node[style=medium box](div) at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, -0.3){};
+                \node[style=none] (divsnd) at (-0.3, 0.3){};
+                \node[style=none] (divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{edgelayer}
+                \draw(a1att.center) to (v1);
+                \draw(a2att.center) to (v2);
+                \draw[out=0, in=-120] (v1) to (divfst.center);
+                \draw[out=0, in=120](v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+\end{tikzpicture}
+\end{center}
+
 %

### 2025-03-11 calco/main.tex
diagrammi

@@
 \begin{example}
+		\[
+                \xymatrix@C=10pt@R=6pt{
+                &\emptyset \ar@{>->}[dd]|\hole_(.65){a}\ar@{>->}[rr]^{v} \ar@{>->}[dl]_{u} &&
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                                \node[style=node](v) at (0, 0){};
+                                \node[style=none] at(0, 0.5){$c$};
+		\end{pgfonlayer}
+                \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
+                \end{tikzpicture} \ar@{>->}[dd]^{b} \ar@{>->}[dl]_{y} \\
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(0, 0){};
+                        \node[style=none]at(0, 0.5){$b$};
+                \end{pgfonlayer}
+                \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
+        \end{tikzpicture}
+                \ar@{>->}[dd]_{c}\ar@{>->}[rr]^(.7){z} & &
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(-0.5, 0){};
+                        \node[style=none]at(-0.5, 0.5){$b$};
+                        \node[style=node]at(0.5, 0){};
+                        \node[style=none]at(0.5, 0.5){$c$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
+                \end{pgfonlayer}\end{tikzpicture}
+                \ar@<2ex>@{>->}[dd]_(.3){d}\\&
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(0, 0){};
+                        \node[style=none]at(0, 0.5){$a$};
+                \end{pgfonlayer}
+                \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
+        \end{tikzpicture}
+                \ar@{>->}[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && 
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(-0.5, 0){};
+                        \node[style=none]at(-0.5, 0.5){$a$};
+                        \node[style=node]at(0.5, 0){};
+                        \node[style=none]at(0.5, 0.5){$c$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
+                \end{pgfonlayer}\end{tikzpicture}
+                \ar@{>->}[dl]^{n} \\
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(-0.5, 0){};
+                        \node[style=none]at(-0.5, 0.5){$a$};
+                        \node[style=node]at(0.5, 0){};
+                        \node[style=none]at(0.5, 0.5){$b$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
+                \end{pgfonlayer}\end{tikzpicture}
+                \ar@{>->}[rr]_{g} & & 
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(0, 0){};
+                        \node[style=none]at(0, 0.5){$a$};
+                        \node[style=node]at(1, 0){};
+                        \node[style=none]at(1, 0.5){$b$};
+                        \node[style=node]at(2, 0){};
+                        \node[style=none]at(2, 0.5){$c$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-.3, 0.3) rectangle (2.3, -0.3);
+                \end{pgfonlayer}\end{tikzpicture} }
+\]
 
@@
 in the picture above
-\[\mbox{to draw DPO rule, x in the same equivalence class} \]
+\begin{center}
+\[\xymatrix{
+                \begin{tikzpicture}[baseline=(w)]\begin{pgfonlayer}{nodelayer}
+                \node[style=node](v1) at (-0.9, 0.3){};
+                \node[style=node](v2) at (-0.9, -0.3){};
+                \node[style=medium box] at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, 0.3){};
+                \node[style=none](divsnd) at (-0.3, -0.3){};
+                \node[style=none](divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}        
+        \begin{pgfonlayer}{edgelayer}
+                \draw(v1) to (divfst.center);
+                \draw(v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
+        \end{pgfonlayer}\begin{pgfonlayer}{background}
+                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+        \end{pgfonlayer}\end{tikzpicture}
+        & \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
+                \node[style=node](v1) at (-0.9, 0.3){};
+                \node[style=node](v2) at (-0.9, -0.3){};
+                \node[style=medium box] at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, 0.3){};
+                \node[style=none](divsnd) at (-0.3, -0.3){};
+                \node[style=none](divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}        
+        \begin{pgfonlayer}{edgelayer}
+                \draw(v1) to (divfst.center);
+                \draw(v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
+                \end{pgfonlayer}\begin{pgfonlayer}{background}
+                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+                \end{pgfonlayer}
+        \end{tikzpicture}
+	\ar[l] \ar[r] &
+        \begin{tikzpicture}[baseline=(nil.center)]\begin{pgfonlayer}{nodelayer}
+                \node[style=node](v1) at (-0.9, 0.3){};
+                \node[style=node](v2) at (-0.9, -0.3){};
+                \node[style=medium box] at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, 0.3){};
+                \node[style=none](divsnd) at (-0.3, -0.3){};
+                \node[style=none](divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+                \node[style=small box] at (0, -1){$1$};
+                \node[style=none](one) at (0.3, -1){};
+                \node[style=node](z) at (0.9, -1){};
+                \node[style=none](nil) at (0, -0.5){};
+        \end{pgfonlayer}        
+        \begin{pgfonlayer}{edgelayer}
+                \draw(v1) to (divfst.center);
+                \draw(v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+                \draw(one.center) to (z);
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
+                \draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
+        \end{pgfonlayer}\begin{pgfonlayer}{background}
+                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+        \end{pgfonlayer}\end{tikzpicture}
+}\]\end{center}
+
 The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.

### 2025-03-11 calco/main.tex
diagrammi
qualche bla-bla

@@
 \subsection{Term Graphs}
-\todo{a very nice introduction}
-
-Let us start using labelled hypergraphs to define term graphs.
+Term graphs have been adopted as a convenient way to represents terms over a signature with an explicit sharing of sub-terms,
+and as such have been a convenient tool for an efficient implementation of term rewriting~\cite{Plu:TGR-ENTCS}.
+We elaborate here on the presentation given in~\cite{CastelnovoGM24}.
 
@@
 \label{hypereq}
-\todo{A very nice instroduction}
+The use of hypergraphs equipped with an equivalence relation over their nodes has been argued as a convenient way to express concurrency in the DPO approach to rewriting~\cite{concur2006}
+This section presents the framework by means of adhesive categories, including also its version for term graphs, as a stepping stone towards a analogous characterisation for e-graphs.
 
@@
 \begin{example}
-		\[
+It is noteworthy to show that pushouts along regular monos are not stable. 
+\begin{minipage}[l]{.35\linewidth}Consider e.g. the cube aside: the vertices are just graphs without edges, and in the graphs themselves the equivalence classes 
+are denoted by encircling nodes with a dotted line. All the arrows are regular mono. It is immediate to see that the bottom face is a pushout and the side faces are pullback. Unfortunately, 
+the top face fails to be a pushout
+  \end{minipage}\hfill
+\begin{minipage}[r]{.60\linewidth}
                 \xymatrix@C=10pt@R=6pt{
@@
                 \end{pgfonlayer}\end{tikzpicture} }
-\]
-
-	\todo{Qua va l'esempio di Fabio}
+  \end{minipage}
 \end{example}
@@
 Being a purely graphical representation, EGGS allows for redundancy and possibly ambiguity,
-so that e.g. a term such as $a \div a$ admits a few different representations as a term graph, as shown below
-%
-\[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
-
-\begin{center}\begin{tikzpicture}
+so that e.g. a term such as $a / a$ admits a few different representations as a term graph, as shown below
+%
+%\[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
+
+\begin{center}\begin{tikzpicture}[baseline=(w)]
         \begin{pgfonlayer}{nodelayer}
@@
 \qquad
-\begin{tikzpicture}
+\begin{tikzpicture}[baseline=(w)]
         \begin{pgfonlayer}{nodelayer}
@@
 \end{center}
-
 %
@@
 arrows in $\mathcal{M}$, then we can lift all the standard properties
-of the DPO approach to the category at hand. However, the structure of rules that is advanced in~\cite{DetlefsNS05},
+of the DPO approach.
+% to the category at hand. 
+However, the structure of rules that is advanced in~\cite{DetlefsNS05},
 is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity, hence in $\mathcal{M}$,
-while the second component does not necessarily belong to $\mathcal{M}$. 
-%
-Consider e.g. an EGG rule such $x \div x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}, 
-can be modelled as the DPO rule below,
-which can be applied with a match that is injective on equivalence classes to the left-most and the middle EGG
-in the picture above
-\begin{center}
-\[\xymatrix{
-                \begin{tikzpicture}[baseline=(w)]\begin{pgfonlayer}{nodelayer}
-                \node[style=node](v1) at (-0.9, 0.3){};
-                \node[style=node](v2) at (-0.9, -0.3){};
-                \node[style=medium box] at (0, 0){$/$};
-                \node[style=none](divfst) at (-0.3, 0.3){};
-                \node[style=none](divsnd) at (-0.3, -0.3){};
-                \node[style=none](divout) at (0.3, 0){};
-                \node[style=node] (w) at (0.9, 0){};
-        \end{pgfonlayer}        
-        \begin{pgfonlayer}{edgelayer}
-                \draw(v1) to (divfst.center);
-                \draw(v2) to (divsnd.center);
-                \draw(divout.center) to (w);
-        \end{pgfonlayer}
-        \begin{pgfonlayer}{eqlayer}
-                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
-        \end{pgfonlayer}\begin{pgfonlayer}{background}
-                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
-        \end{pgfonlayer}\end{tikzpicture}
-        & \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
+while the second component may not belong to $\mathcal{M}$.
+
+\noindent
+\begin{minipage}[l]{.48\linewidth}
+Consider e.g. an EGG rule such $x / x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}.
+It can be modelled as the DPO rule aside, concisely represented as the arrow $L \rightarrow R$,
+which can be applied with a match that is injective on equivalence classes to the legal EGGs
+above.
+\end{minipage}\hfill
+\begin{minipage}[r]{.60\linewidth}
+\xymatrix{        
+ \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
                 \node[style=node](v1) at (-0.9, 0.3){};
@@
         \end{tikzpicture}
-	\ar[l] \ar[r] &
+	\ar@{=>}[r] &
         \begin{tikzpicture}[baseline=(nil.center)]\begin{pgfonlayer}{nodelayer}
@@
         \end{pgfonlayer}\end{tikzpicture}
-}\]\end{center}
-
+}
+\end{minipage}
+
+\noindent
 The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.
@@
 \begin{proof}
-\emph{Only if}
-
-	\parbox{11cm}{	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos. 
+	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
+	\parbox{11cm}{
 	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
@@
 
-	\noindent
-	\emph{If}
 	Let us assume instead that $h_E$, $h_V$, and $h_Q$  are monos. XXXXX

### 2025-03-12 calco/main.tex
altro lemma

--- 2025-03-11 calco/main.tex
@@
 
+We can now prove that $\pbc$ is a class suitable to prove adhesivity with respect to it (a proof can be found in \Cref{proof:pbmono}).
+
 \begin{restatable}{lemma}{pbm}\label{lem:pbmono}
-	The class $\pbc$ is closed under composition, decomposition and it is stable under pullbacks and pushouts.
+	The class $\pbc$ contains all isomorphisms, it is closed under composition, decomposition and it is stable under pullbacks and pushouts.
 \end{restatable}
-\begin{proof}
-	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}.
-We are left with stability under pullbacks.
-Consider the diagrams below, in which the first square is a pullback with $h$ in $\pbc$.
-In particular, by \Cref{prop:eqhyp_complete}, the two halves of the diagram on the right are pullbacks and so, by \Cref{lem:pb1} the whole rectangle is a pullback too.
-
-	\[\]
-
-		\[
-	\xymatrix@C=10pt@R=10pt{&& & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'}  \\\mathcal{P} & & \mathcal{G}_1 &
-	A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
-	&& V_{\mathcal{P}} && V_1 && Q_1\\
-	 &&&&A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E}  \\
-		\mathcal{G}_2 && \mathcal{G}_3 & V_3 \ar@{>->}[rr]_{p_E} & & A_4 && V_2 && V_3 && Q_3 }
-	\]
-
-	Thus, by \Cref{lem:pb1} also the right rectangle is a pullback.
-\end{proof}
-
-In particular, we are now going to show that $\EqHyp$ is $\reg(\EqHyp)$-adhesive.
+
+We are now going to show that $\EqHyp$ is $\pbc$-adhesive.
 
@@
 	\noindent 
-	\parbox{8.5cm}{
+	\parbox{8.5cm}{\hspace{15pt}
 	For $Q'_1$, we can make a similar argument.
@@
 
-We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-
-Now, consider the cube below, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
+\smallskip \noindent 
+\parbox{8cm}{ \hspace{15pt}We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
+If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+
+	\hspace{15pt}Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
 We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
-\[\xymatrix@C=10pt@R=10pt{
-	&B_1'\ar@{>>}[dd]|(.53)\hole^(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rrrr]^{h_V'} \ar[dl]_(.6){k_V'} &&&& B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]^-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\
-	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rrrr]^(.7){p_V'} & & &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
-	&T\ar@{>->}[rrrr]|(.68)\hole_{x_1} \ar[dl]_{w} &&&& U\ar[dl]^(.4){u_1} && K_{m_3\circ q'_3} \ar@{>->}[rr]_-{k_{p'_V}} && K_{q'_4} \\
-	Y \ar@{>->}[rrrr]_{y_1} & & && Q'_4}\]
 
 	By construction we have that 
-\[m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1 = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad  m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 = m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2 \]
+	\begin{align*}
+		m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1& = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \\
+		m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 &= m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2
+		\end{align*} 
+	}\hfill\parbox{4cm}{\xymatrix@C=10pt@R=10pt{
+	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
+	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
+	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]_{w} && U\ar[dl]^(.4){u_1} \\
+	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
+}
 	but since $m_3$ and $m_2$ are monos this implies
@@
 Computing, we obtain
-\[\begin{split}
-	q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} &= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1 \\
-	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 \\
-	&= w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
-	&= w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 \\
-	&= q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 \\
-	&= q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 \\
-	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}
-\end{split}\qquad\begin{split}
-	q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} &= q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 \\
-	&= q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 \\
-	&= o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
-	&= o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 \\
-	&= q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 \\
-	&= q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 \\
-	&= q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
-\end{split}\]
-Since the previous cube has a pushout as top face, by universal property, we have
+\begin{align*}
+	&q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 = w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
+	=& w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 = q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}\\
+&q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} = q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 = o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
+	= &o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
+\end{align*}
+
+As already nopticed the square above is a pushout, hence we can conclude that
 \[
@@
 
+Having prove stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
+
 \begin{lemma}\label{lemma:van_kampen}
-	In $\EqHyp$, pushouts along regular monos are $\reg(\EqHyp)$-Van Kampen.
+	In $\EqHyp$, pushouts along arrows in $\pbc$ are $\reg(\EqHyp)$-Van Kampen.
 \end{lemma}
@@
 \begin{proof}
-	In lieu of \Cref{lemma:stab}, it is enough to proof that, given a cube as the one below, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is a regular mono,
-	the front faces are pullbacks too, where $\mathcal{G}_i = (A_i, B_i, C_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', C_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
-	\[
-	\xymatrix@C=10pt@R=6pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{t'} \\ \mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d}\\&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{t} \\\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 }
-	\]
-	By \Cref{prop:eqhyp_complete} and \Cref{cor:mono_in_EqGrph}, the following two cubes have $\mathcal{M}$-pushouts as bottom faces and pullbacks as back faces,
+
+Consider a cube as the one below on the left, with regular monos as vertical arrows,, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
+In lieu of \Cref{lemma:stab}, if we show that 	the front faces are pullbacks too we can conclude.
+
+To fix the notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
+By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
 	thus their front faces are pullbacks too.
 	\[
-	\xymatrix@C=10pt@R=6pt{&A_1'\ar[dd]|\hole_(.65){a_E}\ar[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]^{b_E} \ar[dl]_{t_E'} \\ A_3'  \ar[dd]_{c_E}\ar[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}\\&A_1\ar[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{t_E} \\A_3 \ar[rr]_{p_E} & & A_4 }
-	\qquad
-	\xymatrix@C=10pt@R=6pt{&B_1'\ar[dd]|\hole_(.65){a_V}\ar[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{t_V'} \\ B_3'  \ar[dd]_{c_V}\ar[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\&B_1\ar[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{t_V} \\B_3 \ar[rr]_{p_V} & & B_4 }
+	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\
+		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
+		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
+		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
+		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
 	\]
-	On the other hand we can consider the diagrams below, in which the inner squares are pullbacks.
-	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon C'_2\to U$, $m_3\colon C'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
-	\[\xymatrix{C'_3 \ar@{.>}[dr]^{m_3} \ar@/^.3cm/[drr]^{p'_3} \ar@/_.3cm/[ddr]_{d_3} &&& C'_2 \ar@{.>}[dr]^{m_2} \ar@/^.3cm/[drr]^{t'_3} \ar@/_.3cm/[ddr]_{d_2}\\&Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
-
-	\[\xymatrix{B'_3 \ar@{.>}[dr]^{a_3} \ar[r]^{p'_2} \ar[d]_{q'_3} &B'_4\ar[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{t'_2} \ar[d]_{q'_2} &B'_4\ar[dr]^{q'_4}\\C'_3 \ar[dr]_{d_3} &Y \ar[r]_{y_1} \ar[d]_{y_2}& C'_4\ar[d]^{d_3}&C_2' \ar[dr]_{d_2}& U \ar[d]_{u_2}\ar[r]_{u_1}& C'_4 \ar[d]^{d_3}\\&C_3 \ar[r]_{p_3}& C_4 &&C_2 \ar[r]_{t_3}& C_4 }\]
-
-	Now, notice that  $m_3$ and $m_2$ are monos because $d_3$ and $d_2$ are regular monos. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
+
+Let us now consider the diagrams below, in which the inner squares are pullbacks.	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon Q'_2\to U$, $m_3\colon Q'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
+
+\smallskip 
+\noindent 
+\parbox{5.2cm}{\hspace{15pt}Now, notice that  $m_3$ and $m_2$ are monos because $c_Q$ and $b_2$ are injections. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
 	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
 
-	Indeed, if the previous equations hold, then $C'_3$ and $C'_2$ are epi-mono factorizations of $a_3$ and $a_2$ and the thesis follows from \Cref{cor:unique} and the proof of \Cref{prop:eqhyp_complete}.
-
-	No if we compute we have:
+		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the thesis follows from \Cref{prop:eqhyp_complete}.
+	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
+\xymatrix@R=16pt{B'_3 \ar@{.>}[dr]^{a_3} \ar@{>->}[r]^{p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_Q}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }}
+
+	Now if we compute we have:
 \[\begin{split}
-		y_1\circ a_3&= q'_4\circ p'_2\\&=p'_3 \circ q'_3\\&=y_1\circ m_3\circ q'_3  
-	\end{split}\qquad \begin{split}
-		u_1\circ a_2&= q'_4\circ t'_2\\&=t'_3 \circ q'_3\\&=u_1\circ m_2\circ q'_2  
-	\end{split}\]
-	\[\begin{split}
-		y_2\circ a_3&= d_3\circ q_3'\\&=y_2\circ m_3\circ q'_3
-	\end{split}\qquad \begin{split}
-		u_2\circ a_2&= d_2\circ q_2'\\&=u_2\circ m_2\circ q'_2
+	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
+u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
+\end{split} \qquad \begin{split}
+ 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
+u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
 \end{split}\]	
@@
 \[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
-
-\begin{center}\begin{tikzpicture}
-        \begin{pgfonlayer}{nodelayer}
-                \node[style=small box](a) at (-1.8, 0){$a$};
-                \node[style=none] (aatt) at (-1.5, 0){};
-                \node[style=node](v) at (-0.9, 0){};
-                \node[style=medium box](div) at (0, 0){$/$};
-                \node[style=none](divfst) at (-0.3, -0.3){};
-                \node[style=none] (divsnd) at (-0.3, 0.3){};
-                \node[style=none] (divout) at (0.3, 0){};
-                \node[style=node] (w) at (0.9, 0){};
-        \end{pgfonlayer}
-        \begin{pgfonlayer}{edgelayer}
-                \draw(aatt.center) to (v);
-                \draw[out=-60, in=-180] (v) to (divfst.center);
-                \draw[out=60, in=-180](v) to (divsnd.center);
-                \draw(divout.center) to (w);
-        \end{pgfonlayer}
-\end{tikzpicture}
-\qquad
-\begin{tikzpicture}
-        \begin{pgfonlayer}{nodelayer}
-                \node[style=small box](a1) at (-1.8, -0.5){$a$};
-                \node[style=none] (a1att) at (-1.5, -0.5){};
-                \node[style=node](v1) at (-0.9, -0.5){};
-                \node[style=small box](a2) at (-1.8, 0.5){$a$};
-                \node[style=none] (a2att) at (-1.5, 0.5){};
-                \node[style=node](v2) at (-0.9, 0.5){};
-                \node[style=medium box](div) at (0, 0){$/$};
-                \node[style=none](divfst) at (-0.3, -0.3){};
-                \node[style=none] (divsnd) at (-0.3, 0.3){};
-                \node[style=none] (divout) at (0.3, 0){};
-                \node[style=node] (w) at (0.9, 0){};
-        \end{pgfonlayer}
-        \begin{pgfonlayer}{edgelayer}
-                \draw(a1att.center) to (v1);
-                \draw(a2att.center) to (v2);
-                \draw[out=0, in=-120] (v1) to (divfst.center);
-                \draw[out=0, in=120](v2) to (divsnd.center);
-                \draw(divout.center) to (w);
-        \end{pgfonlayer}
-        \begin{pgfonlayer}{eqlayer}
-                \draw[dashed, rounded corners] (-1.2, -0.8) rectangle (-0.6, 0.8);
-        \end{pgfonlayer}
-\end{tikzpicture}
-\qquad
-\begin{tikzpicture}
-        \begin{pgfonlayer}{nodelayer}
-                \node[style=small box](a1) at (-1.8, -0.5){$a$};
-                \node[style=none] (a1att) at (-1.5, -0.5){};
-                \node[style=node](v1) at (-0.9, -0.5){};
-                \node[style=small box](a2) at (-1.8, 0.5){$a$};
-                \node[style=none] (a2att) at (-1.5, 0.5){};
-                \node[style=node](v2) at (-0.9, 0.5){};
-                \node[style=medium box](div) at (0, 0){$/$};
-                \node[style=none](divfst) at (-0.3, -0.3){};
-                \node[style=none] (divsnd) at (-0.3, 0.3){};
-                \node[style=none] (divout) at (0.3, 0){};
-                \node[style=node] (w) at (0.9, 0){};
-        \end{pgfonlayer}
-        \begin{pgfonlayer}{edgelayer}
-                \draw(a1att.center) to (v1);
-                \draw(a2att.center) to (v2);
-                \draw[out=0, in=-120] (v1) to (divfst.center);
-                \draw[out=0, in=120](v2) to (divsnd.center);
-                \draw(divout.center) to (w);
-        \end{pgfonlayer}
-\end{tikzpicture}
-\end{center}
-
 %
@@
 
-As in the point above, uniqueness is guaranteed by faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
+As in the point aboce, uniqueness is guaranteed by faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
 	\end{enumerate}
@@
 \begin{proof}
-\emph{Only if}
-
-	\parbox{11cm}{	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos. 
-	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
-	$\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
-	is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono 
-	$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that 
-	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
-	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.}
-	\hfill
+	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
+
+	\noindent 
 	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
-
-	\noindent
-	\emph{If}
-	Let us assume instead that $h_E$, $h_V$, and $h_Q$  are monos. XXXXX
+	\hfill 	\parbox{11cm}{Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$.
+Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in $\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$.
+From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono $m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside.
+Now, notice that
+	}\hfill 
+	\[e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}\]
+	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.
 \end{proof}
@@
 }
+
+\pbm*
+
+\begin{proof}\label{proof:pbmono}
+	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}. We are left with stability under pullbacks. 
+	Let $h\colon \mathcal{G}_1\to \mathcal{G}_3$ be an arrow in $\pbc$ and $k\colon \mathcal{G}_2\to \mathcal{G}_3$ be another morphism of $\EqHyp$, with $\mathcal{G}_{i}=(E_i, V_i, Q_i, s_i, t_i, q_i)$.
+
+	Consider the diagrams below, in which the square on the left is a pullback in $\EqHyp$, with $\mathcal{P}=(E_{\mathcal{P}, V_{\mathcal{P}}}, Q_{\mathcal{P}}, s_{\mathcal{P}}, t_{\mathcal{P}}, q_{\mathcal{P}})$, and in which the right half of the right rectangle is a pullback too, so that the existence of $m_\mathcal{P}$ is guaranteed by \Cref{prop:eqhyp_complete}.
+
+	Again by \Cref{prop:eqhyp_complete} the two halves of the central rectangler are pullbacks and so, by \Cref{lem:pb1} the whole rectangle is a pullback too.
+This, in turn entails that the the whole right rectangle is a pullback and so, also its left half is a pullback (again by \Cref{lem:pb1}).
+	\[
+	\xymatrix@R=15pt{\mathcal{P} \ar[r]^{p} \ar[d]_{r}&  \mathcal{G}_1 \ar[d]^{h} &
+		V_{\mathcal{P}} \ar@/^.4cm/[rr]^{p_Q\circ q_{\mathcal{P}}} \ar[r]_{p_V} \ar@{>->}[d]_{r_V}& V_1  \ar@{>>}[r]_{q_1} \ar@{>->}[d]_{h_V}& Q_1 \ar@{>->}[d]^{h_Q}& V_{\mathcal{P}} \ar@{>>}[r]_{q_{\mathcal{P}}} \ar@{>->}[d]_{r_V} & Q_{\mathcal{P}} \ar@{>->}[dr]_{r_Q} \ar@/^.4cm/[rr]^{p_Q} \ar@{>->}[r]_{m_{\mathcal{P}}}& T \ar[r]_{t_1} \ar@{>->}[d]_{t_2} & Q_1 \ar@{>->}[d]^{h_Q}\\
+		\mathcal{G}_2 \ar[r]_{k} & \mathcal{G}_3 &   V_2  \ar@/_.3cm/[rr]_{k_Q\circ q_2}\ar[r]^{k_V}& V_3 \ar@{>>}[r]^{q_3} & Q_3 &V_2 \ar@{>>}[rr]^{q_2}&& Q_2 \ar[r]^{k_Q} & Q_3 }
+	\]
+
+	Let now $z_1\colon Z\to Q_{\mathcal{P}}$ and $z_2\colon Z\to V_2$ be two arrows such that $q_2\circ z_2=r_Q\circ z_1$. Then there exists a unique arrow $z\colon Z\to V_{\mathcal{P}}$ such that
+	\[m_{\mathcal{P}}\circ q_{\mathcal{P}}\circ z= m_{\mathcal{P}}\circ z_1 \qquad r_V\circ z=z_2\]
+	Since $m_\mathcal{P}$ is mono we conclude that $q_{\mathcal{P}}\circ z=z_1$ as wanted.
+
+	Uniqueness follows at once since $r_V$, being the pullback of $h_V$ is a mono.
+\end{proof}
 

### 2025-03-12 calco/main.tex

@@
 \begin{example}
-
-	\todo{Qua va l'esempio di Fabio}
+It is noteworthy to show that pushouts along regular monos are not stable. 
+\begin{minipage}[l]{.35\linewidth}Consider e.g. the cube aside: the vertices are just graphs without edges, and in the graphs themselves the equivalence classes 
+are denoted by encircling nodes with a dotted line. All the arrows are regular mono. It is immediate to see that the bottom face is a pushout and the side faces are pullback. Unfortunately, 
+the top face fails to be a pushout
+  \end{minipage}\hfill
+\begin{minipage}[r]{.60\linewidth}
+                \xymatrix@C=10pt@R=6pt{
+                &\emptyset \ar@{>->}[dd]|\hole_(.65){a}\ar@{>->}[rr]^{v} \ar@{>->}[dl]_{u} &&
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                                \node[style=node](v) at (0, 0){};
+                                \node[style=none] at(0, 0.5){$c$};
+		\end{pgfonlayer}
+                \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
+                \end{tikzpicture} \ar@{>->}[dd]^{b} \ar@{>->}[dl]_{y} \\
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(0, 0){};
+                        \node[style=none]at(0, 0.5){$b$};
+                \end{pgfonlayer}
+                \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
+        \end{tikzpicture}
+                \ar@{>->}[dd]_{c}\ar@{>->}[rr]^(.7){z} & &
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(-0.5, 0){};
+                        \node[style=none]at(-0.5, 0.5){$b$};
+                        \node[style=node]at(0.5, 0){};
+                        \node[style=none]at(0.5, 0.5){$c$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
+                \end{pgfonlayer}\end{tikzpicture}
+                \ar@<2ex>@{>->}[dd]_(.3){d}\\&
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(0, 0){};
+                        \node[style=none]at(0, 0.5){$a$};
+                \end{pgfonlayer}
+                \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
+        \end{tikzpicture}
+                \ar@{>->}[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && 
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(-0.5, 0){};
+                        \node[style=none]at(-0.5, 0.5){$a$};
+                        \node[style=node]at(0.5, 0){};
+                        \node[style=none]at(0.5, 0.5){$c$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
+                \end{pgfonlayer}\end{tikzpicture}
+                \ar@{>->}[dl]^{n} \\
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(-0.5, 0){};
+                        \node[style=none]at(-0.5, 0.5){$a$};
+                        \node[style=node]at(0.5, 0){};
+                        \node[style=none]at(0.5, 0.5){$b$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
+                \end{pgfonlayer}\end{tikzpicture}
+                \ar@{>->}[rr]_{g} & & 
+                \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+                        \node[style=node](v)at(0, 0){};
+                        \node[style=none]at(0, 0.5){$a$};
+                        \node[style=node]at(1, 0){};
+                        \node[style=none]at(1, 0.5){$b$};
+                        \node[style=node]at(2, 0){};
+                        \node[style=none]at(2, 0.5){$c$};
+                \end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
+                        \draw[dashed, rounded corners](-.3, 0.3) rectangle (2.3, -0.3);
+                \end{pgfonlayer}\end{tikzpicture} }
+  \end{minipage}
 \end{example}
@@
 Being a purely graphical representation, EGGS allows for redundancy and possibly ambiguity,
-so that e.g. a term such as $a \div a$ admits a few different representations as a term graph, as shown below
-%
-\[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
+so that e.g. a term such as $a / a$ admits a few different representations as a term graph, as shown below
+%
+%\[a \div a \mbox{ con 2 a sharate, con 2 a nella stessa classe di equivalenze, e con 2 a separate}\]
+
+\begin{center}\begin{tikzpicture}[baseline=(w)]
+        \begin{pgfonlayer}{nodelayer}
+                \node[style=small box](a) at (-1.8, 0){$a$};
+                \node[style=none] (aatt) at (-1.5, 0){};
+                \node[style=node](v) at (-0.9, 0){};
+                \node[style=medium box](div) at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, -0.3){};
+                \node[style=none] (divsnd) at (-0.3, 0.3){};
+                \node[style=none] (divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{edgelayer}
+                \draw(aatt.center) to (v);
+                \draw[out=-60, in=-180] (v) to (divfst.center);
+                \draw[out=60, in=-180](v) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[baseline=(w)]
+        \begin{pgfonlayer}{nodelayer}
+                \node[style=small box](a1) at (-1.8, -0.5){$a$};
+                \node[style=none] (a1att) at (-1.5, -0.5){};
+                \node[style=node](v1) at (-0.9, -0.5){};
+                \node[style=small box](a2) at (-1.8, 0.5){$a$};
+                \node[style=none] (a2att) at (-1.5, 0.5){};
+                \node[style=node](v2) at (-0.9, 0.5){};
+                \node[style=medium box](div) at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, -0.3){};
+                \node[style=none] (divsnd) at (-0.3, 0.3){};
+                \node[style=none] (divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{edgelayer}
+                \draw(a1att.center) to (v1);
+                \draw(a2att.center) to (v2);
+                \draw[out=0, in=-120] (v1) to (divfst.center);
+                \draw[out=0, in=120](v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+                \draw[dashed, rounded corners] (-1.2, -0.8) rectangle (-0.6, 0.8);
+        \end{pgfonlayer}
+\end{tikzpicture}
+\qquad
+\begin{tikzpicture}[baseline=(w)]
+        \begin{pgfonlayer}{nodelayer}
+                \node[style=small box](a1) at (-1.8, -0.5){$a$};
+                \node[style=none] (a1att) at (-1.5, -0.5){};
+                \node[style=node](v1) at (-0.9, -0.5){};
+                \node[style=small box](a2) at (-1.8, 0.5){$a$};
+                \node[style=none] (a2att) at (-1.5, 0.5){};
+                \node[style=node](v2) at (-0.9, 0.5){};
+                \node[style=medium box](div) at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, -0.3){};
+                \node[style=none] (divsnd) at (-0.3, 0.3){};
+                \node[style=none] (divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{edgelayer}
+                \draw(a1att.center) to (v1);
+                \draw(a2att.center) to (v2);
+                \draw[out=0, in=-120] (v1) to (divfst.center);
+                \draw[out=0, in=120](v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+\end{tikzpicture}
+\end{center}
 %
@@
 arrows in $\mathcal{M}$, then we can lift all the standard properties
-of the DPO approach to the category at hand. However, the structure of rules that is advanced in~\cite{DetlefsNS05},
+of the DPO approach.
+% to the category at hand. 
+However, the structure of rules that is advanced in~\cite{DetlefsNS05},
 is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity, hence in $\mathcal{M}$,
-while the second component does not necessarily belong to $\mathcal{M}$. 
-%
-Consider e.g. an EGG rule such $x \div x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}, 
-can be modelled as the DPO rule below,
-which can be applied with a match that is injective on equivalence classes to the left-most and the middle EGG
-in the picture above
-\[\mbox{to draw DPO rule, x in the same equivalence class} \]
+while the second component may not belong to $\mathcal{M}$.
+
+\noindent
+\begin{minipage}[l]{.48\linewidth}
+Consider e.g. an EGG rule such $x / x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}.
+It can be modelled as the DPO rule aside, concisely represented as the arrow $L \rightarrow R$,
+which can be applied with a match that is injective on equivalence classes to the legal EGGs
+above.
+\end{minipage}\hfill
+\begin{minipage}[r]{.60\linewidth}
+\xymatrix{        
+ \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
+                \node[style=node](v1) at (-0.9, 0.3){};
+                \node[style=node](v2) at (-0.9, -0.3){};
+                \node[style=medium box] at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, 0.3){};
+                \node[style=none](divsnd) at (-0.3, -0.3){};
+                \node[style=none](divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+        \end{pgfonlayer}        
+        \begin{pgfonlayer}{edgelayer}
+                \draw(v1) to (divfst.center);
+                \draw(v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
+                \end{pgfonlayer}\begin{pgfonlayer}{background}
+                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+                \end{pgfonlayer}
+        \end{tikzpicture}
+	\ar@{=>}[r] &
+        \begin{tikzpicture}[baseline=(nil.center)]\begin{pgfonlayer}{nodelayer}
+                \node[style=node](v1) at (-0.9, 0.3){};
+                \node[style=node](v2) at (-0.9, -0.3){};
+                \node[style=medium box] at (0, 0){$/$};
+                \node[style=none](divfst) at (-0.3, 0.3){};
+                \node[style=none](divsnd) at (-0.3, -0.3){};
+                \node[style=none](divout) at (0.3, 0){};
+                \node[style=node] (w) at (0.9, 0){};
+                \node[style=small box] at (0, -1){$1$};
+                \node[style=none](one) at (0.3, -1){};
+                \node[style=node](z) at (0.9, -1){};
+                \node[style=none](nil) at (0, -0.5){};
+        \end{pgfonlayer}        
+        \begin{pgfonlayer}{edgelayer}
+                \draw(v1) to (divfst.center);
+                \draw(v2) to (divsnd.center);
+                \draw(divout.center) to (w);
+                \draw(one.center) to (z);
+        \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+                \draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
+                \draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
+        \end{pgfonlayer}\begin{pgfonlayer}{background}
+                        \draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+        \end{pgfonlayer}\end{tikzpicture}
+}
+\end{minipage}
+
+\noindent
 The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.
@@
 	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
-
-	\noindent 
+	\parbox{11cm}{
+	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
+	$\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
+	is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono 
+	$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that 
+	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
+	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.}
+	\hfill
 	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
-	\hfill 	\parbox{11cm}{Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$.
-Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in $\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$.
-From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono $m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside.
-Now, notice that
-	}\hfill 
-	\[e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}\]
-	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.
+
+	Let us assume instead that $h_E$, $h_V$, and $h_Q$  are monos. XXXXX
 \end{proof}

### 2025-03-12 calco/main.tex
corollario 4.9

@@
 
-	Let us assume instead that $h_E$, $h_V$, and $h_Q$  are monos. XXXXX
+	Let us assume that $h_E$, $h_V$, and $h_Q$  are monos. 
+	We can build the witnesses component-wise.
+	\parbox{11cm}{It suffices to take the co-kernels of the three arrows, as done 
+	for $h_Q$ in the pushout aside. The resulting triple $\mathcal{K}$ is indeed an hypergraph 
+	with equivalence, and the components of the arrows 
+	$(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ 
+	are equalised by $h_E$, $h_V$, and $h_Q$, respectively. It is immediate to check that as
+	arrows in $\EqHyp$ they are equalised by $(h_E, h_V, h_Q)$.
+	} \hfill
+	\parbox{2cm}{
+	     \xymatrix@R=18pt{
+	        Q_\mathcal{G} \ar@{>->}[d]_{h_Q} \ar@{>->}[r]^{h_Q}& Q_\mathcal{H} \ar@{>->}[d]^{g_Q} \\
+	        Q_H \ar@{>->}[r]_{f_Q} & Q_\mathcal{{K}}
+              }
+         }   
 \end{proof}

### 2025-03-12 calco/main.tex
minima

@@
 The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.
-Such an asymmetry between and left- and right-hand side falls in the research about left-linear rules for 
-adhesive categories that has 
-been pursued e.g. in~\cite{BaldanC0G24},
+Such an asymmetry between and left- and right-hand side falls in the current research about left-linear rules for 
+adhesive categories, as pursued e.g. in~\cite{BaldanC0G24}.
 

### 2025-03-12 calco/main.tex
minima
Term graphs with closed eq

@@
 %
-We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\sigma$ as the source function and $\delta_1$ as target function, which always picks the element $1$.
+We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\Sigma$ as the source function and $\delta_1$ as target function, which always picks the element $1$.
 The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
@@
 	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
-\end{restatable}\todo{manca ancora la dimostrazione dell'implicazione da destra a sinistra}
+\end{restatable}
 
@@
                 \xymatrix@C=10pt@R=6pt{
-                &\emptyset \ar@{>->}[dd]|\hole_(.65){a}\ar@{>->}[rr]^{v} \ar@{>->}[dl]_{u} &&
+                &\emptyset \ar@{>->}[dd]|\hole \ar@{>->}[rr] \ar@{>->}[dl] &&
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
                 \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
-                \end{tikzpicture} \ar@{>->}[dd]^{b} \ar@{>->}[dl]_{y} \\
+                \end{tikzpicture} \ar@{>->}[dd] \ar@{>->}[dl] \\
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
         \end{tikzpicture}
-                \ar@{>->}[dd]_{c}\ar@{>->}[rr]^(.7){z} & &
+                \ar@{>->}[dd]\ar@{>->}[rr] & &
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
         \end{tikzpicture}
-                \ar@{>->}[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && 
+                \ar@{>->}[rr]|\hole \ar@{>->}[dl] && 
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
 \subsection{Term graphs with closed equivalence}
+
+\begin{remark}\label[remark]{sig_egg}
+	Given a signature $\Sigma = (O_\Sigma, \ari_\Sigma)$,
+	the hypergraph 
+	$R(\mathcal{G}^\Sigma) = (O_\Sigma, 1, 1, \ari_\Sigma, \delta_1, \id{1})$
+	is an object of $\egg$.
+	Indeed, if $(S, \pi_1, \pi_2)$ is the kernel pair of $\id{1}^\star \circ \ari_\Sigma$,
+	we have that $\id{1}^\star \circ \delta_1 \circ \pi_1$ and $\id{1}^\star \circ \delta_1 \circ \pi_2$ are both the contant functions of value $1$.
+\end{remark}
+
+\begin{definition}\label[definintion]{def:GEqTGs}
+	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\egg/R(\mathcal{G}^\Sigma)$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono.
+The incusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
+\end{definition}
+
 \todo{Here we must introduce $\GEqTGs$}

### 2025-03-12 calco/main.tex
term graph con equi

--- 2025-03-12 calco/main.tex
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:tlim}
 Let $\Sigma$ be an algebraic signature. Then it holds
@@
 \Cref{thm:slice-functors}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{CorradiniG05}.
-\begin{corollary}
+\begin{corollary}\label{cor:term}
 	The category $\tg$ is quasiadhesive.
@@
 
-As we have done in \Cref{sssect:hyp_alg_sign}, we can define the category of hypergraphs with equivalence labeled over an algebraic signature.
+We are now going to generalize the work done in the previous section equipping term graphs with equivalence relation. First of all we need a notion of labelling for $\EqHyp$.
 
 \begin{definition}
-	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to $\Sigma$.
-	Then the \emph{hypergraph with equivalence} associated to $\Sigma$ is $R(\mathcal{G}^\Sigma)$ and the category of hypergraphs with 
-	equivalence labeled over $\Sigma$ is the 
-	slice category $\EqHyp_\Sigma = \EqHyp/L(\mathcal{G}^\Sigma)$.
+	Let $\Sigma$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to it.
+A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\EqHyp$.
+A \emph{morphsim of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.
+
+	We will denote the resulting category by $\EqHyp_\Sigma$.
 \end{definition}
 
-By \Cref{thm:slice_functors}, we can deduce the following.
-
-\begin{proposition}
-	$\EqHyp_\Sigma$ is $\reg (\EqHyp_\Sigma)$-adhesive.
+Let $(\mathcal{H}, l)$ be an object of $\EqHyp_\Sigma$, then, since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ correponds to the arrow $(l, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G}^\Sigma)$.
+It is immediate to see that this correspondence extends to an equivalence with the slice over $R(\mathcal{G}^\Sigma)$.
+
+\begin{proposition}\label{prop:slice}
+$\EqHyp_\Sigma$ is equivalent to $\EqHyp/R(\mathcal{G}^\Sigma)$.
 \end{proposition}
 
-%We can lift the adjunction given by $T$ and $L$ to $\EqHyp_\Sigma$ and $\hyp_\Sigma$.\todo{Non capisco se è uno svarione mio o ha senso}
-
-We can define a functor $T_\Sigma: \EqHyps \to \hyps$ which sends each labeled hypergraph $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ to $T_\Sigma(l) = T(l)$, and each morphism $h = (h_E, h_V, h_C)$ onto $T_\Sigma(h) = T(h)$.
-Such functor is faithful since so is $T$, hence we have the following property.
-
-\begin{proposition}\label{prop:monos_in_eqhyps}
-	A morphism $h$ between two objects of $\EqHyps$ is a mono if and only if $T(h)$ is a mono.
+$V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
+From the second point of \Cref{thm:slice-functors,prop:forghyp,lim} we can deduce the following.
+
+\begin{proposition}\label{prop:lim}The following facts hold true:
+	\begin{enumerate}
+		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$, in particular it has all equalizers and pullbacks;
+		\item $\EqHyp_\Sigma$ is $\pbc_\Sigma$-adhesive.
+	\end{enumerate}
 \end{proposition}
 
-\begin{definition}
-	Let $\Sigma$ be an algebraic signature.
-	A labeled hypergraph with equivalence $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ is a \emph{term graph with equivalence} if $t_{\mathcal{G}}$ is mono.
-	We define category of term graphs with equivalence over $\Sigma$, denoted $\EqTG_{\Sigma}$, as the full subcategory of $\EqHyp_\Sigma$,
-	and the corresponding inclusion functor $I_{\EqTG_\Sigma}$.
+Using \Cref{cor:mono1,cor:mono2} we immediately get the following result.
+
+\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$, then:
+	\begin{enumerate}
+		\item $h$ is mono if and only if $h_E$ and $h_V$ are injective;
+		\item $h$ is a regular mono if and onky if $h_E$, $h_V$ and $h_Q$ are injective.
+	\end{enumerate}
+\end{corollary}
+
+We can now easily define term graphs with equivalence.
+
+\begin{definition}Let $\Sigma$ be an algebraic signature.
+	An object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph.
+We will denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyp_\Sigma$ so defined and by $I_{\eq}$ the correspoding inclusion functor.
  \end{definition}
 
-\begin{proposition}
-	If $l: \mathcal{G \to G}^\Sigma$ is a term graph, then $R(l)$ is a term graph with equivalence.
-\end{proposition}
-
-We have a functor $T_{\eq} : \EqTGs \to \tg$, defined to be $T_\Sigma \circ I_\eq$. Since both $T_\Sigma$ and $I_\eq$ are faithful, so is $T_\eq$.
-
-If $h: \mathcal{H \to G}$ is a mono between $l': \mathcal{H} \to L(\mathcal{G}^\Sigma)$ and $l: \mathcal{G}\to L(\mathcal{G}^\Sigma)$, then, if $l\in\EqTGs$, $l'\in\EqTGs$ as well.
-This let us deduce what follows.
-
-\begin{proposition}
-	$\EqTGs$ has equalizers, and $I_{\EqTGs}$ creates them.
-\end{proposition}
+\noindent 
+\parbox{9.5cm}{\begin{remark}\label{rem:obv}
+Let $T_\Sigma$ be  $T\circ V_\Sigma$.
+Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ if and only if $T(\mathcal{H})$ is in $\tg$.
+Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
+\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{I_\eq}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}}
+
+\begin{remark}\label{rem:t}
+	Notice that, by \Cref{cor:limcolim} and \Cref{prop:lim}, the functor $T_\Sigma$ preserves all connected limits and all colimits.
+\end{remark}
+
+ The previous remark allows us to prove an analog of \Cref{prop:tlim}. We refer the reader to \Cref{proof:term} for details.
+
+ \begin{restatable}{proposition}{trm}\label{prop:term}
+$\EqTG_{\Sigma}$ has equalizers, binary products and pullbacks and they are created by $I_\eq$.
+ \end{restatable}
+
+\noindent
+\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image trhough $S_\Sigma$ is a regular mono in $\tg$.
+Unwrapping the definition and using $\Cref{lem:reg}$, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }
+
+\smallskip 
+In particular, by \Cref{cor:term} and \Cref{lemma:stab}, $\mathcal{T}$ contains all isomorphisms, is closed under composition and decomposition and stable under pushout and pullbacks.
+
+The following proposition is now an easy corollary of \Cref{prop:push,prop:lim,rem:obv}. We provide the details in \Cref{proof:tade}.
+
+\begin{restatable}{proposition}{po}\label{prop:po}
+$\EqTG_{\Sigma}$ has all $\mathcal{T}$.pushouts, which are created by $I_{\eq}$.
+\end{restatable}
+
+\begin{corollary}\label{cor:tade}
+	$\EqTG_{\Sigma}$ is $\mathcal{T}$-adhesive.
+\end{corollary}
 
@@
 
+\trm*
+\begin{proof}\label{proof:term}
+	Let $F\colon \D\to \EqTG_{\Sigma}$ be the diagram of an equalizer, a binary product or of a pullback.
+By \Cref{prop:lim} we can consider a limiting cone $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$.
+By \Cref{rem:t} we know that $T_\Sigma$ preserves limits, thus by \Cref{rem:obv}  $(l, \{T_\Sigma(\pi_d)\}_{d\in \D})$ is limiting for $I_\Sigma\circ S_\Sigma$.
+By \Cref{prop:tlim} then $l$ is a term graph.
+We conclude, again by \Cref{rem:obv} that $(\mathcal{L}, l)$ is in $\EqTG_{\Sigma}$ and the thesis follows.
+\end{proof}
+
+\po*
+\begin{proof}\label{proof:tade}
+	Suppose that the square on the left below is a pushout in $\EqHyp_\Sigma$, with $h$ in $\mathcal{T}$.
+Then, by \Cref{rem:t} the square on the right is a pushout and by the definition of $\mathcal{T}$ and \Cref{rem:obv}, $T_\Sigma(h)$ is a regular mono in $\tg$.
+	\[\xymatrix{I_\eq(\mathcal{G}_0, l_0) \ar[r]^{k} \ar[d]_{h}& I_\eq(\mathcal{G}_1, l_1) \ar[d]^{p} &T_\Sigma (I_\eq(\mathcal{G}_0, l_0)) \ar[r]^{T_{\Sigma}(k)} \ar[d]_{T_{\Sigma}(h)}& T_\Sigma (I_\eq(\mathcal{G}_1, l_1)) \ar[d]^{T_\Sigma(p)}\\
+I_\eq(\mathcal{G}_1, l_1) \ar[r]_{q}& I_\eq(\mathcal{H}, l) & T_\Sigma(I_\eq(\mathcal{G}_1, l_1)) \ar[r]_{T_\Sigma(q)}& T_\Sigma(I_\eq(\mathcal{H}, l))}\]
+
+	We conclude using \Cref{prop:push,rem:obv}.
+\end{proof}
+
 \section{Some properties of comma categories}
@@
 
-A straightforward application of \Cref{lim} now yields the following.
+A straightforward application of \Cref{lim,colim} now yields the following.
 \begin{corollary}\label[corollary]{cor:pbapp}
-	If $\X$ has pullbacks, then for every object $X$, the slice $\X/X$ has pullbacks too.
+For eery object $\X$, $\X/X$ has all colimits and connected limits that $\X$ has. Moreover such limits and colimits are created by $\dom_X$.
+
+In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$, the slice $\X/X$ has such limits and colimits too.
 \end{corollary}

### 2025-03-12 calco/main.tex
shuffle

@@
 
-Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ which sends an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
-We can now explore some of its properties to deduce some information on the structure of $\EqHyp$.
-
-\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  The following are true:
+Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ sending an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
+We now explore some of its properties to deduce information on the structure of $\EqHyp$.
+%
+A proof is in \Cref{proof:forghyp}.
+
+\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then it holds
 	\begin{enumerate}
@@
 \end{restatable}
-A proof is provided in \Cref{proof:forghyp}.
 
@@
 
-Let us notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
-We are now going to exploit it to compute limits and colimits in $\EqHyp$.
+Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
+We  exploit it to compute limits and colimits in $\EqHyp$.
 In order to do so.
@@
 
+A proof is in \Cref{proof:regmono}.
 We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.
 
+\noindent
+\parbox{10cm}{
 \begin{definition}
-	We define $\pbc$ as the class of all regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
+	We define $\pbc$ as the class of  regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
 \end{definition}
-
-We can now prove that $\pbc$ is a class suitable to prove adhesivity with respect to it (a proof can be found in \Cref{proof:pbmono}).
+} \hfill
+	\parbox{2cm}{
+	     \xymatrix@R=18pt{
+	        V_\mathcal{G} \ar@{>>}[d]_{q_\mathcal{G}} \ar@{>->}[r]_{h_V}& V_\mathcal{H} \ar@{>>}[d]^{q_\mathcal{H}} \\
+	        Q_\mathcal{G} \ar@{>->}[r]^{h_Q} & Q_\mathcal{{H}}
+              }
+         }
+
+Now, we show that $\pbc$ is a suitable class for adhesivity. A proof is in \Cref{proof:pbmono}.
 
@@
 
-We are now going to show that $\EqHyp$ is $\pbc$-adhesive.
-
-\begin{lemma}\label{lemma:stab}
+We now show that key lemma for $\pbc$-adhesivity of $\EqHyp$ is. A proof is in \Cref{proof:pbstable}.
+
+\begin{restatable}{lemma}{pbs}\label{lemma:stab}
 	In $\EqHyp$, $\pbc$-pushouts are stable.
-\end{lemma}
-
-\begin{proof}
-	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
-	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
-By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
-	\[
-	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\
-		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
-		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
-		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
-		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
-	\]
-
-	\noindent 
-\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
-Notice, moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
-By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
-By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
-
-	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below.
-
-	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} \\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4}\]
-
-	\noindent 
-	\parbox{8.5cm}{\hspace{15pt}
-	For $Q'_1$, we can make a similar argument.
-Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ which makes the diagram aside commutative.}\hfill
-	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
-
-We have to show that the top face of the cube with which we have began is a pushout.
-Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
-Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
-\[v_E\circ p'_E=w_E \quad v_V\circ p'_V=w_V \quad v_E\circ z'_E=o_e \quad v_V\circ z'_V=o_V\]
-
-\commentato{\xymatrix@C=10pt@R=6pt{
-		&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
-		B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
-		&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
-		Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
-}}
-
-\smallskip \noindent 
-\parbox{8cm}{ \hspace{15pt}We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
-If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-
-	\hspace{15pt}Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
-We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
-
-	By construction we have that 
-	\begin{align*}
-		m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1& = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \\
-		m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 &= m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2
-		\end{align*} 
-	}\hfill\parbox{4cm}{\xymatrix@C=10pt@R=10pt{
-	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
-	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
-	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]_{w} && U\ar[dl]^(.4){u_1} \\
-	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
-}
-	but since $m_3$ and $m_2$ are monos this implies
-\[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]
-
-Computing, we obtain
-\begin{align*}
-	&q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 = w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
-	=& w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 = q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}\\
-&q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} = q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 = o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
-	= &o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
-\end{align*}
-
-As already nopticed the square above is a pushout, hence we can conclude that
-\[
-q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
-\]
-
-Now, $q'_4$ is a regular epi and so it is the coequalizer of its kernel pair, hence there exists $v_Q\colon Q'_4\to Q$ such that $v_Q\circ q'_4=q\circ v_V$ and we can conclude.
-\end{proof}
+\end{restatable}
 
@@
 By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
-	thus their front faces are pullbacks too.
+	thus their front faces are pullbacks
 	\[
@@
 
-\begin{proof}
+\begin{proof}\label{proof:regmono}
 	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
@@
 	Uniqueness follows at once since $r_V$, being the pullback of $h_V$ is a mono.
+\end{proof}
+
+\pbs*
+
+\begin{proof}\label{proof:pbstable}
+	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
+	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
+By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
+	\[
+	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\
+		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
+		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
+		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
+		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
+	\]
+
+	\noindent 
+\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
+Notice, moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
+By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
+By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
+
+	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below.
+
+	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} \\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4}\]
+
+	\noindent 
+	\parbox{8.5cm}{\hspace{15pt}
+	For $Q'_1$, we can make a similar argument.
+Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ which makes the diagram aside commutative.}\hfill
+	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
+
+We have to show that the top face of the cube with which we have began is a pushout.
+Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
+Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
+\[v_E\circ p'_E=w_E \quad v_V\circ p'_V=w_V \quad v_E\circ z'_E=o_e \quad v_V\circ z'_V=o_V\]
+
+\commentato{\xymatrix@C=10pt@R=6pt{
+		&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
+		B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
+		&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
+		Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
+}}
+
+\smallskip \noindent 
+\parbox{8cm}{ \hspace{15pt}We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
+If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+
+	\hspace{15pt}Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
+We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
+
+	By construction we have that 
+	\begin{align*}
+		m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1& = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \\
+		m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 &= m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2
+		\end{align*} 
+	}\hfill\parbox{4cm}{\xymatrix@C=10pt@R=10pt{
+	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
+	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
+	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]_{w} && U\ar[dl]^(.4){u_1} \\
+	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
+}
+	but since $m_3$ and $m_2$ are monos this implies
+\[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]
+
+Computing, we obtain
+\begin{align*}
+	&q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 = w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
+	=& w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 = q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}\\
+&q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} = q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 = o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
+	= &o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
+\end{align*}
+
+As already nopticed the square above is a pushout, hence we can conclude that
+\[
+q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
+\]
+
+Now, $q'_4$ is a regular epi and so it is the coequalizer of its kernel pair, hence there exists $v_Q\colon Q'_4\to Q$ such that $v_Q\circ q'_4=q\circ v_V$ and we can conclude.
 \end{proof}

### 2025-03-12 calco/main.tex
shuffle

@@
 Having prove stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
-
-\begin{lemma}\label{lemma:van_kampen}
+%
+A proof is found in \Cref{proof:pbvk}.
+
+\begin{restatable}{lemma}{pbvk}\label{lemma:van_kampen}
 	In $\EqHyp$, pushouts along arrows in $\pbc$ are $\reg(\EqHyp)$-Van Kampen.
-\end{lemma}
-
-\begin{proof}
-
-Consider a cube as the one below on the left, with regular monos as vertical arrows,, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
-In lieu of \Cref{lemma:stab}, if we show that 	the front faces are pullbacks too we can conclude.
-
-To fix the notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
-By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
-	thus their front faces are pullbacks
-	\[
-	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\
-		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
-		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
-		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
-		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
-	\]
-
-Let us now consider the diagrams below, in which the inner squares are pullbacks.	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon Q'_2\to U$, $m_3\colon Q'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
-
-\smallskip 
-\noindent 
-\parbox{5.2cm}{\hspace{15pt}Now, notice that  $m_3$ and $m_2$ are monos because $c_Q$ and $b_2$ are injections. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
-	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
-
-		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the thesis follows from \Cref{prop:eqhyp_complete}.
-	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
-\xymatrix@R=16pt{B'_3 \ar@{.>}[dr]^{a_3} \ar@{>->}[r]^{p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_Q}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }}
-
-	Now if we compute we have:
-\[\begin{split}
-	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
-u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
-\end{split} \qquad \begin{split}
- 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
-u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
-\end{split}\]	
-	And we have done.
-\end{proof}
+\end{restatable}
 
@@
 A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\EqHyp$.
-A \emph{morphsim of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.
-
-	We will denote the resulting category by $\EqHyp_\Sigma$.
+A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.
+
+	We denote the resulting category by $\EqHyp_\Sigma$.
 \end{definition}
@@
 
-$V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
+Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
 From the second point of \Cref{thm:slice-functors,prop:forghyp,lim} we can deduce the following.
@@
 
+\pbvk*
+
+\begin{proof}\label{proof:pbvk}
+
+Consider a cube as the one below on the left, with regular monos as vertical arrows, pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
+Given \Cref{lemma:stab}, if we show that the front faces are pullbacks too we can conclude.
+
+To fix notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
+By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
+	thus their front faces are pullbacks
+	\[
+	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\
+		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
+		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
+		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
+		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
+	\]
+
+Let us now consider the diagrams below, in which the inner squares are pullbacks.	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon Q'_2\to U$, $m_3\colon Q'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
+
+\smallskip 
+\noindent 
+\parbox{5.2cm}{\hspace{15pt}Now, notice that  $m_3$ and $m_2$ are monos because $c_Q$ and $b_2$ are injections. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
+	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
+
+		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the thesis follows from \Cref{prop:eqhyp_complete}.
+	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
+\xymatrix@R=16pt{B'_3 \ar@{.>}[dr]^{a_3} \ar@{>->}[r]^{p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_Q}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }}
+
+	Now we have done, since by computing we have
+\[\begin{split}
+	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
+u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
+\end{split} \qquad \begin{split}
+ 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
+u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
+\end{split}\]	
+%	And we have done.
+\end{proof}
+
 \trm*

### 2025-03-12 calco/main.tex
fino a 4.1 incluso

@@
 \end{corollary}
-\begin{proof}
-	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.   
-\end{proof}
+%\begin{proof}
+%	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.   
+%\end{proof}
 
@@
 Let us look at the picture below. It represent an hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
-and edges, respectively, such that  $h_1, h_2$ are constants and $h_3, h_4$ are binary operators
+and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair nodes
 	\begin{center}
@@
 
-We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
+We extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
 
@@
 
+\commentato{
 \todo{Se questo remark sotto non serve nel pezzo sulle equivalenze possiamo toglierlo}
@@
 
-\begin{proposition}\label{prop:lim}The following facts hold true:
+\begin{proposition}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then it holds
 	\begin{enumerate}
-		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$, in particular it has all equalizers and pullbacks;
+		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by $V_{\Sigma}$;
 		\item $\EqHyp_\Sigma$ is $\pbc_\Sigma$-adhesive.
@@
 
+In particular, $\EqHyp_\Sigma$ has all equalizers and pullbacks.
 Using \Cref{cor:mono1,cor:mono2} we immediately get the following result.
 
-\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$, then:
+\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then it holds
 	\begin{enumerate}
@@
 \parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image trhough $S_\Sigma$ is a regular mono in $\tg$.
-Unwrapping the definition and using $\Cref{lem:reg}$, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }
+Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }
 
@@
 
-The following proposition is now an easy corollary of \Cref{prop:push,prop:lim,rem:obv}. We provide the details in \Cref{proof:tade}.
+The following proposition is now an easy corollary of \Cref{prop:push}, \Cref{prop:lim}, and \Cref{rem:obv}. We provide the details in \Cref{proof:tade}.
 
 \begin{restatable}{proposition}{po}\label{prop:po}
-$\EqTG_{\Sigma}$ has all $\mathcal{T}$.pushouts, which are created by $I_{\eq}$.
+$\EqTG_{\Sigma}$ has all $\mathcal{T}$-pushouts, which are created by $I_{\eq}$.
 \end{restatable}

### 2025-03-12 calco/main.tex
sezine 4.2

@@
 
-Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
+Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
 From the second point of \Cref{thm:slice-functors,prop:forghyp,lim} we can deduce the following.
@@
 
-In particular, $\EqHyp_\Sigma$ has all equalizers and pullbacks.
+%In particular, $\EqHyp_\Sigma$ has all equalizers and pullbacks.
 Using \Cref{cor:mono1,cor:mono2} we immediately get the following result.
@@
 		\item $h$ is mono if and only if $h_E$ and $h_V$ are injective;
-		\item $h$ is a regular mono if and onky if $h_E$, $h_V$ and $h_Q$ are injective.
+		\item $h$ is a regular mono if and only if $h_E$, $h_V$ and $h_Q$ are injective.
 	\end{enumerate}
@@
 	An object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph.
-We will denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyp_\Sigma$ so defined and by $I_{\eq}$ the correspoding inclusion functor.
+We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyp_\Sigma$ so defined and by $I_{\eq}$ the corresponding inclusion functor.
  \end{definition}
@@
 \noindent
-\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image trhough $S_\Sigma$ is a regular mono in $\tg$.
+\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.
 Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }

### 2025-03-12 calco/main.tex
Sezione 4.2.

@@
 %
-However, despite the elegance and effectiveness and the immediate advantages of proving a category 
-to be adhesive, proving that a given category satisfies the conditions 
+However, despite the elegance and effectiveness and the immediate advantages, 
+%to be adhesive, 
+proving that a given category satisfies the conditions 
 for being adhesive can be a daunting task. For this reason,  sufficient criteria have been provided for the core 
@@
 %
-For some graph-like structures, such as those called \emph{hypergraph with equivalence} in~\cite{concur2006}, the question 
+For some structures such as \emph{hypergraphs with equivalence} in~\cite{concur2006}, the question 
 of their adhesivity has not yet been settled.
@@
 \begin{restatable}{lemma}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
-	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given. 
+	Let $f\colon X \to Y$ and $g\colon Z \to W$ be arrows admitting kernel pairs and suppose that the solid part of the four squares below is given. 
 	%
@@
 
-		Moreover, the following hold true:
+		Moreover, it holds
 		\begin{enumerate}
@@
 \parbox{7.5cm}{\begin{restatable}{lemma}{mps}\label{prop:kerset}
-	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top and bottom faces are pushout, the left face a pulllback and such that $m\colon A\mto C$ is an injection.
-Then the following are true:
-	\parbox{14cm}{\begin{enumerate}
+	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top and bottom faces are pushout, the left face a pulllback and $m\colon A\mto C$ is an injection. 
+	Then it holds
+	\begin{enumerate}
 		\item the right face of the cube is a pullback too;
 		\item the right square, made by the kernel pairs of the vertical arrows, is a pushout.
-	\end{enumerate}}
+	\end{enumerate}
 \end{restatable}}\hfill 
-\parbox{6cm}{\vspace{-1.1cm}\xymatrix@C=10pt@R=5pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
+\parbox{6cm}{\xymatrix@C=10pt@R=5pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
 
@@
 
+Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the result below follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.
+
 \begin{corollary}\label[corollary]{prop:hypadh}
@@
 \end{corollary}
-%\begin{proof}
-%	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.   
-%\end{proof}
 
@@
 	}\]
-	The category of hypergraphs with equivalences and their morphisms is denoted $\EqHyp$.
+	The category of hypergraphs with equivalence and their morphisms is denoted $\EqHyp$.
 
@@
 	Let $\Sigma$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to it.
-A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\EqHyp$.
+A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\hyp$.
 A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.
@@
 %
-In general, note that both a maximally minimally and a shared representation of an EGG exist, and for our 
+In general, note that both a maximally and a minimally shared representation of an EGG exist, and for our 
 toy example are the left-most and the middle one above, respectively. In general terms,
@@
 However, the structure of rules that is advanced in~\cite{DetlefsNS05},
-is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity, hence in $\mathcal{M}$,
-while the second component may not belong to $\mathcal{M}$.
+is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity, thus in $\pbc_\Sigma$,
+while the second component may not belong to $\pbc_\Sigma$.
 
@@
 \begin{minipage}[l]{.48\linewidth}
+\vspace{.1cm}
 Consider e.g. an EGG rule such $x / x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}.
@@
 
+\vspace{.1cm}
 \noindent

### 2025-03-13 calco/main.tex
minori

--- 2025-03-12 calco/main.tex
@@
 \end{corollary}
-%\begin{proof}
-%	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.   
-%\end{proof}
+\begin{proof}
+	By hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the thesis follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.   
+\end{proof}
 
@@
 Let us look at the picture below. It represent an hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
-and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair nodes
+and edges, respectively, such that  $h_1, h_2$ are constants and $h_3, h_4$ are binary operators
 	\begin{center}
@@
 
-We extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
+We will extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
 
@@
 
-\commentato{
 \todo{Se questo remark sotto non serve nel pezzo sulle equivalenze possiamo toglierlo}
@@
 \end{remark}
-}
 
@@
 
-Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ sending an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
-We now explore some of its properties to deduce information on the structure of $\EqHyp$.
-%
-A proof is in \Cref{proof:forghyp}.
-
-\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then it holds
+Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ which sends an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
+We can now explore some of its properties to deduce some information on the structure of $\EqHyp$.
+
+\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  The following are true:
 	\begin{enumerate}
@@
 \end{restatable}
+A proof is provided in \Cref{proof:forghyp}.
 
@@
 
-Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
-We  exploit it to compute limits and colimits in $\EqHyp$.
+Let us notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
+We are now going to exploit it to compute limits and colimits in $\EqHyp$.
 In order to do so.
@@
 
-A proof is in \Cref{proof:regmono}.
 We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.
 
-\noindent
-\parbox{10cm}{
 \begin{definition}
-	We define $\pbc$ as the class of  regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
+	We define $\pbc$ as the class of all regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
 \end{definition}
-} \hfill
-	\parbox{2cm}{
-	     \xymatrix@R=18pt{
-	        V_\mathcal{G} \ar@{>>}[d]_{q_\mathcal{G}} \ar@{>->}[r]_{h_V}& V_\mathcal{H} \ar@{>>}[d]^{q_\mathcal{H}} \\
-	        Q_\mathcal{G} \ar@{>->}[r]^{h_Q} & Q_\mathcal{{H}}
-              }
-         }
-
-Now, we show that $\pbc$ is a suitable class for adhesivity. A proof is in \Cref{proof:pbmono}.
+
+We can now prove that $\pbc$ is a class suitable to prove adhesivity with respect to it (a proof can be found in \Cref{proof:pbmono}).
 
@@
 
-We now show that key lemma for $\pbc$-adhesivity of $\EqHyp$ is. A proof is in \Cref{proof:pbstable}.
-
-\begin{restatable}{lemma}{pbs}\label{lemma:stab}
+We are now going to show that $\EqHyp$ is $\pbc$-adhesive.
+
+\begin{lemma}\label{lemma:stab}
 	In $\EqHyp$, $\pbc$-pushouts are stable.
-\end{restatable}
+\end{lemma}
+
+\begin{proof}
+	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
+	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
+By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
+	\[
+	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\
+		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
+		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
+		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
+		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
+	\]
+
+	\noindent 
+\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
+Notice, moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
+By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
+By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
+
+	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below.
+
+	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} \\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4}\]
+
+	\noindent 
+	\parbox{8.5cm}{\hspace{15pt}
+	For $Q'_1$, we can make a similar argument.
+Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ which makes the diagram aside commutative.}\hfill
+	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
+
+We have to show that the top face of the cube with which we have began is a pushout.
+Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
+Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
+\[v_E\circ p'_E=w_E \quad v_V\circ p'_V=w_V \quad v_E\circ z'_E=o_e \quad v_V\circ z'_V=o_V\]
+
+\commentato{\xymatrix@C=10pt@R=6pt{
+		&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
+		B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
+		&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
+		Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
+}}
+
+\smallskip \noindent 
+\parbox{8cm}{ \hspace{15pt}We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
+If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+
+	\hspace{15pt}Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
+We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
+
+	By construction we have that 
+	\begin{align*}
+		m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1& = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \\
+		m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 &= m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2
+		\end{align*} 
+	}\hfill\parbox{4cm}{\xymatrix@C=10pt@R=10pt{
+	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
+	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
+	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]_{w} && U\ar[dl]^(.4){u_1} \\
+	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
+}
+	but since $m_3$ and $m_2$ are monos this implies
+\[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]
+
+Computing, we obtain
+\begin{align*}
+	&q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 = w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
+	=& w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 = q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}\\
+&q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} = q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 = o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
+	= &o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
+\end{align*}
+
+As already nopticed the square above is a pushout, hence we can conclude that
+\[
+q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
+\]
+
+Now, $q'_4$ is a regular epi and so it is the coequalizer of its kernel pair, hence there exists $v_Q\colon Q'_4\to Q$ such that $v_Q\circ q'_4=q\circ v_V$ and we can conclude.
+\end{proof}
 
@@
 Having prove stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
-%
-A proof is found in \Cref{proof:pbvk}.
-
-\begin{restatable}{lemma}{pbvk}\label{lemma:van_kampen}
+
+\begin{lemma}\label{lemma:van_kampen}
 	In $\EqHyp$, pushouts along arrows in $\pbc$ are $\reg(\EqHyp)$-Van Kampen.
-\end{restatable}
+\end{lemma}
+
+\begin{proof}
+
+Consider a cube as the one below on the left, with regular monos as vertical arrows,, with pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
+In lieu of \Cref{lemma:stab}, if we show that 	the front faces are pullbacks too we can conclude.
+
+To fix the notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
+By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
+	thus their front faces are pullbacks too.
+	\[
+	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\
+		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
+		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
+		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
+		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
+	\]
+
+Let us now consider the diagrams below, in which the inner squares are pullbacks.	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon Q'_2\to U$, $m_3\colon Q'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
+
+\smallskip 
+\noindent 
+\parbox{5.2cm}{\hspace{15pt}Now, notice that  $m_3$ and $m_2$ are monos because $c_Q$ and $b_2$ are injections. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
+	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
+
+		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the thesis follows from \Cref{prop:eqhyp_complete}.
+	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
+\xymatrix@R=16pt{B'_3 \ar@{.>}[dr]^{a_3} \ar@{>->}[r]^{p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_Q}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }}
+
+	Now if we compute we have:
+\[\begin{split}
+	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
+u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
+\end{split} \qquad \begin{split}
+ 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
+u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
+\end{split}\]	
+	And we have done.
+\end{proof}
 
@@
 A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\EqHyp$.
-A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.
-
-	We denote the resulting category by $\EqHyp_\Sigma$.
+A \emph{morphsim of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.
+
+	We will denote the resulting category by $\EqHyp_\Sigma$.
 \end{definition}
@@
 
-Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
+$V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and let $\pbc_\Sigma$ be the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
 From the second point of \Cref{thm:slice-functors,prop:forghyp,lim} we can deduce the following.
 
-\begin{proposition}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then it holds
+\begin{proposition}\label{prop:lim}The following facts hold true:
 	\begin{enumerate}
-		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by $V_{\Sigma}$;
+		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$, in particular it has all equalizers and pullbacks;
 		\item $\EqHyp_\Sigma$ is $\pbc_\Sigma$-adhesive.
@@
 
-In particular, $\EqHyp_\Sigma$ has all equalizers and pullbacks.
 Using \Cref{cor:mono1,cor:mono2} we immediately get the following result.
 
-\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then it holds
+\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$, then:
 	\begin{enumerate}
@@
 \parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image trhough $S_\Sigma$ is a regular mono in $\tg$.
-Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }
+Unwrapping the definition and using $\Cref{lem:reg}$, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }
 
@@
 
-The following proposition is now an easy corollary of \Cref{prop:push}, \Cref{prop:lim}, and \Cref{rem:obv}. We provide the details in \Cref{proof:tade}.
+The following proposition is now an easy corollary of \Cref{prop:push,prop:lim,rem:obv}. We provide the details in \Cref{proof:tade}.
 
 \begin{restatable}{proposition}{po}\label{prop:po}
-$\EqTG_{\Sigma}$ has all $\mathcal{T}$-pushouts, which are created by $I_{\eq}$.
+$\EqTG_{\Sigma}$ has all $\mathcal{T}$.pushouts, which are created by $I_{\eq}$.
 \end{restatable}
@@
 
-\subsection{Hypergraph with closed equivalence}
+\subsection{E-hypergraphs}
+
+We start introducing the notion of \emph{e-hypergraphs}, hypergraphs equipped with an equivalence relation which is closed under the source and target arrow.
+This means that whenever the relations identifies the source of an hyperedge, it identifies the targets too.
+
 \begin{definition}
-	Let $\mathcal{G} = (E, V, C, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair of $q^\star \circ s$.
-	Then, $\mathcal{G}$ is an \emph{e-hypergraph} whenever $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
-	$\egg$ is the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and $I: \egg \to \EqHyp$ is the inclusion functor.
+	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
+	We will say that $\mathcal{G}$ is an \emph{e-hypergraph} if $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
+
+	We will denote by $\egg$ the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and by $I\colon \egg \to \EqHyp$ the associated inclusion functor.
 \end{definition}
@@
 \begin{lemma}
-	$\egg$ has all limits and $I$ preserves them.
+	$\egg$ has all limits and $I$ creates them.
 \end{lemma}
@@
 \end{proof}
-
-\begin{corollary}
-	$I$ creates limits.
-\end{corollary}
 
@@
 
-\begin{proof}\label{proof:regmono}
-	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
+\begin{proof}
+$(\Rightarrow)$	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
 	\parbox{11cm}{
@@
 	Uniqueness follows at once since $r_V$, being the pullback of $h_V$ is a mono.
-\end{proof}
-
-\pbs*
-
-\begin{proof}\label{proof:pbstable}
-	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
-	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
-By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
-	\[
-	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\
-		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
-		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
-		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
-		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
-	\]
-
-	\noindent 
-\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
-Notice, moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
-By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
-By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
-
-	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below.
-
-	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} \\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4}\]
-
-	\noindent 
-	\parbox{8.5cm}{\hspace{15pt}
-	For $Q'_1$, we can make a similar argument.
-Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ which makes the diagram aside commutative.}\hfill
-	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
-
-We have to show that the top face of the cube with which we have began is a pushout.
-Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
-Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
-\[v_E\circ p'_E=w_E \quad v_V\circ p'_V=w_V \quad v_E\circ z'_E=o_e \quad v_V\circ z'_V=o_V\]
-
-\commentato{\xymatrix@C=10pt@R=6pt{
-		&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
-		B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
-		&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
-		Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
-}}
-
-\smallskip \noindent 
-\parbox{8cm}{ \hspace{15pt}We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
-If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-
-	\hspace{15pt}Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
-We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
-
-	By construction we have that 
-	\begin{align*}
-		m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1& = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \\
-		m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 &= m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2
-		\end{align*} 
-	}\hfill\parbox{4cm}{\xymatrix@C=10pt@R=10pt{
-	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
-	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
-	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]_{w} && U\ar[dl]^(.4){u_1} \\
-	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
-}
-	but since $m_3$ and $m_2$ are monos this implies
-\[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]
-
-Computing, we obtain
-\begin{align*}
-	&q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 = w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
-	=& w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 = q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}\\
-&q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} = q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 = o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
-	= &o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
-\end{align*}
-
-As already nopticed the square above is a pushout, hence we can conclude that
-\[
-q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
-\]
-
-Now, $q'_4$ is a regular epi and so it is the coequalizer of its kernel pair, hence there exists $v_Q\colon Q'_4\to Q$ such that $v_Q\circ q'_4=q\circ v_V$ and we can conclude.
-\end{proof}
-
-\pbvk*
-
-\begin{proof}\label{proof:pbvk}
-
-Consider a cube as the one below on the left, with regular monos as vertical arrows, pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
-Given \Cref{lemma:stab}, if we show that the front faces are pullbacks too we can conclude.
-
-To fix notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
-By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
-	thus their front faces are pullbacks
-	\[
-	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\
-		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
-		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
-		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
-		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
-	\]
-
-Let us now consider the diagrams below, in which the inner squares are pullbacks.	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon Q'_2\to U$, $m_3\colon Q'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
-
-\smallskip 
-\noindent 
-\parbox{5.2cm}{\hspace{15pt}Now, notice that  $m_3$ and $m_2$ are monos because $c_Q$ and $b_2$ are injections. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
-	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
-
-		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the thesis follows from \Cref{prop:eqhyp_complete}.
-	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
-\xymatrix@R=16pt{B'_3 \ar@{.>}[dr]^{a_3} \ar@{>->}[r]^{p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_Q}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }}
-
-	Now we have done, since by computing we have
-\[\begin{split}
-	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
-u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
-\end{split} \qquad \begin{split}
- 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
-u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
-\end{split}\]	
-%	And we have done.
 \end{proof}

### 2025-03-13 calco/main.tex

--- 2025-03-12 calco/main.tex
@@
 \begin{proof}\label{proof:regmono}
-	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
+
+$(\Rightarrow)$	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
+
 	\parbox{11cm}{

### 2025-03-13 calco/main.tex
equa

@@
 
+\noindent
 	\parbox{11cm}{
-	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
+		\hspace{15pt}Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
 	$\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
@@
 
-	Let us assume that $h_E$, $h_V$, and $h_Q$  are monos. 
+	$(\Leftarrow)$ Suppose that $h_E$, $h_V$, and $h_Q$  are monos. 
 	We can build the witnesses component-wise.
-	\parbox{11cm}{It suffices to take the co-kernels of the three arrows, as done 
-	for $h_Q$ in the pushout aside. The resulting triple $\mathcal{K}$ is indeed an hypergraph 
-	with equivalence, and the components of the arrows 
-	$(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ 
-	are equalised by $h_E$, $h_V$, and $h_Q$, respectively. It is immediate to check that as
-	arrows in $\EqHyp$ they are equalised by $(h_E, h_V, h_Q)$.
-	} \hfill
-	\parbox{2cm}{
-	     \xymatrix@R=18pt{
-	        Q_\mathcal{G} \ar@{>->}[d]_{h_Q} \ar@{>->}[r]^{h_Q}& Q_\mathcal{H} \ar@{>->}[d]^{g_Q} \\
-	        Q_H \ar@{>->}[r]_{f_Q} & Q_\mathcal{{K}}
+
+	To do so, it suffices to build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which, by \Cref{prop:regmono}, are also pullbacks.
+	\[     \xymatrix@R=15pt{
+	E_\mathcal{G} \ar@{>->}[d]_{h_E} \ar@{>->}[r]^{h_E}&E_\mathcal{H} \ar@{>->}[d]^{g_E} &	V_\mathcal{G} \ar@{>->}[d]_{h_V} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>->}[d]^{g_V} &Q_\mathcal{G} \ar@{>->}[d]_{h_Q} \ar@{>->}[r]^{h_Q}& Q_\mathcal{H} \ar@{>->}[d]^{g_Q} \\
+		E_\mathcal{H} \ar@{>->}[r]_{f_E} & E_\mathcal{{K}} & V_H \ar@{>->}[r]_{f_V} & V_\mathcal{{K}} & Q_\mathcal{H} \ar@{>->}[r]_{f_Q} & Q_\mathcal{{K}}
 	}
-         }   
+	\]
+
+	Now, we know by \Cref{prop:com} and \Cref{colim} that there exists arrows $s,t\colon E_{\mathcal{K}}\rightrightarrows V_{\mathcal{K}}$ such that the resulting hypergraph is the cokernel pair of $(h_E, h_V)$ in $\hyp$.
+Moreover, by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi} we know that the unique arrow $q\colon V_{\mathcal{K}}\to Q_{\mathcal{K}}$
+	induced by $q_{Q}\circ q_{\mathcal{H}}$ and $f_{Q}\circ q_{\mathcal{H}}$ is a regular epi. Let thus $\mathcal{K}$ be the resulting hypergraph with equivalence.
+
+	By construction we have two arrows 	$(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ such that 
+	\[(f_E, f_V, f_Q)\circ (h_E, h_V, h_Q) =(g_E, g_V, g_Q)\circ (h_E, h_V, h_Q)\]
+
+	Now, in $\Set$ every mono is regular \cite{maclane2012sheaves}, so by the dual of \Cref{prop:reg_epi_coeq} we deduce that $h_E$, $h_V$ adn $h_Q$ are the equalizers of the arrows built above.
+By \Cref{prop:com,lim} we also know that $(h_E, h_V)$ is the equalizer in $\hyp$ of $(f_E, f_V)$ and $(g_E, g_V)$.
+Hence, if $(z_E, z_V, z_Q)\colon \mathcal{Z}\to \mathcal{H}$ is an arrow such that
+			\[(f_E, f_V, f_Q)\circ (z_E, z_V, z_Q) =(g_E, g_V, g_Q)\circ (z_E, z_V, z_Q)\]
+	then we get a unique morphism $(a_E, a_V)\colon (E_{\mathcal{Z}}, V_{\mathcal{Z}})\to (E_{\mathcal{G}}, V_{\mathcal{G}})$ such that $(h_E, h_V)\circ (a_E, a_V) =(z_E, z_V)$.
+Moreover, since $g_Q\circ z_Q=f_Q\circ z_Q$ there is a unique $a_Q\colon Q_{\mathcal{Z}}\to Q_\mathcal{G}$ such that $h_Q\circ a_Q=z_Q$.
+Thus
+	\[h_Q\circ a_Q\circ q_{\mathcal{Z}}=z_Q\circ q_{\mathcal{Z}}=q_{\mathcal{H}}\circ z_{V}=q_{\mathcal{H}}\circ h_V\circ a_V=h_Q\circ q_{\mathcal{G}}\circ a_V\]
+	Since $h_Q$ is mono we conclude that $a_Q\circ q_{\mathcal{Z}}=q_{\mathcal{G}}\circ a_V$ and we conclude.
 \end{proof}

### 2025-03-13 calco/main.tex
minori

@@
 \begin{proof}
-	Let $D: \cat{I} \to \egg$ be a diagram, with $D(i) = (A_i, B_i, C_i, s_i, t_i, q_i)$, let $(U_i, u_1^i, u_2^i)$ be the kernel pair of $q_i\circ s_i$.
-	Let now be $(A, B, C, s, t, q)$, togehter with projections $(\pi_E^i, \pi_V^i, \pi_C^i)_{i \in \cat I}$ the limit of $I \circ D$,
-	let $(U, u_1, u_2)$ be the kernel pair of $q\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ D$.
+	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, C_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
+	Let now $(A, B, C, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_C^d)_{d\in \D}$ be the limit of $I \circ F$.
+Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ D$.
 	By construction (proof of \Cref{prop:eqhyp_complete}), there exists a mono $m: C \to L$ such that $\pi_C^i = l_i \circ m$. Notice that

### 2025-03-13 calco/main.tex
minori

@@
 
-Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$.
+Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, Q, s, t, q)$ to $Q$, and a morphism $(h_E, h_V, h_Q)$ to $h_Q$.
 We  exploit it to compute limits and colimits in $\EqHyp$.
@@
 
-	Now we have done, since by computing we have
+Computing we have
 \[\begin{split}
@@
 \end{split}\]	
-%	And we have done.
+And we have done.
 \end{proof}

### 2025-03-13 calco/main.tex
minima

@@
 \parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.
-Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]^{h_Q}& Q_{\mathcal{H}}} }
+Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill
+\parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]_{h_Q}& Q_{\mathcal{H}}} }
 
@@
 \label{eggs}
-
-\todo{introduction}
+The previous section proved some adhesivity property for the categories $\EqHyp$ and $\EqTG_{\Sigma}$. We extends these results ito
+encompass equivalence classes which are closed under the target arrow, i.e. under operator composition for term graphs, thus precisely capturing EGGs.
+%
+%\todo{introduction}
 
@@
 
-We start introducing the notion of \emph{e-hypergraphs}, hypergraphs equipped with an equivalence relation which is closed under the source and target arrow.
-This means that whenever the relations identifies the source of an hyperedge, it identifies the targets too.
+We start introducing the notion of \emph{e-hypergraphs}, hypergraphs equipped with an equivalence relation which is closed under the target arrow:
+in other words, whenever the relation identifies the source of two hyperedges, it identifies their targets too.
 

### 2025-03-13 calco/main.tex
minima
minori

--- 2025-03-13 calco/main.tex
@@
 \newcommand{\pbc}{\mathsf{Pb}}
+\newcommand{\pbe}{\mathsf{ePb}}
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
@@
 
+\begin{corollary}\label{cor:eqade}
+	$\EqHyp$ is $\pbc$-adhesive.
+\end{corollary}
+
 %\input{Hypergraphs_with_equivalences}
@@
 Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
-From the second point of \Cref{thm:slice-functors,prop:forghyp,lim} we can deduce the following.
+From the second point of \Cref{thm:slice-functors,prop:eqhyp_complete,lim} we can deduce the following.
 
@@
 
+A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proof are in \Cref{proof:elim}.
+
+\begin{restatable}{lemma}{elim}\label{lem:elim}
+	$\egg$ has all limits and $I$ creates them.
+\end{restatable}
+
+\begin{corollary}\label{cor:ereg}
+	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is so in $\hyp$. 
+\end{corollary}
+
+We can now turn to pushouts.
+
 \begin{lemma}
-	$\egg$ has all limits and $I$ creates them.
-\end{lemma}
-
-\begin{proof}
-	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, C_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
-	Let now $(A, B, C, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_C^d)_{d\in \D}$ be the limit of $I \circ F$.
-Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ D$.
-	By construction (proof of \Cref{prop:eqhyp_complete}), there exists a mono $m: C \to L$ such that $\pi_C^i = l_i \circ m$. Notice that
-	\begin{align*}
-		q_i^\star \circ s_i\circ \pi^i_E\circ u_1      &= q_i^\star\circ (\pi^i_V)^\star \circ s\circ u_1\\
-		&= (\pi_C^i)^\star\circ q^\star\circ s\circ u_1\\
-		&=(\pi_C^i)^\star\circ q^\star\circ s\circ u_2\\
-		&= q_i^\star \circ s_i \circ \pi_E^i \circ u_2
-	\end{align*}
-	Then, for each $i$, there exists an arrow $a_i:U\to U_i$ making the following diagram to commute
-	\[
-	\xymatrix{
-		U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_i} & A \ar[dr]^{\pi_E^i} & \\
-		A \ar[dr]_{\pi_E^i} & U_i \ar[r]^{u_1^i} \ar[d]_{u_2^i}& A_i \ar[d]^{q_i^\star \circ s_i} \\
-		& A_i  \ar[r]_{q_i^\star \circ s_i}& C_i^\star
-	}
-	\]
-	We have then
-	\begin{align*}
-		l_i^\star\circ m^\star \circ q^\star \circ t \circ u_1    &= q_i^\star\circ (\pi_V^i)^\star \circ t \circ u_1 \\
-		&= q_i^\star \circ t_i \circ \pi_E^i \circ u_1 \\
-		&= q_i^\star \circ t_i \circ u_1^i \circ a_i \\
-		&= q_i^\star \circ t_i \circ u_2^i \circ a_i \\
-		&= q_i^\star \circ t_i \circ \pi_E^i \circ u_2 \\
-		&= q_i^\star \circ (\pi_V^i)^\star \circ t \circ u_2 \\
-		&= l_i^\star \circ m^\star \circ q^\star \circ t \circ u_2
-	\end{align*}
-	By universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$, and, since $m$ is mono, $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the thesis.
-\end{proof}
-
-\begin{corollary}
-	Let $h: \mathcal{G \to H}$ be an arrow in $\egg$. Then it is a regular mono 
-	%in $\egg$
-	if and only if $I(h)$ is a regular mono.
-	% in $\EqHyp$.
-\end{corollary}
-
-\begin{lemma}
-	Consider the following pushout square in $\EqHyp$.
+	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ a regular mono.
+If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is an e-hypergraph too.
+	following pushout square in $\EqHyp$.
 	\[\xymatrix{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{k}&\mathcal{P}}\]
-	with $m$ regular mono. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is an e-hypergraph too, and $n$ is regular mono.
+	with $m$ regular mono. 
 \end{lemma}
@@
 
-By direct application of \Cref{thm:slice-functors}, we can conclude what follows.
+\begin{corollary}\label{cor:rege}
+		An arrow $h: \mathcal{G \to H}$  is a regular mono in $\egg$ if and onlu if $I(h)$ is a regular mono in $\hyp$. 
+\end{corollary}
+
+Let now $\pbe$ be the class of all regular monos in $\egg$ which are sent to $\pbc$ by $I$.
+By definition and \Cref{lem:pbmono} such class is closed under composition, decomposition, contains all isomorphisms and it is stable under pullbacks.
+Using \Cref{cor:rege} we can also deduce that it is stable under pushouts.
+Then \Cref{thm:slice-functors,cor:eqade} yield the following.
 
 \begin{corollary}
-	$\egg$ is $\reg(\egg)$-adhesive.
+	$\egg$ is $\pbe$-adhesive.
 \end{corollary}
 
-\subsection{Term graphs with closed equivalence}
+\subsection{Labelling e-hypergraphs}
 
@@
 
+\subsection{Proofs for \Cref{eggs}}
+\elim*
+\begin{proof}\label{proof:elim}
+	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, Q_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
+	Let now $(A, B, Q, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_Q^d)_{d\in \D}$ be the limit of $I \circ F$.
+Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ F$.
+If we show that it lies in $\egg$ we are done.
+
+	By \Cref{prop:eqhyp_complete} there exists a mono $m\colon Q \mto L$ such that $\pi_Q^d = l_d \circ m$. Notice that
+	\begin{align*}
+		&q_d^\star \circ s_d\circ \pi^d_E\circ u_1  = q_d^\star\circ (\pi^d_V)^\star \circ s\circ u_1= (\pi_Q^d)^\star\circ q^\star\circ s\circ u_1\\=&(\pi_Q^d)^\star\circ q^\star\circ s\circ u_2= q_d^\star\circ (\pi^d_V)^\star\circ s\circ u_2=q_d^\star \circ s_d \circ \pi_E^d \circ u_2\\
+	\end{align*}
+
+	\noindent 
+	\parbox{9.5cm}{ \hspace{15pt}
+	Thus for each $d$ in $\D$, there exists an arrow $a_d:U\to U_i$ making the diagram on the right commutative.
+Then we have
+\begin{align*}
+	&l_d^\star\circ m^\star \circ q^\star \circ t \circ u_1    = q_d^\star\circ (\pi_V^d)^\star \circ t \circ u_1 \\
+	= &q_d^\star \circ t_d \circ \pi_E^d \circ u_1
+	= q_d^\star \circ t_d \circ u_1^d \circ a_d 
+	= q_d^\star \circ t_d \circ u_2^d \circ a_d\\ 
+	=& q_d^\star \circ t_d \circ \pi_E^d \circ u_2 = q_d^\star \circ (\pi_V^d)^\star \circ t \circ u_2 = l_d^\star \circ m^\star \circ q^\star \circ t \circ u_2
+\end{align*}}\hfill \parbox{4cm}{	\xymatrix{
+		U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_d} & A \ar[dr]^{\pi_E^d} & \\
+		A \ar[dr]_{\pi_E^d} & U_d \ar[r]^{u_1^d} \ar[d]_{u_2^d}& A_d \ar[d]^{q_d^\star \circ s_d} \\
+		& A_i  \ar[r]_{q_d^\star \circ s_d}& Q_d^\star
+	}}
+
+	By universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$.
+Since $m$ is mono we deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the thesis.
+\end{proof}
+
 \section{Some properties of comma categories}

### 2025-03-13 calco/main.tex

@@
 
-\subsection{Labelling e-hypergraphs}
+\subsection{E-Term graphs, a.k.a. EGGs}
 
@@
 	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\egg/R(\mathcal{G}^\Sigma)$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono.
-The incusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
+The inclusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
 \end{definition}

### 2025-03-13 calco/main.tex
sec 5

@@
 \newcommand{\pbe}{\mathsf{ePb}}
+\newcommand{\pbes}{\pbe_\Sigma}
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
@@
 \newcommand{\egg}{\catname{GEqHyp}}
+\newcommand{\eggs}{\egg_\Sigma}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:epo}
 	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ a regular mono.
@@
 
-\begin{remark}\label[remark]{sig_egg}
+\begin{remark}\label[remark]{rem:sig_egg}
 	Given a signature $\Sigma = (O_\Sigma, \ari_\Sigma)$,
@@
 \end{remark}
+
+\begin{definition}\label[definition]{def:label_egraphs}
+	Let $\Sigma$ be an algebraic signature, and $\mathcal{G}^\Sigma$ the hypergraph associated to it.
+	A \emph{labeled e-hypergraph} is a pait $(\mathcal{E}, l)$, where $\mathcal{E}$ is an e-hypergraph and $l: T \circ I (\mathcal{H}) \to \mathcal{G}^\Sigma$ is a morphism of $\hyp$.
+	A \emph{morphism of labeled e-hypergraphs} $(\mathcal{E}, l)\to (\mathcal{E}', l')$ is a morphism $h: \mathcal{E \to E}'$ such that $l = l' \circ (T \circ I)(h)$.
+	We denote the resulting category by $\eggs$.
+\end{definition}
+
+%Functor from GEqhyp_S to EqHyp_S
+
+With a similar argument as the one done in \Cref{prop:slice}, and by \Cref{rem:sig_egg} we get a characterization of $\eggs$.
+
+\begin{proposition}
+	The category $\eggs$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$
+\end{proposition}
+
+Consider now the functor that forgets the label $V_\eq : \eggs \to \egg$, and $\pbes$ the class of morphisms in $\eggs$ whose image through $V_\eq$ is in $\pbe$.
+From \Cref{thm:slice-functors}, \Cref{lim},  \Cref{lem:elim,lem:epo}, we can deduce what follows.
+
+\begin{proposition}\label[proposition]{prop:eadh}
+	The following facts hold true:
+	\begin{enumerate}
+	\item $\eggs$ has all limits and pushouts along regular monos, which are created by $V_\eq$;
+	\item $\eggs$ is $\pbes$-adhesive.
+	\end{enumerate}
+\end{proposition}
+
+Now, by \Cref{cor:rege,cor:mono1,cor:mono2}, we get what follows.
+
+\begin{corollary}\label{cor:emon}
+	Let $h = (h_E, h_V, h_Q)$ be an arrow in $\eggs$. Then the following holds.
+	\begin{enumerate}
+	\item $h$ is mono if and only if $h_E$ and $h_V$ are injective;
+	\item $h$ is regular mono in and only if each component of it is injective.
+	\end{enumerate}
+\end{corollary}
 

### 2025-03-13 calco/main.tex
Term graphs with closed eq

@@
 
-\begin{definition}
+\begin{definition}\label[definition]{def:ehyp1}
 	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
@@
 
-\begin{definition}\label[definintion]{def:GEqTGs}
-	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\egg/R(\mathcal{G}^\Sigma)$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono.
+We can now introduce term graphs with closed equivalences.
+
+%\begin{definition}\label[definintion]{def:GEqTGs}
+%	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\eggs$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono.
 The inclusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
+%\end{definition}
+
+\begin{definition}\label[definition]{def:GEqTGs}
+	Let $\Sigma$ be an algebraic signature.
+An object $(\mathcal{T}, l)$ of $\eggs$ is an \emph{e-term graph} if $l: T(\mathcal{T})\to \mathcal{G}^\Sigma$ is a term graph.
+We denote by $\GEqTGs$ the full subcategory of $\eggs$ so defined, and denote by $I_{\GEqTGs}$ the corresponding inclusion functor.
 \end{definition}
-
-\todo{Here we must introduce $\GEqTGs$}
+\noindent
+\parbox{8.5cm}{\begin{remark}\label[remark]{rem:inclusions}
+	The category $\GEqTGs$ is also a full subcategory of $\EqTGs$, since each object $(\mathcal{H}, l)$ is a term graph with equivalence too.
+	We denote the corresponding inclusion functor as $S_\eq$.
+Hence, we have a situation similiar to the one in \Cref{rem:obv}, as the diagram aside shows, where $T_\eq$ is the inclusion functor of \Cref{def:ehyp1} lifted to the slice category, i.e., is such that $V_\Sigma \circ T_\eq = I \circ V_\eq$.
+\end{remark}}
+	\hfill\parbox{4.5cm}{\[\xymatrix@R=20pt@C=38pt{\GEqTGs \ar[r]^{I_{\GEqTGs}}  \ar[d]_{S_\eq}& \eggs \ar[d]^{T_\eq} \\ \EqTGs \ar[r]_{I_\eq}& \EqHyp_{\Sigma}}\]}
+
+%\todo{Here we must introduce $\GEqTGs$}
 

### 2025-03-13 calco/main.tex
Update main.tex

@@
 \begin{corollary}\label{cor:ereg}
-	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is so in $\hyp$. 
+	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is so in $\EqHyp$. 
 \end{corollary}
@@
 \begin{corollary}\label{cor:rege}
-		An arrow $h: \mathcal{G \to H}$  is a regular mono in $\egg$ if and onlu if $I(h)$ is a regular mono in $\hyp$. 
+		An arrow $h: \mathcal{G \to H}$  is a regular mono in $\egg$ if and only if $I(h)$ is a regular mono in $\EqHyp$. 
 \end{corollary}

### 2025-03-13 calco/main.tex
fine

--- 2025-03-13 calco/main.tex
@@
 \newcommand{\pbe}{\mathsf{ePb}}
-\newcommand{\pbes}{\pbe_\Sigma}
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
@@
 \newcommand{\terminal}{\mathds{1}}
-\newcommand{\eg}[1]{\mathbf{EqGraph}_{\textbf {\textup{#1}}}}
-%\newcommand{\egg}[1]{\mathbf{EGG}_{\textbf {\textup{#1}}}}
+%\newcommand{\eg}[1]{\mathbf{EqGraph}_{\textbf {\textup{#1}}}}
+\newcommand{\eg}[0]{\mathbf{EGG}}
 
@@
 \newcommand{\egg}{\catname{GEqHyp}}
-\newcommand{\eggs}{\egg_\Sigma}
 
@@
 \parbox{7.5cm}{\begin{restatable}{lemma}{mps}\label{prop:kerset}
-	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top and bottom faces are pushout, the left face a pulllback and $m\colon A\mto C$ is an injection. 
-	Then it holds
+	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top face is a pushout, the left and bottom faces are pullbacks,  and $n\colon B\mto D$ is an injection. 
+	Then it holds:
 	\begin{enumerate}
@@
 %
-We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\Sigma$ as the source function and $\delta_1$ as target function, which always picks the element $1$.
+We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\Sigma$ as the source function and $\gamma_1$ as target function, which always picks the element $1$.
 The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
@@
 	An object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph.
-We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyp_\Sigma$ so defined and by $I_{\eq}$ the corresponding inclusion functor.
+We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyp_\Sigma$ so defined and by $J_{\Sigma}$ the corresponding inclusion functor.
  \end{definition}
@@
 \parbox{9.5cm}{\begin{remark}\label{rem:obv}
-Let $T_\Sigma$ be  $T\circ V_\Sigma$.
+Let $T_\Sigma$ be the functor sending $(\mathcal{H}, l)$ to $(T(\mathcal{H}), T(l))$.
 Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ if and only if $T(\mathcal{H})$ is in $\tg$.
 Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
-\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{I_\eq}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}}
+\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}}
 
@@
  \begin{restatable}{proposition}{trm}\label{prop:term}
-$\EqTG_{\Sigma}$ has equalizers, binary products and pullbacks and they are created by $I_\eq$.
+$\EqTG_{\Sigma}$ has equalizers, binary products and pullbacks and they are created by $J_\Sigma$.
  \end{restatable}
@@
 \noindent
-\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $I_\eq$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.
+\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $J_\Sigma$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.
 Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill
@@
 \begin{restatable}{proposition}{po}\label{prop:po}
-$\EqTG_{\Sigma}$ has all $\mathcal{T}$-pushouts, which are created by $I_{\eq}$.
+$\EqTG_{\Sigma}$ has all $\mathcal{T}$-pushouts, which are created by $J_{\Sigma}$.
 \end{restatable}
@@
 
-We can now turn to pushouts.
-
-\begin{lemma}\label{lem:epo}
-	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ a regular mono.
-If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is an e-hypergraph too.
-	following pushout square in $\EqHyp$.
-	\[\xymatrix{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{k}&\mathcal{P}}\]
-	with $m$ regular mono. 
-\end{lemma}
-
+We can now turn to pushouts. We refer again the reader to \Cref{proof:epo} for the details.
+
+\noindent
+\parbox{11.5cm}{\begin{restatable}{lemma}{epo}\label{lem:epo}
+	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ an arrow in $\pbc$.
+If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is an object of $\egg$ too.
+\end{restatable}}\hfill 
+\parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
+
+\commentato{ 
+\begin{restatable}{corollary}{rege}\label{cor:rege}
+		An arrow $h\colon \mathcal{G \to H}$  is a regular mono in $\egg$ if and only if $I(h)$ is a regular mono in $\hyp$.
+In particular a morphism of $\egg$ is a regular mono if and only if all its components are injections.
+\end{restatable}
 \begin{proof}
-	Let $\mathcal{P} = (A, B, C, s, t, q)$, $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, and let $(U, u_1, u_2)$ the kernel pair of $q^\star \circ s$ .
-	Consider then the following situation.
-	\[\xymatrix@C=10pt@R=6pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar[dl]_{k_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){k_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{C_1^\star}\ar[rr]|\hole^(.65){h_C^\star}\ar[dl]^{m_C^\star} && {C_2^\star} \ar[dl]^{n_C^\star} \\{C_3^\star} \ar[rr]_{k_C^\star} & & C^\star}\]
-	Since $m$ is regular mono, $m_E$ is mono ({\color{red}{inserire citazione}}).
-	Then, by construction, the top face is a pushout, and since $\Set$ is adhesive, by \Cref{lem:mpo} , the square below is a pushout.
-	\[\xymatrix{K_1\ar[r]^{f_k}\ar[d]_{f_m}&K_2\ar[d]^{f_n}\\K_3\ar[r]_{f_k}&U}\]
-	Computing, we have
-	\[
-	\begin{split}
-		q^\star \circ t \circ u_1 \circ f_n &= q^\star \circ t \circ n_E \circ \pi_2^1 \\ &= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^1 \\&= n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^2 \\&=q^\star \circ t \circ u_2 \circ f_n
-	\end{split}
-	\qquad
-	\begin{split} q^\star \circ t \circ u_1 \circ f_k &= q^\star \circ t \circ k_E \circ \pi_3^1 \\ &= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^1 \\&= k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^2 \\&=q^\star \circ t \circ u_2 \circ f_k
-	\end{split}
-	\]
-	By universal property of pushouts, we deduce $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the thesis follows.
+	contenuto...
 \end{proof}
-
-\begin{corollary}\label{cor:rege}
-		An arrow $h: \mathcal{G \to H}$  is a regular mono in $\egg$ if and onlu if $I(h)$ is a regular mono in $\hyp$. 
-\end{corollary}
-
-Let now $\pbe$ be the class of all regular monos in $\egg$ which are sent to $\pbc$ by $I$.
+}
+
+Let now $\pbe$ be the class of arrows in $\egg$ which are sent to $\pbc$ by $I$.
 By definition and \Cref{lem:pbmono} such class is closed under composition, decomposition, contains all isomorphisms and it is stable under pullbacks.
-Using \Cref{cor:rege} we can also deduce that it is stable under pushouts.
+Using \Cref{lem:pbmono,lem:epo} we can also deduce that it is stable under pushouts.
 Then \Cref{thm:slice-functors,cor:eqade} yield the following.
 
-\begin{corollary}
+\begin{corollary}\label{cor:pbe}
 	$\egg$ is $\pbe$-adhesive.
@@
 
-\subsection{E-Term graphs, a.k.a. EGGs}
-
-\begin{remark}\label[remark]{rem:sig_egg}
+\subsection{E-term graphs, a.k.a. EGGs}
+
+We turn now to the labelled context.
+
+\begin{definition} We say that an object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
+We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs.
+We will denote by $j_\Sigma$ the corresponding inclusion functor .
+\end{definition}
+
+To prove some adhesivity property of $\egg_\Sigma$ let us begin with the following elementary, but useful observation.
+
+\begin{remark}\label{rem:algegg}
 	Given a signature $\Sigma = (O_\Sigma, \ari_\Sigma)$,
 	the hypergraph 
-	$R(\mathcal{G}^\Sigma) = (O_\Sigma, 1, 1, \ari_\Sigma, \delta_1, \id{1})$
+	$R(\mathcal{G}^\Sigma) = (O_\Sigma, 1, 1, \ari_\Sigma, \gamma_1, \id{1})$
 	is an object of $\egg$.
-	Indeed, if $(S, \pi_1, \pi_2)$ is the kernel pair of $\id{1}^\star \circ \ari_\Sigma$,
-	we have that $\id{1}^\star \circ \delta_1 \circ \pi_1$ and $\id{1}^\star \circ \delta_1 \circ \pi_2$ are both the contant functions of value $1$.
+	Indeed, under the identification of $1^\star$ with $\mathbb{N}$, the kernel $(S, \pi_1, \pi_2)$  of $\id{\mathbb{N}} \circ \ari_\Sigma$, is given by
+	\[S:=\{(o_1, o_2)\in O_\Sigma \times O_\Sigma \mid \ari_\Sigma(o_1)=\ari_\Sigma(o_2)\}\]
+	equipped with the two projections.
+Onthe other hand $\id{\mathbb{N}} \circ \gamma_1 \circ \pi_1$ and $\id{\mathbb{N}}\circ \gamma_1 \circ \pi_2$ are both the function $O_\Sigma \to \mathbb{N}$ constant in $1$.
 \end{remark}
 
-\begin{definition}\label[definition]{def:label_egraphs}
-	Let $\Sigma$ be an algebraic signature, and $\mathcal{G}^\Sigma$ the hypergraph associated to it.
-	A \emph{labeled e-hypergraph} is a pait $(\mathcal{E}, l)$, where $\mathcal{E}$ is an e-hypergraph and $l: T \circ I (\mathcal{H}) \to \mathcal{G}^\Sigma$ is a morphism of $\hyp$.
-	A \emph{morphism of labeled e-hypergraphs} $(\mathcal{E}, l)\to (\mathcal{E}', l')$ is a morphism $h: \mathcal{E \to E}'$ such that $l = l' \circ (T \circ I)(h)$.
-	We denote the resulting category by $\eggs$.
-\end{definition}
-
-%Functor from GEqhyp_S to EqHyp_S
-
-With a similar argument as the one done in \Cref{prop:slice}, and by \Cref{rem:sig_egg} we get a characterization of $\eggs$.
-
-\begin{proposition}
-	The category $\eggs$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$
-\end{proposition}
-
-Consider now the functor that forgets the label $V_\eq : \eggs \to \egg$, and $\pbes$ the class of morphisms in $\eggs$ whose image through $V_\eq$ is in $\pbe$.
-From \Cref{thm:slice-functors}, \Cref{lim},  \Cref{lem:elim,lem:epo}, we can deduce what follows.
-
-\begin{proposition}\label[proposition]{prop:eadh}
-	The following facts hold true:
+\Cref{rem:algegg} now implies at once the following result.
+\begin{proposition}\label{prop:varie}
+	Let $\Sigma$ be an algebraic signature. Then the following hold true:
 	\begin{enumerate}
-	\item $\eggs$ has all limits and pushouts along regular monos, which are created by $V_\eq$;
-	\item $\eggs$ is $\pbes$-adhesive.
+		\item $\egg_\Sigma$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$.
+		\item There exists a functor $W_\Sigma \colon \egg_\Sigma\to \Sigma$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
 	\end{enumerate}
@@
 
-Now, by \Cref{cor:rege,cor:mono1,cor:mono2}, we get what follows.
-
-\begin{corollary}\label{cor:emon}
-	Let $h = (h_E, h_V, h_Q)$ be an arrow in $\eggs$. Then the following holds.
-	\begin{enumerate}
-	\item $h$ is mono if and only if $h_E$ and $h_V$ are injective;
-	\item $h$ is regular mono in and only if each component of it is injective.
-	\end{enumerate}
+Let $\pbe_\Sigma$ be the class of morphisms in $\egg_\Sigma$ whose image in $\egg$ lies in $\pbe$.
+Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $j_\Sigma$ is in $\pbc_\Sigma$.
+
+By \Cref{thm:slice-functors} we get the following.
+
+\begin{corollary}\label{cor:eggade1}
+	$\egg_\Sigma$ is $\pbe_\Sigma$-adhesive.
 \end{corollary}
 
+We turn now to term graphs with equivalence.
+
 \begin{definition}\label[definintion]{def:GEqTGs}
-	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\egg/R(\mathcal{G}^\Sigma)$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono.
-The inclusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
+	Given a signature $\Sigma$,  we say that an object $(\mathcal{H}, l)$ of $\EqTG_{\Sigma}$ is a \emph{e-term graph} if $\mathcal{H}$ is an e-hypergraph.
+We define the category $\eg$ as the full subcategory of $\EqTG_{\Sigma}$ given by e-term graphs and denote by $k_\Sigma$ the corresponding inclusion.
 \end{definition}
 
-\todo{Here we must introduce $\GEqTGs$}
+\begin{remark}
+	By definition we also have an inclusion functor $K_\Sigma\colon \eg\to \egg_\Sigma$.
+\end{remark}
+
+\noindent 
+\parbox{7.5cm}{\begin{remark}
+	Now that we have introduced all the characters of this work, it is worth to give a visual map of all the categories that we have introduced in this paper and of the relationships between them.
+We will use the curved arrows to denote full and faithful inclusions.
+\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{K_\Sigma} \ar@{^{(}->}[d]_{k_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{j_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
+
+We can now prove our last three results. The interested reader can find the proof in \Cref{proof:tlim}.
+
+\begin{restatable}{proposition}{limt}\label{prop:limt}
+	$\eg$ has equalizer, binary products and pullbacks and they are created by $k_\Sigma$.
+\end{restatable}
+
+Let now $\mathcal{T}_\Sigma$ be the class of morphisms of $\eg$ which are sent by $k_\Sigma$ to the class $\mathcal{T}$. Then \Cref{colim,lem:epo,prop:po} allow us to deduce the following result.
+
+\begin{restatable}{proposition}{pot}\label{prop:pot}
+	$\eg$ has $\mathcal{T}_\Sigma$-pushouts which are created by $k_\Sigma$.
+\end{restatable}
+
+Reasoning as in the previous sections, \Cref{prop:limt,prop:pot} now give us the following.
+
+\begin{corollary}
+	$\eg$ is $\mathcal{T}_\Sigma$-adhesive.
+\end{corollary}
 
@@
 \begin{proof}\label{proof:kerset}
-	We can start noticing that $m'$, being the pullback of $m$ is mono too.
-This, in turn, entails that $n$ and $n'$ are mono too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.
+	We can start noticing that $m$, being the pullback of $n$ is mono too.
+This, in turn, entails that $m'$, being the pullback of $m$, is mono, and so $n'$ is injective too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.
 
@@
 	Let $\iota' \colon E'\mto C'$ and $\iota\colon E\to C$ be the inclusions of the complement of the images of of $m'$ and $m$ respectively .
-By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ and $(D, \{n, g\circ \iota\})$ are coproducts.
+By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ is a coproduct.
 We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}
@@
 
-		By adhesivity of $\Set$ and \Cref{prop:regmono} the bottom face of the given cube is a pullback, therefore there exists an arrow $u\colon T_0\to A$ such that 
+		By hypothesis the bottom face of the given cube is a pullback, therefore there exists an arrow $u\colon T_0\to A$ such that 
 		\[f\circ u=b\circ t_2\circ l_0 \qquad m\circ u=c\circ \iota'\circ h_0\]
@@
 \begin{proof}\label{proof:pbmono}
-	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability under pushouts is the first point of \Cref{prop:kerset}. We are left with stability under pullbacks. 
+	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability follows from the first point of \Cref{prop:kerset} because pushouts along injections are also pullbacks by \Cref{prop:regmono}.
+We are left with stability under pullbacks.
 	Let $h\colon \mathcal{G}_1\to \mathcal{G}_3$ be an arrow in $\pbc$ and $k\colon \mathcal{G}_2\to \mathcal{G}_3$ be another morphism of $\EqHyp$, with $\mathcal{G}_{i}=(E_i, V_i, Q_i, s_i, t_i, q_i)$.
@@
 Then, by \Cref{rem:t} the square on the right is a pushout and by the definition of $\mathcal{T}$ and \Cref{rem:obv}, $T_\Sigma(h)$ is a regular mono in $\tg$.
-	\[\xymatrix{I_\eq(\mathcal{G}_0, l_0) \ar[r]^{k} \ar[d]_{h}& I_\eq(\mathcal{G}_1, l_1) \ar[d]^{p} &T_\Sigma (I_\eq(\mathcal{G}_0, l_0)) \ar[r]^{T_{\Sigma}(k)} \ar[d]_{T_{\Sigma}(h)}& T_\Sigma (I_\eq(\mathcal{G}_1, l_1)) \ar[d]^{T_\Sigma(p)}\\
-I_\eq(\mathcal{G}_1, l_1) \ar[r]_{q}& I_\eq(\mathcal{H}, l) & T_\Sigma(I_\eq(\mathcal{G}_1, l_1)) \ar[r]_{T_\Sigma(q)}& T_\Sigma(I_\eq(\mathcal{H}, l))}\]
+	\[\xymatrix{J_\Sigma(\mathcal{G}_0, l_0) \ar[r]^{k} \ar[d]_{h}& J_\Sigma(\mathcal{G}_1, l_1) \ar[d]^{p} &T_\Sigma (J_\Sigma(\mathcal{G}_0, l_0)) \ar[r]^{T_{\Sigma}(k)} \ar[d]_{T_{\Sigma}(h)}& T_\Sigma (J_\Sigma(\mathcal{G}_1, l_1)) \ar[d]^{T_\Sigma(p)}\\
+J_\Sigma(\mathcal{G}_1, l_1) \ar[r]_{q}& J_\Sigma(\mathcal{H}, l) & T_\Sigma(J_\Sigma(\mathcal{G}_1, l_1)) \ar[r]_{T_\Sigma(q)}& T_\Sigma(J_\Sigma(\mathcal{H}, l))}\]
 
@@
 	\noindent 
-	\parbox{9.5cm}{ \hspace{15pt}
+	\parbox{9.5cm}{ \vspace{-.8cm}\hspace{15pt}
 	Thus for each $d$ in $\D$, there exists an arrow $a_d:U\to U_i$ making the diagram on the right commutative.
@@
 	=& q_d^\star \circ t_d \circ \pi_E^d \circ u_2 = q_d^\star \circ (\pi_V^d)^\star \circ t \circ u_2 = l_d^\star \circ m^\star \circ q^\star \circ t \circ u_2
-\end{align*}}\hfill \parbox{4cm}{	\xymatrix{
+\end{align*}}\hfill \parbox{4cm}{\vspace{-1cm}	\xymatrix@R=20pt{
 		U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_d} & A \ar[dr]^{\pi_E^d} & \\
@@
 
+\begin{remark}\label{rem:kleene}
+	Let $\delta_1\colon 1\to \mathbb{N}$ be the arrow which picks $1\in \mathbb{N}$. Consider the
+
+	\noindent
+	\parbox{11.5cm}{ inclusion $v_1\colon X\to X^\star $  defined by the first point of \Cref{prop:fact}.
+By extensivity we know that the square on the right is a pullback.}\hfill \parbox{4cm}{\vspace{-.5cm}\xymatrix@R=15pt{X \ar[r]_{!_{X}} \ar[d]_{!_{X}}& 1\ar[d]^{\delta_1} \\1 \ar[r]^{\lgh_{X}} & \mathbb{N}} }
+
+	\noindent 
+	\parbox{4cm}{\vspace{-.2cm} \xymatrix@C=15pt@R=1pt{&X\ar[dd]|\hole_(.65){!_{X}}\ar@{->}[rr]^{!_X} \ar@{>}[dl]_{f} && 1 \ar[dd]^{\delta_1} \ar[dl]^{\id{1}} \\ Y  \ar[dd]_{!_Y}\ar@{>}[rr]^(.7){!_Y} & & 1 \ar[dd]_(.3){\delta_1}\\&X^\star\ar@{>->}[rr]|(.53)\hole^(.70){\lgh_{X}} \ar@{>->}[dl]_{f^\star} && \mathbb{N} \ar[dl]^{\id{N}} \\Y^\star \ar@{>->}[rr]_{\lgh_{Y}} & & \mathbb{N}}}\hfill \parbox{9.5cm}{\vspace{-.3cm}\hspace{15pt}Let now $f\colon X\to Y$ be an arrow.
+Then we can build the cube aside which, by what we have just observed above, has pullbacks as back, front and right faces.
+Thus, by \Cref{lem:pb1} its left face is a pullback too.}
+
+\end{remark}
+
+\noindent
+\parbox{11.5cm}{
+\epo*}\hfill 
+\parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
+\begin{proof}\label{proof:epo}
+	Let $\mathcal{P} $ be $(A, B, C, s, t, q)$ and consider the kernel pair $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, for $i\in \{1, 2, 3\}$.
+Let also $(U, u_1, u_2)$ be the kernel pair of $q^\star \circ s$.
+
+	\noindent
+	\parbox{10cm}{\hspace{15pt}Consider now the cube on the right.
+By hypothesis and \Cref{rem:kleene} its left face is a pullback, moreover its bottom face, while not a pushout it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.}\hfill \parbox{3cm}{\xymatrix@C=10pt@R=2pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar@{>->}[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar@{>.>}[dl]_(.6){n_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){z_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{Q_1^\star}\ar[rr]|\hole^(.65){h_Q^\star}\ar@{>->}[dl]_{m_Q^\star} && {Q_2^\star} \ar@{>->}[dl]^{n_Q^\star} \\{Q_3^\star} \ar[rr]_{z_Q^\star} & & Q^\star}}
+
+	\noindent
+	\parbox{2cm}{\vspace{-.25cm}\xymatrix@R=15pt{K_1\ar[r]_{k_{h_E}}\ar@{>->}[d]_{k_{m_E}}&K_2\ar@{>->}[d]^{k_{n_E}}\\K_3\ar[r]^{k_{z_E}}&U}}
+\hfill \parbox{11.5cm}{ \vspace{-.25cm}\hspace{15pt}By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout.
+Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout.}
+		Computing we obtain
+	\begin{align*}
+		q^\star \circ t \circ u_1 \circ f_n &= q^\star \circ t \circ n_E \circ \pi_2^1 = n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^1 = n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^2 =q^\star \circ t \circ u_2 \circ f_n \\
+		q^\star \circ t \circ u_1 \circ f_k &= q^\star \circ t \circ k_E \circ \pi_3^1 = k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^1 = k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^2 =q^\star \circ t \circ u_2 \circ f_k
+	\end{align*}
+	We can therefore deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the thesis follows.
+\end{proof}
+
+\limt*
+\begin{proof}\label{proof:tlim}
+Let $F\colon \D\to \eg$ be a diagram of one of the sapes mentioned in the proposition.
+Let $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$ be a limiting cone for $k_\Sigma \circ F$.
+By \Cref{lim,prop:term,proof:elim} we know that $\mathcal{L}$ is an e-termgraph and we can conclude.
+\end{proof}
+
 \section{Some properties of comma categories}
@@
 	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comma{L}{R}$ is the category in which
-	\begin{itemize}
+
+\noindent
+\parbox{10.5cm}{\vspace{-.5cm}\begin{itemize}
 		\item objects are triples $(A, B, f)$ with $A\in \A$, $B\in \B$, and $f\colon L(A)\rightarrow R(B)$; 
-		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the following diagram commutes
-		\[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}\]
-	\end{itemize}
+		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the diagram aside commutes\end{itemize}}\hfill
+	\parbox{4cm}{\vspace{-.1cm}\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}}
 \end{definition} 
@@
 Given $L\colon \A\to \X$ and $R\colon \B\to \X$, we can also consider their duals $L^{op}\colon \A^{op}\to \X^{op}$ and $R^{op}\colon \B^{op}\to \X^{op}$.
-An arrow $f\colon L(A)\to R(B)$ in $\X$ is the same ting as an arrow $f\colon R^{op}(B)\to L^{op}(A)$ in $\X^{op}$, thus $\left(\comma{L}{R}\right)$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
-Moreover, the commutativity in  $\X$ of the square
-\[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}\]
-is tantamount to the commutativity in $\X^{op}$ of the square 
-\[\xymatrix@C=25pt{ R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ L(A') \ar[r]_{L(h)}  & L(A) }\]
+An arrow $f\colon L(A)\to R(B)$ in $\X$ is the same thing as an arrow $f\colon R^{op}(B)\to L^{op}(A)$ in $\X^{op}$.
+Thus $\comma{L}{R}$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
+Moreover  of the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$.
+\[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g} & R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B') & L(A') \ar[r]_{L(h)}  & L(A)}\]
+
 Summing up we have just proved the following fact.
@@
 By hypothesis $\left(L(A), \{L\left(a_D\right)\}_{D\in \D}\right)$ is colimiting for $L\circ U_L\circ F$.
-Now, if we define
-	\[F(D):=(A_D, B_D, f_D)\]
+Now, if we define $F(D):=(A_D, B_D, f_D)$
 	then we have arrows $R(a_i)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comma{L}{R}$ and so
 	\begin{align*}
-		R\left(b_{D'}\right)\circ f_{D'}\circ L(U_L(F(d)))&=R\left(b_{D'}\right)\circ R\left(U_R\left(F(d)\right)\right)\circ f_D\\&=R\left(b_{D'}\circ U_R\left(F(d)\right)\right)\circ f_D\\&=R\left(b_D\right)\circ f_D
+		&R\left(b_{D'}\right)\circ f_{D'}\circ L(U_L(F(d)))=R\left(b_{D'}\right)\circ R\left(U_R\left(F(d)\right)\right)\circ f_D\\=&R\left(b_{D'}\circ U_R\left(F(d)\right)\right)\circ f_D=R\left(b_D\right)\circ f_D
 	\end{align*}
-	Thus there exists $f\colon L(A)\rightarrow R(B)$ such that
-	\[\xymatrix@C=35pt{ L(A_D) \ar[r]^{L(a_D)} \ar[d]_{f_D}& L(A) \ar[d]^{f}\\ R(B_D) \ar[r]_{R(b_D)} &R(B)}\]
+
+	\noindent \parbox{10cm}{
+	\hspace{15pt}Thus there exists $f\colon L(A)\rightarrow R(B)$ fitting in the diagram on the right.
 Notice that $f$ is the unique arrow in $\X$ wich makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comma{L}{R}$.
-If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.
+If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.}\hfill
+	\parbox{4cm}{\xymatrix@C=35pt@R=15pt{ L(A_D) \ar[r]^{L(a_D)} \ar[d]_{f_D}& L(A) \ar[d]^{f}\\ R(B_D) \ar[r]_{R(b_D)} &R(B)}}
 
@@
 	\begin{align*}
-		\left(a_{D'}, b_{D'}\right)\circ F(d)&=	\left(a_{D'}, b_{D'}\right)\circ \left(U_L(F(d)), U_R(F(d))\right)\\&=\left( a_{D'}\circ U_L(F(d)),  b_{D'}\circ U_R(F(d)) \right)\\&=\left(a_D, b_D\right)
+		&\left(a_{D'}, b_{D'}\right)\circ F(d)=	\left(a_{D'}, b_{D'}\right)\circ \left(U_L(F(d)), U_R(F(d))\right)\\=&\left( a_{D'}\circ U_L(F(d)),  b_{D'}\circ U_R(F(d)) \right)=\left(a_D, b_D\right)
 	\end{align*}
+
 	For the colimiting property, let $\left((X, Y, g), \left\{\left(x_D, y_D\right)\right\}_{D\in \D}\right)$ be another cocone on $F$.
@@
 	\begin{align*}
-		R(y)\circ f\circ L(a_D)&=R(y)\circ R\left(b_D\right)\circ f_D\\&=R\left(y\circ b_D\right)\circ f_D\\&=R\left(y_D\right)\circ f_D\\&= g\circ L\left(x_D\right)\\&=g\circ L\left(x\circ a_D\right)\\&=g\circ L(x)\circ L\left(a_D\right)
+		&R(y)\circ f\circ L(a_D)=R(y)\circ R\left(b_D\right)\circ f_D=R\left(y\circ b_D\right)\circ f_D\\=&R\left(y_D\right)\circ f_D= g\circ L\left(x_D\right)=g\circ L\left(x\circ a_D\right)=g\circ L(x)\circ L\left(a_D\right)
 	\end{align*}
-	from which it follows  that the following diagram commutes.
-	\[\xymatrix@C=35pt{L(A)\ar[d]_{f} \ar[r]^{L(x)} & X \ar[d]^{g}\\ R(B) \ar[r]_{R(y)}& Y}\]
-	This shows that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ and the thesis follows.    
+	from which it follows  that $g\circ L(x)=R(y)\circ f$ as wanted.
 \end{proof}
@@
 \begin{proof}
-	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the following square is a pullback in $\comma{L}{R}$
-	\[\xymatrix@C=50pt{(A, B, f)  \ar[r]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}& (A, B, f)  \ar[d]^{(h,k)} \\ (A, B, f)  \ar[r]_{(h,k)}& (A', B', g) }\]
-	Using \Cref{lim} we deduce that the following two squares are pullbacks in $\A$ and $\B$.
-	\[\xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
-	From which it follows that $h$ and $k$ are monos.
+	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the first rectangle below is a pullback in $\comma{L}{R}$.
+By \Cref{lim} then also the other two squares are pullbacks, respectively in $\A$ and $\B$, proving that both $h$ and $k$ are monos.
+	\[\xymatrix{(A, B, f)  \ar[rr]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}&& (A, B, f)  \ar[d]^{(h,k)}& A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ (A, B, f)  \ar[rr]_{(h,k)}&& (A', B', g) &A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
 
 	\smallskip\noindent 
-	$(\Leftarrow)$ Since $h$ and $k$ are monos then we have two pullback squares 	
-	\[\xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
-	By \Cref{lim} this implies that 
-	\[\xymatrix@C=50pt{(A, B, f)  \ar[r]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}& (A, B, f)  \ar[d]^{(h,k)} \\ (A, B, f)  \ar[r]_{(h,k)}& (A', B', g) }\]
-	is a pullback in $\comma{L}{R}$ and we are done.   
+	\parbox{4cm}{ \xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}}\hfill \parbox{8.5cm}{$(\Leftarrow)$ Since $h$ and $k$ are monos then we have two pullback squares on the left.
+Thus by \Cref{lim} the pullback of $(h,k)$ along itself has isomorphisms as projections and so $(h,k)$ is mono.
+\qedhere}
+
 \end{proof}
@@
 \begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{B})$, where $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
-Consider $\id{B}\colon B\to U_R(\Delta(B))$ be the identity, and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given.
-By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, since $L$ preserves initial objects, the following square commutes.
-	\[\xymatrix@C=30pt{L(0) \ar[r]^{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B')}\]
+Consider $\id{B}\colon B\to U_R(\Delta(B))$ be the
+
+	\noindent 
+	\parbox{10cm}{\vspace{-.2cm}identity, and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given.
+By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, since $L$ preserves initial objects, the square aside commutes.}\hfill
+	\parbox{2cm}{\vspace{-.1cm}\xymatrix@C=30pt@R=15pt{L(0) \ar[r]_{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]^{R(k)}& R(B')}}
 	Thus $(h,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$	such that $U_R(h,k)=k$.   
@@
 
-	\begin{itemize}
-		\item The \emph{ slice category over $X$} is the category $\X/X$ which has as objects arrows $f\colon Y\to X$ and  in which an arrow $h\colon f\to g$ is $h\colon Y\to Y'$ in $\X$ such that the following triangle commutes.
-		\[\xymatrix@C=15pt{Y \ar[dr]_{f} \ar[rr]^{h}&& Y' \ar[dl]^{g}\\ & X}\] 
-		\item  	 Dually, the \emph{ slice category under $X$} is the category $X/\X$ in which objects are arrows $f\colon X\to Y$  with domain $X$ and a morphism $h\colon  f\to g$ is an arrow of $\X$ fitting in a triangle as the one below.
-		\[\xymatrix@C=15pt{&X \ar[dr]^{g}\ar[dl]_{f}\\ Y  \ar[rr]_{h}&& Y'}\] 
-	\end{itemize}
+	\noindent 
+	\parbox{11cm}{\vspace{-.5cm}\begin{itemize}
+		\item The \emph{ slice category over $X$} is the category $\X/X$ which has as objects arrows $f\colon Y\to X$ and  in which an arrow $h\colon f\to g$ is $h\colon Y\to Y'$ in $\X$ such that the triangle on the right commutes.
+		\item  	 Dually, the \emph{ slice category under $X$} is the category $X/\X$ in which objects are arrows $f\colon X\to Y$  with domain $X$ and a morphism $h\colon  f\to g$ is an arrow of $\X$ fitting in a triangle as the one aside.
+	\end{itemize}} \hfill \parbox{2cm}{\vspace{-0cm}\xymatrix@C=15pt@R=15pt{Y \ar[dr]_{f} \ar[rr]^{h}&& Y' \ar[dl]^{g}\\ & X} \xymatrix@C=15pt@R=15pt{&X \ar[dr]^{g}\ar[dl]_{f}\\ Y  \ar[rr]_{h}&& Y'}}
 \end{definition}

### 2025-03-13 calco/main.tex

@@
 \parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
-
-\commentato{ 
-\begin{restatable}{corollary}{rege}\label{cor:rege}
-		An arrow $h\colon \mathcal{G \to H}$  is a regular mono in $\egg$ if and only if $I(h)$ is a regular mono in $\hyp$.
-In particular a morphism of $\egg$ is a regular mono if and only if all its components are injections.
-\end{restatable}
-\begin{proof}
-	contenuto...
-\end{proof}
-}
 
@@
 \end{corollary}
+
+\commentato{ 
+\begin{remark}\label[remark]{rem:sig_egg}
+	Given a signature $\Sigma = (O_\Sigma, \ari_\Sigma)$,
+	the hypergraph 
+	$R(\mathcal{G}^\Sigma) = (O_\Sigma, 1, 1, \ari_\Sigma, \delta_1, \id{1})$
+	is an object of $\egg$.
+	Indeed, if $(S, \pi_1, \pi_2)$ is the kernel pair of $\id{1}^\star \circ \ari_\Sigma$,
+	we have that $\id{1}^\star \circ \delta_1 \circ \pi_1$ and $\id{1}^\star \circ \delta_1 \circ \pi_2$ are both the contant functions of value $1$.
+\end{remark}
+
+\begin{definition}\label[definition]{def:label_egraphs}
+	Let $\Sigma$ be an algebraic signature, and $\mathcal{G}^\Sigma$ the hypergraph associated to it.
+	A \emph{labeled e-hypergraph} is a pait $(\mathcal{E}, l)$, where $\mathcal{E}$ is an e-hypergraph and $l: T \circ I (\mathcal{H}) \to \mathcal{G}^\Sigma$ is a morphism of $\hyp$.
+	A \emph{morphism of labeled e-hypergraphs} $(\mathcal{E}, l)\to (\mathcal{E}', l')$ is a morphism $h: \mathcal{E \to E}'$ such that $l = l' \circ (T \circ I)(h)$.
+	We denote the resulting category by $\eggs$.
+\end{definition}
+
+%Functor from GEqhyp_S to EqHyp_S
+
+With a similar argument as the one done in \Cref{prop:slice}, and by \Cref{rem:sig_egg} we get a characterization of $\eggs$.
+
+\begin{proposition}
+	The category $\eggs$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$
+\end{proposition}
+
+Consider now the functor that forgets the label $V_\eq : \eggs \to \egg$, and $\pbes$ the class of morphisms in $\eggs$ whose image through $V_\eq$ is in $\pbe$.
+From \Cref{thm:slice-functors}, \Cref{lim},  \Cref{lem:elim,lem:epo}, we can deduce what follows.
+
+\begin{proposition}\label[proposition]{prop:eadh}
+	The following facts hold true:
+	\begin{enumerate}
+	\item $\eggs$ has all limits and pushouts along regular monos, which are created by $V_\eq$;
+	\item $\eggs$ is $\pbes$-adhesive.
+	\end{enumerate}
+\end{proposition}
+
+Now, by \Cref{cor:rege,cor:mono1,cor:mono2}, we get what follows.
+
+\begin{corollary}\label{cor:emon}
+	Let $h = (h_E, h_V, h_Q)$ be an arrow in $\eggs$. Then the following holds.
+	\begin{enumerate}
+	\item $h$ is mono if and only if $h_E$ and $h_V$ are injective;
+	\item $h$ is regular mono in and only if each component of it is injective.
+	\end{enumerate}
+\end{corollary}
+
+We can now introduce term graphs with closed equivalences.
+
+%\begin{definition}\label[definintion]{def:GEqTGs}
+%	Given a signature $\Sigma$, we define the category $\GEqTGs$ as the full subcategory of $\eggs$ in which objects are arrows $l: \mathcal{G} \to R(\mathcal{G}^\Sigma)$ where $t_\mathcal{G}$ is mono.
+The inclusion functor is denoted $I_{\GEqTGs} : \GEqTGs \to \egg/R(\mathcal{G}^\Sigma)$.
+%\end{definition}
+
+\begin{definition}\label[definition]{def:GEqTGs}
+	Let $\Sigma$ be an algebraic signature.
+An object $(\mathcal{T}, l)$ of $\eggs$ is an \emph{e-term graph} if $l: T(\mathcal{T})\to \mathcal{G}^\Sigma$ is a term graph.
+We denote by $\GEqTGs$ the full subcategory of $\eggs$ so defined, and denote by $I_{\GEqTGs}$ the corresponding inclusion functor.
+\end{definition}
+\noindent
+\parbox{8.5cm}{\begin{remark}\label[remark]{rem:inclusions}
+	The category $\GEqTGs$ is also a full subcategory of $\EqTGs$, since each object $(\mathcal{H}, l)$ is a term graph with equivalence too.
+	We denote the corresponding inclusion functor as $S_\eq$.
+Hence, we have a situation similiar to the one in \Cref{rem:obv}, as the diagram aside shows, where $T_\eq$ is the inclusion functor of \Cref{def:ehyp1} lifted to the slice category, i.e., is such that $V_\Sigma \circ T_\eq = I \circ V_\eq$.
+\end{remark}}
+	\hfill\parbox{4.5cm}{\[\xymatrix@R=20pt@C=38pt{\GEqTGs \ar[r]^{I_{\GEqTGs}}  \ar[d]_{S_\eq}& \eggs \ar[d]^{T_\eq} \\ \EqTGs \ar[r]_{I_\eq}& \EqHyp_{\Sigma}}\]}
+
+%\todo{Here we must introduce $\GEqTGs$}
+>>>>>>> refs/remotes/origin/main}
 

### 2025-03-13 calco/mainTmp.tex
minima

--- 2025-03-13 calco/main.tex
@@
 \begin{corollary}\label{cor:mono1}
-	An arrow $h = (h_E, h_V, h_C): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
+	An arrow $(h_E, h_V, h_C): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
 \end{corollary}
@@
 \parbox{9.5cm}{\begin{remark}\label{rem:obv}
-Let $T_\Sigma$ be  $T\circ V_\Sigma$.
-Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ if and only if $T(\mathcal{H})$ is in $\tg$.
+Let $T_\Sigma:  \EqHyp_{\Sigma} \to \hyp_{\Sigma}$ the forgetful functor lifting
+$T:  \EqHyp \to \hyp$.
+%
+%$T_\Sigma = T\circ V_\Sigma$.   
+Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ amounts to say that $(T(\mathcal{H}), l)$ is in $\tg$. 
 Thus there exists a functor $S_\Sigma$ as in the diagram on the right.

### 2025-03-13 calco/main.tex
minori

--- 2025-03-13 calco/main.tex
@@
 %
-The theory of $\mathcal{M}$-adhesivity~\cite{xxx} extend the core framework, still ensuring that if the arrow 
-of the rules are in $\mathcal{M}$,
+The theory of $\mathcal{M}$-adhesivity~\cite{xxx} extend the core framework, still ensuring that if the arrows 
+of the rules are in a suitable class $\mathcal{M}$ of monomorphisms
 %and the match is in $\mathcal{N}$, 
 then the classical results from the theory of graph 
-transformation can still be lifted~\cite{xxx}. 
+transformation can still be obtained~\cite{xxx}. 
 If only the left-hand side belongs to $\mathcal{M}$, the current theory is stil under development, as witnessed e.g.
@@
 \parbox{9.5cm}{\begin{remark}\label{rem:obv}
-Let $T_\Sigma$ be the functor sending $(\mathcal{H}, l)$ to $(T(\mathcal{H}), T(l))$.
+Let $T_\Sigma:  \EqHyp_{\Sigma} \to \hyp_{\Sigma}$ the forgetful functor lifting
+$T:  \EqHyp \to \hyp$.
+%
+%$T_\Sigma = T\circ V_\Sigma$.   
+Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ amounts to say that $(T(\mathcal{H}), l)$ is in $\tg$. 
+Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
+%Let $T_\Sigma$ be the functor sending $(\mathcal{H}, l)$ to $(T(\mathcal{H}), T(l))$.
 Notice that, by definition, $(\mathcal{H}, l)$ is in $\EqTG_{\Sigma}$ if and only if $T(\mathcal{H})$ is in $\tg$.
 Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
-\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}}
+\end{remark}}
+\hfill 
+\parbox{4cm}{\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}}
 
@@
 \label{conclusioni}
-The aim of our paper was to extend the theory of adhesive categories in order to include EGGS, 
+The aim of our paper was to extend the theory of $\mathcal{M}$-adhesive categories in order to include EGGS, 
 a formalism for program optimisation 
@@
 This fact allows for exploiting the properties 
-of the adhesive framework when discussing about the optimisation process.
+of the $\mathcal{M}$-adhesive framework when discussing about the optimisation process.
 
@@
 Also, it still needs to be exploited how parallelism and causality, the key features for DPO rewriting
-on adhesive categories, can be exploited in the context of EGGs implementation. 
+on $\mathcal{M}$-adhesive categories, can be exploited in the context of EGGs implementation. 
 Another venue for development is using the adhesive 
@@
 At the same time, we both consider the DPO approach for rewriting, even if only our solution guarantees that the resulting category
-is actually adhesive, thus allowing to exploit all the features of the framework.
+is actually $\mathcal{M}$-adhesive, thus allowing to exploit all the features of the framework.
 

### 2025-03-13 calco/main.tex
Update main.tex

--- 2025-03-13 calco/main.tex
@@
 
-We can now prove our last three results. The interested reader can find the proof in \Cref{proof:tlim}.
+We can now prove our last three results. The reader can find the proof in \Cref{proof:tlim}.
 

### 2025-03-14 calco/main.tex
minima

--- 2025-03-13 calco/main.tex
@@
 Adhesive categories provides such a disparate set of formalisms with a common abstract framework 
-where many of these general results could be recast and uniformly proved once and for all.
+where many of these general results can be recast and uniformly proved once and for all.
 
@@
 %and the match is in $\mathcal{N}$, 
-then the classical results from the theory of graph 
-transformation can still be obtained~\cite{xxx}. 
+then the benefiots of adhesivity
+%the classical results from the theory of graph transformation 
+can still be obtained~\cite{xxx}. 
 If only the left-hand side belongs to $\mathcal{M}$, the current theory is stil under development, as witnessed e.g.
@@
 proving that a given category satisfies the conditions 
-for being adhesive can be a daunting task. For this reason,  sufficient criteria have been provided for the core 
+for being $\mathcal{M}$-adhesive can be a daunting task. For this reason, sufficient criteria have been provided for the core 
 framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, as well as for the extended one of
@@
 	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top face is a pushout, the left and bottom faces are pullbacks,  and $n\colon B\mto D$ is an injection. 
-	Then it holds:
+	Then it holds
 	\begin{enumerate}
@@
 
-Having prove stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
+Having proved stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
 %
@@
 \parbox{11.5cm}{\begin{restatable}{lemma}{epo}\label{lem:epo}
-	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ an arrow in $\pbc$.
-If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is an object of $\egg$ too.
+	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ an arrow in $\pbc$. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is so too.
+	%an object of $\egg$ too.
 \end{restatable}}\hfill 
-\parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
+\parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar@{>->}[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
 
@@
 
-We turn now to the labelled context.
+We now turn our attention to the labelled context.
 
@@
 We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs.
-We will denote by $j_\Sigma$ the corresponding inclusion functor .
+We denote by $J_\Sigma$ the corresponding inclusion functor .
 \end{definition}
@@
 	Indeed, under the identification of $1^\star$ with $\mathbb{N}$, the kernel $(S, \pi_1, \pi_2)$  of $\id{\mathbb{N}} \circ \ari_\Sigma$, is given by
-	\[S:=\{(o_1, o_2)\in O_\Sigma \times O_\Sigma \mid \ari_\Sigma(o_1)=\ari_\Sigma(o_2)\}\]
+	$S:=\{(o_1, o_2)\in O_\Sigma \times O_\Sigma \mid \ari_\Sigma(o_1)=\ari_\Sigma(o_2)\}$
 	equipped with the two projections.
-Onthe other hand $\id{\mathbb{N}} \circ \gamma_1 \circ \pi_1$ and $\id{\mathbb{N}}\circ \gamma_1 \circ \pi_2$ are both the function $O_\Sigma \to \mathbb{N}$ constant in $1$.
+On the other hand $\id{\mathbb{N}} \circ \gamma_1 \circ \pi_1$ and $\id{\mathbb{N}}\circ \gamma_1 \circ \pi_2$ are both the function $O_\Sigma \to \mathbb{N}$ constant in $1$.
 \end{remark}
@@
 \begin{proposition}\label{prop:varie}
-	Let $\Sigma$ be an algebraic signature. Then the following hold true:
+	Let $\Sigma$ be an algebraic signature. Then it holds
 	\begin{enumerate}
@@
 Let $\pbe_\Sigma$ be the class of morphisms in $\egg_\Sigma$ whose image in $\egg$ lies in $\pbe$.
-Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $j_\Sigma$ is in $\pbc_\Sigma$.
-
-By \Cref{thm:slice-functors} we get the following.
+Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $J_\Sigma$ is in $\pbc_\Sigma$.
+%
+By \Cref{thm:slice-functors} we get the following result.
 
@@
 	Given a signature $\Sigma$,  we say that an object $(\mathcal{H}, l)$ of $\EqTG_{\Sigma}$ is a \emph{e-term graph} if $\mathcal{H}$ is an e-hypergraph.
-We define the category $\eg$ as the full subcategory of $\EqTG_{\Sigma}$ given by e-term graphs and denote by $k_\Sigma$ the corresponding inclusion.
+We define the category $\eg$ as the full subcategory of $\EqTG_{\Sigma}$ given by e-term graphs and denote by $K_\Sigma$ the corresponding inclusion.
 \end{definition}
@@
 \begin{remark}
-	By definition we also have an inclusion functor $K_\Sigma\colon \eg\to \egg_\Sigma$.
+	By definition we also have an inclusion functor $Y_\Sigma\colon \eg\to \egg_\Sigma$.
 \end{remark}
@@
 \parbox{7.5cm}{\begin{remark}
-	Now that we have introduced all the characters of this work, it is worth to give a visual map of all the categories that we have introduced in this paper and of the relationships between them.
+	Now that we have introduced all the of this work in place, it is worthwhile to give a visual map of all the categories that we have introduced in this paper and of the relationships between them.
 We will use the curved arrows to denote full and faithful inclusions.
-\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{K_\Sigma} \ar@{^{(}->}[d]_{k_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{j_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
-
-We can now prove our last three results. The interested reader can find the proof in \Cref{proof:tlim}.
+\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{j_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
+
+We can now prove our last three results. The reader can find the proof in \Cref{proof:tlim}.
 
 \begin{restatable}{proposition}{limt}\label{prop:limt}
-	$\eg$ has equalizer, binary products and pullbacks and they are created by $k_\Sigma$.
+	$\eg$ has equalizers, binary products and pullbacks and they are created by $K_\Sigma$.
 \end{restatable}
 
-Let now $\mathcal{T}_\Sigma$ be the class of morphisms of $\eg$ which are sent by $k_\Sigma$ to the class $\mathcal{T}$. Then \Cref{colim,lem:epo,prop:po} allow us to deduce the following result.
+Let now $\mathcal{T}_\Sigma$ be the class of morphisms of $\eg$ which are sent by $K_\Sigma$ to the class $\mathcal{T}$. Then \Cref{colim,lem:epo,prop:po} allow us to deduce the following result.
 
 \begin{restatable}{proposition}{pot}\label{prop:pot}
-	$\eg$ has $\mathcal{T}_\Sigma$-pushouts which are created by $k_\Sigma$.
+	$\eg$ has $\mathcal{T}_\Sigma$-pushouts which are created by $K_\Sigma$.
 \end{restatable}
@@
 \label{rewriting}
-The previous sections has shown how term graphs with equivalence,
+The previous sections have shown how term graphs with equivalence,
 possibly closed with respect to operator composition,
@@
 %
-Admittedly, the third one is illegal, i.e. it is an object of $\EqTGs$ but not one of $\GEqTGs$: constants have no input, 
+Admittedly, the third one is illegal, i.e. it is an object of $\EqTGs$ but not one of $\eg$:
+%$\GEqTGs$: 
+constants have no input, 
 and nodes that are targets of edges with the same label and source the empty word must be equivalent,
@@
 for an EGG $\mathcal{G}$, such canonical forms are the final and the initial objects of the comma category 
-$\mathcal{G}  \downarrow \GEqTGs$. 
+$\mathcal{G}  \downarrow \eg$.
+%\GEqTGs$. 
 The former part is a standard result in term graph rewriting, see e.g.~\cite{xxx}, while the latter is specific 
@@
 %
-The same construction carries on when restricting to the full category of $\GEqTGs$ of those objects whose 
+The same construction carries on when restricting to the full subcategory of $\eg$
+%$\GEqTGs$ 
+of those objects whose 
 underlying term graph is \emph{acyclic}.
@@
 
+\newpage
 What about rewriting? The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
@@
 %
-To do so, we revisited and generalised the notions of hyper-graph and term graph with equivalence, and
-we extended it in order to capture EGGS as term graphs satisfying a suitable closure property.
-Summing up, we proved that EGGs are objects of an $\mathcal{M}$-adhesive category $\GEqTGs$ 
+To do so, we revisited the notion of hyper-graph and introduced  term graph with equivalence, 
+proving that they are $\mathcal{M}$-adhesive categories, and we extended this resulr in order to capture
+also prove the same property for EGGS as term graphs with equivalence satisfying a suitable closure constraint.
+Summing up, we proved that EGGs are objects of an $\mathcal{M}$-adhesive category $\eg$ 
 and that optimisation steps are obtained via DPO rules (possibly with negative application conditions) whose 
@@
 \emph{Future works.}
-Our result on $\GEqTGs$ opens a few threads of research. The first is to check how the $\mathcal{M}$-adhesivity 
+Our result on $\eg$ opens a few threads of research. The first is to check how the $\mathcal{M}$-adhesivity 
 of EGGs can be pushed to model their rewriting via the double-pushout (DPO) approach. We have seen that 
@@
 Also, it still needs to be exploited how parallelism and causality, the key features for DPO rewriting
-on $\mathcal{M}$-adhesive categories, can be exploited in the context of EGGs implementation. 
+on $\mathcal{M}$-adhesive categories, can be exploited in the context of implementing the 
+EGGs updates. 
 Another venue for development is using the adhesive 
@@
 At the same time, we both consider the DPO approach for rewriting, even if only our solution guarantees that the resulting category
-is actually $\mathcal{M}$-adhesive, thus allowing to exploit all the features of the framework.
+is actually $\mathcal{M}$-adhesive, thus allowing to exploit all the features of the framework
+as they hold for standard graph transformation.
 
@@
 
- 		\item  We begin by computing to get:
+ 		\item  We begin by computing 
 		\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]
@@
 \begin{remark}\label{rem:disj}
-	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~ that the pullback between two coproduct injections is given by the initial object (with initial maps ad coprojections).
+	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.
+that the pullback between two coproduct injections is given by the initial object (with initial maps ad coprojections).
 To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and let $k$ be an element of $I$.
@@
 This, in turn, entails that $m'$, being the pullback of $m$, is mono, and so $n'$ is injective too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.
+\vspace{.1cm}
 
@@
 We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}
+
+\vspace{.1cm}
 
@@
 
-We focus now on $K_3$. Computing we get
+We focus now on $K_3$. By computing we get
 	\begin{align*}
@@
 \noindent 
-\parbox{3cm}{\xymatrix@R=15pt{ K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & C' \ar[r]_{c} & C }}\hfill\parbox{9.5cm}{By \Cref{lem:po_set} $g\circ \iota$ is a monomorphism, thus $w\circ p_3=w\circ q_3$ and therefore:
+\parbox{3cm}{\xymatrix@R=15pt{ K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & C' \ar[r]_{c} & C }}\hfill\parbox{9.5cm}{By \Cref{lem:po_set} $g\circ \iota$ is a monomorphism, thus $w\circ p_3=w\circ q_3$ and therefore
 \[c\circ \iota'\circ p_3=\iota\circ w\circ p_3=\iota \circ w\circ q_3=c\circ \iota'\circ q_3\]
@@
  \parbox{7.5cm}{We can go further. The outer part of the diagram on the right commutes, so that we have the dotted $\psi_0\circ K_b\to K_0$.
- Now, on the one hand $\phi_0\circ \psi_0=\id{K_b}$ because if we compute we get:
+ Now, on the one hand $\phi_0\circ \psi_0=\id{K_b}$ because if we compute we get
   \[(\pi^1_b, \pi^2_b)\circ \phi_0\circ \psi_0=(p_0, q_0)\circ \psi_0=(\pi^1_b, \pi^2_b)\]}\hfill \parbox{4cm}{\vspace{-.5cm}\xymatrix{K_b \ar[dr]_{(\pi^1_b, \pi^2_b)}  \ar@{>->}@/^.4cm/[rr]^{k_{n'}} \ar@{.>}[r]_{\psi_0}& K_0 \ar@{>->}[r]_{j_0}  \ar[d]^{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)} \\
@@
 
-By definition of complement, we also know that $(C', \{\iota', m'\})$ is a coproduct. We can then apply again \Cref{lem:nodim}, decomposing $K_c$ in four parts, given by the pullbacks below:
+By definition of complement, we also know that $(C', \{\iota', m'\})$ is a coproduct. We can then apply again \Cref{lem:nodim}, decomposing $K_c$ in four parts, given by the pullbacks below
  \[\xymatrix@C=45pt@R=15pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
@@
  \[m\circ a\circ y_0=c\circ m'\circ y_0=c\circ \pi^1_c\circ x_0=c\circ pi^2_c\circ x_0=c\circ m'\circ z_0=m\circ a \circ z_0\]
- Since $m$ is a monomorphism $a\circ y_0=a\circ z_0$ and there exists an arrow $h'_0\colon H_0\to K_a$ such that $\pi^1_a\circ h'_0=y_0$ and $\pi^2_a\circ h'_0=z_0$. Notice, that
+ Since $m$ is a monomorphism $a\circ y_0=a\circ z_0$ and there exists an arrow $h'_0\colon H_0\to K_a$ such that $\pi^1_a\circ h'_0=y_0$ and $\pi^2_a\circ h'_0=z_0$. Notice that
  \[(\pi^1_b\circ \pi^2_b)\circ h_0=(f'\times f')\circ (y_0, z_0)=(f'\times f')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(\pi^1_b, \pi^2_b)\circ k_{f'}\circ h'_0\]
@@
 
-We can prove another property of $h'_0$. Computing we have:
+We can prove another property of $h'_0$. By computing we have
 \[(\pi^1_c, \pi^2_c)\circ k'_{m'}\circ h'_0=(m'\times m')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(m'\times m')\circ (y_0, z_0)=(\pi^1_c, \pi^2_c)\circ x_0\]
@@
 
-As a next step, let us focus on $H_1$ and $H_2$. Two computations yield: \small
+As a next step, let us focus on $H_1$ and $H_2$. Two computations yield \small
  \[\begin{split}
@@
    E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
- Their solid part commute, indeed we have:
+ Their solid part commute. Indeed, we have
  \[\begin{split}
@@
 
-Thus we get the dotted arrows $\alpha_3$ and $\beta_3$ which are one the inverse of the other. Indeed on the one hand we have:
+Thus we get the dotted arrows $\alpha_3$ and $\beta_3$ which are one the inverse of the other. Indeed, on the one hand we have
 \begin{align*}
@@
  \[(\pi^1_c, \pi^2_c)\circ \phi_3\circ \alpha_3 =(\iota'\times \iota')\circ (p_3, q_3)\circ \alpha_3= (\iota'\times \iota')\circ (y_3, z_3)=(\pi^1_c, \pi^2_c)\circ x_3\]
- Therefore $\phi_3\circ \alpha_3=x_3$ and thus $x_3\circ \beta_3\circ \alpha_3=x_3$. Moreover:
+ Therefore $\phi_3\circ \alpha_3=x_3$ and thus $x_3\circ \beta_3\circ \alpha_3=x_3$. Moreover
  \[(y_3, z_3)\circ \beta_3\circ \alpha_3=(p_3, q_3\circ \alpha_3)=(y_3, z_3)\]
@@
 
- On the other hand, 
+ On the other hand
  \[\theta \circ k_{g'}\circ x_0=\theta \circ k_{n'}\circ h_0=\gamma \circ h_0=\gamma \circ k_{f'}\circ h'_0=\delta \circ k_{m'}\circ h'_0=\delta \circ x_0 \]
@@
 By construction we have $T(L(\mathcal{H}))=\mathcal{H}$, thus we can define
-		$\eta_\mathcal{H}\colon \mathcal{H}\to T(L(\mathcal{H}))$ as the identitye $\id{\mathcal{H}}$.
+		$\eta_\mathcal{H}\colon \mathcal{H}\to T(L(\mathcal{H}))$ as the identity $\id{\mathcal{H}}$.
 
@@
 In particular, we need the fact that they form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.
-This amount to ask that:
+This amount to ask that
 
@@
 	\begin{enumerate} 
-		\item Every arrow $f\colon X\to Y$ can be factored as $m\circ e$, where $e\colon X\eto Q$ is a regular epi and $m\colon Q\mto Y$ is a mono;
+		\item every arrow $f\colon X\to Y$ can be factored as $m\circ e$, where $e\colon X\eto Q$ is a regular epi and $m\colon Q\mto Y$ is a mono;
 			\item for every square as the one on the right, with $e\colon X\eto E$ a surjection and $m\colon N\mto Y$ a mono, there exists a unique $k\colon E\to N$ making it commutative.
@@
 \begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
-	Let $F,G\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
+	Let $F,G\colon \D\rightrightarrows \X$ be two diagrams and suppose that $\X$ has all colimits of shape $\D$.
 Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in D})$ be the colimits of $F$ and $G$, respectively.
@@
 		\item We know by \Cref{prop:cocomp} that $\hyp$ is cocomplete.
-Let thus $(E, V, s, t)$ together with $\{(\kappa_E^d, \kappa_V^d)\}_{d \in \D}$ be a colimit for $T \circ F$.
+Thus, let $(E, V, s, t)$ together with $\{(\kappa_E^d, \kappa_V^d)\}_{d \in \D}$ be a colimit for $T \circ F$.
 By \Cref{colim} we also know that
@@
 		\hfill 
-		\parbox{2cm}{\xymatrix{V_d \ar[r]^{h_2} \ar@{>>}[d]_{q_d} & V_{d'} \ar@{>>}[d]^{q_{d'}}\\ Q_{d} \ar[r]_{h_3} & Q_{d'}}}
+		\parbox{2cm}{\xymatrix{V_d \ar[r]_{h_2} \ar@{>>}[d]_{q_d} & V_{d'} \ar@{>>}[d]^{q_{d'}}\\ Q_{d} \ar[r]^{h_3} & Q_{d'}}}
+		\vspace{.05cm}
 
@@
 By \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}, the induced arrow $q: V \to C$ between the colimits is a surjection.
-We can then consider the object $(E, V, C, s, t, q)$ of $\EqHyp$, together with the family  $\{(\kappa_E^d, \kappa_V^d, c_d)\}_{d\in \D}$ which, by construction is a cocone on $F$.
+We can then consider the object $(E, V, C, s, t, q)$ of $\EqHyp$, together with the family  $\{(\kappa_E^d, \kappa_V^d, c_d)\}_{d\in \D}$, which by construction is a cocone on $F$.
 Let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^d_E, h^d_V, h^d_Q)\}_{d\in \D})$ be a cocone, then $((E_\mathcal{G},V_\mathcal{G},, s_{\mathcal{G}}, t_{\mathcal{G}}), \{(h^d_E, h^d_V)\}_{d\in \D})$ and $(Q_{\mathcal{G}}, \{h^d_Q\}_{d\in \D})$ are cocone on, respectively, $T\circ F$ and $K\circ D$, giving arrows $(h_E, h_V)$ in $\hyp$ and $h_Q$ in $\Set$ such that
 		\[(h_E, h_V)\circ (\kappa_E^d, \kappa_V^d)=(h^d_E, h^d_V) \qquad h_Q\circ c_D=h^d_Q\]
-		Now, to show that $(h_E, h_V, h_Q)$ is an arrow of $\EqHyp$ we can compute:
+		Now, to show that $(h_E, h_V, h_Q)$ is an arrow of $\EqHyp$ we can compute
 		\[h_Q\circ q\circ \kappa^d_V=h_Q\circ c_d\circ q_d=h^d_Q\circ q_d=q_{\mathcal{G}} \circ h^d_V=q_{\mathcal{G}}\circ h_V\circ \kappa^d_V \]
@@
 
-	Let $\alpha$ be an arrow $d\to d'$ in $\D$, then we have:
+	Let $\alpha$ be an arrow $d\to d'$ in $\D$. Then we have
 		\[T(F\alpha\circ (\pi^d_{E}, \pi^d_V, \pi^d_Q))=T(F(\alpha))\circ (\pi^d_E, \pi^d_V)=(\pi^{d'}_E, \pi^{d'}_V)=T(\pi^{d'}_{E}, \pi^{d'}_V, \pi^{d'}_Q)\]
@@
 		Moreover, applying $K$ we get that $(Q_{\mathcal{G}}, \{h^d_{Q}\}_{d\in \D})$ is a cone over $K\circ F$, so that there is an arrow $h\colon Q_{\mathcal{G}} \to L$ such that $l_d\circ h=h^d_{Q}$.
-Thus:
+Thus
 		\[l_d\circ h\circ q_\mathcal{G}=h^d_Q\circ q_{\mathcal{G}}=q_{d}\circ h^d_V=q_d\circ \pi^d\circ h_V=l_d\circ l\circ h_V\]
@@
 \parbox{2cm}{\xymatrix@R=15pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[ur]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
-We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that}
-\[(\pi^d_E, \pi^d_V, \pi^dQ)\circ (h_E, h_V, k_Q)=(h^d_E, h^d_V, h^d_Q)\]
+We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that
+\[(\pi^d_E, \pi^d_V, \pi^dQ)\circ (h_E, h_V, k_Q)=(h^d_E, h^d_V, h^d_Q)\]}
 
@@
 	We can build the witnesses component-wise.
-
-	To do so, it suffices to build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which, by \Cref{prop:regmono}, are also pullbacks.
+	%
+	It suffices to build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks.
 	\[     \xymatrix@R=15pt{
@@
 
-	Now, in $\Set$ every mono is regular \cite{maclane2012sheaves}, so by the dual of \Cref{prop:reg_epi_coeq} we deduce that $h_E$, $h_V$ adn $h_Q$ are the equalizers of the arrows built above.
+	Now, in $\Set$ every mono is regular \cite{maclane2012sheaves}, so by the dual of \Cref{prop:reg_epi_coeq} we deduce that $h_E$, $h_V$ and $h_Q$ are the equalizers of the arrows built above.
 By \Cref{prop:com,lim} we also know that $(h_E, h_V)$ is the equalizer in $\hyp$ of $(f_E, f_V)$ and $(g_E, g_V)$.
@@
 
-	Again by \Cref{prop:eqhyp_complete} the two halves of the central rectangler are pullbacks and so, by \Cref{lem:pb1} the whole rectangle is a pullback too.
-This, in turn entails that the the whole right rectangle is a pullback and so, also its left half is a pullback (again by \Cref{lem:pb1}).
+	Again by \Cref{prop:eqhyp_complete} the two halves of the central rectangle are pullbacks and so by \Cref{lem:pb1} the whole rectangle is a pullback too.
+This, in turn entails that the whole right rectangle is a pullback and so, also its left half is a pullback (again by \Cref{lem:pb1}).
 	\[
@@
 	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
-	and that suppose in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
+	and  suppose that in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
 By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
@@
 \parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
-Notice, moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
+Notice moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
 By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
@@
 	For $Q'_1$, we can make a similar argument.
-Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ which makes the diagram aside commutative.}\hfill
+Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ that makes the diagram aside commutative.}\hfill
 	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
 
-We have to show that the top face of the cube with which we have began is a pushout.
-Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exists  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
+We have to show that the top face of the cube with which we have begun is a pushout.
+Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exist  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
 Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
@@
 
-Computing, we obtain
+By computing, we obtain
 \begin{align*}
@@
 
-As already nopticed the square above is a pushout, hence we can conclude that
+As already noticed the square above is a pushout, hence we can conclude that
 \[
@@
 
-Computing we have
+By computing we have
 \[\begin{split}
@@
 By \Cref{rem:t} we know that $T_\Sigma$ preserves limits, thus by \Cref{rem:obv}  $(l, \{T_\Sigma(\pi_d)\}_{d\in \D})$ is limiting for $I_\Sigma\circ S_\Sigma$.
-By \Cref{prop:tlim} then $l$ is a term graph.
+Then by \Cref{prop:tlim} $l$ is a term graph.
 We conclude, again by \Cref{rem:obv} that $(\mathcal{L}, l)$ is in $\EqTG_{\Sigma}$ and the thesis follows.
@@
 	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, Q_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
-	Let now $(A, B, Q, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_Q^d)_{d\in \D}$ be the limit of $I \circ F$.
+	Now let $(A, B, Q, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_Q^d)_{d\in \D}$, be the limit of $I \circ F$.
 Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ F$.
@@
 
+	\vspace{.1cm}
 	\noindent 
@@
 Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout.}
-		Computing we obtain
+		By computing we obtain
 	\begin{align*}
@@
 \begin{proof}\label{proof:tlim}
-Let $F\colon \D\to \eg$ be a diagram of one of the sapes mentioned in the proposition.
+Let $F\colon \D\to \eg$ be a diagram of one of the shapes mentioned in the statement.
 Let $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$ be a limiting cone for $k_\Sigma \circ F$.
-By \Cref{lim,prop:term,proof:elim} we know that $\mathcal{L}$ is an e-termgraph and we can conclude.
+By \Cref{lim}, \Cref{prop:term}, and \Cref{proof:elim} we know that $\mathcal{L}$ is an e-termgraph and we can conclude.
 \end{proof}
@@
 \section{Some properties of comma categories}
-In this section we will briefly recall the definition of the comma category \cite{mac2013categories} associated to two functors and some of its properties.
+In this section we briefly recall the definition of the comma category \cite{mac2013categories} associated to two functors and some of its properties.
 \begin{definition}\index{category!comma -}
@@
 \end{definition} 
-We have two forgetful functors 	$U_L\colon \comma{L}{R}\to \A$ and $U_R\colon \comma{L}{R} \to \B$ given, respectively by
+We have two forgetful functors 	$U_L\colon \comma{L}{R}\to \A$ and $U_R\colon \comma{L}{R} \to \B$ given respectively by
 \[
@@
 Thus $\comma{L}{R}$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
-Moreover  of the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$.
+Moreover, the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$.
 \[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g} & R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B') & L(A') \ar[r]_{L(h)}  & L(A)}\]
@@
 \begin{proposition}\label[proposition]{prop:dual}
-	$(\comma{L}{R})^{op}$ is equal to	$\comma{R^{op}}{L^{op}}$, moreover $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
+	$(\comma{L}{R})^{op}$ is equal to	$\comma{R^{op}}{L^{op}}$, and $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
 \end{proposition}
@@
 \begin{proof}
-	Suppose that $U_L\circ F$ and $U_R\circ F$ have colimiting cocones  $\left(A, \{a_D\}_{D\in \D}\right)$ and $\left(B, \{b_D\}_{D\in \D}\right)$ respectively.
+	Suppose that $U_L\circ F$ and $U_R\circ F$ have respectively colimiting cocones  $\left(A, \{a_D\}_{D\in \D}\right)$ and $\left(B, \{b_D\}_{D\in \D}\right)$.
 By hypothesis $\left(L(A), \{L\left(a_D\right)\}_{D\in \D}\right)$ is colimiting for $L\circ U_L\circ F$.
@@
 
-	First of all, let us show that it is a cocone. Given $d\colon D\to D'$ in $\D$ we have:
+	First of all, let us show that it is a cocone. Given $d\colon D\to D'$ in $\D$ we have
 	\begin{align*}
@@
 	For the colimiting property, let $\left((X, Y, g), \left\{\left(x_D, y_D\right)\right\}_{D\in \D}\right)$ be another cocone on $F$.
-In particular $\left(X, \left\{x_D\right\}_{D\in \D}\right)$ and $\left(Y, \left\{y_D\right\}_{D\in \D}\right)$ are cocones on $U_L\circ F$ and $U_R\circ F$ respectively, so we have uniquely determined arrows $x\colon A\rightarrow X$ and $y\colon B\rightarrow Y$ such that
+In particular, $\left(X, \left\{x_D\right\}_{D\in \D}\right)$ and $\left(Y, \left\{y_D\right\}_{D\in \D}\right)$ are cocones on $U_L\circ F$ and $U_R\circ F$ respectively, so we have uniquely determined arrows $x\colon A\rightarrow X$ and $y\colon B\rightarrow Y$ such that
 	\[x\circ a_D= x_D \qquad y\circ b_D= y_D\]
@@
 	\smallskip\noindent 
-	\parbox{4cm}{ \xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}}\hfill \parbox{8.5cm}{$(\Leftarrow)$ Since $h$ and $k$ are monos then we have two pullback squares on the left.
+	\parbox{4cm}{ \xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}}\hfill \parbox{8.5cm}{$(\Leftarrow)$ Since $h$ and $k$ are monos then we have the two pullback squares on the left.
 Thus by \Cref{lim} the pullback of $(h,k)$ along itself has isomorphisms as projections and so $(h,k)$ is mono.
@@
 \end{proposition}
-\begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{B})$, where $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
-Consider $\id{B}\colon B\to U_R(\Delta(B))$ be the
-
-	\noindent 
-	\parbox{10cm}{\vspace{-.2cm}identity, and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given.
-By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, since $L$ preserves initial objects, the square aside commutes.}\hfill
+\begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{B})$, for $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
+Consider $\id{B}\colon B\to U_R(\Delta(B))$ be the identity,
+
+	\noindent 
+	\parbox{10cm}{and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given. By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, 
+	since $L$ preserves initial objects, the square aside commutes. Thus $(h,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$ such that $U_R(h,k)=k$. }\hfill 
 	\parbox{2cm}{\vspace{-.1cm}\xymatrix@C=30pt@R=15pt{L(0) \ar[r]_{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]^{R(k)}& R(B')}}  
-	Thus $(h,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$	such that $U_R(h,k)=k$.   
 \end{proof}
@@
 \begin{definition}\index{category!slice -}
-	Let $X$ be an object of a category $\X$, we will define the following two categories.
+	Let $X$ be an object of a category $\X$. We define the following two categories.
 
@@
 \begin{corollary}\label[corollary]{cor:pbapp}
-For eery object $\X$, $\X/X$ has all colimits and connected limits that $\X$ has. Moreover such limits and colimits are created by $\dom_X$.
+For every object $\X$, $\X/X$ has all colimits and connected limits that $\X$ has. Moreover such limits and colimits are created by $\dom_X$.
 

### 2025-03-14 calco/main.tex
intro

@@
 \begin{minipage}[l]{.78\linewidth}In short, following the double-pushout (DPO) approach
-to graph transformation~\cite{xxx}, a rule is given by two arrows $l: K \to L$ and $r: K \rightarrow R$
+to graph transformation~\cite{ehrig1999handbook,ehrig2006fundamentals,corradini1997algebraic}, a rule is given by two arrows $l: K \to L$ and $r: K \rightarrow R$
 and its execution requires a match $m: L \to G$ such that the rewriting step from $G$
-to $H$ is given by the diagram aside, whose square are pushouts.
+to $H$ is given by the diagram aside, whose halves
   \end{minipage}%
@@
 \noindent
-Thus, $L$ and $R$ are the lift- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
+ are pushouts. Thus, $L$ and $R$ are the lift- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
 be present for the rule to be executed, yet they are not affected by the rule itself.
@@
 %
-The theory of $\mathcal{M}$-adhesivity~\cite{xxx} extend the core framework, still ensuring that if the arrows 
+The theory of $\mathcal{M}$-adhesivity~\cite{azzi2019essence,heindel2009category} extends the core framework, still ensuring that if the arrows 
 of the rules are in a suitable class $\mathcal{M}$ of monomorphisms
 %and the match is in $\mathcal{N}$, 
-then the benefiots of adhesivity
+then the benefits of adhesivity
 %the classical results from the theory of graph transformation 
-can still be obtained~\cite{xxx}. 
+can still be obtained~\cite{ehrig2012,ehrig2014adhesive}. 
 If only the left-hand side belongs to $\mathcal{M}$, the current theory is stil under development, as witnessed e.g.
@@
 For some structures such as \emph{hypergraphs with equivalence} in~\cite{concur2006}, the question 
-of their adhesivity has not yet been settled.
+of their $\mathcal{M}$-adhesivity has not yet been settled.
 

### 2025-03-14 calco/main.tex
rev intro

@@
 \begin{minipage}[l]{.78\linewidth}In short, following the double-pushout (DPO) approach
-to graph transformation~\cite{ehrig1999handbook,ehrig2006fundamentals,corradini1997algebraic}, a rule is given by two arrows $l: K \to L$ and $r: K \rightarrow R$
-and its execution requires a match $m: L \to G$ such that the rewriting step from $G$
-to $H$ is given by the diagram aside, whose halves
+to graph transformation~\cite{CorradiniMREHL97,ehrig2006fundamentals}, 
+%~\cite{ehrig1999handbook,ehrig2006fundamentals,corradini1997algebraic}, 
+a rule is given by two arrows $l: K \to L$ and $r: K \rightarrow R$
+and its application requires a match $m: L \to G$: the rewriting step from $G$
+to $H$ is then given by the diagram aside, whose halves are pushouts.
   \end{minipage}%
@@
 \noindent
- are pushouts. Thus, $L$ and $R$ are the lift- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
+Thus, $L$ and $R$ are the lift- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
 be present for the rule to be executed, yet they are not affected by the rule itself.
@@
 
-EGGs can be concisely defined as (acyclic) term graphs with an additional notion of equivalence on nodes
-that is closed under the operators of the signature~\cite[Section~4.2]{DetlefsNS05}.
-In the presentation of term graphs via string diagrams~\cite{CastelnovoGM24}, EGGs are (hyper)trees equipped with 
-the possibility of sharing subtrees, as in terms graphs, with an additional equivalence relation $\equiv$ on nodes that 
+EGGs can be concisely defined as term graphs equipped with a notion of equivalence on nodes
+that is closed under the operators of a signature~\cite[Section~4.2]{DetlefsNS05}.
+%(i.e., graphs whose components are labelled with the operators of a signature)
+In the presentation of term graphs via string diagrams~\cite{CastelnovoGM24}, EGGs are (hyper)trees 
+whose edges are labelled by operators and with
+the possibility of sharing subtrees, with an additional equivalence relation $\equiv$ on nodes that 
 is closed under composition. In plain words and using a toy example:

### 2025-03-14 calco/main.tex
update sezione 6

@@
 
+\vspace{.1cm}
 Now, we show that $\pbc$ is a suitable class for adhesivity. A proof is in \Cref{proof:pbmono}.
@@
 
-We now show that key lemma for $\pbc$-adhesivity of $\EqHyp$ is. A proof is in \Cref{proof:pbstable}.
+\vspace{.1cm}
+Finally, we show the key lemma for $\pbc$-adhesivity of $\EqHyp$. A proof is in \Cref{proof:pbstable}.
 
@@
 \parbox{7.5cm}{\begin{remark}
-	Now that we have introduced all the of this work in place, it is worthwhile to give a visual map of all the categories that we have introduced in this paper and of the relationships between them.
+	Now that we have put all the structures of this work in place, it is worthwhile to give a visual map of all the categories that we have discussed/introduced and of the relationships between them.
 We will use the curved arrows to denote full and faithful inclusions.
@@
 and possibly the same.
-%
-In general, note that both a maximally and a minimally shared representation of an EGG exist, and for our 
-toy example are the left-most and the middle one above, respectively. In general terms,
-for an EGG $\mathcal{G}$, such canonical forms are the final and the initial objects of the comma category 
-$\mathcal{G}  \downarrow \eg$.
-%\GEqTGs$. 
-The former part is a standard result in term graph rewriting, see e.g.~\cite{xxx}, while the latter is specific 
-of the setting with equivalences.
-%
-The same construction carries on when restricting to the full subcategory of $\eg$
-%$\GEqTGs$ 
-of those objects whose 
-underlying term graph is \emph{acyclic}.
-%and in this case if $\mathcal{G}$ has no empty nodes, then the unique arrow 
-%from $\mathcal{G}$ to the terminal object is easily shown to be injective on equivalence classes.
-
-\newpage
+
+In general, for term graphs without equivalence, a maximally and a minimally shared representation
+exists, and for our toy example are the right-most and the left-most diagram above, respectively.
+These are standard results in term graph rewriting, see e.g.~\cite{AriolaKP00}, 
+and they can easily seen as the final and the initial objects of a suitable comma category 
+$\mathcal{G}  \downarrow \tg$, respectively.
+%
+The same properties carries on 
+%when restricting to the full subcategory of acyclic term graphs.
+%
+for EGGSs, even if the minimally shared representation is now 
+the middle diagram.
+%
+All the previous considerations can be lifted to the full sub-categories whose objects
+have underlying hypergraphs that are acyclic.
+%an EGG exist, and for our 
+%toy example are the left-most and the middle one above, respectively. In general terms,
+%for an EGG $\mathcal{G}$, such canonical forms are the final and the initial objects of the comma category 
+%$\mathcal{G}  \downarrow \eg$.
+%%\GEqTGs$. 
+%The former part is a standard result in term graph rewriting, see e.g.~\cite{xxx}, while the latter is specific 
+%of the setting with equivalences.
+%%
+%The same construction carries on when restricting to the full subcategory of $\eg$
+%%$\GEqTGs$ 
+%of those objects whose 
+%underlying term graph is \emph{acyclic}.
+%%and in this case if $\mathcal{G}$ has no empty nodes, then the unique arrow 
+%%from $\mathcal{G}$ to the terminal object is easily shown to be injective on equivalence classes.
+
+%\newpage
 What about rewriting? The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
@@
 % to the category at hand. 
-However, the structure of rules that is advanced in~\cite{DetlefsNS05},
+However, the structure of rules that is advanced in~\cite{DetlefsNS05}
 is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity, thus in $\pbc_\Sigma$,
@@
 possibility to keep on repeating the same rewriting step.
-However, this is easily forbidden adopting rules \emph{with negative application conditions}~\cite{xxx}, which are given by the usual span 
+However, this is easily forbidden adopting rules \emph{with negative application conditions}, which are given by the usual span 
 $L \leftarrow K \rightarrow R$ plus an additional arrow $n: L\rightarrow N$, such that a match $m: L \to G$ is admissible if it cannot
@@
 %
-The theory of $\mathcal{M}$-adhesivity carries on with such rules, see e.g~\cite{xxx}.
+The theory of $\mathcal{M}$-adhesivity carries on with such rules, see~\cite{ehrig2012,ehrig2014adhesive}.
 
@@
 To do so, we revisited the notion of hyper-graph and introduced  term graph with equivalence, 
-proving that they are $\mathcal{M}$-adhesive categories, and we extended this resulr in order to capture
-also prove the same property for EGGS as term graphs with equivalence satisfying a suitable closure constraint.
+proving that they are $\mathcal{M}$-adhesive categories, and we extended this results in order to capture
+also prove the same property for EGGs as term graphs with equivalence satisfying a suitable closure constraint.
 Summing up, we proved that EGGs are objects of an $\mathcal{M}$-adhesive category $\eg$ 

### 2025-03-14 calco/main.tex
update conclusioni

@@
 possibility to keep on repeating the same rewriting step.
-However, this is easily forbidden adopting rules \emph{with negative application conditions}, which are given by the usual span 
+However, this is easily forbidden adopting rules \emph{with negative application conditions}, given as the usual span 
 $L \leftarrow K \rightarrow R$ plus an additional arrow $n: L\rightarrow N$, such that a match $m: L \to G$ is admissible if it cannot
-be factorised through $n$. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side itself.
+be factorised through $n$~\cite{HabelHT96}. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side itself.
 %
@@
 %
-To do so, we revisited the notion of hyper-graph and introduced  term graph with equivalence, 
-proving that they are $\mathcal{M}$-adhesive categories, and we extended this results in order to capture
-also prove the same property for EGGs as term graphs with equivalence satisfying a suitable closure constraint.
+To do so, we revisited the notions of hyper-graphs and term graphs with equivalence, 
+proving that they are $\mathcal{M}$-adhesive categories, and we extended these results in order to
+prove the same property for EGGs as term graphs with equivalence satisfying a suitable closure constraint.
 Summing up, we proved that EGGs are objects of an $\mathcal{M}$-adhesive category $\eg$ 
 and that optimisation steps are obtained via DPO rules (possibly with negative application conditions) whose 
-left-hand side is in $\mathcal{M}$, and in fact an identity. 
+left-hand side is in $\mathcal{M}$,
+%, and in fact an identity. 
 %and via a match that is in $\mathcal{N}$. 
-This fact allows for exploiting the properties 
-of the $\mathcal{M}$-adhesive framework when discussing about the optimisation process.
+and fact allows for exploiting the properties 
+of the $\mathcal{M}$-adhesive framework.
+% when discussing about the optimisation process.
 
@@
 %
-In both cases, the key intuition is  to use string diagrams to represents (acyclic) term graphs. We adopted a
+In both cases, the key intuition is  to use string diagrams to represents term graphs. We adopted a
 more down-to-Earth approach by equipping
-concretely the nodes of a term graph with an equivalence relation, thus directly equivalent to the original presentation~\cite{DetlefsNS05},
-at the same time extending and generalising~\cite{concur2006} in the contemporary jargon of adhesive categories.
+concretely the nodes of a term graph with an equivalence relation, thus directly corresponding to the original presentation~\cite{DetlefsNS05},
+at the same time extending and generalising it~\cite{concur2006} in the contemporary jargon of adhesive categories.
 The route chosen in~\cite{ghica} is to consider term graphs as arrows of a symmetric monoidal category,

### 2025-03-14 calco/main.tex

@@
  \[m\circ a\circ y_0=c\circ m'\circ y_0=c\circ \pi^1_c\circ x_0=c\circ pi^2_c\circ x_0=c\circ m'\circ z_0=m\circ a \circ z_0\]
- Since $m$ is a monomorphism $a\circ y_0=a\circ z_0$ and there exists an arrow $h'_0\colon H_0\to K_a$ such that $\pi^1_a\circ h'_0=y_0$ and $\pi^2_a\circ h'_0=z_0$. Notice that
+ Since $m$ is a mono $a\circ y_0=a\circ z_0$ and there exists an arrow $h'_0\colon H_0\to K_a$ such that $\pi^1_a\circ h'_0=y_0$ and $\pi^2_a\circ h'_0=z_0$. 
+ We now can conclude that $k_{f'}\circ h'_0=h_0$, noticing that
  \[(\pi^1_b\circ \pi^2_b)\circ h_0=(f'\times f')\circ (y_0, z_0)=(f'\times f')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(\pi^1_b, \pi^2_b)\circ k_{f'}\circ h'_0\]
-and therefore we can conclude that $k_{f'}\circ h'_0=h_0$.
 
@@
 
- On the other hand
+ On the other hand, we can conclude that $\theta \circ k_{g'}=\delta$ as wanted, since
  \[\theta \circ k_{g'}\circ x_0=\theta \circ k_{n'}\circ h_0=\gamma \circ h_0=\gamma \circ k_{f'}\circ h'_0=\delta \circ k_{m'}\circ h'_0=\delta \circ x_0 \]
- and we can conclude that $\theta \circ k_{g'}=\delta$ as wanted.
 

### 2025-05-05 calco/rebuttal/letter.tex
rebuttal

\documentclass[english,11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{cleveref}
\usepackage{fullpage}

\title{``EGGs are adhesive!''\\
	Answer to reviewers}
\author{R. Biondo, D. Castelnovo, F. Gadducci}

\begin{document}
	\maketitle

We wish to thank the reviewers for the time they have dedicated to our paper, and for the many useful suggestions. We corrected all typos indicated; below we explain how we have addressed the issues raised by the reviewers.

\section*{Reviewer 1}
\subsection*{Comments}
\begin{itemize}
\item  
\end{itemize}
\subsection*{Bibliography}
\begin{itemize}
	\item 
\end{itemize}

\subsection*{Sources of theorems and definitions}
\begin{itemize}
	\item 
\end{itemize}

\section*{Reviewer 2}

\end{document}

### 2025-05-05 calco/rebuttal/letter.tex
r1

@@
 \usepackage{babel}
+\usepackage{amsfonts}
 \usepackage{cleveref}
@@
 \begin{itemize}
-\item  
+\item  $91$:  Put this in a definition + add the definition of ``closed under decomposition'', since this is mentioned line $122$.
+
+ANSWER: Since this notions are well known and we are recalling them only for the sake of completeness, we prefer to keep the present style, without using a definition box.
+We added the definition of closure under decomposition.
+
+\item $108$: Add to the list that it is well-behaved w.r.t comma categories and certain subcategories.
+
+ANSWER: We added the reference to subcategories. Since comma categories are slices that case is already covered.
+
+\item $109$: It would be helpful to include precise theorem numbers when referring to [14,24], as this would make it easier for readers to verify the claims without unnecessary effort.
+In this case, the first item of Proposition 2.4 seem to correspond to [14, Theorem 4.15], which speaks of (weak) adhesive HLR categories.
+If that's your reference, you should add how this notion relates to M-adhesivity, as done in Remark 2.3 for adhesivity and quasiadhesivity.
+
+ANSWER: Added the references to the relevant theorems or proposition. and the comparison with [14].
+
+\item $112$: R:X -> A should be preserve *M*-pullbacks, shouldn't it?
+
+ANSWER: fixed.
+
+\item $113$ and $116$: add diagrams if space permits.
+
+ANSWER: we think that adding diagrams at lines 113 and 116 would not  significantly enhance clarity or understanding.
+
+\item $129$: Why refer to strict Reg(sGraphs)-adhesive as quasiadhesive? Seems strange to use two naming conventions.
+
+ANSWER: it is conventional to use the term quasiadhesive for categories which are strictly adhesive with respect to the class of regular monos.
+Other proposals have been made (e.g.~ in [18]) but we prefer to stick with the more used convention.
+
+\item $159$: Why mention here that a proof of Lemma 2.14 can be found in the appendix, and not for Lemma 2.12 or Proposition 2.13?
+Moreover, it is already mentioned in the synopsis that missing proofs would be in the appendix.
+
+ANSWER: there is a pointer to the appenix befor Lemma 2.12. Such pointer (and all the others) are there to provide the reader with a quick link to the correct proof in the appendix.
+
+\item $160$: Surprising that the bottom is now supposed to be a pullback, instead of a pushout as in Proposition 2.13. Can any intuition be given for this change in the assumptions?
+
+ANSWER: In Prop.~2.13 it is not assumed that the bottom face is a pushout, eve if this property can be deduced from $\mathcal{M}$-adhesivity.
+Notice, however that to Prop.~2.13 it should be enough to ask for stability of $\mathcal{M}$-pushouts: in such a case the bottom face of the cube is not guaranteed to be a pushout (we do not need such level of generality here).
+
+On the other hand, we need a result allowing us to present the kernel pair of $d$ as a pushout even without the hypothesis that the back face is a pullback.
+This is the content of Lem.~$2.14$ and the proof relies on some peculiar properties of the category of sets.
+We suspect that the proof carry on in any extensive and distributive category but, again, we do not need such a level of generality here.
+
+Notice, by the way, that distributivity and extensivity are exactly the properties needed to build a Kleene star functor satisfying Prop.~3.1.
+
+\item $167$: Give the type of f$^\star$.
+
+ANSWER: Fixed.
+
+\item $171$: Say explicitly that $\mathsf{lg}_X$ = $(!_X)^\star$.
+
+ANSWER: this would be slightly imprecise since $1^\star$ is not $\mathbb{N}$, but only canonically isomorphic to it.
+
+\item $162$ and $173$: Maybe mention that it is the definition of hypergraph **that you will work with in this paper**. There are multiple existing definitions.
+
+ANSWER: while there exists multiple definitions of hypergraphs, it seems to us that this is well known and widely used, at least in the field of algebraic models of graph rewriting.
+We believe that it would be redundant to specify that this definition is the one used in the paper in which it appears.
+
+\item $175$: Why call $V_G$ the set of nodes? Maybe denote it $N_G$ or call it the set of vertices, to be consistent.
+
+ANSWER: we do not believe that this issue is crucial to the readability of understandability of the paper.
+
+\item $176$: Please give the type of $\mathsf{prod}^\star$. Is it $\mathbf{Set} \to \mathbf{Set}$?. Also, split this sentence into two sentences.
+
+ANSWER: Fixed
+
+\item $180$: Corollary 3.7 basically says that $\mathsf{Mono}(\mathbf{Set}) \downarrow \mathsf{Mono}(\mathbf{Set}) = \mathsf{Mono}(\mathbf{Hyp})$, which is part of the (unwritten) proof of Corollary 3.6, yet this is not mentioned.
+The order of the results is not logical.
+Moreover, the fact that Corollary 3.7 follows from Corollary B.5 is not mentioned.
+
+ANSWER: Fixed.
+
+\item $180$: Was this result not previously known in the literature?
+
+ANSWER: Indeed it was, we added a pointer to [14].
+
+\item $194$: Did you forget to draw $v_5$ or is it on purpose?
+
+ANSWER: It's a typo, $v_5$ is not needed.
+
+\item $198$: Why not more precisely say presheaf categories instead of functor categories?
+
+ANSWER: we changed the text.
+
+\item $208$: The target function $\gamma_1$ is supposed to output a list in $1^\star$. Does it return the one element list [1]?
+
+ANSWER: we removed the brackets since they were useless. Since we are identifying $1^\star$ with $\mathbb{N}$, $\gamma_1$ as codomain $\mathbb{N}$is precisely the element $1\in \mathbb{N}$.
+
+\item $214$: Why have the two diagram squares been oriented differently that the ones in Definition 3.4?
+Moreover, it should be twice the set $V_\mathcal{H}^*$ in the bottom left corners, and it should be $\gamma_1$ for the right morphism in the bottom square.
+
+ANSWER: Fixed
+
+ \item $214$: It seems to me that the second diagram can first be explained in much simpler terms, such as "in labelled hypergraphs, all hyperedges must have a single target vertex", and then it could be restated as a factorisation result for $t_\mathcal{H}$.
+The current explanation is not clear enough.
+
+ ANSWER: Fixed.
+
+ \item $215$: What is $U_{\mathbf{X}}$?
+Is it $U_{\mathbf{Set}}$?
+Or maybe $U_{\mathbf{Hyp}}$ that gives the set of vertices?
+There has been a lot of forgetful functor introduced so far, and here is one more being defined, so it would help to have a description in words added to this sentence.
+
+ ANSWER: $U_{\mathbf{X}}$ should be $U_{\mathbf{Hyp}}$. Fixed.
+
+ \item $216$: What is $\Delta_{\mathbf{X}}$?
+Only $\Delta_{\mathbf{Hyp}}$ has been introduced so far, and from my understanding $\mathbf{X}$ (in bold) is a typo for $\mathbf{Set}$ or $\mathbf{Hyp}$.
+Please draw the diagram for $\Delta_\Sigma(X) = (?,!)$ to visualise and understand what it represents, and give additional explanations in words.
+
+ANSWER: same as above.
+$\Delta_\Sigma(X)$ is the discrete hypergraph on $X$ (the one with no edges) labeled in the unique possible way.
+In our opinion drawing a diagram of it would not enhance the clarity of the paragraph.
+
+\item $217$: What is the definition of the functor $\Delta_\Sigma$ on morphisms? The proof of Proposition 3.17 is not straightforward and would be welcomed to be added.
+
+ANSWER: The proof is omitted for lack of space and since it is neither particularly informative nor useful.
+Indeed, given $(h,k)\colon \mathcal{H}\to \mathcal{G}^\Sigma$,  a morphism $X\to U_{\Sigma}(h,k)$ is just an arrow from $X$ to the set of nodes of $\mathcal{H}$.
+Since the set of hyperedges of $\Delta_{\Sigma}(X)$ is empty, it can be extended in a unique way to a morphism of hypergraph which, moreover, respect the labeling (because on $\Delta_{\Sigma}(X)$ there is nothing to label).
+
+\item $224-225$: What do you mean by "identifier"? Do you mean "label"? And what does "the latter" refer to?
+
+ANSWER: we haveused "labels"
 \end{itemize}
@@
 \begin{itemize}
-	\item 
+	\item $109$: [14,24] (as mentioned earlier)
+
+	ANSWER: added a pointer to the relevant results.
 \end{itemize}

### 2025-05-05 calco/final.tex
r1

--- 2025-03-14 calco/main.tex
@@
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
-\usepackage{tikz-cd}
+%\usepackage{tikz-cd}
 \usepackage{hyperref, cleveref} %simboli matematici
@@
 \usepackage{csquotes}
-
-\usepackage{tikz-cd}
 
@@
 
+\nolinenumbers
+
 \begin{document}
@@
 	\item		\emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one aside, if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
-		\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable.
+		\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable;
+		\item \emph{closed under decomposition}, or \emph{left-cancellable}, if whenever $g$ and $g\circ f$ belong to $\mathcal{A}$, then $f\in \mathcal{A}$. 
 \end{itemize}}\hfill
@@
 	Let $\X$ be a category and $\mathcal{M}$ a subclass of
-	$\mon(\X)$  including  all isos, closed under composition,  and stable under pullbacks and pushouts.  The category  $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
+	$\mon(\X)$  including  all isos, closed under composition, decomposition,  and stable under pullbacks and pushouts.  The category  $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
 	\begin{enumerate}
@@
 \begin{remark}
-	\label{rem:salva}
-	\emph{Adhesivity} and \emph{quasiadhesivity} 
+	\label{rem:salva} Our notion of $\mathcal{M}$-adhesive category corresponds to what in \cite{ehrig2006fundamentals} is called \emph{weak adhesive HLR category}, while a strict $\mathcal{M}$-adhesive categories corresponds to \emph{adhesive HLR} ones.
+Finally, 	\emph{Adhesivity} and \emph{quasiadhesivity}
 	\cite{lack2005adhesive,garner2012axioms} coincide with strict
 	$\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity,
-	respectively.
+	respectively. On the other hand
 \end{remark}
 
-$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of slice and functor categories \cite{mac2013categories}, as shown by the following theorems~\cite{ehrig2006fundamentals,lack2005adhesive}.
+$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of (co-)slice and functor categories \cite{mac2013categories}, as well with respect to subcategories, as shown by the following theorems~\cite[Thm.~4.15]{ehrig2006fundamentals}, \cite[Prop.~3.5]{lack2005adhesive} and  \cite[Thm.~2.12]{CastelnovoGM24}.
 
@@
 	\begin{enumerate}
-		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to A$ one preserving pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
+		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to \A$ one preserving $\mathcal{M}$-pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
 		\[\comma{\mathcal{N}}{\mathcal{M}}:=\{(h,k) \in \mor(\comma{L}{R}) \mid h\in \mathcal{N}, k\in \mathcal{M}\}\]
@@
 
-In this section we briefly recall the notion of \emph{hypergraph}. In order to do so, a pivotal role is played by the \emph{Kleen star monad} $(-)^\star\colon \Set\to \Set$, also known as 
+In this section we briefly recall the notion of \emph{hypergraph}. In order to do so, a pivotal role is played by the \emph{Kleene star monad} $(-)^\star\colon \Set\to \Set$, also known as 
 \emph{list monad},
@@
 		\item there are arrows $v_{n}\colon X^n\to X^\star $ such that $(X^\star, \{v_{n}\}_{n\in \mathbb{N}})$ is a coproduct;
-		\item for every arrow $f\colon X\to Y$, $f^\star$ is the coproduct of the family $\{f^n\}_{n\in \mathbb{N}}$;
+		\item for every arrow $f\colon X\to Y$, $f^\star\colon X^\star \to Y^\star$ is the coproduct of the family $\{f^n\}_{n\in \mathbb{N}}$;
 		\item $(-)^\star$ preserves all \emph{connected limits} \cite{carboni1995connected}, in particular it preserves pullbacks and equalizers.
@@
 
-Let $\pro^\star$ be the functor sending $X$ to $X^\star\times X^\star$: we can get $\hyp$ as a comma category.
+Let $\pro^\star$ be the functor $\Set\to \Set$ sending $X$ to the product $X^\star\times X^\star$.  We can use it to present $\hyp$ as a comma category.
 
@@
 
-Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, thus the result below follows from  \Cref{thm:slice-functors} and \Cref{prop:com}.
+Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, by \Cref{prop:com} and \Cref{cor:mono} we can deduce the following result.
+
+\begin{corollary}\label[corollary]{cor:monhyper}
+	A morphism $(h,k)$ is a mono in $\hyp$ if and only if both its components are injective functions.
+\end{corollary}
+
+Applying \Cref{thm:slice-functors} we also get the next corollary (cfr.~\cite[Fact 4.17]{ehrig2006fundamentals}).
 
@@
 	 $\hyp$ is an adhesive category.
-\end{corollary}
-
-Another useful corollary of \Cref{prop:com} is the following one.
-
-\begin{corollary}\label[corollary]{cor:monhyper}
-A morphism $(h,k)$ is a mono in $\hyp$ if and only if both its components are injective functions.
 \end{corollary}
@@
 exit from the right of the box.
-Let us look at the picture below. It represent an hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
+Let us look at the picture below. It represent an hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
 and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair nodes
@@
 \begin{remark}\label{rem:functor}
-	It is worth to point out, as first noted in \cite{bonchi2022string}, that $\hyp$ is equivalent to a category of functors. 
+	It is worth to point out, as first noted in \cite{bonchi2022string}, that $\hyp$ is equivalent to a category of presheaves. 
 	%
@@
 %
-We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $\{1\}$ as set of nodes, so that $\{1\}^\star$ is $\mathbb{N}$, $\ari_\Sigma$ as the source function and $\gamma_1$ as target function, which always picks the element $1$.
+We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes, so that $1^\star$ is $\mathbb{N}$, $\ari_\Sigma$ as the source function and $\gamma_1$, which always picks the element $1$, as target function.
 The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
@@
 \hspace{10pt}Now, consider a coprojection $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$.
-The second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V^{\star}$ of words of length $1$, i.e.
-$t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
-\end{remark}} \hfill \parbox{3cm}{\xymatrix@R=15pt{E_{\mathcal{H}} \ar[r]_{h}\ar[d]_{s_{\mathcal{H}}} & O_\Sigma \ar[d]^{\ari_\Sigma} \\ V_{\mathcal{H}} \ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=15pt{E_{\mathcal{H}} \ar[r]_{h}\ar[d]_{t_{\mathcal{H}}} & O_\Sigma \ar[d]^{\ari_\Sigma}\\ V_{\mathcal{H}}\ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}}
-
-$\hyp_{\Sigma}$, has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \X$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\X}(\mathcal{H}$).
-Now, $U_{\hyp}(\mathcal{G}^{\Sigma})=1$ thus, for every set $X$ we can define $\Delta_{\Sigma}(X)\colon \Delta_{\X}(X)\to \mathcal{G}^{\Sigma}$  as $(?_{O_\Sigma}, !_{X})$.
+By the second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V_\mathcal{H}^{\star}$ of words of length $1$, i.e.~all hyperedges must have a single target vertex, that is $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
+\end{remark}} \hfill \parbox{3cm}{\xymatrix@R=15pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\ari_\Sigma}& \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=15pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\gamma_1}& \mathbb{N}}}
+
+$\hyp_{\Sigma}$, has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \X$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\hyp}(\mathcal{H}$).
+Now, $U_{\hyp}(\mathcal{G}^{\Sigma})=1$ thus, for every set $X$ we can define $\Delta_{\Sigma}(X)\colon \Delta_{\hyp}(X)\to \mathcal{G}^{\Sigma}$  as $(?_{O_\Sigma}, !_{X})$.
 It is straightforward to see that in this way we get a left adjoint to $U_\Sigma$.
@@
 	If $l(h(1) = a$, $l(h_2) = 2$, $l(h_3) = *$, and $l(h_4) = /$, we represent it visually 
-	by putting the identifiers of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$,
-	and removing the idetifiers on the nodes and edges of the latter, as
+	by putting the labels of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$.
 		\begin{center}

### 2025-05-06 calco/final.tex
minori

@@
 \newcommand{\Dwnarrow}{\Downarrow \hspace{-2pt}}
-\newcommand{\egg}{\catname{GEqHyp}}
+\newcommand{\egg}{\mathsf{e}\text{-}\catname{EqHyp}}
 
@@
 	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is a mono.
-We define $\tg$ to be the full subcategory of $\hyp_{\Sigma}$ and denote by $I_\Sigma$ the inclusion.
+We define $\tg$ to be the full subcategory of $\hyp_{\Sigma}$ given by term graphs and denote by $I_\Sigma$ the inclusion.
 Restricting $U_\Sigma\colon \hyp_{\Sigma}\to \catname{Set}$ we get a forgetful functor $U_{\tg}\colon \tg\to \catname{Set}$.
@@
 
+\begin{example}
+The labelled hypergraph of \Cref{lab_2} is a term graph.
+\end{example}
+
 We now examine some properties of $\tg$, in order to study its adhesivity properties.
+We begin noticing that, for every set $X$,  $\Delta_\Sigma(X)$ has no hyperedges and so is a term graph.
+this yields at once the following.
 
@@
 \begin{lemma}\label[lemma]{prop:push} Consider three term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$.
-Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout along $(f_2, g_2)$,  then their pushout $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ is a term graph too.
+Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout  $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ along $(f_2, g_2)$ is a term graph too.
 \end{lemma}
 
-\Cref{thm:slice-functors}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{CorradiniG05}.
+\Cref{thm:slice-functors,prop:mono}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{CorradiniG05} (see also \cite[Cor.~5.15]{CastelnovoGM24} for the details of the argument presented here).
 \begin{corollary}\label{cor:term}
@@
 	%
-	A morphism $h\colon \mathcal{G\to H}$ is a triple $(h_E, h_V, h_C)$ such that the following diagrams commute
+	A morphism $h\colon \mathcal{G\to H}$ is a triple $(h_E, h_V, h_Q)$ such that the following diagrams commute
 	\[\xymatrix@R=15pt{
-		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_C} \\
+		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_Q} \\
 		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}^\star}}& {V_\mathcal{H}}\ar@{>>}[r]_{q_\mathcal{H}} & {Q_\mathcal{H}}
@@
 
-Combining together the previous corollary with \Cref{rem:eqhyp_morphs} we get the following characterization of monos in $\EqHyp$.
+From the previous results we get the following characterization of monos in $\EqHyp$.
 
 \begin{corollary}\label{cor:mono1}
-	An arrow $(h_E, h_V, h_C): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
+	An arrow $(h_E, h_V, h_Q): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
 \end{corollary}
@@
 		\item $F$ has a colimit which is preserved by $K$;
-	\item if $(L, \{l_d\}_{d\in \D})$ is a limiting cocone for $K \circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$, where $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ is limiting for $T\circ F$.
+	\item consider a cone $(L, \{l_d\}_{d\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$.
 \end{enumerate}
@@
 	The action of the functor on a morphism of hypergraphs with equivalences gives a morphism of hypergraphs,
-	in fact $q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E = q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G} = h_C^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}$.
+	in fact $q^{\star}_\mathcal{H} \circ s_\mathcal{H} \circ h_E = q^{\star}_\mathcal{H} \circ h_V^\star \circ s_\mathcal{G} = h_Q^\star \circ q^{\star}_\mathcal{G} \circ s_\mathcal{G}$.
 	The same is valid for $t_\mathcal{H}$ and $t_\mathcal{G}$. 
@@
 \noindent
-\parbox{10cm}{
+\parbox{11cm}{
 \begin{definition}
@@
 	     \xymatrix@R=18pt{
-	        V_\mathcal{G} \ar@{>>}[d]_{q_\mathcal{G}} \ar@{>->}[r]_{h_V}& V_\mathcal{H} \ar@{>>}[d]^{q_\mathcal{H}} \\
-	        Q_\mathcal{G} \ar@{>->}[r]^{h_Q} & Q_\mathcal{{H}}
+	        V_\mathcal{G} \ar@{>>}[r]_{q_\mathcal{G}} \ar@{>->}[d]_{h_V}& Q_\mathcal{G} \ar@{>->}[d]^{h_Q}\\
+	        V_\mathcal{H} \ar@{>>}[r]^{q_\mathcal{H}}  & Q_\mathcal{{H}}
               }
@@
 Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
-From the second point of \Cref{thm:slice-functors,prop:eqhyp_complete,lim} we can deduce the following.
+From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors,cor:eqade}, we can deduce the following.
 
@@
 \parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $J_\Sigma$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.
-Unwrapping the definition and using \Cref{lem:reg}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill
+By \Cref{lem:reg,prop:monos_in_eqhyps}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill
 \parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]_{h_Q}& Q_{\mathcal{H}}} }
@@
 
+\begin{example}
+	Consider the hypergraph of $\mathcal{G}$ \Cref{exa_2} and consider as quotient the identity $\id{V_\mathcal{G}}\colon V_\mathcal{G}\colon \to\mathcal{G}$.
+Then the kernel pair of $\id{V^\star_\mathcal{G}} \circ s$ concide with the kernel pair of $s$ which is empty.
+Thus  $\mathcal{G}$ is, trivially, an e-hypergraph
+\end{example}
 A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proof are in \Cref{proof:elim}.
@@
 \begin{corollary}\label{cor:ereg}
-	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is so in $\hyp$. 
+	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is a regular mono in $\hyp$. 
 \end{corollary}
@@
 \comp*}\hfill 
-\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>->}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
+\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
 
@@
 By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
-By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_C} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
+By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_Q} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
 

### 2025-05-06 calco/rebuttal/letter.tex
minori

@@
 
-ANSWER: we haveused "labels"
+ANSWER: changed with "labels"
+
+\item $233$: Mention that the objects of $\mathbf{TG}_\Sigma$ are precisely the term graphs.
+
+ANSWER: Fixed.
+
+\item $234-237$: Please add somewhere an example of a term graph.
+
+ANSWER: added
+
+\item $236$: Since every labelled hyperedge has a unique vertex as target, being a term graph simply means each hyperedge having a distinct target. This could have been said more explicitly.
+
+ANSWER: That's true but it seems to us that this formulation is neither clearer nor more informative that ours.
+
+\item $238$: What is the left adjoint $\Delta_{\mathbf{TG}_\Sigma}$?
+Is it equal to $\Delta_{\Sigma}$?
+If that's the case, it's worth it to say in one sentence that there is nothing to be checked in order to prove that the resulting labelled hypergraph is a term graph, as there are no hyperedges.
+
+ANSWER: Added.
+
+\item $247$: A little more explanation is required.
+Are you doing a proof by contradiction supposing a terminal object $1$ (with at most one hyperedge) and then showing that two hypergraphs $\mathcal{G}_a$ and $\mathcal{G}_b$, with one hyperedge each labeled $a$ and $b$ respectively, then the unique morphisms $\mathcal{G}_a \to 1$ and $\mathcal{G}_b \to 1$ lead to a contradiction about the label of the hyperedge in 1 (in the case 1 has an hyperedge, and with another argument in case $1$ has no hyperedge)?
+
+ANSWER: if $1$ has no hyperedge than no argument is needed since $\mathcal{G}_a$ does not have arrows into it.
+If $1$ has one hyperedge than the existence of arrows $\mathcal{G}_a\to 1$ and $\mathcal{G}_b\to 1$ entails that $a=b$, which is a contradiction.
+Alll the details are in the cited reference [10].
+
+\item $259$: The wording is confused: "then its pushout along (f2,g2), then their pushout".
+
+ANSWER: Fixed.
+
+\item $263$: How does Corollary 3.27 follow from Proposition 2.4, Proposition 3.25, and Lemmma 3.26?
+This needs to be fleshed out.
+Does it use the fact that $\mathbf{Hyp}$ is adhesive (Corollary 3.6) and the subcategory property of Proposition 2.4?
+
+ANSWER: $\mathbf{Hyp}_\Sigma$ is adhesive, $\mathbf{TG}_\Sigma$ is closed in it under pullbacks and pushout along monos which preserve input nodes.
+Since these are the regular monos Prop.~2.4(4) entails the thesis.
+We add (another) pointer to [10] for details.
+
+\item $273$: Why is the notation $h_C$ and not $h_Q$?
+ANSWER: Fixed.
+
+\item $285$: Do you mean to say that proofs (pural) of Section 4 can be found in Appendix A.2?
+
+ANSWER: This pointer refers to the proof of Prop.~4.4. There is another pointer some lines below for the proof of Lem,~4.8.
+
+\item $293$: Please add a proof of Corollary 4.6, even if it's only a short one.
+
+ANSWER: We would rather not.
+As stated Cor.
+4.6 is an immediate consequence of Prop.~4.4 because a faithful right adjoint preserves and reflects monos.
+We have eliminated the reference to Rem.~4.3 as it was misleading.
+
+\item $297$: It wouldn't hurt to have the diagram showing the two adjunctions in arrow.
+
+ANSWER: in our opinion it would not enhance the clarity of the paper.
+
+\item $301$: In item 2, the sentence wording uses once again the confusing structure of ending with a definition. Please restructure the sentence.
+
+ANSWER: we do not find the original sentence confusing at all. We nonetheless rephrased it.
+
+\item $301$: Why draw a different diagram here than on line 753?
+
+ANSWER: on line 753 there the same exact diagram, just turned by 90 degree for typographical reasons.
+
+\item $306$: Why is this square not in the same orientation as the one on line 277?
+
+ANSWER: Fixed, even if this change does not affect in the slightest way the readability of the paper.
+
+\item $307$: Be more precise about the sense in which you mean ``suitable", i.e., as the suitable class of monos $\mathcal{M}$ for which $\mathcal{M}$-adhesivity holds.
+
+ANSWER: we find the meaning completely clear from the context. Moreover, the meaning of ``suitable'' is made explicit by the content of Lem.~4.11.
+
+\item $321$: You could add a reference to Definition 3.13 for $\mathcal{G}^\Sigma$.
+
+ANSWER: we find no need to do so: Def.~3.13 is just three pages before.
+
+\item $325$: You could mention that $EqHyp_\Sigma$ can be seen as the comma category $T \downarrow$ ``Constant functor at $\mathcal{G}^\Sigma$".
+This would make the parallel with the definition of the category of labelled hypergraphs that was defined as a slice category.
+Moreover, you could then give a reference for the proof of Proposition 4.17, such as [MacLane Categories for the working mathematician, IV.1, Exercise 2, p86].
+
+ANSWER: We rather not: what the reviewer asked us to mention is exactly the content of Prop.~4.17.
+In turn, we do not see any need to quote the exercise of MacLane's book since the proof Prop.~4.17 it's a complete triviality.
+
+\item $327$: ``to the arrow" -> ``to an arrow"? And why is this arrow necessarily of the form (l,!)? Please provide more details
+
+ANSWER:  no: as mentioned, $R$  is the right adjoint to $T$ so $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to a unique arrow $\mathcal{H}\to R(\mathcal{G}_\Sigma)$.
+That this mate is exactly $(l, !_{V_{\mathcal{H}}})$ follows from the proof of Prop.~4.4 but it's also commpletely obvious given the definition of $\mathcal{G}^\Sigma$.
+
+\item $332$: Please provide details on how invoking those Proposition/Lemma/Corollary really prove Proposition 4.18.
+
+ANSWER: we do not think that these details should be provided because they are already contained in the  Proposition, Lemma and Corollaries quoted.
+added a reference to Cor.~B.11 in which the details are spelled out even more explicitly.
+Point $1$ follows immediately from Cor.~B.11 and Lem.~4.8 and point $2$ is simply the closure of adhesivity properties under the slice construction.
+
+\item$343-344$: Please provide an example of a term graph with equivalence.
+
+ANSWER: we do not think that there is a need to provide an explicit example. If the reviewer needs one, it can equip the term graph of Ex.~3.21 with the equality
+
+\item $344$: ``Thus ...
+right": You meant to say that $S_\Sigma$ makes the diagram on the right commute, right?
+Moreover, please describe what $S_\Sigma$ does explicitly, and why it would make the diagram commute.
+
+ANSWER: the action of $S_\Sigma$ is already in the text: it sends $(\mathcal{H},l)$ to $(T(\mathcal{H}),l)$.
+
+\item $345$: Please provide a proof of this claim.
+ANSWER: we have already provided the proof citing Cor.~4.5 and Prop.~4.18.
+
+\item $351$: Please turn this observation into a lemma and provide a detailed proof of it.
+
+ANSWER: we added a reference to Cor.~4.19  and we believe that this is all that's needed.
+
+\item $367$: What does it mean concretely to ask for $q^\star \circ t\circ \pi_1= q^\star \circ t \circ \pi_2$?
+Please add a connection between the intuitive explanation given in lines 364-365 and the mathematical equation given here.
+
+ANSWER: we do not think that a further explanation is needed because the equation $q^\star \circ t\circ \pi_1= q^\star \circ t \circ \pi_2$ is \emph{exactly} the symbolic translation of ``whenever the relation identifies the source of two hyperedges, it identifies their targets too''.
+
+\item $367$: Also, add a diagram corresponding to the equality, in order to visualise the types of each morphism.
+
+ANSWER: this would be unnecessary and space consuming.
+
+\item $368$: Why does going from ``hypergraph with equivalence" to ``e-hypergraph" result in the category names going ``EqHyp" to ``GEqHyp"? What does the ``G" mean?
+
+ANSWER: notation changed to $\mathsf{e}-\mathbf{EqHyp}$
+
+\item $369-370$: Please add an example of an e-hypergraph.
+ANSWER: added an example
+
+\item $374$: "is so" -> "is a regular mono"
+
+ANSWER: fixed.
+
+\item $383$: Does the use of the word ``context" in this sentence refer to its common meaning in graph rewriting?
+
+ANSWER: no.
+
+\item $391$: Shouldn't $\mathsf{id}_\mathbb{N}$ be $\mathsf{id}^\star_1$ instead?
+
+ANSWER: no, see the answers above about the isomorphism between $\mathbb{N}$ and $1^\star$.
+
+\item $405$: Why the name ``EGG"? Why is this short for ``e-term graph"?
+
+ANSWER: indeed the name ``EGG'', which comes from the already existing literature, is short for ``e-term graph'' or for ``e-graph''.
+
+\item $412$: A detailed explanation and example of what lies precisely in the class $\mathcal{T}_\Sigma$ is necessary to appreciate the next adhesivity result, and figure out its potential applications.
+
+ANSWER: we disagree on the fact that such an explanation is necessary: it is simply the restriction of $\mathcal{T}$ to the subcategory $\mathbf{EGG}$ and $\mathcal{T}$ has been already descripted in elementary terms.
  \end{itemize}

### 2025-05-06 calco/final.tex
r1 e r2

@@
 \noindent
-Thus, $L$ and $R$ are the lift- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
-be present for the rule to be executed, yet they are not affected by the rule itself.
+Thus, $L$ and $R$ are the left- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
+be present for the rule to be executed, yet that are not affected by the rule itself.
 %
@@
 can still be obtained~\cite{ehrig2012,ehrig2014adhesive}. 
-If only the left-hand side belongs to $\mathcal{M}$, the current theory is stil under development, as witnessed e.g.
+If only the left-hand side belongs to $\mathcal{M}$, the current theory is still under development, as witnessed e.g.
 by~\cite{BaldanC0G24}.
@@
 	\label{thm:slice-functors}
-	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category. Then it holds
+	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category. Then the following holds
 	\begin{enumerate}
-		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to \A$ one preserving $\mathcal{M}$-pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
+		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category, $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to \A$ one preserving $\mathcal{M}$-pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
 		\[\comma{\mathcal{N}}{\mathcal{M}}:=\{(h,k) \in \mor(\comma{L}{R}) \mid h\in \mathcal{N}, k\in \mathcal{M}\}\]
 		\item for every object $X$
-		the categories $\X/X$  and $X/X$ are, respectively, (strictly) $\mathcal{M}/X$-adhesive and (strictly) $X/\mathcal{M}$-adhesive, where
+		the categories $\X/X$  and $X/\X$ are, respectively, (strictly) $\mathcal{M}/X$-adhesive and (strictly) $X/\mathcal{M}$-adhesive, where
 		\[\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
@@
 		\mathcal{M} \text{ for every } Y\in \Y\}$;
-		\item if $\Y$ is a full subcategory of $\X$ closed in it under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ that is stable under pullbacks and pushouts, contains all isos, and is closed under composition and decomposition.
+		\item if $\Y$ is a full subcategory of $\X$ closed under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ that is stable under pullbacks and pushouts, contains all isos, and is closed under composition and decomposition.
 	\end{enumerate} 
@@
 We can state some useful properties of $\mathcal{M}$-adhesive category.
-
+(see, for instance, \cite[Thm.~4.26]{ehrig2006fundamentals} or \cite[Fact 2.6]{azzi2019essence}). A proof is provided in \Cref{regmono-proof}.
 \begin{restatable}{proposition}{regmono}\label{prop:regmono}
-	Let $\X$ be an $\mathcal{M}$-adhesive category. Then it holds
+	Let $\X$ be an $\mathcal{M}$-adhesive category. Then the following hold
 	\begin{enumerate}
@@
 \end{restatable}
-%  [Proof in \Cref{regmono-proof}]
+%  [Proof in ]
 
@@
 	If the leftmost square is commutative, then there is a a unique arrow $k_h\colon K_f \to K_g$ making the other three commutative.
-	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}& K_f  \ar@{.>}[r]^{k_h} \ar[d]_{(\pi^1_f,\pi^2_f)} & K_g \ar[d]^{(\pi^1_g, \pi^2_g)}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z & X\times X \ar[r]_{h\times h}& X\times Z}\]
-
-		Moreover, it holds
+	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}& K_f  \ar@{.>}[r]^{k_h} \ar[d]_{(\pi^1_f,\pi^2_f)} & K_g \ar[d]^{(\pi^1_g, \pi^2_g)}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z & X\times Z \ar[r]_{h\times h}& X\times Z}\]
+
+		Moreover, the following hold
 		\begin{enumerate}
 			\item if $h$ is mono then $k_h$ is mono too;
-			\item if the leftmost square is a pullback, then also the central too are so;
-			\item if $h$ is mono and the first square is a pullback then the last one is a pullback too.
+			\item if the leftmost square is a pullback, then also the central two are so;
+			\item if $h$ is mono and the leftmost square is a pullback then the rightmost is a pullback too.
 		\end{enumerate} 
@@
 \parbox{7.5cm}{\begin{restatable}{lemma}{mps}\label{prop:kerset}
-	Suppose that in $\Set$ the cube in the diagram on the left is given, whose top face is a pushout, the left and bottom faces are pullbacks,  and $n\colon B\mto D$ is an injection. 
-	Then it holds
+	Suppose that in $\Set$ the commuting cube in the diagram on the left is given, whose top face is a pushout, the left and bottom faces are pullbacks,  and $n\colon B\mto D$ is an injection. 
+	Then the following hold
 	\begin{enumerate}
@@
 
-\begin{proposition}\label{cor:left}  The forgetful functor $U_{\hyp}$ which sends an hypergraph $\mathcal{G}$ to its object of nodes has a left adjoint $\Delta_{\hyp}$.
+\begin{proposition}\label{cor:left}  The forgetful functor $U_{\hyp}$ which sends a hypergraph $\mathcal{G}$ to its set of nodes has a left adjoint $\Delta_{\hyp}$.
 \end{proposition}
 
-\begin{example}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\Set}(X)$ is the hypergraph which has $X$ as set of nodes, $\emptyset$ as set of hyperedges, and $?_X$ as source and target function.
+\begin{example}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\hyp}(X)$ is the hypergraph which has $X$ as set of nodes, $\emptyset$ as set of hyperedges, and $?_X$ as source and target function.
 \end{example}
@@
 \begin{example}\label[example]{exa_2}
-We represent hypergraphs visually: dots denote nodes and boxes hyperedges. Should we interested in their identity, we put a name near the corresponding dot or box. 
+We represent hypergraphs visually: dots denote nodes and boxes hyperedges. Should we be interested in their identity, we put a name near the corresponding dot or box. 
 Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge comes from the left of the box, while the lines to the targets 
 exit from the right of the box.
-Let us look at the picture below. It represent an hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
-and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair nodes
+Let us look at the picture below. It represent a hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
+and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair of nodes
 	\begin{center}
@@
 
-\begin{proposition}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then it holds
+\begin{proposition}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then the following hold
 	\begin{enumerate}
@@
 \parbox{10.8cm}{\begin{remark}\label[remark]{rem:label}	
-Let $\mathcal{H}=(E, V, s, t)$ be an hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a morphism $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
+Let $\mathcal{H}=(E, V, s, t)$ be a hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
 
@@
 	$(l, !_{V_\mathcal{G}}): \mathcal{G} \to \mathcal{G}^\Sigma$ that is characterised by the image of the edges. 
-	If $l(h(1) = a$, $l(h_2) = 2$, $l(h_3) = *$, and $l(h_4) = /$, we represent it visually 
+	If $l(h_1) = a$, $l(h_2) = 2$, $l(h_3) = *$, and $l(h_4) = /$, we represent it visually 
 	by putting the labels of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$.
@@
 \subsection{Term Graphs}
-Term graphs have been adopted as a convenient way to represents terms over a signature with an explicit sharing of sub-terms,
+Term graphs have been adopted as a convenient way to represent terms over a signature with an explicit sharing of sub-terms,
 and as such have been a convenient tool for an efficient implementation of term rewriting~\cite{Plu:TGR-ENTCS}.
@@
 
-We can list some other categorical properties of $\tg$.
+We can list some other categorical properties of $\tg$ (see \cite[Sec.~5]{CastelnovoGM24}).
 
 \begin{proposition}\label{prop:tlim}
-Let $\Sigma$ be an algebraic signature. Then it holds
+Let $\Sigma$ be an algebraic signature. Then the following hold
 \begin{enumerate}
-	\item if  $(i,j)\colon \mathcal{H}\to \mathcal{G}$ is a mono between  $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\hyp_\Sigma$ and the latter is in $\tg$, then also the former is in $\tg$
+	\item if  $(i,j)\colon \mathcal{H}\to \mathcal{G}$ is a mono from $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ to $(l', !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\hyp_\Sigma$ and the latter is in $\tg$, then also the former is in $\tg$
 	\item $\tg$ has equalizers, binary products and pullbacks and they are created by $I_\Sigma$.
@@
 	Let $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$  be a term graph.
-A \emph{input node} is an element of $V_{\mathcal{G}}$ not in the image of $\tau_{\mathcal{H}}$.
+A \emph{input node} is an element of $V_{\mathcal{G}}$ not in the image of $\tau_{\mathcal{G}}$.
 A morphism $(f,g)$ between
-	Let $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l, !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\tg$, is said to \emph{preserve input nodes} if $g$ sends input nodes to input nodes.
+	 $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l, !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\tg$, is said to \emph{preserve input nodes} if $g$ sends input nodes to input nodes.
 \end{definition}
@@
 
-Preservation of inputs characterizes regular monos in $\tg$.
+Preservation of input nodes characterizes regular monos in $\tg$.
 
@@
 The use of hypergraphs equipped with an equivalence relation over their nodes has been argued as a convenient way to express concurrency in the DPO approach to rewriting~\cite{concur2006}
-This section presents the framework by means of adhesive categories, including also its version for term graphs, as a stepping stone towards a analogous characterisation for e-graphs.
+This section presents the framework by means of adhesive categories, including also its version for term graphs, as a stepping stone towards an analogous characterisation for e-graphs.
 
@@
 	\[\xymatrix@R=15pt{
-		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}^\star}}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_Q} \\
-		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}^\star}}& {V_\mathcal{H}}\ar@{>>}[r]_{q_\mathcal{H}} & {Q_\mathcal{H}}
+		{E_\mathcal{G}}\ar[r]^{s_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {E_\mathcal{G}}\ar[r]^{t_\mathcal{G}}\ar[d]_{h_E} & {V_{\mathcal{G}}^\star}\ar[d]^{h_V^\star} & {V_\mathcal{G}}\ar@{>>}[r]^{q_\mathcal{G}}\ar[d]_{h_V} & {Q_{\mathcal{G}}} \ar[d]^{h_Q} \\
+		{E_\mathcal{H}}\ar[r]_{s_\mathcal{H}} & {V_{\mathcal{H}}^\star}	& {E_\mathcal{H}}\ar[r]_{t_\mathcal{H}} & {V_{\mathcal{H}}^\star}& {V_\mathcal{H}}\ar@{>>}[r]_{q_\mathcal{H}} & {Q_\mathcal{H}}
 	}\]
@@
 
-Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ sending an hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
+Forgetting the quotient part yields a functor $T\colon \EqHyp \to \hyp$ sending a hypergraph with equivalence $(E_\mathcal{G}, V_{\mathcal{G}}, C_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ to $(E_{\mathcal{G}}, V_{\mathcal{G}}, s_\mathcal{G}, t_{\mathcal{G}})$.
 We now explore some of its properties to deduce information on the structure of $\EqHyp$.
@@
 
-\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then it holds
+\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then the following hold
 	\begin{enumerate}
@@
 
-Now, we can consider the forgetful functor $U_{\eq}\colon \EqHyp\to \Set$ obtained composing $T$ and $U_{\hyp}$.  By \Cref{cor:left} and the second point of \Cref{prop:forghyp} we get the following.
+Now, we can consider the forgetful functor $U_{\eq}\colon \EqHyp\to \Set$ obtained by composing $T$ and $U_{\hyp}$.
+By \Cref{cor:left} and the second point of \Cref{prop:forghyp} we get the following.
 
@@
 We  exploit it to compute limits and colimits in $\EqHyp$.
-In order to do so.
 A full proof of the following lemma can be found in \Cref{proof:comp}.
@@
 \begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
-Let $F\colon \D \to \EqHyp$ be a diagram and $(E_d, V_d, Q_d, s_d, t_d, q_d)$ the image of an object $d$. Then it holds
+Let $F\colon \D \to \EqHyp$ be a diagram and $(E_D, V_D, Q_D, s_D, t_D, q_D)$ the image of an object $D$. Then the following hold
 \begin{enumerate}
 		\item $F$ has a colimit which is preserved by $K$;
-	\item consider a cone $(L, \{l_d\}_{d\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^d_E, \pi^d_V)\}_{d\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $d\in \D$.
+	\item consider a cone $(L, \{l_D\}_{D\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $D\in \D$.
 \end{enumerate}
 \end{restatable}}\hfill 
-\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
+\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_D}}
 
@@
 
-We can now build another functor $\EqHyp \to \hyp$: the idea is that from an object of $\EqHyp$ one can build an hypergraph taking as set of nodes directly the codomain of the quotient map.
+We can now build another functor $\EqHyp \to \hyp$: the idea is that from an object of $\EqHyp$ one can build a hypergraph taking as set of nodes directly the codomain of the quotient map.
 
@@
 
-On the one hand, if we apply $\quo$ and compute the pullback of the resulting morphisms, we obtain an hypergraph with no hyperdeges and $A\times B$ as set of nodes.
+On the one hand, if we apply $\quo$ and compute the pullback of the resulting morphisms, we obtain a hypergraph with no hyperdeges and $A\times B$ as set of nodes.
 On the other hand, \Cref{prop:eqhyp_complete} we know that taking the pullback of the original two morphisms gives us the hypergraph with equivalence $(\emptyset, \emptyset, Q, ?_{\emptyset^\star}, ?_{\emptyset^\star}, q)$ where $Q$ is the image of $?_{A\times B}$, so that $Q$ is also empty.
@@
 \begin{minipage}[l]{.35\linewidth}Consider e.g. the cube aside: the vertices are just graphs without edges, and in the graphs themselves the equivalence classes 
-are denoted by encircling nodes with a dotted line. All the arrows are regular mono. It is immediate to see that the bottom face is a pushout and the side faces are pullback. Unfortunately, 
+are denoted by encircling nodes with a dotted line. All the arrows are regular monos. It is immediate to see that the bottom face is a pushout and the side faces are pullback. Unfortunately, 
 the top face fails to be a pushout
@@
 A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\hyp$.
-A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{H})$.
+A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{h})$.
 
@@
 
-Let $(\mathcal{H}, l)$ be an object of $\EqHyp_\Sigma$, then, since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ correponds to the arrow $(l, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G}^\Sigma)$.
+Let $(\mathcal{H}, l)$ be an object of $\EqHyp_\Sigma$, then, since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to the arrow $(l, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G}^\Sigma)$.
 It is immediate to see that this correspondence extends to an equivalence with the slice over $R(\mathcal{G}^\Sigma)$.
@@
 
-\begin{proposition}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then it holds
+\begin{proposition}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then the following hold
 	\begin{enumerate}
@@
 
-\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then it holds
+\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then the following hold
 	\begin{enumerate}
@@
 \label{eggs}
-The previous section proved some adhesivity property for the categories $\EqHyp$ and $\EqTG_{\Sigma}$. We extends these results ito
-encompass equivalence classes which are closed under the target arrow, i.e. under operator composition for term graphs, thus precisely capturing EGGs.
+The previous section proved some adhesivity property for the categories $\EqHyp$ and $\EqTG_{\Sigma}$. We extend these results to
+encompass equivalence classes which are closed under the target arrow, i.e.~under operator composition for term graphs, thus precisely capturing EGGs.
 %
@@
 \parbox{11.5cm}{\begin{restatable}{lemma}{epo}\label{lem:epo}
-	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ an arrow in $\pbc$. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is so too.
+	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ a mono in $\pbc$. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is so too.
 	%an object of $\egg$ too.
@@
 \begin{proposition}\label{prop:varie}
-	Let $\Sigma$ be an algebraic signature. Then it holds
+	Let $\Sigma$ be an algebraic signature. Then the following hold
 	\begin{enumerate}
 		\item $\egg_\Sigma$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$.
-		\item There exists a functor $W_\Sigma \colon \egg_\Sigma\to \Sigma$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
+		\item There exists a functor $W_\Sigma \colon \egg_\Sigma\to \egg$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
 	\end{enumerate}
@@
 \begin{definition}\label[definintion]{def:GEqTGs}
-	Given a signature $\Sigma$,  we say that an object $(\mathcal{H}, l)$ of $\EqTG_{\Sigma}$ is a \emph{e-term graph} if $\mathcal{H}$ is an e-hypergraph.
+	Given a signature $\Sigma$,  we say that an object $(\mathcal{H}, l)$ of $\EqTG_{\Sigma}$ is an \emph{e-term graph} if $\mathcal{H}$ is an e-hypergraph.
 We define the category $\eg$ as the full subcategory of $\EqTG_{\Sigma}$ given by e-term graphs and denote by $K_\Sigma$ the corresponding inclusion.
@@
 can be described as a suitable $\mathcal{M}$-adhesive category. 
-The latter precisely capture EGGS, as originally
+The latter precisely capture EGGs, as originally
 presented in~\cite{WillseyNWFTP21}. 
 %
-Being a purely graphical representation, EGGS allows for redundancy and possibly ambiguity,
+Being a purely graphical representation, EGGs allows for redundancy and possible ambiguity,
 so that e.g. a term such as $a / a$ admits a few different representations as a term graph, as shown below
@@
 %
-Admittedly, the third one is illegal, i.e. it is an object of $\EqTGs$ but not one of $\eg$:
+Admittedly, the third one is illegal, i.e.~it is an object of $\EqTGs$ but not one of $\eg$:
 %$\GEqTGs$: 
@@
 These are standard results in term graph rewriting, see e.g.~\cite{AriolaKP00}, 
-and they can easily seen as the final and the initial objects of a suitable comma category 
+and they can be easily seen as the final and the initial objects of a suitable comma category 
 $\mathcal{G}  \downarrow \tg$, respectively.
@@
 %
-for EGGSs, even if the minimally shared representation is now 
+for EGGs, even if the minimally shared representation is now 
 the middle diagram.
@@
 \label{conclusioni}
-The aim of our paper was to extend the theory of $\mathcal{M}$-adhesive categories in order to include EGGS, 
-a formalism for program optimisation 
+The aim of our paper was to extend the theory of $\mathcal{M}$-adhesive categories in order to include EGGs, 
+a formalism for program optimisation. 
 %via a compact representation and 
@@
 %and via a match that is in $\mathcal{N}$. 
-and fact allows for exploiting the properties 
+and that allows for exploiting the properties 
 of the $\mathcal{M}$-adhesive framework.
@@
 In both cases, the key intuition is  to use string diagrams to represents term graphs. We adopted a
-more down-to-Earth approach by equipping
+more down-to-earth approach by equipping
 concretely the nodes of a term graph with an equivalence relation, thus directly corresponding to the original presentation~\cite{DetlefsNS05},
@@
 %
-We begin recalling  a well-known fact about composition and decomposition of pullbacks \cite{mac2013categories}.
+We begin recalling  a well-known fact about composition and decomposition of pullbacks \cite[Lem.~1.1]{lack2005adhesive}.
 
@@
 \subsection{Proofs for \Cref{sec:ade}}\label{app:primo}
-\commentato{
+
 \regmono*
@@
 		By construction the top face of the cube is a pushout and the back one a pullback.
-The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the thesis follows.
+The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the claim follows.
 		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback.
@@
 \end{proof}
-}
 
 \kpp*
-\begin{proof}\label{kpp-proof}\begin{enumerate}
+\begin{proof}\label{kpp-proof}
+	We begin by computing 
+	\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]
+	so that  existence  and uniqueness of the wanted $k_h$ follow at once from the universal property of $K_g$ as the pullback of $g$ along itself.
+
+	\begin{enumerate}
 		\item Let $a,b\colon T\rightrightarrows K_f$ be two arrows such that $k_h\circ a=k_h\circ b$, then we have
@@
 Since $h$ is mono this entails that
-\[pi^1_f\circ a=pi^1_f\circ b \qquad pi^2_f\circ a=\pi^2_f\circ b\]
+\[	\pi^1_f\circ a=\pi^1_f\circ b \qquad \pi^2_f\circ a=\pi^2_f\circ b\]
 and thus $a$ must coincide with $b$.
 
- 		\item  We begin by computing 
-		\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]
-		so that  existence  and uniqueness of the wanted $k_h$ follow at once from the the universal property of $K_g$ as the pullback of $g$ along itself.
-
-		To prove the second half of the thesis, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
+ 		\item  
+		To prove the second half of the claim, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
 		\[\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
@@
 
-		But then the following ones are pullbacks too.
+		But then the outer rectangle in the  following diagrams are pullbacks too.
 		\[\xymatrix@R=15pt{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
@@
 
-		Thus there exist two arrows $x, y\colon T\rightrightarrows K_f$ fitting in the diagrams below.
+		Thus, by point $2$, there exist two arrows $x, y\colon T\rightrightarrows K_f$ fitting in the diagrams below.
 		\[\xymatrix@R=15pt{T\ar@{.>}[r]_-{x} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_1}& K_f \ar@{->}[r]_{k_h} \ar[d]_{\pi^1_f} & K_g \ar[d]^{\pi^1_g} & T \ar@{.>}[r]_-{y} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_2} & K_f  \ar@{->}[r]_{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ & X \ar@{>->}[r]_{h} & Y &&X \ar@{>->}[r]_{h}& Y} \]
@@
 
-		Uniqueness follows now at once again from the fact that $k_h$ is mono.
+		Uniqueness now follows once again from the fact that $k_h$ is mono.
 		\qedhere
@@
 \noindent 
-\parbox{4cm}{\xymatrix@C=10pt@R=6pt{&K_a\ar[dd]|\hole_(.65){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_n\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_(.55){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }} \hfill \parbox{9cm}{\begin{proof}\label{mpo-proof}
-	By  \Cref{prop:regmono}  we know that the the top face of the original cube is a pullback.
-Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks.
-	The thesis now follows from strict $\mathcal{M}$-adhesivity.
+\parbox{4cm}{\xymatrix@C=10pt@R=6pt{&K_a\ar[dd]|\hole_(.65){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_b\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_(.55){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }} \hfill \parbox{9cm}{\begin{proof}\label{mpo-proof}
+	By  \Cref{prop:regmono}  we know that the top face of the original cube is a pullback. Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks.
+	The claim now follows from strict $\mathcal{M}$-adhesivity.
 	\end{proof}}
@@
 Define $\phi\colon B\to Z$ as the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\]
-		By construction there is a unique arrow $\psi \colon D\to Z$ such that $\psi \circ n=k$ and $\psi \circ h=\phi$, thus 
+		By the universal property of pushouts there is a unique arrow $\psi \colon D\to Z$ such that $\psi \circ n=k$ and $\psi \circ h=\phi$, thus 
 		\[
@@
 
-We are left with uniqueness. Let $\psi'\colon D\to Z$ be another arrow such that $\psi' \circ n=k$ and $\psi' \circ h\circ \iota_m=f$. Then we have
+To conclude we have to show that $\psi$ is the unique arrow $D\to Z$ such that $\psi \circ n =k$ and $\psi \circ h\circ \iota_m=f$.
+Let $\psi'\colon D\to Z$ be another arrow such that $\psi' \circ n=k$ and $\psi' \circ h\circ \iota_m=f$.
+Then we have
 		\[\psi'\circ h\circ m=\psi'\circ n\circ g=k\circ g=\phi \circ m =\psi \circ h\circ m \]
-		Hence $\psi'\circ h=\psi \circ h$ and so $\psi'=\psi$ because $(B, \{m, h\circ\iota_m \})$ is a coproduct. 
+	Since $m$ is mono then $\psi'\circ h=\psi \circ h$,  but $(D, \{n, h\})$ is a pushout and so $\psi'=\psi$. 
 \end{proof}
 
-The category of $\Set$ enjoys two other remarkable and useful properties; it is \emph{distributive} and \emph{extensive}.
+The category of $\Set$ enjoys two other remarkable and useful properties; it is \emph{distributive} and \emph{extensive} \cite{carboni1993introduction}.
 Distributivity amount to the following property: for every family $\{X_i\}_{i}$ and an object $Y$, the unique morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms.
-\[\xymatrix@C=15pt@R=15pt{&Y\times X_i \ar@{>->}[dl]_{j_i} \ar@{>->}[dr]^{\id{Y}\times h_i} &&&X_i \times Y \ar@{>->}[dl]_{k_i} \ar@{>->}[dr]^{ h_i \times \id{Y}} \\ \Sum_{i\in I} Y\times X_i \ar@{.>}[rr]_{\phi}&& Y\times (\Sum_{i\in I}X_i) & \Sum_{i\in I}  X_i \times Y \ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \times Y }\]
-
-\noindent 
-\parbox{11.5cm}{\hspace{15pt} Extensivity means that given a family of objects $\{X_{i}\}_{i\in I}$ and a family of squares as the one on the right, where $j_i$ is a  coprojection, then all the squares are pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.}\hfill
+\[\xymatrix@C=15pt@R=15pt{&Y\times X_i \ar@{>->}[dl]_{j_i} \ar@{>->}[dr]^{\id{Y}\times h_i} &&& X_i \times Y \ar@{>->}[dl]_{k_i} \ar@{>->}[dr]^{ h_i \times \id{Y}} \\ \Sum_{i\in I} (Y\times X_i) \ar@{.>}[rr]_{\phi}&& Y\times (\Sum_{i\in I}X_i) & \Sum_{i\in I}  (X_i \times Y )\ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \times Y }\]
+
+\noindent 
+\parbox{11.5cm}{\hspace{15pt} Extensivity means that given a family of objects $\{X_{i}\}_{i\in I}$ and a family of commuting squares as the one on the right, where $j_i$ is a  coprojection, then all the squares are pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.}\hfill
 \parbox{2cm}{\xymatrix@R=15pt{Z_i \ar[r]_{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar@{>->}[r]^{j_i} & X}}
@@
 \begin{remark}\label{rem:disj}
-	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.
-that the pullback between two coproduct injections is given by the initial object (with initial maps ad coprojections).
+	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~that the pullback between two coprojections is given by the initial object (with initial maps as coprojections).
 To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and let $k$ be an element of $I$.
@@
 By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ is a coproduct.
-We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}
+}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}
 
@@
 	\noindent
-	\parbox{10.5cm}{\hspace{15pt}To see this, let $e$ be in $E'$ and suppose that  $c(\iota'(e))=m(x)$ for some $x\in A$.
-Then we can apply the  universal property of pullbacks to build the dotted arrow in the diagram aside, where $v_0$ and $v_1$ are the arrows picking $x$ and $\iota'(e)$, respectively.
+	\parbox{10.5cm}{\hspace{15pt}We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.To see this, let $e$ be in $E'$ and suppose that  $c(\iota'(e))=m(x)$ for some $x\in A$.
+Then we can apply the  universal property of pullbacks to build the dotted arrow $v$ in the diagram aside, where $v_0$ and $v_1$ are the arrows picking $x$ and $\iota'(e)$, respectively.
 But then $e$ must belong to the image of $m'$, which is a contradiction.}\hfill  \parbox{4cm}{\xymatrix@R=15pt{1 \ar[dr]_{v_0}  \ar@/^.3cm/[rr]^{v_1} \ar@{.>}[r]_{v}& A' \ar[d]_{a} \ar@{>->}[r]_{m'} & C' \ar[d]^{c}\\& A  \ar@{>->}[r]^{m}& C}}
@@
 
-		\noindent\parbox{9.5cm}{ of $\Set$, we already know that $(T, \{l_i\}_{i=0}^1)$ is a coproduct, where $l_i\colon T_i\mto T$ are defined by the diagram aside, whose two halves are pullbacks aside.
+		\noindent\parbox{9.5cm}{ of $\Set$, we already know that $(T, \{l_i\}_{i=0}^1)$ is a coproduct, where $l_i\colon T_i\mto T$ are defined by the diagram aside, whose two halves are pullbacks.
 }\hfill\parbox{4cm}{\xymatrix@R=15pt{T_0 \ar@{>->}[r]_{l_0} \ar[d]_{h_0} & T \ar[d]^{t_1} & T_1 \ar@{>->}[l]^{l_1} \ar[d]^{h_1}\\ E' \ar@{>->}[r]^{g'\circ \iota'} & D' & B' \ar@{>->}[l]_{n'}}}
@@
 		By hypothesis the bottom face of the given cube is a pullback, therefore there exists an arrow $u\colon T_0\to A$ such that 
-		\[f\circ u=b\circ t_2\circ l_0 \qquad m\circ u=c\circ \iota'\circ h_0\]
+		\[f\circ u=n\circ t_2\circ l_0 \qquad m\circ u=c\circ \iota'\circ h_0\]
 
@@
 \[n\circ b\circ h_1\circ l^{-1}_1=d\circ n'\circ h_1\circ l^{-1}_1=d\circ t_1=n\circ t_2\]
-And we can conclude that $b\circ \circ h_1\circ l^{-1}_1=t_2$ because $n$ is a mono. The thesis now follows from the fact that  also $n'$ is mono.
-
-		\item 	 By \Cref{lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks.
+And we can conclude that $b\circ h_1\circ l^{-1}_1=t_2$ because $n$ is a mono. The claim now follows from the fact that  also $n'$ is mono.
+
+		\item 	 By \Cref{lem:po_set,lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks.
 		\[\xymatrix@C=45pt@R=15pt{K_b \ar@{>->}[r]^{k_{n'}}  \ar[d]_{(\pi^1_b, \pi^2_b)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
@@
 \begin{align*}
-	n\circ b\circ p_1&=d\circ n'\circ p_1=d\circ \pi^1_d\circ j_1=d\circ \pi^2_d\circ j_1=d\circ g'\circ \iota'\circ q_1\\
+	n\circ b\circ p_1&=d\circ n'\circ p_1=d\circ \pi^1_d\circ j_1=d\circ \pi^2_d\circ j_1=d\circ g'\circ \iota'\circ q_1=g\circ c \circ \iota'\circ q_1\\
 	n\circ b\circ q_2 &=d\circ n'\circ p_2=d\circ\pi^2_D\circ j_2
-	=d\circ \pi^1_d\circ j_2=d\circ g'\circ \iota'\circ p_2
+	=d\circ \pi^1_d\circ j_2=d\circ g'\circ \iota'\circ p_2 = g\circ c \circ \iota'\circ p_2
 \end{align*}
 
-Since the bottom face of the original cube is a pullback (by \Cref{prop:regmono}), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
-\[m\circ k_1=\iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=\iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]
+Since the bottom face of the original cube is a pullback (by hypothesis), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
+\[m\circ k_1= c \iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=c \iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]
 
@@
  Thus we get the dotted arrow $h_0\colon H_0\to K_b$ in the diagram above. Moreover, we have
- \[m\circ a\circ y_0=c\circ m'\circ y_0=c\circ \pi^1_c\circ x_0=c\circ pi^2_c\circ x_0=c\circ m'\circ z_0=m\circ a \circ z_0\]
+ \[m\circ a\circ y_0=c\circ m'\circ y_0=c\circ \pi^1_c\circ x_0=c\circ \pi^2_c\circ x_0=c\circ m'\circ z_0=m\circ a \circ z_0\]
  Since $m$ is a mono $a\circ y_0=a\circ z_0$ and there exists an arrow $h'_0\colon H_0\to K_a$ such that $\pi^1_a\circ h'_0=y_0$ and $\pi^2_a\circ h'_0=z_0$. 
  We now can conclude that $k_{f'}\circ h'_0=h_0$, noticing that
- \[(\pi^1_b\circ \pi^2_b)\circ h_0=(f'\times f')\circ (y_0, z_0)=(f'\times f')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(\pi^1_b, \pi^2_b)\circ k_{f'}\circ h'_0\]
+ \[(\pi^1_b, \pi^2_b)\circ h_0=(f'\times f')\circ (y_0, z_0)=(f'\times f')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(\pi^1_b, \pi^2_b)\circ k_{f'}\circ h'_0\]
 
 We can prove another property of $h'_0$. By computing we have
-\[(\pi^1_c, \pi^2_c)\circ k'_{m'}\circ h'_0=(m'\times m')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(m'\times m')\circ (y_0, z_0)=(\pi^1_c, \pi^2_c)\circ x_0\]
-so that $k'_{m'}\circ h'_0$ must coincide with $x_0$.
+\[(\pi^1_c, \pi^2_c)\circ k_{m'}\circ h'_0=(m'\times m')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(m'\times m')\circ (y_0, z_0)=(\pi^1_c, \pi^2_c)\circ x_0\]
+so that $k_{m'}\circ h'_0$ must coincide with $x_0$.
 
@@
  \[\begin{split}
- 	(\pi^1_d, \pi^2_d\circ k_{g'})\circ x_3&=(g'\times g')\circ (\pi^1_c, \pi^2_c) \circ x_3\\=&(g'\times g')\circ (\iota'\times \iota')\circ (y_3\times z_3)\\=&(g'\circ \iota') \times (g'\circ \iota')\circ (y_3, z_3)
+ 	(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_3&=(g'\times g')\circ (\pi^1_c, \pi^2_c) \circ x_3\\=&(g'\times g')\circ (\iota'\times \iota')\circ (y_3\times z_3)\\=&(g'\circ \iota') \times (g'\circ \iota')\circ (y_3, z_3)
  \end{split}\qquad \begin{split}
@@
 \begin{align*}
-j_3\circ \alpha_3\circ \beta_3=k_{g'}\circ x_3\circ \beta_3=k_{g'} \circ \phi_3=\phi_3  \qquad 
+j_3\circ \alpha_3\circ \beta_3=k_{g'}\circ x_3\circ \beta_3=k_{g'} \circ \phi_3=j_3  \qquad 
 (p_3, q_3)\circ \alpha_3\circ \beta_3=(y_3, z_3)\circ \beta_3=(p_3, q_3) 
@@
  Therefore $\phi_3\circ \alpha_3=x_3$ and thus $x_3\circ \beta_3\circ \alpha_3=x_3$. Moreover
- \[(y_3, z_3)\circ \beta_3\circ \alpha_3=(p_3, q_3\circ \alpha_3)=(y_3, z_3)\]
+ \[(y_3, z_3)\circ \beta_3\circ \alpha_3=(p_3, q_3)\circ \alpha_3=(y_3, z_3)\]
 
@@
 
- We have already proved that $(K_d, \{k'_n, j_3\})$ is a coproduct, thus there is a unique arrow $\theta\colon K_d\to Z$ such that  $\theta \circ k'_{n'}=\gamma$ and $\theta \circ j_3=\delta \circ \phi_3 $.
+ We have already proved that $(K_d, \{k_n, j_3\})$ is a coproduct, thus there is a unique arrow $\theta\colon K_d\to Z$ such that  $\theta \circ k_{n'}=\gamma$ and $\theta \circ j_3=\delta \circ \phi_3 $.
  Now, on the one hand we have
@@
 
- We are left with uniqueness. If $\theta'$ is another arrow $K_d\to Z$ such that $\theta'\circ k_{n'}=\gamma$ and $\theta'\circ k'_{g'}= \delta$. If we compute we get
- \[\theta'\circ j_3=\theta'\circ k_{g'}\circ x_3=\delta \circ x_3=\theta \circ k_{g'}\circ x_3=\theta \circ j_3 \]
+ We are left with uniqueness. If $\theta'$ is another arrow $K_d\to Z$ such that $\theta'\circ k_{n'}=\gamma$ and $\theta'\circ k_{g'}= \delta$. If we compute we get
+ \[\theta'\circ j_3=\theta'\circ k_{g'}\circ \phi_3=\delta \circ \phi_3=\theta \circ j_3 \]
  We already know that $\theta'\circ k_{n'}=\theta \circ k_{n'}$, so the previous identity entails that $\theta =\theta'$.
@@
 In particular, we need the fact that they form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.
-This amount to ask that
+This amounts to ask that
 
@@
 		\item every arrow $f\colon X\to Y$ can be factored as $m\circ e$, where $e\colon X\eto Q$ is a regular epi and $m\colon Q\mto Y$ is a mono;
-			\item for every square as the one on the right, with $e\colon X\eto E$ a surjection and $m\colon N\mto Y$ a mono, there exists a unique $k\colon E\to N$ making it commutative.
-	\end{enumerate}}\hfill \parbox{2cm}{\xymatrix{X \ar@{>>}[d]_{e}\ar[r]^{f}& N \ar@{>->}[d]^{m} \\ E \ar[r]_{g} & Y}}
+			\item for every commuting square as the one on the right, with $e\colon X\eto E$ a surjection and $m\colon N\mto Y$ a mono, there exists a unique $k\colon E\to N$ making it commutative.
+	\end{enumerate}}\hfill \parbox{2cm}{\xymatrix{X \ar@{>>}[d]_{e}\ar[r]^{f}& N \ar@{>->}[d]^{m} \\ E \ar@{.>}[ur]^{k}\ar[r]_{g} & Y}}
 
 	\hspace{1pt}\newline 
-	From these properties, one can deduce that if $f=m\circ e$ and $f=m'\circ e'$ are two factorizations of $f$ then there is an isomorphism $\phi$ such that $m=m'\circ \phi$ and $\phi \circ e=e'$.
+	From these properties, one can deduce that if $f=m\circ e$ and $f=m'\circ e'$ are two factorizations of $f$ then there is a bijection $\phi$ such that $m=m'\circ \phi$ and $\phi \circ e=e'$.
 \end{remark}
@@
 \comp*}\hfill 
-\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^d_V}& V_d \ar@{>>}[dd]^{q_d}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_d}}
+\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_D}}
 
@@
 		\item We know by \Cref{prop:cocomp} that $\hyp$ is cocomplete.
-Thus, let $(E, V, s, t)$ together with $\{(\kappa_E^d, \kappa_V^d)\}_{d \in \D}$ be a colimit for $T \circ F$.
+Thus, let $(E, V, s, t)$ together with $\{(\kappa_E^D, \kappa_V^D)\}_{D \in \D}$ be a colimit for $T \circ F$.
 By \Cref{colim} we also know that
@@
 		 \noindent 
-		 \parbox{10.5cm}{$(V, \{\kappa^d_V\}_{d\in \D})$ is a colimit for $U_\eq\circ F$.
+		 \parbox{10.5cm}{$(V, \{\kappa^D_V\}_{D\in \D})$ is a colimit for $U_\eq\circ F$.
 Moreover, since $\Set$ is cocomplete too we can also take a colimit $(C, \{c_d\}_{d\in \D})$ for $K\circ F$.
-Now,  let $\alpha$ be an arrow $d\to d'$ in $\D$, and suppose that $F(\alpha)$ is $(h_1, h_2, h_3)$.
+Now,  let $\alpha$ be an arrow $D\to D'$ in $\D$, and suppose that $F(\alpha)$ is $(h_1, h_2, h_3)$.
 By definition of morphisms in $\EqHyp$, the square on the right commutes.}
 		\hfill 
-		\parbox{2cm}{\xymatrix{V_d \ar[r]_{h_2} \ar@{>>}[d]_{q_d} & V_{d'} \ar@{>>}[d]^{q_{d'}}\\ Q_{d} \ar[r]^{h_3} & Q_{d'}}}
+		\parbox{2cm}{\xymatrix{V_d \ar[r]_{h_2} \ar@{>>}[d]_{q_D} & V_{D'} \ar@{>>}[d]^{q_{D'}}\\ Q_{D} \ar[r]^{h_3} & Q_{D'}}}
 		\vspace{.05cm}
 
-		Thus the family $\{q_d\}_{d\in \D}$ form a natural transformation $U_\eq\circ F\to K\circ F$.
+		Thus the family $\{q_D\}_{D\in \D}$ form a natural transformation $U_\eq\circ F\to K\circ F$.
 By \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}, the induced arrow $q: V \to C$ between the colimits is a surjection.
-We can then consider the object $(E, V, C, s, t, q)$ of $\EqHyp$, together with the family  $\{(\kappa_E^d, \kappa_V^d, c_d)\}_{d\in \D}$, which by construction is a cocone on $F$.
-Let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^d_E, h^d_V, h^d_Q)\}_{d\in \D})$ be a cocone, then $((E_\mathcal{G},V_\mathcal{G},, s_{\mathcal{G}}, t_{\mathcal{G}}), \{(h^d_E, h^d_V)\}_{d\in \D})$ and $(Q_{\mathcal{G}}, \{h^d_Q\}_{d\in \D})$ are cocone on, respectively, $T\circ F$ and $K\circ D$, giving arrows $(h_E, h_V)$ in $\hyp$ and $h_Q$ in $\Set$ such that
-		\[(h_E, h_V)\circ (\kappa_E^d, \kappa_V^d)=(h^d_E, h^d_V) \qquad h_Q\circ c_D=h^d_Q\]
+We can then consider the object $(E, V, C, s, t, q)$ of $\EqHyp$, together with the family  $\{(\kappa_E^D, \kappa_V^D, c_D)\}_{D\in \D}$, which by construction is a cocone on $F$.
+Let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^D_E, h^D_V, h^D_Q)\}_{D\in \D})$ be a cocone, then $((E_\mathcal{G},V_\mathcal{G}, s_{\mathcal{G}}, t_{\mathcal{G}}), \{(h^D_E, h^D_V)\}_{D\in \D})$ and $(Q_{\mathcal{G}}, \{h^D_Q\}_{D\in \D})$ are cocone on, respectively, $T\circ F$ and $K\circ D$, giving arrows $(h_E, h_V)$ in $\hyp$ and $h_Q$ in $\Set$ such that
+		\[(h_E, h_V)\circ (\kappa_E^D, \kappa_V^D)=(h^D_E, h^D_V) \qquad h_Q\circ c_D=h^D_Q\]
 		Now, to show that $(h_E, h_V, h_Q)$ is an arrow of $\EqHyp$ we can compute
-		\[h_Q\circ q\circ \kappa^d_V=h_Q\circ c_d\circ q_d=h^d_Q\circ q_d=q_{\mathcal{G}} \circ h^d_V=q_{\mathcal{G}}\circ h_V\circ \kappa^d_V \]
+		\[h_Q\circ q\circ \kappa^D_V=h_Q\circ c_D\circ q_D=h^D_Q\circ q_D=q_{\mathcal{G}} \circ h^D_V=q_{\mathcal{G}}\circ h_V\circ \kappa^D_V \]
 
@@
 
-		\item   $\hyp$ is complete, again by \Cref{prop:cocomp}, we can then consider a limiting cone $((E, V, s, t), \{(\pi^i_E, \pi^d_V)\}_{d\in \D})$ over of $T \circ F$.
-Now, $(V, \{q_d\circ \pi_V^d\}_{d\in \D})$, is a cone for $K \circ F$: indeed, if $\alpha: d \to d'$ is an arrow of $\D$, and $F(\alpha)=(h_1, h_2, h_3)$, then we have
-	\[h_3\circ q_d\circ \pi^d_V =q_{d'} \circ h_2\circ \pi^d_{V}=q_{d'}\circ \pi^{d'}_V\]
-
-\noindent 
-\parbox{9.5cm}{Thus there is an arrow $l\colon V\to L$ such that $l_d\circ l=q_d\circ \pi^d_V$.
-We know that there exist $m\colon Q\mto L$ and $q\colon X\eto Q $ such that $m\circ q=l$.
-Since the identity is mono then there exists a unique arrow $\pi^d_Q$ fitting in the rectangle aside.} 	\hfill \parbox{3cm}{\xymatrix{
-	V\ar[r]^{\pi_V^d}\ar@{>>}[d]_{q}&V_d\ar@{>>}[r]^{q_d}&Q_d\ar[d]^{\id{Q_d}}\\Q\ar@{>->}[r]_{m}\ar@{.>}[urr]_{\pi_Q^d}&L\ar[r]_{l_d}&{Q_d}
+		\item   $\hyp$ is complete, again by \Cref{prop:cocomp}, we can then consider a limiting cone $((E, V, s, t), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ over of $T \circ F$.
+Now, $(V, \{q_D\circ \pi_V^D\}_{D\in \D})$, is a cone for $K \circ F$: indeed, if $\alpha\colon D \to D'$ is an arrow of $\D$, and $F(\alpha)=(h_1, h_2, h_3)$, then we have
+	\[h_3\circ q_D\circ \pi^D_V =q_{D'} \circ h_2\circ \pi^D_{V}=q_{D'}\circ \pi^{D'}_V\]
+
+\noindent 
+\parbox{9.5cm}{Thus there is an arrow $l\colon V\to L$ such that $l_D\circ l=q_D\circ \pi^D_V$.
+By \Cref{rem:fact}, we know that there exist $m\colon Q\mto L$ and $q\colon X\eto Q $ such that $m\circ q=l$.
+Since the identity is mono, \Cref{rem:fact} yield a unique arrow $\pi^D_Q$ fitting in the rectangle aside.} 	\hfill \parbox{3cm}{\xymatrix{
+	V\ar[r]^{\pi_V^D}\ar@{>>}[d]_{q}&V_D\ar@{>>}[r]^{q_D}&Q_D\ar[d]^{\id{Q_D}}\\Q\ar@{>->}[r]_{m}\ar@{.>}[urr]_{\pi_Q^D}&L\ar[r]_{l_D}&{Q_D}
 	}}
 
-	Let $\alpha$ be an arrow $d\to d'$ in $\D$. Then we have
-		\[T(F\alpha\circ (\pi^d_{E}, \pi^d_V, \pi^d_Q))=T(F(\alpha))\circ (\pi^d_E, \pi^d_V)=(\pi^{d'}_E, \pi^{d'}_V)=T(\pi^{d'}_{E}, \pi^{d'}_V, \pi^{d'}_Q)\]
-
-		Thus, $((E, V, C, s, t, q), \{(\pi_E^d, \pi_V^d, \pi_C^i)\}_{d\in \D})$ is a cone over $F$.
-To see that it is terminal, let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^d_E, h^d_V, h^d_Q)\}_{d\in \D})$ be another cone, then in particular there is an arrow $(h_E, h_V)\colon (E_\mathcal{G},V_\mathcal{G},  s_{\mathcal{G}}, t_{\mathcal{G}})\to (E, V, s, t)$ in $\hyp$ such that
-		\[\pi^d_E\circ h_E=h^d_E \qquad \pi^d_V\circ h_V=h^d_V\]
-
-		Moreover, applying $K$ we get that $(Q_{\mathcal{G}}, \{h^d_{Q}\}_{d\in \D})$ is a cone over $K\circ F$, so that there is an arrow $h\colon Q_{\mathcal{G}} \to L$ such that $l_d\circ h=h^d_{Q}$.
+	Let $\alpha$ be an arrow $D\to D'$ in $\D$. Then we have
+		\[T(F\alpha\circ (\pi^D_{E}, \pi^D_V, \pi^D_Q))=T(F(\alpha))\circ (\pi^D_E, \pi^D_V)=(\pi^{D'}_E, \pi^{D'}_V)=T(\pi^{D'}_{E}, \pi^{D'}_V, \pi^{D'}_Q)\]
+
+		Thus, by faitfhulness of $T$, $((E, V, C, s, t, q), \{(\pi_E^D, \pi_V^D, \pi_Q^D)\}_{D\in \D})$ is a cone over $F$.
+To see that it is terminal, let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^D_E, h^D_V, h^D_Q)\}_{D\in \D})$ be another cone.
+In particular there is an arrow $(h_E, h_V)\colon (E_\mathcal{G},V_\mathcal{G},  s_{\mathcal{G}}, t_{\mathcal{G}})\to (E, V, s, t)$ in $\hyp$ such that
+		\[\pi^D_E\circ h_E=h^D_E \qquad \pi^D_V\circ h_V=h^D_V\]
+
+		Moreover, applying $K$ we get that $(Q_{\mathcal{G}}, \{h^D_{Q}\}_{D\in \D})$ is a cone over $K\circ F$, so that there is an arrow $h\colon Q_{\mathcal{G}} \to L$ such that $l_D\circ h=h^D_{Q}$.
 Thus
-		\[l_d\circ h\circ q_\mathcal{G}=h^d_Q\circ q_{\mathcal{G}}=q_{d}\circ h^d_V=q_d\circ \pi^d\circ h_V=l_d\circ l\circ h_V\]
-
-\noindent 
-\parbox{2cm}{\xymatrix@R=15pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[ur]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
+		\[l_D\circ h\circ q_\mathcal{G}=h^D_Q\circ q_{\mathcal{G}}=q_{D}\circ h^D_V=q_D\circ \pi^D\circ h_V=l_D\circ l\circ h_V\]
+
+\noindent 
+\parbox{2cm}{\xymatrix@R=15pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[urr]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
 We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that
-\[(\pi^d_E, \pi^d_V, \pi^dQ)\circ (h_E, h_V, k_Q)=(h^d_E, h^d_V, h^d_Q)\]}
+\[(\pi^D_E, \pi^D_V, \pi^D_Q)\circ (h_E, h_V, k_Q)=(h^D_E, h^D_V, h^D_Q)\]}
 
@@
 	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
-	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the thesis follows.}
+	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the claim follows.}
 	\hfill
@@
 	$(\Leftarrow)$ Suppose that $h_E$, $h_V$, and $h_Q$  are monos. 
-	We can build the witnesses component-wise.
-	%
-	It suffices to build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks.
+	We can build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks.
 	\[     \xymatrix@R=15pt{
@@
 \begin{proof}\label{proof:quot}
-  Given an hypergraph $\mathcal{H}:=(E, V, s, t)$, let us define $R(E, V, s, t)$ as $(E, V, V, s, t, \id{B})$.
+  Given a hypergraph $\mathcal{H}:=(E, V, s, t)$, let us define $R(E, V, s, t)$ as $(E, V, V, s, t, \id{B})$.
 By construction $\quo(R(\mathcal{{H}})) =\mathcal{H}$ so that we can take the identity as $\epsilon_{\mathcal{H}}\colon \quo(R(\mathcal{H}))\to \mathcal{H} $.
@@
 
-		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the thesis follows from \Cref{prop:eqhyp_complete}.
+		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the claim follows from \Cref{prop:eqhyp_complete}.
 	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
@@
 Then by \Cref{prop:tlim} $l$ is a term graph.
-We conclude, again by \Cref{rem:obv} that $(\mathcal{L}, l)$ is in $\EqTG_{\Sigma}$ and the thesis follows.
+We conclude, again by \Cref{rem:obv} that $(\mathcal{L}, l)$ is in $\EqTG_{\Sigma}$ and the claim follows.
 \end{proof}
@@
 	By universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$.
-Since $m$ is mono we deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the thesis.
+Since $m$ is mono we deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the claim.
 \end{proof}
@@
 	\end{align*}
-	We can therefore deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the thesis follows.
+	We can therefore deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the claim follows.
 \end{proof}
@@
 	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
-Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite{castelnovo2023thesis,CastelnovoGM24}).
+Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite[Sec.~5.1.3]{castelnovo2023thesis} or \cite[Sec.~2.3]{CastelnovoGM24}).
 \end{lemma}
@@
 By hypothesis $\left(L(A), \{L\left(a_D\right)\}_{D\in \D}\right)$ is colimiting for $L\circ U_L\circ F$.
-Now, if we define $F(D):=(A_D, B_D, f_D)$
-	then we have arrows $R(a_i)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comma{L}{R}$ and so
+Now, let $F(D)$ be $(A_D, B_D, f_D)$,
+	then we have arrows $R(b_D)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comma{L}{R}$ and so
 	\begin{align*}
@@
 \Cref{prop:dual} and \Cref{colim} now yields the following.
-\begin{corollary}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ I$.
+\begin{corollary}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ F$.
 \end{corollary}
@@
 \end{proposition}
-\begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{B})$, for $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
-Consider $\id{B}\colon B\to U_R(\Delta(B))$ be the identity,
+\begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{R(B)})$, for $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
+Let $\id{B}\colon B\to U_R(\Delta(B))$ be the identity,
 
@@
 	\parbox{10cm}{and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given. By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, 
-	since $L$ preserves initial objects, the square aside commutes. Thus $(h,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$ such that $U_R(h,k)=k$. }\hfill 
+	since $L$ preserves initial objects, the square aside commutes. Thus $(?_A,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$ such that $U_R(?_A,k)=k$. }\hfill 
 	\parbox{2cm}{\vspace{-.1cm}\xymatrix@C=30pt@R=15pt{L(0) \ar[r]_{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]^{R(k)}& R(B')}}  

### 2025-05-06 calco/rebuttal/letter.tex
r1 e r2

@@
 ANSWER: we disagree on the fact that such an explanation is necessary: it is simply the restriction of $\mathcal{T}$ to the subcategory $\mathbf{EGG}$ and $\mathcal{T}$ has been already descripted in elementary terms.
+
+\item $418-448$: The wording in Section 6 could be improved. Many sentences are confusing, use colloquial language, or unprecise wording.
+
+TO DO
+
+\item $438$: Why does the depicted DPO rule correspond to $x/x -> 1$?
+
+TO DO
+
+\item $440$: What is ``the arriving one"?
+
+TO DO
+\item $442$: What is ``their nature"?
+
+TO DO
+\item $443-444$: what do you mean by ``the drawback ... same rewriting step"?
+
+TO DO
+
+\item $447-448$: Why is $n$ necessarily the right-hand side itself? Couldn't we consider any $n$?
+
+TO DO
+
+\item $448$: What is exactly meant by this last sentence?
+
+TO DO
+
+\item $465-466$: What do you mean by ``Another venue ... EGGs formalism."?
+
+TO DO
+
+\item $473$: Why ``In both cases"? Aren't you referring to a single paper?
+
+TO DO
+
+\item $571$: The proof of the first claim of Lemma 2.12, i.e., that there exists a unique $k_h$ such that ...
+, is currently in the proof of item 2, and should be instead at the start of the proof (or in its own item).
+
+ANSWER: fixed.
+
+\item $576$: Reasoning goes too fast. Explain why (Universal property of pullbacks) and draw the corresponding diagram.
+
+ANSWER: we disagree with the reviewer and we think that all the details needed for the proof to be followed have been provided.
+
+\item $581$: here and also at multiple other places, the word ``thesis" is used in a way I haven't heard yet.
+Please check if this is a correct meaning of the word or replace it with something more appropriate like ``claim" or ``statement".
+
+ANSWER: fixed.
+
+\item $581-582$: ``two rectangles below are pullbacks" Explain why in more details: left square is a pullback by definition of kernel pairs, and right square is a pullback by assumption, thus by Lemma A1 the outer square is also a pullback.
+
+ANSWER: all the details cited by the reviewer are already in the text (they are quite literally the hypotheses of Lem.~2.12) and so we do not find necesary to recall them again in the proof.
+
+\item $584$: following ones -> following outer rectangles
+
+ANSWER: fixed.
+
+\item $587-588$: Draw the relevant diagram
+
+ANSWER: we think that such diagram is not needed and a waste of space.
+
+\item $589$ : Mention why this holds, namely item 2 and the current assumption.
+
+ANSWER: fixed.
+
+\item $597$: There is a lot of ad hoc reasoning done in order to prove Lemma 2.14. I'm curious if a more elegant and abstract proof could exist.
+
+ANSWER: we didn't find a more abstract proof, even if we suspect that the present proof works in any extensive and distributive monoidal category (see the answer above regarding the Kleene star).
+
+\item $600$: unique arrow s.t. ...: why? Give the reasoning and add the coproduct diagram to help visualise.
+
+ANSWER: in line $600$ we are using the universal property of a product to \emph{define} the arrow $\phi$, so we do not understand the reviewer's question.
+Adding a diagram here would be completely uninformative.
+
+\item $602$: By construction -> By the universal property of pushouts
+
+ANSWER : fixed.
+
+\item $602$: Start a new sentence at ``Thus"
+
+ANSWER: fixed
+
+\item $604$: uniqueness of what? Specify it. Moreover, isn't uniqueness already guaranteed on line 602?
+
+ANSWER: fixed.
+No, the uniqueness invoked in line $602$ is not the same that we must be proved: we know that $\psi$ is the unique arrow such that $\psi \circ n=k$ and $\psi \circ h =\phi$.
+A further (even if elementary) step is needed to show that it is the unque arrow such that it is the unique one such that $\psi \circ n=k$ and $\psi \circ h \circ \iota_m=f$.
+Notice that the uniqueness cited in line $602$ is used in the last line to conclude the proof.
+
+\item $607$: Say that the first claim is by monotonicity of $m$.
+ANSWER: fixed.
+
+\item $607$: Why does $(B,{m,\iota_m})$ being a coproduct implies that $\psi' = \psi$? Explain more
+
+ANSWER: this is an error which we have fixed. What we are using here is that $(D, \{n, h\})$ is a pushout.
+
+\item $613$: ``where $j_i$ is a coprojection" -> why not more directly say that $(X, \{j_i\})$ is a coproduct?
+
+ANSWER: we prefer our formulation.
+
+\item $631$: ``By Lemma A.2 … coproduct." Draw the diagram or mention explicitly which pushout square we consider (i.e., the one on top)
+
+ANSWER: there is no need to draw a diagram since we already mention that we are referring to $(D', \{n', g'\circ \iota\})$ and there is only one pushout in which $D'$ appears.
+
+\item $631$: Be careful about naming conventions. In Lemma A2, the pushout square is ABCD, whereas here it is ACBD.
+
+ANSWER: this change, which amounts to a rotation of the cube, has been done for typographical reason and it is completely harmful.
+
+\item $631$: Put the sentence ``We can … the right" in the same paragraph as its explanation.
+
+ANSWER: Fixed.
+
+\item $632$: First define $v_0$ and $v_1$ then introduce $v$.
+
+ANSWER: we prefer the actual formulation.
+
+\item $632$: ``the dotted arrow": mention its name
+
+ANSWER: fixed.
+
+\item $633$: Draw the corresponding diagram
+
+ANSWER: there is no need to do so and it would be simply a waste of space.
+
+\item $634$: Break down this sentence into more steps. Start by defining $l_0$ and $l_1$. Then mention extensivity.
+
+ANSWER: we find this sentence clear as it is.
+
+\item $638$: Draw the corresponding diagram
+
+ANSWER: as in many previous answers, such diagram is not needed since the two equations are as informative as that.
+
+\item $640$: More explanations are needed.
+It seems you're using that $c \circ \iota' = \iota \circ w$, but if that's the case it needs to be mentioned.
+Right now, the two equations above only have the inclusion of the complement of $C'$, whereas we consider the square with $C$
+
+ANSWER: indeed we are using that propery, which hold by the observations before the bullet points.
+As in the answers before, we do not think that repeating all the hypotheses used every half of a page is needed.
+
+\item $643-644$ Mention more explicitly what "the thesis" is in order to guide the reader and make a stronger case for you proof.
+You're trying to prove the square $B'D'BD$ is a pullback, i.e., to show there exists a unique morphism/function $k \colon  T \to B'$ such that $b\circ k=t_2$ and $n'\circ k = t_1$.
+For the existence of such a $k$, mention explicitly that $h_1 \circ l_1^{-1}$ is one such morphism that satisfies the two desired equalities.
+For the uniqueness of $k$, detail more why it follows from $n'$ being a mono.
+
+ANSWER:  we do not believe that such additional observations are needed, especially if they amounts to restating that we are trying to prove the universal property of pullbacks!
+Similarly, it's a completely trivial observation that then monotonicity of $n'$ entails uniqueness.
+
+\item $645$: Please recall the goal (trying to prove $K_aK_bK_cK_d$ is a pushout) and explain which strategy will be employed (Without warning, I'd expect a standard proof that assumes some morphisms $K_b \to Z \textleftarrow K_c$ and prove the existence and uniqueness of the fitting $K_d \to Z$.) In fact this happens but on line 695, two pages later.
+This proof is too long and should be splift into multiple sub results.
+
+ANSWER: we agree that this result is very technical and its proof quite involved.
+That's why it's been deferred to the appendix.
+However, as in the answer above we do not find the need to restate our claims.
+We also find the strategy quite natural and a standard application of extensivity and distributivty.
+
+\item $645-647$: Break this down into multiple steps.
+
+ANSWER: we prefer to maintain the current formulation.
+
+\item $645-647$: The usage of Lemma A.5 requires to see D' as the coproduct $D' = B' + E'$ which has been said in the text, but never written down mathematically.
+
+ANSWER: we've added a reference to Lem.~A.2
+
+\item $645-647$: What about $j_0$? Is $j_0 = k_{n'}$ up to some unique isomorphism? Please be explicit.
+
+ANSWER: $j_0$ \emph{is} $k_{n'}$, compare the third rectangle of Lem.~2.12. That's why there is a pointer to such lemma.
+
+\item $652$: Rewriting those long series of equalities as only one equality per line with, in the margin, an explanation or a reference to the corresponding commuting square would help follow the reasoning.
+This applies to all other similar long series of equalities in the paper.
+Here, for instance, I cannot find the reason why $d \circ \pi^1_d \circ j_1 = d \circ \pi^2_d \circ j_1$.
+
+ANSWER: this approach would occupy much more space and, in our opinion, not add much in terms of clarity. The equation mentioned by the reviewer follows from the definition of kernel pair.
+
+\item $645-705$: The rest of the proof is difficult to follow and could benefit from restructuring and more guiding.
+What is the prupose of seeing $K_d$ and $K_3$ as coproducts?
+For $K_d$, this is used on lines $697-698$, but I don't see a similar use for $K_3$ (maybe it's my bad).
+
+ANSWER: we did not decompose $K_3$ as a coproduct.
+Lines $659-666$ are needed to build $\phi_3$, which is used later.
+As pointed out by the reviewer, the decomposition of $K_d$ is used in lines $697-698$.
+
+\item $715-716$: Please flesh out this last sentence finishing the proof in more details, and provide appopropriate diagrams.
+
+ANSWER: as in some answers above, we do not find useful to draw the diagram alongide the equation.
+
+\item $719-722$: Same comment
+
+ANSWER: same as above.
+
+\item $734$: Please provide the diagram showing the arrow from X to Y induced by $\phi$.
+
+ANSWER: same as above. It is a very well known fact that a natural transformation between two diagrams induces an arrow between the colimits and there is no need to restate it.
+
+\item $737$: Please provide the type of $\kappa$.
+
+ANSWER: they are \emph{defined} as coprojojections, so there is no need to further specify their typings.
+
+\item $737$: The objects in $\mathbf{D}$ are denoted $d$, and are denoted $D$ in the proof of Lemma B.3, please choose one notation. Same for $\alpha: D \to  D'$ and $d: D \to  D'$.
+
+ANSWER: fixed.
+
+\item $737$: ``By Lemma B.3 ...": The use of this lemma is too quick, with important details missing.
+Which comma category are you considering?
+The only one considered so far is $\mathbf{Hyp} = \mathsf{id}_{\mathbf{Set}} \downarrow \mathsf{prod}^\star$.
+If that's the case, which functor are you considering to play the role of $F$ in Lemma B.3?
+Is it $T\circ F : \mathbf{D} \to  \mathbf{Hyp}$?
+The conclusion of your sentence is about the colimit of $U_{\mathsf{eq}}\circ F$, which has type $\mathbf{D} \to \mathbf{EqHyp} \to \mathbf{Set}$, so are you instead considering $\mathbf{Set}$ as a (trivial) comma category?
+If you want to invoke Lemma B.3, you also need to prove that the functor $L$ preserves colimits along $U_L \circ F$, which you don't mention.
+
+ANSWER: We beg to disagree that the use of this lemma is too quick.
+The further comments of the reviewer suggest that some misunderstanding is at play here.
+Indeed we are considering the fact that $\mathbf{Hyp}$ is equivalent to $\mathsf{id}_{\mathbf{Set}} \downarrow \mathsf{prod}^\star$.
+By Lem.~B.3 $\{U_L, U_R\}$ jointly creates colimits of $F$, in particular $U_L$ preserves colimits and so $(V, \{\kappa^D_V\})$ is colimiting as claimed.
+Notice that, In our case $L$  is the identity and so it preserves colimits along any $F$, moreover $U_L$ becomes $U_{\mathsf{eq}}$.
+
+\item $738-748$: Please add diagrams everywhere where helpful.
+
+ANSWER: see answers above: we do not find necessary to draw diagrams here.
+
+\item $742$: ``by construction": Difficult to see without diagrams/equations/etc.
+
+ANSER: see above.
+
+\item $748$: Please add a summary of what has been just done to check that the two claims of item 1 have indeed be proven.
+
+ANSWER: we believe that such summary is neither needed nor informative.
+
+\item $753$: Please add a diagram of the limiting cone with$ V,L,KF(d)$, and $KF(d')$.
+
+ANSWER:  see answers above: we do not think that adding such diagram is useful.
+
+\item $753$: ``We know ...": it seems you're doing a (regular epi,mono) factorisation of $l$. If that's the case, please be explicit about it.
+
+ANSWER: indeed we are doing such a factorization. We have out a reference to Rem.~A.6
+
+\item $753$: ``Since the identity ...": it seems you're using the property of q being a regular epi. If that's the case, please be explicit about it (and give a reference to Remark A.6)
+
+ANSWER: added.
+
+\item $753$: "fitting in the rectangle aside" -> making the rectangle aside commute.
+
+ANSWER: we prefer our original formulation.
+
+\item $753$: please use mono notation for $\mathsf{id}_{Q_d}$ in the diagram, i.e., add a tail.
+
+ANSWER: We have sistematically avoided the use the tail for isos as the identities. Moreover adding the tail here is completely not informative.
+
+\item $756$: There is some confusion in this whole proof about the quotient set being denoted C or Q. Here, $\pi_C$ is a typo for $\pi_Q$. Please use consistent notations.
+
+ANSWER: fixed
+
+\item $756$: Why does proving that T(cone diagram) commutes necessarily implies that the cone diagram also commutes? Which property are you using? Please, be explicit.
+
+ANSWER: this is just an application of faithfullness of $T$. Added.
+
+\item $763$: ``Hence": You're using the uniqueness of the function $V_G \to L$ in the universal property of L as the limit of KF. Please be explicit about it.
+
+ANSWER: Indeed we are using that property, and, given the computation which happens just above, there is no need to further remark on it.
+
+\item $763$: The morphism $k_Q$ has the wrong target in the diagram.
+
+ANSWER: fixed.
+
+\item $768$: Please go slower and add diagrams.
+Proposition 3.1.3 says that $(-)^\star$ preserves all connected limits.
+Where in the sentences here is it question at all of a set where the star operation has been applied?
+Corollary B.4 requires a diagram in a comma category; which comma category are you considering?
+
+ANSWER:  We are applying Cor.~B.4 to the category of hypergraphs.
+Since the Kleene stars preserves connected limits then, in particular, equalizers are computed componentwise (another proof is obtained appealing to the presentation of term graphs as presheaves).
+
+\item $768$: Regarding the conclusive sentence: be more explicit about having $e,m$ monos and having $h_Q=e\circ m$ entailing that $h_Q$ is mono.
+
+ANSWER: we do not think that it should be mentioned explicitly that the composit of two monos is mono.
+
+\item $769$: What are the ``witnesses"? You're trying to prove that $(h_E,H_V,h_Q)$ is a regular mono. Be more precise.
+
+ANSWER: rephrased.
+
+\item $773$: Once again, please be more precise on how yo apply Lemma B.3.
+
+ANSWER: it seems to us that the application of Lemma B.3 is clear here, since $\mathbf{Hyp}$ is cited explicitly.
+
+\item $789-893$: I didn't have time to go over this part of the proofs. Please check them and improve clarity whenever possible.
+
+ANSWER: Done.
+
+\item $894$: There could have been a mention of this appendix earlier in the text than line 184. It could benefit from being properly mentioned earlier.
+
+ANSWER: this appendix is entirely technical and contains only very well known results. As such it has been quoted only when needed.
+
+\item $911$: What is the reference [9,10] for? For the statement or proof of Lemma B.3? For the definition of what "jointly creating colimits" means?
+
+ANSWER: Precisely.
+
+\item $911$: Can you give a detailed explanation or example of what you mean by ``$\{U_L, U_R\}$ jointly creates colimits of $F$"?
+The definition is currently diluted in the proof, and the reader could benefit greatly from having it from the get-go.
+
+ANSWER: see the answers above. Since this is a technical appendix we think that it sufficient to provide a pointer to the relevant literature.
+
+\item $914$: The word ``define" does not really fit, as F is already defined. Maybe "denote"?
+
+ANSWER: fixed.
+
+\item $916$: Please draw the cocone diagram + the square diagram showing the two components $(LU_LF(d),RU_RF(d))$ of the morphism $F(d):F(D) \to F(D')$. Both would really help visualise the situation.
+
+ANSWER: since this result is entriely known and elementary, we do not think that drawing a diagram is necessary.
+
+\item $918$ and $921$: Same comment as line $652$.
+
+ANSWER: same answer as above.
+
+\item $921$: Shouldn't it be $(L(a_D'),R(b_D'))$ everytime? Also, shouldn't $F(d) = (LU_LF(d),RU_RF(d))$?
+
+ANSWER:  no, it's correct in this formulation.
+
+\item $924$: Please draw the cocone diagrams for $(X,Y,g)$, $(X,{x_D})$, and $(Y,{y_D})$.
+
+ANSWER: same answers regardin the diagrams as above.
+
+\item $930$: "from which it follows": this uses the universal property of $L(A)$ as the colimit of $LU_LF$, which should be explicitly mentioned (and a diagram wouldn't hurt).
+
+ANSWER: same answer as above.
+
+\item $932$: What is the functor I? Is this a typo for F?
+ANSWER: Indeed, fixed.
+
+\item $944$ and $951$: Why the mention of the initial object and terminal object with a plural?
+
+ANSWER: a category can have more than one terminal/inital objects, albeit if they are, obviously, all isomorphic.
+
+\item $948$: The argument for the uniqueness of $(?_A,k)$ could be made clearer. A diagram of the universal morphism would have been helpful
+
+ANSWER: fixed a typo. We do not think that a further clarification is needed.
+
  \end{itemize}
@@
 \begin{itemize}
-	\item 
+	\item  Can you add the DOI of the references, or is it not in line with the assigned format?
+
+	ANSWER: We prefer not to add them.
+
+	\item It seems to me that there is a lack of citations regarding other publications with the similar goal of proving that certain categories of graphs satisfy some form of adhesivity.
+Here are some results from a quick google search.
+Maybe select and cite some relevant ones?
+	\begin{enumerate}
+		\item  Attribution of Graphs by Composition of M, N-adhesive Categories. Christoph Peuser and Annegret Habel
+		\item Weak Adhesive High-Level Replacement Categories and Systems: A Unifying Framework for Graph and Petri Net Transformations. Hartmut Ehrig, Ulrike Golas
+		\item Adhesive Subcategories of Functor Categories with Instantiation to Partial Triple Graphs Extended Version. Jens Kosiol, Lars Fritsche, Andy Schürr, Gabriele Taentzer
+		\item  Fuzzy Presheaves are Quasitoposes. Aloïs Rosset, Roy Overbeek, Jörg Endrullis
+		\item  Towards M-Adhesive Categories Based on Coalgebras and Comma Categories. Julia Padberg
+	\end{enumerate}
+
+	ANSWER: we do not believe that citing the suggested works would be helpful or appropriate, as they appear to be unrelated to the topic at hand.
+
+	507: Should M,N-adhesivity use math notation similarly to line 505?
+
+	ANSWER: indeed, fixed.
+
 \end{itemize}
@@
 \subsection*{Sources of theorems and definitions}
+
+Please add them (with theorem/definition numbers):
 \begin{itemize}
@@
 	ANSWER: added a pointer to the relevant results.
+
+	\item $131$: Proposition 2.6
+
+	ANSWER: added a pointer to the relevant results.
+We added in appendix the proof of the second point for which, while well known, we were unable to find a source in the literature (likely because it follows at once from the first point).
+
+\item $137$: Remark 2.8
+
+ANSWER: this is a basic and elementary result of basic category theory.
+
+\item $139$: Remark 2.9
+
+ANSWER: this is a basic and elementary result of basic category theory.
+
+\item $142$: Proposition 2.10
+
+ANSWER: this is a basic and elementary result of basic category theory.
+
+\item $165$: Proposition 3.1
+
+ANSWER: the only not obvious property of the Kleene star is the first and the reference is provided.
+
+	\item $436$: Definition/theorem number in [13]
+
+TO DO
+
+	\item  $438$: "introductory example in [32]" -> give example number if it exists, or section/page number.
+
+TO DO
+
+	\item $560$: Give theorem number in [26]. You can moreover mention the name of the lemma (either pullback lemma or pasting law for pullbacks).
+
+ANSWER: added the reference.
+
+	\item $608$: Proofs that Set satisfies both properties
+
+	ANSWER: this is a well known fact and so we believe that no further reference is needed.
+
+	\item $609$: Definition of distributivity
+
+	ANSWER: added the relevant references.
+
+	\item $613$: Definition of extensivity
+
+	ANSWER: added the relevant references.
+
+	\item $621$: Lemma A.5
+
+	ANSWER: this is an exercise using the definition of distributivity and extensivity.
+
+\item 	$169$: Remark 3.2
+
+ANSWER: preservation of pullbacks always entails preservation of monos. This is again an exercise in basic category theory.
+
+	\item $175$: Definition 3.4: There are various definitions of hypergraphs. Why this one in particular?
+
+	ANSWER: see answer above.
+
+	\item $177$: Proposition 3.5
+
+	ANSWER: This is not a reference to an already published result. Is a fact which holds basically by definition.
+
+\item $178$: Property of the list monad preserving pullbacks
+
+ANSWER: see above.
+
+	\item $178$: Property of prod being continuous + definition of what is a continuous functor.
+
+ANSWER: we do not believe that there is the need to recall the definition of continuity nor that limits commute with limits.
+
+	\item $240$: Proposition 3.22
+
+	ANSWER: added references.
+
+\item 	$731$: Lemma A.7
+
+	ANSWER: this is, again, an easy exercise of basic category theory.
+
+\item $	911$: Theorem numbers
+
+	ANSWER: added references.
+
 \end{itemize}
 
+\subsection*{Typos}
+
+\begin{itemize}
+\item $37$: left-
+
+ANSWER: fixed.
+
+\item $38$: yet they are -> yet that are
+
+ANSWER: fixed.
+
+\item $110$: Then it holds -> The following holds: (this happens multiple times in the paper)
+
+ANSWER: fixed.
+
+\item $111$: category L -> category, L
+ANSWER: fixed.
+
+\item $114$: forgotten to put the category in bold in the coslice category "$X/ \mathbf{X}$"
+ANSWER: fixed.
+
+\item $150$: solid -> non-dotted?
+
+ANSWER: correct as it is.
+
+\item $185$: object -> set
+ANSWER: fixed.
+
+\item $187$: $\Delta_{Set}$ -> $\Delta_{Hyp}$
+
+ANSWER: fixed.
+
+\item $190$: interested -> be interested
+
+ANSWER: fixed.
+
+\item $214$: V -> $V_\mathcal{H}$
+ANSWER: fixed.
+
+\item $223$: $h(1$ -> $h_1$
+
+ANSWER: fixed.
+
+\item $225$: idetifiers -> identifiers, as -> as follows:
+
+ANSWER: fixed.
+
+\item $251$: $\tau_\mathcal{H}$ -> $\tau_\mathcal{G}$
+
+ANSWER: fixed.
+
+\item $251$: remove "Let"
+
+ANSWER: fixed.
+
+\item $253$: inputs -> input nodes
+
+ANSWER: fixed.
+
+\item $295$: composing -> by composing
+
+ANSWER: fixed.
+\item $301$: limiting cocone -> limiting cone (I think)
+
+ANSWER: fixed.
+
+\item $324$: $T(\mathcal{H})$ -> $T(h)$
+
+ANSWER: fixed.
+
+\item $327$: correponds -> corresponds
+
+ANSWER: fixed.
+
+\item $332$: , ,
+
+ANSWER: fixed.
+
+\item $360$: extends -> extend
+
+ANSWER: fixed.
+
+\item $360$: ito -> to
+
+ANSWER: fixed.
+
+\item $424$: , i.e. -> , i.e.,
+
+ANSWER: fixed.
+
+\item $431$: EGGSs -> EGGs
+
+ANSWER: fixed.
+
+\item $451$: EGGS -> EGGs
+
+ANSWER: fixed.
+
+\item $451$: optimisation To -> optimisation. To
+
+ANSWER: fixed.
+
+\item $474$: down-to-Earth -> down-to-earth
+
+ANSWER: fixed.
+
+\item $575$: pi -> $\pi$
+
+ANSWER: fixed.
+
+\item $593$: now at once -> now once
+ANSWER: fixed.
+\item $607$: $(B,{m, h \circ \iota_m})$ -> $(B,{m,\iota_m})$
+
+ANSWER: fixed.
+
+\item $631$: iota -> iota'
+
+ANSWER: fixed.
+
+\item $634$: twice the word "aside"
+
+ANSWER: fixed.
+
+\item $639$: "$b \circ t_2 \circ l_0$" -> "$t_2 \circ l_0$"
+ANSWER: replaced $b$ with $n$.
+
+\item $643$: $\circ \circ$
+
+ANSWER: fixed.
+
+\item $743$: ,,
+
+ANSWER: fixed.
+
+\item $750$: $\pi^i_E$ -> $\pi^d_E$
+
+ANSWER: fixed.
+
+\item $756$: $\pi^i_C$ -> $\pi^d_C$
+
+ANSWER: fixed.
+
+\item $763$: $\pi^dQ$ -> $\pi^d_Q$
+
+ANSWER: fixed.
+
+\item $914$: $R(a_i)$ -> $R(b_D)$
+
+ANSWER: fixed.
+
+\item $946$: $?_{R(B)}$
+
+ANSWER: fixed.
+
+\item $947$: Consider -> Let
+
+ANSWER: fixed.
+
+\end{itemize} 
 \section*{Reviewer 2}
 
+\begin{itemize}
+\item l. 37 lift -> left
+
+ANSWER: fixed
+
+\item l. 40 "the presence of the match ensures that the two pushouts exist,
+hence a rewriting step can be 41 performed." not true, even if l is
+mono. What is true if l is mono is that if the pushout complement C
+exists then it is unique up to iso.
+
+TO DO
+
+\item l. 44 stil -> still
+
+ANSWER: fixed
+
+\item l. 114 $X/X$ -> $X/\mathbf{X}$
+
+ANSWER: fixed
+
+\item l. 119 "closed in it" not very clear. "closed under pullback" should be enough.
+
+ANSWER: fixed
+
+\item l. 122 please define "closed under decomposition"
+
+ANSWER: fixed
+
+\item l. 155 too -> two
+
+ANSWER: fixed
+
+\item l. 156 first, last -> leftmost, rightmost (to be consistent)
+
+ANSWER: fixed
+
+\item l. 163 Kleen -> Kleene
+
+ANSWER: fixed
+
+\item l. 175 and many others: an hypergraph -> a hypergraph
+
+ANSWER: fixed
+
+\item l.187 $\Delta_Set$ -> $\Delta_Hyp$ (as in Prop 3.8)
+
+ANSWER: fixed
+
+\item l. 190 should we -> should we be
+
+ANSWER: fixed
+
+\item l. 194 you don't need $v_5$
+
+ANSWER: fixed
+
+\item l. 195 a pair -> a pair of
+
+ANSWER: fixed
+
+\item l. 214 (and elsewhere) arrow -> morphism
+a morphism h -> a function h (this is more precise)
+above -> aside
+$V^\star$ -> $V^\star_H$
+in the diagrams, $V_H$ -> $V^*_H$
+in the second diagram, $\mathsf{ar}_\Sigma$ -> $\gamma_1$
+
+ANSWER: we prefer to keep using the term arrow as synonymous to morphism, as standard usage of category theory. We fixed the other observations.
+
+\item  l. 215 $\mathbf{X}$ -> $\mathbf{Set}$
+$U_X$ -> $U_Hyp$
+
+ANSWER: fixed
+
+\item l. 223 $l(h(1)$ -> $l(h_1)$
+
+ANSWER: fixed
+
+\item l. 228 to represents -> to represent
+
+ANSWER: fixed
+
+\item l. 232 is a mono -> is injective
+same thing on l. 236
+
+ANSWER: since monos and injective functions are the same in $\mathbf{Set}$ we have chosen to use both.
+
+\item l. 241 between ... and -> from ... to
+
+ANSWER: fixed
+
+\item l. 250 A input -> An input
+
+ANSWER: fixed
+
+\item l. 259 "then its pushout along (f2,g2), then their pushout ..." remove
+the last part
+
+ANSWER: fixed
+
+\item l. 268 a analogous -> an analogous
+
+ANSWER: fixed
+
+\item 
+l. 277 middle diagram, $V_{G^\star}$ and $V_{H^\star}$ should be $V^\star_G$ and $V^\star_H$
+
+ANSWER: fixed
+
+\item l. 300 "In order to do so." what?
+
+ANSWER: fixed
+
+\item l. 313 are regular mono -> monos
+
+ANSWER: fixed
+
+\item l. 324 $T(H)$ -> $T(h)$
+
+ANSWER: fixed
+
+\item l. 360 extends -> extend
+ito -> to
+
+ANSWER: fixed
+
+\item l. 373 arrow -> morphism
+
+ANSWER: see answer above
+
+\item l. 376 an arrow in Pb -> a mono in Pb
+
+ANSWER: fixed
+
+\item l. 397 "-> $\Sigma$" should be GEqHyp
+
+ANSWER: fixed
+
+\item l. 404 a e-term -> an e-term
+
+ANSWER: fixed
+
+\item l. 421 possibly ambiguity -> possible ambiguity
+
+ANSWER: fixed
+
+\item l. 430 can easily seen -> can be easily seen
+
+ANSWER: fixed
+
+\item l. 451 optimisation To -> optimisation. To
+
+ANSWER: fixed
+
+\item l. 456 fact -> that
+
+ANSWER: fixed
+
+l. 566 rightmost square, $X\times Z$ -> $Z\times Z$
+
+ANSWER: fixed
+
+\item l. 575 pi -> $\pi$
+
+ANSWER: fixed
+
+\item l. 579 the the
+
+ANSWER: fixed
+
+\item l. 595 $K_n$ -> $K_b$
+
+ANSWER: fixed
+
+\item l. 612 $\sum_{i\in I}X_i\times Y$ -> $\sum_{i\in I}(X_i\times Y)$
+
+ANSWER: fixed
+
+\item l. 613 of squares -> of commuting squares
+
+ANSWER: fixed
+
+\item l. 614 coproduct, coproduct injections -> coprojections
+ad -> as
+
+ANSWER: fixed
+
+\item l. 627 the cube -> the commuting cube
+
+ANSWER: fixed
+
+\item l. 639 b -> n
+
+\item l. 643 $\circ\circ$ -> $\circ$
+
+ANSWER: fixed
+
+\item l. 652 add = $g \circ c \circ i \circ q_1$ at the end
+
+ANSWER: fixed
+
+\item l. 653 similarly
+
+ANSWER: fixed
+
+\item l. 654 by Proposition 2.6 -> by hypothesis
+
+ANSWER: fixed
+
+\item l. 656 $i' \circ q_1$ -> $c \circ i' \circ q_1$
+$i' \circ q_2 $-> $c \circ i' \circ p_2$
+
+ANSWER: fixed
+
+\item l. 673 pi -> $\pi$
+
+ANSWER: fixed
+
+\item l. 676 $(\pi^1_b \circ \pi^2_b)$ -> $(\pi^1_b , \pi^2_b)$
+
+ANSWER: fixed
+
+\item  l. 678 $k'_{m'}$ -> $k_{m'}$
+
+ANSWER: fixed
+
+\item l. 679 $k'_{m'}$ -> $k_{m'}$
+
+ANSWER: fixed
+
+l. 686 $(\pi^1_d , \pi^2_d \circ k_{g'})$ -> $(\pi^1_d , \pi^2_d) \circ k_{g'}$
+
+ANSWER: fixed
+
+\item l. 689 $= \phi_3$ -> $= j_3$
+
+ANSWER: fixed
+
+\item l. 693 $(p_3, q_3 \circ \alpha_3)$ -> $(p_3, q_3) \circ \alpha_3$
+
+ANSWER: fixed
+
+\item l. 697 $ k'_n$ -> $k_{n'}$
+
+ANSWER: fixed
+
+\item l. 698 $k'_{n'}$ -> $k_{n'}$
+
+ANSWER: fixed
+
+\item l. 703 $k'_{g'}$ -> $k_{g'}$
+
+ANSWER: fixed
+
+\item l. 704 $x_3$ -> $\phi_3$ (3 occ.)
+
+ANSWER: fixed
+
+l. 725 a a, This amount to -> amounts to
+
+ANSWER: fixed
+
+l. 726 every square -> every commuting square
+
+ANSWER: fixed
+
+l. 729 an isomorphism -> a bijection
+
+ANSWER: fixed
+\end{itemize}
+
 \end{document}

### 2025-05-18 calco/final.tex
passata

@@
 %
-If a category is adhesive, and the arrows of the rules are monomorphisms, then the presence of a match ensures that the
-two pushouts exist, hence a rewriting step can be performed.
-%
-The theory of $\mathcal{M}$-adhesivity~\cite{azzi2019essence,heindel2009category} extends the core framework, still ensuring that if the arrows 
+Should a category be adhesive, and the arrows of the rules monomorphisms, the presence of a match ensures that
+if the pushout complement $C \to G$ exists then it is unique, hence a rewriting step can be deterministically performed.
+%
+The theory of $\mathcal{M}$-adhesivity~\cite{azzi2019essence,heindel2009category} extends the core framework, ensuring that if the arrows 
 of the rules are in a suitable class $\mathcal{M}$ of monomorphisms
@@
 %the classical results from the theory of graph transformation 
-can still be obtained~\cite{ehrig2012,ehrig2014adhesive}. 
-If only the left-hand side belongs to $\mathcal{M}$, the current theory is still under development, as witnessed e.g.
+can be recovered~\cite{ehrig2012,ehrig2014adhesive}. 
+If only the left-hand side belongs to $\mathcal{M}$, the theory is still under development, as witnessed e.g.
 by~\cite{BaldanC0G24}.
 %
-However, despite the elegance and effectiveness and the immediate advantages, 
+However, despite the elegance and effectiveness,
+% and the immediate advantages, 
 %to be adhesive, 
@@
 
+\vspace{-.25cm}
 \parbox{11cm}{\begin{itemize}
@@
 	\begin{definition}
-
 	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the cube below on the right.
@@
 	A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
-	if $\mathcal{M}$-pushouts are Van Kampen. We write $m\colon X \mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
+	if $\mathcal{M}$-pushouts are Van Kampen. {\color{red} We write $m\colon X \mto Y$} to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
 \end{definition}
@@
 	\label{rem:salva} Our notion of $\mathcal{M}$-adhesive category corresponds to what in \cite{ehrig2006fundamentals} is called \emph{weak adhesive HLR category}, while a strict $\mathcal{M}$-adhesive categories corresponds to \emph{adhesive HLR} ones.
-Finally, 	\emph{Adhesivity} and \emph{quasiadhesivity}
+Finally, 	\emph{adhesivity} and \emph{quasiadhesivity}
 	\cite{lack2005adhesive,garner2012axioms} coincide with strict
 	$\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity,
-	respectively. On the other hand
+	respectively. %On the other hand
 \end{remark}
 
-$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of (co-)slice and functor categories \cite{mac2013categories}, as well with respect to subcategories, as shown by the following theorems~\cite[Thm.~4.15]{ehrig2006fundamentals}, \cite[Prop.~3.5]{lack2005adhesive} and  \cite[Thm.~2.12]{CastelnovoGM24}.
+$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of (co-)slice and functor categories \cite{mac2013categories}, as well with respect to subcategories, as shown by the following properties, taken from~\cite[Thm.~4.15]{ehrig2006fundamentals}, \cite[Prop.~3.5]{lack2005adhesive} and  \cite[Thm.~2.12]{CastelnovoGM24}.
 
@@
 	\label{thm:slice-functors}
-	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category. Then the following holds
+	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category. Then the following hold
 	\begin{enumerate}
@@
 		\[\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
-		\mathcal{M}\} \hspace{5pt} X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}\]
+		\mathcal{M}\} \hspace{25pt} X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}\]
 		\item for every small category $\Y$, the category $\X^\Y$ of
@@
 
-We can state some useful properties of $\mathcal{M}$-adhesive category.
+We can state some useful properties of $\mathcal{M}$-adhesive category
 (see, for instance, \cite[Thm.~4.26]{ehrig2006fundamentals} or \cite[Fact 2.6]{azzi2019essence}). A proof is provided in \Cref{regmono-proof}.
@@
 We conclude this section exploring some properties of kernel pairs in an $\mathcal{M}$-adhesive category. 
-The results below appear to be original, and we give their proofs in \Cref{kpp-proof}.
+The results below are simple, yet they appear to be original, and we give their proofs in \Cref{kpp-proof}.
 
@@
 	%
-	If the leftmost square is commutative, then there is a a unique arrow $k_h\colon K_f \to K_g$ making the other three commutative.
+	If the leftmost square is commutative, then there is a unique arrow $k_h\colon K_f \to K_g$ making the other three commutative.
 	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}& K_f  \ar@{.>}[r]^{k_h} \ar[d]_{(\pi^1_f,\pi^2_f)} & K_g \ar[d]^{(\pi^1_g, \pi^2_g)}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z & X\times Z \ar[r]_{h\times h}& X\times Z}\]
@@
 		\begin{enumerate}
-			\item if $h$ is mono then $k_h$ is mono too;
-			\item if the leftmost square is a pullback, then also the central two are so;
-			\item if $h$ is mono and the leftmost square is a pullback then the rightmost is a pullback too.
+			\item if $h$ is a mono then $k_h$ is a mono;
+			\item if the leftmost square is a pullback then the central two are pullbacks;
+			\item if $h$ is mono and the leftmost square is a pullback then the rightmost is a pullback.
 		\end{enumerate} 
@@
 \begin{restatable}{proposition}{mpo}\label{lem:mpo}
-	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top is an $\mathcal{M}$-pushout and all the vertical faces are pullbacks.
+	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top face is an $\mathcal{M}$-pushout and all the vertical faces are pullbacks.
 Then the right square is a pushout.
@@
 	\begin{enumerate}
-		\item the right face of the cube is a pullback too;
+		\item the right face of the cube is a pullback;
 		\item the right square, made by the kernel pairs of the vertical arrows, is a pushout.
@@
 
-\Cref{prop:left,prop:com} allow us to deduce immediately the following.
+{\color{red} \Cref{prop:left,prop:com}} allow us to deduce immediately the following.
 
@@
 We represent hypergraphs visually: dots denote nodes and boxes hyperedges. Should we be interested in their identity, we put a name near the corresponding dot or box. 
-Sources and targets are represented by lines between dots and squares: the lines from the sources of an hyperedge comes from the left of the box, while the lines to the targets 
+Sources and targets are represented by lines between dots and squares: the lines from the sources of a hyperedge comes from the left of the box, while the lines to the targets 
 exit from the right of the box.
@@
 	%
-	The functors $\catname{H}\to \Set$ corresponds exactly to hypergaphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
+	The functors $\catname{H}\to \Set$ corresponds exactly to hypergraphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
 \end{remark}
@@
 
-\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
+{\color{red} \Cref{cor:mono}} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
 
@@
 
-$\hyp_{\Sigma}$, has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \X$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\hyp}(\mathcal{H}$).
-Now, $U_{\hyp}(\mathcal{G}^{\Sigma})=1$ thus, for every set $X$ we can define $\Delta_{\Sigma}(X)\colon \Delta_{\hyp}(X)\to \mathcal{G}^{\Sigma}$  as $(?_{O_\Sigma}, !_{X})$.
+$\hyp_{\Sigma}$ has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \X$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\hyp}(\mathcal{H}$).
+Now, since $U_{\hyp}(\mathcal{G}^{\Sigma})=1$
+for every set $X$ we can define $\Delta_{\Sigma}(X)\colon \Delta_{\hyp}(X)\to \mathcal{G}^{\Sigma}$  as $(?_{O_\Sigma}, !_{X})$.
 It is straightforward to see that in this way we get a left adjoint to $U_\Sigma$.
@@
 \begin{remark}\label[remark]{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
-Notice that since $t_{\mathcal{G}}$ is a mono then $\tau_{\mathcal{G}}$ is a mono too.
+Notice that since $t_{\mathcal{G}}$ is a mono then $\tau_{\mathcal{G}}$ is a mono.
 \end{remark}
@@
 	Since $U_{\tg}$ preserves limits, if a terminal object exists it must have the singleton as set of nodes, therefore the set of hyperedges must be empty or a singleton. 
-	Hence, for a counterexample, it suffices to take as signature the one given by two operations $a$ and $b$, both of arity $0$.
+	Hence, for a counterexample, it suffices to take a signature with two operations $a$ and $b$, both of arity $0$.
 	$\tg$ is not an adhesive category, either. 
@@
 \begin{lemma}\label[lemma]{prop:push} Consider three term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$.
-Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout  $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ along $(f_2, g_2)$ is a term graph too.
+Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout  $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ along $(f_2, g_2)$ is a term graph.
 \end{lemma}
@@
 \label{hypereq}
-The use of hypergraphs equipped with an equivalence relation over their nodes has been argued as a convenient way to express concurrency in the DPO approach to rewriting~\cite{concur2006}
+The use of hypergraphs equipped with an equivalence relation over their nodes has been argued as a convenient way to express concurrency in the DPO approach to rewriting~\cite{concur2006}.
 This section presents the framework by means of adhesive categories, including also its version for term graphs, as a stepping stone towards an analogous characterisation for e-graphs.
@@
 \begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
-Let $F\colon \D \to \EqHyp$ be a diagram and $(E_D, V_D, Q_D, s_D, t_D, q_D)$ the image of an object $D$. Then the following hold
+Consider a diagram $F\colon \D \to \EqHyp$ and let $(E_D, V_D, Q_D, s_D, t_D, q_D)$ be the image of an object $D$. Then the following hold
 \begin{enumerate}
-		\item $F$ has a colimit which is preserved by $K$;
-	\item consider a cone $(L, \{l_D\}_{D\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $D\in \D$.
+		\item $F$ has a colimit, which is preserved by $K$;
+	\item consider a cone $(L, \{l_D\}_{D\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a {\color{red} mono $m\colon Q\mto L$} such that the diagram on the right commutes for every $D\in \D$.
 \end{enumerate}
@@
 A proof is in \Cref{proof:regmono}.
-We have now all the ingredient necessary to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.
+We have now all the ingredients to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.
 
@@
                 \xymatrix@C=10pt@R=6pt{
-                &\emptyset \ar@{>->}[dd]|\hole \ar@{>->}[rr] \ar@{>->}[dl] &&
+                &\emptyset \ar@{>->}[dd]|\hole \ar@{>->}[rr] \ar@{>->}@(dl,)[dl] &&
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
                 \begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
-                \end{tikzpicture} \ar@{>->}[dd] \ar@{>->}[dl] \\
+                \end{tikzpicture} \ar@{>->}[dd] \ar@{>->}@(dl,)[dl]!<6ex,0ex> \\
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
                 \end{pgfonlayer}\end{tikzpicture}
-                \ar@<2ex>@{>->}[dd]_(.3){d}\\&
+                \ar@<2ex>@{>->}[dd]\\&
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
         \end{tikzpicture}
-                \ar@{>->}[rr]|\hole \ar@{>->}[dl] && 
+                \ar@{>->}[rr]|\hole \ar@{>->}@(dl,)[dl] && 
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
                 \end{pgfonlayer}\end{tikzpicture}
-                \ar@{>->}[dl]^{n} \\
+                \ar@{>->}@(,r)[dl] \\
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
 A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\hyp$.
-A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(\mathcal{h})$.
+A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(h)$.
 
@@
 
-Let $(\mathcal{H}, l)$ be an object of $\EqHyp_\Sigma$, then, since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to the arrow $(l, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G}^\Sigma)$.
+Let $(\mathcal{H}, l)$ be an object of $\EqHyp_\Sigma$: since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to the arrow $(l, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G}^\Sigma)$.
 It is immediate to see that this correspondence extends to an equivalence with the slice over $R(\mathcal{G}^\Sigma)$.
@@
 
-We start introducing the notion of \emph{e-hypergraphs}, hypergraphs equipped with an equivalence relation which is closed under the target arrow:
+We start introducing the notion of \emph{e-hypergraphs}, hypergraphs equipped with an equivalence relation that is closed under the target arrow:
 in other words, whenever the relation identifies the source of two hyperedges, it identifies their targets too.
@@
 \begin{example}
-	Consider the hypergraph of $\mathcal{G}$ \Cref{exa_2} and consider as quotient the identity $\id{V_\mathcal{G}}\colon V_\mathcal{G}\colon \to\mathcal{G}$.
-Then the kernel pair of $\id{V^\star_\mathcal{G}} \circ s$ concide with the kernel pair of $s$ which is empty.
+	Consider the hypergraph $\mathcal{G}$ of \Cref{exa_2} and consider as quotient the identity $\id{V_\mathcal{G}}\colon V_\mathcal{G}\colon \to\mathcal{G}$.
+Then the kernel pair of $\id{V^\star_\mathcal{G}} \circ s$ concide with the kernel pair of $s$, which is empty.
 Thus  $\mathcal{G}$ is, trivially, an e-hypergraph
 \end{example}
-A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proof are in \Cref{proof:elim}.
+A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proofs are in \Cref{proof:elim}.
 
@@
 \parbox{11.5cm}{\begin{restatable}{lemma}{epo}\label{lem:epo}
-	Suppose that the square on the right is a pushout in $\EqHyp$ with $m$ a mono in $\pbc$. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is so too.
+	Suppose that the square on the right is a pushout in $\EqHyp$ and that $m$ is a mono in $\pbc$. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is 
+	is an e-hypergraph.
+	%so too.
 	%an object of $\egg$ too.
@@
 
-Let now $\pbe$ be the class of arrows in $\egg$ which are sent to $\pbc$ by $I$.
-By definition and \Cref{lem:pbmono} such class is closed under composition, decomposition, contains all isomorphisms and it is stable under pullbacks.
-Using \Cref{lem:pbmono,lem:epo} we can also deduce that it is stable under pushouts.
+Let now $\pbe$ be the class of arrows in $\egg$ that are sent to $\pbc$ by $I$.
+By definition and \Cref{lem:pbmono} we have that such class is closed under composition and decomposition, it contains all isomorphisms and it is stable under pullbacks.
+Using \Cref{lem:pbmono,lem:epo} we can further deduce that it is stable under pushouts.
 Then \Cref{thm:slice-functors,cor:eqade} yield the following.
@@
 We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs.
-We denote by $J_\Sigma$ the corresponding inclusion functor .
+We denote {\color{red} by $J_\Sigma$} the corresponding inclusion functor .
 \end{definition}
 
-To prove some adhesivity property of $\egg_\Sigma$ let us begin with the following elementary, but useful observation.
+To prove some adhesivity property of $\egg_\Sigma$, we begin with the following elementary, yet useful observation.
 
@@
 	equipped with the two projections.
-On the other hand $\id{\mathbb{N}} \circ \gamma_1 \circ \pi_1$ and $\id{\mathbb{N}}\circ \gamma_1 \circ \pi_2$ are both the function $O_\Sigma \to \mathbb{N}$ constant in $1$.
+On the other hand, both $\id{\mathbb{N}} \circ \gamma_1 \circ \pi_1$ and $\id{\mathbb{N}}\circ \gamma_1 \circ \pi_2$ are the function $O_\Sigma \to \mathbb{N}$ constant in $1$.
 \end{remark}
@@
 \Cref{rem:algegg} now implies at once the following result.
-\begin{proposition}\label{prop:varie}
+
+\samepage{\begin{proposition}\label{prop:varie}
 	Let $\Sigma$ be an algebraic signature. Then the following hold
 	\begin{enumerate}
-		\item $\egg_\Sigma$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$.
-		\item There exists a functor $W_\Sigma \colon \egg_\Sigma\to \egg$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
+		\item $\egg_\Sigma$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$;
+		\item there exists a functor $W_\Sigma \colon \egg_\Sigma\to \egg$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
 	\end{enumerate}
 \end{proposition}
+}
 
@@
 \begin{restatable}{proposition}{pot}\label{prop:pot}
-	$\eg$ has $\mathcal{T}_\Sigma$-pushouts which are created by $K_\Sigma$.
+	$\eg$ has $\mathcal{T}_\Sigma$-pushouts, which are created by $K_\Sigma$.
 \end{restatable}
@@
 \label{rewriting}
-The previous sections have shown how term graphs with equivalence,
-possibly closed with respect to operator composition,
-can be described as a suitable $\mathcal{M}$-adhesive category. 
-The latter precisely capture EGGs, as originally
-presented in~\cite{WillseyNWFTP21}. 
-%
-Being a purely graphical representation, EGGs allows for redundancy and possible ambiguity,
-so that e.g. a term such as $a / a$ admits a few different representations as a term graph, as shown below
+The previous sections have shown how hypergraphs and term graphs with equivalence
+can be described as suitable $\mathcal{M}$-adhesive categories. 
+The same fact holds for their sub-categories where the equivalence is
+ closed with respect to operator composition, and this allows to
+ model EGGs, as originally presented in~\cite{WillseyNWFTP21}.
+
+\emph{Sharing.} 
+Terms are trees, thus different term graphs may represent the same term, up-to the sharing of sub-terms.
+Consider e.g. a constant $a$ and a binary operator $/$: the term $a / a$ admits a few different 
+representations as a term graph with equivalence, as shown below
+
+%Being a purely graphical representation, EGGs allows for redundancy and possible ambiguity,
+%so that e.g. a term such as $a / a$ admits a few different representations as a term graph, as shown below
 %
@@
 %
-Admittedly, the third one is illegal, i.e.~it is an object of $\EqTGs$ but not one of $\eg$:
+The left-most and the right-most images represent just ordinary term graphs, the middle one is a term graph with equivalence.
+As such, they are all objects of $\EqTGs$.
+However, note that the right-most image is not an object of $\eg$:
 %$\GEqTGs$: 
 constants have no input, 
-and nodes that are targets of edges with the same label and source the empty word must be equivalent,
-and possibly the same.
-
-In general, for term graphs without equivalence, a maximally and a minimally shared representation
-exists, and for our toy example are the right-most and the left-most diagram above, respectively.
-These are standard results in term graph rewriting, see e.g.~\cite{AriolaKP00}, 
-and they can be easily seen as the final and the initial objects of a suitable comma category 
+and nodes that are targets of edges with the same label and whose source is the empty word must be equivalent
+and possibly coincide,
+as in the middle and in the left-most image, respectively,
+
+In general, for (acyclic) term graphs, a maximally shared and a minimally shared representation
+exist, and for our toy example are the left-most and the tight-most diagram above, respectively:
+it is a standard result for term graph rewriting, see e.g.~\cite{AriolaKP00}. 
+These two representations can be interpreted as the final and the initial object of a suitable comma category 
 $\mathcal{G}  \downarrow \tg$, respectively.
 %
-The same properties carries on 
+The same properties carry on 
 %when restricting to the full subcategory of acyclic term graphs.
 %
-for EGGs, even if the minimally shared representation is now 
-the middle diagram.
-%
-All the previous considerations can be lifted to the full sub-categories whose objects
-have underlying hypergraphs that are acyclic.
-%an EGG exist, and for our 
-%toy example are the left-most and the middle one above, respectively. In general terms,
-%for an EGG $\mathcal{G}$, such canonical forms are the final and the initial objects of the comma category 
-%$\mathcal{G}  \downarrow \eg$.
-%%\GEqTGs$. 
-%The former part is a standard result in term graph rewriting, see e.g.~\cite{xxx}, while the latter is specific 
+for term graphs with equivalence and for EGGs. However, while in the former case the
+two representations are the same of those for ordinary term graphs, in the latter case
+the minimally shared representation is now the middle image.
+%
+%All the previous considerations can be lifted to the full sub-categories whose objects
+%have underlying hypergraphs that are acyclic.
+%%an EGG exist, and for our 
+%%toy example are the left-most and the middle one above, respectively. In general terms,
+%%for an EGG $\mathcal{G}$, such canonical forms are the final and the initial objects of the comma category 
+%%$\mathcal{G}  \downarrow \eg$.
+%%%\GEqTGs$. 
+%%The former part is a standard result in term graph rewriting, see e.g.~\cite{xxx}, while the latter is specific 
 %of the setting with equivalences.
@@
 
-%\newpage
-What about rewriting? The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
+\emph{Rewriting.} The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
 arrows in $\mathcal{M}$, then we can lift all the standard properties
-of the DPO approach.
+of the DPO approach that hold in the category of graphs.
 % to the category at hand. 
-However, the structure of rules that is advanced in~\cite{DetlefsNS05}
-is given as a span $L \leftarrow L \rightarrow R$, where the first component is the identity, thus in $\pbc_\Sigma$,
+However, as we recalled in the introduction, instead of removing sub-terms, the EGG approach is to
+just add new terms and link them to the older ones via the equivalence relation~\cite{DetlefsNS05}.
+% until an optimal program is 
+%reached and extracted.
+So, the corresponding DPO rules 
+are spans $L \leftarrow L \rightarrow R$, where the first component is the identity, thus in $\pbc_\Sigma$,
 while the second component may not belong to $\pbc_\Sigma$.
 
-\noindent
-\begin{minipage}[l]{.48\linewidth}
-\vspace{.1cm}
 Consider e.g. an EGG rule such $x / x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}.
-It can be modelled as the DPO rule aside, concisely represented as the arrow $L \rightarrow R$,
-which can be applied with a match that is injective on equivalence classes to the legal EGGs
-above.
-\end{minipage}\hfill
-\begin{minipage}[r]{.60\linewidth}
-\xymatrix{        
+Variables in a term graph are represented as nodes that do not belong to the targets of any edge, 
+hence that rule can be modelled as the DPO rule below, concisely represented by the arrow $L \rightarrow R$.
+
+\begin{center}\xymatrix{        
  \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
@@
 }
-\end{minipage}
-
-\vspace{.1cm}
-\noindent
-The right-hand side is a regular mono, though, and if the starting term graph is acyclic, so is also the arriving one.
-Such an asymmetry between and left- and right-hand side falls in the current research about left-linear rules for 
+\end{center}
+
+\noindent
+In this case $L$ is the minimally shared EGG corresponding to the term $x / x$,
+thus the rule could be applied to the two EGGs
+depicted above with a match that is injective on equivalence classes 
+%
+In general, if the term graph underlying the EGG to whom the DPO rule is applied is acyclic,
+the same property holds for the EGG obtained as the result of the rule application.
+%
+
+The right-hand side is a regular mono, though, hence it is not an arrow in $\pbc_\Sigma$.
+The asymmetry between left-hand and right-hand sides falls in the current research about left-linear rules for 
 adhesive categories, as pursued e.g. in~\cite{BaldanC0G24}.
 
-Note also that for their nature, all the rules adopted for EGGs have the identity as the left-hand side. 
-Potentially, they thus belong to any choice of $\mathcal{M}$, even if the drawback is the 
-possibility to keep on repeating the same rewriting step.
-However, this is easily forbidden adopting rules \emph{with negative application conditions}, given as the usual span 
+\emph{Application conditions.} 
+As argued above, the DPO rules that are suitable for the EGG approach have identities as left-hand side,
+thus they belong to any choice of $\mathcal{M}$.
+%
+However, this would allow for the repeated application of the same rule, hence the 
+possibility to keep on performing the same rewriting step.
+This is forbidden by using rules \emph{with negative application conditions}, given as the usual span 
 $L \leftarrow K \rightarrow R$ plus an additional arrow $n: L\rightarrow N$, such that a match $m: L \to G$ is admissible if it cannot
-be factorised through $n$~\cite{HabelHT96}. For EGGs and rules $L \leftarrow L \rightarrow R$, $n$ is simply the right-hand side itself.
-%
-The theory of $\mathcal{M}$-adhesivity carries on with such rules, see~\cite{ehrig2012,ehrig2014adhesive}.
+be factorised through $n$~\cite{HabelHT96}. For EGGs and rules $L \leftarrow L \rightarrow R$, it suffices to choose $n$ as the right-hand side itself.
+%
+The theory of $\mathcal{M}$-adhesivity carries on for rules with negative application conditions, see~\cite{ehrig2012,ehrig2014adhesive}.
 
@@
 %
-Also, it still needs to be exploited how parallelism and causality, the key features for DPO rewriting
+However, it still needs to be shown how parallelism and causality, the key features for DPO rewriting
 on $\mathcal{M}$-adhesive categories, can be exploited in the context of implementing the 
 EGGs updates. 
-Another venue for development is using the adhesive 
-machinery to extend the EGGs formalism. In fact, most of the results
+Moreover, extensions of the EGGs formalism could be suggested by the adhesive 
+machinery we developed.
+In fact, most of the results
 presented here for hypergraphs can be generalised to hierarchical hypergraphs, that is, 
 hypergraphs with a hierarchy (a partial order) among 
-edges~\cite{ghicaZan,CastelnovoGM24}, which is useful for adding structural information, such as encapsulation and sandboxing.
+edges~\cite{ghicaZan,CastelnovoGM24}.
+The additional structure is useful for modelling properties such as encapsulation and sandboxing,
+and it seems worthwhile to check the expressiveness and applications of hierarchical EGGS.
 
@@
 %
-In both cases, the key intuition is  to use string diagrams to represents term graphs. We adopted a
+In fact, for both proposals the key intuition is  to use string diagrams to represents term graphs. We adopted a
 more down-to-earth approach by equipping
@@
 is actually $\mathcal{M}$-adhesive, thus allowing to exploit all the features of the framework
-as they hold for standard graph transformation.
+as they hold for DPO graph transformation.
 
@@
 
-We are now ready to exploit the previous propertis to prove \Cref{prop:kerset}, as promised.
+We are now ready to exploit the previous properties to prove \Cref{prop:kerset}. % as promised.
 
@@
 
-In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$, the slice $\X/X$ has such limits and colimits too.
+In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$, the slice $\X/X$ has such limits and colimits.
 \end{corollary}

### 2025-05-18 calco/rebuttal/letter.tex
passata

@@
 \usepackage{fullpage}
+\usepackage{xcolor}
 
@@
 
-ANSWER: there is a pointer to the appenix befor Lemma 2.12. Such pointer (and all the others) are there to provide the reader with a quick link to the correct proof in the appendix.
+ANSWER: there is a pointer to the appendix before Lemma 2.12. Such pointer (and all the others) are there to provide the reader with a quick link to the correct proof in the appendix.
 
@@
 
-ANSWER: In Prop.~2.13 it is not assumed that the bottom face is a pushout, eve if this property can be deduced from $\mathcal{M}$-adhesivity.
-Notice, however that to Prop.~2.13 it should be enough to ask for stability of $\mathcal{M}$-pushouts: in such a case the bottom face of the cube is not guaranteed to be a pushout (we do not need such level of generality here).
+ANSWER: In Prop.~2.13 it is not assumed that the bottom face is a pushout, even if this property can be deduced from $\mathcal{M}$-adhesivity.
+Notice however that to Prop.~2.13 it should be enough to ask for stability of $\mathcal{M}$-pushouts: in such a case the bottom face of the cube is not guaranteed to be a pushout (we do not need such level of generality here).
 
@@
 
-ANSWER: we removed the brackets since they were useless. Since we are identifying $1^\star$ with $\mathbb{N}$, $\gamma_1$ as codomain $\mathbb{N}$is precisely the element $1\in \mathbb{N}$.
+ANSWER: we removed the brackets since they were useless. Since we are identifying $1^\star$ with $\mathbb{N}$, $\gamma_1$ as codomain $\mathbb{N}$ is precisely the element $1\in \mathbb{N}$.
 
@@
 
- \item $214$: It seems to me that the second diagram can first be explained in much simpler terms, such as "in labelled hypergraphs, all hyperedges must have a single target vertex", and then it could be restated as a factorisation result for $t_\mathcal{H}$.
+ \item $214$: It seems to me that the second diagram can first be explained in much simpler terms, such as ``in labelled hypergraphs, all hyperedges must have a single target vertex'', and then it could be restated as a factorisation result for $t_\mathcal{H}$.
 The current explanation is not clear enough.
@@
 Or maybe $U_{\mathbf{Hyp}}$ that gives the set of vertices?
-There has been a lot of forgetful functor introduced so far, and here is one more being defined, so it would help to have a description in words added to this sentence.
+There has been a lot of forgetful functors introduced so far, and here is one more being defined, so it would help to have a description in words added to this sentence.
 
@@
 
-\item $224-225$: What do you mean by "identifier"? Do you mean "label"? And what does "the latter" refer to?
-
-ANSWER: changed with "labels"
+\item $224-225$: What do you mean by ``identifier''? Do you mean ``label'' And what does ``the latter'' refer to?
+
+ANSWER: Changed with ``labels''.
 
@@
 
-ANSWER: added
+ANSWER: Added.
 
@@
 
-ANSWER: That's true but it seems to us that this formulation is neither clearer nor more informative that ours.
+ANSWER: That is true but it seems to us that this formulation is neither clearer nor more informative that ours.
 
@@
 
-ANSWER: if $1$ has no hyperedge than no argument is needed since $\mathcal{G}_a$ does not have arrows into it.
+ANSWER: If $1$ has no hyperedge than no argument is needed since $\mathcal{G}_a$ does not have arrows into it.
 If $1$ has one hyperedge than the existence of arrows $\mathcal{G}_a\to 1$ and $\mathcal{G}_b\to 1$ entails that $a=b$, which is a contradiction.
-Alll the details are in the cited reference [10].
-
-\item $259$: The wording is confused: "then its pushout along (f2,g2), then their pushout".
-
-ANSWER: Fixed.
-
-\item $263$: How does Corollary 3.27 follow from Proposition 2.4, Proposition 3.25, and Lemmma 3.26?
+All the details are in the cited reference [10].
+
+\item $259$: The wording is confused: ``then its pushout along (f2,g2), then their pushout''.
+
+ANSWER: Fixed.
+
+\item $263$: How does Corollary 3.27 follow from Proposition 2.4, Proposition 3.25, and Lemma 3.26?
 This needs to be fleshed out.
@@
 \item $273$: Why is the notation $h_C$ and not $h_Q$?
-ANSWER: Fixed.
-
-\item $285$: Do you mean to say that proofs (pural) of Section 4 can be found in Appendix A.2?
-
-ANSWER: This pointer refers to the proof of Prop.~4.4. There is another pointer some lines below for the proof of Lem,~4.8.
+
+ANSWER: Fixed.
+
+\item $285$: Do you mean to say that proofs (plural) of Section 4 can be found in Appendix A.2?
+
+ANSWER: This pointer refers to the proof of Prop.~4.4. There is another pointer some lines below for the proof of Lem.~4.8.
 
@@
 
-ANSWER: in our opinion it would not enhance the clarity of the paper.
+ANSWER: We believe it would not enhance the clarity of the paper.
 
@@
 
-ANSWER: we do not find the original sentence confusing at all. We nonetheless rephrased it.
+ANSWER: We do not find the original sentence confusing. We nonetheless rephrased it.
 
@@
 
-\item $307$: Be more precise about the sense in which you mean ``suitable", i.e., as the suitable class of monos $\mathcal{M}$ for which $\mathcal{M}$-adhesivity holds.
-
-ANSWER: we find the meaning completely clear from the context. Moreover, the meaning of ``suitable'' is made explicit by the content of Lem.~4.11.
+\item $307$: Be more precise about the sense in which you mean ``suitable'', i.e., as the suitable class of monos $\mathcal{M}$ for which $\mathcal{M}$-adhesivity holds.
+
+ANSWER: We find the meaning  clear from the context. Moreover, the meaning of ``suitable'' is made explicit by the content of Lem.~4.11.
 
@@
 
-\item $325$: You could mention that $EqHyp_\Sigma$ can be seen as the comma category $T \downarrow$ ``Constant functor at $\mathcal{G}^\Sigma$".
+\item $325$: You could mention that $EqHyp_\Sigma$ can be seen as the comma category $T \downarrow$ ``Constant functor at $\mathcal{G}^\Sigma$''.
 This would make the parallel with the definition of the category of labelled hypergraphs that was defined as a slice category.
@@
 ANSWER: We rather not: what the reviewer asked us to mention is exactly the content of Prop.~4.17.
-In turn, we do not see any need to quote the exercise of MacLane's book since the proof Prop.~4.17 it's a complete triviality.
-
-\item $327$: ``to the arrow" -> ``to an arrow"? And why is this arrow necessarily of the form (l,!)? Please provide more details
-
-ANSWER:  no: as mentioned, $R$  is the right adjoint to $T$ so $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to a unique arrow $\mathcal{H}\to R(\mathcal{G}_\Sigma)$.
-That this mate is exactly $(l, !_{V_{\mathcal{H}}})$ follows from the proof of Prop.~4.4 but it's also commpletely obvious given the definition of $\mathcal{G}^\Sigma$.
+In turn, we do not see any need to quote the exercise of MacLane's book since the proof Prop.~4.17 is trivial.
+
+\item $327$: ``to the arrow'' -> ``to an arrow''? And why is this arrow necessarily of the form (l,!)? Please provide more details
+
+ANSWER:  No: as mentioned, $R$  is the right adjoint to $T$ so $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to a unique arrow $\mathcal{H}\to R(\mathcal{G}_\Sigma)$.
+That this mate is exactly $(l, !_{V_{\mathcal{H}}})$ follows from the proof of Prop.~4.4 but it is also obvious given the definition of $\mathcal{G}^\Sigma$.
 
@@
 
-ANSWER: we do not think that these details should be provided because they are already contained in the  Proposition, Lemma and Corollaries quoted.
-added a reference to Cor.~B.11 in which the details are spelled out even more explicitly.
+ANSWER: We do not think that these details should be provided because they are already contained in the  Proposition, Lemma and Corollaries quoted.
+We added a reference to Cor.~B.11 in which the details are spelled out even more explicitly.
 Point $1$ follows immediately from Cor.~B.11 and Lem.~4.8 and point $2$ is simply the closure of adhesivity properties under the slice construction.
@@
 
-ANSWER: we do not think that there is a need to provide an explicit example. If the reviewer needs one, it can equip the term graph of Ex.~3.21 with the equality
+ANSWER: We believe that there is no need to provide an explicit example. %If the reviewer needs one, it can equip the term graph of Ex.~3.21 with the equality
 
 \item $344$: ``Thus ...
-right": You meant to say that $S_\Sigma$ makes the diagram on the right commute, right?
+right'': You meant to say that $S_\Sigma$ makes the diagram on the right commute, right?
 Moreover, please describe what $S_\Sigma$ does explicitly, and why it would make the diagram commute.
 
-ANSWER: the action of $S_\Sigma$ is already in the text: it sends $(\mathcal{H},l)$ to $(T(\mathcal{H}),l)$.
+ANSWER: The action of $S_\Sigma$ is already in the text: it sends $(\mathcal{H},l)$ to $(T(\mathcal{H}),l)$.
 
 \item $345$: Please provide a proof of this claim.
-ANSWER: we have already provided the proof citing Cor.~4.5 and Prop.~4.18.
+
+ANSWER: We have already provided the proof citing Cor.~4.5 and Prop.~4.18.
 
@@
 
-ANSWER: we added a reference to Cor.~4.19  and we believe that this is all that's needed.
+ANSWER: We added a reference to Cor.~4.19  and we believe that this is all that is needed.
 
@@
 
-ANSWER: we do not think that a further explanation is needed because the equation $q^\star \circ t\circ \pi_1= q^\star \circ t \circ \pi_2$ is \emph{exactly} the symbolic translation of ``whenever the relation identifies the source of two hyperedges, it identifies their targets too''.
+ANSWER: We believe that no further explanation is needed because the equation $q^\star \circ t\circ \pi_1= q^\star \circ t \circ \pi_2$ is \emph{exactly} the symbolic translation of ``whenever the relation identifies the source of two hyperedges, it identifies their targets too''.
 
@@
 
-ANSWER: this would be unnecessary and space consuming.
-
-\item $368$: Why does going from ``hypergraph with equivalence" to ``e-hypergraph" result in the category names going ``EqHyp" to ``GEqHyp"? What does the ``G" mean?
-
-ANSWER: notation changed to $\mathsf{e}-\mathbf{EqHyp}$
+${\mathbf ANSWER: This would be unnecessary and space consuming.}$
+
+\item $368$: Why does going from ``hypergraph with equivalence'' to ``e-hypergraph'' result in the category names going ``EqHyp'' to ``GEqHyp''? What does the ``G'' mean?
+
+ANSWER: Notation changed to $\mathsf{e}-\mathbf{EqHyp}$
 
 \item $369-370$: Please add an example of an e-hypergraph.
-ANSWER: added an example
-
-\item $374$: "is so" -> "is a regular mono"
-
-ANSWER: fixed.
-
-\item $383$: Does the use of the word ``context" in this sentence refer to its common meaning in graph rewriting?
-
-ANSWER: no.
+
+ANSWER: Added.
+
+\item $374$: ``is so'' -> ``is a regular mono''.
+
+ANSWER: Fixed.
+
+\item $383$: Does the use of the word ``context'' in this sentence refer to its common meaning in graph rewriting?
+
+ANSWER: No.
 
@@
 
-ANSWER: no, see the answers above about the isomorphism between $\mathbb{N}$ and $1^\star$.
-
-\item $405$: Why the name ``EGG"? Why is this short for ``e-term graph"?
-
-ANSWER: indeed the name ``EGG'', which comes from the already existing literature, is short for ``e-term graph'' or for ``e-graph''.
+ANSWER: No, see the answers above about the isomorphism between $\mathbb{N}$ and $1^\star$.
+
+\item $405$: Why the name ``EGG''? Why is this short for ``e-term graph''?
+
+ANSWER: Indeed the name ``EGG'', which comes from the already existing literature, is short for ``e-term graph'' or for ``e-graph''.
 
@@
 
-ANSWER: we disagree on the fact that such an explanation is necessary: it is simply the restriction of $\mathcal{T}$ to the subcategory $\mathbf{EGG}$ and $\mathcal{T}$ has been already descripted in elementary terms.
+ANSWER: We disagree that such an explanation is necessary: it is simply the restriction of $\mathcal{T}$ to the subcategory $\mathbf{EGG}$ and $\mathcal{T}$ has been already descripted in elementary terms.
 
@@
 
-TO DO
+ANSWER: We streamlined and cleaned up the presentation, also adding details.
 
@@
 
-TO DO
+ANSWER: Added explanation.
 
@@
 
-TO DO
+ANSWER: Added explanation.
+
 \item $442$: What is ``their nature"?
 
-TO DO
+ANSWER: Added explanation.
+
 \item $443-444$: what do you mean by ``the drawback ... same rewriting step"?
 
-TO DO
+ANSWER: Rephrased sentence.
 
@@
 
-TO DO
+ANSWER: Not necessarily, But for the EGGs rule, it suffices to forbid that the same rule is applied twice. Rephrased sentence.
 
@@
 
-TO DO
+ANSWER: We meant rules with negative application conditions. Added.
 
@@
 
-TO DO
+ANSWER: Rephrased sentence.
 
@@
 
-TO DO
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed.
+ANSWER: Fixed.
 
@@
 
-ANSWER: we disagree with the reviewer and we think that all the details needed for the proof to be followed have been provided.
-
-\item $581$: here and also at multiple other places, the word ``thesis" is used in a way I haven't heard yet.
+ANSWER: We disagree with the reviewer and we think that all the details needed for the proof to be followed have been provided.
+
+\item $581$: here and also at multiple other places, the word ``thesis'' is used in a way I haven't heard yet.
 Please check if this is a correct meaning of the word or replace it with something more appropriate like ``claim" or ``statement".
 
-ANSWER: fixed.
-
-\item $581-582$: ``two rectangles below are pullbacks" Explain why in more details: left square is a pullback by definition of kernel pairs, and right square is a pullback by assumption, thus by Lemma A1 the outer square is also a pullback.
-
-ANSWER: all the details cited by the reviewer are already in the text (they are quite literally the hypotheses of Lem.~2.12) and so we do not find necesary to recall them again in the proof.
+ANSWER: Fixed.
+
+\item $581-582$: ``two rectangles below are pullbacks''.
+Explain why in more details: left square is a pullback by definition of kernel pairs, and right square is a pullback by assumption, thus by Lemma A1 the outer square is also a pullback.
+
+ANSWER: All the details cited by the reviewer are already in the text (they are quite literally the hypotheses of Lem.~2.12) and so we do not find necesary to recall them again in the proof.
 
@@
 
-ANSWER: we think that such diagram is not needed and a waste of space.
+{\color{red} ANSWER: we think that such diagram is not needed and a waste of space.}
 
@@
 
-ANSWER: we didn't find a more abstract proof, even if we suspect that the present proof works in any extensive and distributive monoidal category (see the answer above regarding the Kleene star).
+ANSWER: We did not find a more abstract proof, even if we suspect that the present proof works in any extensive and distributive monoidal category (see the answer above regarding the Kleene star).
 
@@
 
-ANSWER: in line $600$ we are using the universal property of a product to \emph{define} the arrow $\phi$, so we do not understand the reviewer's question.
-Adding a diagram here would be completely uninformative.
+ANSWER: In line $600$ we are using the universal property of a product to \emph{define} the arrow $\phi$, so we do not understand the reviewer's question. Adding a diagram here would be uninformative.
 
@@
 
-ANSWER : fixed.
+ANSWER : Fixed.
 
@@
 
-ANSWER: fixed
+ANSWER: Fixed
 
@@
 
-ANSWER: fixed.
+ANSWER: Fixed.
 No, the uniqueness invoked in line $602$ is not the same that we must be proved: we know that $\psi$ is the unique arrow such that $\psi \circ n=k$ and $\psi \circ h =\phi$.
@@
 \item $607$: Say that the first claim is by monotonicity of $m$.
+
 ANSWER: fixed.
 
-\item $607$: Why does $(B,{m,\iota_m})$ being a coproduct implies that $\psi' = \psi$? Explain more
-
-ANSWER: this is an error which we have fixed. What we are using here is that $(D, \{n, h\})$ is a pushout.
+\item $607$: Why does $(B,{m,\iota_m})$ being a coproduct implies that $\psi' = \psi$? Explain more.
+
+ANSWER: This is an error which we have fixed. What we are using here is that $(D, \{n, h\})$ is a pushout.
 
@@
 
-ANSWER: we prefer our formulation.
-
-\item $631$: ``By Lemma A.2 … coproduct." Draw the diagram or mention explicitly which pushout square we consider (i.e., the one on top)
-
-ANSWER: there is no need to draw a diagram since we already mention that we are referring to $(D', \{n', g'\circ \iota\})$ and there is only one pushout in which $D'$ appears.
+ANSWER: We prefer our formulation.
+
+\item $631$: ``By Lemma A.2 … coproduct.'' Draw the diagram or mention explicitly which pushout square we consider (i.e., the one on top)
+
+ANSWER: There is no need to draw a diagram since we already mention that we are referring to $(D', \{n', g'\circ \iota\})$ and there is only one pushout in which $D'$ appears.
 
@@
 
-ANSWER: this change, which amounts to a rotation of the cube, has been done for typographical reason and it is completely harmful.
-
-\item $631$: Put the sentence ``We can … the right" in the same paragraph as its explanation.
+ANSWER: This change, which amounts to a rotation of the cube, has been done for typographical reason and it is completely harmful.
+
+\item $631$: Put the sentence ``We can \ldots the right'' in the same paragraph as its explanation.
 
@@
 
-ANSWER: we prefer the actual formulation.
-
-\item $632$: ``the dotted arrow": mention its name
-
-ANSWER: fixed.
-
-\item $633$: Draw the corresponding diagram
-
-ANSWER: there is no need to do so and it would be simply a waste of space.
+ANSWER: We prefer the actual formulation.
+
+\item $632$: ``the dotted arrow'': mention its name
+
+ANSWER: Fixed.
+
+\item $633$: Draw the corresponding diagram.
+
+{\color{red} ANSWER: there is no need to do so and it would be simply a waste of space.}
 
@@
 
-ANSWER: we find this sentence clear as it is.
-
-\item $638$: Draw the corresponding diagram
-
-ANSWER: as in many previous answers, such diagram is not needed since the two equations are as informative as that.
+ANSWER: We prefer the current formulation.
+
+\item $638$: Draw the corresponding diagram.
+
+{\color{red} ANSWER: As in many previous answers, such diagram is not needed since the two equations are as informative as that.}
 
@@
 
-ANSWER: indeed we are using that propery, which hold by the observations before the bullet points.
+ANSWER: Indeed we are using that property, which hold by the observations before the bullet points.
 As in the answers before, we do not think that repeating all the hypotheses used every half of a page is needed.
 
-\item $643-644$ Mention more explicitly what "the thesis" is in order to guide the reader and make a stronger case for you proof.
+\item $643-644$ Mention more explicitly what ``the thesis'' is in order to guide the reader and make a stronger case for you proof.
 You're trying to prove the square $B'D'BD$ is a pullback, i.e., to show there exists a unique morphism/function $k \colon  T \to B'$ such that $b\circ k=t_2$ and $n'\circ k = t_1$.
@@
 
-ANSWER:  we do not believe that such additional observations are needed, especially if they amounts to restating that we are trying to prove the universal property of pullbacks!
-Similarly, it's a completely trivial observation that then monotonicity of $n'$ entails uniqueness.
+ANSWER:  We do not believe that such additional observations are needed, especially if they amounts to restating that we are trying to prove the universal property of pullbacks!
+Similarly, it is a trivial observation that the monotonicity of $n'$ entails uniqueness.
 
@@
 
-ANSWER: we agree that this result is very technical and its proof quite involved.
-That's why it's been deferred to the appendix.
+ANSWER: We agree that this result is very technical and its proof quite involved.
+That is why it has been deferred to the appendix.
 However, as in the answer above we do not find the need to restate our claims.
@@
 
-ANSWER: we prefer to maintain the current formulation.
+ANSWER: We prefer to maintain the current formulation.
 
@@
 
-ANSWER: we've added a reference to Lem.~A.2
+ANSWER: We have added a reference to Lem.~A.2.
 
@@
 
-ANSWER: $j_0$ \emph{is} $k_{n'}$, compare the third rectangle of Lem.~2.12. That's why there is a pointer to such lemma.
+ANSWER: $j_0$ \emph{is} $k_{n'}$, compare the third rectangle of Lem.~2.12. That is why there is a pointer to such lemma.
 
@@
 
-ANSWER: this approach would occupy much more space and, in our opinion, not add much in terms of clarity. The equation mentioned by the reviewer follows from the definition of kernel pair.
+ANSWER: This approach would occupy much more space and, in our opinion, not add much in terms of clarity. The equation mentioned by the reviewer follows from the definition of kernel pair.
 
 \item $645-705$: The rest of the proof is difficult to follow and could benefit from restructuring and more guiding.
-What is the prupose of seeing $K_d$ and $K_3$ as coproducts?
+What is the purpose of seeing $K_d$ and $K_3$ as coproducts?
 For $K_d$, this is used on lines $697-698$, but I don't see a similar use for $K_3$ (maybe it's my bad).
 
-ANSWER: we did not decompose $K_3$ as a coproduct.
+ANSWER: We did not decompose $K_3$ as a coproduct.
 Lines $659-666$ are needed to build $\phi_3$, which is used later.
@@
 
-\item $715-716$: Please flesh out this last sentence finishing the proof in more details, and provide appopropriate diagrams.
-
-ANSWER: as in some answers above, we do not find useful to draw the diagram alongide the equation.
-
-\item $719-722$: Same comment
-
-ANSWER: same as above.
+\item $715-716$: Please flesh out this last sentence finishing the proof in more details, and provide appropriate diagrams.
+
+ANSWER: As in some answers above, we do not find useful to draw the diagram alongside the equation.
+
+\item $719-722$: Same comment.
+
+ANSWER: Same as above.
 
@@
 
-ANSWER: same as above. It is a very well known fact that a natural transformation between two diagrams induces an arrow between the colimits and there is no need to restate it.
+ANSWER: Same as above. It is a very well known fact that a natural transformation between two diagrams induces an arrow between the colimits and there is no need to restate it.
 
@@
 
-ANSWER: they are \emph{defined} as coprojojections, so there is no need to further specify their typings.
+ANSWER: they are \emph{defined} as coprojections, so there is no need to further specify their typings.
 
@@
 
-ANSWER: fixed.
-
-\item $737$: ``By Lemma B.3 ...": The use of this lemma is too quick, with important details missing.
+ANSWER: Fixed.
+
+\item $737$: ``By Lemma B.3 ...'': The use of this lemma is too quick, with important details missing.
 Which comma category are you considering?
@@
 By Lem.~B.3 $\{U_L, U_R\}$ jointly creates colimits of $F$, in particular $U_L$ preserves colimits and so $(V, \{\kappa^D_V\})$ is colimiting as claimed.
-Notice that, In our case $L$  is the identity and so it preserves colimits along any $F$, moreover $U_L$ becomes $U_{\mathsf{eq}}$.
+Notice that in our case $L$  is the identity and so it preserves colimits along any $F$, moreover $U_L$ becomes $U_{\mathsf{eq}}$.
 
@@
 
-ANSWER: see answers above: we do not find necessary to draw diagrams here.
-
-\item $742$: ``by construction": Difficult to see without diagrams/equations/etc.
-
-ANSER: see above.
+ANSWER: See answers above: we do not find necessary to draw diagrams here.
+
+\item $742$: ``by construction'': Difficult to see without diagrams/equations/etc.
+
+ANSER: See above.
 
@@
 
-ANSWER: we believe that such summary is neither needed nor informative.
+ANSWER: We believe that such summary is neither needed nor informative.
 
@@
 
-ANSWER:  see answers above: we do not think that adding such diagram is useful.
-
-\item $753$: ``We know ...": it seems you're doing a (regular epi,mono) factorisation of $l$. If that's the case, please be explicit about it.
-
-ANSWER: indeed we are doing such a factorization. We have out a reference to Rem.~A.6
-
-\item $753$: ``Since the identity ...": it seems you're using the property of q being a regular epi. If that's the case, please be explicit about it (and give a reference to Remark A.6)
-
-ANSWER: added.
+ANSWER:  See answers above: we do not think that adding such diagram is useful.
+
+\item $753$: ``We know ...'': it seems you're doing a (regular epi,mono) factorisation of $l$. If that's the case, please be explicit about it.
+
+ANSWER: indeed we are doing such a factorization. We put a reference to Rem.~A.6
+
+\item $753$: ``Since the identity ...'': it seems you're using the property of q being a regular epi. If that's the case, please be explicit about it (and give a reference to Remark A.6)
+
+ANSWER: Added.
 
@@
 
-ANSWER: we prefer our original formulation.
+ANSWER: We prefer our original formulation.
 
@@
 
-ANSWER: We have sistematically avoided the use the tail for isos as the identities. Moreover adding the tail here is completely not informative.
+ANSWER: We have avoided the use the tail for isos as the identities. Moreover adding the tail here is not informative.
 
@@
 
-ANSWER: this is just an application of faithfullness of $T$. Added.
-
-\item $763$: ``Hence": You're using the uniqueness of the function $V_G \to L$ in the universal property of L as the limit of KF. Please be explicit about it.
+ANSWER: This is  an application of the faithfulness of $T$. Added.
+
+\item $763$: ``Hence'': You're using the uniqueness of the function $V_G \to L$ in the universal property of L as the limit of KF. Please be explicit about it.
 
@@
 ANSWER:  We are applying Cor.~B.4 to the category of hypergraphs.
-Since the Kleene stars preserves connected limits then, in particular, equalizers are computed componentwise (another proof is obtained appealing to the presentation of term graphs as presheaves).
+Since the Kleene stars preserves connected limits then, in particular, equalizers are computed component-wise (another proof is obtained appealing to the presentation of term graphs as presheaves).
 
@@
 
-ANSWER: we do not think that it should be mentioned explicitly that the composit of two monos is mono.
-
-\item $769$: What are the ``witnesses"? You're trying to prove that $(h_E,H_V,h_Q)$ is a regular mono. Be more precise.
-
-ANSWER: rephrased.
+ANSWER: We do not think that it should be mentioned explicitly that the composition of two monos is mono.
+
+\item $769$: What are the ``witnesses''? You're trying to prove that $(h_E,H_V,h_Q)$ is a regular mono. Be more precise.
+
+ANSWER: Rephrased.
 
@@
 
-ANSWER: this appendix is entirely technical and contains only very well known results. As such it has been quoted only when needed.
-
-\item $911$: What is the reference [9,10] for? For the statement or proof of Lemma B.3? For the definition of what "jointly creating colimits" means?
+ANSWER: This appendix is entirely technical and contains only very well known results. As such it has been quoted only when needed.
+
+\item $911$: What is the reference [9,10] for? For the statement or proof of Lemma B.3? For the definition of what ``jointly creating colimits'' means?
 
@@
 
-\item $911$: Can you give a detailed explanation or example of what you mean by ``$\{U_L, U_R\}$ jointly creates colimits of $F$"?
+\item $911$: Can you give a detailed explanation or example of what you mean by ``$\{U_L, U_R\}$ jointly creates colimits of $F$''?
 The definition is currently diluted in the proof, and the reader could benefit greatly from having it from the get-go.
 
-ANSWER: see the answers above. Since this is a technical appendix we think that it sufficient to provide a pointer to the relevant literature.
-
-\item $914$: The word ``define" does not really fit, as F is already defined. Maybe "denote"?
-
-ANSWER: fixed.
+ANSWER: See the answers above. Since this is a technical appendix we think that it sufficient to provide a pointer to the relevant literature.
+
+\item $914$: The word ``define'' does not really fit, as F is already defined. Maybe ``denote''?
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: since this result is entriely known and elementary, we do not think that drawing a diagram is necessary.
+ANSWER: Since this result is known and elementary, we do not think that drawing a diagram is necessary.
 
@@
 
-ANSWER: same answer as above.
-
-\item $921$: Shouldn't it be $(L(a_D'),R(b_D'))$ everytime? Also, shouldn't $F(d) = (LU_LF(d),RU_RF(d))$?
-
-ANSWER:  no, it's correct in this formulation.
+ANSWER: Same answer as above.
+
+\item $921$: Shouldn't it be $(L(a_D'),R(b_D'))$ every time? Also, shouldn't $F(d) = (LU_LF(d),RU_RF(d))$?
+
+ANSWER:  No, it is correct in this formulation.
 
@@
 
-ANSWER: same answers regardin the diagrams as above.
+ANSWER: Same answers regarding the diagrams as above.
 
@@
 
-ANSWER: same answer as above.
+ANSWER: Same answer as above.
 
 \item $932$: What is the functor I? Is this a typo for F?
+
 ANSWER: Indeed, fixed.
@@
 
-ANSWER: a category can have more than one terminal/inital objects, albeit if they are, obviously, all isomorphic.
-
-\item $948$: The argument for the uniqueness of $(?_A,k)$ could be made clearer. A diagram of the universal morphism would have been helpful
-
-ANSWER: fixed a typo. We do not think that a further clarification is needed.
+ANSWER: A category can have more than one terminal/initial objects, albeit if they are, obviously, all isomorphic.
+
+\item $948$: The argument for the uniqueness of $(?_A,k)$ could be made clearer. A diagram of the universal morphism would have been helpful.
+
+ANSWER: Fixed a typo. We do not think that a further clarification is needed.
 
@@
 
-	ANSWER: we do not believe that citing the suggested works would be helpful or appropriate, as they appear to be unrelated to the topic at hand.
+	ANSWER: We do not believe that citing the suggested works would be helpful or appropriate, as they appear to be unrelated to the topic at hand.
 
@@
 
-	ANSWER: indeed, fixed.
+	ANSWER: Indeed, fixed.
 
@@
 
-	ANSWER: added a pointer to the relevant results.
+	ANSWER: Added a pointer to the relevant results.
 
@@
 
-	ANSWER: added a pointer to the relevant results.
+	ANSWER: Added a pointer to the relevant results.
 We added in appendix the proof of the second point for which, while well known, we were unable to find a source in the literature (likely because it follows at once from the first point).
@@
 
-ANSWER: this is a basic and elementary result of basic category theory.
+ANSWER: This is an elementary result of basic category theory.
 
@@
 
-ANSWER: the only not obvious property of the Kleene star is the first and the reference is provided.
+ANSWER: The only not obvious property of the Kleene star is the first and the reference is provided.
 
@@
 
-	\item  $438$: "introductory example in [32]" -> give example number if it exists, or section/page number.
+	\item  $438$: ``introductory example in [32]'' -> give example number if it exists, or section/page number.
 
@@
 
-ANSWER: added the reference.
+ANSWER: Added the reference.
 
@@
 
-	ANSWER: this is a well known fact and so we believe that no further reference is needed.
+	ANSWER: This is a well known fact and so we believe that no further reference is needed.
 
@@
 
-	ANSWER: added the relevant references.
+	ANSWER: Added the relevant references.
 
@@
 
-	ANSWER: this is an exercise using the definition of distributivity and extensivity.
+	ANSWER: This is an exercise using the definition of distributivity and extensivity.
 
@@
 
-ANSWER: preservation of pullbacks always entails preservation of monos. This is again an exercise in basic category theory.
+ANSWER: Preservation of pullbacks always entails preservation of monos. This is again an exercise in basic category theory.
 
@@
 
-	ANSWER: see answer above.
+	ANSWER: See answer above.
 
@@
 
-ANSWER: see above.
+ANSWER: See above.
 
@@
 
-ANSWER: we do not believe that there is the need to recall the definition of continuity nor that limits commute with limits.
+ANSWER: We do not believe that there is the need to recall the definition of continuity nor that limits commute with limits.
 
@@
 
-	ANSWER: added references.
+	ANSWER: Added references.
 
@@
 
-	ANSWER: this is, again, an easy exercise of basic category theory.
+	ANSWER: This is, again, an easy exercise of basic category theory.
 
@@
 
-ANSWER: fixed.
+ANSWER: Fixed.
 
 \item $111$: category L -> category, L
-ANSWER: fixed.
-
-\item $114$: forgotten to put the category in bold in the coslice category "$X/ \mathbf{X}$"
-ANSWER: fixed.
+
+ANSWER: Fixed.
+
+\item $114$: forgotten to put the category in bold in the coslice category ``$X/ \mathbf{X}$''
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: correct as it is.
+ANSWER: Correct as it is.
 
 \item $185$: object -> set
-ANSWER: fixed.
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed.
+ANSWER: Fixed.
 
 \item $214$: V -> $V_\mathcal{H}$
-ANSWER: fixed.
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed.
-
-\item $251$: remove "Let"
-
-ANSWER: fixed.
+ANSWER: Fixed.
+
+\item $251$: remove ``Let''
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed.
+ANSWER: Fixed.
+
 \item $301$: limiting cocone -> limiting cone (I think)
 
-ANSWER: fixed.
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed.
+ANSWER: Fixed.
 
 \item $593$: now at once -> now once
-ANSWER: fixed.
+
+ANSWER: Fixed.
+
 \item $607$: $(B,{m, h \circ \iota_m})$ -> $(B,{m,\iota_m})$
 
-ANSWER: fixed.
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed
-
-\item l. 40 "the presence of the match ensures that the two pushouts exist,
-hence a rewriting step can be 41 performed." not true, even if l is
-mono. What is true if l is mono is that if the pushout complement C
+ANSWER: Fixed.
+
+\item l.
+40 ``the presence of the match ensures that the two pushouts exist, hence a rewriting step can be 41 performed.'' not true, even if l is mono.
+What is true if l is mono is that if the pushout complement C
 exists then it is unique up to iso.
 
-TO DO
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed
-
-\item l. 119 "closed in it" not very clear. "closed under pullback" should be enough.
-
-ANSWER: fixed
-
-\item l. 122 please define "closed under decomposition"
-
-ANSWER: fixed
+ANSWER: Fixed.
+
+\item l. 119 ``closed in it'' not very clear. ``closed under pullback'' should be enough.
+
+ANSWER: Fixed
+
+\item l. 122 please define ``closed under decomposition''
+
+ANSWER: Fixed
 
@@
 
-ANSWER: we prefer to keep using the term arrow as synonymous to morphism, as standard usage of category theory. We fixed the other observations.
+ANSWER: We prefer to keep using the term arrow as synonymous to morphism, as standard usage of category theory. We fixed the other observations.
 
 \item  l. 215 $\mathbf{X}$ -> $\mathbf{Set}$
-$U_X$ -> $U_Hyp$
-
-ANSWER: fixed
+$U_X$ -> $U_{Hyp}$
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: since monos and injective functions are the same in $\mathbf{Set}$ we have chosen to use both.
+ANSWER: Since monos and injective functions are the same in $\mathbf{Set}$ we have chosen to use both.
 
@@
 
-ANSWER: fixed
-
-\item l. 259 "then its pushout along (f2,g2), then their pushout ..." remove
-the last part
-
-ANSWER: fixed
+ANSWER: Fixed.
+
+\item l. 259 ``then its pushout along (f2,g2), then their pushout ...'' remove the last part
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: fixed
-
-\item l. 300 "In order to do so." what?
-
-ANSWER: fixed
+ANSWER: Fixed.
+
+\item l. 300 ``In order to do so.'' what?
+
+ANSWER: Fixed.
 
@@
 
-ANSWER: see answer above
+ANSWER: See answer above.
 

### 2025-05-19 calco/final.tex
typo

@@
 and possibly coincide,
-as in the middle and in the left-most image, respectively,
+as in the middle and in the left-most image, respectively.
 
@@
 
+\newpage
 \bibliography{biblio}
 
+\newpage
 \appendix

### 2025-05-26 calco/finalArxiv.tex
versione arxiv

--- 2025-05-19 calco/final.tex
@@
 		\item $F$ has a colimit, which is preserved by $K$;
-	\item consider a cone $(L, \{l_D\}_{D\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a {\color{red} mono $m\colon Q\mto L$} such that the diagram on the right commutes for every $D\in \D$.
+	\item consider a cone $(L, \{l_D\}_{D\in \D})$ limiting  for $K \circ F$ and let $((E, V), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ be one for $T\circ F$, then $F$ has a limit $(E, V, Q, s, t, q)$ and there is a mono $m\colon Q\mto L$ such that the diagram on the right commutes for every $D\in \D$.
 \end{enumerate}
@@
 We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs.
-We denote {\color{red} by $J_\Sigma$} the corresponding inclusion functor .
+We denote by $Z_\Sigma$ the corresponding inclusion functor .
 \end{definition}
@@
 Let $\pbe_\Sigma$ be the class of morphisms in $\egg_\Sigma$ whose image in $\egg$ lies in $\pbe$.
-Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $J_\Sigma$ is in $\pbc_\Sigma$.
+Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $Z_\Sigma$ is in $\pbc_\Sigma$.
 %
@@
 We will use the curved arrows to denote full and faithful inclusions.
-\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{j_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
+\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
 
@@
 
-\begin{center}\xymatrix{        
+\begin{center}
+\hspace{.5cm}
+\xymatrix{        
  \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
@@
 \newpage
+
+\interlinepenalty 1000
 \bibliography{biblio}

### 2025-05-26 calco/finalArxiv.tex
revisioni

@@
 	A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
-	if $\mathcal{M}$-pushouts are Van Kampen. {\color{red} We write $m\colon X \mto Y$} to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
+	if $\mathcal{M}$-pushouts are Van Kampen. We write $m\colon X \mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
 \end{definition}
@@
 
-Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, by \Cref{prop:com} and \Cref{cor:mono} we can deduce the following result.
+Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, 
+hence by \Cref{prop:com} and \Cref{cor:mono} we can deduce the following result.
 
@@
 
-{\color{red} \Cref{prop:left,prop:com}} allow us to deduce immediately the following.
+\Cref{prop:left,prop:com} allow us to deduce immediately the following.
 
@@
 
-{\color{red} \Cref{cor:mono}} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
+\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
 
@@
 
-In general, for (acyclic) term graphs, a maximally shared and a minimally shared representation
-exist, and for our toy example are the left-most and the tight-most diagram above, respectively:
+In general, for (acyclic) term graphs, a maximally and a minimally shared representation
+exist, and for our toy example are the left-most and the right-most diagram above, respectively:
 it is a standard result for term graph rewriting, see e.g.~\cite{AriolaKP00}. 
-These two representations can be interpreted as the final and the initial object of a suitable comma category 
-$\mathcal{G}  \downarrow \tg$, respectively.
+These two representations can be interpreted as the final and the initial object of a suitable comma category.
+%$\mathcal{G}  \downarrow \tg$, 
+respectively.
 %
@@
 two representations are the same of those for ordinary term graphs, in the latter case
-the minimally shared representation is now the middle image.
+the minimally shared representation is now the middle diagram.
 %
@@
 \emph{Rewriting.} The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
-arrows in $\mathcal{M}$, then we can lift all the standard properties
+arrows in $\mathcal{M}$, then we can lift the standard properties
 of the DPO approach that hold in the category of graphs.
 % to the category at hand. 
-However, as we recalled in the introduction, instead of removing sub-terms, the EGG approach is to
+However, as we recalled in the introduction, instead of removing sub-terms, the EGG approach 
+chooses to
 just add new terms and link them to the older ones via the equivalence relation~\cite{DetlefsNS05}.
@@
 Consider e.g. an EGG rule such $x / x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}.
-Variables in a term graph are represented as nodes that do not belong to the targets of any edge, 
-hence that rule can be modelled as the DPO rule below, concisely represented by the arrow $L \rightarrow R$.
+Variables in a term graph are represented as nodes that do not occur among the targets of an edge, 
+thus the rule can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
 
 \begin{center}
-\hspace{.5cm}
+\hspace{.25cm}
 \xymatrix{        
@@
 thus the rule could be applied to the two EGGs
-depicted above with a match that is injective on equivalence classes 
+depicted above with a match that is injective on equivalence classes.
 %
@@
 %
-
 The right-hand side is a regular mono, though, hence it is not an arrow in $\pbc_\Sigma$.
@@
 	\begin{enumerate}
-		\item  Consider the following cube in which the bottom face is an $\mathcal{M}$-pushout.
+		\item  Consider the following cube in which the bottom face is an $\mathcal{M}$-pushout
 		\[\xymatrix@C=15pt@R=9pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_(.6){\id{B}} \\ A  \ar@{>->}[dd]_{m}\ar[rr]^(.65){g} & & B \ar@{>->}[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{f} & & D}\]
@@
 The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the claim follows.
-		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback.
+		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback
 		\[\xymatrix{X \ar@{>->}[r]^{m} \ar@{>->}[d]_{m}& Y \ar@{>->}[d]^{h}\\ Y \ar@{>->}[r]^{k} & Z}\]
@@
  		\item  
-		To prove the second half of the claim, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
+		To prove the second half of the claim, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks
 		\[\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
@@
 
-		But then the outer rectangle in the  following diagrams are pullbacks too.
+		But then the outer rectangle in the  following diagrams are pullbacks too
 		\[\xymatrix@R=15pt{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
@@
 
-		Thus, by point $2$, there exist two arrows $x, y\colon T\rightrightarrows K_f$ fitting in the diagrams below.
+		Thus, by point $2$, there exist two arrows $x, y\colon T\rightrightarrows K_f$ fitting in the diagrams below
 		\[\xymatrix@R=15pt{T\ar@{.>}[r]_-{x} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_1}& K_f \ar@{->}[r]_{k_h} \ar[d]_{\pi^1_f} & K_g \ar[d]^{\pi^1_g} & T \ar@{.>}[r]_-{y} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_2} & K_f  \ar@{->}[r]_{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ & X \ar@{>->}[r]_{h} & Y &&X \ar@{>->}[r]_{h}& Y} \]
@@
 
-The category of $\Set$ enjoys two other remarkable and useful properties; it is \emph{distributive} and \emph{extensive} \cite{carboni1993introduction}.
-Distributivity amount to the following property: for every family $\{X_i\}_{i}$ and an object $Y$, the unique morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms.
+The category of $\Set$ enjoys two other remarkable properties; it is \emph{distributive} and \emph{extensive} \cite{carboni1993introduction}.
+Distributivity amount to the following property: for every family $\{X_i\}_{i}$ and an object $Y$, the unique morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms
 \[\xymatrix@C=15pt@R=15pt{&Y\times X_i \ar@{>->}[dl]_{j_i} \ar@{>->}[dr]^{\id{Y}\times h_i} &&& X_i \times Y \ar@{>->}[dl]_{k_i} \ar@{>->}[dr]^{ h_i \times \id{Y}} \\ \Sum_{i\in I} (Y\times X_i) \ar@{.>}[rr]_{\phi}&& Y\times (\Sum_{i\in I}X_i) & \Sum_{i\in I}  (X_i \times Y )\ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \times Y }\]
@@
 \noindent
-\parbox{11cm}{
+\parbox{11.5cm}{
 \begin{remark}\label{rem:disj}
-	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~that the pullback between two coprojections is given by the initial object (with initial maps as coprojections).
-To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and let $k$ be an element of $I$.
-Then  $(X_k, \{t_i\}_{i\in I})$ with
-	\[t_i=\begin{cases}
-		\id{X_k} & i=k\\?_{X_k} & i\neq k
-	\end{cases}\]
+	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~the pullback between two coprojections is given by the initial object (with initial maps as coprojections).
+To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and $k$ an element of $I$.
+Then  $(X_k, \{t_i\}_{i\in I})$
+such that $t_i = \id{X_k}$ if $i=k$, and $?_{X_k}$ otherwise,
+	%\end{cases}\]	
+	%with
+	%\[t_i=\begin{cases}
+	%	\id{X_k} & i=k\\?_{X_k} & i\neq k
+	%\end{cases}\]
 	is a coproduct and so the squares on the right are pullbacks.
-\end{remark}}\hfill\parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}
+\end{remark}}\hfill\parbox{2cm}{\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}
 
@@
 Let $\iota \colon E\mto Y$ be the inclusion of the complement of the image of $p_1$.
-If there exist two  arrows $t_1\colon T\to E$ and $t_2\colon T\to X$ such that \[g\circ \iota\circ t_1= f\circ t_2\] then $T$ is empty.
-\end{proposition}}\hfill \parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
+If there exist two  arrows $t_1\colon T\to E$ and $t_2\colon T\to X$ such that $g\circ \iota\circ t_1= f\circ t_2$ then $T$ is empty.
+\end{proposition}}\hfill \parbox{2cm}{\vspace{-.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
 \begin{proof}
@@
 	Let $f,g\colon A\rightrightarrows B+C$ be two arrows with a coproduct as codomain. Then $(A, \{j_i\}_{i=0}^
-	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares.
+	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares
 	\[\xymatrix@C=30pt@R=15pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
@@
 
-		\item 	 By \Cref{lem:po_set,lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks.
+		\item 	 By \Cref{lem:po_set,lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks
 		\[\xymatrix@C=45pt@R=15pt{K_b \ar@{>->}[r]^{k_{n'}}  \ar[d]_{(\pi^1_b, \pi^2_b)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
@@
 \normalsize
-
- Hence, we have arrows $h_1\colon H_1\to K_1$ and $h_2\colon H_2\to K_2$, showing that $H_1$ and $H_2$ are empty. For $H_3$, let us consider the two diagrams below.
-
+ Hence, we have arrows $h_1\colon H_1\to K_1$ and $h_2\colon H_2\to K_2$, showing that $H_1$ and $H_2$ are empty. For $H_3$, let us consider the two diagrams below
  \[ \xymatrix@C=45pt@R=15pt{ H_3 \ar@{.>}[d]^{\alpha_3} \ar[r]^{x_3} \ar@/_.4cm/[dd]_{(y_3, z_3)} & K_c \ar[d]_{k_{g'}}& K_3 \ar@{.>}[d]^{\beta_3} \ar@/^.3cm$ $/[dr]^{\phi_3} \ar@/_.4cm/[dd]_{(p_3, q_3)}\\K_3 \ar@{>->}[r]^{j_3}  \ar[d]^{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} &  H_3 \ar@{>->}[r]^{x_3}  \ar[d]^{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)}  \\
@@
 (\iota'\times \iota')\circ (p_3, q_3)\\& \end{split}\] 
-
 Thus we get the dotted arrows $\alpha_3$ and $\beta_3$ which are one the inverse of the other. Indeed, on the one hand we have
@@
  \[(y_3, z_3)\circ \beta_3\circ \alpha_3=(p_3, q_3)\circ \alpha_3=(y_3, z_3)\]
-
  Summing up, we have just proved that $(K_c, \{x_0, \phi_3\})$ is a coproduct.
@@
  \end{align*}
-
  On the other hand, we can conclude that $\theta \circ k_{g'}=\delta$ as wanted, since
  \[\theta \circ k_{g'}\circ x_0=\theta \circ k_{n'}\circ h_0=\gamma \circ h_0=\gamma \circ k_{f'}\circ h'_0=\delta \circ k_{m'}\circ h'_0=\delta \circ x_0 \]
-
  We are left with uniqueness. If $\theta'$ is another arrow $K_d\to Z$ such that $\theta'\circ k_{n'}=\gamma$ and $\theta'\circ k_{g'}= \delta$. If we compute we get
@@
 
+\newpage
 \subsection{Proofs for \Cref{hypereq}}\label{app:due}
@@
 	$(\Leftarrow)$ Suppose that $h_E$, $h_V$, and $h_Q$  are monos. 
-	We can build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks.
+	We can build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks
 	\[     \xymatrix@R=15pt{
@@
 	Again by \Cref{prop:eqhyp_complete} the two halves of the central rectangle are pullbacks and so by \Cref{lem:pb1} the whole rectangle is a pullback too.
-This, in turn entails that the whole right rectangle is a pullback and so, also its left half is a pullback (again by \Cref{lem:pb1}).
+This, in turn entails that the whole right rectangle is a pullback and so, also its left half is a pullback (again by \Cref{lem:pb1})
 	\[
@@
 	and  suppose that in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
-By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
+By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts
 	\[
@@
 
-	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below.
+	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below
 
@@
 
+\newpage
 	\noindent 
@@
 	Suppose that the square on the left below is a pushout in $\EqHyp_\Sigma$, with $h$ in $\mathcal{T}$.
-Then, by \Cref{rem:t} the square on the right is a pushout and by the definition of $\mathcal{T}$ and \Cref{rem:obv}, $T_\Sigma(h)$ is a regular mono in $\tg$.
+Then, by \Cref{rem:t} the square on the right is a pushout and by the definition of $\mathcal{T}$ and \Cref{rem:obv}, $T_\Sigma(h)$ is a regular mono in $\tg$
 	\[\xymatrix{J_\Sigma(\mathcal{G}_0, l_0) \ar[r]^{k} \ar[d]_{h}& J_\Sigma(\mathcal{G}_1, l_1) \ar[d]^{p} &T_\Sigma (J_\Sigma(\mathcal{G}_0, l_0)) \ar[r]^{T_{\Sigma}(k)} \ar[d]_{T_{\Sigma}(h)}& T_\Sigma (J_\Sigma(\mathcal{G}_1, l_1)) \ar[d]^{T_\Sigma(p)}\\
@@
 	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the first rectangle below is a pullback in $\comma{L}{R}$.
-By \Cref{lim} then also the other two squares are pullbacks, respectively in $\A$ and $\B$, proving that both $h$ and $k$ are monos.
+By \Cref{lim} then also the other two squares are pullbacks, respectively in $\A$ and $\B$, proving that both $h$ and $k$ are monos
 	\[\xymatrix{(A, B, f)  \ar[rr]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}&& (A, B, f)  \ar[d]^{(h,k)}& A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ (A, B, f)  \ar[rr]_{(h,k)}&& (A', B', g) &A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
 
+\newpage
 	\smallskip\noindent 
@@
 \end{proposition}
+
+\newpage
 \begin{proof} Define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows

### 2025-05-26 calco/finalCalco.tex
revisioni

--- 2025-05-19 calco/final.tex
@@
 %
-For the sake of space, the proofs appear in the appendices. 
+All the proofs can be found in the full version of the 
+paper~\cite{biondo}
+
+%For the sake of space, the proofs appear in the appendices. 
 %For the sake of completeness, 
@@
 We can state some useful properties of $\mathcal{M}$-adhesive category
-(see, for instance, \cite[Thm.~4.26]{ehrig2006fundamentals} or \cite[Fact 2.6]{azzi2019essence}). A proof is provided in \Cref{regmono-proof}.
+(see, for instance, \cite[Thm.~4.26]{ehrig2006fundamentals} or \cite[Fact 2.6]{azzi2019essence}). 
+%A proof is provided in \Cref{regmono-proof}.
 \begin{restatable}{proposition}{regmono}\label{prop:regmono}
@@
 We conclude this section exploring some properties of kernel pairs in an $\mathcal{M}$-adhesive category. 
-The results below are simple, yet they appear to be original, and we give their proofs in \Cref{kpp-proof}.
+The results below are simple, yet they appear to be original.
+%and we give their proofs in \Cref{kpp-proof}.
 
@@
 
+\newpage
 		Moreover, the following hold
@@
 
-Focusing on $\Set$, we can prove a sharper result (see \Cref{proof:kerset} for the proof).
+Focusing on $\Set$, we can prove a sharper result. % (see \Cref{proof:kerset} for the proof).
 
@@
 
-Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, by \Cref{prop:com} and \Cref{cor:mono} we can deduce the following result.
+Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, hence by \Cref{prop:com} and the characterisation of monos 
+in comma categories we can deduce the following result.
 
@@
 
-{\color{red} \Cref{prop:left,prop:com}} allow us to deduce immediately the following.
+Again \Cref{prop:com} allow us to deduce immediately the following.
 
@@
 %
-A proof is in \Cref{proof:forghyp}.
+%A proof is in \Cref{proof:forghyp}.
 
@@
 
-Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, Q, s, t, q)$ to $Q$, and a morphism $(h_E, h_V, h_Q)$ to $h_Q$.
-We  exploit it to compute limits and colimits in $\EqHyp$.
-A full proof of the following lemma can be found in \Cref{proof:comp}.
+Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, Q, s, t, q)$ to $Q$, and a morphism $(h_E, h_V, h_Q)$ to $h_Q$. We  exploit it to compute limits and colimits in $\EqHyp$. 
+%A full proof of the following lemma can be found in \Cref{proof:comp}.
 
@@
 
-A proof is in \Cref{proof:regmono}.
+%A proof is in \Cref{proof:regmono}.
 We have now all the ingredients to study the adhesivity properties of $\EqHyp$.  As a first step we need to introduce a class of monos.
@@
 \vspace{.1cm}
-Now, we show that $\pbc$ is a suitable class for adhesivity. A proof is in \Cref{proof:pbmono}.
+Now, we show that $\pbc$ is a suitable class for adhesivity. %A proof is in \Cref{proof:pbmono}.
 
@@
 \vspace{.1cm}
-Finally, we show the key lemma for $\pbc$-adhesivity of $\EqHyp$. A proof is in \Cref{proof:pbstable}.
+Finally, we show the key lemma for $\pbc$-adhesivity of $\EqHyp$. %A proof is in \Cref{proof:pbstable}.
 
@@
 %
-A proof is found in \Cref{proof:pbvk}.
+%A proof is found in \Cref{proof:pbvk}.
 
@@
 
- The previous remark allows us to prove an analog of \Cref{prop:tlim}. We refer the reader to \Cref{proof:term} for details.
+ The previous remark allows us to prove an analog of \Cref{prop:tlim}. %We refer the reader to \Cref{proof:term} for details.
 
@@
 
-The following proposition is now an easy corollary of \Cref{prop:push}, \Cref{prop:lim}, and \Cref{rem:obv}. We provide the details in \Cref{proof:tade}.
+The following proposition is now an easy corollary of \Cref{prop:push}, \Cref{prop:lim}, and \Cref{rem:obv}. %We provide the details in \Cref{proof:tade}.
 
@@
 \end{example}
-A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proofs are in \Cref{proof:elim}.
+A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. %Full proofs are in \Cref{proof:elim}.
 
@@
 
-We can now turn to pushouts. We refer again the reader to \Cref{proof:epo} for the details.
+We can now turn to pushouts. %We refer again the reader to \Cref{proof:epo} for the details.
 
@@
 
-\samepage{\begin{proposition}\label{prop:varie}
+\samepage{
+\begin{proposition}\label{prop:varie}
 	Let $\Sigma$ be an algebraic signature. Then the following hold
@@
 We will use the curved arrows to denote full and faithful inclusions.
-\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{j_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
-
-We can now prove our last three results. The reader can find the proof in \Cref{proof:tlim}.
+\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
+
+We can now prove our last three results. %The reader can find the proof in \Cref{proof:tlim}.
 
@@
 
-Let now $\mathcal{T}_\Sigma$ be the class of morphisms of $\eg$ which are sent by $K_\Sigma$ to the class $\mathcal{T}$. Then \Cref{colim,lem:epo,prop:po} allow us to deduce the following result.
+Let now $\mathcal{T}_\Sigma$ be the class of morphisms of $\eg$ which are sent by $K_\Sigma$ to the class $\mathcal{T}$. Then \Cref{lem:epo,prop:po} allow us to deduce the following result.
 
@@
 Consider e.g. an EGG rule such $x / x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}.
-Variables in a term graph are represented as nodes that do not belong to the targets of any edge, 
-hence that rule can be modelled as the DPO rule below, concisely represented by the arrow $L \rightarrow R$.
-
-\begin{center}\xymatrix{        
+Variables in a term graph are represented as nodes that do not occur among the targets of an edge, 
+thus the rule can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
+
+\begin{center}
+\hspace{.25cm}
+\xymatrix{        
  \begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
@@
 \newpage
+
+\interlinepenalty 1000
 \bibliography{biblio}
+\end{document}
 

### 2025-05-28 calco/calco_submission/finalCalco.tex
sottomissione

--- 2025-05-26 calco/finalCalco.tex
@@
 %\usepackage{tikz-cd}
-\usepackage{hyperref, cleveref} %simboli matematici
+\usepackage{hyperref} %simboli matematici
 \usepackage[all, cmtip]{xy}
@@
 \nolinenumbers
-
+\ArticleNo{14}
 \begin{document}
@@
 
-%
-%\begin{notation}
-We open this background section by fixing some notation.
-%
-Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
+We open this background section by fixing some notation. Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
 ``$X\in \X$'' means that $X$ is an object of $\X$.
@@
 
-Together with \Cref{lem:pb1}, the previous remarks allow us to prove the following result.
+The previous remarks allow us to prove the following result.
 
@@
 
-\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
+ \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
 
@@
 Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
-From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors,cor:eqade}, we can deduce the following.
+From \Cref{prop:eqhyp_complete}, the second point of \Cref{thm:slice-functors,cor:eqade}, we can deduce the following.
 
@@
 \end{document}
-
-\newpage
-\appendix
-
-\section{Omitted proofs}
-
-This section contains the proofs which are omitted from the main body of the paper. 
-%
-We begin recalling  a well-known fact about composition and decomposition of pullbacks \cite[Lem.~1.1]{lack2005adhesive}.
-
-\noindent
-\parbox{10cm}{
-\begin{lemma}\label{lem:pb1}
-	Let $\X$ be a category, and consider the diagram aside, in which the right square is a pullback. Then the whole rectangle is a pullback if and only if the left square is one.
-\end{lemma}} 
-	\parbox{4cm}{
-	\xymatrix@R=15pt{X \ar[d]_{a} \ar[r]_{f}& \ar[r]_{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]^{h}& B \ar[r]^{k}& C}}
-\commentato{
-\begin{proof}
-	$(\Rightarrow)$ Let $q_1\colon Q\to Y$ and $q_2\colon Q\to A$ be two arrows such that $b\circ q_1=h\circ q_2$, if we compute we get
-	\[c\circ g\circ q_1  =k\circ b\circ q_1=k\circ h\circ q_2\]
-	\parbox{9cm}{Thus by the pullback property of the whole rectangle we get the dotted $l$ in the diagram on the side. 
-	All we have to prove is that $f\circ l=q_1$. By construction we know that $g\circ f\circ l= g\circ q_1$, while we also have}
-	\hfill \parbox{4cm}{\xymatrix@R=18pt{Q \ar@/_.3cm/[dr]_{q_2}\ar@/^.4cm/[rrr]^{g\circ q_1} \ar@{.>}[r]_{l} & X \ar[d]_{a} \ar[r]_{f}& \ar[r]_{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ & A \ar[r]_{h}& B \ar[r]_{k}& C}}
-	\[	b\circ f\circ l = h\circ a\circ l= h\circ q_2=b\circ q_1\]
-	and we can conclude since the right square in the original diagram is a pullback.
-
-	For uniqueness: if $l'\colon Q\to X$ is such that $f\circ l'= q_1$ and $a\circ l'=q_2$
-	then  $g\circ f \circ l' = g\circ q_1$ and we can conclude applying the pullback property of the outer rectangle.
-
-	\smallskip \noindent 
-	\parbox{9cm}{
-	$(\Leftarrow)$ Take two arrows $q_1\colon Q\to Z$ and $q_2\colon Q\to A$ such that $c\circ q_1=k\circ h \circ q_2$
-	We can apply the pullback property of the right square to get the dotted $q\colon Q\to Y$ in the following
-
-	Now, by construction we have $b\circ q =h\circ q_2$
-	and thus, since the left square is a pullback, we get also a unique $l\colon Q\to X$ such that  $f\circ l = q$ and $a \circ l = q_2$
-	but then we clearly have} \hfill 
-	\parbox{6cm}{\vspace{7pt}
-		\xymatrix@R=18pt{Q \ar@/_.3cm/[ddr]_{q_2}\ar@/^.5cm/[drrr]^{ q_1} \ar@{.>}@/^.3cm/[drr]^(.6){ q} \ar@{.>}[dr]^{l}  \\& X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]_{b}& Z \ar[d]^{c}\\ & A \ar[r]_{h}& B \ar[r]_{k}& C}}
-	\[	g\circ f \circ l = g\circ q = q_1	\]
-
-	We are left with uniqueness. Let $l'\colon Q\to X$ be another arrow such that $q_1 = g\circ f \circ l'$ and $q_2=a\circ l'$,  then we must also have
-	\[
-	b\circ f \circ l'= h\circ a \circ l' = h\circ q_2= b\circ q\]
-	which implies $f\circ l' = q$, from which $l=l'$ follows.
-\end{proof}
-}
-%
-
-\subsection{Proofs for \Cref{sec:ade}}\label{app:primo}
-
-\regmono*
-\begin{proof}\label{regmono-proof}
-	\begin{enumerate}
-		\item  Consider the following cube in which the bottom face is an $\mathcal{M}$-pushout.
-		\[\xymatrix@C=15pt@R=9pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_(.6){\id{B}} \\ A  \ar@{>->}[dd]_{m}\ar[rr]^(.65){g} & & B \ar@{>->}[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{f} & & D}\]
-		By construction the top face of the cube is a pushout and the back one a pullback.
-The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the claim follows.
-		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback.
-		\[\xymatrix{X \ar@{>->}[r]^{m} \ar@{>->}[d]_{m}& Y \ar@{>->}[d]^{h}\\ Y \ar@{>->}[r]^{k} & Z}\]
-		It is now immediate to see that $m$ is the equalizer of $h$ and $k$.   \qedhere
-	\end{enumerate}
-\end{proof}
-
-\kpp*
-\begin{proof}\label{kpp-proof}
-	We begin by computing 
-	\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]
-	so that  existence  and uniqueness of the wanted $k_h$ follow at once from the universal property of $K_g$ as the pullback of $g$ along itself.
-
-	\begin{enumerate}
-		\item Let $a,b\colon T\rightrightarrows K_f$ be two arrows such that $k_h\circ a=k_h\circ b$, then we have
-\begin{align*}h\circ \pi^1_f\circ a&=\pi^1_g\circ k_h\circ a=\pi^1_g\circ k_h\circ b=h\circ \pi^1_f\circ b\\
-	h\circ \pi^2_f\circ a&=\pi^2_g\circ k_h\circ a=\pi^2_g\circ k_h\circ b=h\circ \pi^2_f\circ b
-\end{align*}
-Since $h$ is mono this entails that
-\[	\pi^1_f\circ a=\pi^1_f\circ b \qquad \pi^2_f\circ a=\pi^2_f\circ b\]
-and thus $a$ must coincide with $b$.
-
- 		\item  
-		To prove the second half of the claim, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
-		\[\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
-			X \ar[r]_{f}& Y \ar[r]_{t} & W & X \ar[r]_{f} & Y  \ar[r]_{t}& W}\]
-
-		But then the outer rectangle in the  following diagrams are pullbacks too.
-		\[\xymatrix@R=15pt{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
-			X \ar[r]^{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]^{g} & W & X \ar[r]^{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]^{g} & W}\]
-
-		Thus the left halves of the rectangle above are pullbacks again by \Cref{lem:pb1}.
-
-		\item 		For the last square, let $(t_1, t_2)\colon T\to X\times X$ and $s\colon T\to K_g$ be two arrows such that
-		\[(\pi^1_g, \pi^2_g)\circ s=(h\times h)\circ (t_1, t_2)\]
-
-		Thus, by point $2$, there exist two arrows $x, y\colon T\rightrightarrows K_f$ fitting in the diagrams below.
-		\[\xymatrix@R=15pt{T\ar@{.>}[r]_-{x} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_1}& K_f \ar@{->}[r]_{k_h} \ar[d]_{\pi^1_f} & K_g \ar[d]^{\pi^1_g} & T \ar@{.>}[r]_-{y} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_2} & K_f  \ar@{->}[r]_{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ & X \ar@{>->}[r]_{h} & Y &&X \ar@{>->}[r]_{h}& Y} \]
-		By the first point $k_h$ is mono, thus we can deduce that $x=y$. By construction we have
-		\[(\pi^1_f, \pi^2_f)\circ x=(t_1, t_2) \qquad k_h\circ x=s\]
-
-		Uniqueness now follows once again from the fact that $k_h$ is mono.
-		\qedhere
-
-	\end{enumerate}
-
-\end{proof}
-
-\noindent
-\parbox{7cm}{\mpo*}\hfill \parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
-
-\noindent 
-\parbox{4cm}{\xymatrix@C=10pt@R=6pt{&K_a\ar[dd]|\hole_(.65){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_b\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_(.55){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }} \hfill \parbox{9cm}{\begin{proof}\label{mpo-proof}
-	By  \Cref{prop:regmono}  we know that the top face of the original cube is a pullback. Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks.
-	The claim now follows from strict $\mathcal{M}$-adhesivity.
-	\end{proof}}
-
-\commentato{
-\epic*
-\noindent 
-\parbox{10cm}{
-\begin{proof}\label{epic-proof}
-	By hypothesis, there exists a pair $f, g\colon Z \rightrightarrows X$ of which $e$ is the coequalizer.
-	 Since $e \circ f = e \circ g$ we get the dotted arrow fitting in the digram aside.
-
-	\parbox{\textwidth}{Let now $h: Z \to V$ be an arrow such that $h \circ \pi_1 = h \circ \pi_2$, then
-	\[	h \circ f = h \circ \pi_1 \circ k 
-	= h \circ \pi_2 \circ k 
-	= h \circ g\]
-	and thus there exists a unique $l: Y \to V$ such that $l \circ e = h$. \qedhere}
-\end{proof}}\hfill
-\parbox{9cm}{\vspace{-2cm}\xymatrix{Z \ar@{.>}[r]_k \ar@/_.3cm/[dr]_{g} \ar@/^.4cm/[rr]^{f} & K_e \ar[r]_{\pi^{1}_e}  \ar[d]_{\pi^2_e}& X \ar[d]^{e}\\ & X \ar[r]_{e} & Y}}
-
-\natepi*
-\begin{proof}\label{natepi-proof}
-	Let $(K_i, \pi_d^1, \pi_d^2)$ be the kernel pair of $\phi_d$ for each object $d$ in $\D$. Given an arrow $\alpha: d \to d'$ of $\D$, we have
-	\[\phi_{d'} \circ F(\alpha) \circ \pi_d^1 = G(\alpha) \circ \phi_d \circ \pi_d^1 
-	= G(\alpha) \circ \phi_d\circ \pi_d^2 
-	= \phi_{d'} \circ F(\alpha) \circ \pi_d^2
-	\]
-
-	Thus, the solid part of the diagram below commutes, yielding the dotted arrow $K(\alpha)$.
-
-	\noindent 
-\parbox{5cm}{\xymatrix{K_d \ar[r]^{\pi^1_d} \ar[d]_{\pi^2_d} \ar@{.>}[dr]^{K(\alpha)}& F(d) \ar[dr]^{F(\alpha)} \\ F(d) \ar[dr]_{F(\alpha)} & K_{d'} \ar[r]^{\pi^1_{d'}} \ar[d]_{\pi^2_{d'}}& F(d') \ar[d]^{\phi_{d'}}\\ & F(d') \ar[r]_{\phi_{d'}} & G(d')}} \hfill \parbox{9cm}{In this way, we get a functor $K\colon \D\to \X$ mapping $d$ to $K_d$ and each arrow $\alpha$ onto $K(\alpha)$.
-Indeed, notice that $K(\id{d}) \colon  K_d \to K_d$ is the arrow such that
-\begin{align*}
-\pi_d^1 \circ K(\id{d})&=F(\id{d})\circ \pi^1_d=\id{F(d)}\circ \pi^{1}_d=\pi^1_d\\
-\pi_d^2 \circ K(\id{d})&=F(\id{d})\circ \pi^2_d=\id{F(d)}\circ \pi^{2}_d=\pi^2_d
-\end{align*}
-Thus, by the universal property of pullbacks, $K(\id{d}) = \id{K_d}$.
-}
-
-	Let now $\alpha \colon a \to b$ and $\beta\colon b \to c$ be two arrows in $\D$,  computing, we have
-	\begin{align*}
-		\pi_c^1 \circ K(\beta \circ \alpha) &
-		= F(\beta) \circ F(\alpha) \circ \pi_a^1 
-		= F(\beta) \circ \pi_b^1 \circ K(\alpha) 
-		= \pi_c^1 \circ K(\beta) \circ K(\alpha)\\
-			\pi_c^2 \circ K(\beta \circ \alpha) &
-		= F(\beta) \circ F(\alpha) \circ \pi_a^2 
-		= F(\beta) \circ \pi_b^2 \circ K(\alpha) 
-		= \pi_c^2 \circ K(\beta) \circ K(\alpha)
-	\end{align*}
-	Allowing us to conclude that $K(\beta \circ \alpha) = K(\beta) \circ K(\alpha)$, proving the functoriality of $K$.
-
-	Hence,  by construction we have two natural transformations $\pi^1, \pi^2\colon  K \rightrightarrows F$.
-By \Cref{prop:reg_epi_coeq}, every component $\phi_d$ is the coequalizer of $\pi_d^1, \pi_d^2\colon K(d) \rightrightarrows F$, and so $\phi$ is the coequalizer of $\pi^1$ and $\pi^2$.
-\end{proof}
-
-\epicol*
-
-\begin{proof}\label{epicol-proof}
-	By \Cref{cor:reg_epi_components_reg_epi_nat_trans}, we know that $\phi\colon F \to G$ is a regular epi, so that there is a functor $E\colon \D\to \X$ and $\eta, \theta\colon E \rightrightarrows F$ such that $\phi$ is the coequalizer of $\eta$ and $\theta$.
-Let now $(P, \{p_d\}_{d \in \D})$ be the colimit of $E$ and consider the unique arrows $a, b\colon P \rightrightarrows X$ fitting in the squares below
-\medskip
-
-\noindent 
-	\parbox{4cm}{\xymatrix{E(d) \ar[r]^{p_d} \ar[d]_{\eta_d}& P \ar@{.>}[d]^{a} &E(d) \ar[d]_{\theta_d}
-		 \ar[r]^{p_d}& P \ar@{.>}[d]^{b}\\ F(d) \ar[r]_{x_d} & X & F(d) \ar[r]_{x_d} & X}} \hfill	\parbox{8cm}{
-	We want to show that $\phi$ coequalizes $a$ and $n$. Let thus $h\colon X \to Z$ be an arrow such that $h \circ a = h \circ b$. Then, for every $d$, 
-	we have
-	\[h \circ x_d \circ \eta_d = h \circ a \circ p_d 
-	= h \circ b \circ p_d 
-	= h \circ x_d \circ \theta_d\]}
-
-	\noindent
-	Thus, there is $h_d: G(d) \to Z$ such that $h\circ x_d = h_d \circ \phi_d$.
-It is now easy to see that $(Z, \{h_d\}_{d \in \D})$ is a cocone on $G$.
-Suppose $\alpha: d \to d'$ is an arrow of $\D$, then
-	\[h_d\circ \phi_d=h\circ y_d=h\circ y_{d'}\circ F(\alpha)=h_{d'}\circ \phi_{d'}\circ F(\alpha)=h_{d'}\circ G(\alpha)\circ \phi_d\]
-		By the hypothesis $\phi_d$ is regular epi for each $d$ and so we can conclude that $h_d = h_{d'} \circ G(\alpha)$.
-
-	Therefore, we have an arrow $k\colon Y \to Z$ such that $k \circ y_d = h_d$. But then
-	\[
-	k \circ \phi \circ x_d = k \circ y_d \circ \phi_d = h_d \circ \phi_d = h\circ x_d\]
-	Showing that $k \circ \phi = h$.
-
-	For the uniqueness, let $k': Y \to Z$ be another arrow such that $k' \circ \phi = h$. Then we have
-	\[k'\circ y_d\circ \phi_d=k'\circ \phi \circ x_d=h\circ x_d=h_d\circ \phi_d\]
-
-	Since $\phi_d$ is a regular epi, we have $k' \circ y_d = h_d$ allowing us to conclude.
-\end{proof}
-}
-
-To prove \Cref{prop:kerset} we need some results about pushouts and coproducts in $\Set$.
-
-\noindent 
-		\parbox{11.7cm}{
-\begin{lemma}\label{lem:po_set}
-Suppose that the square aside is a pushout, with $m\colon A\mto B$ an injection.
-Let $\iota_{m}\colon E\mto B$ be the inclusion of the complement of the image of $m$.
-Then $(D, \{n, h\circ \iota_m \})$ is a coproduct.
-In particular, $h\circ \iota_m$ is mono.
-\end{lemma}}\hfill \parbox{2cm}{\vspace{0cm}\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
-\begin{proof}
-		 Let $f\colon E\to Z$ and $k\colon C\to Z$ be two arrows with the same codomain.
-By definition of complement and since $m$ is mono we know that $(B, \{m, \iota_m\})$ is a coproduct.
-Define $\phi\colon B\to Z$ as the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\]
-		By the universal property of pushouts there is a unique arrow $\psi \colon D\to Z$ such that $\psi \circ n=k$ and $\psi \circ h=\phi$, thus 
-		\[
-		\psi \circ h\circ \iota_m =\phi \circ \iota_m=f\]
-
-To conclude we have to show that $\psi$ is the unique arrow $D\to Z$ such that $\psi \circ n =k$ and $\psi \circ h\circ \iota_m=f$.
-Let $\psi'\colon D\to Z$ be another arrow such that $\psi' \circ n=k$ and $\psi' \circ h\circ \iota_m=f$.
-Then we have
-		\[\psi'\circ h\circ m=\psi'\circ n\circ g=k\circ g=\phi \circ m =\psi \circ h\circ m \]
-	Since $m$ is mono then $\psi'\circ h=\psi \circ h$,  but $(D, \{n, h\})$ is a pushout and so $\psi'=\psi$. 
-\end{proof}
-
-The category of $\Set$ enjoys two other remarkable and useful properties; it is \emph{distributive} and \emph{extensive} \cite{carboni1993introduction}.
-Distributivity amount to the following property: for every family $\{X_i\}_{i}$ and an object $Y$, the unique morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms.
-\[\xymatrix@C=15pt@R=15pt{&Y\times X_i \ar@{>->}[dl]_{j_i} \ar@{>->}[dr]^{\id{Y}\times h_i} &&& X_i \times Y \ar@{>->}[dl]_{k_i} \ar@{>->}[dr]^{ h_i \times \id{Y}} \\ \Sum_{i\in I} (Y\times X_i) \ar@{.>}[rr]_{\phi}&& Y\times (\Sum_{i\in I}X_i) & \Sum_{i\in I}  (X_i \times Y )\ar@{.>}[rr]_{\psi}&&  (\Sum_{i\in I}X_i) \times Y }\]
-
-\noindent 
-\parbox{11.5cm}{\hspace{15pt} Extensivity means that given a family of objects $\{X_{i}\}_{i\in I}$ and a family of commuting squares as the one on the right, where $j_i$ is a  coprojection, then all the squares are pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.}\hfill
-\parbox{2cm}{\xymatrix@R=15pt{Z_i \ar[r]_{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar@{>->}[r]^{j_i} & X}}
-
-\noindent
-\parbox{11cm}{
-\begin{remark}\label{rem:disj}
-	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~that the pullback between two coprojections is given by the initial object (with initial maps as coprojections).
-To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and let $k$ be an element of $I$.
-Then  $(X_k, \{t_i\}_{i\in I})$ with
-	\[t_i=\begin{cases}
-		\id{X_k} & i=k\\?_{X_k} & i\neq k
-	\end{cases}\]
-	is a coproduct and so the squares on the right are pullbacks.
-\end{remark}}\hfill\parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}
-
-In particular, the previous remark yields at once the following fact.
-
-\noindent 
-\parbox{11.5cm}{\begin{proposition}\label{prop:isempty}
-	Suppose that the square on the right is a pullback.
-Let $\iota \colon E\mto Y$ be the inclusion of the complement of the image of $p_1$.
-If there exist two  arrows $t_1\colon T\to E$ and $t_2\colon T\to X$ such that \[g\circ \iota\circ t_1= f\circ t_2\] then $T$ is empty.
-\end{proposition}}\hfill \parbox{2cm}{\vspace{-1.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
-\begin{proof}
-	By the universal property of pullbacks we get an arrow $t\colon T\to P$ such that 
-	\[p_1\circ t=\iota \circ t_1 \qquad p_2\circ t=t_2\]
-	\parbox{2cm}{\xymatrix{T \ar@{.>}[r]^{s}\ar@{>>}[dr]_{\pi} \ar@/^.4cm/[rr]^{t_1} & \emptyset \ar@{>->}[r]_{?_{E}} \ar@{>->}[d]_{?_I}& E \ar@{>->}[d]^{\iota}\\ & I \ar@{>->}[r]_{i} & Y}}\hfill \parbox{10.5cm}{Let $i\colon I\mto Y$ be the inclusion of the image of $p_1$, so that we have also an epi $q\colon P\eto I$.
-By definition of complement $(Y, \{i, \iota\})$ is a coproduct, thus by  \Cref{rem:disj} the inner square in the diagram on the left is a pullback and we get a dotted arrow $s\colon T\to \emptyset$ filling the diagram.
-But a set with an arrow towards the empty set must be empty and we conclude.
-\qedhere }
-\end{proof}
-
-Extensivity and distributivity, moreover, yield the following fact.
-
-\begin{lemma}\label{lem:nodim}
-	Let $f,g\colon A\rightrightarrows B+C$ be two arrows with a coproduct as codomain. Then $(A, \{j_i\}_{i=0}^
-	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares.
-	\[\xymatrix@C=30pt@R=15pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
-		B\times B \ar@{>->}[r]_-{i_B\times i_B} & (B+C)\times (B+C) & B\times C \ar@{>->}[r]_-{i_B\times i_C} & (B+C)\times (B+C)}\]
-	\[ \xymatrix@C=30pt@R=15pt{A_2 \ar@{>->}[r]^{j_2}  \ar[d]_{p_2}& A   \ar[d]^{(f,g)}& A_3 \ar@{>->}[r]^{j_3}  \ar[d]_{p_3} & A \ar[d]^{(f,g)} \\
-		C\times B \ar@{>->}[r]_-{i_C\times i_B} & (B+C)\times (B+C) & C\times C \ar@{>->}[r]_-{i_C\times i_C} & (B+C)\times (B+C)}\]
-\end{lemma}
-
-We are now ready to exploit the previous properties to prove \Cref{prop:kerset}. % as promised.
-
-\noindent
-\parbox{7.5cm}{\mps*}\hfill
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{->}[rr]_{g} & & D }}
-
-\begin{proof}\label{proof:kerset}
-	We can start noticing that $m$, being the pullback of $n$ is mono too.
-This, in turn, entails that $m'$, being the pullback of $m$, is mono, and so $n'$ is injective too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.
-\vspace{.1cm}
-
-	\noindent 
-	\parbox{11.5cm}{\hspace{15pt}
-	Let $\iota' \colon E'\mto C'$ and $\iota\colon E\to C$ be the inclusions of the complement of the images of of $m'$ and $m$ respectively .
-By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ is a coproduct.
-}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}
-
-\vspace{.1cm}
-
-	\noindent
-	\parbox{10.5cm}{\hspace{15pt}We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.To see this, let $e$ be in $E'$ and suppose that  $c(\iota'(e))=m(x)$ for some $x\in A$.
-Then we can apply the  universal property of pullbacks to build the dotted arrow $v$ in the diagram aside, where $v_0$ and $v_1$ are the arrows picking $x$ and $\iota'(e)$, respectively.
-But then $e$ must belong to the image of $m'$, which is a contradiction.}\hfill  \parbox{4cm}{\xymatrix@R=15pt{1 \ar[dr]_{v_0}  \ar@/^.3cm/[rr]^{v_1} \ar@{.>}[r]_{v}& A' \ar[d]_{a} \ar@{>->}[r]_{m'} & C' \ar[d]^{c}\\& A  \ar@{>->}[r]^{m}& C}}
-
-	\begin{enumerate}
-		\item Consider two arrows $t_1\colon T\to D' $ and $t_2\colon T\to B$ such that $d\circ t_1=n\circ t_2$. By extensivity
-
-		\noindent\parbox{9.5cm}{ of $\Set$, we already know that $(T, \{l_i\}_{i=0}^1)$ is a coproduct, where $l_i\colon T_i\mto T$ are defined by the diagram aside, whose two halves are pullbacks.
-}\hfill\parbox{4cm}{\xymatrix@R=15pt{T_0 \ar@{>->}[r]_{l_0} \ar[d]_{h_0} & T \ar[d]^{t_1} & T_1 \ar@{>->}[l]^{l_1} \ar[d]^{h_1}\\ E' \ar@{>->}[r]^{g'\circ \iota'} & D' & B' \ar@{>->}[l]_{n'}}}
-
-		If we compute we get
-		\[g\circ c \circ \iota' \circ h_0=d\circ g'\circ \iota' \circ h_0=d\circ t_1\circ l_0=n\circ t_2\circ l_0\]
-
-		By hypothesis the bottom face of the given cube is a pullback, therefore there exists an arrow $u\colon T_0\to A$ such that 
-		\[f\circ u=n\circ t_2\circ l_0 \qquad m\circ u=c\circ \iota'\circ h_0\]
-
-	By \Cref{prop:isempty} we conclude that $T_0$ is empty. Therefore $l_1$ is an isomorphism and we have $n'\circ h_1\circ l^{-1}_1=t_1$. On the other hand
-\[n\circ b\circ h_1\circ l^{-1}_1=d\circ n'\circ h_1\circ l^{-1}_1=d\circ t_1=n\circ t_2\]
-And we can conclude that $b\circ h_1\circ l^{-1}_1=t_2$ because $n$ is a mono. The claim now follows from the fact that  also $n'$ is mono.
-
-		\item 	 By \Cref{lem:po_set,lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks.
-		\[\xymatrix@C=45pt@R=15pt{K_b \ar@{>->}[r]^{k_{n'}}  \ar[d]_{(\pi^1_b, \pi^2_b)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
-			B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota')} & D'\times D'}\]
-		\[ \xymatrix@C=45pt@R=15pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
-			E'\times B' \ar@{>->}[r]_-{(g'\circ \iota') \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D'}\]
-
-Let us now examine $K_1$ and $K_2$. We have
-\begin{align*}
-	n\circ b\circ p_1&=d\circ n'\circ p_1=d\circ \pi^1_d\circ j_1=d\circ \pi^2_d\circ j_1=d\circ g'\circ \iota'\circ q_1=g\circ c \circ \iota'\circ q_1\\
-	n\circ b\circ q_2 &=d\circ n'\circ p_2=d\circ\pi^2_D\circ j_2
-	=d\circ \pi^1_d\circ j_2=d\circ g'\circ \iota'\circ p_2 = g\circ c \circ \iota'\circ p_2
-\end{align*}
-
-Since the bottom face of the original cube is a pullback (by hypothesis), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
-\[m\circ k_1= c \iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=c \iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]
-
-By \Cref{prop:isempty} we conclude that $K_1$ and $K_2$
-are both empty. In particular, this implies that $(K_d, \{k_{n'}, j_3\})$ is a coproduct.
-
-We focus now on $K_3$. By computing we get
-	\begin{align*}
-	&g\circ \iota \circ w\circ p_3=g\circ c\circ \iota'\circ p_3=d\circ g'\circ \iota'\circ p_3=d\circ \pi^1_d\circ j_3\\=&d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota' \circ q_3=g\circ c\circ \iota'\circ q_3=g\circ \iota \circ w\circ q_3
-	\end{align*}
-
-\noindent 
-\parbox{3cm}{\xymatrix@R=15pt{ K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & C' \ar[r]_{c} & C }}\hfill\parbox{9.5cm}{By \Cref{lem:po_set} $g\circ \iota$ is a monomorphism, thus $w\circ p_3=w\circ q_3$ and therefore
-\[c\circ \iota'\circ p_3=\iota\circ w\circ p_3=\iota \circ w\circ q_3=c\circ \iota'\circ q_3\]
-Thus we get the dotted $\phi_3\colon K_3\to K_c$ in the diagram aside.}
-
-Moreover, $k_{g'}\circ \phi_3=j_3$ as shown by the following computation.
-\begin{align*}
-&(\pi^1_d, \pi^2_d)\circ k_{g'}\circ \phi_3=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ \phi_3=(g'\times g')\circ (\iota'\circ p_3, \iota'\circ q_3)\\=&((g'\circ \iota') \times (g'\circ \iota'))\circ (p_3, q_3)=(\pi^1_d, \pi^2_d)\circ j_3
-\end{align*}
-
- \commentato{
-
- 	\smallskip
- \parbox{7.5cm}{We can go further. The outer part of the diagram on the right commutes, so that we have the dotted $\psi_0\circ K_b\to K_0$.
- Now, on the one hand $\phi_0\circ \psi_0=\id{K_b}$ because if we compute we get
-  \[(\pi^1_b, \pi^2_b)\circ \phi_0\circ \psi_0=(p_0, q_0)\circ \psi_0=(\pi^1_b, \pi^2_b)\]}\hfill \parbox{4cm}{\vspace{-.5cm}\xymatrix{K_b \ar[dr]_{(\pi^1_b, \pi^2_b)}  \ar@{>->}@/^.4cm/[rr]^{k_{n'}} \ar@{.>}[r]_{\psi_0}& K_0 \ar@{>->}[r]_{j_0}  \ar[d]^{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)} \\
- 	& B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' }
- 	}
-
- On the other hand, notice that 
- \begin{align*}
- \pi^1_{d}\circ k_{n'}\circ \phi_0&=n'\circ \pi^1_b\circ \phi_0=n'\circ p_0=\pi^1_d\circ j_0 \\
- \pi^2_{d}\circ k_{n'}\circ \phi_0&=n'\circ \pi^2_b\circ \phi_0=n'\circ p_0=\pi^2_d\circ j_0
- \end{align*}
-
-  Thus $k_{n'}\circ \phi_0=j_0$ and we have
- \[(p_0, q_0)\circ \psi_0\circ \phi_0=(\pi^1_b, \pi^2_b)\circ \phi_0=(p_0, q_0) \qquad  j_0\circ \psi_0\circ \phi_0 = k_{n'}\circ \phi_0=j_0\]
-We can conclude that $\phi_0$ is an isomorphism, $(K_b, \{k_{n'}, (\pi^1_b, \pi^2_b)\})$ is a pullback for $(\pi^1_d, \pi^2_d)$ along $n'\times n'$ and  that$(K_d, \{k_{n'}, j_3\})$ is a coproduct.}
-
-By definition of complement, we also know that $(C', \{\iota', m'\})$ is a coproduct. We can then apply again \Cref{lem:nodim}, decomposing $K_c$ in four parts, given by the pullbacks below
- \[\xymatrix@C=45pt@R=15pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
- 	A'\times A' \ar@{>->}[r]_-{m'\times m'} & C'\times C' & A'\times E' \ar@{>->}[r]_-{m'\times  \iota'} & C'\times C'}\]
- \[ \xymatrix@C=45pt@R=15pt{H_2 \ar@{>->}[r]^{x_2}  \ar[d]_{(y_2, z_2)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_3 \ar@{>->}[r]^{x_3}  \ar[d]_{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
- 	E'\times A' \ar@{>->}[r]_-{\iota' \times m'} & C'\times C' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
-
- \noindent
-\parbox{7cm}{ Let us examine $H_0$. We start noticing that 
- \begin{align*}
- 	(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_0=&(g'\times g')\circ(\pi^1_c, \pi^2_c)\circ x_0\\=&(g'\times g')\circ (m'\times m')\circ (y_0, z_0)\\=&((g'\circ m')\times (g'\circ m'))\circ (y_0, z_0)\\=&((n'\circ f')\times (n'\circ f'))\circ (y_0, z_0)\\=&(n'\times n')\circ (f'\times f')\circ (y_0, z_0) \end{align*}}\hfill \parbox{5cm}{\xymatrix@C=30pt{H_0 \ar[rr]^{(y_0, z_0)} \ar[d]_{x_0} \ar@{.>}[dr]^{h_0}&& A'\times A' \ar[d]_{f'\times f'}\\K_c \ar[dr]_{k_{g'}}& K_b \ar[r]_-{(\pi^1_b, \pi^2_b)} \ar[d]_{k_{n'}} & B'\times B' \ar[d]_{n'\times n'}\\ &K_d \ar[r]^-{(\pi^1_d, \pi^2_d)} & D'\times D'}}
-
- Thus we get the dotted arrow $h_0\colon H_0\to K_b$ in the diagram above. Moreover, we have
- \[m\circ a\circ y_0=c\circ m'\circ y_0=c\circ \pi^1_c\circ x_0=c\circ \pi^2_c\circ x_0=c\circ m'\circ z_0=m\circ a \circ z_0\]
- Since $m$ is a mono $a\circ y_0=a\circ z_0$ and there exists an arrow $h'_0\colon H_0\to K_a$ such that $\pi^1_a\circ h'_0=y_0$ and $\pi^2_a\circ h'_0=z_0$. 
- We now can conclude that $k_{f'}\circ h'_0=h_0$, noticing that
- \[(\pi^1_b, \pi^2_b)\circ h_0=(f'\times f')\circ (y_0, z_0)=(f'\times f')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(\pi^1_b, \pi^2_b)\circ k_{f'}\circ h'_0\]
-
-We can prove another property of $h'_0$. By computing we have
-\[(\pi^1_c, \pi^2_c)\circ k_{m'}\circ h'_0=(m'\times m')\circ (\pi^1_a, \pi^2_a)\circ h'_0=(m'\times m')\circ (y_0, z_0)=(\pi^1_c, \pi^2_c)\circ x_0\]
-so that $k_{m'}\circ h'_0$ must coincide with $x_0$.
-
-As a next step, let us focus on $H_1$ and $H_2$. Two computations yield \small
- \[\begin{split}
-(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_1&=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_1\\=&(g'\times g')\circ (m'\times \iota')\circ (y_1, z_1)\\=&((g'\circ m') \times (g'\circ \iota'))\circ (y_1, z_1)\\=&((n'\circ f') \times (g'\circ \iota'))\circ (y_1, z_1)\\=&(n'\times  (g'\circ \iota'))\circ (f'\circ y_1, z_1)
- \end{split} \hspace{1pt} \begin{split}
- (\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_2&=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ x_2\\=&(g'\times g')\circ ( \iota' \times m')\circ (y_2, z_2)\\=&((g'\circ \iota') \times (g'\circ m'))\circ (y_2, z_2)\\=&( (g'\circ \iota') \times (n'\circ f'))\circ (y_2, z_2)\\=&((g'\circ \iota') \times n')\circ (y_2, f'\circ z_2)
- \end{split} \]
-\normalsize
-
- Hence, we have arrows $h_1\colon H_1\to K_1$ and $h_2\colon H_2\to K_2$, showing that $H_1$ and $H_2$ are empty. For $H_3$, let us consider the two diagrams below.
-
- \[ \xymatrix@C=45pt@R=15pt{ H_3 \ar@{.>}[d]^{\alpha_3} \ar[r]^{x_3} \ar@/_.4cm/[dd]_{(y_3, z_3)} & K_c \ar[d]_{k_{g'}}& K_3 \ar@{.>}[d]^{\beta_3} \ar@/^.3cm$ $/[dr]^{\phi_3} \ar@/_.4cm/[dd]_{(p_3, q_3)}\\K_3 \ar@{>->}[r]^{j_3}  \ar[d]^{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} &  H_3 \ar@{>->}[r]^{x_3}  \ar[d]^{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)}  \\
-   E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
- Their solid part commute. Indeed, we have
- \[\begin{split}
- 	(\pi^1_d, \pi^2_d)\circ k_{g'}\circ x_3&=(g'\times g')\circ (\pi^1_c, \pi^2_c) \circ x_3\\=&(g'\times g')\circ (\iota'\times \iota')\circ (y_3\times z_3)\\=&(g'\circ \iota') \times (g'\circ \iota')\circ (y_3, z_3)
- \end{split}\qquad \begin{split}
- (\pi^1_c, \pi^2_c)\circ \phi_3=&(\iota'\circ p_3, \iota' \circ q_3)\\=&
-(\iota'\times \iota')\circ (p_3, q_3)\\& \end{split}\]
-
-Thus we get the dotted arrows $\alpha_3$ and $\beta_3$ which are one the inverse of the other. Indeed, on the one hand we have
-\begin{align*}
-j_3\circ \alpha_3\circ \beta_3=k_{g'}\circ x_3\circ \beta_3=k_{g'} \circ \phi_3=j_3  \qquad 
-(p_3, q_3)\circ \alpha_3\circ \beta_3=(y_3, z_3)\circ \beta_3=(p_3, q_3) 
-\end{align*}
- On the other hand, notice that
- \[(\pi^1_c, \pi^2_c)\circ \phi_3\circ \alpha_3 =(\iota'\times \iota')\circ (p_3, q_3)\circ \alpha_3= (\iota'\times \iota')\circ (y_3, z_3)=(\pi^1_c, \pi^2_c)\circ x_3\]
- Therefore $\phi_3\circ \alpha_3=x_3$ and thus $x_3\circ \beta_3\circ \alpha_3=x_3$. Moreover
- \[(y_3, z_3)\circ \beta_3\circ \alpha_3=(p_3, q_3)\circ \alpha_3=(y_3, z_3)\]
-
- Summing up, we have just proved that $(K_c, \{x_0, \phi_3\})$ is a coproduct.
-
- Let now $\gamma\colon K_b\to Z$ and $\delta\colon K_c\to Z$ be two arrows such that $\gamma\circ k_{f'}=\delta\circ k_{m'}$.
-We want to construct an arrow $\theta\colon K_d\to Z$ such that $\theta\circ k_{g'}=\delta$ and $\theta\circ k_{n'}=\gamma$.
-
- We have already proved that $(K_d, \{k_n, j_3\})$ is a coproduct, thus there is a unique arrow $\theta\colon K_d\to Z$ such that  $\theta \circ k_{n'}=\gamma$ and $\theta \circ j_3=\delta \circ \phi_3 $.
- Now, on the one hand we have
- \begin{align*}
- 	\theta \circ k_{g'}\circ \phi_3=\theta \circ  j_3=\delta\circ \phi_3 
- \end{align*}
-
- On the other hand, we can conclude that $\theta \circ k_{g'}=\delta$ as wanted, since
- \[\theta \circ k_{g'}\circ x_0=\theta \circ k_{n'}\circ h_0=\gamma \circ h_0=\gamma \circ k_{f'}\circ h'_0=\delta \circ k_{m'}\circ h'_0=\delta \circ x_0 \]
-
- We are left with uniqueness. If $\theta'$ is another arrow $K_d\to Z$ such that $\theta'\circ k_{n'}=\gamma$ and $\theta'\circ k_{g'}= \delta$. If we compute we get
- \[\theta'\circ j_3=\theta'\circ k_{g'}\circ \phi_3=\delta \circ \phi_3=\theta \circ j_3 \]
- We already know that $\theta'\circ k_{n'}=\theta \circ k_{n'}$, so the previous identity entails that $\theta =\theta'$.
-			 \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\subsection{Proofs for \Cref{hypereq}}\label{app:due}
-\fhyp*
-
-\begin{proof}\label{proof:forghyp}
-	\begin{enumerate}
-		\item  This follows at once from \Cref{rem:eqhyp_morphs}.
-		\item  	Let $\mathcal{H}$ be a hypergraph, and define $L(\mathcal{H}) := (E_\mathcal{H}, V_{\mathcal{H}}, V_{\mathcal{H}}, s_\mathcal{H}, t_\mathcal{H}, \id{V_\mathcal{H}})$.
-By construction we have $T(L(\mathcal{H}))=\mathcal{H}$, thus we can define
-		$\eta_\mathcal{H}\colon \mathcal{H}\to T(L(\mathcal{H}))$ as the identity $\id{\mathcal{H}}$.
-
-		To see that in this way we get a unit,  take an arrow $(h, k)\colon \mathcal{H}\to T(\mathcal{G})$ for some $\mathcal{G}$ in $\EqHyp$.
-Then $(h,k, q_{\mathcal{G}}\circ k)$ is an arrow $L(\mathcal{H})\to \mathcal{G}$ and the unique one such that $T(h,k, q_{\mathcal{G}}\circ k)\circ \eta_{\mathcal{H}}=(h,k)$
-
-		\item For every hypergraph $\mathcal{H}$ define $R(\mathcal{H})$ as $(E_\mathcal{H}, V_{\mathcal{H}}, 1, s_\mathcal{H}, t_\mathcal{H}, !_{V_\mathcal{H}})$, so that $T(R(\mathcal{H}))$ is again $\mathcal{H}$.
-Now, let $\epsilon_{\mathcal{H}}\colon T(R(\mathcal{H}))\to \mathcal{H}$ be the identity and take an arrow $(h,k)\colon T(\mathcal{G})\to \mathcal{H}$ for some $\mathcal{G}$ in $\EqHyp$.
-Notice that $!_{Q_\mathcal{G}}\circ q_{\mathcal{G}}=!_{V_{\mathcal{H}}}\circ k$
-		so that $(h,k, !_{Q_\mathcal{G}})$ is an arrow $\mathcal{G}\to R(\mathcal{H})$ of $\EqHyp$ such that $\epsilon_{\mathcal{H}}\circ T(h,k, !_{Q_\mathcal{G}})=(h,k)$.
-
-		Uniqueness of such an arrow follows at once from the first point and the fact that $1$ is terminal. \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{remark}\label{rem:fact}
-	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~surjections) and of monos in $\Set$.
-In particular, we need the fact that they form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.
-This amounts to ask that
-
-	\noindent 
-	\parbox{11.5cm}{
-	\begin{enumerate} 
-		\item every arrow $f\colon X\to Y$ can be factored as $m\circ e$, where $e\colon X\eto Q$ is a regular epi and $m\colon Q\mto Y$ is a mono;
-			\item for every commuting square as the one on the right, with $e\colon X\eto E$ a surjection and $m\colon N\mto Y$ a mono, there exists a unique $k\colon E\to N$ making it commutative.
-	\end{enumerate}}\hfill \parbox{2cm}{\xymatrix{X \ar@{>>}[d]_{e}\ar[r]^{f}& N \ar@{>->}[d]^{m} \\ E \ar@{.>}[ur]^{k}\ar[r]_{g} & Y}}
-
-	\hspace{1pt}\newline 
-	From these properties, one can deduce that if $f=m\circ e$ and $f=m'\circ e'$ are two factorizations of $f$ then there is a bijection $\phi$ such that $m=m'\circ \phi$ and $\phi \circ e=e'$.
-\end{remark}
-
-We will also need the following well-known fact about regular epis.
-
-\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
-	Let $F,G\colon \D\rightrightarrows \X$ be two diagrams and suppose that $\X$ has all colimits of shape $\D$.
-Let $(X, \{x_d\}_{d \in \D})$ and $(Y, \{y_d\}_{d\in D})$ be the colimits of $F$ and $G$, respectively.
-If $\phi\colon  F \to G$ is a natural transformation whose components are regular epis, then the arrow induced by $\phi$ from $X$ to $Y$ is a regular epi.
-\end{lemma}
-
-\noindent
-\parbox{11.4cm}{
-\comp*}\hfill 
-\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_D}}
-
-\begin{proof}\label{proof:comp}
-	\begin{enumerate}
-		\item We know by \Cref{prop:cocomp} that $\hyp$ is cocomplete.
-Thus, let $(E, V, s, t)$ together with $\{(\kappa_E^D, \kappa_V^D)\}_{D \in \D}$ be a colimit for $T \circ F$.
-By \Cref{colim} we also know that
-
-		 \noindent 
-		 \parbox{10.5cm}{$(V, \{\kappa^D_V\}_{D\in \D})$ is a colimit for $U_\eq\circ F$.
-Moreover, since $\Set$ is cocomplete too we can also take a colimit $(C, \{c_d\}_{d\in \D})$ for $K\circ F$.
-Now,  let $\alpha$ be an arrow $D\to D'$ in $\D$, and suppose that $F(\alpha)$ is $(h_1, h_2, h_3)$.
-By definition of morphisms in $\EqHyp$, the square on the right commutes.}
-		\hfill 
-		\parbox{2cm}{\xymatrix{V_d \ar[r]_{h_2} \ar@{>>}[d]_{q_D} & V_{D'} \ar@{>>}[d]^{q_{D'}}\\ Q_{D} \ar[r]^{h_3} & Q_{D'}}}
-		\vspace{.05cm}
-
-		Thus the family $\{q_D\}_{D\in \D}$ form a natural transformation $U_\eq\circ F\to K\circ F$.
-By \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}, the induced arrow $q: V \to C$ between the colimits is a surjection.
-We can then consider the object $(E, V, C, s, t, q)$ of $\EqHyp$, together with the family  $\{(\kappa_E^D, \kappa_V^D, c_D)\}_{D\in \D}$, which by construction is a cocone on $F$.
-Let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^D_E, h^D_V, h^D_Q)\}_{D\in \D})$ be a cocone, then $((E_\mathcal{G},V_\mathcal{G}, s_{\mathcal{G}}, t_{\mathcal{G}}), \{(h^D_E, h^D_V)\}_{D\in \D})$ and $(Q_{\mathcal{G}}, \{h^D_Q\}_{D\in \D})$ are cocone on, respectively, $T\circ F$ and $K\circ D$, giving arrows $(h_E, h_V)$ in $\hyp$ and $h_Q$ in $\Set$ such that
-		\[(h_E, h_V)\circ (\kappa_E^D, \kappa_V^D)=(h^D_E, h^D_V) \qquad h_Q\circ c_D=h^D_Q\]
-		Now, to show that $(h_E, h_V, h_Q)$ is an arrow of $\EqHyp$ we can compute
-		\[h_Q\circ q\circ \kappa^D_V=h_Q\circ c_D\circ q_D=h^D_Q\circ q_D=q_{\mathcal{G}} \circ h^D_V=q_{\mathcal{G}}\circ h_V\circ \kappa^D_V \]
-
-		Uniqueness of such arrow follows form the fact that $T$ is faithful and \Cref{rem:eqhyp_morphs}.
-
-		\item   $\hyp$ is complete, again by \Cref{prop:cocomp}, we can then consider a limiting cone $((E, V, s, t), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ over of $T \circ F$.
-Now, $(V, \{q_D\circ \pi_V^D\}_{D\in \D})$, is a cone for $K \circ F$: indeed, if $\alpha\colon D \to D'$ is an arrow of $\D$, and $F(\alpha)=(h_1, h_2, h_3)$, then we have
-	\[h_3\circ q_D\circ \pi^D_V =q_{D'} \circ h_2\circ \pi^D_{V}=q_{D'}\circ \pi^{D'}_V\]
-
-\noindent 
-\parbox{9.5cm}{Thus there is an arrow $l\colon V\to L$ such that $l_D\circ l=q_D\circ \pi^D_V$.
-By \Cref{rem:fact}, we know that there exist $m\colon Q\mto L$ and $q\colon X\eto Q $ such that $m\circ q=l$.
-Since the identity is mono, \Cref{rem:fact} yield a unique arrow $\pi^D_Q$ fitting in the rectangle aside.} 	\hfill \parbox{3cm}{\xymatrix{
-	V\ar[r]^{\pi_V^D}\ar@{>>}[d]_{q}&V_D\ar@{>>}[r]^{q_D}&Q_D\ar[d]^{\id{Q_D}}\\Q\ar@{>->}[r]_{m}\ar@{.>}[urr]_{\pi_Q^D}&L\ar[r]_{l_D}&{Q_D}
-	}}
-
-	Let $\alpha$ be an arrow $D\to D'$ in $\D$. Then we have
-		\[T(F\alpha\circ (\pi^D_{E}, \pi^D_V, \pi^D_Q))=T(F(\alpha))\circ (\pi^D_E, \pi^D_V)=(\pi^{D'}_E, \pi^{D'}_V)=T(\pi^{D'}_{E}, \pi^{D'}_V, \pi^{D'}_Q)\]
-
-		Thus, by faitfhulness of $T$, $((E, V, C, s, t, q), \{(\pi_E^D, \pi_V^D, \pi_Q^D)\}_{D\in \D})$ is a cone over $F$.
-To see that it is terminal, let $((E_\mathcal{G},V_\mathcal{G}, Q_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}}, q_{\mathcal{G}}), \{(h^D_E, h^D_V, h^D_Q)\}_{D\in \D})$ be another cone.
-In particular there is an arrow $(h_E, h_V)\colon (E_\mathcal{G},V_\mathcal{G},  s_{\mathcal{G}}, t_{\mathcal{G}})\to (E, V, s, t)$ in $\hyp$ such that
-		\[\pi^D_E\circ h_E=h^D_E \qquad \pi^D_V\circ h_V=h^D_V\]
-
-		Moreover, applying $K$ we get that $(Q_{\mathcal{G}}, \{h^D_{Q}\}_{D\in \D})$ is a cone over $K\circ F$, so that there is an arrow $h\colon Q_{\mathcal{G}} \to L$ such that $l_D\circ h=h^D_{Q}$.
-Thus
-		\[l_D\circ h\circ q_\mathcal{G}=h^D_Q\circ q_{\mathcal{G}}=q_{D}\circ h^D_V=q_D\circ \pi^D\circ h_V=l_D\circ l\circ h_V\]
-
-\noindent 
-\parbox{2cm}{\xymatrix@R=15pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[urr]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
-We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that
-\[(\pi^D_E, \pi^D_V, \pi^D_Q)\circ (h_E, h_V, k_Q)=(h^D_E, h^D_V, h^D_Q)\]}
-
-As in the point above, uniqueness is guaranteed by faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
-	\end{enumerate}
-\end{proof}
-
-\mn*
-
-\begin{proof}\label{proof:regmono}
-
-$(\Rightarrow)$	If $(h_E, h_V, h_Q)$ is mono, from \Cref{cor:mono1} we have that $h_E$ and $h_V$ are monos.
-
-\noindent
-	\parbox{11cm}{
-		\hspace{15pt}Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
-	$\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
-	is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono 
-	$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that 
-	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
-	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the claim follows.}
-	\hfill
-	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
-
-	$(\Leftarrow)$ Suppose that $h_E$, $h_V$, and $h_Q$  are monos. 
-	We can build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks.
-	\[     \xymatrix@R=15pt{
-	E_\mathcal{G} \ar@{>->}[d]_{h_E} \ar@{>->}[r]^{h_E}&E_\mathcal{H} \ar@{>->}[d]^{g_E} &	V_\mathcal{G} \ar@{>->}[d]_{h_V} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>->}[d]^{g_V} &Q_\mathcal{G} \ar@{>->}[d]_{h_Q} \ar@{>->}[r]^{h_Q}& Q_\mathcal{H} \ar@{>->}[d]^{g_Q} \\
-		E_\mathcal{H} \ar@{>->}[r]_{f_E} & E_\mathcal{{K}} & V_H \ar@{>->}[r]_{f_V} & V_\mathcal{{K}} & Q_\mathcal{H} \ar@{>->}[r]_{f_Q} & Q_\mathcal{{K}}
-	}
-	\]
-
-	Now, we know by \Cref{prop:com} and \Cref{colim} that there exists arrows $s,t\colon E_{\mathcal{K}}\rightrightarrows V_{\mathcal{K}}$ such that the resulting hypergraph is the cokernel pair of $(h_E, h_V)$ in $\hyp$.
-Moreover, by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi} we know that the unique arrow $q\colon V_{\mathcal{K}}\to Q_{\mathcal{K}}$
-	induced by $q_{Q}\circ q_{\mathcal{H}}$ and $f_{Q}\circ q_{\mathcal{H}}$ is a regular epi. Let thus $\mathcal{K}$ be the resulting hypergraph with equivalence.
-
-	By construction we have two arrows 	$(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ such that 
-	\[(f_E, f_V, f_Q)\circ (h_E, h_V, h_Q) =(g_E, g_V, g_Q)\circ (h_E, h_V, h_Q)\]
-
-	Now, in $\Set$ every mono is regular \cite{maclane2012sheaves}, so by the dual of \Cref{prop:reg_epi_coeq} we deduce that $h_E$, $h_V$ and $h_Q$ are the equalizers of the arrows built above.
-By \Cref{prop:com,lim} we also know that $(h_E, h_V)$ is the equalizer in $\hyp$ of $(f_E, f_V)$ and $(g_E, g_V)$.
-Hence, if $(z_E, z_V, z_Q)\colon \mathcal{Z}\to \mathcal{H}$ is an arrow such that
-			\[(f_E, f_V, f_Q)\circ (z_E, z_V, z_Q) =(g_E, g_V, g_Q)\circ (z_E, z_V, z_Q)\]
-	then we get a unique morphism $(a_E, a_V)\colon (E_{\mathcal{Z}}, V_{\mathcal{Z}})\to (E_{\mathcal{G}}, V_{\mathcal{G}})$ such that $(h_E, h_V)\circ (a_E, a_V) =(z_E, z_V)$.
-Moreover, since $g_Q\circ z_Q=f_Q\circ z_Q$ there is a unique $a_Q\colon Q_{\mathcal{Z}}\to Q_\mathcal{G}$ such that $h_Q\circ a_Q=z_Q$.
-Thus
-	\[h_Q\circ a_Q\circ q_{\mathcal{Z}}=z_Q\circ q_{\mathcal{Z}}=q_{\mathcal{H}}\circ z_{V}=q_{\mathcal{H}}\circ h_V\circ a_V=h_Q\circ q_{\mathcal{G}}\circ a_V\]
-	Since $h_Q$ is mono we conclude that $a_Q\circ q_{\mathcal{Z}}=q_{\mathcal{G}}\circ a_V$ and we conclude.
-\end{proof}
-
-\commentato{
-\quot*
-\begin{proof}\label{proof:quot}
-  Given a hypergraph $\mathcal{H}:=(E, V, s, t)$, let us define $R(E, V, s, t)$ as $(E, V, V, s, t, \id{B})$.
-By construction $\quo(R(\mathcal{{H}})) =\mathcal{H}$ so that we can take the identity as $\epsilon_{\mathcal{H}}\colon \quo(R(\mathcal{H}))\to \mathcal{H} $.
-
-		Suppose that $\mathcal{G}$ is an object of $\EqHyp$ and take an arrow $(h_E, h_V): \quo(\mathcal{G}) \to \mathcal{H}$, then the three squares below commute, so that $(h_E,  h_V \circ q_{\mathcal{G}}, h_V)$ is a morphism of $\EqHyp$.
-		\[\xymatrix@R=15pt@C=30pt{
-			E_{\mathcal{G}} \ar[r]^{h_E}\ar[d]_{s_{\mathcal{G}}} & E \ar[d]^{s} & E_\mathcal{G} \ar[r]^{h_E}\ar[d]_{t_{\mathcal{G}}} & V \ar[d]^{t} & V_{\mathcal{G}} \ar[r]^{h_V \circ q_{\mathcal{G}}} \ar@{>>}[d]_{q_{\mathcal{G}}} & V \ar@{>>}[d]^{\id{V}} \\
-			V_{\mathcal{G}}^{\star} \ar[r]_-{h_V^\star\circ q_{\mathcal{G}}^\star} & V^{\star} & V_{\mathcal{G}}^{\star} \ar[r]_{h_V^\star\circ q_\mathcal{G}^\star} & V^{\star} & C \ar[r]_{h_V} & V
-		}\]
-
-		By construction $\epsilon_{\mathcal{H}}\circ\quo(h_E,  h_V\circ q, h_V)=(h_E, h_V)$.
-To see that such an arrow is unique, let $(f_E, f_V, f_Q)$ be a morphism such that $\epsilon_{\mathcal{H}}\circ\quo(f_E, f_V, f_Q)=(h_E, h_V)$, then $f_E=h_E$ and $f_Q=h_V$, moreover
-		\[f_V=\id{V}\circ f_V=f_Q\circ q_{\mathcal{G}}=h_{V}\circ q_\mathcal{G}  \]
-	allowing us to conclude.		
-\end{proof}
-\commentato{		\item 	Since $\quo$ is a left adjoint, it preserves colimits.
-		Let $F\colon \D \to \EqHyp$ be a diagram, to fix the notation, let  $\mathcal{C}$ be  $(E, V, s, t)$,  and $F(d)$ be $(E_d, V_d, Q_d, s_d, t_d, q_d)$.
-
-		By \Cref{prop:eqhyp_complete} we know that $F$ has a colimit, thus we only have to proof that $\quo$ reflects colimits.
-Let $(\mathcal{G}, \{\kappa^d_E, \kappa^d_V, \kappa^d_Q\}_{d\in \D})$ be a cocone over $F$ such that $(\quo(\mathcal{G}).
-\{\kappa^d_E, \kappa^d_Q\}_{d\in \D})$ is colimiting for $\quo\circ F$.
-
-		and let $(\mathcal{C}, \{(c^d_E, c^d_V)\}_{d\in \D})$, be a colimiting cocone for $\quo \circ F$.
-
-		Let $, )$ be a colimit of $F$, which exists by \Cref{prop:eqhyp_complete},  then by the same proposition we know that $(Q, \{\kappa^d_Q\}_{d\in \D})$ is colimiting for
-
-		Now, let $(U, \{\kappa_d\}_{d\in \D})$  be a colimit for $U_\eq\circ F$.
-We have already noticed in the proof of the first point of \Cref{prop:eqhyp_complete} that  the family $\{q_d\}_{d\in \D}$ defines a natural transformation $U_{\eq}\circ F\to K\circ F$, moreover, by \Cref{prop:com,colim}, $(V, \{c^d_V\}_{d\in \D})$ is colimiting for  $K\circ F$, yielding an arrow $q: V \to C$, which is a surjection by \Cref{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}.
-
-Define now $W: \EqHyp \to \Set$ as the functors $(X, Y, Z, x, y, z)$ to the set of hyperedges $X$ and each morphism to its first component.
-Again by \Cref{prop:com,colim} $(E, \{c^d_E\}_{d\in \D})$ is colimiting for $W \circ F$.
-Moreover, let $\alpha\colon d\to d'$  be an arrow in $\D$ and suppose that $F(\alpha)=(h_1, h_2, h_3)$, then we have
-\begin{align*}
-	\kappa^\star_{d'}\circ s_{d'} \circ W(F(\alpha))&= \kappa^\star_{d'}\circ s_{d'} \circ h_1= \kappa^\star_{d'}\circ h_2\circ s_{d}=\kappa^\star\_{d'}circ U(F(\alpha))\circ s^d =\kappa^\star_d\circ s_d
-	\\\kappa^\star_{d'}\circ t_{d'} \circ W(F(\alpha))&= \kappa^\star_{d'}\circ t_{d'} \circ h_1= \kappa^\star_{d'}\circ h_2\circ t_{d}=\kappa^\star\_{d'}circ U(F(\alpha))\circ s^d =\kappa^\star_d\circ t_d
-\end{align*}
-So that $(U^\star, \{\kappa^\star_d\circ s_d\}_{d\in \D})$ and $(U^\star, \{\kappa^\star_d\circ t_d\}_{d\in \D})$ are cocones over $W\circ F$, yielding two arrows $s, t\colon E\rightrightarrows U^\star$.
-
-By the proof of the first point of \Cref{prop:eqhyp_complete} the . \qedhere }
-}
-
-\pbm*
-
-\begin{proof}\label{proof:pbmono}
-	Closure under composition and decomposition follows from \Cref{lem:pb1}, while stability follows from the first point of \Cref{prop:kerset} because pushouts along injections are also pullbacks by \Cref{prop:regmono}.
-We are left with stability under pullbacks.
-	Let $h\colon \mathcal{G}_1\to \mathcal{G}_3$ be an arrow in $\pbc$ and $k\colon \mathcal{G}_2\to \mathcal{G}_3$ be another morphism of $\EqHyp$, with $\mathcal{G}_{i}=(E_i, V_i, Q_i, s_i, t_i, q_i)$.
-
-	Consider the diagrams below, in which the square on the left is a pullback in $\EqHyp$, with $\mathcal{P}=(E_{\mathcal{P}, V_{\mathcal{P}}}, Q_{\mathcal{P}}, s_{\mathcal{P}}, t_{\mathcal{P}}, q_{\mathcal{P}})$, and in which the right half of the right rectangle is a pullback too, so that the existence of $m_\mathcal{P}$ is guaranteed by \Cref{prop:eqhyp_complete}.
-
-	Again by \Cref{prop:eqhyp_complete} the two halves of the central rectangle are pullbacks and so by \Cref{lem:pb1} the whole rectangle is a pullback too.
-This, in turn entails that the whole right rectangle is a pullback and so, also its left half is a pullback (again by \Cref{lem:pb1}).
-	\[
-	\xymatrix@R=15pt{\mathcal{P} \ar[r]^{p} \ar[d]_{r}&  \mathcal{G}_1 \ar[d]^{h} &
-		V_{\mathcal{P}} \ar@/^.4cm/[rr]^{p_Q\circ q_{\mathcal{P}}} \ar[r]_{p_V} \ar@{>->}[d]_{r_V}& V_1  \ar@{>>}[r]_{q_1} \ar@{>->}[d]_{h_V}& Q_1 \ar@{>->}[d]^{h_Q}& V_{\mathcal{P}} \ar@{>>}[r]_{q_{\mathcal{P}}} \ar@{>->}[d]_{r_V} & Q_{\mathcal{P}} \ar@{>->}[dr]_{r_Q} \ar@/^.4cm/[rr]^{p_Q} \ar@{>->}[r]_{m_{\mathcal{P}}}& T \ar[r]_{t_1} \ar@{>->}[d]_{t_2} & Q_1 \ar@{>->}[d]^{h_Q}\\
-		\mathcal{G}_2 \ar[r]_{k} & \mathcal{G}_3 &   V_2  \ar@/_.3cm/[rr]_{k_Q\circ q_2}\ar[r]^{k_V}& V_3 \ar@{>>}[r]^{q_3} & Q_3 &V_2 \ar@{>>}[rr]^{q_2}&& Q_2 \ar[r]^{k_Q} & Q_3 }
-	\]
-
-	Let now $z_1\colon Z\to Q_{\mathcal{P}}$ and $z_2\colon Z\to V_2$ be two arrows such that $q_2\circ z_2=r_Q\circ z_1$. Then there exists a unique arrow $z\colon Z\to V_{\mathcal{P}}$ such that
-	\[m_{\mathcal{P}}\circ q_{\mathcal{P}}\circ z= m_{\mathcal{P}}\circ z_1 \qquad r_V\circ z=z_2\]
-	Since $m_\mathcal{P}$ is mono we conclude that $q_{\mathcal{P}}\circ z=z_1$ as wanted.
-
-	Uniqueness follows at once since $r_V$, being the pullback of $h_V$ is a mono.
-\end{proof}
-
-\pbs*
-
-\begin{proof}\label{proof:pbstable}
-	Let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'_i=(A'_i, B'_i, Q'_i, s'_i, t'_i, q'_i)$, for $i \in \{1, 2, 3, 4\}$, be hypergraphs with equivalence, 
-	and  suppose that in the first diagram below,  all the vertical faces are pullbacks, the bottom face is a pushout $h$ is a regular mono and $k_Q\colon Q_1\mto Q_3$ is mono.
-By \Cref{prop:eqhyp_complete} the same is true for the other two cubes, by \Cref{cor:mono2}, $h_E$ and $h_V$ are monos and so the top faces of these cubes are pushouts.
-	\[
-	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\
-		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
-		&&B_3'  \ar[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar[dd]_(.3){d_V}\\
-		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
-		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
-	\]
-
-	\noindent 
-\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
-Notice moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
-By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
-By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_Q} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
-
-	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below.
-
-	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} \\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4}\]
-
-	\noindent 
-	\parbox{8.5cm}{\hspace{15pt}
-	For $Q'_1$, we can make a similar argument.
-Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ that makes the diagram aside commutative.}\hfill
-	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
-
-We have to show that the top face of the cube with which we have begun is a pushout.
-Let $\mathcal{H}$ be $(E, V, Q, s, t, q)$ and suppose that there exist  $o\colon  \mathcal{G}_2' \to \mathcal{H}$ and $w\colon  \mathcal{G}_3' \to \mathcal{H}$ such that $o \circ h' = w \circ k'$.
-Since $T$ preserves colimits by \Cref{prop:forghyp}, we know that there exists a morphism $(v_E, v_V)\colon T(\mathcal{G'}_4)\to T(\mathcal{H})$ such that
-\[v_E\circ p'_E=w_E \quad v_V\circ p'_V=w_V \quad v_E\circ z'_E=o_e \quad v_V\circ z'_V=o_V\]
-
-\commentato{\xymatrix@C=10pt@R=6pt{
-		&B_1'\ar@{>>}[dd]|\hole_(.65){q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>>}[dd]|\hole_(.65){q_2'} \ar[dl]_(.6){z_V'}\ar[dr]^{o_V}\\
-		B_3'  \ar@{>>}[dd]_{q_3'}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>>}[dd]_(.3){q_4'} \ar[rr]^(.7){v_V}&&  V\ar[dd]^{q}\\
-		&Q_1'\ar@{>->}[rr]|\hole^(.65){h'_Q} \ar[dl]_{k'_Q} && Q_2' \ar[dl]^(.4){z_Q'}\ar[dr]^{o_Q}\\
-		Q'_3 \ar@{>->}[rr]_{p_Q'} & & Q'_4\ar@{.>}[rr]_{v_C} && Q
-}}
-
-\smallskip \noindent 
-\parbox{8cm}{ \hspace{15pt}We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
-If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-
-	\hspace{15pt}Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
-We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
-
-	By construction we have that 
-	\begin{align*}
-		m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1& = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \\
-		m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 &= m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2
-		\end{align*} 
-	}\hfill\parbox{4cm}{\xymatrix@C=10pt@R=10pt{
-	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
-	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
-	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]_{w} && U\ar[dl]^(.4){u_1} \\
-	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
-}
-	but since $m_3$ and $m_2$ are monos this implies
-\[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]
-
-By computing, we obtain
-\begin{align*}
-	&q \circ v_V \circ \pi_{q_4'}^1 \circ k_{p_V'} = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^1= q \circ w_V \circ \pi_{m_3 \circ q_3'}^1 = w_Q \circ q_3' \circ \pi_{m_3 \circ q_3'}^1 \\
-	=& w_Q \circ q_3' \circ \pi_{m_3 \circ q_3}^2 = q \circ w_V \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ p_V' \circ \pi_{m_3 \circ q_3'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{p'_V}\\
-&q \circ v_V \circ \pi_{q'_4}^1 \circ k_{z_V'} = q \circ v_V \circ z_V' \circ \pi_{m_2 \circ q_2'}^1 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^1 = o_Q\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 \\
-	= &o_Q \circ q_2' \circ \pi_{m_2 \circ q_2}^2 = q \circ o_V \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ t_V' \circ \pi_{m_2 \circ q_2'}^2 = q \circ v_V \circ \pi_{q'_4}^2 \circ k_{z'_V}
-\end{align*}
-
-As already noticed the square above is a pushout, hence we can conclude that
-\[
-q \circ v_V \circ \pi_{q'_4}^1 = q \circ v_V \circ \pi_{q'_4}^2
-\]
-
-Now, $q'_4$ is a regular epi and so it is the coequalizer of its kernel pair, hence there exists $v_Q\colon Q'_4\to Q$ such that $v_Q\circ q'_4=q\circ v_V$ and we can conclude.
-\end{proof}
-
-\pbvk*
-
-\begin{proof}\label{proof:pbvk}
-
-Consider a cube as the one below on the left, with regular monos as vertical arrows, pullbacks as back faces, pushouts as bottom and top faces and such that $h$ is in $\pbc$.
-Given \Cref{lemma:stab}, if we show that the front faces are pullbacks too we can conclude.
-
-To fix notation, let $\mathcal{G}_i = (A_i, B_i, Q_i, s_i, t_i, q_i)$, $\mathcal{G}'=(A_i', B_i', Q_i', s_i', t_i', q_i')$, for $i = 1, 2, 3, 4$.
-By \Cref{prop:eqhyp_complete} and \Cref{cor:mono2} we know that the central and right cube below have pushouts as bottom faces and pullbacks as back faces,
-	thus their front faces are pullbacks
-	\[
-	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar@{>->}[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar@{>->}[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar@{>->}[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar@{>->}[dd]^{b_V} \ar[dl]_{z_V'} \\
-		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar@{>->}[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar@{>->}[dd]_(.3){d_E}
-		&&B_3'  \ar@{>->}[dd]_{c_V}\ar@{>->}[rr]^(.7){p_V'} & & B_4' \ar@{>->}[dd]_(.3){d_V}\\
-		&\mathcal{G}_1\ar[rr]|\hole^(.65){h} \ar[dl]^{k} && \mathcal{G}_2 \ar[dl]^{z} & &A_1\ar@{>->}[rr]|\hole^(.65){h_E} \ar[dl]^{k_E} && A_2 \ar[dl]^{z_E} &&B_1\ar@{>->}[rr]|\hole^(.65){h_V} \ar[dl]^{k_V} && B_2 \ar[dl]^{z_V} \\
-		\mathcal{G}_3 \ar[rr]_{p} & & \mathcal{G}_4 && A_3 \ar@{>->}[rr]_{p_E} & & A_4&&B_3 \ar@{>->}[rr]_{p_V} & & B_4 }
-	\]
-
-Let us now consider the diagrams below, in which the inner squares are pullbacks.	Since the outer diagrams commute, by definition of morphism of $\EqHyp$, then we have the existence of $m_2\colon Q'_2\to U$, $m_3\colon Q'_3\to Y $, $a_3\colon B'_3\to Y$ and $a_2\colon B'_2\to Y$.
-
-\smallskip 
-\noindent 
-\parbox{5.2cm}{\hspace{15pt}Now, notice that  $m_3$ and $m_2$ are monos because $c_Q$ and $b_2$ are injections. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
-	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
-
-		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the claim follows from \Cref{prop:eqhyp_complete}.
-	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
-\xymatrix@R=16pt{B'_3 \ar@{.>}[dr]^{a_3} \ar@{>->}[r]^{p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_Q}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }}
-
-By computing we have
-\[\begin{split}
-	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
-u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
-\end{split} \qquad \begin{split}
- 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
-u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
-\end{split}\]	
-And we have done.
-\end{proof}
-
-\trm*
-\begin{proof}\label{proof:term}
-	Let $F\colon \D\to \EqTG_{\Sigma}$ be the diagram of an equalizer, a binary product or of a pullback.
-By \Cref{prop:lim} we can consider a limiting cone $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$.
-By \Cref{rem:t} we know that $T_\Sigma$ preserves limits, thus by \Cref{rem:obv}  $(l, \{T_\Sigma(\pi_d)\}_{d\in \D})$ is limiting for $I_\Sigma\circ S_\Sigma$.
-Then by \Cref{prop:tlim} $l$ is a term graph.
-We conclude, again by \Cref{rem:obv} that $(\mathcal{L}, l)$ is in $\EqTG_{\Sigma}$ and the claim follows.
-\end{proof}
-
-\po*
-\begin{proof}\label{proof:tade}
-	Suppose that the square on the left below is a pushout in $\EqHyp_\Sigma$, with $h$ in $\mathcal{T}$.
-Then, by \Cref{rem:t} the square on the right is a pushout and by the definition of $\mathcal{T}$ and \Cref{rem:obv}, $T_\Sigma(h)$ is a regular mono in $\tg$.
-	\[\xymatrix{J_\Sigma(\mathcal{G}_0, l_0) \ar[r]^{k} \ar[d]_{h}& J_\Sigma(\mathcal{G}_1, l_1) \ar[d]^{p} &T_\Sigma (J_\Sigma(\mathcal{G}_0, l_0)) \ar[r]^{T_{\Sigma}(k)} \ar[d]_{T_{\Sigma}(h)}& T_\Sigma (J_\Sigma(\mathcal{G}_1, l_1)) \ar[d]^{T_\Sigma(p)}\\
-J_\Sigma(\mathcal{G}_1, l_1) \ar[r]_{q}& J_\Sigma(\mathcal{H}, l) & T_\Sigma(J_\Sigma(\mathcal{G}_1, l_1)) \ar[r]_{T_\Sigma(q)}& T_\Sigma(J_\Sigma(\mathcal{H}, l))}\]
-
-	We conclude using \Cref{prop:push,rem:obv}.
-\end{proof}
-
-\subsection{Proofs for \Cref{eggs}}
-\elim*
-\begin{proof}\label{proof:elim}
-	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, Q_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
-	Now let $(A, B, Q, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_Q^d)_{d\in \D}$, be the limit of $I \circ F$.
-Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ F$.
-If we show that it lies in $\egg$ we are done.
-
-	By \Cref{prop:eqhyp_complete} there exists a mono $m\colon Q \mto L$ such that $\pi_Q^d = l_d \circ m$. Notice that
-	\begin{align*}
-		&q_d^\star \circ s_d\circ \pi^d_E\circ u_1  = q_d^\star\circ (\pi^d_V)^\star \circ s\circ u_1= (\pi_Q^d)^\star\circ q^\star\circ s\circ u_1\\=&(\pi_Q^d)^\star\circ q^\star\circ s\circ u_2= q_d^\star\circ (\pi^d_V)^\star\circ s\circ u_2=q_d^\star \circ s_d \circ \pi_E^d \circ u_2\\
-	\end{align*}
-
-	\vspace{.1cm}
-	\noindent 
-	\parbox{9.5cm}{ \vspace{-.8cm}\hspace{15pt}
-	Thus for each $d$ in $\D$, there exists an arrow $a_d:U\to U_i$ making the diagram on the right commutative.
-Then we have
-\begin{align*}
-	&l_d^\star\circ m^\star \circ q^\star \circ t \circ u_1    = q_d^\star\circ (\pi_V^d)^\star \circ t \circ u_1 \\
-	= &q_d^\star \circ t_d \circ \pi_E^d \circ u_1
-	= q_d^\star \circ t_d \circ u_1^d \circ a_d 
-	= q_d^\star \circ t_d \circ u_2^d \circ a_d\\ 
-	=& q_d^\star \circ t_d \circ \pi_E^d \circ u_2 = q_d^\star \circ (\pi_V^d)^\star \circ t \circ u_2 = l_d^\star \circ m^\star \circ q^\star \circ t \circ u_2
-\end{align*}}\hfill \parbox{4cm}{\vspace{-1cm}	\xymatrix@R=20pt{
-		U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_d} & A \ar[dr]^{\pi_E^d} & \\
-		A \ar[dr]_{\pi_E^d} & U_d \ar[r]^{u_1^d} \ar[d]_{u_2^d}& A_d \ar[d]^{q_d^\star \circ s_d} \\
-		& A_i  \ar[r]_{q_d^\star \circ s_d}& Q_d^\star
-	}}
-
-	By universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$.
-Since $m$ is mono we deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the claim.
-\end{proof}
-
-\begin{remark}\label{rem:kleene}
-	Let $\delta_1\colon 1\to \mathbb{N}$ be the arrow which picks $1\in \mathbb{N}$. Consider the
-
-	\noindent
-	\parbox{11.5cm}{ inclusion $v_1\colon X\to X^\star $  defined by the first point of \Cref{prop:fact}.
-By extensivity we know that the square on the right is a pullback.}\hfill \parbox{4cm}{\vspace{-.5cm}\xymatrix@R=15pt{X \ar[r]_{!_{X}} \ar[d]_{!_{X}}& 1\ar[d]^{\delta_1} \\1 \ar[r]^{\lgh_{X}} & \mathbb{N}} }
-
-	\noindent 
-	\parbox{4cm}{\vspace{-.2cm} \xymatrix@C=15pt@R=1pt{&X\ar[dd]|\hole_(.65){!_{X}}\ar@{->}[rr]^{!_X} \ar@{>}[dl]_{f} && 1 \ar[dd]^{\delta_1} \ar[dl]^{\id{1}} \\ Y  \ar[dd]_{!_Y}\ar@{>}[rr]^(.7){!_Y} & & 1 \ar[dd]_(.3){\delta_1}\\&X^\star\ar@{>->}[rr]|(.53)\hole^(.70){\lgh_{X}} \ar@{>->}[dl]_{f^\star} && \mathbb{N} \ar[dl]^{\id{N}} \\Y^\star \ar@{>->}[rr]_{\lgh_{Y}} & & \mathbb{N}}}\hfill \parbox{9.5cm}{\vspace{-.3cm}\hspace{15pt}Let now $f\colon X\to Y$ be an arrow.
-Then we can build the cube aside which, by what we have just observed above, has pullbacks as back, front and right faces.
-Thus, by \Cref{lem:pb1} its left face is a pullback too.}
-
-\end{remark}
-
-\noindent
-\parbox{11.5cm}{
-\epo*}\hfill 
-\parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
-\begin{proof}\label{proof:epo}
-	Let $\mathcal{P} $ be $(A, B, C, s, t, q)$ and consider the kernel pair $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, for $i\in \{1, 2, 3\}$.
-Let also $(U, u_1, u_2)$ be the kernel pair of $q^\star \circ s$.
-
-	\noindent
-	\parbox{10cm}{\hspace{15pt}Consider now the cube on the right.
-By hypothesis and \Cref{rem:kleene} its left face is a pullback, moreover its bottom face, while not a pushout it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.}\hfill \parbox{3cm}{\xymatrix@C=10pt@R=2pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar@{>->}[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar@{>.>}[dl]_(.6){n_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){z_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{Q_1^\star}\ar[rr]|\hole^(.65){h_Q^\star}\ar@{>->}[dl]_{m_Q^\star} && {Q_2^\star} \ar@{>->}[dl]^{n_Q^\star} \\{Q_3^\star} \ar[rr]_{z_Q^\star} & & Q^\star}}
-
-	\noindent
-	\parbox{2cm}{\vspace{-.25cm}\xymatrix@R=15pt{K_1\ar[r]_{k_{h_E}}\ar@{>->}[d]_{k_{m_E}}&K_2\ar@{>->}[d]^{k_{n_E}}\\K_3\ar[r]^{k_{z_E}}&U}}
-\hfill \parbox{11.5cm}{ \vspace{-.25cm}\hspace{15pt}By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout.
-Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout.}
-		By computing we obtain
-	\begin{align*}
-		q^\star \circ t \circ u_1 \circ f_n &= q^\star \circ t \circ n_E \circ \pi_2^1 = n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^1 = n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^2 =q^\star \circ t \circ u_2 \circ f_n \\
-		q^\star \circ t \circ u_1 \circ f_k &= q^\star \circ t \circ k_E \circ \pi_3^1 = k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^1 = k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^2 =q^\star \circ t \circ u_2 \circ f_k
-	\end{align*}
-	We can therefore deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the claim follows.
-\end{proof}
-
-\limt*
-\begin{proof}\label{proof:tlim}
-Let $F\colon \D\to \eg$ be a diagram of one of the shapes mentioned in the statement.
-Let $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$ be a limiting cone for $k_\Sigma \circ F$.
-By \Cref{lim}, \Cref{prop:term}, and \Cref{proof:elim} we know that $\mathcal{L}$ is an e-termgraph and we can conclude.
-\end{proof}
-
-\section{Some properties of comma categories}
-In this section we briefly recall the definition of the comma category \cite{mac2013categories} associated to two functors and some of its properties.
-\begin{definition}\index{category!comma -}
-	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comma{L}{R}$ is the category in which
-
-\noindent
-\parbox{10.5cm}{\vspace{-.5cm}\begin{itemize}
-		\item objects are triples $(A, B, f)$ with $A\in \A$, $B\in \B$, and $f\colon L(A)\rightarrow R(B)$; 
-		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the diagram aside commutes\end{itemize}}\hfill
-	\parbox{4cm}{\vspace{-.1cm}\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}}
-\end{definition} 
-We have two forgetful functors 	$U_L\colon \comma{L}{R}\to \A$ and $U_R\colon \comma{L}{R} \to \B$ given respectively by
-\[
-\begin{split}
-	\functor[l]{(A,B, f)}{(h,k)}{(A', B', g)}
-	& \functormapsto
-	\rfunctor{A}{h}{A'}
-\end{split}\quad 
-\begin{split}
-	\functor[l]{(A,B, f)}{(h,k)}{(A', B', g)}
-	& \functormapsto
-	\rfunctor{B}{k}{B'}
-\end{split}
-\]
-
-Given $L\colon \A\to \X$ and $R\colon \B\to \X$, we can also consider their duals $L^{op}\colon \A^{op}\to \X^{op}$ and $R^{op}\colon \B^{op}\to \X^{op}$.
-An arrow $f\colon L(A)\to R(B)$ in $\X$ is the same thing as an arrow $f\colon R^{op}(B)\to L^{op}(A)$ in $\X^{op}$.
-Thus $\comma{L}{R}$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
-Moreover, the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$.
-\[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g} & R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B') & L(A') \ar[r]_{L(h)}  & L(A)}\]
-
-Summing up we have just proved the following fact.
-\begin{proposition}\label[proposition]{prop:dual}
-	$(\comma{L}{R})^{op}$ is equal to	$\comma{R^{op}}{L^{op}}$, and $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
-\end{proposition}
-
-\begin{lemma}\label[lemma]{colim}
-	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
-Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite[Sec.~5.1.3]{castelnovo2023thesis} or \cite[Sec.~2.3]{CastelnovoGM24}).
-\end{lemma}
-\begin{proof}
-	Suppose that $U_L\circ F$ and $U_R\circ F$ have respectively colimiting cocones  $\left(A, \{a_D\}_{D\in \D}\right)$ and $\left(B, \{b_D\}_{D\in \D}\right)$.
-By hypothesis $\left(L(A), \{L\left(a_D\right)\}_{D\in \D}\right)$ is colimiting for $L\circ U_L\circ F$.
-Now, let $F(D)$ be $(A_D, B_D, f_D)$,
-	then we have arrows $R(b_D)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comma{L}{R}$ and so
-	\begin{align*}
-		&R\left(b_{D'}\right)\circ f_{D'}\circ L(U_L(F(d)))=R\left(b_{D'}\right)\circ R\left(U_R\left(F(d)\right)\right)\circ f_D\\=&R\left(b_{D'}\circ U_R\left(F(d)\right)\right)\circ f_D=R\left(b_D\right)\circ f_D
-	\end{align*}
-
-	\noindent \parbox{10cm}{
-	\hspace{15pt}Thus there exists $f\colon L(A)\rightarrow R(B)$ fitting in the diagram on the right.
-Notice that $f$ is the unique arrow in $\X$ wich makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comma{L}{R}$.
-If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.}\hfill
-	\parbox{4cm}{\xymatrix@C=35pt@R=15pt{ L(A_D) \ar[r]^{L(a_D)} \ar[d]_{f_D}& L(A) \ar[d]^{f}\\ R(B_D) \ar[r]_{R(b_D)} &R(B)}}
-
-	First of all, let us show that it is a cocone. Given $d\colon D\to D'$ in $\D$ we have
-	\begin{align*}
-		&\left(a_{D'}, b_{D'}\right)\circ F(d)=	\left(a_{D'}, b_{D'}\right)\circ \left(U_L(F(d)), U_R(F(d))\right)\\=&\left( a_{D'}\circ U_L(F(d)),  b_{D'}\circ U_R(F(d)) \right)=\left(a_D, b_D\right)
-	\end{align*}
-
-	For the colimiting property, let $\left((X, Y, g), \left\{\left(x_D, y_D\right)\right\}_{D\in \D}\right)$ be another cocone on $F$.
-In particular, $\left(X, \left\{x_D\right\}_{D\in \D}\right)$ and $\left(Y, \left\{y_D\right\}_{D\in \D}\right)$ are cocones on $U_L\circ F$ and $U_R\circ F$ respectively, so we have uniquely determined arrows $x\colon A\rightarrow X$ and $y\colon B\rightarrow Y$ such that
-	\[x\circ a_D= x_D \qquad y\circ b_D= y_D\]
-	Let us show that $(x,y)$ is an arrow of $\comma{L}{R}$. Given $D\in \D$ we have
-	\begin{align*}
-		&R(y)\circ f\circ L(a_D)=R(y)\circ R\left(b_D\right)\circ f_D=R\left(y\circ b_D\right)\circ f_D\\=&R\left(y_D\right)\circ f_D= g\circ L\left(x_D\right)=g\circ L\left(x\circ a_D\right)=g\circ L(x)\circ L\left(a_D\right)
-	\end{align*}
-	from which it follows  that $g\circ L(x)=R(y)\circ f$ as wanted.
-\end{proof}
-
-\Cref{prop:dual} and \Cref{colim} now yields the following.
-\begin{corollary}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ F$.
-\end{corollary}
-
-We can use \Cref{lim} to characterize monos in comma categories. 
-\begin{corollary}\label[corollary]{cor:mono}
-	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comma{L}{R}$ is mono if and only if both $h$ and $k$ are monos.
-\end{corollary}
-\begin{proof}
-	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the first rectangle below is a pullback in $\comma{L}{R}$.
-By \Cref{lim} then also the other two squares are pullbacks, respectively in $\A$ and $\B$, proving that both $h$ and $k$ are monos.
-	\[\xymatrix{(A, B, f)  \ar[rr]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}&& (A, B, f)  \ar[d]^{(h,k)}& A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ (A, B, f)  \ar[rr]_{(h,k)}&& (A', B', g) &A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
-
-	\smallskip\noindent 
-	\parbox{4cm}{ \xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}}\hfill \parbox{8.5cm}{$(\Leftarrow)$ Since $h$ and $k$ are monos then we have the two pullback squares on the left.
-Thus by \Cref{lim} the pullback of $(h,k)$ along itself has isomorphisms as projections and so $(h,k)$ is mono.
-\qedhere}
-
-\end{proof}
-
-We end this section pointing out another useful fact,  showing that in some cases we can guarantee  the existence of a left adjoint to $U_R$.
-
-\begin{proposition}\label[proposition]{prop:left}
-	If $\A$ has initial objects and $L$ preserves them then the forgetful functor $U_R\colon \comma{L}{R}\to \B$ has a left adjoint $\Delta$.
-\end{proposition}
-\begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{R(B)})$, for $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
-Let $\id{B}\colon B\to U_R(\Delta(B))$ be the identity,
-
-	\noindent 
-	\parbox{10cm}{and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given. By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, 
-	since $L$ preserves initial objects, the square aside commutes. Thus $(?_A,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$ such that $U_R(?_A,k)=k$. }\hfill 
-	\parbox{2cm}{\vspace{-.1cm}\xymatrix@C=30pt@R=15pt{L(0) \ar[r]_{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]^{R(k)}& R(B')}}  
-\end{proof}
-Dualizing we get immediately the following.
-\begin{corollary}If $\B$ has terminal objects preserved by $R$ then $U_L\colon \comma{L}{R}\to \A$ has a right adjoint.
-\end{corollary}
-
-\subsection{Slice categories}
-
-This section is devoted to recall some basic facts about the so called \emph{slice categories}.
-\begin{definition}\index{category!slice -}
-	Let $X$ be an object of a category $\X$. We define the following two categories.
-
-	\noindent 
-	\parbox{11cm}{\vspace{-.5cm}\begin{itemize}
-		\item The \emph{ slice category over $X$} is the category $\X/X$ which has as objects arrows $f\colon Y\to X$ and  in which an arrow $h\colon f\to g$ is $h\colon Y\to Y'$ in $\X$ such that the triangle on the right commutes.
-		\item  	 Dually, the \emph{ slice category under $X$} is the category $X/\X$ in which objects are arrows $f\colon X\to Y$  with domain $X$ and a morphism $h\colon  f\to g$ is an arrow of $\X$ fitting in a triangle as the one aside.
-	\end{itemize}} \hfill \parbox{2cm}{\vspace{-0cm}\xymatrix@C=15pt@R=15pt{Y \ar[dr]_{f} \ar[rr]^{h}&& Y' \ar[dl]^{g}\\ & X} \xymatrix@C=15pt@R=15pt{&X \ar[dr]^{g}\ar[dl]_{f}\\ Y  \ar[rr]_{h}&& Y'}}
-\end{definition}
-
-\begin{remark} For every $X\in\ X$ we have forgetful functors
-	\[\begin{split}
-		\dom_X&\colon \X/X\to \X\\
-		\functor[l]{f}{h}{g}
-		&\functormapsto
-		\rfunctor{\dom(f) }{h}{\dom(g)}
-	\end{split}\qquad \begin{split}
-		\cod_X&\colon X/\X\to \X\\
-		\functor[l]{f}{h}{g}
-		&\functormapsto
-		\rfunctor{\cod(f) }{h}{\cod(g)}
-	\end{split}\]
-\end{remark}
-
-We can realize the slice over and under an object $X\in \X$ as comma categories.
-
-\begin{proposition}\label[proposition]{prop:commaapp}
-	For every object $X$ in a category $\X$, if $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object $*$, then $\X/X$ and $X/\X$ are isomorphic to, respectively,  $\comma{\id{X}}{\delta_X}$ and $\comma{\delta_X}{\id{X}}$ .
-\end{proposition}
-\begin{proof} Define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows
-	\[	\begin{split}
-		\functor[l]{(Y, *,  f)}{(h, \id{*} )}{( Y', *,  g)}
-		\functormapsto
-		\rfunctor{f }{h}{g}
-	\end{split} \qquad \begin{split}
-		\functor[l]{f }{h}{g}
-		\functormapsto
-		\rfunctor{(\dom(f), *, f)}{(h, \id{*} )}{(\dom(g), *, g)}
-	\end{split}\]
-	Similarly, we have $F_2\colon \comma{\delta_X}{\id{X}}\to X/\X$ and $G_2\colon X/\X\to \comma{\delta_X}{\id{X}}$
-	\[	\begin{split}
-		\functor[l]{(*, Y, f)}{(\id{*},h )}{(*, Y', g)}
-		\functormapsto
-		\rfunctor{f }{h}{g}
-	\end{split} \qquad \begin{split}
-		\functor[l]{f }{h}{g}
-		\functormapsto
-		\rfunctor{(*, \cod(f), f)}{(\id{*}, h )}{(*, \cod(g), g)}
-	\end{split}\]
-	It is now obvious to see that $F_1,G_1$ and $F_2, G_2$ are pairs of inverses.   
-\end{proof}
-
-A straightforward application of \Cref{lim,colim} now yields the following.
-\begin{corollary}\label[corollary]{cor:pbapp}
-For every object $\X$, $\X/X$ has all colimits and connected limits that $\X$ has. Moreover such limits and colimits are created by $\dom_X$.
-
-In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$, the slice $\X/X$ has such limits and colimits.
-\end{corollary}
-
-\iffalse
-\todo{Tutta la parte qua sotto non mi è chiaro a cosa serva}
-In a category $\cat X$ with pullbacks, each $f: X \to Y$ induces a functor $f^*: \cat X/Y \to \cat X/X$,
-which sends each morphism $a: A \to Y$ of $\cat X$ onto its pullback along $f$, $p_a$, and each morphism $h: a \to b$ onto the unique arrow from the pullback of $a$ along $f$ to the pullback of $b$ along $f$.
-
-Then, we have the following result.
-
-\begin{proposition}
-	Let $\cat X$ be a category with pullbacks, $R: \cat{Y \to X}$ be a functor and $L: \cat{X \to Y}$ be its left adjoint, and $\eta$ the unit of the adjunction.
-	Then, each object $X$ of $\cat X$ induces an adjoint pair of functors $L_X: \cat X/X \to \cat Y/L(X)$, $R_X: \cat Y/L(X) \to \cat X/X$, 
-	where $L_X$ is the obvious functor, and $R_X$ is the composite $(\eta_X)^* \circ R$.
-\end{proposition}
-
-\begin{proof}
-	Let $f: L(l) \to b$ be a morphism of $\cat Y/L(X)$, where $l: A \to X$ in $\cat X$ and $b: B \to L(X)$ in $\cat Y$, as shown below.
-	\[\xymatrix{L(A)\ar[rr]^{f}\ar[dr]_{L(l)}&&B\ar[dl]_{b}\\&L(X)}\]
-	Then, we have the following situation in $\cat X$.
-	\[\xymatrix{
-			A \ar[rr]^{\eta_A}\ar[dr]_{l} \ar@/^2.0pc/@[black][rrrr]^{g} && R(L(A)) \ar[rr]^{R(f)} \ar[dr]_{R(L(l))} && R(B) \ar[dl]^{R(b)}\\
-						      & X \ar[rr]_{\eta_X} && R(L(X))
-	}\]
-	Where $g$ is the adjunct of $f$.
-	Consider now the pullback $P$ of $R(p)$ along $\eta_X$, as shown below.
-	\[\xymatrix{
-		A \ar@/^1.0pc/[drr]^{g}\ar@/_2.0pc/[ddr]_{l} \ar@{.>}[dr]^{v}\\&P\ar[r]^{q}\ar[d]_{\eta_X^*(R(b))}&R(B)\ar[d]^{R(b)}\\&X \ar[r]_{\eta_X}&R(L(X))
-	}\]
-	By universal property of pullbacks, the two diagrams express the same morphism $g$.
-	Hence, we can rewrite the first diagram as follows.
-	\[\xymatrix{
-			L(A)\ar[r]^{L(g)}\ar[d]_{L(l)}\ar@/^2.0pc/[rr]^{f}&(L(R(B)))\ar[d]_{L(R(b))}\ar[r]^{\epsilon_B}&B\ar[d]^{b}\\
-			L(X)\ar[r]_{L(\eta_X)}\ar@/_2.0pc/[rr]_{\id{L(X)}}&L(R(L(X)))\ar[r]_{\epsilon_{L(X)}}& L(X)
-	}\]
-	where $\epsilon$ is the counit of the adjunction.
-	This descriveb the action of functors and thus the adjunction, obtained considering the isomorphism on hom-sets of the categories.
-
-\end{proof}
-\fi
-
-%\section{Comparison with Ghica}
-%\todo{Lo vogliamo fare?}
-
-\end{document}

### 2025-06-14 calco/presentazione/pres.tex
presentazione

\documentclass{beamer}
\usepackage{beamer}
\usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{ragged2e}
\usepackage{xcolor}
\colorlet{shaded}{gray!40}

\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows.meta,arrows}
\usepackage[draft]{tikzit}
\input{hypergraph.tikzdefs}
\input{hypergraph.tikzstyles}
\usetikzlibrary{decorations.markings}
\usepackage[all, cmtip]{xy}
\usepackage{svg}

%%% Bibliography
\usepackage[style=numeric,backend=bibtex]{biblatex}
\addbibresource{biblio.bib}
\renewcommand*{\bibfont}{\footnotesize}

% default color is dark

\def\colortheme{dark} % preset themes available are lighten, light, dark
\def\alertcolor{dark} % preset themes available are lighten, light, dark
\def\upperbar{\true} % i want upper index/navigation bar, \true or \false
\def\bottomsectionbar{\true} % i want bottom bar with Title and Frame/Slide number, \true or \false
\def\bottomtitlebar{\false} % i want bottom bar with Section and Institute, \true or \false

% % %
\if\upperbar\false
    \setbeamertemplate{headline}{}
\fi
% % %

\newcommand{\catname}[1]{\textbf{\textup{#1}}}
\newcommand{\tg}[0]{\catname{TG}_{\Sigma}}
\newcommand{\eg}{\catname{EGG}}
\newcommand{\egg}{\mathsf{e}\text{-}\catname{EqHyp}}
\newcommand{\hyp}{\catname{Hyp}}
\newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
\newcommand{\EqHyp}{\catname{EqHyp}} %equivalence hypergraphs
\newcommand{\EqHyps}{\catname{EqHyp}_{\Sigma}}
\newcommand{\EqTG}{\catname{EqTG}}
\newcommand{\EqTGs}{\catname{EqTG}_{\Sigma}}
\newcommand{\eto}{\twoheadrightarrow}
\newcommand{\mto}{\rightarrowtail}

\newcommand{\pbc}{\mathsf{Pb}}
\newcommand{\pbe}{\mathsf{ePb}}

\title{EGGs are adhesive!}
%\subtitle{Subtitle}
\author{R. Biondo, \textbf{D. Castelnovo} and F. Gadducci}
\institute
{
  University of Pisa
}
\date{Glasgow, \today}

\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\def\D{\textbf {\textup{D}}}

\newenvironment{noheadlineframe}
{%
	\setbeamertemplate{headline}{}%
	\begin{frame}
	}
	{%
	\end{frame}
}

\begin{document}

\firstpage % optional. First page

%\indexoverview % optional. Make a slide with index

\section{Intro: EGGs}\justifying

%\sectionoverview % optional. Make a slide with section structure index

\begin{frame}{What are EGGs?} % normal itemize, one frame

    \emph{e-graphs (EGGS)} \cite{DetlefsNS05,WillseyNWFTP21} are a graphical formalism  for program optimisation  via an efficient implementation of equality saturation.

    \pause \medskip

     They can be  defined as (acyclic) term graphs \cite{corradini2005term,Plu:TGR-ENTCS} with an additional notion of  equivalence on nodes that is closed under the operators of the signature.

     \pause \medskip The idea is that nodes representing the same term should be in the same equivalence class. \pause

     \begin{center}
     	\hspace{.25cm}
     		\begin{tikzpicture}[baseline=(nil.center)]\begin{pgfonlayer}{nodelayer}
     				\node[style=node](v1) at (-0.9, 0.3){};
     				\node[style=node](v2) at (-0.9, -0.3){};
     				\node[style=medium box] at (0, 0){$/$};
     				\node[style=none](divfst) at (-0.3, 0.3){};
     				\node[style=none](divsnd) at (-0.3, -0.3){};
     				\node[style=none](divout) at (0.3, 0){};
     				\node[style=node] (w) at (0.9, 0){};
     				\node[style=small box] at (0, -1){$1$};
     				\node[style=none](one) at (0.3, -1){};
     				\node[style=node](z) at (0.9, -1){};
     				\node[style=none](nil) at (0, -0.5){};
     			\end{pgfonlayer}        
     			\begin{pgfonlayer}{edgelayer}
     				\draw(v1) to (divfst.center);
     				\draw(v2) to (divsnd.center);
     				\draw(divout.center) to (w);
     				\draw(one.center) to (z);
     			\end{pgfonlayer}
     			\begin{pgfonlayer}{eqlayer}
     				\draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
     				\draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
     			\end{pgfonlayer}\begin{pgfonlayer}{background}
     				\draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
     		\end{pgfonlayer}\end{tikzpicture}
     \end{center}
\end{frame}

\begin{frame}{Aims of this work} 
    \begin{itemize}
        \item Formalize the definition of EGGs in a categorical setting and study their properties. \pause \medskip 
        \item Develop the theory of EGGs rewriting using the Double Pushout (DPO) paradigm \cite{ehrig2006fundamentals,ehrig1999handbook}.
    \end{itemize}
\end{frame}

\section{DPO rewriting}

\begin{frame}{DPO rewriting systems} 
	\begin{overprint}

		\onslide<1|handout:1>

		A \emph{DPO-rewriting rule} is a pair of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		\onslide<2| handout:0>

	A \emph{DPO-rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		\medskip
		First: find a \emph{match} $m:L\to G$.
		\begin{center}
			\begin{tikzpicture}
				\node(L)at(0,0){$L$};
				\node(K)at(2,0){$K$};
				\node(R)at(4,0){$R$};
				\node(G)at(0,-2){$G$};
				\draw[->](K)--(L)node[pos=0.5, above]{$l$};
				\draw[->](K)--(R)node[pos=0.5, above]{$r$};
				\draw[->, dotted](L)--(G)node[pos=0.5, left]{$m$};
			\end{tikzpicture}
		\end{center}

		\onslide<3| handout:0>

		A \emph{DPO-rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		\medskip
		Second: ``remove'' the image of $m$  building a pushout square. \vspace{-0.075cm}
		\begin{center}
			\begin{tikzpicture}
				\node(L)at(0,0){$L$};
				\node(K)at(2,0){$K$};
				\node(R)at(4,0){$R$};
				\node(G)at(0,-2){$G$};
				\node(C)at(2,-2){$C$};
				\draw[->](K)--(L)node[pos=0.5, above]{$l$};
				\draw[->](K)--(R)node[pos=0.5, above]{$r$};
				\draw[->](L)--(G)node[pos=0.5, left]{$m$};
				\draw[->, dotted](K)--(C)node[pos=0.5, right]{$p$};
				\draw[->, dotted](C)--(G)node[pos=0.5, below]{$l'$};
			\end{tikzpicture}
		\end{center}		
		\onslide<4| handout:0>

	A \emph{DPO-rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		\medskip
		Third: glue $R$ into the ``hole'',  taking a pushout.\vspace{-0.075cm}
		\begin{center}\hspace{0.08cm}
			\begin{tikzpicture}
				\node(L)at(0,0){$L$};
				\node(K)at(2,0){$K$};
				\node(R)at(4,0){$R$};
				\node(G)at(0,-2){$G$};
				\node(C)at(2,-2){$C$};
				\node(H)at(4,-2){$H$};
				\draw[->](K)--(L)node[pos=0.5, above]{$l$};
				\draw[->](K)--(R)node[pos=0.5, above]{$r$};
				\draw[->](L)--(G)node[pos=0.5, left]{$m$};
				\draw[->](K)--(C)node[pos=0.5, right]{$p$};
				\draw[->](C)--(G)node[pos=0.5, below]{$l'$};
				\draw[->, dotted ](C)--(H)node[pos=0.5, below]{$r'$};
				\draw[->, dotted ](R)--(H)node[pos=0.5, right]{$q$};
			\end{tikzpicture}
		\end{center}		
	\end{overprint}  	
\end{frame}

\begin{frame}{$\mathcal{M}$-adhesive categories}
	The categorical framework for DPO rewriting is given by \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2014adhesive, lack2005adhesive}.

		\medskip \pause
		Let $\mathcal{M}$ be a class of monos in a category $\X$, containing all isomorphisms, stable under pullbacks and composition. $\X$ is \emph{$\mathcal{M}$-adhesive} if, given a cube below with the hooked arrows in $\mathcal{M}$, the bottom face a pushout and the back faces pullbacks, we have:

		\parbox{5cm}{\centering \begin{tikzpicture}
				\node(C)at(-1,0.4){$C$};
				\node(A)at(1,0.8){$A$};
				\node(B)at(2,0.4){$B$};
				\node(D)at(0,0){$D$};
				\node(A')at(1,2){$A'$};
				\node(B')at(2,1.6){$B'$};
				\node(C')at(-1,1.6){$C'$};
				\node(D')at(0,1.2){$D'$};
				\draw[<-](B')--(A');
				\draw[>->](B')--(B);
				\draw[>->](C')--(C); 
				\draw[>->](D')--(D);
				\draw[->](A')--(C'); 
				\draw[->](B')--(D');
				\draw[->](C')--(D');
				\draw[->](A)--(B);
				\draw[->](C)--(D);
				\draw[->](B)--(D);
				\draw[>-](A')--(1,1.45);
				\draw[->](1,1.35)--(A);
				\draw[>-](A)--(0.05, 0.61);
				\draw[<-](C)--(-0.05,0.59);
		\end{tikzpicture}} \quad 	\parbox{4cm}{\centering
			Top face is a pushout \\ $\iff$ \\ Front faces are pullbacks}

\end{frame}

\begin{frame}

$\mathcal{M}$-adhesivity is preserved by common categorical constructions:\pause
\begin{itemize}
	\item products\pause 
	\item functor categories \pause
	\item slices and coslices
\end{itemize}

\pause

Moreover, a full subcategory closed under the relevant pullbacks and pushouts inherits the adhesivity properties of the bigger one.
\end{frame}

\section{Hypergraphical structures }

\begin{frame}{Hypergraphs}

A hypergraph is a 4-uple $(E, V, s, t)$ made by two sets $E$ and $V$ (\emph{edges} and \emph{nodes}) and arrows $s, t\colon E \rightrightarrows V^\star$. \pause A \emph{hypergraph morphism} $(E, V, s, t)\to (F, W, s,' t')$  is a pair of arrow $h\colon E\to E'$ and $k\colon V\to V'$ fitting in the digram below.

	\[\xymatrix{ E \ar[r]^{h}\ar[d]_{s}& F \ar[d]^{s'} & E \ar[r]^{k} \ar[d]_{t}& F\ar[d]^{t'}\\ V^\star\ar[r]_{k^\star}& W^\star & V^\star \ar[r]_{k^\star}&W^\star}\]

	\pause 
\begin{theorem}
	The category $\hyp$ of hypergraphs is adhesive.
\end{theorem}

\end{frame}

\begin{frame}{Labelling  hypergraphs}

	\parbox{.5\linewidth}{Given an algebraic signature $\Sigma$ one can build an hypergraph $\mathcal{G}_\Sigma$ with a single node and edges corresponding with operations of $\Sigma$.} \hfill
		\begin{minipage}[r]{.4\linewidth}
			\begin{tikzpicture}
				\begin{pgfonlayer}{nodelayer}
					\node[style=node] (v) at (0, 0){};
					\node[style=none] (vlab) at (0, -0.4){$v$};

					\node[style=small box] (n) at (1.8, 0) {};
					\node[style=none] (nlab) at (2.4, 0.0) {$1$};
					\node[style=none] (nattach) at (1.6, 0) {};

					\node[style=medium box] (times) at (-1, 1.8) {};
					\node[style=none] (timeslab) at (-1, 2.6) {$\cdot$};
					\node[style=none] (timesin1) at (-1.2, 1.25) {};
					\node[style=none] (timesin2) at (-0.8, 1.25) {};
					\node[style=none] (timesout) at (-0.8, 1.8){};

					\node[style=medium box] (div) at (1, 1.8) {};
					\node[style=none] (divlab) at (1, 2.6) {$(-)^{-1}$};
					\node[style=none] (divin1) at (0.8, 1.25) {};
					\node[style=none] (divin2) at (1.2, 1.25) {};
					\node[style=none] (divout) at (0.8, 1.8){};
				\end{pgfonlayer}

				\begin{pgfonlayer}{edgelayer}
					\draw[style=diredge, in=270, out= 160] (v) to (timesin2.center); 
					\draw[style=diredge,out=200, in= 270] (v) to (timesin1.center);
					\draw[style=diredge,in=0, out=0] (nattach.center) to (v);

					\draw[style=diredge,in=270, out=20] (v) to (divin2.center); 
					\draw[style=diredge,out=60, in= 270] (v) to (divin1.center);

					\draw[style=diredge, in=120, out=0] (timesout.center) to (v);
					\draw[style=diredge, in=90, out=180] (divout.center) to (v);
				\end{pgfonlayer}

			\end{tikzpicture}
		\end{minipage}
	\pause

	\medskip 
	The category $\hyp_{\Sigma}$ of \emph{labelled hypergraphs} is the slice $\hyp/\mathcal{G}_\Sigma$.

	\pause 
	\begin{theorem}
		 \hspace{1pt}$\hyp_\Sigma$ is adhesive.
	\end{theorem}	
\end{frame}

\begin{frame}{Term graphs}
A \emph{term graph} \cite{corradini2005term,corradini1997algebraic, Plu:TGR-ENTCS} is a labelled hypergraphs with injective target function. $\tg$ is be the full subcategory of $\hyp_{\Sigma}$ given by them.

\pause 
\begin{itemize}
	\item monos in $\tg$ are morphism which are injective on both edges and nodes;\pause 
	\item regular monos in $\tg$ are monos which preserves \emph{input nodes}, i.e.~nodes not in the image of the target functions.
\end{itemize}
\pause

\begin{theorem}
$\tg$ is quasiadhesive.
\end{theorem}

\end{frame}

\begin{frame}

	Summing up:

	\[\xymatrix@R=15pt@C=15pt{ \color{shaded}\eg \ar@{^{(}->}@[shaded][r]^-{\color{shaded}Y_\Sigma} \ar@{^{(}->}@[shaded][d]_{\color{shaded}K_\Sigma} & \color{shaded}\egg_\Sigma \ar@{^{(}->}@[shaded][d]_{\color{shaded} Z_\Sigma} \ar@[shaded][r]^{\color{shaded}W_\Sigma}&\color{shaded} \egg \ar@{^{(}->}@[shaded][d]^{\color{shaded}I}\\ \color{shaded}\EqTG_{\Sigma} \ar@{^{(}->}@[shaded][r]^{\color{shaded}J_\Sigma}\ar@[shaded][d]_{\color{shaded}S_\Sigma}&\color{shaded} \EqHyp_\Sigma \ar@[shaded][r]^{\color{shaded}V_\Sigma} \ar@[shaded][d]_{\color{shaded}T_\Sigma}&\color{shaded} \EqHyp \ar@[shaded][d]^{\color{shaded}T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}\]

\end{frame}

\section{Adding equivalences}

\begin{frame}{Hypergraphs with equivalence}

A \emph{(labelled) hypergraph/term graph} is a (labelled) hypergraph/term graph equipped with a surjection $q\colon V\eto Q$ from the set of nodes. \pause

We get categories $\EqHyp$, $\EqHyps$ and  $\EqTG_{\Sigma}$ asking that the nodes part of a morpism induces a mrphism between the quotients. 
\[\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{k}& W \ar@{>>}[d]^p\\ Q \ar@{.>}[r]_{u} & P }\]

\pause

\begin{block}{Remark}\justifying
$\EqHyps$ is actually the slice over $\mathcal{G}_\Sigma$ endowed with the only possible quotient from $1$. $ \EqTG_{\Sigma}$ is a full subcategory of $\EqHyps$.
\end{block}
\end{frame}

\begin{frame}{Limits and colimits in $\EqHyp$}
	Colimits are computed componentwise. If $(E_d, V_d, Q_d, s_d, t_d, q_d )$ is a diagram of hypergraphs with equivalence, then a colimit is given by $(E, V, Q, s, t, q)$, where $E$, $V$, $Q$ are the colimits of $\{E_d\}_{d\in \D}$, $\{V_d\}_{d\in \D}$, $\{Q_d\}_{d\in \D}$ and $s, t, q$ are the natural ones.

	\pause  \medskip 
	\begin{minipage}[l]{0.45\linewidth}
		Limits are more difficult. In the example on the right, the pullback of the underlying hypergraphs gives us the empty one. The pullback of quotients is the singleton.
	\end{minipage} \qquad 
\begin{minipage}[r]{0.6\linewidth}
	\xymatrix{
		 &
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v) at (0, 0){};
				\node[style=none] at(0, 0.5){$c$};
			\end{pgfonlayer}
			\begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
		\end{tikzpicture}  \ar@{>->}@(d,)[d]!<0ex,0ex> \\ 
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(0, 0){};
				\node[style=none]at(0, 0.5){$b$};
			\end{pgfonlayer}
			\begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
		\end{tikzpicture}
		\ar@{>->}@(r,)@<-.5ex>[r] & 
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(-0.5, 0){};
				\node[style=none]at(-0.5, 0.5){$b$};
				\node[style=node]at(0.5, 0){};
				\node[style=none]at(0.5, 0.5){$c$};
			\end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
				\draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
		\end{pgfonlayer}\end{tikzpicture}
		 }
	\end{minipage}
\end{frame}

\begin{frame}{Limits and colimits in $\EqHyp$}

Luckily in $\catname{Set}$ we can factor any arrow as a surjection followed by an injection.

\pause 
General recipe for limits: \pause

\begin{enumerate}
	\item compute the limit $(E, V, s,t)$ of the underlying hypergraphs; \pause 
	\item compute the limit $L$ of the family of quotients; \pause 
	\item factor the natural arrow $V\to L$ as $V\eto Q \mto L$; \pause 
	\item $(E, V, Q, s,t, q )$ is a colimit for the original diagram, where $q\colon V\eto Q$.
\end{enumerate}

\end{frame}

\begin{frame}{Hypergraphs with equivalence - adhesivity}

Pushouts along regular monos in $\EqHyp$ are not stable.

\begin{center}
	\xymatrix@C=10pt@R=6pt{
		&\emptyset \ar@{>->}[dd]|\hole \ar@{>->}[rr] \ar@{>->}@(dl,)[dl] &&
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v) at (0, 0){};
				\node[style=none] at(0, 0.5){$c$};
			\end{pgfonlayer}
			\begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
		\end{tikzpicture} \ar@{>->}[dd] \ar@{>->}@(dl,)[dl]!<6ex,0ex> \\
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(0, 0){};
				\node[style=none]at(0, 0.5){$b$};
			\end{pgfonlayer}
			\begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
		\end{tikzpicture}
		\ar@{>->}[dd]\ar@{>->}[rr] & &
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(-0.5, 0){};
				\node[style=none]at(-0.5, 0.5){$b$};
				\node[style=node]at(0.5, 0){};
				\node[style=none]at(0.5, 0.5){$c$};
			\end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
				\draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
		\end{pgfonlayer}\end{tikzpicture}
		\ar@<2ex>@{>->}[dd]\\&
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(0, 0){};
				\node[style=none]at(0, 0.5){$a$};
			\end{pgfonlayer}
			\begin{pgfonlayer}{eqlayer}\draw[dashed, rounded corners] (-0.3, -0.3) rectangle (0.3, 0.3);\end{pgfonlayer}
		\end{tikzpicture}
		\ar@{>->}[rr]|\hole \ar@{>->}@(dl,)[dl] && 
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(-0.5, 0){};
				\node[style=none]at(-0.5, 0.5){$a$};
				\node[style=node]at(0.5, 0){};
				\node[style=none]at(0.5, 0.5){$c$};
			\end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
				\draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
		\end{pgfonlayer}\end{tikzpicture}
		\ar@{>->}@(,r)[dl] \\
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(-0.5, 0){};
				\node[style=none]at(-0.5, 0.5){$a$};
				\node[style=node]at(0.5, 0){};
				\node[style=none]at(0.5, 0.5){$b$};
			\end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
				\draw[dashed, rounded corners](-0.8, 0.3) rectangle (0.8, -0.3);
		\end{pgfonlayer}\end{tikzpicture}
		\ar@{>->}[rr] & & 
		\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
				\node[style=node](v)at(0, 0){};
				\node[style=none]at(0, 0.5){$a$};
				\node[style=node]at(1, 0){};
				\node[style=none]at(1, 0.5){$b$};
				\node[style=node]at(2, 0){};
				\node[style=none]at(2, 0.5){$c$};
			\end{pgfonlayer}\begin{pgfonlayer}{eqlayer}
				\draw[dashed, rounded corners](-.3, 0.3) rectangle (2.3, -0.3);
	\end{pgfonlayer}\end{tikzpicture} }
\end{center}
\end{frame}

\begin{frame}{Hypergraphs with equivalence - adhesivity}
	\begin{minipage}[l]{.6\linewidth}
		We can find another class to test for adhesivity. Let $\pbc$ be the class of monos of $\EqHyp$ such that the square aside is a pullback.
	\end{minipage}\qquad 
	\begin{minipage}{.3\linewidth}
	\xymatrix{V \ar@{>>}[d]_{q} \ar@{>->}[r]^{k}& W \ar@{>>}[d]^p\\ Q \ar@{>->}[r]_{u} & P }
	\end{minipage}
	\pause

	\begin{theorem}
		$\EqHyp$ is $\pbc$-adhesive.
	\end{theorem}
\end{frame}

\begin{frame}{Adhesivity of $\EqHyp_\Sigma$ and $\EqTG_{\Sigma}$}
	In the same way can define a labelled analog $\pbc_\Sigma$ of $\pbc$.
	\pause 
	\begin{theorem}
		$\EqHyp_\Sigma$ is $\pbc_\Sigma$-adhesive.
	\end{theorem}

	\pause 
	For term graph, we can consider the class $\mathcal{T}$ of arrows which are in $\pbc_\Sigma$ and whose underlying term graph morphism is a regular mono.

	\pause 
	\begin{theorem}
		$\EqTG_{\Sigma}$ is $\mathcal{T}$-adhesive.
	\end{theorem}

\end{frame}

\begin{frame}

	Summing up:

	\[\xymatrix@R=15pt@C=15pt{ \color{shaded}\eg \ar@{^{(}->}@[shaded][r]^-{\color{shaded}Y_\Sigma} \ar@{^{(}->}@[shaded][d]_{\color{shaded}K_\Sigma} & \color{shaded}\egg_\Sigma \ar@{^{(}->}@[shaded][d]_{\color{shaded} Z_\Sigma} \ar@[shaded][r]^{\color{shaded}W_\Sigma}&\color{shaded} \egg \ar@{^{(}->}@[shaded][d]^{\color{shaded}I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]^{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]^{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]^{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}\]

\end{frame}

\section{Congruences}

\begin{frame}{Congruences}

General equivalence relations are not enough. We want to restrict our attention to \emph{congruences}: whenever the relation identifies the source of two hyperedges, it identifies their targets too.

\pause

\begin{definition}\justifying 
	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
We will say that $\mathcal{G}$ is an \emph{e-hypergraph} if $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
\end{definition}

	\pause 
	Restricting to e-hypergraphs we get: \pause 
\begin{itemize}\justifying
	\item $\egg$: full subcategory of e-hypergraphs; \pause 
	\item $\egg_\Sigma$: the subcategory of $\EqHyp_\Sigma$ whose underlying hypergraph is in $\egg$, it is actually a slice of $\egg$; \pause 
	\item $\eg$: the category of \emph{eggs}: term graphs with equivalence lying in $\egg_\Sigma$.
\end{itemize}

\end{frame}

\begin{frame}{(labelled) e-hypergraphs and EGGs }
	Let now $\pbe$, $\pbe_\Sigma$ and $\mathcal{T}_\Sigma$ be the restriction of $\pbc$, $\pbc_\Sigma$ and $\mathcal{T}$ to the suitable subcategories of e-hypergraphs.

	\pause 
	\begin{theorem}
	$\egg$ is $\pbe$-adhesive, $\egg_\Sigma$ is $\pbe_\Sigma$-adhesive and $\eg$ is $\mathcal{T}$-adhesive
	\end{theorem}
\end{frame}

\begin{frame}

	Summing up:

	\[\xymatrix@R=15pt@C=15pt{ \eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]_{ Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]^{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]^{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]^{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}\]

\end{frame}

\section{Conclusions}
\begin{frame}{Future works and questions.}

Exploit features of the DPO paradigma (e.g.~parallelism, causality) in the context of EGGs update.\pause

\medskip How far can we move way from $\catname{Set}$?\pause 
\begin{itemize}
	\item Edges and nodes can be taken from a suitable category.   
	\item Combine various categorical construction to add features to EGGs (e.g.~hierarchy of edges) while retaining adhesivity.
\end{itemize}
\end{frame}

\begin{noheadlineframe}
	\huge
	Thank you for your attention!
\end{noheadlineframe}

\appendix 
\begin{noheadlineframe}[allowframebreaks]
	\frametitle{Bibliography}
	\printbibliography		
\end{noheadlineframe}

\end{document}

### 2025-06-15 calco/presentazione/pres.tex
minori

@@
-\documentclass{beamer}
+\documentclass[aspectratio=169]{beamer}
 \usepackage{beamer}
@@
 
-    \emph{e-graphs (EGGS)} \cite{DetlefsNS05,WillseyNWFTP21} are a graphical formalism  for program optimisation  via an efficient implementation of equality saturation.
+    \emph{E-graphs (EGGS)} \cite{DetlefsNS05,WillseyNWFTP21} are a graphical formalism  for program optimisation  via an efficient implementation of equality saturation.
 
@@
 \begin{frame}{$\mathcal{M}$-adhesive categories}
-	The categorical framework for DPO rewriting is given by \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2014adhesive, lack2005adhesive}.
+	A suitable categorical framework for DPO rewriting is given by the notion of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2014adhesive, lack2005adhesive}.
 
@@
 				\draw[<-](C)--(-0.05,0.59);
-		\end{tikzpicture}} \quad 	\parbox{4cm}{\centering
+		\end{tikzpicture}} \qquad 	\parbox{4cm}{\centering
 			Top face is a pushout \\ $\iff$ \\ Front faces are pullbacks}
@@
 
-A hypergraph is a 4-uple $(E, V, s, t)$ made by two sets $E$ and $V$ (\emph{edges} and \emph{nodes}) and arrows $s, t\colon E \rightrightarrows V^\star$.
+A \emph{hypergraph} is a 4-uple $(E, V, s, t)$ made by two sets $E$ and $V$ (\emph{edges} and \emph{nodes}) and arrows $s, t\colon E \rightrightarrows V^\star$.
 \pause A \emph{hypergraph morphism} $(E, V, s, t)\to (F, W, s,' t')$  is a pair of arrow $h\colon E\to E'$ and $k\colon V\to V'$ fitting in the digram below.
@@
 	\pause  \medskip 
-	\begin{minipage}[l]{0.45\linewidth}
+	\begin{minipage}[l]{0.5\linewidth}
 		Limits are more difficult. In the example on the right, the pullback of the underlying hypergraphs gives us the empty one. The pullback of quotients is the singleton.
-	\end{minipage} \qquad 
+	\end{minipage} \qquad \quad 
 \begin{minipage}[r]{0.6\linewidth}
@@
 \begin{itemize}
-	\item Edges and nodes can be taken from a suitable category.   
+	\item Edges and nodes can be taken from another suitable category.   \pause 
 	\item Combine various categorical construction to add features to EGGs (e.g.~hierarchy of edges) while retaining adhesivity.

### 2025-06-15 calco/presentazione/pres.tex
tolta biblio

@@
 
-    \emph{E-graphs (EGGS)} \cite{DetlefsNS05,WillseyNWFTP21} are a graphical formalism  for program optimisation  via an efficient implementation of equality saturation.
+    \emph{E-graphs (EGGS)} are a graphical formalism  for program optimisation  via an efficient implementation of equality saturation.
 
@@
 
-     They can be  defined as (acyclic) term graphs \cite{corradini2005term,Plu:TGR-ENTCS} with an additional notion of  equivalence on nodes that is closed under the operators of the signature.
+     They can be  defined as (acyclic) term graphs with an additional notion of  equivalence on nodes that is closed under the operators of the signature.
 
@@
         \item Formalize the definition of EGGs in a categorical setting and study their properties. \pause \medskip 
-        \item Develop the theory of EGGs rewriting using the Double Pushout (DPO) paradigm \cite{ehrig2006fundamentals,ehrig1999handbook}.
+        \item Develop the theory of EGGs rewriting using the Double Pushout (DPO) paradigm.
     \end{itemize}
@@
 \begin{frame}{$\mathcal{M}$-adhesive categories}
-	A suitable categorical framework for DPO rewriting is given by the notion of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2014adhesive, lack2005adhesive}.
-
+	A categorical framework for DPO rewriting is given by the notion of \emph{$\mathcal{M}$-adhesive categories}.
 		\medskip \pause
@@
 \begin{frame}{Term graphs}
-A \emph{term graph} \cite{corradini2005term,corradini1997algebraic, Plu:TGR-ENTCS} is a labelled hypergraphs with injective target function.
-$\tg$ is be the full subcategory of $\hyp_{\Sigma}$ given by them.
+A \emph{term graph} is a labelled hypergraphs with injective target function. $\tg$ is be the full subcategory of $\hyp_{\Sigma}$ given by them.
 

### 2025-07-03 jlamp/finalArxiv.tex
JLAMP

--- 2025-05-26 calco/finalArxiv.tex
@@
-\documentclass[a4paper,UKenglish,cleveref,pdftex,thm-restate,numberwithinsect]{lipics-v2021}
+\documentclass[a4paper,UKenglish,cleveref,pdftex,amsthm,thm-restate,numberwithinsect]{elsarticle}
 \usepackage{stmaryrd}
@@
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
+
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{remark}[theorem]{Remark}
+
+\usepackage{thmtools} 
+\usepackage{thm-restate}
+
 %\usepackage{tikz-cd}
@@
 \newcommand{\upstr}[1] { {#1}^{\uparrow }}
-\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}#2}
+\newcommand{\comm}[2]{#1\hspace{1pt} {\downarrow}#2}
 \newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}
@@
 \title{EGGs are adhesive!}
-\titlerunning{EGGs are adhesive!} %TODO optional, please use if title is longer than one line
+%\titlerunning{EGGs are adhesive!} %TODO optional, please use if title is longer than one line
 
 % Author with single affiliation.
-\author{Roberto Biondo}
-{Department of Computer Science, University of Pisa, Pisa, IT}
-{r.biondo@studenti.unipi.it}{}{}
-
-\author{Davide Castelnovo}
-{Department of Computer Science, University of Pisa, Pisa, IT}
-{castelnovod@gmail.com}
-{https://orcid.org/0000-0002-5926-5615}{}
-
-\author{Fabio Gadducci}
-{Department of Computer Science, University of Pisa, Pisa, IT}
-{fabio.gadducci@unipi.it}
-{https://orcid.org/0000-0003-0690-3051}{}
-
-\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
-
-\Copyright{Roberto Biondo and Davide Castelnovo and Fabio Gadducci} 
+\author[1]{Roberto Biondo}
+\affiliation[1]{organization={Department of Computer Science, University of Pisa},
+	addressline={},
+	city={Pisa},
+	citysep={},
+	postcode={56127},
+	state={},
+	country={Italy}}
+\ead{r.biondo@studenti.unipi.it}
+
+\author[2]{Davide Castelnovo}
+\ead{castelnovod@gmail.com}
+\ead[url]{https://orcid.org/0000-0002-5926-5615}
+\affiliation[2]{organization={Department of Computer Science, University of Pisa},
+	addressline={},
+	city={Pisa},
+	citysep={},
+	postcode={56127},
+	state={},
+	country={Italy}}
+
+\author[3]{Fabio Gadducci}
+\ead{fabio.gadducci@unipi.it}
+\ead[url]{https://orcid.org/0000-0003-0690-3051}
+\affiliation[3]{organization={Department of Computer Science, University of Pisa},
+	addressline={},
+	city={Pisa},
+	citysep={},
+	postcode={56127},
+	state={},
+	country={Italy}}
+
+%\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
+
+%\Copyright{Roberto Biondo and Davide Castelnovo and Fabio Gadducci} 
+\iffalse
+%TODO: questa roba negli argomenti
 \ccsdesc[500]{Theory of Computation~Models of computation}
@@
 
-\nolinenumbers
-
+%\nolinenumbers
+\fi
 \begin{document}
@@
 
-\vspace{-.25cm}
+%\vspace{-.25cm}
 \parbox{11cm}{\begin{itemize}
@@
 
-\vspace{-.25cm}
+%\vspace{-.25cm}
 \parbox{9.5cm}{We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
@@
 	\begin{enumerate}
-		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category, $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to \A$ one preserving $\mathcal{M}$-pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
-		\[\comma{\mathcal{N}}{\mathcal{M}}:=\{(h,k) \in \mor(\comma{L}{R}) \mid h\in \mathcal{N}, k\in \mathcal{M}\}\]
+		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category, $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to \A$ one preserving $\mathcal{M}$-pullbacks, then $\comm{L}{R}$ is (strictly) $\comm{\mathcal{N}}{\mathcal{M}}$-adhesive, where
+		\[\comm{\mathcal{N}}{\mathcal{M}}:=\{(h,k) \in \mor(\comm{L}{R}) \mid h\in \mathcal{N}, k\in \mathcal{M}\}\]
 		\item for every object $X$
@@
 \begin{proposition}\label[proposition]{prop:com}
-	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
+	$\hyp$ is isomorphic to $\comm{\id{\Set}}{\pro^\star}$
 \end{proposition}
@@
 \begin{definition}\index{category!comma -}
-	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comma{L}{R}$ is the category in which
+	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comm{L}{R}$ is the category in which
 
@@
 \end{definition} 
-We have two forgetful functors 	$U_L\colon \comma{L}{R}\to \A$ and $U_R\colon \comma{L}{R} \to \B$ given respectively by
+We have two forgetful functors 	$U_L\colon \comm{L}{R}\to \A$ and $U_R\colon \comm{L}{R} \to \B$ given respectively by
 \[
@@
 An arrow $f\colon L(A)\to R(B)$ in $\X$ is the same thing as an arrow $f\colon R^{op}(B)\to L^{op}(A)$ in $\X^{op}$.
-Thus $\comma{L}{R}$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
+Thus $\comm{L}{R}$ and $\comm{R^{op}}{L^{op}}$ have the same objects.
 Moreover, the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$.
@@
 \begin{proposition}\label[proposition]{prop:dual}
-	$(\comma{L}{R})^{op}$ is equal to	$\comma{R^{op}}{L^{op}}$, and $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
+	$(\comm{L}{R})^{op}$ is equal to	$\comm{R^{op}}{L^{op}}$, and $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
 \end{proposition}
@@
 \begin{lemma}\label[lemma]{colim}
-	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
+	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comm{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
 Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite[Sec.~5.1.3]{castelnovo2023thesis} or \cite[Sec.~2.3]{CastelnovoGM24}).
@@
 Now, let $F(D)$ be $(A_D, B_D, f_D)$,
-	then we have arrows $R(b_D)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comma{L}{R}$ and so
+	then we have arrows $R(b_D)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comm{L}{R}$ and so
 	\begin{align*}
@@
 	\hspace{15pt}Thus there exists $f\colon L(A)\rightarrow R(B)$ fitting in the diagram on the right.
-Notice that $f$ is the unique arrow in $\X$ wich makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comma{L}{R}$.
+Notice that $f$ is the unique arrow in $\X$ wich makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comm{L}{R}$.
 If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.}\hfill
@@
 	\[x\circ a_D= x_D \qquad y\circ b_D= y_D\]
-	Let us show that $(x,y)$ is an arrow of $\comma{L}{R}$. Given $D\in \D$ we have
+	Let us show that $(x,y)$ is an arrow of $\comm{L}{R}$. Given $D\in \D$ we have
 	\begin{align*}
@@
 \Cref{prop:dual} and \Cref{colim} now yields the following.
-\begin{corollary}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ F$.
+\begin{corollary}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comm{L}{R}$ such that $R$ preserves the limit of $U_R\circ F$.
 \end{corollary}
@@
 \begin{corollary}\label[corollary]{cor:mono}
-	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comma{L}{R}$ is mono if and only if both $h$ and $k$ are monos.
+	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comm{L}{R}$ is mono if and only if both $h$ and $k$ are monos.
 \end{corollary}
 \begin{proof}
-	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the first rectangle below is a pullback in $\comma{L}{R}$.
+	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the first rectangle below is a pullback in $\comm{L}{R}$.
 By \Cref{lim} then also the other two squares are pullbacks, respectively in $\A$ and $\B$, proving that both $h$ and $k$ are monos
@@
 \begin{proposition}\label[proposition]{prop:left}
-	If $\A$ has initial objects and $L$ preserves them then the forgetful functor $U_R\colon \comma{L}{R}\to \B$ has a left adjoint $\Delta$.
+	If $\A$ has initial objects and $L$ preserves them then the forgetful functor $U_R\colon \comm{L}{R}\to \B$ has a left adjoint $\Delta$.
 \end{proposition}
@@
 Dualizing we get immediately the following.
-\begin{corollary}If $\B$ has terminal objects preserved by $R$ then $U_L\colon \comma{L}{R}\to \A$ has a right adjoint.
+\begin{corollary}If $\B$ has terminal objects preserved by $R$ then $U_L\colon \comm{L}{R}\to \A$ has a right adjoint.
 \end{corollary}
@@
 \begin{proposition}\label[proposition]{prop:commaapp}
-	For every object $X$ in a category $\X$, if $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object $*$, then $\X/X$ and $X/\X$ are isomorphic to, respectively,  $\comma{\id{X}}{\delta_X}$ and $\comma{\delta_X}{\id{X}}$ .
+	For every object $X$ in a category $\X$, if $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object $*$, then $\X/X$ and $X/\X$ are isomorphic to, respectively,  $\comm{\id{X}}{\delta_X}$ and $\comm{\delta_X}{\id{X}}$ .
 \end{proposition}
@@
 \newpage
-\begin{proof} Define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows
+\begin{proof} Define functors $F_1\colon \comm{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comm{\id{X}}{\delta_X}$ as follows
 	\[	\begin{split}
@@
 	\end{split}\]
-	Similarly, we have $F_2\colon \comma{\delta_X}{\id{X}}\to X/\X$ and $G_2\colon X/\X\to \comma{\delta_X}{\id{X}}$
+	Similarly, we have $F_2\colon \comm{\delta_X}{\id{X}}\to X/\X$ and $G_2\colon X/\X\to \comm{\delta_X}{\id{X}}$
 	\[	\begin{split}

### 2025-07-03 jlamp/finalArxiv.tex
JLAMP

@@
-\documentclass[a4paper,UKenglish,cleveref,pdftex,amsthm,thm-restate,numberwithinsect]{elsarticle}
+\documentclass[a4paper,UKenglish,cleveref,pdftex,amsthm,thm-restate,numberwithinsect]{cas-sc}
 \usepackage{stmaryrd}
@@
 
-\title{EGGs are adhesive!}
-%\titlerunning{EGGs are adhesive!} %TODO optional, please use if title is longer than one line
+\title[mode=title]{EGGs are adhesive!}
+\tnotemark[1]
+
+\tnotetext[1]{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 ``Spatio-Temporal Enhancement of Neural nets for Deeply
+Hierarchical Automatised Logic'' (STENDHAL) 
+and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information'' (FM4HD).}
 
 % Author with single affiliation.
-\author[1]{Roberto Biondo}
+\author[1]{Roberto Biondo}[type=editor]
 \affiliation[1]{organization={Department of Computer Science, University of Pisa},
-	addressline={},
 	city={Pisa},
-	citysep={},
+%	citysep={},
 	postcode={56127},
-	state={},
 	country={Italy}}
@@
 
-\author[2]{Davide Castelnovo}
+\author[1]{Davide Castelnovo}[type=editor,orcid=0000-0002-5926-5615]
 \ead{castelnovod@gmail.com}
-\ead[url]{https://orcid.org/0000-0002-5926-5615}
-\affiliation[2]{organization={Department of Computer Science, University of Pisa},
-	addressline={},
-	city={Pisa},
-	citysep={},
-	postcode={56127},
-	state={},
-	country={Italy}}
-
-\author[3]{Fabio Gadducci}
+%\ead[url]{https://orcid.org/0000-0002-5926-5615}
+%\affiliation[2]{organization={Department of Computer Science, University of Pisa},
+%	addressline={},
+%	city={Pisa},
+%	citysep={},
+%	postcode={56127},
+%	state={},
+%	country={Italy}}
+
+\author[1]{Fabio Gadducci}[type=editor,orcid=0000-0003-0690-3051]
+\cormark[1]
+\fnmark[1]
 \ead{fabio.gadducci@unipi.it}
-\ead[url]{https://orcid.org/0000-0003-0690-3051}
-\affiliation[3]{organization={Department of Computer Science, University of Pisa},
-	addressline={},
-	city={Pisa},
-	citysep={},
-	postcode={56127},
-	state={},
-	country={Italy}}
+%\ead[url]{https://orcid.org/0000-0003-0690-3051}
+%\affiliation[3]{organization={Department of Computer Science, University of Pisa},
+%       addressline={},
+%       city={Pisa},
+%       citysep={},
+%       postcode={56127},
+%       state={},
+%       country={Italy}}
 
@@
 \end{abstract}
+
+\begin{keywords}
+hypergraphs \sep terms graphs \sep e-graphs \sep adhesive categories
+\end{keywords}
 

### 2025-07-03 jlamp/finalArxiv.tex
JLAMP

@@
 %\Copyright{Roberto Biondo and Davide Castelnovo and Fabio Gadducci}
+
 \iffalse
@@
 \ccsdesc[500]{Theory of Computation~Semantics and reasoning}
-
-\keywords{Hypergraphs, terms graphs, e-graphs, adhesive categories.} %TODO mandatory; please add comma-separated list of keywords
-
-\funding{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 ``Spatio-Temporal Enhancement of Neural nets for Deeply
-Hierarchical Automatised Logic'' (STENDHAL) 
-and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information'' (FM4HD).}
-
-%\nolinenumbers
 \fi
+
 \begin{document}
 
-\maketitle
-
-\begin{abstract}
+%\maketitle
+
+\begin{abstract}[S U M M A R Y]
 The use of rewriting-based visual formalisms is on the rise. 
@@
 \end{keywords}
+
+\maketitle
 

### 2025-07-07 jlamp/jlamp.tex
journal

--- 2025-05-26 calco/finalArxiv.tex
@@
-\documentclass[a4paper,UKenglish,cleveref,pdftex,thm-restate,numberwithinsect]{lipics-v2021}
+\documentclass[3p]{elsarticle}
 \usepackage{stmaryrd}
@@
 \usepackage[all, cmtip]{xy}
+\usepackage{thm-restate}
 
@@
 \newcommand{\upstr}[1] { {#1}^{\uparrow }}
-\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}#2}
+\renewcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}#2}
 \newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}
@@
 \newcommand{\Prod}{\mathlarger{\prod}}
-
-\bibliographystyle{abbrv}
 
@@
 
+%\titlerunning{EGGs are adhesive!} %TODO optional, please use if title is longer than one line
+
+%\Copyright{Roberto Biondo and Davide Castelnovo and Fabio Gadducci} 
+%\ccsdesc[500]{Theory of Computation~Models of computation}
+%\ccsdesc[500]{Theory of Computation~Semantics and reasoning}
+
+%\keywords{Hypergraphs, terms graphs, e-graphs, adhesive categories.} %TODO mandatory; please add comma-separated list of keywords
+
+%\funding{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 ``Spatio-Temporal Enhancement of Neural nets for Deeply
+%Hierarchical Automatised Logic'' (STENDHAL) 
+%and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information'' (FM4HD).}
+
+%For cleveref
+\newcommand{\renewtheorem}[1]{%
+	\expandafter\let\csname #1\endcsname\relax
+	\expandafter\let\csname c@#1\endcsname\relax
+	\expandafter\let\csname end#1\endcsname\relax
+	\newtheorem{#1}%
+}
+%\theoremstyle{plain}
+
+\renewtheorem{thm}{Theorem}[section]
+\renewtheorem{cor}[thm]{Corollary}
+\renewtheorem{lem}[thm]{Lemma}
+\renewtheorem{prop}[thm]{Proposition}
+
+\newtheorem*{pz}{Proposition $\mathbf{4.38}$}
+
+% the following environments keep the roman font:
+\theoremstyle{remark}
+\renewtheorem{rem}[thm]{Remark}
+\renewtheorem{exa}[thm]{Example}
+\newtheorem*{notaz}{Notation}
+%\newtheorem*{pz}{Proposition $4.38$}
+\theoremstyle{definition}
+\renewtheorem{defi}[thm]{Definition}
+
 \title{EGGs are adhesive!}
-\titlerunning{EGGs are adhesive!} %TODO optional, please use if title is longer than one line
-
-% Author with single affiliation.
-\author{Roberto Biondo}
-{Department of Computer Science, University of Pisa, Pisa, IT}
-{r.biondo@studenti.unipi.it}{}{}
-
-\author{Davide Castelnovo}
-{Department of Computer Science, University of Pisa, Pisa, IT}
-{castelnovod@gmail.com}
-{https://orcid.org/0000-0002-5926-5615}{}
-
-\author{Fabio Gadducci}
-{Department of Computer Science, University of Pisa, Pisa, IT}
-{fabio.gadducci@unipi.it}
-{https://orcid.org/0000-0003-0690-3051}{}
-
-\authorrunning{R.~Biondo, D.~Castelnovo, F.~Gadducci}
-
-\Copyright{Roberto Biondo and Davide Castelnovo and Fabio Gadducci} 
-\ccsdesc[500]{Theory of Computation~Models of computation}
-\ccsdesc[500]{Theory of Computation~Semantics and reasoning}
-
-\keywords{Hypergraphs, terms graphs, e-graphs, adhesive categories.} %TODO mandatory; please add comma-separated list of keywords
-
-\funding{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 ``Spatio-Temporal Enhancement of Neural nets for Deeply
-Hierarchical Automatised Logic'' (STENDHAL) 
-and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information'' (FM4HD).}
-
-\nolinenumbers
 
@@
 
-\maketitle
+\author[1]{Roberto Biondo}
+\ead{r.biondo@studenti.unipi.it}
+
+\author[1]{Davide Castelnovo\corref{cor1}%
+}
+\ead{castelnovod@gmail.com}
+%{https://orcid.org/0000-0002-5926-5615}{}
+
+\author[1]{Fabio Gadducci}
+\ead{fabio.gadducci@unipi.it}
+%{https://orcid.org/0000-0003-0690-3051}{}
+
+\cortext[cor1]{Corresponding author}
+
+\affiliation[1]{organization = {Department of Computer Science, University of Pisa},
+	addressline = {Largo B. Pontecorvo, 3},
+	postcode = {56127},
+	city = {Pisa}, 
+	country = {Italy}}
 
@@
 
+\maketitle
+
 \section{Introduction}
@@
 \noindent
-\begin{minipage}[l]{.78\linewidth}In short, following the double-pushout (DPO) approach
+\begin{minipage}[l]{.78\linewidth}
+		\setlength{\parindent}{1.5em}
+		In short, following the double-pushout (DPO) approach
 to graph transformation~\cite{CorradiniMREHL97,ehrig2006fundamentals}, 
@@
       L \ar[d]_{m}
-      & K \ar[r]^r \ar[l]_{l} \ar[d] & R \ar [d] \\
-      G & C \ar[r] \ar[l]                    & H
+      & K \ar[r]^r \ar[l]_{l} \ar[d]_{k} & R \ar [d]^h \\
+      G & C \ar[r]_{g} \ar[l]^{f}                    & H
     }
@@
   \end{minipage}
-\vspace{.1cm}
-
-\noindent
+
 Thus, $L$ and $R$ are the left- and right-hand side of the rule, respectively, while $K$ witnesses those parts that must 
@@
 %and to define it we introduce some notions.  
-Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is said to be
-
-\vspace{-.25cm}
-\parbox{11cm}{\begin{itemize}
+Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is said to be:
+
+\noindent
+\begin{minipage}[l]{.85\linewidth}
+	\begin{itemize}
 		\item		\emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one aside, if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
@@
 		\item \emph{closed under decomposition}, or \emph{left-cancellable}, if whenever $g$ and $g\circ f$ belong to $\mathcal{A}$, then $f\in \mathcal{A}$.
-\end{itemize}}\hfill
-\parbox{1cm}{
-\xymatrix{A \ar[r]^{f} \ar[d]_{m}& B \ar[d]^{n} \\ C \ar[r]_{g} & D}}
-
-	\begin{definition}
+	\end{itemize}
+\end{minipage}\hfill 
+\begin{minipage}[r]{.13\linewidth}
+\xymatrix{A \ar[r]^{f} \ar[d]_{m}& B \ar[d]^{n} \\ C \ar[r]_{g} & D}
+\end{minipage}
+
+	\begin{defi}
 	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the cube below on the right.
 
-\vspace{-.25cm}
-\parbox{9.5cm}{We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
+	\begin{minipage}[l]{.73\linewidth}
+		We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if:
 	\begin{enumerate}
@@
 		if and only if the front and right faces are pullbacks.
-	\end{enumerate}} \hfill
-	\parbox{3cm}{
+	\end{enumerate}
+\end{minipage}\hfill 
+\begin{minipage}[r]{.25\linewidth}
 	\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }
-}
+\end{minipage}
 
@@
 		Kampen} and a $\mor(\X)$-stable square  \emph{stable}.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}[\cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}]
+\begin{defi}[\cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}]
 	Let $\X$ be a category and $\mathcal{M}$ a subclass of
@@
 	if $\mathcal{M}$-pushouts are Van Kampen. We write $m\colon X \mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
-\end{definition}
-
-\begin{remark}
+\end{defi}
+
+\begin{rem}
 	\label{rem:salva} Our notion of $\mathcal{M}$-adhesive category corresponds to what in \cite{ehrig2006fundamentals} is called \emph{weak adhesive HLR category}, while a strict $\mathcal{M}$-adhesive categories corresponds to \emph{adhesive HLR} ones.
@@
 	respectively. %On the other hand
-\end{remark}
+\end{rem}
 
@@
 
-\begin{proposition}
+\begin{prop}
 	\label{thm:slice-functors}
@@
 	\end{enumerate} 
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{example}
+\begin{exa}
 	\label{ex:adhesive}
@@
 	quasiadhesive.
-\end{example}
+\end{exa}
 
 \iffalse 
-\begin{remark}\label{rem:deco}
+\begin{rem}\label{rem:deco}
 We can point out an important property of strict $\mathcal{M}$-adhesive categories with pullbacks.  Consider the solid part of the cube aside, whose bottom case is an $\mathcal{M}$-pushout.
@@
 	Clearly if the arrow $p\colon X\to D$ is in $\mathcal{M}$, we can omit the assumptions of strictness and the existence of all pullbacks.
-\end{remark}
+\end{rem}
 \fi
@@
 (see, for instance, \cite[Thm.~4.26]{ehrig2006fundamentals} or \cite[Fact 2.6]{azzi2019essence}). A proof is provided in \Cref{regmono-proof}.
-\begin{restatable}{proposition}{regmono}\label{prop:regmono}
+\begin{restatable}{prop}{regmono}\label{prop:regmono}
 	Let $\X$ be an $\mathcal{M}$-adhesive category. Then the following hold
@@
 \noindent 
-\parbox{11cm}{
-\begin{definition}
-    A \emph{kernel pair} for an arrow $f\colon A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f\colon K_f \rightrightarrows A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the square aside is a pullback.
-\end{definition}}\hfill 
-\parbox{2cm}{\xymatrix@R=15pt{K_f \ar[r]_{\pi^2_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}}
-
-\smallskip
-\begin{remark}\label{prop:pairng_of_kernel_pairs_mono}
+\begin{minipage}[l]{.85\linewidth}
+\begin{defi} A \emph{kernel pair} for an arrow $f\colon A \to B$ is an object $K_f$ together with two arrows $\pi^1_f, \pi^2_f\colon K_f \rightrightarrows A$, denoted as $(K_f, \pi^1_f, \pi^2_f)$, such that the square aside is a pullback.
+\end{defi}
+\end{minipage} \hfill 
+\begin{minipage}[r]{.18\linewidth}
+	\xymatrix@R=15pt{K_f \ar[r]_{\pi^2_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}
+\end{minipage}
+
+\begin{rem}\label{prop:pairng_of_kernel_pairs_mono}
 If $(K_f, \pi^1_f, \pi^2_f)$ is a a kernel pair for $f\colon X \to Y$ and a product of $X$ with itself exists, then the canonical arrow $\langle \pi^1_f, \pi^2_f\rangle \colon K_f \to X \times X$ is a mono.
-\end{remark}
-
-\begin{remark}\label{prop:kermono}
+\end{rem}
+
+\begin{rem}\label{prop:kermono}
 An arrow $m\colon M\to X$ is a mono if and only if it admits $(M, \id{M}, \id{M})$ as a kernel pair.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{proposition}\label{cor:kermono}
+\begin{prop}\label{cor:kermono}
 	Let $f\colon X\to Y$ be an arrow and $m\colon Y\to Z$ a mono. If
 	$(K_f, \pi_f^1, \pi_f^2)$ is a kernel pair for $f\colon X\to Y$, then it is also a kernel pair for $m\circ f$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{restatable}{proposition}{epic}\label{prop:reg_epi_coeq}
+\begin{restatable}{prop}{epic}\label{prop:reg_epi_coeq}
     Let $e\colon X \eto Y$ be a regular epi in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then, $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
@@
 \commentato{ 
-\begin{restatable}{corollary}{natepi}\label{cor:reg_epi_components_reg_epi_nat_trans}
+\begin{restatable}{cor}{natepi}\label{cor:reg_epi_components_reg_epi_nat_trans}
     Let $\X$ be a category with pullbacks and $\phi\colon F \to G$ a natural transformation between functors $F, G: \D \rightrightarrows \X$.
@@
 
-\begin{restatable}{lemma}{epicol}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
+\begin{restatable}{lem}{epicol}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
     Let $F,G\colon \D\rightrightarrows \X$ be two diagrams, and suppose that $\X$ has all colimits of shape $\D$.
@@
 
-\begin{restatable}{lemma}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
+\begin{restatable}{lem}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
 	Let $f\colon X \to Y$ and $g\colon Z \to W$ be arrows admitting kernel pairs and suppose that the solid part of the four squares below is given. 
@@
 
-%\todo{A questo punto la proposizione seguente possiamo anche buttarla via se serve recuperare spazio}
-\noindent
-\parbox{7.5cm}{
-\begin{restatable}{proposition}{mpo}\label{lem:mpo}
+\noindent
+\begin{minipage}[l]{.6\linewidth}
+\begin{restatable}{prop}{mpo}\label{lem:mpo}
 	Let $\X$ be a strict $\mathcal{M}$-adhesive category with all pullbacks, and suppose that in the cube aside the top face is an $\mathcal{M}$-pushout and all the vertical faces are pullbacks.
 Then the right square is a pushout.
-\end{restatable}}\hfill 
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+\end{restatable}
+\end{minipage}\hfill 
+\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }
+	\end{minipage}
 
@@
 Focusing on $\Set$, we can prove a sharper result (see \Cref{proof:kerset} for the proof).
-
-\noindent
-\parbox{7.5cm}{\begin{restatable}{lemma}{mps}\label{prop:kerset}
+\smallskip
+
+\noindent
+\begin{minipage}[l]{.6\linewidth}
+	\begin{restatable}{lem}{mps}\label{prop:kerset}
 		Suppose that in $\Set$ the commuting cube in the diagram on the left is given, whose top face is a pushout, the left and bottom faces are pullbacks,  and $n\colon B\mto D$ is an injection. 
@@
 		\end{enumerate}
-\end{restatable}}\hfill 
-\parbox{6cm}{\xymatrix@C=10pt@R=5pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }}
+	\end{restatable}
+\end{minipage}  \hfill 
+\begin{minipage}[r]{.35\linewidth}
+	\xymatrix@C=10pt@R=5pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{>->}[rr]_{g} & & D }
+\end{minipage}
 
@@
 
-\begin{proposition}\label{prop:fact}
+\begin{prop}\label{prop:fact}
 	Let $X$ be a set and $n\in \mathbb{N}$. Then the following facts hold
@@
 	\end{enumerate}
-\end{proposition}
-
-\begin{remark}\label{rem:mono}
+\end{prop}
+
+\begin{rem}\label{rem:mono}
 	Preservation of pullbacks implies that $(-)^\star$ sends monos to monos.
-\end{remark}
-
-\begin{remark}\label[remark]{rem:length}Notice that $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length.
-\end{remark}
+\end{rem}
+
+\begin{rem}\label[remark]{rem:length}Notice that $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length.
+\end{rem}
 
@@
 \noindent
-\parbox{10.8cm}{\begin{definition}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the sets of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
-
-\hspace{10pt} A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the diagrams on the right are commutative.
-
-\hspace{10pt}	We define $\hyp$ to be the resulting category.
-\end{definition}}\hfill\parbox{3cm}{\xymatrix@R=15pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{s_{\mathcal{H}}} & V^\star_{\mathcal{H}}} \hspace{1pt}\\ \xymatrix@R=15pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{t_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{t_{\mathcal{H}}} & V^\star_{\mathcal{H}}} }
+\begin{minipage}[l]{.83\linewidth}
+	\setlength{\parindent}{1.5em}
+	\begin{defi}An \emph{hypergraph} is a 4-uple $\mathcal{G}:=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ made by two sets $E_\mathcal{G}$ and $V_\mathcal{G}$, called respectively the sets of \emph{hyperedges} and \emph{nodes}, plus a pair of \emph{source} and \emph{target} arrows  $s_\mathcal{G}, t_\mathcal{G}\colon E_\mathcal{G}\rightrightarrows V_\mathcal{G}^\star$.
+
+A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the diagrams on the right are commutative.
+
+We define $\hyp$ to be the resulting category.
+\end{defi}\end{minipage} \hfill 
+\begin{minipage}[r]{.15\linewidth}
+\xymatrix@R=8pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{s_{\mathcal{H}}} & V^\star_{\mathcal{H}}} \hspace{1pt}\\ \xymatrix@R=8pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{t_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{t_{\mathcal{H}}} & V^\star_{\mathcal{H}}}
+\end{minipage}
 
@@
 
-\begin{proposition}\label[proposition]{prop:com}
+\begin{prop}\label[proposition]{prop:com}
 	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{corollary}\label[corollary]{cor:monhyper}
+\begin{cor}\label[corollary]{cor:monhyper}
 	A morphism $(h,k)$ is a mono in $\hyp$ if and only if both its components are injective functions.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{corollary}\label[corollary]{prop:hypadh}
+\begin{cor}\label[corollary]{prop:hypadh}
 	 $\hyp$ is an adhesive category.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{proposition}\label{cor:left}  The forgetful functor $U_{\hyp}$ which sends a hypergraph $\mathcal{G}$ to its set of nodes has a left adjoint $\Delta_{\hyp}$.
-\end{proposition}
-
-\begin{example}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\hyp}(X)$ is the hypergraph which has $X$ as set of nodes, $\emptyset$ as set of hyperedges, and $?_X$ as source and target function.
-\end{example}
+\begin{prop}\label{cor:left}  The forgetful functor $U_{\hyp}$ which sends a hypergraph $\mathcal{G}$ to its set of nodes has a left adjoint $\Delta_{\hyp}$.
+\end{prop}
+
+\begin{exa}Since the initial object of $\catname{Set}$ is the empty set,  $\Delta_{\hyp}(X)$ is the hypergraph which has $X$ as set of nodes, $\emptyset$ as set of hyperedges, and $?_X$ as source and target function.
+\end{exa}
 
@@
 
-\begin{example}\label[example]{exa_2}
+\begin{exa}\label[example]{exa_2}
 We represent hypergraphs visually: dots denote nodes and boxes hyperedges. Should we be interested in their identity, we put a name near the corresponding dot or box. 
@@
 	\end{center}
-\end{example}
+\end{exa}
 %We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
@@
 \iffalse 
-\begin{example}
+\begin{exa}
 Take $V_{\mathcal{G}}$ to be be $\{v_1, v_2, v_3, v_4, v_5\}$ and $E_{\mathcal{G}}$ to be $\{h_1, h_2, h_3\}$. Sources and targets are given by:
@@
 	\end{center}
-\end{example}
-
-\begin{example}\label[example]{exa_21} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
+\end{exa}
+
+\begin{exa}\label[example]{exa_21} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
 	\[\begin{matrix}
@@
 	\end{center}
-\end{example}
+\end{exa}
 \fi
@@
 \commentato{
-\begin{example}\label[example]{exa_2}
+\begin{exa}\label[example]{exa_2}
 	Let $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$, and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$. Then we define:
@@
 
-\end{example}
+\end{exa}
 }
 
-\begin{remark}\label{rem:functor}
+\begin{rem}\label{rem:functor}
 	It is worth to point out, as first noted in \cite{bonchi2022string}, that $\hyp$ is equivalent to a category of presheaves. 
@@
 	The functors $\catname{H}\to \Set$ corresponds exactly to hypergraphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
-\end{remark}
+\end{rem}
 
@@
 
-\begin{proposition}\label{prop:cocomp}
+\begin{prop}\label{prop:cocomp}
 	$\hyp$ has all limits and colimits.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{definition}Let $\catname{H}$ be the category such that
+\begin{defi}Let $\catname{H}$ be the category such that
 	\begin{itemize}
@@
 	\end{itemize}
-\end{definition}
+\end{defi}
 
@@
 
-\begin{proposition}
+\begin{prop}
 	$\hyp$ is equivalent to the category $\Set^{\catname{H}}$.
-\end{proposition}
+\end{prop}
 \fi
@@
 \begin{minipage}[l]{.73\linewidth}
-\begin{definition}
+\begin{defi}
 An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ and an \emph{arity function} $\ari_\Sigma\colon O_\Sigma \to \mathbb{N}$. 
@@
 The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{example}\label[example]{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature in $\Set$.
+\begin{exa}\label[example]{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature in $\Set$.
 This simply amount to a set of \emph{operations} with an associated natural number, called \emph{arity}.
@@
 	\end{center}
-\end{example}\fi
-
-\begin{example}\label[example]{exa_3}
+\end{exa}\fi
+
+\begin{exa}\label[example]{exa_3}
 	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the signature with $O_\Sigma =  \mathbb{N} \uplus A \uplus \{*, /\}$, 
@@
 	$\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then the hypergraph $\mathcal{G}^\Sigma$ is depicted as the picture aside.
-\end{example}
+\end{exa}
 \end{minipage}
@@
 
-\begin{proposition}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then the following hold
+\begin{prop}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then the following hold
 	\begin{enumerate}
@@
 	\end{enumerate}
-\end{proposition}
-
-\noindent 
-\parbox{10.8cm}{\begin{remark}\label[remark]{rem:label}	
+\end{prop}
+
+\noindent 
+\begin{minipage}[l]{.8\linewidth}	
+	\begin{rem}\label[remark]{rem:label}	
+			\setlength{\parindent}{1.5em}
 		Let $\mathcal{H}=(E, V, s, t)$ be a hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
 
-\hspace{10pt}Now, consider a coprojection $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$.
+		Now, consider a coprojection $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$.
 By the second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V_\mathcal{H}^{\star}$ of words of length $1$, i.e.~all hyperedges must have a single target vertex, that is $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
-\end{remark}} \hfill \parbox{3cm}{\xymatrix@R=15pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\ari_\Sigma}& \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=15pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\gamma_1}& \mathbb{N}}}
+	\end{rem}
+\end{minipage} \hfill 
+\begin{minipage}[r]{.15\linewidth}
+	\xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\ari_\Sigma}& \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\gamma_1}& \mathbb{N}}
+\end{minipage}
 
@@
 
-\begin{proposition} $U_\Sigma$
+\begin{prop} $U_\Sigma$
 	has a left adjoint $\Delta_\Sigma$.
-\end{proposition}
+\end{prop}
 \iffalse 
@@
 
-\begin{example}\label[example]{lab_1}
+\begin{exa}\label[example]{lab_1}
 	The simplest example is given by the identity $\id{\mathcal{G}^\Sigma}\colon \mathcal{G}^\Sigma\rightarrow \mathcal{G}^{\Sigma}$. If $\Sigma$ is the signature of groups $\Sigma_G$ we get 
@@
 	\end{center}
-\end{example}
+\end{exa}
 
@@
 
-\begin{example}\label[example]{lab_2}
+\begin{exa}\label[example]{lab_2}
 	Consider again $\Sigma$ the signature of \Cref{exa_3}, then the hypergraph $\mathcal{G}$ of \Cref{exa_2} can be labeled by a morphism
@@
 	\end{center}\fi
-\end{example}
+\end{exa}
 
@@
 
-\begin{definition}\label[definition]{def:tg}\index{term graph}
+\begin{defi}\label[definition]{def:tg}\index{term graph}
 	Given an algebraic signature $\Sigma$, we say that a labelled hypergraph $(l, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ is a \emph{term graph} if $t_\mathcal{G}$ is a mono.
@@
 Restricting $U_\Sigma\colon \hyp_{\Sigma}\to \catname{Set}$ we get a forgetful functor $U_{\tg}\colon \tg\to \catname{Set}$.
-\end{definition}
-
-\begin{remark}\label[remark]{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
+\end{defi}
+
+\begin{rem}\label[remark]{rem:mono2}By \Cref{rem:label}, we know that if $\mathcal{G}$ is a term graph then $t_{\mathcal{G}}=v_1\circ \tau_{\mathcal{G}}$, where $v_1$ is the coprojection of $V_{\mathcal{G}}$ into $V^\star_{\mathcal{G}}$.
 Notice that since $t_{\mathcal{G}}$ is a mono then $\tau_{\mathcal{G}}$ is a mono.
-\end{remark}
-
-\begin{example}
+\end{rem}
+
+\begin{exa}
 The labelled hypergraph of \Cref{lab_2} is a term graph.
-\end{example}
+\end{exa}
 
@@
 
-\begin{proposition}\label[proposition]{term:left}The forgetful functor $U_{\tg}$ has a left adjoint $\Delta_{\tg}$.
-\end{proposition}
+\begin{prop}\label[proposition]{term:left}The forgetful functor $U_{\tg}$ has a left adjoint $\Delta_{\tg}$.
+\end{prop}
 \commentato{
@@
 
-\begin{proposition}\label{prop:tlim}
+\begin{prop}\label{prop:tlim}
 Let $\Sigma$ be an algebraic signature. Then the following hold
@@
 \end{enumerate}
-\end{proposition}
-
-\begin{remark}
+\end{prop}
+
+\begin{rem}
 	$\tg$ in general does not have terminal objects. 
@@
 	 it does not have pushouts along all monos. 
-\end{remark}
+\end{rem}
 
 \commentato{
-\begin{remark}
+\begin{rem}
 	$\tg$ in general does not have terminal objects.
@@
 	There are no morphisms in $\tg$ between the last two and from the last two to the first one, therefore none of them can be terminal.
-\end{remark}
-
-\begin{remark}
+\end{rem}
+
+\begin{rem}
 	$\tg$ is not an adhesive category. In particular it does not have pushouts along all monos. For instance, if we take the three term graphs of the previous remark, then have two arrows
@@
 	a=l_a(h)=q(g_E(h))=q(k_E(h))=l_b(h)=b\]
-\end{remark}
+\end{rem}
 }
 
-\begin{definition}
+\begin{defi}
 	Let $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$  be a term graph.
@@
 	 $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and $(l, !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ in $\tg$, is said to \emph{preserve input nodes} if $g$ sends input nodes to input nodes.
-\end{definition}
+\end{defi}
 
@@
 \todo{Se questo remark sotto non serve nel pezzo sulle equivalenze possiamo toglierlo}
-\begin{remark}\label{prop:image}
+\begin{rem}\label{prop:image}
 	Suppose that $(f,g)\colon (l, !_{V_{\mathcal{G}}})\to (l', !_{V_{\mathcal{H}}})$ preserves input nodes.
@@
 But then $\tau_{\mathcal{H}}(f(k))=g(v)$ and we can conclude that $f(k)=h$.
-\end{remark}
+\end{rem}
 }
@@
 
-\begin{proposition}\label[proposition]{lem:reg} Let $(i,j)$ be a mono between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$.
+\begin{prop}\label[proposition]{lem:reg} Let $(i,j)$ be a mono between two term graphs  $(l, !_{V_{\mathcal{G}}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$ and  $(l', !_{V_{\mathcal{H}}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$.
 Then it is a regular mono if and only if it preserves the input nodes.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{lemma}\label[lemma]{prop:push} Consider three term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$.
+\begin{lem}\label[lemma]{prop:push} Consider three term graphs $(l_0, !_{V_\mathcal{G}})\colon \mathcal{G}\to \mathcal{G}^{\Sigma}$, $(l_1, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ and $(l_2, !_{V_\mathcal{K}})\colon \mathcal{K}\to \mathcal{G}^{\Sigma}$.
 Given $(f_1, g_1)\colon (l_0, !_{V_\mathcal{G}})\to (l_1, !_{V_\mathcal{H}})$, $(f_2, g_2)\colon (l_0, !_{V_\mathcal{G}})\to (l_2, !_{V_\mathcal{K}})$, if $(f_1, g_1)$ is a regular mono, then its pushout  $(p, !_{V_{\mathcal{P}}})\colon \mathcal{P}\to \mathcal{G}^{\Sigma}$ in $\hyp_{\Sigma}$ along $(f_2, g_2)$ is a term graph.
-\end{lemma}
+\end{lem}
 
 \Cref{thm:slice-functors,prop:mono}, \Cref{lem:reg} and \Cref{prop:push} allow us to recover the following result, previously proved by direct computation in \cite[Thm.~4.2]{CorradiniG05} (see also \cite[Cor.~5.15]{CastelnovoGM24} for the details of the argument presented here).
-\begin{corollary}\label{cor:term}
+\begin{cor}\label{cor:term}
 	The category $\tg$ is quasiadhesive.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition}
+\begin{defi}
 	A \emph{hypergraph with equivalence} $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, Q_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$ is a 6-tuple such that $\mathcal{G} = (E_\mathcal{G}, V_{\mathcal{G}}, s_\mathcal{G}, t_\mathcal{G})$ is a hypergraph, $Q_\mathcal{G}$ is a set and $q_{\mathcal{G}}: V_{\mathcal{G}}\eto Q_{\mathcal{G}}$ is a surjection called \emph{quotient map}.
@@
 
-\end{definition}
-
-\begin{remark}
+\end{defi}
+
+\begin{rem}
 	Notice that in $\Set$ the classes of surjections, epis and regular epis coincide.
-\end{remark}
-
-\begin{remark}\label{rem:eqhyp_morphs}
+\end{rem}
+
+\begin{rem}\label{rem:eqhyp_morphs}
 	Morphisms of hypergraphs with equivalences are uniquely determined by the first two components.
@@
 	Since $q_\mathcal{G}$ is epi, we obtain $f = g$.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{restatable}{proposition}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then the following hold
+\begin{restatable}{prop}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then the following hold
 	\begin{enumerate}
@@
 
-\begin{corollary}\label{cor:limcolim}
+\begin{cor}\label{cor:limcolim}
 	The functor $T$ preserves limits and colimits.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{corollary}\label{cor:mono1}
+\begin{cor}\label{cor:mono1}
 	An arrow $(h_E, h_V, h_Q): \mathcal{G \to H}$ in $\EqHyp$ is a mono if and only if $(h_E, h_V)$ is a mono in $\hyp$.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{corollary}\label{cor:ladj}
+\begin{cor}\label{cor:ladj}
 	$U_{\eq}$ has a left adjoint $\Delta_{\eq}\colon \Set \to \EqHyp$.
-\end{corollary}
+\end{cor}
 
@@
 \noindent
-\parbox{11.4cm}{
-\begin{restatable}{lemma}{comp}\label{prop:eqhyp_complete}
+\begin{minipage}[l]{.83\linewidth}
+	\begin{restatable}{lem}{comp}\label{prop:eqhyp_complete}
 		Consider a diagram $F\colon \D \to \EqHyp$ and let $(E_D, V_D, Q_D, s_D, t_D, q_D)$ be the image of an object $D$. Then the following hold
@@
 		\end{enumerate}
-\end{restatable}}\hfill 
-\parbox{3cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_D}}
-
-\begin{restatable}{corollary}{mn}\label{cor:mono2}
+	\end{restatable}
+\end{minipage}\hfill
+\begin{minipage}[r]{.15\linewidth}
+\xymatrix{V \ar@{>>}[d]_{q} \ar[r]_{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]^{l_d} & Q_D}
+\end{minipage}
+
+\begin{restatable}{cor}{mn}\label{cor:mono2}
 	An arrow $(h_E, h_V, h_Q): \mathcal{G\to H}$ in $\EqHyp$ is a regular mono if and only if all its components are injective functions.
@@
 
-\begin{definition}
+\begin{defi}
 	We define the \emph{quotient functor} $\quo :\EqHyp\to \hyp $ as the one sending $(E, V, Q, s, t, q)$ to $(E, Q, q^{\star}\circ s, q^{\star}\circ t)$ and an arrow $(h_E, h_V, h_Q)$ to $(h_E, h_Q)$.
-\end{definition}
+\end{defi}
 
 \commentato{
-\begin{remark}
+\begin{rem}
 	The action of the functor on a morphism of hypergraphs with equivalences gives a morphism of hypergraphs,
@@
 	The same is valid for $t_\mathcal{H}$ and $t_\mathcal{G}$. 
-\end{remark}
+\end{rem}
 }
@@
 
-\begin{restatable}{lemma}{quot}\label{lemma:quot} The functor $\quo$ is a left adjoint.
+\begin{restatable}{lem}{quot}\label{lemma:quot} The functor $\quo$ is a left adjoint.
 \end{restatable}
 
-\begin{example} Notice that, due to the way in which limits in $\EqHyp$ are computed (see \Cref{prop:eqhyp_complete}), $\quo$ does not preserve them.
+\begin{exa} Notice that, due to the way in which limits in $\EqHyp$ are computed (see \Cref{prop:eqhyp_complete}), $\quo$ does not preserve them.
 For instance,  let $A$ and $B$ be two non-empty sets and define
@@
 On the other hand, \Cref{prop:eqhyp_complete} we know that taking the pullback of the original two morphisms gives us the hypergraph with equivalence $(\emptyset, \emptyset, Q, ?_{\emptyset^\star}, ?_{\emptyset^\star}, q)$ where $Q$ is the image of $?_{A\times B}$, so that $Q$ is also empty.
-\end{example}
+\end{exa}
 }
@@
 \noindent
-\parbox{11cm}{
-\begin{definition}
+\begin{minipage}[l]{.83\linewidth}
+\begin{defi}
 	We define $\pbc$ as the class of  regular monos $(h_E, h_V, h_Q)\colon \mathcal{G}\to \mathcal{H}$ in $\EqHyp$ such that the square on the right is a pullback
-\end{definition}
-} \hfill
-	\parbox{2cm}{
-	     \xymatrix@R=18pt{
-	        V_\mathcal{G} \ar@{>>}[r]_{q_\mathcal{G}} \ar@{>->}[d]_{h_V}& Q_\mathcal{G} \ar@{>->}[d]^{h_Q}\\
+\end{defi}
+\end{minipage} \hfill 
+\begin{minipage}[r]{.15\linewidth}
+	     \xymatrix@R=12pt{
+	        V_\mathcal{G} \ar@{>>}[r]_{q^\mathcal{G}} \ar@{>->}[d]_{h_V}& Q_\mathcal{G} \ar@{>->}[d]^{h_Q}\\
 	        V_\mathcal{H} \ar@{>>}[r]^{q_\mathcal{H}}  & Q_\mathcal{{H}}
               }
-         }
+ \end{minipage}
 
@@
 
-\begin{restatable}{lemma}{pbm}\label{lem:pbmono}
+\begin{restatable}{lem}{pbm}\label{lem:pbmono}
 	The class $\pbc$ contains all isomorphisms, it is closed under composition, decomposition and it is stable under pullbacks and pushouts.
@@
 
-\begin{restatable}{lemma}{pbs}\label{lemma:stab}
+\begin{restatable}{lem}{pbs}\label{lemma:stab}
 	In $\EqHyp$, $\pbc$-pushouts are stable.
@@
 
-\begin{example}
+\begin{exa}
 It is noteworthy to show that pushouts along regular monos are not stable.
-\begin{minipage}[l]{.35\linewidth}Consider e.g. the cube aside: the vertices are just graphs without edges, and in the graphs themselves the equivalence classes 
+
+\noindent 
+\begin{minipage}[l]{.45\linewidth}
+		\setlength{\parindent}{1.5em}
+		\indent Consider e.g. the cube aside: the vertices are just graphs without edges, and in the graphs themselves the equivalence classes 
 are denoted by encircling nodes with a dotted line. All the arrows are regular monos. It is immediate to see that the bottom face is a pushout and the side faces are pullback. Unfortunately, 
@@
 \begin{minipage}[r]{.60\linewidth}
-                \xymatrix@C=10pt@R=6pt{
+                \xymatrix@C=10pt@R=1pt{
                 &\emptyset \ar@{>->}[dd]|\hole \ar@{>->}[rr] \ar@{>->}@(dl,)[dl] &&
@@
         \end{tikzpicture}
-                \ar@{>->}[rr]|\hole \ar@{>->}@(dl,)[dl] && 
+                \ar@{>->}[rr]|(.51)\hole \ar@{>->}@(dl,)[dl] && 
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
                 \end{pgfonlayer}\end{tikzpicture}
-                \ar@{>->}[rr]_{g} & & 
+                \ar@{>->}[rr] & & 
                 \begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
@@
   \end{minipage}
-\end{example}
+\end{exa}
 
@@
 
-\begin{restatable}{lemma}{pbvk}\label{lemma:van_kampen}
+\begin{restatable}{lem}{pbvk}\label{lemma:van_kampen}
 	In $\EqHyp$, pushouts along arrows in $\pbc$ are $\reg(\EqHyp)$-Van Kampen.
@@
 
-\begin{corollary}\label{cor:eqade}
+\begin{cor}\label{cor:eqade}
 	$\EqHyp$ is $\pbc$-adhesive.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition}
+\begin{defi}
 	Let $\Sigma$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to it.
@@
 	We denote the resulting category by $\EqHyp_\Sigma$.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{proposition}\label{prop:slice}
+\begin{prop}\label{prop:slice}
 $\EqHyp_\Sigma$ is equivalent to $\EqHyp/R(\mathcal{G}^\Sigma)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then the following hold
+\begin{prop}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then the following hold
 	\begin{enumerate}
@@
 	\end{enumerate}
-\end{proposition}
+\end{prop}
 
 %In particular, $\EqHyp_\Sigma$ has all equalizers and pullbacks.
-Using \Cref{cor:mono1,cor:mono2} we immediately get the following result.
-
-\begin{corollary}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then the following hold
+Using \Cref{cor:mono1} and \Cref{cor:mono2} we immediately get the following result.
+
+\begin{cor}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then the following hold
 	\begin{enumerate}
@@
 	\end{enumerate}
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition}Let $\Sigma$ be an algebraic signature.
+\begin{defi}Let $\Sigma$ be an algebraic signature.
 	An object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph.
 We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyp_\Sigma$ so defined and by $J_{\Sigma}$ the corresponding inclusion functor.
- \end{definition}
-
-\noindent 
-\parbox{9.5cm}{\begin{remark}\label{rem:obv}
+ \end{defi}
+
+\noindent 
+\parbox{9.5cm}{\begin{rem}\label{rem:obv}
 Let $T_\Sigma:  \EqHyp_{\Sigma} \to \hyp_{\Sigma}$ the forgetful functor lifting
@@
 Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
-\end{remark}}
+\end{rem}}
 \hfill 
@@
 
-\begin{remark}\label{rem:t}
+\begin{rem}\label{rem:t}
 	Notice that, by \Cref{cor:limcolim} and \Cref{prop:lim}, the functor $T_\Sigma$ preserves all connected limits and all colimits.
-\end{remark}
+\end{rem}
 
@@
 
- \begin{restatable}{proposition}{trm}\label{prop:term}
+ \begin{restatable}{prop}{trm}\label{prop:term}
 $\EqTG_{\Sigma}$ has equalizers, binary products and pullbacks and they are created by $J_\Sigma$.
@@
 
-\begin{restatable}{proposition}{po}\label{prop:po}
+\begin{restatable}{prop}{po}\label{prop:po}
 $\EqTG_{\Sigma}$ has all $\mathcal{T}$-pushouts, which are created by $J_{\Sigma}$.
@@
 
-\begin{corollary}\label{cor:tade}
+\begin{cor}\label{cor:tade}
 	$\EqTG_{\Sigma}$ is $\mathcal{T}$-adhesive.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition}
+\begin{defi}
 	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
@@
 	We will denote by $\egg$ the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and by $I\colon \egg \to \EqHyp$ the associated inclusion functor.
-\end{definition}
-
-\begin{example}
+\end{defi}
+
+\begin{exa}
 	Consider the hypergraph $\mathcal{G}$ of \Cref{exa_2} and consider as quotient the identity $\id{V_\mathcal{G}}\colon V_\mathcal{G}\colon \to\mathcal{G}$.
@@
 Thus  $\mathcal{G}$ is, trivially, an e-hypergraph
-\end{example}
+\end{exa}
 A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proofs are in \Cref{proof:elim}.
 
-\begin{restatable}{lemma}{elim}\label{lem:elim}
+\begin{restatable}{lem}{elim}\label{lem:elim}
 	$\egg$ has all limits and $I$ creates them.
@@
 
-\begin{corollary}\label{cor:ereg}
+\begin{cor}\label{cor:ereg}
 	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is a regular mono in $\hyp$. 
-\end{corollary}
+\end{cor}
 
@@
 \noindent
-\parbox{11.5cm}{\begin{restatable}{lemma}{epo}\label{lem:epo}
+\parbox{11.5cm}{\begin{restatable}{lem}{epo}\label{lem:epo}
 	Suppose that the square on the right is a pushout in $\EqHyp$ and that $m$ is a mono in $\pbc$. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is 
@@
 \commentato{ 
-\begin{restatable}{corollary}{rege}\label{cor:rege}
+\begin{restatable}{cor}{rege}\label{cor:rege}
 		An arrow $h\colon \mathcal{G \to H}$  is a regular mono in $\egg$ if and only if $I(h)$ is a regular mono in $\hyp$.
@@
 
-\begin{corollary}\label{cor:pbe}
+\begin{cor}\label{cor:pbe}
 	$\egg$ is $\pbe$-adhesive.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition} We say that an object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
+\begin{defi} We say that an object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
 We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs.
 We denote by $Z_\Sigma$ the corresponding inclusion functor .
-\end{definition}
+\end{defi}
 
@@
 
-\begin{remark}\label{rem:algegg}
+\begin{rem}\label{rem:algegg}
 	Given a signature $\Sigma = (O_\Sigma, \ari_\Sigma)$,
@@
 On the other hand, both $\id{\mathbb{N}} \circ \gamma_1 \circ \pi_1$ and $\id{\mathbb{N}}\circ \gamma_1 \circ \pi_2$ are the function $O_\Sigma \to \mathbb{N}$ constant in $1$.
-\end{remark}
+\end{rem}
 
@@
 
-\samepage{\begin{proposition}\label{prop:varie}
+\samepage{\begin{prop}\label{prop:varie}
 	Let $\Sigma$ be an algebraic signature. Then the following hold
@@
 	\end{enumerate}
-\end{proposition}
+\end{prop}
 }
@@
 
-\begin{corollary}\label{cor:eggade1}
+\begin{cor}\label{cor:eggade1}
 	$\egg_\Sigma$ is $\pbe_\Sigma$-adhesive.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition}\label[definintion]{def:GEqTGs}
+\begin{defi}\label[definintion]{def:GEqTGs}
 	Given a signature $\Sigma$,  we say that an object $(\mathcal{H}, l)$ of $\EqTG_{\Sigma}$ is an \emph{e-term graph} if $\mathcal{H}$ is an e-hypergraph.
 We define the category $\eg$ as the full subcategory of $\EqTG_{\Sigma}$ given by e-term graphs and denote by $K_\Sigma$ the corresponding inclusion.
-\end{definition}
-
-\begin{remark}
+\end{defi}
+
+\begin{rem}
 	By definition we also have an inclusion functor $Y_\Sigma\colon \eg\to \egg_\Sigma$.
-\end{remark}
-
-\noindent 
-\parbox{7.5cm}{\begin{remark}
+\end{rem}
+
+\noindent 
+\parbox{7.5cm}{\begin{rem}
 	Now that we have put all the structures of this work in place, it is worthwhile to give a visual map of all the categories that we have discussed/introduced and of the relationships between them.
 We will use the curved arrows to denote full and faithful inclusions.
-\end{remark}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
+\end{rem}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
 
@@
 
-\begin{restatable}{proposition}{limt}\label{prop:limt}
+\begin{restatable}{prop}{limt}\label{prop:limt}
 	$\eg$ has equalizers, binary products and pullbacks and they are created by $K_\Sigma$.
@@
 
-\begin{restatable}{proposition}{pot}\label{prop:pot}
+\begin{restatable}{prop}{pot}\label{prop:pot}
 	$\eg$ has $\mathcal{T}_\Sigma$-pushouts, which are created by $K_\Sigma$.
@@
 
-\begin{corollary}
+\begin{cor}
 	$\eg$ is $\mathcal{T}_\Sigma$-adhesive.
-\end{corollary}
+\end{cor}
 
@@
 
-\newpage
-
-\interlinepenalty 1000
-\bibliography{biblio}
-
-\newpage
+\bibliographystyle{plain}
+\bibliography{biblio.bib}
+
 \appendix
-
+\renewcommand{\thesection}{\Alph{section}}
 \section{Omitted proofs}
@@
 \parbox{10cm}{
-\begin{lemma}\label{lem:pb1}
+\begin{lem}\label{lem:pb1}
 	Let $\X$ be a category, and consider the diagram aside, in which the right square is a pullback. Then the whole rectangle is a pullback if and only if the left square is one.
-\end{lemma}} 
+\end{lem}} 
 	\parbox{4cm}{
@@
 \noindent
-\parbox{7cm}{\mpo*}\hfill \parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }}
+\begin{minipage}[l]{.6\linewidth}
+\mpo*
+\end{minipage} 
+\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }
+\end{minipage}
 
@@
 \parbox{11.7cm}{
-\begin{lemma}\label{lem:po_set}
+\begin{lem}\label{lem:po_set}
 Suppose that the square aside is a pushout, with $m\colon A\mto B$ an injection.
@@
 In particular, $h\circ \iota_m$ is mono.
-\end{lemma}}\hfill \parbox{2cm}{\vspace{0cm}\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
+\end{lem}}\hfill \parbox{2cm}{\vspace{0cm}\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
 \begin{proof}
@@
 \parbox{11.5cm}{
-\begin{remark}\label{rem:disj}
+\begin{rem}\label{rem:disj}
 	Notice that extensivity entails that coproducts are \emph{disjoint}, i.e.~the pullback between two coprojections is given by the initial object (with initial maps as coprojections).
@@
 	is a coproduct and so the squares on the right are pullbacks.
-\end{remark}}\hfill\parbox{2cm}{\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}
+\end{rem}}\hfill\parbox{2cm}{\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}
 
@@
 \noindent 
-\parbox{11.5cm}{\begin{proposition}\label{prop:isempty}
+\parbox{11.5cm}{\begin{prop}\label{prop:isempty}
 	Suppose that the square on the right is a pullback.
@@
 If there exist two  arrows $t_1\colon T\to E$ and $t_2\colon T\to X$ such that $g\circ \iota\circ t_1= f\circ t_2$ then $T$ is empty.
-\end{proposition}}\hfill \parbox{2cm}{\vspace{-.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
+\end{prop}}\hfill \parbox{2cm}{\vspace{-.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
 \begin{proof}
@@
 
-\begin{lemma}\label{lem:nodim}
+\begin{lem}\label{lem:nodim}
 	Let $f,g\colon A\rightrightarrows B+C$ be two arrows with a coproduct as codomain. Then $(A, \{j_i\}_{i=0}^
@@
 		C\times B \ar@{>->}[r]_-{i_C\times i_B} & (B+C)\times (B+C) & C\times C \ar@{>->}[r]_-{i_C\times i_C} & (B+C)\times (B+C)}\]
-\end{lemma}
+\end{lem}
 
@@
 \noindent
-\parbox{7.5cm}{\mps*}\hfill
-\parbox{6cm}{\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{->}[rr]_{g} & & D }}
-
+\begin{minipage}[l]{.6\linewidth}\mps*
+\end{minipage}
+\begin{minipage}[r]{.35\linewidth}
+\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar@{->}[rr]_{g} & & D }
+\end{minipage}
 \begin{proof}\label{proof:kerset}
@@
 
-\begin{remark}\label{rem:fact}
+\begin{rem}\label{rem:fact}
 	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~surjections) and of monos in $\Set$.
@@
 	From these properties, one can deduce that if $f=m\circ e$ and $f=m'\circ e'$ are two factorizations of $f$ then there is a bijection $\phi$ such that $m=m'\circ \phi$ and $\phi \circ e=e'$.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{lemma}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
+\begin{lem}\label{lemma:nat_trans_reg_epi_canonical_arrow_reg_epi}
 	Let $F,G\colon \D\rightrightarrows \X$ be two diagrams and suppose that $\X$ has all colimits of shape $\D$.
@@
 If $\phi\colon  F \to G$ is a natural transformation whose components are regular epis, then the arrow induced by $\phi$ from $X$ to $Y$ is a regular epi.
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{remark}\label{rem:kleene}
+\begin{rem}\label{rem:kleene}
 	Let $\delta_1\colon 1\to \mathbb{N}$ be the arrow which picks $1\in \mathbb{N}$. Consider the
@@
 
-\end{remark}
+\end{rem}
 
@@
 In this section we briefly recall the definition of the comma category \cite{mac2013categories} associated to two functors and some of its properties.
-\begin{definition}\index{category!comma -}
+\begin{defi}\index{category!comma -}
 	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comma{L}{R}$ is the category in which
@@
 	\parbox{4cm}{\vspace{-.1cm}\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}}
-\end{definition} 
+\end{defi} 
 We have two forgetful functors 	$U_L\colon \comma{L}{R}\to \A$ and $U_R\colon \comma{L}{R} \to \B$ given respectively by
@@
 Summing up we have just proved the following fact.
-\begin{proposition}\label[proposition]{prop:dual}
+\begin{prop}\label[proposition]{prop:dual}
 	$(\comma{L}{R})^{op}$ is equal to	$\comma{R^{op}}{L^{op}}$, and $U^{op}_L=U_{L^{op}}$ and $U^{op}_R=U_{R^{op}}$.
-\end{proposition}
-
-\begin{lemma}\label[lemma]{colim}
+\end{prop}
+
+\begin{lem}\label[lemma]{colim}
 	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
 Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite[Sec.~5.1.3]{castelnovo2023thesis} or \cite[Sec.~2.3]{CastelnovoGM24}).
-\end{lemma}
+\end{lem}
 \begin{proof}
@@
 \Cref{prop:dual} and \Cref{colim} now yields the following.
-\begin{corollary}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ F$.
-\end{corollary}
+\begin{cor}\label[corollary]{lim} The family $\{U_L, U_R\}$ jointly creates limits along every diagram $F\colon \D\to \comma{L}{R}$ such that $R$ preserves the limit of $U_R\circ F$.
+\end{cor}
 
 We can use \Cref{lim} to characterize monos in comma categories. 
-\begin{corollary}\label[corollary]{cor:mono}
+\begin{cor}\label[corollary]{cor:mono}
 	If $R$ preserves pullbacks then an arrow $(h,k)$ in $\comma{L}{R}$ is mono if and only if both $h$ and $k$ are monos.
-\end{corollary}
+\end{cor}
 \begin{proof}
@@
 
-\begin{proposition}\label[proposition]{prop:left}
+\begin{prop}\label[proposition]{prop:left}
 	If $\A$ has initial objects and $L$ preserves them then the forgetful functor $U_R\colon \comma{L}{R}\to \B$ has a left adjoint $\Delta$.
-\end{proposition}
+\end{prop}
 \begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{R(B)})$, for $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
@@
 Dualizing we get immediately the following.
-\begin{corollary}If $\B$ has terminal objects preserved by $R$ then $U_L\colon \comma{L}{R}\to \A$ has a right adjoint.
-\end{corollary}
+\begin{cor}If $\B$ has terminal objects preserved by $R$ then $U_L\colon \comma{L}{R}\to \A$ has a right adjoint.
+\end{cor}
 
@@
 This section is devoted to recall some basic facts about the so called \emph{slice categories}.
-\begin{definition}\index{category!slice -}
+\begin{defi}\index{category!slice -}
 	Let $X$ be an object of a category $\X$. We define the following two categories.
@@
 	\end{itemize}} \hfill \parbox{2cm}{\vspace{-0cm}\xymatrix@C=15pt@R=15pt{Y \ar[dr]_{f} \ar[rr]^{h}&& Y' \ar[dl]^{g}\\ & X} \xymatrix@C=15pt@R=15pt{&X \ar[dr]^{g}\ar[dl]_{f}\\ Y  \ar[rr]_{h}&& Y'}}
-\end{definition}
-
-\begin{remark} For every $X\in\ X$ we have forgetful functors
+\end{defi}
+
+\begin{rem} For every $X\in\ X$ we have forgetful functors
 	\[\begin{split}
@@
 	\end{split}\]
-\end{remark}
+\end{rem}
 
@@
 
-\begin{proposition}\label[proposition]{prop:commaapp}
+\begin{prop}\label[proposition]{prop:commaapp}
 	For every object $X$ in a category $\X$, if $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object $*$, then $\X/X$ and $X/\X$ are isomorphic to, respectively,  $\comma{\id{X}}{\delta_X}$ and $\comma{\delta_X}{\id{X}}$ .
-\end{proposition}
+\end{prop}
 
@@
 A straightforward application of \Cref{lim,colim} now yields the following.
-\begin{corollary}\label[corollary]{cor:pbapp}
+\begin{cor}\label[corollary]{cor:pbapp}
 For every object $\X$, $\X/X$ has all colimits and connected limits that $\X$ has. Moreover such limits and colimits are created by $\dom_X$.
@@
 In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$, the slice $\X/X$ has such limits and colimits.
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{proposition}
+\begin{prop}
 	Let $\cat X$ be a category with pullbacks, $R: \cat{Y \to X}$ be a functor and $L: \cat{X \to Y}$ be its left adjoint, and $\eta$ the unit of the adjunction.
@@
 	where $L_X$ is the obvious functor, and $R_X$ is the composite $(\eta_X)^* \circ R$.
-\end{proposition}
+\end{prop}
 

### 2025-07-28 jlamp/jlamp.tex
revisione

@@
 \newcommand{\lgh}{\mathsf{lg}}
+\newcommand{\ind}[1]{\mathsf{in}_{\mathcal{#1}}}
+\newcommand{\ino}[1]{\mathsf{IN}({\mathcal{#1}})}
+\newcommand{\outd}[1]{\mathsf{out}_{\mathcal{#1}}}
 \newcommand{\eq}{\mathsf{eq}}
@@
 \newcommand{\lab}{\catname{LHyp}}
+\newcommand{\lmo}{\catname{LMH}}
 \newcommand{\hyp}{\catname{Hyp}}
+\newcommand{\shyp}{\catname{SepHyp}}
 \newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
@@
 \renewcommand{\sp}{\mathsf{sp}}
+\newcommand{\is}[1]{{#1}_{is}}
 \renewcommand{\sup}{\mathsf{sup}}
@@
 \newcommand{\ari}{\mathsf{ar}}
+\newcommand{\coar}{\mathsf{co}}
 \newcommand{\abs}[1]{\lvert #1\rvert}
@@
 \maketitle
+
+%questo sparirà, serve a me per non diventare scemo
+\setcounter{secnumdepth}{4}
+\setcounter{tocdepth}{4}
+\tableofcontents
 
@@
 \emph{E-graphs} (shortly, EGGs) are an up-and-coming formalism for program optimisation and synthesis via a compact 
-representation and efficient implementation of equality saturation. 
-%
-Albeit a classical data structure~\cite{DetlefsNS05}, EGGs received 
-new impulse after the seminal~\cite{WillseyNWFTP21} and
-developed a thriving community, as witnessed by the official website~\cite{eggs}.
+representation and efficient implementation of equality saturation. Albeit a classical data structure \cite{DetlefsNS05}, EGGs received 
+new impulse after the seminal \cite{WillseyNWFTP21} and
+developed a thriving community, as witnessed by the official website \cite{eggs}.
 %
@@
 We will also use the notation $e\colon X\eto Y$ to denote that an arrow $e\colon X\to Y$ is a regular epi.
-%\end{notation}
 
@@
 		\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable;
-		\item \emph{closed under decomposition}, or \emph{left-cancellable}, if whenever $g$ and $g\circ f$ belong to $\mathcal{A}$, then $f\in \mathcal{A}$.
 	\end{itemize}
@@
 \end{minipage}
+\begin{itemize}	\item \emph{closed under decomposition}, or \emph{left-cancellable}, if whenever $g$ and $g\circ f$ belong to $\mathcal{A}$, then $f\in \mathcal{A}$.
+\end{itemize}
 
@@
 \begin{minipage}[r]{.18\linewidth}
-	\xymatrix@R=15pt{K_f \ar[r]_{\pi^2_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}
+	\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}
 \end{minipage}
@@
 \end{minipage}\hfill 
-\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }
+\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=2pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]_(.3){f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]_{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]_(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]_{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]^{g} & & D }
 	\end{minipage}
@@
 Focusing on $\Set$, we can prove a sharper result (see \Cref{proof:kerset} for the proof).
-\smallskip
+\medskip
 
@@
 
-\begin{prop}\label{prop:fact}
+\begin{prop}\label[prop]{prop:fact}
 	Let $X$ be a set and $n\in \mathbb{N}$. Then the following facts hold
@@
 
-\begin{rem}\label[remark]{rem:length}Notice that $1^\star$ can be canonically identified with $\mathbb{N}$, thus for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length.
+\noindent
+\begin{minipage}[l]{.83\linewidth}
+	\begin{rem}\label[remark]{rem:length} It is well known that $(\mathbb{N}), \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
+Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathcal{N}\to 1^\star$.
+In particular, every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
 	\end{rem}
+\end{minipage}\hfill \begin{minipage}[r]{.15\linewidth}\noindent
+\xymatrix@R=10pt{1 \ar[r]^{\id{1}} \ar[d]^{u_n}& 1 \ar[d]^{v_n}\\ \mathbb{N} \ar@{.>}[r]^{\Delta}& 1^\star} \hspace{1pt}\\
+\xymatrix@R=10pt@C=22pt{\mathbb{N} \ar[r]^{\Delta} \ar@{.>}[dr]_{\lgh_{X}}& 1^\star\\ & X^\star \ar[u]_{!^\star_X}}
+\end{minipage}
+
+\begin{notaz}
+	Given a word $w\in X^\star$ of length $l$, for every $1\leq i \leq l$, we will denote by $w_i$ the $i^\mathrm{th}$ letter of $w$.  
+\end{notaz}
 
@@
 
-We open this section with the definition of hypergraphs and we show how to label them with an algebraic signature.
+Let us begin this section with the definition of hypergraphs.
 
@@
 \begin{minipage}[r]{.15\linewidth}
-\xymatrix@R=8pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{s_{\mathcal{H}}} & V^\star_{\mathcal{H}}} \hspace{1pt}\\ \xymatrix@R=8pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]_{t_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{t_{\mathcal{H}}} & V^\star_{\mathcal{H}}}
+\xymatrix@R=8pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]^{s_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{s_{\mathcal{H}}} & V^\star_{\mathcal{H}}} \hspace{1pt}\\ \xymatrix@R=8pt{E_{\mathcal{G}} \ar[d]_{h} \ar[r]^{t_{\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{k^\star}\\E_{\mathcal{G}} \ar[r]^{t_{\mathcal{H}}} & V^\star_{\mathcal{H}}}
 \end{minipage}
@@
 
-\begin{prop}\label[proposition]{prop:com}
+\begin{prop}[prop]\label{prop:com}
 	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
@@
 
-Note that by hypothesis $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, 
+Note that by, \Cref{prop:fact}, $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, 
 hence by \Cref{prop:com} and \Cref{cor:mono} we can deduce the following result.
@@
 \end{exa}
-%We  decorate the arrow corresponding to the $i^{th}$ letter of a target or a source with a label $i$.
-%\todo{Ho lasciato un unico esempio (che è anche un term graph): occorre riscrivere questo paragrafo una volta che abbiamo deciso come rappresentare i grafi}
-\iffalse 
-\begin{exa}
-Take $V_{\mathcal{G}}$ to be be $\{v_1, v_2, v_3, v_4, v_5\}$ and $E_{\mathcal{G}}$ to be $\{h_1, h_2, h_3\}$. Sources and targets are given by:
-	\[\begin{matrix}
-		s_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}}  & \begin{matrix}
-			0 \mapsto v_1\\
-			1\mapsto v_2
-		\end{matrix} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
-			0 \mapsto v_3\\
-			1\mapsto v_4 
-		\end{matrix} && s_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 
-		0 \mapsto v_5\\
-		t_{\mathcal{G}}(h_1)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
-			0 \mapsto v_3\\
-			1\mapsto v_4
-		\end{matrix} && t_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & 0\mapsto v_5 && t_{\mathcal{G}}(h_3)\colon 0\to V_{\mathcal{G}} &  t_{\mathcal{G}}(h_3)=?_{ V_{\mathcal{G}}} 
-	\end{matrix}\]
-
-	We can draw the resulting $\mathcal{G}$ as follows:
-	\begin{center}\begin{tikzpicture}
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,0) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-1.5) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_5$}] (E) at (6,-0.75) {};
-			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
-			\draw[->-=.5](4.75,-0.75)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5](E)--(7,-0.75)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[rounded corners] (4.25, -1) rectangle (4.75, -0.5) {};
-			\node at (4.5, -0.3){$h_2$};
-			\node at (1.5, -0.3){$h_1$};
-			\node at (7.25, -0.3){$h_3$};
-			\draw[rounded corners] (7, -1) rectangle (7.5, -0.5) {};
-			\draw(A)[->-=.5]..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw(B)[->-=.5]..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-
-			\draw(C)[->-=.5]..controls(3.5,0)and(4.2,-0.25)..(4.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw(D)[->-=.5]..controls(3.5,-1.5)and(4.2,-1.3)..(4.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-
-			\draw[->-=.5](1.75,-0.9)..controls(1.8,-1.3)and(2.5,-1.5)..(D)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-			\draw[->-=.5] (1.75,-0.6)..controls(1.8,-0.25)and(2.5,0)..(C) node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-		\end{tikzpicture}
-	\end{center}
+
+A rich source of example is given by \emph{monoidal signatures}.
+
+\smallskip 
+\noindent
+\begin{minipage}[l]{.75\linewidth}
+	\begin{defi}
+		A \emph{(single typed) monoidal signature} $\Sigma$ is a triple $(O_\Sigma, \ari_\Sigma, \coar_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ together with \emph{arity} and \emph{coarity} functions $\ari_\Sigma, \coar_\Sigma\colon O_\Sigma \rightrightarrows \mathbb{N}$.
+
+		We say that $\Sigma$ is \emph{algebraic} if $\coar_{\Sigma}$ is the constant function in $1$.
+
+		We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes and $\Delta \circ \ari_\Sigma$ as the source function and $ \Delta \coar_{\Sigma}$ as target function, where $\Delta \colon \mathbb{N}\to 1$ is the isomorphism of \Cref{rem:length}.
+	\end{defi}
+
+	\begin{exa}\label{exa_3} 
+		Given a set $A$, let $\Sigma = (O_\Sigma, \ari_\Sigma, \coar_{\Sigma})$ be the algebraic signature with $O_\Sigma =  \mathbb{N} + A + \{*, /\}$, 
+		and 
+		\[\ari_\Sigma(n)=0 \quad \ari_\Sigma(a) = 0, \quad \ari_\Sigma(*) =2 \quad  \ari_\Sigma(/) = 2\]
+		for every $n\in \mathbb{N}$ and $a\in A$. Then we can depict the hypergraph $\mathcal{G}^\Sigma$  as in the picture aside.
 	\end{exa}
-
-\begin{exa}\label[example]{exa_21} Let $V_{\mathcal{G}}$ be as in the previous example and $E_{\mathcal{G}}=\{h_1, h_2, h_3\}$.	Then we define
-	\[\begin{matrix}
-		A && s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}}  & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} && s_{\mathcal{G}}(h_2)\colon 2\to V_{\mathcal{G}} & \begin{matrix}
-			0 \mapsto v_1\\
-			1\mapsto v_2
-		\end{matrix}&& s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
-			0 \mapsto v_1\\
-			1\mapsto v_4	
-		\end{matrix}\\
-			B && t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 
-		0 \mapsto v_1 && 		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3 &&   t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_5
-	\end{matrix}\]
-
-	Now we can depict $\mathcal{G}$ as
-	\begin{center}\begin{tikzpicture}
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_1$}] (A) at (0,0) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_2$}] (B) at (0,-1.5) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_3$}] (C) at (3,-0.75) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v_4$}] (D) at (3,-2.25) {};
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=right:{$v_5$}] (E) at (6,-1.5) {};
-			\draw[->-=.5] (1.75,-0.75)--(C)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[rounded corners] (1.25, -1) rectangle (1.75, -0.5) {};
-			\draw[->-=.5] (4.75,-1.5)--(E)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5] (-1.5,0)--(A)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[rounded corners] (4.25, -1.75) rectangle (4.75, -1.25) {};
-			\node at (4.5, -1.05){$h_3$};
-			\node at (1.5, -0.3){$h_2$};
-			\node at (-1.75, 0.45){$h_1$};
-			\draw[rounded corners] (-2, -0.25) rectangle (-1.5, 0.25) {};
-			\draw[->-=.5] (A)..controls(0.5,0)and(1.2,-0.2)..(1.25,-0.6)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5] (B)..controls(0.5,-1.5)and(1.2,-1.3)..(1.25,-0.9)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-
-			\draw[->-=.5] (C)..controls(3.5,-0.75)and(4.2,-0.95)..(4.25,-1.35)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5] (D)..controls(3.5,-2.25)and(4.2,-2.05)..(4.25,-1.65)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-		\end{tikzpicture}
-	\end{center}
-\end{exa}
-\fi
-
-\commentato{
-\begin{exa}\label[example]{exa_2}
-	Let $V_\mathcal{G} = \{v_1, v_2, v_3, v_4, v_5\}$, and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$. Then we define:
-	\[\begin{matrix}
-		s_{\mathcal{G}}(h_1)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_1)=?_{V_\mathcal{G}} &&
-		s_{\mathcal{G}}(h_2)\colon 0\to V_{\mathcal{G}} & s_{\mathcal{G}}(h_2)=?_{V_\mathcal{G}}\\
-		s_{\mathcal{G}}(h_3)\colon 2\to V_{\mathcal{G}} & \begin{matrix} 
-					0 \mapsto v_1\\
-					1\mapsto v_2
-				\end{matrix}&& s_{\mathcal{G}}(h_4)\colon 2 \to V_\mathcal{G} & \begin{matrix}
-					0 \mapsto v_3\\
-					1\mapsto v_2
-				\end{matrix}\\
-		t_{\mathcal{G}}(h_1)\colon 1\to V_{\mathcal{G}} & 0 \mapsto v_1 &&
-		t_{\mathcal{G}}(h_2)\colon 1\to V_{\mathcal{G}} & 0\mapsto v_3\\
-		t_{\mathcal{G}}(h_3)\colon 1\to V_{\mathcal{G}} & 1\mapsto v_3 &&
-		t_\mathcal{G}(h_4)\colon 1 \to V_\mathcal{G} & 0 \mapsto v_4
-	\end{matrix}\]
-
-	Now, we can depict $\mathcal{G}$ as
-
-	\begin{center}
+	\end{minipage}
+	%\begin{center}
+	\hfill
+	\begin{minipage}[r]{.22\linewidth}
 	\begin{tikzpicture}
 		\begin{pgfonlayer}{nodelayer}
-                        \node[style=none] (lab1) at (-1.8, 0.8) {$h_1$};
-                        \node[style=small box] (h1) at (-1.8, 0.3) {};
-                        \node[style=small box] (2) at (-1.8, -0.5) {};
-                        \node[style=none] (lab2) at (-1.8, -1.0) {$h_2$};
-                        \node[style=none] (h1b) at (-1.8, 0.3) {};
-                        \node[style=none] (th2) at (-0.3, 0.3) {};
-                        \node[style=none] (bh2) at (-0.3, -0.3) {};
-                        \node[style=none] (h2b) at (0, 0) {};
-                        \node[style=none] (th3) at (1.5, 0){};
-                        \node[style=none] (bh3) at (1.5, -0.6){};
-                        \node[style=none] (h3c) at (1.8, -0.3){};
-                        \node[style=none] (2c) at (-1.8, -0.5){};
-                        \node[style=none] (lab3) at (0, 0.8) {$h_3$};
-                        \node[style=medium box] (h2) at (0, 0) {};
-                        \node[style=none] (lab4) at (1.8, 0.5) {$h_4$};
-                        \node[style=medium box] (h3) at (1.8, -0.3) {};
-                        \node[style=none](labv2) at (-0.9, -0.9) {$v_2$};
-                        \node[style=node] (v2) at (-0.9, -0.5) {};
-                        \node[style=none] (labv1) at (-0.9, 0.7) {$v_1$};
-                        \node[style=node] (v1) at (-0.9, 0.3) {};
-                        \node[style=none] (labv3) at (0.9, 0.4) {$v_3$};
-                        \node[style=node] (v3) at (0.9, 0) {};
-                        \node[style=none] (labv4) at (2.7, 0.1) {$v_4$};
-                        \node[style=node] (v4) at (2.7, -0.3) {};
+			\node[style=node] (v) at (0, 0){};
+			\node[style=none] (vlab) at (0, -0.4){$v$};
+
+			\node[style=small box] (n) at (-1.8, 0.4) {};
+			\node[style=none] (nlab) at (-1.8, 0.9) {$n$};
+			\node[style=none] (nattach) at (-1.6, 0.4) {};
+
+			\node[style=small box] (const) at (-1.8, -0.4) {};
+			\node[style=none] (constlab) at (-1.8, -0.9){$a$};
+			\node[style=none] (constattach) at (-1.6, -0.4){};
+
+			\node[style=medium box] (times) at (0, 1.8) {};
+			\node[style=none] (timeslab) at (0, 2.6) {$*$};
+			\node[style=none] (timesin1) at (-0.3, 2.1) {};
+			\node[style=none] (timesin2) at (-0.3, 1.5) {};
+			\node[style=none] (timesout) at (0.2, 1.8){};
+
+			\node[style=medium box] (div) at (0, -1.8) {};
+			\node[style=none] (divlab) at (0, -2.6) {$/$};
+			\node[style=none] (divin1) at (-0.3, -2.1) {};
+			\node[style=none] (divin2) at (-0.3, -1.5) {};
+			\node[style=none] (divout) at (0.2, -1.8){};
 		\end{pgfonlayer}
+
 		\begin{pgfonlayer}{edgelayer}
-                        \draw[style=diredge] (h1b.center) to (v1);
-                        \draw[style=diredge] (v1) to (th2.center);
-                        \draw[style=diredge] (2c.center) to (v2);
-                        \draw[style=diredge, in=180, out=30] (v2) to (bh2.center);
-                        \draw[style=diredge] (v3) to (th3.center);
-                        \draw[style=diredge] (h3c.center) to (v4);
-                        \draw[style=diredge] (h2b.center) to (v3);
-                        \draw[style=diredge,in=180, out=-30](v2) to (bh3);
+			\draw[style=diredge, in=180, out= 112.5] (v) to (timesin2.center); 
+			\draw[style=diredge,out=135, in= 180] (v) to (timesin1.center);
+			\draw[style=diredge,in=165, out=0] (nattach.center) to (v);
+
+			\draw[style=diredge,out=0, in=-165] (constattach.center) to (v);
+			\draw[style=diredge,in=180, out= -112.5] (v) to (divin2.center); 
+			\draw[style=diredge,out=-135, in= 180] (v) to (divin1.center);
+
+			\draw[style=diredge, in=30, out=0] (timesout.center) to (v);
+			\draw[style=diredge, in=-30, out=0] (divout.center) to (v);
 		\end{pgfonlayer}
 	\end{tikzpicture}
-\end{center}
-
-\end{exa}
-}
+	\end{minipage}
+
+ \smallskip 
+ We can interpret an arbitrary hypergaph as a \emph{typed} or \emph{colored} monoidal signature: the set of nodes provides the \emph{types} or \emph{colors}, while hyperedges can be thought of as operations, with arity and coarity provided by the source and target function.
+This suggest the following definition, which will be used in Section \ref{par:tg}.
+
+\begin{defi}
+An hypergraph $\mathcal{G}=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}})$ is \emph{algebraic} if $t_{\mathcal{G}}(e)$ has length $1$ for every $e\in E_{\mathcal{G}}$.
+\end{defi}
 
@@
 \end{prop}
+
+\begin{rem}It is worth mentioning that limits in $\hyp$ are not computed componentwise.
+By \Cref{prop:fact,prop:com,lim} we know that the two forgetful functors $U_{\hyp}, H_{\hyp}\colon \hyp \to \Set$, sending an hypergraph to, respectively, its set of nodes and that of hyperedges only jointly creates conneted limits.
+For instance, let $\phi\colon \mathbb{N}\to 1^\star$  $(\mathbb{N}, 1, \phi)$
+\end{rem}
 
@@
 
-\subsubsection{Labelling hypergraph with an algebraic signature}\label{sssect:hyp_alg_sign}
-
-Our interest for hypergraphs stems from their use as a graphical representation of algebraic terms. We thus need a way to label hyperedges with symbols taken from a signature.
-
-\noindent
-\begin{minipage}[l]{.73\linewidth}
+\subsubsection{Some  subcategories of $\hyp$}
+
+We are now going to introduce three classes of hypergraphs, and the relative subcategories, which will provide the base for our definitions of EGGs  (cfr.~\Cref{sec:sepegg,sec:lmegg}).
+
+\paragraph{Separated hypergraphs}
+
+Let us begin with the subcategory of $\hyp$ which, in \Cref{sec:sepegg}, will give us the underlying hypergraphs for EGGs with minimally identified tokens.
+
+\begin{defi} Given a set $X$, we say that two words $X^\star$ are \emph{disjoint} is they do not share any letter.
+An hypergraph $\mathcal{G}=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}})$ is \emph{separated} if:
+	\begin{enumerate}
+		\item for every hyperedge $e$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ do not have repeated letters;
+		\item for every two, not necessarily distinct, hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint;
+		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $s_{\mathcal{G}}(e')$ are disjoint;
+		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $t_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint.
+	\end{enumerate}
+We will denote by $\shyp$ the full subcategory of $\hyp$ given by separated hypergraphs and by $S$ the inclusion functor.
+\end{defi}
+\iffalse 
 \begin{defi}
-An \emph{algebraic signature} $\Sigma$ is a pair $(O_\Sigma, \ari_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ and an \emph{arity function} $\ari_\Sigma\colon O_\Sigma \to \mathbb{N}$. 
-%
-We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes, so that $1^\star$ is $\mathbb{N}$, $\ari_\Sigma$ as the source function and $\gamma_1$, which always picks the element $1$, as target function.
-The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
+Given an hypergraph $\mathcal{\mathcal{G}}=(E_{\mathcal{G}}, V_{\mathcal{F}}, s_{\mathcal{G}}, t_{\mathcal{G}})$, for every hyperedge $e\in E_{\mathcal{G}}$ with $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we can consider the coproduct $(V_e, \{\iota^e_{i}\}_{i=1}^{n_e+m_e})$ of $n_e+m_e$ copies of $1$.
+
+ Moreover, let $\is{(V_{\mathcal{G}})}$ be the set of isolated nodes  of $\mathcal{G}$ i.e.~those which are not in the image of $s_{\mathcal{G}}$ or of $t_{\mathcal{G}}$.
+Furthermore, let $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}} \cup \{\iota_{is}\})$ be the coproduct of the family $\{V_{e}\}_{e\in E_\mathcal{G}} \cup \{\is{(V_{\mathcal{G}})}\}$ and define:
+\[\begin{split}
+	s_{\sp(\mathcal{G})} \colon E_{\mathcal{G}}&\to V_{\sp(\mathcal{G})}^\star\\
+	e &\mapsto \prod_{i=1}^{n_e} \iota_e(\iota^e_{i}(0))
+\end{split}\qquad \begin{split}
+	t_{\sp(\mathcal{G})} \colon E_{\mathcal{G}}&\to V_{\sp(\mathcal{G})}^\star\\
+	e &\mapsto \prod_{i=n_e+1}^{m_e} \iota_e(\iota^e_{i}(0))
+\end{split} \]
+where $0$ is the unique element of $1$.
+
+We can finally define the \emph{separated graph associated to $\mathcal{G}$}  as $\sp(\mathcal{G}):= (E_{\mathcal{G}}, V_{\sp(\mathcal{G})}, s_{\sp(\mathcal{G})}, t_{\sp(\mathcal{G})})$.
 \end{defi}
-
-\iffalse
-\todo{Decidere se tenere questo esempio}
-
-\begin{exa}\label[example]{exa_3} Let $\Sigma=(O_\Sigma, \ari_\Sigma)$ be an algebraic signature in $\Set$.
-This simply amount to a set of \emph{operations} with an associated natural number, called \emph{arity}.
-	For instance let $\Sigma_G$ be the signature of groups, then $\mathcal{G}^{\Sigma_G}$ can be depicted as the picture aside.
-	\begin{center}
-		\begin{tikzpicture}
-			\node[circle,fill=black,inner sep=0pt,minimum size=6pt,label=above:{$v$}] (V) at (0,0) {};
-			\node(E)at(-2, 0.4){$e$};
-			\node(M)at(0, 2.15){$\cdot$};
-			\node(I)at(2, 0.5){$(-)^{-1}$};
-			\draw[->-=.5](-1.75,0)--(V)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5](V)..controls(-0.5,0.5)and(-0.8,1)..(-0.25,1.6)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$2$};
-			\draw[->-=.5](V)..controls(-1,0.6)and(-1,1.1)..(-0.25,1.9)node[pos=0.5, left,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5](0.25,1.75)..controls(0.8,0.8)and(0.5,0.5)..(V)node[pos=0.5, right,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5](V)--(1.75,0)node[pos=0.5, above,font=\fontsize{7}{0}\selectfont]{$1$};
-			\draw[->-=.5](2.25,0)..controls(3.5,0)and(2.5,-2)..(V)node[pos=0.5, below,font=\fontsize{7}{0}\selectfont]{$2$};
-			\draw[rounded corners] (-2.25, -0.25) rectangle (-1.75, 0.25) {};
-			\draw[rounded corners] (-0.25, 1.5) rectangle (0.25, 2) {};
-			\draw[rounded corners] (2.25, -0.25) rectangle (1.75, 0.25) {};
+\begin{rem}\label{rem:ob}
+ By construction $\sp(\mathcal{G})$ is an object of $\shyp$. 
+\end{rem}
+
+\begin{exa}\label{ex:alg}
+	Let $\Sigma$ be a monoidal signature, then $\sp(\mathcal{G}^\Sigma)$ collects all the operation of $\Sigma$ as edges with disjoint sources and targets.
+For instance let $\Sigma$ be the algebraic signature of monoids, with $O_\Sigma = (\cdot, e )$ with
+	\[\ari_\Sigma(\cdot)=2 \qquad \ari_\Sigma(e)=0\]
+
+	We can then depict $\mathcal{G}^\Sigma $ and $\sp(\mathcal{G}^\Sigma )$ as below.
+	\begin{center}	\begin{tikzpicture}
+			\begin{pgfonlayer}{nodelayer}
+				\node[style=node] (v) at (0, 0){};
+				\node[style=none] (vlab) at (0, -0.4){$v$};
+				\node[style=small box] (n) at (-1.5, 0) {};
+				\node[style=none] (nlab) at (-1.5, 0.5) {$e$};
+				\node[style=none] (nattach) at (-1.6, 0) {};
+
+				\node[style=small box] (const) at (3, 0) {};
+				\node[style=none] (constlab) at (2.5, 0){$e$};
+				\node[style=none] (constattach) at (3.3, -0){};
+
+				\node[style=medium box] (times) at (0, 1.5) {};
+				\node[style=none] (timeslab) at (0, 2.2) {$\cdot$};
+				\node[style=none] (timesin1) at (-0.3, 1.8) {};
+				\node[style=none] (timesin2) at (-0.3, 1.2) {};
+				\node[style=none] (timesout) at (0.2, 1.5){};
+
+				\node[style=medium box] (div) at (4, 1.3) {};
+				\node[style=none] (divlab) at (4, 2) {$\cdot$};
+				\node[style=none] (divin1) at (3.7, 1.6) {};
+				\node[style=none] (divin2) at (3.7, 1) {};
+				\node[style=none] (divout) at (4.2, 1.3){};
+
+				\node[style=node] (a) at (3, 1.8){};
+				\node[style=none] (alab) at (3, 2.1){$a$};
+				\node[style=node] (b) at (3, 0.8){};
+				\node[style=none] (blab) at (3, 1.1){$b$};
+				\node[style=node] (c) at (5, 0){};
+				\node[style=none] (clab) at (5, -.3 ){$c$};
+				\node[style=node] (d) at (5, 1.3){};
+				\node[style=none] (dlab) at (5, 1.6){$d$};
+
+			\end{pgfonlayer}
+
+			\begin{pgfonlayer}{edgelayer}
+				\draw[style=diredge, in=180, out= 135] (v) to (timesin2.center); 
+				\draw[style=diredge,out=165, in= 180] (v) to (timesin1.center);
+				\draw[style=diredge,in=180, out=0] (nattach.center) to (v);
+
+				\draw[style=diredge,out=0, in=180] (constattach.center) to (c);
+				\draw[style=diredge,in=165, out= -15] (a) to (divin1.west); 
+				\draw[style=diredge,out=15, in=195 ] (b) to (divin2.west);
+
+				\draw[style=diredge, in=30, out=0] (timesout.center) to (v);
+				\draw[style=diredge, in=180, out=0] (divout.center) to (d);
+			\end{pgfonlayer}
 		\end{tikzpicture}
 	\end{center}
-\end{exa}\fi
-
-\begin{exa}\label[example]{exa_3}
-	Let $\Sigma = (O_\Sigma, \ari_\Sigma)$ be the signature with $O_\Sigma =  \mathbb{N} \uplus A \uplus \{*, /\}$, 
-	where $n$ stands for any natural number and $a$ for any element in $A$, both sets of constants, and
-	%so that $\ari_\Sigma(n)=\ari_\Sigma(a) = 0$, 
-	$\ari_\Sigma(*) = \ari_\Sigma(/) = 2$. Then the hypergraph $\mathcal{G}^\Sigma$ is depicted as the picture aside.
+
 \end{exa}
+
+\begin{prop}There exists a functor $\sp \colon \hyp\to \shyp$ sending $\mathcal{G}$ to $\sp(\mathcal{G})$.
+\end{prop}
+\begin{proof}
+Let $(h_1, h_2)\colon \mathcal{G}\to \mathcal{H}$ be a morphism of hypergraph. For every $a$
+
+Preservation of compositions and identities follows at once from the construction.
+Now, for every $e\in \mathcal{E}_\mathcal{G}$ and $i$ between $1$ and $n_e+m_e$  we can define 
+\begin{align*}f_{e, i}\colon 1&\to V_{\mathcal{G}}\\
+	* & \mapsto\begin{cases}
+		(s_{\mathcal{G}}(e))_i & i \leq n_e\\
+		(t_{\mathcal{G}}(e))_i & n_e < i
+	\end{cases}
+\end{align*}
+These arrows, in turn, give us $f_ e\colon V_e\to V_{\mathcal{G}} $ and so an arrow $f_{\mathcal{G}}:V_{\sp(\mathcal{G})}\to V_{\mathcal{G}}$ such that 
+\[f_{\mathcal{G}}\circ \iota_e = f_e \qquad f_{\mathcal{G}}\circ \is{\iota} =  j_{\mathcal{G}}\]
+where $j_{\mathcal{G}}$ is the inclusion of $\is{(V_{\mathcal{G}})}\mto V_{\mathcal{G}}$. Notice that, for every $e\in E_{\mathcal{G}}$, $1\leq i\leq n_e$ and $1\leq k\leq m_e$ we have:
+\[\begin{split}
+	(f_{\mathcal{G}}^\star( s_{\sp(\mathcal{G})}(e)) )_i & = f_{\mathcal{G}}( s_{\sp(\mathcal{G})}(e) _i)\\
+	&=f(\iota_e(\iota^e_i(*)))\\&=f_e(\iota^e_i(*))\\&=f_{e, i}(*)\\&=
+	(s_{\mathcal{G}}(e))_i 
+\end{split} \qquad 
+\begin{split}
+	(f^\star( t_{\sp(\mathcal{G})}(e)) )_k & = f( t_{\sp(\mathcal{G})}(e) _k)\\
+	&=f(\iota_e(\iota^e_{n_e+k}(*)))\\&=f_e(\iota^e_{n_e+k}(*))\\&=f_{e, n_e+k}(*)\\&=
+	(t_{\mathcal{G}}(e))_k
+\end{split}
+\]
+and so we get an arrow $(\id{E_{\mathcal{G}}}, f_{\mathcal{G}})\colon V\to \mathcal{V}_{\mathcal{G}}$.
+
+Now, let $\mathcal{H}=(E_{\mathcal{H}}, V_{\mathcal{H}}, s_{\mathcal{H}}, t_{\mathcal{H}})$ be another separated hypergraph with an arrow $(h_1, h_2)\colon S(\mathcal{H})\to \mathcal{G}$.
+We can define
+\begin{align*}
+\hat{h}\colon V_{\mathcal{H}}&\to V_{\sp(\mathcal{G})} \\
+v & \mapsto \begin{cases}
+	\iota_{is}(h_2(v)) & h_2(v)\in \is{(V_{\mathcal{G}})}\\
+	\iota_e(h_2(v)) & h_2(v) \text{ is a letter of } s_{\mathcal{G}}(e) \text{ for some } e\in E_{\mathcal{G}}\\
+		\iota_e(h_2(v)) & h_2(v) \text{ is a letter of } t_{\mathcal{G}}(e) \text{ for some } e\in E_{\mathcal{G}}\\
+\end{cases}
+\end{align*}
+
+We first have to show that the previous definition gives us a well-defined function.
+By definition of isolated node we know that the three cases are exhaustive.
+Now, suppose that there are $e_1$ and $e_2$, not necessarily distinct, in $E_\mathcal{G}$ such that $h_2(v)$ is a letter of both
+
+\noindent
+\begin{minipage}[l]{.75\linewidth}
+\setlength{\parindent}{1.5em}
+\indent 	Since $\mathcal{H}$ is a separated hypergraph, $\hat{h}$
+	is a well-defined function. Moreover,  by construction $(h_1, \hat{h})$ defines a morphism $\mathcal{H}\to V_{\sp(\mathcal{G})}$ fitting in the diagram aside.
+\end{minipage} \hfill 
+\begin{minipage}[r]{.25\linewidth}
+	\xymatrix@C=40pt@R=10pt{S(\mathcal{H}) \ar[dr]^{(h_1, h_2)} \ar[d]_{S(h_1, \hat{h})}\\ S(\sp(\mathcal{G}))  \ar[r]_-{(\id{E_{\mathcal{G}}}, f_{\mathcal{G}})}& \mathcal{G}}
 \end{minipage}
-%\begin{center}
+
+To prove uniqueness of such an arrow, let $(k_1, k_2)$ be a morphism $(\mathcal{H})\to \sp(\mathcal{G})$ such that 
+\[(h_1, h_2)=(\id{E_{\mathcal{G}}}, f)\circ (k_1, k_2)\]
+Clearly this implies $k_1 = h_2$.   Let now $v$ be an element of $V_\mathcal{H}$. Then we have three cases.
+\begin{itemize}
+	\item $v\in \is{(V_{\mathcal{H}})}$. In this case we have:
+\begin{align*}
+	j(h_2(v))&=f(\iota_{is}(h_2(v)))\\&=f(\hat{h}(v))\\&=h_2(v)\\&=
+\end{align*}
+	\item 
+\end{itemize}
+
+The previous three points allow us to conclude.
+\end{proof}
+
+\noindent 
+\begin{minipage}[l]{.68\linewidth}
+\begin{rem}Notice that $\sp$ is neither right nor left adjoint to $S$.
+	\begin{itemize}
+		\item To see that $\sp$ cannot be a right adjoint to $S$, consider the ``double loop'' $\mathcal{D}=(2, 1, !_2, !_2)$ depicted aside.
+$\sp(\mathcal{D})$ is then isomorphic to the graph $\mathcal{G}=(2, 4, s_{\mathcal{G}}, t_{\mathcal{G}})$ with
+		\[s_{\mathcal{G}}(0) = 0 \quad  t_{\mathcal{G}}(0) =  1 \quad  s_{\mathcal{G}}(1) = 2 \quad  t_{\mathcal{G}}(1) = 3 \]
+
+		Let $\mathcal{H}$ be $(\emptyset, 1, ?_1, ?_1)$, which is clearly a separated hypergraph.
+Now,  $\shyp(\mathcal{H}, \sp(\mathcal{D}))$ has the same cardinality of  $\shyp(\mathcal{H}, \mathcal{G})$, which is $4$, while $\hyp(S(\mathcal{H}), \mathcal{D})$ is a singleton.
+		\item Consider now the ``single loop'' $\mathcal{L}=(1, 1, \id{1}, \id{1})$.
+Then $\sp(\mathcal{L})$ is isomorphic to $(1, 2, \id{2}, \id{2})$ and so there are no arrows $\mathcal{L}\to S(\sp(\mathcal{L}))$.
+In particular this shows that $\sp$ cannot be left adjoint to $S$.
+	\end{itemize} 
+\end{rem}
+\end{minipage}
 \hfill
-\begin{minipage}[r]{.22\linewidth}
+\begin{minipage}[r]{.27\linewidth}
 	\begin{tikzpicture}
@@
 			\node[style=node] (v) at (0, 0){};
-                \node[style=none] (vlab) at (0, -0.4){$v$};
-
-                \node[style=small box] (n) at (-1.8, 0.4) {};
-                \node[style=none] (nlab) at (-1.8, 0.9) {$n$};
-                \node[style=none] (nattach) at (-1.6, 0.4) {};
-
-                \node[style=small box] (const) at (-1.8, -0.4) {};
-                \node[style=none] (constlab) at (-1.8, -0.9){$a$};
-                \node[style=none] (constattach) at (-1.6, -0.4){};
-
-                \node[style=medium box] (times) at (0, 1.8) {};
-                \node[style=none] (timeslab) at (0, 2.6) {$*$};
-                \node[style=none] (timesin1) at (-0.3, 2.1) {};
-                \node[style=none] (timesin2) at (-0.3, 1.5) {};
-                \node[style=none] (timesout) at (0.2, 1.8){};
-
-                \node[style=medium box] (div) at (0, -1.8) {};
-                \node[style=none] (divlab) at (0, -2.6) {$/$};
-                \node[style=none] (divin1) at (-0.3, -2.1) {};
-                \node[style=none] (divin2) at (-0.3, -1.5) {};
-                \node[style=none] (divout) at (0.2, -1.8){};
+			\node[style=none] (vlab) at (0, 0.3){$0$};
+			\node[style=small box] (times) at (-1, 1) {};
+			\node[style=none] (timeslab) at (-1, 1.5) {$0$};
+			\node[style=none] (timesin) at (-1, .7) {};
+			\node[style=none] (timesout) at (-.7, 1){};
+			\node[style=small box] (div) at (1, 1) {};
+			\node[style=none] (divlab) at (1, 1.5) {$1$};
+			\node[style=none] (divin) at (1, .7) {};
+			\node[style=none] (divout) at (.7, 1){};
+
+			\node[style=node] (a) at (-1, -1.5){};
+			\node[style=none] (alab) at (-1, -1.2){$0$};
+			\node[style=node] (b) at (1, -1.5){};
+			\node[style=none] (blab) at (1, -1.2){$1$};
+			\node[style=node] (c) at (-1, -2.5){};
+			\node[style=none] (clab) at (-1, -2.8){$2$};
+			\node[style=node] (d) at (1, -2.5){};
+			\node[style=none] (dlab) at (1, -2.8){$3$};
+
+			\node[style = small box] (zero) at (0, -1.5) {};
+			\node[style=none] (zeroin) at (-.3, -1.5) {};
+			\node[style=none] (zeroout) at (.3, -1.5){};
+			\node[style=none] (zlab) at (0, -1){$0$};
+
+			\node[style=small box] (1) at (0, -2.5) {};
+			\node[style=none] (unoin) at (-.3, -2.5) {};
+			\node[style=none] (unoout) at (0.3, -2.5){};
+			\node[style=none] (ulab) at (0, -3){$1$};
 		\end{pgfonlayer}
@@
 		\begin{pgfonlayer}{edgelayer} 
-                \draw[style=diredge, in=180, out= 112.5] (v) to (timesin2.center); 
-                \draw[style=diredge,out=135, in= 180] (v) to (timesin1.center);
-                \draw[style=diredge,in=165, out=0] (nattach.center) to (v);
-
-                \draw[style=diredge,out=0, in=-165] (constattach.center) to (v);
-                \draw[style=diredge,in=180, out= -112.5] (v) to (divin2.center); 
-                \draw[style=diredge,out=-135, in= 180] (v) to (divin1.center);
-
-                \draw[style=diredge, in=30, out=0] (timesout.center) to (v);
-                \draw[style=diredge, in=-30, out=0] (divout.center) to (v);
+			\draw[style=diredge,out=180, in= 270] (v) to (timesin.center);
+			\draw[style=diredge,out=0, in= 270] (v) to (divin.center);
+			\draw[style=diredge, in=135, out=345] (timesout.center) to (v);
+			\draw[style=diredge, in=45, out=195] (divout.center) to (v);
+			\draw[style=diredge, in=180, out=0] (a.center) to (zeroin.west);
+			\draw[style=diredge, in=180, out=0] (c.center) to (unoin.west);
+			\draw[style=diredge, in=180, out=0] (zeroout.east) to (b.west);
+			\draw[style=diredge, in=180, out=0] (unoout.east) to (d.west);
 		\end{pgfonlayer}
@@
 \end{minipage}
+
+\fi
+
+The following result will be useful. A proof of it is \Cref{proof:seplim}
+
+\begin{restatable}{lem}{seppb}\label{lem:seplim}
+	$\shyp$ is closed in $\hyp$ under connected limits.
+\end{restatable}
+
+\begin{exa}\label{ex:noterm}
+In general $\shyp$ is not complete. For instance it does not have a terminal object. Too see this notice that the $\mathcal{H}:=(\emptyset, 1, ?_{1^\star}, 1_{1^\star} )$ is separated and that 
+$\shyp(\mathcal{H}, \mathcal{G})$ is in bijection with $V_{\mathcal{G}}$ for every hypergraph $\mathcal{G}$.
+Thus if  $\mathcal{T}$ is terminal in $\shyp$, then its set of vertices $V_{\mathcal{T}}$ must have cardinality $1$.
+
+Since $\mathcal{T}$ must be separated, we have two (non disjoint) cases:
+
+\begin{minipage}[l]{.65\linewidth}
+	\begin{itemize}
+		\item  all the hyperedges of $\mathcal{T}$ have sources with length zero; 
+		\item all the hyperedges of $\mathcal{T}$ have targets with length zero.
+	\end{itemize}
+\end{minipage}
+\begin{minipage}[r]{.15\linewidth}
+\begin{tikzpicture}
+	\begin{pgfonlayer}{nodelayer}
+		\node[style=medium box] (div) at (5, 1.3) {};
+		\node[style=none] (divlab) at (5, 2) {$e$};
+		\node[style=none] (divin1) at (4.7, 1.6) {};
+		\node[style=none] (divin2) at (4.7, 1) {};
+		\node[style=none] (divout) at (5.2, 1.3){};
+
+		\node[style=node] (a) at (3, 1.6){};
+		\node[style=none] (alab) at (2.6, 1.7){$a$};
+		\node[style=node] (b) at (3, 1){};
+		\node[style=none] (blab) at (2.6, 1){$b$};
+		\node[style=node] (d) at (7, 1.3){};
+		\node[style=none] (dlab) at (7, 1.6){$c$};
+	\end{pgfonlayer}
+
+	\begin{pgfonlayer}{edgelayer}
+		\draw[style=diredge] (a) to (divin1.west); 
+		\draw[style=diredge] (b) to (divin2.west);
+		\draw[style=diredge] (divout.center) to (d);
+	\end{pgfonlayer}
+\end{tikzpicture}
+\end{minipage}
+
+\medskip
+In both cases there are no morphism from the hypergraph depicted on the right and $\mathcal{T}$.
+\end{exa}
+
+\smallskip 
+\noindent 
+\begin{minipage}[l]{.58\linewidth}
+\begin{exa}\label{ex:nopush}
+	In general $\shyp$ does not have pushout.
+For instance consider the solid part of diagram aside.
+Let us call the two unnamed hypergraphs on the top row $\mathcal{H}$ and $\mathcal{K}$, respectively, while will call the third one $\mathcal{Q}$.
+
+	Suppose that there exists $\mathcal{G}$ and arrows $(p_1, p_2)\colon \mathcal{Q}\to \mathcal{G}$ and $(q_1, q_2)\colon \mathcal{K}\to \mathcal{G}$ which make the square a pushout in $\shyp$. 
+	By construction we have
+	\[s_{\mathcal{G}}(q_1(e)) = q^\star_2(s_{\mathcal{K}}(e)) = q^\star_2(j^\star_2(v))=p^\star_2(i^\star_2(v)) = p^\star_2(t^\star_{\mathcal{Q}}(e))= t_{\mathcal{G}}(p_2(e))\]
+	and so $\mathcal{G}$ cannot ber in $\shyp$, yielding a contradiction.
+\end{exa}
+\end{minipage} \hfill \begin{minipage}[r]{.5\linewidth} \vspace{-2cm}
+\xymatrix@R=6pt@C=30pt{\begin{tikzpicture}
+		\node[style=node](v) at (0, 0){};
+	\node[style=none] at(0, 0.3){$v$};
+	\end{tikzpicture}\ar[d]_{(i_1, i_2)} \ar[r]^-{(j_1, j_2)}  &
+	\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+			\node[style=node](v) at (-1, 0){};
+			\node[style=none] at(-1, 0.3){$j_2(v)$};
+			\node[style=node](u) at (1, 0){};
+			\node[style=none] at(1, 0.3){$w$};
+			\node[style=small box] (edge) at (0, 0) {};
+			\node[style=none] (edge) at (0, 0.5) {$e$};
+			\node[style=none] (in) at (-0.3, 0) {};
+			\node[style=none] (out) at (0.2, 0){};
+		\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw[style=diredge] (v) to (in.east); 
+		\draw[style=diredge] (out.east) to (u.west);
+	\end{pgfonlayer}
+	\end{tikzpicture} 
+	\ar@{.>}[d]^{(q_1, q_2)} \\\begin{tikzpicture}[baseline=(v.base)]\begin{pgfonlayer}{nodelayer}
+			\node[style=node](v) at (-1, 0){};
+			\node[style=none] at(-1, 0.3){$u$};
+			\node[style=node](u) at (1, 0){};
+			\node[style=none] at(1, 0.3){$i_2(v)$};
+			\node[style=small box] (edge) at (0, 0) {};
+			\node[style=none] (edge) at (0, -0.5) {$e$};
+			\node[style=none] (in) at (-0.3, 0) {};
+			\node[style=none] (out) at (0.2, 0){};
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{edgelayer}
+			\draw[style=diredge] (v) to (in.east); 
+			\draw[style=diredge] (out.east) to (u.west);
+		\end{pgfonlayer}
+	\end{tikzpicture} 
+	\ar@{.>}[r]_-{(p_1, p_2)}&
+	\mathcal{G}
+	}
+\end{minipage}
+
+\paragraph{Left-monogamous hypergraphs}
+
+We can now turn to the second subcategory of $\hyp$ of interest, that of \emph{left-monogamous} hypergraphs \cite{milosavljevic2023string,fritz2023free}.
+
+\begin{defi}
+	Let $\mathcal{H}=(E_{\mathcal{H}}, V_{\mathcal{H}}, s_{\mathcal{H}}, t_{\mathcal{H}})$ be an hypergraph.
+We define two functions $\ind{H}, \outd{H}\colon V_{\mathcal{H}}\times E_{\mathcal{H}}\rightrightarrows \mathbb{B}$ where $\ind{H}(v,e)$ is the number of occurences of $v$ in $s_{\mathcal{H}}(e)$ and $\outd{H}(v,e)$ that of $v$ in $t_{\mathcal{H}}(e)$.
+
+ 	If $v$ is such that $\outd{H}(v,e)=0$ for every hyperedge $e$ we say that $v$ is an \emph{input} node. We will denote the set of input nodes by $\ino{H}$
+
+ 		 	A hypergraph $\mathcal{H}$ is \emph{left-monogamous} if for every $v$ in $V_\mathcal{H}$, $\outd{H}(v,e)$ is nonzero for only finitely many hyperedges and
+ 		 	\[\sum_{e\in E_{\mathcal{H}}} \outd{H}(v, e) = 1 - \chi_{\ino{H}}(v)\]
+ 		 	where $\chi_{\ino{H}}\colon V_{\mathcal{H}}\to 2$ is the characteristic function of $\ind{H}$.
+
+ 	We will denote by $\lmo$ the full subcategory of $\hyp$ given by left-monogamous hypergraphs. The corresponding inclusion functor will be denoted by $M$.
+\end{defi}
+
+\begin{rem}We can rephrase the previous definition in a more elementary way.
+Let $\mathcal{H}$ be a hypergraph, indeed if $v$ is an input node then there are no edges with $\outd{H}(v, e)\neq 0$ and so the equation above is automatically satisfied.
+If $v$ does not belong to $\ino{H}$, then the request of left monogamy amount to the existence of precisely one hyperedge $e$ such that $v$ occurs precisely one time in $t_{\mathcal{H}}(e)$.
+\end{rem} 
+\begin{rem}In \cite{fritz2023free} the definition of left-monogamous hypergraphs includes the request of \emph{acyclicity}.  We prefer to deal with acyclicity separately, see Paragraph \ref{sub:ac}.
+\end{rem}
+
+\begin{rem}
+	Every separated hypergraph is left-monogamous.
+Indeed if $\mathcal{H}$ is separated then there exists at most one $e\in E_{\mathcal{H}}$ such that $\outd{H}(v, e) \neq 0$.
+Moreover, in a separated graph the target of an hyperedge cannot have repeated letters and so we have that  $\outd{H}(v, e) = 1$ for at most one $e\in E_{\mathcal{H}}$.
+Left-monogamy now follows at once.
+\end{rem}
+
+\begin{exa} The hypergraph of example \Cref{exa_2} is left-monogamous but not separated.
+\end{exa}
+
+\noindent
+\begin{minipage}[l]{.6\linewidth}
+	\begin{exa}The hypergraphs $\mathcal{G}$ and $\mathcal{H}$ below are examples of non left-monogamous hypergraph.
+In the first the left-monogamy fails because $\outd{\mathcal{G}}(a, e) = 2$, while in the second we have \[\outd{H}(u, e_1) + \outd{H}(u, e_1)=1+1 = 2\]
+	\end{exa}
+\end{minipage} \hfill 
+\begin{minipage}[r]{.35\linewidth}
+		\begin{tikzpicture}
+		\begin{pgfonlayer}{nodelayer}
+			\node[style=medium box] (div) at (0, 0) {};
+			\node[style=none] (divlab) at (0, .7) {$e$};
+			\node[style=none] (divin1) at (.2, .2) {};
+			\node[style=none] (divin2) at (.2, -.2) {};
+			\node[style=none] (divout) at (-.3, 0){};
+
+			\node[style=node] (a) at (2, 0){};
+			\node[style=none] (alab) at (2, .3){$v$};
+			\node[style=node] (d) at (-2, 0){};
+			\node[style=none] (dlab) at (-2, .3){$w$};
+
+			\node[style=node] (e) at (0, -1.5){};
+			\node[style=none] (u) at (0, -1.2){$u$};
+			\node[style=small box] (c1) at (-2, -1.5) {};
+			\node[style=small box] (c2) at (2, -1.5) {};
+			\node[style=none](o) at (-1.7, -1.5){};
+			\node[style=none] (olab) at (-2, -1) {$e_1$};
+			\node[style=none] (olab) at (2, -1) {$e_2$};
+			\node[style=none](i) at (1.8, -1.5){};
+		\end{pgfonlayer}
+
+		\begin{pgfonlayer}{edgelayer}
+			\draw[style=diredge, in=135, out= 45] (divin1.east) to (a); 
+			\draw[style=diredge, in=-135, out= -45] (divin2.east) to(a) ;
+			\draw[style=diredge] (d) to (divout.center);
+			\draw[style=diredge] (o) to (e);
+			\draw[style=diredge] (i) to (e);
+		\end{pgfonlayer}
+	\end{tikzpicture}
+	\end{minipage}
+
+\medskip 	
+The remaining of this section is devoted to the proof of quasiadhesivity of $\lmo$. We begin by computing pullbacks and equalizers of left-monogamous hypergraphs .
+
+\begin{rem}Notice that  $\lmo$ is not complete: for instance it lacks a terminal object.
+The reasoning is similar to that of \Cref{ex:noterm}: if $\mathcal{T}$ is terminal, since  $\mathcal{H}:=(\emptyset, 1, ?_{1^\star}, 1_{1^\star} )$ is left-monogamous, we have that $V_{\mathcal{T}}$ must be a singleton.
+We have two possibilities:
+
+\medskip 
+\begin{minipage}[l]{.65\linewidth}
+	\begin{itemize}
+		\item  all the hyperedges of $\mathcal{T}$ have the empty word as target.
+		\item there is a (necessarily unique) $\mathcal{T}$ with a target of length one.
+	\end{itemize}
+\end{minipage}
+\begin{minipage}[r]{.15\linewidth}
+	\begin{tikzpicture}
+
+\begin{pgfonlayer}{nodelayer}
+	\node[style=medium box] (div) at (0, 0) {};
+	\node[style=none] (divlab) at (0, .7) {$e$};
+	\node[style=none] (divin1) at (.2, .3) {};
+	\node[style=none] (divin2) at (.2, -.3) {};
+	\node[style=none] (divout) at (-.3, 0){};
+
+	\node[style=node] (a) at (2, .3){};
+	\node[style=none] (alab) at (2.3, .3){$v$};
+	\node[style=node] (b) at (2, -.3){};
+	\node[style=none] (ulab) at (2.3, -.3){$u$};
+	\node[style=node] (d) at (-2, 0){};
+	\node[style=none] (dlab) at (-2, .3){$w$};
+\end{pgfonlayer}
+
+\begin{pgfonlayer}{edgelayer}
+	\draw[style=diredge] (divin1.east) to (a); 
+	\draw[style=diredge] (divin2.east) to(b) ;
+	\draw[style=diredge] (d) to (divout.center);
+\end{pgfonlayer}
+	\end{tikzpicture}
+\end{minipage}
+
+\medskip
+In both cases there are no morphism from the hypergraph depicted on the right and $\mathcal{T}$. 
+\end{rem}
+
+An elementary, but fundamental observation is given by the following (see \Cref{proof:count} for a proof).
+
+\begin{restatable}{prop}{count}\label{prop:count}
+	Let $(f,g)\colon \mathcal{G}\to \mathcal{H}$ be an arrow in $\hyp$.
+	The following are true:
+	\begin{enumerate}
+		\item for every $v\in V_{\mathcal{H}}$ and $e\in E_\mathcal{G}$ it holds:
+	\begin{align*}\ind{H}(f(e), g(v))&= \ind{G}(e, v)\cdot \abs{g^{-1}(g(v))\cap \mathsf{set}(s_{\mathcal{G}}(e))} \\\outd{H}(f(e), g(v))&= \outd{G}(e, v)\cdot \abs{g^{-1}(g(v))\cap \mathsf{set}(t_{\mathcal{G}}(e))}
+	\end{align*}
+		where, for $w\in V^\star_{\mathcal{G}}$, $\mathsf{set}(w)$ is the set of nodes appearing in $w$;
+		\item $\lmo$ is closed in $\hyp$ under subobject: if $(f, g)$ is mono and $\mathcal{H}$ is left-monogamous, then $\mathcal{G}$ is left-monogamous too.
+	\end{enumerate}
+\end{restatable}
+
+Since $\lmo$ is a full subcategory of $\hyp$, 
+\Cref{prop:count} provides equalizers of left-monogamous hypergraphs.
+\begin{cor}\label{cor:eq}
+	$\lmo$ is closed in $\hyp$ under equalizers.
+\end{cor}
+
+\begin{restatable}{lem}{lmol}
+	$\lmo$ is closed in $\hyp$ under pullbacks and equalizers.
+\end{restatable}
+
+\begin{defi}
+classe di morfismi
+\end{defi}
+
+\begin{prop}
+	contenuto...
+\end{prop}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\paragraph{Acyclic hypergraphs}\label{sub:ac}
+
+\subsection{Labelled hypergraphs}\label{sssect:hyp_alg_sign}
+
+Our interest for hypergraphs stems from their use as a graphical representation of algebraic terms. We thus need a way to label hyperedges with symbols taken from a signature.
+
+\begin{exa}segnature The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
+\end{exa}
 
@@
 		Now, consider a coprojection $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$.
-By the second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V_\mathcal{H}^{\star}$ of words of length $1$, i.e.~all hyperedges must have a single target vertex, that is $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
+By the second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V_\mathcal{H}^{\star}$ of words of length $1$, i.e.~all hyperedges must have targets of length $1$, that is $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
 	\end{rem}
@@
 \begin{minipage}[r]{.15\linewidth}
-	\xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\ari_\Sigma}& \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\gamma_1}& \mathbb{N}}
+	\xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]^{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\ari_\Sigma}& \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]^{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\gamma_1}& \mathbb{N}}
 \end{minipage}
@@
 
-\subsection{Term Graphs}
+\subsubsection{Labelled left-monogamous hypergraphs}
+
+\color{red}
+TO DO - questo comprende anche la sezione successiva (?) come sottosezione + versione etichettata (anche con cose monoidali) dopo
+
+Ipergrafi scoppiati con equivalenza/congruenza -> adesività (spero) + versione etichettata (monoidale boh)
+
+\color{black}
+\paragraph{Term Graphs}\label{par:tg}
 Term graphs have been adopted as a convenient way to represent terms over a signature with an explicit sharing of sub-terms,
@@
 \end{cor}
+
+TO DO: aciclici
 
@@
 \noindent 
-\parbox{9.5cm}{\begin{rem}\label{rem:obv}
-Let $T_\Sigma:  \EqHyp_{\Sigma} \to \hyp_{\Sigma}$ the forgetful functor lifting
-$T:  \EqHyp \to \hyp$.
+\begin{minipage}[l]{.72\linewidth}
+	\begin{rem}\label{rem:obv}
+		Let $T_\Sigma:  \EqHyp_{\Sigma} \to \hyp_{\Sigma}$ the functor sending an object of $\EqHyp_{\Sigma}$ to its underlying  labelled hypergraph.
 		%
@@
 Thus there exists a functor $S_\Sigma$ as in the diagram on the right.
-\end{rem}}
+	\end{rem}
+\end{minipage}
 \hfill 
-\parbox{4cm}{\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}}
+\begin{minipage}[r]{.23\linewidth}
+	\xymatrix{\EqTG_{\Sigma} \ar[r]^{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}
+\end{minipage}
 
@@
 \noindent
-\parbox{11cm}{\hspace{15pt}Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $J_\Sigma$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.
-By \Cref{lem:reg,prop:monos_in_eqhyps}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.} \hfill
-\parbox{2cm}{\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]_{h_Q}& Q_{\mathcal{H}}} }
-
-\smallskip 
+\begin{minipage}[l]{.8\linewidth}
+	Let now $\mathcal{T}$ be the class of morphism in $\EqTG_{\Sigma}$ whose image through $J_\Sigma$ is in $\pbc_\Sigma$ and whose image through $S_\Sigma$ is a regular mono in $\tg$.
+By \Cref{lem:reg,prop:monos_in_eqhyps}, we have that a morphism $(h_E, h_V, h_Q)\colon (\mathcal{G},l)\to (\mathcal{H}, l')$ is in $\mathcal{T}$ if and only if all of its components are injections and the square on the right is a pullback.
+\end{minipage} \hfill 
+\begin{minipage}[r]{.18\linewidth}
+	\xymatrix{V_{\mathcal{G}}\ar@{>->}[r]^{h_V} \ar@{>>}[d]_{q_{\mathcal{H}}}& V_{\mathcal{H}} \ar@{>>}[d]^{q_{\mathcal{H}}}\\ Q_{\mathcal{G}} \ar@{>->}[r]_{h_Q}& Q_{\mathcal{H}}}
+\end{minipage}
+
 In particular, by \Cref{cor:term} and \Cref{lemma:stab}, $\mathcal{T}$ contains all isomorphisms, is closed under composition and decomposition and stable under pushout and pullbacks.
@@
 encompass equivalence classes which are closed under the target arrow, i.e.~under operator composition for term graphs, thus precisely capturing EGGs.
-%
-%\todo{introduction}
 
@@
 \noindent
-\parbox{11.5cm}{\begin{restatable}{lem}{epo}\label{lem:epo}
+\begin{minipage}[l]{.83\linewidth}
+	\begin{restatable}{lem}{epo}\label{lem:epo}
 		Suppose that the square on the right is a pushout in $\EqHyp$ and that $m$ is a mono in $\pbc$. If $\mathcal{G}_1$, $\mathcal{G}_2$ and $\mathcal{G}_3$ are e-hypergraphs, then $\mathcal{P}$ is 
@@
 		%an object of $\egg$ too.
-\end{restatable}}\hfill 
-\parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar@{>->}[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
-
-\commentato{ 
-\begin{restatable}{cor}{rege}\label{cor:rege}
-		An arrow $h\colon \mathcal{G \to H}$  is a regular mono in $\egg$ if and only if $I(h)$ is a regular mono in $\hyp$.
-In particular a morphism of $\egg$ is a regular mono if and only if all its components are injections.
 	\end{restatable}
-\begin{proof}
-	contenuto...
-\end{proof}
-}
+\end{minipage}\hfill 
+\begin{minipage}[r]{.15\linewidth}
+	\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]_{h}\ar@{>->}[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]^{z}&\mathcal{P}}
+\end{minipage}
 
@@
 By definition and \Cref{lem:pbmono} we have that such class is closed under composition and decomposition, it contains all isomorphisms and it is stable under pullbacks.
-Using \Cref{lem:pbmono,lem:epo} we can further deduce that it is stable under pushouts.
-Then \Cref{thm:slice-functors,cor:eqade} yield the following.
+Using \Cref{lem:pbmono} and \Cref{lem:epo} we can further deduce that it is stable under pushouts.
+Then \Cref{thm:slice-functors} and \Cref{cor:eqade} yield the following.
 
@@
 
-\samepage{\begin{prop}\label{prop:varie}
+\begin{prop}\label{prop:varie}
 	Let $\Sigma$ be an algebraic signature. Then the following hold
@@
 \noindent 
-\parbox{7.5cm}{\begin{rem}
+\begin{minipage}[l]{.58\linewidth}
+	\begin{rem}
 		Now that we have put all the structures of this work in place, it is worthwhile to give a visual map of all the categories that we have discussed/introduced and of the relationships between them.
 We will use the curved arrows to denote full and faithful inclusions.
-\end{rem}}\hfill \parbox{4cm}{\xymatrix@R=15pt@C=15pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]_{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]_{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]_{T}\\ \tg \ar@{^{(}->}[r]_{I_\Sigma}& \hyp_{\Sigma} \ar[r]_{U_\Sigma}  &\hyp}}
+	\end{rem}
+\end{minipage}\hfill
+\begin{minipage}[r]{.20\linewidth}
+	\xymatrix@R=10pt@C=20pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]^-{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]^-{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]^{T}\\ \tg \ar@{^{(}->}[r]^-{I_\Sigma}& \hyp_{\Sigma} \ar[r]^-{U_\Sigma}  &\hyp}
+\end{minipage}
 
@@
 
-Reasoning as in the previous sections, \Cref{prop:limt,prop:pot} now give us the following.
+Reasoning as in the previous sections, \Cref{prop:limt} and \Cref{prop:pot} now give us the following.
 
@@
 \end{cor}
+
+\subsubsection{BOH}\label{sec:sepegg}
+
+qui vanno gli egg fatti con i separati
+
+\subsubsection{BOH}\label{sec:lmegg}
+
+qui vanno gli egg fatti con i left monogamous (probabilmente sussume la 5.2)
 
@@
 Variables in a term graph are represented as nodes that do not occur among the targets of an edge, 
-thus the rule can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
-
-\begin{center}
+thus the rule can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$:
+\[
 	\hspace{.25cm}
@@
 	}
-\end{center}
-
-\noindent
+\]
+
 In this case $L$ is the minimally shared EGG corresponding to the term $x / x$,
@@
 Thus, the solution in~\cite{ghica}  is  more general than ours since it can be lifted to term graphs defined over categories other than
-$\Set$.
-%
-At the same time, we both consider the DPO approach for rewriting, even if only our solution guarantees that the resulting category
+$\Set$. At the same time, we both consider the DPO approach for rewriting, even if only our solution guarantees that the resulting category
 is actually $\mathcal{M}$-adhesive, thus allowing to exploit all the features of the framework
@@
 
-\newpage
+\subsection{Proofs for \Cref{sec:hyper}}
+\seppb*
+\begin{proof}\label{proof:seplim}
+	Let $F\colon \D\to \shyp $ be a diagram with a connected category as domain and let $(\mathcal{L}, \{(p_E^D, p^D_V)\}_{D\in \D})$ be a limit for $S\circ F$.
+We have to show that $\mathcal{L}$ is separated.
+
+	By \Cref{lim} and Propositions \ref{prop:fact} and \ref{prop:com} we know that  $(V_\mathcal{L}, \{p_{V, D}\}_{D\in \D})$  and $(E_\mathcal{L}, \{p_{E, D}\}_{D\in \D})$ are limiting cone for, respectively,  $U_{\hyp}\circ S\circ F$ and $V_{\hyp}\circ S\circ F$, where $U_{\hyp}, V_{\hyp}$.
+We proceed by cases.
+	\begin{itemize}
+		\item Suppose that there exists a node $v\in V_{\mathcal{L}}$ appearing two times in  $s_{\mathcal{L}}(e)$ for some hyperedge $e\in E_{\mathcal{L}}$.
+Thus there are indexes $1\leq i, k \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ with $i\neq k$  such that
+		\[(s_{\mathcal{L}}(e))_i=v \qquad  (s_{\mathcal{L}}(e) )_k= v\]
+
+		Since $\D$ is connected then it is non empty. Let  $D$ be an object of $\D$, then we have:
+		\begin{align*}
+		&(s_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(s_{\mathcal{L}}(e)))_i=p^\star_{V, D}((s_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((s_{\mathcal{L}}(e))_k)=(p^\star_{V,D}(s_{\mathcal{L}}(e)))_k=(s_{S(F(D))}( p_{E,D}(e)))_k
+		\end{align*}
+		contradicting the fact that $S(F(D))$ is separated.
+
+		Similarly, suppose that there is $v\in V_{\mathcal{H}}$ such that
+			\[(t_{\mathcal{L}}(e))_i=v \qquad  (t_{\mathcal{L}}(e) )_k= v\]
+			for some $e\in E_{\mathcal{H}}$ and $1\leq i, k \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ with $i\neq k$ . Then for any $D\in \D$:
+			\begin{align*}
+				&(t_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(t_{\mathcal{L}}(e)))_i=p^\star_{V, D}((t_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((t_{\mathcal{L}}(e))_k)=(p^\star_{V,D}(t_{\mathcal{L}}(e)))_k=(t_{S(F(D))}( p_{E,D}(e)))_k
+			\end{align*}
+			which yields again a contradiction.
+		\item Suppose that there exist two hyperedges $e, e'\in E_{\mathcal{L}}$ and  a node $v\in V_{\mathcal{L}}$ such that \[(s_{\mathcal{L}}(e))_i=v \qquad  (t_{\mathcal{L}}(e') )_k= v\]
+		for indexes $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ and $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $.
+We have already noticed that$\D$ is non empty.
+Let $D\in \D$, we have:
+		\begin{align*}&(s_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(s_{\mathcal{L}}(e)))_i=p^\star_{V, D}((s_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((t_{\mathcal{L}}(e'))_k)=(p^\star_{V,D}(t_{\mathcal{L}}(e')))_k=(t_{S(F(D))}( p_{E,D}(e')))_k
+		\end{align*}
+		But this is a contradiction since, by hypothesis, $S(F(D))$ is separated. 
+		\item Let now $e, e'$ be two distinct hyperedges of $\mathcal{L}$ such that there exists $v\in V_{\mathcal{L}}$ with the property that 
+		 \[(s_{\mathcal{L}}(e))_i=v \qquad  (s_{\mathcal{L}}(e') )_k= v\]
+		with $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ and $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $. For every $D\in \D$ we can compute to get:
+		\begin{align*}&(s_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(s_{\mathcal{L}}(e)))_i=p^\star_{V, D}((s_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((s_{\mathcal{L}}(e'))_k)=(p^\star_{V,D}(s_{\mathcal{L}}(e')))_k=(s_{S(F(D))}( p_{E,D}(e')))_k
+		\end{align*}
+		Since $S(F(D))$ is an object of $\shyp$ we get that, for every $D\in \D$,  $p_{E,D}(e)$ and $p_{E,D}(e')$ must be equal.
+Since $(E_\mathcal{L}, \{p_{E, D}\}_{D\in \D})$ this entails that $e = e'$, which is a contradiction.
+		\item  We proceed as before, supposing that $e$ and $e'$ are distinct elements of $\mathcal{L}$ for which there are $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$, $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $ and a node $v\in V_{\mathcal{L}}$ such that:
+				\[(t_{\mathcal{L}}(e))_i=v \qquad  (t_{\mathcal{L}}(e') )_k= v\]
+		Then, givem $D\in \D$ we have:
+		\begin{align*}&(t_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(t_{\mathcal{L}}(e)))_i=p^\star_{V, D}((t_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((t_{\mathcal{L}}(e'))_k)=(p^\star_{V,D}(t_{\mathcal{L}}(e')))_k=(t_{S(F(D))}( p_{E,D}(e')))_k
+		\end{align*}
+		Therefore,  $p_{E,D}(e)$ and $p_{E,D}(e')$ coincide for every $D\in \D$. Thus  $e = e'$ and we end up again with a contradiction. \qedhere 
+	\end{itemize}
+\end{proof}
+
+\count*
+\begin{proof}\label{proof:count}
+	\begin{enumerate}
+		\item Let $n$ and $m$ be the lengths of, respectively $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ and suppose that
+		\[s_{\mathcal{G}}(e)=\prod_{i=1}^{n}a_i \qquad t_{\mathcal{G}}(e)=\prod_{i=1}^{n}b_i\]
+
+		\item \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\begin{proof}\label{proof:prod}
+\end{proof}
 \subsection{Proofs for \Cref{hypereq}}\label{app:due}

### 2025-07-28 jlamp/jlamp.tex
minima

@@
 
-\author[1]{Roberto Biondo}
+\author{Roberto Biondo}
 \ead{r.biondo@studenti.unipi.it}
 
-\author[1]{Davide Castelnovo\corref{cor1}%
+\author{Davide Castelnovo\corref{cor1}%
 }
@@
 
-\author[1]{Fabio Gadducci}
+\author{Fabio Gadducci}
 \ead{fabio.gadducci@unipi.it}
@@
 
-\affiliation[1]{organization = {Department of Computer Science, University of Pisa},
-	addressline = {Largo B. Pontecorvo, 3},
-	postcode = {56127},
+\affiliation{organization = {Department of Computer Science, University of Pisa},
 	city = {Pisa}, 
 	country = {Italy}}
+
+\fntext[miur]{Research partially supported by the Italian MUR project PRIN
+20228KXFN2 ``STENDHAL''.}
 

### 2025-07-30 jlamp/jlamp.tex
minima

@@
 This work describes EGGs via adhesive categories. 
-Besides the benefits in itself of a formal presentation, which renders the 
-properties of the data structure precise, the description of the addition of equivalent 
+Besides the usual benefits of a formal presentation, which makes the 
+properties of a data structure precise, describing the addition of equivalent 
 program components using standard graph transformation tools offers the advantages 
@@
 Adhesive categories provides such a disparate set of formalisms with a common abstract framework 
-where many of these general results can be recast and uniformly proved once and for all.
-
-\vspace{.1cm}
+where many general results can be recast and uniformly proved once and for all.
+
+%\vspace{.1cm}
 \noindent
@@
 for being $\mathcal{M}$-adhesive can be a daunting task. For this reason, sufficient criteria have been provided for the core 
-framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, as well as for the extended one of
-$\mathcal{M}$-adhesivity~\cite{CastelnovoGM24}.
-%
-For some structures such as \emph{hypergraphs with equivalence} in~\cite{concur2006}, the question 
+framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, and for the $\mathcal{M}$-adhesivity~\cite{CastelnovoGM24}.
+%
+For structures such as \emph{hypergraphs with equivalence} in~\cite{concur2006}, the question 
 of their $\mathcal{M}$-adhesivity has not yet been settled.
@@
 
-EGGs can be concisely defined as term graphs equipped with a notion of equivalence on nodes
+EGGs can be concisely defined as (acyclic) term graphs equipped with an equivalence on nodes
 that is closed under the operators of a signature~\cite[Section~4.2]{DetlefsNS05}.
@@
 whose edges are labelled by operators and with
-the possibility of sharing subtrees, with an additional equivalence relation $\equiv$ on nodes that 
-is closed under composition. In plain words and using a toy example:
+possibly sharing subtrees, with an equivalence relation $\equiv$ on nodes that 
+is closed under composition. In plain words and with a toy example:
 if $a$ and $b$ are two constants such that $a \equiv b$, then $f(a) \equiv f(b)$ for any unary operator $f$.
@@
 The advantages from this characterisation are two-fold. On the one side, 
-we put the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
+the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
 On the other side, describing the optimisation steps via the DPO approach
@@
 
-\emph{Synopsis}
+\emph{Synopsis.}
 The paper has the following structure. 
@@
 
+\emph{Differenza con la versione da conferenza}
+
 \section{Facts about $\mathcal{M}$-adhesive categories and kernel pairs}\label{sec:ade}
 
-We open this background section by fixing some notation. Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
-``$X\in \X$'' means that $X$ is an object of $\X$.
-We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.
+We open the background section by fixing notation. Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
+``$X\in \X$'' means that $X$ is an object of $\X$. We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.  
 Given an object $X$, we  denote by $?_X$ the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one. 
-We will also use the notation $e\colon X\eto Y$ to denote that an arrow $e\colon X\to Y$ is a regular epi.
+The notation $e\colon X\eto Y$ denotes that an arrow $e\colon X\to Y$ is a regular epi.
 
@@
 
-\begin{defi}[\cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}]
+\begin{defi}[\cite{azzi2019essence,ehrig2012,ehrig2014adhesive,heindel2009category,lack2005adhesive}]
 	Let $\X$ be a category and $\mathcal{M}$ a subclass of
@@
 	A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
-	if $\mathcal{M}$-pushouts are Van Kampen. We write $m\colon X \mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
+	if $\mathcal{M}$-pushouts are Van Kampen squares. We write $m\colon X \mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
 \end{defi}
@@
 	\begin{enumerate}
-		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category, $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to \A$ one preserving $\mathcal{M}$-pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
+		\item if $\Y$ is an (strict) $\mathcal{N}$-adhesive category, $L\colon \Y\to \A$ a functor preserving $\mathcal{N}$-pushouts and $R\colon \X\to \A$ 
+		a functor preserving $\mathcal{M}$-pullbacks, then $\comma{L}{R}$ is (strictly) $\comma{\mathcal{N}}{\mathcal{M}}$-adhesive, where
 		\[\comma{\mathcal{N}}{\mathcal{M}}:=\{(h,k) \in \mor(\comma{L}{R}) \mid h\in \mathcal{N}, k\in \mathcal{M}\}\]
@@
 		the categories $\X/X$  and $X/\X$ are, respectively, (strictly) $\mathcal{M}/X$-adhesive and (strictly) $X/\mathcal{M}$-adhesive, where
-		\[\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
-		\mathcal{M}\} \hspace{25pt} X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}\]
+		\[\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in \mathcal{M}\} \hspace{25pt} X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}\]
 		\item for every small category $\Y$, the category $\X^\Y$ of
 		functors $\Y\to \X$ is (strictly) $\mathcal{M}^{\Y}$-adhesive, where
-		$\mathcal{M}^{\Y}:=\{\eta \in \mor(\X^\Y) \mid \eta_Y \in
-		\mathcal{M} \text{ for every } Y\in \Y\}$;
+		\[\mathcal{M}^{\Y}:=\{\eta \in \mor(\X^\Y) \mid \eta_Y \in
+		\mathcal{M} \text{ for every } Y\in \Y\}\];
 		\item if $\Y$ is a full subcategory of $\X$ closed under pullbacks and $\mathcal{M}$-pushouts, then $\Y$ is (strictly) $\mathcal{N}$-adhesive for every class of arrows $\mathcal{N}$ of $\Y$ contained in $\mathcal{M}$ that is stable under pullbacks and pushouts, contains all isos, and is closed under composition and decomposition.
@@
 	\label{ex:adhesive}
-	$\cat{Set}$ is adhesive, and, more generally, every topos is
+	$\cat{Set}$ is adhesive, and in fact every topos is
 	adhesive~\cite{lack2006toposes}. By the closure properties above, every presheaf $[\cat{X},\cat{Set}]$ is adhesive, thus the category
@@
 
-Regular epis are particular well-behaved with respect to their kernel pairs.
+Regular epis are particularly well-behaved with respect to their kernel pairs.
 
@@
 \begin{minipage}[l]{.83\linewidth}
-	\begin{rem}\label[remark]{rem:length} It is well known that $(\mathbb{N}), \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
+	\begin{rem}\label[remark]{rem:length} It is well known that $(\mathbb{N}, \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
 Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathcal{N}\to 1^\star$.
-In particular, every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
+	In particular, for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
 	\end{rem}
@@
 
-Note that by, \Cref{prop:fact}, $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, 
+Note that by \Cref{prop:fact}, $(-)^\star$ preserves pullbacks, while $\pro$ is continuous by definition, 
 hence by \Cref{prop:com} and \Cref{cor:mono} we can deduce the following result.
@@
 
-\Cref{prop:left,prop:com} allow us to deduce immediately the following.
+\Cref{prop:left} and \Cref{prop:com} allow us to deduce immediately the following.
 
@@
 Let us look at the picture below. It represent a hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
-and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair of nodes
+and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ have a pair of nodes as soruce
 	\begin{center}

### 2025-08-03 jlamp/jlamp.tex
minori
minima

@@
 	\begin{rem}\label[remark]{rem:length} It is well known that $(\mathbb{N}, \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
-Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathcal{N}\to 1^\star$.
+Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathbb{N}\to 1^\star$.
 	In particular, for every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
@@
 \begin{exa}\label[example]{exa_2}
-We represent hypergraphs visually: dots denote nodes and boxes hyperedges. Should we be interested in their identity, we put a name near the corresponding dot or box. 
+We represent hypergraphs visually: bullets denote nodes and boxes hyperedges. Should we be interested in their identity, we put a name near the corresponding bullet or box. 
 Sources and targets are represented by lines between dots and squares: the lines from the sources of a hyperedge comes from the left of the box, while the lines to the targets 
 exit from the right of the box.
-Let us look at the picture below. It represent a hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
-and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ have a pair of nodes as soruce
+Let us look at the picture below. It represents a hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
+and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ have a pair of nodes as source
 	\begin{center}
@@
 
-		We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes and $\Delta \circ \ari_\Sigma$ as the source function and $ \Delta \coar_{\Sigma}$ as target function, where $\Delta \colon \mathbb{N}\to 1$ is the isomorphism of \Cref{rem:length}.
+		We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes and $\Delta \circ \ari_\Sigma$ as the source function and $ \Delta \coar_{\Sigma}$ as target function, where $\Delta \colon \mathbb{N}\to 1^\star$ is the isomorphism of \Cref{rem:length}.
 	\end{defi}
@@
  \smallskip 
- We can interpret an arbitrary hypergaph as a \emph{typed} or \emph{colored} monoidal signature: the set of nodes provides the \emph{types} or \emph{colors}, while hyperedges can be thought of as operations, with arity and coarity provided by the source and target function.
-This suggest the following definition, which will be used in Section \ref{par:tg}.
+ We can interpret an arbitrary hypergaph as a \emph{typed} or \emph{colored} monoidal signature: the set of nodes provides the \emph{types} or \emph{colors}, while hyperedges can be thought of as operations, with arity and coarity provided by the source and target functions, respectively.
+This suggests the following definition, which will be used in Section \ref{par:tg}.
 
@@
 	%
-	The functors $\catname{H}\to \Set$ corresponds exactly to hypergraphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
+	The functors $\catname{H}\to \Set$ correspond exactly to hypergraphs: the set of nodes corresponds to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
 \end{rem}
@@
 \begin{rem}It is worth mentioning that limits in $\hyp$ are not computed componentwise.
-By \Cref{prop:fact,prop:com,lim} we know that the two forgetful functors $U_{\hyp}, H_{\hyp}\colon \hyp \to \Set$, sending an hypergraph to, respectively, its set of nodes and that of hyperedges only jointly creates conneted limits.
-For instance, let $\phi\colon \mathbb{N}\to 1^\star$  $(\mathbb{N}, 1, \phi)$
+By \Cref{prop:fact}, \Cref{prop:com}, and \Cref{lim} we know that the two forgetful functors $U_{\hyp}, H_{\hyp}\colon \hyp \to \Set$, sending an hypergraph to, respectively, its set of nodes and its set of hyperedges jointly creates connected limits.
+For instance, let $\phi\colon \mathbb{N}\to 1^\star$  $(\mathbb{N}, 1, \phi)$ -- TO BE COMPLETED
 \end{rem}
@@
 
-Let us begin with the subcategory of $\hyp$ which, in \Cref{sec:sepegg}, will give us the underlying hypergraphs for EGGs with minimally identified tokens.
+Let us begin with the subcategory of $\hyp$, which in \Cref{sec:sepegg} will give us the underlying hypergraphs for EGGs with minimally identified tokens.
 
 \begin{defi} Given a set $X$, we say that two words $X^\star$ are \emph{disjoint} is they do not share any letter.
-An hypergraph $\mathcal{G}=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}})$ is \emph{separated} if:
+An hypergraph $\mathcal{G}=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}})$ is \emph{separated} if for every pair of not necessarily distinct hyperedges $e, e'\in E_{\mathcal{G}}$
 	\begin{enumerate}
-		\item for every hyperedge $e$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ do not have repeated letters;
-		\item for every two, not necessarily distinct, hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint;
-		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $s_{\mathcal{G}}(e')$ are disjoint;
-		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $t_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint.
+	\item $s_{\mathcal{G}}(e)$ and $s_{\mathcal{G}}(e')$ are disjoint, unless $e = e'$;
+	\item $t_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint, unless $e = e'$;	
+	\item $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint.
+%		\item for every hyperedge $e$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ do not have repeated letters;
+%		\item for every two, not necessarily distinct, hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint;
+%		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $s_{\mathcal{G}}(e')$ are disjoint;
+%		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $t_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint.
 	\end{enumerate}
@@
 \end{defi}
-\iffalse 
+
+\marginpar{non basta, non ci devono essere ripetizioni}
+
 \begin{defi}
@@
  Moreover, let $\is{(V_{\mathcal{G}})}$ be the set of isolated nodes  of $\mathcal{G}$ i.e.~those which are not in the image of $s_{\mathcal{G}}$ or of $t_{\mathcal{G}}$.
-Furthermore, let $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}} \cup \{\iota_{is}\})$ be the coproduct of the family $\{V_{e}\}_{e\in E_\mathcal{G}} \cup \{\is{(V_{\mathcal{G}})}\}$ and define:
+Furthermore, let $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}} \cup \{\iota_{is}\})$ be the coproduct of the family $\{V_{e}\}_{e\in E_\mathcal{G}} \cup \{\is{(V_{\mathcal{G}})}\}$ and define
 \[\begin{split}
@@
 
-\fi
-
-The following result will be useful. A proof of it is \Cref{proof:seplim}
+\begin{defi} 
+	isolati e connessi
+\end{defi}
+
+\begin{prop}
+	aggiunto dx
+\end{prop}
+\
+
+Finally, we conclude our exam of separated hypergraph proving a result regarding connected limits. A proof of it is \Cref{proof:seplim}
 

### 2025-08-11 jlamp/jlamp.tex
minori

--- 2025-07-28 jlamp/jlamp.tex
@@
 
-\author{Roberto Biondo}
+\author[1]{Roberto Biondo}
 \ead{r.biondo@studenti.unipi.it}
 
-\author{Davide Castelnovo\corref{cor1}%
+\author[1]{Davide Castelnovo\corref{cor1}%
 }
@@
 
-\author{Fabio Gadducci}
+\author[1]{Fabio Gadducci}
 \ead{fabio.gadducci@unipi.it}
@@
 
-\affiliation{organization = {Department of Computer Science, University of Pisa},
+\affiliation[1]{organization = {Department of Computer Science, University of Pisa},
+	addressline = {Largo B. Pontecorvo, 3},
+	postcode = {56127},
 	city = {Pisa}, 
 	country = {Italy}}
-
-\fntext[miur]{Research partially supported by the Italian MUR project PRIN
-20228KXFN2 ``STENDHAL''.}
 
@@
 		Suppose that in $\Set$ the commuting cube in the diagram on the left is given, whose top face is a pushout, the left and bottom faces are pullbacks,  and $n\colon B\mto D$ is an injection. 
-		Then the following hold
+		Then the following hold true:
 		\begin{enumerate}
@@
 	\begin{enumerate}
-		\item there are arrows $v_{n}\colon X^n\to X^\star $ such that $(X^\star, \{v_{n}\}_{n\in \mathbb{N}})$ is a coproduct;
+		\item there are arrows $v_{n}\colon X^n\mto X^\star $ such that $(X^\star, \{v_{n}\}_{n\in \mathbb{N}})$ is a coproduct;
 		\item for every arrow $f\colon X\to Y$, $f^\star\colon X^\star \to Y^\star$ is the coproduct of the family $\{f^n\}_{n\in \mathbb{N}}$;
@@
 \begin{minipage}[l]{.83\linewidth}
-	\begin{rem}\label[remark]{rem:length} It is well known that $(\mathbb{N}), \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
-Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathcal{N}\to 1^\star$.
-In particular, every set $X$ the arrow $!_\X\colon X\to 1$ induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
+	\begin{rem}\label{rem:length} It is well known that $(\mathbb{N}), \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
+Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathbb{N}\to 1^\star$.
+In particular, for every set $X$ the unique arrow $!_\X\colon X\to 1$ into the terminal induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
 	\end{rem}
 \end{minipage}\hfill \begin{minipage}[r]{.15\linewidth}\noindent
-\xymatrix@R=10pt{1 \ar[r]^{\id{1}} \ar[d]^{u_n}& 1 \ar[d]^{v_n}\\ \mathbb{N} \ar@{.>}[r]^{\Delta}& 1^\star} \hspace{1pt}\\
-\xymatrix@R=10pt@C=22pt{\mathbb{N} \ar[r]^{\Delta} \ar@{.>}[dr]_{\lgh_{X}}& 1^\star\\ & X^\star \ar[u]_{!^\star_X}}
+\xymatrix@R=8pt@C=30pt{1 \ar[r]^{\id{1}} \ar@{>->}[d]^{\delta_n}& 1 \ar@{>->}[d]^{v_n}\\ \mathbb{N} \ar@{.>}[r]^{\Delta}& 1^\star} \hspace{1pt}\\
+\xymatrix@R=8pt@C=28pt{\mathbb{N} \ar[r]^{\Delta} \ar@{<.}[dr]_{\lgh_{X}}& 1^\star\\ & X^\star \ar[u]_{!^\star_X}}
+\end{minipage}
+
+\begin{rem}\label{rem:le} Consider a function $f\colon X\to Y$  and suppose that $(X^\star, \{x_n\}_{n\in \mathbb{N}})$ and $\{Y^\star, \{y_n\}_{n\in \mathbb{N}}\}$ are the coproducts given by the first point of \Cref{prop:fact}, then for every $n\in \mathbb{N}$ we have
+	\begin{align*}
+&\lgh_{Y}\circ f^\star \circ x_n = \lgh_{Y}\circ y_n \circ f^n= \Delta^{-1}\circ !^\star_{Y} \circ y_n\circ f^n =  \Delta^{-1}\circ v_n \circ !^n_{Y} \circ f^n \\=& \Delta^{-1}\circ v_n \circ (!_{Y} \circ f)^n  = \Delta^{-1}\circ v_n \circ (!_{X})^n = \Delta^{-1}\circ !^\star_{X} \circ x_n = \lgh_{X}\circ x_n
+	\end{align*}
+and so $\lgh_{Y}\circ f^\star= \lgh_{X}$.
+\end{rem}
+
+\noindent
+\begin{minipage}[r]{.83\linewidth}
+	\begin{rem}\label{rem:len} Let $X$ be a set.
+It is worth noticing that, for every $n\in \mathbb{N}$, $X^n$ is the preimage of $n$ along $\lgh_{X}$.
+This amount to say that the square aside is a pullback.
+This follows at once from the fact that $\Set$ is \emph{extensive} (see \cite{carboni1993introduction} and also \Cref{word:ext}).
+	\end{rem}
+\end{minipage}\hfill \begin{minipage}[l]{.15\linewidth}
+\xymatrix@R=10pt{X^n \ar@{>->}[r]^{v_n} \ar[d]^{!_{X^n}}& X^\star  \ar[d]^{\lgh_{X}}\\ 1 \ar@{>->}[r]^{\delta_n} & \mathbb{N}}
 \end{minipage}
@@
 
-\begin{prop}[prop]\label{prop:com}
+\begin{prop}\label{prop:com}
 	$\hyp$ is isomorphic to $\comma{\id{\Set}}{\pro^\star}$
@@
 
-\begin{rem}\label{rem:functor}
-	It is worth to point out, as first noted in \cite{bonchi2022string}, that $\hyp$ is equivalent to a category of presheaves. 
-	%
-	Indeed, consider the category $\catname{H}$ in which the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$ and arrows are given by the identities $\id{k,l}$, $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$.
-	%
-	The functors $\catname{H}\to \Set$ corresponds exactly to hypergraphs: nodes correspond to the image of $\bullet$ while the set of hyperedges with source of length $k$ and target of length $l$ corresponds to the image of $(k,l)$ (see \cite{CastelnovoGM24}).
-\end{rem}
-
-In particular, \Cref{rem:functor} entails the following result.
+In order to deal with general limits of hypergraphs, it is worth to recall that, as first noted in \cite{bonchi2022string}, $\hyp$ is equivalent to a category of presheaves.
+
+\begin{defi} We define the category $\catname{H}$  as the one in which the set of objects is given by $ (\mathbb{N}\times \mathbb{N}) + \{\bullet\}$ and arrows are given by the identities $\id{k,l}$, $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$.
+\end{defi}
+
+It is possible to show that hypergraphs corresponds to presheaves over $\catname{H}$ (\cite{bonchi2022string,castelnovo2023thesis,CastelnovoGM24}).
+In \Cref{proof:equi} we report a proof of this claim for the interested reader.
+
+\noindent 
+\begin{minipage}[r]{.75\linewidth}
+	\begin{restatable}{lem}{equi}\label{lem:equi}
+		There is an equivalence of categories $\Set^{\catname{H}}\to \hyp$ sending a functor $F\colon \catname{H}\to \Set$ to $\mathcal{G}_F:=(E_F, F(\bullet), s_{F}, t_F)$, where $(E_F, \{\iota^F_{k,l}\})$ is a coproduct for $\{F(k,l)\}_{k,l\in\mathbb{N}}$
+		and $s_F, t_F\colon E_F\rightrightarrows V^\star_F$ are the unique arrows fitting in the diagrams aside, where $(F(\bullet), \{v^F_n\}_{n\in \mathbb{N}})$ is the coproduct coming from the first point of\Cref{prop:fact} and $s^F_{k,l}, t^F_{k,l}\colon F(k,l)\to F(\bullet)^k$, $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ are the arrows induced by, respectively, $\{F(f_i)\}_{i=0}^{k-1}$ and $\{F(f_i)\}_{i=k}^{k+l-1}$.
+	\end{restatable}
+\end{minipage}\hfill
+\begin{minipage}[l]{.25\linewidth}
+\xymatrix@R=10pt@C=40pt{F(k,l) \ar@{>->}[d]_{\iota^F_{k,l}}\ar[r]_{s^F_{k,l}} & F(\bullet)^k \ar@{>->}[d]^{v^F_k} \\ E_F \ar@{.>}[r]^{s^F} & F(\bullet)^\star}
+\xymatrix@R=10pt@C=40pt{F(k,l) \ar[r]_{t^F_{k,l}} \ar@{>->}[d]_{\iota^F_{k,l}} & F(\bullet)^l\ar@{>->}[d]^{v^F_l}  \\ E_F \ar@{.>}[r]^{t^F} & F(\bullet)^\star}
+\end{minipage}
+
+In particular, \Cref{lem:equi} entails the following result.
 
@@
 
-\begin{rem}It is worth mentioning that limits in $\hyp$ are not computed componentwise.
-By \Cref{prop:fact,prop:com,lim} we know that the two forgetful functors $U_{\hyp}, H_{\hyp}\colon \hyp \to \Set$, sending an hypergraph to, respectively, its set of nodes and that of hyperedges only jointly creates conneted limits.
-For instance, let $\phi\colon \mathbb{N}\to 1^\star$  $(\mathbb{N}, 1, \phi)$
-\end{rem}
-
-\iffalse
-\subsubsection{$\hyp$ as a category of functors}
-
-Following \cite{bonchi2022string}, we can present $\hyp$ as a category of functor over a suitable category.
-
-\begin{defi}Let $\catname{H}$ be the category such that
-	\begin{itemize}
-		\item the set of objects is $ (\mathbb{N}\times \mathbb{N}) \cup \{\bullet\}$;
-		\item arrows are given by the identities $\id{k,l}$ and $\id{\bullet}$ and exactly $k+l$ arrows $f_i\colon (k,l)\rightarrow \bullet$, where $i$ ranges from $0$ to $k+l-1$;
-		\item composition is defined by putting
-		%\begin{equation*}
-			$f_i=f_i\circ \id{k,l}$ and $f_i = \id{\bullet}\circ f_i$
-		%\end{equation*}
-		for every $f_i\colon (k,l)\rightarrow \bullet$.
-	\end{itemize}
-\end{defi}
-
-The idea is that for every functor $F\colon \catname{H}\to \catname{Set}$ we can define
-\[E_F:=\sum_{k,l\in \mathbb{N}}F(k,l)\]
-%
-Now, for every $k$, $l$, $i$ and $j$ in $\mathbb{N}$ with $i< k$ and $j< l$ we define $s^F_{k,l}\colon F(k,l)\to F(\bullet)^k$ and  $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ as the unique arrows fitting in the diagrams below, where the vertical arrows are the projections
-\[\xymatrix{F(k,l)  \ar@{.>}[r]^{s^F_{k,l}} \ar[dr]_{F(f_i)}& F(\bullet)^{k} \ar[d]^{\pi^F_{k,i}} & F(k,l) \ar@{.>}[r]^{t^F_{k,l}} \ar[dr]_{F(f_{k+j})} & F(\bullet)^{l} \ar[d]^{\pi^F_{l,j}} \\ & F(\bullet) && F(\bullet)}\]
-%
-In turn, these arrows allow us to consider
-$s_F, t_F\colon E_F\rightrightarrows F(\bullet)^{\star}$ as the unique arrows fitting in the diagrams below, where the vertical arrows are coprojections
-\[\xymatrix{F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{s^{F}_{k,l}}& F(\bullet)^{k} \ar[d]^{b^F_{k}} & F(k,l) \ar[d]_{a^F_{k,l}}  \ar[r]^{t^{F}_{k,l}}& F(\bullet)^{l} \ar[d]^{b^F_{l}}\\ E_F \ar@{.>}[r]_-{s_F}& F(\bullet)^\star & E_F \ar@{.>}[r]_-{t_F}& F(\bullet)^\star}\]
-
-Let $\mathcal{G}_F$ be the resulting hypergraph.
-One can now show that  sending $F$ to $\mathcal{G}_F$ can be extended to an equivalence $\mathcal{G}_{-}\colon \Set^{\catname{H}}\to \hyp$ (see \cite{castelnovo2023thesis,CastelnovoGM24} for details).
-
-\begin{prop}
-	$\hyp$ is equivalent to the category $\Set^{\catname{H}}$.
-\end{prop}
-\fi
+It is worth mentioning that limits in $\hyp$ which are not connected  are not computed componentwise. The following lemma shows how to compute products (see \Cref{proof:produ} for the proof).
+
+	\begin{restatable}{lem}{produ}\label{lem:prod}
+		Let $F\colon \D\to \hyp $ be a  discrete diagram.
+Let $F(D)$ be $(E_D, V_D, s_D,  t_D)$ and suppose that $(V, \{\pi^D_V\}_{D\in \D})$ is the product of $\{V_D\}_{D\in \D}$.
+For every $D\in \D$ and $(k,l)\in \mathbb{N}\times \mathbb{N}$, define
+		\[E^D_{k,l}:=\{e\in E_D \mid \lgh_{V_D}(s_{D}(e)) = k \text{ and } \lgh_{V_D}(t_{D}(e)) = l \}\]
+		with the canonical inclusion $i^D_{k,l}\colon E^D_{k,l}\mto E_D$.	Now, consider the product $(E_{k,l}, \{\pi^D_{k,l}\}_{D\in \D})$ and take the coproduct $(E_{\mathcal{L}}, \{\iota_{k,l}\}_{k,l \in \mathbb{N}})$ of the family $\{E_{k,l}\}_{k,l \in \mathbb{N}}$.
+Then there are arrows $s_{\mathcal{L}}, t_{\mathcal{L}}\colon E_{\mathcal{L}}\rightrightarrows V^\star$ and $\pi^D_E\colon E_{\mathcal{L}}\to E_D$ fitting in the diagram below and making $((E_{\mathcal{L}}, V, s_{\mathcal{L}}, t_{\mathcal{L}}), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ a limit for $F$.
+		\[\xymatrix@R=10pt@C=30pt{E^D_{k,l} \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{s_D} & V^\star_D  &E^D_{k,l} \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{t_D} & V^\star_D & E_{k,l} \ar[r]^{\pi^D_{k,l}} \ar[dd]_{\iota_{k,l}} & E^{D}_{k,l} \ar[dd]^{i^D_{k,l}}\\  E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}}  & & &E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}}  & & \\  E_{\mathcal{L}}   \ar@{.>}[rr]_{s_\mathcal{L}}& &V^\star \ar[uu]_{(\pi^D_V)^\star} &  E_{\mathcal{L}}   \ar@{.>}[rr]_{t_\mathcal{L}}& &V^\star \ar[uu]_{(\pi^D_V)^\star} & E_{\mathcal{L}} \ar@{.>}[r]_{\pi^D_E} & E_D}
+		\]
+	\end{restatable}
+
+\begin{exa}\label{ex:term} For instance, a terminal object of $\hyp$ is given by $(\mathbb{N}\times \mathbb{N}, 1, \Delta\circ \pi_1, \Delta\circ \pi_2)$, where $\pi_1, \pi_2\colon \mathbb{N}\times \mathbb{N}\to \mathbb{N}$ are the projections and $\Delta\colon \mathbb{N}\to 1^\star$ the canonical isomorphism introduced in \Cref{rem:length}.
+\end{exa}
 
@@
 \end{defi}
-\iffalse 
+
+We begin by introducing a construction which ``split'' a given hypergraph to produce a separated one.
+
 \begin{defi}
@@
 
- Moreover, let $\is{(V_{\mathcal{G}})}$ be the set of isolated nodes  of $\mathcal{G}$ i.e.~those which are not in the image of $s_{\mathcal{G}}$ or of $t_{\mathcal{G}}$.
-Furthermore, let $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}} \cup \{\iota_{is}\})$ be the coproduct of the family $\{V_{e}\}_{e\in E_\mathcal{G}} \cup \{\is{(V_{\mathcal{G}})}\}$ and define:
+Let $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}} \cup \{\iota_{is}\})$ be the coproduct of the family $\{V_{e}\}_{e\in E_\mathcal{G}}$ and define:
 \[\begin{split}
@@
 
+\begin{exa}\label{ex:empty}
+	If $\mathcal{G}$ has no hyperedges, then $\sp(\mathcal{G})$ is the empty hypergraph.
+\end{exa}
+
 \begin{exa}\label{ex:alg}
@@
 	\end{center}
-
 \end{exa}
+
+This construction can be extended to a functor.
 
@@
 \begin{proof}
-Let $(h_1, h_2)\colon \mathcal{G}\to \mathcal{H}$ be a morphism of hypergraph. For every $a$
-
+Let $(h_1, h_2)\colon \mathcal{G}\to \mathcal{H}$ be a morphism of hypergraphs.  For every hyperedge $e\in E_{\mathcal{G}}$,
+the universal property of coproducts, there are arrows $V_e\to V_{h_1(e)}$ fitting in the diagram below, on the left.
+These, in turn, yield the dotted $V_{\sp(\mathcal{G})} \to V_{\sp(\mathcal{G})}$ on the right.
+\[\xymatrix{1 & 1 \\ V_{e} & V_{h_1(e)} }\]
 Preservation of compositions and identities follows at once from the construction.
@@
 and so we get an arrow $(\id{E_{\mathcal{G}}}, f_{\mathcal{G}})\colon V\to \mathcal{V}_{\mathcal{G}}$. 
-
-Now, let $\mathcal{H}=(E_{\mathcal{H}}, V_{\mathcal{H}}, s_{\mathcal{H}}, t_{\mathcal{H}})$ be another separated hypergraph with an arrow $(h_1, h_2)\colon S(\mathcal{H})\to \mathcal{G}$.
-We can define
-\begin{align*}
-\hat{h}\colon V_{\mathcal{H}}&\to V_{\sp(\mathcal{G})} \\
-v & \mapsto \begin{cases}
-	\iota_{is}(h_2(v)) & h_2(v)\in \is{(V_{\mathcal{G}})}\\
-	\iota_e(h_2(v)) & h_2(v) \text{ is a letter of } s_{\mathcal{G}}(e) \text{ for some } e\in E_{\mathcal{G}}\\
-		\iota_e(h_2(v)) & h_2(v) \text{ is a letter of } t_{\mathcal{G}}(e) \text{ for some } e\in E_{\mathcal{G}}\\
-\end{cases}
-\end{align*}
-
-We first have to show that the previous definition gives us a well-defined function.
-By definition of isolated node we know that the three cases are exhaustive.
-Now, suppose that there are $e_1$ and $e_2$, not necessarily distinct, in $E_\mathcal{G}$ such that $h_2(v)$ is a letter of both
-
-\noindent
-\begin{minipage}[l]{.75\linewidth}
-\setlength{\parindent}{1.5em}
-\indent 	Since $\mathcal{H}$ is a separated hypergraph, $\hat{h}$
-	is a well-defined function. Moreover,  by construction $(h_1, \hat{h})$ defines a morphism $\mathcal{H}\to V_{\sp(\mathcal{G})}$ fitting in the diagram aside.
-\end{minipage} \hfill 
-\begin{minipage}[r]{.25\linewidth}
-	\xymatrix@C=40pt@R=10pt{S(\mathcal{H}) \ar[dr]^{(h_1, h_2)} \ar[d]_{S(h_1, \hat{h})}\\ S(\sp(\mathcal{G}))  \ar[r]_-{(\id{E_{\mathcal{G}}}, f_{\mathcal{G}})}& \mathcal{G}}
-\end{minipage}
-
-To prove uniqueness of such an arrow, let $(k_1, k_2)$ be a morphism $(\mathcal{H})\to \sp(\mathcal{G})$ such that 
-\[(h_1, h_2)=(\id{E_{\mathcal{G}}}, f)\circ (k_1, k_2)\]
-Clearly this implies $k_1 = h_2$.   Let now $v$ be an element of $V_\mathcal{H}$. Then we have three cases.
-\begin{itemize}
-	\item $v\in \is{(V_{\mathcal{H}})}$. In this case we have:
-\begin{align*}
-	j(h_2(v))&=f(\iota_{is}(h_2(v)))\\&=f(\hat{h}(v))\\&=h_2(v)\\&=
-\end{align*}
-	\item 
-\end{itemize}
-
-The previous three points allow us to conclude.
 \end{proof}
@@
 
-\fi
-
-The following result will be useful. A proof of it is \Cref{proof:seplim}
+\begin{defi} 
+	isolati e connessi
+\end{defi}
+
+\begin{prop}
+	aggiunto dx
+\end{prop}
+
+Finally, we conclude our exam of separated hypergraph proving a result regarding connected limits. A proof of it is \Cref{proof:seplim}
 
@@
 
+\begin{rem}\label{rem:map1}
+	diagramma generale dei vari ipergrafi
+\end{rem}
 \subsection{Labelled hypergraphs}\label{sssect:hyp_alg_sign}
@@
 
-The category of $\Set$ enjoys two other remarkable properties; it is \emph{distributive} and \emph{extensive} \cite{carboni1993introduction}.
+The category of $\Set$ enjoys two other remarkable properties; it is \emph{distributive} and \emph{extensive} \cite{carboni1993introduction}\label{word:ext}.
 Distributivity amount to the following property: for every family $\{X_i\}_{i}$ and an object $Y$, the unique morphisms $\phi$ and $\psi $ fitting in the diagrams below, where $j_i$, $k_i$ and $h_i$ are coprojections, are isomorphisms
@@
 \subsection{Proofs for \Cref{sec:hyper}}
+
+\noindent 
+\begin{minipage}[r]{.75\linewidth}
+\equi*
+\end{minipage}\hfill 
+\begin{minipage}[l]{.25\linewidth}
+	\xymatrix@R=10pt@C=40pt{F(k,l) \ar@{>->}[d]_{\iota^F_{k,l}}\ar[r]_{s^F_{k,l}} & F(\bullet)^k \ar@{>->}[d]^{v^F_k} \\ E_F \ar@{.>}[r]^{s^F} & F(\bullet)^\star}
+	\xymatrix@R=10pt@C=40pt{F(k,l) \ar[r]_{t^F_{k,l}} \ar@{>->}[d]_{\iota^F_{k,l}} & F(\bullet)^l\ar@{>->}[d]^{v^F_l}  \\ E_F \ar@{.>}[r]^{t^F} & F(\bullet)^\star}
+\end{minipage}
+
+\begin{proof}\label{proof:equi}
+	Let $\eta\colon F\rightarrow G$ be a natural transformation between $F, G\colon \catname{H}\rightrightarrows \Set$.
+By the universal property of coproducts there is an arrow $\hat{\eta}\colon E_F\to E_G$ fitting in the diagram aside.
+
+	\smallskip 
+	\noindent 
+	\begin{minipage}[r]{.8\linewidth}
+		\setlength{\parindent}{1.5em}
+		For every $i, n\in \mathbb{N}$ with $i< n$, let $\pi^G_{n, i}\colon G(\bullet)^n\to G(\bullet)$ be the $i^{\mathrm{th}}$ projections, then:
+		\begin{gather*}
+			\pi^G_{n, i}\circ s^G_{k,l}\circ \eta_{(k,l)} = G(f_i)\circ \eta_{(k,l)} = \eta_\bullet \circ F(f_i) = \eta_\bullet \circ \pi^G_{n, i} \circ s^F_{k,l} = \pi^G_{n, i}\circ \eta^k_\bullet  \circ s^F_{k,l}\\
+			\pi^G_{n, i}\circ t^G_{k,l}\circ \eta_{(k,l)} = G(f_{i+k})\circ \eta_{(k,l)} = \eta_\bullet \circ F(f_{i+k}) = \eta_\bullet \circ \pi^G_{n, i} \circ t^F_{k,l} = \pi^G_{n, i}\circ \eta^k_\bullet \circ  t^F_{k,l}
+		\end{gather*}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[l]{.15\linewidth} \vspace{-.5cm}
+	\xymatrix{F(k,l) \ar[r]^{\eta_{(k,l)}} \ar@{>->}[d]_{\iota^F_{k,l}}& G(k,l) \ar@{>->}[d]^{\iota^G_{k,l}}\\E _F \ar@{.>}[r]_{\hat{\eta}}& E_G}
+	\end{minipage}
+	\smallskip 
+	therefore  $s^G_{k,l}\circ \eta_{(k,l)} =  \eta^k_\bullet  \circ s^F_{k,l}$ and $t^G_{k,l}\circ \eta_{(k,l)} =  \eta^k_\bullet \circ t^F_{k,l}$.
+We can use these identities to show that $(\hat{\eta}, \eta_{\bullet})$ is a morphism of $\hyp$:
+	\begin{gather*}
+		s_G\circ \hat{\eta} \circ \iota^F_{k,l}=s_G\circ \iota^G_{k,l}\circ \eta_{(k,l)}=v^F_k\circ s^F_{k,l}\circ \eta_{(k,l)} = v^F_k \circ \eta^k_\bullet  \circ s^F_{k,l} = \eta^\star_\bullet \circ v^F_k\circ s^{F}_{k,l} =\eta^\star_\bullet \circ s^F\circ \iota^F_{k,l}\\
+		t_G\circ \hat{\eta} \circ \iota^F_{k,l}=t_G\circ \iota^G_{k,l}\circ \eta_{(k,l)}=v^F_k\circ t^F_{k,l}\circ \eta_{(k,l)} = v^F_k \circ \eta^k_\bullet  \circ t^F_{k,l} = \eta^\star_\bullet \circ v^F_k\circ t^{F}_{k,l} =\eta^\star_\bullet \circ t^F\circ \iota^F_{k,l}
+	\end{gather*}
+
+	Thus for every $\eta\colon F\to G$ we get an arrow $\mathcal{G}_{\eta}\colon \mathcal{G}_F\to \mathcal{G}_G$.
+By definition $\mathcal{G}_{\id{F}}$ is $\id{\mathcal{G}_F}$.
+Moreover, if $\psi$ is another natural transformation $G\to H$ we have
+	\[\hat{\psi\circ \eta}\circ \iota^{F}_{k,l}=\iota^{H}_{k,l}\circ \psi_{(k,l)}\circ \eta_{(k,l)} = \hat{\psi}\circ \iota^G_{k,l}\circ \eta_{(k,l)} = \hat{\psi}\circ \hat{\eta}\circ \iota^{F}_{k,l}\]
+	and so $\hat{\psi\circ \eta}=\hat{\psi}\circ \hat{\eta}$.
+
+	Summing up we have just define a functor $\mathcal{G}_{-}\colon \catname{Set}^{\catname{H}}\to \hyp$. We have now to show that such functor is full, faithful and essentially surjective.
+	\begin{itemize}
+		\item For faithfulness, suppose that $\eta, \psi\colon F\rightrightarrows G$ are arrows such that $\mathcal{G}_\eta = \mathcal{G}_\psi$.
+Then, by definition $\eta_{\bullet}=\psi_{\bullet}$ and, for every $(k,l)\in \catname{H}$:
+		\[\iota^G_{k,l}\circ \eta_{(k,l)} = \hat{\eta}\circ \iota^F_{k,l}=\hat{\psi}\circ \iota^F_{k,l} = \iota^G_{k,l}\circ \psi_{(k,l)} \]
+
+		Since $\iota^G_{k,l}$ is mono we conclude that $\eta_{(k,l)}=\psi_{(k,l)}$ and so $\eta = \psi$.
+		\item To prove that $\mathcal{G}$ is full, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of hypergraphs and define $f_{k,l}$ to be $f\circ \iota^F_{k,l}$, the composition of $h$ with Now, if $x\in F(k,l)$ then
+		\[\begin{split}
+			s_H (f_{k,l} (x))&=s_H \left(f \left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt}\left(s_{F} \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)
+		\end{split}\qquad \begin{split}
+			t_H (f_{k,l} (x))&=s_t\hspace{-1pt} \left(f \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt} \left(t_{F}\hspace{-1pt} \left(\iota^F_{k,l} (x)\right)\right)
+		\end{split}\]
+		Therefore there exists $\eta_{k,l}\colon F(k,l)\to H(k,l)$ fitting in the diagram below
+		\[\xymatrix{F(k,l) \ar[r]^-{\iota^{F}_{k,l}} \ar@{.>}[d]_{\eta_{k,l}}& E_F \ar[d]^{f_{k,l}}\\ H(k,l) \ar[r]_-{\iota^{H}_{k,l}}& E_H}\]
+		Define $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ simply as $g^\star$, then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
+Indeed, if $f_i\colon (k,l)\to \bullet$ we have:
+		\[\xymatrix{F(k,l) \ar@/^.4cm/[rr]^{s^F_{k,l}} \ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{s_F}& F(\bullet)^\star \ar[d]^{g^\star}&F(k,l) \ar@/^.4cm/[rr]^{t^F_{k,l}}\ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{t_F}& F(\bullet)^\star \ar[d]^{g^\star}\\ H(k,l) \ar@/_.4cm/[rr]_{s^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{s_H}& H(\bullet)^\star& H(k,l) \ar@/_.4cm/[rr]_{t^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{t_H}& H(\bullet)^\star}\]
+		Thus if $i<k$ then
+		\begin{align*}
+			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(s^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(s^F_{k,l}(x)\right)(i)\\&=s^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
+		\end{align*}
+		while, if $k\leq i < k+l-1$
+		\begin{align*}
+			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(t^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(t^F_{k,l}(x)\right)(i)\\&=t^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
+		\end{align*}
+		Finally, by contruction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$. 
+		\item Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define 
+		\[F_{\mathcal{G}}(k,l):=s_\mathcal{G}^{-1}(V_k)\cap t_\mathcal{G}^{-1}(V_l) \qquad F_{\mathcal{G}}(\bullet):=V_\mathcal{G}\]
+		Given $f_i\colon (k,l)\to \bullet$ we put
+		\[F_{\mathcal{G}}(f_i)\colon F_{\mathcal{G}}(k,l)\to F_{\mathcal{G}}(\bullet) \qquad x\mapsto \begin{cases}
+			s_\mathcal{G}(x)(i) & i<k\\
+			t_\mathcal{G}(x) (i-k) &i\leq k < k+l-1
+		\end{cases}  \]
+
+		$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$ and for every $h\in E_\mathcal{G}$ there exists a unique pair $(k,l)$ such that $h\in F_{\mathcal{G}}(k,l) $, namely the pair $(\dom(s_\mathcal{G})(h), \dom(t_\mathcal{G})(h))$thus
+		\[\sum_{k,l\in \mathbb{N}}F_{\mathcal{G}}(k,l)\simeq E\]
+		Moreover, by construction $s_{F_{\mathcal{G}}}=s$ and $t_{F_{\mathcal{G}}}=t$, from which the thesis follows. \qedhere
+	\end{itemize}
+\end{proof}
+
+\produ*
+\begin{proof}\label{proof:produ}
+	Let us build the wanted arrows.
+The existence of  $\pi^D_E\colon E_{\mathcal{L}}\to E_D$ follows at once from the universal property of coproducts.
+For the other two,  recall that by the first point of \Cref{prop:fact}  we know that $(V^\star, \{v_n\}_{n\in \mathbb{N}})$ and $(V_D^\star, \{v_{D, n}\}_{n\in \mathbb{N}})$ are coproducts for, respectively, $\{V^n\}_{n\in \mathbb{N}}$ and $\{V^n_D\}_{n\in \mathbb{N}}$.
+
+		\noindent
+	\begin{minipage}[r]{.6\linewidth}
+		\setlength{\parindent}{1.5em}
+
+		\medskip
+		Now,  by \Cref{rem:len} the bottom halves of the two diagrams aside are pullbacks while their outer boundaries are commutative by the definition of $E^D_{k,l}$.
+The universal property of pullbacks now yields us the two dotted arrows $s^{k,l}_{D}\colon E_{k,l} \to V^k_D$ and  $t^{k,l}_{D}\colon E_{k,l} \to V^l_D$.
+Since limits commute with limits  $(V^n, \{\pi^n_D\}_{D\in \D})$ is a product for the family $\{V_D^n\}_{D\in \D}$ and so we also get $s^{k,l}_{\mathcal{L}}\colon E_{k,l} \to V^k_D$ and  $t^{k,l}_{\mathcal{L}}\colon E_{k,l} \to V^l_D$ fitting in the diagrams below.
+	\end{minipage}\hfill 
+	\begin{minipage}[l]{.3\linewidth}
+	\xymatrix@R=15pt{ E^D_{k,l} \ar@{.>}[d]_{s^{k,l}_D}\ar@/^.5cm/[dd]^(.3){!_{E^D_{k,l}}}|(.52)\hole \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[d]^{s_D} &  E^D_{k,l} \ar@{.>}[d]_{t^{k,l}_D} \ar@{>->}[r]^{i^D_{k,l}} \ar@/^.5cm/[dd]^(.3){!_{E^D_{k,l}}}|(.52)\hole& E_D \ar[d]^{t_D}\\ V^k_D \ar@{>->}[r]_(.55){v_{D, k}} \ar[d]_{!_{V^k_D}}&  V_D^\star  \ar[d]^{\lgh_{V_D}}  & V^l_D \ar[d]_{!_{V^l_D}} \ar@{>->}[r]_(.55){v_{D, l}} & V_D^\star \ar[d]^{\lgh_{V_D}}\\ 1 \ar@{>->}[r]_{\delta_k}& \mathbb{N}  &1 \ar@{>->}[r]_{\delta_l} & \mathbb{N}}
+	\end{minipage}
+
+			\[\xymatrix@R=15pt@C=35pt{E^D_{k,l} \ar[drr]^(.6){s^{k,l}_D}\ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{s_D} & V^\star_D  &E^D_{k,l} \ar[drr]^(.6){s^{k,l}_D}\ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{t_D} & V^\star_D \\  E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}} \ar@{.>}[r]^{s^{k,l}_\mathcal{L}} & V^k \ar@/_.3cm/@{>->}[dr]_(.3){v_k} \ar[r]_{\pi^k_D}& V^k_D \ar@{>->}[u]^{v^D_k}&E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}} \ar@{.>}[r]^{s^{k,l}_\mathcal{L}} & V^l \ar@/_.3cm/@{>->}[dr]_(.3){v_l} \ar[r]_{\pi^l_D}& V^l_D \ar@{>->}[u]^{v^D_l}\\  E_{\mathcal{L}}   \ar@{.>}[rr]_{s_\mathcal{L}}& &V^\star \ar@/_.5cm/[uu]_(.35){(\pi^D_V)^\star} &  E_{\mathcal{L}}   \ar@{.>}[rr]_{t_\mathcal{L}}& &V^\star \ar@/_.5cm/[uu]_(.35){(\pi^D_V)^\star}}
+	\]
+
+	But then we get the existence of the dotted arrows $s_{\mathcal{L}}, t_{\mathcal{L}}\colon \rightrightarrows E_{\mathcal{L}}\to V^\star$ in the bottom row of the two previous diagrams.
+
+	As a next step,  we have to verify that $(\pi^D_E, \pi^D_V)$ is really a morphism of $\hyp$ for every $D\in \D$. To do this it is enough to compute:
+\begin{gather*}
+	(\pi^D_V)^\star \circ s_{\mathcal{L}}\circ \iota_{k,l} = (\pi^D_V)^\star\circ s^{k,l}_{\mathcal{L}} \circ \pi^D_{k,l}=s_D\circ i^D_{k,l}\circ \pi^D_{k,l} = s_D\circ i^D_{k,l}\circ \pi^D_{k,l}
+	=s_D\circ \pi^D_E \circ \iota_{k,l} \\
+		(\pi^D_V)^\star\circ t_{\mathcal{L}}\circ \iota_{k,l} = (\pi^D_V)^\star\circ t^{k,l}_{\mathcal{L}} \circ \pi^D_{k,l}=t_D\circ i^D_{k,l}\circ \pi^D_{k,l} = t_D\circ i^D_{k,l}\circ \pi^D_{k,l}
+	=t_D\circ \pi^D_E \circ \iota_{k,l} 
+\end{gather*}
+
+Let now $(\mathcal{G}, \{(h_{1,D}, h_{2,D})\}_{D\in \D})$ be a cone over $F$. Since $(V, \{\pi^D_V\}_{D\in \D})$ is limiting we obtain an arrow $h\colon V_{\mathcal{G}}\to V$.  Now, let 
+\[E_{k,l}^{\mathcal{G}}:=\{	E^{\mathcal{G}}_{k,l}:=\{e\in E_{\mathcal{G}} \mid \lgh_{V_{\mathcal{G}}}(s_{{\mathcal{G}}}(e)) = k \text{ and } \lgh_{V_{\mathcal{G}}}(t_{{\mathcal{G}}}(e)) = l \}\]
+
+\noindent 
+\begin{minipage}[l]{.72\linewidth}
+			\setlength{\parindent}{1.5em}
+
+Let $i^{\mathcal{G}}_{k,l}\colon E^{\mathcal{G}}_{k,l} \mto E_{\mathcal{G}} $ be the inclusion.
+By definition of $E^{D}_{k,l}$ and $E^{\mathcal{G}}_{k,l}$, the two squares aside are pullback.
+By extensivity, this entails that $(E_{\mathcal{G}}, \{i^\mathcal{G}_{k,l}\})$ is the coproduct of the family $\{E_{k,l}^{\mathcal{G}}\}_{k,l \in \mathbb{N}}$, where $i^\mathcal{G}_{k,l}\colon E_{k,l}^{\mathcal{G}}\mto E_{\mathcal{G}}$ is the inclusion.
+Using \Cref{rem:le}, we have:
+\begin{gather*}\lgh_{V_D} \circ s_{D}\circ h_{1,D}\circ \iota^{\mathcal{G}}_{k,l}=\lgh_{V_D}\circ h^\star_{2,D}\circ s_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l}=\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l} = \delta_{k} \circ !_{E^{\mathcal{G}}_{k,l}}\\
+	\lgh_{V_D} \circ t_{D}\circ h_{1,D}\circ \iota^{\mathcal{G}}_{k,l}=\lgh_{V_D}\circ h^\star_{2,D}\circ t_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l}=\lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l} = \delta_{l} \circ !_{E^{\mathcal{G}}_{k,l}}
+\end{gather*}
+
+By the universal property of the second square, the previous equations give us the dotted $f^D_{k,l} \colon E^{\mathcal{G}}_{k,l}\to E^D_{k,l}$ in the last diagram aside.
+Since $(E_{k,l}, \{\pi^D_{k,l}\}_{D\in \D})$ is the product of the family $\{E^D_{k,l}\}_{D\in \D}$, then $\{f^D_{k,l}\}_{D\in \D}$ gives us the dotted arrow $f_{k,l}\colon E^{\mathcal{G}}_{k,l}\to E_{k,l}$ inthe middle row.
+Finally, by the universal property of coproducts,  the family $\{f^D_{k,l}\}_{k,l\in \mathbb{N}}$ induces the morphism $h_1\colon E_{\mathcal{G}}\to E_{\mathcal{L}}$ in the top row.
+\end{minipage} \hfill
+\begin{minipage}[r]{.25\linewidth}
+	\xymatrix@R=10pt@C=55pt{E^{\mathcal{G}}_{k,l} \ar[d]_{!_{E^{\mathcal{G}}_{k,l}}} \ar@{>->}[r]^{i^{\mathcal{G}}_{k,l}}& E_{\mathcal{G}}\ar[d]_{(\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}})}\\ 1 \ar@{>->}[r]_{(\delta_k, \delta_l)}& \mathbb{N}\times \mathbb{N}}
+
+\xymatrix@R=10pt@C=55pt{E^{D}_{k,l} \ar[d]_{!_{E^{D}_{k,l}}} \ar@{>->}[r]^{i^{D}_{k,l}}& E_D\ar[d]_{(\lgh_{V_{D}}\circ s_{D}, \lgh_{V_{D}}\circ t_{D})}\\ 1 \ar@{>->}[r]_{(\delta_k, \delta_l)}& \mathbb{N}\times \mathbb{N}}
+
+	\xymatrix@R=10pt@C=35pt{ E_{\mathcal{G}} \ar@{.>}[r]^{h_1} \ar@/_.5cm/[dd]_(.3){h_{1,D}}& E_{\mathcal{L}} \\ E^{\mathcal{G}}_{k,l} \ar@{>->}[u]_{\iota^{\mathcal{G}}_{k,l}} \ar@{.>}[r]^{f_{k,l}} \ar@{.>}[dr]_{f^D_{k,l}} & E_{k,l} \ar[d]^{\pi^D_{k,l}} \ar@{>->}[u]_{\iota_{k,l}}\\ E_{D}  & E^D_{k,l} \ar@{>->}[l]^{\iota^D_{k,l}}}
+\end{minipage}
+
+Now, computing we get:
+\begin{align*}
+	s_{\mathcal{L}}\circ h_1 \circ \iota^{\mathcal{G}}_{k,l} = s_{\mathcal{L}}\circ \iota_{k,l}\circ f_{k,l} =v_k\circ s^{k, l}_{\mathcal{L}} \circ f_{k,l}\\
+	h^\star\circ s_{\mathcal{G}}\circ \iota^{\mathcal{G}}_{k,l}
+\end{align*}
+
+For uniqueness,
+
+	\end{proof}
+
 \seppb*
@@
 			\[(t_{\mathcal{L}}(e))_i=v \qquad  (t_{\mathcal{L}}(e) )_k= v\]
-			for some $e\in E_{\mathcal{H}}$ and $1\leq i, k \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ with $i\neq k$ . Then for any $D\in \D$:
+			for some $e\in E_{\mathcal{H}}$ and $1\leq i, k \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ with $i\neq k$. Then for any $D\in \D$:
 			\begin{align*}
@@
 		for indexes $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ and $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $.
-We have already noticed that$\D$ is non empty.
+We have already noticed that $\D$ is non empty.
 Let $D\in \D$, we have:

### 2025-08-19 jlamp/jlamp.tex
fine 3.1

@@
 \newcommand{\hyp}{\catname{Hyp}}
-\newcommand{\shyp}{\catname{SepHyp}}
+\newcommand{\phyp}{\catname{pHyp}}
+\newcommand{\pshyp}{\catname{pSep}}
+\newcommand{\shyp}{\catname{Sep}}
 \newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
@@
 
-\title{EGGs are adhesive!}
+\title{EGGs are adhesive!\\ An algebraic account of equality saturation}
 
@@
 %
-In the formal methods community, this is due also to the introduction of adhesive
+In the formal methods community, this is partly due to the introduction of adhesive
 categories, where most properties of classical approaches to graph transformation, 
@@
 via an efficient implementation of equality saturation. 
-In short, EGGs can be  defined as (acyclic) term graphs with an additional notion of 
+In short, EGGs are (acyclic) term graphs with an additional
 equivalence on nodes that is closed under the operators of the signature.
 Instead of replacing the components of a program, the optimisation step 
-is performed by adding new components and linking them to 
+adds new components and links them to 
 the existing ones via an equivalence relation, until an optimal program is reached.
@@
   \end{minipage}
+  \vspace{.01cm}
 
@@
 %
-Should a category be adhesive, and the arrows of the rules monomorphisms, the presence of a match ensures that
+If a category is adhesive, and the arrows of the rules are monomorphisms, the presence of a match ensures that
 if the pushout complement $C \to G$ exists then it is unique, hence a rewriting step can be deterministically performed.
@@
 %to be adhesive, 
-proving that a given category satisfies the conditions 
+proving that a category satisfies the conditions 
 for being $\mathcal{M}$-adhesive can be a daunting task. For this reason, sufficient criteria have been provided for the core 
-framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, as well as for the extended one of
+framework, e.g. that every elementary topos is adhesive \cite{lack2006toposes}, as well as for %the extended one of
 $\mathcal{M}$-adhesivity~\cite{CastelnovoGM24}.
@@
 
-EGGs can be concisely defined as term graphs equipped with a notion of equivalence on nodes
+EGGs can be concisely defined as term graphs equipped with an equivalence on nodes
 that is closed under the operators of a signature~\cite[Section~4.2]{DetlefsNS05}.
@@
 whose edges are labelled by operators and with
-the possibility of sharing subtrees, with an additional equivalence relation $\equiv$ on nodes that 
+the possibility of sharing subtrees, with an equivalence relation $\equiv$ on nodes that 
 is closed under composition. In plain words and using a toy example:
@@
 On the other side, describing the optimisation steps via the DPO approach
-offers the tools for modelling their parallel and concurrent execution
-and for proving their confluence and termination.
+offers the tools for modelling  parallel and concurrent execution
+and for proving  confluence and termination.
 
@@
 
-We open this background section by fixing some notation. Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
+We open this background section by fixing notation. Given a category $\X$ we do not distinguish notationally between $\X$ and its class of objects, so
 ``$X\in \X$'' means that $X$ is an object of $\X$.
 We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.
-Given an object $X$, we  denote by $?_X$ the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one.
-We will also use the notation $e\colon X\eto Y$ to denote that an arrow $e\colon X\to Y$ is a regular epi.
+Given an object $X$, $?_X$ denotes the unique arrow from an initial object into $X$ and by $!_X$ that  unique arrow from $X$ into a terminal one.
+We also use the notation $e\colon X\eto Y$ to denote that an arrow $e\colon X\to Y$ is a regular epi.
 
@@
 %and to define it we introduce some notions.  
-Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is said to be:
+Let  $\X$ be a category. A subclass $\mathcal{A}$ of $\mor(\X)$ is said to be
 
@@
 	\item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable;
+	\item \emph{closed under decomposition}, or \emph{left-cancellable}, if whenever $g$ and $g\circ f$ belong to $\mathcal{A}$, then $f\in \mathcal{A}$.
 	\end{itemize}
@@
 \end{minipage}
-\begin{itemize}	\item \emph{closed under decomposition}, or \emph{left-cancellable}, if whenever $g$ and $g\circ f$ belong to $\mathcal{A}$, then $f\in \mathcal{A}$.
-\end{itemize}
+%\begin{itemize}
+%\end{itemize}
 
 	\begin{defi}
-	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the cube below on the right.
-
-	\begin{minipage}[l]{.73\linewidth}
-		We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if:
+	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the cube below. %on the right. 
+	We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
+\vspace{-.5cm}
+
+	\begin{minipage}[l]{.68\linewidth}
 	\begin{enumerate}
@@
 \end{minipage}\hfill 
-\begin{minipage}[r]{.25\linewidth}
+\begin{minipage}[r]{.3\linewidth}
 	\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }
 \end{minipage}
-
 	Pushout squares that enjoy only the ``if'' half of item (2) above are called \emph{$\mathcal{A}$-stable}. A $\mor(\X)$-Van Kampen square is called  \emph{Van
@@
 
-\begin{prop}
+\begin{thm}
 	\label{thm:slice-functors}
-	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category. Then the following hold
+	Let $\X$ be an (strict) $\mathcal{M}$-adhesive category. Then the following facts hold
 	\begin{enumerate}
@@
 	\end{enumerate} 
-\end{prop}
+\end{thm}
 
@@
 	\label{ex:adhesive}
-	$\cat{Set}$ is adhesive, and, more generally, every topos is
+	$\cat{Set}$ is adhesive and, in fact, every topos is
 	adhesive~\cite{lack2006toposes}. By the closure properties above, every presheaf $[\cat{X},\cat{Set}]$ is adhesive, thus the category
@@
 (see, for instance, \cite[Thm.~4.26]{ehrig2006fundamentals} or \cite[Fact 2.6]{azzi2019essence}). A proof is provided in \Cref{regmono-proof}.
-\begin{restatable}{prop}{regmono}\label{prop:regmono}
-	Let $\X$ be an $\mathcal{M}$-adhesive category. Then the following hold
+\begin{restatable}{prop}{rgmono}\label{prop:regmono}
+	Let $\X$ be an $\mathcal{M}$-adhesive category. Then the following facts hold
 	\begin{enumerate}
@@
 \begin{restatable}{prop}{epic}\label{prop:reg_epi_coeq}
-    Let $e\colon X \eto Y$ be a regular epi in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then, $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
+    Let $e\colon X \eto Y$ be a regular epi in a category $\X$ with a kernel pair $(K_e, \pi^1_e, \pi^2_e)$. Then $e$ is the coequalizer of $\pi^1_e$ and $\pi^2_e$.
 \end{restatable}
@@
 
-		Moreover, the following hold
+		Moreover, the following facts hold
 		\begin{enumerate}
@@
 \end{minipage}\hfill 
-\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=2pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]_(.3){f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]_{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]_(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]_{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]^{g} & & D }
+\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=1pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]_{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]^{k_{g'}}&& K_d\\C \ar[rr]^{g} & & D }
 	\end{minipage}
@@
 		Suppose that in $\Set$ the commuting cube in the diagram on the left is given, whose top face is a pushout, the left and bottom faces are pullbacks,  and $n\colon B\mto D$ is an injection. 
-		Then the following hold true:
+		Then the following facts hold
 		\begin{enumerate}
@@
 Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathbb{N}\to 1^\star$.
-In particular, for every set $X$ the unique arrow $!_\X\colon X\to 1$ into the terminal induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
+In particular, for every set $X$ the unique arrow $!_\X\colon X\to 1$ into the terminal objects induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
 		\end{rem}
@@
 \begin{minipage}[r]{.83\linewidth}
-	\begin{rem}\label{rem:len} Let $X$ be a set.
-It is worth noticing that, for every $n\in \mathbb{N}$, $X^n$ is the preimage of $n$ along $\lgh_{X}$.
+	\begin{rem}\label{rem:len} It is worth noticing that for $X$ a set and every $n\in \mathbb{N}$, $X^n$ is the preimage of $n$ along $\lgh_{X}$.
 This amount to say that the square aside is a pullback.
@@
 	\end{rem}
-\end{minipage}\hfill \begin{minipage}[l]{.15\linewidth}
-\xymatrix@R=10pt{X^n \ar@{>->}[r]^{v_n} \ar[d]^{!_{X^n}}& X^\star  \ar[d]^{\lgh_{X}}\\ 1 \ar@{>->}[r]^{\delta_n} & \mathbb{N}}
+\end{minipage}\hfill \begin{minipage}[l]{.15\linewidth} \vspace{-.2cm}
+\xymatrix@R=13pt{X^n \ar@{>->}[r]^{v_n} \ar[d]^{!_{X^n}}& X^\star  \ar[d]^{\lgh_{X}}\\ 1 \ar@{>->}[r]^{\delta_n} & \mathbb{N}}
 \end{minipage}
@@
 \begin{notaz}
-	Given a word $w\in X^\star$ of length $l$, for every $1\leq i \leq l$, we will denote by $w_i$ the $i^\mathrm{th}$ letter of $w$.  
+	Given a word $w\in X^\star$ of length $l$, for every $1\leq i \leq l$, we denote by $w_i$ the $i^\mathrm{th}$ letter of $w$.
+Formally, if $\lgh_X(w)=l$, then $w=v_l(w')$ for some $w'\in X^l$ and $w_i$ is $\pi_i(w')$, for $\pi_i\colon X^l\to X$ the $i^\mathrm{th}$-projection.
 \end{notaz}
@@
 
-A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the diagrams on the right are commutative.
+A \emph{hypergraph morphism} $(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})\to (E_\mathcal{H}, V_\mathcal{H}, s_\mathcal{H}, t_\mathcal{H})$ is a pair $(h,k)$ of functions $h\colon E_\mathcal{G}\to E_\mathcal{H}$, $k\colon V_\mathcal{G}\to V_\mathcal{H}$ such that the diagrams on the right commute.
 
@@
 \begin{cor}\label[corollary]{cor:monhyper}
-	A morphism $(h,k)$ is a mono in $\hyp$ if and only if both its components are injective functions.
+	A morphism $(h,k)$ is a mono in $\hyp$ if and only if its components are injective functions.
 \end{cor}
@@
 \begin{exa}\label[example]{exa_2}
-We represent hypergraphs visually: dots denote nodes and boxes hyperedges. Should we be interested in their identity, we put a name near the corresponding dot or box. 
+We represent hypergraphs visually: bullets denote nodes and boxes hyperedges. Should we be interested in their identity, we put a name near the corresponding bullet or box. 
 Sources and targets are represented by lines between dots and squares: the lines from the sources of a hyperedge comes from the left of the box, while the lines to the targets 
 exit from the right of the box.
-Let us look at the picture below. It represent a hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
-and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ a pair of nodes
+
+Consider, for instance, the picture below. It represents a hypergraph $\mathcal{G}$ with sets $V_\mathcal{G} = \{v_1, v_2, v_3, v_4\}$ and $E_\mathcal{G} = \{h_1, h_2, h_3, h_4\}$ of nodes 
+and edges, respectively, such that  $h_1, h_2$ have no source and $h_3, h_4$ have the lists $v_1v_2$ and $v_3v_2$  as sources, , respectively.
 	\begin{center}
@@
 
-A rich source of example is given by \emph{monoidal signatures}.
+A rich source of examples is given by \emph{monoidal signatures}.
 
@@
 		and 
-		\[\ari_\Sigma(n)=0 \quad \ari_\Sigma(a) = 0, \quad \ari_\Sigma(*) =2 \quad  \ari_\Sigma(/) = 2\]
-		for every $n\in \mathbb{N}$ and $a\in A$. Then we can depict the hypergraph $\mathcal{G}^\Sigma$  as in the picture aside.
+		\[\ari_\Sigma(n)=0 \quad \ari_\Sigma(a) = 0 \quad \ari_\Sigma(*) =2 \quad  \ari_\Sigma(/) = 2\]
+		for every $n\in \mathbb{N}$ and $a\in A$. We depict the hypergraph $\mathcal{G}^\Sigma$  as in the picture aside.
 	\end{exa}
@@
 
-			\node[style=medium box] (times) at (0, 1.8) {};
-			\node[style=none] (timeslab) at (0, 2.6) {$*$};
-			\node[style=none] (timesin1) at (-0.3, 2.1) {};
-			\node[style=none] (timesin2) at (-0.3, 1.5) {};
-			\node[style=none] (timesout) at (0.2, 1.8){};
-
-			\node[style=medium box] (div) at (0, -1.8) {};
-			\node[style=none] (divlab) at (0, -2.6) {$/$};
-			\node[style=none] (divin1) at (-0.3, -2.1) {};
-			\node[style=none] (divin2) at (-0.3, -1.5) {};
-			\node[style=none] (divout) at (0.2, -1.8){};
+			\node[style=medium box] (times) at (0, 1.9) {};
+			\node[style=none] (timeslab) at (0, 2.7) {$*$};
+			\node[style=none] (timesin1) at (-0.3, 2.2) {};
+			\node[style=none] (timesin2) at (-0.3, 1.6) {};
+			\node[style=none] (timesout) at (0.2, 1.9){};
+
+			\node[style=medium box] (div) at (0, -1.9) {};
+			\node[style=none] (divlab) at (0, -2.7) {$/$};
+			\node[style=none] (divin1) at (-0.3, -2.2) {};
+			\node[style=none] (divin2) at (-0.3, -1.6) {};
+			\node[style=none] (divout) at (0.2, -1.9){};
 		\end{pgfonlayer}
@@
 		\begin{pgfonlayer}{edgelayer}
-			\draw[style=diredge, in=180, out= 112.5] (v) to (timesin2.center); 
-			\draw[style=diredge,out=135, in= 180] (v) to (timesin1.center);
-			\draw[style=diredge,in=165, out=0] (nattach.center) to (v);
-
-			\draw[style=diredge,out=0, in=-165] (constattach.center) to (v);
-			\draw[style=diredge,in=180, out= -112.5] (v) to (divin2.center); 
-			\draw[style=diredge,out=-135, in= 180] (v) to (divin1.center);
-
-			\draw[style=diredge, in=30, out=0] (timesout.center) to (v);
-			\draw[style=diredge, in=-30, out=0] (divout.center) to (v);
+%			\draw[style=diredge, in=180, out= 112.5] (v) to (timesin2.center); 
+			\draw[in=180, out= 112.5] (v) to (timesin2.center); 
+			\draw[out=135, in= 180] (v) to (timesin1.center);
+			\draw[in=165, out=0] (nattach.center) to (v);
+
+			\draw[out=0, in=-165] (constattach.center) to (v);
+			\draw[in=180, out= -112.5] (v) to (divin2.center); 
+			\draw[out=-135, in= 180] (v) to (divin1.center);
+
+			\draw[in=30, out=0] (timesout.center) to (v);
+			\draw[in=-30, out=0] (divout.center) to (v);
 		\end{pgfonlayer}
@@
 
-In order to deal with general limits of hypergraphs, it is worth to recall that, as first noted in \cite{bonchi2022string}, $\hyp$ is equivalent to a category of presheaves.
+In order to deal with general limits of hypergraphs, it is worth to recall that, as first noted in \cite{bonchi2022string},  we can realize $\hyp$ as a category of presheaves  (\cite{bonchi2022string,castelnovo2023thesis,CastelnovoGM24}).
+In \Cref{proof:equi} we report a proof of this claim for the interested reader.
 
@@
 \end{defi}
-
-It is possible to show that hypergraphs corresponds to presheaves over $\catname{H}$ (\cite{bonchi2022string,castelnovo2023thesis,CastelnovoGM24}).
-In \Cref{proof:equi} we report a proof of this claim for the interested reader.
 
@@
 		There is an equivalence of categories $\Set^{\catname{H}}\to \hyp$ sending a functor $F\colon \catname{H}\to \Set$ to $\mathcal{G}_F:=(E_F, F(\bullet), s_{F}, t_F)$, where $(E_F, \{\iota^F_{k,l}\})$ is a coproduct for $\{F(k,l)\}_{k,l\in\mathbb{N}}$
-		and $s_F, t_F\colon E_F\rightrightarrows V^\star_F$ are the unique arrows fitting in the diagrams aside, where $(F(\bullet), \{v^F_n\}_{n\in \mathbb{N}})$ is the coproduct coming from the first point of\Cref{prop:fact} and $s^F_{k,l}, t^F_{k,l}\colon F(k,l)\to F(\bullet)^k$, $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ are the arrows induced by, respectively, $\{F(f_i)\}_{i=0}^{k-1}$ and $\{F(f_i)\}_{i=k}^{k+l-1}$.
+		and $s_F, t_F\colon E_F\rightrightarrows V^\star_F$ are the unique arrows fitting in the diagrams aside, where $(F(\bullet), \{v^F_n\}_{n\in \mathbb{N}})$ is the coproduct coming from the first point of \Cref{prop:fact} and $s^F_{k,l}, t^F_{k,l}\colon F(k,l)\to F(\bullet)^k$, $t^F_{k,l}\colon F(k,l)\to F(\bullet)^l$ are the arrows induced by, respectively, $\{F(f_i)\}_{i=0}^{k-1}$ and $\{F(f_i)\}_{i=k}^{k+l-1}$.
 	\end{restatable}
@@
 \begin{minipage}[l]{.25\linewidth}
-\xymatrix@R=10pt@C=40pt{F(k,l) \ar@{>->}[d]_{\iota^F_{k,l}}\ar[r]_{s^F_{k,l}} & F(\bullet)^k \ar@{>->}[d]^{v^F_k} \\ E_F \ar@{.>}[r]^{s^F} & F(\bullet)^\star}
-\xymatrix@R=10pt@C=40pt{F(k,l) \ar[r]_{t^F_{k,l}} \ar@{>->}[d]_{\iota^F_{k,l}} & F(\bullet)^l\ar@{>->}[d]^{v^F_l}  \\ E_F \ar@{.>}[r]^{t^F} & F(\bullet)^\star}
-\end{minipage}
-
-In particular, \Cref{lem:equi} entails the following result.
-
-\begin{prop}\label{prop:cocomp}
+\xymatrix@R=10pt@C=40pt{F(k,l) \ar@{>->}[d]_{\iota^F_{k,l}}\ar[r]_{s^F_{k,l}} & F(\bullet)^k \ar@{>->}[d]^{v^F_k} \\ E_F \ar@{.>}[r]^{s_F} & F(\bullet)^\star}
+\xymatrix@R=10pt@C=40pt{F(k,l) \ar[r]_{t^F_{k,l}} \ar@{>->}[d]_{\iota^F_{k,l}} & F(\bullet)^l\ar@{>->}[d]^{v^F_l}  \\ E_F \ar@{.>}[r]^{t_F} & F(\bullet)^\star}
+\end{minipage}
+
+\begin{cor}\label{prop:cocomp}
 	$\hyp$ has all limits and colimits.
-\end{prop}
-
-It is worth mentioning that limits in $\hyp$ which are not connected  are not computed componentwise. The following lemma shows how to compute products (see \Cref{proof:produ} for the proof).
-
-	\begin{restatable}{lem}{produ}\label{lem:prod}
-		Let $F\colon \D\to \hyp $ be a  discrete diagram.
-Let $F(D)$ be $(E_D, V_D, s_D,  t_D)$ and suppose that $(V, \{\pi^D_V\}_{D\in \D})$ is the product of $\{V_D\}_{D\in \D}$.
+\end{cor}
+
+\Cref{lem:equi} not only entails that $\hyp$ is complete, but it provides us with a recipe to compute limits, even if they are not connected.
+	\begin{cor}\label{lem:prod}
+		Let $F\colon \D\to \hyp $ be a  discrete diagram and let $F(D)$ be $(E_D, V_D, s_D,  t_D)$.
+Suppose that $(V_{\mathcal{L}}, \{\pi^D_V\}_{D\in \D})$ is the product of $\{V_D\}_{D\in \D}$.
 For every $D\in \D$ and $(k,l)\in \mathbb{N}\times \mathbb{N}$, define
@@
 		with the canonical inclusion $i^D_{k,l}\colon E^D_{k,l}\mto E_D$.	Now, consider the product $(E_{k,l}, \{\pi^D_{k,l}\}_{D\in \D})$ and take the coproduct $(E_{\mathcal{L}}, \{\iota_{k,l}\}_{k,l \in \mathbb{N}})$ of the family $\{E_{k,l}\}_{k,l \in \mathbb{N}}$.
-Then there are arrows $s_{\mathcal{L}}, t_{\mathcal{L}}\colon E_{\mathcal{L}}\rightrightarrows V^\star$ and $\pi^D_E\colon E_{\mathcal{L}}\to E_D$ fitting in the diagram below and making $((E_{\mathcal{L}}, V, s_{\mathcal{L}}, t_{\mathcal{L}}), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ a limit for $F$.
-		\[\xymatrix@R=10pt@C=30pt{E^D_{k,l} \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{s_D} & V^\star_D  &E^D_{k,l} \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{t_D} & V^\star_D & E_{k,l} \ar[r]^{\pi^D_{k,l}} \ar[dd]_{\iota_{k,l}} & E^{D}_{k,l} \ar[dd]^{i^D_{k,l}}\\  E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}}  & & &E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}}  & & \\  E_{\mathcal{L}}   \ar@{.>}[rr]_{s_\mathcal{L}}& &V^\star \ar[uu]_{(\pi^D_V)^\star} &  E_{\mathcal{L}}   \ar@{.>}[rr]_{t_\mathcal{L}}& &V^\star \ar[uu]_{(\pi^D_V)^\star} & E_{\mathcal{L}} \ar@{.>}[r]_{\pi^D_E} & E_D}
+Then there are arrows $s_{\mathcal{L}}, t_{\mathcal{L}}\colon E_{\mathcal{L}}\rightrightarrows V_{\mathcal{L}}^\star$ and $\pi^D_E\colon E_{\mathcal{L}}\to E_D$ fitting in the diagram below and making $((E_{\mathcal{L}}, V_{\mathcal{L}}, s_{\mathcal{L}}, t_{\mathcal{L}}), \{(\pi^D_E, \pi^D_V)\}_{D\in \D})$ a limit for $F$.
+		\[\xymatrix@R=10pt@C=30pt{E^D_{k,l} \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{s_D} & V^\star_D  &E^D_{k,l} \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{t_D} & V^\star_D & E_{k,l} \ar[r]^{\pi^D_{k,l}} \ar[dd]_{\iota_{k,l}} & E^{D}_{k,l} \ar[dd]^{i^D_{k,l}}\\  E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}}  & & &E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}}  & & \\  E_{\mathcal{L}}   \ar@{.>}[rr]_{s_\mathcal{L}}& &V_{\mathcal{L}}^\star \ar[uu]_{(\pi^D_V)^\star} &  E_{\mathcal{L}}   \ar@{.>}[rr]_{t_\mathcal{L}}& &V_{\mathcal{L}}^\star \ar[uu]_{(\pi^D_V)^\star} & E_{\mathcal{L}} \ar@{.>}[r]_{\pi^D_E} & E_D}
 		\]
-	\end{restatable}
+	\end{cor}
 
@@
 
-\subsubsection{Some  subcategories of $\hyp$}
-
-We are now going to introduce three classes of hypergraphs, and the relative subcategories, which will provide the base for our definitions of EGGs  (cfr.~\Cref{sec:sepegg,sec:lmegg}).
+\subsubsection{Two  subcategories of $\hyp$}
+
+We are now going to introduce two classes of hypergraphs, and the relative subcategories, which will provide the base for our definitions of EGGs  (cfr.~\Cref{sec:sepegg,sec:lmegg}).
+
+\paragraph{Left-monogamous hypergraphs}\label{par:lm}
+We start by introducing \emph{left-monogamous} hypergraphs \cite{milosavljevic2023string,fritz2023free}, which are the generalization of \emph{term graphs} \cite{corradini2005term,Plu:TGR-ENTCS}.
+
+\begin{defi}
+	Let $\mathcal{H}=(E_{\mathcal{H}}, V_{\mathcal{H}}, s_{\mathcal{H}}, t_{\mathcal{H}})$ be an hypergraph.
+We define two functions $\ind{H}, \outd{H}\colon V_{\mathcal{H}}\times E_{\mathcal{H}}\rightrightarrows \mathbb{B}$ where $\ind{H}(v,e)$ is the number of occurences of $v$ in $s_{\mathcal{H}}(e)$ and $\outd{H}(v,e)$ that of $v$ in $t_{\mathcal{H}}(e)$.
+If $v$ is such that $\outd{H}(v,e)=0$ for every hyperedge $e$ we say that $v$ is an \emph{input} node.
+We will denote the set of input nodes by $\ino{H}$.
+
+	A hypergraph $\mathcal{H}$ is \emph{left-monogamous} if for every $v$ in $V_\mathcal{H}$, there is at most one hyperedge $e_v$ such that $\outd{H}(v,e_v)$ is non-zero and for such $e_v$ we have $\outd{H}(v,e_v) = 1$.
+
+	We will denote by $\lmo$ the full subcategory of $\hyp$ given by left-monogamous hypergraphs. The corresponding inclusion functor will be denoted by $M$.
+\end{defi}
+
+\begin{rem}Notice that our definition, unlike the one of \cite{fritz2023free}, allows for the presence of cycles in left-monogamous hypergraphs.
+\end{rem}
+
+Given a set $X$, we say that two words $X^\star$ are \emph{disjoint} is they do not share any letter.
+We can exploit this notion to rephrase the previous definition in a more elementary way (see \Cref{proof:elem} for a proof).
+\begin{restatable}{prop}{elem}\label{rem:elem} Given an hypergraph $\mathcal{H}$, the following facts are equivalent
+	\begin{enumerate}
+		\item $\mathcal{H}$ is left-monogamous;
+		\item for every $e\in E_{\mathcal{H}}$, $t_{\mathcal{H}}(e)$ has no repeated letter and $t_{\mathcal{H}}(e)$ is disjoint from $t_{\mathcal{H}}(e')$ for every other hyperedge $e'$.
+	\end{enumerate}
+\end{restatable}
+
+\begin{exa} The hypergraph of \Cref{exa_2} is left-monogamous but not separated.
+\end{exa}
+
+\noindent
+\begin{minipage}[l]{.6\linewidth}
+	\begin{exa}The hypergraphs $\mathcal{G}$ and $\mathcal{H}$ below are examples of non left-monogamous hypergraph.
+In the first the left-monogamy fails because $\outd{\mathcal{G}}(a, e) = 2$, while in the second we have \[\outd{H}(u, e_1) = \outd{H}(u, e_2)=1\]
+	\end{exa}
+\end{minipage} \hfill 
+\begin{minipage}[r]{.35\linewidth}
+	\begin{tikzpicture}
+		\begin{pgfonlayer}{nodelayer}
+			\node[style=medium box] (div) at (0, 0) {};
+			\node[style=none] (divlab) at (0, .7) {$e$};
+			\node[style=none] (divin1) at (.2, .2) {};
+			\node[style=none] (divin2) at (.2, -.2) {};
+			\node[style=none] (divout) at (-.3, 0){};
+
+			\node[style=node] (a) at (2, 0){};
+			\node[style=none] (alab) at (2, .3){$v$};
+			\node[style=node] (d) at (-2, 0){};
+			\node[style=none] (dlab) at (-2, .3){$w$};
+
+			\node[style=node] (e) at (0, -1.5){};
+			\node[style=none] (u) at (0, -1.2){$u$};
+			\node[style=small box] (c1) at (-2, -1.5) {};
+			\node[style=small box] (c2) at (2, -1.5) {};
+			\node[style=none](o) at (-1.7, -1.5){};
+			\node[style=none] (olab) at (-2, -1) {$e_1$};
+			\node[style=none] (olab) at (2, -1) {$e_2$};
+			\node[style=none](i) at (1.8, -1.5){};
+		\end{pgfonlayer}
+
+		\begin{pgfonlayer}{edgelayer}
+			\draw[style=none, in=135, out= 45] (divin1.east) to (a); 
+			\draw[style=none, in=-135, out= -45] (divin2.east) to(a) ;
+			\draw[style=none] (d) to (divout.center);
+			\draw[style=none] (o) to (e);
+			\draw[style=none] (i) to (e);
+		\end{pgfonlayer}
+	\end{tikzpicture}
+\end{minipage}
+
+\medskip 	
+The remaining of this section is devoted to the proof of quasiadhesivity of $\lmo$. We begin by computing pullbacks and equalizers of left-monogamous hypergraphs .
+
+\begin{rem}\label{rem:con}Notice that  $\lmo$ is not complete: it lacks e.g.
+a terminal object.
+To see this, notice that the $\mathcal{H}:=(\emptyset, 1, ?_{1^\star}, 1_{1^\star} )$ is left-monogamous and that
+	$\lmo(\mathcal{H}, \mathcal{G})$ is in bijection with $V_{\mathcal{G}}$ for every hypergraph $\mathcal{G}$.
+Thus if  $\mathcal{T}$ is terminal in $\lmo$, then its set of vertices $V_{\mathcal{T}}$ must have cardinality $1$.
+We have two possibilities
+
+%	\medskip 
+\vspace{.1cm}
+	\begin{minipage}[l]{.65\linewidth}
+		\begin{itemize}
+			\item  all the hyperedges of $\mathcal{T}$ have the empty word as target.
+			\item there is a (necessarily unique) $\mathcal{T}$ with a target of length one.
+		\end{itemize}
+	\end{minipage}
+	\begin{minipage}[r]{.15\linewidth}
+		\begin{tikzpicture}
+
+			\begin{pgfonlayer}{nodelayer}
+				\node[style=medium box] (div) at (0, 0) {};
+				\node[style=none] (divlab) at (0, .7) {$e$};
+				\node[style=none] (divin1) at (.2, .3) {};
+				\node[style=none] (divin2) at (.2, -.3) {};
+				\node[style=none] (divout) at (-.3, 0){};
+
+				\node[style=node] (a) at (2, .3){};
+				\node[style=none] (alab) at (2.3, .3){$v$};
+				\node[style=node] (b) at (2, -.3){};
+				\node[style=none] (ulab) at (2.3, -.3){$u$};
+				\node[style=node] (d) at (-2, 0){};
+				\node[style=none] (dlab) at (-2, .3){$w$};
+			\end{pgfonlayer}
+
+			\begin{pgfonlayer}{edgelayer}
+				\draw[style=none] (divin1.east) to (a); 
+				\draw[style=none] (divin2.east) to(b) ;
+				\draw[style=none] (d) to (divout.center);
+			\end{pgfonlayer}
+		\end{tikzpicture}
+	\end{minipage}
+
+%	\medskip
+\vspace{.1cm}
+\noindent
+In both cases there is no morphism from the left-monogamous hypergraph depicted above and $\mathcal{T}$. 
+\end{rem}
+
+An elementary, but fundamental observation is stated below (see \Cref{proof:count} for a proof).
+
+\begin{restatable}{prop}{cnt}\label{prop:count}
+	$\lmo$ is closed in $\hyp$ under subobject: if $(f,g)\colon \mathcal{G}\to \mathcal{H}$ is a mono in $\hyp$ and $\mathcal{H}$ is left-monogamous, then $\mathcal{G}$ is left-monogamous too.
+\end{restatable}
+
+Being $\lmo$ a full subcategory of $\hyp$, 
+\Cref{prop:count} provides equalizers of left-monogamous hypergraphs.
+\begin{cor}\label{cor:eq}
+	$\lmo$ is closed in $\hyp$ under equalizers.
+\end{cor}
+
+As shown by \Cref{rem:con}, $\lmo$ does not have all products, nonetheless left-monogamous hypergraphs are closed in $\hyp$ under binary products (a proof can be found in \Cref{proof:pro}).
+
+\begin{restatable}{lem}{lmol}\label{lem:pro}
+	$\lmo$ is closed in $\hyp$ under binary products.
+\end{restatable}
+
+Pullbacks are built from products and equalizers, so  \Cref{cor:eq} and \Cref{lem:pro} give us the following.
+
+\begin{cor}	$\lmo$ is closed in $\hyp$ under pullbacks.
+\end{cor}
+
+\begin{defi}
+A morphism $(f,g)\colon \mathcal{G}\to \mathcal{H}$ of hypergraphs  is \emph{downward-closed} if  $t_{\mathcal{H}}(h)$ has a letter belonging to the image of $g$, then $h$ is in the image of $f$. 
+\end{defi}
+
+Being downward-closed is related to preservation of input nodes, as shown by the following lemma (see \Cref{proof:inp} for the proof).
+
+\begin{restatable}{lem}{inp}\label{lem:inp}
+	Let $(f,g)\colon \mathcal{G}\to \mathcal{H}$ be a morphism of hypergraphs with $\mathcal{H}$ left-monogamous, then the following facts hold
+	\begin{enumerate}
+		\item if $g$ sends input nodes to input nodes, then $(f,g)$ is downward-closed; 
+		\item if $g$ is mono and $(f,g)$ is downward-closed, then $g$ sends input nodes to input nodes.
+	\end{enumerate}
+\end{restatable}
+
+Downward-closedness allows us to guarantee the existence of some pushouts in $\lmo$, as shown by the following proposition, whose proof is postponed to \Cref{proof:pusho}. 
+\begin{restatable}{prop}{pusho}\label{prop:pusho}
+Let $(f_1,g_1)\colon \mathcal{G}\to \mathcal{H}$ and $(f_2, g_2)\colon \mathcal{G}\to \mathcal{K}$ be two morphisms in $\lmo$.
+If $M(f_1,g_1)$ is mono and downward-closed, then the pushout $\mathcal{P}$ of $M(f_1,g_1)$ along $M(f_2, g_2)$ in $\hyp$ is left-monogamous.
+\end{restatable}
+
+\begin{cor}\label{cor:pusho}
+	$\lmo$ is closed in $\hyp$ under pushouts along downward-closed morphisms.
+\end{cor}
+
+We can use \Cref{prop:pusho} to completely characterise regular monos in $\lmo$. We refer again the reader to \Cref{proof:regmon} for the proof.
+
+\begin{restatable}{lem}{regmono}\label{lem:regmon}
+	Let $(f,g)\colon \mathcal{G}\to \mathcal{H}$ be s monomorphism in $\lmo$.
+Then the following facts are equivalent
+ 	\begin{enumerate}
+		\item $(f,g)$ is a regular mono;
+		\item $(f,g)$ sends input nodes to input nodes;
+		\item $(f,g)$ is downward-closed
+	\end{enumerate}
+\end{restatable}
+
+Putting together \Cref{thm:slice-functors} with \Cref{cor:pusho}  and \Cref{lem:regmon}, we get the following.
+
+\begin{cor}$\lmo$ is quasiadhesive.
+\end{cor}
 
 \paragraph{Separated hypergraphs}
-
-Let us begin with the subcategory of $\hyp$ which, in \Cref{sec:sepegg}, will give us the underlying hypergraphs for EGGs with minimally identified tokens.
-
-\begin{defi} Given a set $X$, we say that two words $X^\star$ are \emph{disjoint} is they do not share any letter.
-An hypergraph $\mathcal{G}=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}})$ is \emph{separated} if:
+We can now introduce the second  subcategory of $\hyp$ in which we are interested in and that will be used in \Cref{sec:sepegg} to give us the underlying hypergraphs for EGGs with minimally identified tokens.
+
+\begin{defi}  A left-monogamous hypergraph $\mathcal{G}=(E_{\mathcal{G}}, V_{\mathcal{G}}, s_{\mathcal{G}}, t_{\mathcal{G}})$ is \emph{separated} if
 	\begin{enumerate}
-		\item for every hyperedge $e$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ do not have repeated letters;
-		\item for every two, not necessarily distinct, hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint;
-		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $s_{\mathcal{G}}(e)$ and $s_{\mathcal{G}}(e')$ are disjoint;
-		\item  for every two different hyperedges $e, e'\in E_{\mathcal{G}}$, $t_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint.
+	\item it is \emph{right-monogamous}, i.e.~$(E_{\mathcal{G}}, V_{\mathcal{G}}, t_{\mathcal{G}}, s_{\mathcal{G}})$ is left-monogamous;
+	\item for every pair of, not necessarily distinct, hyperedges $e$ and $e'$,  $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e')$ are disjoint.
 	\end{enumerate}
@@
 
-We begin by introducing a construction which ``split'' a given hypergraph to produce a separated one.
+\begin{rem} Let $\mathcal{G}$ be an hypergraph.
+By \Cref{rem:elem}, right monogamy amount to the request that for every vertex $v\in V_{\mathcal{G}}$ there exists at most one $e_V\in E_{\mathcal{G}}$ such that $\ind{G}(v, e) \neq 0$ and  for such hyperedge we have $\ind{G}(v,e)=1$.
+ \end{rem}
+
+ \begin{rem}\label{rem:elem2}
+ 	Let $\mathcal{G}$ be a separated hypergraph,  
+ 	applying \Cref{rem:elem} we this is equivalent to say that, for every hyperedge $e$:
+ 	\begin{itemize}
+ 		\item $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ do not contain repeated letters;
+ 		\item $s_{\mathcal{G}}(e)$ is disjoint from $t_{\mathcal{G}}(e')$ for every $e'\in E_{\mathcal{G}}$;
+ 		\item for every $e'\in E_{\mathcal{G}}$ different from $e$, $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ are disjoint from, respectively $s_{\mathcal{G}}(e')$ and $t_{\mathcal{G}}(e')$.
+ 	\end{itemize}
+ \end{rem}
+
+We can provide a construction which ``split'' a given hypergraph to produce a separated one.
 
@@
 Given an hypergraph $\mathcal{\mathcal{G}}=(E_{\mathcal{G}}, V_{\mathcal{F}}, s_{\mathcal{G}}, t_{\mathcal{G}})$, for every hyperedge $e\in E_{\mathcal{G}}$ with $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we can consider the coproduct $(V_e, \{\iota^e_{i}\}_{i=1}^{n_e+m_e})$ of $n_e+m_e$ copies of $1$.
-
-Let $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}} \cup \{\iota_{is}\})$ be the coproduct of the family $\{V_{e}\}_{e\in E_\mathcal{G}}$ and define:
+We can further take the coproduct $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}})$ of the family $\{V_{e}\}_{e\in E_\mathcal{G}}$ and define:
 \[\begin{split}
@@
 	t_{\sp(\mathcal{G})} \colon E_{\mathcal{G}}&\to V_{\sp(\mathcal{G})}^\star\\
-	e &\mapsto \prod_{i=n_e+1}^{m_e} \iota_e(\iota^e_{i}(0))
+	e &\mapsto \prod_{i=n_e+1}^{n_e + m_e} \iota_e(\iota^e_{i}(0))
 \end{split} \]
@@
 
-We can finally define the \emph{separated graph associated to $\mathcal{G}$}  as $\sp(\mathcal{G}):= (E_{\mathcal{G}}, V_{\sp(\mathcal{G})}, s_{\sp(\mathcal{G})}, t_{\sp(\mathcal{G})})$.
+We define the \emph{separated graph associated to $\mathcal{G}$}  as $\sp(\mathcal{G}):= (E_{\mathcal{G}}, V_{\sp(\mathcal{G})}, s_{\sp(\mathcal{G})}, t_{\sp(\mathcal{G})})$.
 \end{defi}
 \begin{rem}\label{rem:ob}
- By construction $\sp(\mathcal{G})$ is an object of $\shyp$. 
+ By construction $\sp(\mathcal{G})$ is an object of $\shyp$. To see this it is enough to apply \Cref{rem:elem2}:
+ \begin{itemize}
+ 	\item every letter of $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ lies in the image of a different coprojection $\iota_e\circ \iota^e_i$, so it cannot appear more than one time;
+ 	\item a letter of $s_{\mathcal{G}}(e)$ are all contained in the image of $\iota_{e}\circ \iota^e_i$  for $i\leq n_e$, while every letter of $t_{\mathcal{G}}(e)$ lies in the image of $\iota_{e}\circ \iota^e_j$  for $n_e < j$, guaranteeing disjointness;
+ 	\item if $e$ is different from $e'$, then all the letters of $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ are contained in the image of $\iota_e$, while those of  $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ are in the image of $\iota_{e'}$ and so, again, we get the wanted disjointness.
+ \end{itemize}
 \end{rem}
@@
 				\node[style=none] (divlab) at (4, 2) {$\cdot$};
-				\node[style=none] (divin1) at (3.7, 1.6) {};
-				\node[style=none] (divin2) at (3.7, 1) {};
+				\node[style=none] (divin1) at (3.72, 1.6) {};
+				\node[style=none] (divin2) at (3.72, 1) {};
 				\node[style=none] (divout) at (4.2, 1.3){};
@@
 			\begin{pgfonlayer}{edgelayer}
-				\draw[style=diredge, in=180, out= 135] (v) to (timesin2.center); 
-				\draw[style=diredge,out=165, in= 180] (v) to (timesin1.center);
-				\draw[style=diredge,in=180, out=0] (nattach.center) to (v);
-
-				\draw[style=diredge,out=0, in=180] (constattach.center) to (c);
-				\draw[style=diredge,in=165, out= -15] (a) to (divin1.west); 
-				\draw[style=diredge,out=15, in=195 ] (b) to (divin2.west);
-
-				\draw[style=diredge, in=30, out=0] (timesout.center) to (v);
-				\draw[style=diredge, in=180, out=0] (divout.center) to (d);
+				\draw[style=none, in=180, out= 135] (v) to (timesin2.center); 
+				\draw[style=none,out=165, in= 180] (v) to (timesin1.center);
+				\draw[style=none,in=180, out=0] (nattach.center) to (v);
+
+				\draw[style=none,out=0, in=180] (constattach.center) to (c);
+				\draw[style=none,in=165, out= -15] (a) to (divin1.west); 
+				\draw[style=none,out=15, in=195 ] (b) to (divin2.west);
+
+				\draw[style=none, in=30, out=0] (timesout.center) to (v);
+				\draw[style=none, in=180, out=0] (divout.center) to (d);
 			\end{pgfonlayer}
@@
 
-This construction can be extended to a functor.
-
-\begin{prop}There exists a functor $\sp \colon \hyp\to \shyp$ sending $\mathcal{G}$ to $\sp(\mathcal{G})$.
-\end{prop}
-\begin{proof}
-Let $(h_1, h_2)\colon \mathcal{G}\to \mathcal{H}$ be a morphism of hypergraphs.  For every hyperedge $e\in E_{\mathcal{G}}$,
-the universal property of coproducts, there are arrows $V_e\to V_{h_1(e)}$ fitting in the diagram below, on the left.
-These, in turn, yield the dotted $V_{\sp(\mathcal{G})} \to V_{\sp(\mathcal{G})}$ on the right.
-\[\xymatrix{1 & 1 \\ V_{e} & V_{h_1(e)} }\]
-Preservation of compositions and identities follows at once from the construction.
-Now, for every $e\in \mathcal{E}_\mathcal{G}$ and $i$ between $1$ and $n_e+m_e$  we can define 
-\begin{align*}f_{e, i}\colon 1&\to V_{\mathcal{G}}\\
-	* & \mapsto\begin{cases}
-		(s_{\mathcal{G}}(e))_i & i \leq n_e\\
-		(t_{\mathcal{G}}(e))_i & n_e < i
-	\end{cases}
-\end{align*}
-These arrows, in turn, give us $f_ e\colon V_e\to V_{\mathcal{G}} $ and so an arrow $f_{\mathcal{G}}:V_{\sp(\mathcal{G})}\to V_{\mathcal{G}}$ such that 
-\[f_{\mathcal{G}}\circ \iota_e = f_e \qquad f_{\mathcal{G}}\circ \is{\iota} =  j_{\mathcal{G}}\]
-where $j_{\mathcal{G}}$ is the inclusion of $\is{(V_{\mathcal{G}})}\mto V_{\mathcal{G}}$. Notice that, for every $e\in E_{\mathcal{G}}$, $1\leq i\leq n_e$ and $1\leq k\leq m_e$ we have:
-\[\begin{split}
-	(f_{\mathcal{G}}^\star( s_{\sp(\mathcal{G})}(e)) )_i & = f_{\mathcal{G}}( s_{\sp(\mathcal{G})}(e) _i)\\
-	&=f(\iota_e(\iota^e_i(*)))\\&=f_e(\iota^e_i(*))\\&=f_{e, i}(*)\\&=
-	(s_{\mathcal{G}}(e))_i 
-\end{split} \qquad 
-\begin{split}
-	(f^\star( t_{\sp(\mathcal{G})}(e)) )_k & = f( t_{\sp(\mathcal{G})}(e) _k)\\
-	&=f(\iota_e(\iota^e_{n_e+k}(*)))\\&=f_e(\iota^e_{n_e+k}(*))\\&=f_{e, n_e+k}(*)\\&=
-	(t_{\mathcal{G}}(e))_k
-\end{split}
-\]
-and so we get an arrow $(\id{E_{\mathcal{G}}}, f_{\mathcal{G}})\colon V\to \mathcal{V}_{\mathcal{G}}$. 
-\end{proof}
+The construction we have just introduced can be extended to a functor (see \Cref{proof:sep} for a proof).
+
+\begin{restatable}{prop}{sep}\label{prop:sep}There exists a functor $\sp \colon \hyp\to \shyp$ sending $\mathcal{G}$ to $\sp(\mathcal{G})$.
+\end{restatable}
 
@@
 		\begin{pgfonlayer}{edgelayer} 
-			\draw[style=diredge,out=180, in= 270] (v) to (timesin.center);
-			\draw[style=diredge,out=0, in= 270] (v) to (divin.center);
-			\draw[style=diredge, in=135, out=345] (timesout.center) to (v);
-			\draw[style=diredge, in=45, out=195] (divout.center) to (v);
-			\draw[style=diredge, in=180, out=0] (a.center) to (zeroin.west);
-			\draw[style=diredge, in=180, out=0] (c.center) to (unoin.west);
-			\draw[style=diredge, in=180, out=0] (zeroout.east) to (b.west);
-			\draw[style=diredge, in=180, out=0] (unoout.east) to (d.west);
+			\draw[style=none,out=180, in= 270] (v) to (timesin.center);
+			\draw[style=none,out=0, in= 270] (v) to (divin.center);
+			\draw[style=none, in=135, out=345] (timesout.center) to (v);
+			\draw[style=none, in=45, out=195] (divout.center) to (v);
+			\draw[style=none, in=180, out=0] (a.center) to (zeroin.west);
+			\draw[style=none, in=180, out=0] (c.center) to (unoin.west);
+			\draw[style=none, in=180, out=0] (zeroout.east) to (b.west);
+			\draw[style=none, in=180, out=0] (unoout.east) to (d.west);
 		\end{pgfonlayer}
@@
 
-\begin{defi} 
-	isolati e connessi
+\smallskip
+If we restrict our attention to separated hypergraph without isolated nodes, then $\sp$ becomes a right adjoint. The interested reader can consult \Cref{proof:dx} for a proof.
+
+\begin{defi} Let $\mathcal{G}$ be an hypergraph.
+A node $v\in V_{\mathcal{G}}$ is \emph{isolated} if for every $e\in E_{\mathcal{G}}$ $v$ does not occur as a letter in neither $s_{\mathcal{G}}$ nor in $t_{\mathcal{G}}$.
+$\mathcal{G}$ is \emph{pruned} if it does not have isolated nodes.
+We denote by $\phyp$ and $\pshyp$ the full subcategories of $\hyp$ given by, respectively, pruned hypergraphs and those which are pruned and separated.
 \end{defi}
 
-\begin{prop}
-	aggiunto dx
-\end{prop}
+\begin{rem}\label{rem:prun}
+	By construction, $\sp{G}$ is pruned for every hypergraph $\mathcal{G}$.
+\end{rem}
+
+\begin{restatable}{prop}{dx}\label{prop:dx}
+	The inclusion functor $P\colon \pshyp\to \phyp$ has a right adjoint $\sp_P$.
+\end{restatable}
 
@@
 	\begin{pgfonlayer}{edgelayer}
-		\draw[style=diredge] (a) to (divin1.west); 
-		\draw[style=diredge] (b) to (divin2.west);
-		\draw[style=diredge] (divout.center) to (d);
+		\draw[style=none] (a) to (divin1.west); 
+		\draw[style=none] (b) to (divin2.west);
+		\draw[style=none] (divout.center) to (d);
 	\end{pgfonlayer}
@@
 	\begin{pgfonlayer}{edgelayer}
-		\draw[style=diredge] (v) to (in.east); 
-		\draw[style=diredge] (out.east) to (u.west);
+		\draw[style=none] (v) to (in.east); 
+		\draw[style=none] (out.east) to (u.west);
 	\end{pgfonlayer}
@@
 		\begin{pgfonlayer}{edgelayer}
-			\draw[style=diredge] (v) to (in.east); 
-			\draw[style=diredge] (out.east) to (u.west);
+			\draw[style=none] (v) to (in.east); 
+			\draw[style=none] (out.east) to (u.west);
 		\end{pgfonlayer}
@@
 
-\paragraph{Left-monogamous hypergraphs}
-
-We can now turn to the second subcategory of $\hyp$ of interest, that of \emph{left-monogamous} hypergraphs \cite{milosavljevic2023string,fritz2023free}.
-
-\begin{defi}
-	Let $\mathcal{H}=(E_{\mathcal{H}}, V_{\mathcal{H}}, s_{\mathcal{H}}, t_{\mathcal{H}})$ be an hypergraph.
-We define two functions $\ind{H}, \outd{H}\colon V_{\mathcal{H}}\times E_{\mathcal{H}}\rightrightarrows \mathbb{B}$ where $\ind{H}(v,e)$ is the number of occurences of $v$ in $s_{\mathcal{H}}(e)$ and $\outd{H}(v,e)$ that of $v$ in $t_{\mathcal{H}}(e)$.
-
- 	If $v$ is such that $\outd{H}(v,e)=0$ for every hyperedge $e$ we say that $v$ is an \emph{input} node. We will denote the set of input nodes by $\ino{H}$
-
- 		 	A hypergraph $\mathcal{H}$ is \emph{left-monogamous} if for every $v$ in $V_\mathcal{H}$, $\outd{H}(v,e)$ is nonzero for only finitely many hyperedges and
- 		 	\[\sum_{e\in E_{\mathcal{H}}} \outd{H}(v, e) = 1 - \chi_{\ino{H}}(v)\]
- 		 	where $\chi_{\ino{H}}\colon V_{\mathcal{H}}\to 2$ is the characteristic function of $\ind{H}$.
-
- 	We will denote by $\lmo$ the full subcategory of $\hyp$ given by left-monogamous hypergraphs. The corresponding inclusion functor will be denoted by $M$.
-\end{defi}
-
-\begin{rem}We can rephrase the previous definition in a more elementary way.
-Let $\mathcal{H}$ be a hypergraph, indeed if $v$ is an input node then there are no edges with $\outd{H}(v, e)\neq 0$ and so the equation above is automatically satisfied.
-If $v$ does not belong to $\ino{H}$, then the request of left monogamy amount to the existence of precisely one hyperedge $e$ such that $v$ occurs precisely one time in $t_{\mathcal{H}}(e)$.
-\end{rem} 
-\begin{rem}In \cite{fritz2023free} the definition of left-monogamous hypergraphs includes the request of \emph{acyclicity}.  We prefer to deal with acyclicity separately, see Paragraph \ref{sub:ac}.
-\end{rem}
-
-\begin{rem}
-	Every separated hypergraph is left-monogamous.
-Indeed if $\mathcal{H}$ is separated then there exists at most one $e\in E_{\mathcal{H}}$ such that $\outd{H}(v, e) \neq 0$.
-Moreover, in a separated graph the target of an hyperedge cannot have repeated letters and so we have that  $\outd{H}(v, e) = 1$ for at most one $e\in E_{\mathcal{H}}$.
-Left-monogamy now follows at once.
-\end{rem}
-
-\begin{exa} The hypergraph of example \Cref{exa_2} is left-monogamous but not separated.
-\end{exa}
-
-\noindent
-\begin{minipage}[l]{.6\linewidth}
-	\begin{exa}The hypergraphs $\mathcal{G}$ and $\mathcal{H}$ below are examples of non left-monogamous hypergraph.
-In the first the left-monogamy fails because $\outd{\mathcal{G}}(a, e) = 2$, while in the second we have \[\outd{H}(u, e_1) + \outd{H}(u, e_1)=1+1 = 2\]
-	\end{exa}
-\end{minipage} \hfill 
-\begin{minipage}[r]{.35\linewidth}
-		\begin{tikzpicture}
-		\begin{pgfonlayer}{nodelayer}
-			\node[style=medium box] (div) at (0, 0) {};
-			\node[style=none] (divlab) at (0, .7) {$e$};
-			\node[style=none] (divin1) at (.2, .2) {};
-			\node[style=none] (divin2) at (.2, -.2) {};
-			\node[style=none] (divout) at (-.3, 0){};
-
-			\node[style=node] (a) at (2, 0){};
-			\node[style=none] (alab) at (2, .3){$v$};
-			\node[style=node] (d) at (-2, 0){};
-			\node[style=none] (dlab) at (-2, .3){$w$};
-
-			\node[style=node] (e) at (0, -1.5){};
-			\node[style=none] (u) at (0, -1.2){$u$};
-			\node[style=small box] (c1) at (-2, -1.5) {};
-			\node[style=small box] (c2) at (2, -1.5) {};
-			\node[style=none](o) at (-1.7, -1.5){};
-			\node[style=none] (olab) at (-2, -1) {$e_1$};
-			\node[style=none] (olab) at (2, -1) {$e_2$};
-			\node[style=none](i) at (1.8, -1.5){};
-		\end{pgfonlayer}
-
-		\begin{pgfonlayer}{edgelayer}
-			\draw[style=diredge, in=135, out= 45] (divin1.east) to (a); 
-			\draw[style=diredge, in=-135, out= -45] (divin2.east) to(a) ;
-			\draw[style=diredge] (d) to (divout.center);
-			\draw[style=diredge] (o) to (e);
-			\draw[style=diredge] (i) to (e);
-		\end{pgfonlayer}
-	\end{tikzpicture}
-	\end{minipage}
-
-\medskip 	
-The remaining of this section is devoted to the proof of quasiadhesivity of $\lmo$. We begin by computing pullbacks and equalizers of left-monogamous hypergraphs .
-
-\begin{rem}Notice that  $\lmo$ is not complete: for instance it lacks a terminal object.
-The reasoning is similar to that of \Cref{ex:noterm}: if $\mathcal{T}$ is terminal, since  $\mathcal{H}:=(\emptyset, 1, ?_{1^\star}, 1_{1^\star} )$ is left-monogamous, we have that $V_{\mathcal{T}}$ must be a singleton.
-We have two possibilities:
-
-\medskip 
-\begin{minipage}[l]{.65\linewidth}
-	\begin{itemize}
-		\item  all the hyperedges of $\mathcal{T}$ have the empty word as target.
-		\item there is a (necessarily unique) $\mathcal{T}$ with a target of length one.
-	\end{itemize}
-\end{minipage}
-\begin{minipage}[r]{.15\linewidth}
-	\begin{tikzpicture}
-
-\begin{pgfonlayer}{nodelayer}
-	\node[style=medium box] (div) at (0, 0) {};
-	\node[style=none] (divlab) at (0, .7) {$e$};
-	\node[style=none] (divin1) at (.2, .3) {};
-	\node[style=none] (divin2) at (.2, -.3) {};
-	\node[style=none] (divout) at (-.3, 0){};
-
-	\node[style=node] (a) at (2, .3){};
-	\node[style=none] (alab) at (2.3, .3){$v$};
-	\node[style=node] (b) at (2, -.3){};
-	\node[style=none] (ulab) at (2.3, -.3){$u$};
-	\node[style=node] (d) at (-2, 0){};
-	\node[style=none] (dlab) at (-2, .3){$w$};
-\end{pgfonlayer}
-
-\begin{pgfonlayer}{edgelayer}
-	\draw[style=diredge] (divin1.east) to (a); 
-	\draw[style=diredge] (divin2.east) to(b) ;
-	\draw[style=diredge] (d) to (divout.center);
-\end{pgfonlayer}
-	\end{tikzpicture}
-\end{minipage}
-
-\medskip
-In both cases there are no morphism from the hypergraph depicted on the right and $\mathcal{T}$. 
-\end{rem}
-
-An elementary, but fundamental observation is given by the following (see \Cref{proof:count} for a proof).
-
-\begin{restatable}{prop}{count}\label{prop:count}
-	Let $(f,g)\colon \mathcal{G}\to \mathcal{H}$ be an arrow in $\hyp$.
-	The following are true:
-	\begin{enumerate}
-		\item for every $v\in V_{\mathcal{H}}$ and $e\in E_\mathcal{G}$ it holds:
-	\begin{align*}\ind{H}(f(e), g(v))&= \ind{G}(e, v)\cdot \abs{g^{-1}(g(v))\cap \mathsf{set}(s_{\mathcal{G}}(e))} \\\outd{H}(f(e), g(v))&= \outd{G}(e, v)\cdot \abs{g^{-1}(g(v))\cap \mathsf{set}(t_{\mathcal{G}}(e))}
-	\end{align*}
-		where, for $w\in V^\star_{\mathcal{G}}$, $\mathsf{set}(w)$ is the set of nodes appearing in $w$;
-		\item $\lmo$ is closed in $\hyp$ under subobject: if $(f, g)$ is mono and $\mathcal{H}$ is left-monogamous, then $\mathcal{G}$ is left-monogamous too.
-	\end{enumerate}
-\end{restatable}
-
-Since $\lmo$ is a full subcategory of $\hyp$, 
-\Cref{prop:count} provides equalizers of left-monogamous hypergraphs.
-\begin{cor}\label{cor:eq}
-	$\lmo$ is closed in $\hyp$ under equalizers.
-\end{cor}
-
-\begin{restatable}{lem}{lmol}
-	$\lmo$ is closed in $\hyp$ under pullbacks and equalizers.
-\end{restatable}
-
-\begin{defi}
-classe di morfismi
-\end{defi}
-
-\begin{prop}
-	contenuto...
-\end{prop}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\paragraph{Acyclic hypergraphs}\label{sub:ac}
-
-\begin{rem}\label{rem:map1}
-	diagramma generale dei vari ipergrafi
-\end{rem}
 \subsection{Labelled hypergraphs}\label{sssect:hyp_alg_sign}
@@
 
-\begin{prop}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then the following hold
+\begin{prop}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then the following facts hold
 	\begin{enumerate}
@@
 
-\subsubsection{Labelled left-monogamous hypergraphs}
+\subsubsection{Labelled left-monogamous and separated hypergraphs}
 
@@
 \begin{prop}\label{prop:tlim}
-Let $\Sigma$ be an algebraic signature. Then the following hold
+Let $\Sigma$ be an algebraic signature. Then the following facts hold
 \begin{enumerate}
@@
 
-TO DO: aciclici
+\begin{rem}\label{rem:map1}
+	diagramma generale dei vari ipergrafi
+\end{rem}
 
@@
 
-\begin{restatable}{prop}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then the following hold
+\begin{restatable}{prop}{fhyp}\label{prop:forghyp}  Consider the forgetful functor $T\colon \EqHyp \to \hyp$. Then the following facts hold
 	\begin{enumerate}
@@
 
-From the previous results we get the following characterization of monos in $\EqHyp$.
+From the previous results we get the following characterisation of monos in $\EqHyp$.
 
@@
 	\begin{restatable}{lem}{comp}\label{prop:eqhyp_complete}
-		Consider a diagram $F\colon \D \to \EqHyp$ and let $(E_D, V_D, Q_D, s_D, t_D, q_D)$ be the image of an object $D$. Then the following hold
+		Consider a diagram $F\colon \D \to \EqHyp$ and let $(E_D, V_D, Q_D, s_D, t_D, q_D)$ be the image of an object $D$. Then the following facts hold
 		\begin{enumerate}
@@
 
-\subsection{Term graphs with equivalence}
+\subsection{Labelled hypergraphs with equivalence}
 
@@
 
-\begin{prop}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then the following hold
+\begin{prop}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then the following facts hold
 	\begin{enumerate}
@@
 
-\begin{cor}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then the following hold
+\begin{cor}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then the following facts hold
 	\begin{enumerate}
@@
 \begin{prop}\label{prop:varie}
-	Let $\Sigma$ be an algebraic signature. Then the following hold
+	Let $\Sigma$ be an algebraic signature. Then the following facts hold
 	\begin{enumerate}
@@
 \noindent
-\parbox{10cm}{
+\begin{minipage}[l]{.75\linewidth}
 \begin{lem}\label{lem:pb1}
 	Let $\X$ be a category, and consider the diagram aside, in which the right square is a pullback. Then the whole rectangle is a pullback if and only if the left square is one.
-\end{lem}} 
-	\parbox{4cm}{
-	\xymatrix@R=15pt{X \ar[d]_{a} \ar[r]_{f}& \ar[r]_{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]^{h}& B \ar[r]^{k}& C}}
+\end{lem}
+\end{minipage} \hfill
+\begin{minipage}[r]{.20\linewidth}
+	\xymatrix@R=15pt{X \ar[d]_{a} \ar[r]_{f}& \ar[r]_{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]^{h}& B \ar[r]^{k}& C}
+\end{minipage}
+
 \commentato{
@@
 
-\regmono*
+\rgmono*
 \begin{proof}\label{regmono-proof}
+\mbox{ }
+
 \begin{enumerate}
-		\item  Consider the following cube in which the bottom face is an $\mathcal{M}$-pushout
-		\[\xymatrix@C=15pt@R=9pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_(.6){\id{B}} \\ A  \ar@{>->}[dd]_{m}\ar[rr]^(.65){g} & & B \ar@{>->}[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]_{f} & & D}\]
-		By construction the top face of the cube is a pushout and the back one a pullback.
-The left face is a pullback because $m$ is mono, thus the Van Kampen property yields that the front and the right faces are pullbacks too and the claim follows.
-		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback
-		\[\xymatrix{X \ar@{>->}[r]^{m} \ar@{>->}[d]_{m}& Y \ar@{>->}[d]^{h}\\ Y \ar@{>->}[r]^{k} & Z}\]
+\begin{minipage}[l]{.68\linewidth}
+		\item  Consider the cube aside in which the bottom face is an $\mathcal{M}$-pushout.
+		By construction the top face of the cube is a pushout and the back one a pullback. The left face is a pullback because $m$ is mono, 
+		thus the Van Kampen property yields that the front and the right faces are pullbacks too and the claim follows.
+
+		\item Let $m\colon X\mto Y$ be an arrow in $\mathcal{M}$, we can then take its pushout along itself, which, by the previous point, is also a pullback.
 		It is now immediate to see that $m$ is the equalizer of $h$ and $k$.   \qedhere
+\end{minipage}\hfill
+\begin{minipage}[r]{.30\linewidth}\vspace{-.3cm}
+\xymatrix@C=15pt@R=2pt{&A\ar[dd]|\hole_(.7){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_(.6){\id{B}} \\ A  \ar@{>->}[dd]_{m}\ar[rr]^(.65){g} & & B \ar@{>->}[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar@{>->}[dl]^{m} && B \ar@{>->}[dl]^{n} \\C \ar[rr]^(.7){f} & & D\\ X \ar@{>->}[rr]_{m} \ar@{>->}[dd]_{m}&& Y \ar@{>->}[dd]^{h}\\\\ Y \ar@{>->}[rr]^{k} && Z}
+\end{minipage}
+\begin{minipage}[l]{.68\linewidth}
+\end{minipage}\hfill
+\begin{minipage}[r]{.30\linewidth}
+		\xymatrix{}
+\end{minipage}
 	\end{enumerate}
@@
  		\item  
-		To prove the second half of the claim, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks
+		To prove the second half of the claim, we notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks
 		\[\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
@@
 \end{minipage} 
-\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]_{k_{g'}}&& K_d\\C \ar[rr]_{g} & & D }
-\end{minipage}
-
-\noindent 
-\parbox{4cm}{\xymatrix@C=10pt@R=6pt{&K_a\ar[dd]|\hole_(.65){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_b\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_(.55){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }} \hfill \parbox{9cm}{\begin{proof}\label{mpo-proof}
-	By  \Cref{prop:regmono}  we know that the top face of the original cube is a pullback. Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the following cube the vertical faces are pullbacks.
+\begin{minipage}[r]{.38\linewidth}\xymatrix@C=10pt@R=1pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar@{>->}[dl]_(.55){m'} && B' \ar[dd]^{b} \ar@{>->}[dl]_(.55){n'} & K_a\ar[rr]^{k_{f'}} \ar[dd]_{k_{m'}}&& K_b \ar[dd]^{k_{n'}} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]_{m} && B \ar[dl]^{n}  & K_{c} \ar[rr]^{k_{g'}}&& K_d\\C \ar[rr]^{g} & & D }
+\end{minipage}
+
+\noindent
+\begin{minipage}[l]{.7\linewidth}
+\begin{proof}\label{mpo-proof}
+	By  \Cref{prop:regmono}  we know that the top face of the original cube is a pullback. Thus \Cref{lemma:kern_pairs_pres_pullbacks} entails that in the cube aside the vertical faces are pullbacks.
 	The claim now follows from strict $\mathcal{M}$-adhesivity.
-	\end{proof}}
+	\end{proof}
+\end{minipage}
+\hfill 
+\begin{minipage}[r]{.30\linewidth}		
+\xymatrix@C=10pt@R=2pt{&K_a\ar[dd]|\hole_(.7){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_b\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_(.55){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }
+\end{minipage}
 
@@
 \noindent
-\parbox{11.7cm}{
+\begin{minipage}[l]{.8\linewidth}
 \begin{lem}\label{lem:po_set}
@@
 In particular, $h\circ \iota_m$ is mono.
-\end{lem}}\hfill \parbox{2cm}{\vspace{0cm}\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
+\end{lem}
+\end{minipage}
+\hfill 
+\begin{minipage}[r]{.23\linewidth}
+\xymatrix@R=15pt@C=30pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}
+\end{minipage}
 \begin{proof}
 		 Let $f\colon E\to Z$ and $k\colon C\to Z$ be two arrows with the same codomain.
-By definition of complement and since $m$ is mono we know that $(B, \{m, \iota_m\})$ is a coproduct.
-Define $\phi\colon B\to Z$ as the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\]
-		By the universal property of pushouts there is a unique arrow $\psi \colon D\to Z$ such that $\psi \circ n=k$ and $\psi \circ h=\phi$, thus 
+By definition of complement and since $m$ is mono $(B, \{m, \iota_m\})$ is a coproduct.
+Let $\phi\colon B\to Z$ be the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\]
+		By the universality of pushouts there is a unique arrow $\psi \colon D\to Z$ such that $\psi \circ n=k$ and $\psi \circ h=\phi$, thus 
 		\[
 		\psi \circ h\circ \iota_m =\phi \circ \iota_m=f\]	
-
 To conclude we have to show that $\psi$ is the unique arrow $D\to Z$ such that $\psi \circ n =k$ and $\psi \circ h\circ \iota_m=f$.
@@
 
+\vspace{.2cm}
 \noindent
@@
 \begin{proof}\label{proof:kerset}
-	We can start noticing that $m$, being the pullback of $n$ is mono too.
+	We can start noticing that $m$, being the pullback of $n$, is mono too.
 This, in turn, entails that $m'$, being the pullback of $m$, is mono, and so $n'$ is injective too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.
@@
 
-		By hypothesis the bottom face of the given cube is a pullback, therefore there exists an arrow $u\colon T_0\to A$ such that 
+		The bottom face of the given cube is a pullback, thus there is an arrow $u\colon T_0\to A$ such that 
 		\[f\circ u=n\circ t_2\circ l_0 \qquad m\circ u=c\circ \iota'\circ h_0\]
@@
 \[n\circ b\circ h_1\circ l^{-1}_1=d\circ n'\circ h_1\circ l^{-1}_1=d\circ t_1=n\circ t_2\]
-And we can conclude that $b\circ h_1\circ l^{-1}_1=t_2$ because $n$ is a mono. The claim now follows from the fact that  also $n'$ is mono.
-
-		\item 	 By \Cref{lem:po_set,lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks
+and we can conclude that $b\circ h_1\circ l^{-1}_1=t_2$ because $n$ is a mono. The claim now follows from the fact that  also $n'$ is mono.
+
+		\item By \Cref{lem:po_set} and \Cref{lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks
 		\[\xymatrix@C=45pt@R=15pt{K_b \ar@{>->}[r]^{k_{n'}}  \ar[d]_{(\pi^1_b, \pi^2_b)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
@@
 
-Since the bottom face of the original cube is a pullback (by hypothesis), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
+Since by hypothesis the bottom face of the original cube is a pullback, we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
 \[m\circ k_1= c \iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=c \iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]
@@
 
-Moreover, $k_{g'}\circ \phi_3=j_3$ as shown by the following computation.
+Moreover, $k_{g'}\circ \phi_3=j_3$ as shown by the following computation
 \begin{align*}
@@
 (\iota'\times \iota')\circ (p_3, q_3)\\& \end{split}\] 
-Thus we get the dotted arrows $\alpha_3$ and $\beta_3$ which are one the inverse of the other. Indeed, on the one hand we have
+Thus we get the dotted arrows $\alpha_3$ and $\beta_3$, which are mutually inverse. Indeed, on the one hand
 \begin{align*}
@@
 
- Let now $\gamma\colon K_b\to Z$ and $\delta\colon K_c\to Z$ be two arrows such that $\gamma\circ k_{f'}=\delta\circ k_{m'}$.
+ Now let $\gamma\colon K_b\to Z$ and $\delta\colon K_c\to Z$ be two arrows such that $\gamma\circ k_{f'}=\delta\circ k_{m'}$.
 We want to construct an arrow $\theta\colon K_d\to Z$ such that $\theta\circ k_{g'}=\delta$ and $\theta\circ k_{n'}=\gamma$.
@@
  \[\theta \circ k_{g'}\circ x_0=\theta \circ k_{n'}\circ h_0=\gamma \circ h_0=\gamma \circ k_{f'}\circ h'_0=\delta \circ k_{m'}\circ h'_0=\delta \circ x_0 \]
- We are left with uniqueness. If $\theta'$ is another arrow $K_d\to Z$ such that $\theta'\circ k_{n'}=\gamma$ and $\theta'\circ k_{g'}= \delta$. If we compute we get
+ We are left with uniqueness. Let $\theta'$ be another arrow $K_d\to Z$ such that $\theta'\circ k_{n'}=\gamma$ and $\theta'\circ k_{g'}= \delta$. If we compute we get
  \[\theta'\circ j_3=\theta'\circ k_{g'}\circ \phi_3=\delta \circ \phi_3=\theta \circ j_3 \]
@@
 \begin{minipage}[l]{.25\linewidth}
-	\xymatrix@R=10pt@C=40pt{F(k,l) \ar@{>->}[d]_{\iota^F_{k,l}}\ar[r]_{s^F_{k,l}} & F(\bullet)^k \ar@{>->}[d]^{v^F_k} \\ E_F \ar@{.>}[r]^{s^F} & F(\bullet)^\star}
-	\xymatrix@R=10pt@C=40pt{F(k,l) \ar[r]_{t^F_{k,l}} \ar@{>->}[d]_{\iota^F_{k,l}} & F(\bullet)^l\ar@{>->}[d]^{v^F_l}  \\ E_F \ar@{.>}[r]^{t^F} & F(\bullet)^\star}
+	\xymatrix@R=10pt@C=40pt{F(k,l) \ar@{>->}[d]_{\iota^F_{k,l}}\ar[r]_{s^F_{k,l}} & F(\bullet)^k \ar@{>->}[d]^{v^F_k} \\ E_F \ar@{.>}[r]^{s_F} & F(\bullet)^\star}
+	\xymatrix@R=10pt@C=40pt{F(k,l) \ar[r]_{t^F_{k,l}} \ar@{>->}[d]_{\iota^F_{k,l}} & F(\bullet)^l\ar@{>->}[d]^{v^F_l}  \\ E_F \ar@{.>}[r]^{t_F} & F(\bullet)^\star}
 \end{minipage}
@@
 		\setlength{\parindent}{1.5em}
-		For every $i, n\in \mathbb{N}$ with $i< n$, let $\pi^G_{n, i}\colon G(\bullet)^n\to G(\bullet)$ be the $i^{\mathrm{th}}$ projections, then:
+		For every $i, n\in \mathbb{N}$ with $i< n$, let $\pi^G_{n, i}\colon G(\bullet)^n\to G(\bullet)$ be the $i^{\mathrm{th}}$ projections, then
 		\begin{gather*}
@@
 	\end{minipage}
-	\smallskip 
+
+	\smallskip \noindent 
 	therefore  $s^G_{k,l}\circ \eta_{(k,l)} =  \eta^k_\bullet  \circ s^F_{k,l}$ and $t^G_{k,l}\circ \eta_{(k,l)} =  \eta^k_\bullet \circ t^F_{k,l}$.
-We can use these identities to show that $(\hat{\eta}, \eta_{\bullet})$ is a morphism of $\hyp$:
+We can use these identities to show that $(\hat{\eta}, \eta_{\bullet})$ is a morphism of $\hyp$
 	\begin{gather*}
@@
 Moreover, if $\psi$ is another natural transformation $G\to H$ we have
-	\[\hat{\psi\circ \eta}\circ \iota^{F}_{k,l}=\iota^{H}_{k,l}\circ \psi_{(k,l)}\circ \eta_{(k,l)} = \hat{\psi}\circ \iota^G_{k,l}\circ \eta_{(k,l)} = \hat{\psi}\circ \hat{\eta}\circ \iota^{F}_{k,l}\]
-	and so $\hat{\psi\circ \eta}=\hat{\psi}\circ \hat{\eta}$.
-
-	Summing up we have just define a functor $\mathcal{G}_{-}\colon \catname{Set}^{\catname{H}}\to \hyp$. We have now to show that such functor is full, faithful and essentially surjective.
+	\[\widehat{\psi\circ \eta}\circ \iota^{F}_{k,l}=\iota^{H}_{k,l}\circ \psi_{(k,l)}\circ \eta_{(k,l)} = \hat{\psi}\circ \iota^G_{k,l}\circ \eta_{(k,l)} = \hat{\psi}\circ \hat{\eta}\circ \iota^{F}_{k,l}\]
+	and so $\widehat{\psi\circ \eta}=\hat{\psi}\circ \hat{\eta}$.
+
+	Summing up we have just defined a functor $\mathcal{G}_{-}\colon \catname{Set}^{\catname{H}}\to \hyp$. We have now to show that such functor is full, faithful and essentially surjective.
 	\begin{itemize}
 		\item For faithfulness, suppose that $\eta, \psi\colon F\rightrightarrows G$ are arrows such that $\mathcal{G}_\eta = \mathcal{G}_\psi$.
-Then, by definition $\eta_{\bullet}=\psi_{\bullet}$ and, for every $(k,l)\in \catname{H}$:
+Then, by definition $\eta_{\bullet}=\psi_{\bullet}$ and, for every $(k,l)\in \catname{H}$
 		\[\iota^G_{k,l}\circ \eta_{(k,l)} = \hat{\eta}\circ \iota^F_{k,l}=\hat{\psi}\circ \iota^F_{k,l} = \iota^G_{k,l}\circ \psi_{(k,l)} \]
@@
 		Since $\iota^G_{k,l}$ is mono we conclude that $\eta_{(k,l)}=\psi_{(k,l)}$ and so $\eta = \psi$.
-		\item To prove that $\mathcal{G}$ is full, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{H}$ be a morphism of hypergraphs and define $f_{k,l}$ to be $f\circ \iota^F_{k,l}$, the composition of $h$ with Now, if $x\in F(k,l)$ then
-		\[\begin{split}
-			s_H (f_{k,l} (x))&=s_H \left(f \left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt}\left(s_{F} \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)
-		\end{split}\qquad \begin{split}
-			t_H (f_{k,l} (x))&=s_t\hspace{-1pt} \left(f \hspace{-1pt}\left(\iota^F_{k,l} (x)\right)\right)\\&=g^{\star}\hspace{-1pt} \left(t_{F}\hspace{-1pt} \left(\iota^F_{k,l} (x)\right)\right)
-		\end{split}\]
-		Therefore there exists $\eta_{k,l}\colon F(k,l)\to H(k,l)$ fitting in the diagram below
-		\[\xymatrix{F(k,l) \ar[r]^-{\iota^{F}_{k,l}} \ar@{.>}[d]_{\eta_{k,l}}& E_F \ar[d]^{f_{k,l}}\\ H(k,l) \ar[r]_-{\iota^{H}_{k,l}}& E_H}\]
-		Define $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ simply as $g^\star$, then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
-Indeed, if $f_i\colon (k,l)\to \bullet$ we have:
-		\[\xymatrix{F(k,l) \ar@/^.4cm/[rr]^{s^F_{k,l}} \ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{s_F}& F(\bullet)^\star \ar[d]^{g^\star}&F(k,l) \ar@/^.4cm/[rr]^{t^F_{k,l}}\ar[r]_-{\iota^{F}_{k,l}} \ar[d]_{\eta_{k,l}}& E_F \ar[d]_{f_{k,l}} \ar[r]_-{t_F}& F(\bullet)^\star \ar[d]^{g^\star}\\ H(k,l) \ar@/_.4cm/[rr]_{s^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{s_H}& H(\bullet)^\star& H(k,l) \ar@/_.4cm/[rr]_{t^H_{k,l}} \ar[r]^-{\iota^{H}_{k,l}}& E_H \ar[r]^-{t_H}& H(\bullet)^\star}\]
-		Thus if $i<k$ then
+		\item To prove that $\mathcal{G}$ is full, let $(f,g)\colon \mathcal{G}_F\to \mathcal{G}_{G}$ be a morphism of hypergraphs and define $f_{k,l}$ to be $f\circ \iota^F_{k,l}$.
+Now, notice that, by extensivity, the diagram on the right is a pullback.
+
+		\noindent 
+		\begin{minipage}[l]{.7\linewidth}
+			Now, by \Cref{rem:le} we have
 			\begin{align*}
-			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(s^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(s^F_{k,l}(x)\right)(i)\\&=s^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
+			&\lgh_{G(\bullet)}\circ s_G\circ f_{k,l} = \lgh_{G(\bullet)}\circ s_G\circ f\circ \iota^F_{k,l} =  \lgh_{G(\bullet)}\circ g^\star \circ s_F\circ  \iota^F_{k,l}\\ &= \lgh_{F(\bullet)}\circ s_F \circ  \iota^F_{k,l} = \delta_{k}\circ !_{F(k,l)}
 			\end{align*}
-		while, if $k\leq i < k+l-1$
-		\begin{align*}
-			\eta_\bullet(F(f_i)(x))&=g(F(f_i)(x))\\&=g\hspace{-1pt}\left(t^F_{k,l}(x)(i)\right)\\&=g^\star\hspace{-1pt}\left(t^F_{k,l}(x)\right)(i)\\&=t^H_{k,l}\hspace{-1pt}\left(\eta_{k,l}(x)\right)(i)\\&=F(f_i)(\eta_{k,l}(x))
-		\end{align*}
-		Finally, by contruction it is clear that $(\hat{\eta}, \eta_{\bullet})=(f,g)$. 
-		\item Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define 
-		\[F_{\mathcal{G}}(k,l):=s_\mathcal{G}^{-1}(V_k)\cap t_\mathcal{G}^{-1}(V_l) \qquad F_{\mathcal{G}}(\bullet):=V_\mathcal{G}\]
-		Given $f_i\colon (k,l)\to \bullet$ we put
+		\end{minipage}\hfill 
+		\begin{minipage}[r]{.25\linewidth} \vspace{-.5cm}
+		\xymatrix@C=50pt{G(k,l) \ar[d]_{!_{G(k,l)}} \ar@{>->}[r]^{\iota^G_{k,l}}& E_G \ar[d]_{(\lgh_{G(\bullet)}\circ s_{G}, \lgh_{G(\bullet)}\circ t_{G})} \\ 1\ar[r]_{(\delta_{k}, \delta_{l})}&\mathbb{N}\times \mathbb{N}}
+		\end{minipage}
+		\[	\lgh_{G(\bullet)}\circ t_G\circ f_{k,l} = \lgh_{G(\bullet)}\circ t_G\circ f\circ \iota^F_{k,l} =  \lgh_{G(\bullet)}\circ g^\star \circ t_F\circ  \iota^F_{k,l} = \lgh_{F(\bullet)}\circ t_F\circ  \iota^F_{k,l} = \delta_{l}\circ !_{F(k,l)}\]
+
+		\noindent
+		 	 \begin{minipage}[r]{.5\linewidth}
+		 	Thus there exists an arrow $\eta_{k,l}\colon F(k,l)\to H(k,l)$ fitting in the diagram on the right.
+Let $\eta_{\bullet}\colon F(\bullet)\to H(\bullet)$ be simply the arrow $g$, then  the collection of all the $\eta_{k,l}$ and of $\eta_\bullet$ defines a natural transformation $\eta\colon F\to H$.
+To see this, we can first notice that for every object $(k, l)\in \catname{H}$ we have
+		 \end{minipage} \quad \begin{minipage}[l]{.3\linewidth}\vspace{-.1cm}
+		 	\xymatrix@C=50pt@R=13pt{F(k,l) \ar@{.>}[dr]_{\eta_{(k,l)}} \ar@/_.3cm/[ddr]_{!_{F(k,l)}} \ar@{>->}[r]_(.6){\iota^F_{k,l}}& E_F \ar[dr]^{f}\\& G(k,l) \ar[d]_{!_{G(k,l)}} \ar@{>->}[r]^(.4){\iota^G_{k,l}}& E_G \ar[d]_{(\lgh_{G(\bullet)}\circ s_{G}, \lgh_{G(\bullet)}\circ t_{G})} \\ &1\ar[r]_{(\delta_{k}, \delta_{l})}&\mathbb{N}\times \mathbb{N}}
+		 \end{minipage}
+		 \begin{gather*}
+		 	v^{G}_k\circ g^k\circ s^F_{k,l}= g^\star \circ v^{F}_{k}\circ s^F_{k,l} = g^\star \circ s_F\circ \iota^F_{k,l}=s_G\circ f \circ \iota^F_{k,l}= s_G\circ \iota^{G}_{k,l}\circ \eta_{(k,l)}=v^G_k\circ s^G_{k,l}\circ \eta_{(k,l)}\\
+		 	v^{G}_l\circ g^l\circ t^F_{k,l}= g^\star \circ v^{F}_{l}\circ t^F_{k,l} = g^\star \circ t_F\circ \iota^F_{k,l}=t_G\circ f \circ \iota^F_{k,l}= t_G\circ \iota^{G}_{k,l}\circ \eta_{(k,l)}=v^G_l\circ t^G_{k,l}\circ \eta_{(k,l)}
+		 \end{gather*}
+		 so that $g^k\circ s^F_{k,l} =  s^G_{k,l}\circ \eta_{(k,l)}$ and $g^l\circ t^F_{k,l}= t^G_{k,l}\circ \eta_{(k,l)}$.
+
+		 Now, let $f_i\colon (k,l)\to \bullet$ be an arrow in $\catname{H}$. We have two cases
+		 \begin{itemize}
+		 	\item if $i<k$ then 
+		 	\[\eta_{\bullet}\circ F(f_i) = g\circ F(f_i) = g\circ \pi^F_{k, i}\circ s^F_{k,l}= \pi^G_{k,i}\circ g^k\circ s^F_{k,l} = \pi^G_{k,i} \circ s^G_{k,l}\circ \eta_{(k,l)} = G(f_i)\circ \eta_{(k,l)}  \]
+		 	\item if $k\leq i < k+l-1$ then
+		 	\[\eta_{\bullet} \circ F(f_i) = g\circ F(f_i) = g\circ \pi^F_{l, i-k} \circ t^{F}_{k,l} = \pi^G_{l, i-k}\circ g^l \circ t^F_{k,l}= \pi^G_{k, i-k}\circ t^G_{k,l}\circ \eta_{(k,l)} = G(f_i)\circ \eta_{(k,l)}\]
+		 \end{itemize}
+
+	By construction $f_{k,l}= \iota^G_{k,l} \circ \eta_{(k,l)}$ and so $(\hat{\eta}, \eta_{\bullet})=(f,g)$ as wanted.
+
+		\item We are left with essential surjectivity of $\mathcal{G}_{(-)}$. Given an hypergraph $\mathcal{G}=(E_\mathcal{G}, V_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G})$ we can define 
+		\[	F_{\mathcal{G}}(k,l):=\{e\in E_{\mathcal{G}} \mid \lgh_{V_{\mathcal{G}}}(s_{{\mathcal{G}}}(e)) = k \text{ and } \lgh_{V_{\mathcal{G}}}(t_{{\mathcal{G}}}(e)) = l \} \qquad F_{\mathcal{G}}(\bullet):=V_\mathcal{G}\]
+		while for every arrow $f_i\colon (k,l)\to \bullet$ we put
 		\[F_{\mathcal{G}}(f_i)\colon F_{\mathcal{G}}(k,l)\to F_{\mathcal{G}}(\bullet) \qquad x\mapsto \begin{cases}
-			s_\mathcal{G}(x)(i) & i<k\\
-			t_\mathcal{G}(x) (i-k) &i\leq k < k+l-1
+			s_\mathcal{G}(x)_i& i<k\\
+			t_\mathcal{G}(x)_{i-k} &i\leq k < k+l-1
 		\end{cases}  \]
 
-		$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$ and for every $h\in E_\mathcal{G}$ there exists a unique pair $(k,l)$ such that $h\in F_{\mathcal{G}}(k,l) $, namely the pair $(\dom(s_\mathcal{G})(h), \dom(t_\mathcal{G})(h))$thus
-		\[\sum_{k,l\in \mathbb{N}}F_{\mathcal{G}}(k,l)\simeq E\]
-		Moreover, by construction $s_{F_{\mathcal{G}}}=s$ and $t_{F_{\mathcal{G}}}=t$, from which the thesis follows. \qedhere
+		\begin{minipage}[r]{.7\linewidth}
+			$F_{\mathcal{G}}$ so defined is a functor $\catname{H}\to \catname{Set}$.
+Let $\iota^{\mathcal{G}}_{k,l}\colon F_{\mathcal{G}}(k,l)\mto E_{\mathcal{G}}$ be the inclusion, by definition the diagram on the right is a pullback and thus, by extensivity, $(E_{\mathcal{G}}, \{\iota^{\mathcal{G}}_{k,l}\}_{k,l\in \mathbb{N}})$ is a coproduct and so we have an isomorphism $\phi \colon E_{\mathcal{G}}\to E_{\mathcal{F}_{\mathcal{G}}}$ such that, for every $k,l\in \mathbb{N}$, $\phi\circ \iota^{\mathcal{G}}_{k,l} = \iota^{F_\mathcal{G}}_{k,l}$.
+		\end{minipage}
+		\hfill 
+		\begin{minipage}[r]{.25\linewidth} \vspace{-.1cm}
+			\xymatrix@C=50pt@R=20pt{F_{\mathcal{G}}(k,l) \ar[d]_{!_{G(k,l)}} \ar@{>->}[r]^{\iota^G_{k,l}}& E_{\mathcal{G}} \ar[d]_{(\lgh_{G(\bullet)}\circ s_{G}, \lgh_{G(\bullet)}\circ t_{G})} \\ 1\ar@{>->}[r]^{(\delta_{k}, \delta_{l})}&\mathbb{N}\times \mathbb{N}}
+		\end{minipage}
+		\begin{minipage}[l]{.55\linewidth}
+		Moreover, by definition of $F_{\mathcal{G}}(k,l)$, the solid parts of the diagrams aside commute and so \Cref{rem:len} gives us the dotted arrows $s_{k,l}^{\mathcal{G}}\colon F_{\mathcal{G}}(k,l)\to V^k_{\mathcal{G}}$.
+
+		Now for every $i<k$ and $j <l$ we have
+		\begin{gather*}
+			\pi^{F_\mathcal{G}}_{k,i} (s_{k,l}^{\mathcal{G}}(e)) = (v^{F_\mathcal{G}}_k(s_{k,l}^{\mathcal{G}}(e)))_i = F_{\mathcal{G}}(f_i)(e) =\pi^{F_\mathcal{G}}_{k,i} (s_{k,l}^{F_\mathcal{G}}(e))    \\
+			\pi^{F_\mathcal{G}}_{l,j} (t_{k,l}^{\mathcal{G}}(e)) = (v^{F_\mathcal{G}}_l(t_{k,l}^{\mathcal{G}}(e)))_j = F_{\mathcal{G}}(f_{j+k})(e) =\pi^{F_\mathcal{G}}_{l,j} (t_{k,l}^{F_\mathcal{G}}(e))   
+		\end{gather*}
+		\end{minipage}\hfill \begin{minipage}[r]{.5\linewidth}
+	\xymatrix@R=18pt{F_{\mathcal{G}}(k,l) \ar@/^.45cm/[dd]|(.51)\hole^(.7){!_{F_\mathcal{G}(k,l)}} \ar@{>->}[r]_-{\iota^{\mathcal{G}}_{k,l}} \ar@{.>}[d]_{s_{k,l}^{\mathcal{G}}}& E_{\mathcal{G}} \ar[d]^{s_\mathcal{G}}&   F_{\mathcal{G}}(k,l)\ar@/^.45cm/[dd]|(.51)\hole^(.65){!_{F_\mathcal{G}(k,l)}} \ar@{.>}[d]_{t_{k,l}^{\mathcal{G}}} \ar@{>->}[r]_-{\iota^{\mathcal{G}}_{k,l}} & E_{\mathcal{G}} \ar[d]_{t_\mathcal{G}}  \\  V^k_{\mathcal{G}} \ar[d]_{!_{V^k_{\mathcal{G}}}} \ar@{>->}[r]^{v_k^{F_\mathcal{G}}}& V^\star_{\mathcal{G}}  \ar[d]^{\lgh_{V_{\mathcal{G}}}} &V^l_{\mathcal{G}} \ar[d]_{!_{V^l_{\mathcal{G}}}} \ar@{>->}[r]^{v_l^{F_\mathcal{G}}}& V^\star_{\mathcal{G}} \ar[d]_(.6){\lgh_{V_{\mathcal{G}}}} \\  1 \ar@{>->}[r]^{\delta_{k}} & \mathbb{N} & 1  \ar@{>->}[r]^{\delta_{l}}& \mathbb{N}}
+		\end{minipage}
+
+	but this means that $s^{\mathcal{G}}_{k,l}= s^{F_{\mathcal{G}}}_{k,l}$ and 
+$t^{\mathcal{G}}_{k,l}= t^{F_{\mathcal{G}}}_{k,l}$ and so
+\begin{gather*}
+s_{F_{\mathcal{G}}}\circ \phi \circ \iota^{\mathcal{G}}_{k,l}=  s_{F^{\mathcal{G}}}\circ \iota^{F_{\mathcal{G}}}_{k,l}= v^{F_{\mathcal{G}}}_k \circ s^{F_{\mathcal{G}}}_{k,l} = v^{F_{\mathcal{G}}}_k \circ  s^{\mathcal{G}}_{k,l} = s_{\mathcal{G}}\circ \iota^{\mathcal{G}}_{k,l}\\
+t_{F_{\mathcal{G}}}\circ \phi \circ \iota^{\mathcal{G}}_{k,l}=  t_{F^{\mathcal{G}}}\circ \iota^{F_{\mathcal{G}}}_{k,l}= v^{F_{\mathcal{G}}}_l \circ t^{F_{\mathcal{G}}}_{k,l} = v^{F_{\mathcal{G}}}_l \circ  t^{\mathcal{G}}_{k,l} = t_{\mathcal{G}}\circ \iota^{\mathcal{G}}_{k,l}
+\end{gather*}
+Therefore $(\phi,\id{V_\mathcal{G}})$ is an isomorphism of hypergraphs $\mathcal{G}\to \mathcal{G}_{F_{\mathcal{G}}}$ and the thesis follows. \qedhere
 	\end{itemize}
@@
 
-\produ*
-\begin{proof}\label{proof:produ}
-	Let us build the wanted arrows.
-The existence of  $\pi^D_E\colon E_{\mathcal{L}}\to E_D$ follows at once from the universal property of coproducts.
-For the other two,  recall that by the first point of \Cref{prop:fact}  we know that $(V^\star, \{v_n\}_{n\in \mathbb{N}})$ and $(V_D^\star, \{v_{D, n}\}_{n\in \mathbb{N}})$ are coproducts for, respectively, $\{V^n\}_{n\in \mathbb{N}}$ and $\{V^n_D\}_{n\in \mathbb{N}}$.
-
-		\noindent
-	\begin{minipage}[r]{.6\linewidth}
+\subsubsection{Left-monogamous hypergraphs - proofs}
+
+\elem*
+\begin{proof}\label{proof:elem}
+	$(1\Rightarrow 2)$ If $t_{\mathcal{H}}(e)$ has a repeated letter $v$, then $\outd{H}(v,e)$ is at least $2$, thus $\mathcal{H}$ is not left-monogamous.
+By definition, if $v$ appears in $t_{\mathcal{H}}(e)$ and $t_{\mathcal{H}}(e')$ for $e\neq e'$, then $\mathcal{H}$ is not in $\lmo$,
+	\smallskip \noindent
+
+	$(2\Rightarrow 1)$ Let $v$ be an element of $V_{\mathcal{H}}$.
+Since $t_{\mathcal{H}}(e)$ has no repeated letter then $\outd{H}(v,e)\leq 1$ for every hyperedge $e$.
+On the other hand, since $t_{\mathcal{H}}(e)$ is disjoint from $t_{\mathcal{H}}(e')$ for every $e$ different from $e$, we also get that there is at most one hyperedge such that  $\outd{H}(v,e) = 1$.
+\end{proof}
+
+\cnt*
+\begin{proof}\label{proof:count}
+	By \Cref{cor:monhyper} we know that $f\colon E_{\mathcal{G}}\to E_{\mathcal{H}}$ and $g\colon V_{\mathcal{G}}\to V_\mathcal{H}$ are injective.
+Now, given $v\in V_{\mathcal{G}}$ and $w\in V_{\mathcal{H}}$, we can define
+	\[E^{\mathcal{G}}_v=\{e\in E_{\mathcal{G}} \mid \outd{G}(v,e) \neq 0\} \qquad E^{\mathcal{H}}_w=\{e\in E_{\mathcal{H}} \mid \outd{G}(w,e) \neq 0\}\]
+
+	\noindent 
+			\begin{minipage}[r]{.8\linewidth}
 					\setlength{\parindent}{1.5em}
-
-		\medskip
-		Now,  by \Cref{rem:len} the bottom halves of the two diagrams aside are pullbacks while their outer boundaries are commutative by the definition of $E^D_{k,l}$.
-The universal property of pullbacks now yields us the two dotted arrows $s^{k,l}_{D}\colon E_{k,l} \to V^k_D$ and  $t^{k,l}_{D}\colon E_{k,l} \to V^l_D$.
-Since limits commute with limits  $(V^n, \{\pi^n_D\}_{D\in \D})$ is a product for the family $\{V_D^n\}_{D\in \D}$ and so we also get $s^{k,l}_{\mathcal{L}}\colon E_{k,l} \to V^k_D$ and  $t^{k,l}_{\mathcal{L}}\colon E_{k,l} \to V^l_D$ fitting in the diagrams below.
+		Now, if $e\in E^{\mathcal{G}}_v$ then $g(v)$ is a letter of $t_{\mathcal{H}}(f(e))$ and so $f(e)$ belongs to $E^{\mathcal{H}}_{g(v)}$.
+Thus there exists an arrow $f_v\colon  E^{\mathcal{G}}_v\to E^{\mathcal{H}}_{g(v)} $ as in the diagram aside.
+Since $f$ is injective then $f_{v}$ is injective too and we know, by left-monogamy of $\mathcal{H}$, that $E^{\mathcal{H}}_{g(v)}$ is finite.
+Therefore also $E^{\mathcal{G}}_v$ is finite.
+	\end{minipage}
+	\hfill 
+	\begin{minipage}[r]{.2\linewidth} \vspace{-.3cm}
+		\xymatrix@C=40pt@R=18pt{E^{\mathcal{G}}_v \ar@{>->}[d]_{\iota^{\mathcal{G}}_v} \ar@{.>}[r]_{f_v}& E^{\mathcal{H}}_{g(v)} \ar@{>->}[d]^{\iota^{\mathcal{H}}_v} \\ E_{\mathcal{G}}\ar@{>->}[r]^{f} & E_{\mathcal{H}}}
+	\end{minipage}
+
+	Given an hyperedge $e$, if $t_{\mathcal{G}}(e)$ has a repeated letter, then there are two different indexes $1\leq i \leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{L}(e)})$, $1\leq k \leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{L}(e')}) $ such that $t_{\mathcal{G}}(e)_i=t_{\mathcal{G}}(e)_k$ and so
+\[t_{\mathcal{H}}(f(e))_k=g^\star(t_{\mathcal{G}}(e))_k=g(t_{\mathcal{G}}(e)_k)=g(t_{\mathcal{G}}(e)_i)=g^\star(t_{\mathcal{G}}(e))_i=t_{\mathcal{H}}(f(e))_i \]
+But $\mathcal{H}$ is left-monogamous and thus, by \Cref{rem:elem}, $f(e)$ cannot have a repeated letter.
+
+	Moreover, let $e$ and $e'$ be two non-disjoint hyperedges, i.e.~there are indexes $1\leq i \leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{L}(e)})$, $1\leq k \leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{L}(e')}) $ such that $t_{\mathcal{G}}(e)_i=t_{\mathcal{G}}(e') _k$.
+Then
+\[t_{\mathcal{H}}(f(e'))_k=g^\star(t_{\mathcal{G}}(e'))_k=g(t_{\mathcal{G}}(e')_k)=g(t_{\mathcal{G}}(e)_i)=g^\star(t_{\mathcal{G}}(e))_i=t_{\mathcal{H}}(f(e))_i \]
+%
+Since $\mathcal{H}$ is left-monogamous then $f(e)=f(e')$ and so, by injectivity of $f$, $e = e'$.
+Thus every hyperedge $e$ is disjoint from any other $e'\in E_{\mathcal{G}}$.
+We then conclude appealing to \Cref{rem:elem}.
+\end{proof}
+
+\lmol*
+\begin{proof}\label{proof:pro}
+	Consider two hypergraphs $\mathcal{G}_0$ and $\mathcal{G}_1$ and their product $(\mathcal{P}, \{(\pi^E_{\mathcal{G}_i}, \pi^V_{\mathcal{G}_i})\}_{i=0}^1)$.
+By \Cref{lem:prod} we know that $(V_{\mathcal{P}},  \{ \pi^V_{\mathcal{G}_i}\}_{i=0}^1))$ is a product
+	 and the diagrams below on the right commute for $i\in \{0, 1\}$.
+
+	 \noindent 
+	 \begin{minipage}[r]{.57\linewidth}	\setlength{\parindent}{1.5em}
+	 Let $e$ be an element of $E_{\mathcal{P}}$, we know that there exists $h$ in $E_{k,l}$ and $k, l\in \mathbb{N}$ such that $\iota_{k,l }(h)=e$.
+
+	 Suppose that there exists $1\leq n, m\leq l$, with $n\neq m$ such that 
+	 \[t_{\mathcal{P}}(e)_n =t_{\mathcal{P}}(e)_m\]
+	 then for every $i\in \{0,1\}$ we have
 	 \end{minipage}\hfill 
-	\begin{minipage}[l]{.3\linewidth}
-	\xymatrix@R=15pt{ E^D_{k,l} \ar@{.>}[d]_{s^{k,l}_D}\ar@/^.5cm/[dd]^(.3){!_{E^D_{k,l}}}|(.52)\hole \ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[d]^{s_D} &  E^D_{k,l} \ar@{.>}[d]_{t^{k,l}_D} \ar@{>->}[r]^{i^D_{k,l}} \ar@/^.5cm/[dd]^(.3){!_{E^D_{k,l}}}|(.52)\hole& E_D \ar[d]^{t_D}\\ V^k_D \ar@{>->}[r]_(.55){v_{D, k}} \ar[d]_{!_{V^k_D}}&  V_D^\star  \ar[d]^{\lgh_{V_D}}  & V^l_D \ar[d]_{!_{V^l_D}} \ar@{>->}[r]_(.55){v_{D, l}} & V_D^\star \ar[d]^{\lgh_{V_D}}\\ 1 \ar@{>->}[r]_{\delta_k}& \mathbb{N}  &1 \ar@{>->}[r]_{\delta_l} & \mathbb{N}}
-	\end{minipage}
-
-			\[\xymatrix@R=15pt@C=35pt{E^D_{k,l} \ar[drr]^(.6){s^{k,l}_D}\ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{s_D} & V^\star_D  &E^D_{k,l} \ar[drr]^(.6){s^{k,l}_D}\ar@{>->}[r]^{i^D_{k,l}} & E_D \ar[r]^{t_D} & V^\star_D \\  E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}} \ar@{.>}[r]^{s^{k,l}_\mathcal{L}} & V^k \ar@/_.3cm/@{>->}[dr]_(.3){v_k} \ar[r]_{\pi^k_D}& V^k_D \ar@{>->}[u]^{v^D_k}&E_{k,l} \ar@{>->}[d]_{\iota_{k,l}} \ar[u]^{\pi^D_{k,l}} \ar@{.>}[r]^{s^{k,l}_\mathcal{L}} & V^l \ar@/_.3cm/@{>->}[dr]_(.3){v_l} \ar[r]_{\pi^l_D}& V^l_D \ar@{>->}[u]^{v^D_l}\\  E_{\mathcal{L}}   \ar@{.>}[rr]_{s_\mathcal{L}}& &V^\star \ar@/_.5cm/[uu]_(.35){(\pi^D_V)^\star} &  E_{\mathcal{L}}   \ar@{.>}[rr]_{t_\mathcal{L}}& &V^\star \ar@/_.5cm/[uu]_(.35){(\pi^D_V)^\star}}
-	\]
-
-	But then we get the existence of the dotted arrows $s_{\mathcal{L}}, t_{\mathcal{L}}\colon \rightrightarrows E_{\mathcal{L}}\to V^\star$ in the bottom row of the two previous diagrams.
-
-	As a next step,  we have to verify that $(\pi^D_E, \pi^D_V)$ is really a morphism of $\hyp$ for every $D\in \D$. To do this it is enough to compute:
+	 \begin{minipage}[l]{.25\linewidth}
+\xymatrix@R=10pt@C=20pt{  E^i_{k,l} \ar@{>->}[r]^{\iota^i_{k,l}} & E_{\mathcal{G}_i} \ar[r]^{t_{\mathcal{G}_i}} & V^\star_{\mathcal{G}_i} & E_{k,l} \ar[r]^{\pi^i_{k,l}} \ar@{>->}[dd]_{\iota_{k,l}} & E^{i}_{k,l} \ar@{>->}[dd]_{\iota^i_{k,l}}\\ E_{k,l} \ar@{>->}[d]^{\iota_{k,l}} \ar[u]_{\pi^i_{k,l}}  & & \\   E_{\mathcal{P}}   \ar@{>}[rr]_{t_\mathcal{P}}& &V_{\mathcal{P}}^\star \ar[uu]^{(\pi^V_{\mathcal{G}_i})^\star} & E_{\mathcal{P}} \ar@{>}[r]_{\pi^E_{\mathcal{G}_i}} & E_{\mathcal{G}_i}}
+	 \end{minipage}
+	 \begin{align*}
+	& t_{\mathcal{G}_i}( \iota^i_{k,l}(\pi^i_{k,l}(h)))_n = ((\pi^V_{\mathcal{G}_i})^\star(t_{\mathcal{P}}(\iota_{k,l }(h))))_n= \pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(\iota_{k,l }(h))_n)=  \pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(e)_n)\\ =& \pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(e)_m)=\pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(\iota_{k,l }(h))_m) =((\pi^V_{\mathcal{G}_i})^\star(t_{\mathcal{P}}(\iota_{k,l }(h))))_m = t_{\mathcal{G}_i}( \iota^i_{k,l}(\pi^i_{k,l}(h)))_m
+	 \end{align*}
+	But this contradicts the the left-monogamy of $\mathcal{G}_0$ and $\mathcal{G}_1$.
+
+	Now, let now $e$ and $e'$ be two non-disjoint hyperedges.
+We know that $e=\iota_{k,l}(h)$ and $e'=\iota_{k',l'}(h')$ for some $h\in E_{k,l}$ and $h'\in E_{k', l'}$ and that there exist $1\leq n \leq l$ and $1\leq m \leq l'$ such that $t_{\mathcal{P}}(e)_n =t_{\mathcal{P}}(e')_m$.
+	Computing we get
+\begin{align*}
+& t_{\mathcal{G}_i}( \iota^i_{k,l}(\pi^i_{k,l}(h)))_n = ((\pi^V_{\mathcal{G}_i})^\star(t_{\mathcal{P}}(\iota_{k,l }(h))))_n= \pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(\iota_{k,l }(h))_n)=  \pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(e)_n)\\ =& \pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(e')_m)=\pi^V_{\mathcal{G}_i}(t_{\mathcal{P}}(\iota_{k',l' }(h'))_m) =((\pi^V_{\mathcal{G}_i})^\star(t_{\mathcal{P}}(\iota_{k',l' }(h'))))_m = t_{\mathcal{G}_i}( \iota^i_{k',l'}(\pi^i_{k',l'}(h')))_m
+\end{align*}
+	By left-monogamy this entails that $\iota^i_{k,l}(\pi^i_{k,l}(h)) = \iota^i_{k',l'}(\pi^i_{k',l'}(h'))$.
+Since coproducts in $\Set$ are disjoint then $k= k'$ and $l=l'$ and since $\iota^i_{k,l}$ is injective we get
+	\[\pi^0_{k,l}(h)= \pi^0_{k,l}(h') \qquad \pi^1_{k,l}(h)= \pi^1_{k,l}(h')\]
+	Thus $h=h'$ and $e =e'$ too. We conclude by \Cref{rem:elem}.
+\end{proof}
+
+\inp*
+\begin{proof}\label{proof:inp}
+	\begin{enumerate}
+		\item Suppose that $v\in V_{\mathcal{G}}$ is a node such that $g(v)$ is a letter of $t_{\mathcal{H}}(h)$ for some hyperedge $h$, hence $g(v)$ is not an input node and so $v$ does not belong to $\ino{G}$.
+Therefore there is $k\in E_{\mathcal{G}}$ such that $v$ occurs in $t_{\mathcal{G}}(k)$.
+But then $\outd{H}(g(v), f(k))\neq 0$ and so, by left-monogamy, $f(k)$ must coincide with $h$ as wanted.
+		\item  Let $v$ be an input node and suppose that there is $h\in E_{\mathcal{H}}$ such that $g(v)$ appears in $t_{\mathcal{H}}(h)$.
+Thus there is $k\in E_{\mathcal{G}}$ such that $f(k)=h$.
+Now, let $1\leq n\leq \lgh_{V_{\mathcal{H}}}(h)$ be such that $t_{\mathcal{H}}(h)_n=g(v)$, then, by \Cref{rem:le}, $\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(k))=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{H}}(h))$ and
+		\[g(t_{\mathcal{G}}(k)_n)=g^\star(t_{\mathcal{G}}(k)_n)=(g^\star(t_{\mathcal{G}}(k)))_n=t_{\mathcal{H}}(f(k))_n = t_{\mathcal{H}}(h)_n=g(v)\]
+		By injectivity of $g$ we have $t_{\mathcal{G}}(k)_n=g(v)$, contradicting the assumption that $v$ is an input node.	  \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\pusho*
+\begin{proof}\label{proof:pusho}
+	By \Cref{prop:com} and \Cref{colim}, we know that there pushout squares in $\catname{Set}$ as the ones aside.
+
+	\noindent\begin{minipage}[l]{.65\linewidth}
+			\setlength{\parindent}{1.5em}
+
+	By \Cref{cor:monhyper}, $f_1$ and $g_1$ are monos, thus also $k_V$ and $k_E$ are injective as they are the pushout of injective arrows.
+By \Cref{rem:mono}, moreover, we know that $k^\star_V$ is injective too.
+	\end{minipage}
+	\hfill\begin{minipage}[r]{.4\linewidth}
+\xymatrix@R=10pt{E_{\mathcal{G}} \ar[r]_{f_2} \ar@{>->}[d]^{f_1} & E_{\mathcal{K}} \ar@{>->}[d]_{k_E} & V_{\mathcal{G}}  \ar[r]_{g_2} \ar@{>->}[d]^{g_1}& V_{\mathcal{K}} \ar@{>->}[d]_{k_V}\\ E_{\mathcal{H}} \ar[r]^{h_E} & E_{\mathcal{P}} & V_{\mathcal{H}}  \ar[r]^{h_V}& V_{\mathcal{P}}}
+	\end{minipage}
+
+	\noindent 
+	\begin{minipage}[l]{.42\linewidth}
+		\setlength{\parindent}{1.5em}
+
+	Moreover, the first of the diagrams above fits in other two diagrams as the ones aside.
+Let $\iota_E\colon A\mto E_{\mathcal{H}}$ and $\iota_V\colon B\mto V_{\mathcal{H}}$ be the inclusions of the complements of the images of, respectively $f_1$ and $g_1$.
+By \Cref{lem:po_set}, we know that $(E_{\mathcal{P}}, \{k_E, h_E\circ \iota_E\})$ and $(V_{\mathcal{P}}, \{k_V, h_V\circ \iota_V\})$ are coproducts.
+	\end{minipage}
+\hfill 
+\begin{minipage}[r]{.5\linewidth}
+\xymatrix@C=15pt@R=10pt{V^\star_{\mathcal{G}} \ar@{>->}[ddd]^{g^\star_1}\ar[rrr]_{g^\star_2} &&&V^\star_{\mathcal{K}} \ar@{>->}[ddd]_{k^\star_V} & V^\star_{\mathcal{G}} \ar@{>->}[ddd]^{g^\star_1} \ar[rrr]_{g^\star_2}&&& V^\star_{\mathcal{K}}\ar@{>->}[ddd]_{k^\star_V} \\ & E_{\mathcal{G}} \ar[ul]^{s_{\mathcal{G}}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}} \ar[ur]_{s_{\mathcal{K}}} \ar@{>->}[d]^{k_E}&&& E_{\mathcal{G}} \ar[ul]^{t_{\mathcal{G}}} \ar[r]^{f_2} \ar@{>->}[d]_{f_1} & E_{\mathcal{K}}\ar[ur]_{t_{\mathcal{K}}}\ar@{>->}[d]^{k_E}\\ & E_{\mathcal{H}} \ar[dl]_{s_{\mathcal{H}}} \ar[r]_{h_E} & E_{\mathcal{P}} \ar[dr]^{s_{\mathcal{P}}}&&& E_{\mathcal{H}} \ar[dl]_{t_{\mathcal{H}}}\ar[r]_{h_E} & E_{\mathcal{P}} \ar[dr]^{t_{\mathcal{P}}} \\V^\star_{\mathcal{H}} \ar[rrr]^{h^\star_V} &&&V^\star_{\mathcal{P}} & V^\star_{\mathcal{H}}\ar[rrr]^{h^\star_V} &&& V^\star_{\mathcal{P}} }
+\end{minipage}
+
+We want to use \Cref{rem:elem} to prove that $\mathcal{P}$ is left-monogamous.
+To do so, we need to show that the target of every element of $E_{\mathcal{P}}$ has no repeated letter and that every two different hyperedges of $\mathcal{P}$ have disjoint targets.
+
+Suppose that there exists $e \in E_{\mathcal{P}}$ such that $\outd{P}(v,e) > 1$ for some $v\in V_{\mathcal{P}}$.
+So that there are two different  indexes $1\leq n, m \leq \lgh_{V_{\mathcal{P}}}(e)$ such that $t_{\mathcal{P}}(e)_n=t_{\mathcal{P}}(e)_m$.
+We have two cases.
+\begin{itemize}
+	\item $e= k_E(h)$ for some $h\in E_{\mathcal{K}}$.  %Suppose . 
+	Then we have
+	\begin{align*}
+		&k_V(t_{\mathcal{K}}(h)_n)=(k^\star_V(t_{\mathcal{K}}(h)))_n=t_{\mathcal{P}}(k_E(h))_n=t_{\mathcal{P}}(e)_n \\=& t_{\mathcal{P}}(e)_m = t_{\mathcal{P}}(k_E(h))_m=(k^\star_V(t_{\mathcal{K}}(h)))_m = k_V(t_{\mathcal{K}}(h)_m)	\end{align*}
+
+	Since $k_V$ is injective, then $t_{\mathcal{K}}(h)_n=t_{\mathcal{K}}(h)_m$, which contradicts the left monogamy of $\mathcal{K}$.
+
+	\item $e=h_E(\iota_E(h))$ for some $h$ in the complement $A$ of the image of $f_1$.
+Now, suppose that there exists $u \in V_{\mathcal{G}}$ such that $t_{\mathcal{H}}(h)_n = g_1(u) $ or $t_{\mathcal{H}}(h)_m = g_1(u)$.
+Since $(f_1, g_1)$ is downward-closed in both cases we get $h_1\in E_{\mathcal{G}}$ such that $f_1(h_1)=h$, which is absurd.
+
+	Thus there exist $b_1, b_2\in B$ such that
+	\[t_{\mathcal{H}}(\iota_E(h))_n = \iota_V(b_1) \qquad  t_{\mathcal{H}}(\iota_E(h))_m = \iota_V(b_2)\] 
+	But then we have
+	\begin{align*}
+		&h_V(\iota_V(b_1))=h_V(t_{\mathcal{H}}(\iota_E(h))_n)=(h^\star_V(t_{\mathcal{H}}(\iota_E(h))))_n=t_{\mathcal{P}}(h_E(\iota_E(h)))_n=t_{\mathcal{P}}(e)_n\\=&t_{\mathcal{P}}(e)_m=t_{\mathcal{P}}(h_E(\iota_E(h)))_m=(h^\star_V(t_{\mathcal{H}}(\iota_E(h))))_m=h_V(t_{\mathcal{H}}(\iota_E(h))_m)=	h_V(\iota_V(b_2))
+	\end{align*}
+	By \Cref{lem:po_set} $h_V\circ \iota_V$ is injective and so $b_1 = b_2$. Hence $t_{\mathcal{H}}(\iota_E(h))_n =t_{\mathcal{H}}(\iota_E(h))_m $, which is absurd since $\mathcal{H}$ is left-monogamous.
+\end{itemize}
+
+ Suppose now that there are $e_1, e_2\in E_{\mathcal{P}}$ such that $t_{\mathcal{P}}(e_1)_n=t_{\mathcal{P}}(e_2)_m$ for some indexes $1\leq n \leq \lgh_{V_{\mathcal{P}}}(e_1)$ and $1\leq m \leq \lgh_{V_{\mathcal{P}}}(e_2)$.
+To conclude, we have to show that $e_1=e_2$.
+We can again use \Cref{lem:po_set} to split the cases.
+
+\begin{itemize}
+	\item $e_1=k_E(k_1)$ and $e_2=k_E(k_2)$ for some $k_1$ and $k_2\in E_{\mathcal{K}}$. Then we have
+	\begin{align*}
+		&k_V(t_{\mathcal{K}}(k_1)_n)=(k^\star_V(t_{\mathcal{K}}(k_1)))_n=t_{\mathcal{P}}(k_E(k_1))_n=t_{\mathcal{P}}(h_1)_n\\=&t_{\mathcal{P}}(h_2)_m=t_{\mathcal{P}}(k_E(k_2))_m=(k^\star_V(t_{\mathcal{K}}(k_2)))_m=k_V(t_{\mathcal{K}}(k_2)_m)
+	\end{align*}
+	Since $k_V$ is injective, $t_{\mathcal{K}}(k_1)_n=t_{\mathcal{K}}(k_1)_m$. And  $\mathcal{K}$ is left-monogamous, so we conclude that $k_1=k_2$ and so also $e_1$ and $e_2$ are equal.
+	\item $e_1=k_E(k)$ and $e_2=h_E(\iota_{E}(h))$ for some $k\in E_{\mathcal{K}}$ and $h\in A$. 
+	then we have
+	\begin{align*}
+		&k_V(t_{\mathcal{K}}(k)_n)= (k^\star_V(t_{\mathcal{K}}(k)))_n=t_{\mathcal{P}}(k_E(k))_n=t_{\mathcal{P}}(e_1)_n\\=&t_{\mathcal{P}}(e_2)_m=t_{\mathcal{P}}(h_E(\iota_E(h)))_m=(h^\star_V(t_{\mathcal{H}}(\iota_E(h))))_m= h_V(t_{\mathcal{H}}(\iota_{E}(h))_m)
+	\end{align*}
+	By the first point of \Cref{prop:regmono}, there exists $w\in V_{\mathcal{G}}$ such that 
+	\[t_{\mathcal{K}}(k)_n=g_2(w) \qquad t_{\mathcal{H}}(\iota_{E}(h))_m=g_1(w)\]
+Since $(f_1, g_1)$ is downward-closed, the second equation above entails that there exists $a\in E_{\mathcal{G}}$ such that $\iota_E(h)=f_1(a)$.
+But this is absurd since coproducts in $\Set$ are disjoint.
+
+	\item  $e_1=h_E(\iota_{E}(h))$ and $e_2=k_E(k)$ for some $k\in E_{\mathcal{K}}$ and $h\in A$. This is done as in the previous case swapping the role of $e_1$ and $e_2$.
+
+	\item $e_1=h_E(\iota_E(h_1))$ and $e_2=h_E(\iota_E(h_1))$ for some $h_1$ and $h_2\in A$.  Suppose that there exist $x_1, x_2\in V_{\mathcal{G}}$ such that
+	\[t_{\mathcal{H}}(\iota_E(h_1))_n = g_1(x_1) \qquad t_{\mathcal{H}}(\iota_E(h_1))_m = g_1(x_2)\]
+	Being $(f_1, g_1)$ downward-closed, these identities entails the existence of $a_1, a_2\in E_{\mathcal{G}}$ such that 
+	\[\iota_E(h_1)=f_1(a_1) \qquad \iota_E(h_2 = f_1(a_2))\]
+	which is absurd. Thus there there exist $b_1, b_2\in B$ such that
+	\[t_{\mathcal{H}}(\iota_E(h_1))_n=\iota_V(b_1) \qquad t_{\mathcal{H}}(\iota_E(h_2))_m=\iota_V(b_2)\]
+	Moreover
+	\begin{align*}
+	&h_V(\iota_V(b_1))=h_V(t_{\mathcal{H}}(\iota_E(h_1))_n)=(h^\star_V(t_{\mathcal{H}}(\iota_E(h_1))))_n=t_{\mathcal{P}}(h_E(\iota_E(h_1)))_n=t_{\mathcal{P}}(e_1)_n\\=&t_{\mathcal{P}}(e_2)_m=t_{\mathcal{P}}(h_E(\iota_E(h_2)))_m=(h^\star_V(t_{\mathcal{H}}(\iota_E(h_2))))_m=h_V(t_{\mathcal{H}}(\iota_E(h_2))_m)=h_V(\iota_V(b_2))
+	\end{align*}
+	But $h_V\circ \iota_V\colon B\mto V_{\mathcal{P}}$ is injective and so $b_1$ and $b_2$ are equal.
+Hence $t_{\mathcal{H}}(\iota_E(h_1))_n = t_{\mathcal{H}}(\iota_E(h_2))_m$.
+Since $\mathcal{H}$ is in $\lmo$ we get that $\iota_E(h_1)=\iota_E(h_2)$ and so $e_1$ is equal to $e_2$.
+	\qedhere 
+\end{itemize}
+\end{proof}
+
+\regmono*
+\begin{proof}\label{proof:regmon} $(1\Rightarrow 2)$ Let $(h_1, k_1)$ and $(h_2, k_2): \mathcal{H}\rightrightarrows \mathcal{K}$  be two arrows  equalized by $(f,g)$ and define
+
+	\noindent 
+ \begin{minipage}[r]{.7\linewidth} 	\setlength{\parindent}{1.5em}
+ \vspace{-.5cm}
+ 	\[ E_{h_1, h_2}:= \{e\in E_{\mathcal{H}} \mid h_1(e) = h_2(e)\} \qquad E_{k_1, k_2}:= \{v\in V_{\mathcal{H}} \mid k_1(v) = k_2(v)\} \]
+
+Let $\iota_E\colon E_{h_1, h_2}\mto E_{\mathcal{H}} $ and $\iota_V\colon V_{k_1, k_2}\mto V_{\mathcal{H}}$ be the corresponding inclusions. Let 
+$s_{\mathcal{E}}, t_{\mathcal{E}} \colon E_{h_1, k_1}\rightrightarrows V^\star_{k_1, k_2}$ be the unique arrows fitting in the diagram aside and define $\mathcal{E}$ as $(E_{h_1, h_2}, V_{k_1, k_2}, s_{\mathcal{E}}, t_{\mathcal{E}})$.
+We know by  Propositions \ref{prop:fact}, \ref{prop:com} and \Cref{lim}, that  $(\mathcal{E}, (\iota_E, \iota_V))$, is an equalizer  for $(h_1, k_1)$ and $(h_2, k_2)$.
+Thus there is an isomorphism $(\phi, \psi) \colon \mathcal{G}\to \mathcal{E}$ whose components fit in the diagram aside and such that
+\[\iota_V\circ \psi = g \qquad \iota_E\circ \phi = f\] 
+		\end{minipage}\hfill 	 \begin{minipage}[r]{.3\linewidth}
+	 	\xymatrix@R=8pt{E_{\mathcal{G}} \ar@/^.3cm/@{>->}[rr]^{f} \ar[d]_{s_{\mathcal{G}}}\ar@{.>}[r]_-{\phi}&  E_{h_1, h_2} \ar@{.>}[d]_{s_{\mathcal{E}}} \ar@{>->}[r]_-{\iota_E} & E_{\mathcal{H}} \ar[d]_{s_{\mathcal{H}}}\\V^\star_{\mathcal{G}} \ar@/_.3cm/@{>->}[rr]_{g^\star} \ar@{.>}[r]^-{\psi^\star}& V^\star_{k_1, k_2} \ar@{>->}[r]^-{\iota^\star_V}& V^\star_{\mathcal{H}}}
+	 	\xymatrix@R=8pt{E_{\mathcal{G}} \ar@/^.3cm/@{>->}[rr]^{f} \ar[d]_{t_{\mathcal{G}}}\ar@{.>}[r]_-{\phi}&  E_{h_1, h_2} \ar@{.>}[d]_{t_{\mathcal{E}}} \ar@{>->}[r]_-{\iota_E} & E_{\mathcal{H}} \ar[d]_{t_{\mathcal{H}}}\\V^\star_{\mathcal{G}}\ar@/_.3cm/@{>->}[rr]_{g^\star} \ar@{.>}[r]^-{\psi^\star}& V^\star_{k_1, k_2} \ar@{>->}[r]^-{\iota^\star_V}& V^\star_{\mathcal{H}}}
+	 \end{minipage}
+
+	Now, let $v\in V_{\mathcal{G}}$ be an input node and suppose that there exists $h\in E_{\mathcal{H}}$ such that $\outd{H}(g(v), h)>0$. For such an hyperedge. For such an hyperedge we have
+	\[\outd{K}(k_1(g(v)), h_1(h)) >0 \qquad \outd{K}(k_2(g(v)), h_2(h)) >0 \]
+	but we also have that 
+	\[k_1(g(v))=k_1(\iota_V(\psi(v))=k_2(\iota_V(\psi(v)))=k_2(g(v))\]
+	and so, by left-monogamy of $\mathcal{K}$, $h$ must belong to $E_{h_1, h_2}$.
+Thus there exists $e\in E_{\mathcal{G}}$ such that $\iota_E(\phi(e))=h$ and such that $\psi(e)$ is a letter of $t_{\mathcal{E}}(\phi(e))$.
+But then
+	\[\outd{G}(v, e) = \outd{E}(\psi(v), \phi(e)) > 0\]
+	contradicting the fact that $v$ is an input node.
+
+	\smallskip \noindent
+	$(2\Rightarrow 3)$ This follows at once from \Cref{lem:inp}.
+
+	\smallskip \noindent
+	$(3\Rightarrow 1)$ Let us consider the pushout of $(f,g)$ along itself in $\hyp$ as depicted by the first square below.
+By \Cref{prop:com} and \Cref{colim} we know that the other two squares are pushouts too
+	\[\xymatrix@C=35pt{\mathcal{G} \ar[r]^{(f,g)}  \ar[d]_{(f,g)}& \mathcal{H}\ar[d]^{(p_1, p_2)} & E_{\mathcal{G}} \ar@{>->}[d]_{f}\ar@{>->}[r]^{f} & E_{\mathcal{H}} \ar[d]^{p_1}& V_{\mathcal{G}}\ar@{>->}[r]^{g} \ar@{>->}[d]^{g} & V_{\mathcal{H}} \ar[d]^{p_2}\\\mathcal{H} \ar[r]_{(q_1, q_2)} & \mathcal{P} & E_{\mathcal{H}} \ar[r]_{q_1}& E_{\mathcal{P}} & V_{\mathcal{H}}\ar[r]_{q_2} & V_{\mathcal{P}}}\]
+
+	 By \Cref{cor:monhyper} we also know that $f$ and $g$ are monos in $\Set$ and so, by the dual of \Cref{prop:reg_epi_coeq} $(E_\mathcal{G}, f)$ and $(V_{\mathcal{G}}, g)$ are equalizers for, respectively, $p_1, q_1\colon E_{\mathcal{H}}\rightrightarrows E_{\mathcal{P}}$ and $p_2, q_2\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{P}}$.
+
+	By \Cref{prop:com} and \Cref{lim} this entails that $(\mathcal{G}, (f,g))$ is the equalizer in $\hyp$ of $(p_1, p_2)$ and $(q_1, q_2)$.
+By \Cref{prop:pusho}, $\mathcal{P}$ is left-monogamous, thus by \Cref{cor:eq} $(f,g)$ is regular mono as wanted.
+\end{proof}
+
+\subsubsection{Separated hypergraphs - proofs}
+
+\sep*
+
+\begin{proof}\label{proof:sep}
+	Let $(h_1, h_2)\colon \mathcal{G}\to \mathcal{H}$ be a morphism of hypergraphs. For every hyperedge $e\in E_{\mathcal{G}}$,
+	the universal property of coproducts, there are arrows $f_e\colon V_e\to V_{h_1(e)}$ fitting in the middle of the diagram below.
+These, in turn, yield the dotted $\hat{h}_1\colon V_{\sp(\mathcal{G})} \to V_{\sp(\mathcal{G})}$ on the bottom.
+
+	\noindent 
+	\begin{minipage}[l]{.65\linewidth}
+		\setlength{\parindent}{1.5em}
+		Given $e\in E_{\mathcal{G}}$, if $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we have :
+		\begin{align*}
+			&\hat{h}_1^\star(s_{\sp(\mathcal{G})}(e)) = \hat{h}_1^\star(\prod_{i=1}^{n_e} \iota_e(\iota^e_{i}(0)))=\prod_{i=1}^{n_e} \hat{h}_1(\iota_e(\iota^e_{i}(0)))=\prod_{i=1}^{n_e} \iota_{h_1(e)}(\iota^{h_1(e)}_{i}(0)) =   s_{\sp(\mathcal{G})}(h_1(e))
+		\end{align*}
+		\[\hat{h}_1^\star(t_{\sp(\mathcal{G})}(e)) =\hat{h}_1^\star(\prod_{i=n_e+1}^{m_e} \iota_e(\iota^e_{i}(0)))=\prod_{i=n_e+1}^{m_e} \hat{h}_1(\iota_e(\iota^e_{i}(0)))=\prod_{i=n_e+1}^{m_e} \iota_{h_1(e)}(\iota^{h_1(e)}_{i}(0)) =   t_{\sp(\mathcal{G})}(h_1(e))\]
+		so that $(\id{E_{\mathcal{G}}}, \hat{h}_1)$ is a morphism of hypergraphs.
+	\end{minipage}
+	\hfill
+	\begin{minipage}[r]{.3\linewidth} \vspace{-1.9cm}
+		\xymatrix@R=10pt@C=30pt{1 \ar[r]^{\id{1}} \ar@{>->}[d]^{\iota^e_i}& 1 \ar@{>->}[d]_{\iota^{h_1(e)}_i}\\ V_e  \ar@{.>}[r]^-{f_e} \ar@{>->}[d]^{\iota_{e}}& V_{h_1(e)} \ar@{>->}[d]_{\iota_{h_1(e)}}\\ V_{\sp(\mathcal{G})} \ar@{.>}[r]^-{\hat{h}_1} &  V_{\sp(\mathcal{H})}}
+	\end{minipage}
+
+	If $h_1$ is the identity, then clearly  $\hat{h}_1=\id{V_{\sp(\mathcal{G})}}$. If $(k_1, k_2)$ is another morphism $\mathcal{H}\to \mathcal{K}$, then we have:
+	\[\hat{k}_1\circ \hat{h}_1\circ \iota_e\circ \iota^e_i=\hat{k}_1\circ \iota_{h_1(e)}\circ \iota^{h_1(e)}_i =\iota_{k_1(h_1(e))}\circ \iota^{k_1(h_1(e))}_i\]
+	which entails preservation of composition.
+\end{proof}
+
+\dx*
+\begin{proof}\label{proof:dx}
+	Let $\mathcal{G}$ be an hypergraph.
+For every $e\in E_{\mathcal{G}}$, let $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$.
+Given $1\leq i\leq n_e+m_e$,  we can define $\delta^e_i\colon \mto V_{\mathcal{G}}$ as
+	\[\delta^e_i(0) =\begin{cases}
+		s_{\mathcal{G}}(e)_i & i\leq n_e\\
+		t_{\mathcal{G}}(e)_{i-n_e} &  n_e < i
+	\end{cases}\]
+
+In turn,this allows us to define $\epsilon_{G}\colon V_{\sp(\mathcal{G})}\to V_{\mathcal{G}}$ as the unique one fitting in the diagram below.
+
+	\noindent 
+	\begin{minipage}[l]{.8\linewidth}
+		\setlength{\parindent}{1.5em}
+		Now, for every hyperedge $e\in E_{\mathcal{G}}$ we have :
 		\begin{gather*}
-	(\pi^D_V)^\star \circ s_{\mathcal{L}}\circ \iota_{k,l} = (\pi^D_V)^\star\circ s^{k,l}_{\mathcal{L}} \circ \pi^D_{k,l}=s_D\circ i^D_{k,l}\circ \pi^D_{k,l} = s_D\circ i^D_{k,l}\circ \pi^D_{k,l}
-	=s_D\circ \pi^D_E \circ \iota_{k,l} \\
-		(\pi^D_V)^\star\circ t_{\mathcal{L}}\circ \iota_{k,l} = (\pi^D_V)^\star\circ t^{k,l}_{\mathcal{L}} \circ \pi^D_{k,l}=t_D\circ i^D_{k,l}\circ \pi^D_{k,l} = t_D\circ i^D_{k,l}\circ \pi^D_{k,l}
-	=t_D\circ \pi^D_E \circ \iota_{k,l} 
+			\epsilon_{\mathcal{G}}^\star(s_{\sp(\mathcal{G})}(e)) = \epsilon_{\mathcal{G}}^\star(\prod_{i=1}^{n_e} \iota_e(\iota^e_{i}(0)))=\prod_{i=1}^{n_e} \epsilon_{\mathcal{G}}(\iota_e(\iota^e_{i}(0)))=\prod_{i=1}^{n_e} \delta^e_i(0) =\prod_{i=1}^{n_e} s_{\mathcal{G}}(e)_i=   s_{\mathcal{G}}(e)\\
+		\epsilon_{\mathcal{G}}^\star(t_{\sp(\mathcal{G})}(e)) = \epsilon_{\mathcal{G}}^\star(\prod_{i=n_e+1}^{n_e + m_e} \iota_e(\iota^e_{i}(0)))=\prod_{i=n_e+1}^{n_e + m_e} \epsilon_{\mathcal{G}}(\iota_e(\iota^e_{i}(0)))=\prod_{n_e+i=1}^{n_e + m_e} \delta^e_i(0) = \prod_{n_e+i=1}^{n_e + m_e}  t_{\mathcal{G}}(e)_i  = t_{\mathcal{G}}(e)
 		\end{gather*} 
-
-Let now $(\mathcal{G}, \{(h_{1,D}, h_{2,D})\}_{D\in \D})$ be a cone over $F$. Since $(V, \{\pi^D_V\}_{D\in \D})$ is limiting we obtain an arrow $h\colon V_{\mathcal{G}}\to V$.  Now, let 
-\[E_{k,l}^{\mathcal{G}}:=\{	E^{\mathcal{G}}_{k,l}:=\{e\in E_{\mathcal{G}} \mid \lgh_{V_{\mathcal{G}}}(s_{{\mathcal{G}}}(e)) = k \text{ and } \lgh_{V_{\mathcal{G}}}(t_{{\mathcal{G}}}(e)) = l \}\]
-
-\noindent 
-\begin{minipage}[l]{.72\linewidth}
-			\setlength{\parindent}{1.5em}
-
-Let $i^{\mathcal{G}}_{k,l}\colon E^{\mathcal{G}}_{k,l} \mto E_{\mathcal{G}} $ be the inclusion.
-By definition of $E^{D}_{k,l}$ and $E^{\mathcal{G}}_{k,l}$, the two squares aside are pullback.
-By extensivity, this entails that $(E_{\mathcal{G}}, \{i^\mathcal{G}_{k,l}\})$ is the coproduct of the family $\{E_{k,l}^{\mathcal{G}}\}_{k,l \in \mathbb{N}}$, where $i^\mathcal{G}_{k,l}\colon E_{k,l}^{\mathcal{G}}\mto E_{\mathcal{G}}$ is the inclusion.
-Using \Cref{rem:le}, we have:
-\begin{gather*}\lgh_{V_D} \circ s_{D}\circ h_{1,D}\circ \iota^{\mathcal{G}}_{k,l}=\lgh_{V_D}\circ h^\star_{2,D}\circ s_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l}=\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l} = \delta_{k} \circ !_{E^{\mathcal{G}}_{k,l}}\\
-	\lgh_{V_D} \circ t_{D}\circ h_{1,D}\circ \iota^{\mathcal{G}}_{k,l}=\lgh_{V_D}\circ h^\star_{2,D}\circ t_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l}=\lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}}\circ i^{\mathcal{G}}_{k,l} = \delta_{l} \circ !_{E^{\mathcal{G}}_{k,l}}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[r]{.3\linewidth} \vspace{-.9cm}
+		\xymatrix@R=10pt@C=30pt{1 \ar[r]_{\id{1}} \ar@{>->}[d]^{\iota^e_i}& 1 \ar@{>->}[dd]_{\delta^e_i}\\ V_e \ar@{>->}[d]^{\iota_e}  \\ V_{\sp(\mathcal{G})} \ar@{.>}[r]^-{\epsilon_{\mathcal{G}}} &  V_{\mathcal{G}}}
+	\end{minipage}
+
+	\smallskip 
+	Hence $(\id{E_{\mathcal{G}}}, \epsilon_{G})$ is a morphism $P(\sp(\mathcal{G}))\to \mathcal{G}$.
+Now, let $(f,g)\colon P(\mathcal{H})\to \mathcal{G}$ be a  morphism of pruned hypergraphs with $\mathcal{H}$ separated.
+Given a node $v$ in $V_{\mathcal{H}}$ we know that there exists exactly one $e_v$ such that $v$ occurs in $s_{\mathcal{H}}(e_v)$ or in $t_{\mathcal{H}}(e_v)$.
+Moreover, $v$ occurs exactly once and not in both.
+Let $i_v$ be the index at which it appears.
+We define:
+	\[\hat{g}(v):=\begin{cases}
+		\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0)) & v \text{ occurs in } s_{\mathcal{H}}(e)\\
+		\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0)) & v \text{ occurs in } t_{\mathcal{H}}(e)\\
+	\end{cases}\]
+	Computing we get:
+	\begin{gather*}
+		\hat{g}^\star(s_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{n_e} s_{\mathcal{H}}(e)_i)=\prod_{i=1}^{n_e}(\hat{g}(s_{\mathcal{H}}(e)_i))=\prod_{i=1}^{n_e}\iota_{f(e)}( \iota^{f(e)}_i(0))=s_{\sp(\mathcal{G})}(f(e))\\
+		\hat{g}^\star(t_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{m_e} t_{\mathcal{H}}(e)_i)=\prod_{i=1}^{m_e}(\hat{g}(t_{\mathcal{H}}(e)_i))=\prod_{i=1}^{m_e}\iota_{f(e)}( \iota^{f(e)}_{n_e+i}(0))=\prod_{i=n_e + 1}^{n_e + m_e}\iota_{f(e)}( \iota^{f(e)}_{i}(0))=t_{\sp(\mathcal{G})}(f(e))
 	\end{gather*}
-
-By the universal property of the second square, the previous equations give us the dotted $f^D_{k,l} \colon E^{\mathcal{G}}_{k,l}\to E^D_{k,l}$ in the last diagram aside.
-Since $(E_{k,l}, \{\pi^D_{k,l}\}_{D\in \D})$ is the product of the family $\{E^D_{k,l}\}_{D\in \D}$, then $\{f^D_{k,l}\}_{D\in \D}$ gives us the dotted arrow $f_{k,l}\colon E^{\mathcal{G}}_{k,l}\to E_{k,l}$ inthe middle row.
-Finally, by the universal property of coproducts,  the family $\{f^D_{k,l}\}_{k,l\in \mathbb{N}}$ induces the morphism $h_1\colon E_{\mathcal{G}}\to E_{\mathcal{L}}$ in the top row.
-\end{minipage} \hfill
-\begin{minipage}[r]{.25\linewidth}
-	\xymatrix@R=10pt@C=55pt{E^{\mathcal{G}}_{k,l} \ar[d]_{!_{E^{\mathcal{G}}_{k,l}}} \ar@{>->}[r]^{i^{\mathcal{G}}_{k,l}}& E_{\mathcal{G}}\ar[d]_{(\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}})}\\ 1 \ar@{>->}[r]_{(\delta_k, \delta_l)}& \mathbb{N}\times \mathbb{N}}
-
-\xymatrix@R=10pt@C=55pt{E^{D}_{k,l} \ar[d]_{!_{E^{D}_{k,l}}} \ar@{>->}[r]^{i^{D}_{k,l}}& E_D\ar[d]_{(\lgh_{V_{D}}\circ s_{D}, \lgh_{V_{D}}\circ t_{D})}\\ 1 \ar@{>->}[r]_{(\delta_k, \delta_l)}& \mathbb{N}\times \mathbb{N}}
-
-	\xymatrix@R=10pt@C=35pt{ E_{\mathcal{G}} \ar@{.>}[r]^{h_1} \ar@/_.5cm/[dd]_(.3){h_{1,D}}& E_{\mathcal{L}} \\ E^{\mathcal{G}}_{k,l} \ar@{>->}[u]_{\iota^{\mathcal{G}}_{k,l}} \ar@{.>}[r]^{f_{k,l}} \ar@{.>}[dr]_{f^D_{k,l}} & E_{k,l} \ar[d]^{\pi^D_{k,l}} \ar@{>->}[u]_{\iota_{k,l}}\\ E_{D}  & E^D_{k,l} \ar@{>->}[l]^{\iota^D_{k,l}}}
-\end{minipage}
-
-Now, computing we get:
+	proving that $(f, \hat{g})\colon \mathcal{H}\to\sp( \mathcal{G})$ is a morphism of $\pshyp$. Notice that	
 	\begin{align*}
-	s_{\mathcal{L}}\circ h_1 \circ \iota^{\mathcal{G}}_{k,l} = s_{\mathcal{L}}\circ \iota_{k,l}\circ f_{k,l} =v_k\circ s^{k, l}_{\mathcal{L}} \circ f_{k,l}\\
-	h^\star\circ s_{\mathcal{G}}\circ \iota^{\mathcal{G}}_{k,l}
+		&\epsilon_\mathcal{G}(\hat{g}(v))=\begin{cases}
+			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0))) & v \text{ occurs in } s_{\mathcal{H}}(e_v)\\
+			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0))) & v \text{ occurs in } t_{\mathcal{H}}(e_v)
+		\end{cases}=	\begin{cases}
+		\delta^{f(e_v)}_{i_v}(0)& v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		\delta^{f(e_v)}_{i_v}(0)& v \text{ occurs in } t_{\mathcal{G}}(e)
+		\end{cases}\\ =&
+		\begin{cases}
+			s_{\mathcal{G}}(f(e_v))_{i_v}& v \text{ occurs in } s_{\mathcal{G}}(e)\\
+			t_{\mathcal{G}}(f(e_v))_{i_v}& v \text{ occurs in } t_{\mathcal{G}}(e)
+		\end{cases}= \begin{cases}
+		(g^\star(s_{\mathcal{H}}(e_v)))_{i_v}& v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		(g^\star(t_{\mathcal{H}}(e_v)))_{i_v}& v \text{ occurs in } t_{\mathcal{G}}(e)\\
+		\end{cases}\\=&\begin{cases}
+		g(s_{\mathcal{H}}(e_v)_{i_v})& v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		g(t_{\mathcal{H}}(e_v)_{i_v})& v \text{ occurs in } t_{\mathcal{G}}(e)\\
+		\end{cases}=g(v)
 	\end{align*}
-
-For uniqueness,
-
+and so $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(f, \hat{g})=(f,g)$.
+
+	Let now $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(h, k)=(f,g)$.
+This entails immediately that $h =f$.
+Let $v$ be a node $V_{\mathcal{H}}$, since $\mathcal{H}$ is pruned, we have two cases:
+	\begin{itemize}
+		\item $v$ occurs in $s_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have:
+		\[\hat{g}(v)=\hat{g}(s_{\mathcal{H}}(e)_i)=(g^\star(s_{\mathcal{H}}(e)))_i=s_{\sp(\mathcal{G})}(f(e))_i=(k^\star(s_{\mathcal{H}}(e)))_i=k(s_{\mathcal{H}}(e)_i)=k(v)\]
+		\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have:
+		\[\hat{g}(v)=\hat{g}(t_{\mathcal{H}}(e)_i)=(g^\star(t_{\mathcal{H}}(e)))_i=t_{\sp(\mathcal{G})}(f(e))_i=(k^\star(t_{\mathcal{H}}(e)))_i=k(t_{\mathcal{H}}(e)_i)=k(v)\]
+	\end{itemize}
+In both cases $\hat{g}(v)=k(v)$ and so $\hat{g}= k$ as wanted.
 \end{proof}
@@
 				\[(t_{\mathcal{L}}(e))_i=v \qquad  (t_{\mathcal{L}}(e') )_k= v\]
-		Then, givem $D\in \D$ we have:
+		Then, given $D\in \D$ we have:
 		\begin{align*}&(t_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(t_{\mathcal{L}}(e)))_i=p^\star_{V, D}((t_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((t_{\mathcal{L}}(e'))_k)=(p^\star_{V,D}(t_{\mathcal{L}}(e')))_k=(t_{S(F(D))}( p_{E,D}(e')))_k
@@
 
-\count*
-\begin{proof}\label{proof:count}
-	\begin{enumerate}
-		\item Let $n$ and $m$ be the lengths of, respectively $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ and suppose that
-		\[s_{\mathcal{G}}(e)=\prod_{i=1}^{n}a_i \qquad t_{\mathcal{G}}(e)=\prod_{i=1}^{n}b_i\]
-
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{proof}\label{proof:prod}
-\end{proof}
 \subsection{Proofs for \Cref{hypereq}}\label{app:due}

### 2025-08-20 jlamp/jlamp.tex
sez. 3

@@
 
-\subsection{The category of hypergraphs}
+\subsection{The category of hypergraphs}\label{sub:hyp}
 
@@
 
-		We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes and $\Delta \circ \ari_\Sigma$ as the source function and $ \Delta \coar_{\Sigma}$ as target function, where $\Delta \colon \mathbb{N}\to 1^\star$ is the isomorphism of \Cref{rem:length}.
+		We define the \emph{hypergraph $\mathcal{G}_\Sigma$ associated with $\Sigma$} taking $O_\Sigma$ as set of hyperedges, $1$ as set of nodes and $\Delta \circ \ari_\Sigma$ as the source function and $ \Delta \circ  \coar_{\Sigma}$ as target function, where $\Delta \colon \mathbb{N}\to 1^\star$ is the isomorphism of \Cref{rem:length}.
 	\end{defi}
@@
  We can interpret an arbitrary hypergaph as a \emph{typed} or \emph{colored} monoidal signature: the set of nodes provides the \emph{types} or \emph{colors}, while hyperedges can be thought of as operations, with arity and coarity provided by the source and target functions, respectively.
-This suggests the following definition, which will be used in Section \ref{par:tg}.
+This suggests the following definition, which will be used in Section \ref{par:tg}\label{sub:hyp_alg}.
 
@@
 
-\subsubsection{Two  subcategories of $\hyp$}
+\subsubsection{Two  subcategories of $\hyp$}\label{sub:sub}
 
@@
 
-\begin{cor}$\lmo$ is quasiadhesive.
+\begin{cor}\label{cor:lmquasi}$\lmo$ is quasiadhesive.
 \end{cor}
@@
 
-Our interest for hypergraphs stems from their use as a graphical representation of algebraic terms. We thus need a way to label hyperedges with symbols taken from a signature.
-
-\begin{exa}segnature The category $\hyps$ of \emph{algebraically labelled hypergraphs} is the slice category $\hyp/\mathcal{G}^\Sigma$.
-\end{exa}
-
-\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\Sigma}$ and a characterisation of monos in it.
-
-\begin{prop}\label[proposition]{prop:mono} Let $\Sigma$ be an algebraic signature. Then the following facts hold
+Our interest for hypergraphs stems from their use as a graphical representation of algebraic terms.
+As  noted in \Cref{sub:hyp_alg}, an hypergraph can be thought as a colored monoidal signature.
+Thus labelling correspnds to the operationn of taking the slice category over a suitable hypergraph.
+
+\begin{defi}
+	Given an hypergraph $\mathcal{G}$, the category $\hyp_\mathcal{G}$ of hypergraphs \emph{labelled by $\mathcal{G}$}  or of \emph{$\mathcal{G}$-hypergraphs} is $\hyp/\mathcal{G}$.
+\end{defi}
+
+\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\mathcal{G}}$ and a characterisation of monos in it.
+
+\begin{prop}\label{prop:mono} Let $\mathcal{G}$ be an hypergraph. Then the following facts hold
 	\begin{enumerate}
-		\item an arrow $(h,k)$ in $\hyp_{\Sigma}$ is a mono if and only if $h$ and $k$ are injective;
-		\item $\hyp_{\Sigma}$ is an adhesive category. 
+		\item an arrow $(h,k)$ in $\hyp_{\mathcal{G}}$ is a mono if and only if $h$ and $k$ are injective;
+		\item $\hyp_{\mathcal{G}}$ is an adhesive category. 
 	\end{enumerate}
@@
 
+\begin{exa} A useful example is given by an algebraic signature $\Sigma$. Consider the hypregraph of \Cref{exa_3}, the category $\hyps$ of
+	hypergraphs labelled by $\Sigma$ is the slice category $\hyp/\mathcal{G}^\Sigma$.
+\end{exa}
+
 \noindent 
 \begin{minipage}[l]{.8\linewidth}	
-	\begin{rem}\label[remark]{rem:label}	
+	\begin{rem}	\label{rem:label}
 			\setlength{\parindent}{1.5em}
-		Let $\mathcal{H}=(E, V, s, t)$ be a hypergraph, by definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
+
+			Consider an algebraic signature $\Sigma$ and an hypergraph $\mathcal{H}=(E, V, s, t)$.
+By definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
 
 		Now, consider a coprojection $v_n\colon V^n_\mathcal{H}\to  V^\star_{\mathcal{H}}$.
-By the second diagram above entails that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V_\mathcal{H}^{\star}$ of words of length $1$, i.e.~all hyperedges must have targets of length $1$, that is $t_{\mathcal{H}}=v_1\circ \tau_{\mathcal{H}}$ for some $\tau_{\mathcal{H}}\colon E_{\mathcal{H}}\to V_{\mathcal{H}}$.
+Since $\Delta\circ \coar_\Sigma$ is the constant function in $1$,  the second diagram aside entails, together with \Cref{rem:len}, that $t_{\mathcal{H}}$ factors via the inclusion $v_1\colon V_{\mathcal{H}}\to V_\mathcal{H}^{\star}$ of words of length $1$, i.e $\mathcal{H}$ must be algebraic.
 	\end{rem}
@@
 \begin{minipage}[r]{.15\linewidth}
-	\xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]^{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\ari_\Sigma}& \mathbb{N}} \hspace{1pt}\\ \xymatrix@R=10pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]^{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\gamma_1}& \mathbb{N}}
-\end{minipage}
-
-$\hyp_{\Sigma}$ has a forgetful functor $U_{\Sigma}\colon \hyp_{\Sigma}\to \X$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $U_{\hyp}(\mathcal{H}$).
-Now, since $U_{\hyp}(\mathcal{G}^{\Sigma})=1$
+	\xymatrix@R=14pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{s_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\Delta\circ \ari_\Sigma}& \mathbb{N}} 
+	 \xymatrix@R=14pt{E_{\mathcal{H}} \ar[d]_{h}\ar[r]_{t_{\mathcal{H}}} & V^\star_{\mathcal{H}} \ar[d]^{\lgh_{V_{\mathcal{H}}}} \\  O_\Sigma \ar[r]^{\Delta\circ \coar_\Sigma}& \mathbb{N}}
+\end{minipage}
+
+\iffalse 
+\smallskip 
+$\hyp_{\mathcal{G}}$ has a forgetful functor $U_{\mathcal{G}}\colon \hyp_{\mathcal{G}}\to \Set/V_{\mathcal{G}}$ which sends $(h,k)\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ to $k\colon V_\mathcal{H} \to V_{\mathcal{G}}$.
+Now, since $U_{\hyp}(\mathcal{G}^{\Sigma}=1$
 for every set $X$ we can define $\Delta_{\Sigma}(X)\colon \Delta_{\hyp}(X)\to \mathcal{G}^{\Sigma}$  as $(?_{O_\Sigma}, !_{X})$.
@@
 \end{prop}
-\iffalse 
+
+\begin{rem}
+	contenuto...
+\end{rem}
 \begin{proof}Let $(h, !_{V_\mathcal{H}})\colon \mathcal{H}\to \mathcal{G}^{\Sigma}$ be an object of $\hyp_{\Sigma}$, and suppose that there exists $f\colon X\to U_{\Sigma}(\mathcal{H})$.
@@
 
-We extend our graphical notation of hypergraphs to labeled ones putting the label of an hyperedge $h$ inside its corresponding square.
+\smallskip
+
+We extend our graphical notation of hypergraphs to labelled ones putting the label of an hyperedge $h$ inside its corresponding square.
 
@@
 
-\color{red}
-TO DO - questo comprende anche la sezione successiva (?) come sottosezione + versione etichettata (anche con cose monoidali) dopo
-
-Ipergrafi scoppiati con equivalenza/congruenza -> adesività (spero) + versione etichettata (monoidale boh)
-
+As we have done in \Cref{sub:sub}, we can restrict our attention to two subcategories of labelled hypergraphs.
+
+\begin{defi}
+	Let $\mathcal{G}$ be an hypergraph and $(h,k)\colon \mathcal{H}\to \mathcal{G}$  a $\mathcal{G}$-hypergraph.
+We say that $(h,k)$ is a \emph{left-monogamous} (resp.~\emph{separated}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated).
+
+	We will denote by $\lmo_{\mathcal{G}}$ and $\shyp_{\mathcal{G}}$  the corresponding subcategories of $\hyp_{\mathcal{G}}$.
+\end{defi}
+
+We can easily realize $\lmo_{\mathcal{G}}$ and $\shyp_{\mathcal{G}}$ as comma categories.
+
+\begin{prop}
+Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Let, moreover, $\Delta_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then:
+\begin{enumerate}
+	\item $\lmo_{\mathcal{G}}$ is equivalent to $\comma{M}{\Delta_\mathcal{G}}$;
+	\item $\shyp_{\mathcal{G}}$ is equivalent to $\comma{S}{\Delta_\mathcal{G}}$; 
+\end{enumerate}
+\end{prop}
+
+\Cref{lim} allows us to easily characterize regular monos in $\hyp_{\mathcal{G}}$.
+\begin{prop}
+	A morphism $(f,g)$ between $(h_1, k_1)\colon \mathcal{H}\to \mathcal{G}$ and  $(h_2, k_2)\colon \mathcal{K}\to \mathcal{G}$ is a regular mono in $\lmo_{\mathcal{G}}$ if and only if $(f,g)\colon \mathcal{H}\to \mathcal{K}$ is a regular mono in $\lmo$.
+\end{prop}
+
+In turn, by \Cref{thm:slice-functors}, Corollaries \ref{cor:eq}, \ref{cor:pusho} and \Cref{lem:regmon} we get the following.
+
+\begin{thm} Given an hypergraph $\mathcal{G}$, the following hold true:
+	\begin{enumerate}
+		\item an arrow $(f,g)$  if and only if is so in $\lmo$.
+		\item $\lmo_{\mathcal{G}}$ is quasiadhesive.
+	\end{enumerate}
+\end{thm}
+
+\begin{rem}\label{rem:tg}
+	Let $\Sigma$ be an algebraic signature.
+Then we know that every hypergraph labelled by $\Sigma$ must be algebraic.
+By \Cref{rem:elem} this means that an hypergraph $(h,k)\colon \mathcal{H}\to \mathcal{G}^\Sigma$ labelled by $\Sigma$ is left-monogamous if and only if $t_{\mathcal{H}}$ is injective.
+This is precisely the definition of (cyclic) \emph{term graphs} in \cite{Plu:TGR-ENTCS,CorradiniG05,CastelnovoGM24}.
+\end{rem}
+
+\iffalse 
 \color{black}
@@
 \end{cor}
-
-\begin{rem}\label{rem:map1}
-	diagramma generale dei vari ipergrafi
-\end{rem}
-
+\fi 
 \section{Adding equivalences to hypergraphical structures}

### 2025-08-20 jlamp/jlamp.tex

@@
 Variables in a term graph are represented as nodes that do not occur among the targets of an edge, 
-thus the rule can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$:
+thus the rule can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
 \[

### 2025-08-20 jlamp/jlamp.tex
minima

@@
 
+\smallskip 
 \noindent
@@
 
+\medskip
+\begin{minipage}[l]{.73\linewidth}
 	\begin{defi}
-	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the cube below. %on the right. 
-	We say that the bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
-\vspace{-.5cm}
-
-	\begin{minipage}[l]{.68\linewidth}
+	Let $\mathcal{A}\subseteq \mor(\X)$ be a class of arrows in a category $\X$ and consider the cube aside. 
+	%We say that the 
+	The bottom square is an \emph{$\mathcal{A}$-Van Kampen square} if
+%\vspace{-.5cm}	
 	\begin{enumerate}
@@
 	\end{enumerate}
-\end{minipage}\hfill 
-\begin{minipage}[r]{.3\linewidth}
+\end{defi}
+\end{minipage}
+\hfill 
+\begin{minipage}[r]{.25\linewidth}
+\vspace{-.cm}
 	\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }
 \end{minipage}
+
+\medskip
 Pushout squares that enjoy only the ``if'' half of item (2) above are called \emph{$\mathcal{A}$-stable}. A $\mor(\X)$-Van Kampen square is called  \emph{Van
 Kampen} and a $\mor(\X)$-stable square  \emph{stable}.
-\end{defi}
 
@@
  \smallskip 
- We can interpret an arbitrary hypergaph as a \emph{typed} or \emph{colored} monoidal signature: the set of nodes provides the \emph{types} or \emph{colors}, while hyperedges can be thought of as operations, with arity and coarity provided by the source and target functions, respectively.
-This suggests the following definition, which will be used in Section \ref{par:tg}\label{sub:hyp_alg}.
+ We can interpret an arbitrary hypergaph as a \emph{typed} or \emph{colored} monoidal signature: the nodes provide the \emph{types} or \emph{colors}, while hyperedges can be thought of as operations, with arity and coarity provided by the source and target functions, respectively.
+This suggests the following definition, which is used later on.
+ % in Section \ref{par:tg}\label{sub:hyp_alg}.
 
@@
 \paragraph{Separated hypergraphs}
-We can now introduce the second  subcategory of $\hyp$ in which we are interested in and that will be used in \Cref{sec:sepegg} to give us the underlying hypergraphs for EGGs with minimally identified tokens.
+We can now introduce the second  subcategory of $\hyp$ in which we are interested in and that is going to be used in \Cref{sec:sepegg} to give the underlying hypergraphs for EGGs with minimally identified tokens.
 
@@
 	\end{enumerate}
-We will denote by $\shyp$ the full subcategory of $\hyp$ given by separated hypergraphs and by $S$ the inclusion functor.
+We denote by $\shyp$ the full subcategory of $\hyp$ of separated hypergraphs and by $S$ the inclusion functor.
 \end{defi}
@@
  \begin{rem}\label{rem:elem2}
- 	Let $\mathcal{G}$ be a separated hypergraph,  
- 	applying \Cref{rem:elem} we this is equivalent to say that, for every hyperedge $e$:
+ 	Let $\mathcal{G}$ be a separated hypergraph.
+ 	By applying \Cref{rem:elem}, this fact is equivalent to say that for every hyperedge $e$
  	\begin{itemize}
@@
 Given an hypergraph $\mathcal{\mathcal{G}}=(E_{\mathcal{G}}, V_{\mathcal{F}}, s_{\mathcal{G}}, t_{\mathcal{G}})$, for every hyperedge $e\in E_{\mathcal{G}}$ with $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we can consider the coproduct $(V_e, \{\iota^e_{i}\}_{i=1}^{n_e+m_e})$ of $n_e+m_e$ copies of $1$.
-We can further take the coproduct $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}})$ of the family $\{V_{e}\}_{e\in E_\mathcal{G}}$ and define:
+We can further take the coproduct $(V_{\sp(\mathcal{G})}, \{\iota_e\}_{e\in E_{\mathcal{G}}})$ of the family $\{V_{e}\}_{e\in E_\mathcal{G}}$ and define
 \[\begin{split}
@@
 where $0$ is the unique element of $1$. 
-
-We define the \emph{separated graph associated to $\mathcal{G}$}  as $\sp(\mathcal{G}):= (E_{\mathcal{G}}, V_{\sp(\mathcal{G})}, s_{\sp(\mathcal{G})}, t_{\sp(\mathcal{G})})$.
+\marginpar{ovvero?}
+
+We define the \emph{separated graph associated to $\mathcal{G}$}  as $\sp(\mathcal{G}) = (E_{\mathcal{G}}, V_{\sp(\mathcal{G})}, s_{\sp(\mathcal{G})}, t_{\sp(\mathcal{G})})$.
 \end{defi}
 \begin{rem}\label{rem:ob}
- By construction $\sp(\mathcal{G})$ is an object of $\shyp$. To see this it is enough to apply \Cref{rem:elem2}:
+ By construction $\sp(\mathcal{G})$ is an object of $\shyp$. To see this it is enough to apply \Cref{rem:elem2}
  \begin{itemize}
  	\item every letter of $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ lies in the image of a different coprojection $\iota_e\circ \iota^e_i$, so it cannot appear more than one time;
- 	\item a letter of $s_{\mathcal{G}}(e)$ are all contained in the image of $\iota_{e}\circ \iota^e_i$  for $i\leq n_e$, while every letter of $t_{\mathcal{G}}(e)$ lies in the image of $\iota_{e}\circ \iota^e_j$  for $n_e < j$, guaranteeing disjointness;
- 	\item if $e$ is different from $e'$, then all the letters of $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ are contained in the image of $\iota_e$, while those of  $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ are in the image of $\iota_{e'}$ and so, again, we get the wanted disjointness.
+ 	\item every letter of $s_{\mathcal{G}}(e)$ lies in the image of $\iota_{e}\circ \iota^e_i$  for $i\leq n_e$, while every letter of $t_{\mathcal{G}}(e)$ lies in the image of $\iota_{e}\circ \iota^e_j$  for $n_e < j$, guaranteeing disjointness;
+ 	\item if $e$ is different from $e'$, then all the letters of $s_{\mathcal{G}}(e)$ and $t_{\mathcal{G}}(e)$ are  in the image of $\iota_e$, while those of  $s_{\mathcal{G}}(e')$ and $t_{\mathcal{G}}(e')$ are in the image of $\iota_{e'}$ and so, again, we get the required disjointness.
  \end{itemize}
@@
 
-	We can then depict $\mathcal{G}^\Sigma $ and $\sp(\mathcal{G}^\Sigma )$ as below.
+	We can then depict $\mathcal{G}^\Sigma $ and $\sp(\mathcal{G}^\Sigma )$ as below\marginpar{e le lettere?}
 	\begin{center}	\begin{tikzpicture}
@@
 Then $\sp(\mathcal{L})$ is isomorphic to $(1, 2, \id{2}, \id{2})$ and so there are no arrows $\mathcal{L}\to S(\sp(\mathcal{L}))$.
-In particular this shows that $\sp$ cannot be left adjoint to $S$.
+In particular, this shows that $\sp$ cannot be left adjoint to $S$.
 	\end{itemize} 
@@
 
-\smallskip
-If we restrict our attention to separated hypergraph without isolated nodes, then $\sp$ becomes a right adjoint. The interested reader can consult \Cref{proof:dx} for a proof.
-
-\begin{defi} Let $\mathcal{G}$ be an hypergraph.
-A node $v\in V_{\mathcal{G}}$ is \emph{isolated} if for every $e\in E_{\mathcal{G}}$ $v$ does not occur as a letter in neither $s_{\mathcal{G}}$ nor in $t_{\mathcal{G}}$.
-$\mathcal{G}$ is \emph{pruned} if it does not have isolated nodes.
-We denote by $\phyp$ and $\pshyp$ the full subcategories of $\hyp$ given by, respectively, pruned hypergraphs and those which are pruned and separated.
+\medskip
+If we restrict our attention to separated hypergraphs without isolated nodes, then $\sp$ becomes a right adjoint. The interested reader can consult \Cref{proof:dx} for a proof.
+
+\begin{defi} Let $\mathcal{G}$ be an hypergraph. A node $v\in V_{\mathcal{G}}$ is \emph{isolated} if it does not occur as a letter in either $s_{\mathcal{G}}(e)$ or in
+$t_{\mathcal{G}}(e)$ for every $e\in E_{\mathcal{G}}$.
+$\mathcal{G}$ is \emph{pruned} if it has no isolated nodes.
+We denote by $\phyp$ and $\pshyp$ the full subcategories of $\hyp$ given by, respectively, pruned and pruned and separated hypergraphs.
 \end{defi}
@@
 \begin{rem}\label{rem:prun}
-	By construction, $\sp{G}$ is pruned for every hypergraph $\mathcal{G}$.
+	By construction, $\sp(\mathcal{G})$ is pruned for every hypergraph $\mathcal{G}$.
 \end{rem}
@@
 
-Finally, we conclude our exam of separated hypergraph proving a result regarding connected limits. A proof of it is \Cref{proof:seplim}
+Finally, we conclude our exam of separated hypergraphs proving a result regarding connected limits. A proof of it is \Cref{proof:seplim}
 
@@
 
-Since $\mathcal{T}$ must be separated, we have two (non disjoint) cases:
-
+\smallskip
+Since $\mathcal{T}$ must be separated, we have two (non disjoint) cases
+
+\medskip
 \begin{minipage}[l]{.65\linewidth}
@@
 \begin{minipage}[r]{.15\linewidth}
+\vspace{-.5cm}
 \begin{tikzpicture}
@@
 \begin{exa}\label{ex:nopush}
-	In general $\shyp$ does not have pushout.
+	In general $\shyp$ does not have pushouts.
 For instance consider the solid part of diagram aside.
@@
 	\[s_{\mathcal{G}}(q_1(e)) = q^\star_2(s_{\mathcal{K}}(e)) = q^\star_2(j^\star_2(v))=p^\star_2(i^\star_2(v)) = p^\star_2(t^\star_{\mathcal{Q}}(e))= t_{\mathcal{G}}(p_2(e))\]
-	and so $\mathcal{G}$ cannot ber in $\shyp$, yielding a contradiction.
+	and so $\mathcal{G}$ cannot be in $\shyp$, yielding a contradiction.
 \end{exa}
@@
 As  noted in \Cref{sub:hyp_alg}, an hypergraph can be thought as a colored monoidal signature.
-Thus labelling correspnds to the operationn of taking the slice category over a suitable hypergraph.
+Thus labelling corresponds to the operation of taking the slice category over a suitable hypergraph.
 
@@
 
-\Cref{cor:mono} and \Cref{thm:slice-functors} give us immediately an adhesivity result for $\hyp_{\mathcal{G}}$ and a characterisation of monos in it.
+\Cref{cor:mono} and \Cref{thm:slice-functors} give an adhesivity result for $\hyp_{\mathcal{G}}$ and a characterisation of its monos.
 
@@
 			Consider an algebraic signature $\Sigma$ and an hypergraph $\mathcal{H}=(E, V, s, t)$.
-By definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$, is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
+By definition we know that $U_{\hyp}(\mathcal{G}^{\Sigma})$ is the terminal object $1$, so an arrow $\mathcal{H}\rightarrow \mathcal{G}^{\Sigma}$ is determined by a function $h\colon E_\mathcal{H}\to O_\Sigma$  making the two squares on the right commutative (cfr.~\Cref{rem:length}).
 
@@
 
-As we have done in \Cref{sub:sub}, we can restrict our attention to two subcategories of labelled hypergraphs.
+As done in \Cref{sub:sub}, we can restrict our attention to two subcategories of labelled hypergraphs.
 
@@
 \begin{prop}
-Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Let, moreover, $\Delta_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then:
+Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Let, moreover, $\Delta_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then
 \begin{enumerate}
@@
 
-\Cref{lim} allows us to easily characterize regular monos in $\hyp_{\mathcal{G}}$.
+\Cref{lim} allows us to easily characterise regular monos in $\hyp_{\mathcal{G}}$.
 \begin{prop}
@@
 
-In turn, by \Cref{thm:slice-functors}, Corollaries \ref{cor:eq}, \ref{cor:pusho} and \Cref{lem:regmon} we get the following.
-
-\begin{thm} Given an hypergraph $\mathcal{G}$, the following hold true:
+In turn, by \Cref{thm:slice-functors}, Corollaries \ref{cor:eq}, \ref{cor:pusho} and \Cref{lem:regmon} we get the following result
+
+\begin{thm} Let $\mathcal{G}$ be an hypergraph. Then the following fact hold
 	\begin{enumerate}
-		\item an arrow $(f,g)$  if and only if is so in $\lmo$.
+		\item an arrow $(f,g)$  if and only if is so in $\lmo$; \marginpar{ovvero?}
 		\item $\lmo_{\mathcal{G}}$ is quasiadhesive.
@@
 By \Cref{rem:elem} this means that an hypergraph $(h,k)\colon \mathcal{H}\to \mathcal{G}^\Sigma$ labelled by $\Sigma$ is left-monogamous if and only if $t_{\mathcal{H}}$ is injective.
-This is precisely the definition of (cyclic) \emph{term graphs} in \cite{Plu:TGR-ENTCS,CorradiniG05,CastelnovoGM24}.
+This is precisely the definition of \emph{term graphs} in \cite{Plu:TGR-ENTCS,CorradiniG05,CastelnovoGM24}.
 \end{rem}
@@
 
- Suppose now that there are $e_1, e_2\in E_{\mathcal{P}}$ such that $t_{\mathcal{P}}(e_1)_n=t_{\mathcal{P}}(e_2)_m$ for some indexes $1\leq n \leq \lgh_{V_{\mathcal{P}}}(e_1)$ and $1\leq m \leq \lgh_{V_{\mathcal{P}}}(e_2)$.
-To conclude, we have to show that $e_1=e_2$.
+ Suppose that there are $e_1, e_2\in E_{\mathcal{P}}$ such that $t_{\mathcal{P}}(e_1)_n=t_{\mathcal{P}}(e_2)_m$ for some indexes $1\leq n \leq \lgh_{V_{\mathcal{P}}}(e_1)$ and $1\leq m \leq \lgh_{V_{\mathcal{P}}}(e_2)$.
+We have to show that $e_1=e_2$.
 We can again use \Cref{lem:po_set} to split the cases.
@@
 	By \Cref{prop:com} and \Cref{lim} this entails that $(\mathcal{G}, (f,g))$ is the equalizer in $\hyp$ of $(p_1, p_2)$ and $(q_1, q_2)$.
-By \Cref{prop:pusho}, $\mathcal{P}$ is left-monogamous, thus by \Cref{cor:eq} $(f,g)$ is regular mono as wanted.
+By \Cref{prop:pusho}, $\mathcal{P}$ is left-monogamous, thus by \Cref{cor:eq} $(f,g)$ is regular mono.
 \end{proof}
@@
 	Let $(h_1, h_2)\colon \mathcal{G}\to \mathcal{H}$ be a morphism of hypergraphs. For every hyperedge $e\in E_{\mathcal{G}}$,
-	the universal property of coproducts, there are arrows $f_e\colon V_e\to V_{h_1(e)}$ fitting in the middle of the diagram below.
+	the universal property of coproducts tells us that there are arrows $f_e\colon V_e\to V_{h_1(e)}$ fitting in the middle of the diagram below.
 These, in turn, yield the dotted $\hat{h}_1\colon V_{\sp(\mathcal{G})} \to V_{\sp(\mathcal{G})}$ on the bottom.
+	\smallskip
 
@@
 		\setlength{\parindent}{1.5em}
-		Given $e\in E_{\mathcal{G}}$, if $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we have :
+		Given $e\in E_{\mathcal{G}}$, if $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$, we have
 		\begin{align*}
@@
 
-	If $h_1$ is the identity, then clearly  $\hat{h}_1=\id{V_{\sp(\mathcal{G})}}$. If $(k_1, k_2)$ is another morphism $\mathcal{H}\to \mathcal{K}$, then we have:
+	If $h_1$ is the identity, then clearly  $\hat{h}_1=\id{V_{\sp(\mathcal{G})}}$. If $(k_1, k_2)$ is another morphism $\mathcal{H}\to \mathcal{K}$, then we have
 	\[\hat{k}_1\circ \hat{h}_1\circ \iota_e\circ \iota^e_i=\hat{k}_1\circ \iota_{h_1(e)}\circ \iota^{h_1(e)}_i =\iota_{k_1(h_1(e))}\circ \iota^{k_1(h_1(e))}_i\]
-	which entails preservation of composition.
+	which entails the preservation of composition.
 \end{proof}
@@
 
-In turn,this allows us to define $\epsilon_{G}\colon V_{\sp(\mathcal{G})}\to V_{\mathcal{G}}$ as the unique one fitting in the diagram below.
+In turn, this allows us to define $\epsilon_{G}\colon V_{\sp(\mathcal{G})}\to V_{\mathcal{G}}$ as the unique one fitting in the diagram below.
 
@@
 		\setlength{\parindent}{1.5em}
-		Now, for every hyperedge $e\in E_{\mathcal{G}}$ we have :
+		Now, for every hyperedge $e\in E_{\mathcal{G}}$ we have
 		\begin{gather*}
@@
 Let $i_v$ be the index at which it appears.
-We define:
+We define
 	\[\hat{g}(v):=\begin{cases}
@@
 	\end{cases}\]
-	Computing we get:
+	Computing we get
 	\begin{gather*}
@@
 
-	Let now $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(h, k)=(f,g)$.
+	Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(h, k)=(f,g)$.
 This entails immediately that $h =f$.
-Let $v$ be a node $V_{\mathcal{H}}$, since $\mathcal{H}$ is pruned, we have two cases:
+Let $v$ be a node $V_{\mathcal{H}}$.
+Since $\mathcal{H}$ is pruned, we have two cases
 	\begin{itemize}
-		\item $v$ occurs in $s_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have:
+		\item $v$ occurs in $s_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have
 		\[\hat{g}(v)=\hat{g}(s_{\mathcal{H}}(e)_i)=(g^\star(s_{\mathcal{H}}(e)))_i=s_{\sp(\mathcal{G})}(f(e))_i=(k^\star(s_{\mathcal{H}}(e)))_i=k(s_{\mathcal{H}}(e)_i)=k(v)\]
-		\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have:
+		\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have
 		\[\hat{g}(v)=\hat{g}(t_{\mathcal{H}}(e)_i)=(g^\star(t_{\mathcal{H}}(e)))_i=t_{\sp(\mathcal{G})}(f(e))_i=(k^\star(t_{\mathcal{H}}(e)))_i=k(t_{\mathcal{H}}(e)_i)=k(v)\]
@@
 
-	By \Cref{lim} and Propositions \ref{prop:fact} and \ref{prop:com} we know that  $(V_\mathcal{L}, \{p_{V, D}\}_{D\in \D})$  and $(E_\mathcal{L}, \{p_{E, D}\}_{D\in \D})$ are limiting cone for, respectively,  $U_{\hyp}\circ S\circ F$ and $V_{\hyp}\circ S\circ F$, where $U_{\hyp}, V_{\hyp}$.
+	By \Cref{lim} and Propositions \ref{prop:fact} and \ref{prop:com} we know that  $(V_\mathcal{L}, \{p_{V, D}\}_{D\in \D})$  and $(E_\mathcal{L}, \{p_{E, D}\}_{D\in \D})$ are limiting cones for, respectively,  $U_{\hyp}\circ S\circ F$ and $V_{\hyp}\circ S\circ F$, where $U_{\hyp}, V_{\hyp}$.
 We proceed by cases.
@@
 
-		Since $\D$ is connected then it is non empty. Let  $D$ be an object of $\D$, then we have:
+		Since $\D$ is connected then it is non empty. Let  $D$ be an object of $\D$. Then we have
 		\begin{align*}
-		&(s_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(s_{\mathcal{L}}(e)))_i=p^\star_{V, D}((s_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((s_{\mathcal{L}}(e))_k)=(p^\star_{V,D}(s_{\mathcal{L}}(e)))_k=(s_{S(F(D))}( p_{E,D}(e)))_k
+		&(s_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(s_{\mathcal{L}}(e)))_i=p^\star_{V, D}((s_{\mathcal{L}}(e))_i)\\ = & p_{V,D}(v)=p_{V, D}((s_{\mathcal{L}}(e))_k)=(p^\star_{V,D}(s_{\mathcal{L}}(e)))_k=(s_{S(F(D))}( p_{E,D}(e)))_k
 		\end{align*}
@@
 			\[(t_{\mathcal{L}}(e))_i=v \qquad  (t_{\mathcal{L}}(e) )_k= v\]
-			for some $e\in E_{\mathcal{H}}$ and $1\leq i, k \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ with $i\neq k$. Then for any $D\in \D$:
+			for some $e\in E_{\mathcal{H}}$ and $1\leq i, k \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ with $i\neq k$. Then for any $D\in \D$
 			\begin{align*}
@@
 We have already noticed that $\D$ is non empty.
-Let $D\in \D$, we have:
+So, let $D\in \D$.
+Then we have
 		\begin{align*}&(s_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(s_{\mathcal{L}}(e)))_i=p^\star_{V, D}((s_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((t_{\mathcal{L}}(e'))_k)=(p^\star_{V,D}(t_{\mathcal{L}}(e')))_k=(t_{S(F(D))}( p_{E,D}(e')))_k
@@
 		 \[(s_{\mathcal{L}}(e))_i=v \qquad  (s_{\mathcal{L}}(e') )_k= v\]
-		with $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ and $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $. For every $D\in \D$ we can compute to get:
+		with $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$ and $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $. For every $D\in \D$ we can compute to get
 		\begin{align*}&(s_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(s_{\mathcal{L}}(e)))_i=p^\star_{V, D}((s_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((s_{\mathcal{L}}(e'))_k)=(p^\star_{V,D}(s_{\mathcal{L}}(e')))_k=(s_{S(F(D))}( p_{E,D}(e')))_k
@@
 Since $(E_\mathcal{L}, \{p_{E, D}\}_{D\in \D})$ this entails that $e = e'$, which is a contradiction.
-		\item  We proceed as before, supposing that $e$ and $e'$ are distinct elements of $\mathcal{L}$ for which there are $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$, $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $ and a node $v\in V_{\mathcal{L}}$ such that:
+		\item  We proceed as before, supposing that $e$ and $e'$ are distinct elements of $\mathcal{L}$ for which there are $1\leq i \leq \lgh_{V_{\mathcal{L}}}(s_{\mathcal{L}(e)})$, $1\leq k \leq \lgh_{V_{\mathcal{L}}}(t_{\mathcal{L}(e)}) $ and a node $v\in V_{\mathcal{L}}$ such that
 				\[(t_{\mathcal{L}}(e))_i=v \qquad  (t_{\mathcal{L}}(e') )_k= v\]
-		Then, given $D\in \D$ we have:
+		Then, given $D\in \D$ we have
 		\begin{align*}&(t_{S(F(D))}( p^D_{E}(e)))_i = ( p^\star_{V,D}(t_{\mathcal{L}}(e)))_i=p^\star_{V, D}((t_{\mathcal{L}}(e))_i)\\=&p_{V,D}(v)=p_{V, D}((t_{\mathcal{L}}(e'))_k)=(p^\star_{V,D}(t_{\mathcal{L}}(e')))_k=(t_{S(F(D))}( p_{E,D}(e')))_k
 		\end{align*}
-		Therefore,  $p_{E,D}(e)$ and $p_{E,D}(e')$ coincide for every $D\in \D$. Thus  $e = e'$ and we end up again with a contradiction. \qedhere 
+		Thus  $p_{E,D}(e)$ and $p_{E,D}(e')$ coincide for every $D\in \D$, hence  $e = e'$ and again we get a contradiction. \qedhere 
 	\end{itemize}
@@
 \section{Some properties of comma categories}
-In this section we briefly recall the definition of the comma category \cite{mac2013categories} associated to two functors and some of its properties.
+In this section we briefly recall the definition of the comma category \cite{mac2013categories} and some of its properties.
 \begin{defi}\index{category!comma -}
@@
 \noindent
-\parbox{10.5cm}{\vspace{-.5cm}\begin{itemize}
+\parbox{10.5cm}{\vspace{-.1cm}\begin{itemize}
 		\item objects are triples $(A, B, f)$ with $A\in \A$, $B\in \B$, and $f\colon L(A)\rightarrow R(B)$; 
-		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the diagram aside commutes\end{itemize}}\hfill
+		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the diagram aside commutes.\end{itemize}}\hfill
 	\parbox{4cm}{\vspace{-.1cm}\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}}
@@
 Thus $\comma{L}{R}$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
-Moreover, the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$.
+Moreover, the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$
 \[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g} & R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B') & L(A') \ar[r]_{L(h)}  & L(A)}\]
@@
 \begin{lem}\label[lemma]{colim}
-	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ be a diagram such that $L$ preserves colimits along $U_L\circ F$.
+	Let $L\colon \A\to \X$ and $R\colon \B\to \X$ be functors and $F\colon \D\to\comma{L}{R}$ a diagram such that $L$ preserves colimits along $U_L\circ F$.
 Then the family $\{U_L, U_R\}$ jointly creates colimits of $F$ (see \cite[Sec.~5.1.3]{castelnovo2023thesis} or \cite[Sec.~2.3]{CastelnovoGM24}).
@@
 By hypothesis $\left(L(A), \{L\left(a_D\right)\}_{D\in \D}\right)$ is colimiting for $L\circ U_L\circ F$.
-Now, let $F(D)$ be $(A_D, B_D, f_D)$,
-	then we have arrows $R(b_D)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$: if $d\colon D\to D'$ is an arrow in $\D$ then $F(d)$ is an arrow in $\comma{L}{R}$ and so
+Now, let $F(D)$ be $(A_D, B_D, f_D)$:
+	we have arrows $R(b_D)\circ f_D\colon L(A_D)\to R(B)$ that forms a cocone on $L\circ U_L\circ F$. If $d\colon D\to D'$ is an arrow in $\D$, then $F(d)$ is an arrow in $\comma{L}{R}$ and so
 	\begin{align*}
@@
 	\hspace{15pt}Thus there exists $f\colon L(A)\rightarrow R(B)$ fitting in the diagram on the right.
-Notice that $f$ is the unique arrow in $\X$ wich makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comma{L}{R}$.
+Notice that $f$ is the unique arrow in $\X$ which makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comma{L}{R}$.
 If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.}\hfill
@@
 \begin{prop}\label[proposition]{prop:left}
-	If $\A$ has initial objects and $L$ preserves them then the forgetful functor $U_R\colon \comma{L}{R}\to \B$ has a left adjoint $\Delta$.
+	If $\A$ has initial objects and $L$ preserves them, then the forgetful functor $U_R\colon \comma{L}{R}\to \B$ has a left adjoint $\Delta$.
 \end{prop}
@@
 \end{proof}
-Dualizing we get immediately the following.
-\begin{cor}If $\B$ has terminal objects preserved by $R$ then $U_L\colon \comma{L}{R}\to \A$ has a right adjoint.
+Dualising we get immediately the following.
+\begin{cor}If $\B$ has terminal objects preserved by $R$, then $U_L\colon \comma{L}{R}\to \A$ has a right adjoint.
 \end{cor}
@@
 
-This section is devoted to recall some basic facts about the so called \emph{slice categories}.
+This section is devoted to recall some basic facts about \emph{slice categories}.
 \begin{defi}\index{category!slice -}
 	Let $X$ be an object of a category $\X$. We define the following two categories.
+	\smallskip
 
@@
 
-We can realize the slice over and under an object $X\in \X$ as comma categories.
+We can obtain the slice over and under an object $X\in \X$ as comma categories.
 
 \begin{prop}\label[proposition]{prop:commaapp}
-	For every object $X$ in a category $\X$, if $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object $*$, then $\X/X$ and $X/\X$ are isomorphic to, respectively,  $\comma{\id{X}}{\delta_X}$ and $\comma{\delta_X}{\id{X}}$ .
+	Let  $X$ be an object in a category $\X$.
+If $\delta_X\colon \T\to \X$ is  the constant functor of value  $X$ from the category with only one object, then $\X/X$ and $X/\X$ are isomorphic to $\comma{\id{X}}{\delta_X}$ and $\comma{\delta_X}{\id{X}}$, respectively.
 \end{prop}
@@
 \newpage
-\begin{proof} Define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows
+\begin{proof} 
+Let $*$ be the only object of the category $\T$ and define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows
 	\[	\begin{split}
@@
 For every object $\X$, $\X/X$ has all colimits and connected limits that $\X$ has. Moreover such limits and colimits are created by $\dom_X$.
-
-In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$, the slice $\X/X$ has such limits and colimits.
 \end{cor}
+
+In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$ the slice $\X/X$ has such limits and colimits.
 

### 2025-08-20 jlamp/jlamp.tex
minima

@@
 \begin{minipage}[l]{.83\linewidth}
-	\begin{rem}\label{rem:length} It is well known that $(\mathbb{N}), \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
+	\begin{rem}\label{rem:length} It is well known that $(\mathbb{N}, \{\delta_n\}_{n\in \mathbb{N}})$ is a coproduct for $\aleph_0$ copies of $1$, where $\delta_n\colon 1\to \mathbb{N}$ is the function picking the element $n$.
 Thus by the first point of \Cref{prop:fact} there is a canonical isomorphism $\Delta\colon \mathbb{N}\to 1^\star$.
-In particular, for every set $X$ the unique arrow $!_\X\colon X\to 1$ into the terminal objects induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
+In particular, for every set $X$ the unique arrow $!_\X\colon X\to 1$ into the terminal object induces a \emph{length function} $\lgh_{X}\colon X^\star \to \mathbb{N}$, which sends a word to its length, as in the diagram aside.
 		\end{rem}
@@
 	\begin{rem}\label{rem:len} It is worth noticing that for $X$ a set and every $n\in \mathbb{N}$, $X^n$ is the preimage of $n$ along $\lgh_{X}$.
-This amount to say that the square aside is a pullback.
+This amounts to say that the square aside is a pullback.
 This follows at once from the fact that $\Set$ is \emph{extensive} (see \cite{carboni1993introduction} and also \Cref{word:ext}).
@@
 
-\begin{rem}\label{rem:con}Notice that  $\lmo$ is not complete: it lacks e.g.
-a terminal object.
-To see this, notice that the $\mathcal{H}:=(\emptyset, 1, ?_{1^\star}, 1_{1^\star} )$ is left-monogamous and that
+\begin{rem}\label{rem:con}Notice that  $\lmo$ is not complete: it lacks e.g. a terminal object. To see this, notice that the $\mathcal{H}:=(\emptyset, 1, ?_{1}, ?_{1} )$ is left-monogamous and that 
 	$\lmo(\mathcal{H}, \mathcal{G})$ is in bijection with $V_{\mathcal{G}}$ for every hypergraph $\mathcal{G}$.
@@
 \end{split} \]
-where $0$ is the unique element of $1$. 
+where $0$ is the unique element of the terminal object $1$. 
 \marginpar{ovvero?}
@@
 
-	We can then depict $\mathcal{G}^\Sigma $ and $\sp(\mathcal{G}^\Sigma )$ as below\marginpar{e le lettere?}
+	We can then depict $\mathcal{G}^\Sigma $ and $\sp(\mathcal{G}^\Sigma )$ as below
 	\begin{center}	\begin{tikzpicture}
@@
 		\item To see that $\sp$ cannot be a right adjoint to $S$, consider the ``double loop'' $\mathcal{D}=(2, 1, !_2, !_2)$ depicted aside.
-$\sp(\mathcal{D})$ is then isomorphic to the graph $\mathcal{G}=(2, 4, s_{\mathcal{G}}, t_{\mathcal{G}})$ with
+Then $\sp(\mathcal{D})$ is isomorphic to the graph $\mathcal{G}=(2, 4, s_{\mathcal{G}}, t_{\mathcal{G}})$ with
 		\[s_{\mathcal{G}}(0) = 0 \quad  t_{\mathcal{G}}(0) =  1 \quad  s_{\mathcal{G}}(1) = 2 \quad  t_{\mathcal{G}}(1) = 3 \]
 
-		Let $\mathcal{H}$ be $(\emptyset, 1, ?_1, ?_1)$, which is clearly a separated hypergraph.
+		Let $\mathcal{H}$ be $(\emptyset, 1, ?_{1^\star}, ?_{1^\star})$, which is clearly a separated hypergraph.
 Now,  $\shyp(\mathcal{H}, \sp(\mathcal{D}))$ has the same cardinality of  $\shyp(\mathcal{H}, \mathcal{G})$, which is $4$, while $\hyp(S(\mathcal{H}), \mathcal{D})$ is a singleton.
@@
 \begin{exa}\label{ex:noterm}
-In general $\shyp$ is not complete. For instance it does not have a terminal object. Too see this notice that the $\mathcal{H}:=(\emptyset, 1, ?_{1^\star}, 1_{1^\star} )$ is separated and that 
+In general $\shyp$ is not complete. For instance it does not have a terminal object. Too see this notice that the $\mathcal{H}:=(\emptyset, 1, ?_{1^\star}, ?_{1^\star} )$ is separated and that 
 $\shyp(\mathcal{H}, \mathcal{G})$ is in bijection with $V_{\mathcal{G}}$ for every hypergraph $\mathcal{G}$.
@@
 
-In turn, by \Cref{thm:slice-functors}, Corollaries \ref{cor:eq}, \ref{cor:pusho} and \Cref{lem:regmon} we get the following result
-
-\begin{thm} Let $\mathcal{G}$ be an hypergraph. Then the following fact hold
-	\begin{enumerate}
-		\item an arrow $(f,g)$  if and only if is so in $\lmo$; \marginpar{ovvero?}
-		\item $\lmo_{\mathcal{G}}$ is quasiadhesive.
-	\end{enumerate}
+In turn, by \Cref{thm:slice-functors}, Corollaries \ref{cor:eq}, \ref{cor:pusho} and \Cref{lem:regmon} we get the following result.
+
+\begin{thm} Let $\mathcal{G}$ be an hypergraph. Then %the following fact hold
+%	\begin{enumerate}
+%		\item an arrow $(f,g)$  if and only if is so in $\lmo$; \marginpar{ovvero?}
+		%\item 
+		$\lmo_{\mathcal{G}}$ is quasiadhesive.
+%	\end{enumerate}
 \end{thm}
@@
 
-\newpage
+%\newpage
 	\smallskip\noindent 
@@
 
-\newpage
 \begin{proof} 
-Let $*$ be the only object of the category $\T$ and define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows
+Let $1$ be the only object of the category $\T$ and define functors $F_1\colon \comma{\id{X}}{\delta_X}\to \X/X$ and $G_1\colon \X/X\to \comma{\id{X}}{\delta_X}$ as follows
 	\[	\begin{split}
-		\functor[l]{(Y, *,  f)}{(h, \id{*} )}{( Y', *,  g)}
+		\functor[l]{(Y, 1,  f)}{(h, \id{1} )}{( Y', 1,  g)}
 		\functormapsto
@@
 		\functormapsto
-		\rfunctor{(\dom(f), *, f)}{(h, \id{*} )}{(\dom(g), *, g)}
+		\rfunctor{(\dom(f), 1, f)}{(h, \id{1} )}{(\dom(g), 1, g)}
 	\end{split}\]
@@
 	\[	\begin{split}
-		\functor[l]{(*, Y, f)}{(\id{*},h )}{(*, Y', g)}
+		\functor[l]{(1, Y, f)}{(\id{1},h )}{(1, Y', g)}
 		\functormapsto
@@
 		\functormapsto
-		\rfunctor{(*, \cod(f), f)}{(\id{*}, h )}{(*, \cod(g), g)}
+		\rfunctor{(1, \cod(f), f)}{(\id{1}, h )}{(1, \cod(g), g)}
 	\end{split}\]
@@
 
-In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$ the slice $\X/X$ has such limits and colimits.
+%In particular, if $\X$ has pullbacks, equalizers or pushouts, then for every object $X$ the slice $\X/X$ has such limits and colimits.
 
@@
 \todo{Tutta la parte qua sotto non mi è chiaro a cosa serva}
-In a category $\cat X$ with pullbacks, each $f: X \to Y$ induces a functor $f^*: \cat X/Y \to \cat X/X$,
+In a category $\cat X$ with pullbacks, each $f: X \to Y$ induces a functor $f^\*: \cat X/Y \to \cat X/X$,
 which sends each morphism $a: A \to Y$ of $\cat X$ onto its pullback along $f$, $p_a$, and each morphism $h: a \to b$ onto the unique arrow from the pullback of $a$ along $f$ to the pullback of $b$ along $f$.

### 2025-08-21 jlamp/jlamp.tex
pruned e separati

@@
  We can interpret an arbitrary hypergaph as a \emph{typed} or \emph{colored} monoidal signature: the nodes provide the \emph{types} or \emph{colors}, while hyperedges can be thought of as operations, with arity and coarity provided by the source and target functions, respectively.
-This suggests the following definition, which is used later on.
+This suggests the following definition, which is used later on\label{sub:hyp_alg}.
  % in Section \ref{par:tg}\label{sub:hyp_alg}.
@@
 			\node[style=none] (vlab) at (0, 0.3){$0$};
-			\node[style=small box] (times) at (-1, 1) {};
-			\node[style=none] (timeslab) at (-1, 1.5) {$0$};
-			\node[style=none] (timesin) at (-1, .7) {};
-			\node[style=none] (timesout) at (-.7, 1){};
-			\node[style=small box] (div) at (1, 1) {};
-			\node[style=none] (divlab) at (1, 1.5) {$1$};
-			\node[style=none] (divin) at (1, .7) {};
-			\node[style=none] (divout) at (.7, 1){};
+			\node[style=small box] (times) at (-.8, 1) {};
+			\node[style=none] (timeslab) at (-.8, 1.5) {$0$};
+			\node[style=none] (timesin) at (-1.1, 1) {};
+			\node[style=none] (timesout) at (-.5, 1){};
+			\node[style=small box] (div) at (.8, 1) {};
+			\node[style=none] (divlab) at (.8, 1.5) {$1$};
+			\node[style=none] (divin) at (.5, 1) {};
+			\node[style=none] (divout) at (1.1, 1){};
 
@@
 		\begin{pgfonlayer}{edgelayer} 
-			\draw[style=none,out=180, in= 270] (v) to (timesin.center);
-			\draw[style=none,out=0, in= 270] (v) to (divin.center);
+			\draw[style=none,out=200, in= 180] (v) to (timesin.center);
+			\draw[style=none,out=45, in= 200] (v) to (divin.center);
 			\draw[style=none, in=135, out=345] (timesout.center) to (v);
-			\draw[style=none, in=45, out=195] (divout.center) to (v);
+			\draw[style=none, in=345, out=0] (divout.center) to (v);
 			\draw[style=none, in=180, out=0] (a.center) to (zeroin.west);
@@
 	By construction, $\sp(\mathcal{G})$ is pruned for every hypergraph $\mathcal{G}$.
+\end{rem}
+
+\begin{rem}\label{rem:mprun}
+	Let $(f,g)$ and $(h, k)$ be two morphisms $\mathcal{G}\rightrightarrows \mathcal{H}$ of $\phyp$ and suppose that $f=h$.
+We can use the absence of isolated nodes to show that $g=k$ too.
+Let $v\in V_{\mathcal{G}}$, we have two cases:
+	\begin{itemize}
+		\item $v$ occurs in $s_{\mathcal{G}}(e)$ for some $e\in E_{\mathcal{G}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have
+		\[g(v)=g(s_{\mathcal{G}}(e)_i)=(g^\star(s_{\mathcal{G}}(e)))_i=s_{\mathcal{H}}(f(e))_i=s_{\mathcal{H}}(h(e))_i=(k^\star(s_{\mathcal{G}}(e)))_i=k(s_{\mathcal{G}}(e)_i)=k(v)\]
+		\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have
+		\[g(v)=g(t_{\mathcal{G}}(e)_i)=(g^\star(t_{\mathcal{G}}(e)))_i=t_{\mathcal{H}}(f(e))_i=t_{\mathcal{H}}(h(e))_i=(k^\star(t_{\mathcal{G}}(e)))_i=k(t_{\mathcal{G}}(e)_i)=k(v)\]
+	\end{itemize}
+	In both cases $\hat{g}(v)=k(v)$ and so $\hat{g}= k$ as wanted.
 \end{rem}
@@
 \end{exa}
-\end{minipage} \hfill \begin{minipage}[r]{.5\linewidth} \vspace{-2cm}
-\xymatrix@R=6pt@C=30pt{\begin{tikzpicture}
+\end{minipage} \hfill \begin{minipage}[r]{.45\linewidth} \vspace{-2cm}
+\xymatrix@R=6pt@C=25pt{\begin{tikzpicture}
 		\node[style=node](v) at (0, 0){};
@@
 \end{minipage}
+
+If we restrict to pruned separated hypergraph the previous issue disappeares.
+The crucial observation is that the a pruned separated hypergraph is characterized by its set of hyperedges and the length of their sources and targets.
+See \Cref{proof:pruned} for a proof.
+
+\begin{restatable}{lem}{pruned}\label{lem:pruned}
+$\pshyp$ is equivalent to $\Set/(\mathbb{N}\times \mathbb{N})$.
+\end{restatable}
+\begin{cor}\label{cor:pruned}
+	$\pshyp$ is adhesive.
+\end{cor}
 
@@
 
-\begin{thm} Let $\mathcal{G}$ be an hypergraph. Then %the following fact hold
+\begin{thm} Let $\mathcal{G}$ be an hypergraph, then %the following fact hold
 %	\begin{enumerate}
@@
 
+\subsubsection{title}
+\paragraph{title}
+\paragraph{title}
 %\input{Hypergraphs_with_equivalences}
@@
 \end{cor}
+
+\subsubsection{title}
 
@@
 	Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(h, k)=(f,g)$.
-This entails immediately that $h =f$.
-Let $v$ be a node $V_{\mathcal{H}}$.
-Since $\mathcal{H}$ is pruned, we have two cases
-	\begin{itemize}
-		\item $v$ occurs in $s_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have
-		\[\hat{g}(v)=\hat{g}(s_{\mathcal{H}}(e)_i)=(g^\star(s_{\mathcal{H}}(e)))_i=s_{\sp(\mathcal{G})}(f(e))_i=(k^\star(s_{\mathcal{H}}(e)))_i=k(s_{\mathcal{H}}(e)_i)=k(v)\]
-		\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have
-		\[\hat{g}(v)=\hat{g}(t_{\mathcal{H}}(e)_i)=(g^\star(t_{\mathcal{H}}(e)))_i=t_{\sp(\mathcal{G})}(f(e))_i=(k^\star(t_{\mathcal{H}}(e)))_i=k(t_{\mathcal{H}}(e)_i)=k(v)\]
-	\end{itemize}
-In both cases $\hat{g}(v)=k(v)$ and so $\hat{g}= k$ as wanted.
+This entails immediately that $h =f$ and so uniqueness follows from \Cref{rem:mprun}.
 \end{proof}
@@
 
+\pruned*
+
+\begin{proof}{\label{proof:pruned}}
+	Let $\mathcal{G}$ be a pruned and separated hypergraph.
+We can define $F(\mathcal{G})$ as $(\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}}) \colon E_{\mathcal{G}}\to \mathbb{N}\times \mathbb{N}$.
+Given a morphism $(h,k)\colon \mathcal{G}\to \mathcal{H}$ and using \Cref{rem:le} we	have
+	\[(\lgh_{V_{\mathcal{H}}}\circ s_{\mathcal{H}}, \lgh_{V_{\mathcal{H}}}\circ t_{\mathcal{H}})\circ h = (\lgh_{V_{\mathcal{H}}}\circ s_{\mathcal{H}}\circ h, \lgh_{V_{\mathcal{H}}}\circ t_{\mathcal{H}}\circ h)=(\lgh_{V_{\mathcal{H}}}\circ k^\star\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{H}}}\circ k^\star\circ t_{\mathcal{G}})= (\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}})\]
+	Thus we can define $F(h,k)$ simply as $h$ to get a functor $\pshyp\to \Set/(\mathbb{N}\times \mathbb{N})$. Let us show that it is an equivalence.
+	\begin{itemize}
+		\item $F$ is faithful. This follows at once from \Cref{rem:prun}.
+		\item $F$ is full. Let $k\colon E_{\mathcal{G}}\to E_{\mathcal{H}}$ be an arrow such that 
+		\[(\lgh_{V_{\mathcal{H}}}\circ s_{\mathcal{H}}, \lgh_{V_{\mathcal{H}}}\circ t_{\mathcal{H}})\circ f =(\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}})\]
+
+		Now, for every $e \in E_\mathcal{G}$, let $\iota^s_e\colon V^s_e\mto V_{\mathcal{G}}$ and $\iota^t_e\colon V^t_e\mto V_{\mathcal{G}}$ be the inclusions of
+		\[V^s_e=\{v \in V_{\mathcal{G}} \mid \ind{G}(v,e)=1\} \qquad V^t_e=\{v \in V_{\mathcal{G}} \mid \outd{G}(v,e)=1\}\]
+
+		\noindent
+		\begin{minipage}[l]{.78\linewidth}
+		Since $\mathcal{G}$ is pruned and separated, $(V_{\mathcal{G}}, \{\iota^s_e\}_{e\in E_{\mathcal{G}}}+\{\iota^t_e\}_{e\in E_{\mathcal{G}}})$ is a coproduct.
+Given $v\in V^s_e$ and $w\in V^t_e$, let $i_v$ and $k_w$ be the unique indexes such that $\iota^s_e(v)=s_{\mathcal{G}}(e)_{i_v}$ and $\iota^t_e(w)= t_{\mathcal{G}}(e)_{k_w}$ and define:
+			\[\begin{split}
+				g^s_e\colon V^s_{e} &\to V_{\mathcal{H}}\\
+				v&\mapsto  s_{\mathcal{H}}(f(e))_{i_v}
+			\end{split} \qquad \begin{split}
+				g^t_e\colon V^t_{e} &\to V_{\mathcal{H}}\\
+				w&\mapsto  t_{\mathcal{H}}(f(e))_{k_w}
+			\end{split}\]
+			so that there is an arrow $g\colon V_ {\mathcal{G}}\to \mathcal{H}$ fitting in the diagram aside.
+		\end{minipage}\hfill
+		\begin{minipage}[r]{.2\linewidth}
+		\xymatrix@R=14pt@C=14pt{&V^s_{\mathcal{G}} \ar[dr]^{g^s_e} \ar@{>->}[dl]_{\iota^s_e}\\ V_{\mathcal{G}} \ar@{.>}[rr]^-{g} && V_{\mathcal{H}}}		
+		\xymatrix@R=14pt@C=14pt{&V^t_{\mathcal{G}} \ar[dr]^{g^t_e} \ar@{>->}[dl]_{\iota^t_e}\\ V_{\mathcal{G}} \ar@{.>}[rr]^-{g} && V_{\mathcal{H}}}		
+		\end{minipage}
+
+		Given $e\in E_\mathcal{G}$, for every $1\leq i \leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $1\leq k \leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$ we can compute to get:
+		\begin{align*}
+		(g^\star(s_{\mathcal{G}}(e)))_i&=(g^\star(s_{\mathcal{G}}(e)))_i=g(s_{\mathcal{G}}(e)_i)=s_{\mathcal{H}}(f(e))_i\\
+		(g^\star(t_{\mathcal{G}}(e)))_k&=(g^\star(t_{\mathcal{G}}(e)))_k=g(t_{\mathcal{G}}(e)_k)=t_{\mathcal{H}}(f(e))_k
+		\end{align*}
+
+		Hence $(f,g)$ is a morphism $\mathcal{G}\to \mathcal{H}$ such that $F(f,g)=f$.
+		\item $F$ is essentially surjective.
+Consider a function $(f_1, f_2)\colon X\to \mathbb{N}\times \mathbb{N}$.
+Given $x\in X$,  we can consider $f_1(x)$ and $f_2(x)$ as ordinal sets and take the coproduct $(V, \{\iota^1_x\}_{x\in X}+ \{\iota^2_x\}_{x\in X})$ of the family $\{f_1(x)\}_{x\in X}+\{f_2(x)\}_{x\in X}$.
+Define:
+		\[\begin{split}  
+			s\colon X&\to V^\star\\
+			x &\mapsto \prod_{n=0}^{f_1(x)-1}\iota^1_x(n)
+		\end{split} \qquad  \begin{split}  
+		t\colon X&\to V^\star\\
+		x &\mapsto \prod_{n=0}^{f_2(x)-1}\iota^2_x(n)
+		\end{split}\]
+		Let $\mathcal{G}$ be $(X, V, s, t)$, by construction $F(\mathcal{G})=(f_1, f_2)$ and we can conclude.
+		 \qedhere 
+	\end{itemize}
+
+\end{proof}
+
 \subsection{Proofs for \Cref{hypereq}}\label{app:due}
@@
 \begin{defi}\index{category!comma -}
-	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comma{L}{R}$ is the category in which
-
-\noindent
-\parbox{10.5cm}{\vspace{-.1cm}\begin{itemize}
+	Let $L\colon \A\to \X$ and  $R\colon \B\rightarrow \X$ be two functors with the same codomain, the \emph{comma category} $\comma{L}{R}$ is the category in which:
+
+\noindent
+\begin{minipage}[l]{.8\linewidth}
+	\begin{itemize}
 		\item objects are triples $(A, B, f)$ with $A\in \A$, $B\in \B$, and $f\colon L(A)\rightarrow R(B)$; 
-		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the diagram aside commutes.\end{itemize}}\hfill
-	\parbox{4cm}{\vspace{-.1cm}\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]_{R(k)}& R(B')}}
+		\item a morphism $(A, B, f)\rightarrow (A', B', g)$ is a pair $(h, k)$ with $h\colon A\rightarrow A'$ in $\A$ and $k\colon B\rightarrow B'$ in $\B$ such that the diagram aside commutes.\end{itemize}
+\end{minipage}\hfill
+\begin{minipage}[r]{.25\linewidth}
+	\xymatrix@R=15pt{L(A) \ar[r]_{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g}\\ R(B) \ar[r]^{R(k)}& R(B')}
+\end{minipage} 
 \end{defi} 
@@
 Thus $\comma{L}{R}$ and $\comma{R^{op}}{L^{op}}$ have the same objects.
-Moreover, the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$
-\[\xymatrix@C=25pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g} & R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B') & L(A') \ar[r]_{L(h)}  & L(A)}\]
+Moreover, the left square below commutes in $\X$ if and only if the right one commutes in $\X^{op}$.
+\[\xymatrix@R=15pt{L(A) \ar[r]^{L(h)} \ar[d]_{f} & L(A') \ar[d]^{g} & R(B') \ar[d]_{g} \ar[r]^{R(k)}& R(B) \ar[d]^{f}\\ R(B) \ar[r]_{R(k)}& R(B') & L(A') \ar[r]_{L(h)}  & L(A)}\]
 
@@
 
-	\noindent \parbox{10cm}{
-	\hspace{15pt}Thus there exists $f\colon L(A)\rightarrow R(B)$ fitting in the diagram on the right.
+	\begin{minipage}[l]{.75\linewidth}
+	Thus there exists $f\colon L(A)\rightarrow R(B)$ fitting in the diagram on the right.
 Notice that $f$ is the unique arrow in $\X$ which makes $\left(a_D, b_D\right)$ an arrow $\left(A_D, B_D, f_D\right)\to \left(A, B, f\right)$ of $\comma{L}{R}$.
-If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.}\hfill
-	\parbox{4cm}{\xymatrix@C=35pt@R=15pt{ L(A_D) \ar[r]^{L(a_D)} \ar[d]_{f_D}& L(A) \ar[d]^{f}\\ R(B_D) \ar[r]_{R(b_D)} &R(B)}}
+If we show that $\left((A, B, f), \left\{(a_D, b_D)\right\}_{D\in \D}\right)$ is colimiting for $F$ we are done.
+	\end{minipage}
+	\hfill
+	\begin{minipage}[r]{.2\linewidth}
+	\xymatrix@R=10pt{ L(A_D) \ar[r]^{L(a_D)} \ar[d]_{f_D}& L(A) \ar[d]^{f}\\ R(B_D) \ar[r]_{R(b_D)} &R(B)}
+	\end{minipage}
 
@@
 	$(\Rightarrow)$  If $(h,k)\colon (A,B,f)\to (A', B', g)$ is a mono then the first rectangle below is a pullback in $\comma{L}{R}$.
-By \Cref{lim} then also the other two squares are pullbacks, respectively in $\A$ and $\B$, proving that both $h$ and $k$ are monos
-	\[\xymatrix{(A, B, f)  \ar[rr]^{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}&& (A, B, f)  \ar[d]^{(h,k)}& A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ (A, B, f)  \ar[rr]_{(h,k)}&& (A', B', g) &A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}\]
-
-%\newpage
+By \Cref{lim} then also the other two squares are pullbacks, respectively in $\A$ and $\B$, proving that both $h$ and $k$ are monos.
+	\[\xymatrix@R=15pt{(A, B, f)  \ar[rr]_{\id{(A,B,f)}} \ar[d]_{\id{(A,B,f)}}&& (A, B, f)  \ar[d]^{(h,k)}& A \ar[r]_{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]_{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ (A, B, f)  \ar[rr]^{(h,k)}&& (A', B', g) &A \ar[r]^{h} & A' & B \ar[r]^{k} & B'}\]
 	\smallskip\noindent
-	\parbox{4cm}{ \xymatrix{A \ar[r]^{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]^{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]_{h} & A' & B \ar[r]_{k} & B'}}\hfill \parbox{8.5cm}{$(\Leftarrow)$ Since $h$ and $k$ are monos then we have the two pullback squares on the left.
+	\begin{minipage}[l]{.3\linewidth}
+		 \xymatrix@R=13pt{A \ar[r]_{\id{A}} \ar[d]_{\id{A}} & A \ar[d]^{h} & B \ar[r]_{\id{B}} \ar[d]_{\id{B}} & B  \ar[d]^{k}\\ A \ar[r]^{h} & A' & B \ar[r]^{k} & B'}
+	\end{minipage} 
+	\hfill
+	\begin{minipage}[r]{.65\linewidth}
+		$(\Leftarrow)$ Since $h$ and $k$ are monos then we have the two pullback squares on the left.
 Thus by \Cref{lim} the pullback of $(h,k)$ along itself has isomorphisms as projections and so $(h,k)$ is mono.
-\qedhere}
-
+\qedhere
+	\end{minipage}
 \end{proof}
@@
 \begin{proof} For an object $B\in \B$ we can define $\Delta(B)$ as $(0, B, ?_{R(B)})$, for $0$ is an initial object in $\A$ and $?_{R(B)}$ is the unique arrow $L(0)\to R(B)$.
-Let $\id{B}\colon B\to U_R(\Delta(B))$ be the identity,
-
-	\noindent 
-	\parbox{10cm}{and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given. By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, 
-	since $L$ preserves initial objects, the square aside commutes. Thus $(?_A,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$ such that $U_R(?_A,k)=k$. }\hfill 
-	\parbox{2cm}{\vspace{-.1cm}\xymatrix@C=30pt@R=15pt{L(0) \ar[r]_{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]^{R(k)}& R(B')}}  
+Let $\id{B}\colon B\to U_R(\Delta(B))$ be the identity, and suppose that a $k\colon B\to U_R(A, B', f)$ in $\B$ is given.
+
+	\noindent
+\begin{minipage}[l]{.2\linewidth}
+	\xymatrix@C=30pt@R=8pt{L(0) \ar[r]_{L(?_A)} \ar[d]_{?_{R(B)}} & L(A) \ar[d]^{f}\\ R(B) \ar[r]^{R(k)}& R(B')}
+\end{minipage}  \hfill 
+	\begin{minipage}[r]{.75\linewidth}
+		By initiality of $0$, there is only one arrow $?_A\colon 0\to A $ in $\A$ and, 
+		since $L$ preserves initial objects, the square aside commutes. Thus $(?_A,k)$ is the unique morphism $\Delta(B)\to (A, B', f)$ such that $U_R(?_A,k)=k$. \qedhere 
+	\end{minipage}
+
 \end{proof}
@@
 	\noindent 
-	\parbox{11cm}{\vspace{-.5cm}\begin{itemize}
+	\begin{minipage}[l]{.8\linewidth}
+		\begin{itemize}
 			\item The \emph{ slice category over $X$} is the category $\X/X$ which has as objects arrows $f\colon Y\to X$ and  in which an arrow $h\colon f\to g$ is $h\colon Y\to Y'$ in $\X$ such that the triangle on the right commutes.
+		\end{itemize}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[r]{.2\linewidth}
+		\xymatrix@C=15pt@R=10pt{Y \ar[dr]_{f} \ar[rr]^{h}&& Y' \ar[dl]^{g}\\ & X} 
+	\end{minipage}
+
+	\noindent 
+	\begin{minipage}[l]{.8\linewidth}
+		\begin{itemize}
 			\item  	 Dually, the \emph{ slice category under $X$} is the category $X/\X$ in which objects are arrows $f\colon X\to Y$  with domain $X$ and a morphism $h\colon  f\to g$ is an arrow of $\X$ fitting in a triangle as the one aside.
-	\end{itemize}} \hfill \parbox{2cm}{\vspace{-0cm}\xymatrix@C=15pt@R=15pt{Y \ar[dr]_{f} \ar[rr]^{h}&& Y' \ar[dl]^{g}\\ & X} \xymatrix@C=15pt@R=15pt{&X \ar[dr]^{g}\ar[dl]_{f}\\ Y  \ar[rr]_{h}&& Y'}}
+		\end{itemize}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[r]{.2\linewidth}
+	 \xymatrix@C=15pt@R=10pt{&X \ar[dr]^{g}\ar[dl]_{f}\\ Y  \ar[rr]_{h}&& Y'}
+	\end{minipage}
 \end{defi}

### 2025-08-23 jlamp/jlamp.tex
minima

@@
 \begin{defi} Let $\mathcal{G}$ be an hypergraph. A node $v\in V_{\mathcal{G}}$ is \emph{isolated} if it does not occur as a letter in either $s_{\mathcal{G}}(e)$ or in
-$t_{\mathcal{G}}(e)$ for every $e\in E_{\mathcal{G}}$.
+$t_{\mathcal{G}}(e)$ for any $e\in E_{\mathcal{G}}$.
 $\mathcal{G}$ is \emph{pruned} if it has no isolated nodes.
@@
 We can use the absence of isolated nodes to show that $g=k$ too.
-Let $v\in V_{\mathcal{G}}$, we have two cases:
+Let $v\in V_{\mathcal{G}}$: we have two cases
 	\begin{itemize}
@@
 
-If we restrict to pruned separated hypergraph the previous issue disappeares.
+\smallskip
+The previous issue disappears if we restrict to pruned separated hypergraphs.
 The crucial observation is that the a pruned separated hypergraph is characterized by its set of hyperedges and the length of their sources and targets.
@@
 \begin{defi}
-	Given an hypergraph $\mathcal{G}$, the category $\hyp_\mathcal{G}$ of hypergraphs \emph{labelled by $\mathcal{G}$}  or of \emph{$\mathcal{G}$-hypergraphs} is $\hyp/\mathcal{G}$.
+	Let $\mathcal{G}$ be an hypergraph. The category $\hyp_\mathcal{G}$ of hypergraphs \emph{labelled by $\mathcal{G}$}  or of \emph{$\mathcal{G}$-hypergraphs} is $\hyp/\mathcal{G}$.
 \end{defi}
@@
 	If $l(h_1) = a$, $l(h_2) = 2$, $l(h_3) = *$, and $l(h_4) = /$, we represent it visually 
-	by putting the labels of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$.
+	by putting the labels of the edges in  $\mathcal{G}^\Sigma$ inside the boxes representing the edges of $\mathcal{G}$
 		\begin{center}
@@
 
-\begin{thm} Let $\mathcal{G}$ be an hypergraph, then %the following fact hold
+\begin{thm} Let $\mathcal{G}$ be an hypergraph. Then %the following fact hold
 %	\begin{enumerate}
@@
 	\[\delta^e_i(0) =\begin{cases}
-		s_{\mathcal{G}}(e)_i & i\leq n_e\\
-		t_{\mathcal{G}}(e)_{i-n_e} &  n_e < i
+		s_{\mathcal{G}}(e)_i & \mbox{if } i\leq n_e\\
+		t_{\mathcal{G}}(e)_{i-n_e} &  \mbox{otherwise}
 	\end{cases}\]
@@
 	\[\hat{g}(v):=\begin{cases}
-		\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0)) & v \text{ occurs in } s_{\mathcal{H}}(e)\\
-		\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0)) & v \text{ occurs in } t_{\mathcal{H}}(e)\\
+		\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0)) & \text{if } v \text{ occurs in } s_{\mathcal{H}}(e)\\
+		\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0)) & \text{if } v \text{ occurs in } t_{\mathcal{H}}(e)\\
 	\end{cases}\]
@@
 		&\epsilon_\mathcal{G}(\hat{g}(v))=\begin{cases}
-			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0))) & v \text{ occurs in } s_{\mathcal{H}}(e_v)\\
-			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0))) & v \text{ occurs in } t_{\mathcal{H}}(e_v)
+			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0))) & \text{if } v \text{ occurs in } s_{\mathcal{H}}(e_v)\\
+			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0))) & \text{if }v \text{ occurs in } t_{\mathcal{H}}(e_v)
 		\end{cases}=	\begin{cases}
-		\delta^{f(e_v)}_{i_v}(0)& v \text{ occurs in } s_{\mathcal{G}}(e)\\
-		\delta^{f(e_v)}_{i_v}(0)& v \text{ occurs in } t_{\mathcal{G}}(e)
+		\delta^{f(e_v)}_{i_v}(0)& \text{if }v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		\delta^{f(e_v)}_{i_v}(0)& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)
 		\end{cases}\\ =&
 		\begin{cases}
-			s_{\mathcal{G}}(f(e_v))_{i_v}& v \text{ occurs in } s_{\mathcal{G}}(e)\\
-			t_{\mathcal{G}}(f(e_v))_{i_v}& v \text{ occurs in } t_{\mathcal{G}}(e)
+			s_{\mathcal{G}}(f(e_v))_{i_v}& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
+			t_{\mathcal{G}}(f(e_v))_{i_v}& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)
 		\end{cases}= \begin{cases}
-		(g^\star(s_{\mathcal{H}}(e_v)))_{i_v}& v \text{ occurs in } s_{\mathcal{G}}(e)\\
-		(g^\star(t_{\mathcal{H}}(e_v)))_{i_v}& v \text{ occurs in } t_{\mathcal{G}}(e)\\
+		(g^\star(s_{\mathcal{H}}(e_v)))_{i_v}& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		(g^\star(t_{\mathcal{H}}(e_v)))_{i_v}& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)\\
 		\end{cases}\\=&\begin{cases}
-		g(s_{\mathcal{H}}(e_v)_{i_v})& v \text{ occurs in } s_{\mathcal{G}}(e)\\
-		g(t_{\mathcal{H}}(e_v)_{i_v})& v \text{ occurs in } t_{\mathcal{G}}(e)\\
+		g(s_{\mathcal{H}}(e_v)_{i_v})& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		g(t_{\mathcal{H}}(e_v)_{i_v})& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)\\
 		\end{cases}=g(v)
@@
 	\[(\lgh_{V_{\mathcal{H}}}\circ s_{\mathcal{H}}, \lgh_{V_{\mathcal{H}}}\circ t_{\mathcal{H}})\circ h = (\lgh_{V_{\mathcal{H}}}\circ s_{\mathcal{H}}\circ h, \lgh_{V_{\mathcal{H}}}\circ t_{\mathcal{H}}\circ h)=(\lgh_{V_{\mathcal{H}}}\circ k^\star\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{H}}}\circ k^\star\circ t_{\mathcal{G}})= (\lgh_{V_{\mathcal{G}}}\circ s_{\mathcal{G}}, \lgh_{V_{\mathcal{G}}}\circ t_{\mathcal{G}})\]
-	Thus we can define $F(h,k)$ simply as $h$ to get a functor $\pshyp\to \Set/(\mathbb{N}\times \mathbb{N})$. Let us show that it is an equivalence.
+	Thus we can define $F(h,k)$ as $h$ to get a functor $\pshyp\to \Set/(\mathbb{N}\times \mathbb{N})$. Let us show that it is an equivalence.
 	\begin{itemize}
@@
 		Since $\mathcal{G}$ is pruned and separated, $(V_{\mathcal{G}}, \{\iota^s_e\}_{e\in E_{\mathcal{G}}}+\{\iota^t_e\}_{e\in E_{\mathcal{G}}})$ is a coproduct.
-Given $v\in V^s_e$ and $w\in V^t_e$, let $i_v$ and $k_w$ be the unique indexes such that $\iota^s_e(v)=s_{\mathcal{G}}(e)_{i_v}$ and $\iota^t_e(w)= t_{\mathcal{G}}(e)_{k_w}$ and define:
+Given $v\in V^s_e$ and $w\in V^t_e$, let $i_v$ and $k_w$ be the unique indexes such that $\iota^s_e(v)=s_{\mathcal{G}}(e)_{i_v}$ and $\iota^t_e(w)= t_{\mathcal{G}}(e)_{k_w}$ and define
 			\[\begin{split}
@@
 
-		Given $e\in E_\mathcal{G}$, for every $1\leq i \leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $1\leq k \leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$ we can compute to get:
+		Given $e\in E_\mathcal{G}$, for every $1\leq i \leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $1\leq k \leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$ we can compute to get
 		\begin{align*}
@@
 Given $x\in X$,  we can consider $f_1(x)$ and $f_2(x)$ as ordinal sets and take the coproduct $(V, \{\iota^1_x\}_{x\in X}+ \{\iota^2_x\}_{x\in X})$ of the family $\{f_1(x)\}_{x\in X}+\{f_2(x)\}_{x\in X}$.
-Define:
+Define
 		\[\begin{split}  

### 2025-08-23 jlamp/jlamp.tex
minima

@@
 
-\author[1]{Davide Castelnovo\corref{cor1}%
+\author[1,mur]{Davide Castelnovo\corref{cor1}%
 }
@@
 
-\author[1]{Fabio Gadducci}
+\author[1,mur]{Fabio Gadducci}
 \ead{fabio.gadducci@unipi.it}
@@
 	country = {Italy}}
+
+\fntext[mur]{The research has been partially supported by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 
+``Spatio-Temporal Enhancement of Neural nets for Deeply Hierarchical Automatised Logic'' (STENDHAL).}
 
@@
 \end{abstract}
+
+\begin{keyword}
+Hypergraphs, terms graphs, e-graphs, adhesive categories.
+\end{keyword}
 
@@
 
+\section*{Acknowledgments}
+Hypergraphs, terms graphs, e-graphs, adhesive categories.
+
 \bibliographystyle{plain}

### 2025-09-08 jlamp/jlamp.tex
sez. 4

--- 2025-08-21 jlamp/jlamp.tex
@@
 \newcommand{\pbe}{\mathsf{ePb}}
+\newcommand{\pbl}{\mathsf{LPb}}
+\newcommand{\pble}{\mathsf{eLPb}}
+\newcommand{\pbs}{\mathsf{SPb}}
+\newcommand{\pbse}{\mathsf{eSPb}}
 \usepackage{amsthm,amsmath,amssymb,mathrsfs, dsfont}
@@
 \newcommand{\hyps}{\catname{Hyp}_{\Sigma}}
-\newcommand{\EqHyp}{\catname{EqHyp}} %equivalence hypergraphs
-\newcommand{\EqHyps}{\catname{EqHyp}_{\Sigma}}
+\newcommand{\EqHyp}{\catname{Hyp}_{\mathsf{eq}}} %equivalence hypergraphs
+\newcommand{\EqsHyp}{\catname{Sep}_{\mathsf{eq}}} 
+\newcommand{\EqpHyp}{\catname{pHyp}_{\mathsf{eq}}}
+\newcommand{\EqpsHyp}{\catname{pSep}_{\mathsf{eq}}}
+\newcommand{\Eqlmo}{\catname{LMH}_{\mathsf{eq}}}
+\newcommand{\EqHyps}{\catname{Hyp}_{\mathsf{eq}, \mathcal{G}}}
 \newcommand{\EqTG}{\catname{EqTG}}
@@
 \renewcommand{\sp}{\mathsf{sp}}
+\newcommand{\pr}{\mathsf{pr}}
 \newcommand{\is}[1]{{#1}_{is}}
@@
 \begin{minipage}[r]{.18\linewidth}
-	\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}
+	\xymatrix@R=15pt{K_f \ar[r]_{\pi^2_f} \ar[d]_{\pi^1_f}& A \ar[d]^f \\ A \ar[r]^{f}& B}
 \end{minipage}
@@
 \begin{minipage}[l]{.75\linewidth}
-	\begin{defi}
+	\begin{defi}\label{def:alg}
 		A \emph{(single typed) monoidal signature} $\Sigma$ is a triple $(O_\Sigma, \ari_\Sigma, \coar_\Sigma)$ given by a \emph{set of operations} $O_\Sigma$ together with \emph{arity} and \emph{coarity} functions $\ari_\Sigma, \coar_\Sigma\colon O_\Sigma \rightrightarrows \mathbb{N}$.
@@
 
-\subsubsection{Two  subcategories of $\hyp$}\label{sub:sub}
-
-We are now going to introduce two classes of hypergraphs, and the relative subcategories, which will provide the base for our definitions of EGGs  (cfr.~\Cref{sec:sepegg,sec:lmegg}).
+\subsubsection{Some subcategories of $\hyp$}\label{sub:sub}
+
+We are now going to introduce some classes of hypergraphs, and the relative subcategories, which will provide the base for our definitions of EGGs  (cfr.~\Cref{sec:sepegg,sec:lmegg}).
 
@@
 
-\begin{cor}	$\lmo$ is closed in $\hyp$ under pullbacks.
+\begin{cor}\label{cor:pb}	$\lmo$ is closed in $\hyp$ under pullbacks.
 \end{cor}
@@
 
-\paragraph{Separated hypergraphs}
-We can now introduce the second  subcategory of $\hyp$ in which we are interested in and that is going to be used in \Cref{sec:sepegg} to give the underlying hypergraphs for EGGs with minimally identified tokens.
+\paragraph{Pruned and separated hypergraphs}
+We can now introduce another  subcategory of $\hyp$ in which we are interested in and that is going to be used in \Cref{sec:sepegg} to give the underlying hypergraphs for EGGs with minimally identified tokens.
 
@@
  	\end{itemize}
+ \end{rem}
+
+ \begin{rem}\label{rem:count}
+ 	By \Cref{rem:elem2} it is clear that separated hypergraphs enjoy a property similar to the one enjoyed by left-monogamous ones (cfr.~\Cref{proof:count}): if $\mathcal{G}$ is separated and $(f,g)\colon \mathcal{H}\to \mathcal{G}$ is a mono, then $\mathcal{H}$ is separated too.
  \end{rem}
@@
 
-We define the \emph{separated graph associated to $\mathcal{G}$}  as $\sp(\mathcal{G}) = (E_{\mathcal{G}}, V_{\sp(\mathcal{G})}, s_{\sp(\mathcal{G})}, t_{\sp(\mathcal{G})})$.
+We define the \emph{separated hypergraph associated to $\mathcal{G}$}  as $\sp(\mathcal{G}) = (E_{\mathcal{G}}, V_{\sp(\mathcal{G})}, s_{\sp(\mathcal{G})}, t_{\sp(\mathcal{G})})$.
 \end{defi}
@@
 \begin{rem}\label{rem:mprun}
-	Let $(f,g)$ and $(h, k)$ be two morphisms $\mathcal{G}\rightrightarrows \mathcal{H}$ of $\phyp$ and suppose that $f=h$.
-We can use the absence of isolated nodes to show that $g=k$ too.
+	Let $(f,g)$ and $(h, k)$ be two morphisms $\mathcal{G}\rightrightarrows \mathcal{H}$ of $\hyp$ with $\mathcal{G}$ pruned and suppose that $f=h$.
+We can use the absence of isolated nodes in $\mathcal{G}$ to show that $g=k$ too.
 Let $v\in V_{\mathcal{G}}$, we have two cases:
@@
 
-\begin{restatable}{prop}{dx}\label{prop:dx}
-	The inclusion functor $P\colon \pshyp\to \phyp$ has a right adjoint $\sp_P$.
+\begin{restatable}{prop}{dx}\label{prop:dx}The following hold true:
+	\begin{enumerate}
+		\item the inclusion functor $P\colon \phyp \to \hyp$ has a right adjoint $\pr$;
+		\item The inclusion functor $S_p\colon \pshyp\to \phyp$ has a right adjoint $\sp_P$.
+	\end{enumerate}
 \end{restatable}
@@
 
+\smallskip
 If we restrict to pruned separated hypergraph the previous issue disappeares.
@@
 \end{cor}
+
+We can use \Cref{lem:pruned} to say something more about colimits and pullbacks in $\pshyp$. A proof can be found in \Cref{proof:limpsy}
+
+\begin{restatable}{prop}{limps}\label{prop:limpsy}
+	$\pshyp$ is closed in $\hyp$ under colimits and pullbacks.
+\end{restatable}
 
@@
 	Let $\mathcal{G}$ be an hypergraph and $(h,k)\colon \mathcal{H}\to \mathcal{G}$  a $\mathcal{G}$-hypergraph.
-We say that $(h,k)$ is a \emph{left-monogamous} (resp.~\emph{separated}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated).
-
-	We will denote by $\lmo_{\mathcal{G}}$ and $\shyp_{\mathcal{G}}$  the corresponding subcategories of $\hyp_{\mathcal{G}}$.
+We say that $(h,k)$ is a \emph{left-monogamous} (resp.~\emph{separated, pruned}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated, pruned).
+
+	We will denote by $\lmo_{\mathcal{G}}$, $\phyp_{\mathcal{G}}$, $\shyp_{\mathcal{G}}$ and $\pshyp_{\mathcal{G}}$ the corresponding subcategories of $\hyp_{\mathcal{G}}$.
 \end{defi}
 
+\begin{rem}Of the four subcategories  defined above, we are interested only in  $\lmo_{\mathcal{G}}$, $\shyp_{\mathcal{G}}$ and $\pshyp_{\mathcal{G}}$.
+This is due to the fact that we do not have an adhesivity result for $\phyp$.
+\end{rem}
+
+\begin{rem} The functors $\pr$ and $\sp_P$ induce right adjoints to the inclusions $P_\mathcal{G}\colon \phyp_\mathcal{G} \to \hyp_{\mathcal{G}}$ and $S_{p, \mathcal{G}}\colon \pshyp_\mathcal{G}\to \phyp_{\mathcal{G}}$.
+\end{rem}
 We can easily realize $\lmo_{\mathcal{G}}$ and $\shyp_{\mathcal{G}}$ as comma categories.
@@
 \begin{prop}
-Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Let, moreover, $\Delta_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then
+Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Let, moreover, $\Gamma_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then
 \begin{enumerate}
-	\item $\lmo_{\mathcal{G}}$ is equivalent to $\comma{M}{\Delta_\mathcal{G}}$;
-	\item $\shyp_{\mathcal{G}}$ is equivalent to $\comma{S}{\Delta_\mathcal{G}}$; 
+	\item $\lmo_{\mathcal{G}}$ is equivalent to $\comma{M}{\Gamma_\mathcal{G}}$;
+	\item $\shyp_{\mathcal{G}}$ is equivalent to $\comma{S}{\Gamma_\mathcal{G}}$; 
+	\item $\pshyp_{\mathcal{G}}$ is equivalent to $\pshyp/\sp(\pr(\mathcal{G}))$. 
 \end{enumerate}
@@
 		%\item 
-		$\lmo_{\mathcal{G}}$ is quasiadhesive.
+		$\lmo_{\mathcal{G}}$ is quasiadhesive and $\pshyp_{\mathcal{G}}$ is adhesive.
 %	\end{enumerate}
@@
 \end{rem}
+
+\noindent 
+\begin{minipage}[l]{.5\linewidth}
+	\begin{rem}\label{rem:map1}
+		Now that we have introduced all the flavours of hypergraphs we need, it is worthwhile to give a visual map of all the categories that we have discussed/introduced and of the relationships between them.
+We will use the curved arrows to denote full and faithful inclusions, while the vertical arrows are forgetful functors.
+	\end{rem}
+\end{minipage}\hfill
+\begin{minipage}[r]{.45\linewidth}
+	\xymatrix@R=8pt@C=10pt{& \pshyp_\mathcal{G} \ar[dd]_(.7){W_\mathcal{G}}|\hole \ar@/_.2cm/@{_{(}->}[rr]_{S_{p,\mathcal{G}}} \ar@{_{(}->}[dl]_{I_\mathcal{G}} && \phyp_\mathcal{G} \ar[dd]^(.7){V_\mathcal{G}}|\hole \ar@/_.2cm/[ll]^{\sp_\mathcal{G}}\ar@/_.2cm/@{_{(}->}[dr]_(.35){P_\mathcal{G}}\\\shyp_\mathcal{G} \ar@{^{(}->}[rr]^(.35){S_\mathcal{G}} \ar[dd]_{R_\mathcal{G}}&& \lmo_\mathcal{G}  \ar@{^{(}->}[rr]^(.35){M_\mathcal{G}} \ar[dd]_(.25){O_\mathcal{G}}&& \hyp_\mathcal{G} \ar@/_.2cm/[ul]_{\pr_\mathcal{G}} \ar[dd]^{U_\mathcal{G}}\\& \pshyp \ar@/_.2cm/@{_{(}->}[rr]_(.35){S_p}|\hole \ar@{^{(}->}[dl]_{I} && \phyp \ar@/_.2cm/[ll]^(.35){\sp}|\hole\ar@/_.2cm/@{_{(}->}[dr]_(.3){P}\\\shyp \ar@{_{(}->}[rr]^{S} && \lmo  \ar@{_{(}->}[rr]^(.35){M}&& \hyp \ar@/_.2cm/[ul]_{\pr}}
+\end{minipage}
 
@@
 The use of hypergraphs equipped with an equivalence relation over their nodes has been argued as a convenient way to express concurrency in the DPO approach to rewriting~\cite{concur2006}.
-This section presents the framework by means of adhesive categories, including also its version for term graphs, as a stepping stone towards an analogous characterisation for e-graphs.
+This section presents the framework through adhesive categories, including its extension to the various kinds of hypergraphs introduced in the previous section, as a stepping stone towards an analogous characterization for e-graphs.
 
@@
 
-\begin{restatable}{lem}{pbs}\label{lemma:stab}
+\begin{restatable}{lem}{pbsa}\label{lemma:stab}
 	In $\EqHyp$, $\pbc$-pushouts are stable.
@@
 \begin{exa}
-It is noteworthy to show that pushouts along regular monos are not stable.
+It is noteworthy to show that pushouts along regular monos in $\EqHyp$ are not stable.
 
@@
 		\setlength{\parindent}{1.5em}
-		\indent Consider e.g. the cube aside: the vertices are just graphs without edges, and in the graphs themselves the equivalence classes 
+		\indent As a counterexample, let us consider the cube aside, where the morphisms are the inclusions defined by the labels of the nodes.
+The vertices are just graphs without edges, and in the graphs themselves the equivalence classes
 are denoted by encircling nodes with a dotted line. All the arrows are regular monos. It is immediate to see that the bottom face is a pushout and the side faces are pullback. Unfortunately, 
-the top face fails to be a pushout
+the top face fails to be a pushout.
   \end{minipage}\hfill
 \begin{minipage}[r]{.60\linewidth}
-                \xymatrix@C=10pt@R=1pt{
+                \xymatrix@C=10pt@R=.05pt{
                 &\emptyset \ar@{>->}[dd]|\hole \ar@{>->}[rr] \ar@{>->}@(dl,)[dl] &&
@@
 
-\subsubsection{title}
-\paragraph{title}
-\paragraph{title}
-%\input{Hypergraphs_with_equivalences}
-%\input{Labeled_hyp_with_eq}
+\subsubsection{Some subcategories of $\EqHyp$}
+
+We can now focus to the various kind of hypergraphs introduced in \Cref{sub:sub}.
+
+\begin{defi}Given an hypergraph with equivalence $\mathcal{H}:=(E_\mathcal{G}, V_{\mathcal{G}}, Q_\mathcal{G}, s_\mathcal{G}, t_\mathcal{G}, q_\mathcal{G})$, we say that $\mathcal{H}$ is \emph{left-monogamous} (resp.~\emph{separated, pruned}) if $T(\mathcal{H})$ is left-monogamous (resp.~\emph{separated, pruned}).
+We will denote by $\Eqlmo$, $\EqsHyp$ and $\EqpsHyp$ the  subcategories  given by left-monogamous, separated, pruned and separated hypergraphs with equivalence.
+\end{defi}
+
+\begin{rem}\label{rem:obv1}
+By definition, there exist functors $a$ as in the diagrams below, where the horizontal arrows are full and faithful inclusions.
+\[\xymatrix{\Eqlmo \ar[r]^-{M_{\mathsf{eq}}} \ar[d]_{O_{\mathsf{eq}}}& \EqHyp\ar[d]^{T} & \EqsHyp \ar[r]^-{S_{\mathsf{eq}}} \ar[d]_{R_{\mathsf{eq}}} & \EqHyp \ar[d]^{T} & \EqpsHyp \ar[r]^-{S_{p, \mathsf{eq}}} \ar[d]_{W_{\mathsf{eq}}} & \EqHyp\ar[d]^{T}\\ \lmo \ar[r]_{M} & \hyp & \shyp \ar[r]_{S} & \hyp  & \pshyp \ar[r]_-{S_p}& \hyp}\]
+
+\end{rem}
+
+Let us start by dealing with some class of limits in these subcategories (see \Cref{proof:equ} for a proof).
+
+\begin{restatable}{lem}{equ}\label{lem:equ} The following are true:
+	\begin{enumerate}
+		\item 	$\Eqlmo$ is closed in $\EqHyp$ under equalizers, binary products and pullbacks.
+		\item $\EqsHyp$ is closed in $\EqHyp$ under connected limits; 
+		\item $\EqpsHyp$ is closed in $\EqHyp$ under pullbacks.
+	\end{enumerate}
+\end{restatable}
+
+We can now turn to colimits, applying the same strategy. A proof is deferred to \Cref{proof:coequ}
+
+\begin{restatable}{lem}{coequ}\label{lem:coequ}
+ The following are true:
+\begin{enumerate}
+	\item 	$\Eqlmo$ is closed in $\EqHyp$ under pushouts along morphism whose image through $T$ is downward-closed.
+	\item $\EqpsHyp$ is closed in $\EqHyp$ under colimits.
+\end{enumerate}
+\end{restatable}
+
+We are now ready to prove two adhesivity results for $\Eqlmo$ and $\EqpsHyp$.
+
+\begin{defi}We define the following two classes of arrows:
+\begin{itemize}
+	\item $\pbl$ is the class of all arrows in $\Eqlmo$ sent by $M_{\eq}$ to $\pbc$;
+	\item $\pbs$ is the class of all arrows in $\EqpsHyp$ sent by $S_{p,\eq}$ to $\pbc$.
+\end{itemize}
+\end{defi}
+
+By definition, \Cref{lem:pbmono} and putting together Lemmas \ref{lem:equ}, \ref{lem:coequ} with \Cref{thm:slice-functors} we get the following.
+
+\begin{cor}$\Eqlmo$ is $\pbl$-adhesive and $\EqpsHyp$ is $\pbs$-adhesive
+\end{cor}
 
@@
 \begin{defi}
-	Let $\Sigma$ be an algebraic signature and $\mathcal{G}^{\Sigma}$ the hypergraph associated to it.
-A \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, l)$ where $\mathcal{H}$ is an object of $\EqHyp$ and $l$ a morphism $T(\mathcal{H})\to \mathcal{G}^\Sigma$ of $\hyp$.
-A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, l)$ and $(\mathcal{H}', l')$ is an arrow $h\colon \mathcal{H}\to \mathcal{H}'$ such that $l= l'\circ T(h)$.
-
-	We denote the resulting category by $\EqHyp_\Sigma$.
+	Let $\mathcal{G}$ be an hypergraph, a \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, (f,g))$ where $\mathcal{H}$ is an object of $\EqHyp$ and $(f,g)$ a morphism $T(\mathcal{H})\to \mathcal{G}$ of $\hyp$.
+A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, (f,g))$ and $(\mathcal{H}', (h,k))$ is an arrow $(a,b, c)\colon \mathcal{H}\to \mathcal{H}'$ such that:
+	\[h\circ a = f \qquad k\circ b = g \].
+
+	We denote the resulting category by $\EqHyps$.
 \end{defi}
 
-Let $(\mathcal{H}, l)$ be an object of $\EqHyp_\Sigma$: since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to the arrow $(l, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G}^\Sigma)$.
-It is immediate to see that this correspondence extends to an equivalence with the slice over $R(\mathcal{G}^\Sigma)$.
+\noindent 
+\begin{minipage}[l]{.8\linewidth}
+		\setlength{\parindent}{1.5em}
+		\begin{rem}Let $\Sigma$ be a single typed monoidal signature (cfr~\Cref{def:alg}).
+Since $\mathcal{G}_{\Sigma}$ has a single node, then to label another hypergraph $\mathcal{H}$ it is enough to provide a function $l\colon E_{\mathcal{H}}\to O_{\Sigma}$ such that the diagrams aside commute.
+
+			Notice that, if $\Sigma$ is algebraic, than such a function exists only if $\mathcal{H}$ is algebraic too. In that case the second diagram commute by default.
+		\end{rem}
+\end{minipage} \hfill 
+\begin{minipage}[r]{.15\linewidth}
+	\xymatrix{xy code}
+	\end{minipage}
+
+Let $(\mathcal{H}, l)$ be an object of $\EqHyps$: since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $(f,g)\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to the arrow $(f, g, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G})$.
+It is immediate to see that this correspondence extends to an equivalence with the slice category over $R(\mathcal{G})$.
 
 \begin{prop}\label{prop:slice}
-$\EqHyp_\Sigma$ is equivalent to $\EqHyp/R(\mathcal{G}^\Sigma)$.
+$\EqHyps$ is equivalent to $\EqHyp/R(\mathcal{G})$.
 \end{prop}
 
-Let $V_\Sigma\colon \EqHyp_\Sigma\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyp_\Sigma$ whose image in $\EqHyp$ is in $\pbc$.
+Let $V_\Sigma\colon \EqHyps\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyps$ whose image in $\EqHyp$ is in $\pbc$.
 From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors,cor:eqade}, we can deduce the following.
 
-\begin{prop}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyp_\Sigma\to \EqHyp$. Then the following facts hold
+\begin{prop}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyps\to \EqHyp$. Then the following facts hold
 	\begin{enumerate}
-		\item $\EqHyp_\Sigma$ has all colimits and all connected limits, which are created by $V_{\Sigma}$;
-		\item $\EqHyp_\Sigma$ is $\pbc_\Sigma$-adhesive.
+		\item $\EqHyps$ has all colimits and all connected limits, which are created by $V_{\Sigma}$;
+		\item $\EqHyps$ is $\pbc_\Sigma$-adhesive.
 	\end{enumerate}
@@
 
-%In particular, $\EqHyp_\Sigma$ has all equalizers and pullbacks.
+%In particular, $\EqHyps$ has all equalizers and pullbacks.
 Using \Cref{cor:mono1} and \Cref{cor:mono2} we immediately get the following result.
 
-\begin{cor}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyp_\Sigma$. Then the following facts hold
+\begin{cor}\label{prop:monos_in_eqhyps} Let $h=(h_{E}, h_V, h_Q)$ be an arrow in $\EqHyps$. Then the following facts hold
 	\begin{enumerate}
@@
 \begin{defi}Let $\Sigma$ be an algebraic signature.
-	An object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph.
-We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyp_\Sigma$ so defined and by $J_{\Sigma}$ the corresponding inclusion functor.
+	An object $(\mathcal{H}, l)$ of $\EqHyps$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph.
+We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyps$ so defined and by $J_{\Sigma}$ the corresponding inclusion functor.
  \end{defi}
@@
 	\begin{rem}\label{rem:obv}
-		Let $T_\Sigma:  \EqHyp_{\Sigma} \to \hyp_{\Sigma}$ the functor sending an object of $\EqHyp_{\Sigma}$ to its underlying  labelled hypergraph.
+		Let $T_\Sigma:  \EqHyps \to \hyp_{\Sigma}$ the functor sending an object of $\EqHyps$ to its underlying  labelled hypergraph.
 		%
@@
 \begin{minipage}[r]{.23\linewidth}
-	\xymatrix{\EqTG_{\Sigma} \ar[r]^{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}
+	\xymatrix@R=15pt{\EqTG_{\Sigma} \ar[r]_{J_\Sigma}  \ar[d]_{S_\Sigma}& \EqHyps \ar[d]^{T_\Sigma} \\ \tg \ar[r]^{I_\Sigma}& \hyp_{\Sigma}}
 \end{minipage}
@@
 
-\subsubsection{title}
-
+\begin{rem}\label{rem:map2}
+	contenuto...
+\end{rem}
 \section{EGGs}
@@
 
-\begin{defi} We say that an object $(\mathcal{H}, l)$ of $\EqHyp_\Sigma$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
-We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyp_\Sigma$ given by labelled e-hypergraphs.
+\begin{defi} We say that an object $(\mathcal{H}, l)$ of $\EqHyps$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
+We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyps$ given by labelled e-hypergraphs.
 We denote by $Z_\Sigma$ the corresponding inclusion functor .
@@
 \begin{minipage}[r]{.20\linewidth}
-	\xymatrix@R=10pt@C=20pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]^-{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyp_\Sigma \ar[r]^-{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]^{T}\\ \tg \ar@{^{(}->}[r]^-{I_\Sigma}& \hyp_{\Sigma} \ar[r]^-{U_\Sigma}  &\hyp}
+	\xymatrix@R=10pt@C=20pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]^-{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyps \ar[r]^-{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]^{T}\\ \tg \ar@{^{(}->}[r]^-{I_\Sigma}& \hyp_{\Sigma} \ar[r]^-{U_\Sigma}  &\hyp}
 \end{minipage}
@@
 \noindent
-\begin{minipage}[l]{.7\linewidth}
+\begin{minipage}[l]{.65\linewidth}
 \begin{proof}\label{mpo-proof}
@@
 \hfill 
-\begin{minipage}[r]{.30\linewidth}		
-\xymatrix@C=10pt@R=2pt{&K_a\ar[dd]|\hole_(.7){\pi^1_a}\ar[rr]^{k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_b\ar[dd]^{\pi^1_b} \ar@{>->}[dl]_(.55){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]^(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]^(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]_{g'} & & D' }
+\begin{minipage}[r]{.40\linewidth}		
+\xymatrix@C=20pt@R=2pt{&K_a\ar[dd]|\hole_(.7){\pi^1_a}\ar[rr]_(.4){k_{f'}} \ar@{>->}[dl]_(.55){k_{m'}} && K_b\ar[dd]^{\pi^1_b} \ar@{>->}[dl]^(.45){k_{n'}} \\ K_c  \ar[dd]_{\pi^1_c}\ar[rr]_(.7){k_{g'}} & & K_d \ar[dd]_(.3){\pi^1_d}\\&A'\ar[rr]|\hole^(.65){f'} \ar@{>->}[dl]_(.4){m'} && B' \ar@{>->}[dl]^{n'}  \\C' \ar[rr]^(.6){g'} & & D' }
 \end{minipage}
@@
 		\end{minipage}\hfill 	 \begin{minipage}[r]{.3\linewidth}
-	 	\xymatrix@R=8pt{E_{\mathcal{G}} \ar@/^.3cm/@{>->}[rr]^{f} \ar[d]_{s_{\mathcal{G}}}\ar@{.>}[r]_-{\phi}&  E_{h_1, h_2} \ar@{.>}[d]_{s_{\mathcal{E}}} \ar@{>->}[r]_-{\iota_E} & E_{\mathcal{H}} \ar[d]_{s_{\mathcal{H}}}\\V^\star_{\mathcal{G}} \ar@/_.3cm/@{>->}[rr]_{g^\star} \ar@{.>}[r]^-{\psi^\star}& V^\star_{k_1, k_2} \ar@{>->}[r]^-{\iota^\star_V}& V^\star_{\mathcal{H}}}
-	 	\xymatrix@R=8pt{E_{\mathcal{G}} \ar@/^.3cm/@{>->}[rr]^{f} \ar[d]_{t_{\mathcal{G}}}\ar@{.>}[r]_-{\phi}&  E_{h_1, h_2} \ar@{.>}[d]_{t_{\mathcal{E}}} \ar@{>->}[r]_-{\iota_E} & E_{\mathcal{H}} \ar[d]_{t_{\mathcal{H}}}\\V^\star_{\mathcal{G}}\ar@/_.3cm/@{>->}[rr]_{g^\star} \ar@{.>}[r]^-{\psi^\star}& V^\star_{k_1, k_2} \ar@{>->}[r]^-{\iota^\star_V}& V^\star_{\mathcal{H}}}
+	 	\xymatrix@R=8pt{E_{\mathcal{G}} \ar@/^.3cm/@{>->}[rr]^(.3){f} \ar[d]_{s_{\mathcal{G}}}\ar@{.>}[r]_-{\phi}&  E_{h_1, h_2} \ar@{.>}[d]_{s_{\mathcal{E}}} \ar@{>->}[r]_-{\iota_E} & E_{\mathcal{H}} \ar[d]_{s_{\mathcal{H}}}\\V^\star_{\mathcal{G}} \ar@/_.3cm/@{>->}[rr]_(.3){g^\star} \ar@{.>}[r]^-{\psi^\star}& V^\star_{k_1, k_2} \ar@{>->}[r]^-{\iota^\star_V}& V^\star_{\mathcal{H}}}
+	 	\xymatrix@R=8pt{E_{\mathcal{G}} \ar@/^.3cm/@{>->}[rr]^(.3){f} \ar[d]_{t_{\mathcal{G}}}\ar@{.>}[r]_-{\phi}&  E_{h_1, h_2} \ar@{.>}[d]_{t_{\mathcal{E}}} \ar@{>->}[r]_-{\iota_E} & E_{\mathcal{H}} \ar[d]_{t_{\mathcal{H}}}\\V^\star_{\mathcal{G}}\ar@/_.3cm/@{>->}[rr]_(.3){g^\star} \ar@{.>}[r]^-{\psi^\star}& V^\star_{k_1, k_2} \ar@{>->}[r]^-{\iota^\star_V}& V^\star_{\mathcal{H}}}
 	 \end{minipage}
@@
 By \Cref{prop:com} and \Cref{colim} we know that the other two squares are pushouts too
-	\[\xymatrix@C=35pt{\mathcal{G} \ar[r]^{(f,g)}  \ar[d]_{(f,g)}& \mathcal{H}\ar[d]^{(p_1, p_2)} & E_{\mathcal{G}} \ar@{>->}[d]_{f}\ar@{>->}[r]^{f} & E_{\mathcal{H}} \ar[d]^{p_1}& V_{\mathcal{G}}\ar@{>->}[r]^{g} \ar@{>->}[d]^{g} & V_{\mathcal{H}} \ar[d]^{p_2}\\\mathcal{H} \ar[r]_{(q_1, q_2)} & \mathcal{P} & E_{\mathcal{H}} \ar[r]_{q_1}& E_{\mathcal{P}} & V_{\mathcal{H}}\ar[r]_{q_2} & V_{\mathcal{P}}}\]
+	\[\xymatrix@C=35pt@R=15pt{\mathcal{G} \ar[r]^{(f,g)}  \ar[d]_{(f,g)}& \mathcal{H}\ar[d]^{(p_1, p_2)} & E_{\mathcal{G}} \ar@{>->}[d]_{f}\ar@{>->}[r]^{f} & E_{\mathcal{H}} \ar[d]^{p_1}& V_{\mathcal{G}}\ar@{>->}[r]^{g} \ar@{>->}[d]_{g} & V_{\mathcal{H}} \ar[d]^{p_2}\\\mathcal{H} \ar[r]_{(q_1, q_2)} & \mathcal{P} & E_{\mathcal{H}} \ar[r]_{q_1}& E_{\mathcal{P}} & V_{\mathcal{H}}\ar[r]_{q_2} & V_{\mathcal{P}}}\]
 
@@
 \begin{proof}\label{proof:dx}
-	Let $\mathcal{G}$ be an hypergraph.
+	\begin{enumerate}
+\item Given an hypergraph $\mathcal{G}$, let $\iota_{\pr(\mathcal{G})}\colon V_{\pr(\mathcal{G})}\mto V_{\mathcal{G}}$ be the inclusion of non isolated nodes.
+By definition we know that there exists $s_{\pr(\mathcal{G})}, t_{\pr(\mathcal{G})}\colon E_{\mathcal{G}}\rightrightarrows V_{\pr(\mathcal{G})}$ such that
+\[s_{\mathcal{G}}=\iota_{\pr(\mathcal{G})}\circ s_{\pr(\mathcal{G})}\qquad t_{\mathcal{G}}=\iota_{\pr(\mathcal{G})}\circ t_{\pr(\mathcal{G})}\]
+
+ Thus we can define $\pr(\mathcal{G})$ as $(E_{\mathcal{G}}, V_{\pr(\mathcal{G})}, s_{\pr(\mathcal{G})}, t_{\pr(\mathcal{G})})$.
+Clearly $(\id{E_{\mathcal{G}}}, \iota_{\pr(\mathcal{G})})$ is a morphism $P(\pr(\mathcal{G}))\to \mathcal{G}$.
+
+ Let $(f,g)\colon P(\mathcal{H})\to \mathcal{G}$ be a morphism with pruned domain. For every $v \in V_{\mathcal{H}}$ we have two cases:
+ \begin{itemize}
+ 	\item $v$ occurs in $s_{\mathcal{G}}(e)$ for some $e\in E_{\mathcal{G}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ be such that $v=s_{\mathcal{G}}(e)_i$, then we have
+ 	\[g(v)=g(s_{\mathcal{G}}(e)_i)=(g^\star(s_{\mathcal{G}}(e)))_i=s_{\mathcal{H}}(f(e))_i\]
+ 	\item $v$ occurs in $t_{\mathcal{H}}(e)$ for some $e\in E_{\mathcal{H}}$. Let $1\leq i\leq \lgh_{V_{\mathcal{H}}}(t_{\mathcal{G}}(e))$ be such that $v=t_{\mathcal{G}}(e)_i$, then we have
+ 	\[g(v)=g(t_{\mathcal{G}}(e)_i)=(g^\star(t_{\mathcal{G}}(e)))_i=t_{\mathcal{H}}(f(e))_i\]
+ \end{itemize}
+
+ Thus $g(v)$ belongs to $V_{\pr(\mathcal{G})}$ for every node $v$ of $\mathcal{H}$ and so there exists $\hat{g}\colon V_{\mathcal{H}}\to V_{\pr(\mathcal{G})}$ such that $g=\iota_{\pr(\mathcal{G})}\circ \hat{g}$.
+
+ Computing we get
+ \begin{align*}
+ 	\iota^\star_{\pr(\mathcal{G})}\circ s_{\pr(\mathcal{G})}\circ f &= s_{\mathcal{G}}\circ f = g^\star \circ s_{\mathcal{H}} = \iota^\star_{\pr(\mathcal{G})} \circ \hat{g}^\star \circ s_{\mathcal{H}} \\
+ 	\iota^\star_{\pr(\mathcal{G})}\circ t_{\pr(\mathcal{G})}\circ f &= t_{\mathcal{G}}\circ f = g^\star \circ t_{\mathcal{H}} = \iota^\star_{\pr(\mathcal{G})} \circ \hat{g}^\star \circ t_{\mathcal{H}}
+ \end{align*}
+
+ Since $(-)^\star$ sends monos to mono it follows that $(f, \hat{g})$ is a morphsim $\mathcal{H}\to \pr(\mathcal{G}) $ which, by construction, is such that $(\id{E_{\mathcal{G}}}, \iota_{\pr(\mathcal{G})})\circ (f, \hat{g}) = (f,g)$.
+  Uniqueness follows at once since $\iota_{\pr(\mathcal{G})}$ is mono.
+
+\item Let $\mathcal{G}$ be an hypergraph.
 For every $e\in E_{\mathcal{G}}$, let $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$.
@@
 \smallskip 
-	Hence $(\id{E_{\mathcal{G}}}, \epsilon_{G})$ is a morphism $P(\sp(\mathcal{G}))\to \mathcal{G}$.
+Hence $(\id{E_{\mathcal{G}}}, \epsilon_{G})$ is a morphism $S_p(\sp(\mathcal{G}))\to \mathcal{G}$.
 Now, let $(f,g)\colon P(\mathcal{H})\to \mathcal{G}$ be a  morphism of pruned hypergraphs with $\mathcal{H}$ separated.
@@
 Computing we get
-	\begin{gather*}
-		\hat{g}^\star(s_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{n_e} s_{\mathcal{H}}(e)_i)=\prod_{i=1}^{n_e}(\hat{g}(s_{\mathcal{H}}(e)_i))=\prod_{i=1}^{n_e}\iota_{f(e)}( \iota^{f(e)}_i(0))=s_{\sp(\mathcal{G})}(f(e))\\
-		\hat{g}^\star(t_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{m_e} t_{\mathcal{H}}(e)_i)=\prod_{i=1}^{m_e}(\hat{g}(t_{\mathcal{H}}(e)_i))=\prod_{i=1}^{m_e}\iota_{f(e)}( \iota^{f(e)}_{n_e+i}(0))=\prod_{i=n_e + 1}^{n_e + m_e}\iota_{f(e)}( \iota^{f(e)}_{i}(0))=t_{\sp(\mathcal{G})}(f(e))
-	\end{gather*}
+\begin{align*}
+	&\hat{g}^\star(s_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{n_e} s_{\mathcal{H}}(e)_i)=\prod_{i=1}^{n_e}(\hat{g}(s_{\mathcal{H}}(e)_i))=\prod_{i=1}^{n_e}\iota_{f(e)}( \iota^{f(e)}_i(0))=s_{\sp(\mathcal{G})}(f(e))\\
+	&\hat{g}^\star(t_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{m_e} t_{\mathcal{H}}(e)_i)=\prod_{i=1}^{m_e}(\hat{g}(t_{\mathcal{H}}(e)_i))=\prod_{i=1}^{m_e}\iota_{f(e)}( \iota^{f(e)}_{n_e+i}(0))\\=&\prod_{i=n_e + 1}^{n_e + m_e}\iota_{f(e)}( \iota^{f(e)}_{i}(0))=t_{\sp(\mathcal{G})}(f(e))
+\end{align*}
 proving that $(f, \hat{g})\colon \mathcal{H}\to\sp( \mathcal{G})$ is a morphism of $\pshyp$. Notice that	
@@
 \end{align*}
-and so $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(f, \hat{g})=(f,g)$.
-
-	Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(h, k)=(f,g)$.
-This entails immediately that $h =f$ and so uniqueness follows from \Cref{rem:mprun}.
+and so $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ S_p(f, \hat{g})=(f,g)$.
+
+Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ S_p(h, k)=(f,g)$.
+This entails immediately that $h =f$ and so uniqueness follows from \Cref{rem:mprun}.	\qedhere
+	\end{enumerate}	
 \end{proof}
@@
 
+\limps*
+
+\begin{proof}\label{proof:limpsy}
+	Let  $F\colon \D \to \pshyp$ be a diagram and suppose that $(\mathcal{C}, \{(q^D_E, q^D_V)\}_{D\in \D})$  is a colimiting cocone for $F$.
+By \Cref{prop:dx} we know that $P\circ S_p$ preserves colimits, but then the vertex of every colimiting cocone for $P\circ S_p \circ F$ is isomorphic to $\mathcal{C}$ and thus  it must be pruned and separated.
+
+	\noindent
+	\begin{minipage}[l]{.73\linewidth}\setlength{\parindent}{1.5em}
+	We can now turn to pullbacks.
+Let us consider a pullback square in $\hyp$ as the one aside in which $\mathcal{G}$, $\mathcal{H}$ and $\mathcal{K}$ are pruned and separated.
+We already know, by \Cref{lem:seplim} that $\mathcal{P}$ is separated, so it is enough to show that $\mathcal{P}$ is pruned.
+	\end{minipage}\hfill \begin{minipage}[r]{.25\linewidth}\vspace{-.4cm}
+	\xymatrix@R=15pt@C=40pt{\mathcal{P} \ar[r]_{(p_1, p_2)} \ar[d]_{(q_1, q_2)}& \mathcal{G} \ar[d]^{(f_1, f_2)} \\ \mathcal{H} \ar[r]^{(g_1, g_2)} & \mathcal{K}}
+	\end{minipage}
+
+	Let $v$ be a node in $V_{\mathcal{P}}$. Since $\mathcal{G}$ and $\mathcal{H}$ are pruned we know that $p_2(v)$ and $q_2(v)$ must occur in the source or target of some hyperedge. We have four cases.
+	\begin{itemize}
+		\item There exist $e\in E_{\mathcal{G}}$ and $h\in E_{\mathcal{H}}$ such that $p_2(v)$ occurs in the source of $e$ and $q_2(v)$ in  that of $h$.
+Let $1\leq i\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $1\leq j\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{H}}(h))$ be indexes such that:
+		\[s_{\mathcal{G}}(e)_i = p_2(v) \qquad s_{\mathcal{H}}(h)_j = q_2(v)\]
+		Hence we have:
+		\begin{align*}
+		&s_{\mathcal{K}}(f_1(e))_i=(f^\star_2(s_{\mathcal{G}}(e)))_i=f_2(s_{\mathcal{G}}(e)_i)=f_2(p_2(v))\\=&g_2(q_2(v))=g_2(s_{\mathcal{H}}(h)_j)=(g^\star_2(s_{\mathcal{H}}(h)))_k=s_{\mathcal{H}}(g_1(h))_j
+		\end{align*}
+	Since $\mathcal{K}$ is separated this entails that $i = j$ and  $f_1(e)=g(e)$. So there exists $a\in E_{\mathcal{P}}$ such that $p_1(a)=e$
+ and $q_1(a)=h$. Computing we have:
+ \begin{align*}
+ 	p_2(s_{\mathcal{P}}(a)_i)&=(p^\star_2(s_{\mathcal{P}}(a)))_i=s_{\mathcal{G}}(p_1(a))_i=s_{\mathcal{G}}(e)_i = p_2(v)\\
+ 	q_2(s_{\mathcal{P}}(a)_i)&=(q^\star_2(s_{\mathcal{P}}(a)))_i=s_{\mathcal{G}}(q_1(a))_i=s_{\mathcal{G}}(h)_i = q_2(v)
+ \end{align*}
+ and so $s_{\mathcal{P}}(a)_i=v$.
+ 		\item 	There exist $e\in E_{\mathcal{G}}$ and $h\in E_{\mathcal{H}}$ such that $p_2(v)$ occurs in $t_{\mathcal{G}}(e)$ and $q_2(v)$ in $t_{\mathcal{H}}(h)$.
+As before, let $1\leq i\leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$ and $1\leq j\leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{H}}(h))$ be indexes such that:
+ 		\[t_{\mathcal{G}}(e)_i = p_2(v) \qquad t_{\mathcal{H}}(h)_j = q_2(v)\]
+ 		so that
+ 		\begin{align*}
+ 			&t_{\mathcal{K}}(f_1(e))_i=(f^\star_2(t_{\mathcal{G}}(e)))_i=f_2(t_{\mathcal{G}}(e)_i)=f_2(p_2(v))\\=&g_2(q_2(v))=g_2(t_{\mathcal{H}}(h)_j)=(g^\star_2(t_{\mathcal{H}}(h)))_k=t_{\mathcal{H}}(g_1(h))_j
+ 		\end{align*}
+ 		The fact that $\mathcal{K}$ is separated assures that $i = j$ and  $f_1(e)=g(e)$. Let then $a\in E_{\mathcal{P}}$ be such that $p_1(a)=e$
+ 		and $q_1(a)=h$. Computing we have:
+ 		\begin{align*}
+ 			p_2(t_{\mathcal{P}}(a)_i)&=(p^\star_2(t_{\mathcal{P}}(a)))_i=t_{\mathcal{G}}(p_1(a))_i=t_{\mathcal{G}}(e)_i = p_2(v)\\
+ 			q_2(t_{\mathcal{P}}(a)_i)&=(q^\star_2(t_{\mathcal{P}}(a)))_i=t_{\mathcal{G}}(q_1(a))_i=t_{\mathcal{G}}(h)_i = q_2(v)
+ 		\end{align*}
+ 		allowing us to deduce that $t_{\mathcal{P}}(a)_i=v$.
+
+		\item Suppose that there are indexes $1\leq i\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $1\leq j\leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{H}}(h))$ such that:
+		\[s_{\mathcal{G}}(e)_i = p_2(v) \qquad t_{\mathcal{H}}(h)_j = q_2(v)\]
+		Computing we get:
+			\begin{align*}
+			&s_{\mathcal{K}}(f_1(e))_i=(f^\star_2(s_{\mathcal{G}}(e)))_i=f_2(s_{\mathcal{G}}(e)_i)=f_2(p_2(v))\\=&g_2(q_2(v))=g_2(t_{\mathcal{H}}(h)_j)=(g^\star_2(t_{\mathcal{H}}(h)))_k=t_{\mathcal{H}}(g_1(h))_j
+		\end{align*}
+		This contradicts the fact that $\mathcal{K}$ is separated.
+		\item Consider now indexes $1\leq i\leq \lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$ and $1\leq j\leq \lgh_{V_{\mathcal{G}}}(s_{\mathcal{H}}(h))$ such that:
+		\[t_{\mathcal{G}}(e)_i = p_2(v) \qquad s_{\mathcal{H}}(h)_j = q_2(v)\] 
+		Proceeding as in the previous point we have:
+				\begin{align*}
+			&t_{\mathcal{K}}(f_1(e))_i=(f^\star_2(t_{\mathcal{G}}(e)))_i=f_2(t_{\mathcal{G}}(e)_i)=f_2(p_2(v))\\=&g_2(q_2(v))=g_2(s_{\mathcal{H}}(h)_j)=(g^\star_2(s_{\mathcal{H}}(h)))_k=s_{\mathcal{H}}(g_1(h))_j
+		\end{align*}
+		This again stands in contradiction with $\mathcal{K}$ being an object of $\shyp$. \qedhere
+	\end{itemize}
+\end{proof}
+
 \subsection{Proofs for \Cref{hypereq}}\label{app:due}
@@
 	Before proceeding further, let us recall the following result about the classes of regular epis (i.e.~surjections) and of monos in $\Set$.
-In particular, we need the fact that they form a a \emph{factorization system} \cite{kelly2006note} on $\Set$.
+In particular, we need the fact that they form a \emph{factorization system} \cite{kelly2006note} on $\Set$.
 This amounts to ask that
@@
 	\noindent 
-	\parbox{11.5cm}{
+	\begin{minipage}[l]{.8\linewidth}
 		\begin{enumerate} 
@@
 			\item for every commuting square as the one on the right, with $e\colon X\eto E$ a surjection and $m\colon N\mto Y$ a mono, there exists a unique $k\colon E\to N$ making it commutative.
-	\end{enumerate}}\hfill \parbox{2cm}{\xymatrix{X \ar@{>>}[d]_{e}\ar[r]^{f}& N \ar@{>->}[d]^{m} \\ E \ar@{.>}[ur]^{k}\ar[r]_{g} & Y}}
+		\end{enumerate}
+	\end{minipage}\hfill
+	\begin{minipage}[r]{.2\linewidth}
+	\xymatrix@C=45pt{X \ar@{>>}[d]_{e}\ar[r]^{f}& N \ar@{>->}[d]^{m} \\ E \ar@{.>}[ur]^{k}\ar[r]_{g} & Y}
+	\end{minipage}
 
@@
 \noindent
-\parbox{11.4cm}{
-\comp*}\hfill 
-\parbox{2cm}{\xymatrix{V \ar@{>>}[d]_{q} \ar[r]^{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]_{l_d} & Q_D}}
-
+\begin{minipage}[l]{.83\linewidth}
+	\comp*
+\end{minipage}\hfill
+\begin{minipage}[r]{.15\linewidth}
+	\xymatrix{V \ar@{>>}[d]_{q} \ar[r]_{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]^{l_d} & Q_D}
+\end{minipage} 
 \begin{proof}\label{proof:comp}
@@
 Thus, let $(E, V, s, t)$ together with $\{(\kappa_E^D, \kappa_V^D)\}_{D \in \D}$ be a colimit for $T \circ F$.
-By \Cref{colim} we also know that
-
-		 \noindent 
-		 \parbox{10.5cm}{$(V, \{\kappa^D_V\}_{D\in \D})$ is a colimit for $U_\eq\circ F$.
+By \Cref{colim} we also know that $(V, \{\kappa^D_V\}_{D\in \D})$ is a colimit for $U_\eq\circ F$.
+
+		\noindent
+		\begin{minipage}[l]{.8\linewidth}
 			Moreover, since $\Set$ is cocomplete too we can also take a colimit $(C, \{c_d\}_{d\in \D})$ for $K\circ F$.
 Now,  let $\alpha$ be an arrow $D\to D'$ in $\D$, and suppose that $F(\alpha)$ is $(h_1, h_2, h_3)$.
-By definition of morphisms in $\EqHyp$, the square on the right commutes.}
+By definition of morphisms in $\EqHyp$, the square on the right commutes.
+		\end{minipage}
 		\hfill 
-		\parbox{2cm}{\xymatrix{V_d \ar[r]_{h_2} \ar@{>>}[d]_{q_D} & V_{D'} \ar@{>>}[d]^{q_{D'}}\\ Q_{D} \ar[r]^{h_3} & Q_{D'}}}
-		\vspace{.05cm}
-
+		\begin{minipage}[r]{.2\linewidth}
+			\xymatrix@R=10pt{V_d \ar[r]_{h_2} \ar@{>>}[d]_{q_D} & V_{D'} \ar@{>>}[d]^{q_{D'}}\\ Q_{D} \ar[r]^{h_3} & Q_{D'}}
+		\end{minipage}
+
+		\smallskip 
 		Thus the family $\{q_D\}_{D\in \D}$ form a natural transformation $U_\eq\circ F\to K\circ F$.
@@
 
-\noindent 
-\parbox{9.5cm}{Thus there is an arrow $l\colon V\to L$ such that $l_D\circ l=q_D\circ \pi^D_V$.
+\begin{minipage}[l]{.7\linewidth}
+	Thus there is an arrow $l\colon V\to L$ such that $l_D\circ l=q_D\circ \pi^D_V$.
 By \Cref{rem:fact}, we know that there exist $m\colon Q\mto L$ and $q\colon X\eto Q $ such that $m\circ q=l$.
-Since the identity is mono, \Cref{rem:fact} yield a unique arrow $\pi^D_Q$ fitting in the rectangle aside.} 	\hfill \parbox{3cm}{\xymatrix{
-	V\ar[r]^{\pi_V^D}\ar@{>>}[d]_{q}&V_D\ar@{>>}[r]^{q_D}&Q_D\ar[d]^{\id{Q_D}}\\Q\ar@{>->}[r]_{m}\ar@{.>}[urr]_{\pi_Q^D}&L\ar[r]_{l_D}&{Q_D}
-	}}
+Since the identity is mono, \Cref{rem:fact} yield a unique arrow $\pi^D_Q$ fitting in the rectangle aside.
+\end{minipage}\hfill\begin{minipage}[r]{.3\linewidth}
+\xymatrix@R=20pt{
+	V\ar[r]^{\pi_V^D}\ar@{>>}[d]_{q}&V_D\ar@{>>}[r]^{q_D}&Q_D\ar[d]^{\id{Q_D}}\\Q\ar@{>->}[r]^{m}\ar@{.>}@/^.2cm/[urr]^(.3){\pi_Q^D}&L\ar[r]^{l_D}&{Q_D}
+}
+\end{minipage}
 
@@
 \noindent 
-\parbox{2cm}{\xymatrix@R=15pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]^{m}\\ Q_{\mathcal{G}}  \ar@{.>}[urr]_{k_Q}\ar[rr]_{h} && L }}\hfill \parbox{9.5cm}{Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
+\begin{minipage}[l]{.3\linewidth}
+\xymatrix@R=20pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar[r]^{h_V}& V \ar@{>>}[r]^{q}  & Q \ar@{>->}[d]_{m}\\ Q_{\mathcal{G}}  \ar@{.>}[urr]^(.4){k_Q}\ar[rr]^{h} && L }
+\end{minipage}
+\hfill
+\begin{minipage}[r]{.75\linewidth}
+Hence the  outer boundary of the square on the left commutes, yielding the dotted diagonal arrow $k_Q\colon Q_\mathcal{G}\to Q$.
 We have therefore built an arrow $(h_E, h_V, k_Q)$ of $\EqHyp$ such that
-\[(\pi^D_E, \pi^D_V, \pi^D_Q)\circ (h_E, h_V, k_Q)=(h^D_E, h^D_V, h^D_Q)\]}
-
+\vspace{-.2cm}
+\[(\pi^D_E, \pi^D_V, \pi^D_Q)\circ (h_E, h_V, k_Q)=(h^D_E, h^D_V, h^D_Q)\]
+\end{minipage}
+
+\smallskip 
 As in the point above, uniqueness is guaranteed by faithfulness of $T$ and \Cref{rem:eqhyp_morphs}.	\qedhere 
@@
 \noindent
-	\parbox{11cm}{
-		\hspace{15pt}Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
+	\begin{minipage}[l]{.82\linewidth}	\setlength{\parindent}{1.5em}
+	Let now $(f_E, f_V, f_Q), (g_E, g_V, g_Q): \mathcal{H\rightrightarrows K}$ be arrows equalized by $(h_E, h_V, h_Q)$. Let $e\colon E_Q\mto Q_{\mathcal{H}}$ be the equalizer in
 $\Set$ of $f_Q, g_Q\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{K}}$. From the third point of \Cref{prop:fact} and \Cref{lim} we know that $h_V\colon V_{\mathcal{G}}\mto V_{\mathcal{H}} $ 
 is the equalizer of $f_V, g_V\colon V_{\mathcal{H}}\rightrightarrows V_{\mathcal{K}}$, thus by the second point of \Cref{prop:eqhyp_complete} we know that there is a mono 
-	$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that 
-	$e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}$.
-	Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the claim follows.}
+$m\colon Q_{\mathcal{G}}\mto E_Q$ fitting in the diagram aside. Now, notice that: 
+\vspace{-.2cm}
+\[e\circ m\circ q_{\mathcal{G}}=q_\mathcal{H}\circ h_V=h_{Q}\circ q_{\mathcal{G}}\]
+	\end{minipage}
 	\hfill
-	\parbox{2cm}{\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]^{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]_{e} & Q_\mathcal{{H}}}}
+	\begin{minipage}[r]{.2\linewidth}
+		\xymatrix@R=18pt{V_\mathcal{G} \ar@{>>}[d]_{q_{\mathcal{G}}} \ar@{>->}[r]_{h_V}& V_\mathcal{H} \ar@{>>}[dd]^{q_{\mathcal{H}}}\\Q_\mathcal{G} \ar@{>.>}[d]_{m}&\\ E_Q \ar@{>->}[r]^{e} & Q_\mathcal{{H}}}
+	\end{minipage}
+
+	\smallskip  
+Since $q_{\mathcal{G}}$ is epi we conclude that $e\circ m=h_Q$, from which the claim follows.
 
 	$(\Leftarrow)$ Suppose that $h_E$, $h_V$, and $h_Q$  are monos. 
-	We can build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks
+	We can build the cokernel pair of the three arrows, taking the pushout of $h_E$, $h_V$ and $h_Q$ along itself, obtaining the three diagrams below, which by \Cref{prop:regmono} are also pullbacks.
 	\[     \xymatrix@R=15pt{
@@
 
-\pbs*
+\pbsa*
 
@@
 	\[
-	\xymatrix@C=10pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_{z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_{z_V'} \\
+	\xymatrix@C=10pt@R=8pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'} & &A_1'\ar[dd]|\hole_(.65){a_E}\ar@{>->}[rr]^{h_E'} \ar[dl]_{k_E'} && A_2' \ar[dd]_{b_E} \ar[dl]_(.55){z_E'} &&B_1'\ar[dd]|\hole_(.65){a_V}\ar@{>->}[rr]^{h_V'} \ar[dl]_{k_V'} && B_2' \ar[dd]^{b_V} \ar[dl]_(.55){z_V'} \\
 		\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}_4' \ar[dd]_(.3){d} &&A_3'  \ar[dd]_{c_E}\ar@{>->}[rr]^(.7){p_E'} & & A_4' \ar[dd]_(.3){d_E}
@@
 	\noindent 
-\parbox{10cm}{Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
+	\begin{minipage}[l]{.73\linewidth}	\setlength{\parindent}{1.5em}
+		Now, if $d=(d_E, d_V, d_Q)$, we can pull back the third component to get the solid part of the cube aside.
 Notice moreover that the commutativity of the solid diagram yields the existence of the dotted $w\colon T\to Y$.
 By the usual composition and decomposition properties of pullbacks (cfr.~\Cref{lem:pb1}) the left face is a pullback.
-By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.}\hfill\parbox{3cm}{\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]^{x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_Q} \ar@{>->}[dl]^{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]_{p_C} & & Q_4 }}
-
-	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the diagrams below
-
-	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} \\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4}\]
-
-\newpage
-	\noindent 
-	\parbox{8.5cm}{\hspace{15pt}
+By the first point of \Cref{prop:eqhyp_complete} the bottom face is a pushout and $h_Q$ is a mono by \Cref{cor:mono2}, so the top face is a pushout too.
+	\end{minipage}\hfill 
+	\begin{minipage}[r]{.3\linewidth}
+		\xymatrix@C=10pt@R=10pt{&T\ar[dd]|\hole_(.65){x_2}\ar@{>->}[rr]_(.4){x_1} \ar@{>.>}[dl]_{w} && U \ar[dd]^{u_2} \ar[dl]_{u_1} \\ Y  \ar[dd]_{y_2}\ar@{>->}[rr]^(.7){y_1} & & Q_4' \ar[dd]_(.3){d_Q}\\&Q_1\ar@{>->}[rr]|\hole^(.65){h_Q} \ar@{>->}[dl]_{k_Q} && Q_2 \ar[dl]^{z_Q} \\Q_3 \ar@{>->}[rr]^{p_C} & & Q_4 }
+	\end{minipage}
+
+	By the second point of \Cref{prop:eqhyp_complete} we know that there are monos $m_2\colon Q'_2\mto U$ and $m_3\colon Q'_3\mto Y$  fitting in the first two diagrams below:
+	\[\xymatrix@R=15pt{B'_3 \ar@{>>}[d]^{q'_3} \ar@/_.3cm/[dd]_{c_V} \ar@{>->}[r]^{p'_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} & & B'_2 \ar[r]^{z_V} \ar@{>>}[d]^{q'_2} \ar@/_.3cm/[dd]_{b_V}& B'_4 \ar@/^.2cm/@{>>}[dr]^{q'_4} &&B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]^{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\ Q'_3 \ar@{>.>}[r]^{m_3}& Y  \ar@{>->}[r]^{y_1} \ar[d]_{y_2}& Q'_4 \ar[d]_{d_C}& Q'_2 \ar@{>.>}[r]^{m_2} & U \ar[d]_{u_2} \ar[r]^{u_1} & Q'_4 \ar[d]_{d_C} &B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\ B_3 \ar@{>>}[r]_{q_3} & Q_3 \ar@{>->}[r]_{p_Q} & Q_4 &B_2 \ar@{>>}[r]_{q_3} & Q_2 \ar[r]_{z_Q} & Q_4&& Q'_2 \ar@{>->}[r]^{m_2}& U \ar[r]^{u_2}& Q_2 }\]
+
 	For $Q'_1$, we can make a similar argument.
-Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ that makes the diagram aside commutative.}\hfill
-	\parbox{4cm}{\xymatrix@R=15pt{B'_1\ar@{>>}[r]_{q'_1} \ar@{>->}[d]_{h'_V} \ar@/^.3cm/[rr]^{a_V} & Q'_1 \ar@{>.>}[d]_{m_1} & B_1 \ar@{>>}[dr]^{q_1}\\B'_2 \ar@{>>}[dr]_{q'_2} & S \ar@{>->}[r]^{s_2} \ar[d]_{s_1} & T \ar[r]^{x_2} \ar@{>->}[d]_{x_1}  & Q_1 \ar@{>->}[d]^{h_Q}\\& Q'_2 \ar@{>->}[r]_{m_2}& U \ar[r]_{u_2}& Q_2 }}
+Taking $(S, s_1, s_2)$ as the pullback of $m_2$ along $x_1$, we can use again the composition properties of pullbacks and the second point of \Cref{prop:eqhyp_complete} to guarantee the existence of a monomorphism $m_1\colon Q'_1\to S$ that makes the last diagram above commutative.
 
@@
 
-\smallskip \noindent 
-\parbox{8cm}{ \hspace{15pt}We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$.
-If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
-
-	\hspace{15pt}Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
+\noindent
+\begin{minipage}[l]{.65\linewidth}\setlength{\parindent}{1.5em}
+	We want to extend such a morphism to one of $\EqHyp$ between $\mathcal{G}'_4\to \mathcal{H}$. If we are able to do so we can conclude because uniqueness is guaranteed by \Cref{rem:eqhyp_morphs}.
+
+	Now, consider the cube aside, $h$ is in $\pbc$ so by \Cref{lem:pb1} we know that its back face is a pullback.
 We can then apply the second point of \Cref{prop:kerset} to deduce that the square on the right is a pushout.
 
-	By construction we have that 
-	\begin{align*}
-		m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1& = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \\
-		m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 &= m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2
-		\end{align*} 
-	}\hfill\parbox{4cm}{\xymatrix@C=10pt@R=10pt{
-	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]^{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
-	B_3'  \ar[dd]_{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
-	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]_{w} && U\ar[dl]^(.4){u_1} \\
-	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]_{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]^{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
-}
+	By construction we have that:
+\[	m_3\circ q'_3 \circ \pi_{m_3 \circ q'_3}^1 = m_3\circ q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad m_2\circ q_2' \circ \pi_{m_2 \circ q_2'}^1 = m_2\circ q'_2 \circ \pi_{m_2 \circ q_2'}^2 \]
 but since $m_3$ and $m_2$ are monos this implies
 \[q'_3 \circ \pi_{m_3 \circ q'_3}^1 = q'_3 \circ \pi_{m_3\circ q_3'}^2 \qquad q_2' \circ \pi_{m_2 \circ q_2'}^1 = q'_2 \circ \pi_{m_2 \circ q_2'}^2\]
+\end{minipage}\quad \hfill
+\begin{minipage}[r]{.35\linewidth}
+\xymatrix@C=10pt@R=8pt{
+	&B_1'\ar@{>>}[dd]|(.53)\hole_(.67){s_2\circ m_1\circ q_1'}\ar@{>->}[rr]^{h_V'} \ar[dl]_(.6){k_V'} && B_2' \ar@{>}[dd]_{m_2\circ q_2'} \ar[dl]_(.6){z_V'} & & \\
+	B_3'  \ar[dd]^{m_3\circ q_3'}\ar@{>->}[rr]^(.7){p_V'}  &&B_4' \ar@{>>}[dd]_(.3){q_4'} \\
+	&T\ar@{>->}[rr]_(.3){x_1}|(.5)\hole \ar[dl]^{w} && U\ar[dl]^(.4){u_1} \\
+	Y \ar@{>->}[rr]_{y_1} & &  Q'_4\\K_{s_2\circ m_1\circ q'_1}  \ar@{>->}[rr]_-{k_{h'_V}} \ar[dd]^{k_{k'_V}}&& K_{m_2\circ q'_2} \ar[dd]_{k_{z'_V}}\\ \\ K_{m_3\circ q'_3} \ar@{>->}[rr]^-{k_{p'_V}} && K_{q'_4}}
+\end{minipage}
 
@@
 \noindent
-\parbox{5.2cm}{\hspace{15pt}Now, notice that  $m_3$ and $m_2$ are monos because $c_Q$ and $b_2$ are injections. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that
+\begin{minipage}[l]{.4\linewidth}\setlength{\parindent}{1.5em}
+	Now,  since $c_Q$ and $b_2$ are injective functions, then $m_3$ and $m_2$ are monomorphisms. By the proof of \Cref{prop:eqhyp_complete}, to conclude it is enough to show that 
 	\[m_3\circ q'_3 = a_3 \qquad m_2\circ q'_2=a_2\]
 
-		\hspace{15pt}Indeed, if the previous equations hold, then $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and the claim follows from \Cref{prop:eqhyp_complete}.
-	}\hfill \parbox{3.5cm}{\xymatrix@R=16pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_3}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }
-\xymatrix@R=16pt{B'_3 \ar@{.>}[dr]^{a_3} \ar@{>->}[r]^{p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]^{a_2} \ar[r]^{z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]_{p_Q}& Q_4 &&Q_2 \ar[r]_{z_Q}& Q_4 }}
-
-By computing we have
+	Now, from the previous two equations we can deduce that $Q'_3$ and   $Q'_2$ are images for $a_3$ and $a_2$ and therefore the claim follows from \Cref{prop:eqhyp_complete}.
+\end{minipage}\hfill 
+\begin{minipage}[r]{.5\linewidth}\vspace{-.5cm}
+	\xymatrix@R=13pt@C=30pt{Q'_3 \ar@{.>}[r]_{m_3} \ar@{>->}@/^.3cm/[rr]^{p'_Q} \ar@{>->}@/_.3cm/[dr]_{c_Q} &Y \ar@{>->}[d]_{y_2}\ar@{>->}[r]_{y_1}& Q'_4 \ar@{>->}[d]^{d_Q}& Q'_2 \ar@{.>}[r]_{m_2} \ar@/^.3cm/[rr]^{z'_Q} \ar@{>->}@/_.3cm/[dr]_{b_Q}&U \ar[r]_{u_1} \ar@{>->}[d]_{u_2}& Q'_4\ar[d]^{d_Q}\\&Q_3 \ar@{>->}[r]^{p_3}& Q_4 &&Q_2 \ar[r]^{z_Q}& Q_4 }
+	\xymatrix@R=13pt@C=30pt{B'_3 \ar@{.>}[dr]_{a_3} \ar@{>->}[r]_(.6){p'_V} \ar@{>>}[d]_{q'_3} &B'_4\ar@{>>}[dr]^{q'_4}&& B'_2\ar@{.>}[dr]_{a_2} \ar[r]_(.6){z'_2} \ar@{>>}[d]_{q'_2} &B'_4\ar@{>>}[dr]^{q'_4}\\Q'_3 \ar@{>->}[dr]_{c_Q} &Y \ar@{>->}[r]_{y_1} \ar@{>->}[d]_{y_2}& Q'_4\ar[d]^{d_Q}&Q_2' \ar@{>->}[dr]_{c_Q}& U \ar@{>->}[d]_{u_2}\ar[r]_{u_1}& Q'_4 \ar@{>->}[d]^{d_Q}\\&Q_3 \ar@{>->}[r]^{p_Q}& Q_4 &&Q_2 \ar[r]^{z_Q}& Q_4 }
+\end{minipage}
+
+\smallskip 
+Computing we have:
 \[\begin{split}
@@
 \end{split}\]	
-And we have done.
+And we are done.
+\end{proof}
+
+\equ*
+\begin{proof}\label{proof:equ}
+	\begin{enumerate}
+		\item Let $F\colon \D\to \Eqlmo$ be a functor with binary product, pullback or equalizer shape.
+Let $(E_{\mathcal{L}}, V_{\mathcal{L}}, Q_{\mathcal{L}}, s_{\mathcal{L}}, t_{\mathcal{L}}, q_{\mathcal{L}})$ be a vertex for a limiting cone for $M_{\eq}\circ F$.
+By \Cref{prop:eqhyp_complete} we know that $\mathcal{L}:=(E_{\mathcal{L}}, V_{\mathcal{L}}, s_{\mathcal{L}}, t_{\mathcal{L}})$ is the vertex of a limiting cone for $T\circ M_{\eq}\circ F$ and so by Corollaries \ref{cor:eq} and \ref{cor:pb} and \Cref{lem:pro} it is left-monogamous.
+
+		\item Let $\D$ be a connected category and $F\colon \D\to \EqsHyp$ a functor.
+If $(E_{\mathcal{L}}, V_{\mathcal{L}}, Q_{\mathcal{L}}, s_{\mathcal{L}}, t_{\mathcal{L}}, q_{\mathcal{L}})$ is a vertex for a limiting cone for $S_{\eq}\circ F$ then, by Lemmas \ref{lem:seplim} and \ref{prop:eqhyp_complete}, $(E_{\mathcal{L}}, V_{\mathcal{L}}, s_{\mathcal{L}}, t_{\mathcal{L}})$  is separated, proving the claim.
+
+		\item  This is done as int he previous two points using \Cref{prop:limpsy}. \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\coequ*
+\begin{proof}\label{proof:coequ}
+	\begin{enumerate} 
+		\item Consider two arrows $(f,g)\colon \mathcal{G}\to \mathcal{H}$
+		and $(h,k)\colon \mathcal{G}\to \mathcal{K}$ in $\EqHyp$ with the same domain.
+Let $\mathcal{P}$ be the vertex of a pushout diagram for them.
+By \Cref{prop:eqhyp_complete} we know that $T(\mathcal{P})$ is a pushout for $T(f,g)$ along $T(h,k)$.
+Thus if $T(\mathcal{G})$ and $T(\mathcal{H})$ are left-monogamous and $T(f,g)$ is downward-closed, by \Cref{cor:pusho} we deduce that $T(\mathcal{P})$ is left-monogamous and so $\mathcal{P}$ is in $\Eqlmo$.
+
+		\item Let $F\colon \D\to \EqpsHyp$ be a functor.
+Let $\mathcal{C}$ be the vertex of a colimiting cocone for $S_{p, \eq}\circ F$.
+by the first point of \Cref{prop:eqhyp_complete} we know that $T(\mathcal{C})$ is the vertex of a colimiting cocone for $T\circ S_{p,\eq}\circ F$.
+By \Cref{prop:limpsy}, thus, $T(\mathcal{C})$  is pruned and separated and we can conclude.
+\qedhere
+	\end{enumerate}
 \end{proof}
@@
 \begin{proof}\label{proof:tade}
-	Suppose that the square on the left below is a pushout in $\EqHyp_\Sigma$, with $h$ in $\mathcal{T}$.
+	Suppose that the square on the left below is a pushout in $\EqHyps$, with $h$ in $\mathcal{T}$.
 Then, by \Cref{rem:t} the square on the right is a pushout and by the definition of $\mathcal{T}$ and \Cref{rem:obv}, $T_\Sigma(h)$ is a regular mono in $\tg$

### 2025-09-08 jlamp/jlamp.tex
sez.4

@@
 Let $v\in V_{\mathcal{G}}$, we have two cases:
+
 	\begin{itemize}
@@
 \end{rem}
-We can easily realize $\lmo_{\mathcal{G}}$ and $\shyp_{\mathcal{G}}$ as comma categories.
+We can easily realize $\lmo_{\mathcal{G}}$, $\shyp_{\mathcal{G}}$ and $\pshyp_{\mathcal{G}}$ as comma categories.
 
@@
 \begin{rem}\label{rem:obv1}
-By definition, there exist functors $a$ as in the diagrams below, where the horizontal arrows are full and faithful inclusions.
+By definition, there exist functors $O_{\eq}$, $R_{\eq}$ and $W_{\eq}$ as in the diagrams below, where the horizontal arrows are full and faithful inclusions.
 \[\xymatrix{\Eqlmo \ar[r]^-{M_{\mathsf{eq}}} \ar[d]_{O_{\mathsf{eq}}}& \EqHyp\ar[d]^{T} & \EqsHyp \ar[r]^-{S_{\mathsf{eq}}} \ar[d]_{R_{\mathsf{eq}}} & \EqHyp \ar[d]^{T} & \EqpsHyp \ar[r]^-{S_{p, \mathsf{eq}}} \ar[d]_{W_{\mathsf{eq}}} & \EqHyp\ar[d]^{T}\\ \lmo \ar[r]_{M} & \hyp & \shyp \ar[r]_{S} & \hyp  & \pshyp \ar[r]_-{S_p}& \hyp}\]
@@
 
-			Notice that, if $\Sigma$ is algebraic, than such a function exists only if $\mathcal{H}$ is algebraic too. In that case the second diagram commute by default.
+			Notice that, if $\Sigma$ is algebraic, then such a function exists only if $\mathcal{H}$ is algebraic too.
+In that case, since the image of $\lg_{V_{\mathcal{H}}}$ is simply the singleton $\{1\}$, the second diagram commutes by default.
 		\end{rem}
@@
 \begin{minipage}[r]{.15\linewidth}
-	\xymatrix{xy code}
+	\xymatrix@R=8pt{E_{\mathcal{H}} \ar[r]_{l} \ar[d]_{s_{\mathcal{H}}}& O_{\Sigma} \ar[d]^{\ari_\Sigma}\\ V^\star_{\mathcal{H}} \ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}
+	\xymatrix@R=8pt{E_{\mathcal{H}} \ar[r]_{l} \ar[d]_{t_{\mathcal{H}}}& O_{\Sigma} \ar[d]^{\coar_\Sigma}\\ V^\star_{\mathcal{H}} \ar[r]^{\lgh_{V_{\mathcal{H}}}} & \mathbb{N}}
 	\end{minipage}
@@
 
-Let $V_\Sigma\colon \EqHyps\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\Sigma$ the class of morphisms in $\EqHyps$ whose image in $\EqHyp$ is in $\pbc$.
-From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors,cor:eqade}, we can deduce the following.
-
-\begin{prop}\label{prop:lim}Consider the forgetful functor $V_{\Sigma}\colon \EqHyps\to \EqHyp$. Then the following facts hold
+Let $V_\mathcal{G}\colon \EqHyps\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\mathcal{G}$ the class of morphisms in $\EqHyps$ whose image in $\EqHyp$ is in $\pbc$.
+From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors} and from \Cref{cor:eqade}, we can deduce the following.
+
+\begin{prop}\label{prop:lim}Consider the forgetful functor $V_\mathcal{G}\colon \EqHyps\to \EqHyp$. Then the following facts hold
 	\begin{enumerate}
-		\item $\EqHyps$ has all colimits and all connected limits, which are created by $V_{\Sigma}$;
-		\item $\EqHyps$ is $\pbc_\Sigma$-adhesive.
+		\item $\EqHyps$ has all colimits and all connected limits, which are created by $V_\mathcal{G}$;
+		\item $\EqHyps$ is $\pbc_\mathcal{G}$-adhesive.
 	\end{enumerate}
@@
 
-We can now easily define term graphs with equivalence.
-
-\begin{defi}Let $\Sigma$ be an algebraic signature.
-	An object $(\mathcal{H}, l)$ of $\EqHyps$ is a \emph{term graph with equivalence} if $l\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ is a term graph.
-We denote by $\EqTG_{\Sigma}$ the full subcategory of $\EqHyps$ so defined and by $J_{\Sigma}$ the corresponding inclusion functor.
+We can now easily define left-monogamous, pruned ans separated labelled hypergraphs with equivalence.
+
+\begin{defi}Let$\mathcal{G}$ be an hypergraph and $(\mathcal{H},(f,g))$ labelled hypergraph with equivalence.
+We say that $(\mathcal{H},(f,g))$ is a \emph{left-monogamous} (resp.~\emph{separated, pruned}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated, pruned).
+
+	We will denote by $\lmo_{\eq, \mathcal{G}}$, $\shyp_{\eq, \mathcal{G}}$, $\pshyp_{\eq, \mathcal{G}}$ the subcategories of $\hyp_{\eq, \mathcal{G}}$ given by left-monogamous, separated, pruned  and separated labelled hypergraphs with equivalence.
  \end{defi}
 
+ Clearly we can realize $\lmo_{\eq, \mathcal{G}}$, $\shyp_{\eq, \mathcal{G}}$, $\pshyp_{\eq, \mathcal{G}}$ as comma categories.
+
+ \begin{prop}
+ 	Let $M_{\eq}\colon \Eqlmo\to \EqHyp$ and $S_{\eq}\colon \EqsHyp \to \EqHyp$ be the inclusion functors.
+Let, moreover, $\Gamma_{R(\mathcal{G})}\colon 1\to \hyp$ be the constant functor in $R(\mathcal{G})$.
+Then
+ 	\begin{enumerate}
+ 		\item $\lmo_{\eq, \mathcal{G}}$ is equivalent to $\comma{M_\eq}{\Gamma_{R(\mathcal{G})}}$;
+ 		\item $\shyp_{\eq, \mathcal{G}}$ is equivalent to $\comma{S_\eq}{\Gamma_{R(\mathcal{G})}}$; 
+ 		\item $\pshyp_{\mathcal{G}}$ is equivalent to $\pshyp_{\eq}/R(\sp(\pr(\mathcal{G})))$. 
+ 	\end{enumerate}
+ \end{prop}
+
+\begin{defi}We define the following two classes of arrows:
+	\begin{itemize}
+		\item $\pbl_{\mathcal{G}}$ is the class of all arrows in $\lmo_{\eq, \mathcal{G}}$ sent by $M_{\eq, \mathcal{G}}$ to $\pbc_{\mathcal{G}}$;
+		\item $\pbs$ is the class of all arrows in $\pshyp_{\eq, \mathcal{G}}$ sent by the inclusion  to $\pbc_{\mathcal{G}}$.
+	\end{itemize}
+\end{defi}
+
+We can  now use \Cref{thm:slice-functors} to get the following.
+
+\begin{cor}$\lmo_{\eq, \mathcal{G}}$ is $\pbl_{\mathcal{G}}$-adhesive and $\pshyp_{\eq, \mathcal{G}}$ is $\pbs_{\mathcal{G}}$-adhesive
+\end{cor}
+
+\begin{rem}When $\mathcal{G}$ is the hypergraph associated to an algebraic signature $\Sigma$, then left-monogamous labelled hypergraphs with equivalence are exactly the \emph{term graphs with equivalence} of \cite{uovadesive}.
+\end{rem}
+\iffalse 
 \noindent 
@@
 	\end{rem}
+
+	\[	\xymatrix@R=8pt@C=10pt{& \pshyp_\mathcal{G} \ar[dd]_(.7){W_\mathcal{G}}|\hole \ar@/_.2cm/@{_{(}->}[rr]_{S_{p,\mathcal{G}}} \ar@{_{(}->}[dl]_{I_\mathcal{G}} && \phyp_\mathcal{G} \ar[dd]^(.7){V_\mathcal{G}}|\hole \ar@/_.2cm/[ll]^{\sp_\mathcal{G}}\ar@/_.2cm/@{_{(}->}[dr]_(.35){P_\mathcal{G}}\\\shyp_\mathcal{G} \ar@{^{(}->}[rr]^(.35){S_\mathcal{G}} \ar[dd]_{R_\mathcal{G}}&& \lmo_\mathcal{G}  \ar@{^{(}->}[rr]^(.35){M_\mathcal{G}} \ar[dd]_(.25){O_\mathcal{G}}&& \hyp_\mathcal{G} \ar@/_.2cm/[ul]_{\pr_\mathcal{G}} \ar[dd]^{U_\mathcal{G}}\\& \pshyp \ar@/_.2cm/@{_{(}->}[rr]_(.35){S_p}|\hole \ar@{^{(}->}[dl]_{I} && \phyp \ar@/_.2cm/[ll]^(.35){\sp}|\hole\ar@/_.2cm/@{_{(}->}[dr]_(.3){P}\\\shyp \ar@{_{(}->}[rr]^{S} && \lmo  \ar@{_{(}->}[rr]^(.35){M}&& \hyp \ar@/_.2cm/[ul]_{\pr}}\]
 \end{minipage}
@@
 
-\begin{rem}\label{rem:map2}
-	contenuto...
-\end{rem}
+\fi 
 \section{EGGs}
@@
 	\end{enumerate}
+
+	Let $\mathcal{G}$ be an hypergraph.
+For every $e\in E_{\mathcal{G}}$, let $n_e=\lgh_{V_{\mathcal{G}}}(s_{\mathcal{G}}(e))$ and $m_e=\lgh_{V_{\mathcal{G}}}(t_{\mathcal{G}}(e))$.
+Given $1\leq i\leq n_e+m_e$,  we can define $\delta^e_i\colon \mto V_{\mathcal{G}}$ as
+	\[\delta^e_i(0) =\begin{cases}
+		s_{\mathcal{G}}(e)_i & \mbox{if } i\leq n_e\\
+		t_{\mathcal{G}}(e)_{i-n_e} &  \mbox{otherwise}
+	\end{cases}\]
+
+In turn, this allows us to define $\epsilon_{G}\colon V_{\sp(\mathcal{G})}\to V_{\mathcal{G}}$ as the unique one fitting in the diagram below.
+
+	\noindent 
+	\begin{minipage}[l]{.8\linewidth}
+		\setlength{\parindent}{1.5em}
+		Now, for every hyperedge $e\in E_{\mathcal{G}}$ we have
+		\begin{gather*}
+			\epsilon_{\mathcal{G}}^\star(s_{\sp(\mathcal{G})}(e)) = \epsilon_{\mathcal{G}}^\star(\prod_{i=1}^{n_e} \iota_e(\iota^e_{i}(0)))=\prod_{i=1}^{n_e} \epsilon_{\mathcal{G}}(\iota_e(\iota^e_{i}(0)))=\prod_{i=1}^{n_e} \delta^e_i(0) =\prod_{i=1}^{n_e} s_{\mathcal{G}}(e)_i=   s_{\mathcal{G}}(e)\\
+		\epsilon_{\mathcal{G}}^\star(t_{\sp(\mathcal{G})}(e)) = \epsilon_{\mathcal{G}}^\star(\prod_{i=n_e+1}^{n_e + m_e} \iota_e(\iota^e_{i}(0)))=\prod_{i=n_e+1}^{n_e + m_e} \epsilon_{\mathcal{G}}(\iota_e(\iota^e_{i}(0)))=\prod_{n_e+i=1}^{n_e + m_e} \delta^e_i(0) = \prod_{n_e+i=1}^{n_e + m_e}  t_{\mathcal{G}}(e)_i  = t_{\mathcal{G}}(e)
+		\end{gather*} 
+	\end{minipage}
+	\hfill
+	\begin{minipage}[r]{.3\linewidth} \vspace{-.9cm}
+		\xymatrix@R=10pt@C=30pt{1 \ar[r]_{\id{1}} \ar@{>->}[d]^{\iota^e_i}& 1 \ar@{>->}[dd]_{\delta^e_i}\\ V_e \ar@{>->}[d]^{\iota_e}  \\ V_{\sp(\mathcal{G})} \ar@{.>}[r]^-{\epsilon_{\mathcal{G}}} &  V_{\mathcal{G}}}
+	\end{minipage}
+
+	\smallskip 
+	Hence $(\id{E_{\mathcal{G}}}, \epsilon_{G})$ is a morphism $P(\sp(\mathcal{G}))\to \mathcal{G}$.
+Now, let $(f,g)\colon P(\mathcal{H})\to \mathcal{G}$ be a  morphism of pruned hypergraphs with $\mathcal{H}$ separated.
+Given a node $v$ in $V_{\mathcal{H}}$ we know that there exists exactly one $e_v$ such that $v$ occurs in $s_{\mathcal{H}}(e_v)$ or in $t_{\mathcal{H}}(e_v)$.
+Moreover, $v$ occurs exactly once and not in both.
+Let $i_v$ be the index at which it appears.
+We define
+	\[\hat{g}(v):=\begin{cases}
+		\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0)) & \text{if } v \text{ occurs in } s_{\mathcal{H}}(e)\\
+		\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0)) & \text{if } v \text{ occurs in } t_{\mathcal{H}}(e)\\
+	\end{cases}\]
+	Computing we get
+	\begin{gather*}
+		\hat{g}^\star(s_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{n_e} s_{\mathcal{H}}(e)_i)=\prod_{i=1}^{n_e}(\hat{g}(s_{\mathcal{H}}(e)_i))=\prod_{i=1}^{n_e}\iota_{f(e)}( \iota^{f(e)}_i(0))=s_{\sp(\mathcal{G})}(f(e))\\
+		\hat{g}^\star(t_{\mathcal{H}}(e))= \hat{g}^\star(\prod_{i=1}^{m_e} t_{\mathcal{H}}(e)_i)=\prod_{i=1}^{m_e}(\hat{g}(t_{\mathcal{H}}(e)_i))=\prod_{i=1}^{m_e}\iota_{f(e)}( \iota^{f(e)}_{n_e+i}(0))=\prod_{i=n_e + 1}^{n_e + m_e}\iota_{f(e)}( \iota^{f(e)}_{i}(0))=t_{\sp(\mathcal{G})}(f(e))
+	\end{gather*}
+	proving that $(f, \hat{g})\colon \mathcal{H}\to\sp( \mathcal{G})$ is a morphism of $\pshyp$. Notice that	
+	\begin{align*}
+		&\epsilon_\mathcal{G}(\hat{g}(v))=\begin{cases}
+			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{i_v}(0))) & \text{if } v \text{ occurs in } s_{\mathcal{H}}(e_v)\\
+			\epsilon_\mathcal{G}(\iota_{f(e_v)}(\iota^{f(e_v)}_{n_e + i_v}(0))) & \text{if }v \text{ occurs in } t_{\mathcal{H}}(e_v)
+		\end{cases}=	\begin{cases}
+		\delta^{f(e_v)}_{i_v}(0)& \text{if }v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		\delta^{f(e_v)}_{i_v}(0)& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)
+		\end{cases}\\ =&
+		\begin{cases}
+			s_{\mathcal{G}}(f(e_v))_{i_v}& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
+			t_{\mathcal{G}}(f(e_v))_{i_v}& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)
+		\end{cases}= \begin{cases}
+		(g^\star(s_{\mathcal{H}}(e_v)))_{i_v}& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		(g^\star(t_{\mathcal{H}}(e_v)))_{i_v}& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)\\
+		\end{cases}\\=&\begin{cases}
+		g(s_{\mathcal{H}}(e_v)_{i_v})& \text{if } v \text{ occurs in } s_{\mathcal{G}}(e)\\
+		g(t_{\mathcal{H}}(e_v)_{i_v})& \text{if } v \text{ occurs in } t_{\mathcal{G}}(e)\\
+		\end{cases}=g(v)
+	\end{align*}
+and so $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(f, \hat{g})=(f,g)$.
+
+	Now let $(h,k)$ be another morphism $\mathcal{H}\to \sp(\mathcal{G})$ such that $(\id{E_{\mathcal{G}}}, \epsilon_{G})\circ P(h, k)=(f,g)$.
+This entails immediately that $h =f$ and so uniqueness follows from \Cref{rem:mprun}.
 \end{proof}
@@
 
+\iffalse 
 \trm*
@@
 \end{proof}
-
+\fi 
 \subsection{Proofs for \Cref{eggs}}

### 2025-09-08 jlamp/jlamp.tex
minima

@@
 \paragraph{Left-monogamous hypergraphs}\label{par:lm}
-We start by introducing \emph{left-monogamous} hypergraphs \cite{milosavljevic2023string,fritz2023free}, which are the generalization of \emph{term graphs} \cite{corradini2005term,Plu:TGR-ENTCS}.
+We start by introducing \emph{left-monogamous} hypergraphs \cite{milosavljevic2023string,fritz2023free}, which are the generalization of \emph{term graphs} \cite{CorradiniG05,Plu:TGR-ENTCS}.
 
@@
 where $0$ is the unique element of the terminal object $1$.
-\marginpar{ovvero?}
 

### 2025-09-09 jlamp/jlamp.tex
fine

--- 2025-09-08 jlamp/jlamp.tex
@@
 \newcommand{\pbs}{\mathsf{SPb}}
+\newcommand{\epbl}{\mathsf{eLPb}}
+\newcommand{\epbs}{\mathsf{eSPb}}
+
 \newcommand{\pbse}{\mathsf{eSPb}}
@@
 \newcommand{\Dwnarrow}{\Downarrow \hspace{-2pt}}
-\newcommand{\egg}{\mathsf{e}\text{-}\catname{EqHyp}}
+\newcommand{\egg}{\mathsf{e}\text{-}\catname{Hyp}_\eq}
+\newcommand{\eggl}{\mathsf{e}\text{-}\catname{Hyp}_{\eq, \mathcal{G}}}
+\newcommand{\elm}{\mathsf{e}\text{-}\catname{LMO}_\eq}
+\newcommand{\eps}{\mathsf{e}\text{-}\catname{pSep}_\eq}
+\newcommand{\lelm}{\mathsf{e}\text{-}\catname{LMO}_{\eq, \mathcal{G}}}
+\newcommand{\leps}{\mathsf{e}\text{-}\catname{pSep}_{\eq, \mathcal{G}}}
 
@@
 %questo sparirà, serve a me per non diventare scemo
-\setcounter{secnumdepth}{4}
-\setcounter{tocdepth}{4}
-\tableofcontents
+%\setcounter{secnumdepth}{4}
+%\setcounter{tocdepth}{4}
+%\tableofcontents
 
@@
  	Let $M_{\eq}\colon \Eqlmo\to \EqHyp$ and $S_{\eq}\colon \EqsHyp \to \EqHyp$ be the inclusion functors.
-Let, moreover, $\Gamma_{R(\mathcal{G})}\colon 1\to \hyp$ be the constant functor in $R(\mathcal{G})$.
+Let, moreover, $\Gamma_{R(\mathcal{G})}\colon 1\to \EqHyp$ be the constant functor in $R(\mathcal{G})$.
 Then
@@
 		\item $\pbl_{\mathcal{G}}$ is the class of all arrows in $\lmo_{\eq, \mathcal{G}}$ sent by $M_{\eq, \mathcal{G}}$ to $\pbc_{\mathcal{G}}$;
-		\item $\pbs$ is the class of all arrows in $\pshyp_{\eq, \mathcal{G}}$ sent by the inclusion  to $\pbc_{\mathcal{G}}$.
+		\item $\pbs_{\mathcal{G}}$ is the class of all arrows in $\pshyp_{\eq, \mathcal{G}}$ sent by the inclusion  to $\pbc_{\mathcal{G}}$.
 	\end{itemize}
@@
 \label{eggs}
-The previous section proved some adhesivity property for the categories $\EqHyp$ and $\EqTG_{\Sigma}$. We extend these results to
+The previous section proved some adhesivity property for the categories $\EqHyp$, $\Eqlmo$,  $\EqpsHyp$ and for their labelled variants. We extend these results to
 encompass equivalence classes which are closed under the target arrow, i.e.~under operator composition for term graphs, thus precisely capturing EGGs.
@@
 
-	We will denote by $\egg$ the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and by $I\colon \egg \to \EqHyp$ the associated inclusion functor.
+	We will denote by $\egg$ the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and by $E\colon \egg \to \EqHyp$ the associated inclusion functor.
 \end{defi}
@@
 \begin{exa}
-	Consider the hypergraph $\mathcal{G}$ of \Cref{exa_2} and consider as quotient the identity $\id{V_\mathcal{G}}\colon V_\mathcal{G}\colon \to\mathcal{G}$.
+	Consider the hypergraph $\mathcal{G}$ of \Cref{exa_2} and take as quotient the identity $\id{V_\mathcal{G}}\colon V_\mathcal{G}\colon \to\mathcal{G}$.
 Then the kernel pair of $\id{V^\star_\mathcal{G}} \circ s$ concide with the kernel pair of $s$, which is empty.
@@
 \end{exa}
+
 A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proofs are in \Cref{proof:elim}.
@@
 \begin{restatable}{lem}{elim}\label{lem:elim}
-	$\egg$ has all limits and $I$ creates them.
+	$\egg$ has all limits and $E$ creates them.
 \end{restatable}
@@
 \begin{cor}\label{cor:ereg}
-	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $I(h)$ is a regular mono in $\hyp$. 
+	If an arrow $h: \mathcal{G \to H}$ in $\egg$ is a regular mono in $\egg$ then $E(h)$ is a regular mono in $\hyp$. 
 \end{cor}
@@
 \begin{minipage}[r]{.15\linewidth}
-	\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]_{h}\ar@{>->}[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]^{z}&\mathcal{P}}
-\end{minipage}
-
-Let now $\pbe$ be the class of arrows in $\egg$ that are sent to $\pbc$ by $I$.
+	\xymatrix@R=10pt{\mathcal{G}_1 \ar[r]_{h}\ar@{>->}[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]^{z}&\mathcal{P}}
+\end{minipage}
+
+Let now $\pbe$ be the class of arrows in $\egg$ that are sent to $\pbc$ by $E$.
 By definition and \Cref{lem:pbmono} we have that such class is closed under composition and decomposition, it contains all isomorphisms and it is stable under pullbacks.
@@
 
-\subsection{E-term graphs, a.k.a. EGGs}
-
-We now turn our attention to the labelled context.
-
-\begin{defi} We say that an object $(\mathcal{H}, l)$ of $\EqHyps$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
-We define the category $\egg_\Sigma$ as the full subcategory of $\EqHyps$ given by labelled e-hypergraphs.
-We denote by $Z_\Sigma$ the corresponding inclusion functor .
+As in the previous section, we can focus ourselves to two subcategories of $\egg$.
+
+\begin{defi}We will define $\elm$, $\eps$ as the full subcategories of $\egg$ given by those e-hypergraphs which are, respectively, left-monogamous and pruned and separated.
+We will denote by $M_{\mathsf{e}}$ and by $S_{\mathsf{e}}$ the corresponding functors.
 \end{defi}
 
-To prove some adhesivity property of $\egg_\Sigma$, we begin with the following elementary, yet useful observation.
-
-\begin{rem}\label{rem:algegg}
-	Given a signature $\Sigma = (O_\Sigma, \ari_\Sigma)$,
-	the hypergraph 
-	$R(\mathcal{G}^\Sigma) = (O_\Sigma, 1, 1, \ari_\Sigma, \gamma_1, \id{1})$
-	is an object of $\egg$.
-	Indeed, under the identification of $1^\star$ with $\mathbb{N}$, the kernel $(S, \pi_1, \pi_2)$  of $\id{\mathbb{N}} \circ \ari_\Sigma$, is given by
-	$S:=\{(o_1, o_2)\in O_\Sigma \times O_\Sigma \mid \ari_\Sigma(o_1)=\ari_\Sigma(o_2)\}$
-	equipped with the two projections.
-On the other hand, both $\id{\mathbb{N}} \circ \gamma_1 \circ \pi_1$ and $\id{\mathbb{N}}\circ \gamma_1 \circ \pi_2$ are the function $O_\Sigma \to \mathbb{N}$ constant in $1$.
-\end{rem}
-
-\Cref{rem:algegg} now implies at once the following result.
+Let $\epbl$ and $\epbs$ be the classes of arrows in  $\elm$, $\eps$ which lies, respectively in $\pbl$ and $\pbs$.
+By Lemmas \ref{lem:equ}, \ref{lem:coequ} and \Cref{cor:pbe} we obtain immediately the following result.
+
+\begin{cor}
+	$\elm$ is $\epbl$-adhesive, while $\eps$ is $\epbs$-adhesive.
+\end{cor}
+
+\subsection{Labelled e-hypergraphs}\label{sec:sepegg}
+
+Finally, we can turn our attention to the labelled context.
+
+\begin{defi} Let $\mathcal{G}$ be an hypergraph.
+We say that an object $(\mathcal{H}, (f,g))$ of $\EqHyps$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
+We define the category $\eggl$ as the full subcategory of $\EqHyps$ given by labelled e-hypergraphs.
+We denote by $E_\mathcal{G}$ the corresponding inclusion functor .
+\end{defi}
+
+From the definitions, we get at once the follosing result.
 
 \begin{prop}\label{prop:varie}
-	Let $\Sigma$ be an algebraic signature. Then the following facts hold
+	Let $\mathcal{G}$ be an hypergraph and $\Gamma_{R(\mathcal{G})}$ the costant functor in $R(\mathcal{G})$. Then the following facts hold
 	\begin{enumerate}
-		\item $\egg_\Sigma$ is equivalent to $\egg/R(\mathcal{G}^\Sigma)$;
-		\item there exists a functor $W_\Sigma \colon \egg_\Sigma\to \egg$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
+		\item $\eggl$ is equivalent to $\comma{E}/\Gamma_{R(\mathcal{G})}$;
+		\item there exists a functor $W_\mathcal{G}\colon \eggl\to \egg$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
 	\end{enumerate}
@@
 
-Let $\pbe_\Sigma$ be the class of morphisms in $\egg_\Sigma$ whose image in $\egg$ lies in $\pbe$.
-Notice that $\pbe_\Sigma$ is also the class of arrows whose image through $Z_\Sigma$ is in $\pbc_\Sigma$.
+Let $\pbe_\mathcal{G}$ be the class of morphisms in $\eggl$ whose image in $\egg$ lies in $\pbe$.
+Notice that $\pbe_\mathcal{G}$ is also the class of arrows whose image through $E_\mathcal{G}$ is in $\pbc_\mathcal{G}$.
 %
@@
 \begin{cor}\label{cor:eggade1}
-	$\egg_\Sigma$ is $\pbe_\Sigma$-adhesive.
+	$\eggl$ is $\pbe_\mathcal{G}$-adhesive.
 \end{cor}
 
+Now, let $\lelm$ and $\leps$ be the full subcategories of $\eggl$ given by the objects whose underlying hypergraphs with equivalence are, respectively, left-monogamous and pruned and separated.
+
+\begin{rem}
+When $\mathcal{G}$ is the hypergraph associated to an algebraic signature, the object of  $\lelm$ coincides with what in \cite{uovadesive} are called \emph{e-termgraphs with equivalence}. 
+\end{rem}
+
+\begin{lem}Let $\mathcal{G}$ be an hypergraph and $\Gamma_{R(\mathcal{G})}$ the costant functor in $R(\mathcal{G})$. 
+	\begin{enumerate}
+		\item $\lelm$ is equivalent to $\comma{E\circ M_{\mathsf{e}}}{\Gamma_{R(\mathcal{G})}}$
+		\item $\leps$ is equivalent to $\comma{E\circ S_{\mathsf{e}}}{\Gamma_{R(\mathcal{G})}}$
+	\end{enumerate}
+\end{lem}
+
+Define $\epbl_{\mathcal{G}}$ and $\epbs_{\mathcal{G}}$ as the classes of arrows whose underlying morphisms are in $\epbl$ or in $\epbs$. The following result now follows at once.
+
+\begin{cor}
+	$\lelm$ is $\epbl_{\mathcal{G}}$-adhesive, while $\leps$ is $\epbs_{\mathcal{G}}$-adhesive.
+\end{cor}
+
+\iffalse 
 We turn now to term graphs with equivalence.
@@
 \begin{rem}
-	By definition we also have an inclusion functor $Y_\Sigma\colon \eg\to \egg_\Sigma$.
+	By definition we also have an inclusion functor $Y_\Sigma\colon \eg\to {\egg}_\Sigma$.
 \end{rem}
@@
 \end{minipage}\hfill
-\begin{minipage}[r]{.20\linewidth}
+\iffalse \begin{minipage}[r]{.20\linewidth}
 	\xymatrix@R=10pt@C=20pt{\eg \ar@{^{(}->}[r]^-{Y_\Sigma} \ar@{^{(}->}[d]_{K_\Sigma} & \egg_\Sigma \ar@{^{(}->}[d]^{Z_\Sigma} \ar[r]^{W_\Sigma}& \egg \ar@{^{(}->}[d]^{I}\\ \EqTG_{\Sigma} \ar@{^{(}->}[r]^-{J_\Sigma}\ar[d]_{S_\Sigma}& \EqHyps \ar[r]^-{V_\Sigma} \ar[d]_{T_\Sigma}& \EqHyp \ar[d]^{T}\\ \tg \ar@{^{(}->}[r]^-{I_\Sigma}& \hyp_{\Sigma} \ar[r]^-{U_\Sigma}  &\hyp}
 \end{minipage}
-
+\fi 
 We can now prove our last three results. The reader can find the proof in \Cref{proof:tlim}.
@@
 \end{cor}
-
-\subsubsection{BOH}\label{sec:sepegg}
-
-qui vanno gli egg fatti con i separati
-
-\subsubsection{BOH}\label{sec:lmegg}
-
-qui vanno gli egg fatti con i left monogamous (probabilmente sussume la 5.2)
+\fi
 
@@
 \noindent
-\begin{minipage}[l]{.8\linewidth}
+\begin{minipage}[l]{.85\linewidth}
 \begin{lem}\label{lem:po_set}
@@
 \begin{minipage}[r]{.23\linewidth}
-\xymatrix@R=15pt@C=30pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}
+\xymatrix@R=15pt@C=30pt{A \ar@{>->}[r]_{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]^{n} & D}
 \end{minipage}
@@
 \noindent 
-\parbox{11.5cm}{\hspace{15pt} Extensivity means that given a family of objects $\{X_{i}\}_{i\in I}$ and a family of commuting squares as the one on the right, where $j_i$ is a  coprojection, then all the squares are pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.}\hfill
-\parbox{2cm}{\xymatrix@R=15pt{Z_i \ar[r]_{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar@{>->}[r]^{j_i} & X}}
-
-\noindent
-\parbox{11.5cm}{
+\begin{minipage}[l]{.83\linewidth}
+	\setlength{\parindent}{1.5em}
+Extensivity means that given a family of objects $\{X_{i}\}_{i\in I}$ and a family of commuting squares as the one on the right, where $j_i$ is a  coprojection, then all the squares are pullbacks if and only if $(Z, \{k_i\}_{i\in I})$ is a coproduct.
+\end{minipage}\hfill
+\begin{minipage}[r]{.2\linewidth}
+\xymatrix@R=10pt{Z_i \ar[r]_{k_i} \ar[d]_{f_i} & Z\ar[d]^{f} \\ X_i \ar@{>->}[r]^{j_i} & X}
+\end{minipage}
+
+\noindent
+\begin{minipage}[l]{.83\linewidth}
+	\setlength{\parindent}{1.5em}
 \begin{rem}\label{rem:disj}
@@
 To see this, let $\{X, \{j_i\}_{i\in I}\}$ be the coproduct of the family $\{X_i\}_{i\in I}$ and $k$ an element of $I$.
-Then  $(X_k, \{t_i\}_{i\in I})$
-such that $t_i = \id{X_k}$ if $i=k$, and $?_{X_k}$ otherwise,
-	%\end{cases}\]	
-	%with
-	%\[t_i=\begin{cases}
-	%	\id{X_k} & i=k\\?_{X_k} & i\neq k
-	%\end{cases}\]
+Consider $(X_k, \{t_i\}_{i\in I})$, where:
+	\[X_i=\begin{cases}
+		X_k & i=k\\\emptyset  & i\neq k
+	\end{cases} \qquad  t_i=\begin{cases}
+		\id{X_k} & i=k\\?_{X_k} & i\neq k
+	\end{cases}\]
 		is a coproduct and so the squares on the right are pullbacks.
-\end{rem}}\hfill\parbox{2cm}{\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]_{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]^{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]_{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]^{j_k} & X}}
-
-In particular, the previous remark yields at once the following fact.
-
-\noindent 
-\parbox{11.5cm}{\begin{prop}\label{prop:isempty}
+	\end{rem}
+\end{minipage}\hfill 
+\begin{minipage}[r]{.2\linewidth}
+	\xymatrix@R=15pt{\emptyset \ar@{>->}[d]_{?_{X_i}} \ar@{>->}[r]^{?_{X_k}}& X_k \ar@{>->}[d]^{j_k} \\ X_i \ar@{>->}[r]_{j_i} & X} \xymatrix@R=15pt{X_k \ar[r]^{\id{X}} \ar[d]_{\id{X}}& X_k \ar@{>->}[d]^{j_k}\\X_k \ar@{>->}[r]_{j_k} & X}
+\end{minipage}
+\parbox{11.5cm}{}\hfill\parbox{2cm}{}
+
+\noindent 
+\begin{minipage}[l]{.83\linewidth}
+\begin{prop}\label{prop:isempty}
 	Suppose that the square on the right is a pullback.
@@
 If there exist two  arrows $t_1\colon T\to E$ and $t_2\colon T\to X$ such that $g\circ \iota\circ t_1= f\circ t_2$ then $T$ is empty.
-\end{prop}}\hfill \parbox{2cm}{\vspace{-.5cm}\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}}
+\end{prop}
+\end{minipage}
+\hfill
+\begin{minipage}[r]{.2\linewidth}
+\xymatrix@R=15pt{P \ar[r]_{p_1} \ar[d]_{p_2}& Y \ar[d]^{g}\\X \ar[r]^{f}& Z}
+\end{minipage}
 \begin{proof}
 	By the universal property of pullbacks we get an arrow $t\colon T\to P$ such that
+
+	\noindent
+	\begin{minipage}[l]{.3\linewidth}
+	\xymatrix{T \ar@{.>}[r]^{s}\ar@{>>}[dr]_{\pi} \ar@/^.4cm/[rr]^{t_1} & \emptyset \ar@{>->}[r]_{?_{E}} \ar@{>->}[d]_{?_I}& E \ar@{>->}[d]^{\iota}\\ & I \ar@{>->}[r]^{i} & Y}
+	\end{minipage}\hfill
+	\begin{minipage}[r]{.78\linewidth}	\setlength{\parindent}{1.5em}
 		\[p_1\circ t=\iota \circ t_1 \qquad p_2\circ t=t_2\]
-	\parbox{2cm}{\xymatrix{T \ar@{.>}[r]^{s}\ar@{>>}[dr]_{\pi} \ar@/^.4cm/[rr]^{t_1} & \emptyset \ar@{>->}[r]_{?_{E}} \ar@{>->}[d]_{?_I}& E \ar@{>->}[d]^{\iota}\\ & I \ar@{>->}[r]_{i} & Y}}\hfill \parbox{10.5cm}{Let $i\colon I\mto Y$ be the inclusion of the image of $p_1$, so that we have also an epi $q\colon P\eto I$.
+
+Let $i\colon I\mto Y$ be the inclusion of the image of $p_1$, so that we have also an epi $q\colon P\eto I$.
 By definition of complement $(Y, \{i, \iota\})$ is a coproduct, thus by  \Cref{rem:disj} the inner square in the diagram on the left is a pullback and we get a dotted arrow $s\colon T\to \emptyset$ filling the diagram.
 But a set with an arrow towards the empty set must be empty and we conclude.
-\qedhere }
+\qedhere
+	\end{minipage}
 \end{proof}
@@
 This, in turn, entails that $m'$, being the pullback of $m$, is mono, and so $n'$ is injective too because in $\Set$, as in any adhesive category, monomorphisms are stable under pushouts.
-\vspace{.1cm}
-
-	\noindent 
-	\parbox{11.5cm}{\hspace{15pt}
+
+	\noindent
+	\begin{minipage}[l]{.83\linewidth}
+			\setlength{\parindent}{1.5em}
 	Let $\iota' \colon E'\mto C'$ and $\iota\colon E\to C$ be the inclusions of the complement of the images of of $m'$ and $m$ respectively .
-By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ is a coproduct.
-}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}
-
-\vspace{.1cm}
-
-	\noindent
-	\parbox{10.5cm}{\hspace{15pt}We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.To see this, let $e$ be in $E'$ and suppose that  $c(\iota'(e))=m(x)$ for some $x\in A$.
+By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ is a coproduct.	\end{minipage}
+	\hfill
+	\begin{minipage}[r]{.2\linewidth}
+\xymatrix@R=10pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}
+	\end{minipage}
+
+	\noindent
+	\begin{minipage}[l]{.75\linewidth}
+	\setlength{\parindent}{1.5em}
+We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.
+To see this, let $e$ be in $E'$ and suppose that  $c(\iota'(e))=m(x)$ for some $x\in A$.
 Then we can apply the  universal property of pullbacks to build the dotted arrow $v$ in the diagram aside, where $v_0$ and $v_1$ are the arrows picking $x$ and $\iota'(e)$, respectively.
-But then $e$ must belong to the image of $m'$, which is a contradiction.}\hfill  \parbox{4cm}{\xymatrix@R=15pt{1 \ar[dr]_{v_0}  \ar@/^.3cm/[rr]^{v_1} \ar@{.>}[r]_{v}& A' \ar[d]_{a} \ar@{>->}[r]_{m'} & C' \ar[d]^{c}\\& A  \ar@{>->}[r]^{m}& C}}
-
+But then $e$ must belong to the image of $m'$, which is a contradiction.
+\end{minipage}\hfill 
+\begin{minipage}[r]{.35\linewidth}
+	\xymatrix@R=15pt{1 \ar[dr]_{v_0}  \ar@/^.3cm/[rr]^{v_1} \ar@{.>}[r]_{v}& A' \ar[d]_{a} \ar@{>->}[r]_{m'} & C' \ar[d]^{c}\\& A  \ar@{>->}[r]^{m}& C}
+\end{minipage}
 	\begin{enumerate}
-		\item Consider two arrows $t_1\colon T\to D' $ and $t_2\colon T\to B$ such that $d\circ t_1=n\circ t_2$. By extensivity
-
-		\noindent\parbox{9.5cm}{ of $\Set$, we already know that $(T, \{l_i\}_{i=0}^1)$ is a coproduct, where $l_i\colon T_i\mto T$ are defined by the diagram aside, whose two halves are pullbacks.
-}\hfill\parbox{4cm}{\xymatrix@R=15pt{T_0 \ar@{>->}[r]_{l_0} \ar[d]_{h_0} & T \ar[d]^{t_1} & T_1 \ar@{>->}[l]^{l_1} \ar[d]^{h_1}\\ E' \ar@{>->}[r]^{g'\circ \iota'} & D' & B' \ar@{>->}[l]_{n'}}}
+		\begin{minipage}[l]{.75\linewidth}
+			\setlength{\parindent}{1.5em}
+			\item Consider two arrows $t_1\colon T\to D' $ and $t_2\colon T\to B$ such that $d\circ t_1=n\circ t_2$.
+By extensivity of $\Set$, we already know that $(T, \{l_i\}_{i=0}^1)$ is a coproduct, where $l_i\colon T_i\mto T$ are defined by the diagram aside, whose two halves are pullbacks.
+	\end{minipage}
+			\hfill 
+			\begin{minipage}[r]{.25\linewidth}
+				\xymatrix@R=15pt{T_0 \ar@{>->}[r]_{l_0} \ar[d]_{h_0} & T \ar[d]^{t_1} & T_1 \ar@{>->}[l]^{l_1} \ar[d]^{h_1}\\ E' \ar@{>->}[r]^{g'\circ \iota'} & D' & B' \ar@{>->}[l]_{n'}}
+			\end{minipage}
 
@@
 \noindent
-\parbox{3cm}{\xymatrix@R=15pt{ K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & C' \ar[r]_{c} & C }}\hfill\parbox{9.5cm}{By \Cref{lem:po_set} $g\circ \iota$ is a monomorphism, thus $w\circ p_3=w\circ q_3$ and therefore
+\begin{minipage}[l]{.3\linewidth}
+	\xymatrix@R=10pt{ K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\E' \ar[dr]_{\iota'}&K_c \ar[r]_{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & C' \ar[r]_{c} & C }
+\end{minipage}\hfill
+\begin{minipage}[r]{.7\linewidth}
+	By \Cref{lem:po_set} $g\circ \iota$ is a monomorphism, thus $w\circ p_3=w\circ q_3$ and therefore
 	\[c\circ \iota'\circ p_3=\iota\circ w\circ p_3=\iota \circ w\circ q_3=c\circ \iota'\circ q_3\]
-Thus we get the dotted $\phi_3\colon K_3\to K_c$ in the diagram aside.}
+	Thus we get the dotted $\phi_3\colon K_3\to K_c$ in the diagram aside.
+\end{minipage}
 
@@
 	\end{align*}
-
-	\vspace{.1cm}
-	\noindent 
-	\parbox{9.5cm}{ \vspace{-.8cm}\hspace{15pt}
+\vspace{-1cm}
+
+	\noindent 
+	\begin{minipage}[l]{.7\linewidth}
 	Thus for each $d$ in $\D$, there exists an arrow $a_d:U\to U_i$ making the diagram on the right commutative.
-Then we have
+	Then we have:
 	\begin{align*}
@@
 		=& q_d^\star \circ t_d \circ \pi_E^d \circ u_2 = q_d^\star \circ (\pi_V^d)^\star \circ t \circ u_2 = l_d^\star \circ m^\star \circ q^\star \circ t \circ u_2
-\end{align*}}\hfill \parbox{4cm}{\vspace{-1cm}	\xymatrix@R=20pt{
+	\end{align*}
+	\end{minipage}
+\hfill
+\begin{minipage}[r]{.3\linewidth}
+\xymatrix@R=20pt{
 	U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_d} & A \ar[dr]^{\pi_E^d} & \\
@@
 	& A_i  \ar[r]_{q_d^\star \circ s_d}& Q_d^\star
-	}}
+}
+\end{minipage}
 
@@
 
+\noindent
+\begin{minipage}[l]{.7\linewidth}
 \begin{rem}\label{rem:kleene}
-	Let $\delta_1\colon 1\to \mathbb{N}$ be the arrow which picks $1\in \mathbb{N}$. Consider the
-
-	\noindent
-	\parbox{11.5cm}{ inclusion $v_1\colon X\to X^\star $  defined by the first point of \Cref{prop:fact}.
-By extensivity we know that the square on the right is a pullback.}\hfill \parbox{4cm}{\vspace{-.5cm}\xymatrix@R=15pt{X \ar[r]_{!_{X}} \ar[d]_{!_{X}}& 1\ar[d]^{\delta_1} \\1 \ar[r]^{\lgh_{X}} & \mathbb{N}} }
-
-	\noindent 
-	\parbox{4cm}{\vspace{-.2cm} \xymatrix@C=15pt@R=1pt{&X\ar[dd]|\hole_(.65){!_{X}}\ar@{->}[rr]^{!_X} \ar@{>}[dl]_{f} && 1 \ar[dd]^{\delta_1} \ar[dl]^{\id{1}} \\ Y  \ar[dd]_{!_Y}\ar@{>}[rr]^(.7){!_Y} & & 1 \ar[dd]_(.3){\delta_1}\\&X^\star\ar@{>->}[rr]|(.53)\hole^(.70){\lgh_{X}} \ar@{>->}[dl]_{f^\star} && \mathbb{N} \ar[dl]^{\id{N}} \\Y^\star \ar@{>->}[rr]_{\lgh_{Y}} & & \mathbb{N}}}\hfill \parbox{9.5cm}{\vspace{-.3cm}\hspace{15pt}Let now $f\colon X\to Y$ be an arrow.
-Then we can build the cube aside which, by what we have just observed above, has pullbacks as back, front and right faces.
-Thus, by \Cref{lem:pb1} its left face is a pullback too.}
-
+	Let $\delta_1\colon 1\to \mathbb{N}$ be the arrow which picks $1\in \mathbb{N}$.
+Let $f\colon X\to Y$ be an arrow and consider theinclusion $v_1\colon X\to X^\star $  defined by the first point of \Cref{prop:fact}.
+Then we can build the cube aside which, by extensivity, has pullbacks as back, front and right faces.
+Thus, by \Cref{lem:pb1} its left face is a pullback too.
 	\end{rem}
-
-\noindent
-\parbox{11.5cm}{
-\epo*}\hfill 
-\parbox{4cm}{\xymatrix@R=15pt{\mathcal{G}_1 \ar[r]^{h}\ar[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]_{z}&\mathcal{P}}}
+\end{minipage}
+\hfill
+\begin{minipage}[r]{.45\linewidth}
+\xymatrix@C=15pt@R=5pt{&X\ar[dd]|\hole_(.65){!_{X}}\ar@{->}[rr]_{!_X} \ar@{>}[dl]_{f} && 1 \ar[dd]^{v_1} \ar[dl]^{\id{1}} \\ Y  \ar[dd]_{!_Y}\ar@{>}[rr]^(.7){!_Y} & & 1 \ar[dd]_(.3){\delta_1}\\&X^\star\ar@{>->}[rr]|(.53)\hole^(.70){\lgh_{X}} \ar@{>->}[dl]_{f^\star} && \mathbb{N} \ar[dl]^{\id{N}} \\Y^\star \ar@{>->}[rr]^(.7){\lgh_{Y}} & & \mathbb{N}}
+\end{minipage}
+
+\noindent
+\begin{minipage}[l]{.83\linewidth}
+\epo*
+\end{minipage}
+\hfill 
+\begin{minipage}[r]{.15\linewidth}
+	\xymatrix@R=10pt{\mathcal{G}_1 \ar[r]_{h}\ar@{>->}[d]_{m}&\mathcal{G}_2\ar[d]^{n}\\\mathcal{G}_3\ar[r]^{z}&\mathcal{P}}
+\end{minipage}
 \begin{proof}\label{proof:epo}
@@
 
-	\noindent
-	\parbox{10cm}{\hspace{15pt}Consider now the cube on the right.
-By hypothesis and \Cref{rem:kleene} its left face is a pullback, moreover its bottom face, while not a pushout it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.}\hfill \parbox{3cm}{\xymatrix@C=10pt@R=2pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar@{>->}[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar@{>.>}[dl]_(.6){n_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){z_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{Q_1^\star}\ar[rr]|\hole^(.65){h_Q^\star}\ar@{>->}[dl]_{m_Q^\star} && {Q_2^\star} \ar@{>->}[dl]^{n_Q^\star} \\{Q_3^\star} \ar[rr]_{z_Q^\star} & & Q^\star}}
-
-	\noindent
-	\parbox{2cm}{\vspace{-.25cm}\xymatrix@R=15pt{K_1\ar[r]_{k_{h_E}}\ar@{>->}[d]_{k_{m_E}}&K_2\ar@{>->}[d]^{k_{n_E}}\\K_3\ar[r]^{k_{z_E}}&U}}
-\hfill \parbox{11.5cm}{ \vspace{-.25cm}\hspace{15pt}By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout.
-Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout.}
-		By computing we obtain
+	\vspace{-.3cm}
+	\noindent
+	\begin{minipage}[l]{.7\linewidth}
+			\setlength{\parindent}{1.5em}
+		Consider now the cube on the right.
+By hypothesis and \Cref{rem:kleene} its left face is a pullback, moreover its bottom face, while not a pushout it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.
+	\end{minipage}\hfill 
+	\begin{minipage}[r]{.4\linewidth}
+	\xymatrix@C=10pt@R=2pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar@{>->}[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar@{>.>}[dl]_(.6){n_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){z_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{Q_1^\star}\ar[rr]|\hole^(.65){h_Q^\star}\ar@{>->}[dl]_{m_Q^\star} && {Q_2^\star} \ar@{>->}[dl]^{n_Q^\star} \\{Q_3^\star} \ar[rr]^(.65){z_Q^\star} & & Q^\star}	\end{minipage}
+
+	\noindent
+	\begin{minipage}[l]{.2\linewidth}
+		\xymatrix@R=15pt{K_1\ar[r]_{k_{h_E}}\ar@{>->}[d]_{k_{m_E}}&K_2\ar@{>->}[d]^{k_{n_E}}\\K_3\ar[r]^{k_{z_E}}&U}
+	\end{minipage}\hfill
+	\begin{minipage}[r]{.8\linewidth}
+			\setlength{\parindent}{1.5em}
+			By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout. Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout. 
+			By computing we obtain:
+	\end{minipage}
+\vspace{-.3cm}
 	\begin{align*}
@@
 
+\iffalse 
 \limt*

### 2025-09-09 jlamp/jlamp.tex
minima

@@
 
-Having proved stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
+Having proved the stability of $\pbc$-pushouts, we now turn to prove that they are Van Kampen with respect to regular monos.
 %
@@
 \begin{rem}\label{rem:obv1}
-By definition, there exist functors $O_{\eq}$, $R_{\eq}$ and $W_{\eq}$ as in the diagrams below, where the horizontal arrows are full and faithful inclusions.
+By definition, there exist functors $O_{\eq}$, $R_{\eq}$ and $W_{\eq}$ as in the diagrams below, where the horizontal arrows are full and faithful inclusions
 \[\xymatrix{\Eqlmo \ar[r]^-{M_{\mathsf{eq}}} \ar[d]_{O_{\mathsf{eq}}}& \EqHyp\ar[d]^{T} & \EqsHyp \ar[r]^-{S_{\mathsf{eq}}} \ar[d]_{R_{\mathsf{eq}}} & \EqHyp \ar[d]^{T} & \EqpsHyp \ar[r]^-{S_{p, \mathsf{eq}}} \ar[d]_{W_{\mathsf{eq}}} & \EqHyp\ar[d]^{T}\\ \lmo \ar[r]_{M} & \hyp & \shyp \ar[r]_{S} & \hyp  & \pshyp \ar[r]_-{S_p}& \hyp}\]
@@
 
-\begin{restatable}{lem}{equ}\label{lem:equ} The following are true:
+\begin{restatable}{lem}{equ}\label{lem:equ} The following facts hold
 	\begin{enumerate}
@@
 \begin{restatable}{lem}{coequ}\label{lem:coequ}
- The following are true:
+ The following facts hold
 \begin{enumerate}
-	\item 	$\Eqlmo$ is closed in $\EqHyp$ under pushouts along morphism whose image through $T$ is downward-closed.
+	\item 	$\Eqlmo$ is closed in $\EqHyp$ under pushouts along morphisms whose image through $T$ is downward-closed.
 	\item $\EqpsHyp$ is closed in $\EqHyp$ under colimits.
@@
 
-\begin{defi}We define the following two classes of arrows:
+\begin{defi}We define two classes of arrows
 \begin{itemize}
@@
 
-We are now going to generalize the work done in the previous section equipping term graphs with equivalence relation. First of all we need a notion of labelling for $\EqHyp$.
+We are now going to generalize the work done in the previous sections equipping term graphs with an equivalence relation. First of all we need a notion of labelling for $\EqHyp$.
 
@@
 	Let $\mathcal{G}$ be an hypergraph, a \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, (f,g))$ where $\mathcal{H}$ is an object of $\EqHyp$ and $(f,g)$ a morphism $T(\mathcal{H})\to \mathcal{G}$ of $\hyp$.
-A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, (f,g))$ and $(\mathcal{H}', (h,k))$ is an arrow $(a,b, c)\colon \mathcal{H}\to \mathcal{H}'$ such that:
-	\[h\circ a = f \qquad k\circ b = g \].
-
+A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, (f,g))$ and $(\mathcal{H}', (h,k))$ is an arrow $(a,b, c)\colon \mathcal{H}\to \mathcal{H}'$ such that $h\circ a = f$ and $k\circ b = g$.
+%
 	We denote the resulting category by $\EqHyps$.
@@
 Let $V_\mathcal{G}\colon \EqHyps\to \EqHyp$ be the functor forgetting the labelling and $\pbc_\mathcal{G}$ the class of morphisms in $\EqHyps$ whose image in $\EqHyp$ is in $\pbc$.
-From \Cref{prop:eqhyp_complete,cor:pbapp}, the second point of \Cref{thm:slice-functors} and from \Cref{cor:eqade}, we can deduce the following.
+From \Cref{prop:eqhyp_complete} and \Cref{cor:pbapp}, the second point of \Cref{thm:slice-functors} and from \Cref{cor:eqade}, we can deduce the following.
 
@@
 
-\begin{defi}Let$\mathcal{G}$ be an hypergraph and $(\mathcal{H},(f,g))$ labelled hypergraph with equivalence.
+\begin{defi}Let$\mathcal{G}$ be an hypergraph and $(\mathcal{H},(f,g))$ a labelled hypergraph with equivalence.
 We say that $(\mathcal{H},(f,g))$ is a \emph{left-monogamous} (resp.~\emph{separated, pruned}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated, pruned).
@@
  	Let $M_{\eq}\colon \Eqlmo\to \EqHyp$ and $S_{\eq}\colon \EqsHyp \to \EqHyp$ be the inclusion functors.
-Let, moreover, $\Gamma_{R(\mathcal{G})}\colon 1\to \EqHyp$ be the constant functor in $R(\mathcal{G})$.
+Moreover, let $\Gamma_{R(\mathcal{G})}\colon 1\to \EqHyp$ be the constant functor in $R(\mathcal{G})$.
 Then
@@
 
-\begin{defi}We define the following two classes of arrows:
+\begin{defi}We define two classes of arrows
 	\begin{itemize}

### 2025-09-09 jlamp/jlamp.tex
minima

@@
 \begin{prop}
-Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Let, moreover, $\Gamma_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then
+Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Moreover, let $\Gamma_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then
 \begin{enumerate}
@@
 \begin{prop}\label{prop:slice}
-$\EqHyps$ is equivalent to $\EqHyp/R(\mathcal{G})$.
+$\EqHyps$ is equivalent to $\EqHyp \downarrow R(\mathcal{G})$.
 \end{prop}
@@
 Let now $\pbe$ be the class of arrows in $\egg$ that are sent to $\pbc$ by $E$.
-By definition and \Cref{lem:pbmono} we have that such class is closed under composition and decomposition, it contains all isomorphisms and it is stable under pullbacks.
+By definition and \Cref{lem:pbmono}, we have that such class is closed under composition and decomposition, it contains all isomorphisms and it is stable under pullbacks.
 Using \Cref{lem:pbmono} and \Cref{lem:epo} we can further deduce that it is stable under pushouts.
@@
 
-Let $\epbl$ and $\epbs$ be the classes of arrows in  $\elm$, $\eps$ which lies, respectively in $\pbl$ and $\pbs$.
+Let $\epbl$ and $\epbs$ be the classes of arrows in  $\elm$ and $\eps$ lying in $\pbl$ and $\pbs$, respectively.
 By Lemmas \ref{lem:equ}, \ref{lem:coequ} and \Cref{cor:pbe} we obtain immediately the following result.
@@
 \begin{cor}
-	$\elm$ is $\epbl$-adhesive, while $\eps$ is $\epbs$-adhesive.
+	$\elm$ is $\epbl$-adhesive and $\eps$ is $\epbs$-adhesive.
 \end{cor}

### 2025-09-09 jlamp/jlamp.tex
minima

@@
 \begin{prop}\label{prop:slice}
-$\EqHyps$ is equivalent to $\EqHyp \downarrow R(\mathcal{G})$.
+$\EqHyps$ is equivalent to $\EqHyp / R(\mathcal{G})$.
 \end{prop}
@@
 	\begin{enumerate}
-		\item $\eggl$ is equivalent to $\comma{E}/\Gamma_{R(\mathcal{G})}$;
-		\item there exists a functor $W_\mathcal{G}\colon \eggl\to \egg$ forgetting the labeling which creates all colimits, pullbacks and equalizers. 
+		\item $\eggl$ is equivalent to $\comma{E}\Gamma_{R(\mathcal{G})}$;
+		\item the functor $W_\mathcal{G}\colon \eggl\to \egg$ forgetting the labeling creates all colimits, pullbacks and equalizers. 
 	\end{enumerate}
@@
 \begin{cor}
-	$\lelm$ is $\epbl_{\mathcal{G}}$-adhesive, while $\leps$ is $\epbs_{\mathcal{G}}$-adhesive.
+	$\lelm$ is $\epbl_{\mathcal{G}}$-adhesive and $\leps$ is $\epbs_{\mathcal{G}}$-adhesive.
 \end{cor}
@@
 	\begin{minipage}[l]{.7\linewidth}
-	Thus for each $d$ in $\D$, there exists an arrow $a_d:U\to U_i$ making the diagram on the right commutative.
-	Then we have:
+	Thus for each $d$ in $\D$ there exists an arrow $a_d:U\to U_i$ making the diagram on the right commutative.
+	Then we have
 	\begin{align*}
@@
 
-	By universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$.
+	By the universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$.
 Since $m$ is mono we deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the claim.
@@
 	Let $\delta_1\colon 1\to \mathbb{N}$ be the arrow which picks $1\in \mathbb{N}$.
-Let $f\colon X\to Y$ be an arrow and consider theinclusion $v_1\colon X\to X^\star $  defined by the first point of \Cref{prop:fact}.
+Let $f\colon X\to Y$ be an arrow and consider the inclusion $v_1\colon X\to X^\star $  defined by the first point of \Cref{prop:fact}.
 Then we can build the cube aside which, by extensivity, has pullbacks as back, front and right faces.
@@
 \begin{proof}\label{proof:epo}
-	Let $\mathcal{P} $ be $(A, B, C, s, t, q)$ and consider the kernel pair $(K_i, \pi_i^1, \pi_i^2)$ the kernel pair of $q_i^\star \circ s_i$, for $i\in \{1, 2, 3\}$.
+	Let $\mathcal{P} $ be $(A, B, C, s, t, q)$ and let $(K_i, \pi_i^1, \pi_i^2)$ be the kernel pair of $q_i^\star \circ s_i$, for $i\in \{1, 2, 3\}$.
 Let also $(U, u_1, u_2)$ be the kernel pair of $q^\star \circ s$.
@@
 		Consider now the cube on the right.
-By hypothesis and \Cref{rem:kleene} its left face is a pullback, moreover its bottom face, while not a pushout it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.
+By hypothesis and \Cref{rem:kleene} its left face is a pullback.
+Moreover its bottom face is not a pushout but it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.
 	\end{minipage}\hfill 
@@
 			By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout. Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout. 
-			By computing we obtain:
+			By computing we obtain
 	\end{minipage}

### 2025-09-17 jlamp/jlamp.tex
section 6

@@
 \newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
+
+\newcommand{\comment}[1]{ }
 
@@
 \newcommand{\EqHyps}{\catname{Hyp}_{\mathsf{eq}, \mathcal{G}}}
+\newcommand{\Eqhyps}{\catname{Hyp}_{\mathsf{eq}, \Sigma}}
 \newcommand{\EqTG}{\catname{EqTG}}
@@
 \newcommand{\eggl}{\mathsf{e}\text{-}\catname{Hyp}_{\eq, \mathcal{G}}}
+\newcommand{\eggll}{\mathsf{e}\text{-}\catname{Hyp}_{\eq, \Sigma}}
 \newcommand{\elm}{\mathsf{e}\text{-}\catname{LMO}_\eq}
@@
 \newcommand{\leps}{\mathsf{e}\text{-}\catname{pSep}_{\eq, \mathcal{G}}}
+\newcommand{\lelmBis}{\mathsf{e}\text{-}\catname{LMO}_{\eq, \Sigma}}
+\newcommand{\lepsBis}{\mathsf{e}\text{-}\catname{pSep}_{\eq, \Sigma}}
 
@@
 
-\begin{exa} A useful example is given by an algebraic signature $\Sigma$. Consider the hypregraph of \Cref{exa_3}, the category $\hyps$ of
+\begin{exa} A useful example is given by an algebraic signature $\Sigma$. Consider the hypergraph of \Cref{exa_3}, the category $\hyps$ of
 	hypergraphs labelled by $\Sigma$ is the slice category $\hyp/\mathcal{G}^\Sigma$.
@@
 
-\begin{defi}Let$\mathcal{G}$ be an hypergraph and $(\mathcal{H},(f,g))$ a labelled hypergraph with equivalence.
+\begin{defi}Let $\mathcal{G}$ be an hypergraph and $(\mathcal{H},(f,g))$ a labelled hypergraph with equivalence.
 We say that $(\mathcal{H},(f,g))$ is a \emph{left-monogamous} (resp.~\emph{separated, pruned}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated, pruned).
@@
 
-\section{Pros and cons of adhesive rewriting}
+\section{On term representations, and their adhesive rewriting}
 \label{rewriting}
-The previous sections have shown how hypergraphs and term graphs with equivalence
+The previous sections offered a tour on various categories of hypergraphs,
+with and without an equivalence. 
+%and term graphs. 
+In particular, we have shown how they 
 can be described as suitable $\mathcal{M}$-adhesive categories.
-The same fact holds for their sub-categories where the equivalence is
- closed with respect to operator composition, and this allows to
- model EGGs, as originally presented in~\cite{WillseyNWFTP21}.
-
-\emph{Sharing.} 
-Terms are trees, thus different term graphs may represent the same term, up-to the sharing of sub-terms.
-Consider e.g. a constant $a$ and a binary operator $/$: the term $a / a$ admits a few different 
-representations as a term graph with equivalence, as shown below
+%
+%
+%The fact holds for various classes of hypergraphs, and 
+Most importantly, the fact holds for the class of e-hypergraphs, the one 
+where the equivalence is closed with respect to operator composition.
+%
+The overall trajectory aimed at recasting the EGGs formalism, 
+as originally presented in~\cite{WillseyNWFTP21}, in the adhesive mold.
+%
+However, when confronted with the many graphical presentations discussed 
+in the previous chapters, the reader may feel overwhelmed.
+
+\subsection{Sharing} 
+The classical view of term graphs is that they represent terms as labelled hypergraphs, instead of trees, in order to
+exploit the sharing of sub-terms for efficiency reasons. The introduction of equivalence adds another layer of
+expressiveness.
+%
+%Terms are trees, thus different term graphs may represent the same term, up-to the sharing of sub-terms.
+%
+Consider e.g. a signature $\Sigma$ with a constant $a$ and a binary operator $/$: the term $a / a$ admits a few different 
+representations as a term graph with equivalence, such as those below
 
@@
 \end{center}
-%
+
+Consider the pictures above.
+They depict left-monogamous hypergraphs with equivalence, labelled over 
+$\Sigma$: hence, term graphs.
+%
+As for the picture indicated by (1), it is the standard representation of $a / a$ as a tree. 
+%
+The picture indicated by (2) represents the same term, but as a term graph with a non-trivial equivalence on nodes.
+However, neither of them is an e-term graph:
+constants have no input, and nodes that are targets of edges with the same label and whose source is the empty word 
+must belong to the same equivalence class. Intuitively, picture (1) is the representation of $a / a$ 
+among labelled hypergraphs, i.e. objects of $\hyps$, which has the minimal amount of sharing between nodes.
+%Instead, picture (2) is the minimally-shared representation 
+%among labelled hypergraphs with equivalence, i.e. objects of $\Eqhyps$.
+%
+Consider instead the pictures indicated by (3) and (4). They are both e-term graphs. Pictures (3) is the classical representation 
+of $a / a$ as a maximally-shared term graph; while picture (4) is 
+% the minimally-shared representation among 
+a labelled e-hypergraph that is pruned and separated.
+
+In the original paper~\cite{DetlefsNS05} EGGs were simply defined as term graphs with an equivalence relation on nodes that is composition-closed, 
+resulting in some ambiguity in which is the canonical EGG associated to a term. To this end, we decided to introduce two different categories,
+namely $\lelmBis$ and $\lepsBis$.
+In particular, e-term graphs offer a representation that directly recalls the original definition; while the sub-category of pruned, separated 
+e-term graphs guarantees a unique representation for a term, and it seems more in touch with recent implementations~\cite{eggs}.
+
+\comment{
 The left-most and the right-most images represent just ordinary term graphs, the middle one is a term graph with equivalence.
@@
 %%from $\mathcal{G}$ to the terminal object is easily shown to be injective on equivalence classes.
-
-\emph{Rewriting.} The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
+}
+
+\subsection{Rewriting} The theory of $\mathcal{M}$-adhesivity ensures that if the rules are spans of 
 arrows in $\mathcal{M}$, then we can lift the standard properties
@@
 So, the corresponding DPO rules 
-are spans $L \leftarrow L \rightarrow R$, where the first component is the identity, thus in $\pbc_\Sigma$,
-while the second component may not belong to $\pbc_\Sigma$.
-
-Consider e.g. an EGG rule such $x / x \to 1$, from the introductory example in~\cite{WillseyNWFTP21}.
-Variables in a term graph are represented as nodes that do not occur among the targets of an edge, 
-thus the rule can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
+are spans $L \leftarrow L \rightarrow R$, where the left-hand side is the identity.
+% thus in $\pbc_\Sigma$, while the second component may not belong to $\pbc_\Sigma$.
+
+Consider the term rewriting rule such $x / x \to 1$, from the key example in~\cite{WillseyNWFTP21}.
+This is a problematic rule to be simulates using classical term graph rewriting, since it is not left-linear
+(that is, $x$ occurs twice in the left-hand side)~\cite{xxx}.
+Using e-term graphs (variables are represented as nodes that do not occur among the targets of an edge),
+ it can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
 \[
@@
 
-In this case $L$ is the minimally shared EGG corresponding to the term $x / x$,
-thus the rule could be applied to the two EGGs
-depicted above with a match that is injective on equivalence classes.
-%
-In general, if the term graph underlying the EGG to whom the DPO rule is applied is acyclic,
-the same property holds for the EGG obtained as the result of the rule application.
-%
-The right-hand side is a regular mono, though, hence it is not an arrow in $\pbc_\Sigma$.
-The asymmetry between left-hand and right-hand sides falls in the current research about left-linear rules for 
-adhesive categories, as pursued e.g. in~\cite{BaldanC0G24}.
-
-\emph{Application conditions.} 
-As argued above, the DPO rules that are suitable for the EGG approach have identities as left-hand side,
-thus they belong to any choice of $\mathcal{M}$.
-%
-However, this would allow for the repeated application of the same rule, hence the 
+In this case $L$ is the minimally-shared e-term graph corresponding to the term $x / x$.
+%thus the rule could be applied to any of the term graph with equivalence
+%depicted above with a match that is injective on equivalence classes.
+The rule cannot be applied to the term graphs with equivalence
+ in the pictures (1) and (2) above, while the result of the application of the rule 
+to the e-term graphs in the pictures (3) and (4) is shown below
+
+\[xxx\]
+
+As noted above, the DPO rules have the shape
+$L \leftarrow L \rightarrow R$: the left-hand side component is the identity,
+hence it belongs to any possible choice of $\mathcal{M}$. 
+However, the situation is different for the right-hand side.
+Since the rule must preserve the $L$ component, that is nodes and edges of 
+the e-hypergraph to which $L$ is mapped must not be deleted, 
+the arrow $L \rightarrow R$ is an injection, and more precisely it is 
+a regular mono.
+%
+However, the arrow $L \rightarrow R$ does not necessarily belong to $\pbc_\Sigma$,
+hence it is not currently possible to lift to the categories at hand all the properties of the $\mathcal{M}$-adhesive framework.
+The asymmetry between left- and right-hand sides falls in the research about left-linear rules for 
+$\mathcal{M}$-adhesive categories, as pursued e.g. in~\cite{BaldanC0G24}.
+
+\subsection{Issues: Cycles and application conditions}
+We just remarked that the DPO rules under consideration have the shape
+$L \leftarrow L \rightarrow R$, where the left-hand side is the identity 
+and the right-hand side arrow is  a regular mono.
+%
+Despite their simplicity, though, such rules may raise some expressiveness issues.
+
+The fact that the right-hand side is a regular mono ensures that if the e-hypergraph to whom a rule is applied is acyclic,
+the same property holds for the e-hypergraph obtained as the result.
+%
+Note however that cycles may implicitly occur due to the presence of the equivalence 
+on nodes for what are called collapsing rules, i.e. where the right-hand side is a single variable. 
+%
+Looking again at the key example of~\cite{xxx}, consider the rule $1 \times x = x$,
+which can be modelled as the DPO rule below
+%
+\[xxx\]
+%
+Intuitively, the e-term graph obtained after the application of the rule represents a recursive term such 
+as $rec_x. 1 \times x$, thus highlighting the difficulty of extracting a term representation out of an e-term graph.
+
+The fact that the left-hand side of a rule is the identity allows for the repeated application of such rule, hence the 
 possibility to keep on performing the same rewriting step.
@@
 $L \leftarrow K \rightarrow R$ plus an additional arrow $n: L\rightarrow N$, such that a match $m: L \to G$ is admissible if it cannot
-be factorised through $n$~\cite{HabelHT96}. For EGGs and rules $L \leftarrow L \rightarrow R$, it suffices to choose $n$ as the right-hand side itself.
+be factorised through $n$~\cite{HabelHT96}. For e-term graphs and rules $L \leftarrow L \rightarrow R$, it suffices to choose $n$ 
+as the right-hand side itself.
 %

### 2025-09-17 jlamp/jlamp.tex
sezione 7

@@
 proving that they are $\mathcal{M}$-adhesive categories, and we extended these results in order to
-prove the same property for EGGs as term graphs with equivalence satisfying a suitable closure constraint.
-Summing up, we proved that EGGs are objects of an $\mathcal{M}$-adhesive category $\eg$ 
+prove the same property for e-hyper-graphs and e-term graphs , i.e. where the equivalence satisfies 
+a suitable closure constraint.
+Summing up, we proved that EGGs are objects of an $\mathcal{M}$-adhesive category
 and that optimisation steps are obtained via DPO rules (possibly with negative application conditions) whose 
@@
 \emph{Future works.}
-Our result on $\eg$ opens a few threads of research. The first is to check how the $\mathcal{M}$-adhesivity 
+Our results open a few threads of research. The first is to check how the $\mathcal{M}$-adhesivity 
 of EGGs can be pushed to model their rewriting via the double-pushout (DPO) approach. We have seen that 

### 2025-09-17 jlamp/jlamp.tex
minima

@@
 This is a problematic rule to be simulates using classical term graph rewriting, since it is not left-linear
-(that is, $x$ occurs twice in the left-hand side)~\cite{xxx}.
+(that is, $x$ occurs twice in the left-hand side)~\cite{AriolaKP00}.
 Using e-term graphs (variables are represented as nodes that do not occur among the targets of an edge),
@@
 %
-Looking again at the key example of~\cite{xxx}, consider the rule $1 \times x = x$,
+Looking again at the key example of~\cite{WillseyNWFTP21}, consider the rule $1 \times x = x$,
 which can be modelled as the DPO rule below
@@
 
-\section*{Acknowledgments}
-Hypergraphs, terms graphs, e-graphs, adhesive categories.
+%\section*{Acknowledgments}
+%Hypergraphs, terms graphs, e-graphs, adhesive categories.
 

### 2025-09-24 jlamp/jlamp.tex
minori

@@
 \usepackage{tikz}
+\usetikzlibrary{fit}
 \usepackage[draft]{tikzit}
@@
 Consider e.g. a signature $\Sigma$ with a constant $a$ and a binary operator $/$: the term $a / a$ admits a few different 
-representations as a term graph with equivalence, such as those below
+representations as a term graph with equivalence, such as those below.
 
@@
 
-\begin{center}\begin{tikzpicture}[baseline=(w)]
-        \begin{pgfonlayer}{nodelayer}
-                \node[style=small box](a) at (-1.8, 0){$a$};
-                \node[style=none] (aatt) at (-1.5, 0){};
-                \node[style=node](v) at (-0.9, 0){};
-                \node[style=medium box](div) at (0, 0){$/$};
-                \node[style=none](divfst) at (-0.3, -0.3){};
-                \node[style=none] (divsnd) at (-0.3, 0.3){};
-                \node[style=none] (divout) at (0.3, 0){};
-                \node[style=node] (w) at (0.9, 0){};
-        \end{pgfonlayer}
-        \begin{pgfonlayer}{edgelayer}
-                \draw(aatt.center) to (v);
-                \draw[out=-60, in=-180] (v) to (divfst.center);
-                \draw[out=60, in=-180](v) to (divsnd.center);
-                \draw(divout.center) to (w);
-        \end{pgfonlayer}
-\end{tikzpicture}
-\qquad
+\begin{center}
 \begin{tikzpicture}[baseline=(w)]
@@
                 \node[style=node] (w) at (0.9, 0){};
+
+                 \node [below=.5cm, align=flush center,text width=2cm] at (v1)
+                {
+                	Figure $(1)$.
+                };
         \end{pgfonlayer}
@@
         \end{pgfonlayer}
-        \begin{pgfonlayer}{eqlayer}
-                \draw[dashed, rounded corners] (-1.2, -0.8) rectangle (-0.6, 0.8);
-        \end{pgfonlayer}
 \end{tikzpicture}
-\qquad
+\quad 
 \begin{tikzpicture}[baseline=(w)]
 	\begin{pgfonlayer}{nodelayer}
-                \node[style=small box](a1) at (-1.8, -0.5){$a$};
-                \node[style=none] (a1att) at (-1.5, -0.5){};
-                \node[style=node](v1) at (-0.9, -0.5){};
-                \node[style=small box](a2) at (-1.8, 0.5){$a$};
-                \node[style=none] (a2att) at (-1.5, 0.5){};
-                \node[style=node](v2) at (-0.9, 0.5){};
+		\node[style=small box](a1) at (-2.3, -0.5){$a$};
+		\node[style=none] (a1att) at (-2.3, -0.5){};
+		\node[style=node](v1) at (-1.4, -0.5){};
+		\node[style=node](w1) at (-0.9, -0.5){};
+		\node[style=small box](a2) at (-2.3, 0.5){$a$};
+		\node[style=none] (a2att) at (-2.3, 0.5){};
+		\node[style=node](v2) at (-1.4, 0.5){};
+		\node[style=node](w2) at (-0.9, 0.5){};
 		\node[style=medium box](div) at (0, 0){$/$};
@@
 		\node[style=node] (w) at (0.9, 0){};
+
+		      \node [below=.5cm, align=flush center,text width=2cm] at (-1.15,-0.5)
+		{
+			Figure $(2)$.
+		};
 	\end{pgfonlayer}
@@
 		\draw(a2att.center) to (v2);
-                \draw[out=0, in=-120] (v1) to (divfst.center);
-                \draw[out=0, in=120](v2) to (divsnd.center);
+		\draw[out=0, in=-120] (w1) to (divfst.center);
+		\draw[out=0, in=120](w2) to (divsnd.center);
 		\draw(divout.center) to (w);
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{eqlayer}
+		\draw[dashed, rounded corners] (-1.7, -0.8) rectangle (-0.6, 0.8);
+	\end{pgfonlayer}
+\end{tikzpicture}
+\quad 
+\begin{tikzpicture}[baseline=(w)]
+	\begin{pgfonlayer}{nodelayer}
+		\node[style=small box](a) at (-1.8, 0){$a$};
+		\node[style=none] (aatt) at (-1.5, 0){};
+		\node[style=node](v) at (-0.9, 0){};
+		\node[style=medium box](div) at (0, 0){$/$};
+		\node[style=none](divfst) at (-0.3, -0.3){};
+		\node[style=none] (divsnd) at (-0.3, 0.3){};
+		\node[style=none] (divout) at (0.3, 0){};
+		\node[style=node] (w) at (0.9, 0){};
+		      \node [below=.5cm, align=flush center,text width=2cm] at (-0.9,-0.5)
+		{
+			Figure $(3)$.
+		};
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw(aatt.center) to (v);
+		\draw[out=-60, in=-180] (v) to (divfst.center);
+		\draw[out=60, in=-180](v) to (divsnd.center);
+		\draw(divout.center) to (w);
+	\end{pgfonlayer}
+\end{tikzpicture}
+\quad 
+\begin{tikzpicture}[baseline=(w)]
+	\begin{pgfonlayer}{nodelayer}
+		\node[style=node](w1) at (-0.9, -0.5){};
+		\node[style=small box](a2) at (-2.3, 0){$a$};
+		\node[style=none] (a2att) at (-2.3, 0){};
+		\node[style=node](v) at (-1.4, 0){};
+		\node[style=node](w2) at (-0.9, 0.5){};
+		\node[style=medium box](div) at (0, 0){$/$};
+		\node[style=none](divfst) at (-0.3, -0.3){};
+		\node[style=none] (divsnd) at (-0.3, 0.3){};
+		\node[style=none] (divout) at (0.3, 0){};
+		\node[style=node] (w) at (0.9, 0){};
+
+		      \node [below=.5cm, align=flush center,text width=2cm] at (-1.15, -0.5)
+		{
+			Figure $(4)$.
+		};
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw(a2att.center) to (v);
+		\draw[out=0, in=-120] (w1) to (divfst.center);
+		\draw[out=0, in=120](w2) to (divsnd.center);
+		\draw(divout.center) to (w);
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{eqlayer}
+		\draw[dashed, rounded corners] (-1.7, -0.8) rectangle (-0.6, 0.8);
 	\end{pgfonlayer}
@@
 Using e-term graphs (variables are represented as nodes that do not occur among the targets of an edge),
- it can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
+ it can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$.
 \[
@@
  in the pictures (1) and (2) above, while the result of the application of the rule 
-to the e-term graphs in the pictures (3) and (4) is shown below
-
-\[xxx\]
+to the e-term graphs in the pictures (3) and (4) is shown below.
+\[
+	\begin{tikzpicture}[baseline=(w)]
+		\begin{pgfonlayer}{nodelayer}
+			\node[style=small box](a) at (-1.8, 0){$a$};
+			\node[style=none] (aatt) at (-1.5, 0){};
+			\node[style=node](v) at (-0.9, 0){};
+			\node[style=medium box](div) at (0, 0){$/$};
+			\node[style=none](divfst) at (-0.3, -0.3){};
+			\node[style=none] (divsnd) at (-0.3, 0.3){};
+			\node[style=none] (divout) at (0.3, 0){};
+			\node[style=node] (w) at (0.9, 0){};
+				\node[style=small box] at (0, -1){$1$};
+			\node[style=none](one) at (0.3, -1){};
+			\node[style=node](z) at (0.9, -1){};
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{edgelayer}
+			\draw(aatt.center) to (v);
+			\draw[out=-60, in=-180] (v) to (divfst.center);
+			\draw[out=60, in=-180](v) to (divsnd.center);
+			\draw(divout.center) to (w);
+			\draw(one.center) to (z);
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{eqlayer}
+			\draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
+		\end{pgfonlayer}
+	\end{tikzpicture}
+	\qquad \qquad 
+	\begin{tikzpicture}[baseline=(w)]
+		\begin{pgfonlayer}{nodelayer}
+			\node[style=node](w1) at (-0.9, -0.5){};
+			\node[style=small box](a2) at (-2.3, 0){$a$};
+			\node[style=none] (a2att) at (-2.3, 0){};
+			\node[style=node](v) at (-1.4, 0){};
+			\node[style=node](w2) at (-0.9, 0.5){};
+			\node[style=medium box](div) at (0, 0){$/$};
+			\node[style=none](divfst) at (-0.3, -0.3){};
+			\node[style=none] (divsnd) at (-0.3, 0.3){};
+			\node[style=none] (divout) at (0.3, 0){};
+			\node[style=node] (w) at (0.9, 0){};
+			\node[style=small box] at (0, -1){$1$};
+			\node[style=none](one) at (0.3, -1){};
+			\node[style=node](z) at (0.9, -1){};
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{edgelayer}
+			\draw(a2att.center) to (v);
+			\draw[out=0, in=-120] (w1) to (divfst.center);
+			\draw[out=0, in=120](w2) to (divsnd.center);
+			\draw(divout.center) to (w);
+			\draw(one.center) to (z);
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{eqlayer}
+			\draw[dashed, rounded corners] (-1.7, -0.8) rectangle (-0.6, 0.8);
+			\draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
+		\end{pgfonlayer}
+	\end{tikzpicture}
+\]
 
@@
 Looking again at the key example of~\cite{WillseyNWFTP21}, consider the rule $1 \times x = x$,
-which can be modelled as the DPO rule below
-%
-\[xxx\]
-%
+which can be modelled as the DPO rule below.
+\[
+\hspace{.25cm}
+\xymatrix{        
+	\begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
+			\node[style=node](v1) at (-0.9, 0.3){};
+			\node[style=node](v2) at (-0.9, -0.3){};
+			\node[style=medium box] at (0, 0){$\times$};
+			\node[style=none](divfst) at (-0.3, 0.3){};
+			\node[style=none](divsnd) at (-0.3, -0.3){};
+			\node[style=none](divout) at (0.3, 0){};
+			\node[style=node] (w) at (0.9, 0){};
+			\node[style=small box] at (-2.3, 0.3){$1$};
+			\node[style=none](one) at (-2, 0.3){};
+			\node[style=node](z) at (-1.4, 0.3){};
+		\end{pgfonlayer}        
+		\begin{pgfonlayer}{edgelayer}
+			\draw(v1) to (divfst.center);
+			\draw(v2) to (divsnd.center);
+			\draw(divout.center) to (w);
+			\draw(one.center) to (z);
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{eqlayer}
+			\draw[dashed, rounded corners](-1.7, 0.6) rectangle (-0.6, -0);
+		\end{pgfonlayer}\begin{pgfonlayer}{background}
+			\draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+		\end{pgfonlayer}
+	\end{tikzpicture}
+	\ar@{=>}[r] &	\hspace{10pt}
+	\begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
+			\node[style=node](v1) at (-0.9, 0.3){};
+			\node[style=node](v2) at (-0.9, -0.3){};
+			\node[style=medium box] at (0, 0){$\times$};
+			\node[style=none](divfst) at (-0.3, 0.3){};
+			\node[style=none](divsnd) at (-0.3, -0.3){};
+			\node[style=none](divout) at (0.3, 0){};
+			\node[style=node] (w) at (0.9, 0){};
+			\node[style=small box] at (-2.3, 0.3){$1$};
+			\node[style=none](one) at (-2, 0.3){};
+			\node[style=node](z) at (-1.4, 0.3){};
+		\end{pgfonlayer}        
+		\begin{pgfonlayer}{edgelayer}
+			\draw(v1) to (divfst.center);
+			\draw(v2) to (divsnd.center);
+			\draw(divout.center) to (w);
+			\draw(one.center) to (z);
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{eqlayer}
+			\draw[dashed, rounded corners](-1.7, 0.6) rectangle (-0.6, -0);
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{background}
+			\draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+		\end{pgfonlayer}
+		\draw[dashed,rounded corners]
+		([shift={(0,0.2)}]v2.north) --
+		([shift={(-0.2,0)}]v2.west) --
+		(-.9,-1.2)--(.9,-1.2)--([shift={(0.2,0)}]w.east)--
+		([shift={(0,0.2)}]w.north)  -- ([shift={(-0.2,0)}]w.west)-- (0.7,-0.8)--(-0.7,-0.8)--([shift={(0.2,0)}]v2.east)-- cycle;
+	\end{tikzpicture}
+}
+\]
+
 Intuitively, the e-term graph obtained after the application of the rule represents a recursive term such 
@@
 as they hold for DPO graph transformation.
-
+Moreover, our construction is technically simpler, which not only facilitates its practical application and theoretical analysis, but also aligns with the traditional methodology of endowing certain (hyper)graphs with an additional \emph{structure}.
 %\section*{Acknowledgments}

### 2025-09-24 jlamp/jlamp.tex
minima

@@
 Consider e.g. a signature $\Sigma$ with a constant $a$ and a binary operator $/$: the term $a / a$ admits a few different 
-representations as a term graph with equivalence, such as those below.
+representations as a term graph with equivalence, such as those below
 
@@
 Using e-term graphs (variables are represented as nodes that do not occur among the targets of an edge),
- it can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$.
+ it can be modelled as the DPO rule below, concisely given by the arrow $L \rightarrow R$
 \[
@@
  in the pictures (1) and (2) above, while the result of the application of the rule 
-to the e-term graphs in the pictures (3) and (4) is shown below.
+to the e-term graphs in the pictures (3) and (4) is shown below
 \[
@@
 Looking again at the key example of~\cite{WillseyNWFTP21}, consider the rule $1 \times x = x$,
-which can be modelled as the DPO rule below.
+which can be modelled as the DPO rule below
 \[
@@
 \]
-
-Intuitively, the e-term graph obtained after the application of the rule represents a recursive term such 
-as $rec_x. 1 \times x$, thus highlighting the difficulty of extracting a term representation out of an e-term graph.
+%
+Intuitively, the e-term graph obtained after the application of the rule seem to represent a recursive term such 
+as $rec_x. 1 \times x$, highlighting the difficulty of extracting a term representation out of an e-term graph.
 
@@
 as the right-hand side itself.
+Indeed, consider again the rule $x / x \to 1$: once $1$ has been added once to the equivalence class of $x / x$, it is not necessary to
+
 %
@@
 %
-To do so, we revisited the notions of hyper-graphs and term graphs with equivalence, 
+To do so, we revisited the notions of hypergraphs and term graphs with equivalence, 
 proving that they are $\mathcal{M}$-adhesive categories, and we extended these results in order to
-prove the same property for e-hyper-graphs and e-term graphs , i.e. where the equivalence satisfies 
+prove the same property for e-hypergraphs and e-term graphs , i.e. where the equivalence satisfies 
 a suitable closure constraint.
@@
 is actually $\mathcal{M}$-adhesive, thus allowing to exploit all the features of the framework
-as they hold for DPO graph transformation.
-Moreover, our construction is technically simpler, which not only facilitates its practical application and theoretical analysis, but also aligns with the traditional methodology of endowing certain (hyper)graphs with an additional \emph{structure}.
+as they hold for DPO graph transformation.  Moreover, our construction is technically simpler, which facilitates its practical application 
+and theoretical analysis, and aligns with the traditional methodology adopted in the graph transformation community 
+of explicitly endowing (hyper)graphs with additional structure.
 %\section*{Acknowledgments}

### 2025-09-25 jlamp/jlamp.tex
minori
minima

@@
 
-Building on the criterion developed in~\cite{CastelnovoGM24}, this work proves that both hypergraphs with equivalence
-and EGGs form an 
+Building on the criterion developed in~\cite{CastelnovoGM24}, this work considers a family of categories of hypergraphs
+with equivalence, including EGGs, and prove that they form an 
 $\mathcal{M}$-adhesive category for a suitable choice of $\mathcal{M}$.
 The advantages from this characterisation are two-fold. On the one side, 
-we put the benefits \emph{per se} of a formal presentation, making precise the properties of the data structure. 
+we put the benefits \emph{per se} of a formal presentation, making precise 
+the properties of the data structures and the correspondence between them.
 On the other side, describing the optimisation steps via the DPO approach
@@
 and term graphs with equivalence and in Section~\ref{eggs} of
-their variants where equivalences are closed with respect to operator application,
+a few variants where equivalences are closed with respect to operator application,
 thus subsuming EGGs.
@@
 In Section~\ref{rewriting} we put the machinery at work, showing how the optimisation steps
-can be rephrased as the application of term graph rewriting rules.
+can be rephrased as the application of DPO rewriting rules, at the same time
+highlighting the issues linked to the format of such rules.
 %
@@
 brief remarks on related works.
+
+For the sake of readability, all the proofs appear in the appendices. 
+This work is an extended version of~\cite{uovadesive}.
+With respect to the conference paper, the way term graphs
+are described is completely changed: they are now presented 
+as an instance of the newly introduced category of 
+left-monogamous hypergraphs. Also the notion of separated 
+hypergraphs is original, so that Sections 3.1.1 and 3.2.1 are largely new,
+and consequently so Section 4.1.1, 4.2 and 5. 
 %
-For the sake of space, the proofs appear in the appendices. 
+Finally, also Section~6 on the applications of DPO rewriting has been rewritten 
+and expanded, trying to highlight the nuances of its use.
 %For the sake of completeness, 
@@
 	\begin{pgfonlayer}{eqlayer}
-		\draw[dashed, rounded corners] (-1.7, -0.8) rectangle (-0.6, 0.8);
+		\draw[dashed, rounded corners] (-1.7, 0.2) rectangle (-0.6, 0.8);
+		\draw[dashed, rounded corners] (-1.7, -0.8) rectangle (-0.6, -0.2);
 	\end{pgfonlayer}
@@
 	\end{tikzpicture}
-	\ar@{=>}[r] &	\hspace{10pt}
+	\ar@{=>}[r] &	\hspace{12pt}
 	\begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
@@
 Indeed, consider again the rule $x / x \to 1$: once $1$ has been added once to the equivalence class of $x / x$, it is not necessary to
-
+keep on adding it, since e.g. the two pictures below represent the same EGG
+\[xxx\]
 %

### 2025-09-25 jlamp/jlamp.tex
minima

@@
 hypergraphs is original, so that Sections 3.1.1 and 3.2.1 are largely new,
-and consequently so Section 4.1.1, 4.2 and 5. 
+and consequently so Sections 4.1.1, 4.2, and 5. 
 %
-Finally, also Section~6 on the applications of DPO rewriting has been rewritten 
-and expanded, trying to highlight the nuances of its use.
+Finally, also Section~6 on the use of DPO rewriting has been rewritten 
+and expanded, trying to highlight the nuances of its application.
 %For the sake of completeness, 

### 2025-09-25 jlamp/jlamp.tex
Update jlamp.tex

@@
 This is expanded in Section~\ref{hypereq} for proving the $\mathcal{M}$-adhesivity
-of hypergraphs 
-and term graphs with equivalence and in Section~\ref{eggs} of
-a few variants where equivalences are closed with respect to operator application,
+of hypergraphs and term graphs with equivalence, as well as their separated variants,
+and in Section~\ref{eggs}, where equivalences are closed with respect to operator application,
 thus subsuming EGGs.
@@
 Finally, also Section~6 on the use of DPO rewriting has been rewritten 
-and expanded, trying to highlight the nuances of its application.
+and expanded, trying to highlight the nuances concerning its application.
 %For the sake of completeness, 

### 2025-09-25 jlamp/jlamp.tex
Update jlamp.tex

@@
 This work is an extended version of~\cite{uovadesive}.
-With respect to the conference paper, the way term graphs
-are described is completely changed: they are now presented 
+Its overall structure reflects the one of the conference paper, 
+but the way term graphs
+are described is completely changed: They are now presented 
 as an instance of the newly introduced category of 
@@
 Indeed, consider again the rule $x / x \to 1$: once $1$ has been added once to the equivalence class of $x / x$, it is not necessary to
-keep on adding it, since e.g. the two pictures below represent the same EGG
+keep on adding it, since e.g. the two pictures below intuitively represent the same EGG
 \[xxx\]

### 2025-09-26 jlamp/jlamp.tex
fine

@@
 \end{rem}
-
-\begin{rem}
-	$\tg$ is not an adhesive category. In particular it does not have pushouts along all monos. For instance, if we take the three term graphs of the previous remark, then have two arrows
+In particular it does not have pushouts along all monos. For instance, if we take the three term graphs of the previous remark, then have two arrows
 	$(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_a, !_{V_{\mathcal{G}_a}})$ and $(?_{\{h\}}, \id{\{v\}})\colon \Delta_{\tg}(\{v\})\to (l_b, !_{V_{\mathcal{G}_a}})$ which cannot be completed to a square.
@@
 \begin{minipage}[r]{.15\linewidth}
-\xymatrix{V \ar@{>>}[d]_{q} \ar[r]_{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]^{l_d} & Q_D}
+\xymatrix{V \ar@{>>}[d]_{q} \ar[r]_{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]^{l_D} & Q_D}
 \end{minipage}
@@
 \begin{defi}
-	Let $\mathcal{G}$ be an hypergraph, a \emph{labelled hypergraph with equivalence} is a pair $(\mathcal{H}, (f,g))$ where $\mathcal{H}$ is an object of $\EqHyp$ and $(f,g)$ a morphism $T(\mathcal{H})\to \mathcal{G}$ of $\hyp$.
-A \emph{morphism of labelled hypergraphs with equivalence} between $(\mathcal{H}, (f,g))$ and $(\mathcal{H}', (h,k))$ is an arrow $(a,b, c)\colon \mathcal{H}\to \mathcal{H}'$ such that $h\circ a = f$ and $k\circ b = g$.
-%
-	We denote the resulting category by $\EqHyps$.
+	Let $\mathcal{G}$ be an hypergraph with equivalence, the category $\EqHyps$ of \emph{labelled hypergraph with equivalence}  is $\EqHyp/\mathcal{G}$.
 \end{defi}
+
+\begin{rem} The equivalence relation on the  nodes of the labelling hypergraph put constraints on the possible relations on the labelled hypergraphs.
+Indeed, consider the following hypergraphs with equivalences $\mathcal{G}$ and $\mathcal{H}$.
+
+\noindent
+\begin{minipage}[l]{.6\linewidth}
+	\setlength{\parindent}{1.5em}
+	Notice that there is no morphism $\mathcal{H}\to \mathcal{G}$.
+Indeed $\id{T(\mathcal{G})}$ is the unique morphism $T(\mathcal{G})\to T(\mathcal{H})$ while there are only two morphisms $f, g\colon Q_{\mathcal{H}}\rightrightarrows Q_{\mathcal{G}}$: the first one is constant in $v$, while the second one is constant in $w$.
+\end{minipage}\hfill \qquad 
+\begin{minipage}[r]{.4\linewidth}
+\begin{tikzpicture}[baseline=(v1)]
+	\begin{pgfonlayer}{nodelayer}
+		\node[style=small box](a1) at (-.5, 1){};
+		\node[style=none] (a1att) at (-.5, 1){};
+		\node[style=node](v1) at (-.5, 0){};
+		\node[style=small box](a2) at (.5, 1){};
+		\node[style=none] (a2in) at (.22, 1){};
+		\node[style=none] (a2out) at (.78, 1){};
+		\node[style=node](v2) at (.5, 0){};
+		\node[style=none] (l1) at (-.5, 1.5){$a$};
+		\node[style=none](l2) at (.5, 1.5){$b$};
+		\node[style=none] (l1) at (-1, 0){$v$};
+		\node[style=none](l2) at (1, 0){$w$};
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw(a1att.south) to (v1);
+		\draw[style=none, out=180, in=180](v2) to (a2in.west);
+		\draw[style=none, out=0, in=0](v2) to (a2out.east);
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{eqlayer}
+		\draw[dashed, rounded corners] (-.8, -0.3) rectangle (-.2, 0.3);
+		\draw[dashed, rounded corners] (.2, -0.3) rectangle (.8, 0.3);
+	\end{pgfonlayer}
+\end{tikzpicture}\qquad  
+\begin{tikzpicture}[baseline=(v1)]
+	\begin{pgfonlayer}{nodelayer}
+		\node[style=small box](a1) at (-.5, 1){};
+		\node[style=none] (a1att) at (-.5, 1){};
+		\node[style=node](v1) at (-.5, 0){};
+		\node[style=small box](a2) at (.5, 1){};
+		\node[style=none] (a2in) at (.22, 1){};
+		\node[style=none] (a2out) at (.78, 1){};
+		\node[style=node](v2) at (.5, 0){};
+		\node[style=none] (l1) at (-.5, 1.5){$a$};
+		\node[style=none](l2) at (.5, 1.5){$b$};
+		\node[style=none] (l1) at (-1, 0){$v$};
+		\node[style=none](l2) at (1, 0){$w$};
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{edgelayer}
+		\draw(a1att.south) to (v1);
+		\draw[style=none, out=180, in=180](v2) to (a2in.west);
+		\draw[style=none, out=0, in=0](v2) to (a2out.east);
+	\end{pgfonlayer}
+	\begin{pgfonlayer}{eqlayer}
+		\draw[dashed, rounded corners] (-.8, -0.3) rectangle (.8, 0.3);
+	\end{pgfonlayer}
+\end{tikzpicture}
+\end{minipage}
+
+ For both cases we have:
+\[ f(q_{\mathcal{H}}(w))=v \neq w =q_{\mathcal{G}}(w)=q_\mathcal{G}(\id{V_{\mathcal{G}}}(w)) \qquad  g(q_{\mathcal{H}}(v))=w \neq v =q_{\mathcal{G}}(v)=q_\mathcal{G}(\id{V_{\mathcal{G}}}(v))  \]
+
+	Intuitively, labelling with $\mathcal{G}$ force us to keep all the sorts (i.e.~the labellings of the nodes) distinguished, while labelling with $\mathcal{H}$ allows us to merge different sorts.
+\end{rem}
 
@@
 	\setlength{\parindent}{1.5em}
-		\begin{rem}Let $\Sigma$ be a single typed monoidal signature (cfr~\Cref{def:alg}).
+\begin{exa}
+	Let $\Sigma$ be a single typed monoidal signature (cfr~\Cref{def:alg}).
 Since $\mathcal{G}_{\Sigma}$ has a single node, then to label another hypergraph $\mathcal{H}$ it is enough to provide a function $l\colon E_{\mathcal{H}}\to O_{\Sigma}$ such that the diagrams aside commute.
@@
 In that case, since the image of $\lg_{V_{\mathcal{H}}}$ is simply the singleton $\{1\}$, the second diagram commutes by default.
-		\end{rem}
+\end{exa}	
 \end{minipage} \hfill 
@@
 \end{minipage}
-
-Let $(\mathcal{H}, l)$ be an object of $\EqHyps$: since $T$ has a right adjoint $R$ by \Cref{prop:forghyp}, $(f,g)\colon T(\mathcal{H})\to \mathcal{G}^\Sigma$ corresponds to the arrow $(f, g, !_{Q_{\mathcal{H}}})\colon \mathcal{H}\to R(\mathcal{G})$.
-It is immediate to see that this correspondence extends to an equivalence with the slice category over $R(\mathcal{G})$.
-
-\begin{prop}\label{prop:slice}
-$\EqHyps$ is equivalent to $\EqHyp / R(\mathcal{G})$.
-\end{prop}
 
@@
 
- \begin{prop}
- 	Let $M_{\eq}\colon \Eqlmo\to \EqHyp$ and $S_{\eq}\colon \EqsHyp \to \EqHyp$ be the inclusion functors.
-Moreover, let $\Gamma_{R(\mathcal{G})}\colon 1\to \EqHyp$ be the constant functor in $R(\mathcal{G})$.
+ \begin{prop}\label{prop:eti}
+ 	Let $\mathcal{G}$ be an hypegraph with equivalence and consider the inclusion functors $M_{\eq}\colon \Eqlmo\to \EqHyp$, $S_{\eq}\colon \EqsHyp \to \EqHyp$ and $S_{p, \eq}\colon \pshyp_{\eq}\to \EqHyp$.
+Let $\Gamma_{\mathcal{G}}\colon 1\to \EqHyp$ be the constant functor in $\mathcal{G}$.
 Then
  	\begin{enumerate}
- 		\item $\lmo_{\eq, \mathcal{G}}$ is equivalent to $\comma{M_\eq}{\Gamma_{R(\mathcal{G})}}$;
- 		\item $\shyp_{\eq, \mathcal{G}}$ is equivalent to $\comma{S_\eq}{\Gamma_{R(\mathcal{G})}}$; 
- 		\item $\pshyp_{\mathcal{G}}$ is equivalent to $\pshyp_{\eq}/R(\sp(\pr(\mathcal{G})))$. 
+ 		\item $\lmo_{\eq, \mathcal{G}}$ is equivalent to $\comma{M_\eq}{\Gamma_{\mathcal{G}}}$;
+ 		\item $\shyp_{\eq, \mathcal{G}}$ is equivalent to $\comma{S_\eq}{\Gamma_{\mathcal{G}}}$; 
+ 		\item $\pshyp_{\mathcal{G}}$ is equivalent to $\comma{S_{p, \eq}}{\Gamma_{\mathcal{G}}}$. 
  	\end{enumerate}
  \end{prop}
+
+ In particular, the previous  proposition, together with Lemmas \ref{lem:equ}, \ref{lem:coequ}, \ref{colim} and \Cref{lim}, yields the following
+
+ \begin{cor}\label{cor:eti}
+ $\lmo_{\eq, \mathcal{G}}$ is closed in $\hyp_{\eq, \mathcal{G}}$ under equalizers, binary product and pullbacks.
+$\pshyp_{\eq, \mathcal{G}}$ is closed in $\hyp_{\eq, \mathcal{G}}$ under pullbacks.
+Both are closed in  $\hyp_{\eq, \mathcal{G}}$ under pushouts along arrows in $\pbc_{\mathcal{G}}$.
+ \end{cor}
 
@@
 
-We can  now use \Cref{thm:slice-functors} to get the following.
+We can  now use \Cref{thm:slice-functors} together with Lemmas \ref{lem:equ} and \ref{lem:coequ} to get the following.
 
@@
 \begin{defi}
-	Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence and $(S, \pi_1, \pi_2)$ a kernel pair for $q^\star \circ s$.
-	We will say that $\mathcal{G}$ is an \emph{e-hypergraph} if $q^\star \circ t \circ \pi_1 = q^\star \circ t \circ \pi_2$.
-
+Let $\mathcal{G} = (E, V, Q, s, t, q)$ be a hypergraph with equivalence, two  hyperedges $e, e'\in E$ are \emph{$q$-joined} if $q^\star(t(e'))=q^\star(t(e))$.
+
+We will say that $\mathcal{G}$ is an \emph{e-hypergraph} if every two  hyperedges $e,e'$ such that
+$q^\star(s(e'))=q^\star(s(e))$ are $q$-joined.
 We will denote by $\egg$ the full subcategory of $\EqHyp$ whose objects are e-hypergraphs, and by $E\colon \egg \to \EqHyp$ the associated inclusion functor. 
 \end{defi}
+
+We can reformulate the definition of e-hypergraphs in two other ways. See \Cref{proof:eh} for a proof
+
+\begin{restatable}{prop}{eh}\label{prop:eh}
+Consider an hypergraph with equivalence $\mathcal{G} = (E, V, Q, s, t, q)$ and let $(A, \pi^A_1, \pi^A_2)$, $(B, \pi^B_1, \pi^B_2)$ be kernel pairs for, respectively, $q^\star\circ s$ and $q^\star\circ t$.
+Then the following are equivalent:
+\begin{enumerate}
+	\item $\mathcal{G}$ is an e-hypergraph;
+	\item $q^\star\circ t\circ \pi^A_1=q^\star\circ t\circ \pi^A_2$;
+	\item there exists a unique arrow $k\colon A\to B$ such that 
+	\[\pi^B_1\circ k = \pi^A_1 \qquad \pi^B_2\circ k = \pi^A_2 \]
+	\end{enumerate}\end{restatable}
 
@@
 
-A first result that we need is that limits in $\egg$ are computed as in $\EqHyp$. Full proofs are in \Cref{proof:elim}.
-
-\begin{restatable}{lem}{elim}\label{lem:elim}
-	$\egg$ has all limits and $E$ creates them.
+As a next step, we we need to prove that connected limits in $\egg$ are computed as in $\EqHyp$. Full proofs are in \Cref{proof:elim}.
+
+\begin{restatable}{lem}{elim}\label{lem:elimc}
+Let $F\colon \D\to \hyp_{\eq}$ be a connected diagram and let $F(D)$ be $(E_D, V_D, Q_D, s_D, t_D, q_D)$.
+Suppose that $(\mathcal{L}, \{(a_D, b_D, c_D)\}_{D\in \D})$ is a limiting cone for $F$, then for every hyperedges $e,e'\in E_{\mathcal{L}}$, if $a_D(e)$ and $a_D(e')$ are $q_D$-joined for every $D\in \D$, then $e$ and $e'$ are $q_{\mathcal{L}}$-joined.
+\end{restatable}
+
+\begin{restatable}{cor}{ecim}\label{lem:elim}
+	$\egg$ has all connected limits and $E$ creates them.
 \end{restatable}
@@
 Finally, we can turn our attention to the labelled context.
-
-\begin{defi} Let $\mathcal{G}$ be an hypergraph.
-We say that an object $(\mathcal{H}, (f,g))$ of $\EqHyps$ is a \emph{labelled e-hypergraph} if $\mathcal{H}$ is an e-hypergraph.
-We define the category $\eggl$ as the full subcategory of $\EqHyps$ given by labelled e-hypergraphs.
-We denote by $E_\mathcal{G}$ the corresponding inclusion functor .
+In such an environment, we want the equivalence relation to identify the target of two hyperedges whenever their sources are related \emph{and} their labels are the same.
+This justifies the following definition.
+
+\begin{defi} Let $\mathcal{G}$ be an hypergraph with equivalence.
+We say that an object $(a,b,c)\colon \mathcal{H}\to \mathcal{G}$ of $\EqHyps$ is a \emph{labelled e-hypergraph} if every two hyperedges $e,e'\in E_{\mathcal{H}}$ such that
+	\[q^\star_{\mathcal{H}}(s(e))=q^\star_{\mathcal{H}}(s(e')) \qquad a(e) = a(e')\]
+	are $q_\mathcal{H}$-joined.
+
+ We define the category $\eggl$ as the full subcategory of $\EqHyps$ given by labelled e-hypergraphs. We denote by $E_\mathcal{G}$ the corresponding inclusion functor .
 \end{defi}
 
-From the definitions, we get at once the follosing result.
-
-\begin{prop}\label{prop:varie}
-	Let $\mathcal{G}$ be an hypergraph and $\Gamma_{R(\mathcal{G})}$ the costant functor in $R(\mathcal{G})$. Then the following facts hold
+\noindent
+\begin{minipage}[l]{.75\linewidth}
+	\begin{exa}
+		Let $\mathcal{G}$ be the graph aside. Notice that $\id{\mathcal{G}}$ is a labelled e-hypergraph even if its underlying hypergraphs with equivalence $\mathcal{G}$ is not in $\egg$.
+	\end{exa}
+\end{minipage} \hfill \begin{minipage}[r]{.21\linewidth}
+	\begin{tikzpicture}[baseline=(v1)]
+		\begin{pgfonlayer}{nodelayer}
+			\node[style=small box](a1) at (-1.4, 0){};
+			\node[style=none] (a1att) at (-1.4, 0){};
+			\node[style=node](v1) at (-.5, 0){};
+			\node[style=small box](a2) at (1.4, 0){};
+			\node[style=none] (a2in) at (1.4, 0){};
+			\node[style=node](v2) at (.5, 0){};
+			\node[style=none] (l1) at (-1.4, .5){$a$};
+			\node[style=none](l2) at (1.4, .5){$b$};
+			\node[style=none] (l1) at (-.5, -.5){$v$};
+			\node[style=none](l2) at (.5, -.5){$w$};
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{edgelayer}
+			\draw(a1att) to (v1);
+			\draw[style=none](v2) to (a2in.south);
+		\end{pgfonlayer}
+		\begin{pgfonlayer}{eqlayer}
+			\draw[dashed, rounded corners] (-.8, -0.3) rectangle (-.2, 0.3);
+			\draw[dashed, rounded corners] (.2, -0.3) rectangle (.8, 0.3);
+		\end{pgfonlayer}
+	\end{tikzpicture}
+\end{minipage}
+
+We begin by providing an equivalent characterization to labelled e-hypergraphs (see \Cref{proof:fh} for details).
+
+\begin{restatable}{lem}{fh}\label{lem:fh}
+Let $(a,b,c)\colon \mathcal{H}\to \mathcal{G}$ be an object of $\hyp_{\eq, \mathcal{G}}$ and let $(A, \pi^A_1, \pi^A_2)$, $(B, \pi^B_1, \pi^B_2)$ be kernel pairs for, respectively, $(q^\star\circ s_{\mathcal{H}}, a),(q^\star\circ t_{\mathcal{H}}, a)\colon E_{\mathcal{H}}\to Q_{\mathcal{H}}\times E_{\mathcal{G}}$.
+Then the following are equivalent:
 \begin{enumerate}
-		\item $\eggl$ is equivalent to $\comma{E}\Gamma_{R(\mathcal{G})}$;
-		\item the functor $W_\mathcal{G}\colon \eggl\to \egg$ forgetting the labeling creates all colimits, pullbacks and equalizers. 
+	\item $(a,b,c)$ is a labelled e-hypergraph;
+	\item $q^\star\circ t_{\mathcal{H}}\circ \pi^A_1=q^\star\circ t_{\mathcal{H}}\circ \pi^A_2$;
+	\item there exists a unique arrow $k\colon A\to B$ such that 
+	\[\pi^B_1\circ k = \pi^A_1 \qquad \pi^B_2\circ k = \pi^A_2 \]
 \end{enumerate}
-\end{prop}
-
-Let $\pbe_\mathcal{G}$ be the class of morphisms in $\eggl$ whose image in $\egg$ lies in $\pbe$.
-Notice that $\pbe_\mathcal{G}$ is also the class of arrows whose image through $E_\mathcal{G}$ is in $\pbc_\mathcal{G}$.
+\end{restatable}
+
+We want now to show that pullbacks and pushout in $\eggl$ are computed as in $\hyp_{\eq, \mathcal{G}}$. See \Cref{proof:varie} for a proof.
+
+\begin{restatable}{lem}{varie}\label{prop:varie}
+	Let $\mathcal{G}$ be an hypergraph with equivalence, then $\eggl$ is closed in $\hyp_{\eq, \mathcal{G}}$ under connected limits and pushouts alongs arrows in $\pbe_\mathcal{G}$, where $\pbe_\mathcal{G}$ is the class of morphisms in $\eggl$ whose image through $E_\mathcal{G}$ is in $\pbc_\mathcal{G}$.
+\end{restatable}
+
 %
@@
 \begin{rem}
-When $\mathcal{G}$ is the hypergraph associated to an algebraic signature, the object of  $\lelm$ coincides with what in \cite{uovadesive} are called \emph{e-termgraphs with equivalence}. 
+When $\mathcal{G}$ is the hypergraph associated to an algebraic signature, the object of  $\lelm$ coincides with what in \cite{uovadesive} are called \emph{e-term graphs with equivalence}. 
 \end{rem}
 
-\begin{lem}Let $\mathcal{G}$ be an hypergraph and $\Gamma_{R(\mathcal{G})}$ the costant functor in $R(\mathcal{G})$. 
-	\begin{enumerate}
-		\item $\lelm$ is equivalent to $\comma{E\circ M_{\mathsf{e}}}{\Gamma_{R(\mathcal{G})}}$
-		\item $\leps$ is equivalent to $\comma{E\circ S_{\mathsf{e}}}{\Gamma_{R(\mathcal{G})}}$
-	\end{enumerate}
+Putting together \Cref{cor:eti} with \Cref{prop:varie} we get the following.
+
+\begin{lem}Let $\mathcal{G}$ be an hypergraph with equivalence, then $\lelm$ and $\leps$ are closed in $\hyp_{\eq, \mathcal{G}}$ under pullbacks and pushouts along arrows in $\pbc_{\mathcal{G}}$.
 \end{lem}
 
-Define $\epbl_{\mathcal{G}}$ and $\epbs_{\mathcal{G}}$ as the classes of arrows whose underlying morphisms are in $\epbl$ or in $\epbs$. The following result now follows at once.
+Define $\epbl_{\mathcal{G}}$ and $\epbs_{\mathcal{G}}$ as the classes of arrows whose underlying morphisms are in $\pbc_{\mathcal{G}}$ or in $\pbc_{\mathcal{G}}$.
+The following result now follows at once.
 
@@
         \end{pgfonlayer}
+        \begin{pgfonlayer}{eqlayer}
+        	\draw[dashed, rounded corners] (-1.2, -0.8) rectangle (-.6, -0.2);
+        	\draw[dashed, rounded corners] (-1.2, 0.2) rectangle (-.6, 0.8);
+        	\draw[dashed, rounded corners] (.6, -0.3) rectangle (1.2, 0.3);
+        \end{pgfonlayer}
 \end{tikzpicture}
@@
 		\draw[dashed, rounded corners] (-1.7, -0.8) rectangle (-0.6, -0.2);
+			\draw[dashed, rounded corners] (.6, -0.3) rectangle (1.2, 0.3);
 	\end{pgfonlayer}
@@
 	\end{pgfonlayer}
+	\begin{pgfonlayer}{eqlayer}
+			\draw[dashed, rounded corners] (.6, -0.3) rectangle (1.2, 0.3);
+				\draw[dashed, rounded corners] (-1.2, -0.3) rectangle (-.6, 0.3);
+	\end{pgfonlayer}
 \end{tikzpicture}
@@
 		\draw[dashed, rounded corners] (-1.7, -0.8) rectangle (-0.6, 0.8);
+			\draw[dashed, rounded corners] (.6, -0.3) rectangle (1.2, 0.3);
 	\end{pgfonlayer}
@@
 				\draw[dashed, rounded corners](-1.2, 0.6) rectangle (-0.6, -0.6);
+					\draw[dashed, rounded corners] (.6, -0.3) rectangle (1.2, 0.3);
 			\end{pgfonlayer}\begin{pgfonlayer}{background}
@@
 			\draw[dashed, rounded corners](0.6, 0.3) rectangle (1.2, -1.3);
+				\draw[dashed, rounded corners] (-1.2, -0.3) rectangle (-.6, 0.3);
 		\end{pgfonlayer}
@@
 	\begin{tikzpicture}[baseline=(w.base)]\begin{pgfonlayer}{nodelayer}
-			\node[style=node](v1) at (-0.9, 0.3){};
-			\node[style=node](v2) at (-0.9, -0.3){};
+			\node[style=node](v1) at (-0.9, 0.4){};
+			\node[style=node](v2) at (-0.9, -0.4){};
 			\node[style=medium box] at (0, 0){$\times$};
@@
 			\node[style=none](one) at (-2, 0.3){};
-			\node[style=node](z) at (-1.4, 0.3){};
+			\node[style=node](z) at (-1.4, 0.4){};
 		\end{pgfonlayer}        
@@
 		\begin{pgfonlayer}{eqlayer}
-			\draw[dashed, rounded corners](-1.7, 0.6) rectangle (-0.6, -0);
+			\draw[dashed, rounded corners](-1.7, 0.1) rectangle (-0.6, 0.7);
+			\draw[dashed, rounded corners](1.2, -0.3) rectangle (0.6, 0.3);
+			\draw[dashed, rounded corners] (-1.2, -0.7) rectangle (-.6, -0.1);
 		\end{pgfonlayer}\begin{pgfonlayer}{background}
-			\draw[color=white] (-1.5, 0.2) rectangle (1.5, -0.2);
+			\draw[color=white] (-1.5, 0.1) rectangle (1.5, -0.3);
 		\end{pgfonlayer}
@@
 \begin{minipage}[r]{.15\linewidth}
-	\xymatrix{V \ar@{>>}[d]_{q} \ar[r]_{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]^{l_d} & Q_D}
+	\xymatrix{V \ar@{>>}[d]_{q} \ar[r]_{\pi^D_V}& V_D \ar@{>>}[dd]^{q_D}\\Q \ar@{>.>}[d]_{m}&\\ L \ar[r]^{l_D} & Q_D}
 \end{minipage} 
@@
 \subsection{Proofs for \Cref{eggs}}
+
+\eh*
+\begin{proof}\label{proof:eh}  Define
+	\[A_E:=\{(e,e')\in E \mid q^\star(s(e))=q^\star(s(e'))\}\] 
+	If $p_1, p_2\colon A_E\rightrightarrows E$ are the two projections, we know that $(A_E, p_1, p_1)$ is a kernel pair for $q^\star \circ s$.
+Thus there exists an isomorphism $\phi \colon A_E\to A$ such that
+	\[\pi^A_1\circ \phi =p_1 \qquad \pi^A_2\circ \phi = p_2\]
+
+	\smallskip \noindent
+	$(1\Rightarrow 2)$ By hypothesis $\mathcal{G}$ is an e-hypergraph, then the components of $\phi^{-1}(a)$ are $q$-joined for every $a\in A$ and so:
+	\[q^\star(t(\pi^A_1(a)))=q^\star(t(p_1(\phi^{-1}(a))))=q^\star(t(p_2(\phi^{-1}(a))))=q^\star(t(\pi^A_2(a)))\]
+	\smallskip \noindent $(2\Rightarrow 3)$ This follows at once from the definition of kernel pairs.
+
+	\smallskip \noindent $(3\Rightarrow 1)$ Let $e, e'$ be hyperedges such that $q^\star(s(e))=q^\star(s(e'))$. Then $(e,e')$ belongs to $A_E$ and thus we have:
+	\begin{align*}
+		&q^\star(t(e))=q^\star(t(p_1(e, e')))=q^\star(t(\pi^A_1(\phi(e,e'))))=q^\star(t(\pi^B_1(k(\phi(e,e')))))\\=&q^\star(t(\pi^B_2(k(\phi(e,e')))))=q^\star(t(\pi^A_2(\phi(e,e'))))=q^\star(t(p_2(e, e')))=q^\star(t(e'))
+	\end{align*}
+	and we can conclude. \qedhere
+
+\end{proof}
+
 \elim*
 \begin{proof}\label{proof:elim}
-	Let $F: \D \to \egg$ be a diagram, with $F(d) = (A_d, B_d, Q_d, s_d, t_d, q_d)$.  Let $(U_d, u_1^d, u_2^d)$ be a kernel pair for $q_d\circ s_d$.
-	Now let $(A, B, Q, s, t, q)$, together with projections $(\pi_E^d, \pi_V^d, \pi_Q^d)_{d\in \D}$, be the limit of $I \circ F$.
-Suppose that $(U, u_1, u_2)$ is the kernel pair of $q^\star\circ s$ and let $(L, (l_i)_{i \in \cat I})$ be the limit of $K \circ I \circ F$.
-If we show that it lies in $\egg$ we are done.
-
-	By \Cref{prop:eqhyp_complete} there exists a mono $m\colon Q \mto L$ such that $\pi_Q^d = l_d \circ m$. Notice that
+	Let $\mathcal{L}$ be $(E_{\mathcal{L}}, V_{\mathcal{L}}, Q_{\mathcal{L}}, s_{\mathcal{L}}, t_{\mathcal{L}}, q_{\mathcal{L}})$ and consider $e, e'\in E_{\mathcal{L}}$.
+	Take a limit $(L, (l_i)_{i \in \cat I})$ for $K \circ F$.
+By \Cref{prop:eqhyp_complete} there exists a mono $m\colon Q_{\mathcal{L}} \mto L$ such that $c_D = l_D \circ m$.
+Since $\D$ is connected then by \Cref{prop:fact} we know that $(L^\star, \{l^\star_D\}_{D\in \D})$ is a limiting cone.
+Computing we get
 	\begin{align*}
-		&q_d^\star \circ s_d\circ \pi^d_E\circ u_1  = q_d^\star\circ (\pi^d_V)^\star \circ s\circ u_1= (\pi_Q^d)^\star\circ q^\star\circ s\circ u_1\\=&(\pi_Q^d)^\star\circ q^\star\circ s\circ u_2= q_d^\star\circ (\pi^d_V)^\star\circ s\circ u_2=q_d^\star \circ s_d \circ \pi_E^d \circ u_2\\
+		&l^\star_D(m^\star(q_{\mathcal{L}}^\star(t_{\mathcal{L}}(e))))=c^\star_D(q_{\mathcal{L}}^\star(t_\mathcal{L}(e)))=q^\star_D(b^\star_D(t_\mathcal{L}(e)))=q^\star_D(t_D(a_D(e)))\\=&q^\star_D(t_D(a_D(e')))=q^\star_D(b^\star_D(t_\mathcal{L}(e')))=c^\star_D(q_{\mathcal{L}}^\star(t_\mathcal{L}(e')))=l^\star_D(m^\star(q_{\mathcal{L}}^\star(t_{\mathcal{L}}(e'))))
 	\end{align*} 
-\vspace{-1cm}
-
-	\noindent 
-	\begin{minipage}[l]{.7\linewidth}
-	Thus for each $d$ in $\D$ there exists an arrow $a_d:U\to U_i$ making the diagram on the right commutative.
-	Then we have
+	Thus we deduce that $m^\star(q_{\mathcal{L}}^\star(t_{\mathcal{L}}(e)))=m^\star(q_{\mathcal{L}}^\star(t_{\mathcal{L}}(e')))$.
+But by \Cref{prop:fact}, $(-)^\star$ sends monos to monos and so we can conclude.
+\end{proof}
+
+\ecim*
+\begin{proof}\label{proof:ecim} Let $F\colon \D\to \egg$ be a connected diagram.
+Let $F(D)$ be $(E_D, V_D, Q_D, s_D, t_D, q_D)$ and suppose that $(\mathcal{L}, \{(a_D, b_D, c_D)\}_{D\in \D})$ is a limiting cone for $E\circ F$.
+If we show that $\mathcal{L}$ is an e-hypergraph we are done.
+Let $e, e'\in E_{\mathcal{L}}$ be such that $q^\star_{\mathcal{L}}(s_{\mathcal{L}}(e))=q^\star_{\mathcal{L}}(s_{\mathcal{L}}(e'))$.
+Thus for every $D\in \D$ we have:
 	\begin{align*}
-		&l_d^\star\circ m^\star \circ q^\star \circ t \circ u_1    = q_d^\star\circ (\pi_V^d)^\star \circ t \circ u_1 \\
-		= &q_d^\star \circ t_d \circ \pi_E^d \circ u_1
-		= q_d^\star \circ t_d \circ u_1^d \circ a_d 
-		= q_d^\star \circ t_d \circ u_2^d \circ a_d\\ 
-		=& q_d^\star \circ t_d \circ \pi_E^d \circ u_2 = q_d^\star \circ (\pi_V^d)^\star \circ t \circ u_2 = l_d^\star \circ m^\star \circ q^\star \circ t \circ u_2
+		&q^\star_D(s_D(a_D(e)))=q^\star(b^\star_D(s_{\mathcal{L}}(e)))=c^\star_D(q_{\mathcal{L}}(s_{\mathcal{L}}(e)))\\=&c^\star_D(q_{\mathcal{L}}(s_{\mathcal{L}}(e')))=c^\star_D(q_{\mathcal{L}}(s_{\mathcal{L}}(e')))=q^\star(b^\star_D(s_{\mathcal{L}}(e')))=q^\star_D(s_D(a_D(e')))
 	\end{align*}
-	\end{minipage}
-\hfill
-\begin{minipage}[r]{.3\linewidth}
-\xymatrix@R=20pt{
-	U \ar[r]^{u_1} \ar[d]_{u_2} \ar@{.>}[dr]_{a_d} & A \ar[dr]^{\pi_E^d} & \\
-	A \ar[dr]_{\pi_E^d} & U_d \ar[r]^{u_1^d} \ar[d]_{u_2^d}& A_d \ar[d]^{q_d^\star \circ s_d} \\
-	& A_i  \ar[r]_{q_d^\star \circ s_d}& Q_d^\star
-}
-\end{minipage}
-
-	By the universal property of limits, we have that \- $m^\star\circ q^\star \circ t \circ u_1 = m^\star \circ q^\star \circ t \circ u_2$.
-Since $m$ is mono we deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, hence the claim.
+	and so we conclude that $q^\star_D(t_D(a_D(e)))=q^\star_D(t_D(a_D(e')))$. Thus $a_D(e)$ and $a_D(e')$ are $q_D$-joined and we can conclude by \Cref{lem:elimc}.
 \end{proof}
@@
 \end{minipage}
-\begin{proof}\label{proof:epo}
-	Let $\mathcal{P} $ be $(A, B, C, s, t, q)$ and let $(K_i, \pi_i^1, \pi_i^2)$ be the kernel pair of $q_i^\star \circ s_i$, for $i\in \{1, 2, 3\}$.
-Let also $(U, u_1, u_2)$ be the kernel pair of $q^\star \circ s$.
-
-	\vspace{-.3cm}
+\begin{proof}\label{proof:epo} To fix the notation, let $\mathcal{P} $ be $(E, V, Q, s, t, q)$ and, for $i\in \{1, 2, 3\}$ let $\mathcal{G}_i$ be $(E_{i}, V_i, Q_i, s_i, t_i, q_i)$.
+Let, moreover, $(K_i, \pi_i^1, \pi_i^2)$
+	be a kernel pair of $q_i^\star \circ s_i$, again for $i\in \{1, 2, 3\}$. Finally, let $(U, u_1, u_2)$ be the kernel pair of $q^\star \circ s$.
+
 	\noindent
@@
 By hypothesis and \Cref{rem:kleene} its left face is a pullback.
-Moreover its bottom face is not a pushout but it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.
+Its bottom face is not a pushout but it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact}.
+
+		\noindent 
+		\begin{minipage}[l]{.2\linewidth}
+			\xymatrix@R=15pt{K_1\ar[r]_{k_{h_E}}\ar@{>->}[d]_{k_{m_E}}&K_2\ar@{>->}[d]^{k_{n_E}}\\K_3\ar[r]^{k_{z_E}}&U}
+		\end{minipage} \hfill \begin{minipage}[r]{.7\linewidth}
+		\setlength{\parindent}{1.5em}
+			By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout. Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout.
+		\end{minipage}
 	\end{minipage}\hfill 
 	\begin{minipage}[r]{.4\linewidth}
-	\xymatrix@C=10pt@R=2pt{&A_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar@{>->}[dl]_{m_E} && A_2 \ar[dd]^{q_2^\star \circ s_2} \ar@{>.>}[dl]_(.6){n_E} \\ A_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){z_E} & & A \ar[dd]_(.3){q^\star \circ s}\\&{Q_1^\star}\ar[rr]|\hole^(.65){h_Q^\star}\ar@{>->}[dl]_{m_Q^\star} && {Q_2^\star} \ar@{>->}[dl]^{n_Q^\star} \\{Q_3^\star} \ar[rr]^(.65){z_Q^\star} & & Q^\star}	\end{minipage}
-
-	\noindent
-	\begin{minipage}[l]{.2\linewidth}
-		\xymatrix@R=15pt{K_1\ar[r]_{k_{h_E}}\ar@{>->}[d]_{k_{m_E}}&K_2\ar@{>->}[d]^{k_{n_E}}\\K_3\ar[r]^{k_{z_E}}&U}
-	\end{minipage}\hfill
-	\begin{minipage}[r]{.8\linewidth}
-			\setlength{\parindent}{1.5em}
-			By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout. Thus we can apply \Cref{prop:kerset} to deduce that the square on the left is a pushout. 
+	\xymatrix@C=10pt@R=10pt{&E_1\ar[dd]|\hole_(.65){q_1^\star \circ s_1}\ar[rr]^{h_E} \ar@{>->}[dl]_{m_E} && E_2 \ar[dd]^{q_2^\star \circ s_2} \ar@{>->}[dl]_(.6){n_E} \\ E_3 \ar[dd]_{q_3^\star \circ s_3}\ar[rr]^(.7){z_E} & & E \ar[dd]_(.3){q^\star \circ s}\\&{Q_1^\star}\ar[rr]|\hole^(.65){h_Q^\star}\ar@{>->}[dl]_(.4){m_Q^\star} && {Q_2^\star} \ar@{>->}[dl]^{n_Q^\star} \\{Q_3^\star} \ar[rr]^(.65){z_Q^\star} & & Q^\star}	\end{minipage}
+
 		 	By computing we obtain
-	\end{minipage}
 \vspace{-.3cm}
 	\begin{align*}
-		q^\star \circ t \circ u_1 \circ f_n &= q^\star \circ t \circ n_E \circ \pi_2^1 = n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^1 = n_C^\star \circ q_2^\star \circ s_2 \circ \pi_2^2 =q^\star \circ t \circ u_2 \circ f_n \\
-		q^\star \circ t \circ u_1 \circ f_k &= q^\star \circ t \circ k_E \circ \pi_3^1 = k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^1 = k_C^\star \circ q_3^\star \circ s_3 \circ \pi_3^2 =q^\star \circ t \circ u_2 \circ f_k
+		&q^\star \circ t \circ u_1 \circ k_{n_E} = q^\star \circ t \circ n_E \circ \pi_2^1 =q^\star \circ n_V\circ t_2\circ \pi^1_2=
+		 n_Q^\star \circ q_2^\star \circ t_2 \circ \pi_2^1 \\= &n_Q^\star \circ q_2^\star \circ t_2 \circ \pi_2^2 =q^\star \circ n_V\circ t_2\circ \pi^2_2= q^\star \circ t \circ n_E \circ \pi_2^2 = q^\star \circ t \circ u_1 \circ k_{n_E}\\
+		 &q^\star \circ t \circ u_1 \circ k_{z_E} = q^\star \circ t \circ z_E \circ \pi_3^1 =q^\star \circ n_V\circ t_3\circ \pi^1_3=
+		 z_Q^\star \circ q_3^\star \circ t_3 \circ \pi_3^1 \\= &z_Q^\star \circ q_3^\star \circ t_3 \circ \pi_3^2 =q^\star \circ z_V\circ t_3\circ \pi^3_2= q^\star \circ t \circ z_E \circ \pi_3^2 = q^\star \circ t \circ u_1 \circ k_{z_E}
 	\end{align*}
-	We can therefore deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the claim follows.
+
+	We can therefore deduce that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the claim now follows from \Cref{prop:eh}.
 \end{proof}
 
-\iffalse 
-\limt*
-\begin{proof}\label{proof:tlim}
-Let $F\colon \D\to \eg$ be a diagram of one of the shapes mentioned in the statement.
-Let $((\mathcal{L}, l), \{\pi_d\}_{d\in \D})$ be a limiting cone for $k_\Sigma \circ F$.
-By \Cref{lim}, \Cref{prop:term}, and \Cref{proof:elim} we know that $\mathcal{L}$ is an e-termgraph and we can conclude.
+\fh*
+\begin{proof}\label{proof:fh} We proceed more or less as in the proof of \Cref{prop:eh}. Define
+	\[A_E:=\{(e,e')\in E \mid q^\star(s(e))=q^\star(s(e')) \text{ and } a(e)=a(e')\}\] 
+	If $p_1, p_2\colon A_E\rightrightarrows E$ are the two projections, we know that $(A_E, p_1, p_1)$ is a kernel pair for $(q^\star \circ s, a)$.
+Thus there exists an isomorphism $\phi \colon A_E\to A$ such that
+	\[\pi^A_1\circ \phi =p_1 \qquad \pi^A_2\circ \phi = p_2\]
+
+	\smallskip \noindent
+	$(1\Rightarrow 2)$ By hypothesis $(a,b,c)$ is an e-hypergraph, then the components of $\phi^{-1}(x)$ are $q$-joined for every $x\in A$ and so:
+	\[q^\star(t_{\mathcal{H}}(\pi^A_1(x)))=q^\star(t_{\mathcal{H}}(p_1(\phi^{-1}(x))))=q^\star(t_{\mathcal{H}}(p_2(\phi^{-1}(x))))=q^\star(t_{\mathcal{H}}(\pi^A_2(x)))\]
+	\smallskip \noindent $(2\Rightarrow 3)$ This follows at once from the definition of kernel pairs.
+
+	\smallskip \noindent $(3\Rightarrow 1)$ Let $e, e'$ be hyperedges such that $q^\star(s(e))=q^\star(s(e'))$ and $a(e)=a(e0)$. Then $(e,e')$ belongs to $A_E$ and thus we have:
+	\begin{align*}
+		&q^\star(t(e))=q^\star(t(p_1(e, e')))=q^\star(t(\pi^A_1(\phi(e,e'))))=q^\star(t(\pi^B_1(k(\phi(e,e')))))\\=&q^\star(t(\pi^B_2(k(\phi(e,e')))))=q^\star(t(\pi^A_2(\phi(e,e'))))=q^\star(t(p_2(e, e')))=q^\star(t(e'))
+	\end{align*}
+allowing us to conclude. \qedhere 
 \end{proof}
-\fi
+
+\varie*
+
+\begin{proof}\label{proof:varie}
+	Let us examine connected limits and pushouts separately.
+	\begin{enumerate}
+		\item Let $F\colon \D\to \eggl$ be a connected diagram.
+Let $F(D)$ be $(f_D,g_D,h_D)\colon \mathcal{H}_D\to \mathcal{G}$, with $ \mathcal{H}_D:=(E_D, V_D, Q_D, s_D, t_D, q_D)$.
+Suppose that $((f,g,h), \{(a_D, b_D, c_D)\}_{D\in \D})$ is a limiting cone for $E_{\mathcal{G}}\circ F$ with $(f,g,h)\colon \mathcal{L}\to \mathcal{G}$.
+If we show that $(f,g,h)$ is a labelled e-hypergraph we are done.
+Let $e, e'\in E_{\mathcal{L}}$ be such that
+		\[q^\star_{\mathcal{L}}(s_{\mathcal{L}}(e))=q^\star_{\mathcal{L}}(s_{\mathcal{L}}(e')) \qquad f(e)=f(e')\]
+
+		 Thus for every $D\in \D$ we have:
+		\begin{align*}
+			&q^\star_D(s_D(a_D(e)))=q^\star(b^\star_D(s_{\mathcal{L}}(e)))=c^\star_D(q_{\mathcal{L}}(s_{\mathcal{L}}(e)))\\=&c^\star_D(q_{\mathcal{L}}(s_{\mathcal{L}}(e')))=c^\star_D(q_{\mathcal{L}}(s_{\mathcal{L}}(e')))=q^\star(b^\star_D(s_{\mathcal{L}}(e')))=q^\star_D(s_D(a_D(e')))\\
+			&f_D(a_D(e)) = f(e)=f(e')= f_D(a_D(e'))
+		\end{align*}
+
+		Thus $a_D(e)$ and $a_D(e')$ are $q_D$-joined and we can conclude by \Cref{lem:elimc}.
+		\item We are going to adapt the argument exploited in the proof of \Cref{lem:epo}.
+
+		\noindent 
+		\begin{minipage}[l]{.73\linewidth}
+				Suppose that the square on the right is a pushout in $\hyp_{\eq, \mathcal{G}}$ and that $m$ is a mono in $\pbe_{\mathcal{G}}$ and, for $i\in \{1,2,3\}$, $(a_i,b_i,c_i)\colon \mathcal{G}_i\to \mathcal{G}$ is a labelled e-hypergraph.
+We want to show that $(a,b,c)\colon \mathcal{P}\to \mathcal{G}$ is in $\eggl$ too.
+		\end{minipage}\hfill 
+		\begin{minipage}[r]{.15\linewidth}
+			\xymatrix@R=10pt@C=15pt{(a_1, b_1, c_1) \ar[r]_{h}\ar@{>->}[d]_{m}&(a_2, b_2, c_2)\ar[d]^{n}\\(a_3, b_3, c_3)\ar[r]^{z}&(a,b, c)}
+		\end{minipage}
+
+		To fix the notation, let $\mathcal{P} $ be $(E, V, Q, s, t, q)$ and, for $i\in \{1, 2, 3\}$ let $\mathcal{G}_i$ be $(E_{i}, V_i, Q_i, s_i, t_i, q_i)$.  Let, moreover, $(K_i, \pi_i^1, \pi_i^2)$
+		be a kernel pair of $(q_i^\star \circ s_i, a_i)$, again for $i\in \{1, 2, 3\}$. Finally, let $(U, u_1, u_2)$ be a kernel pair of $(q^\star \circ s, a)$.
+
+		\noindent
+		\begin{minipage}[l]{.4\linewidth}
+			\setlength{\parindent}{1.5em}
+			Consider the cube on the right.
+By hypothesis and \Cref{rem:kleene} its left face is a pullback.
+Moreover its bottom face is not a pushout but it is still a pullback by the first point of \Cref{prop:regmono} and the third one of \Cref{prop:fact} and by the fact that, since limits commute with limits,  $(-)\times E_{\mathcal{G}}$  preserves pullbacks.
+		\end{minipage}\hfill 
+		\begin{minipage}[r]{.5\linewidth}
+			\xymatrix@C=20pt@R=10pt{&E_1\ar[dd]|\hole_(.65){(q_1^\star \circ s_1, a_1)}\ar[rr]^{h_E} \ar@{>->}[dl]_{m_E} && E_2 \ar[dd]_{(q_2^\star \circ s_2, a_2)} \ar@{>->}[dl]_(.6){n_E} \\ E_3 \ar[dd]_{(q_3^\star \circ s_3, a_3)}\ar[rr]^(.7){z_E} & & E \ar[dd]_(.3){(q^\star \circ s, a)}\\&{Q_1^\star}\times E_{\mathcal{G}}\ar[rr]|\hole^(.66){h_Q^\star\times \id{E_{\mathcal{G}}}}\ar@{>->}[dl]_(.55){m_Q^\star\times \id{E_{\mathcal{G}}}} && {Q_2^\star\times E_{\mathcal{G}}} \ar@{>->}[dl]^{n_Q^\star\times \id{E_{\mathcal{G}}}} \\{Q_3^\star}\times E_{\mathcal{G}} \ar[rr]^(.5){z_Q^\star\times \id{E_{\mathcal{G}}}} & & Q^\star\times E_{\mathcal{G}}}	\end{minipage}
+
+		\noindent 
+		\begin{minipage}[l]{.2\linewidth}
+			\xymatrix@R=15pt@C=30pt{K_1\ar[r]_{k_{h_E}}\ar@{>->}[d]_{k_{m_E}}&K_2\ar@{>->}[d]^{k_{n_E}}\\K_3\ar[r]^{k_{z_E}}&U}
+		\end{minipage} \hfill \begin{minipage}[r]{.7\linewidth}
+			\setlength{\parindent}{1.5em}
+			By hypothesis and the first point of \Cref{prop:eqhyp_complete} the top face is a pushout. Thus we can apply \Cref{prop:kerset} to deduce again that the square on the left is a pushout.
+		\end{minipage}
+
+		By computing we obtain
+		\vspace{-.3cm}
+		\begin{align*}
+		&q^\star \circ t \circ u_1 \circ k_{n_E} = q^\star \circ t \circ n_E \circ \pi_2^1 =q^\star \circ n_V\circ t_2\circ \pi^1_2=
+		n_Q^\star \circ q_2^\star \circ t_2 \circ \pi_2^1 \\= &n_Q^\star \circ q_2^\star \circ t_2 \circ \pi_2^2 =q^\star \circ n_V\circ t_2\circ \pi^2_2= q^\star \circ t \circ n_E \circ \pi_2^2 = q^\star \circ t \circ u_1 \circ k_{n_E}\\
+		&q^\star \circ t \circ u_1 \circ k_{z_E} = q^\star \circ t \circ z_E \circ \pi_3^1 =q^\star \circ n_V\circ t_3\circ \pi^1_3=
+		z_Q^\star \circ q_3^\star \circ t_3 \circ \pi_3^1 \\= &z_Q^\star \circ q_3^\star \circ t_3 \circ \pi_3^2 =q^\star \circ z_V\circ t_3\circ \pi^3_2= q^\star \circ t \circ z_E \circ \pi_3^2 = q^\star \circ t \circ u_1 \circ k_{z_E}
+	\end{align*}
+
+		From these identities we get that $q^\star \circ t \circ u_1 = q^\star \circ t \circ u_2$, and the claim follows from \Cref{prop:eh}. \qedhere 
+	\end{enumerate}
+\end{proof}
 

### 2025-09-27 jlamp/jlamp.tex
minima

@@
 
-Let us start with the case of general hypergraphs. These were introduced in~\cite{concur2006}, even if no general consideration about their structure as a category was proved, and adhesivity, 
+Let us start with the case of general hypergraphs. These were introduced in~\cite{concur2006}, even if no general consideration about their structure as a category was provided, and adhesivity, 
 which is the main focus here, was yet to be presented to the world.
@@
 \begin{defi}
-	Let $\mathcal{G}$ be an hypergraph with equivalence, the category $\EqHyps$ of \emph{labelled hypergraph with equivalence}  is $\EqHyp/\mathcal{G}$.
+	Let $\mathcal{G}$ be an hypergraph with equivalence. The category $\EqHyps$ of hypergraph with equivalence \emph{labelled by $\mathcal{G}$}  is $\EqHyp/\mathcal{G}$.
 \end{defi}
 
-\begin{rem} The equivalence relation on the  nodes of the labelling hypergraph put constraints on the possible relations on the labelled hypergraphs.
-Indeed, consider the following hypergraphs with equivalences $\mathcal{G}$ and $\mathcal{H}$.
-
+\begin{rem} The equivalence relation on the  nodes of the labelling hypergraph put constraints on the relations between the labelled hypergraphs.
+Consider the following hypergraphs with equivalences $\mathcal{G}$ and $\mathcal{H}$.
+
+\smallskip
 \noindent
@@
 
- For both cases we have:
+ For both cases we have
 \[ f(q_{\mathcal{H}}(w))=v \neq w =q_{\mathcal{G}}(w)=q_\mathcal{G}(\id{V_{\mathcal{G}}}(w)) \qquad  g(q_{\mathcal{H}}(v))=w \neq v =q_{\mathcal{G}}(v)=q_\mathcal{G}(\id{V_{\mathcal{G}}}(v))  \]
 
-	Intuitively, labelling with $\mathcal{G}$ force us to keep all the sorts (i.e.~the labellings of the nodes) distinguished, while labelling with $\mathcal{H}$ allows us to merge different sorts.
+	Intuitively, labelling with $\mathcal{G}$ force us to keep all the sorts (i.e.~the labelling of the nodes) distinguished, while labelling with $\mathcal{H}$ allows us to merge different sorts.
 \end{rem}
@@
 \begin{defi}Let $\mathcal{G}$ be an hypergraph and $(\mathcal{H},(f,g))$ a labelled hypergraph with equivalence.
-We say that $(\mathcal{H},(f,g))$ is a \emph{left-monogamous} (resp.~\emph{separated, pruned}) $\mathcal{G}$-hypergraph if $\mathcal{H}$ is left-monogamous (resp.~separated, pruned).
+We say that $(\mathcal{H},(f,g))$ is a \emph{left-monogamous} (resp.~\emph{separated, pruned}) $\mathcal{G}$-hypergraph with equivalence if $\mathcal{H}$ is left-monogamous (resp.~separated, pruned).
 
@@
 
- In particular, the previous  proposition, together with Lemmas \ref{lem:equ}, \ref{lem:coequ}, \ref{colim} and \Cref{lim}, yields the following
+ In particular, the previous proposition, together with Lemmas \ref{lem:equ}, \ref{lem:coequ}, \ref{colim} and \Cref{lim}, yields the following result.
 
@@
 \begin{restatable}{prop}{eh}\label{prop:eh}
-Consider an hypergraph with equivalence $\mathcal{G} = (E, V, Q, s, t, q)$ and let $(A, \pi^A_1, \pi^A_2)$, $(B, \pi^B_1, \pi^B_2)$ be kernel pairs for, respectively, $q^\star\circ s$ and $q^\star\circ t$.
-Then the following are equivalent:
+Let $\mathcal{G} = (E, V, Q, s, t, q)$ be an hypergraph with equivalence and $(A, \pi^A_1, \pi^A_2)$, $(B, \pi^B_1, \pi^B_2)$ kernel pairs for, respectively, $q^\star\circ s$ and $q^\star\circ t$.
+Then the following facts are equivalent
 \begin{enumerate}
@@
 Using \Cref{lem:pbmono} and \Cref{lem:epo} we can further deduce that it is stable under pushouts.
-Then \Cref{thm:slice-functors} and \Cref{cor:eqade} yield the following.
+Then \Cref{thm:slice-functors} and \Cref{cor:eqade} yield the following result.
 
@@
 
-\begin{defi}We will define $\elm$, $\eps$ as the full subcategories of $\egg$ given by those e-hypergraphs which are, respectively, left-monogamous and pruned and separated.
+\begin{defi}We will define $\elm$ and $\eps$ as the full subcategories of $\egg$ given by those e-hypergraphs that are, respectively, left-monogamous and pruned and separated.
 We will denote by $M_{\mathsf{e}}$ and by $S_{\mathsf{e}}$ the corresponding functors.
@@
 
-We begin by providing an equivalent characterization to labelled e-hypergraphs (see \Cref{proof:fh} for details).
+\smallskip
+We now provide an equivalent characterisation to labelled e-hypergraphs (see \Cref{proof:fh} for details).
 
 \begin{restatable}{lem}{fh}\label{lem:fh}
-Let $(a,b,c)\colon \mathcal{H}\to \mathcal{G}$ be an object of $\hyp_{\eq, \mathcal{G}}$ and let $(A, \pi^A_1, \pi^A_2)$, $(B, \pi^B_1, \pi^B_2)$ be kernel pairs for, respectively, $(q^\star\circ s_{\mathcal{H}}, a),(q^\star\circ t_{\mathcal{H}}, a)\colon E_{\mathcal{H}}\to Q_{\mathcal{H}}\times E_{\mathcal{G}}$.
-Then the following are equivalent:
+Let $(a,b,c)\colon \mathcal{H}\to \mathcal{G}$ be an object of $\hyp_{\eq, \mathcal{G}}$ and $(A, \pi^A_1, \pi^A_2)$, $(B, \pi^B_1, \pi^B_2)$ kernel pairs for, respectively, $(q^\star\circ s_{\mathcal{H}}, a),(q^\star\circ t_{\mathcal{H}}, a)\colon E_{\mathcal{H}}\to Q_{\mathcal{H}}\times E_{\mathcal{G}}$.
+Then the following are equivalent
 \begin{enumerate}
@@
 \begin{restatable}{lem}{varie}\label{prop:varie}
-	Let $\mathcal{G}$ be an hypergraph with equivalence, then $\eggl$ is closed in $\hyp_{\eq, \mathcal{G}}$ under connected limits and pushouts alongs arrows in $\pbe_\mathcal{G}$, where $\pbe_\mathcal{G}$ is the class of morphisms in $\eggl$ whose image through $E_\mathcal{G}$ is in $\pbc_\mathcal{G}$.
+	Let $\mathcal{G}$ be an hypergraph with equivalence.
+Then $\eggl$ is closed in $\hyp_{\eq, \mathcal{G}}$ under connected limits and pushouts alongs arrows in $\pbe_\mathcal{G}$, where $\pbe_\mathcal{G}$ is the class of morphisms in $\eggl$ whose image through $E_\mathcal{G}$ is in $\pbc_\mathcal{G}$.
 \end{restatable}
@@
 
-Putting together \Cref{cor:eti} with \Cref{prop:varie} we get the following.
+Putting together \Cref{cor:eti} with \Cref{prop:varie} we get the following result.
 
@@
 %
-Intuitively, the e-term graph obtained after the application of the rule seem to represent a recursive term such 
+Intuitively, the e-term graph obtained after the application of the rule seems to represent a recursive term such 
 as $rec_x. 1 \times x$, highlighting the difficulty of extracting a term representation out of an e-term graph.
@@
 as the right-hand side itself.
-Indeed, consider again the rule $x / x \to 1$: once $1$ has been added once to the equivalence class of $x / x$, it is not necessary to
-keep on adding it, since e.g. the two pictures below intuitively represent the same EGG
-\[xxx\]
+If you consider e.g. the rule $x / x \to 1$, once $1$ has been added once to the equivalence class of $x / x$, it is not necessary to
+keep on adding it.
+% since e.g. the two pictures below intuitively represent the same EGG
+%\[xxx\]
 %
@@
 %
-In fact, for both proposals the key intuition is  to use string diagrams to represents term graphs. We adopted a
-more down-to-earth approach by equipping
+%In fact, for both proposals the key intuition is  to use string diagrams to represents term graphs. 
+We adopted a more down-to-earth approach by equipping
 concretely the nodes of a term graph with an equivalence relation, thus directly corresponding to the original presentation~\cite{DetlefsNS05},
@@
 $\Set$. At the same time, we both consider the DPO approach for rewriting, even if only our solution guarantees that the resulting category
-is actually $\mathcal{M}$-adhesive, thus allowing to exploit all the features of the framework
+is $\mathcal{M}$-adhesive, thus allowing to exploit the features of the framework
 as they hold for DPO graph transformation.  Moreover, our construction is technically simpler, which facilitates its practical application 
